### 2013-03-17 writedown/npt-neq/alanine.tex
add tex files

% \documentclass[aip,jcp,preprint,unsortedaddress,a4paper,onecolum]{revtex4-1}
\documentclass[aip,jcp,a4paper,reprint,onecolumn]{revtex4-1}
% \documentclass[aps,pre,twocolumn]{revtex4-1}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}

\usepackage[fleqn]{amsmath}
\usepackage{amssymb}
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{tabularx}
\usepackage{algorithm}
\usepackage{algorithmic}

\makeatletter
\makeatother

\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{blue} #1}}
\newcommand{\greenc}[1]{{\color{green} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\dd}[1]{\textsf{#1}}

\newcommand{\AT}{{\textrm{{AT}}}}
\newcommand{\EX}{{\textrm{EX}}}
\newcommand{\ex}{{\textrm{ex}}}
\newcommand{\CG}{{\textrm{CG}}}
\newcommand{\HY}{{\Delta}}
\newcommand{\rdf}{{\textrm{rdf}}}

\begin{document}

\title{Report: the non-equilibrium molecular dynamics simulation}
\author{Han Wang}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\author{Christof Sch\"utte}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\author{Luigi Delle Site}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}

\begin{abstract}
\end{abstract}

\maketitle

\newpage

\section{System set up}

Let's consider an infinitely large NVE system (here we call it
"universe"). Some interesting process is happening in a small subsystem. For
equilibrium phenomena, this subsystem is the usually considered as NVT
(or NPT, $\mu$VT, depends on how the question is raised) system.
In simulations, we only simulate the subsystem and
use the thermostat to mimic the embedding to the universe.
For non-equilibrium simulation, the physical meaning of directly applying
a thermostat designed for generating equilibrium ensemble is still
not clear. To make the non-equilibrium feasible, we assume the
non-equilibrium process is \emph{local}, i.e. the non-equilibrium perturbation
of the system happens only locally, and the rest of the system
stays the unperturbed (usually assumed under ambient conditions).
This provides us the possibility of simulating only the small subsystem
of the universe: We can simulate only subsystem by providing proper
boundary condition for it, so that it behaves as if it were embeded into
the universe.

\subsection{The water structure around methane under impluse }
In this study, we firstly consider the system of a methane molecule solvated
in the liquid water environment. A local density perturbation is implemented
by applying an impluse  in a shell surronding methane, see Fig.~\ref{fig:tmp1}.
% As far as we concerned, the situation is: we truncate the universe to the
% subsystem, and provide proper boundary condition for this
% subsystem.
Here we denote the size of this subsystem by $R_{\ex}$.
Notice this subsystem is simulated by the Newtonian
dynamics. If the size of the
subsystem is large enough so that the perturbation is
small enough when it travels to the boundary of the subsystem, then a
trivial boundary condition would be: coupling the system to a boundary
layer equilibriated by the thermostat (and barostat or particle reservior),
which mimics the infinitely large equilibrium universe.

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{fig/kick.eps}
  \caption{Schematic plot of the density perturbation.}
  \label{fig:tmp1}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{fig/thermostat.eps}
  \caption{Schematic plot of the truncated non-equilibrium subsystem.
    The white part is the subsystem and the gray part is the boundary
    condition, implemented by the thermostat and barostat mimicing
    the infinitely large universe.}
  \label{fig:tmp2}
\end{figure}

\subsection{Alanine dipeptide under electric field}

We study the response of the configuration of the alanine dipeptide
with respect to a turning on electric field. The direction of this field
is along the $x$ dirction and the magnitude with respect to time is plotted
in Fig.~\ref{fig:tmp3}. From $t=0$ to $t=t_{\textrm{init}}$, the strength
of the field grows linearly, while after $t=t_{\textrm{init}}$, the strength
is kept constant at $E_{\textrm{max}}$. 
\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
  \caption{The maganitude of the external electric field as
    a function of time.}
  \label{fig:tmp3}
\end{figure}
The size of the system is $2.67\times 2.67\times 2.67\,
\textsf{nm}^3$, with one alanine dipeptide solved in 644 TIP3P water
molecules. Firstly, an equilibrium simulation of 100~\textsf{nm} was
performed, along which configurations were taken every
5~\textsf{ps}. They server as starting point of the branching
trajectories. The time step was $\Delta t = 0.002~\textsf{ps}$. The
short-range interaction was switched from $0.8$ to $1.0~\textsf{nm}$.
An energy conserving PME method was applied. Langvin thermostat was
coupled to the system, with a time-scale of $\tau = 0.5~\textsf{ps}$.
On each branching trajectory, $R_{\textrm{ex}}$ was chosen to be
$1.0$~\textsf{nm}, which means that a Langvin thermostat ($\tau =
0.1~\textsf{ps}$) was applied to water molecules that were more than
$1.0$~\textsf{nm} away from the center of the simulation box. In
addition, a Parrinello-Rahman barostat was couple to the system with a
time-scale of $\tau_{\textrm{P}} = 2.0~\textsf{ps}$. To easy the
analysis, the conformation of the alanine dipeptide is projected on
the $\psi$--$\phi$ plane, as shown in Fig.~\ref{fig:tmp4}. The
equilibrium distribution of the conformation on the $\psi$--$\phi$
plane is given in the Left plot of Fig.~\ref{fig:tmp4}.  It is clear
the conformations are populated in several clusters that are called
``metastable states'' in this research. For a clearer definition, we
manually devide the $\psi$--$\phi$ plane into 5 subregions. $A_1$ and $A_2$ are
corresponding to the alpha helix conformation. $B_1$ and $B_2$ are corresponding
to beta sheet conformation. $C$ is corresponding to ill-folding.\\
\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{fig.ala/ext.mode1.100.Ex.01.00.t1200ps/fig-begin-1.eps}
  \includegraphics[width=0.45\textwidth]{fig.ala/ext.mode1.100.Ex.01.00.t1200ps/fig-end-1.eps}
  \caption{The population of different metastable state. Left: the equilibrium state at $t=0$~\textsf{ps}. Right: The non-equilibrium stady state at $t=1200$~\textsf{ps}. The darker color indicates larger population on the $\psi$--$\phi$ phase space.}
  \label{fig:tmp4}
\end{figure}

For all testing cases, the maximum strength of the electric field
$E_{\textrm{max}}$ is chosen to be 1~\textsf{V/nm}.  Three values of
$t_{\textrm{init}}$ (10~\textsf{ps}, 50~\textsf{ps} and
100~\textsf{ps}) are chosen to study the response of the system to the
external electric field perturbation. The result is given in
Fig.~\ref{fig:tmp5}.  No matter how fast is the electric field turned
on, the beta sheet configuration, which presents at the beginning,
fades away as the system relaxes to the new equilibrium. The
population of alpha helix $A_1$ configuration grows from 45\% to 70\%.
alpha helix $A_2$  does not change a lot under the electric field.
The ill-folding configuration $C$ noticably grows from 0\% to 20\%.
Clearly two time-scales of relaxation are observed.  For
configurations $A_2$ and $B_2$, the relaxations are very fast and
comparable to $t_{\textrm{init}}$. For configurations $A_1$, $B_1$ and
$C$, the time-scales of relaxation are roughly 600~\textsf{ps}.
\begin{figure}
  \centering
  \includegraphics[]{fig.ala/fig-meta.eps}
  \caption{The populations of the metastable sets as a function of time.}
  \label{fig:tmp5}
\end{figure}

\end{document}

### 2013-03-17 writedown/npt-neq/main.tex
add tex files

--- 2013-03-17 writedown/npt-neq/alanine.tex
@@
 
-Let's consider an infinitely large NVE system (here we call it
-"universe"). Some interesting process is happening in a small subsystem. For
-equilibrium phenomena, this subsystem is the usually considered as NVT
-(or NPT, $\mu$VT, depends on how the question is raised) system.
-In simulations, we only simulate the subsystem and
-use the thermostat to mimic the embedding to the universe.
-For non-equilibrium simulation, the physical meaning of directly applying
-a thermostat designed for generating equilibrium ensemble is still
-not clear. To make the non-equilibrium feasible, we assume the
-non-equilibrium process is \emph{local}, i.e. the non-equilibrium perturbation
-of the system happens only locally, and the rest of the system
-stays the unperturbed (usually assumed under ambient conditions).
-This provides us the possibility of simulating only the small subsystem
-of the universe: We can simulate only subsystem by providing proper
-boundary condition for it, so that it behaves as if it were embeded into
-the universe.
-
-\subsection{The water structure around methane under impluse }
-In this study, we firstly consider the system of a methane molecule solvated
-in the liquid water environment. A local density perturbation is implemented
-by applying an impluse  in a shell surronding methane, see Fig.~\ref{fig:tmp1}.
-% As far as we concerned, the situation is: we truncate the universe to the
-% subsystem, and provide proper boundary condition for this
-% subsystem.
-Here we denote the size of this subsystem by $R_{\ex}$.
-Notice this subsystem is simulated by the Newtonian
-dynamics. If the size of the
-subsystem is large enough so that the perturbation is
-small enough when it travels to the boundary of the subsystem, then a
-trivial boundary condition would be: coupling the system to a boundary
-layer equilibriated by the thermostat (and barostat or particle reservior),
-which mimics the infinitely large equilibrium universe.
-
 \begin{figure}
@@
 \end{figure}
+
+Let's consider an infinitely large NVE system (here we call it
+"universe"). Some interesting process is happening in a small subsystem. For
+equilibrium phenomena, this subsystem is the usually considered as NVT
+(or NPT, $\mu$VT) system.
+In simulations, we ONLY simulate the subsystem and
+use the thermostat to mimic the embedding to the universe.
 
@@
 
-\subsection{Alanine dipeptide under electric field}
+% If some non-equilibrium perturbation is going on in the subsystem,
+In this study, we consider the system of a methane molecule solvated
+in the liquid water environment. A local density perturbation is implemented
+by applying an impluse  in a shell surronding methane, see Fig.~\ref{fig:tmp1}.
+As far as we concerned, the situation is: we truncate the universe to the
+subsystem, and provide proper boundary condition for this
+subsystem.
+Here we denote the size of this subsystem by $R_{\ex}$.
+Notice this subsystem is simulated by the Newtonian
+dynamics. If the size of the
+subsystem is large enough so that the perturbation is
+small enough when it travels to the boundary of the subsystem, then a
+trivial boundary condition would be: coupling the system to a boundary
+layer equilibriated by the thermostat (and barostat or particle reservior),
+which mimics the infinitely large equilibrium universe.
 
-We study the response of the configuration of the alanine dipeptide
-with respect to a turning on electric field. The direction of this field
-is along the $x$ dirction and the magnitude with respect to time is plotted
-in Fig.~\ref{fig:tmp3}. From $t=0$ to $t=t_{\textrm{init}}$, the strength
-of the field grows linearly, while after $t=t_{\textrm{init}}$, the strength
-is kept constant at $E_{\textrm{max}}$. 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
-  \caption{The maganitude of the external electric field as
-    a function of time.}
-  \label{fig:tmp3}
-\end{figure}
-The size of the system is $2.67\times 2.67\times 2.67\,
-\textsf{nm}^3$, with one alanine dipeptide solved in 644 TIP3P water
-molecules. Firstly, an equilibrium simulation of 100~\textsf{nm} was
-performed, along which configurations were taken every
-5~\textsf{ps}. They server as starting point of the branching
-trajectories. The time step was $\Delta t = 0.002~\textsf{ps}$. The
-short-range interaction was switched from $0.8$ to $1.0~\textsf{nm}$.
-An energy conserving PME method was applied. Langvin thermostat was
-coupled to the system, with a time-scale of $\tau = 0.5~\textsf{ps}$.
-On each branching trajectory, $R_{\textrm{ex}}$ was chosen to be
-$1.0$~\textsf{nm}, which means that a Langvin thermostat ($\tau =
-0.1~\textsf{ps}$) was applied to water molecules that were more than
-$1.0$~\textsf{nm} away from the center of the simulation box. In
-addition, a Parrinello-Rahman barostat was couple to the system with a
-time-scale of $\tau_{\textrm{P}} = 2.0~\textsf{ps}$. To easy the
-analysis, the conformation of the alanine dipeptide is projected on
-the $\psi$--$\phi$ plane, as shown in Fig.~\ref{fig:tmp4}. The
-equilibrium distribution of the conformation on the $\psi$--$\phi$
-plane is given in the Left plot of Fig.~\ref{fig:tmp4}.  It is clear
-the conformations are populated in several clusters that are called
-``metastable states'' in this research. For a clearer definition, we
-manually devide the $\psi$--$\phi$ plane into 5 subregions. $A_1$ and $A_2$ are
-corresponding to the alpha helix conformation. $B_1$ and $B_2$ are corresponding
-to beta sheet conformation. $C$ is corresponding to ill-folding.\\
-\begin{figure}
-  \centering
-  \includegraphics[width=0.45\textwidth]{fig.ala/ext.mode1.100.Ex.01.00.t1200ps/fig-begin-1.eps}
-  \includegraphics[width=0.45\textwidth]{fig.ala/ext.mode1.100.Ex.01.00.t1200ps/fig-end-1.eps}
-  \caption{The population of different metastable state.
-Left: the equilibrium state at $t=0$~\textsf{ps}.
-Right: The non-equilibrium stady state at $t=1200$~\textsf{ps}.
-The darker color indicates larger population on the $\psi$--$\phi$ phase space.}
-  \label{fig:tmp4}
-\end{figure}
-
-For all testing cases, the maximum strength of the electric field
-$E_{\textrm{max}}$ is chosen to be 1~\textsf{V/nm}.  Three values of
-$t_{\textrm{init}}$ (10~\textsf{ps}, 50~\textsf{ps} and
-100~\textsf{ps}) are chosen to study the response of the system to the
-external electric field perturbation. The result is given in
-Fig.~\ref{fig:tmp5}.  No matter how fast is the electric field turned
-on, the beta sheet configuration, which presents at the beginning,
-fades away as the system relaxes to the new equilibrium. The
-population of alpha helix $A_1$ configuration grows from 45\% to 70\%.
-alpha helix $A_2$  does not change a lot under the electric field.
-The ill-folding configuration $C$ noticably grows from 0\% to 20\%.
-Clearly two time-scales of relaxation are observed.  For
-configurations $A_2$ and $B_2$, the relaxations are very fast and
-comparable to $t_{\textrm{init}}$. For configurations $A_1$, $B_1$ and
-$C$, the time-scales of relaxation are roughly 600~\textsf{ps}.
-\begin{figure}
-  \centering
-  \includegraphics[]{fig.ala/fig-meta.eps}
-  \caption{The populations of the metastable sets as a function of time.}
-  \label{fig:tmp5}
-\end{figure}
+The simulation result of the universe is important
+for us, because it servers as the reference of all testing simulations.
+Practically speaking, it is impossible to simulate the infinitely large
+universe. We alway trancate it to a finite size system servered
+by the periodic bounday condition. Therefore, it is important to
+test the convergency of properties of interest with respect to the
+size of the truncated universe.
 

### 2013-03-26 writedown/npt-neq/alanine.tex
back up...

@@
 % \documentclass[aip,jcp,preprint,unsortedaddress,a4paper,onecolum]{revtex4-1}
-\documentclass[aip,jcp,a4paper,reprint,onecolumn]{revtex4-1}
+\documentclass[a4paper,preprint,onecolumn]{revtex4-1}
 % \documentclass[aps,pre,twocolumn]{revtex4-1}
@@
 
-\section{System set up}
+\section{Alanine dipeptide
+  under turning on electric field}
+\begin{figure}
+  \centering
+  \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
+  \caption{The maganitude of the external electric field as
+    a function of time.}
+  \label{fig:tmp3}
+\end{figure}
 
-Let's consider an infinitely large NVE system (here we call it
-"universe"). Some interesting process is happening in a small subsystem. For
-equilibrium phenomena, this subsystem is the usually considered as NVT
-(or NPT, $\mu$VT, depends on how the question is raised) system.
-In simulations, we only simulate the subsystem and
-use the thermostat to mimic the embedding to the universe.
-For non-equilibrium simulation, the physical meaning of directly applying
-a thermostat designed for generating equilibrium ensemble is still
-not clear. To make the non-equilibrium feasible, we assume the
-non-equilibrium process is \emph{local}, i.e. the non-equilibrium perturbation
-of the system happens only locally, and the rest of the system
-stays the unperturbed (usually assumed under ambient conditions).
-This provides us the possibility of simulating only the small subsystem
-of the universe: We can simulate only subsystem by providing proper
-boundary condition for it, so that it behaves as if it were embeded into
-the universe.
-
-\subsection{The water structure around methane under impluse }
-In this study, we firstly consider the system of a methane molecule solvated
-in the liquid water environment. A local density perturbation is implemented
-by applying an impluse  in a shell surronding methane, see Fig.~\ref{fig:tmp1}.
-% As far as we concerned, the situation is: we truncate the universe to the
-% subsystem, and provide proper boundary condition for this
-% subsystem.
-Here we denote the size of this subsystem by $R_{\ex}$.
-Notice this subsystem is simulated by the Newtonian
-dynamics. If the size of the
-subsystem is large enough so that the perturbation is
-small enough when it travels to the boundary of the subsystem, then a
-trivial boundary condition would be: coupling the system to a boundary
-layer equilibriated by the thermostat (and barostat or particle reservior),
-which mimics the infinitely large equilibrium universe.
+We study the response of the configuration of the alanine dipeptide
+with respect to a turning on electric field. The direction of this
+field is along the $x$ dirction and the magnitude with respect to time
+is plotted in Fig.~\ref{fig:tmp3}. From $t=0$ to
+$t=t_{\textrm{init}}$, the strength of the field grows linearly, while
+after $t=t_{\textrm{init}}$, the strength is kept constant at
+$E_{\textrm{max}}$.  The size of the system is $2.67\times 2.67\times
+2.67\, \textsf{nm}^3$, with one alanine dipeptide solved in 644 TIP3P
+water molecules. Firstly, an equilibrium NVT simulation of
+100~\textsf{nm} was performed with a Langvin thermostat (time-scale
+$\tau_T = 0.5~\textsf{ps}$) coupled to the system for constant
+temperature.  Along the trajectory, configurations were taken every
+5~\textsf{ps}.  They server as starting point of the branching
+trajectories. The branching trajectories were integrated by the
+Leap-frog scheme without any temperature and pressure control.  The
+time step was $\Delta t = 0.002~\textsf{ps}$. The short-range
+interaction was smoothed from $0.8$ to $1.0~\textsf{nm}$ by the
+``switch'' method provided by Gromacs.  An energy conserving PME
+method was applied to calculate the electorstatic interaction in this
+periodic system.  On each branching trajectory, to easy the analysis,
+the conformation of the alanine dipeptide is projected on the
+$\psi$--$\phi$ plane, as shown in Fig.~\ref{fig:tmp4}. The equilibrium
+distribution of the conformation on the $\psi$--$\phi$ plane is given
+in the Left plot of Fig.~\ref{fig:tmp4}.  It is clear the
+conformations are populated in several clusters that are called
+``metastable states'' in this research. For a clearer definition, we
+manually devide the $\psi$--$\phi$ plane into 5 subregions. $A_1$ and
+$A_2$ are corresponding to the alpha helix conformation. $B_1$ and
+$B_2$ are corresponding
+to beta sheet conformation. $C$ is corresponding to ill-folding.\\
 
@@
   \centering
-  \includegraphics[width=0.3\textwidth]{fig/kick.eps}
-  \caption{Schematic plot of the density perturbation.}
-  \label{fig:tmp1}
+  \includegraphics[width=0.45\textwidth]{fig.ala/ext.mode1.100.Ex.01.00.t1200ps/fig-begin-1.eps}
+  \includegraphics[width=0.45\textwidth]{fig.ala/ext.mode1.100.Ex.01.00.t1200ps/fig-end-1.eps}
+  \caption{The population of different metastable state.
+Left: the equilibrium state at $t=0$~\textsf{ps}.
+Right: The non-equilibrium stady state at $t=1200$~\textsf{ps}, i.e., fully relaxed when the electric field is switched on.
+The darker color indicates larger population on the $\psi$--$\phi$ phase space.}
+  \label{fig:tmp4}
 \end{figure}
 
+For all testing cases, the maximum strength of the electric field
+$E_{\textrm{max}}$ is chosen to be 1~\textsf{V/nm}.  Three values of
+$t_{\textrm{init}}$ (10~\textsf{ps}, 100~\textsf{ps} and
+500~\textsf{ps}) are chosen to study the response of the system to the
+external electric field perturbation. The result is given in
+Fig.~\ref{fig:tmp5}.  No matter how fast is the electric field turned
+on, the beta sheet configuration, which presents at the beginning,
+fades away as the system relaxes to the new equilibrium. The
+population of alpha helix $A_1$ configuration grows from 45\% to 70\%.
+alpha helix $A_2$  does not change a lot under the electric field.
+The ill-folding configuration $C$ noticably grows from 0\% to 20\%.
+\\
+
+In the case of fastly switching on electric field
+($t_{\textrm{init}}=10~\textsf{ps}$), the dynamics of the population
+of the metastable sets shows three different time-scales. (1) From
+$t=0$ to 10~\textsf{ps}, the population of $A_2$ fastly increases,
+while the population of $A_1$ decreases with the same amount, so it is
+reasonable to argue that there is a fast configurational change from
+$A_1$ to $A_2$. Please see, in Fig.~\ref{fig:tmp5}, the green and read
+peak arount $t = 10~\textsf{ps}$. At the same time, the population of
+other metastable sets remains unchanged.  (2), From $t=10$ to
+40~\textsf{ps}, the population of $B_2$ decreases by 0.15, and this
+configuration almost disappers. Interestingly, the population of $A_1$
+increases by the same amount, and the population of $A_2$ goes back to
+the initial value. The populations of $B_1$ and $C$ start increasing
+and decreasing, correspondingly. The speed of these changes are much
+slower than that of $B_2$ and $A_1$.  (3) At the time scale of $t =
+300~\textsf{ps}$, the population of $A_1$, $B_1$ and $C$ converge to
+the non-equilibrium steady state (system with $E(\infty) = 1~\textsf{V/m}$).
+This time is actually thirty times large than when the electric field
+is fully switched on ($t_{\textrm{init}} = 10~\textsf{ps}$). This 
+indicates that the internal time scale of $A_1$, $B_1$ and $C$
+relaxation is around $300~\textsf{ps}$.\\
+
+To further test the dynamics of metastable population, two simulations
+of $t_{\textrm{init}} = 100~\textsf{ps}$ and $t_{\textrm{init}} =
+500~\textsf{ps}$ are performed. The first time scale of $t =
+10~\textsf{ps}$ disappers in both of the testing simulations. In the
+simulation of $t_{\textrm{init}} = 100~\textsf{ps}$, the population of
+$A$, $B_1$ and $C$ converges to the non-equilibrium steady state at
+around $300~\textsf{ps}$. This further verifies internal time scale of
+$A_1$, $B_1$ and $C$ presented in the testing case of
+$t_{\textrm{init}} = 10~\textsf{ps}$.  The dynamics of $B_2$ is
+faster: it decays to zero as fast as the external electric field is
+switched on. In the case of $t_{\textrm{init}} = 500~\textsf{ps}$, the
+growth of the external electric field is slower than the longest
+internal time scale of system, which means that the changes of the
+perturbation to the system is so slow that the system can catch up
+with that. The numerical results show the same story: the relaxation
+of all populations are around $500 \sim 600~\textsf{ps}$.
+\\
+
+% Clearly two time-scales of relaxation are observed.  For
+% configurations $A_2$ and $B_2$, the relaxations are very fast and
+% comparable to $t_{\textrm{init}}$. For configurations $A_1$, $B_1$ and
+% $C$, the time-scales of relaxation are roughly 600~\textsf{ps}.
+\begin{figure}
+  \centering
+  \includegraphics[]{fig.ala/fig-meta.eps}
+  \caption{The populations of the metastable sets as a function of time.
+    The dashed vertical lines indicate the three different time scale of
+  metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
+  \label{fig:tmp5}
+\end{figure}
+
+\section{Testing the effect of the thermostat and barostat}
 \begin{figure}
@@
 
-\subsection{Alanine dipeptide under electric field}
+% \section{System set up}
 
-We study the response of the configuration of the alanine dipeptide
-with respect to a turning on electric field. The direction of this field
-is along the $x$ dirction and the magnitude with respect to time is plotted
-in Fig.~\ref{fig:tmp3}. From $t=0$ to $t=t_{\textrm{init}}$, the strength
-of the field grows linearly, while after $t=t_{\textrm{init}}$, the strength
-is kept constant at $E_{\textrm{max}}$. 
+% $R_{\textrm{ex}}$ was chosen to be
+% $1.0$~\textsf{nm}, which means that a Langvin thermostat ($\tau =
+% 0.1~\textsf{ps}$) was applied to water molecules that were more than
+% $1.0$~\textsf{nm} away from the center of the simulation box. In
+% addition, a Parrinello-Rahman barostat was couple to the system with a
+% time-scale of $\tau_{\textrm{P}} = 2.0~\textsf{ps}$.
+
+Let's consider an infinitely large NVE system (here we call it
+"universe"). Some interesting process is happening in a small
+subsystem. For equilibrium phenomena, this subsystem is the usually
+considered as NVT (or NPT, $\mu$VT, depends on how the question is
+raised) system.  In simulations, we only simulate the subsystem and
+use the thermostat to mimic the embedment into the universe.  For
+non-equilibrium simulation, we also want to simulate only the
+subsystem of interest, but the physical meaning of directly applying a
+thermostat designed for generating equilibrium ensemble is not clear
+to a non-equilibrium process. Moreover, there is no unique way of
+defining how the subsystem is coupled into the universe: It is subject
+to how the perturbation comes into the subsystem, and how the energy
+of the system dissipates into the universe. In the case of swithing on
+electric field system, two limiting senarios are considered by us: (1)
+the subsystem is isolated from the universe. That is to say the we
+study the non-equilibrium behavior of a system, which conserves the
+energy, volume and number of particle, under the turning on electric
+field.
+
+(1), the
+electric field is applied to the whole universe, the correctness of
+considering a subsystem is tested by varying the size of the
+subsystem, and investigating the convergence of the result.
+
+(2), the
+perturbation is applied locally, and the extra energy dissipates into
+the universe infinitely fast. That is to say the subsystem is coupled
+to a thermostat and barostat with infinitely high
+efficiency. Practically, it is impossible to simulation with a
+``infinitely fast'' thermostat and barostat. We locally truncate the
+system with radius $R_{\textrm{ex}} = 1~\textsf{nm}$ (see
+Fig.~\ref{fig:tmp2} for explanation), and couple it to very sufficient
+thermo- and barostat. We use a Langvin thermostat coupled to the
+thermostating region with a time-scale of $\tau_{T} =
+0.1~\textsf{ps}$, and a Parrinello-Rahman barostat with a time-scale
+of $\tau_{P} = 2.0~\textsf{ps}$.
+
+The non-equilibrium steady temperature and pressure of the
+non-thermostated simulation are $330$ K and -500 Bar,
+correspondingly. Those of the thermostated sytem are $300$ K and 1
+Bar, correspondingly. Therefore, we can see from Fig.~\ref{fig:tmp6}
+that the relaxation of the thermostated system is faster than the
+non-thermostated system. The three time-scale of metastable population
+dynamics in the thermostated system is consistent with that of the
+non-thermostated system. This means that thermostating, in this case,
+does not qulitativly change the population dynamics of metastable
+states.
+
 \begin{figure}
   \centering
-  \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
-  \caption{The maganitude of the external electric field as
-    a function of time.}
-  \label{fig:tmp3}
-\end{figure}
-The size of the system is $2.67\times 2.67\times 2.67\,
-\textsf{nm}^3$, with one alanine dipeptide solved in 644 TIP3P water
-molecules. Firstly, an equilibrium simulation of 100~\textsf{nm} was
-performed, along which configurations were taken every
-5~\textsf{ps}. They server as starting point of the branching
-trajectories. The time step was $\Delta t = 0.002~\textsf{ps}$. The
-short-range interaction was switched from $0.8$ to $1.0~\textsf{nm}$.
-An energy conserving PME method was applied. Langvin thermostat was
-coupled to the system, with a time-scale of $\tau = 0.5~\textsf{ps}$.
-On each branching trajectory, $R_{\textrm{ex}}$ was chosen to be
-$1.0$~\textsf{nm}, which means that a Langvin thermostat ($\tau =
-0.1~\textsf{ps}$) was applied to water molecules that were more than
-$1.0$~\textsf{nm} away from the center of the simulation box. In
-addition, a Parrinello-Rahman barostat was couple to the system with a
-time-scale of $\tau_{\textrm{P}} = 2.0~\textsf{ps}$. To easy the
-analysis, the conformation of the alanine dipeptide is projected on
-the $\psi$--$\phi$ plane, as shown in Fig.~\ref{fig:tmp4}. The
-equilibrium distribution of the conformation on the $\psi$--$\phi$
-plane is given in the Left plot of Fig.~\ref{fig:tmp4}.  It is clear
-the conformations are populated in several clusters that are called
-``metastable states'' in this research. For a clearer definition, we
-manually devide the $\psi$--$\phi$ plane into 5 subregions. $A_1$ and $A_2$ are
-corresponding to the alpha helix conformation. $B_1$ and $B_2$ are corresponding
-to beta sheet conformation. $C$ is corresponding to ill-folding.\\
-\begin{figure}
-  \centering
-  \includegraphics[width=0.45\textwidth]{fig.ala/ext.mode1.100.Ex.01.00.t1200ps/fig-begin-1.eps}
-  \includegraphics[width=0.45\textwidth]{fig.ala/ext.mode1.100.Ex.01.00.t1200ps/fig-end-1.eps}
-  \caption{The population of different metastable state.
-Left: the equilibrium state at $t=0$~\textsf{ps}.
-Right: The non-equilibrium stady state at $t=1200$~\textsf{ps}.
-The darker color indicates larger population on the $\psi$--$\phi$ phase space.}
-  \label{fig:tmp4}
+  \includegraphics[]{fig.ala/fig-meta-stat-10.eps}
+  \caption{ Comparison between simulations with and without
+    temperature and pressure control at $t_{\textrm{init}} =
+    10~\textsf{ps}$. The The populations of the metastable sets as a
+    function of time are plotted.  The dashed vertical lines indicate
+    the three different time scale of metastable set population at
+    $t_{\textrm{init}} = 10~\textsf{ps}$.}
+  \label{fig:tmp6}
 \end{figure}
 
-For all testing cases, the maximum strength of the electric field
-$E_{\textrm{max}}$ is chosen to be 1~\textsf{V/nm}.  Three values of
-$t_{\textrm{init}}$ (10~\textsf{ps}, 50~\textsf{ps} and
-100~\textsf{ps}) are chosen to study the response of the system to the
-external electric field perturbation. The result is given in
-Fig.~\ref{fig:tmp5}.  No matter how fast is the electric field turned
-on, the beta sheet configuration, which presents at the beginning,
-fades away as the system relaxes to the new equilibrium. The
-population of alpha helix $A_1$ configuration grows from 45\% to 70\%.
-alpha helix $A_2$  does not change a lot under the electric field.
-The ill-folding configuration $C$ noticably grows from 0\% to 20\%.
-Clearly two time-scales of relaxation are observed.  For
-configurations $A_2$ and $B_2$, the relaxations are very fast and
-comparable to $t_{\textrm{init}}$. For configurations $A_1$, $B_1$ and
-$C$, the time-scales of relaxation are roughly 600~\textsf{ps}.
-\begin{figure}
-  \centering
-  \includegraphics[]{fig.ala/fig-meta.eps}
-  \caption{The populations of the metastable sets as a function of time.}
-  \label{fig:tmp5}
-\end{figure}
+% To make the non-equilibrium feasible, we assume the
+% non-equilibrium process is \emph{local}, i.e. the non-equilibrium perturbation
+% of the system happens only locally, and the rest of the system
+% stays the unperturbed (usually assumed under ambient conditions).
+% This provides us the possibility of simulating only the small subsystem
+% of the universe: We can simulate only subsystem by providing proper
+% boundary condition for it, so that it behaves as if it were embeded into
+% the universe.
+
+% \subsection{The water structure around methane under impluse }
+% In this study, we firstly consider the system of a methane molecule solvated
+% in the liquid water environment. A local density perturbation is implemented
+% by applying an impluse  in a shell surronding methane, see Fig.~\ref{fig:tmp1}.
+% % As far as we concerned, the situation is: we truncate the universe to the
+% % subsystem, and provide proper boundary condition for this
+% % subsystem.
+% Here we denote the size of this subsystem by $R_{\ex}$.
+% Notice this subsystem is simulated by the Newtonian
+% dynamics. If the size of the
+% subsystem is large enough so that the perturbation is
+% small enough when it travels to the boundary of the subsystem, then a
+% trivial boundary condition would be: coupling the system to a boundary
+% layer equilibriated by the thermostat (and barostat or particle reservior),
+% which mimics the infinitely large equilibrium universe.
+
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.3\textwidth]{fig/kick.eps}
+%   \caption{Schematic plot of the density perturbation.}
+%   \label{fig:tmp1}
+% \end{figure}
 

### 2013-03-26 writedown/npt-neq/alanine.tex
improve

@@
   \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
-  \caption{The maganitude of the external electric field as
+  \caption{The magnitude of the external electric field as
     a function of time.}
@@
 with respect to a turning on electric field. The direction of this
-field is along the $x$ dirction and the magnitude with respect to time
+field is along the $x$ direction and the magnitude with respect to time
 is plotted in Fig.~\ref{fig:tmp3}. From $t=0$ to
@@
 water molecules. Firstly, an equilibrium NVT simulation of
-100~\textsf{nm} was performed with a Langvin thermostat (time-scale
+100~\textsf{nm} was performed with a Langevin thermostat (time-scale
 $\tau_T = 0.5~\textsf{ps}$) coupled to the system for constant
@@
 ``switch'' method provided by Gromacs.  An energy conserving PME
-method was applied to calculate the electorstatic interaction in this
+method was applied to calculate the electrostatic interaction in this
 periodic system.  On each branching trajectory, to easy the analysis,
@@
 ``metastable states'' in this research. For a clearer definition, we
-manually devide the $\psi$--$\phi$ plane into 5 subregions. $A_1$ and
+manually divide the $\psi$--$\phi$ plane into 5 subregions. $A_1$ and
 $A_2$ are corresponding to the alpha helix conformation. $B_1$ and
@@
 Left: the equilibrium state at $t=0$~\textsf{ps}.
-Right: The non-equilibrium stady state at $t=1200$~\textsf{ps}, i.e., fully relaxed when the electric field is switched on.
+Right: The non-equilibrium study state at $t=1200$~\textsf{ps}, i.e., fully relaxed when the electric field is switched on.
 The darker color indicates larger population on the $\psi$--$\phi$ phase space.}
@@
 alpha helix $A_2$  does not change a lot under the electric field.
-The ill-folding configuration $C$ noticably grows from 0\% to 20\%.
+The ill-folding configuration $C$ noticeably grows from 0\% to 20\%.
 \\
@@
 $A_1$ to $A_2$. Please see, in Fig.~\ref{fig:tmp5}, the green and read
-peak arount $t = 10~\textsf{ps}$. At the same time, the population of
+peak around $t = 10~\textsf{ps}$. At the same time, the population of
 other metastable sets remains unchanged.  (2), From $t=10$ to
 40~\textsf{ps}, the population of $B_2$ decreases by 0.15, and this
-configuration almost disappers. Interestingly, the population of $A_1$
+configuration almost disappears. Interestingly, the population of $A_1$
 increases by the same amount, and the population of $A_2$ goes back to
@@
 500~\textsf{ps}$ are performed. The first time scale of $t =
-10~\textsf{ps}$ disappers in both of the testing simulations. In the
+10~\textsf{ps}$ disappears in both of the testing simulations. In the
 simulation of $t_{\textrm{init}} = 100~\textsf{ps}$, the population of
@@
 to how the perturbation comes into the subsystem, and how the energy
-of the system dissipates into the universe. In the case of swithing on
-electric field system, two limiting senarios are considered by us: (1)
-the subsystem is isolated from the universe. That is to say the we
-study the non-equilibrium behavior of a system, which conserves the
-energy, volume and number of particle, under the turning on electric
-field.
-
-(1), the
-electric field is applied to the whole universe, the correctness of
-considering a subsystem is tested by varying the size of the
-subsystem, and investigating the convergence of the result.
-
-(2), the
-perturbation is applied locally, and the extra energy dissipates into
-the universe infinitely fast. That is to say the subsystem is coupled
-to a thermostat and barostat with infinitely high
-efficiency. Practically, it is impossible to simulation with a
-``infinitely fast'' thermostat and barostat. We locally truncate the
-system with radius $R_{\textrm{ex}} = 1~\textsf{nm}$ (see
-Fig.~\ref{fig:tmp2} for explanation), and couple it to very sufficient
-thermo- and barostat. We use a Langvin thermostat coupled to the
-thermostating region with a time-scale of $\tau_{T} =
-0.1~\textsf{ps}$, and a Parrinello-Rahman barostat with a time-scale
-of $\tau_{P} = 2.0~\textsf{ps}$.
+of the system dissipates into the universe. In the case of switching on
+electric field system, two limiting scenarios are considered by us: (1)
+The subsystem is isolated from the universe: The electric field is
+applied to a system that conserves the energy, volume and number of
+particle (i.e. a NVE subsystem in short).  The isolation here means
+that the subsystem does not exchange energy, volume and number of
+particle with the universe, but the perturbation (electric field) does
+come in to the subsystem.  The periodic boundary condition is applied
+here only to avoid the difficulty of defining a experimental
+meaningful boundary in simulation.  In this scenario, the size the
+subsystem is somewhat arbitrary (it depends on experimental setting),
+therefore, it is important to consider the convergence of the
+simulation result with respect to the size of the subregion.  (2) The
+system exchange the energy, volume and particle with the universe, and
+the universe is so big that the perturbation in the subsystem will not
+kick the universe from equilibrium.  In practice, it is impossible to
+simulate the infinite large universe, Instead, we want to simulate the
+considerably smaller subsystem instead.  The idea is to divide the
+simulation region into two parts (see Fig.~\ref{fig:tmp2}): the first
+is called \emph{Newtonian dynamics region} that is a region around the
+molecule of interest, where the dynamics is Newtonian. Note that the
+molecular trajectories in the Newtonian dynamics region are the same
+as if it were couple to the universe, only when a proper boundary
+condition is provided. Strictly speaking, the boundary should be
+provided by the out side infinitely large universe, which immediately
+leads back to the numerical difficulty of simulating a infinite large
+system. However, we notice that the detailed information
+(i.e. position and velocity) of the every molecule outside the
+Newtonian dynamics region is not relevant to the non-equilibrium
+behavior of the molecule of interest, because we are only interest in
+the non-equilibrium averages, which does not depends on the individual
+trajectory, but on the trajectorial ensemble sampled by the
+non-equilibrium simulation.  Therefore, the universe, as a boundary to
+the Newtonian dynamics region, can be replace by
+an efficiently thermo- and barostated subsystem, as indicated by the gray
+part of Fig.~\ref{fig:tmp2}. 
+% That is to say the subsystem is coupled to a
+% thermostat, a barostat and a particle bath with infinitely high
+% efficiency. Practically, it is impossible to simulation with a
+% ``infinitely fast'' thermostat, barostat and particle bath.
+We indicate the radius of the Newtonian dynamics region by
+$R_{\textrm{ex}} = 1~\textsf{nm}$ (see Fig.~\ref{fig:tmp2} for
+explanation), and couple it to very sufficient thermo- and
+barostat. We use a Langevin thermostat coupled to the thermostating
+region with a time-scale of $\tau_{T} = 0.1~\textsf{ps}$, and a
+Parrinello-Rahman barostat with a time-scale of $\tau_{P} =
+2.0~\textsf{ps}$.
 
 The non-equilibrium steady temperature and pressure of the
-non-thermostated simulation are $330$ K and -500 Bar,
-correspondingly. Those of the thermostated sytem are $300$ K and 1
+non-thermostated simulation are $330$ K and $-500$ Bar,
+correspondingly. Those of the thermostated system are $300$ K and 1
 Bar, correspondingly. Therefore, we can see from Fig.~\ref{fig:tmp6}
@@
 non-thermostated system. This means that thermostating, in this case,
-does not qulitativly change the population dynamics of metastable
+does not qualitatively change the population dynamics of metastable
 states.

### 2013-07-19 alanine.nanma/template/tools/angles/app/average.traj.corr.cpp
add meta corr calculator

@@ -1,0 +1,246 @@
+#include <algorithm>
+#include <fstream>
+#include <iomanip>
+#include <iostream>
+#include <iterator>
+#include <list>
+#include <map>
+#include <set>
+#include <sstream>
+#include <string>
+#include <queue>
+#include <vector>
+#include <cmath>
+
+#include "Defines.h"
+#include "Distribution.h"
+#include "Traj.h"
+#include <boost/program_options.hpp>
+namespace po = boost::program_options;
+using namespace std;
+#define MaxLineLength 2048
+
+bool myread (FILE * fp,
+	     float & time,
+	     ValueType & phi,
+	     ValueType & psi)
+{
+  size_t rv;
+  rv = fread (&time, sizeof(float), 1, fp);
+  if (rv != 1){
+    // cerr << "error read time or reach EOF" << endl;
+    return false;
+  }
+  rv = fread (&phi, sizeof(double), 1, fp);
+  if (rv != 1){
+    cerr << "error read phi " << endl;
+    exit(1);
+  }
+  rv = fread (&psi, sizeof(double), 1, fp);
+  if (rv != 1){
+    cerr << "error read psi " << endl;
+    exit(1);
+  }
+  return true;
+}
+
+void depositMetastable (const double & phi,
+			const double & psi,
+			const vector<MetastableSet> & sets,
+			vector<double > & counts)
+{
+  int cc = 0;
+  counts.resize (sets.size());
+  for (unsigned ii = 0; ii < sets.size(); ++ii){
+    counts[ii] = 0;
+    if (sets[ii].inSet(phi, psi)){
+      counts[ii] = 1;
+      cc ++;
+    }
+  }
+  
+  if (cc != 1) {
+    if (cc == 0){
+      cerr << "not in any set!!!" << endl;
+    }
+    else {
+      cerr << "in multi sets" << endl;
+    }
+  }
+}
+
+void calCorr (const vector<double> & counts0,
+	      const vector<double> & counts1,
+	      vector<vector<double > > countCorr)
+{
+  countCorr.resize (counts0.size());
+  for (unsigned ii = 0; ii < countCorr.size(); ++ii){
+    countCorr[ii].resize (counts1.size());
+    for (unsigned jj = 0; jj < countCorr[ii].size(); ++jj){
[…]

### 2013-07-19 alanine.nanma/template/tools/angles/app/average.traj.corr.cpp
fix bugs

@@ -71,7 +71,7 @@ void depositMetastable (const double & phi,
 
 void calCorr (const vector<double> & counts0,
 	      const vector<double> & counts1,
-	      vector<vector<double > > countCorr)
+	      vector<vector<double > > & countCorr)
 {
   countCorr.resize (counts0.size());
   for (unsigned ii = 0; ii < countCorr.size(); ++ii){
@@ -234,8 +234,13 @@ int main(int argc, char * argv[])
     for (unsigned dd = 0; dd < sets.size(); ++dd){
       counts[ii][dd] = counts[ii][dd] / double(countFile);
       fprintf (fp, "%f ", counts[ii][dd]);
-      for (unsigned mm = 0; mm < sets.size(); ++mm){
-	fprintf (fp1, "%f ", corrs[ii][dd][mm] / counts[ii][dd]);
+      if (counts[ii][dd] != 0){
+	for (unsigned mm = 0; mm < sets.size(); ++mm){
+	  fprintf (fp1, "%f ", corrs[ii][dd][mm] / counts[ii][dd] / double (countFile));
+	}
+      }
+      else {
+	fprintf (fp1, "%f ", 0.);
       }
       fprintf (fp1, "  ");
     }

### 2013-07-19 alanine.nanma/template/tools/angles/app/average.traj.corr.cpp
fix a bug

@@ -240,7 +240,9 @@ int main(int argc, char * argv[])
 	}
       }
       else {
-	fprintf (fp1, "%f ", 0.);
+	for (unsigned mm = 0; mm < sets.size(); ++mm){
+	  fprintf (fp1, "%f ", 0.);
+	}
       }
       fprintf (fp1, "  ");
     }

### 2013-07-24 writedown/npt-neq/alanine.tex
constructing paper from the report

@@
 % \documentclass[aip,jcp,preprint,unsortedaddress,a4paper,onecolum]{revtex4-1}
-\documentclass[a4paper,preprint,onecolumn]{revtex4-1}
+\documentclass[aip,jcp,a4paper,preprint,onecolumn]{revtex4-1}
 % \documentclass[aps,pre,twocolumn]{revtex4-1}
@@
 \newcommand{\dd}[1]{\textsf{#1}}
-
-\newcommand{\AT}{{\textrm{{AT}}}}
-\newcommand{\EX}{{\textrm{EX}}}
-\newcommand{\ex}{{\textrm{ex}}}
-\newcommand{\CG}{{\textrm{CG}}}
-\newcommand{\HY}{{\Delta}}
-\newcommand{\rdf}{{\textrm{rdf}}}
+\newcommand{\fwd}[0]{\textrm{fwd}}
+\newcommand{\bwd}[0]{\textrm{bwd}}
 
@@
 
-\title{Report: the non-equilibrium molecular dynamics simulation}
+\title{The non-equilibrium molecular dynamics simulation of the alanine dipeptide under electric field}
 \author{Han Wang}
@@
 \affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
+% \affiliation{Zuse Institute Berlin, Germany}
 \author{Luigi Delle Site}
@@
 
-\section{Alanine dipeptide
-  under turning on electric field}
+\section{Methodology}
+\subsection{Nonequilibrium molecular dynamics simulation}
+Here we fastly review the approach of performing nonequilibrium
+molecular dynamics that was initiated by Giovanni Ciccoti and his
+colleagues~\cite{ciccotti1975direct, ciccotti1979thought,
+  orlandini2011hydrodynamics, orlandini2011hydrodynamics-01}.
+We denote the macroscopic nonequilibrium observable by $O(t)$. If at $t$
+the configurational probability distribution is $\rho(\vect x, t)$, where
+$\vect x$ is the phase space variable, then the observable can be
+expressed by
+\begin{align}\label{eqn:tmp1}
+  O(t) = \int d\vect x\, \hat O(\vect x)\rho(\vect x, t)  = \langle \hat O(\vect x), \rho(\vect x, t)\rangle,
+\end{align}
+where $\hat O (\vect x)$ is the microscopic observable. Compared with
+the macroscopic observable, it is measured at the phase space position $\vect x$.
+The bracket on the right hand side denotes the inner produce in the
+phase space.  We assume the dynamics of the system is governed by the
+Hamiltonian equation, i.e. $\dot {\vect x} = J \cdot \nabla_{\vect x}
+\mathcal H(\vect x)$, where $\mathcal H$ is the Hamiltonian and $J$ is
+the symplectic matrix, then the Liouville equation of the probability
+distribution is
+\begin{align}\label{eqn:tmp2}
+  \frac{\partial \rho(\vect x, t)}{\partial t} = - iL(t) \rho(\vect x, t),
+\end{align}
+where $iL(t) = \{\cdot, \mathcal H\}$ is the Liouville operator and
+$\mathcal H$ is the Hamiltonian of the system. The Eq.~\eqref{eqn:tmp2}
+can be formally solved by $\rho(\vect x, t) = e^{-iL(t)} \rho(\vect x, 0)$.
+On the other hand
+\begin{align}
+  \frac{d \hat O(\vect x(t))}{dt} = \nabla_{\vect x}\hat O\cdot \dot{\vect x}
+  = \nabla_{\vect x}\hat O\cdot J\cdot \nabla_{\vect x}\mathcal H
+  = iL(t) \hat O (\vect x(t))
+\end{align}
+This equation can be formally solved by $\hat O(\vect x(t)) = e^{iL(t)} O(\vect x, 0)$, therefore,
+\begin{align}\nonumber
+  O(t) & = \langle \hat O(\vect x), \rho(\vect x, t)\rangle
+  = \langle \hat O(\vect x), e^{-iL(t)} \rho(\vect x, 0)\rangle
+  = \langle e^{iL(t)}\hat O(\vect x), \rho(\vect x, 0)\rangle\\\label{eqn:tmp4}
+  &= \langle \hat O(\vect x(t)), \rho(\vect x, 0)\rangle
+\end{align}
+If the inital state of the system is in equilibrium, i.e. the initial
+probability distribution is the equilibrium distribution. Then an
+explicit translation of Eq.~\eqref{eqn:tmp4} is that the
+nonequilibrium observable is equal to the ensenble average of
+microscopic observable measured along trajectory $\vect x(t)$, the
+inital configuration of which is subject to the equilibrium
+distribution. In practice, we firstly run an equilibrium MD simulation
+to generate a collection of configurations that are subject to the
+equilibrium distribution. And then by using these configurations as
+inital configuration, the Hamiltonian dynamicses are integrated until
+time $t$. These trajectories are also called \emph{branching
+  trajectories} in this paper. Finially, the macroscopic observable is
+estimated by averaging the microscopic observable measured at the end
+points of the trajectories.
+
+Being more gneralize, if the microscopic depends not only on the end
+configuation of at time $t$ but also depends on the historical
+configurations along the trajectory, the experssion~\eqref{eqn:tmp4} can be generalize to
+\begin{align}
+  O(t) = \int d\vect x\,\rho(\vect x, 0) \int_{\mathcal C\{\vect x, 0; t\}} \hat O[\vect x_s] \,d\mathcal P[\vect x_s] 
+\end{align}
+where the microscopic observable $ \hat O[\vect x_s] $ is now a
+functional of the trajectory.  $\mathcal C\{\vect x, 0; t\}$ is the
+set of all continuous trajectories starting at point $\vect x$ at time
+0, and ending at time $t$. $\mathcal P[\vect x_s] $ is the meansure of
+the trajectory space $\mathcal C$.  In our case, it is the
+$\delta$-function peaked around the trajectory generated by the
+Hamiltonian dynamics. To be general, it can also be the measure of all
+trajectories generated by, for example, a Langevin dynamics, then the
+branching trajectories should be generated by the Langevin
+dynamics rather than the Hamiltonian dynamics.
+
+\subsection{Nonequilibrium temperature control}
+
+The aformentioned nonequilibrium molecular dynamicses simulation algorithm
+does not describe how the boundary of the system should be set up. The 100\% save
+method is to simulate a infinitely large isolated system, or any large enough
+isolated subsystem of it. In practice, it is both impossible and unnecessary to
+do such a simulation. In practice, proper boundary condition should be developped
+based on how the nonequilibrium system is set up, and what are the nonequilibrium
+observables to measure.
+Since we are mainly interested in the non-thermal effect of
+the electric field to the configuration of a solvated alanine dipeptide,
+we assume the alanine is embeded into an infinitely large solvent envrionment,
+and the electric field is only applied to the neighborhood of the alanine. Therefore, 
+extra heat generated by turing on the electric field can be effectively absorbed
+by the envrionment.
+
 \begin{figure}
   \centering
-  \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
-  \caption{The magnitude of the external electric field as
-    a function of time.}
+  \includegraphics[width=0.3\textwidth]{fig/thermostat.eps}
+  \caption{Schematic plot of the truncated nonequilibrium subsystem.
+    The white part is the subsystem and the gray part is the boundary
+    condition, implemented by the thermostat and barostat mimicing
+    the infinitely large universe.}
+  \label{fig:tmp2}
+\end{figure}
+
+In practice, it is impossible to simulate an infinitely large
+environment.  For an equilibrium simulation, the solution is to couple
+the system to a thermostat, under which the canonical ensember can be
+sampled by only simulate a finite size system with periodic boundary
+condition. For a nonequilibrium simulation, simply couple the system
+to a thermostat may not be a good idea, because the \emph{dynamics}
+generated by the thermostat is artificial, and deviation from the
+Hamiltonian dynamics under investigation will introduce artificial
+effects in the nonequilibrium observations. To solve this problem, we
+observe that only the Hamiltonian dynamics of the alanine molecule
+itself and the water molecules in the nearby solvation shell is
+crutial to the configuration change, while the detailed dynamics of
+the water molecules far away has less effect. Notice again we actually
+do not want to precisely calculate each trajectory starting from the
+initial configurations, but want to sample correctly the trajectory
+ensemble correctly, so that the nonequilibrium observable can be
+calculated correctly.  Therefore, instead of simulating an infinitely
+large system, we only simulate a finite size system with periodic
+boundary condition. The simulating region is divided into two
+subregions: Near the alanine dipeptide, the dynamics is kept to be
+Hamiltonian, and this subregion is called the Hamiltonian dynamics
+region. While far from the alanine, the dynamics of water is coupled
+to a Langevin thermostat, and this region is called the thermostating
+region (see Fig.~\ref{fig:tmp2}).  For simplicity, the Hamiltonian
+dynamics region is assumed to be spherical, centered at the
+alpha-carbon of the alanine, and with radius of $R_{ex}$.  Further, we
+freeze the movment of the alpha-carbon, so that the alanine is always
+located at the center of the simulation region.  The validity of this
+setting will be later check by numerical examples showing that the
+nonequilibrium observables do not depends on the size of the system
+and the size of the Hamiltonian dynamics subregion, if they are
+reasonably large and the finite size effect does not play a role.
+
+\section{Example I: Alanine dipeptide
+  under a linearly switching on electric field}
+
+\subsection{System setting up }
+\begin{figure}
+  \centering
+  % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
+  \includegraphics[]{fig.ala/fig-field-dipol.eps}
+  \caption{The magnitude of the external electric field, and the
+    x-component of the dipole moment of the alanine molecule as a
+    function of time. The dashed lines are the strengths of the
+    external electric field, while the solid lines are the dipole
+    moments. Three test cases are indicated by different colors.}
   \label{fig:tmp3}
@@
 
-We study the response of the configuration of the alanine dipeptide
-with respect to a turning on electric field. The direction of this
-field is along the $x$ direction and the magnitude with respect to time
-is plotted in Fig.~\ref{fig:tmp3}. From $t=0$ to
+We want to study the nonequilibrium properties of an alanine dipeptide
+under a changing electric field. As a model system, we study the
+linearly switching on electric field: From $t=0$ to
 $t=t_{\textrm{init}}$, the strength of the field grows linearly, while
 after $t=t_{\textrm{init}}$, the strength is kept constant at
-$E_{\textrm{max}}$.  The size of the system is $2.67\times 2.67\times
-2.67\, \textsf{nm}^3$, with one alanine dipeptide solved in 644 TIP3P
-water molecules. Firstly, an equilibrium NVT simulation of
+$E_{\textrm{max}}$. Fig.~\ref{fig:tmp3} shows the three different
+cases considered in this work: $t_{\textrm{init}} = 10$, 100, and
+500~ps, and 
+in all cases the maximum strength of the electric field is
+$E_{\textrm{max}} = 1$~V/nm.
+The direction of this field is arbitarily chosen: along the
+$x$ direction. Since the dipole of the equilibrium configurations of
+alanine can be along any direction (see also Fig.~\ref{fig:tmp3} for
+the vanished initial dipole moment), applying the electric along x-axis is
+not biased.
+The size of the system is $2.67\times 2.67\times
+2.67\, \textsf{nm}^3$, with one alanine dipeptide described by the CHARMM27 force field, and solved in 644 TIP3P
+water molecules.
+All simulations are performed by a home-modified GROMACS 4.5~\cite{pronk2013gromacs}.
+Firstly, an equilibrium NVT simulation of
 100~\textsf{nm} was performed with a Langevin thermostat (time-scale
@@
 trajectories. The branching trajectories were integrated by the
-Leap-frog scheme without any temperature and pressure control.  The
+Leap-frog scheme with the aformentioned nonequilibrium temperature control technique.  The
 time step was $\Delta t = 0.002~\textsf{ps}$. The short-range
@@
 method was applied to calculate the electrostatic interaction in this
-periodic system.  On each branching trajectory, to easy the analysis,
-the conformation of the alanine dipeptide is projected on the
-$\psi$--$\phi$ plane, as shown in Fig.~\ref{fig:tmp4}. The equilibrium
-distribution of the conformation on the $\psi$--$\phi$ plane is given
-in the Left plot of Fig.~\ref{fig:tmp4}.  It is clear the
-conformations are populated in several clusters that are called
-``metastable states'' in this research. For a clearer definition, we
-manually divide the $\psi$--$\phi$ plane into 5 subregions. $A_1$ and
-$A_2$ are corresponding to the alpha helix conformation. $B_1$ and
-$B_2$ are corresponding
-to beta sheet conformation. $C$ is corresponding to ill-folding.\\
+periodic system. In the thermostating region, the original dyanmics was
+coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
+The whole system is also coupled to a Parrinello-Rahman barostat with $\tau_P = 2.0~\textsf{ps}$ to keep
+the pressure at the ambient condition (1~Bar). Since the
+change of the system size is small and slow, it does not have an obviously effect on the
+dyanmics of the system.
+
+\subsection{Metastable sets}
+
+On each branching trajectory, to easy the analysis, the conformation
+of the alanine dipeptide is plotted by the Ramachandran histogram, as
+shown in Fig.~\ref{fig:tmp4}. The equilibrium distribution of the
+conformation is given in the left plot, and the fully relaxed
+conformation at $E_{\max} = 1$~V/nm is given in the right plot.  It is
+clear the conformations are populated in several clusters, and the
+position of the clusters do not change when the external electric
+field is applied. This means that only a few of the configurations are likely to be observed, while there is nearly
+no oppotunity to see others. 
+These configurations are called ``metastable states''. The strict definition of the
+metastability is not exactly the same as those conformations that are likely to be observed.
+Since in this paper we do not focus on the discussion of the definition for the metastability of the system,
+we assume they have the same meaning.
+We manually divide the
+$\psi$--$\phi$ plane into 5 subregions, see Fig.~\ref{fig:tmp4},
+then the observation on the Ramachandran histogram is projected to the
+observation of these 5 subregions.  These subregions
+correspond to different secondary structure of a peptide chain:
+$A_1$ and $A_2$ are
+corresponding to the alpha helix. $B_1$ and $B_2$ are
+corresponding to beta sheet. $C$ is corresponding to the
+left-handed alpha helix.
 
@@
   \label{fig:tmp4}
+\end{figure}
+
+From Fig.~\ref{fig:tmp4}, it is obvious that the population in each
+metastable sets changes due to the external electric field, for
+example, the population of conformations C vanishes in equilibrium,
+but plays an important role when the electric field is applied. We
+therefore want to study how the alanine changes from one conformation
+to the other, how fast is the change, and the relation to the speed of
+the increasing electric field (i.e. the value of $t_{init}$). 
+Firly, we study the population of the metastable conformations
+Being more strict, we calculate the nonequilibrium observable
+\begin{align}
+  p_I(t) = \mathbb P (\vect x_t \in I), \quad  I \in \{A_1, A_2, B_1, B_2, C\}
+\end{align}
+Secondly, we study the
+forward and backward transition probability of the metastable conformations, which is defined by
+\begin{align}
+  p^{\fwd}_{J,I}(t) & = \mathbb P( \vect x_{t+\Delta t} \in J | \vect x_t \in I) \\
+  p^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J | \vect x_t \in I)
+  \qquad I, J \in \{A_1, A_2, B_1, B_2, C\},
+\end{align}
+where $\Delta t$ is the time-scale of the observation.
+For a revserible and homogeneous Markov process, it is easy to show
+that $p^{\fwd}_{J,I} = p^{\bwd}_{J,I}$, and both of them are time independent. For a general nonequilibrium
+process considered by the present work, this relation is genarlly not guarenteed.
+
+\subsection{Results and discusstions}
+\begin{figure}
+  \centering
+  \includegraphics[]{fig.ala/fig-meta-npt.eps}
+  \caption{The populations of the metastable sets as a function of time.
+    The dashed vertical lines indicate the three different time scale of
+  metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
+  \label{fig:tmp5}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-1.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-5.eps}\\
+  % \caption{The populations of the metastable sets as a function of time.
+  %   The dashed vertical lines indicate the three different time scale of
+  % metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-1.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-5.eps}\\
+  \caption{Forward and backward nonequilibrium transition probability of the case $t_{init} = 10$~ps.}
+  \label{fig:tmp6}
 \end{figure}
@@
 % $C$, the time-scales of relaxation are roughly 600~\textsf{ps}.
-\begin{figure}
-  \centering
-  \includegraphics[]{fig.ala/fig-meta.eps}
-  \caption{The populations of the metastable sets as a function of time.
-    The dashed vertical lines indicate the three different time scale of
-  metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
-  \label{fig:tmp5}
-\end{figure}
 
 \section{Testing the effect of the thermostat and barostat}
-\begin{figure}
-  \centering
-  \includegraphics[width=0.3\textwidth]{fig/thermostat.eps}
-  \caption{Schematic plot of the truncated non-equilibrium subsystem.
-    The white part is the subsystem and the gray part is the boundary
-    condition, implemented by the thermostat and barostat mimicing
-    the infinitely large universe.}
-  \label{fig:tmp2}
-\end{figure}
 
@@
 
+\bibliography{ref}{}
+\bibliographystyle{unsrt}
+
 \end{document}

### 2013-07-30 writedown/npt-neq/alanine.tex
backup manuscript

@@
 
-\newpage
+\section{Introduction}
+
+The possible effect of the electric field (EF) on the conformation of
+proteins gains increasing attantion recently, because it closly
+related to the health problem of exposing human tissue in the
+electromagnetic radiation. Despite the importance of this problem, a
+complete understanding of how the electric field influnece the  protein
+is still lacking, therefore, a conserderable number of
+experimental~\cite{bohr2000microwave, bohr2000microwave-1,
+  dePomerai2000cell, inskip2001cellular, mancinelli2004non} and
+theoretical~\cite{budi2005electric, budi2007effect,
+  budi2008comparative, toschi2008effects, astrakas2011electric,
+  astrakas2012structural, damm2012can, starzyk2013proteins,
+  english2009nonequilibrium, solomentsev2012effects} studies have been devoted to this topic,
+and the references listed above is far from complete.
+
+The molecular dynamics (MD) simulation has been proved to be useful in
+understanding the behavior of a protein (or a short peptide segment)
+in both static and oscilatatory electiric
+fields~\cite{budi2005electric, budi2007effect, budi2008comparative,
+  toschi2008effects, astrakas2011electric, astrakas2012structural,
+  damm2012can, starzyk2013proteins, english2009nonequilibrium,
+  solomentsev2012effects}. In these studies, the initial
+configurations are usually taken from the Protein Data Bank (PDB).
+And then the temperature controlled simulation are performed for from
+a few to tens of nanoseconds, during which the interested
+conformational chanages can be observed. Along the trajectories, the
+secondary structure, root mean square displacement (RMSD), the dipole
+moment and some shape parameters are calculated and investigated by
+either plotted as a function of time, or doing time average over the
+whole simulation. This approach release useful information on how the
+secondary structure is changed by external electiric field.  However,
+by plotting the quantities against time, one may observe strong
+fluctuation in plots, which hintered the quantitative and conclusive
+analysis on what is happening during the conformational change, when
+it happens and what is the strength. Although the statistical
+uncertainty in the time-averaged observations are small, the
+time-average itself is not well defined for a nonequilibrium process
+such as relaxing process to the new conformations under static
+electiric field, and the dynamics under oscilatating electric field.
+
+The dynamical nonequilibrium molecular dyanmics simulation (D-NEMD)
+was firstly developed by G. Ciccotti and his
+colleagues~\cite{ciccotti1975direct, ciccotti1979thought}, and
+recently successfully applied to the study of
+hydrodynamics~\cite{orlandini2011hydrodynamics,
+  orlandini2011hydrodynamics-01}. D-NEMD provides a way of evaluating
+nonequilibrium observables by doing an ensemble of nonequilibrium MD
+simualtions.  This provides a promising way of analysing the
+conformational changing under a generally time-dependent electric
+field. In the present paper, we study the minimal model peptide
+segment -- alanine dipeptide. We take the approach of starting from a
+single peptide rather than a more realistic chain, firstly because it
+is easier to draw clear conclusions on the nonequilibrium properties
+of a single peptide by excluding all possible interplay between
+different peptide segments along a chain, then construct the chain
+nonequilibrium properties from the well-studied single peptides.
+Secondly, the current computationl resource available is not enought
+to study peptide chains by D-NEMD, since one needs to simualte an
+ensemble of MD trajectories (typically a few thousands), so it
+requires much higher computational cost than producing a single MD
+trajectory.
+
+In this paper, we firstly describe the idea of the D-NEMD, then
+observables helping us the analyze the nonequilibrium properties
+(i.e., the dipole moment, time-dependent properties of being a certain
+conformation, the nonequilibrium transition properties and the net
+property flux) are introduced. The numerical results of alanine
+dipeptide under static and sine-shaped oscilatating electric field are
+presented. By calculating the nonequilibrium properties from the D-NEMD
+simulations, we are able to answer from which to which the conformation
+changes, when do these changes happend, and how strong are the changes.
+As far as we know, our simulation is the first D-NEMD simulation
+on the electric field effect on alanine dipeptide, and provides new
+information helping people better understand the nonequilibrium
+effect of electric field on the protein conformation.
 
@@
 observables to measure.
-Since we are mainly interested in the non-thermal effect of
+Since we are mainly interested in the nonthermal~\cite{delaHoz2005microwaves} effect of
 the electric field to the configuration of a solvated alanine dipeptide,
 we assume the alanine is embeded into an infinitely large solvent envrionment,
-and the electric field is only applied to the neighborhood of the alanine. Therefore, 
+and the electric field is only applied to the neighborhood of the alanine.
+Therefore, 
 extra heat generated by turing on the electric field can be effectively absorbed
 by the envrionment.
+It is argued that 
+an accurate reaction temperature control is essential for being able to perform
+reproducible experiments~\cite{damm2012can}.
 
@@
 \section{Example I: Alanine dipeptide
-  under a linearly switching on electric field}
+  under a constant electric field}
 
-\subsection{System setting up }
+\subsection{System settings and simulation protocol}
 \begin{figure}
@@
 under a changing electric field. As a model system, we study the
-linearly switching on electric field: From $t=0$ to
-$t=t_{\textrm{init}}$, the strength of the field grows linearly, while
-after $t=t_{\textrm{init}}$, the strength is kept constant at
-$E_{\textrm{max}}$. Fig.~\ref{fig:tmp3} shows the three different
+a constant electric field. At time $t=0$~ps, the system
+has been fully equilibriated without any electric field. From $t=0$ to
+$t=t_{\textrm{init}}$, the electic field is switched on linearly, while
+after $t=t_{\textrm{init}}$, the field is kept constant at
+$E_{\infty}$. Fig.~\ref{fig:tmp3} shows the three different
 cases considered in this work: $t_{\textrm{init}} = 10$, 100, and
@@
 in all cases the maximum strength of the electric field is
-$E_{\textrm{max}} = 1$~V/nm.
+$E_{\infty} = 1$~V/nm.
 The direction of this field is arbitarily chosen: along the
@@
 conformation is given in the left plot, and the fully relaxed
-conformation at $E_{\max} = 1$~V/nm is given in the right plot.  It is
+conformation at $E_{\infty} = 1$~V/nm is given in the right plot.  It is
 clear the conformations are populated in several clusters, and the
@@
 \begin{align}
-  p_I(t) = \mathbb P (\vect x_t \in I), \quad  I \in \{A_1, A_2, B_1, B_2, C\}
+  p_I(t) = \mathbb P (\vect x_t \in I), \quad  I \in \{A_1, A_2, B_1, B_2, C\},
 \end{align}
+which is the time dependent probability of the alanine being in metastable
+state $I$.
 Secondly, we study the
@@
 \begin{align}
-  p^{\fwd}_{J,I}(t) & = \mathbb P( \vect x_{t+\Delta t} \in J | \vect x_t \in I) \\
-  p^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J | \vect x_t \in I)
-  \qquad I, J \in \{A_1, A_2, B_1, B_2, C\},
+  P^{\fwd}_{J,I}(t) & = \mathbb P( \vect x_{t+\Delta t} \in J | \vect x_t \in I) \\
+  P^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J | \vect x_t \in I) 
+  % \qquad I, J \in \{A_1, A_2, B_1, B_2, C\},
 \end{align}
@@
 For a revserible and homogeneous Markov process, it is easy to show
-that $p^{\fwd}_{J,I} = p^{\bwd}_{J,I}$, and both of them are time independent. For a general nonequilibrium
-process considered by the present work, this relation is genarlly not guarenteed.
+that $P^{\fwd}_{J,I} = P^{\bwd}_{J,I}$, and both of them are time independent. For a general nonequilibrium
+process considered by the present work, this relation is genarlly not guarenteed. Finally, we study the backward net flux from metastable set $I$ to $J$:
+\begin{align}
+  F^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I) - \mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J).
+\end{align}
+Unlike the transition probabilities that are defined by the conditional
+probability, the net flux is defined by the difference between
+two joint probabilities, and prensents how much conformation $J$ is changed
+into $I$ in the past $\Delta t$ interval. A positive value indicates the
+flux from $J$ to $I$, while a negative value indicates a flux from $I$ to $J$.
 
@@
   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-5.eps}\\
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-1.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-5.eps}
   \caption{Forward and backward nonequilibrium transition probability of the case $t_{init} = 10$~ps.}
@@
 
-For all testing cases, the maximum strength of the electric field
-$E_{\textrm{max}}$ is chosen to be 1~\textsf{V/nm}.  Three values of
-$t_{\textrm{init}}$ (10~\textsf{ps}, 100~\textsf{ps} and
-500~\textsf{ps}) are chosen to study the response of the system to the
-external electric field perturbation. The result is given in
-Fig.~\ref{fig:tmp5}.  No matter how fast is the electric field turned
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-1.eps}
+%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-2.eps}
+%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-3.eps}
+%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-4.eps}
+%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-5.eps}\\
+%   % \caption{The populations of the metastable sets as a function of time.
+%   %   The dashed vertical lines indicate the three different time scale of
+%   % metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
+%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-1.eps}
+%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-2.eps}
+%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-3.eps}
+%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-4.eps}
+%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-5.eps}\\
+%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-1.eps}
+%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-2.eps}
+%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-3.eps}
+%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-4.eps}
+%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-5.eps}
+%   \caption{Forward and backward nonequilibrium transition probability of the case $t_{init} = 10$~ps.}
+%   \label{fig:tmp6}
+% \end{figure}
+
+The time-dependent probability of the system in a certain metastable set is given in
+Fig.~\ref{fig:tmp5}, and different speeds of switching on the electric field
+($t_{init} = 10$, 100 and 500~ps) are compared.  No matter how fast is the electric field turned
 on, the beta sheet configuration, which presents at the beginning,
@@
 alpha helix $A_2$  does not change a lot under the electric field.
-The ill-folding configuration $C$ noticeably grows from 0\% to 20\%.
-\\
+The left-hand helix configuration $C$ noticeably grows from 0\% to 20\%.
 
-In the case of fastly switching on electric field
-($t_{\textrm{init}}=10~\textsf{ps}$), the dynamics of the population
-of the metastable sets shows three different time-scales. (1) From
-$t=0$ to 10~\textsf{ps}, the population of $A_2$ fastly increases,
-while the population of $A_1$ decreases with the same amount, so it is
-reasonable to argue that there is a fast configurational change from
-$A_1$ to $A_2$. Please see, in Fig.~\ref{fig:tmp5}, the green and read
-peak around $t = 10~\textsf{ps}$. At the same time, the population of
-other metastable sets remains unchanged.  (2), From $t=10$ to
-40~\textsf{ps}, the population of $B_2$ decreases by 0.15, and this
-configuration almost disappears. Interestingly, the population of $A_1$
-increases by the same amount, and the population of $A_2$ goes back to
-the initial value. The populations of $B_1$ and $C$ start increasing
-and decreasing, correspondingly. The speed of these changes are much
-slower than that of $B_2$ and $A_1$.  (3) At the time scale of $t =
-300~\textsf{ps}$, the population of $A_1$, $B_1$ and $C$ converge to
+For the case of fastly switching on electric field
+($t_{\textrm{init}}=10~\textsf{ps}$),
+we plot the time-dependent forward, backward transition probability and the net backward probability flux
+in Fig.~\ref{fig:tmp6}.
+If the process were time reversible and homogeneous, then the forward and backward transition probabilities
+would be identical. As a matter of fact, the inconsistent forward and backward transition probabilities
+implies the process is indeed nonequilibrium.
+Together with Fig.~\ref{fig:tmp5}, we observe
+three different timescales of 
+the dynamics of the alanine conformation:
+(1) From
+$t=0$ to approximately 20~\textsf{ps}, the population of $A_1$ firstly decreases and then increases to the original value,
+while the population of $A_2$ increases sharply. The plot of the net probability flux shows that 
+there is firstly a fast probability flux (conformational change) from
+$A_1$ to $A_2$, and then follows a probability flux with the same maganitude in the opposite direction, i.e.  from
+$A_2$ to $A_1$.
+In the meanwhile, a clear trend from $\beta$-sheet conformations ($B_1$ and $B_2$)
+into $\alpha$-helix conformations ($A_1$, $A_2$ and $C$), both left- and right-handed,
+has been established.
+Also in this time-scale, strong and increasing probability flux from $B_2$ to $B_1$ is observed from Fig.~\ref{fig:tmp6}.
+The population of $B_1$ remains almost unchanged,
+because it  at the same time loses population to $\alpha$-helix conformations.
+Since  $B_2$ conformations not only changes into $B_1$, but also into $\alpha$-helix conformations, we observe a charp
+decrease of $B_2$ population between 10 and 20~ps.
+(2), From $t=10$ to
+100~\textsf{ps},
+The net flux from  conformation $A_2$ to $A_1$ and from $B_2$ to $B_1$
+gradually decays to 0. Conformational change between $\alpha$-helix and $\beta$ sheet
+is hardly observed, except a very week flux from $B_1$ to $A_1$ and $C$, which will be discussed later.
+At this stage, the population of $B_2$ decreases to almost 0, while the population of $A_2$
+converge to a non-vanishing value of approximately 0.06.
+% the population of $B_2$ decreases by 0.15, and this
+% configuration almost disappears. Interestingly, the population of $A_1$
+% increases by the same amount, and the population of $A_2$ goes back to
+% the initial value. The populations of $B_1$ and $C$ start increasing
+% and decreasing, correspondingly. The speed of these changes are much
+% slower than that of $B_2$ and $A_1$.
+(3) At the time scale of $
+500~\textsf{ps}$, the population of $A_1$, $B_1$ and $C$ converge to
 the non-equilibrium steady state (system with $E(\infty) = 1~\textsf{V/m}$).
-This time is actually thirty times large than when the electric field
-is fully switched on ($t_{\textrm{init}} = 10~\textsf{ps}$). This 
-indicates that the internal time scale of $A_1$, $B_1$ and $C$
-relaxation is around $300~\textsf{ps}$.\\
+We only observed slowing decaying probability flux from $B_1$ to $A_1$ and $C$.
+The maganitude of the flux from $B_1$ to  $C$ is larger than that from  $B_1$ to  $A_1$.
+It is interesting to see that at nonequilibrium steady state, $A_1$ exchange
+population with $A_2$, and $B_1$ exchange
+population with $B_2$. However, when the $C$ conformation hardly changes
+to any other conformation, as indicated by the almost 1 value of the forward
+transition probability of set $C$. This implies that at the left-handed $\alpha$-helix is
+acutally more stable than  other conformations.
+This time-scale is actually 50 times large than when the electric field
+is fully switched on ($t_{\textrm{init}} = 10~\textsf{ps}$).
+Notice that the Fig.~\ref{fig:tmp3}
+shows that the x-component of the dipole moment of the alanine dipeptide
+reaches the maximum value at a time scale  that is the same as
+$t_{init}$. This observation indicates that the alanine can adjust almost immediately its
+dipole according to the external electric field, however, the conformational change
+happens at some much slower time scales.
 
@@
 500~\textsf{ps}$ are performed. The first time scale of $t =
-10~\textsf{ps}$ disappears in both of the testing simulations. In the
+20~\textsf{ps}$ disappears in both of the testing simulations. In the
 simulation of $t_{\textrm{init}} = 100~\textsf{ps}$, the population of
 $A$, $B_1$ and $C$ converges to the non-equilibrium steady state at
-around $300~\textsf{ps}$. This further verifies internal time scale of
+around $500~\textsf{ps}$. This further verifies internal time scale of
 $A_1$, $B_1$ and $C$ presented in the testing case of
 $t_{\textrm{init}} = 10~\textsf{ps}$.  The dynamics of $B_2$ is
-faster: it decays to zero as fast as the external electric field is
+faster: it decays to zero as soon as the external electric field is fully
 switched on. In the case of $t_{\textrm{init}} = 500~\textsf{ps}$, the
-growth of the external electric field is slower than the longest
+growth of the external electric field is comparable to the longest
 internal time scale of system, which means that the changes of the
-perturbation to the system is so slow that the system can catch up
-with that. The numerical results show the same story: the relaxation
+perturbation to the system is so slow that the system can catch up, so
+the process can be treated as  quasi-equilibrium.
+The numerical results show the same story: the relaxation
 of all populations are around $500 \sim 600~\textsf{ps}$.
-\\
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig.ala/fig-meta-conv.eps}
+  \caption{The populations of the metastable sets as a function of time.
+    The dashed vertical lines indicate the three different time scale of
+  metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
+  \label{fig:tmp7}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig.ala/fig-meta-mode2-010.eps}
+  \includegraphics[]{fig.ala/fig-meta-mode2-040.eps}
+  \includegraphics[]{fig.ala/fig-meta-mode2-200.eps}
+  \caption{The populations of the metastable sets as a function of time.
+    The dashed vertical lines indicate the three different time scale of
+  metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
+  \label{fig:tmp5}
+\end{figure}
 
@@
 
-\section{Testing the effect of the thermostat and barostat}
+% \section{Testing the effect of the thermostat and barostat}
 
-% \section{System set up}
+% % \section{System set up}
 
-% $R_{\textrm{ex}}$ was chosen to be
-% $1.0$~\textsf{nm}, which means that a Langvin thermostat ($\tau =
-% 0.1~\textsf{ps}$) was applied to water molecules that were more than
-% $1.0$~\textsf{nm} away from the center of the simulation box. In
-% addition, a Parrinello-Rahman barostat was couple to the system with a
-% time-scale of $\tau_{\textrm{P}} = 2.0~\textsf{ps}$.
+% % $R_{\textrm{ex}}$ was chosen to be
+% % $1.0$~\textsf{nm}, which means that a Langvin thermostat ($\tau =
+% % 0.1~\textsf{ps}$) was applied to water molecules that were more than
+% % $1.0$~\textsf{nm} away from the center of the simulation box. In
+% % addition, a Parrinello-Rahman barostat was couple to the system with a
+% % time-scale of $\tau_{\textrm{P}} = 2.0~\textsf{ps}$.
 
-Let's consider an infinitely large NVE system (here we call it
-"universe"). Some interesting process is happening in a small
-subsystem. For equilibrium phenomena, this subsystem is the usually
-considered as NVT (or NPT, $\mu$VT, depends on how the question is
-raised) system.  In simulations, we only simulate the subsystem and
-use the thermostat to mimic the embedment into the universe.  For
-non-equilibrium simulation, we also want to simulate only the
-subsystem of interest, but the physical meaning of directly applying a
-thermostat designed for generating equilibrium ensemble is not clear
-to a non-equilibrium process. Moreover, there is no unique way of
-defining how the subsystem is coupled into the universe: It is subject
-to how the perturbation comes into the subsystem, and how the energy
-of the system dissipates into the universe. In the case of switching on
-electric field system, two limiting scenarios are considered by us: (1)
-The subsystem is isolated from the universe: The electric field is
-applied to a system that conserves the energy, volume and number of
-particle (i.e. a NVE subsystem in short).  The isolation here means
-that the subsystem does not exchange energy, volume and number of
-particle with the universe, but the perturbation (electric field) does
-come in to the subsystem.  The periodic boundary condition is applied
-here only to avoid the difficulty of defining a experimental
-meaningful boundary in simulation.  In this scenario, the size the
-subsystem is somewhat arbitrary (it depends on experimental setting),
-therefore, it is important to consider the convergence of the
-simulation result with respect to the size of the subregion.  (2) The
-system exchange the energy, volume and particle with the universe, and
-the universe is so big that the perturbation in the subsystem will not
-kick the universe from equilibrium.  In practice, it is impossible to
-simulate the infinite large universe, Instead, we want to simulate the
-considerably smaller subsystem instead.  The idea is to divide the
-simulation region into two parts (see Fig.~\ref{fig:tmp2}): the first
-is called \emph{Newtonian dynamics region} that is a region around the
-molecule of interest, where the dynamics is Newtonian. Note that the
-molecular trajectories in the Newtonian dynamics region are the same
-as if it were couple to the universe, only when a proper boundary
-condition is provided. Strictly speaking, the boundary should be
-provided by the out side infinitely large universe, which immediately
-leads back to the numerical difficulty of simulating a infinite large
-system. However, we notice that the detailed information
-(i.e. position and velocity) of the every molecule outside the
-Newtonian dynamics region is not relevant to the non-equilibrium
-behavior of the molecule of interest, because we are only interest in
-the non-equilibrium averages, which does not depends on the individual
-trajectory, but on the trajectorial ensemble sampled by the
-non-equilibrium simulation.  Therefore, the universe, as a boundary to
-the Newtonian dynamics region, can be replace by
-an efficiently thermo- and barostated subsystem, as indicated by the gray
-part of Fig.~\ref{fig:tmp2}. 
-% That is to say the subsystem is coupled to a
-% thermostat, a barostat and a particle bath with infinitely high
-% efficiency. Practically, it is impossible to simulation with a
-% ``infinitely fast'' thermostat, barostat and particle bath.
-We indicate the radius of the Newtonian dynamics region by
-$R_{\textrm{ex}} = 1~\textsf{nm}$ (see Fig.~\ref{fig:tmp2} for
-explanation), and couple it to very sufficient thermo- and
-barostat. We use a Langevin thermostat coupled to the thermostating
-region with a time-scale of $\tau_{T} = 0.1~\textsf{ps}$, and a
-Parrinello-Rahman barostat with a time-scale of $\tau_{P} =
-2.0~\textsf{ps}$.
+% Let's consider an infinitely large NVE system (here we call it
+% "universe"). Some interesting process is happening in a small
+% subsystem. For equilibrium phenomena, this subsystem is the usually
+% considered as NVT (or NPT, $\mu$VT, depends on how the question is
+% raised) system.  In simulations, we only simulate the subsystem and
+% use the thermostat to mimic the embedment into the universe.  For
+% non-equilibrium simulation, we also want to simulate only the
+% subsystem of interest, but the physical meaning of directly applying a
+% thermostat designed for generating equilibrium ensemble is not clear
+% to a non-equilibrium process. Moreover, there is no unique way of
+% defining how the subsystem is coupled into the universe: It is subject
+% to how the perturbation comes into the subsystem, and how the energy
+% of the system dissipates into the universe. In the case of switching on
+% electric field system, two limiting scenarios are considered by us: (1)
+% The subsystem is isolated from the universe: The electric field is
+% applied to a system that conserves the energy, volume and number of
+% particle (i.e. a NVE subsystem in short).  The isolation here means
+% that the subsystem does not exchange energy, volume and number of
+% particle with the universe, but the perturbation (electric field) does
+% come in to the subsystem.  The periodic boundary condition is applied
+% here only to avoid the difficulty of defining a experimental
+% meaningful boundary in simulation.  In this scenario, the size the
+% subsystem is somewhat arbitrary (it depends on experimental setting),
+% therefore, it is important to consider the convergence of the
+% simulation result with respect to the size of the subregion.  (2) The
+% system exchange the energy, volume and particle with the universe, and
+% the universe is so big that the perturbation in the subsystem will not
+% kick the universe from equilibrium.  In practice, it is impossible to
+% simulate the infinite large universe, Instead, we want to simulate the
+% considerably smaller subsystem instead.  The idea is to divide the
+% simulation region into two parts (see Fig.~\ref{fig:tmp2}): the first
+% is called \emph{Newtonian dynamics region} that is a region around the
+% molecule of interest, where the dynamics is Newtonian. Note that the
+% molecular trajectories in the Newtonian dynamics region are the same
+% as if it were couple to the universe, only when a proper boundary
+% condition is provided. Strictly speaking, the boundary should be
+% provided by the out side infinitely large universe, which immediately
+% leads back to the numerical difficulty of simulating a infinite large
+% system. However, we notice that the detailed information
+% (i.e. position and velocity) of the every molecule outside the
+% Newtonian dynamics region is not relevant to the non-equilibrium
+% behavior of the molecule of interest, because we are only interest in
+% the non-equilibrium averages, which does not depends on the individual
+% trajectory, but on the trajectorial ensemble sampled by the
+% non-equilibrium simulation.  Therefore, the universe, as a boundary to
+% the Newtonian dynamics region, can be replace by
+% an efficiently thermo- and barostated subsystem, as indicated by the gray
+% part of Fig.~\ref{fig:tmp2}. 
+% % That is to say the subsystem is coupled to a
+% % thermostat, a barostat and a particle bath with infinitely high
+% % efficiency. Practically, it is impossible to simulation with a
+% % ``infinitely fast'' thermostat, barostat and particle bath.
+% We indicate the radius of the Newtonian dynamics region by
+% $R_{\textrm{ex}} = 1~\textsf{nm}$ (see Fig.~\ref{fig:tmp2} for
+% explanation), and couple it to very sufficient thermo- and
+% barostat. We use a Langevin thermostat coupled to the thermostating
+% region with a time-scale of $\tau_{T} = 0.1~\textsf{ps}$, and a
+% Parrinello-Rahman barostat with a time-scale of $\tau_{P} =
+% 2.0~\textsf{ps}$.
 
-The non-equilibrium steady temperature and pressure of the
-non-thermostated simulation are $330$ K and $-500$ Bar,
-correspondingly. Those of the thermostated system are $300$ K and 1
-Bar, correspondingly. Therefore, we can see from Fig.~\ref{fig:tmp6}
-that the relaxation of the thermostated system is faster than the
-non-thermostated system. The three time-scale of metastable population
-dynamics in the thermostated system is consistent with that of the
-non-thermostated system. This means that thermostating, in this case,
-does not qualitatively change the population dynamics of metastable
-states.
+% The non-equilibrium steady temperature and pressure of the
+% non-thermostated simulation are $330$ K and $-500$ Bar,
+% correspondingly. Those of the thermostated system are $300$ K and 1
+% Bar, correspondingly. Therefore, we can see from Fig.~\ref{fig:tmp6}
+% that the relaxation of the thermostated system is faster than the
+% non-thermostated system. The three time-scale of metastable population
+% dynamics in the thermostated system is consistent with that of the
+% non-thermostated system. This means that thermostating, in this case,
+% does not qualitatively change the population dynamics of metastable
+% states.
 
-\begin{figure}
-  \centering
-  \includegraphics[]{fig.ala/fig-meta-stat-10.eps}
-  \caption{ Comparison between simulations with and without
-    temperature and pressure control at $t_{\textrm{init}} =
-    10~\textsf{ps}$. The The populations of the metastable sets as a
-    function of time are plotted.  The dashed vertical lines indicate
-    the three different time scale of metastable set population at
-    $t_{\textrm{init}} = 10~\textsf{ps}$.}
-  \label{fig:tmp6}
-\end{figure}
+% % \begin{figure}
+% %   \centering
+% %   \includegraphics[]{fig.ala/fig-meta-stat-10.eps}
+% %   \caption{ Comparison between simulations with and without
+% %     temperature and pressure control at $t_{\textrm{init}} =
+% %     10~\textsf{ps}$. The The populations of the metastable sets as a
+% %     function of time are plotted.  The dashed vertical lines indicate
+% %     the three different time scale of metastable set population at
+% %     $t_{\textrm{init}} = 10~\textsf{ps}$.}
+% %   \label{fig:tmp6}
+% % \end{figure}
 
-% To make the non-equilibrium feasible, we assume the
-% non-equilibrium process is \emph{local}, i.e. the non-equilibrium perturbation
-% of the system happens only locally, and the rest of the system
-% stays the unperturbed (usually assumed under ambient conditions).
-% This provides us the possibility of simulating only the small subsystem
-% of the universe: We can simulate only subsystem by providing proper
-% boundary condition for it, so that it behaves as if it were embeded into
-% the universe.
+% % To make the non-equilibrium feasible, we assume the
+% % non-equilibrium process is \emph{local}, i.e. the non-equilibrium perturbation
+% % of the system happens only locally, and the rest of the system
+% % stays the unperturbed (usually assumed under ambient conditions).
+% % This provides us the possibility of simulating only the small subsystem
+% % of the universe: We can simulate only subsystem by providing proper
+% % boundary condition for it, so that it behaves as if it were embeded into
+% % the universe.
 
-% \subsection{The water structure around methane under impluse }
-% In this study, we firstly consider the system of a methane molecule solvated
-% in the liquid water environment. A local density perturbation is implemented
-% by applying an impluse  in a shell surronding methane, see Fig.~\ref{fig:tmp1}.
-% % As far as we concerned, the situation is: we truncate the universe to the
-% % subsystem, and provide proper boundary condition for this
-% % subsystem.
-% Here we denote the size of this subsystem by $R_{\ex}$.
-% Notice this subsystem is simulated by the Newtonian
-% dynamics. If the size of the
-% subsystem is large enough so that the perturbation is
-% small enough when it travels to the boundary of the subsystem, then a
-% trivial boundary condition would be: coupling the system to a boundary
-% layer equilibriated by the thermostat (and barostat or particle reservior),
-% which mimics the infinitely large equilibrium universe.
+% % \subsection{The water structure around methane under impluse }
+% % In this study, we firstly consider the system of a methane molecule solvated
+% % in the liquid water environment. A local density perturbation is implemented
+% % by applying an impluse  in a shell surronding methane, see Fig.~\ref{fig:tmp1}.
+% % % As far as we concerned, the situation is: we truncate the universe to the
+% % % subsystem, and provide proper boundary condition for this
+% % % subsystem.
+% % Here we denote the size of this subsystem by $R_{\ex}$.
+% % Notice this subsystem is simulated by the Newtonian
+% % dynamics. If the size of the
+% % subsystem is large enough so that the perturbation is
+% % small enough when it travels to the boundary of the subsystem, then a
+% % trivial boundary condition would be: coupling the system to a boundary
+% % layer equilibriated by the thermostat (and barostat or particle reservior),
+% % which mimics the infinitely large equilibrium universe.
 
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.3\textwidth]{fig/kick.eps}
-%   \caption{Schematic plot of the density perturbation.}
-%   \label{fig:tmp1}
-% \end{figure}
+% % \begin{figure}
+% %   \centering
+% %   \includegraphics[width=0.3\textwidth]{fig/kick.eps}
+% %   \caption{Schematic plot of the density perturbation.}
+% %   \label{fig:tmp1}
+% % \end{figure}
 

### 2013-07-30 alanine.nanma/template/tools/average/app/integrate.file.cpp
add smooth and integrate files

@@ -1,0 +1,92 @@
+#include <algorithm>
+#include <fstream>
+#include <iomanip>
+#include <iostream>
+#include <iterator>
+#include <list>
+#include <map>
+#include <set>
+#include <sstream>
+#include <string>
+#include <queue>
+#include <vector>
+#include <cmath>
+#include <boost/program_options.hpp>
+#define MaxLineLength 10240
+
+#include "StringSplit.h"
+#include "BlockAverage.h"
+namespace po = boost::program_options;
+using namespace std;
+
+int main(int argc, char * argv[])
+{
+  std::string ifile, ofile;
+
+  po::options_description desc ("Allow options");
+  desc.add_options()
+      ("help,h", "print this message")
+      ("output,o", po::value<std::string > (&ofile)->default_value ("avg.h.bond.count.out"), "the output of count of h-bond")
+      ("input,f",  po::value<std::string > (&ifile)->default_value ("h.count.name"), "the file of file names");
+      
+  po::variables_map vm;
+  po::store(po::parse_command_line(argc, argv, desc), vm);
+  po::notify (vm);
+  if (vm.count("help")){
+    std::cout << desc<< "\n";
+    return 0;
+  }
+
+  std::ifstream fpname (ifile.c_str());
+  if (!fpname){
+    std::cerr << "cannot open file " << ifile << std::endl;
+    return 1;
+  }
+  std::vector<std::vector<double > > values;
+  std::ifstream fptraj (ifile.c_str());
+  char line [MaxLineLength];
+
+  while (fptraj.getline(line, MaxLineLength)){
+    if (line[0] == '#') continue;
+    std::string thisline (line);
+    std::vector<std::string > words;
+    StringOperation::split (thisline, words);
+    std::vector<double > lineValues;
+    for (unsigned ii = 0; ii < words.size(); ++ii){
+      lineValues.push_back(atof(words[ii].c_str()));
+    }
+    values.push_back(lineValues);
+  }
+  fptraj.close();
+
+  std::vector<std::vector<double > > sums (values.size());
+  for (unsigned ii = 0; ii < values.size(); ++ii){
+    for (unsigned jj = 0; jj < values[ii].size(); ++jj){
+      sums[ii].resize (values[ii].size());
+      if (ii == 0){
[…]

### 2013-07-30 alanine.nanma/template/tools/average/app/smooth.file.cpp

@@ -1,0 +1,83 @@
+#include <algorithm>
+#include <fstream>
+#include <iomanip>
+#include <iostream>
+#include <iterator>
+#include <list>
+#include <map>
+#include <set>
+#include <sstream>
+#include <string>
+#include <queue>
+#include <vector>
+#include <cmath>
+#include <boost/program_options.hpp>
+#define MaxLineLength 10240
+
+#include "StringSplit.h"
+#include "BlockAverage.h"
+namespace po = boost::program_options;
+using namespace std;
+
+int main(int argc, char * argv[])
+{
+  std::string ifile, ofile;
+
+  po::options_description desc ("Allow options");
+  desc.add_options()
+      ("help,h", "print this message")
+      ("output,o", po::value<std::string > (&ofile)->default_value ("avg.h.bond.count.out"), "the output of count of h-bond")
+      ("input,f",  po::value<std::string > (&ifile)->default_value ("h.count.name"), "the file of file names");
+      
+  po::variables_map vm;
+  po::store(po::parse_command_line(argc, argv, desc), vm);
+  po::notify (vm);
+  if (vm.count("help")){
+    std::cout << desc<< "\n";
+    return 0;
+  }
+
+  std::ifstream fpname (ifile.c_str());
+  if (!fpname){
+    std::cerr << "cannot open file " << ifile << std::endl;
+    return 1;
+  }
+  std::vector<std::vector<double > > values;
+  std::ifstream fptraj (ifile.c_str());
+  char line [MaxLineLength];
+
+  while (fptraj.getline(line, MaxLineLength)){
+    if (line[0] == '#') continue;
+    std::string thisline (line);
+    std::vector<std::string > words;
+    StringOperation::split (thisline, words);
+    std::vector<double > lineValues;
+    for (unsigned ii = 0; ii < words.size(); ++ii){
+      lineValues.push_back(atof(words[ii].c_str()));
+    }
+    values.push_back(lineValues);
+  }
+  fptraj.close();
+
+  
+  FILE * fout = fopen (ofile.c_str(), "w");
+  for (unsigned ii = 0; ii < values.size(); ++ii){
+    if (ii == 0 || ii == values.size()-1){
+      for (unsigned jj = 0; jj < values[ii].size(); ++jj){
+	fprintf (fout, "%f  ", values[ii][jj]);
+      }
+      fprintf (fout, "\n");
[…]

### 2013-08-04 alanine.nanma/template/tools/scripts/cal.flux.mat.sh
fix bug

@@ -3,6 +3,12 @@
 file="meta.flux.inte.out"
 up=1000
 lo=600
+if test $# -ge 1; then
+    lo=$1
+fi
+if test $# -ge 2; then
+    up=$2
+fi
 
 echo "# doing linear fitting in [$lo:$up]"
 

### 2013-08-04 writedown/npt-neq/alanine.tex
back up

@@
 
-\title{The non-equilibrium molecular dynamics simulation of the alanine dipeptide under electric field}
+\title{Exploring Molecular Conformations and Related Time Scales via Nonequilibrium Molecular Dynamics Simulation}
+% \title{The non-equilibrium molecular dynamics simulation of the alanine dipeptide under electric field}
 \author{Han Wang}
@@
 understanding the behavior of a protein (or a short peptide segment)
-in both static and oscilatatory electiric
+in both static and oscillatory electiric
 fields~\cite{budi2005electric, budi2007effect, budi2008comparative,
@@
 such as relaxing process to the new conformations under static
-electiric field, and the dynamics under oscilatating electric field.
+electiric field, and the dynamics under oscillating electric field.
 
@@
 property flux) are introduced. The numerical results of alanine
-dipeptide under static and sine-shaped oscilatating electric field are
+dipeptide under static and sine-shaped oscillating electric field are
 presented. By calculating the nonequilibrium properties from the D-NEMD
@@
 
-\subsection{Nonequilibrium temperature control}
+\subsection{Nonequilibrium temperature control}\label{sec:tmp2b}
 
@@
   % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
-  \includegraphics[]{fig.ala/fig-field-dipol.eps}
+  \includegraphics[]{fig.ala/field.dipole/fig-field-dipol-conf.eps}
+  % \\
+  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a1-1.eps}
+  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a2-1.eps}
+  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b1-1.eps}
+  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b2-1.eps}
+  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/c-1.eps}
   \caption{The magnitude of the external electric field, and the
@@
 \begin{align}
-  p_I(t) = \mathbb P (\vect x_t \in I), \quad  I \in \{A_1, A_2, B_1, B_2, C\},
+  P_I(t) = \mathbb P (\vect x_t \in I), \quad  I \in \{A_1, A_2, B_1, B_2, C\},
 \end{align}
@@
 state $I$.
-Secondly, we study the
-forward and backward transition probability of the metastable conformations, which is defined by
+% Secondly, we study the
+% forward and backward transition probability of the metastable conformations, which is defined by
+% \begin{align}
+%   P^{\fwd}_{J,I}(t) & = \mathbb P( \vect x_{t+\Delta t} \in J | \vect x_t \in I) \\
+%   P^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J | \vect x_t \in I) 
+%   % \qquad I, J \in \{A_1, A_2, B_1, B_2, C\},
+% \end{align}
+% where $\Delta t$ is the time-scale of the observation.
+% For a revserible and homogeneous Markov process, it is easy to show
+% that $P^{\fwd}_{J,I} = P^{\bwd}_{J,I}$, and both of them are time independent. For a general nonequilibrium
+% process considered by the present work, this relation is genarlly not guarenteed.
+Secondly,
+we study the net probability flux from metastable set $I$ to $J$, defined by:
+\begin{align}\label{eqn:tmp7}
+  F_{J,I}(t) & =\lim_{\Delta t\rightarrow 0} \frac1{\Delta t} [\mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I) - \mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J)].
+\end{align}
+which prensents the rate of how much conformation $J$ is changed
+into $I$. A positive value indicates the
+flux from $J$ to $I$, while a negative value indicates a flux from $I$ to $J$.
+Now if project the proccess $\vect x_t$ onto the discretized states $\{A_1, A_2, B_1, B_2, C\}$. If the
+project proccess is time-reversible, then it is obvious that
+$ F_{J,I}(t) = 0$. In an other word, the quantity $ F_{J,I}(t) $ represents
+the irreversibility of the conformational change observed in the discretized space $\{A_1, A_2, B_1, B_2, C\}$.
+In practive, to measure $ F_{J,I}(t)$, one need firstly approximate the limit
+in Eq.~\eqref{eqn:tmp7} by finite difference, then the joint probabilities on
+the right-hand-side can be calculated from the molecular trajectories.
+If one wants a precise finite difference approximation, a smaller $\Delta t$ is
+better, but then the statistical uncertainty of measuring the joint probabilities
+is higher. We use a $\Delta t$ that is small enough for a precise finite difference
+approximation, and not too small so that the joint probabilities can be measured
+properly.
+In the oscillating EF case, the net probability flux is also highly oscillating,
+so it is convenient to study the integrated probability flux:
 \begin{align}
-  P^{\fwd}_{J,I}(t) & = \mathbb P( \vect x_{t+\Delta t} \in J | \vect x_t \in I) \\
-  P^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J | \vect x_t \in I) 
-  % \qquad I, J \in \{A_1, A_2, B_1, B_2, C\},
+  Q_{J,I} (t) = \int_0^t F_{J,I}(\tau)d \tau,
 \end{align}
-where $\Delta t$ is the time-scale of the observation.
-For a revserible and homogeneous Markov process, it is easy to show
-that $P^{\fwd}_{J,I} = P^{\bwd}_{J,I}$, and both of them are time independent. For a general nonequilibrium
-process considered by the present work, this relation is genarlly not guarenteed. Finally, we study the backward net flux from metastable set $I$ to $J$:
-\begin{align}
-  F^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I) - \mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J).
-\end{align}
-Unlike the transition probabilities that are defined by the conditional
-probability, the net flux is defined by the difference between
-two joint probabilities, and prensents how much conformation $J$ is changed
-into $I$ in the past $\Delta t$ interval. A positive value indicates the
-flux from $J$ to $I$, while a negative value indicates a flux from $I$ to $J$.
+which presents the time averaged effect of the EF to the molecular conformation.
 
@@
   \centering
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-1.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-2.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-3.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-4.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-5.eps}\\
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-1.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-2.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-3.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-4.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-5.eps}\\
   % \caption{The populations of the metastable sets as a function of time.
@@
   % metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-1.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-2.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-3.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-4.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-5.eps}\\
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-1.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-2.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-3.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-4.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-5.eps}\\
   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-1.eps}
@@
   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-4.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-5.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-5.eps}\\
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-1.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-5.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-1.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-2.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-3.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-4.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-5.eps}\\
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-1.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-2.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-3.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-4.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-5.eps}
   \caption{Forward and backward nonequilibrium transition probability of the case $t_{init} = 10$~ps.}
@@
 
+\subsection{Testing the finite-size effect}
+
 \begin{figure}
@@
 
+Just described in Sec.~\ref{sec:tmp2b}, we perform nonequilibrium MD
+simulations in a finite size periodic system, and further divided it
+into a Hamiltonian dynamics region and a thermostating region.
+Since the periodic boundary condition and the division of the system
+are artificial, 
+we want to understand the finite-size effect of
+these settings and the their influence to the simulation result.
+Therefore, we
+perform two additional simulations: one has box size $L=4.0$~nm and a
+Hamiltonian dynamics region of radius $R_{ex} = 1.0$~nm, while the
+other has box size $L=4.0$~nm and a Hamiltonian dynamics region of
+radius $R_{ex} = 1.5$~nm, and compare them to the system
+we used before, i.e. $L=2.7$~nm and $R_{ex} = 1.0$~nm.
+Fig.~\ref{fig:tmp7} presents very good consistency of
+the simulation results of the three systems, so the finite-size effect is
+actually negligible in the system we used in the previous sections.
+
+\section{Example II:
+  periodically oscillating electric field}
+
+We have tested the periodically oscillating electric field which has
+a $\sin$-wave shape:
+\begin{align}
+  E(t) = E_0\sin(2\pi \omega t),
+\end{align}
+where $E_0$ is the strength of the field, which is chosen to be
+1.0~V/nm.  $\omega$ is the frequency of the field, which is related to
+the period $T$ by $\omega = 1/T$.  Here we tested three different
+periods: 10, 40 and 200.  the periods of the later two are
+commensurate to the time scales discovered by the nonequilibrium MD
+simulation of constant electric field. The first is to test the if the
+period is further reduced to smaller than 20~ps, there is any other
+timescale of interest would play a role. Although the periods are
+chosen according to the discovered time scales in the constant
+electric field simulation, the nonequilibrium phenonema of oscillating
+electric field cannot fully derived from the constant field system.
+As far as the electric field changes, the internal time scale of the
+system also changes, therefore, the nonequilibrium probabilities is a
+complicated interplay of different internal time scales under
+different electric fields. We do not try to theoretically predict
+what will happen under the oscillating EF by a series constant EF simulation
+revealing the internal dynamics under different strength of EF, but just directly
+do the nonequilibrium MD simulation for the oscillating EF, and discuss
+the observed phenonema.
+
 \begin{figure}
   \centering
-  \includegraphics[]{fig.ala/fig-meta-mode2-010.eps}
-  \includegraphics[]{fig.ala/fig-meta-mode2-040.eps}
-  \includegraphics[]{fig.ala/fig-meta-mode2-200.eps}
-  \caption{The populations of the metastable sets as a function of time.
-    The dashed vertical lines indicate the three different time scale of
-  metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
-  \label{fig:tmp5}
+  \includegraphics[]{fig.ala/fig-mode2-dipol.eps}
+  \caption{The nonequilibrium dipole moment of alanine dipeptide as a
+    function of time. Only the $x$-component of the dipole moment is
+    shown here. The black line: the static electric field with turning on
+    time $t_{init} = 10$~ps. The red line: oscillating field with period
+    10~ps. The green line: period 40~ps. The blue line: period 200~ps.}
+  \label{fig:tmp8}
 \end{figure}
+
+Fig.~\ref{fig:tmp8} presents the $x$-component of the dipole moment as
+a function of time. The red, green and blue lines stands for the
+results of $T=10$~ps, 40~ps and 200~ps, respectively. The black lines
+shows the dipole moment of constant electric field with
+$t_{init}=10$~ps for reference. It demonstrates that for all periods
+investigated, the alanine can adjust it's direction, which defined by
+the direction of average dipole, according to the external electric
+field almost immediately. At $T=200$~ps, the maximum magnitude of the
+dipole moment is almost the same as the constant electric field, which
+means that the changing of the electric field is so slow that the
+alanine have enough time to fully relax the internal dipole. However,
+for $T=40$~ps and $T=10$~ps, when the electric field changes faster,
+although the molecules can align to the electric field immediately,
+but it does not have enough time to relax the internal dipole, so we
+see the maximum alanine's dipole moment reached is smaller for the shorter
+period.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.32\textwidth]{fig.ala/fig-meta-mode2-0010.eps}
+  \includegraphics[width=0.32\textwidth]{fig.ala/fig-meta-mode2-0040.eps}
+  \includegraphics[width=0.32\textwidth]{fig.ala/fig-meta-mode2-0200.eps}
+  % \includegraphics[width=0.49\textwidth]{fig.ala/fig-meta-mode2-2000.eps}
+  \caption{ The probability of being in a certain metastable state for
+    periodically oscillating electric field. Different periods,
+    i.e. $T=10$~ps, 40~ps and 200~ps, are presented here.  The
+    probability of being in a certain metastable state $I$, which is
+    denoted by $P_I$ in this paper, is ploted by colored lines against
+    time. The red line: $I = A_1$, the green line: $I = A_2$, the dark
+    blue line: $I = B_1$, the pink line: $I = B_2$ and the light blue
+    line: $I = C$. For $T=10$~ps and 40~ps, the nonequilibrium
+    simulations of time 1000~ps are presented, while for $T=200$~ps,
+    nonequilibrium simulations of tiem 3200~ps is presented.  }
+  \label{fig:tmp9}
+\end{figure}
+
+\begin{figure}
+  \centering
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-flux-1.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-flux-2.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-flux-3.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-flux-4.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-flux-5.eps}\\
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-1.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-5.eps}\\
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-flux-1.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-flux-2.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-flux-3.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-flux-4.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-flux-5.eps}\\
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-1.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-5.eps}\\
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-flux-1.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-flux-2.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-flux-3.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-flux-4.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-flux-5.eps}\\
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-1.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-5.eps}\\
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-flux-1.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-flux-2.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-flux-3.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-flux-4.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-flux-5.eps}\\
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-iflux-1.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-iflux-2.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-iflux-3.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-iflux-4.eps}
+  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-iflux-5.eps}
+  \caption{
+    Integrated probability flux $Q_{J,I}(t)$ of the periodically
+    oscillating EF is plotted against time. The unit of the
+    time (horizontal axises) is picosecond.
+    The integrated
+    probability flux is defined by $Q_{J,I}(t) = \int_0^t F_{J,I}(\tau) d\tau$, where
+    $F(t)$ is the net probability flux from metastable set $I$ to $J$.
+    From up to down the rows present period 10, 40 and 200~ps, respectively.
+    From left to right, the five
+    columes show integrated flux $Q_{J,A_1}$, $Q_{J,A_2}$,
+    $Q_{J,B_1}$, $Q_{J,B_2}$ and $Q_{J,C}$, respectively. In each plot,
+    the red line stands for $J=A_1$, green for $J=A_2$, dark blue for $J=B_1$,
+    purple for $J=B_2$ and light blue for $J=C$. In a certain time interval,
+    if the integrated flux $Q_{J,I}$ increases, then there exist a (time-averaged)
+    non-zero net flux from metastable set $I$ to $J$.
+  }
+  \label{fig:tmp10}
+\end{figure}
+
+The Fig.~\ref{fig:tmp9} shows the probability of being in a certain
+metastable state for periodically oscillating electric field.  The
+Fig.~\ref{fig:tmp10} presents the integrated probability flux of among
+the metastable sets.
+When the period is small, i.e. $T=10$~ps and
+40~ps, the observed phenonema in the figures are basically the same.
+The pobability in $A_1$, $A_2$, $B_1$ and $B_2$ does not change
+too much with respect to time,
+however, the probability in metastable set $C$ astonishingly
+increase to approximately 0.17 for $T=10$~ps  and 0.27 for  $T=10$~ps.
+Notice that in the constant EF case, although the dipole moment is
+bigger than the  $T=40$~ps case (see Fig.~\ref{fig:tmp8}), the
+probability of being in $C$ is indeed lower.  
+The time needed to reach a steady state is
+roughly 400~ps that is the same as the
+constant EF case. Fig~\ref{fig:tmp10} shows some ever increasing
+integrated probability fluxes, which imply some ever lasting and directional
+flux among the metastable sets, see
+Fig.~\ref{fig:tmp11} that presents a schematic plot of the probability
+fluxes for $T=10$~ps. The probability flux of  $T=40$~ps is roughly
+the same as $T=10$~ps, expect that
+the flux from $B_2 $ to $A_1$ does not exist. 
+This demonstrate a interesting phenonemon: the oscillating EF 
+generates a directional probability flux among the metastable sets.
+Moreover, some loops of the flux are detected: $A_1 \rightarrow B_1
+\rightarrow B_2 \rightarrow A_2 \rightarrow A_1$, $A_1 \rightarrow B_1
+\rightarrow B_2 \rightarrow A_1$,  $A_1 \rightarrow B_1
+\rightarrow B_2 \rightarrow C \rightarrow A_1$ and $B_1
+\rightarrow B_2 \rightarrow C \rightarrow B_1$.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.3\textwidth]{fig.ala/graphs/graph-t0010.eps}
+  \caption{The schematic plot of the main probability flux among the metastable
+    states on the Ramachandran histogram
+    for periodically oscillating EF, $T=10$~ps. The thickness 
+    of the arrows approximately presnets the strength of the flux.
+  }
+  \label{fig:tmp11}
+\end{figure}
+
+When the period is $T=200$~ps, the phenonema are substentially different
+from the high frequency cases ($T=10$ and 40~ps). Firstly, from Fig.~\ref{fig:tmp9}, the system reaches staedy state after around 2000~ps, while
+Fig.~\ref{fig:tmp10} suggests an even long time scale, but we cannot draw
+a very clear conclusion on it
+due to the lack of computational power to perform even longer simulations. 
+The steady probability of being in state $C$ is roughly the same as the
+case of $T=40$~ps, although the maximum dipole moment is actually higher
+than the latter. And the steady probability  of being in state $C$ is
+also higher than the constant EF case, even the maximum dipole are roughly
+the same. The time spend to reach the steady state is much longer than
+the higher frequency cases, so this indicates a \emph{dynamically} longer time
+scale in the system, comparing with the static EF case, in which all time scales
+are actually decided by the \emph{static} external field. We also observe
+a suden change in the probability flux from set $A_2$ to $A_1$ at
+around 1600~ps, which may imply a \emph{dynamically} rare event.
+Since we do not have the computer power to perform even longer simulations,
+this hypothesis is not further checked.
 

### 2013-08-06 writedown/npt-neq/alanine.tex
back up, first finished version

@@
 The possible effect of the electric field (EF) on the conformation of
-proteins gains increasing attantion recently, because it closly
+proteins gains increasing attention recently, because it closely
 related to the health problem of exposing human tissue in the
 electromagnetic radiation. Despite the importance of this problem, a
-complete understanding of how the electric field influnece the  protein
-is still lacking, therefore, a conserderable number of
+complete understanding of how the electric field influence the  protein
+is still lacking, therefore, a considerable number of
 experimental~\cite{bohr2000microwave, bohr2000microwave-1,
@@
 understanding the behavior of a protein (or a short peptide segment)
-in both static and oscillatory electiric
+in both static and oscillatory electric
 fields~\cite{budi2005electric, budi2007effect, budi2008comparative,
@@
 a few to tens of nanoseconds, during which the interested
-conformational chanages can be observed. Along the trajectories, the
+conformational changes can be observed. Along the trajectories, the
 secondary structure, root mean square displacement (RMSD), the dipole
@@
 whole simulation. This approach release useful information on how the
-secondary structure is changed by external electiric field.  However,
+secondary structure is changed by external electric field.  However,
 by plotting the quantities against time, one may observe strong
@@
 such as relaxing process to the new conformations under static
-electiric field, and the dynamics under oscillating electric field.
+electric field, and the dynamics under oscillating electric field.
 
-The dynamical nonequilibrium molecular dyanmics simulation (D-NEMD)
+The dynamical nonequilibrium molecular dynamics simulation (D-NEMD)
 was firstly developed by G. Ciccotti and his
@@
 nonequilibrium observables by doing an ensemble of nonequilibrium MD
-simualtions.  This provides a promising way of analysing the
+simulations.  This provides a promising way of analyzing the
 conformational changing under a generally time-dependent electric
@@
 nonequilibrium properties from the well-studied single peptides.
-Secondly, the current computationl resource available is not enought
-to study peptide chains by D-NEMD, since one needs to simualte an
+Secondly, the current computational resource available is not enough
+to study peptide chains by D-NEMD, since one needs to simulate an
 ensemble of MD trajectories (typically a few thousands), so it
@@
 simulations, we are able to answer from which to which the conformation
-changes, when do these changes happend, and how strong are the changes.
+changes, when do these changes happens, and how strong are the changes.
 As far as we know, our simulation is the first D-NEMD simulation
@@
 \end{align}
-where $\hat O (\vect x)$ is the microscopic observable. Compared with
-the macroscopic observable, it is measured at the phase space position $\vect x$.
-The bracket on the right hand side denotes the inner produce in the
+where $\hat O (\vect x)$ is the microscopic observable, 
+which is measured at the phase space position $\vect x$,
+comparing with the macroscopic observable that is not phase space independent.
+In this work, we always assume that the initial probability distribution
+$\rho(\vect x, 0)$ is known, and is equal to the equilibrium distribution
+without any electric field.
+The bracket on the right hand side of Eq.~\eqref{eqn:tmp1} denotes the inner produce in the
 phase space.  We assume the dynamics of the system is governed by the
 Hamiltonian equation, i.e. $\dot {\vect x} = J \cdot \nabla_{\vect x}
-\mathcal H(\vect x)$, where $\mathcal H$ is the Hamiltonian and $J$ is
+\mathcal H(\vect x)$, where $\mathcal H$ is the Hamiltonian, and $J$ is
 the symplectic matrix, then the Liouville equation of the probability
@@
 \end{align}
-where $iL(t) = \{\cdot, \mathcal H\}$ is the Liouville operator and
-$\mathcal H$ is the Hamiltonian of the system. The Eq.~\eqref{eqn:tmp2}
+where $iL(t) = \{\cdot, \mathcal H\}$ is the Liouville operator.
+The Eq.~\eqref{eqn:tmp2}
 can be formally solved by $\rho(\vect x, t) = e^{-iL(t)} \rho(\vect x, 0)$.
@@
 \end{align}
-If the inital state of the system is in equilibrium, i.e. the initial
-probability distribution is the equilibrium distribution. Then an
+Since we assume that the initial
+probability distribution is the equilibrium distribution, an
 explicit translation of Eq.~\eqref{eqn:tmp4} is that the
-nonequilibrium observable is equal to the ensenble average of
+nonequilibrium observable is equal to the ensemble average of
 microscopic observable measured along trajectory $\vect x(t)$, the
-inital configuration of which is subject to the equilibrium
+initial configuration of which is subject to the \emph{equilibrium}
 distribution. In practice, we firstly run an equilibrium MD simulation
-to generate a collection of configurations that are subject to the
+to generate a sampling of configurations that are subject to the
 equilibrium distribution. And then by using these configurations as
-inital configuration, the Hamiltonian dynamicses are integrated until
+initial configuration, the Hamiltonian dynamics are integrated until
 time $t$. These trajectories are also called \emph{branching
-  trajectories} in this paper. Finially, the macroscopic observable is
+  trajectories} in this paper. Finally, the macroscopic observable is
 estimated by averaging the microscopic observable measured at the end
@@
 
-Being more gneralize, if the microscopic depends not only on the end
-configuation of at time $t$ but also depends on the historical
-configurations along the trajectory, the experssion~\eqref{eqn:tmp4} can be generalize to
+Being more generalized, if the microscopic observable depends not only on the end
+configuration at time $t$ but also depends on the historical
+configurations along the trajectory, the expression~\eqref{eqn:tmp4} can be generalize to
 \begin{align}
@@
 set of all continuous trajectories starting at point $\vect x$ at time
-0, and ending at time $t$. $\mathcal P[\vect x_s] $ is the meansure of
+0, and ending at time $t$. $\mathcal P[\vect x_s] $ is the measure of
 the trajectory space $\mathcal C$.  In our case, it is the
-$\delta$-function peaked around the trajectory generated by the
+$\delta$-function peaked around the trajectories governed by the
 Hamiltonian dynamics. To be general, it can also be the measure of all
@@
 
-The aformentioned nonequilibrium molecular dynamicses simulation algorithm
-does not describe how the boundary of the system should be set up. The 100\% save
-method is to simulate a infinitely large isolated system, or any large enough
+The aforementioned nonequilibrium molecular dynamics simulation algorithm
+does not describe how the boundary of the system should be set up.
+The very naive idea of doing the simulation
+is to simulate a infinitely large isolated system, or any large enough
 isolated subsystem of it. In practice, it is both impossible and unnecessary to
-do such a simulation. In practice, proper boundary condition should be developped
-based on how the nonequilibrium system is set up, and what are the nonequilibrium
-observables to measure.
-Since we are mainly interested in the nonthermal~\cite{delaHoz2005microwaves} effect of
-the electric field to the configuration of a solvated alanine dipeptide,
-we assume the alanine is embeded into an infinitely large solvent envrionment,
-and the electric field is only applied to the neighborhood of the alanine.
-Therefore, 
-extra heat generated by turing on the electric field can be effectively absorbed
-by the envrionment.
-It is argued that 
-an accurate reaction temperature control is essential for being able to perform
-reproducible experiments~\cite{damm2012can}.
+do such a simulation, due to the unaffordable computational expense.
+Therefore, proper boundary condition should be supplied
+to truncated the simulation region. It is only possible when we
+have a clear knowledge on
+on how the nonequilibrium system is set up,
+and what are the nonequilibrium observables to measure.
 
@@
 
-In practice, it is impossible to simulate an infinitely large
-environment.  For an equilibrium simulation, the solution is to couple
-the system to a thermostat, under which the canonical ensember can be
-sampled by only simulate a finite size system with periodic boundary
+Since we are mainly interested in the
+nonthermal~\cite{delaHoz2005microwaves} effect of the electric field
+to the configuration of a solvated alanine dipeptide, we assume the
+alanine is embeded into an infinitely large solvent environment, and
+the electric field is only applied to the neighborhood of the alanine.
+Any extra heat generated by the electric field can be effectively
+absorbed by the solvent environment.  It is argued that such an
+accurate reaction temperature control is essential for being able to
+perform reproducible experiments~\cite{damm2012can}.
+Now the question comes to how to truncate the solvent environment
+so that the system can be handled by the limited computer resource.
+% In practice, it is impossible to simulate an infinitely large
+% environment.
+For an equilibrium simulation, the solution is to couple
+the system to a thermostat, under which the canonical ensemble can be
+sampled by only simulating a finite size system with periodic boundary
 condition. For a nonequilibrium simulation, simply couple the system
@@
 effects in the nonequilibrium observations. To solve this problem, we
-observe that only the Hamiltonian dynamics of the alanine molecule
+observe that only preserving the Hamiltonian dynamics of the alanine 
 itself and the water molecules in the nearby solvation shell is
-crutial to the configuration change, while the detailed dynamics of
-the water molecules far away has less effect. Notice again we actually
-do not want to precisely calculate each trajectory starting from the
-initial configurations, but want to sample correctly the trajectory
-ensemble correctly, so that the nonequilibrium observable can be
-calculated correctly.  Therefore, instead of simulating an infinitely
+crucial to the interested nonequilibrium observable
+(in this work, it is the conformational change of alanine),
+while the detailed dynamics of
+the water molecules far away is of less importance. 
+Therefore, instead of simulating an infinitely
 large system, we only simulate a finite size system with periodic
@@
 subregions: Near the alanine dipeptide, the dynamics is kept to be
-Hamiltonian, and this subregion is called the Hamiltonian dynamics
-region. While far from the alanine, the dynamics of water is coupled
-to a Langevin thermostat, and this region is called the thermostating
-region (see Fig.~\ref{fig:tmp2}).  For simplicity, the Hamiltonian
+Hamiltonian, and this subregion is called \emph{the Hamiltonian dynamics
+region}. While far from the alanine, the dynamics of water is coupled
+to a Langevin thermostat, and this region is called \emph{the thermostating
+region} (see Fig.~\ref{fig:tmp2}).  For simplicity, the Hamiltonian
 dynamics region is assumed to be spherical, centered at the
 alpha-carbon of the alanine, and with radius of $R_{ex}$.  Further, we
-freeze the movment of the alpha-carbon, so that the alanine is always
+freeze the movement of the alpha-carbon, so that the alanine is always
 located at the center of the simulation region.  The validity of this
@@
 and the size of the Hamiltonian dynamics subregion, if they are
-reasonably large and the finite size effect does not play a role.
+reasonably large and the finite size effect does not play a dominating role.
+
+% Notice again we actually
+% do not want to precisely calculate each trajectory starting from the
+% initial configurations,
+% but want to correctly calculate the nonequilibrium observable,
+% we
 
@@
 
-We want to study the nonequilibrium properties of an alanine dipeptide
-under a changing electric field. As a model system, we study the
-a constant electric field. At time $t=0$~ps, the system
+In this section,
+we want to study the nonequilibrium properties of an alanine dipeptide
+under a constant EF. At time $t=0$~ps, the system
 has been fully equilibriated without any electric field. From $t=0$ to
-$t=t_{\textrm{init}}$, the electic field is switched on linearly, while
+$t=t_{\textrm{init}}$, the eclectic field is switched on linearly, while
 after $t=t_{\textrm{init}}$, the field is kept constant at
-$E_{\infty}$. Fig.~\ref{fig:tmp3} shows the three different
-cases considered in this work: $t_{\textrm{init}} = 10$, 100, and
-500~ps, and 
-in all cases the maximum strength of the electric field is
-$E_{\infty} = 1$~V/nm.
-The direction of this field is arbitarily chosen: along the
+$E_{\infty}$. In Fig.~\ref{fig:tmp3}, the dashed line shows the 
+cases considered in this work: $t_{\textrm{init}} = 10$~ps,
+and $E_{\infty} = 1$~V/nm.
+The direction of this field is arbitrarily chosen: along the
 $x$ direction. Since the dipole of the equilibrium configurations of
 alanine can be along any direction (see also Fig.~\ref{fig:tmp3} for
-the vanished initial dipole moment), applying the electric along x-axis is
+the vanished initial dipole moment), applying the electric along $x$-axis is
 not biased.
-The size of the system is $2.67\times 2.67\times
-2.67\, \textsf{nm}^3$, with one alanine dipeptide described by the CHARMM27 force field, and solved in 644 TIP3P
+The system is set up in a $2.7\times 2.7\times
+2.7\, \textsf{nm}^3$ periodic simulation region, with one alanine dipeptide
+described by the CHARMM27 force field, and solved in 644 TIP3P
 water molecules.
+The size of the  Hamiltonian dynamics region is $R_{ex} = 1.0$~nm.
 All simulations are performed by a home-modified GROMACS 4.5~\cite{pronk2013gromacs}.
 Firstly, an equilibrium NVT simulation of
-100~\textsf{nm} was performed with a Langevin thermostat (time-scale
+100~\textsf{ns} was performed with a Langevin thermostat (time-scale
 $\tau_T = 0.5~\textsf{ps}$) coupled to the system for constant
 temperature.  Along the trajectory, configurations were taken every
-5~\textsf{ps}.  They server as starting point of the branching
-trajectories. The branching trajectories were integrated by the
-Leap-frog scheme with the aformentioned nonequilibrium temperature control technique.  The
+50~\textsf{ps}, so we use 2000 initial configurations for each nonequilibrium
+MD simulation, if not stated otherwise.
+% They server as starting point of the branching
+% trajectories.
+The branching trajectories were integrated by the
+Leap-frog scheme with the aforementioned nonequilibrium
+temperature control technique.  The
 time step was $\Delta t = 0.002~\textsf{ps}$. The short-range
@@
 method was applied to calculate the electrostatic interaction in this
-periodic system. In the thermostating region, the original dyanmics was
+periodic system. In the thermostating region, the original dynamics was
 coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
@@
 the pressure at the ambient condition (1~Bar). Since the
-change of the system size is small and slow, it does not have an obviously effect on the
-dyanmics of the system.
+change of the system size is small and slow, the pressure control
+does not have an obviously effect on the
+dynamics of the system.
 
 \subsection{Metastable sets}
-
-On each branching trajectory, to easy the analysis, the conformation
-of the alanine dipeptide is plotted by the Ramachandran histogram, as
-shown in Fig.~\ref{fig:tmp4}. The equilibrium distribution of the
-conformation is given in the left plot, and the fully relaxed
-conformation at $E_{\infty} = 1$~V/nm is given in the right plot.  It is
-clear the conformations are populated in several clusters, and the
-position of the clusters do not change when the external electric
-field is applied. This means that only a few of the configurations are likely to be observed, while there is nearly
-no oppotunity to see others. 
-These configurations are called ``metastable states''. The strict definition of the
-metastability is not exactly the same as those conformations that are likely to be observed.
-Since in this paper we do not focus on the discussion of the definition for the metastability of the system,
-we assume they have the same meaning.
-We manually divide the
-$\psi$--$\phi$ plane into 5 subregions, see Fig.~\ref{fig:tmp4},
-then the observation on the Ramachandran histogram is projected to the
-observation of these 5 subregions.  These subregions
-correspond to different secondary structure of a peptide chain:
-$A_1$ and $A_2$ are
-corresponding to the alpha helix. $B_1$ and $B_2$ are
-corresponding to beta sheet. $C$ is corresponding to the
-left-handed alpha helix.
 
@@
   \includegraphics[width=0.45\textwidth]{fig.ala/ext.mode1.100.Ex.01.00.t1200ps/fig-end-1.eps}
-  \caption{The population of different metastable state.
-Left: the equilibrium state at $t=0$~\textsf{ps}.
-Right: The non-equilibrium study state at $t=1200$~\textsf{ps}, i.e., fully relaxed when the electric field is switched on.
-The darker color indicates larger population on the $\psi$--$\phi$ phase space.}
+  \caption{The population of metastable states of the alanine dipeptide.
+    Left: the
+    equilibrium state at $t=0$~\textsf{ps}. Right: The new equilibrium
+    state at $t=1000$~\textsf{ps}, i.e., fully relaxed under the
+    constant electric field 1~V/nm. The darker color
+    indicates larger population on the Ramachandran histogram.}
   \label{fig:tmp4}
@@
 
+On each branching trajectory, to easy the analysis of the conformation
+of alanine dipeptide, the molecular configuration is projected on
+the Ramachandran histogram, as
+shown in Fig.~\ref{fig:tmp4}. The equilibrium distribution of the
+conformation is given in the left plot, and the fully relaxed
+conformation under $E_{\infty} = 1$~V/nm is given in the right plot.  It is
+clear the conformations are populated in several clusters, and the
+position of the clusters do not change when the external electric
+field is applied.
+This means that only a few of the conformations are likely to be observed,
+while there is nearly no opportunity to see others. 
+These conformations are called ``metastable states''.
+The strict definition of the
+metastability is not exactly the same as those conformations that are likely to be observed.
+Since in this paper we do not focus on the discussion of the definition for the metastability of the system,
+we assume they have the same meaning.
+We manually divide the
+Ramachandran histogram into 5 subregions, see Fig.~\ref{fig:tmp4},
+then the observation on the Ramachandran histogram is projected to the
+observation of these 5 states, i.e. $\{A_1, A_2, B_1, B_2, C\}$, which
+correspond to the molecular conformations we are investigating in this work.
+These subregions
+correspond to different secondary structure of a peptide chain:
+$A_1$ and $A_2$ are
+corresponding to the alpha helix. $B_1$ and $B_2$ are
+corresponding to the beta sheet. $C$ is corresponding to the
+left-handed alpha helix.
+
 From Fig.~\ref{fig:tmp4}, it is obvious that the population in each
-metastable sets changes due to the external electric field, for
-example, the population of conformations C vanishes in equilibrium,
+metastable state changes due to the external electric field, for
+example, the population of state $C$ vanishes in equilibrium,
 but plays an important role when the electric field is applied. We
 therefore want to study how the alanine changes from one conformation
-to the other, how fast is the change, and the relation to the speed of
-the increasing electric field (i.e. the value of $t_{init}$). 
-Firly, we study the population of the metastable conformations
-Being more strict, we calculate the nonequilibrium observable
+to the other, how fast is the change, and the relations to the 
+the electric field. 
+Firstly, we calculate the probability of being in a certain state that
+is defined by:
 \begin{align}
@@
 \end{align}
-which is the time dependent probability of the alanine being in metastable
-state $I$.
+please notice that the time dependency of the probability, so it is
+a nonequilibrium observable.
+% which is the time dependent probability of the alanine being in metastable
+% state $I$.
 % Secondly, we study the
@@
 Secondly,
-we study the net probability flux from metastable set $I$ to $J$, defined by:
-\begin{align}\label{eqn:tmp7}
-  F_{J,I}(t) & =\lim_{\Delta t\rightarrow 0} \frac1{\Delta t} [\mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I) - \mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J)].
+we study the net probability flux from metastable state $I$ to $J$, defined by:
+\begin{align}\nonumber
+  F_{J,I}(t) & =\lim_{\Delta t\rightarrow 0} \frac1{\Delta t} [\mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I) - \mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J)], \\\label{eqn:tmp7}
+  & J,I \in \{A_1, A_2, B_1, B_2, C\}.
 \end{align}
-which prensents the rate of how much conformation $J$ is changed
+which presents the rate of how much conformation $J$ is changed
 into $I$. A positive value indicates the
-flux from $J$ to $I$, while a negative value indicates a flux from $I$ to $J$.
-Now if project the proccess $\vect x_t$ onto the discretized states $\{A_1, A_2, B_1, B_2, C\}$. If the
-project proccess is time-reversible, then it is obvious that
+net flux from $J$ to $I$,
+while a negative value indicates a net flux from $I$ to $J$.
+Now project the original nonequilibrium process $\vect x_t$
+onto the discretized states $\{A_1, A_2, B_1, B_2, C\}$,
+if the resulting reduced process 
+is time-reversible, then it is obvious that
 $ F_{J,I}(t) = 0$. In an other word, the quantity $ F_{J,I}(t) $ represents
-the irreversibility of the conformational change observed in the discretized space $\{A_1, A_2, B_1, B_2, C\}$.
-In practive, to measure $ F_{J,I}(t)$, one need firstly approximate the limit
-in Eq.~\eqref{eqn:tmp7} by finite difference, then the joint probabilities on
-the right-hand-side can be calculated from the molecular trajectories.
+the irreversibility of the reduced process on
+$\{A_1, A_2, B_1, B_2, C\}$.
+In practice, to measure $ F_{J,I}(t)$, one need firstly approximate the limit
+in Eq.~\eqref{eqn:tmp7} by the finite difference,
+then calculate the joint probabilities on
+the right-hand-side from the molecular trajectories.
 If one wants a precise finite difference approximation, a smaller $\Delta t$ is
-better, but then the statistical uncertainty of measuring the joint probabilities
-is higher. We use a $\Delta t$ that is small enough for a precise finite difference
-approximation, and not too small so that the joint probabilities can be measured
-properly.
+preferable,
+but then the statistical uncertainty of measuring the joint probabilities
+is higher. In practice,
+we use a $\Delta t$ that is small enough for a precise finite difference approximation,
+and not too small so that the joint probabilities can be calculated properly.
 In the oscillating EF case, the net probability flux is also highly oscillating,
@@
 
-\subsection{Results and discusstions}
+\subsection{Results and discussions}
 \begin{figure}
@@
   \includegraphics[]{fig.ala/fig-meta-npt.eps}
-  \caption{The populations of the metastable sets as a function of time.
-    The dashed vertical lines indicate the three different time scale of
-  metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
+  \caption{The probability of being in a metastable states under a constant EF.
+    The warm-up time $t_{init} = 10$~ps. The red line stands for state $A_1$,
+    green for $A_2$, dark blue for $B_1$, purple for $B_2$ and light blue
+    for $C$.
+  }
   \label{fig:tmp5}
@@
   % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-5.eps}
-  \caption{Forward and backward nonequilibrium transition probability of the case $t_{init} = 10$~ps.}
+  \caption{
+    The net probability flux and its integration under the constant EF case.
+    The warm-up time $t_{init} = 10$~ps.
+    The first row shows the probability flux $F_{J,I}(t)$, while the second
+    shows the integrated  probability flux denoted by $Q_{J,I}(t)$.
+    A constant $Q_{J,I}$ means vanishing net flux, while a increasing (deceasing)
+    $Q_{J,I}$ indicates positive (negative) net flux.
+    From left to right, the five
+    columns present $I = A_1$, $A_2$, $B_1$, $B_2$ and
+    $C$, respectively. In each plot, the red line stands for $J=A_1$,
+    green for $J=A_2$, dark blue for $J=B_1$, purple for $J=B_2$ and light blue
+    for $J=C$. 
+    }
   \label{fig:tmp6}
@@
 
-The time-dependent probability of the system in a certain metastable set is given in
-Fig.~\ref{fig:tmp5}, and different speeds of switching on the electric field
-($t_{init} = 10$, 100 and 500~ps) are compared.  No matter how fast is the electric field turned
-on, the beta sheet configuration, which presents at the beginning,
+The time-dependent probability of the system in a certain metastable state is given in
+Fig.~\ref{fig:tmp5}. The beta sheet conformation,
+which presents at the beginning,
 fades away as the system relaxes to the new equilibrium. The
-population of alpha helix $A_1$ configuration grows from 45\% to 70\%.
-alpha helix $A_2$  does not change a lot under the electric field.
+probability of alpha helix $A_1$ conformation grows from 45\% to 70\%.
+Alpha helix $A_2$  does not change a lot under the electric field.
 The left-hand helix configuration $C$ noticeably grows from 0\% to 20\%.
 
-For the case of fastly switching on electric field
-($t_{\textrm{init}}=10~\textsf{ps}$),
-we plot the time-dependent forward, backward transition probability and the net backward probability flux
-in Fig.~\ref{fig:tmp6}.
-If the process were time reversible and homogeneous, then the forward and backward transition probabilities
-would be identical. As a matter of fact, the inconsistent forward and backward transition probabilities
-implies the process is indeed nonequilibrium.
-Together with Fig.~\ref{fig:tmp5}, we observe
-three different timescales of 
-the dynamics of the alanine conformation:
+We plot the net probability fluxes and their integration in Fig.~\ref{fig:tmp6}.
+When $t$ is short, the net fluxes are generally non-zero.
+When $t$ goes to infinity,
+all fluxes converge to zero. This indicates
+when the EF is switched on, the system firstly is driven from the old
+equilibrium (in zero EF), and this is a nonequilibrium process.
+After a long enough time, the system
+is fully relaxed to the new equilibrium defined by the constant EF,
+% it gradually relaxes to the new equilibrium,
+so we do not see and change
+in the population of the metastable states.
+
+Even though the system is finally relaxed to the new equilibrium,
+the speed of relaxation of each metastable state is different. 
+From Fig.~\ref{fig:tmp6}, we observe mainly
+three different timescales of the conformational relaxation:
 (1) From
-$t=0$ to approximately 20~\textsf{ps}, the population of $A_1$ firstly decreases and then increases to the original value,
-while the population of $A_2$ increases sharply. The plot of the net probability flux shows that 
-there is firstly a fast probability flux (conformational change) from
-$A_1$ to $A_2$, and then follows a probability flux with the same maganitude in the opposite direction, i.e.  from
-$A_2$ to $A_1$.
-In the meanwhile, a clear trend from $\beta$-sheet conformations ($B_1$ and $B_2$)
-into $\alpha$-helix conformations ($A_1$, $A_2$ and $C$), both left- and right-handed,
-has been established.
-Also in this time-scale, strong and increasing probability flux from $B_2$ to $B_1$ is observed from Fig.~\ref{fig:tmp6}.
-The population of $B_1$ remains almost unchanged,
-because it  at the same time loses population to $\alpha$-helix conformations.
-Since  $B_2$ conformations not only changes into $B_1$, but also into $\alpha$-helix conformations, we observe a charp
-decrease of $B_2$ population between 10 and 20~ps.
+$t=0$ to approximately 10~\textsf{ps}, there is firstly
+a flux from $A_1$ to $A_2$, then it goes to the opposite direction, i.e.
+from $A_2$ to $A_1$.
+A similar flux is also observed from $B_1$ to $B_2$.
+% the population of $A_1$ firstly decreases and then increases to the original value,
+% while the population of $A_2$ increases sharply. The plot of the net probability flux shows that 
+% there is firstly a fast probability flux (conformational change) from
+% $A_1$ to $A_2$, and then follows a probability flux with the same maganitude in the opposite direction, i.e.  from
+% $A_2$ to $A_1$.
+In the meanwhile, a net flux from all $\beta$-sheet conformations
+($B_1$ and $B_2$) into $\alpha$-helix conformations ($A_1$, $A_2$ and
+$C$) has been established.
+% Also in this time-scale, strong and increasing probability flux from $B_2$ to $B_1$ is observed from Fig.~\ref{fig:tmp6}.
+% The population of $B_1$ remains almost unchanged,
+% because it  at the same time loses population to $\alpha$-helix conformations.
+% Since  $B_2$ conformations not only changes into $B_1$, but also into $\alpha$-helix conformations, we observe a charp
+% decrease of $B_2$ population between 10 and 20~ps.
 (2), From $t=10$ to
@@
 The net flux from  conformation $A_2$ to $A_1$ and from $B_2$ to $B_1$
-gradually decays to 0. Conformational change between $\alpha$-helix and $\beta$ sheet
-is hardly observed, except a very week flux from $B_1$ to $A_1$ and $C$, which will be discussed later.
-At this stage, the population of $B_2$ decreases to almost 0, while the population of $A_2$
+gradually decays to 0. Conformational change from $B_2$ to $A_1$, $A_2$ and $C$
+vanishes in about 50~ps.
+The net flux from $B_1$  to $A_1$ and $C$ decay slower and 
+will be discussed later.
+At this stage, the probability of $B_2$ decreases to almost 0,
+while the probability of $A_2$
 converge to a non-vanishing value of approximately 0.06.
@@
 500~\textsf{ps}$, the population of $A_1$, $B_1$ and $C$ converge to
-the non-equilibrium steady state (system with $E(\infty) = 1~\textsf{V/m}$).
-We only observed slowing decaying probability flux from $B_1$ to $A_1$ and $C$.
-The maganitude of the flux from $B_1$ to  $C$ is larger than that from  $B_1$ to  $A_1$.
-It is interesting to see that at nonequilibrium steady state, $A_1$ exchange
-population with $A_2$, and $B_1$ exchange
-population with $B_2$. However, when the $C$ conformation hardly changes
-to any other conformation, as indicated by the almost 1 value of the forward
-transition probability of set $C$. This implies that at the left-handed $\alpha$-helix is
-acutally more stable than  other conformations.
-This time-scale is actually 50 times large than when the electric field
-is fully switched on ($t_{\textrm{init}} = 10~\textsf{ps}$).
-Notice that the Fig.~\ref{fig:tmp3}
-shows that the x-component of the dipole moment of the alanine dipeptide
-reaches the maximum value at a time scale  that is the same as
-$t_{init}$. This observation indicates that the alanine can adjust almost immediately its
-dipole according to the external electric field, however, the conformational change
-happens at some much slower time scales.
+the new equilibrium (system with $E(\infty) = 1~\textsf{V/m}$).
+We observed slowing decaying probability flux from $B_1$ 
+to $A_1$ and $C$.
+The magnitude of the flux from $B_1$ to  $C$ is larger than that from  $B_1$ to  $A_1$.
+% It is interesting to see that at nonequilibrium steady state, $A_1$ exchange
+% population with $A_2$, and $B_1$ exchange
+% population with $B_2$. However, when the $C$ conformation hardly changes
+% to any other conformation, as indicated by the almost 1 value of the forward
+% transition probability of set $C$. This implies that at the left-handed $\alpha$-helix is
+% acutally more stable than  other conformations.
+This time-scale is actually 50 times slower than speed, at which
+the electric field is switched on ($t_{\textrm{init}} = 10~\textsf{ps}$).
 
-To further test the dynamics of metastable population, two simulations
-of $t_{\textrm{init}} = 100~\textsf{ps}$ and $t_{\textrm{init}} =
-500~\textsf{ps}$ are performed. The first time scale of $t =
-20~\textsf{ps}$ disappears in both of the testing simulations. In the
-simulation of $t_{\textrm{init}} = 100~\textsf{ps}$, the population of
-$A$, $B_1$ and $C$ converges to the non-equilibrium steady state at
-around $500~\textsf{ps}$. This further verifies internal time scale of
-$A_1$, $B_1$ and $C$ presented in the testing case of
-$t_{\textrm{init}} = 10~\textsf{ps}$.  The dynamics of $B_2$ is
-faster: it decays to zero as soon as the external electric field is fully
-switched on. In the case of $t_{\textrm{init}} = 500~\textsf{ps}$, the
-growth of the external electric field is comparable to the longest
-internal time scale of system, which means that the changes of the
-perturbation to the system is so slow that the system can catch up, so
-the process can be treated as  quasi-equilibrium.
-The numerical results show the same story: the relaxation
-of all populations are around $500 \sim 600~\textsf{ps}$.
+The Fig.~\ref{fig:tmp3}
+shows that the $x$-component of the dipole moment of the alanine dipeptide
+reaches 85\% of the maximum value in only 20~ps, which is comparable to
+the warm-up time $t_{init}$. Then the dipole slowly relaxes to the 
+maximum value in the following 400~ps. Notice that 20~ps is 25 times
+smaller than the slowest time scale of the conformational relaxation.
+This indicate that when the EF is switched on, the alanine almost immediately
+align itself to the
+direction of the external EF without much conformational change.
+And then, the conformation is slowly adjusted according to the
+external field (now it is the same as the molecular dipole),
+finally  the new equilibrium is reached at a much slower time scale
+(approximately 500~ps).
+
+% After aligning to the external EF, the alanine slowly adjust its confromation,
+% and the new equilibrium is reached at slower time scales.
+
+% To further test the dynamics of metastable population, two simulations
+% of $t_{\textrm{init}} = 100~\textsf{ps}$ and $t_{\textrm{init}} =
+% 500~\textsf{ps}$ are performed. The first time scale of $t =
+% 20~\textsf{ps}$ disappears in both of the testing simulations. In the
+% simulation of $t_{\textrm{init}} = 100~\textsf{ps}$, the population of
+% $A$, $B_1$ and $C$ converges to the non-equilibrium steady state at
+% around $500~\textsf{ps}$. This further verifies internal time scale of
+% $A_1$, $B_1$ and $C$ presented in the testing case of
+% $t_{\textrm{init}} = 10~\textsf{ps}$.  The dynamics of $B_2$ is
+% faster: it decays to zero as soon as the external electric field is fully
+% switched on. In the case of $t_{\textrm{init}} = 500~\textsf{ps}$, the
+% growth of the external electric field is comparable to the longest
+% internal time scale of system, which means that the changes of the
+% perturbation to the system is so slow that the system can catch up, so
+% the process can be treated as  quasi-equilibrium.
+% The numerical results show the same story: the relaxation
+% of all populations are around $500 \sim 600~\textsf{ps}$.
 
@@
   \includegraphics[]{fig.ala/fig-meta-conv.eps}
-  \caption{The populations of the metastable sets as a function of time.
+  \caption{The populations of the metastable states as a function of time.
     The dashed vertical lines indicate the three different time scale of
-  metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
+  metastable state population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
   \label{fig:tmp7}
@@
 the period $T$ by $\omega = 1/T$.  Here we tested three different
-periods: 10, 40 and 200.  the periods of the later two are
-commensurate to the time scales discovered by the nonequilibrium MD
-simulation of constant electric field. The first is to test the if the
-period is further reduced to smaller than 20~ps, there is any other
-timescale of interest would play a role. Although the periods are
-chosen according to the discovered time scales in the constant
-electric field simulation, the nonequilibrium phenonema of oscillating
-electric field cannot fully derived from the constant field system.
-As far as the electric field changes, the internal time scale of the
-system also changes, therefore, the nonequilibrium probabilities is a
-complicated interplay of different internal time scales under
-different electric fields. We do not try to theoretically predict
-what will happen under the oscillating EF by a series constant EF simulation
-revealing the internal dynamics under different strength of EF, but just directly
-do the nonequilibrium MD simulation for the oscillating EF, and discuss
-the observed phenonema.
+periods: 10, 40 and 200, which corresponding
+to frequency 100, 25 and 5~GHz.
+% The periods of the later two are
+% commensurate to the time scales discovered by the nonequilibrium MD
+% simulation of constant electric field. The first is to test the if the
+% period is further reduced to smaller than 20~ps, there is any other
+% timescale of interest would play a role. Although the periods are
+% chosen according to the discovered time scales in the constant
+% electric field simulation, the nonequilibrium phenonema of oscillating
+% electric field cannot be derived from the constant field system.
+% As far as the electric field changes, the internal time scale of the
+% system also changes, therefore, the nonequilibrium probabilities is a
+% complicated interplay of different internal time scales under
+% different EF.
+% We do not try to theoretically predict
+% what will happen under the oscillating EF by a series constant EF simulation
+% revealing the internal dynamics under different strength of EF, but just directly
+% do the nonequilibrium MD simulation for the oscillating EF, and discuss
+% the observed phenonema.
 
@@
 
-Fig.~\ref{fig:tmp8} presents the $x$-component of the dipole moment as
+Fig.~\ref{fig:tmp8} presents the $x$-component of the molecular dipole moment as
 a function of time. The red, green and blue lines stands for the
 results of $T=10$~ps, 40~ps and 200~ps, respectively. The black lines
-shows the dipole moment of constant electric field with
-$t_{init}=10$~ps for reference. It demonstrates that for all periods
-investigated, the alanine can adjust it's direction, which defined by
-the direction of average dipole, according to the external electric
-field almost immediately. At $T=200$~ps, the maximum magnitude of the
-dipole moment is almost the same as the constant electric field, which
+shows the dipole moment under constant electric field
+for reference.
+It demonstrates that the periods of the molecular dipole moment
+is the same as the periods of the oscillating EF. Therefore,
+the molecular dipole moment
+is able to response to the external EF almost immediately.
+At $T=200$~ps, the maximum magnitude of the molecular
+dipole moment is almost the same as the case of constant electric field, which
 means that the changing of the electric field is so slow that the
-alanine have enough time to fully relax the internal dipole. However,
-for $T=40$~ps and $T=10$~ps, when the electric field changes faster,
+alanine have enough time to firstly align to the external EF, and then
+relax its internal dipole (although not completely). However,
+for $T=40$~ps, as the electric field changes faster,
 although the molecules can align to the electric field immediately,
-but it does not have enough time to relax the internal dipole, so we
-see the maximum alanine's dipole moment reached is smaller for the shorter
-period.
+it does not have enough time to fully relax the internal dipole, so we
+see the maximum alanine's dipole moment reached is smaller.
+For even smaller period $T=10$~ps, the alanine does not have enough
+time  to properly align the molecular dipole according to the external
+field, so we see the maximum dipole moment is only about one third of the
+constant EF case.
 
@@
     probability of being in a certain metastable state $I$, which is
-    denoted by $P_I$ in this paper, is ploted by colored lines against
+    denoted by $P_I$ in this paper, is plotted by colored lines against
     time. The red line: $I = A_1$, the green line: $I = A_2$, the dark
@@
     simulations of time 1000~ps are presented, while for $T=200$~ps,
-    nonequilibrium simulations of tiem 3200~ps is presented.  }
+    nonequilibrium simulations of time 3200~ps is presented.  }
   \label{fig:tmp9}
@@
     oscillating EF is plotted against time. The unit of the
-    time (horizontal axises) is picosecond.
+    time (horizontal axis) is picosecond.
     The integrated
     probability flux is defined by $Q_{J,I}(t) = \int_0^t F_{J,I}(\tau) d\tau$, where
-    $F(t)$ is the net probability flux from metastable set $I$ to $J$.
+    $F(t)$ is the net probability flux from metastable state $I$ to $J$.
     From up to down the rows present period 10, 40 and 200~ps, respectively.
     From left to right, the five
-    columes show integrated flux $Q_{J,A_1}$, $Q_{J,A_2}$,
+    columns show integrated flux $Q_{J,A_1}$, $Q_{J,A_2}$,
     $Q_{J,B_1}$, $Q_{J,B_2}$ and $Q_{J,C}$, respectively. In each plot,
@@
     if the integrated flux $Q_{J,I}$ increases, then there exist a (time-averaged)
-    non-zero net flux from metastable set $I$ to $J$.
+    non-zero net flux from metastable state $I$ to $J$.
   }
@@
 metastable state for periodically oscillating electric field.  The
-Fig.~\ref{fig:tmp10} presents the integrated probability flux of among
-the metastable sets.
-When the period is small, i.e. $T=10$~ps and
-40~ps, the observed phenonema in the figures are basically the same.
-The pobability in $A_1$, $A_2$, $B_1$ and $B_2$ does not change
+Fig.~\ref{fig:tmp10} presents the integrated probability flux among
+the metastable states. We do not show the probability flux itself,
+because the profiles are highly oscillating and no more
+information can be obtained than the integrated probability flux.
+For all periods investigated,
+the observed time-dependent probabilities of being in a certain metastable
+state are basically the same.
+The probability in $A_1$, $A_2$, $B_1$ and $B_2$ are
+highly oscillating and the average value does not change
 too much with respect to time,
-however, the probability in metastable set $C$ astonishingly
-increase to approximately 0.17 for $T=10$~ps  and 0.27 for  $T=10$~ps.
+however, the probability in metastable state $C$ astonishingly
+increase to approximately 0.17 for $T=10$~ps, 0.27 for  $T=40$~ps, and
+0.25 for $T=200$~ps.
 Notice that in the constant EF case, although the dipole moment is
-bigger than the  $T=40$~ps case (see Fig.~\ref{fig:tmp8}), the
+larger than the  $T=40$~ps case (see Fig.~\ref{fig:tmp8} for comparison), the
 probability of being in $C$ is indeed lower.
-The time needed to reach a steady state is
-roughly 400~ps that is the same as the
-constant EF case. Fig~\ref{fig:tmp10} shows some ever increasing
-integrated probability fluxes, which imply some ever lasting and directional
-flux among the metastable sets, see
-Fig.~\ref{fig:tmp11} that presents a schematic plot of the probability
-fluxes for $T=10$~ps. The probability flux of  $T=40$~ps is roughly
-the same as $T=10$~ps, expect that
-the flux from $B_2 $ to $A_1$ does not exist. 
-This demonstrate a interesting phenonemon: the oscillating EF 
-generates a directional probability flux among the metastable sets.
+For the constant EF case, the probability of state $A_1$
+increases from 0.45 to almost 0.7, and that of $B_1$ almost vanishes.
+These phenomena are not observed in the oscillating EF case.
+In the case of $T=10$ and $40$~ps, the probability of being in a state
+reaches the steady value in around 300~ps, while it costs 1200~ps
+for the $T=200$~ps case to reach the steady probability. That means
+the intrinsic time scales of the nonequilibrium processes are commensurate
+for $T=10$ and $40$~ps, while they are much longer for $T=200$~ps.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{fig.ala/graphs/graph-t0010.eps}
+  \caption{The schematic plot of the main probability flux among the metastable
+    states on the Ramachandran histogram
+    for periodically oscillating EF, $T=10$~ps. The thickness 
+    of the arrows approximately presents the strength of the flux.
+  }
+  \label{fig:tmp11}
+\end{figure}
+
+Fig.~\ref{fig:tmp10} shows some ever increasing
+integrated probability net fluxes, which imply some ever lasting and directional
+flux among the metastable states, see
+Fig.~\ref{fig:tmp11} that presents a schematic plot of the main probability
+fluxes for $T=10$~ps.
+The thickness of the arrow and the number nearby indicate
+the averaged strength of the net fluxes.
+This demonstrate an interesting phenomenon: although
+the oscillating EF is not directional and vanishes in time-average,
+it generates directional probability fluxes among the metastable states.
 Moreover, some loops of the flux are detected: $A_1 \rightarrow B_1
@@
 \rightarrow B_2 \rightarrow C \rightarrow B_1$.
+The probability flux of $T=40$~ps is quantitatively
+comparable to case $T=10$~ps, except that the probability fluxes
+going into state $C$ is stronger, which actually results in
+a more dominant probability in $C$.
+The probability flux of case $T=200$~ps is qualitatively
+similar to $T=10$~ps and $T=40$~ps, however,
+the strength is much lower than the latter two cases.
+Also, we see that the integrated flux reaches the linearly increasing
+stage after about 2400~ps, which is much longer than the time scale,
+at which probability of $C$ reaches its steady value. This indicates
+a even longer intrinsic time scale in the $T=200$~ps case.
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.3\textwidth]{fig.ala/graphs/graph-t0010.eps}
-  \caption{The schematic plot of the main probability flux among the metastable
-    states on the Ramachandran histogram
-    for periodically oscillating EF, $T=10$~ps. The thickness 
-    of the arrows approximately presnets the strength of the flux.
-  }
-  \label{fig:tmp11}
-\end{figure}
+We do not test any period longer than $T=200$~ps, because
+from the trend that longer period indicates even longer intrinsic time scales.
+The computer power available to us is not enough for a longer
+simulation that can discover those intrinsic time scale.
+However, the long-period-limit case is rather easy: When
+the EF changes so slow that at each time point the system
+can be viewed as in equilibrium, then the process is a quasi-equilibrium
+process, and no nonequilibrium phenomenon will be observed. For example,
+the probability being in a  metastable state will change
+smoothly from equilibrium value to the new equilibrium of $E=1$~V/nm, as
+the EF increases.
+And then smoothly goes back to equilibrium, as the EF vanishes.
+the time-averaged net flux will be infinitely small,
+and the integrated flux will be periodical, and being constant in time-average.
 
-When the period is $T=200$~ps, the phenonema are substentially different
-from the high frequency cases ($T=10$ and 40~ps). Firstly, from Fig.~\ref{fig:tmp9}, the system reaches staedy state after around 2000~ps, while
-Fig.~\ref{fig:tmp10} suggests an even long time scale, but we cannot draw
-a very clear conclusion on it
-due to the lack of computational power to perform even longer simulations. 
-The steady probability of being in state $C$ is roughly the same as the
-case of $T=40$~ps, although the maximum dipole moment is actually higher
-than the latter. And the steady probability  of being in state $C$ is
-also higher than the constant EF case, even the maximum dipole are roughly
-the same. The time spend to reach the steady state is much longer than
-the higher frequency cases, so this indicates a \emph{dynamically} longer time
-scale in the system, comparing with the static EF case, in which all time scales
-are actually decided by the \emph{static} external field. We also observe
-a suden change in the probability flux from set $A_2$ to $A_1$ at
-around 1600~ps, which may imply a \emph{dynamically} rare event.
-Since we do not have the computer power to perform even longer simulations,
-this hypothesis is not further checked.
+% similar to $T=10$~ps. For $T=40$~ps, the probability
+% flux is quantiatively comparable to the case $T=10$~ps, while
+% the strength of fluxex for $T=200$~ps is much weaker.
+
+% The time needed to reach a steady state is
+% roughly 400~ps that is the same as the
+% constant EF case.
+
+% When the period is $T=200$~ps, the phenonema are substentially different
+% from the high frequency cases ($T=10$ and 40~ps). Firstly, from Fig.~\ref{fig:tmp9}, the system reaches staedy state after around 2000~ps, while
+% Fig.~\ref{fig:tmp10} suggests an even long time scale, but we cannot draw
+% a very clear conclusion on it
+% due to the lack of computational power to perform even longer simulations. 
+% The steady probability of being in state $C$ is roughly the same as the
+% case of $T=40$~ps, although the maximum dipole moment is actually higher
+% than the latter. And the steady probability  of being in state $C$ is
+% also higher than the constant EF case, even the maximum dipole are roughly
+% the same. The time spend to reach the steady state is much longer than
+% the higher frequency cases, so this indicates a \emph{dynamically} longer time
+% scale in the system, comparing with the static EF case, in which all time scales
+% are actually decided by the \emph{static} external field. We also observe
+% a suden change in the probability flux from state $A_2$ to $A_1$ at
+% around 1600~ps, which may imply a \emph{dynamically} rare event.
+% Since we do not have the computer power to perform even longer simulations,
+% this hypothesis is not further checked.
+
+\section{Concluding remarks}
 

### 2013-08-06 writedown/npt-neq/alanine.tex
more revises

@@
 \affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
-% \affiliation{Zuse Institute Berlin, Germany}
+\affiliation{Zuse Institute Berlin, Germany}
+\author{Giovanni Ciccotti}
+\affiliation{Department of Physics, University of Roma "La Sapienza", Italy}
 \author{Luigi Delle Site}
@@
 The possible effect of the electric field (EF) on the conformation of
-proteins gains increasing attention recently, because it closely
+proteins gains increasing attention recently, because it is closely
 related to the health problem of exposing human tissue in the
 electromagnetic radiation. Despite the importance of this problem, a
-complete understanding of how the electric field influence the  protein
+complete understanding of how the EF influence the  protein
 is still lacking, therefore, a considerable number of
@@
 understanding the behavior of a protein (or a short peptide segment)
-in both static and oscillatory electric
-fields~\cite{budi2005electric, budi2007effect, budi2008comparative,
+in both static and oscillatory EF~\cite{budi2005electric, budi2007effect, budi2008comparative,
   toschi2008effects, astrakas2011electric, astrakas2012structural,
@@
 configurations are usually taken from the Protein Data Bank (PDB).
-And then the temperature controlled simulation are performed for from
+And then the temperature controlled simulation are performed for 
 a few to tens of nanoseconds, during which the interested
@@
 whole simulation. This approach release useful information on how the
-secondary structure is changed by external electric field.  However,
+secondary structure is changed by external  EF.  However,
 by plotting the quantities against time, one may observe strong
 fluctuation in plots, which hintered the quantitative and conclusive
-analysis on what is happening during the conformational change, when
-it happens and what is the strength. Although the statistical
-uncertainty in the time-averaged observations are small, the
-time-average itself is not well defined for a nonequilibrium process
-such as relaxing process to the new conformations under static
-electric field, and the dynamics under oscillating electric field.
+analysis on what is the trend of the conformational change, when
+it happens and what is the strength.
+Although the time average reduces the statistical uncertainty,
+it is indeed not well defined for a nonequilibrium process
+such as relaxing process to the new conformations under a static
+EF, or the dynamics under an oscillating EF.
 
@@
 nonequilibrium observables by doing an ensemble of nonequilibrium MD
-simulations.  This provides a promising way of analyzing the
-conformational changing under a generally time-dependent electric
-field. In the present paper, we study the minimal model peptide
+simulations.  It can be used for analyzing the
+conformational changing under a generally time-dependent EF.
+In the present paper, we study the minimal model peptide
 segment -- alanine dipeptide. We take the approach of starting from a
-single peptide rather than a more realistic chain, firstly because it
+single peptide piece rather than a more realistic chain, firstly because it
 is easier to draw clear conclusions on the nonequilibrium properties
 of a single peptide by excluding all possible interplay between
-different peptide segments along a chain, then construct the chain
-nonequilibrium properties from the well-studied single peptides.
+different peptide segments along a chain.
 Secondly, the current computational resource available is not enough
@@
 ensemble of MD trajectories (typically a few thousands), so it
-requires much higher computational cost than producing a single MD
-trajectory.
+requires much higher computational cost than producing a single
+equilibrium MD trajectory.
 
 In this paper, we firstly describe the idea of the D-NEMD, then
-observables helping us the analyze the nonequilibrium properties
+introduce the
+observables for analyzing the nonequilibrium properties
 (i.e., the dipole moment, time-dependent properties of being a certain
-conformation, the nonequilibrium transition properties and the net
-property flux) are introduced. The numerical results of alanine
-dipeptide under static and sine-shaped oscillating electric field are
+conformation and the net
+probability flux). The numerical results of alanine
+dipeptide under static and sine-shaped oscillating EF are
 presented. By calculating the nonequilibrium properties from the D-NEMD
-simulations, we are able to answer from which to which the conformation
-changes, when do these changes happens, and how strong are the changes.
+simulations, we are able to answer how the peptide
+changes the conformation in a EF, when do these changes happens,
+and how strong are they.
 As far as we know, our simulation is the first D-NEMD simulation
-on the electric field effect on alanine dipeptide, and provides new
+of alanine dipeptide under EF, and provides new
 information helping people better understand the nonequilibrium
-effect of electric field on the protein conformation.
+effect of EF on the protein conformation.
 
@@
 \subsection{Nonequilibrium molecular dynamics simulation}
-Here we fastly review the approach of performing nonequilibrium
-molecular dynamics that was initiated by Giovanni Ciccoti and his
+Here we fastly review the approach of performing dynamical nonequilibrium
+molecular dynamics (D-NEMD) that was initiated by Giovanni Ciccoti and his
 colleagues~\cite{ciccotti1975direct, ciccotti1979thought,
@@
 
-The aforementioned nonequilibrium molecular dynamics simulation algorithm
+The aforementioned D-NEMD simulation algorithm
 does not describe how the boundary of the system should be set up.
@@
   \caption{Schematic plot of the truncated nonequilibrium subsystem.
-    The white part is the subsystem and the gray part is the boundary
-    condition, implemented by the thermostat and barostat mimicing
-    the infinitely large universe.}
+    The white part is the Hamiltonian dynamics subsystem
+    and the gray part is thermostating region. The whole system
+    is subject to the periodic boundary condition.}
   \label{fig:tmp2}
@@
   \caption{The magnitude of the external electric field, and the
-    x-component of the dipole moment of the alanine molecule as a
-    function of time. The dashed lines are the strengths of the
-    external electric field, while the solid lines are the dipole
-    moments. Three test cases are indicated by different colors.}
+    $x$-component of the dipole moment of the alanine molecule as a
+    function of time. The dashed line presents the strengths of the
+    external electric field, while the solid line presents the dipole
+    moments. }
   \label{fig:tmp3}
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{fig.ala/graphs/graph-t0010.eps}
+  \includegraphics[width=0.5\textwidth]{fig.ala/graphs/graph-t0010-1.eps}
   \caption{The schematic plot of the main probability flux among the metastable

### 2013-08-06 alanine.nanma/template/tools/angles/app/average.traj.corr.cpp
print directional flux

@@ -89,7 +89,7 @@ void calCorr (const vector<double> & counts0,
 
 int main(int argc, char * argv[])
 {
-  std::string ifile, ofile, ofwfile, obwfile, ofluxfile;
+  std::string ifile, ofile, ofwfile, obwfile, ofluxfile, odirfile;
   double lagTime;
   // unsigned numBlock = 20;
   // double refh;
@@ -120,6 +120,7 @@ int main(int argc, char * argv[])
       ("output-meta-corr-forward", po::value<std::string > (&ofwfile)->default_value ("meta.corr.fw.out"), "the output of metastable propulation forward correlation")
       ("output-meta-corr-backward", po::value<std::string > (&obwfile)->default_value ("meta.corr.bw.out"), "the output of metastable propulation backward correlation")
       ("output-meta-flux", po::value<std::string > (&ofluxfile)->default_value ("meta.flux.out"), "the output of metastable propulation flux")
+      ("output-meta-direct-flux", po::value<std::string > (&odirfile)->default_value ("meta.direct.flux.out"), "the output of metastable propulation flux")
       ("input,f",  po::value<std::string > (&ifile)->default_value ("angle.name"), "the file of file names");
 
   po::variables_map vm;
@@ -232,6 +233,7 @@ int main(int argc, char * argv[])
   FILE * fp1 = fopen (obwfile.c_str(), "w");
   FILE * fp2 = fopen (ofwfile.c_str(), "w");
   FILE * fp3 = fopen (ofluxfile.c_str(), "w");
+  FILE * fp4 = fopen (odirfile.c_str(), "w");
 
   for (unsigned ii = 0; ii < times.size(); ++ii){
     fprintf (fp, "%f ", times[ii]);
@@ -291,12 +293,24 @@ int main(int argc, char * argv[])
     fprintf (fp3, "\n");
   }
   
+  for (unsigned ii = nLagTime - 1; ii < times.size(); ++ii){
+    fprintf (fp4, "%f ", times[ii]);
+    for (unsigned dd = 0; dd < sets.size(); ++dd){
+      for (unsigned mm = 0; mm < sets.size(); ++mm){
+	fprintf (fp4, "%f ", (corrsBw[ii][dd][mm]) / double (countFile));
+      }
+      fprintf (fp4, "  ");
+    }
+    fprintf (fp4, "\n");
+  }
+  
 
 
   fclose (fp);
   fclose (fp1);
   fclose (fp2);
   fclose (fp3);
+  fclose (fp4);
   
   return 0;
 }

### 2013-08-06 alanine.nanma/template/tools/angles/app/average.traj.corr.cpp
devide the net flux by dt (lag time), add target file as command line input to the mat calculator

@@ -286,7 +286,7 @@ int main(int argc, char * argv[])
     fprintf (fp3, "%f ", times[ii]);
     for (unsigned dd = 0; dd < sets.size(); ++dd){
       for (unsigned mm = 0; mm < sets.size(); ++mm){
-	fprintf (fp3, "%f ", (corrsBw[ii][dd][mm] - corrsBw[ii][mm][dd]) / double (countFile));
+	fprintf (fp3, "%f ", (corrsBw[ii][dd][mm] - corrsBw[ii][mm][dd]) / double (countFile) / lagTime);
       }
       fprintf (fp3, "  ");
     }
@@ -297,7 +297,7 @@ int main(int argc, char * argv[])
     fprintf (fp4, "%f ", times[ii]);
     for (unsigned dd = 0; dd < sets.size(); ++dd){
       for (unsigned mm = 0; mm < sets.size(); ++mm){
-	fprintf (fp4, "%f ", (corrsBw[ii][dd][mm]) / double (countFile));
+	fprintf (fp4, "%f ", (corrsBw[ii][dd][mm]) / double (countFile) / lagTime);
       }
       fprintf (fp4, "  ");
     }

### 2013-08-06 alanine.nanma/template/tools/scripts/cal.flux.mat.sh

@@ -9,8 +9,11 @@ fi
 if test $# -ge 2; then
     up=$2
 fi
+if test $# -ge 3; then
+    file=$3
+fi
 
-echo "# doing linear fitting in [$lo:$up]"
+echo "# doing linear fitting for $file in [$lo:$up]"
 
 echo "set xrange [$lo:$up]"		>  tmp.gp
 echo "f(x) = a*x + b"			>> tmp.gp

### 2013-08-07 alanine.nanma/template/tools/angles/app/conf.dipole.cpp
cal the dipole moment for different metastable sets. not tested

@@ -1,0 +1,256 @@
+#include <algorithm>
+#include <fstream>
+#include <iomanip>
+#include <iostream>
+#include <iterator>
+#include <list>
+#include <map>
+#include <set>
+#include <sstream>
+#include <string>
+#include <queue>
+#include <vector>
+#include <cmath>
+
+#include "Defines.h"
+#include "Distribution.h"
+#include "StringSplit.h"
+#include <boost/program_options.hpp>
+
+namespace po = boost::program_options;
+using namespace std;
+
+#define MaxLineLength 2048
+
+bool myread (FILE * fp,
+	     float & time,
+	     ValueType & phi,
+	     ValueType & psi)
+{
+  size_t rv;
+  rv = fread (&time, sizeof(float), 1, fp);
+  if (rv != 1){
+    // cerr << "error read time or reach EOF" << endl;
+    return false;
+  }
+  rv = fread (&phi, sizeof(double), 1, fp);
+  if (rv != 1){
+    cerr << "error read phi " << endl;
+    exit(1);
+  }
+  rv = fread (&psi, sizeof(double), 1, fp);
+  if (rv != 1){
+    cerr << "error read psi " << endl;
+    exit(1);
+  }
+  return true;
+}
+
+bool myread_dipole (FILE * fp,
+		    float & time,
+		    vector<ValueType> & dipole)
+{
+  char line[MaxLineLength];
+  char * ret;
+
+  while ((ret = fgets(line, MaxLineLength, fp)) &&
+	 (line[0] == '#' || line[0] == '@')) {
+  }
+  if (ret == NULL){
+    return false;
+  }
+
+  vector<string> out;
+  StringOperation::split (string(line), out);
+
+  if (out.size() < 4){
+    return false;
+  }
+  else {
+    time = atof(out[0].c_str());
+    dipole.resize(3);
+    dipole[0] = atof(out[1].c_str());
+    dipole[1] = atof(out[2].c_str());
+    dipole[2] = atof(out[3].c_str());
+    return true;
+  }
+}
+
+
+void depositMetastable (const double & phi,
+			const double & psi,
+			const vector<MetastableSet> & sets,
+			vector<double > & counts)
+{
+  int cc = 0;
+  counts.resize (sets.size());
+  for (unsigned ii = 0; ii < sets.size(); ++ii){
+    counts[ii] = 0;
[…]

### 2013-08-07 alanine.nanma/template/tools/angles/app/print.angles.cpp

@@ -15,8 +15,10 @@
 #include "Defines.h"
 #include "Distribution.h"
 #include <boost/program_options.hpp>
+
 namespace po = boost::program_options;
 using namespace std;
+
 #define MaxLineLength 2048
 
 bool myread (FILE * fp,
@@ -75,10 +77,10 @@ int main(int argc, char * argv[])
   // unsigned numBlock = 20;
   // double refh;
   // float time_prec = .01;
-  double setA_psi_b = 128, setA_psi_e = 13;
-  double setA_phi_b =-125, setA_phi_e = 74;
-  double setB_psi_b = 128, setB_psi_e = 13;
-  double setB_phi_b = 74,  setB_phi_e =-125;
+  // double setA_psi_b = 128, setA_psi_e = 13;
+  // double setA_phi_b =-125, setA_phi_e = 74;
+  // double setB_psi_b = 128, setB_psi_e = 13;
+  // double setB_phi_b = 74,  setB_phi_e =-125;
   double setC_psi_b = 13,  setC_psi_e = 128;
   double setC_phi_b = -180,setC_phi_e = 180;
   

### 2013-08-07 alanine.nanma/template/tools/angles/app/conf.dipole.cpp
add script for conf.dipole

@@ -129,7 +129,7 @@ int main(int argc, char * argv[])
   po::options_description desc ("Allow options");
   desc.add_options()
       ("help,h", "print this message")
-      ("output,o", po::value<std::string > (&ofile)->default_value ("metastable.out"), "the output of metastable propulation")
+      ("output,o", po::value<std::string > (&ofile)->default_value ("conf.dipole.out"), "the output dipole for different conformation")
       ("input-angle",  po::value<std::string > (&iafile)->default_value ("angle.name"), "the file of file names")
       ("input-dipole",  po::value<std::string > (&idfile)->default_value ("dipole.name"), "the file of file names");
 

### 2013-08-07 alanine.nanma/template/tools/scripts/conf.dipole.sh

@@ -1,0 +1,37 @@
+#!/bin/bash
+
+dipole_name=dipole.name
+angle_name=angle.name
+out_dipole_name=consist.dipole.name
+out_angle_name=consist.angle.name
+bin_dir=/home/cocktail/wanghan/study/adress.noneq/alanine.nanma/template/tools/angles/
+bin=$bin_dir/conf.dipole
+make -C $bin_dir/ -j 8
+
+echo "# firstly make the angle name and dipole name consistent"
+
+rm -f $out_angle_name $out_dipole_name
+
+for i in `grep -v \# $dipole_name`;
+do
+    pert_dir=`echo $i | sed 's/.*\(pert\.[0-9]*\).*/\1/g'`
+    echo $pert_dir
+    grep $pert_dir $angle_name >> $out_angle_name
+done
+sort $out_angle_name > tmp.tmp
+mv -f tmp.tmp $out_angle_name
+
+for i in `grep -v \# $angle_name`;
+do
+    pert_dir=`echo $i | sed 's/.*\(pert\.[0-9]*\).*/\1/g'`
+#    echo $pert_dir
+    grep $pert_dir $dipole_name >> $out_dipole_name
+done
+sort $out_dipole_name > tmp.tmp
+mv -f tmp.tmp $out_dipole_name
+
+
+echo "# do the calculation"
+$bin --input-angle $out_angle_name --input-dipole $out_dipole_name
+
+

### 2013-08-08 alanine.nanma/template/tools/angles/app/order.parameter.cpp
calculate the order parameter (along x) for the axis of molecule, not tested

@@ -1,0 +1,247 @@
+#include <algorithm>
+#include <fstream>
+#include <iomanip>
+#include <iostream>
+#include <iterator>
+#include <list>
+#include <map>
+#include <set>
+#include <sstream>
+#include <string>
+#include <queue>
+#include <vector>
+#include <cmath>
+
+#include "Defines.h"
+#include "StringSplit.h"
+#include <boost/program_options.hpp>
+
+namespace po = boost::program_options;
+using namespace std;
+
+#define MaxLineLength 2048
+
+
+bool myread_dipole (FILE * fp,
+		    float & time,
+		    vector<double> & dipole)
+{
+  char line[MaxLineLength];
+  char * ret;
+
+  while ((ret = fgets(line, MaxLineLength, fp)) &&
+	 (line[0] == '#' || line[0] == '@')) {
+  }
+  if (ret == NULL){
+    return false;
+  }
+
+  vector<string> out;
+  StringOperation::split (string(line), out);
+
+  if (out.size() < 4){
+    return false;
+  }
+  else {
+    time = atof(out[0].c_str());
+    dipole.resize(3);
+    dipole[0] = atof(out[1].c_str());
+    dipole[1] = atof(out[2].c_str());
+    dipole[2] = atof(out[3].c_str());
+    return true;
+  }
+}
+
+struct Pair 
+{
+  double x;
+  int y;
+  Pair (double x_, int y_)
+      : x(x_), y(y_)
+      {
+      }
+  bool operator < (const Pair & b) const
+      {
+	return x < b.x;
+      }
+}
+    ;
+
+void mysort (const vector<double > & eigen,
+	     vector<int > & order)
+{
+  vector<Pair > tmp;
+  for (unsigned ii = 0; ii < eigen.size(); ++ii){
+    tmp.push_back (Pair(eigen[ii], ii));
+  }
+  sort (tmp.begin(), tmp.end());
+  order.resize(eigen.size());
+  for (unsigned ii = 0; ii < eigen.size(); ++ii){
+    order[ii] = tmp[ii].y;
+  }
+}
+	     
+
+int main(int argc, char * argv[])
+{
+  std::string ifile_moi, ifile_a1, ifile_a2, ifile_a3, ofile;
+
+  po::options_description desc ("Allow options");
+  desc.add_options()
+      ("help,h", "print this message")
[…]

### 2013-08-08 alanine.nanma/template/tools/angles/app/two.vectors.cpp
add two vector calculator

@@ -1,0 +1,163 @@
+#include <algorithm>
+#include <fstream>
+#include <iomanip>
+#include <iostream>
+#include <iterator>
+#include <list>
+#include <map>
+#include <set>
+#include <sstream>
+#include <string>
+#include <queue>
+#include <vector>
+#include <cmath>
+
+#include "Trajectory.h"
+#include <boost/program_options.hpp>
+
+namespace po = boost::program_options;
+using namespace std;
+
+#define MaxLineLength 2048
+
+
+int main(int argc, char * argv[])
+{
+  std::string ifile, ofile;
+
+  po::options_description desc ("Allow options");
+  desc.add_options()
+      ("help,h", "print this message")
+      ("output,o", po::value<std::string > (&ofile)->default_value ("two.vectors.out"), "the order parameter of the molecule")
+      ("input-dir",  po::value<std::string > (&ifile)->default_value ("dir.name"), "the file of file names");
+
+  po::variables_map vm;
+  po::store(po::parse_command_line(argc, argv, desc), vm);
+  po::notify (vm);
+  if (vm.count("help")){
+    std::cout << desc<< "\n";
+    return 0;
+  }
+
+  ifstream fpname (ifile.c_str());
+  if (!fpname){
+    std::cerr << "cannot open file " << ifile << std::endl;
+    return 1;
+  }
+  
+  char nameline [MaxLineLength];
+  vector<float > times;
+  vector<vector<double > > vector0;
+  vector<vector<double > > vector1;
+  vector<double > length0;
+  vector<double > length1;
+  unsigned countFile = 0;
+  
+
+  while (fpname.getline(nameline, MaxLineLength)){
+    XtcLoader xtcl ;
+    vector<vector<double > > frame;
+    string myfilename (nameline);
+    myfilename += string("/traj.xtc");
+    cout << "reading file " << myfilename << endl;    
+    if (! xtcl.reinit(myfilename)){
+      return 1;
+    }
+    countFile ++;
+    if (countFile == 1){
+      while ( xtcl.load() ) {
+	times.push_back (xtcl.getTime());
[…]

### 2013-08-08 alanine.nanma/template/tools/angles/app/order.parameter.cpp
fix bug of order.parameter

@@ -90,10 +90,10 @@ int main(int argc, char * argv[])
   desc.add_options()
       ("help,h", "print this message")
       ("output,o", po::value<std::string > (&ofile)->default_value ("order.parameter.out"), "the order parameter of the molecule")
-      ("input-moi",  po::value<std::string > (&ifile_moi)->default_value ("pincipal.name"), "the file of file names")
-      ("input-axis1",  po::value<std::string > (&ifile_a1)->default_value ("pincipal.a1.name"), "the file of file names")
-      ("input-axis2",  po::value<std::string > (&ifile_a2)->default_value ("pincipal.a2.name"), "the file of file names")
-      ("input-axis3",  po::value<std::string > (&ifile_a3)->default_value ("pincipal.a3.name"), "the file of file names");
+      ("input-moi",  po::value<std::string > (&ifile_moi)->default_value ("principal.name"), "the file of file names")
+      ("input-axis1",  po::value<std::string > (&ifile_a1)->default_value ("principal.a1.name"), "the file of file names")
+      ("input-axis2",  po::value<std::string > (&ifile_a2)->default_value ("principal.a2.name"), "the file of file names")
+      ("input-axis3",  po::value<std::string > (&ifile_a3)->default_value ("principal.a3.name"), "the file of file names");
 
   po::variables_map vm;
   po::store(po::parse_command_line(argc, argv, desc), vm);
@@ -186,6 +186,7 @@ int main(int argc, char * argv[])
 	}
 	times.push_back (time_moi);
 	mysort (moi, order);
+	// printf ("%f %d %d %d   %f %f %f\n", time_moi, order[0], order[1], order[2], moi[0], moi[1], moi[2]);
 	for (unsigned dd = 0; dd < 3; ++dd){
 	  double cosv = aa[order[dd]][0];
 	  values[dd].push_back (0.5 * (3. * cosv * cosv - 1.));
@@ -209,6 +210,7 @@ int main(int argc, char * argv[])
 	  exit (1);
 	}
 	mysort (moi, order);
+	// printf ("%f %d %d %d   %f %f %f\n", time_moi, order[0], order[1], order[2], moi[0], moi[1], moi[2]);
 	for (unsigned dd = 0; dd < 3; ++dd){
 	  double cosv = aa[order[dd]][0];
[…]

### 2013-08-08 alanine.nanma/template/tools/scripts/conf.dipole.sh
add script for two vectors

@@ -15,7 +15,7 @@ rm -f $out_angle_name $out_dipole_name
 for i in `grep -v \# $dipole_name`;
 do
     pert_dir=`echo $i | sed 's/.*\(pert\.[0-9]*\).*/\1/g'`
-    echo $pert_dir
+#    echo $pert_dir
     grep $pert_dir $angle_name >> $out_angle_name
 done
 sort $out_angle_name > tmp.tmp

### 2013-08-08 alanine.nanma/template/tools/scripts/dipole.avg.sh

@@ -24,6 +24,7 @@ do
 	echo "no backup dir $backup"
 	exit
     fi
+    rm -f Mtot.xvg
     echo 16 | g_dipoles -n $backup_dir/index.ndx  -f alanine.xtc -s $backup_dir//topol.tpr -nice 0 &> /dev/null
     rm -f epsilon.xvg aver.xvg dipdist.xvg
     cd - &>/dev/null

### 2013-08-08 writedown/npt-neq/alanine.tex
start adding orientational order parameter

@@
 % \documentclass[aip,jcp,preprint,unsortedaddress,a4paper,onecolum]{revtex4-1}
-\documentclass[aip,jcp,a4paper,preprint,onecolumn]{revtex4-1}
-% \documentclass[aps,pre,twocolumn]{revtex4-1}
+\documentclass[a4paper,preprint,unsortedaddress,onecolumn]{revtex4-1}
+% \documentclass[aps,pre,twocolumn,unsortedaddress]{revtex4-1}
 % \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}
@@
   % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
-  \includegraphics[]{fig.ala/field.dipole/fig-field-dipol-conf.eps}
+  \includegraphics[width=0.45\textwidth]{fig.ala/field.dipole/fig-dipol-order-conf.eps}
   % \\
@@
   % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/c-1.eps}
-  \caption{The magnitude of the external electric field, and the
-    $x$-component of the dipole moment of the alanine molecule as a
+  \caption{The
+    $x$-component of the dipole moment, and the orientational order parameter
+    of the alanine molecule as a
     function of time. The dashed line presents the strengths of the
@@
 after $t=t_{\textrm{init}}$, the field is kept constant at
-$E_{\infty}$. In Fig.~\ref{fig:tmp3}, the dashed line shows the 
-cases considered in this work: $t_{\textrm{init}} = 10$~ps,
+$E_{\infty}$.  In this work we consider $t_{\textrm{init}} = 10$~ps,
 and $E_{\infty} = 1$~V/nm.
@@
 $x$ direction. Since the dipole of the equilibrium configurations of
-alanine can be along any direction (see also Fig.~\ref{fig:tmp3} for
-the vanished initial dipole moment), applying the electric along $x$-axis is
+alanine can be along any direction, applying the electric along $x$-axis is
 not biased.
@@
 
+%  (see also Fig.~\ref{fig:tmp3} for
+%  the vanished initial dipole moment)
+
 \subsection{Metastable sets}
@@
   \caption{The population of metastable states of the alanine dipeptide.
-    Left: the
-    equilibrium state at $t=0$~\textsf{ps}. Right: The new equilibrium
+    (a): the
+    equilibrium state at $t=0$~\textsf{ps}. (b): The new equilibrium
     state at $t=1000$~\textsf{ps}, i.e., fully relaxed under the
@@
 
+The D-NEMD method. The design of the nonequilibrium thermostating.
+
+Time scales discovered in the constant EF case.
+
+The discover of the directional probability flux introduced by the
+oscillating EF.
+
+Comment on the force field. cite A.Mey's paper.
+
+Comment on the real life-strength and frequency of the EF, if it is
+possible in experiment. such a strong field may distroy the molecule.
+
+Comment on the limitation of the non-polarizable model.
+
 % Clearly two time-scales of relaxation are observed.  For

### 2013-08-09 writedown/npt-neq/alanine.tex
add orientational discussion

@@
 \subsection{System settings and simulation protocol}
-\begin{figure}
-  \centering
-  % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
-  \includegraphics[width=0.45\textwidth]{fig.ala/field.dipole/fig-dipol-order-conf.eps}
-  % \\
-  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a1-1.eps}
-  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a2-1.eps}
-  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b1-1.eps}
-  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b2-1.eps}
-  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/c-1.eps}
-  \caption{The
-    $x$-component of the dipole moment, and the orientational order parameter
-    of the alanine molecule as a
-    function of time. The dashed line presents the strengths of the
-    external electric field, while the solid line presents the dipole
-    moments. }
-  \label{fig:tmp3}
-\end{figure}
 
@@
 \subsection{Results and discussions}
+
+\begin{figure}
+  \centering
+  % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
+  \includegraphics[width=0.45\textwidth]{fig.ala/field.dipole/fig-dipol-order-conf.eps}
+  % \\
+  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a1-1.eps}
+  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a2-1.eps}
+  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b1-1.eps}
+  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b2-1.eps}
+  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/c-1.eps}
+  \caption{The
+    $x$-component of the dipole moment, and the orientational order parameter
+    of the alanine molecule as a
+    function of time. The dashed line presents the strengths of the
+    external electric field, while the solid line presents the dipole
+    moments. }
+  \label{fig:tmp3}
+\end{figure}
+
+The Fig.~\ref{fig:tmp3}
+shows that the $x$-component of the dipole moment of the alanine dipeptide
+reaches 85\% of the maximum value in only 20~ps, which is comparable to
+the warm-up time $t_{init}$. Then the dipole slowly relaxes to the 
+maximum value in the following 400~ps. Notice that 20~ps is 25 times
+smaller than the slowest time scale of the conformational relaxation.
+We also consider the orientation of the alanine dipeptide as a function
+of time. The geometric direction of the alanine is defined by the red vector in
+Fig.~\ref{fig:tmp3}, which is the angle bisector of the two black vectors.
+The black vectors are define to connect the $\alpha$-carbon and the carbons
+on the methyl groups. We define the orientational order parameter
+\begin{align}
+  S_\theta = \langle 3\sin^2\theta - 2\rangle,
+\end{align}
+where $\theta$ is the angle between the orientation of the alanine dipeptide
+and the direction of the electric field. The order parameter
+indicate if the molecule is perpendicular to the electric field.
+If the molecule is perfectly perpendicular to the electric field, then $S_\theta = 1$;
+If the molecule has no directional
+preference at all, then $S_\theta = 0$;
+If the molecule is perfectly parallel to the electric field, then $S_\theta = -2$.
+From $t=0$ to roughly 10~ps, the orientational order parameter fastly
+decreases from 0 to -0.15, which means a weak alignment of the molecule to the external field.
+Then from $t=0$ to 500~ps, the molecule slowy changes to the orientation
+that is perpendicular to the electric field.
+
+% This indicate that when the EF is switched on, the alanine almost immediately
+% changes its conformation so that the molecular dipole is aligned to the
+% external EF.
+% align itself to the
+% direction of the external EF without much conformational change.
+% And then, the conformation is slowly adjusted according to the
+% external field (now it is the same as the molecular dipole),
+% finally  the new equilibrium is reached at a much slower time scale
+% (approximately 500~ps).
+
 \begin{figure}
@@
 
-The Fig.~\ref{fig:tmp3}
-shows that the $x$-component of the dipole moment of the alanine dipeptide
-reaches 85\% of the maximum value in only 20~ps, which is comparable to
-the warm-up time $t_{init}$. Then the dipole slowly relaxes to the 
-maximum value in the following 400~ps. Notice that 20~ps is 25 times
-smaller than the slowest time scale of the conformational relaxation.
-This indicate that when the EF is switched on, the alanine almost immediately
-align itself to the
-direction of the external EF without much conformational change.
-And then, the conformation is slowly adjusted according to the
-external field (now it is the same as the molecular dipole),
-finally  the new equilibrium is reached at a much slower time scale
-(approximately 500~ps).
-
 % After aligning to the external EF, the alanine slowly adjust its confromation,
@@
   \centering
-  \includegraphics[]{fig.ala/fig-mode2-dipol.eps}
-  \caption{The nonequilibrium dipole moment of alanine dipeptide as a
-    function of time. Only the $x$-component of the dipole moment is
-    shown here. The black line: the static electric field with turning on
+  \includegraphics[width=0.48\textwidth]{fig.ala/fig-mode2-dipol.eps}
+  \includegraphics[width=0.48\textwidth]{fig.ala/fig-mode2-order.eps}
+  \caption{The nonequilibrium dipole moment (a) and
+    orientation order parameter (b) of alanine dipeptide as a
+    function of time. In plot (a),
+    only the $x$-component of the dipole moment is
+    shown. The black line: the static electric field with turning on
     time $t_{init} = 10$~ps. The red line: oscillating field with period
@@
 
-Fig.~\ref{fig:tmp8} presents the $x$-component of the molecular dipole moment as
+Fig.~\ref{fig:tmp8} (a)
+presents the $x$-component of the molecular dipole moment as
 a function of time. The red, green and blue lines stands for the
@@
 means that the changing of the electric field is so slow that the
-alanine have enough time to firstly align to the external EF, and then
+alanine have enough time to 
 relax its internal dipole (although not completely). However,
-for $T=40$~ps, as the electric field changes faster,
-although the molecules can align to the electric field immediately,
+for $T=10$ and 40~ps, as the electric field changes faster,
+although the alanine dipeptide can response to the electric field immediately,
 it does not have enough time to fully relax the internal dipole, so we
 see the maximum alanine's dipole moment reached is smaller.
-For even smaller period $T=10$~ps, the alanine does not have enough
-time  to properly align the molecular dipole according to the external
-field, so we see the maximum dipole moment is only about one third of the
-constant EF case.
+% For even smaller period $T=10$~ps, the alanine does not have enough
+% time  to properly align the molecular dipole according to the external
+% field, so we see the maximum dipole moment is only about one third of the
+% constant EF case.
+Plot (b) of Fig.~\ref{fig:tmp9} presents the orientational order
+parameter. The notations are the same as plot (a).
+% From the constant
+% EF simulation, we see that the response of order parameter has
+% two time scales: In the fast time scale, the 
+For all periodically oscillating cases the order parameter is much
+smaller than the constant EF case. One possible reason is that the
+relaxation of the order parameter is very slow, and the molecule does
+not expose to a strong enough EF for a long enough time in a oscillating
+EF. For  $T=10$ and 40~ps, the orientation of the alanine is only weakly
+parallel to the EF. Please notice that for the constant EF case,
+we also observe a quit alignment of molecular orientation to the EF
+at time scale 10~ps. For $T=200$~ps, The molecule periodically
+becomes perpendicular to the EF, but this directional preference is much
+weaker than the constant EF case.
 

### 2013-08-09 writedown/npt-neq/alanine.tex
added discussion of the dipole moment and orientation

@@
   \centering
-  \includegraphics[width=0.45\textwidth]{fig.ala/ext.mode1.100.Ex.01.00.t1200ps/fig-begin-1.eps}
-  \includegraphics[width=0.45\textwidth]{fig.ala/ext.mode1.100.Ex.01.00.t1200ps/fig-end-1.eps}
+  \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{fig.ala/ext.mode1.010.Ex.01.00.t1000ps.recheck/c-2.eps}}
+  \includegraphics[width=0.37\textwidth]{fig.ala/ext.mode1.010.Ex.01.00.t1000ps.recheck/fig-begin-1.eps}
+  \includegraphics[width=0.37\textwidth]{fig.ala/ext.mode1.010.Ex.01.00.t1000ps.recheck/fig-end-1.eps}
   \caption{The population of metastable states of the alanine dipeptide.
@@
   \centering
-  % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
-  \includegraphics[width=0.45\textwidth]{fig.ala/field.dipole/fig-dipol-order-conf.eps}
-  % \\
-  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a1-1.eps}
-  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a2-1.eps}
-  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b1-1.eps}
-  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b2-1.eps}
-  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/c-1.eps}
-  \caption{The
-    $x$-component of the dipole moment, and the orientational order parameter
-    of the alanine molecule as a
-    function of time. The dashed line presents the strengths of the
-    external electric field, while the solid line presents the dipole
-    moments. }
-  \label{fig:tmp3}
-\end{figure}
-
-The Fig.~\ref{fig:tmp3}
-shows that the $x$-component of the dipole moment of the alanine dipeptide
-reaches 85\% of the maximum value in only 20~ps, which is comparable to
-the warm-up time $t_{init}$. Then the dipole slowly relaxes to the 
-maximum value in the following 400~ps. Notice that 20~ps is 25 times
-smaller than the slowest time scale of the conformational relaxation.
-We also consider the orientation of the alanine dipeptide as a function
-of time. The geometric direction of the alanine is defined by the red vector in
-Fig.~\ref{fig:tmp3}, which is the angle bisector of the two black vectors.
-The black vectors are define to connect the $\alpha$-carbon and the carbons
-on the methyl groups. We define the orientational order parameter
-\begin{align}
-  S_\theta = \langle 3\sin^2\theta - 2\rangle,
-\end{align}
-where $\theta$ is the angle between the orientation of the alanine dipeptide
-and the direction of the electric field. The order parameter
-indicate if the molecule is perpendicular to the electric field.
-If the molecule is perfectly perpendicular to the electric field, then $S_\theta = 1$;
-If the molecule has no directional
-preference at all, then $S_\theta = 0$;
-If the molecule is perfectly parallel to the electric field, then $S_\theta = -2$.
-From $t=0$ to roughly 10~ps, the orientational order parameter fastly
-decreases from 0 to -0.15, which means a weak alignment of the molecule to the external field.
-Then from $t=0$ to 500~ps, the molecule slowy changes to the orientation
-that is perpendicular to the electric field.
-
-% This indicate that when the EF is switched on, the alanine almost immediately
-% changes its conformation so that the molecular dipole is aligned to the
-% external EF.
-% align itself to the
-% direction of the external EF without much conformational change.
-% And then, the conformation is slowly adjusted according to the
-% external field (now it is the same as the molecular dipole),
-% finally  the new equilibrium is reached at a much slower time scale
-% (approximately 500~ps).
-
-\begin{figure}
-  \centering
   \includegraphics[]{fig.ala/fig-meta-npt.eps}
@@
 % of all populations are around $500 \sim 600~\textsf{ps}$.
+
+\begin{figure}
+  \centering
+  % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
+  \includegraphics[width=0.45\textwidth]{fig.ala/field.dipole/fig-dipol-order-conf.eps}
+  % \\
+  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a1-1.eps}
+  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a2-1.eps}
+  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b1-1.eps}
+  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b2-1.eps}
+  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/c-1.eps}
+  \caption{The
+    $x$-component of the dipole moment, and the orientational order parameter
+    of the alanine molecule as a
+    function of time. The dashed line presents the strengths of the
+    external electric field, while the solid line presents the dipole
+    moments. }
+  \label{fig:tmp3}
+\end{figure}
+
+The Fig.~\ref{fig:tmp3}
+shows that the $x$-component of the dipole moment of the alanine dipeptide
+reaches 85\% of the maximum value in only 20~ps, which is comparable to
+the warm-up time $t_{init}$. Then the dipole slowly relaxes to the 
+maximum value in the following 400~ps. Notice that 20~ps is 25 times
+smaller than the slowest time scale of the conformational relaxation.
+We calculate the averaged dipole moment of different metastable state
+under the constant EF, and they are 6.8, 6.0, 5.1, 3.1 and 7.1~Debye
+for $A_1$, $A_2$, $B_1$, $B_2$ and $C$, respectively.
+Under a constant EF, the system will be driven towards those
+conformations that with higher dipole moment, because the
+energy of the system will be lowered by aligning the the dipole
+to the external EF.
+It is clear that
+the $\alpha$-helix and left-handed $\alpha$-helix are of higher
+dipole moments than $\beta$-sheet conformations, so the probability
+of being in the $\alpha$-helix conformations were
+observed being increased under the EF.  $A_1$ and $C$ are the most
+probable conformations because their dipole moments are the highest
+among all metastable conformation. Moreover, the $B_2$  vanishes, because
+its dipole is significantly lower than other conformations.
+% This also explains the two-time scale behavior of the molecular dipole
+% moment.
+From 0 to 20~ps, the probability of
+lowest dipole conformation $B_2$ quickly
+vanishes, so there is a sharp increment of the average molecular
+dipole moment. Then until 500~ps, since the conformation slowly migrates from
+$B_1$ to $A_1$ and $C$, and also since the dipole moment $A_1$ and $C$
+is higher than $B_1$, the average molecular dipole moment slowly increases
+to the maximum value.
+
+We also consider the orientation of the alanine dipeptide as a function
+of time.
+The geometric direction of the alanine is defined by the red vector in
+Fig.~\ref{fig:tmp3}, which is the angle bisector of the two black vectors.
+The black vectors are define to connect the $\alpha$-carbon and the carbons
+on the methyl groups. We define the orientational order parameter
+\begin{align}
+  S_\theta = \langle 3\sin^2\theta - 2\rangle,
+\end{align}
+where $\theta$ is the angle between the orientation of the alanine dipeptide
+and the direction of the electric field. The order parameter
+indicate if the molecule is perpendicular to the electric field.
+If the molecule is perfectly perpendicular to the electric field, then $S_\theta = 1$;
+If the molecule has no directional
+preference at all, then $S_\theta = 0$;
+If the molecule is perfectly parallel to the electric field, then $S_\theta = -2$.
+From $t=0$ to roughly 10~ps, the orientational order parameter fastly
+decreases from 0 to -0.15, which means a weak alignment of the molecule to the external field.
+Then from $t=0$ to 500~ps, the molecule slowly changes to the orientation
+that is perpendicular to the electric field.
+
+% This indicate that when the EF is switched on, the alanine almost immediately
+% changes its conformation so that the molecular dipole is aligned to the
+% external EF.
+% align itself to the
+% direction of the external EF without much conformational change.
+% And then, the conformation is slowly adjusted according to the
+% external field (now it is the same as the molecular dipole),
+% finally  the new equilibrium is reached at a much slower time scale
+% (approximately 500~ps).
 

### 2013-08-14 alanine.nanma/template/tools/angles/app/two.vectors.cpp
tried a lot with two vectors

@@ -29,7 +29,7 @@ int main(int argc, char * argv[])
   desc.add_options()
       ("help,h", "print this message")
       ("output,o", po::value<std::string > (&ofile)->default_value ("two.vectors.out"), "the order parameter of the molecule")
-      ("input-dir",  po::value<std::string > (&ifile)->default_value ("dir.name"), "the file of file names");
+      ("input-name",  po::value<std::string > (&ifile)->default_value ("xtc.name"), "the file of file names");
 
   po::variables_map vm;
   po::store(po::parse_command_line(argc, argv, desc), vm);
@@ -49,8 +49,15 @@ int main(int argc, char * argv[])
   vector<float > times;
   vector<vector<double > > vector0;
   vector<vector<double > > vector1;
+  vector<vector<double > > vector2;
   vector<double > length0;
   vector<double > length1;
+  vector<double > length2;
+  vector<double > order0;
+  vector<double > order1;
+  vector<double > order2;
+  vector<double > avg2;
+  vector<double > var2;
   unsigned countFile = 0;
   
 
@@ -58,7 +65,6 @@ int main(int argc, char * argv[])
     XtcLoader xtcl ;
     vector<vector<double > > frame;
     string myfilename (nameline);
-    myfilename += string("/traj.xtc");
     cout << "reading file " << myfilename << endl;    
     if (! xtcl.reinit(myfilename.c_str())){
       return 1;
@@ -81,10 +87,38 @@ int main(int argc, char * argv[])
 	}
 	dd0 = sqrt(dd0);
 	dd1 = sqrt(dd1);
+	for (unsigned dd = 0; dd < 3; ++dd){
+	  c0[dd] /= dd0;
+	  c1[dd] /= dd1;
+	}
+	vector<double > c2(c0);
+	double dd2 = 0.;
+	for (unsigned dd = 0; dd < 3; ++dd){
+	  c2[dd] += c1[dd];
+	  dd2 += c2[dd] * c2[dd];
+	}
+	dd2 = sqrt(dd2);
+	for (unsigned dd = 0; dd < 3; ++dd){
+	  c2[dd] /= dd2;
+	}
 	vector0.push_back (c0);
 	vector1.push_back (c1);
[…]

### 2013-08-14 writedown/npt-neq/alanine.tex

@@
 
-\title{Exploring Molecular Conformations and Related Time Scales via Nonequilibrium Molecular Dynamics Simulation}
+\title{Exploring Conformational Dynamics and Related Time Scales via Nonequilibrium Molecular Dynamics Simulation}
 % \title{The non-equilibrium molecular dynamics simulation of the alanine dipeptide under electric field}
@@
 freeze the movement of the alpha-carbon, so that the alanine is always
-located at the center of the simulation region.  The validity of this
-setting will be later check by numerical examples showing that the
+located at the center of the simulation region.
+Therefore, the dynamics is preseved in the Hamiltonian dynamics region (where the properties of interest are observed)
+and the artificial effect of thermostating is negligible.
+At the same time, the thermostating region works as a infinitely large
+environment that effectively absorbs the extra heat, so that
+the nonthermal effect can be studied.
+The validity of the above
+statement will be later check latter by numerical examples showing that the
 nonequilibrium observables do not depends on the size of the system
@@
 not biased.
+Being more general, in this paper we denote the
+electric field as a function of time $\vect E(t)$.
+Therefore, the constant electric field is
+$\vect E(t) = (E_\infty\cdot t/t_{init},0,0)$ as $0\leq t < t_{init}$, and 
+$\vect E(t) = (E_\infty,0,0)$
+as $t \geq t_{init}$.
 The system is set up in a $2.7\times 2.7\times
@@
 water molecules.
+The electric field exserts force $\vect F = q \vect E(t)$ on
+the partial charge $q$ in the system.
 The size of the  Hamiltonian dynamics region is $R_{ex} = 1.0$~nm.
@@
     The warm-up time $t_{init} = 10$~ps.
-    The first row shows the probability flux $F_{J,I}(t)$, while the second
+    The first row shows the probability flux $F_{J,I}(t)$ with unit $\textrm{ps}^{-1}$, while the second
     shows the integrated  probability flux denoted by $Q_{J,I}(t)$.
@@
     external electric field, while the solid line presents the dipole
-    moments. }
+    moments. The left vertical axis is for the dipole moment, while
+    the right is for the orientational order parameter.
+  }
   \label{fig:tmp3}
@@
 reaches 85\% of the maximum value in only 20~ps, which is comparable to
-the warm-up time $t_{init}$. Then the dipole slowly relaxes to the 
-maximum value in the following 400~ps. Notice that 20~ps is 25 times
+the warm-up time $t_{init}$, and is 25 times
 smaller than the slowest time scale of the conformational relaxation.
+Then in the following 400~ps, the dipole slowly relaxes to the 
+maximum value, that reads
+6.8~Debye, and is  corresponding to a dipole energy of ca.
+$-13.6$~kJ/mol. The main free energy barriers among the
+metastable states are reported to be of order $20\sim 40$~kJ/mol~\cite{bohner2012algorithm},
+which is comparable to the dipole energy. This explains the 
+conformational changes under the electric field.
 We calculate the averaged dipole moment of different metastable state
@@
 From $t=0$ to roughly 10~ps, the orientational order parameter fastly
-decreases from 0 to -0.15, which means a weak alignment of the molecule to the external field.
+decreases from 0 to $-0.15$, which means a weak alignment of the molecule to the external field.
 Then from $t=0$ to 500~ps, the molecule slowly changes to the orientation
@@
 \begin{align}
-  E(t) = E_0\sin(2\pi \omega t),
+  \vect E(t) = (E_0\sin(2\pi \omega t), 0, 0)
 \end{align}
@@
     of the arrows approximately presents the strength of the flux.
+    The numbers near the arrows indicates the strength of the averged
+    probability flux, the unit of which is $10^{-3}\textrm{ps}^{-1}$.
   }

### 2013-08-16 writedown/npt-neq/alanine.tex
backup

@@
 conformational changing under a generally time-dependent EF.
-In the present paper, we study the minimal model peptide
+In the present paper, we study a small model peptide
 segment -- alanine dipeptide. We take the approach of starting from a
@@
 is to simulate a infinitely large isolated system, or any large enough
-isolated subsystem of it. In practice, it is both impossible and unnecessary to
+isolated subsystem of it.
+In practice, it is both impossible and unnecessary to
 do such a simulation, due to the unaffordable computational expense.
@@
 
+\begin{table}
+  \centering
+  \begin{tabular*}{0.4\textwidth}{@{\extracolsep{\fill}}lc}\hline\hline
+    Direction        & time scale [ ps ] \\\hline
+    $A_1\rightarrow A_2$        &       $0\sim 10$      \\
+    $B_1\rightarrow B_2$        &       $0\sim 10$      \\    
+    $A_2\rightarrow A_1$        &       $10\sim 100$      \\
+    $B_2\rightarrow B_1$        &       $10\sim 100$      \\    
+    $B_2\rightarrow A_1,\ A_2,\ C$        &       $10\sim 50$      \\    
+    $B_1\rightarrow A_1,\ C$        &       $10\sim 500$      \\    \hline\hline
+  \end{tabular*}
+  \caption{A list of main probabilty fluxes and the corresponding time scales observed in the constant EF case.}
+  \label{tab:tmp1}
+\end{table}
+
 Even though the system is finally relaxed to the new equilibrium,
@@
 6.8~Debye, and is corresponding to a dipole energy of ca.
-$-13.6$~kJ/mol. The main free energy barriers among the
-metastable states are reported to be of order $20\sim 40$~kJ/mol~\cite{bohner2012algorithm},
+$-13.6$~kJ/mol.
+The EF induced solvent effect on the alanine is also counted by calculating the
+difference of the water-alaine electrostatic interaction 
+between systems with and without the EF, and the
+energy difference is found to be $-19.1$~~kJ/mol that is
+comparable to the dipole energy of the alanine itself.
+The main free energy barriers among the
+metastable states were reported to be of order $20\sim 40$~kJ/mol~\cite{bohner2012algorithm},
 which is comparable to the dipole energy. This explains the 

### 2013-08-19 writedown/npt-neq/alanine.tex
backup

@@
 In this work, we always assume that the initial probability distribution
-$\rho(\vect x, 0)$ is known, and is equal to the equilibrium distribution
-without any electric field.
+$\rho(\vect x, 0)$ is known, and is identical to the equilibrium distribution
+without any EF.
 The bracket on the right hand side of Eq.~\eqref{eqn:tmp1} denotes the inner produce in the
@@
 where $iL(t) = \{\cdot, \mathcal H\}$ is the Liouville operator.
-The Eq.~\eqref{eqn:tmp2}
+Eq.~\eqref{eqn:tmp2}
 can be formally solved by $\rho(\vect x, t) = e^{-iL(t)} \rho(\vect x, 0)$.
@@
 \end{align}
-This equation can be formally solved by $\hat O(\vect x(t)) = e^{iL(t)} O(\vect x, 0)$, therefore,
+This equation can be formally solved by $\hat O(\vect x(t)) = e^{iL(t)} \hat O(\vect x(0))$, therefore,
 \begin{align}\nonumber
@@
 \end{align}
-Since we assume that the initial
-probability distribution is the equilibrium distribution, an
+Since we assume that the system starts from the equilibrium
+distribution, an
 explicit translation of Eq.~\eqref{eqn:tmp4} is that the
 nonequilibrium observable is equal to the ensemble average of
-microscopic observable measured along trajectory $\vect x(t)$, the
-initial configuration of which is subject to the \emph{equilibrium}
+microscopic observable measured along trajectories, the
+initial configurations of which are subject to the \emph{equilibrium}
 distribution. In practice, we firstly run an equilibrium MD simulation
@@
 Being more generalized, if the microscopic observable depends not only on the end
-configuration at time $t$ but also depends on the historical
-configurations along the trajectory, the expression~\eqref{eqn:tmp4} can be generalize to
+configuration at time $t$, but also on the historical
+configurations along the trajectory, then expression~\eqref{eqn:tmp4} takes the generalized form:
 \begin{align}
@@
 
-The aforementioned D-NEMD simulation algorithm
-does not describe how the boundary of the system should be set up.
-The very naive idea of doing the simulation
-is to simulate a infinitely large isolated system, or any large enough
-isolated subsystem of it.
-In practice, it is both impossible and unnecessary to
-do such a simulation, due to the unaffordable computational expense.
-Therefore, proper boundary condition should be supplied
-to truncated the simulation region. It is only possible when we
-have a clear knowledge on
-on how the nonequilibrium system is set up,
-and what are the nonequilibrium observables to measure.
-
 \begin{figure}
@@
   \includegraphics[width=0.3\textwidth]{fig/thermostat.eps}
-  \caption{Schematic plot of the truncated nonequilibrium subsystem.
-    The white part is the Hamiltonian dynamics subsystem
-    and the gray part is thermostating region. The whole system
-    is subject to the periodic boundary condition.}
+  \caption{Schematic plot of the nonequilibrium temperature control.
+    The white part is the Hamiltonian dynamics region
+    and the gray part is thermostating region.
+    $R_{ex}$ denotes the size of the Hamiltonian dynamics region, which
+    is a sphere located at the center of the box in the Figure.
+    The whole system
+    is subject to the periodic boundary condition. }
   \label{fig:tmp2}
@@
 
-Since we are mainly interested in the
-nonthermal~\cite{delaHoz2005microwaves} effect of the electric field
-to the configuration of a solvated alanine dipeptide, we assume the
-alanine is embeded into an infinitely large solvent environment, and
-the electric field is only applied to the neighborhood of the alanine.
-Any extra heat generated by the electric field can be effectively
-absorbed by the solvent environment.  It is argued that such an
-accurate reaction temperature control is essential for being able to
+% The aforementioned D-NEMD simulation algorithm
+% does not describe how the boundary of the system should be set up.
+% The very naive idea of doing the simulation
+% is to simulate a infinitely large isolated system, or any large enough
+% isolated subsystem of it.
+% In practice, 
+% Therefore, we are interested in a
+
+We are mainly interested in the
+nonthermal~\cite{delaHoz2005microwaves} effect of the EF
+to the configuration of a solvated alanine dipeptide,
+so the temperature control in a nonequilibrium system
+becomes an important issue, becuase it was argued that  an
+accurate internal reaction temperature control is essential for being able to
 perform reproducible experiments~\cite{damm2012can}.
-Now the question comes to how to truncate the solvent environment
-so that the system can be handled by the limited computer resource.
+A naive (but close to realistic) implementation of the temperature control is to 
+embeded the alanine into an infinitely large solvent environment, and 
+the EF is only applied to the neighborhood of the alanine, so that
+any extra heat generated by the EF can be effectively
+absorbed by the solvent environment.
+However, in practice, it is sometime too expensive to explicitly
+simulate a very large solvent environment
+due to the usually limited computational resources.
+Therefore, we are interested in how to cheaply replace the infinitely large
+solvent environment by a small affordable system, while
+at the same time accurately reproduce the nonequilibrium
+physical properties of interest.
 % In practice, it is impossible to simulate an infinitely large
 % environment.
-For an equilibrium simulation, the solution is to couple
-the system to a thermostat, under which the canonical ensemble can be
+If only the equilibrium properties are interested, the solution is to couple
+the system to a thermostat, under which the desired ensemble
+(canonical in this case) can be
 sampled by only simulating a finite size system with periodic boundary
-condition. For a nonequilibrium simulation, simply couple the system
-to a thermostat may not be a good idea, because the \emph{dynamics}
-generated by the thermostat is artificial, and deviation from the
-Hamiltonian dynamics under investigation will introduce artificial
-effects in the nonequilibrium observations. To solve this problem, we
+condition.
+However, directly coupling a thermostat to the nonequilibrium system
+will disturb the original Hamiltonian dynamics. This is
+in general problematic, 
+because the dynamics  under thermostating is artificial designed,
+so that the equilibrium distribution can be correctly produce, but not
+the nonequilibrium properties of system.
+% dynamics of the system is no longer Hamiltonian, and is
+% artificial designed to reach the equilibrium probability distribution.
+% However, for a nonequilibrium system, the \emph{dynamics} properties
+% will be distrubed by the thermostat, because the
+% dynamics of the system is no longer Hamiltonian, and is
+% artificial designed to reach the equilibrium probability distribution.
+% For a nonequilibrium simulation, simply couple the system
+% to a thermostat may not be a good idea, because the \emph{dynamics}
+% generated by the thermostat is artificial, and deviation from the
+% Hamiltonian dynamics under investigation will introduce artificial
+% effects in the nonequilibrium observations.
+To solve this problem, we
 observe that only preserving the Hamiltonian dynamics of the alanine 
@@
 large system, we only simulate a finite size system with periodic
-boundary condition. The simulating region is divided into two
+boundary condition. Accordingly, the simulating region is divided into two
 subregions: Near the alanine dipeptide, the dynamics is kept to be
@@
 Therefore, the dynamics is preseved in the Hamiltonian dynamics region (where the properties of interest are observed)
-and the artificial effect of thermostating is negligible.
+and the artificial effect of thermostating is negligible due to the finite corrlation
+range of liquid water.
 At the same time, the thermostating region works as a infinitely large
@@
 \section{Example I: Alanine dipeptide
-  under a constant electric field}
+  under a constant EF}
 
@@
 under a constant EF.  At time $t=0$~ps, the system
-has been fully equilibriated without any electric field. From $t=0$ to
+has been fully equilibriated without any EF. From $t=0$ to
 $t=t_{\textrm{init}}$, the eclectic field is switched on linearly, while
@@
 Being more general, in this paper we denote the
-electric field as a function of time $\vect E(t)$.
-Therefore, the constant electric field is
+EF as a function of time $\vect E(t)$.
+Therefore, the constant EF is
 $\vect E(t) = (E_\infty\cdot t/t_{init},0,0)$ as $0\leq t < t_{init}$, and 
@@
 water molecules.
-The electric field exserts force $\vect F = q \vect E(t)$ on
+The EF exserts force $\vect F = q \vect E(t)$ on
 the partial charge $q$ in the system.
@@
     state at $t=1000$~\textsf{ps}, i.e., fully relaxed under the
-    constant electric field 1~V/nm. The darker color
+    constant EF 1~V/nm. The darker color
     indicates larger population on the Ramachandran histogram.}
@@
 From Fig.~\ref{fig:tmp4}, it is obvious that the population in each
-metastable state changes due to the external electric field, for
+metastable state changes due to the external EF, for
 example, the population of state $C$ vanishes in equilibrium,
-but plays an important role when the electric field is applied. We
+but plays an important role when the EF is applied. We
 therefore want to study how the alanine changes from one conformation
 to the other, how fast is the change, and the relations to the 
-the electric field. 
+the EF. 
 Firstly, we calculate the probability of being in a certain state that
@@
 probability of alpha helix $A_1$ conformation grows from 45\% to 70\%.
-Alpha helix $A_2$  does not change a lot under the electric field.
+Alpha helix $A_2$  does not change a lot under the EF.
 The left-hand helix configuration $C$ noticeably grows from 0\% to 20\%.
@@
 This time-scale is actually 50 times slower than speed, at which
-the electric field is switched on ($t_{\textrm{init}} = 10~\textsf{ps}$).
+the EF is switched on ($t_{\textrm{init}} = 10~\textsf{ps}$).
 
@@
 % $t_{\textrm{init}} = 10~\textsf{ps}$.  The dynamics of $B_2$ is
-% faster: it decays to zero as soon as the external electric field is fully
+% faster: it decays to zero as soon as the external EF is fully
 % switched on. In the case of $t_{\textrm{init}} = 500~\textsf{ps}$, the
-% growth of the external electric field is comparable to the longest
+% growth of the external EF is comparable to the longest
 % internal time scale of system, which means that the changes of the
@@
     function of time. The dashed line presents the strengths of the
-    external electric field, while the solid line presents the dipole
+    external EF, while the solid line presents the dipole
     moments. The left vertical axis is for the dipole moment, while
@@
 which is comparable to the dipole energy. This explains the 
-conformational changes under the electric field.
+conformational changes under the EF.
 We calculate the averaged dipole moment of different metastable state
@@
 where $\theta$ is the angle between the orientation of the alanine dipeptide
-and the direction of the electric field. The order parameter
-indicate if the molecule is perpendicular to the electric field.
-If the molecule is perfectly perpendicular to the electric field, then $S_\theta = 1$;
+and the direction of the EF. The order parameter
+indicate if the molecule is perpendicular to the EF.
+If the molecule is perfectly perpendicular to the EF, then $S_\theta = 1$;
 If the molecule has no directional
 preference at all, then $S_\theta = 0$;
-If the molecule is perfectly parallel to the electric field, then $S_\theta = -2$.
+If the molecule is perfectly parallel to the EF, then $S_\theta = -2$.
 From $t=0$ to roughly 10~ps, the orientational order parameter fastly
@@
 Then from $t=0$ to 500~ps, the molecule slowly changes to the orientation
-that is perpendicular to the electric field.
+that is perpendicular to the EF.
 
@@
 \section{Example II:
-  periodically oscillating electric field}
-
-We have tested the periodically oscillating electric field which has
+  periodically oscillating EF}
+
+We have tested the periodically oscillating EF which has
 a $\sin$-wave shape:
@@
 % commensurate to the time scales discovered by the nonequilibrium MD
-% simulation of constant electric field. The first is to test the if the
+% simulation of constant EF. The first is to test the if the
 % period is further reduced to smaller than 20~ps, there is any other
@@
 % chosen according to the discovered time scales in the constant
-% electric field simulation, the nonequilibrium phenonema of oscillating
-% electric field cannot be derived from the constant field system.
-% As far as the electric field changes, the internal time scale of the
+% EF simulation, the nonequilibrium phenonema of oscillating
+% EF cannot be derived from the constant field system.
+% As far as the EF changes, the internal time scale of the
 % system also changes, therefore, the nonequilibrium probabilities is a
@@
     only the $x$-component of the dipole moment is
-    shown. The black line: the static electric field with turning on
+    shown. The black line: the static EF with turning on
     time $t_{init} = 10$~ps. The red line: oscillating field with period
@@
 results of $T=10$~ps, 40~ps and 200~ps, respectively. The black lines
-shows the dipole moment under constant electric field
+shows the dipole moment under constant EF
 for reference.
@@
 At $T=200$~ps, the maximum magnitude of the molecular
-dipole moment is almost the same as the case of constant electric field, which
-means that the changing of the electric field is so slow that the
+dipole moment is almost the same as the case of constant EF, which
+means that the changing of the EF is so slow that the
 alanine have enough time to 
 relax its internal dipole (although not completely). However,
-for $T=10$ and 40~ps, as the electric field changes faster,
-although the alanine dipeptide can response to the electric field immediately,
+for $T=10$ and 40~ps, as the EF changes faster,
+although the alanine dipeptide can response to the EF immediately,
 it does not have enough time to fully relax the internal dipole, so we
@@
   \caption{ The probability of being in a certain metastable state for
-    periodically oscillating electric field. Different periods,
+    periodically oscillating EF. Different periods,
     i.e. $T=10$~ps, 40~ps and 200~ps, are presented here.  The
@@
 The Fig.~\ref{fig:tmp9} shows the probability of being in a certain
-metastable state for periodically oscillating electric field.  The
+metastable state for periodically oscillating EF.  The
 Fig.~\ref{fig:tmp10} presents the integrated probability flux among
@@
 % of the system dissipates into the universe. In the case of switching on
-% electric field system, two limiting scenarios are considered by us: (1)
-% The subsystem is isolated from the universe: The electric field is
+% EF system, two limiting scenarios are considered by us: (1)
+% The subsystem is isolated from the universe: The EF is
 % applied to a system that conserves the energy, volume and number of

### 2013-08-20 writedown/npt-neq/alanine.tex
revise, send the source to Luigi

@@
 has been fully equilibriated without any EF. From $t=0$ to
-$t=t_{\textrm{init}}$, the eclectic field is switched on linearly, while
-after $t=t_{\textrm{init}}$, the field is kept constant at
-$E_{\infty}$.  In this work we consider $t_{\textrm{init}} = 10$~ps,
+warm-up time $t=t_{\textrm{warm}}$, the eclectic field is switched on linearly, while
+after $t=t_{\textrm{warm}}$, the field is kept constant at
+$E_{\infty}$.  In this work we consider $t_{\textrm{warm}} = 10$~ps,
 and $E_{\infty} = 1$~V/nm.
@@
 Therefore, the constant EF is
-$\vect E(t) = (E_\infty\cdot t/t_{init},0,0)$ as $0\leq t < t_{init}$, and 
+$\vect E(t) = (E_\infty\cdot t/t_{warm},0,0)$ as $0\leq t < t_{warm}$, and 
 $\vect E(t) = (E_\infty,0,0)$
-as $t \geq t_{init}$.
+as $t \geq t_{warm}$.
 The system is set up in a $2.7\times 2.7\times
@@
 
-On each branching trajectory, to easy the analysis of the conformation
+On each branching trajectory, to easy the analysis of the conformational dynamics
 of alanine dipeptide, the molecular configuration is projected on
@@
 shown in Fig.~\ref{fig:tmp4}. The equilibrium distribution of the
-conformation is given in the left plot, and the fully relaxed
-conformation under $E_{\infty} = 1$~V/nm is given in the right plot.  It is
+conformation is given in the plot (a), and the fully relaxed
+conformation under $E_{\infty} = 1$~V/nm is given  plot (b).  It is
 clear the conformations are populated in several clusters, and the
@@
 This means that only a few of the conformations are likely to be observed,
-while there is nearly no opportunity to see others. 
+in the nonequilibrium process.
 These conformations are called ``metastable states''.
@@
 Since in this paper we do not focus on the discussion of the definition for the metastability of the system,
-we assume they have the same meaning.
+we do not distinguish the definations, and assume they have the same meaning.
 We manually divide the
 Ramachandran histogram into 5 subregions, see Fig.~\ref{fig:tmp4},
-then the observation on the Ramachandran histogram is projected to the
-observation of these 5 states, i.e. $\{A_1, A_2, B_1, B_2, C\}$, which
-correspond to the molecular conformations we are investigating in this work.
-These subregions
+then the observation of conformations on the Ramachandran histogram is projected to the
+observation of these 5 states, i.e. $\{A_1, A_2, B_1, B_2, C\}$.
+These states
 correspond to different secondary structure of a peptide chain:
@@
 \end{align}
-please notice that the time dependency of the probability, so it is
+Notice that the time dependency of the probability, so it is
 a nonequilibrium observable.
@@
 \end{align}
-which presents the rate of how much conformation $J$ is changed
-into $I$. A positive value indicates the
+which presents the rate of how much conformation $J$ changes
+into $I$ at time $t$. A positive value indicates the
 net flux from $J$ to $I$,
 while a negative value indicates a net flux from $I$ to $J$.
-Now project the original nonequilibrium process $\vect x_t$
-onto the discretized states $\{A_1, A_2, B_1, B_2, C\}$,
+Now the original nonequilibrium process $\vect x_t$
+is projected onto the discretized states $\{A_1, A_2, B_1, B_2, C\}$,
 if the resulting reduced process 
@@
   \caption{The probability of being in a metastable states under a constant EF.
-    The warm-up time $t_{init} = 10$~ps. The red line stands for state $A_1$,
+    The warm-up time $t_{warm} = 10$~ps. The red line stands for state $A_1$,
     green for $A_2$, dark blue for $B_1$, purple for $B_2$ and light blue
@@
   %   The dashed vertical lines indicate the three different time scale of
-  % metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
+  % metastable set population at $t_{\textrm{warm}} = 10~\textsf{ps}$.}
   % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-1.eps}
@@
     The net probability flux and its integration under the constant EF case.
-    The warm-up time $t_{init} = 10$~ps.
+    The warm-up time $t_{warm} = 10$~ps.
     The first row shows the probability flux $F_{J,I}(t)$ with unit $\textrm{ps}^{-1}$, while the second
@@
 %   %   The dashed vertical lines indicate the three different time scale of
-%   % metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
+%   % metastable set population at $t_{\textrm{warm}} = 10~\textsf{ps}$.}
 %   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-1.eps}
@@
 %   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-5.eps}
-%   \caption{Forward and backward nonequilibrium transition probability of the case $t_{init} = 10$~ps.}
+%   \caption{Forward and backward nonequilibrium transition probability of the case $t_{warm} = 10$~ps.}
 %   \label{fig:tmp6}
@@
 The time-dependent probability of the system in a certain metastable state is given in
-Fig.~\ref{fig:tmp5}. The beta sheet conformation,
+Fig.~\ref{fig:tmp5}. The beta sheet conformation $B_1$ and $B_2$,
 which presents at the beginning,
 fades away as the system relaxes to the new equilibrium. The
-probability of alpha helix $A_1$ conformation grows from 45\% to 70\%.
+probability of alpha helix $A_1$ conformation grows from 0.45 to 0.69.
 Alpha helix $A_2$  does not change a lot under the EF.
-The left-hand helix configuration $C$ noticeably grows from 0\% to 20\%.
+The left-hand helix conformation $C$ noticeably grows from 0 to 0.22.
 
@@
 % it gradually relaxes to the new equilibrium,
-so we do not see and change
+so we do not see any change
 in the population of the metastable states.
@@
     Direction        & time scale [ ps ] \\\hline
-    $A_1\rightarrow A_2$        &       $0\sim 10$      \\
-    $B_1\rightarrow B_2$        &       $0\sim 10$      \\    
-    $A_2\rightarrow A_1$        &       $10\sim 100$      \\
-    $B_2\rightarrow B_1$        &       $10\sim 100$      \\    
-    $B_2\rightarrow A_1,\ A_2,\ C$        &       $10\sim 50$      \\    
-    $B_1\rightarrow A_1,\ C$        &       $10\sim 500$      \\    \hline\hline
+    $A_1\rightarrow A_2$        &       $\sim 10$      \\
+    $B_1\rightarrow B_2$        &       $\sim 10$      \\    
+    $B_2\rightarrow A_1,\ A_2,\ C$        &       $\sim 50$      \\    
+    $A_2\rightarrow A_1$        &       $\sim 100$      \\
+    $B_2\rightarrow B_1$        &       $\sim 100$      \\    
+    $B_1\rightarrow A_1,\ C$        &       $\sim 500$      \\    \hline\hline
   \end{tabular*}
@@
 From Fig.~\ref{fig:tmp6}, we observe mainly
-three different timescales of the conformational relaxation:
+three different timescales of the conformational relaxation, which
+are summarized in Tab.~\ref{tab:tmp1}.
 (1) From
-$t=0$ to approximately 10~\textsf{ps}, there is firstly
-a flux from $A_1$ to $A_2$, then it goes to the opposite direction, i.e.
-from $A_2$ to $A_1$.
+$t=0$ to approximately 10~\textsf{ps}, a net flux from 
+a flux from $A_1$ to $A_2$.
 A similar flux is also observed from $B_1$ to $B_2$.
+Then, these two fluxes vanish and then turn to the opposite direction
+i.e. $A_2$ to $A_1$ and $B_2$ to $B_1$, respectively.
 % the population of $A_1$ firstly decreases and then increases to the original value,
@@
 vanishes in about 50~ps.
-The net flux from $B_1$  to $A_1$ and $C$ decay slower and 
-will be discussed later.
+% The net flux from $B_1$  to $A_1$ and $C$ decay slower and 
+% will be discussed later.
 At this stage, the probability of $B_2$ decreases to almost 0,
@@
 This time-scale is actually 50 times slower than speed, at which
-the EF is switched on ($t_{\textrm{init}} = 10~\textsf{ps}$).
-
-% After aligning to the external EF, the alanine slowly adjust its confromation,
+the EF was switched on ($t_{\textrm{warm}} = 10~\textsf{ps}$).
+
+% After aligning to the external EF, the alanine slowly adjust its conformation,
 % and the new equilibrium is reached at slower time scales.
@@
 % To further test the dynamics of metastable population, two simulations
-% of $t_{\textrm{init}} = 100~\textsf{ps}$ and $t_{\textrm{init}} =
+% of $t_{\textrm{warm}} = 100~\textsf{ps}$ and $t_{\textrm{warm}} =
 % 500~\textsf{ps}$ are performed. The first time scale of $t =
 % 20~\textsf{ps}$ disappears in both of the testing simulations. In the
-% simulation of $t_{\textrm{init}} = 100~\textsf{ps}$, the population of
+% simulation of $t_{\textrm{warm}} = 100~\textsf{ps}$, the population of
 % $A$, $B_1$ and $C$ converges to the non-equilibrium steady state at
@@
 % $A_1$, $B_1$ and $C$ presented in the testing case of
-% $t_{\textrm{init}} = 10~\textsf{ps}$.  The dynamics of $B_2$ is
+% $t_{\textrm{warm}} = 10~\textsf{ps}$.  The dynamics of $B_2$ is
 % faster: it decays to zero as soon as the external EF is fully
-% switched on. In the case of $t_{\textrm{init}} = 500~\textsf{ps}$, the
+% switched on. In the case of $t_{\textrm{warm}} = 500~\textsf{ps}$, the
 % growth of the external EF is comparable to the longest
@@
 reaches 85\% of the maximum value in only 20~ps, which is comparable to
-the warm-up time $t_{init}$, and is 25 times
+the warm-up time $t_{warm}$, and is 25 times
 smaller than the slowest time scale of the conformational relaxation.
@@
 maximum value, that reads
-6.8~Debye, and is corresponding to a dipole energy of ca.
-$-13.6$~kJ/mol.
-The EF induced solvent effect on the alanine is also counted by calculating the
-difference of the water-alaine electrostatic interaction 
-between systems with and without the EF, and the
-energy difference is found to be $-19.1$~~kJ/mol that is
-comparable to the dipole energy of the alanine itself.
-The main free energy barriers among the
-metastable states were reported to be of order $20\sim 40$~kJ/mol~\cite{bohner2012algorithm},
-which is comparable to the dipole energy. This explains the 
-conformational changes under the EF.
+6.8~Debye, and  corresponds to a dipole energy of ca. $-13.6$~kJ/mol.
 We calculate the averaged dipole moment of different metastable state
@@
 for $A_1$, $A_2$, $B_1$, $B_2$ and $C$, respectively.
-Under a constant EF, the system will be driven towards those
+The dipole energy difference between 3.1 and 7.1~Debye is roughly 8.0~kJ/mol.
+The main free energy barriers among the
+metastable states were reported to be of order $20\sim 40$~kJ/mol~\cite{bohner2012algorithm},
+which is comparable to the dipole energy difference. 
+Therefore, under a constant EF, the system will be driven towards those
 conformations that with higher dipole moment, because the
-energy of the system will be lowered by aligning the the dipole
-to the external EF.
-It is clear that
-the $\alpha$-helix and left-handed $\alpha$-helix are of higher
-dipole moments than $\beta$-sheet conformations, so the probability
-of being in the $\alpha$-helix conformations were
-observed being increased under the EF.  $A_1$ and $C$ are the most
+energy of the system will be lowered.  That is why
+we observe that the $\beta$-sheet conformations with lower dipole moment
+are driven towars $\alpha$-helix conformations, 
+and $A_1$ and $C$ are the most
 probable conformations because their dipole moments are the highest
-among all metastable conformation. Moreover, the $B_2$  vanishes, because
+among all metastable conformation. Moreover, the $B_2$ conformation vanishes, because
 its dipole is significantly lower than other conformations.
@@
 lowest dipole conformation $B_2$ quickly
-vanishes, so there is a sharp increment of the average molecular
+vanishes, we observe a sharp increment of the average molecular
 dipole moment. Then until 500~ps, since the conformation slowly migrates from
@@
 is higher than $B_1$, the average molecular dipole moment slowly increases
-to the maximum value.
+to the nonequilibrium steady value.
 
@@
 The black vectors are define to connect the $\alpha$-carbon and the carbons
-on the methyl groups. We define the orientational order parameter
+on the methyl groups. We define the orientational order parameter by
 \begin{align}
@@
 and the direction of the EF. The order parameter
-indicate if the molecule is perpendicular to the EF.
+indicate how perpendicular does the molecule lie to the EF.
 If the molecule is perfectly perpendicular to the EF, then $S_\theta = 1$;
@@
 preference at all, then $S_\theta = 0$;
-If the molecule is perfectly parallel to the EF, then $S_\theta = -2$.
+If the molecule lies perfectly parallel to the EF, then $S_\theta = -2$.
 From $t=0$ to roughly 10~ps, the orientational order parameter fastly
@@
 that is perpendicular to the EF.
+This orientational change coorperates with the observed slowest
+time scale of the conformational change.
 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.48\textwidth]{fig.ala/fig-rdf.eps}
+  \includegraphics[width=0.48\textwidth]{fig.ala/fig-hbond.eps}
+  \caption{The solvent structure around the alanine dipeptide.  Plot
+    (a): the radual distribution function (RDF) between the
+    $\alpha$-carbon and the center-of-mass (COM) of the water molecules at
+    $t = 0$, 10, 100 and 1000~ps.  Plot (b): the number of hydrogen
+    bonds formed between the alanine and water, and between two water
+    molecules.  The number of hydrogen bonds between two water
+    molecules is normalized by the number of water molecules in the
+    system.}
+  \label{fig:tmp7a}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% solvent effect
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We study the solvent effect on the alanine dipeptide by investigating
+the radual distribution function between $\alpha$-carbon and the
+center-of-mass (COM) of the water molecules, see plot (a) of
+Fig.~\ref{fig:tmp7a}. The relative position of water COM with respect
+to the alanine does not remarkably change with respect to time,
+comparing to the statistical uncertainty in the figure. Plot (b) of
+Fig.~\ref{fig:tmp7a} presents the number of hydrogen bonds between the
+alanine and water, and between two water molecules. We see that the
+number hydrogen bonds almost does not change as the EF turns on,
+although the orientation of water molecules aligns to the EF (result
+not shown here). 
+The EF induced solvent effect on the alanine is also counted by calculating the
+difference of the water-alaine electrostatic interaction 
+between systems without and with the EF, and the
+energy difference is found to be $-19.1$~~kJ/mol that is
+comparable to the dipole energy of the alanine itself.
+Therefore, we conclude that the solvent structure around the
+alanine dipole does not noticably change, and the conformational
+dyanmics is mainly driven by the lowered 
+energy of the system that aligns the dipole moment with respect to the external EF.
+
 \subsection{Testing the finite-size effect}
@@
     The dashed vertical lines indicate the three different time scale of
-  metastable state population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
+  metastable state population at $t_{\textrm{warm}} = 10~\textsf{ps}$.}
   \label{fig:tmp7}
@@
 
-Just described in Sec.~\ref{sec:tmp2b}, we perform nonequilibrium MD
+Just as described in Sec.~\ref{sec:tmp2b}, we perform nonequilibrium MD
 simulations in a finite size periodic system, and further divided it
@@
 Since the periodic boundary condition and the division of the system
-are artificial, 
+are approximations to the real dyanmics-preserveing thermal control of the alanine, 
 we want to understand the finite-size effect of
@@
 Therefore, we
-perform two additional simulations: one has box size $L=4.0$~nm and a
+perform two additional simulations: one has box dimension $L=4.0$~nm (box size on all directions are the same) and a
 Hamiltonian dynamics region of radius $R_{ex} = 1.0$~nm, while the
@@
 the period $T$ by $\omega = 1/T$.  Here we tested three different
-periods: 10, 40 and 200, which corresponding
-to frequency 100, 25 and 5~GHz.
+periods: 10, 40 and 200, which correspond
+to frequency 100, 25 and 5~GHz, respectively.
 % The periods of the later two are
@@
     shown. The black line: the static EF with turning on
-    time $t_{init} = 10$~ps. The red line: oscillating field with period
+    time $t_{warm} = 10$~ps. The red line: oscillating field with period
     10~ps. The green line: period 40~ps. The blue line: period 200~ps.}
@@
 presents the $x$-component of the molecular dipole moment as
-a function of time. The red, green and blue lines stands for the
-results of $T=10$~ps, 40~ps and 200~ps, respectively. The black lines
+a function of time. The red, green and blue lines stand for the
+results of $T=10$~ps, 40~ps and 200~ps, respectively. The black line
 shows the dipole moment under constant EF
 for reference.
-It demonstrates that the periods of the molecular dipole moment
-is the same as the periods of the oscillating EF. Therefore,
+It demonstrates that the oscillating period of the molecular dipole moment
+is the same as the period of the oscillating EF. Therefore,
 the molecular dipole moment
@@
 relax its internal dipole (although not completely). However,
-for $T=10$ and 40~ps, as the EF changes faster,
+for $T=10$ and 40~ps, as the EF oscillates faster,
 although the alanine dipeptide can response to the EF immediately,
 it does not have enough time to fully relax the internal dipole, so we
-see the maximum alanine's dipole moment reached is smaller.
+see the maximum dipole moment is smaller.
 % For even smaller period $T=10$~ps, the alanine does not have enough
@@
 % two time scales: In the fast time scale, the 
-For all periodically oscillating cases the order parameter is much
+For all cases the order parameter is much
 smaller than the constant EF case. One possible reason is that the
@@
 parallel to the EF. Please notice that for the constant EF case,
-we also observe a quit alignment of molecular orientation to the EF
+we also observe a quick alignment of molecular orientation to the EF
 at time scale 10~ps. For $T=200$~ps, The molecule periodically
@@
 
-The Fig.~\ref{fig:tmp9} shows the probability of being in a certain
-metastable state for periodically oscillating EF.  The
-Fig.~\ref{fig:tmp10} presents the integrated probability flux among
-the metastable states. We do not show the probability flux itself,
+The Fig.~\ref{fig:tmp9} shows the probability of the
+metastable states against time for periodically oscillating EF.  The
+Fig.~\ref{fig:tmp10} presents the integrated probability fluxes among
+the metastable states. We do not show the probability fluxes themselves,
 because the profiles are highly oscillating and no more
@@
 For all periods investigated,
-the observed time-dependent probabilities of being in a certain metastable
-state are basically the same.
-The probability in $A_1$, $A_2$, $B_1$ and $B_2$ are
+the observed time-dependent probabilities  in $A_1$, $A_2$, $B_1$ and $B_2$ are
 highly oscillating and the average value does not change
@@
 larger than the  $T=40$~ps case (see Fig.~\ref{fig:tmp8} for comparison), the
-probability of being in $C$ is indeed lower.
+probability of being in $C$ is indeed lower (only 0.22).
 For the constant EF case, the probability of state $A_1$
-increases from 0.45 to almost 0.7, and that of $B_1$ almost vanishes.
+increases from 0.45 to 0.69, and that of $B_1$ almost vanishes.
 These phenomena are not observed in the oscillating EF case.
@@
 integrated probability net fluxes, which imply some ever lasting and directional
-flux among the metastable states, see
+fluxes among the metastable states, see
 Fig.~\ref{fig:tmp11} that presents a schematic plot of the main probability
 fluxes for $T=10$~ps.
-The thickness of the arrow and the number nearby indicate
+The thickness of the arrows and the numbers nearby indicates
 the averaged strength of the net fluxes.
@@
 it generates directional probability fluxes among the metastable states.
-Moreover, some loops of the flux are detected: $A_1 \rightarrow B_1
+Moreover, some loops of the flux are detected: for example, $A_1 \rightarrow B_1
 \rightarrow B_2 \rightarrow A_2 \rightarrow A_1$, $A_1 \rightarrow B_1
@@
 Also, we see that the integrated flux reaches the linearly increasing
-stage after about 2400~ps, which is much longer than the time scale,
+stage after about 2400~ps, which is even longer than the time scale,
 at which probability of $C$ reaches its steady value. This indicates
-a even longer intrinsic time scale in the $T=200$~ps case.
+a longer intrinsic time scale in the $T=200$~ps case.
 
@@
 The computer power available to us is not enough for a longer
-simulation that can discover those intrinsic time scale.
+simulation that can discover those intrinsic time scales.
 However, the long-period-limit case is rather easy: When
@@
 % configurations $A_2$ and $B_2$, the relaxations are very fast and
-% comparable to $t_{\textrm{init}}$. For configurations $A_1$, $B_1$ and
+% comparable to $t_{\textrm{warm}}$. For configurations $A_1$, $B_1$ and
 % $C$, the time-scales of relaxation are roughly 600~\textsf{ps}.
@@
 % %   \caption{ Comparison between simulations with and without
-% %     temperature and pressure control at $t_{\textrm{init}} =
+% %     temperature and pressure control at $t_{\textrm{warm}} =
 % %     10~\textsf{ps}$. The The populations of the metastable sets as a
@@
 % %     the three different time scale of metastable set population at
-% %     $t_{\textrm{init}} = 10~\textsf{ps}$.}
+% %     $t_{\textrm{warm}} = 10~\textsf{ps}$.}
 % %   \label{fig:tmp6}

### 2013-08-20 writedown/npt-neq/alanine.tex
Luigi's revise

@@
 
-\title{Exploring Conformational Dynamics and Related Time Scales via Nonequilibrium Molecular Dynamics Simulation}
+\title{Exploring the conformational space of a large molecule in solution using an external electric field: A Nonequilibrium Molecular Dynamics Simulation}
 % \title{The non-equilibrium molecular dynamics simulation of the alanine dipeptide under electric field}
@@
 The possible effect of the electric field (EF) on the conformation of
-proteins gains increasing attention recently, because it is closely
-related to the health problem of exposing human tissue in the
-electromagnetic radiation. Despite the importance of this problem, a
-complete understanding of how the EF influence the  protein
-is still lacking, therefore, a considerable number of
+proteins is a subject of increasing attention since it is linked to the problem of exposing human tissues to
+electromagnetic radiation. Despite its major relevance, a
+satisfactory understanding of how the EF influences the behaviour of proteins
+has not been reached so far although a considerable number of
 experimental~\cite{bohr2000microwave, bohr2000microwave-1,
@@
   astrakas2012structural, damm2012can, starzyk2013proteins,
-  english2009nonequilibrium, solomentsev2012effects} studies have been devoted to this topic,
-and the references listed above is far from complete.
-
-The molecular dynamics (MD) simulation has been proved to be useful in
-understanding the behavior of a protein (or a short peptide segment)
+  english2009nonequilibrium, solomentsev2012effects} studies have been devoted to this topic;
+where the references reported above represent only a minor sample of examples.
+
+In this perspective, molecular dynamics (MD) has been proved to be useful in
+understanding the behavior of a protein 
 in both static and oscillatory EF~\cite{budi2005electric, budi2007effect, budi2008comparative,
@@
   solomentsev2012effects}. In these studies, the initial
-configurations are usually taken from the Protein Data Bank (PDB).
-And then the temperature controlled simulation are performed for 
-a few to tens of nanoseconds, during which the interested
-conformational changes can be observed. Along the trajectories, the
+configurations are usually taken from the Protein Data Bank (PDB),
+and then temperature controlled simulations are performed for a maximum extension of the order of 10-60 of nanoseconds.
+During this simulation time 
+relevant conformational changes characterizing the solvated molecule can be observed. 
+Along the trajectories, various observable, such as the
 secondary structure, root mean square displacement (RMSD), the dipole
-moment and some shape parameters are calculated and investigated by
-either plotted as a function of time, or doing time average over the
-whole simulation. This approach release useful information on how the
-secondary structure is changed by external  EF.  However,
-by plotting the quantities against time, one may observe strong
-fluctuation in plots, which hintered the quantitative and conclusive
-analysis on what is the trend of the conformational change, when
-it happens and what is the strength.
+moment, shape parameters are calculated as a function of time or taking its time average. This approach releases useful information on how the
+secondary structure of the molecule is changed by external  EF.  However,
+by plotting some quantities against time, one may observe strong
+fluctuations; the entity of such fluctuations are such that a quantitative 
+analysis becomes difficult and does not allow for  a clear understanding of the rationale behind the conformational changes.
 Although the time average reduces the statistical uncertainty,
-it is indeed not well defined for a nonequilibrium process
-such as relaxing process to the new conformations under a static
-EF, or the dynamics under an oscillating EF.
-
-The dynamical nonequilibrium molecular dynamics simulation (D-NEMD)
-was firstly developed by G. Ciccotti and his
-colleagues~\cite{ciccotti1975direct, ciccotti1979thought}, and
-recently successfully applied to the study of
+however in this specific case, it is indeed not well defined;
+in fact we are in the presence of a nonequilibrium process
+(e.g. relaxing process to the new conformations under a static
+EF, or the dynamics from one conformation to the other under an oscillating EF).
+
+In this perspective, if one wants to use MD, the proper way to do it would be that of treating a situation of non equilibrium with algorithms that can explicitly describe it.
+This is the approach that will be followed in this work.
+
+The method we employ is the dynamical nonequilibrium molecular dynamics simulation (D-NEMD).
+The method was firstly developed by one of us (GC) and coworkers~\cite{ciccotti1975direct, ciccotti1979thought}.
+It has been recently applied, with success, to the study of
 hydrodynamics~\cite{orlandini2011hydrodynamics,
-  orlandini2011hydrodynamics-01}. D-NEMD provides a way of evaluating
-nonequilibrium observables by doing an ensemble of nonequilibrium MD
-simulations.  It can be used for analyzing the
-conformational changing under a generally time-dependent EF.
-In the present paper, we study a small model peptide
-segment -- alanine dipeptide. We take the approach of starting from a
-single peptide piece rather than a more realistic chain, firstly because it
+  orlandini2011hydrodynamics-01}. The essential feature of D-NEMD is the following: It provides a way of evaluating
+nonequilibrium observables by using a properly determined ensemble of nonequilibrium MD
+simulations.  In this context, the method can be used for analyzing the
+conformational changes of a solvated molecule, subject to a time-dependent EF.
+In the present paper, we study a small peptide, alanine dipeptide, as a model for showing how the method can be used. 
+The choice of a small peptide, rather than a larger one, is done firstly because it
 is easier to draw clear conclusions on the nonequilibrium properties
-of a single peptide by excluding all possible interplay between
+of a single peptide by excluding a possible interplay between
 different peptide segments along a chain.
-Secondly, the current computational resource available is not enough
-to study peptide chains by D-NEMD, since one needs to simulate an
-ensemble of MD trajectories (typically a few thousands), so it
-requires much higher computational cost than producing a single
-equilibrium MD trajectory.
-
-In this paper, we firstly describe the idea of the D-NEMD, then
-introduce the
-observables for analyzing the nonequilibrium properties
-(i.e., the dipole moment, time-dependent properties of being a certain
-conformation and the net
-probability flux). The numerical results of alanine
+Secondly, the computational cost required is rather massive and thus the testing of the various methodolgy developments proposed here would not be easy to accomplish for large molecules.
+Of course, given a positive coming out for such a model system, the aim is that of approaching systems of growing complexity.
+The paper is organized as follows:
+We firstly describe the idea of D-NEMD, then
+introduce the physical
+observables for analyzing the nonequilibrium properties. The numerical results of alanine
 dipeptide under static and sine-shaped oscillating EF are
-presented. By calculating the nonequilibrium properties from the D-NEMD
-simulations, we are able to answer how the peptide
-changes the conformation in a EF, when do these changes happens,
-and how strong are they.
-As far as we know, our simulation is the first D-NEMD simulation
-of alanine dipeptide under EF, and provides new
-information helping people better understand the nonequilibrium
-effect of EF on the protein conformation.
+finally presented. By calculating the nonequilibrium properties from D-NEMD
+simulations, we are able to address the question of how the peptide
+changes the conformation in a EF (conformational space), when do these changes happens (time scale),
+and how likely they are (probability). 
+To our knowledge, this study is one of the few (if not the first)  where non equilibrium is explicitly considered for a large molecule in solution bubject to time-dependent EF.
 
@@
 \subsection{Nonequilibrium molecular dynamics simulation}
-Here we fastly review the approach of performing dynamical nonequilibrium
-molecular dynamics (D-NEMD) that was initiated by Giovanni Ciccoti and his
-colleagues~\cite{ciccotti1975direct, ciccotti1979thought,
+In this section we briefly review the approach for performing dynamical nonequilibrium
+molecular dynamics (D-NEMD) \cite{ciccotti1975direct, ciccotti1979thought,
   orlandini2011hydrodynamics, orlandini2011hydrodynamics-01}.
-We denote the macroscopic nonequilibrium observable by $O(t)$. If at $t$
+In the following we denote the macroscopic observable by $O(t)$. If at $t$
 the configurational probability distribution is $\rho(\vect x, t)$, where
@@
 \end{align}
-where $\hat O (\vect x)$ is the microscopic observable, 
-which is measured at the phase space position $\vect x$,
-comparing with the macroscopic observable that is not phase space independent.
-In this work, we always assume that the initial probability distribution
-$\rho(\vect x, 0)$ is known, and is identical to the equilibrium distribution
-without any EF.
-The bracket on the right hand side of Eq.~\eqref{eqn:tmp1} denotes the inner produce in the
-phase space.  We assume the dynamics of the system is governed by the
+we refer to $\hat O (\vect x)$ as the microscopic observable, 
+which is measured at each point in the phase space $\vect x$.
+Here we always assume that the initial probability distribution
+$\rho(\vect x, 0)$ is known and is identical to the equilibrium distribution of the system
+without EF.
+The bracket on the right hand side of Eq.~\eqref{eqn:tmp1} denotes, as usual, the inner product in the
+phase space.  We assume tthat he dynamics of the system is governed by the
 Hamiltonian equation, i.e. $\dot {\vect x} = J \cdot \nabla_{\vect x}
 \mathcal H(\vect x)$, where $\mathcal H$ is the Hamiltonian, and $J$ is
-the symplectic matrix, then the Liouville equation of the probability
-distribution is
+the symplectic matrix. The Liouville equation for the probability
+distribution writes:
 \begin{align}\label{eqn:tmp2}
@@
 \end{align}
-Since we assume that the system starts from the equilibrium
-distribution, an
-explicit translation of Eq.~\eqref{eqn:tmp4} is that the
-nonequilibrium observable is equal to the ensemble average of
-microscopic observable measured along trajectories, the
+Since we assume that the system starts from the distribution of equilibrium (without EF)
+ Eq.~\eqref{eqn:tmp4} expresses the fact that the 
+observable $O(t)$ calculated in a situation of nonequilibrium is equal to the ensemble average of
+the microscopic observable measured along trajectories, the
 initial configurations of which are subject to the \emph{equilibrium}
-distribution. In practice, we firstly run an equilibrium MD simulation
-to generate a sampling of configurations that are subject to the
-equilibrium distribution. And then by using these configurations as
-initial configuration, the Hamiltonian dynamics are integrated until
+distribution. In practical terms we proceed by first running an equilibrium MD simulation
+to generate a sample of configurations. Next we employ these configurations as
+initial configurations and, for each, the Hamiltonian dynamics is integrated until
 time $t$. These trajectories are also called \emph{branching
-  trajectories} in this paper. Finally, the macroscopic observable is
-estimated by averaging the microscopic observable measured at the end
-points of the trajectories.
-
-Being more generalized, if the microscopic observable depends not only on the end
-configuration at time $t$, but also on the historical
-configurations along the trajectory, then expression~\eqref{eqn:tmp4} takes the generalized form:
-\begin{align}
-  O(t) = \int d\vect x\,\rho(\vect x, 0) \int_{\mathcal C\{\vect x, 0; t\}} \hat O[\vect x_s] \,d\mathcal P[\vect x_s] 
-\end{align}
-where the microscopic observable $ \hat O[\vect x_s] $ is now a
-functional of the trajectory.  $\mathcal C\{\vect x, 0; t\}$ is the
-set of all continuous trajectories starting at point $\vect x$ at time
-0, and ending at time $t$. $\mathcal P[\vect x_s] $ is the measure of
-the trajectory space $\mathcal C$.  In our case, it is the
-$\delta$-function peaked around the trajectories governed by the
-Hamiltonian dynamics. To be general, it can also be the measure of all
-trajectories generated by, for example, a Langevin dynamics, then the
-branching trajectories should be generated by the Langevin
-dynamics rather than the Hamiltonian dynamics.
-
-\subsection{Nonequilibrium temperature control}\label{sec:tmp2b}
+  trajectories} in this paper (see Fig.\ref{branching} for a pictorial representation). 
+Finally, the value of the macroscopic observable at time $t$ is
+calculated by averaging the microscopic observable measured at each time $t$ along each branching trajectory.
+
+%Being more generalized, if the microscopic observable depends not only on the end
+%configuration at time $t$, but also on the historical
+%configurations along the trajectory, then expression~\eqref{eqn:tmp4} takes the generalized form:
+%\begin{align}
+%  O(t) = \int d\vect x\,\rho(\vect x, 0) \int_{\mathcal C\{\vect x, 0; t\}} \hat O[\vect x_s] \,d\mathcal P[\vect x_s] 
+%\end{align}
+%where the microscopic observable $ \hat O[\vect x_s] $ is now a
+%functional of the trajectory.  $\mathcal C\{\vect x, 0; t\}$ is the
+%set of all continuous trajectories starting at point $\vect x$ at time
+%0, and ending at time $t$. $\mathcal P[\vect x_s] $ is the measure of
+%the trajectory space $\mathcal C$.  In our case, it is the
+%$\delta$-function peaked around the trajectories governed by the
+%Hamiltonian dynamics. To be general, it can also be the measure of all
+%trajectories generated by, for example, a Langevin dynamics, then the
+%branching trajectories should be generated by the Langevin
+%dynamics rather than the Hamiltonian dynamics.
+
+\subsection{Control of temperature in Nonequilibrium MD}\label{sec:tmp2b}
 
@@
   \includegraphics[width=0.3\textwidth]{fig/thermostat.eps}
-  \caption{Schematic plot of the nonequilibrium temperature control.
-    The white part is the Hamiltonian dynamics region
-    and the gray part is thermostating region.
+  \caption{Schematic plot of the nonequilibrium temperature control scheme.
+    The white area is the region characterized by Hamiltonian dynamics without the direct action of an external thermostat.
+    The gray area is the region where the external thermostat is used in order to keep the target temperature.
     $R_{ex}$ denotes the size of the Hamiltonian dynamics region, which
-    is a sphere located at the center of the box in the Figure.
-    The whole system
-    is subject to the periodic boundary condition. }
+    is a sphere at the center of the box.
+    The whole system is subject to the periodic boundary conditions. }
   \label{fig:tmp2}
@@
 % Therefore, we are interested in a 
-
-We are mainly interested in the
-nonthermal~\cite{delaHoz2005microwaves} effect of the EF
-to the configuration of a solvated alanine dipeptide,
-so the temperature control in a nonequilibrium system
-becomes an important issue, becuase it was argued that  an
-accurate internal reaction temperature control is essential for being able to
+For this study We are interested in 
+nonthermal~\cite{delaHoz2005microwaves} effects of the EF
+on the configuration of the solvated alanine dipeptide.
+For this reason a proper control of the temperature in a nonequilibrium system
+becomes an important issue; in fact it was argued that  an
+accurate control of the internal reaction temperature is essential for being able to
 perform reproducible experiments~\cite{damm2012can}.
-A naive (but close to realistic) implementation of the temperature control is to 
-embeded the alanine into an infinitely large solvent environment, and 
-the EF is only applied to the neighborhood of the alanine, so that
+A straigthforward (and realistic) implementation of the temperature control consists in 
+embedding the alanine into an infinitely large solvent environment, and 
+the EF is only applied to the neighborhood of the alanine. In this case
 any extra heat generated by the EF can be effectively
-absorbed by the solvent environment.
-However, in practice, it is sometime too expensive to explicitly
-simulate a very large solvent environment
-due to the usually limited computational resources.
-Therefore, we are interested in how to cheaply replace the infinitely large
-solvent environment by a small affordable system, while
-at the same time accurately reproduce the nonequilibrium
+dispersed in the large solvent environment.
+In this way one can identify the effect of the EF on the conformational space of the solvated molecule,
+without the artifact that the surrounding solvant cannot release the additional energy of the EF.
+However, in practice, in most of the cases the computational cost of having large solvant environment is rather massive if not prohibitive.
+Therefore, it is of interest to substitute the infinitely large
+solvent environment with a smaller affordable system and at the same time accurately reproduce the nonequilibrium
 physical properties of interest.
-% In practice, it is impossible to simulate an infinitely large
-% environment.
-If only the equilibrium properties are interested, the solution is to couple
-the system to a thermostat, under which the desired ensemble
+
+As it is well known, in MD, for equilibrium situation, the solution is to couple
+the system to a an external thermostat, under which the desired ensemble
 (canonical in this case) can be
-sampled by only simulating a finite size system with periodic boundary
-condition.
-However, directly coupling a thermostat to the nonequilibrium system
-will disturb the original Hamiltonian dynamics. This is
-in general problematic, 
-because the dynamics  under thermostating is artificial designed,
-so that the equilibrium distribution can be correctly produce, but not
-the nonequilibrium properties of system.
+sampled by simulating a finite size system with periodic boundary
+conditions.
+However, coupling the system to a thermostat for non equilibrium situations is a delicate issue.
+In fact, since a thermostat is explicitly designed to bring the system at equilibrium, any perturbation produced by the EF, would be mostly adsorbed by the thermostat.
+This means that the physics of the original Hamiltonian dynamics with the EF would be lost and the response to the perturbation becomes unphysical.
+%will disturb the original Hamiltonian dynamics. This is
+%in general problematic, 
+%because the dynamics  under thermostating is artificial designed,
+%so that the equilibrium distribution can be correctly produce, but not
+%the nonequilibrium properties of system.
 % dynamics of the system is no longer Hamiltonian, and is
@@
 % Hamiltonian dynamics under investigation will introduce artificial
-% effects in the nonequilibrium observations.
-To solve this problem, we
-observe that only preserving the Hamiltonian dynamics of the alanine 
-itself and the water molecules in the nearby solvation shell is
-crucial to the interested nonequilibrium observable
-(in this work, it is the conformational change of alanine),
-while the detailed dynamics of
-the water molecules far away is of less importance. 
+% a effects in the nonequilibrium observations.
+In this section we propose a procedure to solve the problem: we
+observe the Hamiltonian dynamics (without thermostat) of the alanine 
+itself and the water molecules in the closer solvation shells is
+crucial in order to determine the response of the observable of interest
+under the perturbation of the EF (in this work, it is the conformational change of alanine).
+Instead the detailed dynamics of
+the water molecules far away is not of primary importance, that is the region beyond the first solvation shells plays the role of a thermodynamic bath only. 
 Therefore, instead of simulating an infinitely
 large system, we only simulate a finite size system with periodic
-boundary condition. Accordingly, the simulating region is divided into two
-subregions: Near the alanine dipeptide, the dynamics is kept to be
-Hamiltonian, and this subregion is called \emph{the Hamiltonian dynamics
-region}. While far from the alanine, the dynamics of water is coupled
+boundary condition with the following characteristics. The simulating region is divided in two
+subregions: a spherically defined region around the alanine dipeptide, centered at the
+alpha-carbon of radius $R_{ex}$. Here the dynamics is
+Hamiltonian and molecules are not subject to a thermosat; we refer to such subregion as \emph{the Hamiltonian dynamics
+region}. Instead beyond $R_{ex}$, the dynamics of water is coupled
 to a Langevin thermostat, and this region is called \emph{the thermostating
-region} (see Fig.~\ref{fig:tmp2}).  For simplicity, the Hamiltonian
-dynamics region is assumed to be spherical, centered at the
-alpha-carbon of the alanine, and with radius of $R_{ex}$.  Further, we
-freeze the movement of the alpha-carbon, so that the alanine is always
+region} (see Fig.~\ref{fig:tmp2}). For technical convenience we
+fix the position of the alpha-carbon in space, so that the alanine is always
 located at the center of the simulation region.
-Therefore, the dynamics is preseved in the Hamiltonian dynamics region (where the properties of interest are observed)
-and the artificial effect of thermostating is negligible due to the finite corrlation
+Therefore, a realistic non equilibrium  dynamics is preseved in the Hamiltonian dynamics region (where the properties of interest are observed)
+and possible direct artificial effects of the thermostating process in the region outside are negligible because of the finite correlation
 range of liquid water.
 At the same time, the thermostating region works as a infinitely large
-environment that effectively absorbs the extra heat, so that
-the nonthermal effect can be studied.
+environment that effectively absorbs the extra heat produced by the EF.
 The validity of the above
-statement will be later check latter by numerical examples showing that the
-nonequilibrium observables do not depends on the size of the system
-and the size of the Hamiltonian dynamics subregion, if they are
-reasonably large and the finite size effect does not play a dominating role.
+statement will be later on carefully checked by a series of numerical tests where it is shown that
+the response of observables in nonequilibrium (i.e. under the effect of the EF) does not depend on the size of the system
+and on the size of the Hamiltonian dynamics subregion, provided that they are
+reasonably large.
 
@@
 \section{Example I: Alanine dipeptide
-  under a constant EF}
+  under a uniform  constant EF}
 
 \subsection{System settings and simulation protocol}
-
-In this section,
-we want to study the nonequilibrium properties of an alanine dipeptide
-under a constant EF.  At time $t=0$~ps, the system
+At time $t=0$~ps, the system
 has been fully equilibriated without any EF. From $t=0$ to
 warm-up time $t=t_{\textrm{warm}}$, the eclectic field is switched on linearly, while
-after $t=t_{\textrm{warm}}$, the field is kept constant at
+after $t=t_{\textrm{warm}}$, the field is kept constant in time at
 $E_{\infty}$.  In this work we consider $t_{\textrm{warm}} = 10$~ps,
 and $E_{\infty} = 1$~V/nm.
-The direction of this field is arbitrarily chosen: along the
-$x$ direction. Since the dipole of the equilibrium configurations of
-alanine can be along any direction, applying the electric along $x$-axis is
-not biased.
-Being more general, in this paper we denote the
+The direction of the field is arbitrarily chosen along the
+$x$ direction, in fact the dipole of the equilibrium configurations of
+alanine can be along any direction.
+In this paper we denote the
 EF as a function of time $\vect E(t)$.
@@
 water molecules.
-The EF exserts force $\vect F = q \vect E(t)$ on
-the partial charge $q$ in the system.
+%The EF exserts force $\vect F = q \vect E(t)$ on
+%the partial charge $q$ in the system.
 The size of the  Hamiltonian dynamics region is $R_{ex} = 1.0$~nm.
 All simulations are performed by a home-modified GROMACS 4.5~\cite{pronk2013gromacs}.
-Firstly, an equilibrium NVT simulation of
+First, an equilibrium NVT simulation of
 100~\textsf{ns} was performed with a Langevin thermostat (time-scale
-$\tau_T = 0.5~\textsf{ps}$) coupled to the system for constant
-temperature.  Along the trajectory, configurations were taken every
-50~\textsf{ps}, so we use 2000 initial configurations for each nonequilibrium
-MD simulation, if not stated otherwise.
+$\tau_T = 0.5~\textsf{ps}$).  Along the trajectory, configurations were taken every
+50~\textsf{ps} and we used 2000 initial configurations for each nonequilibrium
+MD simulation (if not stated otherwise for specific cases).
 % They server as starting point of the branching
@@
 change of the system size is small and slow, the pressure control
-does not have an obviously effect on the
+does not have an sizeable effect on the
 dynamics of the system.
@@
     state at $t=1000$~\textsf{ps}, i.e., fully relaxed under the
-    constant EF 1~V/nm. The darker color
+    action of a constant EF of 1~V/nm. The darker color
     indicates larger population on the Ramachandran histogram.}
@@
 
-On each branching trajectory, to easy the analysis of the conformational dynamics
-of alanine dipeptide, the molecular configuration is projected on
+For each branching trajectory,  the molecular configuration of alanine is projected on
 the Ramachandran histogram, as
 shown in Fig.~\ref{fig:tmp4}. The equilibrium distribution of the
-conformation is given in the plot (a), and the fully relaxed
-conformation under $E_{\infty} = 1$~V/nm is given  plot (b).  It is
-clear the conformations are populated in several clusters, and the
-position of the clusters do not change when the external electric
+conformations is given in the plot (a), and the fully relaxed
+conformation under the action of $E_{\infty} = 1$~V/nm is given  plot (b).  It is
+evident from the plot that the conformations are grouped in several clusters, and the
+position of the clusters does not change when the external electric
 field is applied.
-This means that only a few of the conformations are likely to be observed,
+{\bf LUIGI COMMENT: HAN below is really not clear}\\
+This means that only few of the total of conformations are likely to be visited,
 in the nonequilibrium process.
@@
 we do not distinguish the definations, and assume they have the same meaning.
-We manually divide the
+{\bf END COMMENT}\\
+For sake of clarity We divide the
 Ramachandran histogram into 5 subregions, see Fig.~\ref{fig:tmp4},
-then the observation of conformations on the Ramachandran histogram is projected to the
-observation of these 5 states, i.e. $\{A_1, A_2, B_1, B_2, C\}$.
+then the analysis of conformations on the Ramachandran histogram is reduced to the
+analysis of the 5 states, i.e. $\{A_1, A_2, B_1, B_2, C\}$.
 These states
@@
 From Fig.~\ref{fig:tmp4}, it is obvious that the population in each
-metastable state changes due to the external EF, for
-example, the population of state $C$ vanishes in equilibrium,
+metastable state changes when the external EF is applied.
+For instance, the population of state $C$ vanishes in equilibrium,
 but plays an important role when the EF is applied. We
@@
 the EF. 
-Firstly, we calculate the probability of being in a certain state that
-is defined by:
+Firstl, we calculate the probability of being in a certain state,
+defined as:
 \begin{align}
@@
 \end{align}
-Notice that the time dependency of the probability, so it is
-a nonequilibrium observable.
+Notice that the probability is time dependent, being an observable in nonequilibrium situation.
 % which is the time dependent probability of the alanine being in metastable
@@
 % process considered by the present work, this relation is genarlly not guarenteed.
-Secondly,
+Second,
 we study the net probability flux from metastable state $I$ to $J$, defined by:
@@
 \end{align}
-which presents the rate of how much conformation $J$ changes
+$F_{J,I}(t)$ is essentially the rate of how much conformation $J$ changes
 into $I$ at time $t$. A positive value indicates the
@@
 while a negative value indicates a net flux from $I$ to $J$.
-Now the original nonequilibrium process $\vect x_t$
-is projected onto the discretized states $\{A_1, A_2, B_1, B_2, C\}$,
-if the resulting reduced process 
+Through $F_{J,I}(t)$, the original overall nonequilibrium process $\vect x_t$
+is reduced to the probabilistic link between discretized states $\{A_1, A_2, B_1, B_2, C\}$.
+If the resulting reduced process 
 is time-reversible, then it is obvious that
@@
 $\{A_1, A_2, B_1, B_2, C\}$.
-In practice, to measure $ F_{J,I}(t)$, one need firstly approximate the limit
+In practice, to measure $ F_{J,I}(t)$, one need first to approximate the limit
 in Eq.~\eqref{eqn:tmp7} by the finite difference,
@@
 the right-hand-side from the molecular trajectories.
-If one wants a precise finite difference approximation, a smaller $\Delta t$ is
-preferable,
-but then the statistical uncertainty of measuring the joint probabilities
+In this context, for a precise finite difference approximation a smaller $\Delta t$ is
+preferable although the statistical uncertainty of measuring the joint probabilities
 is higher. In practice,
 we use a $\Delta t$ that is small enough for a precise finite difference approximation,
-and not too small so that the joint probabilities can be calculated properly.
-In the oscillating EF case, the net probability flux is also highly oscillating,
-so it is convenient to study the integrated probability flux:
+and not small enough so that the joint probabilities can be calculated with acceptable accuracy.
+In the case of oscillating EF, the net probability flux is also highly oscillating,
+thus it is convenient to study the integrated probability flux:
 \begin{align}
@@
 \end{align}
-which presents the time averaged effect of the EF to the molecular conformation.
+this expresses the average over time of the effects of the EF on the conformation of the molecule.
 
@@
   \includegraphics[]{fig.ala/fig-meta-npt.eps}
-  \caption{The probability of being in a metastable states under a constant EF.
-    The warm-up time $t_{warm} = 10$~ps. The red line stands for state $A_1$,
-    green for $A_2$, dark blue for $B_1$, purple for $B_2$ and light blue
-    for $C$.
+  \caption{The probability that the system is in a metastable states when a constant EF is present.
+    The warm-up time is $t_{warm} = 10$~ps. The red line refers to state $A_1$,
+    green to $A_2$, dark blue to $B_1$, purple to $B_2$ and light blue
+    to $C$.
   }
@@
   \caption{
-    The net probability flux and its integration under the constant EF case.
-    The warm-up time $t_{warm} = 10$~ps.
-    The first row shows the probability flux $F_{J,I}(t)$ with unit $\textrm{ps}^{-1}$, while the second
+    The net probability flux and its integral, for the constant EF case.
+    The warm-up time is $t_{warm} = 10$~ps.
+    The first row shows the probability flux $F_{J,I}(t)$ in units of $\textrm{ps}^{-1}$, while the second
     shows the integrated  probability flux denoted by $Q_{J,I}(t)$.
-    A constant $Q_{J,I}$ means vanishing net flux, while a increasing (deceasing)
+    A constant $Q_{J,I}$ means vanishing net flux, while a increasing (decreasing)
     $Q_{J,I}$ indicates positive (negative) net flux.
@@
 The time-dependent probability of the system in a certain metastable state is given in
-Fig.~\ref{fig:tmp5}. The beta sheet conformation $B_1$ and $B_2$,
-which presents at the beginning,
-fades away as the system relaxes to the new equilibrium. The
+Fig.~\ref{fig:tmp5}. The beta sheet conformations $B_1$ and $B_2$,
+which are present at the initial stage after EF is switched on,
+fade away as the system relaxes to the new equilibrium. The
 probability of alpha helix $A_1$ conformation grows from 0.45 to 0.69.
-Alpha helix $A_2$  does not change a lot under the EF.
+Alpha helix $A_2$  does not change significantly  under the action of EF.
 The left-hand helix conformation $C$ noticeably grows from 0 to 0.22.
@@
 We plot the net probability fluxes and their integration in Fig.~\ref{fig:tmp6}.
-When $t$ is short, the net fluxes are generally non-zero.
-When $t$ goes to infinity,
+Results show that for short $t$, the net fluxes are generally non-zero, however, 
+as $t$ goes to infinity,
 all fluxes converge to zero. This indicates
-when the EF is switched on, the system firstly is driven from the old
-equilibrium (in zero EF), and this is a nonequilibrium process.
+as the EF is switched on, the system first is driven away from the initial
+equilibrium (at zero EF), and this is a nonequilibrium process.
 After a long enough time, the system
-is fully relaxed to the new equilibrium defined by the constant EF,
+is fully relaxed to the new equilibrium defined by the action of the constant EF.\\
 % it gradually relaxes to the new equilibrium,
-so we do not see any change
-in the population of the metastable states.
+{\bf COMMENT LUIGI: Not clear, because some of the states may not be visited again. Anyway the choice of name and definition of ``metastable'' sound really not great}\\
+For this reason we do not see any change
+in the population density of the metastable states.\\
+{\bf END COMMENT}\\
 
@@
 Even though the system is finally relaxed to the new equilibrium,
-the speed of relaxation of each metastable state is different. 
+the timescale of relaxation of each metastable state is different. 
 From Fig.~\ref{fig:tmp6}, we observe mainly
-three different timescales of the conformational relaxation, which
-are summarized in Tab.~\ref{tab:tmp1}.
+three different timescales, as summarized in Tab.~\ref{tab:tmp1}.
 (1) From
@@
 A similar flux is also observed from $B_1$ to $B_2$.
-Then, these two fluxes vanish and then turn to the opposite direction
+Afterwards, these two fluxes vanish and are finally reversed,
 i.e. $A_2$ to $A_1$ and $B_2$ to $B_1$, respectively.
@@
 % $A_2$ to $A_1$.
-In the meanwhile, a net flux from all $\beta$-sheet conformations
+Instead a net flux from all $\beta$-sheet conformations
 ($B_1$ and $B_2$) into $\alpha$-helix conformations ($A_1$, $A_2$ and
@@
 The net flux from  conformation $A_2$ to $A_1$ and from $B_2$ to $B_1$
-gradually decays to 0. Conformational change from $B_2$ to $A_1$, $A_2$ and $C$
+gradually decays to 0. Conformational changes from $B_2$ to $A_1$, $A_2$ and $C$
 vanishes in about 50~ps.
@@
 the new equilibrium (system with $E(\infty) = 1~\textsf{V/m}$).
-We observed slowing decaying probability flux from $B_1$ 
+We observe a decaying probability flux from $B_1$ 
 to $A_1$ and $C$.
-The magnitude of the flux from $B_1$ to  $C$ is larger than that from  $B_1$ to  $A_1$.
+The magnitude of the flux from $B_1$ to  $C$ is larger than that of $B_1$ to  $A_1$.
 % It is interesting to see that at nonequilibrium steady state, $A_1$ exchange
@@
 % acutally more stable than  other conformations.
-This time-scale is actually 50 times slower than speed, at which
+This time-scale is actually 50 times slower than that, at which
 the EF was switched on ($t_{\textrm{warm}} = 10~\textsf{ps}$).
@@
 
+\subsection{Molecular Dipole response}
+
 \begin{figure}
@@
   \caption{The
-    $x$-component of the dipole moment, and the orientational order parameter
+    $x$-component of the molecular dipole moment, and the orientational order parameter
     of the alanine molecule as a
-    function of time. The dashed line presents the strengths of the
-    external EF, while the solid line presents the dipole
+    function of time. The dashed line represents the strength of the
+    external EF, while the solid line represents the dipole
     moments. The left vertical axis is for the dipole moment, while
@@
 Then in the following 400~ps, the dipole slowly relaxes to the 
-maximum value, that reads
+maximum value, that is, 
 6.8~Debye, and  corresponds to a dipole energy of ca. $-13.6$~kJ/mol.
-We calculate the averaged dipole moment of different metastable state
+We calculate the averaged dipole moment of different metastable states
 under the constant EF, and they are 6.8, 6.0, 5.1, 3.1 and 7.1~Debye
@@
 The dipole energy difference between 3.1 and 7.1~Debye is roughly 8.0~kJ/mol.
-The main free energy barriers among the
+The free energy barriers between the
 metastable states were reported to be of order $20\sim 40$~kJ/mol~\cite{bohner2012algorithm},
@@
 Therefore, under a constant EF, the system will be driven towards those
-conformations that with higher dipole moment, because the
-energy of the system will be lowered.  That is why
+conformations with higher dipole moment, because the
+energy of the system will be lowered.  This is the reason why
 we observe that the $\beta$-sheet conformations with lower dipole moment
 are driven towars $\alpha$-helix conformations, 
-and $A_1$ and $C$ are the most
-probable conformations because their dipole moments are the highest
-among all metastable conformation. Moreover, the $B_2$ conformation vanishes, because
+and $A_1$ and $C$ are conformations with higher probability, because their dipole moments are the highest
+among all metastable conformations. Moreover, the $B_2$ conformation vanishes because
 its dipole is significantly lower than other conformations.
@@
 lowest dipole conformation $B_2$ quickly
-vanishes, we observe a sharp increment of the average molecular
-dipole moment. Then until 500~ps, since the conformation slowly migrates from
-$B_1$ to $A_1$ and $C$, and also since the dipole moment $A_1$ and $C$
+vanishes. We observe a sharp increment of the average molecular dipole and finally, approaching  500~ps, the conformation slowly migrates from
+$B_1$ to $A_1$ and $C$. Moreover, since the dipole moment $A_1$ and $C$
 is higher than $B_1$, the average molecular dipole moment slowly increases
 to the nonequilibrium steady value.
-
-We also consider the orientation of the alanine dipeptide as a function
+\subsection{Response of the orientational order parameter}
+
+We also consider the orientation of the alanine dipeptide in space (w.r.t. the direction of EF) as a function
 of time.
@@
 Fig.~\ref{fig:tmp3}, which is the angle bisector of the two black vectors.
-The black vectors are define to connect the $\alpha$-carbon and the carbons
+The black vectors are defined in such a way that they connect the $\alpha$-carbon and the carbons
 on the methyl groups. We define the orientational order parameter by
@@
 and the direction of the EF. The order parameter
-indicate how perpendicular does the molecule lie to the EF.
+indicate how perpendicular does the molecule lie w.r.t. the EF.
 If the molecule is perfectly perpendicular to the EF, then $S_\theta = 1$;
 If the molecule has no directional
-preference at all, then $S_\theta = 0$;
+preference , then $S_\theta = 0$;
 If the molecule lies perfectly parallel to the EF, then $S_\theta = -2$.
@@
 that is perpendicular to the EF.
-This orientational change coorperates with the observed slowest
-time scale of the conformational change.
-
+This orientational change is linked to the observed slowest
+time scale of the molecular conformational change.
+
+\subsection{Effects of EF on the solvant around the molecule}
 % This indicate that when the EF is switched on, the alanine almost immediately
@@
   \caption{The solvent structure around the alanine dipeptide.  Plot
-    (a): the radual distribution function (RDF) between the
+    (a): the radial distribution function (RDF) between the
     $\alpha$-carbon and the center-of-mass (COM) of the water molecules at
@@
 \end{figure}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We study the solvent effect on the alanine dipeptide by investigating
-the radual distribution function between $\alpha$-carbon and the
-center-of-mass (COM) of the water molecules, see plot (a) of
-Fig.~\ref{fig:tmp7a}. The relative position of water COM with respect
-to the alanine does not remarkably change with respect to time,
-comparing to the statistical uncertainty in the figure. Plot (b) of
+We study the solvent effect on the alanine dipeptide in the presence of the EF by investigating
+the radial distribution function between $\alpha$-carbon and the
+center-of-mass (COM) of the water molecules
+(see Fig.~\ref{fig:tmp7a}). The average, relative position of the COM of water molecules measured w.r.t.
+ the alanine does not change significantly as afunction of time (within the statistical error). Plot (b) of
 Fig.~\ref{fig:tmp7a} presents the number of hydrogen bonds between the
-alanine and water, and between two water molecules. We see that the
-number hydrogen bonds almost does not change as the EF turns on,
-although the orientation of water molecules aligns to the EF (result
-not shown here). 
-The EF induced solvent effect on the alanine is also counted by calculating the
-difference of the water-alaine electrostatic interaction 
-between systems without and with the EF, and the
-energy difference is found to be $-19.1$~~kJ/mol that is
-comparable to the dipole energy of the alanine itself.
-Therefore, we conclude that the solvent structure around the
-alanine dipole does not noticably change, and the conformational
-dyanmics is mainly driven by the lowered 
-energy of the system that aligns the dipole moment with respect to the external EF.
-
-\subsection{Testing the finite-size effect}
+alanine and water molecules, and between two water molecules. We see that the
+number hydrogen bonds remains almost the as the EF is turned on,
+although molecular dipoles tend to align with the direction of the EF (result
+not shown). 
+The EF-induced solvent effect on the alanine is also counted by calculating the
+difference of the water-alanine electrostatic interaction 
+between systems without and with the EF.
+The energy difference is found to be $-19.1$~~kJ/mol that is
+comparable to the electrostatic energy associated to the dipole of the alanine itself.
+Therefore, we conclude that the solvation structure around the
+alanine does not change significantly or contribute significantly in determining the conformational dynamics of the alanine under the action of EF.
+
+\subsection{Testing the influence of the finite-size effect of the Hamiltonian region}
 
@@
   \includegraphics[]{fig.ala/fig-meta-conv.eps}
-  \caption{The populations of the metastable states as a function of time.
+  \caption{Populations of the metastable states as a function of time.
     The dashed vertical lines indicate the three different time scale of
@@
 into a Hamiltonian dynamics region and a thermostating region.
-Since the periodic boundary condition and the division of the system
-are approximations to the real dyanmics-preserveing thermal control of the alanine, 
-we want to understand the finite-size effect of
-these settings and the their influence to the simulation result.
+Since the periodic boundary conditions and the division of the system
+are technical (not physical) approximations to the real system with dynamics-preserveing thermal control, 
+the effect of the finite-size in 
+the system settings should be carefully checked.
 Therefore, we
-perform two additional simulations: one has box dimension $L=4.0$~nm (box size on all directions are the same) and a
-Hamiltonian dynamics region of radius $R_{ex} = 1.0$~nm, while the
-other has box size $L=4.0$~nm and a Hamiltonian dynamics region of
-radius $R_{ex} = 1.5$~nm, and compare them to the system
-we used before, i.e. $L=2.7$~nm and $R_{ex} = 1.0$~nm.
-Fig.~\ref{fig:tmp7} presents very good consistency of
-the simulation results of the three systems, so the finite-size effect is
-actually negligible in the system we used in the previous sections.
+perform two additional simulations: one with box dimension $L=4.0$~nm (box size on all directions are the same) and a
+Hamiltonian dynamics region of radius $R_{ex} = 1.0$~nm. A second simulation is done with box size $L=4.0$~nm and a Hamiltonian dynamics region of
+radius $R_{ex} = 1.5$~nm. We compare the results of these two simulations to those of the system we have used so far, i.e. $L=2.7$~nm and $R_{ex} = 1.0$~nm.
+Fig.~\ref{fig:tmp7} presents a satisfactory consistency in
+the simulation results of the three systems, which implies that the finite-size effects are
+actually negligible.
 
@@
 
-We have tested the periodically oscillating EF which has
+A step forward in our study is to consider a periodically oscillating EF which has
 a $\sin$-wave shape:
@@
 \end{align}
-where $E_0$ is the strength of the field, which is chosen to be
-1.0~V/nm.  $\omega$ is the frequency of the field, which is related to
+where $E_0$ is the intensity of the field, which is chosen to be
+1.0~V/nm.  $\omega$ is the oscillating frequency, which is related to
 the period $T$ by $\omega = 1/T$.  Here we tested three different
-periods: 10, 40 and 200, which correspond
-to frequency 100, 25 and 5~GHz, respectively.
+values of $T$: 10, 40 and 200, which correspond
+to frequency of 100, 25 and 5~GHz, respectively.
 % The periods of the later two are
@@
   \includegraphics[width=0.48\textwidth]{fig.ala/fig-mode2-order.eps}
-  \caption{The nonequilibrium dipole moment (a) and
+  \caption{The dipole moment calculated for the nonequilibrium situation (a) and
     orientation order parameter (b) of alanine dipeptide as a
@@
     only the $x$-component of the dipole moment is
-    shown. The black line: the static EF with turning on
-    time $t_{warm} = 10$~ps. The red line: oscillating field with period
-    10~ps. The green line: period 40~ps. The blue line: period 200~ps.}
+    shown. The black line refers to the static EF with turning on
+    time $t_{warm} = 10$~ps. The red line refers to the oscillating field with period
+    10~ps, while the green line is for a period of 40~ps and the blue for 200~ps.}
   \label{fig:tmp8}
@@
 presents the $x$-component of the molecular dipole moment as
-a function of time. The red, green and blue lines stand for the
+a function of time. The red, green and blue lines report the
 results of $T=10$~ps, 40~ps and 200~ps, respectively. The black line
@@
 for reference.
-It demonstrates that the oscillating period of the molecular dipole moment
+It shows that the oscillating period of the molecular dipole moment
 is the same as the period of the oscillating EF. Therefore,
 the molecular dipole moment
-is able to response to the external EF almost immediately.
+is able to respond to the external EF almost immediately.
 At $T=200$~ps, the maximum magnitude of the molecular
-dipole moment is almost the same as the case of constant EF, which
-means that the changing of the EF is so slow that the
-alanine have enough time to 
-relax its internal dipole (although not completely). However,
-for $T=10$ and 40~ps, as the EF oscillates faster,
-although the alanine dipeptide can response to the EF immediately,
-it does not have enough time to fully relax the internal dipole, so we
-see the maximum dipole moment is smaller.
+dipole moment is close to the values obtained in the case of constant EF, which
+means that the variation of the oscillating EF is so slow that the
+alanine has enough time to 
+relax its dipole. However,
+for $T=10$ and 40~ps, the EF oscillates faster,
+and although the alanine dipeptide can respond to the EF action immediately,
+it does not have enough time to fully relax the dipole, as aconsequence the maximum dipole moment is smaller than the previous case.
 % For even smaller period $T=10$~ps, the alanine does not have enough
@@
 Plot (b) of Fig.~\ref{fig:tmp9} presents the orientational order
-parameter. The notations are the same as plot (a).
+parameter. The notations are the same as in plot (a).
 % From the constant
@@
 For all cases the order parameter is much
-smaller than the constant EF case. One possible reason is that the
-relaxation of the order parameter is very slow, and the molecule does
-not expose to a strong enough EF for a long enough time in a oscillating
-EF. For  $T=10$ and 40~ps, the orientation of the alanine is only weakly
-parallel to the EF. Please notice that for the constant EF case,
+smaller than in the case of constant EF. One possible reason is that the
+relaxation of the order parameter is very slow, and the molecule in case of oscillating field is
+not exposed to a strong enough EF for a long enough. For  $T=10$ and 40~ps, the orientation of the alanine is only weakly
+parallel to the EF. It is worth to notice that for the case of constant EF,
 we also observe a quick alignment of molecular orientation to the EF
-at time scale 10~ps. For $T=200$~ps, The molecule periodically
+on the time scale of 10~ps. For $T=200$~ps, The molecule periodically
 becomes perpendicular to the EF, but this directional preference is much
-weaker than the constant EF case.
+weaker than the case of constant EF.
 
@@
     $F(t)$ is the net probability flux from metastable state $I$ to $J$.
-    From up to down the rows present period 10, 40 and 200~ps, respectively.
+    From up to down, rows report results with  period 10, 40 and 200~ps, respectively.
     From left to right, the five
@@
     purple for $J=B_2$ and light blue for $J=C$. In a certain time interval,
-    if the integrated flux $Q_{J,I}$ increases, then there exist a (time-averaged)
+    if the integrated flux $Q_{J,I}$ increases, there exists a (time-averaged)
     non-zero net flux from metastable state $I$ to $J$.
@@
 metastable states against time for periodically oscillating EF.  The
-Fig.~\ref{fig:tmp10} presents the integrated probability fluxes among
-the metastable states. We do not show the probability fluxes themselves,
-because the profiles are highly oscillating and no more
-information can be obtained than the integrated probability flux.
+Fig.~\ref{fig:tmp10} presents the integrated probability fluxes between
+metastable states. Here the probability fluxes are not reported
+because the profiles are highly oscillating and they would not offer 
+ a more complete information of the one that can be obtained from the integrated probability flux.
 For all periods investigated,
@@
 highly oscillating and the average value does not change
-too much with respect to time,
-however, the probability in metastable state $C$ astonishingly
-increase to approximately 0.17 for $T=10$~ps, 0.27 for  $T=40$~ps, and
-0.25 for $T=200$~ps.
-Notice that in the constant EF case, although the dipole moment is
+considerably with respect to time.
+However, the probability in metastable state $C$ significantly
+increases to approximately 0.17 for $T=10$~ps, 0.27 for  $T=40$~ps, and
+0.25 for $T=200$~ps.\\
+{\bf COMMENT LUIGI: sentence and context and reasoning of the part below not clear}
+Note that in the case of constant EF, although the dipole moment is
 larger than the  $T=40$~ps case (see Fig.~\ref{fig:tmp8} for comparison), the
-probability of being in $C$ is indeed lower (only 0.22).
-For the constant EF case, the probability of state $A_1$
+probability of being in $C$ is indeed lower (only 0.22).\\
+{\bf END COMMENT}\\
+For the case of constant EF, the probability of state $A_1$
 increases from 0.45 to 0.69, and that of $B_1$ almost vanishes.
@@
 In the case of $T=10$ and $40$~ps, the probability of being in a state
-reaches the steady value in around 300~ps, while it costs 1200~ps
-for the $T=200$~ps case to reach the steady probability. That means
-the intrinsic time scales of the nonequilibrium processes are commensurate
-for $T=10$ and $40$~ps, while they are much longer for $T=200$~ps.
+reaches the steady value in around 300~ps, while it requires about 1200~ps
+for the $T=200$~ps case. 
+%This suggest that
+%the intrinsic time scales of the nonequilibrium processes are commensurate
+%for $T=10$ and $40$~ps, while they are much longer for $T=200$~ps.
 
@@
   \includegraphics[width=0.5\textwidth]{fig.ala/graphs/graph-t0010-1.eps}
-  \caption{The schematic plot of the main probability flux among the metastable
+  \caption{Schematic plot of the main probability flux between metastable
     states on the Ramachandran histogram
@@
     of the arrows approximately presents the strength of the flux.
-    The numbers near the arrows indicates the strength of the averged
+    The numbers near the arrows indicates the strength of the averaged
     probability flux, the unit of which is $10^{-3}\textrm{ps}^{-1}$.
@@
 \end{figure}
-
-Fig.~\ref{fig:tmp10} shows some ever increasing
-integrated probability net fluxes, which imply some ever lasting and directional
-fluxes among the metastable states, see
-Fig.~\ref{fig:tmp11} that presents a schematic plot of the main probability
-fluxes for $T=10$~ps.
+Fig.~\ref{fig:tmp10} shows increasing
+integrated probability net fluxes, which imply some lasting and directional
+fluxes among the metastable states (see Fig.~\ref{fig:tmp11} for a schematic plot of the main probability
+fluxes for $T=10$~ps).
 The thickness of the arrows and the numbers nearby indicates
-the averaged strength of the net fluxes.
-This demonstrate an interesting phenomenon: although
-the oscillating EF is not directional and vanishes in time-average,
+the average amount of the net fluxes.
+This shows an interesting phenomenon: although
+the oscillating EF is not directional and vanishes in a time-average process,
 it generates directional probability fluxes among the metastable states.
-Moreover, some loops of the flux are detected: for example, $A_1 \rightarrow B_1
+Moreover, we have identified some loops of the flux: for example, $A_1 \rightarrow B_1
 \rightarrow B_2 \rightarrow A_2 \rightarrow A_1$, $A_1 \rightarrow B_1
@@
 similar to $T=10$~ps and $T=40$~ps, however,
-the strength is much lower than the latter two cases.
-Also, we see that the integrated flux reaches the linearly increasing
-stage after about 2400~ps, which is even longer than the time scale,
-at which probability of $C$ reaches its steady value. This indicates
+the amount is much lower than the latter two cases.
+Moreover, we see that the integrated flux reaches a linearly increasing
+stage after about 2400~ps, which is even longer than the time scale
+at which the probability of $C$ reaches its steady value. This indicates
 a longer intrinsic time scale in the $T=200$~ps case.
 
-We do not test any period longer than $T=200$~ps, because
-from the trend that longer period indicates even longer intrinsic time scales.
-The computer power available to us is not enough for a longer
-simulation that can discover those intrinsic time scales.
-However, the long-period-limit case is rather easy: When
-the EF changes so slow that at each time point the system
+We have not studied periods longer than $T=200$~ps, because
+from the trend suggests that a longer period indicates even longer intrinsic time scales.
+This would require massive computational efforts not strictly required at this stage.
+However, the long-period-limit case can be safely guessed: When
+the EF changes so slow that at each time the system
 can be viewed as in equilibrium, then the process is a quasi-equilibrium
-process, and no nonequilibrium phenomenon will be observed. For example,
+process, and nonequilibrium phenomenon will not be observed. For example,
 the probability being in a  metastable state will change
@@
 the time-averaged net flux will be infinitely small,
-and the integrated flux will be periodical, and being constant in time-average.
+and the integrated flux will be periodical, and constant in time-average.
 
@@
 \section{Concluding remarks}
+\subsection{Electric field, force field, polarization and quantum effects}
+\subsection{Conceptual comparison with other non equilibrium approaches}
 

### 2013-08-27 writedown/npt-neq/alanine.tex
Luigi's revise, recheck with correct file format
revise based on Luigi's comments, add conclusion

@@
 
-\title{Exploring the conformational space of a large molecule in solution using an external electric field: A Nonequilibrium Molecular Dynamics Simulation}
+\title{Exploring the conformational dynamics of a large molecule in solution using an external electric field: A Nonequilibrium Molecular Dynamics Simulation}
 % \title{The non-equilibrium molecular dynamics simulation of the alanine dipeptide under electric field}
 \author{Han Wang}
+\email{han.wang@fu-berlin.de}
 \affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
@@
 (e.g. relaxing process to the new conformations under a static
-EF, or the dynamics from one conformation to the other under an oscillating EF).
+EF, or the dynamics from one conformation to the other under an oscillatory EF).
 
@@
 observables for analyzing the nonequilibrium properties. The numerical results of alanine
-dipeptide under static and sine-shaped oscillating EF are
+dipeptide under static and sine-shaped oscillatory EF are
 finally presented. By calculating the nonequilibrium properties from D-NEMD
@@
 region}. Instead beyond $R_{ex}$, the dynamics of water is coupled
-to a Langevin thermostat, and this region is called \emph{the thermostating
+to a Langevin thermostat, and this region is called \emph{the thermostated
 region} (see Fig.~\ref{fig:tmp2}). For technical convenience we
@@
 range of liquid water.
-At the same time, the thermostating region works as a infinitely large
+At the same time, the thermostated region works as a infinitely large
 environment that effectively absorbs the extra heat produced by the EF.
@@
 method was applied to calculate the electrostatic interaction in this
-periodic system. In the thermostating region, the original dynamics was
+periodic system. In the thermostated region, the original dynamics was
 coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
@@
 
-\subsection{Metastable sets}
+\subsection{Molecular conformation and net probability flux}
 
@@
   \centering
-  \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{fig.ala/ext.mode1.010.Ex.01.00.t1000ps.recheck/c-2.eps}}
-  \includegraphics[width=0.37\textwidth]{fig.ala/ext.mode1.010.Ex.01.00.t1000ps.recheck/fig-begin-1.eps}
-  \includegraphics[width=0.37\textwidth]{fig.ala/ext.mode1.010.Ex.01.00.t1000ps.recheck/fig-end-1.eps}
-  \caption{The population of metastable states of the alanine dipeptide.
+  \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{fig.ala/ext.mode1.010.Ex.01.00.t1000ps.recheck.bk/c-2.eps}}
+  \includegraphics[width=0.37\textwidth]{fig.ala/ext.mode1.010.Ex.01.00.t1000ps.recheck.bk/fig-begin-1.eps}
+  \includegraphics[width=0.37\textwidth]{fig.ala/ext.mode1.010.Ex.01.00.t1000ps.recheck.bk/fig-end-1.eps}
+  \caption{The probability of the conformations of the alanine dipeptide plotted on the Ramachandran histogram.
     (a): the
@@
     action of a constant EF of 1~V/nm. The darker color
-    indicates larger population on the Ramachandran histogram.}
+    indicates higher probability.}
   \label{fig:tmp4}
@@
 field is applied.
-{\bf LUIGI COMMENT: HAN below is really not clear}\\
-This means that only few of the total of conformations are likely to be visited,
-in the nonequilibrium process.
-These conformations are called ``metastable states''.
-The strict definition of the
-metastability is not exactly the same as those conformations that are likely to be observed.
-Since in this paper we do not focus on the discussion of the definition for the metastability of the system,
-we do not distinguish the definations, and assume they have the same meaning.
-{\bf END COMMENT}\\
-For sake of clarity We divide the
+% {\bf LUIGI COMMENT: HAN below is really not clear}\\
+% This means that only few of the total of conformations are likely to be visited,
+% in the nonequilibrium process.
+% These conformations are called ``metastable states''.
+% The strict definition of the
+% metastability is not exactly the same as those conformations that are likely to be observed.
+% Since in this paper we do not focus on the discussion of the definition for the metastability of the system,
+% we do not distinguish the definations, and assume they have the same meaning.
+% {\bf END COMMENT}\\
+For the sake of clarity, we divide the
 Ramachandran histogram into 5 subregions, see Fig.~\ref{fig:tmp4},
 then the analysis of conformations on the Ramachandran histogram is reduced to the
-analysis of the 5 states, i.e. $\{A_1, A_2, B_1, B_2, C\}$.
-These states
-correspond to different secondary structure of a peptide chain:
+analysis of the 5 ranges of conformations, i.e. $\{A_1, A_2, B_1, B_2, C\}$,
+or in short we call them conformations (the precise meaning is clear
+from the context).
+In this paper we use:
+$A_1 = \{(\phi, \psi) | -134 \leq \phi <  13, -125 \leq \psi < 74\}$,
+$A_2 = \{(\phi, \psi) |  128 \leq \phi <-134, -125 \leq \psi < 74\}$,
+$B_1 = \{(\phi, \psi) | -110 \leq \phi <  13,   74 \leq \psi <-125\}$,
+$B_2 = \{(\phi, \psi) |  128 \leq \phi <-110,   74 \leq \psi <-125\}$,
+$C   = \{(\phi, \psi) |   13 \leq \phi < 128, -180 \leq \psi < 180\}$.
+Considering the periodic bondary condition, if we write, for example,
+$128 \leq \phi <-134$, it means that $\phi$ is in either range
+$128 \leq \phi < 180$ or in $-180 \leq \phi < -134$.
+These conformations
+correspond to different secondary structures of a peptide chain:
 $A_1$ and $A_2$ are
@@
 From Fig.~\ref{fig:tmp4}, it is obvious that the population in each
-metastable state changes when the external EF is applied.
-For instance, the population of state $C$ vanishes in equilibrium,
+range of conformations changes when the external EF is applied.
+For instance, the population of conformation $C$ vanishes in equilibrium,
 but plays an important role when the EF is applied. We
@@
 the EF. 
-Firstl, we calculate the probability of being in a certain state,
+Firstl, we calculate the probability of being in a certain conformation range,
 defined as:
@@
 Second,
-we study the net probability flux from metastable state $I$ to $J$, defined by:
+we study the net probability flux from conformation $I$ to $J$, defined by:
 \begin{align}\nonumber
@@
 Through $F_{J,I}(t)$, the original overall nonequilibrium process $\vect x_t$
-is reduced to the probabilistic link between discretized states $\{A_1, A_2, B_1, B_2, C\}$.
+is reduced to the probabilistic link between discretized conformations $\{A_1, A_2, B_1, B_2, C\}$.
 If the resulting reduced process 
@@
 and not small enough so that the joint probabilities can be calculated with acceptable accuracy.
-In the case of oscillating EF, the net probability flux is also highly oscillating,
+In the case of oscillatory EF, the net probability flux is also highly oscillatory,
 thus it is convenient to study the integrated probability flux:
@@
 
-\subsection{Results and discussions}
+\subsection{Conformational dynamics}
 
@@
   \includegraphics[]{fig.ala/fig-meta-npt.eps}
-  \caption{The probability that the system is in a metastable states when a constant EF is present.
-    The warm-up time is $t_{warm} = 10$~ps. The red line refers to state $A_1$,
+  \caption{The probability that the system is in the ranges of conformations when a constant EF is present.
+    The warm-up time is $t_{warm} = 10$~ps. The red line refers to conformation $A_1$,
     green to $A_2$, dark blue to $B_1$, purple to $B_2$ and light blue
@@
 
-The time-dependent probability of the system in a certain metastable state is given in
+The time-dependent probability of the system in a certain range of conformations is given in
 Fig.~\ref{fig:tmp5}. The beta sheet conformations $B_1$ and $B_2$,
@@
 all fluxes converge to zero. This indicates
-as the EF is switched on, the system first is driven away from the initial
-equilibrium (at zero EF), and this is a nonequilibrium process.
-After a long enough time, the system
-is fully relaxed to the new equilibrium defined by the action of the constant EF.\\
+that as the EF is switched on, the system first is driven away from the initial
+equilibrium (at zero EF), and this is a nonequilibrium process, 
+after a long enough time, the system
+is fully relaxed to the new equilibrium defined by the action of the constant EF,
+and stays there as long as the EF is kept.
+% \\
 % it gradually relaxes to the new equilibrium,
-{\bf COMMENT LUIGI: Not clear, because some of the states may not be visited again. Anyway the choice of name and definition of ``metastable'' sound really not great}\\
-For this reason we do not see any change
-in the population density of the metastable states.\\
-{\bf END COMMENT}\\
+% {\bf COMMENT LUIGI: Not clear, because some of the states may not be visited again. Anyway the choice of name and definition of ``metastable'' sound really not great}\\
+% For this reason we do not see any change
+% in the population density of the metastable states.\\
+% {\bf END COMMENT}\\
 
@@
 Even though the system is finally relaxed to the new equilibrium,
-the timescale of relaxation of each metastable state is different. 
+the timescale of relaxation of each conformation is different. 
 From Fig.~\ref{fig:tmp6}, we observe mainly
@@
 6.8~Debye, and  corresponds to a dipole energy of ca. $-13.6$~kJ/mol.
-We calculate the averaged dipole moment of different metastable states
+We calculate the averaged dipole moment of different conformations
 under the constant EF, and they are 6.8, 6.0, 5.1, 3.1 and 7.1~Debye
@@
 The free energy barriers between the
-metastable states were reported to be of order $20\sim 40$~kJ/mol~\cite{bohner2012algorithm},
+conformations were reported to be of order $20\sim 40$~kJ/mol~\cite{bohner2012algorithm},
 which is comparable to the dipole energy difference. 
@@
 and $A_1$ and $C$ are conformations with higher probability, because their dipole moments are the highest
-among all metastable conformations. Moreover, the $B_2$ conformation vanishes because
+among all conformations. Moreover, the $B_2$ conformation vanishes because
 its dipole is significantly lower than other conformations.
@@
 
-\subsection{Testing the influence of the finite-size effect of the Hamiltonian region}
+\subsection{The finite-size effect of the Hamiltonian dynamics and thermostated regions}
 
@@
   \includegraphics[]{fig.ala/fig-meta-conv.eps}
-  \caption{Populations of the metastable states as a function of time.
-    The dashed vertical lines indicate the three different time scale of
-  metastable state population at $t_{\textrm{warm}} = 10~\textsf{ps}$.}
+  \caption{Testing the finite-size effect of the Hamiltonian dynamics and thermostated region.
+    Probabilities of different ranges of conformations are presented as a function of time.
+    See the text for more details.
+  }
   \label{fig:tmp7}
@@
 simulations in a finite size periodic system, and further divided it
-into a Hamiltonian dynamics region and a thermostating region.
+into a Hamiltonian dynamics region and a thermostated region.
 Since the periodic boundary conditions and the division of the system
@@
 \section{Example II:
-  periodically oscillating EF}
-
-A step forward in our study is to consider a periodically oscillating EF which has
+  periodically oscillatory EF}
+
+A step forward in our study is to consider a periodically oscillatory EF which has
 a $\sin$-wave shape:
@@
     shown. The black line refers to the static EF with turning on
-    time $t_{warm} = 10$~ps. The red line refers to the oscillating field with period
+    time $t_{warm} = 10$~ps. The red line refers to the oscillatory field with period
     10~ps, while the green line is for a period of 40~ps and the blue for 200~ps.}
@@
 It shows that the oscillating period of the molecular dipole moment
-is the same as the period of the oscillating EF. Therefore,
+is the same as the period of the oscillatory EF. Therefore,
 the molecular dipole moment
@@
 dipole moment is close to the values obtained in the case of constant EF, which
-means that the variation of the oscillating EF is so slow that the
+means that the variation of the oscillatory EF is so slow that the
 alanine has enough time to 
@@
 smaller than in the case of constant EF. One possible reason is that the
-relaxation of the order parameter is very slow, and the molecule in case of oscillating field is
+relaxation of the order parameter is very slow, and the molecule in case of oscillatory field is
 not exposed to a strong enough EF for a long enough. For  $T=10$ and 40~ps, the orientation of the alanine is only weakly
@@
   % \includegraphics[width=0.49\textwidth]{fig.ala/fig-meta-mode2-2000.eps}
-  \caption{ The probability of being in a certain metastable state for
-    periodically oscillating EF. Different periods,
+  \caption{ The probability of being in a certain range of conformations for
+    periodically oscillatory EF. Different periods,
     i.e. $T=10$~ps, 40~ps and 200~ps, are presented here.  The
-    probability of being in a certain metastable state $I$, which is
+    probability of being in a certain conformation range $I$, which is
     denoted by $P_I$ in this paper, is plotted by colored lines against
@@
     Integrated probability flux $Q_{J,I}(t)$ of the periodically
-    oscillating EF is plotted against time. The unit of the
+    oscillatory EF is plotted against time. The unit of the
     time (horizontal axis) is picosecond.
@@
     probability flux is defined by $Q_{J,I}(t) = \int_0^t F_{J,I}(\tau) d\tau$, where
-    $F(t)$ is the net probability flux from metastable state $I$ to $J$.
+    $F(t)$ is the net probability flux from conformation $I$ to $J$.
     From up to down, rows report results with  period 10, 40 and 200~ps, respectively.
@@
     if the integrated flux $Q_{J,I}$ increases, there exists a (time-averaged)
-    non-zero net flux from metastable state $I$ to $J$.
+    non-zero net flux from conformation $I$ to $J$.
   }
@@
 The Fig.~\ref{fig:tmp9} shows the probability of the
-metastable states against time for periodically oscillating EF.  The
+conformations against time for periodically oscillatory EF.  The
 Fig.~\ref{fig:tmp10} presents the integrated probability fluxes between
-metastable states. Here the probability fluxes are not reported
+conformations. Here the probability fluxes are not reported
 because the profiles are highly oscillating and they would not offer 
@@
 considerably with respect to time.
-However, the probability in metastable state $C$ significantly
+However, the probability in conformation $C$ significantly
 increases to approximately 0.17 for $T=10$~ps, 0.27 for  $T=40$~ps, and
-0.25 for $T=200$~ps.\\
-{\bf COMMENT LUIGI: sentence and context and reasoning of the part below not clear}
-Note that in the case of constant EF, although the dipole moment is
-larger than the  $T=40$~ps case (see Fig.~\ref{fig:tmp8} for comparison), the
-probability of being in $C$ is indeed lower (only 0.22).\\
-{\bf END COMMENT}\\
-For the case of constant EF, the probability of state $A_1$
+0.25 for $T=200$~ps.
+% \\
+% {\bf COMMENT LUIGI: sentence and context and reasoning of the part below not clear}
+% Note that in the case of constant EF, although the dipole moment is
+% larger than the  $T=40$~ps case (see Fig.~\ref{fig:tmp8} for comparison), the
+% probability of being in $C$ is indeed lower (only 0.22).\\
+% {\bf END COMMENT}\\
+For the case of constant EF, the probability of conformation $A_1$
 increases from 0.45 to 0.69, and that of $B_1$ almost vanishes.
-These phenomena are not observed in the oscillating EF case.
-In the case of $T=10$ and $40$~ps, the probability of being in a state
+These phenomena are not observed in the oscillatory EF case.
+In the case of $T=10$ and $40$~ps, the probability of being of a conformation
 reaches the steady value in around 300~ps, while it requires about 1200~ps
@@
   \includegraphics[width=0.5\textwidth]{fig.ala/graphs/graph-t0010-1.eps}
-  \caption{Schematic plot of the main probability flux between metastable
-    states on the Ramachandran histogram
-    for periodically oscillating EF, $T=10$~ps. The thickness 
+  \caption{Schematic plot of the main probability flux between conformations
+    on the Ramachandran histogram
+    for periodically oscillatory EF, $T=10$~ps. The thickness 
     of the arrows approximately presents the strength of the flux.
@@
 integrated probability net fluxes, which imply some lasting and directional
-fluxes among the metastable states (see Fig.~\ref{fig:tmp11} for a schematic plot of the main probability
+fluxes among the conformations (see Fig.~\ref{fig:tmp11} for a schematic plot of the main probability
 fluxes for $T=10$~ps).
@@
 This shows an interesting phenomenon: although
-the oscillating EF is not directional and vanishes in a time-average process,
-it generates directional probability fluxes among the metastable states.
+the oscillatory EF is not directional and vanishes in a time-average process,
+it generates directional probability fluxes among the conformations.
 Moreover, we have identified some loops of the flux: for example, $A_1 \rightarrow B_1
@@
 comparable to case $T=10$~ps, except that the probability fluxes
-going into state $C$ is stronger, which actually results in
+going into conformation $C$ is stronger, which actually results in
 a more dominant probability in $C$.
@@
 Moreover, we see that the integrated flux reaches a linearly increasing
-stage after about 2400~ps, which is even longer than the time scale
+stage after about 3200~ps, which is even longer than the time scale
 at which the probability of $C$ reaches its steady value. This indicates
@@
 process, and nonequilibrium phenomenon will not be observed. For example,
-the probability being in a  metastable state will change
+the probability being of a conformation will change
 smoothly from equilibrium value to the new equilibrium of $E=1$~V/nm, as
@@
 
-\section{Concluding remarks}
+\section{Conclusions and discussions}
+
+In this paper, we investigate the nonequilibrium conformational
+dynamics of alanine dipeptide under constant and oscillatory electric
+field (EF) by the dynamical nonequilibrium molecule dynamics (D-NEMD) method.
+The conformations of the alanine dipeptide are
+firstly projected onto the Ramachandran histogram, and
+then manually grouped into 5 ranges of conformations.
+% several conformations are identified by a manual
+% division of the Ramachandran histogram.
+These ranges of conformations
+correspond to different secondary structures of protein.
+Then the time-dependent probability
+of being in a certain conformation range and the net probability flux
+between them are calculated. 
+We conclude that under the constant EF, several different time scales
+of the conformational dynamics are identified. The slowest time scales,
+which are as long as 500~ps, correspond to a conformational change
+from $B_1$ (corresponds to $\beta$-sheet) to $A_1$ and $C$ (right-handed
+and left handed $\alpha$-helix, respectively).
+Under the constant EF, the dipole moment of alanine aligns parallel to the direction
+of the EF, while the direction of the molecule lies perpendicular to the
+EF. Moreover, the dipole moment response of the alanine is
+demonstrated to be much faster than the orientational response.
+The solvation structure around the alanine is investigated
+by calculating the solute-solvent radial distribution function and the average number of hydrogen
+bond, and is proved to be preserved as the EF turns on, though the
+dipole moment of both solute and solvation, at the same time, align with the direction of EF.
+We consider three oscillatory EF cases with different frequency:
+5, 25 and 100~GHz, respectively. The
+probability of conformations are observed to be also oscillatory,
+and the frequency of this oscillation is the same as the external EF.
+After long enough time,
+the system reaches a ``steady state'', and the probabilities oscillate only around
+a time-independent value at the long time scale. Notice that this is not a really ``steady state'' as defined by
+the literature~\cite{seifert2010fluctuation}, because at the
+short time scale, the probabilities are still oscillating.
+% they oscillate only around a time-invariant value,
+% so we say the system reaches a steady state.
+Although the time-averaged EF vanishes, the probabilities of the conformations
+are as a matter of fact changes due to the oscillatory EF. The most impressive phenomenon
+is the increasing of conformation $C$ that corresponds to
+the left-handed $\alpha$-helix.
+The slowest time scale of 25 and 100~GHz systems is about 300~ps, while
+that of the 5~GHz system is significantly higher: 1200~ps.
+We further update the last number to 3200~ps by analyzing the net probability flux.
+% We further present a updated slowest time scale of the  5~GHz system
+% to 3200~ps from the net probability flux.
+In comparison with the periods of the EF, these time scales are much
+slower, which indicate a very strong time scale separation
+in these nonequilibrium conformation dynamics.
+Although the time-average of the oscillatory EF vanishes, we observed a
+\emph{directional} net probability flux between the conformations, and several
+loop structures are observed. This result is unexpected and shed
+light on the phenomenon of nonequilibrium conformational circulations driven
+by oscillatory EF.
+
+To eliminate the thermal effect in the nonequilibrium process, 
+we propose  a nonequilibrium
+temperature control method, by which the Hamiltonian dynamics is kept
+around the molecule of interest, while the solvent far from the
+molecule is thermostated. We prove the effectiveness of this
+temperature control technique for nonequilibrium MD by testing
+the finite size effect of the Hamiltonian dynamics region and the
+thermostated region.
+
+The intensity of the EF used in this paper is 1~V/nm for both constant
+and oscillatory cases. This intensity is 4-5 orders of magnitude
+higher than that reachable in a standard laboratory microwave
+instrument~\cite{damm2012can}. However, this intensity is achievable
+by a sharp electric field emitter tip~\cite{scovell2000phase}, near
+the surface of mica~\cite{starzyk2013proteins}, or by a modern laser
+equipment~\cite{vogel2008femtosecond}. The authors are fully aware
+that the EF investigated in the present paper is idealized, as pointed
+out by previous simulation studies~\cite{budi2005electric,
+  budi2007effect, budi2008comparative, toschi2008effects,
+  astrakas2011electric, astrakas2012structural, damm2012can,
+  starzyk2013proteins, english2009nonequilibrium,
+  solomentsev2012effects}. However, the present work presents a way of
+studying the EF induced conformational dynamics, and opens the
+possibility of conformational manipulation of the protein by applying
+an external EF.
+
+To describe the system, we use a classical force field with TIP3P water model.
+The EF is well know to be able to protonate the water molecule at the
+intensity we used in the paper. However, this happens at the time
+scale of femitonsecond, which is much shorter than the slowest time
+scale revolved by the current research, so on average it should not play an essential role on the conformational dynamics.
+The polarization with respect to the external EF also does
+not play a important role, because  under the EF of 1~V/nm, the induced dipole
+of water is only c.a. 0.05~Debye that is negligible comparing with the
+dipole moment response observed in our simulations.  Therefore, it is
+reasonable to use a non-polarizable model in this study.  The reason we
+prefer a rigid water model is that it is computationally more
+efficient than any polarizable water model.  We also want to remind
+the reader that it has been reported recently the speed of the slowest 
+dynamics differs a lot among the different force
+fields~\cite{vitalini2013speed}, but the qualitative conclusion (for
+example what is the slowest and the second slowest process, from which
+conformation to which) are basically consistent for the alanine.
+Although our results are derived based on the CHARMM27 force field,
+they still provides qualitative information on the dynamical response of the
+alanine's conformation to the external EF.
+
 \subsection{Electric field, force field, polarization and quantum effects}
 \subsection{Conceptual comparison with other non equilibrium approaches}
-
-The D-NEMD method. The design of the nonequilibrium thermostating.
-
-Time scales discovered in the constant EF case.
-
-The discover of the directional probability flux introduced by the
-oscillating EF.
-
-Comment on the force field. cite A.Mey's paper.
-
-Comment on the real life-strength and frequency of the EF, if it is
-possible in experiment. such a strong field may distroy the molecule.
-
-Comment on the limitation of the non-polarizable model.
 
@@
 % explanation), and couple it to very sufficient thermo- and
-% barostat. We use a Langevin thermostat coupled to the thermostating
+% barostat. We use a Langevin thermostat coupled to the thermostated
 % region with a time-scale of $\tau_{T} = 0.1~\textsf{ps}$, and a

### 2013-08-27 writedown/npt-neq/alanine.tex
Luigi's revise to the conclusion

@@
 different peptide segments along a chain.
-Secondly, the computational cost required is rather massive and thus the testing of the various methodolgy developments proposed here would not be easy to accomplish for large molecules.
+Secondly, the computational cost required is rather massive and thus the testing of the various methodology developments proposed here would not be easy to accomplish for large molecules.
 Of course, given a positive coming out for such a model system, the aim is that of approaching systems of growing complexity.
@@
 and how likely they are (probability). 
-To our knowledge, this study is one of the few (if not the first)  where non equilibrium is explicitly considered for a large molecule in solution bubject to time-dependent EF.
+To our knowledge, this study is one of the few (if not the first)  where non equilibrium is explicitly considered for a large molecule in solution subject to time-dependent EF.
 
@@
 The bracket on the right hand side of Eq.~\eqref{eqn:tmp1} denotes, as usual, the inner product in the
-phase space.  We assume tthat he dynamics of the system is governed by the
+phase space.  We assume that he dynamics of the system is governed by the
 Hamiltonian equation, i.e. $\dot {\vect x} = J \cdot \nabla_{\vect x}
@@
 perform reproducible experiments~\cite{damm2012can}.
-A straigthforward (and realistic) implementation of the temperature control consists in 
+A straightforward (and realistic) implementation of the temperature control consists in 
 embedding the alanine into an infinitely large solvent environment, and 
@@
 In this way one can identify the effect of the EF on the conformational space of the solvated molecule,
-without the artifact that the surrounding solvant cannot release the additional energy of the EF.
-However, in practice, in most of the cases the computational cost of having large solvant environment is rather massive if not prohibitive.
+without the artifact that the surrounding solvent cannot release the additional energy of the EF.
+However, in practice, in most of the cases the computational cost of having large solvent environment is rather massive if not prohibitive.
 Therefore, it is of interest to substitute the infinitely large
@@
 alpha-carbon of radius $R_{ex}$. Here the dynamics is
-Hamiltonian and molecules are not subject to a thermosat; we refer to such subregion as \emph{the Hamiltonian dynamics
+Hamiltonian and molecules are not subject to a thermostat; we refer to such subregion as \emph{the Hamiltonian dynamics
 region}. Instead beyond $R_{ex}$, the dynamics of water is coupled
@@
 located at the center of the simulation region.
-Therefore, a realistic non equilibrium  dynamics is preseved in the Hamiltonian dynamics region (where the properties of interest are observed)
+Therefore, a realistic non equilibrium  dynamics is preserved in the Hamiltonian dynamics region (where the properties of interest are observed)
 and possible direct artificial effects of the thermostating process in the region outside are negligible because of the finite correlation
@@
 the EF. 
-Firstl, we calculate the probability of being in a certain conformation range,
+First, we calculate the probability of being in a certain conformation range,
 defined as:
@@
   \end{tabular*}
-  \caption{A list of main probabilty fluxes and the corresponding time scales observed in the constant EF case.}
+  \caption{A list of main probability fluxes and the corresponding time scales observed in the constant EF case.}
   \label{tab:tmp1}
@@
 we observe that the $\beta$-sheet conformations with lower dipole moment
-are driven towars $\alpha$-helix conformations, 
+are driven towards $\alpha$-helix conformations, 
 and $A_1$ and $C$ are conformations with higher probability, because their dipole moments are the highest
@@
 If the molecule lies perfectly parallel to the EF, then $S_\theta = -2$.
-From $t=0$ to roughly 10~ps, the orientational order parameter fastly
+From $t=0$ to roughly 10~ps, the orientational order parameter rapidly
 decreases from 0 to $-0.15$, which means a weak alignment of the molecule to the external field.
@@
 (see Fig.~\ref{fig:tmp7a}). The average, relative position of the COM of water molecules measured w.r.t.
- the alanine does not change significantly as afunction of time (within the statistical error). Plot (b) of
+ the alanine does not change significantly as function of time (within the statistical error). Plot (b) of
 Fig.~\ref{fig:tmp7a} presents the number of hydrogen bonds between the
@@
 Since the periodic boundary conditions and the division of the system
-are technical (not physical) approximations to the real system with dynamics-preserveing thermal control, 
+are technical (not physical) approximations to the real system with dynamics-preserving thermal control, 
 the effect of the finite-size in 
@@
 and although the alanine dipeptide can respond to the EF action immediately,
-it does not have enough time to fully relax the dipole, as aconsequence the maximum dipole moment is smaller than the previous case.
+it does not have enough time to fully relax the dipole, as a consequence the maximum dipole moment is smaller than the previous case.
 % For even smaller period $T=10$~ps, the alanine does not have enough
@@
 
-In this paper, we investigate the nonequilibrium conformational
-dynamics of alanine dipeptide under constant and oscillatory electric
+We have investigated the conformational
+dynamics of alanine dipeptide under the action of a constant and oscillatory electric
 field (EF) by the dynamical nonequilibrium molecule dynamics (D-NEMD) method.
@@
 These ranges of conformations
-correspond to different secondary structures of protein.
-Then the time-dependent probability
+correspond to different secondary structures in larger molecules (i.e. proteins).
+Next, the time-dependent probability
 of being in a certain conformation range and the net probability flux
 between them are calculated. 
-We conclude that under the constant EF, several different time scales
-of the conformational dynamics are identified. The slowest time scales,
-which are as long as 500~ps, correspond to a conformational change
+From the results obtained, we conclude that under a constant EF, several different time scales
+of the conformational dynamics can be identified. The slowest time scale,
+in the range of 500~ps, corresponds to a conformational change
 from $B_1$ (corresponds to $\beta$-sheet) to $A_1$ and $C$ (right-handed
 and left handed $\alpha$-helix, respectively).
-Under the constant EF, the dipole moment of alanine aligns parallel to the direction
-of the EF, while the direction of the molecule lies perpendicular to the
+Under the constant EF, the dipole moment of alanine aligns parallel to the direction of the EF, while the direction of the molecule lies perpendicular to the
 EF. Moreover, the dipole moment response of the alanine is
-demonstrated to be much faster than the orientational response.
+shown to be much faster than the orientational response.
 The solvation structure around the alanine is investigated
 by calculating the solute-solvent radial distribution function and the average number of hydrogen
-bond, and is proved to be preserved as the EF turns on, though the
-dipole moment of both solute and solvation, at the same time, align with the direction of EF.
-We consider three oscillatory EF cases with different frequency:
+bond, and is proved to be preserved as the EF is turned on, though the
+dipole moment of both solute and solvation molecules is aligned with the direction of the EF.
+Then, we consider three oscillatory EF cases with different frequency:
 5, 25 and 100~GHz, respectively. The
@@
 the system reaches a ``steady state'', and the probabilities oscillate only around
-a time-independent value at the long time scale. Notice that this is not a really ``steady state'' as defined by
-the literature~\cite{seifert2010fluctuation}, because at the
-short time scale, the probabilities are still oscillating.
+a time-independent value at the long time scale. Notice that, strictly speaking, this is not a  true ``steady state'' as defined in
+literature~\cite{seifert2010fluctuation}, because at the
+short time scale, the probabilities are still oscillating (with a period that is the same as the EF).
 % they oscillate only around a time-invariant value,
 % so we say the system reaches a steady state.
-Although the time-averaged EF vanishes, the probabilities of the conformations
-are as a matter of fact changes due to the oscillatory EF. The most impressive phenomenon
-is the increasing of conformation $C$ that corresponds to
+Although in a time-average process the EF vanishes, the probabilities of the conformations, as a matter of fact, changes due to the oscillatory EF. The most relevant phenomenon
+is the increasing probability of conformation $C$ that corresponds to
 the left-handed $\alpha$-helix.
@@
 intensity we used in the paper. However, this happens at the time
-scale of femitonsecond, which is much shorter than the slowest time
+scale of femtosecond, which is much shorter than the slowest time
 scale revolved by the current research, so on average it should not play an essential role on the conformational dynamics.
@@
 efficient than any polarizable water model.  We also want to remind
-the reader that it has been reported recently the speed of the slowest 
-dynamics differs a lot among the different force
-fields~\cite{vitalini2013speed}, but the qualitative conclusion (for
-example what is the slowest and the second slowest process, from which
-conformation to which) are basically consistent for the alanine.
-Although our results are derived based on the CHARMM27 force field,
-they still provides qualitative information on the dynamical response of the
-alanine's conformation to the external EF.
-
-\subsection{Electric field, force field, polarization and quantum effects}
-\subsection{Conceptual comparison with other non equilibrium approaches}
-
-% Clearly two time-scales of relaxation are observed.  For
-% configurations $A_2$ and $B_2$, the relaxations are very fast and
-% comparable to $t_{\textrm{warm}}$. For configurations $A_1$, $B_1$ and
-% $C$, the time-scales of relaxation are roughly 600~\textsf{ps}.
-
-% \section{Testing the effect of the thermostat and barostat}
-
-% % \section{System set up}
-
-% % $R_{\textrm{ex}}$ was chosen to be
-% % $1.0$~\textsf{nm}, which means that a Langvin thermostat ($\tau =
-% % 0.1~\textsf{ps}$) was applied to water molecules that were more than
-% % $1.0$~\textsf{nm} away from the center of the simulation box. In
-% % addition, a Parrinello-Rahman barostat was couple to the system with a
-% % time-scale of $\tau_{\textrm{P}} = 2.0~\textsf{ps}$.
-
-% Let's consider an infinitely large NVE system (here we call it
-% "universe"). Some interesting process is happening in a small
-% subsystem. For equilibrium phenomena, this subsystem is the usually
-% considered as NVT (or NPT, $\mu$VT, depends on how the question is
-% raised) system.  In simulations, we only simulate the subsystem and
-% use the thermostat to mimic the embedment into the universe.  For
-% non-equilibrium simulation, we also want to simulate only the
-% subsystem of interest, but the physical meaning of directly applying a
-% thermostat designed for generating equilibrium ensemble is not clear
-% to a non-equilibrium process. Moreover, there is no unique way of
-% defining how the subsystem is coupled into the universe: It is subject
-% to how the perturbation comes into the subsystem, and how the energy
-% of the system dissipates into the universe. In the case of switching on
-% EF system, two limiting scenarios are considered by us: (1)
-% The subsystem is isolated from the universe: The EF is
-% applied to a system that conserves the energy, volume and number of
-% particle (i.e. a NVE subsystem in short).  The isolation here means
-% that the subsystem does not exchange energy, volume and number of
-% particle with the universe, but the perturbation (electric field) does
-% come in to the subsystem.  The periodic boundary condition is applied
-% here only to avoid the difficulty of defining a experimental
-% meaningful boundary in simulation.  In this scenario, the size the
-% subsystem is somewhat arbitrary (it depends on experimental setting),
-% therefore, it is important to consider the convergence of the
-% simulation result with respect to the size of the subregion.  (2) The
-% system exchange the energy, volume and particle with the universe, and
-% the universe is so big that the perturbation in the subsystem will not
-% kick the universe from equilibrium.  In practice, it is impossible to
-% simulate the infinite large universe, Instead, we want to simulate the
-% considerably smaller subsystem instead.  The idea is to divide the
-% simulation region into two parts (see Fig.~\ref{fig:tmp2}): the first
-% is called \emph{Newtonian dynamics region} that is a region around the
-% molecule of interest, where the dynamics is Newtonian. Note that the
-% molecular trajectories in the Newtonian dynamics region are the same
-% as if it were couple to the universe, only when a proper boundary
-% condition is provided. Strictly speaking, the boundary should be
-% provided by the out side infinitely large universe, which immediately
-% leads back to the numerical difficulty of simulating a infinite large
-% system. However, we notice that the detailed information
-% (i.e. position and velocity) of the every molecule outside the
-% Newtonian dynamics region is not relevant to the non-equilibrium
-% behavior of the molecule of interest, because we are only interest in
-% the non-equilibrium averages, which does not depends on the individual
-% trajectory, but on the trajectorial ensemble sampled by the
-% non-equilibrium simulation.  Therefore, the universe, as a boundary to
-% the Newtonian dynamics region, can be replace by
-% an efficiently thermo- and barostated subsystem, as indicated by the gray
-% part of Fig.~\ref{fig:tmp2}. 
-% % That is to say the subsystem is coupled to a
-% % thermostat, a barostat and a particle bath with infinitely high
-% % efficiency. Practically, it is impossible to simulation with a
-% % ``infinitely fast'' thermostat, barostat and particle bath.
-% We indicate the radius of the Newtonian dynamics region by
-% $R_{\textrm{ex}} = 1~\textsf{nm}$ (see Fig.~\ref{fig:tmp2} for
-% explanation), and couple it to very sufficient thermo- and
-% barostat. We use a Langevin thermostat coupled to the thermostated
-% region with a time-scale of $\tau_{T} = 0.1~\textsf{ps}$, and a
-% Parrinello-Rahman barostat with a time-scale of $\tau_{P} =
-% 2.0~\textsf{ps}$.
-
-% The non-equilibrium steady temperature and pressure of the
-% non-thermostated simulation are $330$ K and $-500$ Bar,
-% correspondingly. Those of the thermostated system are $300$ K and 1
-% Bar, correspondingly. Therefore, we can see from Fig.~\ref{fig:tmp6}
-% that the relaxation of the thermostated system is faster than the
-% non-thermostated system. The three time-scale of metastable population
-% dynamics in the thermostated system is consistent with that of the
-% non-thermostated system. This means that thermostating, in this case,
-% does not qualitatively change the population dynamics of metastable
-% states.
-
-% % \begin{figure}
-% %   \centering
-% %   \includegraphics[]{fig.ala/fig-meta-stat-10.eps}
-% %   \caption{ Comparison between simulations with and without
-% %     temperature and pressure control at $t_{\textrm{warm}} =
-% %     10~\textsf{ps}$. The The populations of the metastable sets as a
-% %     function of time are plotted.  The dashed vertical lines indicate
-% %     the three different time scale of metastable set population at
-% %     $t_{\textrm{warm}} = 10~\textsf{ps}$.}
-% %   \label{fig:tmp6}
-% % \end{figure}
-
-% % To make the non-equilibrium feasible, we assume the
-% % non-equilibrium process is \emph{local}, i.e. the non-equilibrium perturbation
-% % of the system happens only locally, and the rest of the system
-% % stays the unperturbed (usually assumed under ambient conditions).
-% % This provides us the possibility of simulating only the small subsystem
-% % of the universe: We can simulate only subsystem by providing proper
-% % boundary condition for it, so that it behaves as if it were embeded into
-% % the universe.
-
-% % \subsection{The water structure around methane under impluse }
-% % In this study, we firstly consider the system of a methane molecule solvated
-% % in the liquid water environment. A local density perturbation is implemented
-% % by applying an impluse  in a shell surronding methane, see Fig.~\ref{fig:tmp1}.
-% % % As far as we concerned, the situation is: we truncate the universe to the
-% % % subsystem, and provide proper boundary condition for this
-% % % subsystem.
-% % Here we denote the size of this subsystem by $R_{\ex}$.
-% % Notice this subsystem is simulated by the Newtonian
-% % dynamics. If the size of the
-% % subsystem is large enough so that the perturbation is
-% % small enough when it travels to the boundary of the subsystem, then a
-% % trivial boundary condition would be: coupling the system to a boundary
-% % layer equilibriated by the thermostat (and barostat or particle reservior),
-% % which mimics the infinitely large equilibrium universe.
-
-% % \begin{figure}
-% %   \centering
-% %   \includegraphics[width=0.3\textwidth]{fig/kick.eps}
-% %   \caption{Schematic plot of the density perturbation.}
-% %   \label{fig:tmp1}
-% % \end{figure}
+the reader that it has been reported recently that the physical scale of the slowest 
+dynamics differs in a considerable way between different force
+fields~\cite{vitalini2013speed}. However, the qualitative conclusions (for
+example the answer to the question of which is the slowest and the second slowest process, from which
+conformation to which conformation the system moves) are basically consistent for the alanine from the point of view of force fields.
 

### 2013-08-27 writedown/npt-neq/alanine.tex
remove the stupid windows end-line symbol

@@
 intensity we used in the paper. However, this happens at the time
-scale of femtosecond, which is much shorter than the slowest time
-scale revolved by the current research, so on average it should not play an essential role on the conformational dynamics.
+scale of femtoseconds, which is much shorter than the slowest time
+scale resolved by the current research, so on average it should not play an essential role on the conformational dynamics.
 The polarization with respect to the external EF also does

### 2013-09-04 writedown/npt-neq/alanine.tex
revision due to Christof

@@
 
-In this perspective, if one wants to use MD, the proper way to do it would be that of treating a situation of non equilibrium with algorithms that can explicitly describe it.
+In this perspective, if one wants to use MD, the proper way to do it would be that of treating a situation of nonequilibrium with algorithms that can explicitly describe it.
 This is the approach that will be followed in this work.
@@
 Secondly, the computational cost required is rather massive and thus the testing of the various methodology developments proposed here would not be easy to accomplish for large molecules.
-Of course, given a positive coming out for such a model system, the aim is that of approaching systems of growing complexity.
+Of course, given a positive outcome for such a model system, the aim is that of approaching systems of growing complexity.
 The paper is organized as follows:
@@
 simulations, we are able to address the question of how the peptide
-changes the conformation in a EF (conformational space), when do these changes happens (time scale),
+changes the conformation in an EF (conformational space), when do these changes happens (time scale),
 and how likely they are (probability). 
-To our knowledge, this study is one of the few (if not the first)  where non equilibrium is explicitly considered for a large molecule in solution subject to time-dependent EF.
+To our knowledge, this study is one of the few (if not the first)  where nonequilibrium w.r.t. conformation is explicitly considered for a large molecule in solution subject to time-dependent EF.
 
@@
 calculated by averaging the microscopic observable measured at each time $t$ along each branching trajectory.
+Stochastic dynamics (Langevin) can be hadeled analogoursly.
 
@@
 % Therefore, we are interested in a 
-For this study We are interested in 
+For this study, we are interested in 
 nonthermal~\cite{delaHoz2005microwaves} effects of the EF
@@
 
-As it is well known, in MD, for equilibrium situation, the solution is to couple
+As it is well known, in MD, for equilibrium situations, the solution is to couple
 the system to a an external thermostat, under which the desired ensemble
@@
 conditions.
-However, coupling the system to a thermostat for non equilibrium situations is a delicate issue.
-In fact, since a thermostat is explicitly designed to bring the system at equilibrium, any perturbation produced by the EF, would be mostly adsorbed by the thermostat.
+However, coupling the system to a thermostat for nonequilibrium situations is a delicate issue.
+In fact, since a thermostat is explicitly designed to bring the system into equilibrium, any perturbation produced by the EF would be mostly adsorbed by the thermostat.
 This means that the physics of the original Hamiltonian dynamics with the EF would be lost and the response to the perturbation becomes unphysical.
@@
 itself and the water molecules in the closer solvation shells is
-crucial in order to determine the response of the observable of interest
+crucial, in order to determine the response of the observable of interest
 under the perturbation of the EF (in this work, it is the conformational change of alanine).
@@
 located at the center of the simulation region.
-Therefore, a realistic non equilibrium  dynamics is preserved in the Hamiltonian dynamics region (where the properties of interest are observed)
+Therefore, a realistic nonequilibrium  dynamics is preserved in the Hamiltonian dynamics region (where the properties of interest are observed)
 and possible direct artificial effects of the thermostating process in the region outside are negligible because of the finite correlation
@@
 has been fully equilibriated without any EF. From $t=0$ to
-warm-up time $t=t_{\textrm{warm}}$, the eclectic field is switched on linearly, while
+the warm-up time $t=t_{\textrm{warm}}$, the eclectic field is switched on linearly, while
 after $t=t_{\textrm{warm}}$, the field is kept constant in time at
@@
 shown in Fig.~\ref{fig:tmp4}. The equilibrium distribution of the
-conformations is given in the plot (a), and the fully relaxed
-conformation under the action of $E_{\infty} = 1$~V/nm is given  plot (b).  It is
+conformations is given in plot (a), and the fully relaxed
+conformation under the action of $E_{\infty} = 1$~V/nm is given in plot (b).  It is
 evident from the plot that the conformations are grouped in several clusters, and the
@@
 therefore want to study how the alanine changes from one conformation
-to the other, how fast is the change, and the relations to the 
+to the other, how fast the change is, and the relations to the 
 the EF. 
@@
 \begin{align}\nonumber
-  F_{J,I}(t) & =\lim_{\Delta t\rightarrow 0} \frac1{\Delta t} [\mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I) - \mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J)], \\\label{eqn:tmp7}
+  F_{J,I}(t) & = \frac1{\Delta t}\, [\mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I) - \mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J)], \\\label{eqn:tmp7}
   & J,I \in \{A_1, A_2, B_1, B_2, C\}.
 \end{align}
+Here the time interval $\Delta t$ should be small enough comparing with the
+time scale of conformational dynamics,
+so that the changes in the conformation probabilities
+can be linearly approximated.
+In the meanwhile,  $\Delta t$ should also be  large enough comparing with
+the timestep of MD integrator, 
+so that the left hand of Eq.~\eqref{eqn:tmp7} is well-defined, and can be
+estimated with good statistical accuracy.
+See also the discussions in Ref.~\cite{schuette2011markov}.
 $F_{J,I}(t)$ is essentially the rate of how much conformation $J$ changes
@@
 $\{A_1, A_2, B_1, B_2, C\}$.
-In practice, to measure $ F_{J,I}(t)$, one need first to approximate the limit
-in Eq.~\eqref{eqn:tmp7} by the finite difference,
-then calculate the joint probabilities on
-the right-hand-side from the molecular trajectories.
-In this context, for a precise finite difference approximation a smaller $\Delta t$ is
-preferable although the statistical uncertainty of measuring the joint probabilities
-is higher. In practice,
-we use a $\Delta t$ that is small enough for a precise finite difference approximation,
-and not small enough so that the joint probabilities can be calculated with acceptable accuracy.
+% In practice, to measure $ F_{J,I}(t)$, one needs first to approximate the limit
+% in Eq.~\eqref{eqn:tmp7} by the finite difference,
+% then calculate the joint probabilities on
+% the right-hand-side from the molecular trajectories.
+% In this context, for a precise finite difference approximation a smaller $\Delta t$ is
+% preferable although the statistical uncertainty of measuring the joint probabilities
+% is higher. In practice,
+% we use a $\Delta t$ that is small enough for a precise finite difference approximation,
+% and not small enough so that the joint probabilities can be calculated with acceptable accuracy.
 In the case of oscillatory EF, the net probability flux is also highly oscillatory,
@@
 that as the EF is switched on, the system first is driven away from the initial
-equilibrium (at zero EF), and this is a nonequilibrium process, 
-after a long enough time, the system
+equilibrium (at zero EF);  This is a nonequilibrium process.
+After a long enough time, the system
 is fully relaxed to the new equilibrium defined by the action of the constant EF,
@@
 $t=0$ to approximately 10~\textsf{ps}, a net flux from 
-a flux from $A_1$ to $A_2$.
+$A_1$ to $A_2$ establishes.
 A similar flux is also observed from $B_1$ to $B_2$.
@@
 % $A_2$ to $A_1$.
-Instead a net flux from all $\beta$-sheet conformations
+Moreover, a net flux from all $\beta$-sheet conformations
 ($B_1$ and $B_2$) into $\alpha$-helix conformations ($A_1$, $A_2$ and
@@
 
-\subsection{Molecular Dipole response}
+\subsection{Molecular dipole response}
 
@@
 
-We also consider the orientation of the alanine dipeptide in space (w.r.t. the direction of EF) as a function
+We also consider the orientation of the alanine dipeptide in space (w.r.t.~the direction of EF) as a function
 of time.
@@
 where $\theta$ is the angle between the orientation of the alanine dipeptide
-and the direction of the EF. The order parameter
-indicate how perpendicular does the molecule lie w.r.t. the EF.
-If the molecule is perfectly perpendicular to the EF, then $S_\theta = 1$;
+and the direction of the EF.
+The ensemble average is taken over the trajectory ensemble, so it is
+a time dependent observable.
+The order parameter
+indicates how perpendicular the molecule lies w.r.t.~the EF.
+If the molecule is perfectly perpendicular to the EF, then $S_\theta = 1$.
 If the molecule has no directional
-preference , then $S_\theta = 0$;
+preference, then $S_\theta = 0$.
 If the molecule lies perfectly parallel to the EF, then $S_\theta = -2$.
@@
 center-of-mass (COM) of the water molecules
-(see Fig.~\ref{fig:tmp7a}). The average, relative position of the COM of water molecules measured w.r.t.
- the alanine does not change significantly as function of time (within the statistical error). Plot (b) of
+(see Fig.~\ref{fig:tmp7a}).
+The average, relative position of the COM of water molecules measured w.r.t.~the alanine does not change significantly as a function of time (within the statistical error).
+Plot (b) of
 Fig.~\ref{fig:tmp7a} presents the number of hydrogen bonds between the
@@
   \includegraphics[width=0.48\textwidth]{fig.ala/fig-mode2-order.eps}
-  \caption{The dipole moment calculated for the nonequilibrium situation (a) and
+  \caption{Illustration of the effect of the oscillatory EF:
+    the dipole moment (a) and
     orientation order parameter (b) of alanine dipeptide as a
@@
 highly oscillating and the average value does not change
-considerably with respect to time.
+considerably w.r.t.~time.
 However, the probability in conformation $C$ significantly
@@
 firstly projected onto the Ramachandran histogram, and
-then manually grouped into 5 ranges of conformations.
+then manually grouped into 5  conformations.
 % several conformations are identified by a manual
 % division of the Ramachandran histogram.
-These ranges of conformations
+These conformations
 correspond to different secondary structures in larger molecules (i.e. proteins).
@@
 scale resolved by the current research, so on average it should not play an essential role on the conformational dynamics.
-The polarization with respect to the external EF also does
+The polarization w.r.t.~the external EF also does
 not play a important role, because  under the EF of 1~V/nm, the induced dipole

### 2013-09-05 writedown/npt-neq/alanine.tex
update according Christof's comment
add abstract. revise for submission

@@
 \begin{abstract}
+  In this paper, we investigate the conformational dynamics of alanine
+  dipeptide under an external electric field (EF) by the
+  nonequilibrium molecular dynamics (MD) simulation, which enables us
+  to calculate the nonequilibrium physical properties that are not
+  available for traditional equilibrium MD simulation.  We study both
+  the constant and oscillatory EF cases, and discuss the way to
+  implement the temperature control in the nonequilibrium MD
+  simulation, which removes the irrelevant thermal effect of the EF
+  from the system. In the constant EF case, different time-scales are
+  discovered in the conformational, dipole moment, and orientational
+  dynamics. Moreover, we prove that the solvent structure only
+  marginally changes when the external EF is switched on.  In the
+  oscillatory EF case, the conformational changes are shown to be as
+  strong as constant EF case, and non-trivial nonequilibrium
+  conformational circulations are presented by calculating the
+  integrated net probability fluxes.
 \end{abstract}
@@
   \centering
-  \includegraphics[width=0.3\textwidth]{fig/thermostat.eps}
+  \includegraphics[width=0.3\textwidth]{thermostat.eps}
   \caption{Schematic plot of the nonequilibrium temperature control scheme.
@@
   \centering
-  \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{fig.ala/ext.mode1.010.Ex.01.00.t1000ps.recheck.bk/c-2.eps}}
-  \includegraphics[width=0.37\textwidth]{fig.ala/ext.mode1.010.Ex.01.00.t1000ps.recheck.bk/fig-begin-1.eps}
-  \includegraphics[width=0.37\textwidth]{fig.ala/ext.mode1.010.Ex.01.00.t1000ps.recheck.bk/fig-end-1.eps}
+  \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{c-2.eps}}
+  \includegraphics[width=0.37\textwidth]{fig-begin-1.eps}
+  \includegraphics[width=0.37\textwidth]{fig-end-1.eps}
   \caption{The probability of the conformations of the alanine dipeptide plotted on the Ramachandran histogram.
@@
 is reduced to the probabilistic link between discretized conformations $\{A_1, A_2, B_1, B_2, C\}$.
-If the resulting reduced process 
-is time-reversible, then it is obvious that
-$ F_{J,I}(t) = 0$. In an other word, the quantity $ F_{J,I}(t) $ represents
-the irreversibility of the reduced process on
-$\{A_1, A_2, B_1, B_2, C\}$.
+% If the resulting reduced process 
+% is time-reversible, then it is obvious that
+% $ F_{J,I}(t) = 0$. In an other word, the quantity $ F_{J,I}(t) $ represents
+% the irreversibility of the reduced process on
+% $\{A_1, A_2, B_1, B_2, C\}$.
 % In practice, to measure $ F_{J,I}(t)$, one needs first to approximate the limit
@@
   \centering
-  \includegraphics[]{fig.ala/fig-meta-npt.eps}
+  \includegraphics[]{fig-meta-npt.eps}
   \caption{The probability that the system is in the ranges of conformations when a constant EF is present.
@@
   % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-5.eps}\\
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-1.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-2.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-3.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-4.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-5.eps}\\
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-1.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-2.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-3.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-4.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-5.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-1.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-5.eps}\\
+  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-1.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-5.eps}
   % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-1.eps}
@@
   % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
-  \includegraphics[width=0.45\textwidth]{fig.ala/field.dipole/fig-dipol-order-conf.eps}
+  \includegraphics[width=0.45\textwidth]{fig-dipol-order-conf.eps}
   % \\
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{fig.ala/fig-rdf.eps}
-  \includegraphics[width=0.48\textwidth]{fig.ala/fig-hbond.eps}
+  \includegraphics[width=0.48\textwidth]{fig-rdf.eps}
+  \includegraphics[width=0.48\textwidth]{fig-hbond.eps}
   \caption{The solvent structure around the alanine dipeptide.  Plot
@@
   \centering
-  \includegraphics[]{fig.ala/fig-meta-conv.eps}
+  \includegraphics[]{fig-meta-conv.eps}
   \caption{Testing the finite-size effect of the Hamiltonian dynamics and thermostated region.
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{fig.ala/fig-mode2-dipol.eps}
-  \includegraphics[width=0.48\textwidth]{fig.ala/fig-mode2-order.eps}
+  \includegraphics[width=0.48\textwidth]{fig-mode2-dipol.eps}
+  \includegraphics[width=0.48\textwidth]{fig-mode2-order.eps}
   \caption{Illustration of the effect of the oscillatory EF:
@@
   \centering
-  \includegraphics[width=0.32\textwidth]{fig.ala/fig-meta-mode2-0010.eps}
-  \includegraphics[width=0.32\textwidth]{fig.ala/fig-meta-mode2-0040.eps}
-  \includegraphics[width=0.32\textwidth]{fig.ala/fig-meta-mode2-0200.eps}
-  % \includegraphics[width=0.49\textwidth]{fig.ala/fig-meta-mode2-2000.eps}
+  \includegraphics[width=0.32\textwidth]{fig-meta-mode2-0010.eps}
+  \includegraphics[width=0.32\textwidth]{fig-meta-mode2-0040.eps}
+  \includegraphics[width=0.32\textwidth]{fig-meta-mode2-0200.eps}
+  % \includegraphics[width=0.49\textwidth]{fig-meta-mode2-2000.eps}
   \caption{ The probability of being in a certain range of conformations for
@@
   % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-flux-5.eps}\\
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-1.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-2.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-3.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-4.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-iflux-5.eps}\\
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-1.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-5.eps}\\
   % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-flux-1.eps}
@@
   % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-flux-5.eps}\\
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-1.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-2.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-3.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-4.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-iflux-5.eps}\\
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-1.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-5.eps}\\
   % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-flux-1.eps}
@@
   % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-flux-5.eps}\\
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-1.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-2.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-3.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-4.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-iflux-5.eps}\\
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-1.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-5.eps}\\
   % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-flux-1.eps}
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{fig.ala/graphs/graph-t0010-1.eps}
+  \includegraphics[width=0.5\textwidth]{graph-t0010-1.eps}
   \caption{Schematic plot of the main probability flux between conformations
@@
 
-\bibliography{ref}{}
-\bibliographystyle{unsrt}
+\begin{thebibliography}{10}
+
+\bibitem{bohr2000microwave}
+Henrik Bohr and Jakob Bohr.
+\newblock Microwave-enhanced folding and denaturation of globular proteins.
+\newblock {\em Physical Review E}, 61(4):4310, 2000.
+
+\bibitem{bohr2000microwave-1}
+Henrik Bohr and Jakob Bohr.
+\newblock Microwave enhanced kinetics observed in ord studies of a protein.
+\newblock {\em Bioelectromagnetics}, 21(1):68--72, 2000.
+
+\bibitem{dePomerai2000cell}
+David de~Pomerai, Clare Daniells, Helen David, Joanna Allan, Ian Duce, Mohammed
+  Mutwakil, David Thomas, Phillip Sewell, John Tattersall, Don Jones, and Peter
+  Candido.
+\newblock Cell biology: Non-thermal heat-shock response to microwaves.
+\newblock {\em Nature}, 405:417--418, 2000.
+
+\bibitem{inskip2001cellular}
+Peter~D Inskip, Robert~E Tarone, Elizabeth~E Hatch, Timothy~C Wilcosky,
+  William~R Shapiro, Robert~G Selker, Howard~A Fine, Peter~M Black, Jay~S
+  Loeffler, and Martha~S Linet.
+\newblock Cellular-telephone use and brain tumors.
+\newblock {\em New England Journal of Medicine}, 344(2):79--86, 2001.
+
+\bibitem{mancinelli2004non}
+Fabrizio Mancinelli, Michele Caraglia, Alberto Abbruzzese, Guglielmo
+  d'Ambrosio, Rita Massa, and Ettore Bismuto.
+\newblock Non-thermal effects of electromagnetic fields at mobile phone
+  frequency on the refolding of an intracellular protein: Myoglobin.
+\newblock {\em Journal of cellular biochemistry}, 93(1):188--196, 2004.
+
+\bibitem{budi2005electric}
+A.~Budi, F.S. Legge, H.~Treutlein, and I.~Yarovsky.
+\newblock Electric field effects on insulin chain-b conformation.
+\newblock {\em The Journal of Physical Chemistry B}, 109(47):22641--22648,
+  2005.
+
+\bibitem{budi2007effect}
+A.~Budi, F.S. Legge, H.~Treutlein, and I.~Yarovsky.
+\newblock Effect of frequency on insulin response to electric field stress.
+\newblock {\em The Journal of Physical Chemistry B}, 111(20):5748--5756, 2007.
+
+\bibitem{budi2008comparative}
+Akin Budi, F~Sue Legge, Herbert Treutlein, and Irene Yarovsky.
+\newblock Comparative study of insulin chain-b in isolated and monomeric
+  environments under external stress.
+\newblock {\em The Journal of Physical Chemistry B}, 112(26):7916--7924, 2008.
+
+\bibitem{toschi2008effects}
+Francesca Toschi, Francesca Lugli, Fabio Biscarini, and Francesco Zerbetto.
+\newblock Effects of electric field stress on a $\beta$-amyloid peptide.
+\newblock {\em The Journal of Physical Chemistry B}, 113(1):369--376, 2008.
+
+\bibitem{astrakas2011electric}
+Loukas Astrakas, Christos Gousias, and Margaret Tzaphlidou.
+\newblock Electric field effects on chignolin conformation.
+\newblock {\em Journal of Applied Physics}, 109(9):094702--094702, 2011.
+
+\bibitem{astrakas2012structural}
+Loukas~G Astrakas, Christos Gousias, and Margaret Tzaphlidou.
+\newblock Structural destabilization of chignolin under the influence of
+  oscillating electric fields.
+\newblock {\em Journal of Applied Physics}, 111(7):074702--074702, 2012.
+
+\bibitem{damm2012can}
+Markus Damm, Christoph Nusshold, David Cantillo, Gerald~N Rechberger, Karl
+  Gruber, Wolfgang Sattler, and C~Oliver Kappe.
+\newblock Can electromagnetic fields influence the structure and enzymatic
+  digest of proteins? a critical evaluation of microwave-assisted proteomics
+  protocols.
+\newblock {\em Journal of proteomics}, 75:5533--5543, 2012.
+
+\bibitem{starzyk2013proteins}
+A.~Starzyk and M.~Cieplak.
+\newblock Proteins in the electric field near the surface of mica.
+\newblock {\em The Journal of Chemical Physics}, 139:045102, 2013.
+
+\bibitem{english2009nonequilibrium}
+N.J. English, G.Y. Solomentsev, and P.~O'Brien.
+\newblock Nonequilibrium molecular dynamics study of electric and low-frequency
+  microwave fields on hen egg white lysozyme.
+\newblock {\em The Journal of chemical physics}, 131:035106, 2009.
+
+\bibitem{solomentsev2012effects}
+G.Y. Solomentsev, N.J. English, and D.A. Mooney.
+\newblock Effects of external electromagnetic fields on the conformational
+  sampling of a short alanine peptide.
+\newblock {\em Journal of Computational Chemistry}, 33:917--923, 2012.
+
+\bibitem{ciccotti1975direct}
+G~Ciccotti and G~Jacucci.
+\newblock Direct computation of dynamical response by molecular dynamics: The
+  mobility of a charged lennard-jones particle.
+\newblock {\em Physical Review Letters}, 35(12):789, 1975.
+
+\bibitem{ciccotti1979thought}
+G.~Ciccotti, G.~Jacucci, and I.R. McDonald.
+\newblock "thought-experiments" by molecular dynamics.
+\newblock {\em Journal of Statistical Physics}, 21(1):1--22, 1979.
+
+\bibitem{orlandini2011hydrodynamics}
+S.~Orlandini, S.~Meloni, and G.~Ciccotti.
+\newblock Hydrodynamics from statistical mechanics: combined dynamical-nemd and
+  conditional sampling to relax an interface between two immiscible liquids.
+\newblock {\em Phys. Chem. Chem. Phys.}, 13:13177--13181, 2011.
+
+\bibitem{orlandini2011hydrodynamics-01}
+Sergio Orlandini, Simone Meloni, and Giovanni Ciccotti.
+\newblock Hydrodynamics from dynamical non-equilibrium md.
+\newblock In {\em AIP Conference Proceedings}, volume 1332, page~77, 2011.
+
+\bibitem{delaHoz2005microwaves}
+Antonio de~la Hoz, Angel Diaz-Ortiz, and Andres Moreno.
+\newblock Microwaves in organic synthesis. thermal and non-thermal microwave
+  effects.
+\newblock {\em Chemical Society Reviews}, 34(2):164--178, 2005.
+
+\bibitem{pronk2013gromacs}
+S.~Pronk, S.~P{\'a}ll, R.~Schulz, P.~Larsson, P.~Bjelkmar, R.~Apostolov, M.R.
+  Shirts, J.C. Smith, P.M. Kasson, D.~van~der Spoel, and Hess B.~Lindahl E.
+\newblock Gromacs 4.5: a high-throughput and highly parallel open source
+  molecular simulation toolkit.
+\newblock {\em Bioinformatics}, pages 1--10, 2013.
+
+\bibitem{schuette2011markov}
+C.~Sch{\"u}tte, F.~No{\'e}, J.~Lu, M.~Sarich, and E.~Vanden-Eijnden.
+\newblock Markov state models based on milestoning.
+\newblock {\em The Journal of Chemical Physics}, 134:204105, 2011.
+
+\bibitem{bohner2012algorithm}
+Matthias~U Bohner and Johannes K{\"a}stner.
+\newblock An algorithm to find minimum free-energy paths using umbrella
+  integration.
+\newblock {\em The Journal of Chemical Physics}, 137:034105, 2012.
+
+\bibitem{seifert2010fluctuation}
+U.~Seifert and T.~Speck.
+\newblock Fluctuation-dissipation theorem in nonequilibrium steady states.
+\newblock {\em EPL (Europhysics Letters)}, 89:10007, 2010.
+
+\bibitem{scovell2000phase}
+Dawn~L Scovell, Tim~D Pinkerton, Valentin~K Medvedev, and Eric~M Stuve.
+\newblock Phase transitions in vapor-deposited water under the influence of
+  high surface electric fields.
+\newblock {\em Surface science}, 457(3):365--376, 2000.
+
+\bibitem{vogel2008femtosecond}
+A.~Vogel, N.~Linz, S.~Freidank, and G.~Paltauf.
+\newblock Femtosecond-laser-induced nanocavitation in water: implications for
+  optical breakdown threshold and cell surgery.
+\newblock {\em Physical review letters}, 100(3):38102, 2008.
+
+\bibitem{vitalini2013speed}
+F.~Vitalini, A.S.J.S. Mey, F.~No\'e, and B.G. Keller.
+\newblock The speed of force fields.
+\newblock {\em unpublished}, 2013.
+
+\end{thebibliography}
+
+% \bibliography{ref}{}
+% \bibliographystyle{unsrt}
 

### 2013-11-04 writedown/npt-neq/alanine.tex
backup ..

@@
 
-\title{Exploring the conformational dynamics of a large molecule in solution using an external electric field: A Nonequilibrium Molecular Dynamics Simulation}
+\title{Exploring the conformational dynamics of a large molecule in solution using an external electric field: A nonequilibrium molecular dynamics simulation}
 % \title{The non-equilibrium molecular dynamics simulation of the alanine dipeptide under electric field}
@@
 In this paper, we investigate the conformational dynamics of alanine
-  dipeptide under an external electric field (EF) by the
-  nonequilibrium molecular dynamics (MD) simulation, which enables us
-  to calculate the nonequilibrium physical properties that are not
-  available for traditional equilibrium MD simulation.  We study both
-  the constant and oscillatory EF cases, and discuss the way to
-  implement the temperature control in the nonequilibrium MD
-  simulation, which removes the irrelevant thermal effect of the EF
-  from the system. In the constant EF case, different time-scales are
-  discovered in the conformational, dipole moment, and orientational
+   dipeptide under an external electric field by the
+   nonequilibrium molecular dynamics simulation.  We consider
+   the case of a constant and of an oscillatory field. In this context we
+propose a procedure to
+   implement the temperature control, which removes the irrelevant thermal
+effects of the field. For the constant field different time-scales are
+   identified  in the conformational, dipole moment, and orientational
    dynamics. Moreover, we prove that the solvent structure only
-  marginally changes when the external EF is switched on.  In the
-  oscillatory EF case, the conformational changes are shown to be as
-  strong as constant EF case, and non-trivial nonequilibrium
-  conformational circulations are presented by calculating the
+   marginally changes when the external field is switched on.  In the
+   case of oscillatory field, the conformational changes are shown to be as
+   strong as the previous case, and non-trivial nonequilibrium
+   circular paths in the conformation space are revealed by calculating the
    integrated net probability fluxes.
+  % In this paper, we investigate the conformational dynamics of alanine
+  % dipeptide under an external electric field (EF) by the
+  % nonequilibrium molecular dynamics (MD) simulation, which enables us
+  % to calculate the nonequilibrium physical properties that are not
+  % available for traditional equilibrium MD simulation.  We study both
+  % the constant and oscillatory EF cases, and discuss the way to
+  % implement the temperature control in the nonequilibrium MD
+  % simulation, which removes the irrelevant thermal effect of the EF
+  % from the system. In the constant EF case, different time-scales are
+  % discovered in the conformational, dipole moment, and orientational
+  % dynamics. Moreover, we prove that the solvent structure only
+  % marginally changes when the external EF is switched on.  In the
+  % oscillatory EF case, the conformational changes are shown to be as
+  % strong as constant EF case, and non-trivial nonequilibrium
+  % conformational circulations are presented by calculating the
+  % integrated net probability fluxes.
 \end{abstract}

### 2013-11-06 writedown/npt-neq/alanine.tex
change according to Giovanni's suggestions. big changes are going to come

@@
 has not been reached so far although a considerable number of
-experimental~\cite{bohr2000microwave, bohr2000microwave-1,
+experimental e.g.~\cite{bohr2000microwave, bohr2000microwave-1,
   dePomerai2000cell, inskip2001cellular, mancinelli2004non} and
-theoretical~\cite{budi2005electric, budi2007effect,
+theoretical e.g.~\cite{budi2005electric, budi2007effect,
   budi2008comparative, toschi2008effects, astrakas2011electric,
   astrakas2012structural, damm2012can, starzyk2013proteins,
-  english2009nonequilibrium, solomentsev2012effects} studies have been devoted to this topic;
-where the references reported above represent only a minor sample of examples.
-
-In this perspective, molecular dynamics (MD) has been proved to be useful in
+  english2009nonequilibrium, solomentsev2012effects}
+studies have been devoted to this topic.
+
+In this perspective, molecular dynamics (MD) has been proven useful in
 understanding the behavior of a protein 
@@
 configurations are usually taken from the Protein Data Bank (PDB),
-and then temperature controlled simulations are performed for a maximum extension of the order of 10-60 of nanoseconds.
+and then temperature controlled simulations are performed for a maximum
+time range of the order of 10-60 nanoseconds.
 During this simulation time 
@@
 secondary structure, root mean square displacement (RMSD), the dipole
-moment, shape parameters are calculated as a function of time or taking its time average. This approach releases useful information on how the
+moment, shape parameters are calculated as a function of time, or
+in stationary condition, taking time averages.
+This approach releases useful information on how the
 secondary structure of the molecule is changed by external  EF.  However,
-by plotting some quantities against time, one may observe strong
-fluctuations; the entity of such fluctuations are such that a quantitative 
+the behavior of observables in time is characterized by 
+strong
+fluctuations. The entity of the fluctuations is such that a quantitative 
 analysis becomes difficult and does not allow for  a clear understanding of the rationale behind the conformational changes.
-Although the time average reduces the statistical uncertainty,
-however in this specific case, it is indeed not well defined;
-in fact we are in the presence of a nonequilibrium process
+A time average can reduce the statistical uncertainty,
+but in non-stationary conditions, it is a not-well-founded procedure.
+In fact, we are studying non-stationary nonequilibrium process
 (e.g. relaxing process to the new conformations under a static
 EF, or the dynamics from one conformation to the other under an oscillatory EF).
-
 In this perspective, if one wants to use MD, the proper way to do it would be that of treating a situation of nonequilibrium with algorithms that can explicitly describe it.
-This is the approach that will be followed in this work.
-
-The method we employ is the dynamical nonequilibrium molecular dynamics simulation (D-NEMD).
-The method was firstly developed by one of us (GC) and coworkers~\cite{ciccotti1975direct, ciccotti1979thought}.
-It has been recently applied, with success, to the study of
+This is the approach that will be followed in this work, using
+the dynamical nonequilibrium molecular dynamics simulation (D-NEMD).
+The method, firstly developed by one of us and coworkers~\cite{ciccotti1975direct, ciccotti1979thought}, 
+has been recently applied, to the study of
 hydrodynamics~\cite{orlandini2011hydrodynamics,
-  orlandini2011hydrodynamics-01}. The essential feature of D-NEMD is the following: It provides a way of evaluating
-nonequilibrium observables by using a properly determined ensemble of nonequilibrium MD
-simulations.  In this context, the method can be used for analyzing the
+  orlandini2011hydrodynamics-01}. The essential feature of D-NEMD is to
+provide a way of evaluating time-dependent
+nonequilibrium averages starting from a properly determined initial ensemble.
+In this context, the method can be used to analyze the
 conformational changes of a solvated molecule, subject to a time-dependent EF.
@@
 is easier to draw clear conclusions on the nonequilibrium properties
-of a single peptide by excluding a possible interplay between
+of a single peptide by excluding the slow-going interplay between
 different peptide segments along a chain.
-Secondly, the computational cost required is rather massive and thus the testing of the various methodology developments proposed here would not be easy to accomplish for large molecules.
-Of course, given a positive outcome for such a model system, the aim is that of approaching systems of growing complexity.
+Secondly, the computational cost required is rather massive and thus  testing
+the various methodology proposed here would be hampered for large molecules,
+although they remain our goal.
+
 The paper is organized as follows:
@@
 introduce the physical
-observables for analyzing the nonequilibrium properties. The numerical results of alanine
-dipeptide under static and sine-shaped oscillatory EF are
+observables chosen to analyze the nonequilibrium responses.
+The numerical results for the response of alanine
+dipeptide under static and oscillatory EF are
 finally presented. By calculating the nonequilibrium properties from D-NEMD
-simulations, we are able to address the question of how the peptide
-changes the conformation in an EF (conformational space), when do these changes happens (time scale),
+simulations, we are able to address
+a few relavant questions: (i)~How the conformation of the peptide
+changes in an EF (conformational space);
+(ii)~When do these changes happen (time scale),
 and how likely they are (probability). 
-To our knowledge, this study is one of the few (if not the first)  where nonequilibrium w.r.t. conformation is explicitly considered for a large molecule in solution subject to time-dependent EF.
+To our knowledge, this study is one of the few (if not the first)  where
+time-dependent nonequilibrium w.r.t. conformation
+is explicitly considered for a large molecule
+in solution subject to time-dependent EF.
 
@@
 \subsection{Nonequilibrium molecular dynamics simulation}
-In this section we briefly review the approach for performing dynamical nonequilibrium
+In this section we briefly review the dynamical approach to nonequilibrium
 molecular dynamics (D-NEMD) \cite{ciccotti1975direct, ciccotti1979thought,
@@
 Here we always assume that the initial probability distribution
-$\rho(\vect x, 0)$ is known and is identical to the equilibrium distribution of the system
+$\rho(\vect x, 0)$ is known. In particular, in our case,
+it is identical to the equilibrium distribution of the system
 without EF.
@@
 Hamiltonian equation, i.e. $\dot {\vect x} = J \cdot \nabla_{\vect x}
-\mathcal H(\vect x)$, where $\mathcal H$ is the Hamiltonian, and $J$ is
+\mathcal H(\vect x, t)$, where $\mathcal H$ is the time-dependent Hamiltonian,
+and $J$ is
 the symplectic matrix. The Liouville equation for the probability
@@
 Eq.~\eqref{eqn:tmp2}
-can be formally solved by $\rho(\vect x, t) = e^{-iL(t)} \rho(\vect x, 0)$.
+can be formally solved by $\rho(\vect x, t) = U^\dagger(t,0) \rho(\vect x, 0)$,
+where $U^\dagger(t,0) = \exp\{-i \int_0^t d t' L(t')\}$.
 On the other hand
@@
 \end{align}
-This equation can be formally solved by $\hat O(\vect x(t)) = e^{iL(t)} \hat O(\vect x(0))$, therefore,
+This equation can be formally solved by
+$\hat O(\vect x(t)) = U(t,0)\,\hat O(\vect x(0))$, therefore,
 \begin{align}\nonumber
   O(t) & = \langle \hat O(\vect x), \rho(\vect x, t)\rangle
-  = \langle \hat O(\vect x), e^{-iL(t)} \rho(\vect x, 0)\rangle
-  = \langle e^{iL(t)}\hat O(\vect x), \rho(\vect x, 0)\rangle\\\label{eqn:tmp4}
+  = \langle \hat O(\vect x), U^\dagger(t,0)\, \rho(\vect x, 0)\rangle
+  = \langle U(t,0)\,\hat O(\vect x), \rho(\vect x, 0)\rangle\\\label{eqn:tmp4}
   &= \langle \hat O(\vect x(t)), \rho(\vect x, 0)\rangle
@@
 observable $O(t)$ calculated in a situation of nonequilibrium is equal to the ensemble average of
-the microscopic observable measured along trajectories, the
-initial configurations of which are subject to the \emph{equilibrium}
+the microscopic observable computed along trajectories, starting from
+initial configurations sampled from an \emph{equilibrium}
 distribution. In practical terms we proceed by first running an equilibrium MD simulation
 to generate a sample of configurations. Next we employ these configurations as
-initial configurations and, for each, the Hamiltonian dynamics is integrated until
-time $t$. These trajectories are also called \emph{branching
-  trajectories} in this paper (see Fig.\ref{branching} for a pictorial representation). 
+initial configurations and, for each, the full Hamiltonian dynamics is integrated until
+time $t$.
+In this paper, these trajectories are called \emph{branching
+  trajectories} (see Fig.\ref{branching} for a pictorial representation). 
 Finally, the value of the macroscopic observable at time $t$ is
 calculated by averaging the microscopic observable measured at each time $t$ along each branching trajectory.
-Stochastic dynamics (Langevin) can be hadeled analogoursly.
+Stochastic dynamics (e.g.~Langevin dynamics) can be handled analogoursly.
 
@@
 
-\subsection{Control of temperature in Nonequilibrium MD}\label{sec:tmp2b}
+\subsection{Control of temperature in nonequilibrium MD}\label{sec:tmp2b}
 
@@
   \caption{Schematic plot of the nonequilibrium temperature control scheme.
-    The white area is the region characterized by Hamiltonian dynamics without the direct action of an external thermostat.
-    The gray area is the region where the external thermostat is used in order to keep the target temperature.
-    $R_{ex}$ denotes the size of the Hamiltonian dynamics region, which
-    is a sphere at the center of the box.
-    The whole system is subject to the periodic boundary conditions. }
+    The white area is the region characterized by pure dynamics without any direct action by the external thermostat.
+    The gray area is the region where the thermostat is used to keep the target temperature.
+    $R_{ex}$ denotes the size of the purely dynamical region, which
+    is a sphere around the molecule of interest (in our case it is the alanine
+    dipeptide).
+    % at the center of the box.
+    The whole system is subject to periodic boundary conditions. }
   \label{fig:tmp2}
@@
 becomes an important issue; in fact it was argued that  an
-accurate control of the internal reaction temperature is essential for being able to
+accurate control of the internal reaction temperature is essential to
 perform reproducible experiments~\cite{damm2012can}.
@@
 physical properties of interest.
-
-As it is well known, in MD, for equilibrium situations, the solution is to couple
-the system to a an external thermostat, under which the desired ensemble
+In MD, for equilibrium situations, the solution is to couple
+the system to an external thermostat, under which the desired ensemble
 (canonical in this case) can be
@@
 conditions.
-However, coupling the system to a thermostat for nonequilibrium situations is a delicate issue.
-In fact, since a thermostat is explicitly designed to bring the system into equilibrium, any perturbation produced by the EF would be mostly adsorbed by the thermostat.
-This means that the physics of the original Hamiltonian dynamics with the EF would be lost and the response to the perturbation becomes unphysical.
+However, coupling the system to a thermostat for nonequilibrium situations is a more delicate issue.
+In fact, since a thermostat is explicitly designed to bring the system into
+thermal equilibrium,
+the perturbation produced by the EF would be mostly adsorbed by the thermostat. This means that the physics of the original dynamics in presence of the EF
+would be lost and the response to the perturbation would be unphysical. 
 %will disturb the original Hamiltonian dynamics. This is
@@
 % a effects in the nonequilibrium observations.
+
 In this section we propose a procedure to solve the problem: we
-observe the Hamiltonian dynamics (without thermostat) of the alanine 
-itself and the water molecules in the closer solvation shells is
-crucial, in order to determine the response of the observable of interest
-under the perturbation of the EF (in this work, it is the conformational change of alanine).
+start observing that the dynamics without thermostat of the alanine, 
+and the water molecules in the closer solvation shells, is
+crucial to determine the response of the observable of interest
+under the EF perturbation
+(in this work, the observable is the conformational change of alanine).
 Instead the detailed dynamics of
-the water molecules far away is not of primary importance, that is the region beyond the first solvation shells plays the role of a thermodynamic bath only. 
+the water molecules far away is not of primary importance: the region beyond the first solvation shells plays mainly the role of a thermodynamic bath. 
 Therefore, instead of simulating an infinitely
-large system, we only simulate a finite size system with periodic
-boundary condition with the following characteristics. The simulating region is divided in two
-subregions: a spherically defined region around the alanine dipeptide, centered at the
-alpha-carbon of radius $R_{ex}$. Here the dynamics is
-Hamiltonian and molecules are not subject to a thermostat; we refer to such subregion as \emph{the Hamiltonian dynamics
-region}. Instead beyond $R_{ex}$, the dynamics of water is coupled
-to a Langevin thermostat, and this region is called \emph{the thermostated
-region} (see Fig.~\ref{fig:tmp2}). For technical convenience we
+large system, we simulate our finite size system with periodic
+boundary condition, and with the following characteristics:
+(i)~The simulating region is divided in two
+subregions, a spherical region around the alanine dipeptide of radius $R_{ex}$,
+centered at the alpha-carbon. Here the dynamics is
+not subject to a thermostat.
+We refer to such subregion as \emph{the  dynamical
+region}. (ii)~Beyond $R_{ex}$, the dynamics of the water molecules is coupled
+to a Langevin thermostat.  This region is called \emph{the thermostated
+region}. For technical convenience we
 fix the position of the alpha-carbon in space, so that the alanine is always
-located at the center of the simulation region.
-Therefore, a realistic nonequilibrium  dynamics is preserved in the Hamiltonian dynamics region (where the properties of interest are observed)
-and possible direct artificial effects of the thermostating process in the region outside are negligible because of the finite correlation
+located at the center of the simulation region (see Fig.~\ref{fig:tmp2}).
+In these conditions, the  dynamics is preserved in the dynamical region (where the properties of interest are observed), while 
+possible artificial effects of the thermostating process in the outside region
+are negligible due to the finite correlation
 range of liquid water.
@@
 The validity of the above
-statement will be later on carefully checked by a series of numerical tests where it is shown that
+statement will be checked by a series of numerical tests where it is shown that
 the response of observables in nonequilibrium (i.e. under the effect of the EF) does not depend on the size of the system
-and on the size of the Hamiltonian dynamics subregion, provided that they are
+and on the size of the  dynamical subregion, provided that they are
 reasonably large.
@@
 
-\section{Example I: Alanine dipeptide
+\section{Case I: Alanine dipeptide
   under a uniform  constant EF}
@@
 \subsection{System settings and simulation protocol}
-At time $t=0$~ps, the system
-has been fully equilibriated without any EF. From $t=0$ to
-the warm-up time $t=t_{\textrm{warm}}$, the eclectic field is switched on linearly, while
-after $t=t_{\textrm{warm}}$, the field is kept constant in time at
-$E_{\infty}$.  In this work we consider $t_{\textrm{warm}} = 10$~ps,
-and $E_{\infty} = 1$~V/nm.
-The direction of the field is arbitrarily chosen along the
-$x$ direction, in fact the dipole of the equilibrium configurations of
-alanine can be along any direction.
-In this paper we denote the
-EF as a function of time $\vect E(t)$.
-Therefore, the constant EF is
-$\vect E(t) = (E_\infty\cdot t/t_{warm},0,0)$ as $0\leq t < t_{warm}$, and 
-$\vect E(t) = (E_\infty,0,0)$
-as $t \geq t_{warm}$.
 The system is set up in a $2.7\times 2.7\times
 2.7\, \textsf{nm}^3$ periodic simulation region, with one alanine dipeptide
-described by the CHARMM27 force field, and solved in 644 TIP3P
+described by the CHARMM27 force field, and dissolved in 644 TIP3P
 water molecules.
@@
 %the partial charge $q$ in the system.
-The size of the  Hamiltonian dynamics region is $R_{ex} = 1.0$~nm.
+The size of the  dynamical region is $R_{ex} = 1.0$~nm.
 All simulations are performed by a home-modified GROMACS 4.5~\cite{pronk2013gromacs}.
@@
 coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
-The whole system is also coupled to a Parrinello-Rahman barostat with $\tau_P = 2.0~\textsf{ps}$ to keep
-the pressure at the ambient condition (1~Bar). Since the
+The whole system is also coupled to a Parrinello-Rahman barostat~\cite{parrinello1981polymorphic} with $\tau_P = 2.0~\textsf{ps}$ to keep
+the pressure at ambient condition (1~Bar). Since the
 change of the system size is small and slow, the pressure control
@@
 dynamics of the system.
+At time $t=0$~ps, the system
+has been fully equilibrated without any EF. From $t=0$ to
+the warm-up time $t=t_{\textrm{warm}}$, the EF is switched on linearly, while
+after $t=t_{\textrm{warm}}$, the field is kept constant in time at
+$E_{\infty}$.  In this work we consider $t_{\textrm{warm}} = 10$~ps,
+and $E_{\infty} = 1$~V/nm.
+The direction of the field is arbitrarily chosen along the
+$x$ direction.
+In this paper we denote the
+EF as a function of time $\vect E(t)$.
+Therefore, for the case of constant EF, we have
+$\vect E(t) = (E_\infty\cdot t/t_{warm},0,0)$ for $0\leq t < t_{warm}$, and 
+$\vect E(t) = (E_\infty,0,0)$
+for $t \geq t_{warm}$.
 
@@
     state at $t=1000$~\textsf{ps}, i.e., fully relaxed under the
-    action of a constant EF of 1~V/nm. The darker color
+    action of a constant EF of 1~V/nm.  Darker color
     indicates higher probability.}
@@
 
-\begin{thebibliography}{10}
-
-\bibitem{bohr2000microwave}
-Henrik Bohr and Jakob Bohr.
-\newblock Microwave-enhanced folding and denaturation of globular proteins.
-\newblock {\em Physical Review E}, 61(4):4310, 2000.
-
-\bibitem{bohr2000microwave-1}
-Henrik Bohr and Jakob Bohr.
-\newblock Microwave enhanced kinetics observed in ord studies of a protein.
-\newblock {\em Bioelectromagnetics}, 21(1):68--72, 2000.
-
-\bibitem{dePomerai2000cell}
-David de~Pomerai, Clare Daniells, Helen David, Joanna Allan, Ian Duce, Mohammed
-  Mutwakil, David Thomas, Phillip Sewell, John Tattersall, Don Jones, and Peter
-  Candido.
-\newblock Cell biology: Non-thermal heat-shock response to microwaves.
-\newblock {\em Nature}, 405:417--418, 2000.
-
-\bibitem{inskip2001cellular}
-Peter~D Inskip, Robert~E Tarone, Elizabeth~E Hatch, Timothy~C Wilcosky,
-  William~R Shapiro, Robert~G Selker, Howard~A Fine, Peter~M Black, Jay~S
-  Loeffler, and Martha~S Linet.
-\newblock Cellular-telephone use and brain tumors.
-\newblock {\em New England Journal of Medicine}, 344(2):79--86, 2001.
-
-\bibitem{mancinelli2004non}
-Fabrizio Mancinelli, Michele Caraglia, Alberto Abbruzzese, Guglielmo
-  d'Ambrosio, Rita Massa, and Ettore Bismuto.
-\newblock Non-thermal effects of electromagnetic fields at mobile phone
-  frequency on the refolding of an intracellular protein: Myoglobin.
-\newblock {\em Journal of cellular biochemistry}, 93(1):188--196, 2004.
-
-\bibitem{budi2005electric}
-A.~Budi, F.S. Legge, H.~Treutlein, and I.~Yarovsky.
-\newblock Electric field effects on insulin chain-b conformation.
-\newblock {\em The Journal of Physical Chemistry B}, 109(47):22641--22648,
-  2005.
-
-\bibitem{budi2007effect}
-A.~Budi, F.S. Legge, H.~Treutlein, and I.~Yarovsky.
-\newblock Effect of frequency on insulin response to electric field stress.
-\newblock {\em The Journal of Physical Chemistry B}, 111(20):5748--5756, 2007.
-
-\bibitem{budi2008comparative}
-Akin Budi, F~Sue Legge, Herbert Treutlein, and Irene Yarovsky.
-\newblock Comparative study of insulin chain-b in isolated and monomeric
-  environments under external stress.
-\newblock {\em The Journal of Physical Chemistry B}, 112(26):7916--7924, 2008.
-
-\bibitem{toschi2008effects}
-Francesca Toschi, Francesca Lugli, Fabio Biscarini, and Francesco Zerbetto.
-\newblock Effects of electric field stress on a $\beta$-amyloid peptide.
-\newblock {\em The Journal of Physical Chemistry B}, 113(1):369--376, 2008.
-
-\bibitem{astrakas2011electric}
-Loukas Astrakas, Christos Gousias, and Margaret Tzaphlidou.
-\newblock Electric field effects on chignolin conformation.
-\newblock {\em Journal of Applied Physics}, 109(9):094702--094702, 2011.
-
-\bibitem{astrakas2012structural}
-Loukas~G Astrakas, Christos Gousias, and Margaret Tzaphlidou.
-\newblock Structural destabilization of chignolin under the influence of
-  oscillating electric fields.
-\newblock {\em Journal of Applied Physics}, 111(7):074702--074702, 2012.
-
-\bibitem{damm2012can}
-Markus Damm, Christoph Nusshold, David Cantillo, Gerald~N Rechberger, Karl
-  Gruber, Wolfgang Sattler, and C~Oliver Kappe.
-\newblock Can electromagnetic fields influence the structure and enzymatic
-  digest of proteins? a critical evaluation of microwave-assisted proteomics
-  protocols.
-\newblock {\em Journal of proteomics}, 75:5533--5543, 2012.
-
-\bibitem{starzyk2013proteins}
-A.~Starzyk and M.~Cieplak.
-\newblock Proteins in the electric field near the surface of mica.
-\newblock {\em The Journal of Chemical Physics}, 139:045102, 2013.
-
-\bibitem{english2009nonequilibrium}
-N.J. English, G.Y. Solomentsev, and P.~O'Brien.
-\newblock Nonequilibrium molecular dynamics study of electric and low-frequency
-  microwave fields on hen egg white lysozyme.
-\newblock {\em The Journal of chemical physics}, 131:035106, 2009.
-
-\bibitem{solomentsev2012effects}
-G.Y. Solomentsev, N.J. English, and D.A. Mooney.
-\newblock Effects of external electromagnetic fields on the conformational
-  sampling of a short alanine peptide.
-\newblock {\em Journal of Computational Chemistry}, 33:917--923, 2012.
-
-\bibitem{ciccotti1975direct}
-G~Ciccotti and G~Jacucci.
-\newblock Direct computation of dynamical response by molecular dynamics: The
-  mobility of a charged lennard-jones particle.
-\newblock {\em Physical Review Letters}, 35(12):789, 1975.
-
-\bibitem{ciccotti1979thought}
-G.~Ciccotti, G.~Jacucci, and I.R. McDonald.
-\newblock "thought-experiments" by molecular dynamics.
-\newblock {\em Journal of Statistical Physics}, 21(1):1--22, 1979.
-
-\bibitem{orlandini2011hydrodynamics}
-S.~Orlandini, S.~Meloni, and G.~Ciccotti.
-\newblock Hydrodynamics from statistical mechanics: combined dynamical-nemd and
-  conditional sampling to relax an interface between two immiscible liquids.
-\newblock {\em Phys. Chem. Chem. Phys.}, 13:13177--13181, 2011.
-
-\bibitem{orlandini2011hydrodynamics-01}
-Sergio Orlandini, Simone Meloni, and Giovanni Ciccotti.
-\newblock Hydrodynamics from dynamical non-equilibrium md.
-\newblock In {\em AIP Conference Proceedings}, volume 1332, page~77, 2011.
-
-\bibitem{delaHoz2005microwaves}
-Antonio de~la Hoz, Angel Diaz-Ortiz, and Andres Moreno.
-\newblock Microwaves in organic synthesis. thermal and non-thermal microwave
-  effects.
-\newblock {\em Chemical Society Reviews}, 34(2):164--178, 2005.
-
-\bibitem{pronk2013gromacs}
-S.~Pronk, S.~P{\'a}ll, R.~Schulz, P.~Larsson, P.~Bjelkmar, R.~Apostolov, M.R.
-  Shirts, J.C. Smith, P.M. Kasson, D.~van~der Spoel, and Hess B.~Lindahl E.
-\newblock Gromacs 4.5: a high-throughput and highly parallel open source
-  molecular simulation toolkit.
-\newblock {\em Bioinformatics}, pages 1--10, 2013.
-
-\bibitem{schuette2011markov}
-C.~Sch{\"u}tte, F.~No{\'e}, J.~Lu, M.~Sarich, and E.~Vanden-Eijnden.
-\newblock Markov state models based on milestoning.
-\newblock {\em The Journal of Chemical Physics}, 134:204105, 2011.
-
-\bibitem{bohner2012algorithm}
-Matthias~U Bohner and Johannes K{\"a}stner.
-\newblock An algorithm to find minimum free-energy paths using umbrella
-  integration.
-\newblock {\em The Journal of Chemical Physics}, 137:034105, 2012.
-
-\bibitem{seifert2010fluctuation}
-U.~Seifert and T.~Speck.
-\newblock Fluctuation-dissipation theorem in nonequilibrium steady states.
-\newblock {\em EPL (Europhysics Letters)}, 89:10007, 2010.
-
-\bibitem{scovell2000phase}
-Dawn~L Scovell, Tim~D Pinkerton, Valentin~K Medvedev, and Eric~M Stuve.
-\newblock Phase transitions in vapor-deposited water under the influence of
-  high surface electric fields.
-\newblock {\em Surface science}, 457(3):365--376, 2000.
-
-\bibitem{vogel2008femtosecond}
-A.~Vogel, N.~Linz, S.~Freidank, and G.~Paltauf.
-\newblock Femtosecond-laser-induced nanocavitation in water: implications for
-  optical breakdown threshold and cell surgery.
-\newblock {\em Physical review letters}, 100(3):38102, 2008.
-
-\bibitem{vitalini2013speed}
-F.~Vitalini, A.S.J.S. Mey, F.~No\'e, and B.G. Keller.
-\newblock The speed of force fields.
-\newblock {\em unpublished}, 2013.
-
-\end{thebibliography}
-
-% \bibliography{ref}{}
-% \bibliographystyle{unsrt}
+\bibliography{ref}{}
+\bibliographystyle{unsrt}
 

### 2013-11-09 writedown/npt-neq/alanine.tex
a lot of changes according to Giovanni.

@@
 the dynamical nonequilibrium molecular dynamics simulation (D-NEMD).
-The method, firstly developed by one of us and coworkers~\cite{ciccotti1975direct, ciccotti1979thought}, 
+The method, firstly developed by one of us and coworkers~\cite{ciccotti1975direct, ciccotti1979thought, ciccotti1993theoretical, palla2008bulk}, 
 has been recently applied, to the study of
@@
 the various methodology proposed here would be hampered for large molecules,
-although they remain our goal.
+although they \bluec{remain (\textit{does Giovanni write ``remain''? I cannot read})} our goal.
 
 The paper is organized as follows:
-We firstly describe the idea of D-NEMD, then
-introduce the physical
-observables chosen to analyze the nonequilibrium responses.
-The numerical results for the response of alanine
+\recheck{
+  We firstly describe the idea of D-NEMD, and a local thermostating method
+for nonequilibrium temperature control.
+% Then
+% introduce the physical
+% observables chosen to analyze the nonequilibrium responses.
+Then
+after introducing the physical
+observables chosen to analyze the nonequilibrium response,
+the numerical results for the response of alanine
 dipeptide under static and oscillatory EF are
-finally presented. By calculating the nonequilibrium properties from D-NEMD
+finally presented.} By calculating the nonequilibrium properties from D-NEMD
 simulations, we are able to address
@@
 time-dependent nonequilibrium w.r.t. conformation
-is explicitly considered for a large molecule
+is explicitly considered for a \bluec{large molecule \textit{what does Giovanni write here? For me, the alanine dipeptide molecule is NOT large at all!}}
 in solution subject to time-dependent EF.
@@
   \centering
-  \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{c-2.eps}}
-  \includegraphics[width=0.37\textwidth]{fig-begin-1.eps}
-  \includegraphics[width=0.37\textwidth]{fig-end-1.eps}
-  \caption{The probability of the conformations of the alanine dipeptide plotted on the Ramachandran histogram.
-    (a): the
-    equilibrium state at $t=0$~\textsf{ps}. (b): The new equilibrium
+  \includegraphics[width=1.00\textwidth]{fig-all-1.eps}
+  % \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{c-2.eps}}
+  % \includegraphics[width=0.37\textwidth]{fig-begin-1.eps}
+  % \includegraphics[width=0.37\textwidth]{fig-end-1.eps}
+  \caption{
+    \recheck{
+    The probability density of the conformations of the alanine dipeptide plotted on the Ramachandran plot.
+    (a): An alanine dipeptide molecule.  Two dihedral angles
+    $\phi$ and $\psi$ that are used to define the Ramachandran plot
+    are shown with the molecule.
+    (b): The equilibrium probability density on Ramachandran plot
+    at $t=0$~\textsf{ps}. (c): The probability density of the new equilibrium
     state at $t=1000$~\textsf{ps}, i.e., fully relaxed under the
     action of a constant EF of 1~V/nm.  Darker color
-    indicates higher probability.}
+    indicates higher probability.
+    The Ramachandran plots are divided into 5 subregions corresponding
+    to 5 molecular conformations:
+    $A_1 = \{(\phi, \psi) | -134 \leq \phi <  13, -125 \leq \psi < 74\}$,
+    $A_2 = \{(\phi, \psi) |  128 \leq \phi <-134, -125 \leq \psi < 74\}$,
+    $B_1 = \{(\phi, \psi) | -110 \leq \phi <  13,   74 \leq \psi <-125\}$,
+    $B_2 = \{(\phi, \psi) |  128 \leq \phi <-110,   74 \leq \psi <-125\}$,
+    $C   = \{(\phi, \psi) |   13 \leq \phi < 128, -180 \leq \psi < 180\}$.
+    Considering the periodic bondary condition, if we write, for example,
+    $128 \leq \phi <-134$, it means that $\phi$ is in either range
+    $128 \leq \phi < 180$ or in $-180 \leq \phi < -134$.
+    This division is the same for both plot (b) and (c).
+    }
+  }
   \label{fig:tmp4}
@@
 
-For each branching trajectory,  the molecular configuration of alanine is projected on
-the Ramachandran histogram, as
-shown in Fig.~\ref{fig:tmp4}. The equilibrium distribution of the
-conformations is given in plot (a), and the fully relaxed
-conformation under the action of $E_{\infty} = 1$~V/nm is given in plot (b).  It is
-evident from the plot that the conformations are grouped in several clusters, and the
-position of the clusters does not change when the external electric
-field is applied.
+\recheck{
+The time-dependent molecular conformations of alanine dipeptide are
+investigated by estimate the probability density $p(\phi,\psi,t)$ on
+the Ramachandran plot at time $t$. The definition of dihedral
+angles $\phi$ and $\psi$ are given in Fig.~\ref{fig:tmp4}~(a).
+The equilibrium probability density of
+the conformations on the Ramachandran plot
+is given in Fig.~\ref{fig:tmp4}~(b), and the fully
+relaxed probability of conformations under
+the action of $E_{\infty} = 1$~V/nm is
+given in Fig.~\ref{fig:tmp4}~(c).  It is evident from the plot that
+the probability density of conformations are grouped in several clusters,
 % {\bf LUIGI COMMENT: HAN below is really not clear}\\
@@
 % {\bf END COMMENT}\\
-For the sake of clarity, we divide the
-Ramachandran histogram into 5 subregions, see Fig.~\ref{fig:tmp4},
-then the analysis of conformations on the Ramachandran histogram is reduced to the
-analysis of the 5 ranges of conformations, i.e. $\{A_1, A_2, B_1, B_2, C\}$,
-or in short we call them conformations (the precise meaning is clear
-from the context).
-In this paper we use:
-$A_1 = \{(\phi, \psi) | -134 \leq \phi <  13, -125 \leq \psi < 74\}$,
-$A_2 = \{(\phi, \psi) |  128 \leq \phi <-134, -125 \leq \psi < 74\}$,
-$B_1 = \{(\phi, \psi) | -110 \leq \phi <  13,   74 \leq \psi <-125\}$,
-$B_2 = \{(\phi, \psi) |  128 \leq \phi <-110,   74 \leq \psi <-125\}$,
-$C   = \{(\phi, \psi) |   13 \leq \phi < 128, -180 \leq \psi < 180\}$.
-Considering the periodic bondary condition, if we write, for example,
-$128 \leq \phi <-134$, it means that $\phi$ is in either range
-$128 \leq \phi < 180$ or in $-180 \leq \phi < -134$.
+therefore, for the sake of clarity, we divide the
+Ramachandran histogram into 5 subregions $\{A_1, A_2, B_1, B_2, C\}$
+(see the caption of Fig.~\ref{fig:tmp4} for definition), and
+call each subregion, in short, a conformation of the alanine dipeptide. 
 These conformations
-correspond to different secondary structures of a peptide chain:
+are found in different secondary structures of a peptide chain:
 $A_1$ and $A_2$ are
-corresponding to the alpha helix. $B_1$ and $B_2$ are
-corresponding to the beta sheet. $C$ is corresponding to the
-left-handed alpha helix.
-
-From Fig.~\ref{fig:tmp4}, it is obvious that the population in each
-range of conformations changes when the external EF is applied.
-For instance, the population of conformation $C$ vanishes in equilibrium,
+corresponding to the $\alpha$-helix. $B_1$ and $B_2$ are
+corresponding to the $\beta$-sheet. $C$ is corresponding to the
+left-handed $\alpha$-helix.
+}
+% In the end,
+% the analysis of conformations on the Ramachandran plot is
+% reduced to the analysis of the 5 conformations.
+
+From Fig.~\ref{fig:tmp4}, it is obvious that the probability of
+conformations changes when the external EF is applied.
+For instance, the probability of conformation $C$ vanishes in equilibrium,
 but plays an important role when the EF is applied. We
@@
 the EF. 
-First, we calculate the probability of being in a certain conformation range,
-defined as:
+Firstly, we calculate the probability
+of each conformation:
 \begin{align}
@@
 % process considered by the present work, this relation is genarlly not guarenteed.
-Second,
+Secondly,
 we study the net probability flux from conformation $I$ to $J$, defined by:
@@
 \end{align}
+\recheck{Where $\mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I)$
+is joint probability of the alanine being of conformation $J$ at
+time $(t-\Delta t)$ \emph{and} being of conformation $I$ at time $t$.
+A similar definition applies to $\mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J)$.}
 Here the time interval $\Delta t$ should be small enough comparing with the
@@
 See also the discussions in Ref.~\cite{schuette2011markov}.
-$F_{J,I}(t)$ is essentially the rate of how much conformation $J$ changes
-into $I$ at time $t$. A positive value indicates the
+% \recheck{$F_{J,I}(t)$ is essentially the time-dependent rate of
+%   conformation change from $J$ to $I$.}
+A positive value \recheck{of $F_{J,I}(t)$} indicates the
 net flux from $J$ to $I$,
@@
 In the case of oscillatory EF, the net probability flux is also highly oscillatory,
-thus it is convenient to study the integrated probability flux:
-\begin{align}
+thus it is convenient to study the integrated net probability flux:
+\begin{align}\label{eqn:tmp7a}
   Q_{J,I} (t) = \int_0^t F_{J,I}(\tau)d \tau,
 \end{align}
-this expresses the average over time of the effects of the EF on the conformation of the molecule.
+\redc{this expresses the cumulative effects of the EF
+on the conformations of the molecule.}
 
@@
   \includegraphics[]{fig-meta-npt.eps}
-  \caption{The probability that the system is in the ranges of conformations when a constant EF is present.
-    The warm-up time is $t_{warm} = 10$~ps. The red line refers to conformation $A_1$,
+  \caption{\recheck{The time-dependent probability of conformations $P_I(t)$} 
+    when a constant EF is present.
+    The warm-up time is $t_{warm} = 10$~ps. The red line refers to conformation $I = A_1$,
     green to $A_2$, dark blue to $B_1$, purple to $B_2$ and light blue
-    to $C$.
+    to $C$. \recheck{Please notice that the summation of all conformational
+      probabilities
+    is identity, i.e.~$\sum_I P_I(t) = 1$.}
   }
@@
     The warm-up time is $t_{warm} = 10$~ps.
-    The first row shows the probability flux $F_{J,I}(t)$ in units of $\textrm{ps}^{-1}$, while the second
-    shows the integrated  probability flux denoted by $Q_{J,I}(t)$.
+    The first row shows the probability flux $F_{J,I}(t)$ (defined by Eqn.~\eqref{eqn:tmp7}) in units of $\textrm{ps}^{-1}$, while the second
+    shows the integrated  probability flux denoted by $Q_{J,I}(t)$ (defined by Eqn.~\eqref{eqn:tmp7a}).
     A constant $Q_{J,I}$ means vanishing net flux, while a increasing (decreasing)
@@
 
-The time-dependent probability of the system in a certain range of conformations is given in
-Fig.~\ref{fig:tmp5}. The beta sheet conformations $B_1$ and $B_2$,
+The time-dependent probability density of \bluec{the system \textit{what does Giovanni add here?} in} a certain
+conformation is given in
+Fig.~\ref{fig:tmp5}. The $\beta$-sheet conformations $B_1$ and $B_2$,
 which are present at the initial stage after EF is switched on,
 fade away as the system relaxes to the new equilibrium. The
-probability of alpha helix $A_1$ conformation grows from 0.45 to 0.69.
-Alpha helix $A_2$  does not change significantly  under the action of EF.
+probability of the $\alpha$-helix conformation $A_1$, grows from 0.45 to 0.69.
+The $\alpha$-helix $A_2$  does not change significantly  under the action of EF.
 The left-hand helix conformation $C$ noticeably grows from 0 to 0.22.
-
 We plot the net probability fluxes and their integration in Fig.~\ref{fig:tmp6}.
@@
 % {\bf END COMMENT}\\
+\recheck{
+Even though the system is finally relaxed to the new equilibrium,
+the timescale of relaxation of each conformation is different. 
+From Fig.~\ref{fig:tmp5} and \ref{fig:tmp6}, we observe mainly
+three different timescales 10~ps, 100~ps and 500~ps,
+as summarized in Tab.~\ref{tab:tmp1}.
+}
 
@@
 
-Even though the system is finally relaxed to the new equilibrium,
-the timescale of relaxation of each conformation is different. 
-From Fig.~\ref{fig:tmp6}, we observe mainly
-three different timescales, as summarized in Tab.~\ref{tab:tmp1}.
-(1) From
-$t=0$ to approximately 10~\textsf{ps}, a net flux from 
-$A_1$ to $A_2$ establishes.
-A similar flux is also observed from $B_1$ to $B_2$.
-Afterwards, these two fluxes vanish and are finally reversed,
-i.e. $A_2$ to $A_1$ and $B_2$ to $B_1$, respectively.
-% the population of $A_1$ firstly decreases and then increases to the original value,
-% while the population of $A_2$ increases sharply. The plot of the net probability flux shows that 
-% there is firstly a fast probability flux (conformational change) from
-% $A_1$ to $A_2$, and then follows a probability flux with the same maganitude in the opposite direction, i.e.  from
-% $A_2$ to $A_1$.
-Moreover, a net flux from all $\beta$-sheet conformations
-($B_1$ and $B_2$) into $\alpha$-helix conformations ($A_1$, $A_2$ and
-$C$) has been established.
-% Also in this time-scale, strong and increasing probability flux from $B_2$ to $B_1$ is observed from Fig.~\ref{fig:tmp6}.
-% The population of $B_1$ remains almost unchanged,
-% because it  at the same time loses population to $\alpha$-helix conformations.
-% Since  $B_2$ conformations not only changes into $B_1$, but also into $\alpha$-helix conformations, we observe a charp
-% decrease of $B_2$ population between 10 and 20~ps.
-(2), From $t=10$ to
-100~\textsf{ps},
-The net flux from  conformation $A_2$ to $A_1$ and from $B_2$ to $B_1$
-gradually decays to 0. Conformational changes from $B_2$ to $A_1$, $A_2$ and $C$
-vanishes in about 50~ps.
-% The net flux from $B_1$  to $A_1$ and $C$ decay slower and 
-% will be discussed later.
-At this stage, the probability of $B_2$ decreases to almost 0,
-while the probability of $A_2$
-converge to a non-vanishing value of approximately 0.06.
-% the population of $B_2$ decreases by 0.15, and this
-% configuration almost disappears. Interestingly, the population of $A_1$
-% increases by the same amount, and the population of $A_2$ goes back to
-% the initial value. The populations of $B_1$ and $C$ start increasing
-% and decreasing, correspondingly. The speed of these changes are much
-% slower than that of $B_2$ and $A_1$.
-(3) At the time scale of $
-500~\textsf{ps}$, the population of $A_1$, $B_1$ and $C$ converge to
-the new equilibrium (system with $E(\infty) = 1~\textsf{V/m}$).
-We observe a decaying probability flux from $B_1$ 
-to $A_1$ and $C$.
-The magnitude of the flux from $B_1$ to  $C$ is larger than that of $B_1$ to  $A_1$.
-% It is interesting to see that at nonequilibrium steady state, $A_1$ exchange
-% population with $A_2$, and $B_1$ exchange
-% population with $B_2$. However, when the $C$ conformation hardly changes
-% to any other conformation, as indicated by the almost 1 value of the forward
-% transition probability of set $C$. This implies that at the left-handed $\alpha$-helix is
-% acutally more stable than  other conformations.
-This time-scale is actually 50 times slower than that, at which
-the EF was switched on ($t_{\textrm{warm}} = 10~\textsf{ps}$).
+% Even though the system is finally relaxed to the new equilibrium,
+% the timescale of relaxation of each conformation is different. 
+% From Fig.~\ref{fig:tmp6}, we observe mainly
+% three different timescales, as summarized in Tab.~\ref{tab:tmp1}.
+% (1) From
+% $t=0$ to approximately 10~\textsf{ps}, a net flux from 
+% $A_1$ to $A_2$ establishes.
+% A similar flux is also observed from $B_1$ to $B_2$.
+% Afterwards, these two fluxes vanish and are finally reversed,
+% i.e. $A_2$ to $A_1$ and $B_2$ to $B_1$, respectively.
+% % the population of $A_1$ firstly decreases and then increases to the original value,
+% % while the population of $A_2$ increases sharply. The plot of the net probability flux shows that 
+% % there is firstly a fast probability flux (conformational change) from
+% % $A_1$ to $A_2$, and then follows a probability flux with the same maganitude in the opposite direction, i.e.  from
+% % $A_2$ to $A_1$.
+% Moreover, a net flux from all $\beta$-sheet conformations
+% ($B_1$ and $B_2$) into $\alpha$-helix conformations ($A_1$, $A_2$ and
+% $C$) has been established.
+% % Also in this time-scale, strong and increasing probability flux from $B_2$ to $B_1$ is observed from Fig.~\ref{fig:tmp6}.
+% % The population of $B_1$ remains almost unchanged,
+% % because it  at the same time loses population to $\alpha$-helix conformations.
+% % Since  $B_2$ conformations not only changes into $B_1$, but also into $\alpha$-helix conformations, we observe a charp
+% % decrease of $B_2$ population between 10 and 20~ps.
+% (2), From $t=10$ to
+% 100~\textsf{ps},
+% The net flux from  conformation $A_2$ to $A_1$ and from $B_2$ to $B_1$
+% gradually decays to 0. Conformational changes from $B_2$ to $A_1$, $A_2$ and $C$
+% vanishes in about 50~ps.
+% % The net flux from $B_1$  to $A_1$ and $C$ decay slower and 
+% % will be discussed later.
+% At this stage, the probability of $B_2$ decreases to almost 0,
+% while the probability of $A_2$
+% converge to a non-vanishing value of approximately 0.06.
+% % the population of $B_2$ decreases by 0.15, and this
+% % configuration almost disappears. Interestingly, the population of $A_1$
+% % increases by the same amount, and the population of $A_2$ goes back to
+% % the initial value. The populations of $B_1$ and $C$ start increasing
+% % and decreasing, correspondingly. The speed of these changes are much
+% % slower than that of $B_2$ and $A_1$.
+% (3) At the time scale of $
+% 500~\textsf{ps}$, the population of $A_1$, $B_1$ and $C$ converge to
+% the new equilibrium (system with $E(\infty) = 1~\textsf{V/m}$).
+% We observe a decaying probability flux from $B_1$ 
+% to $A_1$ and $C$.
+% The magnitude of the flux from $B_1$ to  $C$ is larger than that of $B_1$ to  $A_1$.
+% % It is interesting to see that at nonequilibrium steady state, $A_1$ exchange
+% % population with $A_2$, and $B_1$ exchange
+% % population with $B_2$. However, when the $C$ conformation hardly changes
+% % to any other conformation, as indicated by the almost 1 value of the forward
+% % transition probability of set $C$. This implies that at the left-handed $\alpha$-helix is
+% % acutally more stable than  other conformations.
+% This time-scale is actually 50 times slower than that, at which
+% the EF was switched on ($t_{\textrm{warm}} = 10~\textsf{ps}$).
 
@@
 
-The Fig.~\ref{fig:tmp3}
-shows that the $x$-component of the dipole moment of the alanine dipeptide
+\redc{The dipole momenet of alanine dipeptide is defined by
+\begin{align}\label{eqn:tmp8}
+  \boldsymbol\mu_{\textrm{alanine}}(t) =
+  \bigg\langle
+  \sum_{i\in \{\textrm{atoms of alanine}\}}
+  q_i\, \vect r_i(t)
+  \bigg\rangle,
+\end{align}
+where $q_i$ denotes the partial charge of an atom $i$ on the alanine,
+and the molecule is neutral, i.e.~$\sum_iq_i = 0$.
+$\vect r_i$ denotes the position of the atom $i$.}
+Fig.~\ref{fig:tmp3}
+shows that the $x$-component of the dipole moment 
 reaches 85\% of the maximum value in only 20~ps, which is comparable to
@@
 maximum value, that is, 
-6.8~Debye, and  corresponds to a dipole energy of ca. $-13.6$~kJ/mol.
+6.8~Debye, and  corresponds to a dipole energy
+\redc{$\boldsymbol\mu_{\textrm{alanine}} \cdot \vect E$}
+of c.a.~$-13.6$~kJ/mol.
 We calculate the averaged dipole moment of different conformations
+\redc{(defined by taking averge in Eqn.~\eqref{eqn:tmp8}
+only for a certain conformation)}
 under the constant EF, and they are 6.8, 6.0, 5.1, 3.1 and 7.1~Debye
@@
 The dipole energy difference between 3.1 and 7.1~Debye is roughly 8.0~kJ/mol.
-The free energy barriers between the
-conformations were reported to be of order $20\sim 40$~kJ/mol~\cite{bohner2012algorithm},
-which is comparable to the dipole energy difference. 
+\recheck{NOTE by Han: \textit{
+    I removed the discussion of the free energy barrier.}}
+% The free energy barriers between the
+% conformations were reported to be of order $20\sim 40$~kJ/mol~\cite{bohner2012algorithm},
+% which is comparable to the dipole energy difference. 
 Therefore, under a constant EF, the system will be driven towards those
@@
 to the nonequilibrium steady value.
+
 \subsection{Response of the orientational order parameter}
 
-We also consider the orientation of the alanine dipeptide in space (w.r.t.~the direction of EF) as a function
-of time.
-The geometric direction of the alanine is defined by the red vector in
-Fig.~\ref{fig:tmp3}, which is the angle bisector of the two black vectors.
-The black vectors are defined in such a way that they connect the $\alpha$-carbon and the carbons
-on the methyl groups. We define the orientational order parameter by
+Let us define
+the geometric direction of the alanine by the red vector in
+Fig.~\ref{fig:tmp3}, i.e.~by the angle bisector of the two black vectors,
+which connect the $\alpha$-carbon and the carbons
+on the methyl groups. 
+We considered the angle $\theta$ made by 
+the orientation of the alanine dipeptide in space w.r.t.~the direction of EF
+as a function of time.
+Then we defined the orientational order parameter 
 \begin{align}
@@
 \end{align}
-where $\theta$ is the angle between the orientation of the alanine dipeptide
-and the direction of the EF.
 The ensemble average is taken over the trajectory ensemble, so it is
@@
 The order parameter
-indicates how perpendicular the molecule lies w.r.t.~the EF.
+indicates where lies \bluec{in time average \textit{(is it correct?)}} the molecule w.r.t.~the EF.
 If the molecule is perfectly perpendicular to the EF, then $S_\theta = 1$.
 If the molecule has no directional
-preference, then $S_\theta = 0$.
+preference, then $S_\theta = 0$. \bluec{\textit{What does Giovanni's comment mean here?}}
 If the molecule lies perfectly parallel to the EF, then $S_\theta = -2$.
@@
 Then from $t=0$ to 500~ps, the molecule slowly changes to the orientation
-that is perpendicular to the EF.
+that is perpendicular to the EF. \bluec{\textit{I do not know how to explain here...}}
 This orientational change is linked to the observed slowest
@@
 
-\subsection{Effects of EF on the solvant around the molecule}
+\subsection{Effects of EF on the solvent around the molecule}
 % This indicate that when the EF is switched on, the alanine almost immediately
@@
   \includegraphics[width=0.48\textwidth]{fig-hbond.eps}
-  \caption{The solvent structure around the alanine dipeptide.  Plot
+  \caption{The solvent structure around the alanine dipeptide.  
     (a): the radial distribution function (RDF) between the
     $\alpha$-carbon and the center-of-mass (COM) of the water molecules at
-    $t = 0$, 10, 100 and 1000~ps.  Plot (b): the number of hydrogen
+    $t = 0$, 10, 100 and 1000~ps.  (b): the number of hydrogen
     bonds formed between the alanine and water, and between two water
@@
     molecules is normalized by the number of water molecules in the
-    system.}
+    system. 
+  }
   \label{fig:tmp7a}
@@
 We study the solvent effect on the alanine dipeptide in the presence of the EF by investigating
-the radial distribution function between $\alpha$-carbon and the
+the radial distribution function (RDF) between $\alpha$-carbon and the
 center-of-mass (COM) of the water molecules
-(see Fig.~\ref{fig:tmp7a}).
-The average, relative position of the COM of water molecules measured w.r.t.~the alanine does not change significantly as a function of time (within the statistical error).
-Plot (b) of
-Fig.~\ref{fig:tmp7a} presents the number of hydrogen bonds between the
-alanine and water molecules, and between two water molecules. We see that the
-number hydrogen bonds remains almost the as the EF is turned on,
+(see Fig.~\ref{fig:tmp7a}). The average
+RDF does not change significantly as a function of time
+(within the statistical error). 
+Fig.~\ref{fig:tmp7a}~(b) presents the number of hydrogen bonds between the
+alanine and water molecules, and between two water molecules.
+\recheck{The hydrogen bonds are calculated by standard GROMACS
+routine {\texttt {g\_hbond}}, with donor-acceptor distance cut-off 0.3~nm,
+and hydrogen-donor-acceptor angle cut-off $20^{\circ}$.}
+We see that the
+number of hydrogen bonds remains almost the same as the EF is turned on,
 although molecular dipoles tend to align with the direction of the EF (result
@@
 difference of the water-alanine electrostatic interaction 
-between systems without and with the EF.
+without and with the EF.
 The energy difference is found to be $-19.1$~~kJ/mol that is
@@
 Therefore, we conclude that the solvation structure around the
-alanine does not change significantly or contribute significantly in determining the conformational dynamics of the alanine under the action of EF.
-
-\subsection{The finite-size effect of the Hamiltonian dynamics and thermostated regions}
+alanine does not change or contribute significantly in determining the conformational dynamics of the alanine under the action of EF.
+
+\subsection{The finite-size effect on the dynamical and thermostated regions}
 
@@
   \includegraphics[]{fig-meta-conv.eps}
-  \caption{Testing the finite-size effect of the Hamiltonian dynamics and thermostated region.
-    Probabilities of different ranges of conformations are presented as a function of time.
+  \caption{Testing the finite-size effect on the dynamical and thermostated region.
+    Probabilities of different conformations are presented versus time.
     See the text for more details.
@@
 
-Just as described in Sec.~\ref{sec:tmp2b}, we perform nonequilibrium MD
-simulations in a finite size periodic system, and further divided it
-into a Hamiltonian dynamics region and a thermostated region.
+Just as described in Sec.~\ref{sec:tmp2b}, we performed nonequilibrium MD
+simulations in a finite size periodic system, further divided it
+into a dynamical and a thermostated region.
 Since the periodic boundary conditions and the division of the system
-are technical (not physical) approximations to the real system with dynamics-preserving thermal control, 
+are technical approximations to the real system with dynamics-preserving thermal control, 
 the effect of the finite-size in 
@@
 Therefore, we
-perform two additional simulations: one with box dimension $L=4.0$~nm (box size on all directions are the same) and a
-Hamiltonian dynamics region of radius $R_{ex} = 1.0$~nm. A second simulation is done with box size $L=4.0$~nm and a Hamiltonian dynamics region of
+perform two additional simulations: one with box dimensions
+$L=4.0$~nm (the box is cubic) and a
+Hamiltonian dynamical region of radius $R_{ex} = 1.0$~nm. A second simulation is done with box size $L=4.0$~nm and a dynamical region of
 radius $R_{ex} = 1.5$~nm. We compare the results of these two simulations to those of the system we have used so far, i.e. $L=2.7$~nm and $R_{ex} = 1.0$~nm.
-Fig.~\ref{fig:tmp7} presents a satisfactory consistency in
-the simulation results of the three systems, which implies that the finite-size effects are
-actually negligible.
-
-\section{Example II:
+Fig.~\ref{fig:tmp7} shows essential consistency in
+the simulation results for the three systems. The finite-size effects are
+negligible.
+
+\section{Case II:
   periodically oscillatory EF}
+\bluec{\textit{what does he add besides the caption of the section?}}
 
@@
 \begin{align}
-  \vect E(t) = (E_0\sin(2\pi \omega t), 0, 0)
+  \vect E(t) = (E_0\sin(2\pi t / T), 0, 0)
 \end{align}
 where $E_0$ is the intensity of the field, which is chosen to be
-1.0~V/nm.  $\omega$ is the oscillating frequency, which is related to
-the period $T$ by $\omega = 1/T$.  Here we tested three different
-values of $T$: 10, 40 and 200, which correspond
-to frequency of 100, 25 and 5~GHz, respectively.
+1.0~V/nm.  $T$ is the oscillating period.
+Here we tested three different
+periods 10, 40 and 200~ps.
 % The periods of the later two are
@@
   \caption{Illustration of the effect of the oscillatory EF:
-    the dipole moment (a) and
-    orientation order parameter (b) of alanine dipeptide as a
-    function of time. In plot (a),
+    the dipole moment (a) and the
+    orientational order parameter (b) of alanine dipeptide as a
+    function of time. In (a),
     only the $x$-component of the dipole moment is
     shown. The black line refers to the static EF with turning on
-    time $t_{warm} = 10$~ps. The red line refers to the oscillatory field with period
-    10~ps, while the green line is for a period of 40~ps and the blue for 200~ps.}
+    time $t_{warm} = 10$~ps. The red line refers to the oscillatory field with period of
+    10~ps. The green line is of 40~ps; and the blue of 200~ps.}
   \label{fig:tmp8}
@@
 % constant EF case.
-Plot (b) of Fig.~\ref{fig:tmp9} presents the orientational order
-parameter. The notations are the same as in plot (a).
+Fig.~\ref{fig:tmp9}~(b) presents the orientational order
+parameter. The notations are the same as Fig~\ref{fig:tmp9}~(a).
 % From the constant
@@
 smaller than in the case of constant EF. One possible reason is that the
-relaxation of the order parameter is very slow, and the molecule in case of oscillatory field is
-not exposed to a strong enough EF for a long enough. For  $T=10$ and 40~ps, the orientation of the alanine is only weakly
-parallel to the EF. It is worth to notice that for the case of constant EF,
+relaxation of the order parameter is very slow, and the molecule in the case of oscillatory field is
+not exposed to a strong enough EF for a long enough.
+\bluec{\textit{I cannot read and understand Giovanni's comment referring here on the top of this page.}}
+For  $T=10$ and 40~ps, the orientation of the alanine is only weakly
+parallel to the EF. It is worth to notice that for constant EF,
 we also observe a quick alignment of molecular orientation to the EF
-on the time scale of 10~ps. For $T=200$~ps, The molecule periodically
-becomes perpendicular to the EF, but this directional preference is much
+on the time scale of 10~ps. For $T=200$~ps, the molecule periodically
+becomes \recheck{weakly} perpendicular to the EF, but this directional preference is much
 weaker than the case of constant EF.
@@
   % \includegraphics[width=0.49\textwidth]{fig-meta-mode2-2000.eps}
-  \caption{ The probability of being in a certain range of conformations for
+  \caption{
+    \bluec{\textit{what is the comment on the top of page 17?}}
+    The probability of being in a certain of conformation for
     periodically oscillatory EF. Different periods,
     i.e. $T=10$~ps, 40~ps and 200~ps, are presented here.  The
-    probability of being in a certain conformation range $I$, which is
+    probability of being in a certain conformation $I$, which is
     denoted by $P_I$ in this paper, is plotted by colored lines against
-    time. The red line: $I = A_1$, the green line: $I = A_2$, the dark
-    blue line: $I = B_1$, the pink line: $I = B_2$ and the light blue
+    time. Red line: $I = A_1$,  green line: $I = A_2$,  dark
+    blue line: $I = B_1$,  pink line: $I = B_2$ and  light blue
     line: $I = C$. For $T=10$~ps and 40~ps, the nonequilibrium
-    simulations of time 1000~ps are presented, while for $T=200$~ps,
-    nonequilibrium simulations of time 3200~ps is presented.  }
+    simulations last 1000~ps, while for $T=200$~ps,
+    they last 6400~ps.  }
   \label{fig:tmp9}
@@
     probability flux is defined by $Q_{J,I}(t) = \int_0^t F_{J,I}(\tau) d\tau$, where
-    $F(t)$ is the net probability flux from conformation $I$ to $J$.
+    $F_{J,I}(t)$ is the net probability flux from conformation $J$ to $I$.
+    See also Eqn.~\eqref{eqn:tmp7} and~\eqref{eqn:tmp7a} for definitions
+    of $F_{J,I}(t)$ and $Q_{J,I}(t)$, respectively.
     From up to down, rows report results with  period 10, 40 and 200~ps, respectively.
@@
     the red line stands for $J=A_1$, green for $J=A_2$, dark blue for $J=B_1$,
-    purple for $J=B_2$ and light blue for $J=C$. In a certain time interval,
-    if the integrated flux $Q_{J,I}$ increases, there exists a (time-averaged)
-    non-zero net flux from conformation $I$ to $J$.
+    purple for $J=B_2$ and light blue for $J=C$.
+    \recheck{An increaseing $Q_{J,I}$ indicates a net probability
+      flux from conformation $J$ to $I$,
+      while a decreaseing $Q_{J,I}$ indicates a net probability
+      flux from $I$ to $J$.
+    }
+    % In a certain time interval,
+    % if the integrated flux $Q_{J,I}$ increases, there exists a (time-averaged)
+    % non-zero net flux from conformation $I$ to $J$.
   }
@@
 
-The Fig.~\ref{fig:tmp9} shows the probability of the
-conformations against time for periodically oscillatory EF.  The
-Fig.~\ref{fig:tmp10} presents the integrated probability fluxes between
+Fig.~\ref{fig:tmp9} shows the probability of the
+conformations against time for periodically oscillatory EF,
+\bluec{\textit{what kind of comment does he want us to add here?}}
+while  
+Fig.~\ref{fig:tmp10} presents the integrated net probability fluxes
+(defined by Eqn.~\eqref{eqn:tmp7a}) between
 conformations. Here the probability fluxes are not reported
 because the profiles are highly oscillating and they would not offer 
- a more complete information of the one that can be obtained from the integrated probability flux.
+a better information of the one that can be obtained from the integrated probability flux.
 For all periods investigated,
 the observed time-dependent probabilities  in $A_1$, $A_2$, $B_1$ and $B_2$ are
-highly oscillating and the average value does not change
+highly oscillating and the average value over time cycles does not change
 considerably w.r.t.~time.
@@
 % {\bf END COMMENT}\\
-For the case of constant EF, the probability of conformation $A_1$
-increases from 0.45 to 0.69, and that of $B_1$ almost vanishes.
-These phenomena are not observed in the oscillatory EF case.
-In the case of $T=10$ and $40$~ps, the probability of being of a conformation
+% For the case of constant EF, the probability of conformation $A_1$
+% increases from 0.45 to 0.69, and that of $B_1$ almost vanishes.
+\recheck{The notable increment of probability of $A_1$ and
+  the vanish of $B_1$ in the constant EF case (see Fig.~\ref{fig:tmp5})}
+are not observed in the oscillatory EF case.
+In the case of $T=10$ and $40$~ps, \recheck{the probability of conformation $C$}
 reaches the steady value in around 300~ps, while it requires about 1200~ps
-for the $T=200$~ps case. 
+for the $T=200$~ps case.  \bluec{\textit{why does he say ``what is the interest?''. I do not understand...}}
 %This suggest that
@@
     The numbers near the arrows indicates the strength of the averaged
-    probability flux, the unit of which is $10^{-3}\textrm{ps}^{-1}$.
+    probability flux, the unit of which is $10^{-3}\times\textrm{ps}^{-1}$.
   }
@@
 \end{figure}
+\recheck{
+In comparison to the static EF case, where the probability flux
+vanishes when the system reaches steady state (Fig.~\ref{fig:tmp6}), 
 Fig.~\ref{fig:tmp10} shows increasing
 integrated probability net fluxes, which imply some lasting and directional
-fluxes among the conformations (see Fig.~\ref{fig:tmp11} for a schematic plot of the main probability
-fluxes for $T=10$~ps).
+fluxes among the conformations, even after the
+conformational probabilities reach steady value (see Fig.~\ref{fig:tmp9}).
+}
+Fig.~\ref{fig:tmp11} presents
+a schematic plot of the main probability fluxes for $T=10$~ps.
 The thickness of the arrows and the numbers nearby indicates
-the average amount of the net fluxes.
-This shows an interesting phenomenon: although
-the oscillatory EF is not directional and vanishes in a time-average process,
-it generates directional probability fluxes among the conformations.
-Moreover, we have identified some loops of the flux: for example, $A_1 \rightarrow B_1
-\rightarrow B_2 \rightarrow A_2 \rightarrow A_1$, $A_1 \rightarrow B_1
-\rightarrow B_2 \rightarrow A_1$,  $A_1 \rightarrow B_1
-\rightarrow B_2 \rightarrow C \rightarrow A_1$ and $B_1
-\rightarrow B_2 \rightarrow C \rightarrow B_1$.
+\recheck{the steady value of average net fluxes over periods}.
+% the average amount of the net fluxes.
+\recheck{This shows an interesting phenomenon: although
+the oscillatory EF vanishes by time-averaging over a period,
+it generates directional probability fluxes among the conformations.}
+% Moreover, we have identified some loops of the flux: e.g.~$A_1 \rightarrow B_1
+% \rightarrow B_2 \rightarrow A_2 \rightarrow A_1$, $A_1 \rightarrow B_1
+% \rightarrow B_2 \rightarrow A_1$,  $A_1 \rightarrow B_1
+% \rightarrow B_2 \rightarrow C \rightarrow A_1$ and $B_1
+% \rightarrow B_2 \rightarrow C \rightarrow B_1$.
 The probability flux of $T=40$~ps is quantitatively
@@
 going into conformation $C$ is stronger, which actually results in
-a more dominant probability in $C$.
+a higher steady probability in $C$.
 The probability flux of case $T=200$~ps is qualitatively
 similar to $T=10$~ps and $T=40$~ps, however,
-the amount is much lower than the latter two cases.
-Moreover, we see that the integrated flux reaches a linearly increasing
-stage after about 3200~ps, which is even longer than the time scale
+the strength is much lower than the latter two cases.
+Moreover, \recheck{
+  we see that the integrated fluxes $Q_{A_2,A_1}$ and $Q_{B_1,A_2}$ reach
+  a steadyly
+increasing stage after about 3200~ps}, which is even longer than the time scale
 at which the probability of $C$ reaches its steady value. This indicates
@@
 We have not studied periods longer than $T=200$~ps, because
-from the trend suggests that a longer period indicates even longer intrinsic time scales.
-This would require massive computational efforts not strictly required at this stage.
+the trend suggests that a longer period indicates even longer intrinsic time scales.
+% This would require massive computational efforts not strictly required at this stage.
 However, the long-period-limit case can be safely guessed: When
-the EF changes so slow that at each time the system
-can be viewed as in equilibrium, then the process is a quasi-equilibrium
-process, and nonequilibrium phenomenon will not be observed. For example,
-the probability being of a conformation will change
+the EF changes so slowly that
+at each time the system
+can be viewed as in equilibrium, and
+\recheck{each EF induced infiniesimal change of the system is reversible},
+then the process is a quasi-equilibrium
+process,
+and nonequilibrium phenomena will not appear. For example,
+the probability of being in a given conformation will change
 smoothly from equilibrium value to the new equilibrium of $E=1$~V/nm, as
@@
 And then smoothly goes back to equilibrium, as the EF vanishes.
-the time-averaged net flux will be infinitely small,
-and the integrated flux will be periodical, and constant in time-average.
+The time-averaged net flux will be infinitely small,
+and the integrated flux will be \recheck{periodic.}
 
@@
 dynamics of alanine dipeptide under the action of a constant and oscillatory electric
-field (EF) by the dynamical nonequilibrium molecule dynamics (D-NEMD) method.
+field (EF) by the dynamical nonequilibrium molecular dynamics (D-NEMD) method.
 The conformations of the alanine dipeptide are
-firstly projected onto the Ramachandran histogram, and
-then manually grouped into 5  conformations.
+firstly projected onto the Ramachandran plot, and
+then grouped in 5  conformations.
 % several conformations are identified by a manual
@@
 These conformations
-correspond to different secondary structures in larger molecules (i.e. proteins).
+correspond to different secondary structures in larger molecules
+(i.e.~proteins).
 Next, the time-dependent probability
-of being in a certain conformation range and the net probability flux
+of being in a certain conformation and the net probability flux
 between them are calculated.
-From the results obtained, we conclude that under a constant EF, several different time scales
-of the conformational dynamics can be identified. The slowest time scale,
-in the range of 500~ps, corresponds to a conformational change
-from $B_1$ (corresponds to $\beta$-sheet) to $A_1$ and $C$ (right-handed
-and left handed $\alpha$-helix, respectively).
-Under the constant EF, the dipole moment of alanine aligns parallel to the direction of the EF, while the direction of the molecule lies perpendicular to the
-EF. Moreover, the dipole moment response of the alanine is
-shown to be much faster than the orientational response.
-The solvation structure around the alanine is investigated
-by calculating the solute-solvent radial distribution function and the average number of hydrogen
-bond, and is proved to be preserved as the EF is turned on, though the
-dipole moment of both solute and solvation molecules is aligned with the direction of the EF.
-Then, we consider three oscillatory EF cases with different frequency:
-5, 25 and 100~GHz, respectively. The
-probability of conformations are observed to be also oscillatory,
-and the frequency of this oscillation is the same as the external EF.
-After long enough time,
-the system reaches a ``steady state'', and the probabilities oscillate only around
-a time-independent value at the long time scale. Notice that, strictly speaking, this is not a  true ``steady state'' as defined in
-literature~\cite{seifert2010fluctuation}, because at the
-short time scale, the probabilities are still oscillating (with a period that is the same as the EF).
-% they oscillate only around a time-invariant value,
-% so we say the system reaches a steady state.
-Although in a time-average process the EF vanishes, the probabilities of the conformations, as a matter of fact, changes due to the oscillatory EF. The most relevant phenomenon
-is the increasing probability of conformation $C$ that corresponds to
-the left-handed $\alpha$-helix.
-The slowest time scale of 25 and 100~GHz systems is about 300~ps, while
-that of the 5~GHz system is significantly higher: 1200~ps.
-We further update the last number to 3200~ps by analyzing the net probability flux.
-% We further present a updated slowest time scale of the  5~GHz system
-% to 3200~ps from the net probability flux.
-In comparison with the periods of the EF, these time scales are much
-slower, which indicate a very strong time scale separation
-in these nonequilibrium conformation dynamics.
-Although the time-average of the oscillatory EF vanishes, we observed a
-\emph{directional} net probability flux between the conformations, and several
-loop structures are observed. This result is unexpected and shed
-light on the phenomenon of nonequilibrium conformational circulations driven
-by oscillatory EF.
-
-To eliminate the thermal effect in the nonequilibrium process, 
-we propose  a nonequilibrium
-temperature control method, by which the Hamiltonian dynamics is kept
-around the molecule of interest, while the solvent far from the
-molecule is thermostated. We prove the effectiveness of this
-temperature control technique for nonequilibrium MD by testing
-the finite size effect of the Hamiltonian dynamics region and the
-thermostated region.
+\recheck{
+  We demonstrated the reliablity
+  of the local thermostating temperature control method
+  by showing that the finite size effects of the
+  dynamical region and the thermostated region are negligible.  
+  From the results obtained, we found differnet time scales of
+  conformational response with respect to both the constant  and
+  oscillatory EF, and the probability flux net work established
+  by the oscillatory EF. These phenonema can not be easily investigated
+  by traditional equilibrium MD methods, therefore the effectiveness of
+  the nonequilibrium MD method proposed by this paper
+  is a powerful to study the truely nonequilibrium systems.
+}
+
+% From the results obtained, we conclude that under a constant EF, several different time scales
+% of the conformational dynamics can be identified. The slowest time scale,
+% in the range of 500~ps, corresponds to a conformational change
+% from $B_1$ (corresponds to $\beta$-sheet) to $A_1$ and $C$ (right-handed
+% and left handed $\alpha$-helix, respectively).
+% Under the constant EF, the dipole moment of alanine aligns parallel to the direction of the EF, while the direction of the molecule lies perpendicular to the
+% EF. Moreover, the dipole moment response of the alanine is
+% shown to be much faster than the orientational response.
+% The solvation structure around the alanine is investigated
+% by calculating the solute-solvent radial distribution function and the average number of hydrogen
+% bond, and is proved to be preserved as the EF is turned on, though the
+% dipole moment of both solute and solvation molecules is aligned with the direction of the EF.
+% Then, we consider three oscillatory EF cases with different frequency:
+% 5, 25 and 100~GHz, respectively. The
+% probability of conformations are observed to be also oscillatory,
+% and the frequency of this oscillation is the same as the external EF.
+% After long enough time,
+% the system reaches a ``steady state'', and the probabilities oscillate only around
+% a time-independent value at the long time scale. Notice that, strictly speaking, this is not a  true ``steady state'' as defined in
+% literature~\cite{seifert2010fluctuation}, because at the
+% short time scale, the probabilities are still oscillating (with a period that is the same as the EF).
+% % they oscillate only around a time-invariant value,
+% % so we say the system reaches a steady state.
+% Although in a time-average process the EF vanishes, the probabilities of the conformations, as a matter of fact, changes due to the oscillatory EF. The most relevant phenomenon
+% is the increasing probability of conformation $C$ that corresponds to
+% the left-handed $\alpha$-helix.
+% The slowest time scale of 25 and 100~GHz systems is about 300~ps, while
+% that of the 5~GHz system is significantly higher: 1200~ps.
+% We further update the last number to 3200~ps by analyzing the net probability flux.
+% % We further present a updated slowest time scale of the  5~GHz system
+% % to 3200~ps from the net probability flux.
+% In comparison with the periods of the EF, these time scales are much
+% slower, which indicate a very strong time scale separation
+% in these nonequilibrium conformation dynamics.
+% Although the time-average of the oscillatory EF vanishes, we observed a
+% \emph{directional} net probability flux between the conformations, and several
+% loop structures are observed. This result is unexpected and shed
+% light on the phenomenon of nonequilibrium conformational circulations driven
+% by oscillatory EF.
+
+% To eliminate the thermal effect in the nonequilibrium process, 
+% we propose  a nonequilibrium
+% temperature control method, by which the Hamiltonian dynamics is kept
+% around the molecule of interest, while the solvent far from the
+% molecule is thermostated. We prove the effectiveness of this
+% temperature control technique for nonequilibrium MD by testing
+% the finite size effect of the Hamiltonian dynamics region and the
+% thermostated region.
 
@@
 equipment~\cite{vogel2008femtosecond}. The authors are fully aware
-that the EF investigated in the present paper is idealized, as pointed
+that the EF investigated in the present paper is idealized
+\recheck{
+  in the sence that the field is spacially homogenous and
+  the time-dependency is well defined,} as pointed
 out by previous simulation studies~\cite{budi2005electric,
@@
 not play a important role, because  under the EF of 1~V/nm, the induced dipole
-of water is only c.a. 0.05~Debye that is negligible comparing with the
+of water is only c.a.~0.05~Debye that is negligible comparing with the
 dipole moment response observed in our simulations.  Therefore, it is
@@
 example the answer to the question of which is the slowest and the second slowest process, from which
-conformation to which conformation the system moves) are basically consistent for the alanine from the point of view of force fields.
+conformation to which conformation the system moves)
+seem to be independent from the force field,
+at least for the alanine dipeptide.
+
+% are basically consistent for the alanine from the point of view of force fields.
 

### 2013-11-09 writedown/npt-neq/alanine.tex
revise by Luigi, mostly...

@@
 In this paper, we investigate the conformational dynamics of alanine
-   dipeptide under an external electric field by the
+   dipeptide under an external electric field by 
    nonequilibrium molecular dynamics simulation.  We consider
@@
    integrated net probability fluxes.
-  % In this paper, we investigate the conformational dynamics of alanine
-  % dipeptide under an external electric field (EF) by the
-  % nonequilibrium molecular dynamics (MD) simulation, which enables us
-  % to calculate the nonequilibrium physical properties that are not
-  % available for traditional equilibrium MD simulation.  We study both
-  % the constant and oscillatory EF cases, and discuss the way to
-  % implement the temperature control in the nonequilibrium MD
-  % simulation, which removes the irrelevant thermal effect of the EF
-  % from the system. In the constant EF case, different time-scales are
-  % discovered in the conformational, dipole moment, and orientational
-  % dynamics. Moreover, we prove that the solvent structure only
-  % marginally changes when the external EF is switched on.  In the
-  % oscillatory EF case, the conformational changes are shown to be as
-  % strong as constant EF case, and non-trivial nonequilibrium
-  % conformational circulations are presented by calculating the
-  % integrated net probability fluxes.
+
 \end{abstract}
@@
 \section{Introduction}
-
 The possible effect of the electric field (EF) on the conformation of
@@
 studies have been devoted to this topic.
-
 In this perspective, molecular dynamics (MD) has been proven useful in
-understanding the behavior of a protein 
+understanding the behaviour of a protein 
 in both static and oscillatory EF~\cite{budi2005electric, budi2007effect, budi2008comparative,
@@
 Along the trajectories, various observable, such as the
-secondary structure, root mean square displacement (RMSD), the dipole
+secondary structure, root mean square displacement (RMSD), dipole
 moment, shape parameters are calculated as a function of time, or
@@
 secondary structure of the molecule is changed by external  EF.  However,
-the behavior of observables in time is characterized by 
+the behaviour of observables in time is characterized by 
 strong
@@
 A time average can reduce the statistical uncertainty,
-but in non-stationary conditions, it is a not-well-founded procedure.
+however in non-stationary conditions this would be a not-well-founded procedure.
 In fact, we are studying non-stationary nonequilibrium process
@@
 the various methodology proposed here would be hampered for large molecules,
-although they \bluec{remain (\textit{does Giovanni write ``remain''? I cannot read})} our goal.
-
+although they remain our goal.  \recheck{In any case, alanine dipeptide
+is large enough so that the conformational changes of its internal degrees of freedom represent valid observables for a test of validity and utility of our approach.}
 The paper is organized as follows:
 \recheck{
-  We firstly describe the idea of D-NEMD, and a local thermostating method
-for nonequilibrium temperature control.
-% Then
-% introduce the physical
-% observables chosen to analyze the nonequilibrium responses.
-Then
-after introducing the physical
+  We firstly describe the idea of D-NEMD, and propose a technical improvement consisting in the definition and application of a local thermostating process.
+Next, after introducing the physical
 observables chosen to analyze the nonequilibrium response,
-the numerical results for the response of alanine
-dipeptide under static and oscillatory EF are
-finally presented.} By calculating the nonequilibrium properties from D-NEMD
+the numerical results for the case of a static and oscillatory EF, respectively, are discussed.} By calculating the nonequilibrium properties from D-NEMD
 simulations, we are able to address
-a few relavant questions: (i)~How the conformation of the peptide
+a few relevant questions: (i)~How the conformation of the peptide
 changes in an EF (conformational space);
-(ii)~When do these changes happen (time scale),
+(ii)~When these changes happen (time scale),
 and how likely they are (probability). 
@@
 time-dependent nonequilibrium w.r.t. conformation
-is explicitly considered for a \bluec{large molecule \textit{what does Giovanni write here? For me, the alanine dipeptide molecule is NOT large at all!}}
-in solution subject to time-dependent EF.
+is explicitly considered for a (relatively large) molecule
+in solution subject to an external time-dependent EF.
 
@@
 In this paper, these trajectories are called \emph{branching
-  trajectories} (see Fig.\ref{branching} for a pictorial representation). 
+  trajectories} {\bf EITHER WE PUT THE PICTURE OR REMOVE THIS SENTENCE {(see Fig.\ref{branching} for a pictorial representation)}}. 
 Finally, the value of the macroscopic observable at time $t$ is
 calculated by averaging the microscopic observable measured at each time $t$ along each branching trajectory.
-Stochastic dynamics (e.g.~Langevin dynamics) can be handled analogoursly.
-
-%Being more generalized, if the microscopic observable depends not only on the end
-%configuration at time $t$, but also on the historical
-%configurations along the trajectory, then expression~\eqref{eqn:tmp4} takes the generalized form:
-%\begin{align}
-%  O(t) = \int d\vect x\,\rho(\vect x, 0) \int_{\mathcal C\{\vect x, 0; t\}} \hat O[\vect x_s] \,d\mathcal P[\vect x_s] 
-%\end{align}
-%where the microscopic observable $ \hat O[\vect x_s] $ is now a
-%functional of the trajectory.  $\mathcal C\{\vect x, 0; t\}$ is the
-%set of all continuous trajectories starting at point $\vect x$ at time
-%0, and ending at time $t$. $\mathcal P[\vect x_s] $ is the measure of
-%the trajectory space $\mathcal C$.  In our case, it is the
-%$\delta$-function peaked around the trajectories governed by the
-%Hamiltonian dynamics. To be general, it can also be the measure of all
-%trajectories generated by, for example, a Langevin dynamics, then the
-%branching trajectories should be generated by the Langevin
-%dynamics rather than the Hamiltonian dynamics.
+Stochastic dynamics (e.g.~Langevin dynamics) can be handled analogously.
 
@@
 \end{figure}
-
-% The aforementioned D-NEMD simulation algorithm
-% does not describe how the boundary of the system should be set up.
-% The very naive idea of doing the simulation
-% is to simulate a infinitely large isolated system, or any large enough
-% isolated subsystem of it.
-% In practice, 
-% Therefore, we are interested in a 
 For this study, we are interested in 
@@
 would be lost and the response to the perturbation would be unphysical. 
-%will disturb the original Hamiltonian dynamics. This is
-%in general problematic, 
-%because the dynamics  under thermostating is artificial designed,
-%so that the equilibrium distribution can be correctly produce, but not
-%the nonequilibrium properties of system.
-% dynamics of the system is no longer Hamiltonian, and is
-% artificial designed to reach the equilibrium probability distribution.
-% However, for a nonequilibrium system, the \emph{dynamics} properties
-% will be distrubed by the thermostat, because the
-% dynamics of the system is no longer Hamiltonian, and is
-% artificial designed to reach the equilibrium probability distribution.
-% For a nonequilibrium simulation, simply couple the system
-% to a thermostat may not be a good idea, because the \emph{dynamics}
-% generated by the thermostat is artificial, and deviation from the
-% Hamiltonian dynamics under investigation will introduce artificial
-% a effects in the nonequilibrium observations.
-
 In this section we propose a procedure to solve the problem: we
@@
 
-% Notice again we actually
-% do not want to precisely calculate each trajectory starting from the
-% initial configurations,
-% but want to correctly calculate the nonequilibrium observable,
-% we
-
 \section{Case I: Alanine dipeptide
@@
 MD simulation (if not stated otherwise for specific cases).
-% They server as starting point of the branching
-% trajectories.
 The branching trajectories were integrated by the
@@
 interaction was smoothed from $0.8$ to $1.0~\textsf{nm}$ by the
-``switch'' method provided by Gromacs.  An energy conserving PME
+``switch'' method provided by GROMACS.  An energy conserving PME
 method was applied to calculate the electrostatic interaction in this
@@
 change of the system size is small and slow, the pressure control
-does not have an sizeable effect on the
+does not have an sizable effect on the
 dynamics of the system.
@@
 
-%  (see also Fig.~\ref{fig:tmp3} for
-%  the vanished initial dipole moment)
-
 \subsection{Molecular conformation and net probability flux}
@@
   \centering
-  \includegraphics[width=1.00\textwidth]{fig-all-1.eps}
+  \includegraphics[width=1.00\textwidth]{fig-all.eps}
   % \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{c-2.eps}}
@@
     The probability density of the conformations of the alanine dipeptide plotted on the Ramachandran plot.
-    (a): An alanine dipeptide molecule.  Two dihedral angles
-    $\phi$ and $\psi$ that are used to define the Ramachandran plot
-    are shown with the molecule.
-    (b): The equilibrium probability density on Ramachandran plot
-    at $t=0$~\textsf{ps}. (c): The probability density of the new equilibrium
-    state at $t=1000$~\textsf{ps}, i.e., fully relaxed under the
-    action of a constant EF of 1~V/nm.  Darker color
+    (a): Two dihedral angles
+    $\phi$ and $\psi$ are used to represent the molecular conformations of the alanine dipeptide.
+    (b): The equilibrium probability density 
+    at $t=0$~\textsf{ps}. (c): The probability density of equilibrium at $t=1000$~\textsf{ps}, resulting from the application of a constant EF of 1~V/nm. Darker color
     indicates higher probability.
-    The Ramachandran plots are divided into 5 subregions corresponding
+    Plots are divided into 5 subregions corresponding
     to 5 molecular conformations:
-    $A_1 = \{(\phi, \psi) | -134 \leq \phi <  13, -125 \leq \psi < 74\}$,
-    $A_2 = \{(\phi, \psi) |  128 \leq \phi <-134, -125 \leq \psi < 74\}$,
-    $B_1 = \{(\phi, \psi) | -110 \leq \phi <  13,   74 \leq \psi <-125\}$,
-    $B_2 = \{(\phi, \psi) |  128 \leq \phi <-110,   74 \leq \psi <-125\}$,
-    $C   = \{(\phi, \psi) |   13 \leq \phi < 128, -180 \leq \psi < 180\}$.
-    Considering the periodic bondary condition, if we write, for example,
-    $128 \leq \phi <-134$, it means that $\phi$ is in either range
-    $128 \leq \phi < 180$ or in $-180 \leq \phi < -134$.
+    $A_1 = \{(\phi, \psi) | -134^\circ \leq \phi <  13^\circ, -125^\circ \leq \psi < 74^\circ\}$,
+    $A_2 = \{(\phi, \psi) |  128^\circ \leq \phi <-134^\circ, -125^\circ \leq \psi < 74^\circ\}$,
+    $B_1 = \{(\phi, \psi) | -110^\circ \leq \phi <  13^\circ,   74^\circ \leq \psi <-125^\circ\}$,
+    $B_2 = \{(\phi, \psi) |  128^\circ \leq \phi <-110^\circ,   74^\circ \leq \psi <-125^\circ\}$,
+    $C   = \{(\phi, \psi) |   13^\circ \leq \phi < 128^\circ, -180^\circ \leq \psi < 180^\circ\}$.
+    Considering the angular periodicity, if we write, for example,
+    $128^\circ \leq \phi <-134^\circ$, it implies that $\phi$ is in a range of $98$ degrees, between $128^\circ$ and $226^\circ$ ($226^\circ$ correspond to $-134^\circ$).
     This division is the same for both plot (b) and (c).
@@
 \recheck{
-The time-dependent molecular conformations of alanine dipeptide are
-investigated by estimate the probability density $p(\phi,\psi,t)$ on
-the Ramachandran plot at time $t$. The definition of dihedral
-angles $\phi$ and $\psi$ are given in Fig.~\ref{fig:tmp4}~(a).
-The equilibrium probability density of
-the conformations on the Ramachandran plot
-is given in Fig.~\ref{fig:tmp4}~(b), and the fully
-relaxed probability of conformations under
-the action of $E_{\infty} = 1$~V/nm is
-given in Fig.~\ref{fig:tmp4}~(c).  It is evident from the plot that
-the probability density of conformations are grouped in several clusters,
-% {\bf LUIGI COMMENT: HAN below is really not clear}\\
-% This means that only few of the total of conformations are likely to be visited,
-% in the nonequilibrium process.
-% These conformations are called ``metastable states''.
-% The strict definition of the
-% metastability is not exactly the same as those conformations that are likely to be observed.
-% Since in this paper we do not focus on the discussion of the definition for the metastability of the system,
-% we do not distinguish the definations, and assume they have the same meaning.
-% {\bf END COMMENT}\\
-therefore, for the sake of clarity, we divide the
+The change of conformation in time of the alanine dipeptide is
+investigated by analyzing the probability density $p(\phi,\psi,t)$ on
+the Ramachandran plot at time $t$. The definition of the dihedral
+angles $\phi$ and $\psi$ is given in Fig.~\ref{fig:tmp4}~(a).
+The probability density of conformations of equilibrium in absence of external field is shown in Fig.~\ref{fig:tmp4}~(b), while the same quantity, resulting from the molecular relaxation to the action of $E_{\infty} = 1$~V/nm is
+given in Fig.~\ref{fig:tmp4}~(c). In the plot one can identify several clusters
+in which conformations are grouped.
+Therefore, in order to simplify the analysis, we divide the
 Ramachandran histogram into 5 subregions $\{A_1, A_2, B_1, B_2, C\}$
-(see the caption of Fig.~\ref{fig:tmp4} for definition), and
-call each subregion, in short, a conformation of the alanine dipeptide. 
-These conformations
+(see caption of Fig.~\ref{fig:tmp4} for the corresponding definition).
+It is worth to notice that these conformations
 are found in different secondary structures of a peptide chain:
@@
 }
-% In the end,
-% the analysis of conformations on the Ramachandran plot is
-% reduced to the analysis of the 5 conformations.
-
-From Fig.~\ref{fig:tmp4}, it is obvious that the probability of
-conformations changes when the external EF is applied.
-For instance, the probability of conformation $C$ vanishes in equilibrium,
-but plays an important role when the EF is applied. We
-therefore want to study how the alanine changes from one conformation
-to the other, how fast the change is, and the relations to the 
-the EF. 
-Firstly, we calculate the probability
-of each conformation:
+
+\recheck{From Fig.~\ref{fig:tmp4}, it is evident that the probability with which a
+conformation occurs changes when the external EF is applied.
+The most evident case is conformation $C$; in fact it is not present at all before the external field is applied but appears in a clear way as a response to the action of the EF.
+Following this line of thought, we are interested to study the change of conformation under the action of EF.
+Specifically, for each conformational change, we will analyze the relation between the structural relaxation of the molecule and its corresponding time scale.
+The starting point is the calculation of the probability
+of each conformation}:
 \begin{align}
@@
 Notice that the probability is time dependent, being an observable in nonequilibrium situation.
-% which is the time dependent probability of the alanine being in metastable
-% state $I$.
-% Secondly, we study the
-% forward and backward transition probability of the metastable conformations, which is defined by
-% \begin{align}
-%   P^{\fwd}_{J,I}(t) & = \mathbb P( \vect x_{t+\Delta t} \in J | \vect x_t \in I) \\
-%   P^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J | \vect x_t \in I) 
-%   % \qquad I, J \in \{A_1, A_2, B_1, B_2, C\},
-% \end{align}
-% where $\Delta t$ is the time-scale of the observation.
-% For a revserible and homogeneous Markov process, it is easy to show
-% that $P^{\fwd}_{J,I} = P^{\bwd}_{J,I}$, and both of them are time independent. For a general nonequilibrium
-% process considered by the present work, this relation is genarlly not guarenteed.
-Secondly,
-we study the net probability flux from conformation $I$ to $J$, defined by:
+Next,
+we consider the net probability flux from conformation $I$ to $J$, defined by:
 \begin{align}\nonumber
@@
 \recheck{Where $\mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I)$
-is joint probability of the alanine being of conformation $J$ at
-time $(t-\Delta t)$ \emph{and} being of conformation $I$ at time $t$.
-A similar definition applies to $\mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J)$.}
-Here the time interval $\Delta t$ should be small enough comparing with the
+is the joint probability of the alanine being in conformation $J$ at
+time $(t-\Delta t)$ \emph{and} being in conformation $I$ at time $t$.
+The same definition applies to $\mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J)$.}
+Here the time interval $\Delta t$ should be small enough compared to the
 time scale of conformational dynamics,
 so that the changes in the conformation probabilities
-can be linearly approximated.
-In the meanwhile,  $\Delta t$ should also be  large enough comparing with
-the timestep of MD integrator, 
-so that the left hand of Eq.~\eqref{eqn:tmp7} is well-defined, and can be
-estimated with good statistical accuracy.
-See also the discussions in Ref.~\cite{schuette2011markov}.
-% \recheck{$F_{J,I}(t)$ is essentially the time-dependent rate of
-%   conformation change from $J$ to $I$.}
-A positive value \recheck{of $F_{J,I}(t)$} indicates the
-net flux from $J$ to $I$,
+can be treated in linear approximation.
+At the same time,  $\Delta t$ should be also large enough compared with
+the timestep of the MD integrator, 
+so that the quantities of Eq.~\eqref{eqn:tmp7} are well-defined, and can be
+estimated with sufficient numerical accuracy (see also Ref.~\cite{schuette2011markov}).
+A positive value \recheck{of $F_{J,I}(t)$} indicates that the
+net flux goes from $J$ to $I$,
 while a negative value indicates a net flux from $I$ to $J$.
-Through $F_{J,I}(t)$, the original overall nonequilibrium process $\vect x_t$
-is reduced to the probabilistic link between discretized conformations $\{A_1, A_2, B_1, B_2, C\}$.
-% If the resulting reduced process 
-% is time-reversible, then it is obvious that
-% $ F_{J,I}(t) = 0$. In an other word, the quantity $ F_{J,I}(t) $ represents
-% the irreversibility of the reduced process on
-% $\{A_1, A_2, B_1, B_2, C\}$.
-% In practice, to measure $ F_{J,I}(t)$, one needs first to approximate the limit
-% in Eq.~\eqref{eqn:tmp7} by the finite difference,
-% then calculate the joint probabilities on
-% the right-hand-side from the molecular trajectories.
-% In this context, for a precise finite difference approximation a smaller $\Delta t$ is
-% preferable although the statistical uncertainty of measuring the joint probabilities
-% is higher. In practice,
-% we use a $\Delta t$ that is small enough for a precise finite difference approximation,
-% and not small enough so that the joint probabilities can be calculated with acceptable accuracy.
-In the case of oscillatory EF, the net probability flux is also highly oscillatory,
-thus it is convenient to study the integrated net probability flux:
+Through $F_{J,I}(t)$, the analysis of the nonequilibrium process 
+is projected onto the analysis of the probabilistic link between discretized conformations $\{A_1, A_2, B_1, B_2, C\}$.
+\recheck{In the case of oscillatory EF, the behaviour of the net probability flux is also highly oscillatory, thus, in order to clearly identify the essential features of the molecular conformational changes, it is convenient to study the integrated net probability flux, defined as:
 \begin{align}\label{eqn:tmp7a}
@@
 \end{align}
-\redc{this expresses the cumulative effects of the EF
-on the conformations of the molecule.}
+which expresses the cumulative effects due to the action of EF on the conformations of the molecule.}
 
@@
   \includegraphics[]{fig-meta-npt.eps}
-  \caption{\recheck{The time-dependent probability of conformations $P_I(t)$} 
-    when a constant EF is present.
+  \caption{\recheck{The time-dependent probability of conformations $P_I(t)$ 
+    when a constant EF is present, where $\sum_I P_I(t) = 1, \forall t$.}
     The warm-up time is $t_{warm} = 10$~ps. The red line refers to conformation $I = A_1$,
     green to $A_2$, dark blue to $B_1$, purple to $B_2$ and light blue
-    to $C$. \recheck{Please notice that the summation of all conformational
-      probabilities
-    is identity, i.e.~$\sum_I P_I(t) = 1$.}
+    to $C$. 
   }
@@
   \centering
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-1.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-2.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-3.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-4.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-5.eps}\\
-  % \caption{The populations of the metastable sets as a function of time.
-  %   The dashed vertical lines indicate the three different time scale of
-  % metastable set population at $t_{\textrm{warm}} = 10~\textsf{ps}$.}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-1.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-2.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-3.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-4.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-5.eps}\\
-  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-1.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-2.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-3.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-4.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-010-flux-5.eps}\\
-  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-1.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-2.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-3.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-4.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-010-iflux-5.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-1.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-2.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-3.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-4.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-5.eps}\\
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-1.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-2.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-3.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-4.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-5.eps}
-  \caption{
-    The net probability flux and its integral, for the constant EF case.
+  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-1.eps}
+  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-2.eps}
+  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-3.eps}
+  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-4.eps}
+  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-5.eps}
+  \caption{\recheck{
+    The net probability flux for the constant EF case.
     The warm-up time is $t_{warm} = 10$~ps.
-    The first row shows the probability flux $F_{J,I}(t)$ (defined by Eqn.~\eqref{eqn:tmp7}) in units of $\textrm{ps}^{-1}$, while the second
-    shows the integrated  probability flux denoted by $Q_{J,I}(t)$ (defined by Eqn.~\eqref{eqn:tmp7a}).
-    A constant $Q_{J,I}$ means vanishing net flux, while a increasing (decreasing)
-    $Q_{J,I}$ indicates positive (negative) net flux.
-    From left to right, the five
-    columns present $I = A_1$, $A_2$, $B_1$, $B_2$ and
+    The probability flux $F_{J,I}(t)$ (defined by Eqn.~\eqref{eqn:tmp7}) is reported in units of $\textrm{ps}^{-1}$.
+    From top, left to right we report $I = A_1$, $A_2$, $B_1$; bottom, left to right $B_2$ and
     $C$, respectively. In each plot, the red line stands for $J=A_1$,
     green for $J=A_2$, dark blue for $J=B_1$, purple for $J=B_2$ and light blue
-    for $J=C$. 
+    for $J=C$.} 
     }
@@
 
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-1.eps}
-%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-2.eps}
-%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-3.eps}
-%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-4.eps}
-%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-5.eps}\\
-%   % \caption{The populations of the metastable sets as a function of time.
-%   %   The dashed vertical lines indicate the three different time scale of
-%   % metastable set population at $t_{\textrm{warm}} = 10~\textsf{ps}$.}
-%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-1.eps}
-%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-2.eps}
-%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-3.eps}
-%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-4.eps}
-%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-5.eps}\\
-%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-1.eps}
-%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-2.eps}
-%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-3.eps}
-%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-4.eps}
-%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-5.eps}
-%   \caption{Forward and backward nonequilibrium transition probability of the case $t_{warm} = 10$~ps.}
-%   \label{fig:tmp6}
-% \end{figure}
-
-The time-dependent probability density of \bluec{the system \textit{what does Giovanni add here?} in} a certain
+The time-dependent probability density of the system to stay in a certain
 conformation is given in
@@
 and stays there as long as the EF is kept.
-% \\
-% it gradually relaxes to the new equilibrium,
-% {\bf COMMENT LUIGI: Not clear, because some of the states may not be visited again. Anyway the choice of name and definition of ``metastable'' sound really not great}\\
-% For this reason we do not see any change
-% in the population density of the metastable states.\\
-% {\bf END COMMENT}\\
 \recheck{
-Even though the system is finally relaxed to the new equilibrium,
-the timescale of relaxation of each conformation is different. 
+An important point is that despite the system is finally relaxed to the new conformation of equilibrium,
+the relaxation timescales corresponding to each conformation are rather different. 
 From Fig.~\ref{fig:tmp5} and \ref{fig:tmp6}, we observe mainly
 three different timescales 10~ps, 100~ps and 500~ps,
-as summarized in Tab.~\ref{tab:tmp1}.
-}
+whose corresponding conformations are summarized in Tab.~\ref{tab:tmp1}.
+This is a relevant result because it shows the possibility of employing an external EF as a tool to identify relevant time scales in the conformational behaviour of a molecule in solution.}
 
@@
 
-% Even though the system is finally relaxed to the new equilibrium,
-% the timescale of relaxation of each conformation is different. 
-% From Fig.~\ref{fig:tmp6}, we observe mainly
-% three different timescales, as summarized in Tab.~\ref{tab:tmp1}.
-% (1) From
-% $t=0$ to approximately 10~\textsf{ps}, a net flux from 
-% $A_1$ to $A_2$ establishes.
-% A similar flux is also observed from $B_1$ to $B_2$.
-% Afterwards, these two fluxes vanish and are finally reversed,
-% i.e. $A_2$ to $A_1$ and $B_2$ to $B_1$, respectively.
-% % the population of $A_1$ firstly decreases and then increases to the original value,
-% % while the population of $A_2$ increases sharply. The plot of the net probability flux shows that 
-% % there is firstly a fast probability flux (conformational change) from
-% % $A_1$ to $A_2$, and then follows a probability flux with the same maganitude in the opposite direction, i.e.  from
-% % $A_2$ to $A_1$.
-% Moreover, a net flux from all $\beta$-sheet conformations
-% ($B_1$ and $B_2$) into $\alpha$-helix conformations ($A_1$, $A_2$ and
-% $C$) has been established.
-% % Also in this time-scale, strong and increasing probability flux from $B_2$ to $B_1$ is observed from Fig.~\ref{fig:tmp6}.
-% % The population of $B_1$ remains almost unchanged,
-% % because it  at the same time loses population to $\alpha$-helix conformations.
-% % Since  $B_2$ conformations not only changes into $B_1$, but also into $\alpha$-helix conformations, we observe a charp
-% % decrease of $B_2$ population between 10 and 20~ps.
-% (2), From $t=10$ to
-% 100~\textsf{ps},
-% The net flux from  conformation $A_2$ to $A_1$ and from $B_2$ to $B_1$
-% gradually decays to 0. Conformational changes from $B_2$ to $A_1$, $A_2$ and $C$
-% vanishes in about 50~ps.
-% % The net flux from $B_1$  to $A_1$ and $C$ decay slower and 
-% % will be discussed later.
-% At this stage, the probability of $B_2$ decreases to almost 0,
-% while the probability of $A_2$
-% converge to a non-vanishing value of approximately 0.06.
-% % the population of $B_2$ decreases by 0.15, and this
-% % configuration almost disappears. Interestingly, the population of $A_1$
-% % increases by the same amount, and the population of $A_2$ goes back to
-% % the initial value. The populations of $B_1$ and $C$ start increasing
-% % and decreasing, correspondingly. The speed of these changes are much
-% % slower than that of $B_2$ and $A_1$.
-% (3) At the time scale of $
-% 500~\textsf{ps}$, the population of $A_1$, $B_1$ and $C$ converge to
-% the new equilibrium (system with $E(\infty) = 1~\textsf{V/m}$).
-% We observe a decaying probability flux from $B_1$ 
-% to $A_1$ and $C$.
-% The magnitude of the flux from $B_1$ to  $C$ is larger than that of $B_1$ to  $A_1$.
-% % It is interesting to see that at nonequilibrium steady state, $A_1$ exchange
-% % population with $A_2$, and $B_1$ exchange
-% % population with $B_2$. However, when the $C$ conformation hardly changes
-% % to any other conformation, as indicated by the almost 1 value of the forward
-% % transition probability of set $C$. This implies that at the left-handed $\alpha$-helix is
-% % acutally more stable than  other conformations.
-% This time-scale is actually 50 times slower than that, at which
-% the EF was switched on ($t_{\textrm{warm}} = 10~\textsf{ps}$).
-
-% After aligning to the external EF, the alanine slowly adjust its conformation,
-% and the new equilibrium is reached at slower time scales.
-
-% To further test the dynamics of metastable population, two simulations
-% of $t_{\textrm{warm}} = 100~\textsf{ps}$ and $t_{\textrm{warm}} =
-% 500~\textsf{ps}$ are performed. The first time scale of $t =
-% 20~\textsf{ps}$ disappears in both of the testing simulations. In the
-% simulation of $t_{\textrm{warm}} = 100~\textsf{ps}$, the population of
-% $A$, $B_1$ and $C$ converges to the non-equilibrium steady state at
-% around $500~\textsf{ps}$. This further verifies internal time scale of
-% $A_1$, $B_1$ and $C$ presented in the testing case of
-% $t_{\textrm{warm}} = 10~\textsf{ps}$.  The dynamics of $B_2$ is
-% faster: it decays to zero as soon as the external EF is fully
-% switched on. In the case of $t_{\textrm{warm}} = 500~\textsf{ps}$, the
-% growth of the external EF is comparable to the longest
-% internal time scale of system, which means that the changes of the
-% perturbation to the system is so slow that the system can catch up, so
-% the process can be treated as  quasi-equilibrium.
-% The numerical results show the same story: the relaxation
-% of all populations are around $500 \sim 600~\textsf{ps}$.
-
 \subsection{Molecular dipole response}
-
-\begin{figure}
-  \centering
-  % \includegraphics[width=0.3\textwidth]{fig.ala/ele.field/field.eps}
+\recheck{The fact that our external perturbation corresponds to the action of an electric field, naturally leads to the question of how the behaviour of the electric dipole moment of the molecule is influenced by the direct interaction with EF, and, in turn, how this is related to the overall conformational behaviour of the molecule reported in the previous section.}
+\begin{figure}
+  \centering
   \includegraphics[width=0.45\textwidth]{fig-dipol-order-conf.eps}
-  % \\
-  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a1-1.eps}
-  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/a2-1.eps}
-  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b1-1.eps}
-  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/b2-1.eps}
-  % \includegraphics[width=0.18\textwidth]{fig.ala/confs/ext.mode1.010.Ex.01.00.t1000ps.recheck/c-1.eps}
   \caption{The
@@
 
-\redc{The dipole momenet of alanine dipeptide is defined by
+\redc{The dipole moment of the alanine dipeptide is defined by
 \begin{align}\label{eqn:tmp8}
@@
 shows that the $x$-component of the dipole moment 
-reaches 85\% of the maximum value in only 20~ps, which is comparable to
+reaches 85\% of its maximum value in only 20~ps, which is comparable to
 the warm-up time $t_{warm}$, and is 25 times
 smaller than the slowest time scale of the conformational relaxation.
-Then in the following 400~ps, the dipole slowly relaxes to the 
+Then in the following 400~ps, the dipole slowly relaxes to its 
 maximum value, that is, 
-6.8~Debye, and  corresponds to a dipole energy
+6.8~Debye, and  corresponds to an energy
 \redc{$\boldsymbol\mu_{\textrm{alanine}} \cdot \vect E$}
@@
 We calculate the averaged dipole moment of different conformations
-\redc{(defined by taking averge in Eqn.~\eqref{eqn:tmp8}
+\redc{(defined by taking average in Eqn.~\eqref{eqn:tmp8}
 only for a certain conformation)}
@@
 The dipole energy difference between 3.1 and 7.1~Debye is roughly 8.0~kJ/mol.
-\recheck{NOTE by Han: \textit{
-    I removed the discussion of the free energy barrier.}}
-% The free energy barriers between the
-% conformations were reported to be of order $20\sim 40$~kJ/mol~\cite{bohner2012algorithm},
-% which is comparable to the dipole energy difference. 
-Therefore, under a constant EF, the system will be driven towards those
+\recheck{Under a constant EF, the system will be likely to be driven towards those
 conformations with higher dipole moment, because the
-energy of the system will be lowered.  This is the reason why
+energy of the system will be lowered.  We suggest that this energy difference may be the reason why
 we observe that the $\beta$-sheet conformations with lower dipole moment
 are driven towards $\alpha$-helix conformations, 
-and $A_1$ and $C$ are conformations with higher probability, because their dipole moments are the highest
+($A_1$ and $C$) whose dipole moments are the highest
 among all conformations. Moreover, the $B_2$ conformation vanishes because
-its dipole is significantly lower than other conformations.
-% This also explains the two-time scale behavior of the molecular dipole
-% moment.
+its dipole is significantly lower than other conformations.}
 From 0 to 20~ps, the probability of
@@
 \subsection{Response of the orientational order parameter}
-
-Let us define
+\recheck{As a complementary information to the behaviour of the molecular dipole moment it is of interest to describe the overall orientational behaviour of the molecules w.r.t.
+the EF.
+In fact while the dipole moment specifically expresses the rearrangement of charges within the molecule as a response to the EF, the overall direction of the molecule tells us about the interplay between the internal positional rearrangement of the atoms and their alignment w.r.t.
+the EF.
+To this aim,} let us define
 the geometric direction of the alanine by the red vector in
@@
 as a function of time.
-Then we defined the orientational order parameter 
+Then we defined an orientational order parameter 
 \begin{align}
@@
 \end{align}
-The ensemble average is taken over the trajectory ensemble, so it is
+\recheck{The ensemble average is made along the trajectories, so it is
 a time dependent observable.
 The order parameter
-indicates where lies \bluec{in time average \textit{(is it correct?)}} the molecule w.r.t.~the EF.
-If the molecule is perfectly perpendicular to the EF, then $S_\theta = 1$.
-If the molecule has no directional
-preference, then $S_\theta = 0$. \bluec{\textit{What does Giovanni's comment mean here?}}
-If the molecule lies perfectly parallel to the EF, then $S_\theta = -2$.
+indicates the (time dependent) average orientation of the molecule w.r.t. ~the direction of the EF.}
+If the molecule is perfectly perpendicular to the EF, then $S_\theta = 1$, if is perfectly parallel then $S_\theta = -2$, if it has no directional
+preference, then $S_\theta = 0$. 
 From $t=0$ to roughly 10~ps, the orientational order parameter rapidly
@@
 Then from $t=0$ to 500~ps, the molecule slowly changes to the orientation
-that is perpendicular to the EF. \bluec{\textit{I do not know how to explain here...}}
+that is perpendicular to the EF.
+\recheck{In fact the angle between the vector of the dipole moment and the vector of the geometric direction is always close to $\frac{\pi}{2}$; if one observes the correlation between the value of the dipole moment (which tends to be more parallel to the EF as its value increases) and the angle of the vector of the geometric direction, the result above can be easily explained.}
 This orientational change is linked to the observed slowest
@@
 \subsection{Effects of EF on the solvent around the molecule}
-% This indicate that when the EF is switched on, the alanine almost immediately
-% changes its conformation so that the molecular dipole is aligned to the
-% external EF.
-% align itself to the
-% direction of the external EF without much conformational change.
-% And then, the conformation is slowly adjusted according to the
-% external field (now it is the same as the molecular dipole),
-% finally  the new equilibrium is reached at a much slower time scale
-% (approximately 500~ps).
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-We study the solvent effect on the alanine dipeptide in the presence of the EF by investigating
+\recheck{While so far we have focused our attention on the behaviour of the alanine under the action of the EF, however it is important also to understand the effects of the EF on the solvating water molecules.
+Being water a polar molecule the electrostatic interaction with an EF can dramatically change its solvation structure around the alanine and thus, in turn, influence its conformational behaviour.For this reason, in this section we analyze the behaviour of the solvent around the alanine under the action of the EF by investigating}
 the radial distribution function (RDF) between $\alpha$-carbon and the
@@
 alanine and water molecules, and between two water molecules.
-\recheck{The hydrogen bonds are calculated by standard GROMACS
+\recheck{The number of hydrogen bonds are calculated by standard GROMACS
 routine {\texttt {g\_hbond}}, with donor-acceptor distance cut-off 0.3~nm,
 and hydrogen-donor-acceptor angle cut-off $20^{\circ}$.}
-We see that the
-number of hydrogen bonds remains almost the same as the EF is turned on,
-although molecular dipoles tend to align with the direction of the EF (result
+We observe that the
+number of hydrogen bonds remains almost the same when the EF is turned on,
+although molecular dipoles tend to align along the direction of the EF (result
 not shown). 
@@
   periodically oscillatory EF}
-\bluec{\textit{what does he add besides the caption of the section?}}
-
 A step forward in our study is to consider a periodically oscillatory EF which has
@@
 periods 10, 40 and 200~ps.
-% The periods of the later two are
-% commensurate to the time scales discovered by the nonequilibrium MD
-% simulation of constant EF. The first is to test the if the
-% period is further reduced to smaller than 20~ps, there is any other
-% timescale of interest would play a role. Although the periods are
-% chosen according to the discovered time scales in the constant
-% EF simulation, the nonequilibrium phenonema of oscillating
-% EF cannot be derived from the constant field system.
-% As far as the EF changes, the internal time scale of the
-% system also changes, therefore, the nonequilibrium probabilities is a
-% complicated interplay of different internal time scales under
-% different EF.
-% We do not try to theoretically predict
-% what will happen under the oscillating EF by a series constant EF simulation
-% revealing the internal dynamics under different strength of EF, but just directly
-% do the nonequilibrium MD simulation for the oscillating EF, and discuss
-% the observed phenonema.
-
 \begin{figure}
@@
   \includegraphics[width=0.48\textwidth]{fig-mode2-order.eps}
-  \caption{Illustration of the effect of the oscillatory EF:
+  \caption{Illustration of the effect of the oscillatory EF on the system:
     the dipole moment (a) and the
@@
     only the $x$-component of the dipole moment is
-    shown. The black line refers to the static EF with turning on
-    time $t_{warm} = 10$~ps. The red line refers to the oscillatory field with period of
+    shown. The black line refers to the static EF which is turned on
+    at time $t_{warm} = 10$~ps. The red line refers to the oscillatory field with period of
     10~ps. The green line is of 40~ps; and the blue of 200~ps.}
@@
 \end{figure}
-
 Fig.~\ref{fig:tmp8} (a)
@@
 relax its dipole. However,
-for $T=10$ and 40~ps, the EF oscillates faster,
-and although the alanine dipeptide can respond to the EF action immediately,
-it does not have enough time to fully relax the dipole, as a consequence the maximum dipole moment is smaller than the previous case.
-% For even smaller period $T=10$~ps, the alanine does not have enough
-% time  to properly align the molecular dipole according to the external
-% field, so we see the maximum dipole moment is only about one third of the
-% constant EF case.
+for $T=10$ and 40~ps, the EF oscillates faster and the molecule 
+does not have enough time to fully relax the dipole, as a consequence the maximum dipole moment is smaller than the previous case.
 Fig.~\ref{fig:tmp9}~(b) presents the orientational order
 parameter. The notations are the same as Fig~\ref{fig:tmp9}~(a).
-% From the constant
-% EF simulation, we see that the response of order parameter has
-% two time scales: In the fast time scale, the 
 For all cases the order parameter is much
@@
 not exposed to a strong enough EF for a long enough.
-\bluec{\textit{I cannot read and understand Giovanni's comment referring here on the top of this page.}}
-For  $T=10$ and 40~ps, the orientation of the alanine is only weakly
-parallel to the EF. It is worth to notice that for constant EF,
-we also observe a quick alignment of molecular orientation to the EF
-on the time scale of 10~ps. For $T=200$~ps, the molecule periodically
-becomes \recheck{weakly} perpendicular to the EF, but this directional preference is much
+For  $T=10$ and 40~ps, the orientation of the alanine shows a weak tendency
+to be parallel to the EF. It is worth to notice that for constant EF,
+we also observe a quick alignment of the molecular orientation vector to the EF
+on the time scale of 10~ps. For $T=200$~ps, the molecule tends periodically
+to be perpendicular to the EF, but this directional preference is much
 weaker than the case of constant EF.
@@
   % \includegraphics[width=0.49\textwidth]{fig-meta-mode2-2000.eps}
-  \caption{
-    \bluec{\textit{what is the comment on the top of page 17?}}
-    The probability of being in a certain of conformation for
-    periodically oscillatory EF. Different periods,
-    i.e. $T=10$~ps, 40~ps and 200~ps, are presented here.  The
+  \caption{The probability of being in a certain of conformation for alanine in a   periodically oscillatory EF. Different periods,
+    i.e. $T=10$~ps, 40~ps and 200~ps, are considered here.  The
     probability of being in a certain conformation $I$, which is
@@
   \centering
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-flux-1.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-flux-2.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-flux-3.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-flux-4.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0010-flux-5.eps}\\
   \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-1.eps}
@@
   \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-5.eps}\\
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-flux-1.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-flux-2.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-flux-3.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-flux-4.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0040-flux-5.eps}\\
   \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-1.eps}
@@
   \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-5.eps}\\
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-flux-1.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-flux-2.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-flux-3.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-flux-4.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-0200-flux-5.eps}\\
   \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-1.eps}
@@
   \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-5.eps}\\
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-flux-1.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-flux-2.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-flux-3.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-flux-4.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-flux-5.eps}\\
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-iflux-1.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-iflux-2.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-iflux-3.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-iflux-4.eps}
-  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-mode2-2000-iflux-5.eps}
   \caption{
-    Integrated probability flux $Q_{J,I}(t)$ of the periodically
-    oscillatory EF is plotted against time. The unit of the
-    time (horizontal axis) is picosecond.
+    Integrated probability flux $Q_{J,I}(t)$ for the periodically
+    oscillatory EF, is plotted against time (horizontal axis, in picoseconds).
     The integrated
@@
     of $F_{J,I}(t)$ and $Q_{J,I}(t)$, respectively.
-    From up to down, rows report results with  period 10, 40 and 200~ps, respectively.
+    From top to bottom, rows report results with  period 10, 40 and 200~ps, respectively.
     From left to right, the five
-    columns show integrated flux $Q_{J,A_1}$, $Q_{J,A_2}$,
+    columns show the integrated flux $Q_{J,A_1}$, $Q_{J,A_2}$,
     $Q_{J,B_1}$, $Q_{J,B_2}$ and $Q_{J,C}$, respectively. In each plot,
@@
     purple for $J=B_2$ and light blue for $J=C$.
-    \recheck{An increaseing $Q_{J,I}$ indicates a net probability
+    \recheck{An increasing value of $Q_{J,I}$ indicates a net probability
       flux from conformation $J$ to $I$,
-      while a decreaseing $Q_{J,I}$ indicates a net probability
+      while a decreasing value of $Q_{J,I}$ indicates a net probability
       flux from $I$ to $J$.
     }
-    % In a certain time interval,
-    % if the integrated flux $Q_{J,I}$ increases, there exists a (time-averaged)
-    % non-zero net flux from conformation $I$ to $J$.
   }
@@
 conformations against time for periodically oscillatory EF,
-\bluec{\textit{what kind of comment does he want us to add here?}}
 while  
@@
 0.25 for $T=200$~ps.
-% \\
-% {\bf COMMENT LUIGI: sentence and context and reasoning of the part below not clear}
-% Note that in the case of constant EF, although the dipole moment is
-% larger than the  $T=40$~ps case (see Fig.~\ref{fig:tmp8} for comparison), the
-% probability of being in $C$ is indeed lower (only 0.22).\\
-% {\bf END COMMENT}\\
-% For the case of constant EF, the probability of conformation $A_1$
-% increases from 0.45 to 0.69, and that of $B_1$ almost vanishes.
 \recheck{The notable increment of probability of $A_1$ and
-  the vanish of $B_1$ in the constant EF case (see Fig.~\ref{fig:tmp5})}
+  the vanishing of $B_1$ in the constant EF case (see Fig.~\ref{fig:tmp5})}
 are not observed in the oscillatory EF case.
+\recheck{
 In the case of $T=10$ and $40$~ps, \recheck{the probability of conformation $C$}
 reaches the steady value in around 300~ps, while it requires about 1200~ps
-for the $T=200$~ps case.  \bluec{\textit{why does he say ``what is the interest?''. I do not understand...}}
-%This suggest that
-%the intrinsic time scales of the nonequilibrium processes are commensurate
-%for $T=10$ and $40$~ps, while they are much longer for $T=200$~ps.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.5\textwidth]{graph-t0010-1.eps}
+for the $T=200$~ps case. } \bluec{Here I do not agree with you to remove the above red discussion, because the time scales are
+the main results of the current paper, which should be discussed.}
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{graph-t0010-2.eps}
   \caption{Schematic plot of the main probability flux between conformations
@@
     probability flux, the unit of which is $10^{-3}\times\textrm{ps}^{-1}$.
+    % {\bf LUIGI COMMENT: THE PICTURE MUST BE MUCH MUCH LAREGER SO THAT ONE SEE THE DIFFERENCE IN THE STRUCTURES.
+mOREOVER, THEY HAVE AN INTEREST ONLY THEY CAN BE RELATED TO MORE GENERAL STRUCTURES.
+wHAT IS NEEDED IS THAT CLOSE TO EACH MOLECULE ONE SHOULD WRITE ``$\alpha$-helix-like'' ``$\beta$-sheet-like.
+THE REST, gIOVANNI IS RIGHT, DOES NOT NEED TO BE EXPALINED IN DETAIL BECAUSE IT IS NOT REALLY INTERESTING AND i CUT A LOT.}
   }
@@
 integrated probability net fluxes, which imply some lasting and directional
-fluxes among the conformations, even after the
-conformational probabilities reach steady value (see Fig.~\ref{fig:tmp9}).
+fluxes among the conformations (see Fig.~\ref{fig:tmp9}).
 }
@@
 % the average amount of the net fluxes.
-\recheck{This shows an interesting phenomenon: although
-the oscillatory EF vanishes by time-averaging over a period,
-it generates directional probability fluxes among the conformations.}
-% Moreover, we have identified some loops of the flux: e.g.~$A_1 \rightarrow B_1
-% \rightarrow B_2 \rightarrow A_2 \rightarrow A_1$, $A_1 \rightarrow B_1
-% \rightarrow B_2 \rightarrow A_1$,  $A_1 \rightarrow B_1
-% \rightarrow B_2 \rightarrow C \rightarrow A_1$ and $B_1
-% \rightarrow B_2 \rightarrow C \rightarrow B_1$.
+%\recheck{This shows an interesting phenomenon: although
+%the oscillatory EF vanishes by time-averaging over a period,
+%it generates directional probability fluxes among the conformations.}
 The probability flux of $T=40$~ps is quantitatively
@@
   we see that the integrated fluxes $Q_{A_2,A_1}$ and $Q_{B_1,A_2}$ reach
-  a steadyly
+  a steadily
 increasing stage after about 3200~ps}, which is even longer than the time scale
@@
 at each time the system
-can be viewed as in equilibrium, and
-\recheck{each EF induced infiniesimal change of the system is reversible},
-then the process is a quasi-equilibrium
-process,
-and nonequilibrium phenomena will not appear. For example,
-the probability of being in a given conformation will change
-smoothly from equilibrium value to the new equilibrium of $E=1$~V/nm, as
-the EF increases.
-And then smoothly goes back to equilibrium, as the EF vanishes.
-The time-averaged net flux will be infinitely small,
-and the integrated flux will be \recheck{periodic.}
+can be viewed as in equilibrium and
+the process falls in the category of a quasi-equilibrium
+process. 
+%For example,
+%the probability of being in a given conformation will change
+%smoothly from equilibrium value to the new equilibrium of $E=1$~V/nm, as
+%the EF increases.
+%And then smoothly goes back to equilibrium, as the EF vanishes.
+%The time-averaged net flux will be infinitely small,
+%and the integrated flux will be \recheck{periodic.}
 
@@
 
-\section{Conclusions and discussions}
-
+\section{Discussion and Conclusion}
 We have investigated the conformational
-dynamics of alanine dipeptide under the action of a constant and oscillatory electric
-field (EF) by the dynamical nonequilibrium molecular dynamics (D-NEMD) method.
+dynamics of \recheck{a solvated} alanine dipeptide under the action of a constant and oscillatory electric
+field (EF).
+\recheck{ We have employed the dynamical nonequilibrium molecular dynamics (D-NEMD) method.
+This allowed us to analyze the conformational changes of the molecule in terms of a response to an external perturbation which drives the system away from equilibrium.
+From the technical point of view, we have proposed a local thermostating procedure which does not introduce invalidating artifacts and at the same time avoids the necessity of considering large water bulk systems to solvate the molecule.}
 The conformations of the alanine dipeptide are
@@
 then grouped in 5  conformations.
-% several conformations are identified by a manual
-% division of the Ramachandran histogram.
 These conformations
@@
 between them are calculated.
-\recheck{
-  We demonstrated the reliablity
-  of the local thermostating temperature control method
-  by showing that the finite size effects of the
-  dynamical region and the thermostated region are negligible.  
-  From the results obtained, we found differnet time scales of
-  conformational response with respect to both the constant  and
-  oscillatory EF, and the probability flux net work established
-  by the oscillatory EF. These phenonema can not be easily investigated
-  by traditional equilibrium MD methods, therefore the effectiveness of
-  the nonequilibrium MD method proposed by this paper
-  is a powerful to study the truely nonequilibrium systems.
-}
-
-% From the results obtained, we conclude that under a constant EF, several different time scales
-% of the conformational dynamics can be identified. The slowest time scale,
-% in the range of 500~ps, corresponds to a conformational change
-% from $B_1$ (corresponds to $\beta$-sheet) to $A_1$ and $C$ (right-handed
-% and left handed $\alpha$-helix, respectively).
-% Under the constant EF, the dipole moment of alanine aligns parallel to the direction of the EF, while the direction of the molecule lies perpendicular to the
-% EF. Moreover, the dipole moment response of the alanine is
-% shown to be much faster than the orientational response.
-% The solvation structure around the alanine is investigated
-% by calculating the solute-solvent radial distribution function and the average number of hydrogen
-% bond, and is proved to be preserved as the EF is turned on, though the
-% dipole moment of both solute and solvation molecules is aligned with the direction of the EF.
-% Then, we consider three oscillatory EF cases with different frequency:
-% 5, 25 and 100~GHz, respectively. The
-% probability of conformations are observed to be also oscillatory,
-% and the frequency of this oscillation is the same as the external EF.
-% After long enough time,
-% the system reaches a ``steady state'', and the probabilities oscillate only around
-% a time-independent value at the long time scale. Notice that, strictly speaking, this is not a  true ``steady state'' as defined in
-% literature~\cite{seifert2010fluctuation}, because at the
-% short time scale, the probabilities are still oscillating (with a period that is the same as the EF).
-% % they oscillate only around a time-invariant value,
-% % so we say the system reaches a steady state.
-% Although in a time-average process the EF vanishes, the probabilities of the conformations, as a matter of fact, changes due to the oscillatory EF. The most relevant phenomenon
-% is the increasing probability of conformation $C$ that corresponds to
-% the left-handed $\alpha$-helix.
-% The slowest time scale of 25 and 100~GHz systems is about 300~ps, while
-% that of the 5~GHz system is significantly higher: 1200~ps.
-% We further update the last number to 3200~ps by analyzing the net probability flux.
-% % We further present a updated slowest time scale of the  5~GHz system
-% % to 3200~ps from the net probability flux.
-% In comparison with the periods of the EF, these time scales are much
-% slower, which indicate a very strong time scale separation
-% in these nonequilibrium conformation dynamics.
-% Although the time-average of the oscillatory EF vanishes, we observed a
-% \emph{directional} net probability flux between the conformations, and several
-% loop structures are observed. This result is unexpected and shed
-% light on the phenomenon of nonequilibrium conformational circulations driven
-% by oscillatory EF.
-
-% To eliminate the thermal effect in the nonequilibrium process, 
-% we propose  a nonequilibrium
-% temperature control method, by which the Hamiltonian dynamics is kept
-% around the molecule of interest, while the solvent far from the
-% molecule is thermostated. We prove the effectiveness of this
-% temperature control technique for nonequilibrium MD by testing
-% the finite size effect of the Hamiltonian dynamics region and the
-% thermostated region.
+\recheck{We have compared the case of constant EF and that of oscillatory EF
+and reported the main differences.
+Worth to notice is the possibility of employing an EF in order to identify several time scales related to conformational changes, this would not be straightforward for standard equilibrium MD simulations and thus suggest that D-NEMD proposed here is a powerful tools to investigate the conformational properties of a large molecule in solution.}
 
@@
 equipment~\cite{vogel2008femtosecond}. The authors are fully aware
-that the EF investigated in the present paper is idealized
-\recheck{
-  in the sence that the field is spacially homogenous and
-  the time-dependency is well defined,} as pointed
+that the EFs investigated in the present paper are, \recheck{at this stage, still ideal, above all regarding their spatially homogeneity and
+  the fact that the time-dependency is always well defined (as pointed
 out by previous simulation studies~\cite{budi2005electric,
@@
   starzyk2013proteins, english2009nonequilibrium,
-  solomentsev2012effects}. However, the present work presents a way of
-studying the EF induced conformational dynamics, and opens the
+  solomentsev2012effects}).
+However, the present work is an attempt to understand how the use of D-NEMD as a simulation tool can be applied to the important case of an EF and which information one may extract that is not easily accessible to other MD procedures (e.g.
+EF induced conformational changes and its related time scales which opens the
 possibility of conformational manipulation of the protein by applying
-an external EF.
-
-To describe the system, we use a classical force field with TIP3P water model.
+an external EF.)}
+
+\recheck{In order to sharply define the advantages and limitations of the approach used we must also clarify that in order} to describe the system, we use a classical force field with TIP3P water model.
 The EF is well know to be able to protonate the water molecule at the
@@
 dynamics differs in a considerable way between different force
-fields~\cite{vitalini2013speed}. However, the qualitative conclusions (for
-example the answer to the question of which is the slowest and the second slowest process, from which
-conformation to which conformation the system moves)
-seem to be independent from the force field,
-at least for the alanine dipeptide.
-
-% are basically consistent for the alanine from the point of view of force fields.
+fields~\cite{vitalini2013speed}. \recheck{However, the main qualitative conclusions, for
+example those concerning the determination of time scales or the map of conformational changes, 
+are not likely to change significantly as a function of the force field.}
 

### 2013-11-10 writedown/npt-neq/alanine.tex
my revision again

@@
 conformational changes of a solvated molecule, subject to a time-dependent EF.
+
 In the present paper, we study a small peptide, alanine dipeptide, as a model for showing how the method can be used. 
@@
 where $U^\dagger(t,0) = \exp\{-i \int_0^t d t' L(t')\}$.
-On the other hand
+On the other hand,
 \begin{align}
@@
   = \nabla_{\vect x}\hat O\cdot J\cdot \nabla_{\vect x}\mathcal H
-  = iL(t) \hat O (\vect x(t))
+  = iL(t) \hat O (\vect x(t)).
 \end{align}
@@
   = \langle U(t,0)\,\hat O(\vect x), \rho(\vect x, 0)\rangle\\\label{eqn:tmp4}
-  &= \langle \hat O(\vect x(t)), \rho(\vect x, 0)\rangle
+  &= \langle \hat O(\vect x(t)), \rho(\vect x, 0)\rangle.
 \end{align}
@@
 would be lost and the response to the perturbation would be unphysical.
+
 In this section we propose a procedure to solve the problem: we
@@
 The validity of the above
-statement will be checked by a series of numerical tests where it is shown that
+statements will be checked by a series of numerical tests where it is shown that
 the response of observables in nonequilibrium (i.e. under the effect of the EF) does not depend on the size of the system
@@
 All simulations are performed by a home-modified GROMACS 4.5~\cite{pronk2013gromacs}.
-First, an equilibrium NVT simulation of
+First, an equilibrium NVT simulation at 300~K of
 100~\textsf{ns} was performed with a Langevin thermostat (time-scale
@@
 coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
+\bluec{
+  In all testing cases, this local thermostat is able to control
+  the system at the desired temperature, i.e.~300~K (the results
+  are not presented in this paper).
+  \textit{NOTE: we should mention that the local thermostat works...}
+}
 The whole system is also coupled to a Parrinello-Rahman barostat~\cite{parrinello1981polymorphic} with $\tau_P = 2.0~\textsf{ps}$ to keep
@@
 Therefore, in order to simplify the analysis, we divide the
-Ramachandran histogram into 5 subregions $\{A_1, A_2, B_1, B_2, C\}$
+Ramachandran plot into 5 subregions $\{A_1, A_2, B_1, B_2, C\}$
 (see caption of Fig.~\ref{fig:tmp4} for the corresponding definition).
@@
 conformation occurs changes when the external EF is applied.
-The most evident case is conformation $C$; in fact it is not present at all before the external field is applied but appears in a clear way as a response to the action of the EF.
+The most evident case is conformation $C$; in fact it is \bluec{almost} not present before the external field is applied but appears in a clear way as a response to the action of the EF.
 Following this line of thought, we are interested to study the change of conformation under the action of EF.
@@
 The left-hand helix conformation $C$ noticeably grows from 0 to 0.22.
-We plot the net probability fluxes and their integration in Fig.~\ref{fig:tmp6}.
+We plot the net probability fluxes integration in Fig.~\ref{fig:tmp6}.
 Results show that for short $t$, the net fluxes are generally non-zero, however, 
@@
 6.8~Debye, and  corresponds to an energy
-\redc{$\boldsymbol\mu_{\textrm{alanine}} \cdot \vect E$}
+\redc{($\boldsymbol\mu_{\textrm{alanine}} \cdot \vect E$)}
 of c.a.~$-13.6$~kJ/mol.
@@
 we observe that the $\beta$-sheet conformations with lower dipole moment
-are driven towards $\alpha$-helix conformations, 
-($A_1$ and $C$) whose dipole moments are the highest
+are driven towards $\alpha$-helix conformations
+$A_1$ and $C$, whose dipole moments are the highest
 among all conformations. Moreover, the $B_2$ conformation vanishes because
 its dipole is significantly lower than other conformations.}
-From 0 to 20~ps, the probability of
-lowest dipole conformation $B_2$ quickly
-vanishes. We observe a sharp increment of the average molecular dipole and finally, approaching  500~ps, the conformation slowly migrates from
-$B_1$ to $A_1$ and $C$. Moreover, since the dipole moment $A_1$ and $C$
-is higher than $B_1$, the average molecular dipole moment slowly increases
-to the nonequilibrium steady value.
+\bluec{Comparing Fig.~\ref{fig:tmp3} with~\ref{fig:tmp5},
+  the sharp increment of dipole moment before 20~ps is due to the quick vanishing of conformation
+  $B_2$, while the slow increment of dipole moment until 400~ps is due to
+  the slow migration from conformation $B_1$ to $A_1$ and $C$.
+  \textit{NOTE: here we want to discuss the relation between
+    the conformation and the dipole moment. I rewote this
+    sentence.}
+}
+% From 0 to 20~ps, the probability of
+% lowest dipole conformation $B_2$ quickly
+% vanishes. We observe a sharp increment of the average molecular dipole and finally, approaching  500~ps, the conformation slowly migrates from
+% $B_1$ to $A_1$ and $C$. Moreover, since the dipole moment $A_1$ and $C$
+% is higher than $B_1$, the average molecular dipole moment slowly increases
+% to the nonequilibrium steady value.
 
@@
 \begin{align}
-  S_\theta = \langle 3\sin^2\theta - 2\rangle,
+  S_\theta = \langle 3\sin^2\theta - 2\rangle.
 \end{align}
@@
 that is perpendicular to the EF.
-\recheck{In fact the angle between the vector of the dipole moment and the vector of the geometric direction is always close to $\frac{\pi}{2}$; if one observes the correlation between the value of the dipole moment (which tends to be more parallel to the EF as its value increases) and the angle of the vector of the geometric direction, the result above can be easily explained.}
+\recheck{In fact,
+  \bluec{the vector of the geometric direction tends to be perpendicular
+    to the dipole moment,
+    \textit{NOTE: $\frac{\pi}{2}$ corresponds to $S_\theta = 1$, however,
+      we only have 0.4. So would should say a ``tendency of perpendicular''
+      rather than ``perfectly perpendicular'' ($\frac{\pi}{2}$).}
+  }  
+  % the angle between the vector of the dipole moment and
+  % the vector of the geometric direction is always close to
+  % $\frac{\pi}{2}$;
+  if one observes the correlation between the value
+  of the dipole moment (which tends to be more parallel to the EF as
+  its value increases) and the angle of the vector of the geometric
+  direction, the result above can be easily explained.}
 This orientational change is linked to the observed slowest
@@
 \recheck{While so far we have focused our attention on the behaviour of the alanine under the action of the EF, however it is important also to understand the effects of the EF on the solvating water molecules.
-Being water a polar molecule the electrostatic interaction with an EF can dramatically change its solvation structure around the alanine and thus, in turn, influence its conformational behaviour.For this reason, in this section we analyze the behaviour of the solvent around the alanine under the action of the EF by investigating}
+Being water a polar molecule the electrostatic interaction with an EF can dramatically change its solvation structure around the alanine and thus, in turn, influence its conformational behaviour.
+For this reason, in this section we analyze the behaviour of the solvent around the alanine under the action of the EF by investigating}
 the radial distribution function (RDF) between $\alpha$-carbon and the
 center-of-mass (COM) of the water molecules
-(see Fig.~\ref{fig:tmp7a}). The average
+(see Fig.~\ref{fig:tmp7a} (a)). The average
 RDF does not change significantly as a function of time
@@
   \caption{Illustration of the effect of the oscillatory EF on the system:
-    the dipole moment (a) and the
-    orientational order parameter (b) of alanine dipeptide as a
+    (a) the dipole moment  and (b) the
+    orientational order parameter of alanine dipeptide as a
     function of time. In (a),
@@
 At $T=200$~ps, the maximum magnitude of the molecular
-dipole moment is close to the values obtained in the case of constant EF, which
+dipole moment is close to the value obtained in the case of constant EF, which
 means that the variation of the oscillatory EF is so slow that the
@@
 because the profiles are highly oscillating and they would not offer 
-a better information of the one that can be obtained from the integrated probability flux.
+a better information than the one that can be obtained from the integrated probability flux.
 For all periods investigated,
@@
 0.25 for $T=200$~ps.
+\bluec{
+In the case of $T=10$ and $40$~ps, {the probability of conformation $C$}
+reaches the steady value in around 300~ps, while it requires about 1200~ps
+for the $T=200$~ps case. } \bluec{\textit{Here I do not agree with you to remove the above blue discussion,
+  because the time scales (also the oscillatory EF case) are
+  the main results of the current paper, which should be presented. It is only one sentence, no one would be panic.}}
 \recheck{The notable increment of probability of $A_1$ and
@@
 are not observed in the oscillatory EF case.
-\recheck{
-In the case of $T=10$ and $40$~ps, \recheck{the probability of conformation $C$}
-reaches the steady value in around 300~ps, while it requires about 1200~ps
-for the $T=200$~ps case. } \bluec{Here I do not agree with you to remove the above red discussion, because the time scales are
-the main results of the current paper, which should be discussed.}
 \begin{figure}
   \centering
-  \includegraphics[width=0.5\textwidth]{graph-t0010-2.eps}
+  \includegraphics[width=0.7\textwidth]{graph-t0010-2.eps}
   \caption{Schematic plot of the main probability flux between conformations
-    on the Ramachandran histogram
     for periodically oscillatory EF, $T=10$~ps. The thickness 
@@
 a schematic plot of the main probability fluxes for $T=10$~ps.
-The thickness of the arrows and the numbers nearby indicates
+The thickness of the arrows and the numbers nearby indicate
 \recheck{the steady value of average net fluxes over periods}.

### 2013-11-18 writedown/npt-neq/alanine.tex
back up before revise according to Giovanni

@@
 
-\title{Exploring the conformational dynamics of a large molecule in solution using an external electric field: A nonequilibrium molecular dynamics simulation}
+\title{Exploring the conformational dynamics of alanine dipeptide in solution subjected to an external electric field: A nonequilibrium molecular dynamics simulation}
 % \title{The non-equilibrium molecular dynamics simulation of the alanine dipeptide under electric field}
@@
    case of oscillatory field, the conformational changes are shown to be as
-   strong as the previous case, and non-trivial nonequilibrium
+   strong as in the previous case, and non-trivial nonequilibrium
    circular paths in the conformation space are revealed by calculating the
@@
 The bracket on the right hand side of Eq.~\eqref{eqn:tmp1} denotes, as usual, the inner product in the
-phase space.  We assume that he dynamics of the system is governed by the
+phase space.  We assume that the dynamics of the system is governed by the
 Hamiltonian equation, i.e. $\dot {\vect x} = J \cdot \nabla_{\vect x}
@@
 can be formally solved by $\rho(\vect x, t) = U^\dagger(t,0) \rho(\vect x, 0)$,
-where $U^\dagger(t,0) = \exp\{-i \int_0^t d t' L(t')\}$.
+where $U^\dagger(t,0) = \mathcal T\exp\{-i \int_0^t d t' L(t')\}$, and $\mathcal T$ is the time ordering operator.
 On the other hand,
@@
 \end{align}
-Since we assume that the system starts from the distribution of equilibrium (without EF)
+Since we assume that the system starts from the equilibrium distribution (without EF)
  Eq.~\eqref{eqn:tmp4} expresses the fact that the 
@@
 In this paper, these trajectories are called \emph{branching
-  trajectories} {\bf EITHER WE PUT THE PICTURE OR REMOVE THIS SENTENCE {(see Fig.\ref{branching} for a pictorial representation)}}. 
+  trajectories}.
+% {\bf EITHER WE PUT THE PICTURE OR REMOVE THIS SENTENCE {(see Fig.\ref{branching} for a pictorial representation)}}. 
 Finally, the value of the macroscopic observable at time $t$ is
@@
 coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
-\bluec{
+\recheck{
   In all testing cases, this local thermostat is able to control
@@
   are not presented in this paper).
-  \textit{NOTE: we should mention that the local thermostat works...}
 }
@@
 conformation occurs changes when the external EF is applied.
-The most evident case is conformation $C$; in fact it is \bluec{almost} not present before the external field is applied but appears in a clear way as a response to the action of the EF.
+The most evident case is conformation $C$; in fact it is {almost} not present before the external field is applied but appears in a clear way as a response to the action of the EF.
 Following this line of thought, we are interested to study the change of conformation under the action of EF.
@@
 its dipole is significantly lower than other conformations.}
-\bluec{Comparing Fig.~\ref{fig:tmp3} with~\ref{fig:tmp5},
+\recheck{Comparing Fig.~\ref{fig:tmp3} with~\ref{fig:tmp5},
   the sharp increment of dipole moment before 20~ps is due to the quick vanishing of conformation
@@
   the slow migration from conformation $B_1$ to $A_1$ and $C$.
-  \textit{NOTE: here we want to discuss the relation between
-    the conformation and the dipole moment. I rewote this
-    sentence.}
+  % \textit{NOTE: here we want to discuss the relation between
+  %   the conformation and the dipole moment. I rewote this
+  %   sentence.}
 }
@@
 \recheck{In fact,
-  \bluec{the vector of the geometric direction tends to be perpendicular
+  {the vector of the geometric direction tends to be perpendicular
     to the dipole moment,
-    \textit{NOTE: $\frac{\pi}{2}$ corresponds to $S_\theta = 1$, however,
-      we only have 0.4. So would should say a ``tendency of perpendicular''
-      rather than ``perfectly perpendicular'' ($\frac{\pi}{2}$).}
+    % \textit{NOTE: $\frac{\pi}{2}$ corresponds to $S_\theta = 1$, however,
+    %   we only have 0.4. So would should say a ``tendency of perpendicular''
+    %   rather than ``perfectly perpendicular'' ($\frac{\pi}{2}$).}
   }  
@@
 \begin{align}
-  \vect E(t) = (E_0\sin(2\pi t / T), 0, 0)
+  \vect E(t) = (E_0\sin(2\pi t / T), 0, 0),
 \end{align}
@@
 0.25 for $T=200$~ps.
-\bluec{
+\recheck{
 In the case of $T=10$ and $40$~ps, {the probability of conformation $C$}
 reaches the steady value in around 300~ps, while it requires about 1200~ps
-for the $T=200$~ps case. } \bluec{\textit{Here I do not agree with you to remove the above blue discussion,
-  because the time scales (also the oscillatory EF case) are
-  the main results of the current paper, which should be presented. It is only one sentence, no one would be panic.}}
+for the $T=200$~ps case. }
+% \bluec{\textit{Here I do not agree with you to remove the above blue discussion,
+%   because the time scales (also the oscillatory EF case) are
+%   the main results of the current paper, which should be presented. It is only one sentence, no one would be panic.}}
 \recheck{The notable increment of probability of $A_1$ and

### 2013-11-18 writedown/npt-neq/alanine.tex
my revise, according to Giovanni's notes

@@
 \newcommand{\bwd}[0]{\textrm{bwd}}
+\newcommand{\period}[0]{T_{\textrm{P}}}
 
@@
 \author{Giovanni Ciccotti}
-\affiliation{Department of Physics, University of Roma "La Sapienza", Italy}
+% \affiliation{Department of Physics, University of Roma "La Sapienza", Italy}
+\affiliation{School of Physics, Room 302B UCD-EMSC, University College Dublin, Belfield, Dublin 4, Ireland}
+\affiliation{Dipartimento di Fisica, Università “La Sapienza” and CNISM, Piazzale Aldo Moro 5, 00185 Roma, Italy}
 \author{Luigi Delle Site}
@@
 the various methodology proposed here would be hampered for large molecules,
-although they remain our goal.  \recheck{In any case, alanine dipeptide
-is large enough so that the conformational changes of its internal degrees of freedom represent valid observables for a test of validity and utility of our approach.}
+although they remain our goal.  In any case, alanine dipeptide
+is large enough so that the conformational changes of its internal degrees of freedom represent valid observables for a test of validity and utility of our approach.
 The paper is organized as follows:
-\recheck{
   We firstly describe the idea of D-NEMD, and propose a technical improvement consisting in the definition and application of a local thermostating process.
@@
 observables chosen to analyze the nonequilibrium response,
-the numerical results for the case of a static and oscillatory EF, respectively, are discussed.} By calculating the nonequilibrium properties from D-NEMD
+the numerical results for the case of a static and oscillatory EF, respectively, are discussed. By calculating the nonequilibrium properties from D-NEMD
 simulations, we are able to address
@@
 can be formally solved by $\rho(\vect x, t) = U^\dagger(t,0) \rho(\vect x, 0)$,
-where $U^\dagger(t,0) = \mathcal T\exp\{-i \int_0^t d t' L(t')\}$, and $\mathcal T$ is the time ordering operator.
+\recheck{where $U^\dagger(t,0) = \mathcal T\exp\{-i \int_0^t d t' L(t')\}$, and $\mathcal T$ is the time ordering operator.}
 On the other hand,
@@
 coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
-\recheck{
   In all testing cases, this local thermostat is able to control
@@
   are not presented in this paper).
-}
 The whole system is also coupled to a Parrinello-Rahman barostat~\cite{parrinello1981polymorphic} with $\tau_P = 2.0~\textsf{ps}$ to keep
@@
   \caption{
-    \recheck{
     The probability density of the conformations of the alanine dipeptide plotted on the Ramachandran plot.
@@
     $A_1 = \{(\phi, \psi) | -134^\circ \leq \phi <  13^\circ, -125^\circ \leq \psi < 74^\circ\}$,
-    $A_2 = \{(\phi, \psi) |  128^\circ \leq \phi <-134^\circ, -125^\circ \leq \psi < 74^\circ\}$,
-    $B_1 = \{(\phi, \psi) | -110^\circ \leq \phi <  13^\circ,   74^\circ \leq \psi <-125^\circ\}$,
-    $B_2 = \{(\phi, \psi) |  128^\circ \leq \phi <-110^\circ,   74^\circ \leq \psi <-125^\circ\}$,
+    $A_2 = \{(\phi, \psi) |  128^\circ \leq \phi < 226^\circ, -125^\circ \leq \psi < 74^\circ\}$,
+    $B_1 = \{(\phi, \psi) | -110^\circ \leq \phi <  13^\circ,   74^\circ \leq \psi < 235^\circ\}$,
+    $B_2 = \{(\phi, \psi) |  128^\circ \leq \phi < 250^\circ,   74^\circ \leq \psi < 235^\circ\}$,
     $C   = \{(\phi, \psi) |   13^\circ \leq \phi < 128^\circ, -180^\circ \leq \psi < 180^\circ\}$.
-    Considering the angular periodicity, if we write, for example,
-    $128^\circ \leq \phi <-134^\circ$, it implies that $\phi$ is in a range of $98$ degrees, between $128^\circ$ and $226^\circ$ ($226^\circ$ correspond to $-134^\circ$).
+    \recheck{Considering the angular periodicity, The angle, for example, $226^\circ$ corresponds to $-134^\circ$
+    on the plot (b) and (c).}
+    % Considering the angular periodicity, if we write, for example,
+    % $128^\circ \leq \phi <-134^\circ$, it implies that $\phi$ is in a range of $98$ degrees, between $128^\circ$ and $226^\circ$ ($226^\circ$ correspond to $-134^\circ$).
     This division is the same for both plot (b) and (c).
-    }
   }
@@
 
-\recheck{
 The change of conformation in time of the alanine dipeptide is
@@
 left-handed $\alpha$-helix.
-}
 
-\recheck{From Fig.~\ref{fig:tmp4}, it is evident that the probability with which a
+From Fig.~\ref{fig:tmp4}, it is evident that the probability with which a
 conformation occurs changes when the external EF is applied.
@@
 The starting point is the calculation of the probability
-of each conformation}:
+of each conformation:
+\recheck{
 \begin{align}
-  P_I(t) = \mathbb P (\vect x_t \in I), \quad  I \in \{A_1, A_2, B_1, B_2, C\},
+  P_I(t) = \mathbb P ( (\phi_t,\psi_t) \in I), \quad  I \in \{A_1, A_2, B_1, B_2, C\},
 \end{align}
+}
 Notice that the probability is time dependent, being an observable in nonequilibrium situation.
@@
 we consider the net probability flux from conformation $I$ to $J$, defined by:
+\recheck{
 \begin{align}\nonumber
-  F_{J,I}(t) & = \frac1{\Delta t}\, [\mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I) - \mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J)], \\\label{eqn:tmp7}
+  F_{J,I}(t) & = \frac1{\Delta t}\,
+  \bigg[\,
+  \mathbb P \big( (\phi_{t-\Delta t},\psi_{t-\Delta t}) \in J,\, (\phi_t, \psi_t) \in I \,\big) 
+  -
+  \mathbb P \big( (\phi_{t-\Delta t}, \psi_{t-\Delta t}) \in I,\, (\phi_t, \psi_t) \in J \,\big)
+  \bigg], \\\label{eqn:tmp7}
   & J,I \in \{A_1, A_2, B_1, B_2, C\}.
-\end{align}
-\recheck{Where $\mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I)$
+\end{align}}
+\recheck{\textit{I cannot read what Giovanni wrote on the top of page 9.}}
+Where $\mathbb P\big( (\phi_{t-\Delta t}, \psi_{t-\Delta t}) \in J,\, (\phi_t, \psi_t) \in I\,\big)$
 is the joint probability of the alanine being in conformation $J$ at
 time $(t-\Delta t)$ \emph{and} being in conformation $I$ at time $t$.
-The same definition applies to $\mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J)$.}
+The same definition applies to
+$\mathbb P \big( (\phi_{t-\Delta t}, \psi_{t-\Delta t}) \in I,\, (\phi_t, \psi_t) \in J\,\big)$.
 Here the time interval $\Delta t$ should be small enough compared to the
@@
 estimated with sufficient numerical accuracy (see also Ref.~\cite{schuette2011markov}).
-A positive value \recheck{of $F_{J,I}(t)$} indicates that the
+A positive value of $F_{J,I}(t)$ indicates that the
 net flux goes from $J$ to $I$,
@@
 is projected onto the analysis of the probabilistic link between discretized conformations $\{A_1, A_2, B_1, B_2, C\}$.
-\recheck{In the case of oscillatory EF, the behaviour of the net probability flux is also highly oscillatory, thus, in order to clearly identify the essential features of the molecular conformational changes, it is convenient to study the integrated net probability flux, defined as:
+In the case of oscillatory EF, the behaviour of the net probability flux is also highly oscillatory, thus, in order to clearly identify the essential features of the molecular conformational changes, it is convenient to study the integrated net probability flux, defined as:
 \begin{align}\label{eqn:tmp7a}
@@
 \end{align}
-which expresses the cumulative effects due to the action of EF on the conformations of the molecule.}
+which expresses the cumulative effects due to the action of EF on the conformations of the molecule.
 
@@
   \includegraphics[]{fig-meta-npt.eps}
-  \caption{\recheck{The time-dependent probability of conformations $P_I(t)$ 
-    when a constant EF is present, where $\sum_I P_I(t) = 1, \forall t$.}
+  \caption{The time-dependent probability of conformations $P_I(t)$ 
+    when a constant EF is present, where $\sum_I P_I(t) = 1, \forall t$.
     The warm-up time is $t_{warm} = 10$~ps. The red line refers to conformation $I = A_1$,
@@
   \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-5.eps}
-  \caption{\recheck{
+  \caption{
     The net probability flux for the constant EF case.
@@
     green for $J=A_2$, dark blue for $J=B_1$, purple for $J=B_2$ and light blue
-    for $J=C$.} 
+    for $J=C$.
     }
@@
 The left-hand helix conformation $C$ noticeably grows from 0 to 0.22.
-We plot the net probability fluxes integration in Fig.~\ref{fig:tmp6}.
+We plot the net probability fluxes in Fig.~\ref{fig:tmp6}.
 Results show that for short $t$, the net fluxes are generally non-zero, however, 
@@
 equilibrium (at zero EF);  This is a nonequilibrium process.
-After a long enough time, the system
+After a time long enough, the system
 is fully relaxed to the new equilibrium defined by the action of the constant EF,
 and stays there as long as the EF is kept.
-\recheck{
-An important point is that despite the system is finally relaxed to the new conformation of equilibrium,
+An important point is that despite the system is finally relaxed to the new conformation,
 the relaxation timescales corresponding to each conformation are rather different. 
@@
 whose corresponding conformations are summarized in Tab.~\ref{tab:tmp1}.
-This is a relevant result because it shows the possibility of employing an external EF as a tool to identify relevant time scales in the conformational behaviour of a molecule in solution.}
+This is a relevant result because it shows the possibility of employing an external EF as a tool to identify relevant time scales in the conformational behaviour of a molecule in solution.
 
@@
   \end{tabular*}
-  \caption{A list of main probability fluxes and the corresponding time scales observed in the constant EF case.}
+  \caption{A list of the main probability fluxes and the corresponding time scales observed in the constant EF case.}
   \label{tab:tmp1}
@@
 \subsection{Molecular dipole response}
-\recheck{The fact that our external perturbation corresponds to the action of an electric field, naturally leads to the question of how the behaviour of the electric dipole moment of the molecule is influenced by the direct interaction with EF, and, in turn, how this is related to the overall conformational behaviour of the molecule reported in the previous section.}
+The fact that our external perturbation corresponds to the action of an electric field, naturally leads to the question of how the behaviour of the electric dipole moment of the molecule is influenced by the direct interaction with EF, and, in turn, how this is related to the overall conformational behaviour of the molecule reported in the previous section.
 \begin{figure}
@@
     of the alanine molecule as a
-    function of time. The dashed line represents the strength of the
-    external EF, while the solid line represents the dipole
-    moments. The left vertical axis is for the dipole moment, while
+    function of time. \recheck{The solid line represents the dipole moment,
+    while the dashed line represents the orientational order parameter.}
+    The left vertical axis is for the dipole moment, while
     the right is for the orientational order parameter.
@@
 
-\redc{The dipole moment of the alanine dipeptide is defined by
+The dipole moment of the alanine dipeptide is defined by
 \begin{align}\label{eqn:tmp8}
@@
 \end{align}
-where $q_i$ denotes the partial charge of an atom $i$ on the alanine,
-and the molecule is neutral, i.e.~$\sum_iq_i = 0$.
-$\vect r_i$ denotes the position of the atom $i$.}
+\recheck{where $q_i$ denotes the partial charge of any point particle $i$ defining our model of alnine,
+the molecule being neutral, i.e.~$\sum_iq_i = 0$.}
+$\vect r_i$ denotes the position of the particle $i$.
 Fig.~\ref{fig:tmp3}
@@
 reaches 85\% of its maximum value in only 20~ps, which is comparable to
-the warm-up time $t_{warm}$, and is 25 times
+the warm-up time $t_{warm}$, and is 25 times \recheck{\textit{25 time should be correct, isn't it?}}
 smaller than the slowest time scale of the conformational relaxation.
@@
 6.8~Debye, and  corresponds to an energy
-\redc{($\boldsymbol\mu_{\textrm{alanine}} \cdot \vect E$)}
+($\boldsymbol\mu_{\textrm{alanine}} \cdot \vect E$)
 of c.a.~$-13.6$~kJ/mol.
 We calculate the averaged dipole moment of different conformations
-\redc{(defined by taking average in Eqn.~\eqref{eqn:tmp8}
-only for a certain conformation)}
+(defined by taking average in Eqn.~\eqref{eqn:tmp8}
+only for a certain conformation)
 under the constant EF, and they are 6.8, 6.0, 5.1, 3.1 and 7.1~Debye
@@
 The dipole energy difference between 3.1 and 7.1~Debye is roughly 8.0~kJ/mol.
-\recheck{Under a constant EF, the system will be likely to be driven towards those
+Under a constant EF, the system will be likely to be driven towards those
 conformations with higher dipole moment, because the
@@
 among all conformations. Moreover, the $B_2$ conformation vanishes because
-its dipole is significantly lower than other conformations.}
-\recheck{Comparing Fig.~\ref{fig:tmp3} with~\ref{fig:tmp5},
+its dipole is significantly lower than other conformations.
+Comparing Fig.~\ref{fig:tmp3} with~\ref{fig:tmp5},
   the sharp increment of dipole moment before 20~ps is due to the quick vanishing of conformation
@@
   %   sentence.}
-}
 % From 0 to 20~ps, the probability of
@@
 \subsection{Response of the orientational order parameter}
-\recheck{As a complementary information to the behaviour of the molecular dipole moment it is of interest to describe the overall orientational behaviour of the molecules w.r.t.
+As a complementary information to the behaviour of the molecular dipole moment it is of interest to describe the overall orientational behaviour of the molecules w.r.t.
 the EF.
@@
 the EF.
-To this aim,} let us define
+To this aim, let us define
 the geometric direction of the alanine by the red vector in
@@
 \end{align}
-\recheck{The ensemble average is made along the trajectories, so it is
+The ensemble average is made along the branching trajectories, so it is
 a time dependent observable.
 The order parameter
-indicates the (time dependent) average orientation of the molecule w.r.t. ~the direction of the EF.}
+indicates the (time dependent) average orientation of the molecule w.r.t. ~the direction of the EF.
 If the molecule is perfectly perpendicular to the EF, then $S_\theta = 1$, if is perfectly parallel then $S_\theta = -2$, if it has no directional
@@
 Then from $t=0$ to 500~ps, the molecule slowly changes to the orientation
-that is perpendicular to the EF.
-\recheck{In fact,
-  {the vector of the geometric direction tends to be perpendicular
+that is almost perpendicular to the EF.
+In fact,
+  the vector of the geometric direction tends to be perpendicular
     to the dipole moment,
@@
     %   rather than ``perfectly perpendicular'' ($\frac{\pi}{2}$).}
-  }  
   % the angle between the vector of the dipole moment and
@@
   its value increases) and the angle of the vector of the geometric
-  direction, the result above can be easily explained.}
+  direction, the result above can be easily explained.
 This orientational change is linked to the observed slowest
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\recheck{While so far we have focused our attention on the behaviour of the alanine under the action of the EF, however it is important also to understand the effects of the EF on the solvating water molecules.
-Being water a polar molecule the electrostatic interaction with an EF can dramatically change its solvation structure around the alanine and thus, in turn, influence its conformational behaviour.
-For this reason, in this section we analyze the behaviour of the solvent around the alanine under the action of the EF by investigating}
+So far we have focused our attention on the behaviour of the alanine
+under the action of the EF. However, it is also important to understand
+the effects of the EF on the solvating water molecules. Being water a
+polar molecule the electrostatic interaction with an EF can
+dramatically change its solvation structure around the alanine and
+thus, in turn, influence its conformational behaviour. For this
+reason, in this section we analyze the behaviour of the solvent around
+the alanine under the action of the EF by investigating
 the radial distribution function (RDF) between $\alpha$-carbon and the
@@
 alanine and water molecules, and between two water molecules.
-\recheck{The number of hydrogen bonds are calculated by standard GROMACS
+The number of hydrogen bonds are calculated by standard GROMACS
 routine {\texttt {g\_hbond}}, with donor-acceptor distance cut-off 0.3~nm,
-and hydrogen-donor-acceptor angle cut-off $20^{\circ}$.}
+and hydrogen-donor-acceptor angle cut-off $20^{\circ}$.
 We observe that the
@@
 not shown). 
-The EF-induced solvent effect on the alanine is also counted by calculating the
+The EF-induced solvent effect on the alanine can be also accounted by calculating the
 difference of the water-alanine electrostatic interaction 
 without and with the EF.
-The energy difference is found to be $-19.1$~~kJ/mol that is
+The energy difference is found to be $-19.1$~kJ/mol that is
 comparable to the electrostatic energy associated to the dipole of the alanine itself.
@@
 Just as described in Sec.~\ref{sec:tmp2b}, we performed nonequilibrium MD
-simulations in a finite size periodic system, further divided it
+simulations in a finite size periodic system, further divided 
 into a dynamical and a thermostated region.
@@
 \begin{align}
-  \vect E(t) = (E_0\sin(2\pi t / T), 0, 0),
+  \vect E(t) = (E_0\sin(2\pi t / \period), 0, 0),
 \end{align}
 where $E_0$ is the intensity of the field, which is chosen to be
-1.0~V/nm.  $T$ is the oscillating period.
+1.0~V/nm.  $\period$ is the oscillating period.
 Here we tested three different
@@
 a function of time. The red, green and blue lines report the
-results of $T=10$~ps, 40~ps and 200~ps, respectively. The black line
+results of $\period =10$~ps, 40~ps and 200~ps, respectively. The black line
 shows the dipole moment under constant EF
@@
 is able to respond to the external EF almost immediately.
-At $T=200$~ps, the maximum magnitude of the molecular
+At $\period =200$~ps, the maximum magnitude of the molecular
 dipole moment is close to the value obtained in the case of constant EF, which
@@
 relax its dipole. However,
-for $T=10$ and 40~ps, the EF oscillates faster and the molecule 
+for $\period =10$ and 40~ps, the EF oscillates faster and the molecule 
 does not have enough time to fully relax the dipole, as a consequence the maximum dipole moment is smaller than the previous case.
@@
 relaxation of the order parameter is very slow, and the molecule in the case of oscillatory field is
-not exposed to a strong enough EF for a long enough.
-For  $T=10$ and 40~ps, the orientation of the alanine shows a weak tendency
+not exposed to a strong enough EF for a time long enough.
+For  $\period =10$ and 40~ps, the orientation of the alanine shows a weak tendency
 to be parallel to the EF. It is worth to notice that for constant EF,
 we also observe a quick alignment of the molecular orientation vector to the EF
-on the time scale of 10~ps. For $T=200$~ps, the molecule tends periodically
-to be perpendicular to the EF, but this directional preference is much
-weaker than the case of constant EF.
+on the time scale of 10~ps. For $\period =200$~ps, the molecule tends periodically
+to be more perpendicular to the EF, but this directional preference is much
+weaker than in the case of constant EF.
 
@@
   % \includegraphics[width=0.49\textwidth]{fig-meta-mode2-2000.eps}
-  \caption{The probability of being in a certain of conformation for alanine in a   periodically oscillatory EF. Different periods,
-    i.e. $T=10$~ps, 40~ps and 200~ps, are considered here.  The
+  \caption{The probability of being in a given of conformation for alanine in a   periodically oscillatory EF. Different periods,
+    i.e. $\period =10$~ps, 40~ps and 200~ps, are considered here.  The
     probability of being in a certain conformation $I$, which is
@@
     blue line: $I = B_1$,  pink line: $I = B_2$ and  light blue
-    line: $I = C$. For $T=10$~ps and 40~ps, the nonequilibrium
-    simulations last 1000~ps, while for $T=200$~ps,
+    line: $I = C$. For $\period =10$~ps and 40~ps, the nonequilibrium
+    simulations last 1000~ps, while for $\period =200$~ps,
     they last 6400~ps.  }
@@
     purple for $J=B_2$ and light blue for $J=C$.
-    \recheck{An increasing value of $Q_{J,I}$ indicates a net probability
+    An increasing value of $Q_{J,I}$ indicates a net probability
       flux from conformation $J$ to $I$,
@@
       flux from $I$ to $J$.
-    }
   }
@@
 a better information than the one that can be obtained from the integrated probability flux.
-For all periods investigated,
+Coming back to Fig.~\ref{fig:tmp9}, for all periods investigated,
 the observed time-dependent probabilities  in $A_1$, $A_2$, $B_1$ and $B_2$ are
@@
 However, the probability in conformation $C$ significantly
-increases to approximately 0.17 for $T=10$~ps, 0.27 for  $T=40$~ps, and
-0.25 for $T=200$~ps.
-\recheck{
-In the case of $T=10$ and $40$~ps, {the probability of conformation $C$}
+increases to approximately 0.17 for $\period =10$~ps, 0.27 for  $\period =40$~ps, and
+0.25 for $\period =200$~ps.
+In the case of $\period =10$ and $40$~ps, {the probability of conformation $C$}
 reaches the steady value in around 300~ps, while it requires about 1200~ps
-for the $T=200$~ps case. }
+for the $\period =200$~ps case. 
 % \bluec{\textit{Here I do not agree with you to remove the above blue discussion,
@@
 %   the main results of the current paper, which should be presented. It is only one sentence, no one would be panic.}}
-\recheck{The notable increment of probability of $A_1$ and
-  the vanishing of $B_1$ in the constant EF case (see Fig.~\ref{fig:tmp5})}
+The notable increment of probability of $A_1$ and
+  the vanishing of $B_1$ in the constant EF case (see Fig.~\ref{fig:tmp5})
 are not observed in the oscillatory EF case.
@@
   \caption{Schematic plot of the main probability flux between conformations
-    for periodically oscillatory EF, $T=10$~ps. The thickness 
+    for periodically oscillatory EF, $\period =10$~ps. The thickness 
     of the arrows approximately presents the strength of the flux.
@@
 \end{figure}
-\recheck{
 In comparison to the static EF case, where the probability flux
@@
 fluxes among the conformations (see Fig.~\ref{fig:tmp9}).
-}
 Fig.~\ref{fig:tmp11} presents
-a schematic plot of the main probability fluxes for $T=10$~ps.
+a schematic plot of the main probability fluxes for $\period =10$~ps.
 The thickness of the arrows and the numbers nearby indicate
-\recheck{the steady value of average net fluxes over periods}.
+the steady value of average net fluxes over periods.
 % the average amount of the net fluxes.
@@
 %it generates directional probability fluxes among the conformations.}
-The probability flux of $T=40$~ps is quantitatively
-comparable to case $T=10$~ps, except that the probability fluxes
+The probability flux of $\period =40$~ps is quantitatively
+comparable to the case $\period =10$~ps, except that the probability fluxes
 going into conformation $C$ is stronger, which actually results in
 a higher steady probability in $C$.
-The probability flux of case $T=200$~ps is qualitatively
-similar to $T=10$~ps and $T=40$~ps, however,
+The probability flux of case $\period =200$~ps is qualitatively
+similar to $\period =10$~ps and $\period =40$~ps, however,
 the strength is much lower than the latter two cases.
-Moreover, \recheck{
+Moreover, 
   we see that the integrated fluxes $Q_{A_2,A_1}$ and $Q_{B_1,A_2}$ reach
   a steadily
-increasing stage after about 3200~ps}, which is even longer than the time scale
+increasing stage after about 3200~ps, which is even longer than the time scale
 at which the probability of $C$ reaches its steady value. This indicates
-a longer intrinsic time scale in the $T=200$~ps case.
+a longer intrinsic time scale in the $\period =200$~ps case.
+\recheck{\textit{I think it is interesting because such directional probability
+  flux network is firstly reported by us. How to revise this part to convince Giovanni?}}
 
-We have not studied periods longer than $T=200$~ps, because
+We have not studied periods longer than $\period =200$~ps, because
 the trend suggests that a longer period indicates even longer intrinsic time scales.
@@
 at each time the system
-can be viewed as in equilibrium and
+can be viewed as in equilibrium,
 the process falls in the category of a quasi-equilibrium
@@
 We have investigated the conformational
-dynamics of \recheck{a solvated} alanine dipeptide under the action of a constant and oscillatory electric
+dynamics of a solvated alanine dipeptide under the action of a constant and oscillatory electric
 field (EF).
-\recheck{ We have employed the dynamical nonequilibrium molecular dynamics (D-NEMD) method.
-This allowed us to analyze the conformational changes of the molecule in terms of a response to an external perturbation which drives the system away from equilibrium.
-From the technical point of view, we have proposed a local thermostating procedure which does not introduce invalidating artifacts and at the same time avoids the necessity of considering large water bulk systems to solvate the molecule.}
+We have employed the dynamical nonequilibrium molecular dynamics
+(D-NEMD) method. This allowed us to analyze the conformational changes
+of the molecule in terms of a response to an external perturbation
+which drives the system away from equilibrium. From the technical
+point of view, we have proposed a local thermostating procedure which
+does not introduce invalidating artifacts and at the same time avoids
+the necessity of considering large water bulk systems to solvate the
+molecule.
 The conformations of the alanine dipeptide are
@@
 between them are calculated.
-\recheck{We have compared the case of constant EF and that of oscillatory EF
+We have compared the case of constant EF and that of oscillatory EF
 and reported the main differences.
-Worth to notice is the possibility of employing an EF in order to identify several time scales related to conformational changes, this would not be straightforward for standard equilibrium MD simulations and thus suggest that D-NEMD proposed here is a powerful tools to investigate the conformational properties of a large molecule in solution.}
+Worth to notice is the possibility of employing an EF in order to identify several time scales related to conformational changes, this would not be straightforward for standard equilibrium MD simulations and thus suggest that D-NEMD proposed here is a powerful tools to investigate the conformational properties of a large molecule in solution.
 
@@
 equipment~\cite{vogel2008femtosecond}. The authors are fully aware
-that the EFs investigated in the present paper are, \recheck{at this stage, still ideal, above all regarding their spatially homogeneity and
+that the EFs investigated in the present paper are, at this stage, still ideal, above all regarding their spatially homogeneity and
   the fact that the time-dependency is always well defined (as pointed
@@
 possibility of conformational manipulation of the protein by applying
-an external EF.)}
+an external EF.)
 
-\recheck{In order to sharply define the advantages and limitations of the approach used we must also clarify that in order} to describe the system, we use a classical force field with TIP3P water model.
+In order to sharply define the advantages and limitations of the approach used we must also clarify that in order to describe the system, we use a classical force field with TIP3P water model.
 The EF is well know to be able to protonate the water molecule at the
@@
 dynamics differs in a considerable way between different force
-fields~\cite{vitalini2013speed}. \recheck{However, the main qualitative conclusions, for
+fields~\cite{vitalini2013speed}. However, the main qualitative conclusions, for
 example those concerning the determination of time scales or the map of conformational changes, 
-are not likely to change significantly as a function of the force field.}
+are not likely to change significantly as a function of the force field.
+
+\section*{Acknowledgement}
+\recheck{
+  H.W.~and C.S.~thank the financial support by DFG research center MATHEON.
+  Funding from the IIT SEED project SIMBEDD and from the SFI Grant 08-IN.1-I1869 is acknowledged by G.C..  
+}
 

### 2013-11-19 writedown/npt-neq/alanine.tex
final version before submission to jctc

@@
 \title{Exploring the conformational dynamics of alanine dipeptide in solution subjected to an external electric field: A nonequilibrium molecular dynamics simulation}
-% \title{The non-equilibrium molecular dynamics simulation of the alanine dipeptide under electric field}
 \author{Han Wang}
@@
 \affiliation{School of Physics, Room 302B UCD-EMSC, University College Dublin, Belfield, Dublin 4, Ireland}
-\affiliation{Dipartimento di Fisica, Università “La Sapienza” and CNISM, Piazzale Aldo Moro 5, 00185 Roma, Italy}
+\affiliation{Dipartimento di Fisica, Universit\`a ``La Sapienza'' and CNISM, Piazzale Aldo Moro 5, 00185 Roma, Italy}
 \author{Luigi Delle Site}
@@
    integrated net probability fluxes.
-
+  % In this paper, we investigate the conformational dynamics of alanine dipeptide under an external electric field by nonequilibrium molecular dynamics simulation.
+We consider the case of a constant and of an oscillatory field.
+In this context we propose a procedure to implement the temperature control, which removes the irrelevant thermal effects of the field.
+For the constant field different time-scales are identified  in the conformational, dipole moment, and orientational dynamics.
+Moreover, we prove that the solvent structure only marginally changes when the external field is switched on.
+In the case of oscillatory field, the conformational changes are shown to be as strong as in the previous case, and non-trivial nonequilibrium circular paths in the conformation space are revealed by calculating the integrated net probability fluxes.
 \end{abstract}
@@
 can be formally solved by $\rho(\vect x, t) = U^\dagger(t,0) \rho(\vect x, 0)$,
-\recheck{where $U^\dagger(t,0) = \mathcal T\exp\{-i \int_0^t d t' L(t')\}$, and $\mathcal T$ is the time ordering operator.}
+{where $U^\dagger(t,0) = \mathcal T\exp\{-i \int_0^t d t' L(t')\}$, and $\mathcal T$ is the time ordering operator.}
 On the other hand,
@@
     $C   = \{(\phi, \psi) |   13^\circ \leq \phi < 128^\circ, -180^\circ \leq \psi < 180^\circ\}$.
-    \recheck{Considering the angular periodicity, The angle, for example, $226^\circ$ corresponds to $-134^\circ$
-    on the plot (b) and (c).}
+    Considering the angular periodicity, The angle, for example, $226^\circ$ corresponds to $-134^\circ$
+    on the plot (b) and (c).
     % Considering the angular periodicity, if we write, for example,
@@
 of each conformation:
-\recheck{
 \begin{align}
@@
 \end{align}
-}
 Notice that the probability is time dependent, being an observable in nonequilibrium situation.
@@
 we consider the net probability flux from conformation $I$ to $J$, defined by:
-\recheck{
 \begin{align}\nonumber
@@
   & J,I \in \{A_1, A_2, B_1, B_2, C\}.
-\end{align}}
-\recheck{\textit{I cannot read what Giovanni wrote on the top of page 9.}}
+\end{align}
+% {\bf Here for $\lim_{\Delta \to 0}$ is intended that in the simulation the time interval is taken large enough so that we have  enough events and thus stable numbers (see also Ref.~\cite{schuette2011markov})}.
 Where $\mathbb P\big( (\phi_{t-\Delta t}, \psi_{t-\Delta t}) \in J,\, (\phi_t, \psi_t) \in I\,\big)$
@@
     of the alanine molecule as a
-    function of time. \recheck{The solid line represents the dipole moment,
-    while the dashed line represents the orientational order parameter.}
+    function of time. The solid line represents the dipole moment,
+    while the dashed line represents the orientational order parameter.
     The left vertical axis is for the dipole moment, while
@@
 \end{align}
-\recheck{where $q_i$ denotes the partial charge of any point particle $i$ defining our model of alnine,
-the molecule being neutral, i.e.~$\sum_iq_i = 0$.}
+where $q_i$ denotes the partial charge of any point particle $i$ defining our model of alanine,
+the molecule being neutral, i.e.~$\sum_iq_i = 0$.
 $\vect r_i$ denotes the position of the particle $i$.
@@
 reaches 85\% of its maximum value in only 20~ps, which is comparable to
-the warm-up time $t_{warm}$, and is 25 times \recheck{\textit{25 time should be correct, isn't it?}}
+the warm-up time $t_{warm}$, and is 25 times
 smaller than the slowest time scale of the conformational relaxation.
@@
 for the $\period =200$~ps case. 
-% \bluec{\textit{Here I do not agree with you to remove the above blue discussion,
-%   because the time scales (also the oscillatory EF case) are
-%   the main results of the current paper, which should be presented. It is only one sentence, no one would be panic.}}
 The notable increment of probability of $A_1$ and
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{graph-t0010-2.eps}
+  \includegraphics[width=0.6\textwidth]{graph-t0010-2.eps}
   \caption{Schematic plot of the main probability flux between conformations
@@
     probability flux, the unit of which is $10^{-3}\times\textrm{ps}^{-1}$.
-    % {\bf LUIGI COMMENT: THE PICTURE MUST BE MUCH MUCH LAREGER SO THAT ONE SEE THE DIFFERENCE IN THE STRUCTURES.
-mOREOVER, THEY HAVE AN INTEREST ONLY THEY CAN BE RELATED TO MORE GENERAL STRUCTURES.
-wHAT IS NEEDED IS THAT CLOSE TO EACH MOLECULE ONE SHOULD WRITE ``$\alpha$-helix-like'' ``$\beta$-sheet-like.
-THE REST, gIOVANNI IS RIGHT, DOES NOT NEED TO BE EXPALINED IN DETAIL BECAUSE IT IS NOT REALLY INTERESTING AND i CUT A LOT.}
   }
@@
 the steady value of average net fluxes over periods.
-% the average amount of the net fluxes.
-%\recheck{This shows an interesting phenomenon: although
-%the oscillatory EF vanishes by time-averaging over a period,
-%it generates directional probability fluxes among the conformations.}
+{
+The relevance of Fig.~\ref{fig:tmp11} is in the fact that it suggests,
+in perspective, a general scenario common to all molecules
+characterized by $\beta$-sheet-like or $\alpha$-helix-like
+conformations and how an electric field is likely to modify it.
+}
 The probability flux of $\period =40$~ps is quantitatively
@@
 a longer intrinsic time scale in the $\period =200$~ps case.
-\recheck{\textit{I think it is interesting because such directional probability
-  flux network is firstly reported by us. How to revise this part to convince Giovanni?}}
 
@@
 process.
-%For example,
-%the probability of being in a given conformation will change
-%smoothly from equilibrium value to the new equilibrium of $E=1$~V/nm, as
-%the EF increases.
-%And then smoothly goes back to equilibrium, as the EF vanishes.
-%The time-averaged net flux will be infinitely small,
-%and the integrated flux will be \recheck{periodic.}
-
-% similar to $T=10$~ps. For $T=40$~ps, the probability
-% flux is quantiatively comparable to the case $T=10$~ps, while
-% the strength of fluxex for $T=200$~ps is much weaker.
-
-% The time needed to reach a steady state is
-% roughly 400~ps that is the same as the
-% constant EF case.
-
-% When the period is $T=200$~ps, the phenonema are substentially different
-% from the high frequency cases ($T=10$ and 40~ps). Firstly, from Fig.~\ref{fig:tmp9}, the system reaches staedy state after around 2000~ps, while
-% Fig.~\ref{fig:tmp10} suggests an even long time scale, but we cannot draw
-% a very clear conclusion on it
-% due to the lack of computational power to perform even longer simulations. 
-% The steady probability of being in state $C$ is roughly the same as the
-% case of $T=40$~ps, although the maximum dipole moment is actually higher
-% than the latter. And the steady probability  of being in state $C$ is
-% also higher than the constant EF case, even the maximum dipole are roughly
-% the same. The time spend to reach the steady state is much longer than
-% the higher frequency cases, so this indicates a \emph{dynamically} longer time
-% scale in the system, comparing with the static EF case, in which all time scales
-% are actually decided by the \emph{static} external field. We also observe
-% a suden change in the probability flux from state $A_2$ to $A_1$ at
-% around 1600~ps, which may imply a \emph{dynamically} rare event.
-% Since we do not have the computer power to perform even longer simulations,
-% this hypothesis is not further checked.
 
@@
 
-\section*{Acknowledgement}
-\recheck{
+\section*{Acknowledgment}
+  H.W. acknowledges the valuable discussions with Simone Meloni.
+  This work was partially supported by the Deutsche
+  Forschungsgemeinschaft (DFG), with the Heisenberg
+  Grant provided to L.D.S. (Grant No. DE 1140/5-1),
+  and with the support within the priority program ``Ionic Liquids'' SPP 1191
+  (H.W. and L.D.S.). 
   H.W.~and C.S.~thank the financial support by DFG research center MATHEON.
   Funding from the IIT SEED project SIMBEDD and from the SFI Grant 08-IN.1-I1869 is acknowledged by G.C..
-}
-
-\bibliography{ref}{}
-\bibliographystyle{unsrt}
+
+% \bibliography{ref}{}
+% \bibliographystyle{unsrt}
+
+\begin{thebibliography}{10}
+
+\bibitem{bohr2000microwave}
+Henrik Bohr and Jakob Bohr.
+\newblock Microwave-enhanced folding and denaturation of globular proteins.
+\newblock {\em Physical Review E}, 61(4):4310, 2000.
+
+\bibitem{bohr2000microwave-1}
+Henrik Bohr and Jakob Bohr.
+\newblock Microwave enhanced kinetics observed in ord studies of a protein.
+\newblock {\em Bioelectromagnetics}, 21(1):68--72, 2000.
+
+\bibitem{dePomerai2000cell}
+David de~Pomerai, Clare Daniells, Helen David, Joanna Allan, Ian Duce, Mohammed
+  Mutwakil, David Thomas, Phillip Sewell, John Tattersall, Don Jones, and Peter
+  Candido.
+\newblock Cell biology: Non-thermal heat-shock response to microwaves.
+\newblock {\em Nature}, 405:417--418, 2000.
+
+\bibitem{inskip2001cellular}
+Peter~D Inskip, Robert~E Tarone, Elizabeth~E Hatch, Timothy~C Wilcosky,
+  William~R Shapiro, Robert~G Selker, Howard~A Fine, Peter~M Black, Jay~S
+  Loeffler, and Martha~S Linet.
+\newblock Cellular-telephone use and brain tumors.
+\newblock {\em New England Journal of Medicine}, 344(2):79--86, 2001.
+
+\bibitem{mancinelli2004non}
+Fabrizio Mancinelli, Michele Caraglia, Alberto Abbruzzese, Guglielmo
+  d'Ambrosio, Rita Massa, and Ettore Bismuto.
+\newblock Non-thermal effects of electromagnetic fields at mobile phone
+  frequency on the refolding of an intracellular protein: Myoglobin.
+\newblock {\em Journal of cellular biochemistry}, 93(1):188--196, 2004.
+
+\bibitem{budi2005electric}
+A.~Budi, F.S. Legge, H.~Treutlein, and I.~Yarovsky.
+\newblock Electric field effects on insulin chain-b conformation.
+\newblock {\em The Journal of Physical Chemistry B}, 109(47):22641--22648,
+  2005.
+
+\bibitem{budi2007effect}
+A.~Budi, F.S. Legge, H.~Treutlein, and I.~Yarovsky.
+\newblock Effect of frequency on insulin response to electric field stress.
+\newblock {\em The Journal of Physical Chemistry B}, 111(20):5748--5756, 2007.
+
+\bibitem{budi2008comparative}
+Akin Budi, F~Sue Legge, Herbert Treutlein, and Irene Yarovsky.
+\newblock Comparative study of insulin chain-b in isolated and monomeric
+  environments under external stress.
+\newblock {\em The Journal of Physical Chemistry B}, 112(26):7916--7924, 2008.
+
+\bibitem{toschi2008effects}
+Francesca Toschi, Francesca Lugli, Fabio Biscarini, and Francesco Zerbetto.
+\newblock Effects of electric field stress on a $\beta$-amyloid peptide.
+\newblock {\em The Journal of Physical Chemistry B}, 113(1):369--376, 2008.
+
+\bibitem{astrakas2011electric}
+Loukas Astrakas, Christos Gousias, and Margaret Tzaphlidou.
+\newblock Electric field effects on chignolin conformation.
+\newblock {\em Journal of Applied Physics}, 109(9):094702--094702, 2011.
+
+\bibitem{astrakas2012structural}
+Loukas~G Astrakas, Christos Gousias, and Margaret Tzaphlidou.
+\newblock Structural destabilization of chignolin under the influence of
+  oscillating electric fields.
+\newblock {\em Journal of Applied Physics}, 111(7):074702--074702, 2012.
+
+\bibitem{damm2012can}
+Markus Damm, Christoph Nusshold, David Cantillo, Gerald~N Rechberger, Karl
+  Gruber, Wolfgang Sattler, and C~Oliver Kappe.
+\newblock Can electromagnetic fields influence the structure and enzymatic
+  digest of proteins? a critical evaluation of microwave-assisted proteomics
+  protocols.
+\newblock {\em Journal of proteomics}, 75:5533--5543, 2012.
+
+\bibitem{starzyk2013proteins}
+A.~Starzyk and M.~Cieplak.
+\newblock Proteins in the electric field near the surface of mica.
+\newblock {\em The Journal of Chemical Physics}, 139:045102, 2013.
+
+\bibitem{english2009nonequilibrium}
+N.J. English, G.Y. Solomentsev, and P.~O'Brien.
+\newblock Nonequilibrium molecular dynamics study of electric and low-frequency
+  microwave fields on hen egg white lysozyme.
+\newblock {\em The Journal of chemical physics}, 131:035106, 2009.
+
+\bibitem{solomentsev2012effects}
+G.Y. Solomentsev, N.J. English, and D.A. Mooney.
+\newblock Effects of external electromagnetic fields on the conformational
+  sampling of a short alanine peptide.
+\newblock {\em Journal of Computational Chemistry}, 33:917--923, 2012.
+
+\bibitem{ciccotti1975direct}
+G~Ciccotti and G~Jacucci.
+\newblock Direct computation of dynamical response by molecular dynamics: The
+  mobility of a charged lennard-jones particle.
+\newblock {\em Physical Review Letters}, 35(12):789, 1975.
+
+\bibitem{ciccotti1979thought}
+G.~Ciccotti, G.~Jacucci, and I.R. McDonald.
+\newblock "thought-experiments" by molecular dynamics.
+\newblock {\em Journal of Statistical Physics}, 21(1):1--22, 1979.
+
+\bibitem{ciccotti1993theoretical}
+G.~Ciccotti, C.~Pierleoni, and J.P. Ryckaert.
+\newblock Theoretical foundation and rheological application of non-equilibrium
+  molecular dynamics.
+\newblock In {\em Microscopic simulations of complex hydrodynamic phenomena},
+  pages 25--45. Plenum Press, 1993.
+
+\bibitem{palla2008bulk}
+P.L. Palla, C.~Pierleoni, and G.~Ciccotti.
+\newblock Bulk viscosity of the lennard-jones system at the triple point by
+  dynamical nonequilibrium molecular dynamics.
+\newblock {\em Physical Review E}, 78(2):021204, 2008.
+
+\bibitem{orlandini2011hydrodynamics}
+S.~Orlandini, S.~Meloni, and G.~Ciccotti.
+\newblock Hydrodynamics from statistical mechanics: combined dynamical-nemd and
+  conditional sampling to relax an interface between two immiscible liquids.
+\newblock {\em Phys. Chem. Chem. Phys.}, 13:13177--13181, 2011.
+
+\bibitem{orlandini2011hydrodynamics-01}
+Sergio Orlandini, Simone Meloni, and Giovanni Ciccotti.
+\newblock Hydrodynamics from dynamical non-equilibrium md.
+\newblock In {\em AIP Conference Proceedings}, volume 1332, page~77, 2011.
+
+\bibitem{delaHoz2005microwaves}
+Antonio de~la Hoz, Angel Diaz-Ortiz, and Andres Moreno.
+\newblock Microwaves in organic synthesis. thermal and non-thermal microwave
+  effects.
+\newblock {\em Chemical Society Reviews}, 34(2):164--178, 2005.
+
+\bibitem{pronk2013gromacs}
+S.~Pronk, S.~P{\'a}ll, R.~Schulz, P.~Larsson, P.~Bjelkmar, R.~Apostolov, M.R.
+  Shirts, J.C. Smith, P.M. Kasson, D.~van~der Spoel, and Hess B.~Lindahl E.
+\newblock Gromacs 4.5: a high-throughput and highly parallel open source
+  molecular simulation toolkit.
+\newblock {\em Bioinformatics}, pages 1--10, 2013.
+
+\bibitem{parrinello1981polymorphic}
+M.~Parrinello and A.~Rahman.
+\newblock Polymorphic transitions in single crystals: A new molecular dynamics
+  method.
+\newblock {\em Journal of Applied Physics}, 52:7182, 1981.
+
+\bibitem{schuette2011markov}
+C.~Sch{\"u}tte, F.~No{\'e}, J.~Lu, M.~Sarich, and E.~Vanden-Eijnden.
+\newblock Markov state models based on milestoning.
+\newblock {\em The Journal of Chemical Physics}, 134:204105, 2011.
+
+\bibitem{scovell2000phase}
+Dawn~L Scovell, Tim~D Pinkerton, Valentin~K Medvedev, and Eric~M Stuve.
+\newblock Phase transitions in vapor-deposited water under the influence of
+  high surface electric fields.
+\newblock {\em Surface science}, 457(3):365--376, 2000.
+
+\bibitem{vogel2008femtosecond}
+A.~Vogel, N.~Linz, S.~Freidank, and G.~Paltauf.
+\newblock Femtosecond-laser-induced nanocavitation in water: implications for
+  optical breakdown threshold and cell surgery.
+\newblock {\em Physical review letters}, 100(3):38102, 2008.
+
+\bibitem{vitalini2013speed}
+F.~Vitalini, A.S.J.S. Mey, F.~No\'e, and B.G. Keller.
+\newblock The speed of force fields.
+\newblock {\em unpublished}, 2013.
+
+\end{thebibliography}
 

### 2014-02-21 alanine.nanma/template/tools/angles/app/average.equi.metastable.cpp
cal statistical uncertainty in equi prob

@@ -14,6 +14,7 @@
 
 #include "Defines.h"
 #include "Distribution.h"
+#include "BlockAverage.h"
 #include <boost/program_options.hpp>
 namespace po = boost::program_options;
 using namespace std;
@@ -72,7 +73,7 @@ void depositMetastable (const double & phi,
 int main(int argc, char * argv[])
 {
   std::string itfile, ofile;
-  unsigned every;
+  unsigned every, numDataBlock;
   // unsigned numBlock = 20;
   // double refh;
   // float time_prec = .01;
@@ -97,6 +98,7 @@ int main(int argc, char * argv[])
   desc.add_options()
       ("help,h", "print this message")
       ("every,e", po::value<unsigned > (&every)->default_value (1), "split every frame")
+      ("numDataBlock,n", po::value<unsigned > (&numDataBlock)->default_value (1000), "number of data in each block")
       ("output,o", po::value<std::string > (&ofile)->default_value ("equi.meta.out"), "the output of metastable propulation")
       ("input,f",  po::value<std::string > (&itfile)->default_value ("angle.dat"), "the file of trajectory");
 
@@ -128,6 +130,7 @@ int main(int argc, char * argv[])
   float time;
   ValueType phi, psi;
   vector<double > counts;
+  vector<BlockAverage_acc> avgs;
 
   FILE *fp = fopen (itfile.c_str(), "r");
   cout << "reading file " << itfile << endl;
@@ -146,23 +149,37 @@ int main(int argc, char * argv[])
     depositMetastable (psi, phi, sets, tmpcount);
     if (countFrame == 0){
       counts = tmpcount;
+      avgs.resize (tmpcount.size());
+      for (unsigned dd = 0; dd < tmpcount.size(); ++dd){
+	avgs[dd].reinit (numDataBlock);
+      }
     }
     else {
       for (unsigned dd = 0; dd < tmpcount.size(); ++dd){
 	counts[dd] += tmpcount[dd];
       }
     }
+    for (unsigned dd = 0; dd < tmpcount.size(); ++dd){
+      avgs[dd].deposite (tmpcount[dd]);
+    }      
     countFrame ++;
     countCal ++;
   }
   fclose (fp);
 
   FILE * fpo = fopen (ofile.c_str(), "w");
-  printf ("# calculated from %d frames\n", countCal);
[…]

### 2014-02-21 writedown/npt-neq/alanine.tex
small changes

@@
 
+\recheck{ The proposed temperature control method is very similar to
+  the stochastic boundary condition proposed by Brooks~III and Karplus~\cite{brooks1983deformable}.
+  The only difference is that we do not explicitly consider a boundary
+  region: The system that is divided into a dynamical region (reaction region in their paper) and
+  a thermostated regoin (stochastic buffer region in their paper)
+  is put into a 3-D cubic periodic simulation box.
+}
+
 \section{Case I: Alanine dipeptide
@@
 2.7\, \textsf{nm}^3$ periodic simulation region, with one alanine dipeptide
-described by the CHARMM27 force field, and dissolved in 644 TIP3P
-water molecules.
+described by the CHARMM27 force field~\cite{foloppe2000all}, and dissolved in 644 TIP3P~\cite{jorgensen1983comparison}
+water molecules.  \recheck{The grid-based energy correction map (CMAP)~\cite{mackerell2004extending}
+for the backbone dihedral angles is also taken into consider.}
 %The EF exserts force $\vect F = q \vect E(t)$ on
@@
 The size of the  dynamical region is $R_{ex} = 1.0$~nm.
-All simulations are performed by a home-modified GROMACS 4.5~\cite{pronk2013gromacs}.
+All simulations are performed by a home-modified GROMACS~4.5~\cite{pronk2013gromacs} with support to the CHARMM
+force field~\cite{bjelkmar2010implementation}.
 First, an equilibrium NVT simulation at 300~K of
@@
 temperature control technique.  The
-time step was $\Delta t = 0.002~\textsf{ps}$. The short-range
-interaction was smoothed from $0.8$ to $1.0~\textsf{nm}$ by the
-``switch'' method provided by GROMACS.  An energy conserving PME
+time step was $\Delta t = 0.002~\textsf{ps}$.
+\recheck{The short-range
+interaction (van der Waals interaction)
+had the cut-off radius of 1.0~nm, and was smoothed from $0.8$ to $1.0$~nm by the
+``switch'' method provided by GROMACS.
+A energy conserving particle mesh Ewald method (PME)~\cite{darden1993pme, essmann1995spm}
 method was applied to calculate the electrostatic interaction in this
-periodic system. In the thermostated region, the original dynamics was
+periodic system. The the direct space part of PME was cut-offed and smoothed in the
+same way as the van der Waals interaction.}
+\recheck {All hydrogen involving bonds are constrained by LINCS~\cite{hess1997lincs}, expect that
+  the TIP3P water molecules are constrained by SETTLE algorithm~\cite{miyamoto2004settle}.}
+In the thermostated region, the original dynamics was
 coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
@@
     $C   = \{(\phi, \psi) |   13^\circ \leq \phi < 128^\circ, -180^\circ \leq \psi < 180^\circ\}$.
-    Considering the angular periodicity, The angle, for example, $226^\circ$ corresponds to $-134^\circ$
+    Considering the angular periodicity, the angle, for example, $226^\circ$ corresponds to $-134^\circ$
     on the plot (b) and (c).
@@
 
+\recheck{ The definition of the probability flux is similar to the
+  kinetic rate.  However, we want to stress that, in genarl, the
+  probability flux should not be interpreted as a kinetic rate, and
+  one cannot replace the nonequilibrium molecular dynamics by a
+  kinetic analysis. The main reason is that the conformational
+  dynamics of alanine dipeptide is generally not Markovian for a small
+  time interval $\Delta t$~\cite{prinz2011markov}, therefore, a direct application of the kinetic
+  analysis is questionable. Since the main goal of our research is to propose a
+  nonequilibrium molecular dynamics simulation method, the numerical
+  results will not be compared with a kinetic analysis.
+}
+
 \subsection{Conformational dynamics}
@@
   \centering
-  \includegraphics[]{fig-meta-npt.eps}
+  \includegraphics[]{fig.ala.new/fig-meta-npt.eps}
   \caption{The time-dependent probability of conformations $P_I(t)$ 
@@
   \centering
-  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-1.eps}
-  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-2.eps}
-  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-3.eps}
-  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-4.eps}
-  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-5.eps}
+  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-1.eps}
+  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-2.eps}
+  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-3.eps}
+  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-4.eps}
+  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-5.eps}
   \caption{
@@
     $A_1\rightarrow A_2$        &       $\sim 10$      \\
-    $B_1\rightarrow B_2$        &       $\sim 10$      \\    
+    % $B_1\rightarrow B_2$        &       $\sim 10$      \\    
     $B_2\rightarrow A_1,\ A_2,\ C$        &       $\sim 50$      \\    
@@
 \subsection{Molecular dipole response}
-The fact that our external perturbation corresponds to the action of an electric field, naturally leads to the question of how the behaviour of the electric dipole moment of the molecule is influenced by the direct interaction with EF, and, in turn, how this is related to the overall conformational behaviour of the molecule reported in the previous section.
+The fact that our external perturbation corresponds to the action of
+an electric field, naturally leads to the question of how
+\recheck{
+  the molecular dipole aligns along the direction of external EF}, and, in turn, how this is related
+to the overall \recheck{conformational selection} of the molecule reported in
+the previous section.
 \begin{figure}
   \centering
-  \includegraphics[width=0.45\textwidth]{fig-dipol-order-conf.eps}
+  \includegraphics[width=0.45\textwidth]{fig.ala.new/field.dipole/fig-dipol-order-conf.eps}
   \caption{The
@@
   \centering
-  \includegraphics[]{fig-meta-conv.eps}
+  \includegraphics[]{fig.ala.new/fig-meta-conv.eps}
   \caption{Testing the finite-size effect on the dynamical and thermostated region.
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{fig-mode2-dipol.eps}
-  \includegraphics[width=0.48\textwidth]{fig-mode2-order.eps}
+  \includegraphics[width=0.48\textwidth]{fig.ala.new/fig-mode2-dipol.eps}
+  \includegraphics[width=0.48\textwidth]{fig.ala.new/fig-mode2-order.eps}
   \caption{Illustration of the effect of the oscillatory EF on the system:
@@
   \centering
-  \includegraphics[width=0.32\textwidth]{fig-meta-mode2-0010.eps}
-  \includegraphics[width=0.32\textwidth]{fig-meta-mode2-0040.eps}
-  \includegraphics[width=0.32\textwidth]{fig-meta-mode2-0200.eps}
+  \includegraphics[width=0.32\textwidth]{fig.ala.new/fig-meta-mode2-0010.eps}
+  \includegraphics[width=0.32\textwidth]{fig.ala.new/fig-meta-mode2-0040.eps}
+  \includegraphics[width=0.32\textwidth]{fig.ala.new/fig-meta-mode2-0200.eps}
   % \includegraphics[width=0.49\textwidth]{fig-meta-mode2-2000.eps}
@@
   \centering
-  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-1.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-2.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-3.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-4.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-5.eps}\\
-  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-1.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-2.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-3.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-4.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-5.eps}\\
-  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-1.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-2.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-3.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-4.eps}
-  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-5.eps}\\
+  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-1.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-5.eps}\\
+  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-1.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-5.eps}\\
+  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-1.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-5.eps}\\
   \caption{
@@
 increases to approximately 0.17 for $\period =10$~ps, 0.27 for  $\period =40$~ps, and
-0.25 for $\period =200$~ps.
+0.26 for $\period =200$~ps.
 In the case of $\period =10$ and $40$~ps, {the probability of conformation $C$}
@@
 
-% \bibliography{ref}{}
-% \bibliographystyle{unsrt}
-
-\begin{thebibliography}{10}
-
-\bibitem{bohr2000microwave}
-Henrik Bohr and Jakob Bohr.
-\newblock Microwave-enhanced folding and denaturation of globular proteins.
-\newblock {\em Physical Review E}, 61(4):4310, 2000.
-
-\bibitem{bohr2000microwave-1}
-Henrik Bohr and Jakob Bohr.
-\newblock Microwave enhanced kinetics observed in ord studies of a protein.
-\newblock {\em Bioelectromagnetics}, 21(1):68--72, 2000.
-
-\bibitem{dePomerai2000cell}
-David de~Pomerai, Clare Daniells, Helen David, Joanna Allan, Ian Duce, Mohammed
-  Mutwakil, David Thomas, Phillip Sewell, John Tattersall, Don Jones, and Peter
-  Candido.
-\newblock Cell biology: Non-thermal heat-shock response to microwaves.
-\newblock {\em Nature}, 405:417--418, 2000.
-
-\bibitem{inskip2001cellular}
-Peter~D Inskip, Robert~E Tarone, Elizabeth~E Hatch, Timothy~C Wilcosky,
-  William~R Shapiro, Robert~G Selker, Howard~A Fine, Peter~M Black, Jay~S
-  Loeffler, and Martha~S Linet.
-\newblock Cellular-telephone use and brain tumors.
-\newblock {\em New England Journal of Medicine}, 344(2):79--86, 2001.
-
-\bibitem{mancinelli2004non}
-Fabrizio Mancinelli, Michele Caraglia, Alberto Abbruzzese, Guglielmo
-  d'Ambrosio, Rita Massa, and Ettore Bismuto.
-\newblock Non-thermal effects of electromagnetic fields at mobile phone
-  frequency on the refolding of an intracellular protein: Myoglobin.
-\newblock {\em Journal of cellular biochemistry}, 93(1):188--196, 2004.
-
-\bibitem{budi2005electric}
-A.~Budi, F.S. Legge, H.~Treutlein, and I.~Yarovsky.
-\newblock Electric field effects on insulin chain-b conformation.
-\newblock {\em The Journal of Physical Chemistry B}, 109(47):22641--22648,
-  2005.
-
-\bibitem{budi2007effect}
-A.~Budi, F.S. Legge, H.~Treutlein, and I.~Yarovsky.
-\newblock Effect of frequency on insulin response to electric field stress.
-\newblock {\em The Journal of Physical Chemistry B}, 111(20):5748--5756, 2007.
-
-\bibitem{budi2008comparative}
-Akin Budi, F~Sue Legge, Herbert Treutlein, and Irene Yarovsky.
-\newblock Comparative study of insulin chain-b in isolated and monomeric
-  environments under external stress.
-\newblock {\em The Journal of Physical Chemistry B}, 112(26):7916--7924, 2008.
-
-\bibitem{toschi2008effects}
-Francesca Toschi, Francesca Lugli, Fabio Biscarini, and Francesco Zerbetto.
-\newblock Effects of electric field stress on a $\beta$-amyloid peptide.
-\newblock {\em The Journal of Physical Chemistry B}, 113(1):369--376, 2008.
-
-\bibitem{astrakas2011electric}
-Loukas Astrakas, Christos Gousias, and Margaret Tzaphlidou.
-\newblock Electric field effects on chignolin conformation.
-\newblock {\em Journal of Applied Physics}, 109(9):094702--094702, 2011.
-
-\bibitem{astrakas2012structural}
-Loukas~G Astrakas, Christos Gousias, and Margaret Tzaphlidou.
-\newblock Structural destabilization of chignolin under the influence of
-  oscillating electric fields.
-\newblock {\em Journal of Applied Physics}, 111(7):074702--074702, 2012.
-
-\bibitem{damm2012can}
-Markus Damm, Christoph Nusshold, David Cantillo, Gerald~N Rechberger, Karl
-  Gruber, Wolfgang Sattler, and C~Oliver Kappe.
-\newblock Can electromagnetic fields influence the structure and enzymatic
-  digest of proteins? a critical evaluation of microwave-assisted proteomics
-  protocols.
-\newblock {\em Journal of proteomics}, 75:5533--5543, 2012.
-
-\bibitem{starzyk2013proteins}
-A.~Starzyk and M.~Cieplak.
-\newblock Proteins in the electric field near the surface of mica.
-\newblock {\em The Journal of Chemical Physics}, 139:045102, 2013.
-
-\bibitem{english2009nonequilibrium}
-N.J. English, G.Y. Solomentsev, and P.~O'Brien.
-\newblock Nonequilibrium molecular dynamics study of electric and low-frequency
-  microwave fields on hen egg white lysozyme.
-\newblock {\em The Journal of chemical physics}, 131:035106, 2009.
-
-\bibitem{solomentsev2012effects}
-G.Y. Solomentsev, N.J. English, and D.A. Mooney.
-\newblock Effects of external electromagnetic fields on the conformational
-  sampling of a short alanine peptide.
-\newblock {\em Journal of Computational Chemistry}, 33:917--923, 2012.
-
-\bibitem{ciccotti1975direct}
-G~Ciccotti and G~Jacucci.
-\newblock Direct computation of dynamical response by molecular dynamics: The
-  mobility of a charged lennard-jones particle.
-\newblock {\em Physical Review Letters}, 35(12):789, 1975.
-
-\bibitem{ciccotti1979thought}
-G.~Ciccotti, G.~Jacucci, and I.R. McDonald.
-\newblock "thought-experiments" by molecular dynamics.
-\newblock {\em Journal of Statistical Physics}, 21(1):1--22, 1979.
-
-\bibitem{ciccotti1993theoretical}
-G.~Ciccotti, C.~Pierleoni, and J.P. Ryckaert.
-\newblock Theoretical foundation and rheological application of non-equilibrium
-  molecular dynamics.
-\newblock In {\em Microscopic simulations of complex hydrodynamic phenomena},
-  pages 25--45. Plenum Press, 1993.
-
-\bibitem{palla2008bulk}
-P.L. Palla, C.~Pierleoni, and G.~Ciccotti.
-\newblock Bulk viscosity of the lennard-jones system at the triple point by
-  dynamical nonequilibrium molecular dynamics.
-\newblock {\em Physical Review E}, 78(2):021204, 2008.
-
-\bibitem{orlandini2011hydrodynamics}
-S.~Orlandini, S.~Meloni, and G.~Ciccotti.
-\newblock Hydrodynamics from statistical mechanics: combined dynamical-nemd and
-  conditional sampling to relax an interface between two immiscible liquids.
-\newblock {\em Phys. Chem. Chem. Phys.}, 13:13177--13181, 2011.
-
-\bibitem{orlandini2011hydrodynamics-01}
-Sergio Orlandini, Simone Meloni, and Giovanni Ciccotti.
-\newblock Hydrodynamics from dynamical non-equilibrium md.
-\newblock In {\em AIP Conference Proceedings}, volume 1332, page~77, 2011.
-
-\bibitem{delaHoz2005microwaves}
-Antonio de~la Hoz, Angel Diaz-Ortiz, and Andres Moreno.
-\newblock Microwaves in organic synthesis. thermal and non-thermal microwave
-  effects.
-\newblock {\em Chemical Society Reviews}, 34(2):164--178, 2005.
-
-\bibitem{pronk2013gromacs}
-S.~Pronk, S.~P{\'a}ll, R.~Schulz, P.~Larsson, P.~Bjelkmar, R.~Apostolov, M.R.
-  Shirts, J.C. Smith, P.M. Kasson, D.~van~der Spoel, and Hess B.~Lindahl E.
-\newblock Gromacs 4.5: a high-throughput and highly parallel open source
-  molecular simulation toolkit.
-\newblock {\em Bioinformatics}, pages 1--10, 2013.
-
-\bibitem{parrinello1981polymorphic}
-M.~Parrinello and A.~Rahman.
-\newblock Polymorphic transitions in single crystals: A new molecular dynamics
-  method.
-\newblock {\em Journal of Applied Physics}, 52:7182, 1981.
-
-\bibitem{schuette2011markov}
-C.~Sch{\"u}tte, F.~No{\'e}, J.~Lu, M.~Sarich, and E.~Vanden-Eijnden.
-\newblock Markov state models based on milestoning.
-\newblock {\em The Journal of Chemical Physics}, 134:204105, 2011.
-
-\bibitem{scovell2000phase}
-Dawn~L Scovell, Tim~D Pinkerton, Valentin~K Medvedev, and Eric~M Stuve.
-\newblock Phase transitions in vapor-deposited water under the influence of
-  high surface electric fields.
-\newblock {\em Surface science}, 457(3):365--376, 2000.
-
-\bibitem{vogel2008femtosecond}
-A.~Vogel, N.~Linz, S.~Freidank, and G.~Paltauf.
-\newblock Femtosecond-laser-induced nanocavitation in water: implications for
-  optical breakdown threshold and cell surgery.
-\newblock {\em Physical review letters}, 100(3):38102, 2008.
-
-\bibitem{vitalini2013speed}
-F.~Vitalini, A.S.J.S. Mey, F.~No\'e, and B.G. Keller.
-\newblock The speed of force fields.
-\newblock {\em unpublished}, 2013.
-
-\end{thebibliography}
+\bibliography{ref}{}
+\bibliographystyle{unsrt}
+
+% \begin{thebibliography}{10}
+
+% \bibitem{bohr2000microwave}
+% Henrik Bohr and Jakob Bohr.
+% \newblock Microwave-enhanced folding and denaturation of globular proteins.
+% \newblock {\em Physical Review E}, 61(4):4310, 2000.
+
+% \bibitem{bohr2000microwave-1}
+% Henrik Bohr and Jakob Bohr.
+% \newblock Microwave enhanced kinetics observed in ord studies of a protein.
+% \newblock {\em Bioelectromagnetics}, 21(1):68--72, 2000.
+
+% \bibitem{dePomerai2000cell}
+% David de~Pomerai, Clare Daniells, Helen David, Joanna Allan, Ian Duce, Mohammed
+%   Mutwakil, David Thomas, Phillip Sewell, John Tattersall, Don Jones, and Peter
+%   Candido.
+% \newblock Cell biology: Non-thermal heat-shock response to microwaves.
+% \newblock {\em Nature}, 405:417--418, 2000.
+
+% \bibitem{inskip2001cellular}
+% Peter~D Inskip, Robert~E Tarone, Elizabeth~E Hatch, Timothy~C Wilcosky,
+%   William~R Shapiro, Robert~G Selker, Howard~A Fine, Peter~M Black, Jay~S
+%   Loeffler, and Martha~S Linet.
+% \newblock Cellular-telephone use and brain tumors.
+% \newblock {\em New England Journal of Medicine}, 344(2):79--86, 2001.
+
+% \bibitem{mancinelli2004non}
+% Fabrizio Mancinelli, Michele Caraglia, Alberto Abbruzzese, Guglielmo
+%   d'Ambrosio, Rita Massa, and Ettore Bismuto.
+% \newblock Non-thermal effects of electromagnetic fields at mobile phone
+%   frequency on the refolding of an intracellular protein: Myoglobin.
+% \newblock {\em Journal of cellular biochemistry}, 93(1):188--196, 2004.
+
+% \bibitem{budi2005electric}
+% A.~Budi, F.S. Legge, H.~Treutlein, and I.~Yarovsky.
+% \newblock Electric field effects on insulin chain-b conformation.
+% \newblock {\em The Journal of Physical Chemistry B}, 109(47):22641--22648,
+%   2005.
+
+% \bibitem{budi2007effect}
+% A.~Budi, F.S. Legge, H.~Treutlein, and I.~Yarovsky.
+% \newblock Effect of frequency on insulin response to electric field stress.
+% \newblock {\em The Journal of Physical Chemistry B}, 111(20):5748--5756, 2007.
+
+% \bibitem{budi2008comparative}
+% Akin Budi, F~Sue Legge, Herbert Treutlein, and Irene Yarovsky.
+% \newblock Comparative study of insulin chain-b in isolated and monomeric
+%   environments under external stress.
+% \newblock {\em The Journal of Physical Chemistry B}, 112(26):7916--7924, 2008.
+
+% \bibitem{toschi2008effects}
+% Francesca Toschi, Francesca Lugli, Fabio Biscarini, and Francesco Zerbetto.
+% \newblock Effects of electric field stress on a $\beta$-amyloid peptide.
+% \newblock {\em The Journal of Physical Chemistry B}, 113(1):369--376, 2008.
+
+% \bibitem{astrakas2011electric}
+% Loukas Astrakas, Christos Gousias, and Margaret Tzaphlidou.
+% \newblock Electric field effects on chignolin conformation.
+% \newblock {\em Journal of Applied Physics}, 109(9):094702--094702, 2011.
+
+% \bibitem{astrakas2012structural}
+% Loukas~G Astrakas, Christos Gousias, and Margaret Tzaphlidou.
+% \newblock Structural destabilization of chignolin under the influence of
+%   oscillating electric fields.
+% \newblock {\em Journal of Applied Physics}, 111(7):074702--074702, 2012.
+
+% \bibitem{damm2012can}
+% Markus Damm, Christoph Nusshold, David Cantillo, Gerald~N Rechberger, Karl
+%   Gruber, Wolfgang Sattler, and C~Oliver Kappe.
+% \newblock Can electromagnetic fields influence the structure and enzymatic
+%   digest of proteins? a critical evaluation of microwave-assisted proteomics
+%   protocols.
+% \newblock {\em Journal of proteomics}, 75:5533--5543, 2012.
+
+% \bibitem{starzyk2013proteins}
+% A.~Starzyk and M.~Cieplak.
+% \newblock Proteins in the electric field near the surface of mica.
+% \newblock {\em The Journal of Chemical Physics}, 139:045102, 2013.
+
+% \bibitem{english2009nonequilibrium}
+% N.J. English, G.Y. Solomentsev, and P.~O'Brien.
+% \newblock Nonequilibrium molecular dynamics study of electric and low-frequency
+%   microwave fields on hen egg white lysozyme.
+% \newblock {\em The Journal of chemical physics}, 131:035106, 2009.
+
+% \bibitem{solomentsev2012effects}
+% G.Y. Solomentsev, N.J. English, and D.A. Mooney.
+% \newblock Effects of external electromagnetic fields on the conformational
+%   sampling of a short alanine peptide.
+% \newblock {\em Journal of Computational Chemistry}, 33:917--923, 2012.
+
+% \bibitem{ciccotti1975direct}
+% G~Ciccotti and G~Jacucci.
+% \newblock Direct computation of dynamical response by molecular dynamics: The
+%   mobility of a charged lennard-jones particle.
+% \newblock {\em Physical Review Letters}, 35(12):789, 1975.
+
+% \bibitem{ciccotti1979thought}
+% G.~Ciccotti, G.~Jacucci, and I.R. McDonald.
+% \newblock "thought-experiments" by molecular dynamics.
+% \newblock {\em Journal of Statistical Physics}, 21(1):1--22, 1979.
+
+% \bibitem{ciccotti1993theoretical}
+% G.~Ciccotti, C.~Pierleoni, and J.P. Ryckaert.
+% \newblock Theoretical foundation and rheological application of non-equilibrium
+%   molecular dynamics.
+% \newblock In {\em Microscopic simulations of complex hydrodynamic phenomena},
+%   pages 25--45. Plenum Press, 1993.
+
+% \bibitem{palla2008bulk}
+% P.L. Palla, C.~Pierleoni, and G.~Ciccotti.
+% \newblock Bulk viscosity of the lennard-jones system at the triple point by
+%   dynamical nonequilibrium molecular dynamics.
+% \newblock {\em Physical Review E}, 78(2):021204, 2008.
+
+% \bibitem{orlandini2011hydrodynamics}
+% S.~Orlandini, S.~Meloni, and G.~Ciccotti.
+% \newblock Hydrodynamics from statistical mechanics: combined dynamical-nemd and
+%   conditional sampling to relax an interface between two immiscible liquids.
+% \newblock {\em Phys. Chem. Chem. Phys.}, 13:13177--13181, 2011.
+
+% \bibitem{orlandini2011hydrodynamics-01}
+% Sergio Orlandini, Simone Meloni, and Giovanni Ciccotti.
+% \newblock Hydrodynamics from dynamical non-equilibrium md.
+% \newblock In {\em AIP Conference Proceedings}, volume 1332, page~77, 2011.
+
+% \bibitem{delaHoz2005microwaves}
+% Antonio de~la Hoz, Angel Diaz-Ortiz, and Andres Moreno.
+% \newblock Microwaves in organic synthesis. thermal and non-thermal microwave
+%   effects.
+% \newblock {\em Chemical Society Reviews}, 34(2):164--178, 2005.
+
+% \bibitem{pronk2013gromacs}
+% S.~Pronk, S.~P{\'a}ll, R.~Schulz, P.~Larsson, P.~Bjelkmar, R.~Apostolov, M.R.
+%   Shirts, J.C. Smith, P.M. Kasson, D.~van~der Spoel, and Hess B.~Lindahl E.
+% \newblock Gromacs 4.5: a high-throughput and highly parallel open source
+%   molecular simulation toolkit.
+% \newblock {\em Bioinformatics}, pages 1--10, 2013.
+
+% \bibitem{parrinello1981polymorphic}
+% M.~Parrinello and A.~Rahman.
+% \newblock Polymorphic transitions in single crystals: A new molecular dynamics
+%   method.
+% \newblock {\em Journal of Applied Physics}, 52:7182, 1981.
+
+% \bibitem{schuette2011markov}
+% C.~Sch{\"u}tte, F.~No{\'e}, J.~Lu, M.~Sarich, and E.~Vanden-Eijnden.
+% \newblock Markov state models based on milestoning.
+% \newblock {\em The Journal of Chemical Physics}, 134:204105, 2011.
+
+% \bibitem{scovell2000phase}
+% Dawn~L Scovell, Tim~D Pinkerton, Valentin~K Medvedev, and Eric~M Stuve.
+% \newblock Phase transitions in vapor-deposited water under the influence of
+%   high surface electric fields.
+% \newblock {\em Surface science}, 457(3):365--376, 2000.
+
+% \bibitem{vogel2008femtosecond}
+% A.~Vogel, N.~Linz, S.~Freidank, and G.~Paltauf.
+% \newblock Femtosecond-laser-induced nanocavitation in water: implications for
+%   optical breakdown threshold and cell surgery.
+% \newblock {\em Physical review letters}, 100(3):38102, 2008.
+
+% \bibitem{vitalini2013speed}
+% F.~Vitalini, A.S.J.S. Mey, F.~No\'e, and B.G. Keller.
+% \newblock The speed of force fields.
+% \newblock {\em private communication}, 2013.
+
+% \end{thebibliography}
 

### 2014-02-21 alanine.nanma/template/tools/angles/app/average.traj.metastable.cpp
implement statistical error in metastable calculation. not fully tested

@@ -14,6 +14,7 @@
 
 #include "Defines.h"
 #include "Distribution.h"
+#include "BlockAverage.h"
 #include <boost/program_options.hpp>
 namespace po = boost::program_options;
 using namespace std;
@@ -72,13 +73,13 @@ void depositMetastable (const double & phi,
 int main(int argc, char * argv[])
 {
   std::string ifile, ofile;
-  // unsigned numBlock = 20;
+  unsigned numDataBlock = 20;
   // double refh;
   // float time_prec = .01;
-  double setA_psi_b = 128, setA_psi_e = 13;
-  double setA_phi_b =-125, setA_phi_e = 74;
-  double setB_psi_b = 128, setB_psi_e = 13;
-  double setB_phi_b = 74,  setB_phi_e =-125;
+  // double setA_psi_b = 128, setA_psi_e = 13;
+  // double setA_phi_b =-125, setA_phi_e = 74;
+  // double setB_psi_b = 128, setB_psi_e = 13;
+  // double setB_phi_b = 74,  setB_phi_e =-125;
   double setC_psi_b = 13,  setC_psi_e = 128;
   double setC_phi_b = -180,setC_phi_e = 180;
   
@@ -95,6 +96,7 @@ int main(int argc, char * argv[])
   po::options_description desc ("Allow options");
   desc.add_options()
       ("help,h", "print this message")
+      ("numDataBlock,n", po::value<unsigned > (&numDataBlock)->default_value (1000), "number of data in each block")
       ("output,o", po::value<std::string > (&ofile)->default_value ("metastable.out"), "the output of metastable propulation")
       ("input,f",  po::value<std::string > (&ifile)->default_value ("angle.name"), "the file of file names");
 
@@ -127,7 +129,7 @@ int main(int argc, char * argv[])
   float time;
   ValueType phi, psi;
   vector<float > times;
-  vector<vector<double > > counts;
+  vector<vector<BlockAverage_acc > > avgs;
   unsigned countFile = 0;
 
   while (fpname.getline(nameline, MaxLineLength)){
@@ -144,7 +146,14 @@ int main(int argc, char * argv[])
       while (myread(fp, time, phi, psi)){
 	times.push_back (time);
 	depositMetastable (psi, phi, sets, tmpcount);
[…]

### 2014-02-24 writedown/npt-neq/alanine.tex
change to the paper and add reply

@@
 \newcommand{\period}[0]{T_{\textrm{P}}}
+
+\newcommand{\confaa}[0]{{\alpha_{\textrm{R}}}}
+\newcommand{\confab}[0]{{\alpha_{\textrm{R}}'}}
+\newcommand{\confba}[0]{{\textrm{C}7_{\textrm{eq}}}}
+\newcommand{\confbb}[0]{{\textrm{C}5}}
+\newcommand{\confc}[0]{{\alpha_{\textrm{L}}}}
 
@@
 temperature control technique.  The
-time step was $\Delta t = 0.002~\textsf{ps}$.
+time step was $0.002~\textsf{ps}$.
 \recheck{The short-range
@@
   \centering
-  \includegraphics[width=1.00\textwidth]{fig-all.eps}
+  \includegraphics[width=1.00\textwidth]{fig.ala.new/fig.all/fig-all.eps}
   % \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{c-2.eps}}
@@
     to 5 molecular conformations:
-    $A_1 = \{(\phi, \psi) | -134^\circ \leq \phi <  13^\circ, -125^\circ \leq \psi < 74^\circ\}$,
-    $A_2 = \{(\phi, \psi) |  128^\circ \leq \phi < 226^\circ, -125^\circ \leq \psi < 74^\circ\}$,
-    $B_1 = \{(\phi, \psi) | -110^\circ \leq \phi <  13^\circ,   74^\circ \leq \psi < 235^\circ\}$,
-    $B_2 = \{(\phi, \psi) |  128^\circ \leq \phi < 250^\circ,   74^\circ \leq \psi < 235^\circ\}$,
-    $C   = \{(\phi, \psi) |   13^\circ \leq \phi < 128^\circ, -180^\circ \leq \psi < 180^\circ\}$.
+    $\confaa = \{(\phi, \psi) | -134^\circ \leq \phi <  13^\circ, -125^\circ \leq \psi < 74^\circ\}$,
+    $\confab = \{(\phi, \psi) |  128^\circ \leq \phi < 226^\circ, -125^\circ \leq \psi < 74^\circ\}$,
+    $\confba = \{(\phi, \psi) | -110^\circ \leq \phi <  13^\circ,   74^\circ \leq \psi < 235^\circ\}$,
+    $\confbb = \{(\phi, \psi) |  128^\circ \leq \phi < 250^\circ,   74^\circ \leq \psi < 235^\circ\}$,
+    $\confc   = \{(\phi, \psi) |   13^\circ \leq \phi < 128^\circ, -180^\circ \leq \psi < 180^\circ\}$.
     Considering the angular periodicity, the angle, for example, $226^\circ$ corresponds to $-134^\circ$
@@
 Therefore, in order to simplify the analysis, we divide the
-Ramachandran plot into 5 subregions $\{A_1, A_2, B_1, B_2, C\}$
+Ramachandran plot into 5 subregions $\{\confaa, \confab, \confba, \confbb, \confc\}$
 (see caption of Fig.~\ref{fig:tmp4} for the corresponding definition).
@@
 are found in different secondary structures of a peptide chain:
-$A_1$ and $A_2$ are
-corresponding to the $\alpha$-helix. $B_1$ and $B_2$ are
-corresponding to the $\beta$-sheet. $C$ is corresponding to the
+$\confaa$ and $\confab$ are
+corresponding to the $\alpha$-helix. $\confba$ and $\confbb$ are
+corresponding to the $\beta$-sheet. $\confc$ is corresponding to the
 left-handed $\alpha$-helix.
@@
 conformation occurs changes when the external EF is applied.
-The most evident case is conformation $C$; in fact it is {almost} not present before the external field is applied but appears in a clear way as a response to the action of the EF.
+The most evident case is conformation $\confc$; in fact it is {almost} not present before the external field is applied but appears in a clear way as a response to the action of the EF.
 Following this line of thought, we are interested to study the change of conformation under the action of EF.
@@
 \begin{align}
-  P_I(t) = \mathbb P ( (\phi_t,\psi_t) \in I), \quad  I \in \{A_1, A_2, B_1, B_2, C\},
+  P_I(t) = \mathbb P ( (\phi_t,\psi_t) \in I), \quad  I \in \{\confaa, \confab, \confba, \confbb, \confc\},
 \end{align}
@@
   \bigg], \\\label{eqn:tmp7}
-  & J,I \in \{A_1, A_2, B_1, B_2, C\}.
+  & J,I \in \{\confaa, \confab, \confba, \confbb, \confc\}.
 \end{align}
@@
 estimated with sufficient numerical accuracy (see also Ref.~\cite{schuette2011markov}).
+\recheck{In all the numerical examples of this work, $\Delta t = 1$~ps is used}.
 A positive value of $F_{J,I}(t)$ indicates that the
@@
 Through $F_{J,I}(t)$, the analysis of the nonequilibrium process 
-is projected onto the analysis of the probabilistic link between discretized conformations $\{A_1, A_2, B_1, B_2, C\}$.
+is projected onto the analysis of the probabilistic link between discretized conformations $\{\confaa, \confab, \confba, \confbb, \confc\}$.
+
+\recheck{ The definition of the probability flux is similar to the
+  kinetic rate.  However, we want to stress that, in general, the
+  probability flux should not be interpreted as a kinetic rate, and
+  one cannot replace the nonequilibrium molecular dynamics by a
+  kinetic analysis. The main reason is, firstly, that the nonequilibrium
+  nature of the problem asks for a small time interval $\Delta t$ so that the probability flux is well defined.
+  Secondly, within the small
+  time interval (we use 1~ps), the conformational
+  dynamics of alanine dipeptide is generally not Markovian~\cite{schuette2011markov, prinz2011markov},
+  therefore, a direct application of the kinetic
+  analysis is questionable.
+  % Since the main goal of our research is to propose a
+  % nonequilibrium molecular dynamics simulation method, the numerical
+  % results will not be compared with the kinetic analysis.
+}
+
 In the case of oscillatory EF, the behaviour of the net probability flux is also highly oscillatory, thus, in order to clearly identify the essential features of the molecular conformational changes, it is convenient to study the integrated net probability flux, defined as:
@@
 
-\recheck{ The definition of the probability flux is similar to the
-  kinetic rate.  However, we want to stress that, in genarl, the
-  probability flux should not be interpreted as a kinetic rate, and
-  one cannot replace the nonequilibrium molecular dynamics by a
-  kinetic analysis. The main reason is that the conformational
-  dynamics of alanine dipeptide is generally not Markovian for a small
-  time interval $\Delta t$~\cite{prinz2011markov}, therefore, a direct application of the kinetic
-  analysis is questionable. Since the main goal of our research is to propose a
-  nonequilibrium molecular dynamics simulation method, the numerical
-  results will not be compared with a kinetic analysis.
-}
-
 \subsection{Conformational dynamics}
@@
   \centering
-  \includegraphics[]{fig.ala.new/fig-meta-npt.eps}
+  \includegraphics[]{fig.ala.new/fig-meta-more.eps}
   \caption{The time-dependent probability of conformations $P_I(t)$ 
     when a constant EF is present, where $\sum_I P_I(t) = 1, \forall t$.
-    The warm-up time is $t_{warm} = 10$~ps. The red line refers to conformation $I = A_1$,
-    green to $A_2$, dark blue to $B_1$, purple to $B_2$ and light blue
-    to $C$. 
+    The warm-up time is $t_{warm} = 10$~ps. The red line refers to conformation $I = \confaa$,
+    green to $\confab$, dark blue to $\confba$, purple to $\confbb$ and light blue
+    to $\confc$. \recheck{
+      The solid lines denote the results of one branching trajectory
+      starting from each initial conformation, while the dashed lines denote
+      the results of four branching trajectories (different random seeds for the Langevin thermostat) starting from each initial
+      conformation.
+      The shadow region with each solid line denotes the
+      statistical uncertainty of the result at 95\% confidence level.
+    }
   }
@@
     The probability flux $F_{J,I}(t)$ (defined by Eqn.~\eqref{eqn:tmp7}) is reported in units of $\textrm{ps}^{-1}$.
-    From top, left to right we report $I = A_1$, $A_2$, $B_1$; bottom, left to right $B_2$ and
-    $C$, respectively. In each plot, the red line stands for $J=A_1$,
-    green for $J=A_2$, dark blue for $J=B_1$, purple for $J=B_2$ and light blue
-    for $J=C$.
+    From top, left to right we report $I = \confaa$, $\confab$, $\confba$; bottom, left to right $\confbb$ and
+    $\confc$, respectively. In each plot, the red line stands for $J=\confaa$,
+    green for $J=\confab$, dark blue for $J=\confba$, purple for $J=\confbb$ and light blue
+    for $J=\confc$.
     }
@@
 conformation is given in
-Fig.~\ref{fig:tmp5}. The $\beta$-sheet conformations $B_1$ and $B_2$,
+Fig.~\ref{fig:tmp5}.
+\recheck{The simulation results of starting one branching trajectory
+  from each initial conformation are compared with those starting
+  four branching trajectories from each initial conformation (each with
+  different random seed for the Langevin thermostat).
+  They are consistent within the statistical uncertainty, which
+  means our simulation result is robust with respect to the randomness
+  introduced by the (local) Langevin thermostat.
+}
+The $\beta$-sheet conformations $\confba$ and $\confbb$,
 which are present at the initial stage after EF is switched on,
-fade away as the system relaxes to the new equilibrium. The
-probability of the $\alpha$-helix conformation $A_1$, grows from 0.45 to 0.69.
-The $\alpha$-helix $A_2$  does not change significantly  under the action of EF.
-The left-hand helix conformation $C$ noticeably grows from 0 to 0.22.
+\recheck{fade away as the system relaxes}. The
+probability of the $\alpha$-helix conformation $\confaa$, grows from 0.45 to 0.69.
+The $\alpha$-helix $\confab$  does not change significantly  under the action of EF.
+The left-hand helix conformation $\confc$ noticeably grows from 0 to 0.22.
 We plot the net probability fluxes in Fig.~\ref{fig:tmp6}.
-Results show that for short $t$, the net fluxes are generally non-zero, however, 
+Results show that for short $t$, the net fluxes are generally non-zero,
+however, 
 as $t$ goes to infinity,
@@
 equilibrium (at zero EF);  This is a nonequilibrium process.
-After a time long enough, the system
-is fully relaxed to the new equilibrium defined by the action of the constant EF,
-and stays there as long as the EF is kept.
+\recheck{After a time long enough, the system
+is fully relaxed to the new conformations,
+and stays there as long as the EF is kept. However, whether the new conformations
+are in the new equilibrium defined the constant EF is not clear, because
+there may exist very slow nonequilibrium processes, for example as long as 1~$\mu$s,
+which cannot be discovered by our nonequilibrium simulation of only 1~ns.
+What we can do by the proposed nonequilibrium simulation
+method is to study time-dependent behaviours that are no longer than
+the simulation time. 
+}
+% After a time long enough, the system
+% is fully relaxed to the new equilibrium defined by the action of the constant EF,
+% and stays there as long as the EF is kept.
 An important point is that despite the system is finally relaxed to the new conformation,
@@
     Direction        & time scale [ ps ] \\\hline
-    $A_1\rightarrow A_2$        &       $\sim 10$      \\
-    % $B_1\rightarrow B_2$        &       $\sim 10$      \\    
-    $B_2\rightarrow A_1,\ A_2,\ C$        &       $\sim 50$      \\    
-    $A_2\rightarrow A_1$        &       $\sim 100$      \\
-    $B_2\rightarrow B_1$        &       $\sim 100$      \\    
-    $B_1\rightarrow A_1,\ C$        &       $\sim 500$      \\    \hline\hline
+    $\confaa\rightarrow \confab$        &       $\sim 10$      \\
+    % $\confba\rightarrow \confbb$        &       $\sim 10$      \\    
+    $\confbb\rightarrow \confaa,\ \confab,\ \confc$        &       $\sim 50$      \\    
+    $\confab\rightarrow \confaa$        &       $\sim 100$      \\
+    $\confbb\rightarrow \confba$        &       $\sim 100$      \\    
+    $\confba\rightarrow \confaa,\ \confc$        &       $\sim 500$      \\    \hline\hline
   \end{tabular*}
@@
 under the constant EF, and they are 6.8, 6.0, 5.1, 3.1 and 7.1~Debye
-for $A_1$, $A_2$, $B_1$, $B_2$ and $C$, respectively.
+for $\confaa$, $\confab$, $\confba$, $\confbb$ and $\confc$, respectively.
 The dipole energy difference between 3.1 and 7.1~Debye is roughly 8.0~kJ/mol.
@@
 are driven towards $\alpha$-helix conformations
-$A_1$ and $C$, whose dipole moments are the highest
-among all conformations. Moreover, the $B_2$ conformation vanishes because
+$\confaa$ and $\confc$, whose dipole moments are the highest
+among all conformations. Moreover, the $\confbb$ conformation vanishes because
 its dipole is significantly lower than other conformations.
@@
   the sharp increment of dipole moment before 20~ps is due to the quick vanishing of conformation
-  $B_2$, while the slow increment of dipole moment until 400~ps is due to
-  the slow migration from conformation $B_1$ to $A_1$ and $C$.
+  $\confbb$, while the slow increment of dipole moment until 400~ps is due to
+  the slow migration from conformation $\confba$ to $\confaa$ and $\confc$.
   % \textit{NOTE: here we want to discuss the relation between
@@
 % From 0 to 20~ps, the probability of
-% lowest dipole conformation $B_2$ quickly
+% lowest dipole conformation $\confbb$ quickly
 % vanishes. We observe a sharp increment of the average molecular dipole and finally, approaching  500~ps, the conformation slowly migrates from
-% $B_1$ to $A_1$ and $C$. Moreover, since the dipole moment $A_1$ and $C$
-% is higher than $B_1$, the average molecular dipole moment slowly increases
+% $\confba$ to $\confaa$ and $\confc$. Moreover, since the dipole moment $\confaa$ and $\confc$
+% is higher than $\confba$, the average molecular dipole moment slowly increases
 % to the nonequilibrium steady value.
@@
     See the text for more details.
+    \recheck{The shadow region denotes the
+      statistical uncertainty of the $L=2.7$~nm $R_{ex}=1.0$~nm case at 95\% confidence level.
+    }
   }
@@
     denoted by $P_I$ in this paper, is plotted by colored lines against
-    time. Red line: $I = A_1$,  green line: $I = A_2$,  dark
-    blue line: $I = B_1$,  pink line: $I = B_2$ and  light blue
-    line: $I = C$. For $\period =10$~ps and 40~ps, the nonequilibrium
+    time. Red line: $I = \confaa$,  green line: $I = \confab$,  dark
+    blue line: $I = \confba$,  pink line: $I = \confbb$ and  light blue
+    line: $I = \confc$. For $\period =10$~ps and 40~ps, the nonequilibrium
     simulations last 1000~ps, while for $\period =200$~ps,
@@
     From left to right, the five
-    columns show the integrated flux $Q_{J,A_1}$, $Q_{J,A_2}$,
-    $Q_{J,B_1}$, $Q_{J,B_2}$ and $Q_{J,C}$, respectively. In each plot,
-    the red line stands for $J=A_1$, green for $J=A_2$, dark blue for $J=B_1$,
-    purple for $J=B_2$ and light blue for $J=C$.
+    columns show the integrated flux $Q_{J,\confaa}$, $Q_{J,\confab}$,
+    $Q_{J,\confba}$, $Q_{J,\confbb}$ and $Q_{J,\confc}$, respectively. In each plot,
+    the red line stands for $J=\confaa$, green for $J=\confab$, dark blue for $J=\confba$,
+    purple for $J=\confbb$ and light blue for $J=\confc$.
     An increasing value of $Q_{J,I}$ indicates a net probability
@@
 Coming back to Fig.~\ref{fig:tmp9}, for all periods investigated,
-the observed time-dependent probabilities  in $A_1$, $A_2$, $B_1$ and $B_2$ are
+the observed time-dependent probabilities  in $\confaa$, $\confab$, $\confba$ and $\confbb$ are
 highly oscillating and the average value over time cycles does not change
 considerably w.r.t.~time.
-However, the probability in conformation $C$ significantly
+However, the probability in conformation $\confc$ significantly
 increases to approximately 0.17 for $\period =10$~ps, 0.27 for  $\period =40$~ps, and
 0.26 for $\period =200$~ps.
-In the case of $\period =10$ and $40$~ps, {the probability of conformation $C$}
+In the case of $\period =10$ and $40$~ps, {the probability of conformation $\confc$}
 reaches the steady value in around 300~ps, while it requires about 1200~ps
 for the $\period =200$~ps case. 
-The notable increment of probability of $A_1$ and
-  the vanishing of $B_1$ in the constant EF case (see Fig.~\ref{fig:tmp5})
+The notable increment of probability of $\confaa$ and
+  the vanishing of $\confba$ in the constant EF case (see Fig.~\ref{fig:tmp5})
 are not observed in the oscillatory EF case.
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{graph-t0010-2.eps}
+  \includegraphics[width=0.6\textwidth]{fig.ala.new/graphs/graph-t0010-2.eps}
   \caption{Schematic plot of the main probability flux between conformations
@@
 the steady value of average net fluxes over periods.
-{
 The relevance of Fig.~\ref{fig:tmp11} is in the fact that it suggests,
@@
 conformations and how an electric field is likely to modify it.
+\recheck{
+  Although the conformational transitions presented Fig.~\ref{fig:tmp11} are studied under
+  the nonequilibrium scenario, it is actually qualitatively similar to those
+  discovered in the equilibrium studies, e.g.~\cite{apostolakis1999calculation, gfeller2007complex}.
 }
@@
 comparable to the case $\period =10$~ps, except that the probability fluxes
-going into conformation $C$ is stronger, which actually results in
-a higher steady probability in $C$.
+going into conformation $\confc$ is stronger, which actually results in
+a higher steady probability in $\confc$.
 The probability flux of case $\period =200$~ps is qualitatively
@@
 Moreover, 
-  we see that the integrated fluxes $Q_{A_2,A_1}$ and $Q_{B_1,A_2}$ reach
+  we see that the integrated fluxes reach
   a steadily
 increasing stage after about 3200~ps, which is even longer than the time scale
-at which the probability of $C$ reaches its steady value. This indicates
+at which the probability of $\confc$ reaches its steady value. This indicates
 a longer intrinsic time scale in the $\period =200$~ps case.
@@
 the surface of mica~\cite{starzyk2013proteins}, or by a modern laser
-equipment~\cite{vogel2008femtosecond}. The authors are fully aware
+equipment~\cite{vogel2008femtosecond}.
+\recheck{The minimal frequency investigated here (5.00~GHz, i.e.~$\period = 200$~ps)
+is of the same order of magnitude as the microwave
+irradiation available in laboratory (2.45~GHz). }
+The authors are fully aware
 that the EFs investigated in the present paper are, at this stage, still ideal, above all regarding their spatially homogeneity and
@@
 \section*{Acknowledgment}
-  H.W. acknowledges the valuable discussions with Simone Meloni.
+  H.W. acknowledges the valuable discussions with Simone Meloni and Burkhard Schmidt.
   This work was partially supported by the Deutsche

### 2014-02-24 writedown/npt-neq/reply/reply.tex
change to the paper and add reply

\documentclass[]{revtex4-1}

\usepackage[fleqn]{amsmath}
\usepackage{amssymb,amsthm}
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{tabularx}

\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{blue} #1}}
\newcommand{\greenc}[1]{{\color{green} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\dd}[1]{\textsf{#1}}
\newcommand{\fwd}[0]{\textrm{fwd}}
\newcommand{\bwd}[0]{\textrm{bwd}}
\newcommand{\period}[0]{T_{\textrm{P}}}

\begin{document}

\section*{The scientific issues from referee 1}

\emph{On a principle level I am not sure that the relevant scientific
  question is really the non-equilibrium response since the response
  to the external field -- as the authors note -- is indeed quite
  fast. In fact, most of the discussion in the paper is focused on
  what I think could have been extracted just as well from
  conventional equilibrium simulations (conformational shifts,
  kinetics).}\\

The non-equilibrium responses in the paper are discussed in two
different senses: 1, the perturbation to the system is
time-independent.
The relaxation of the system to the new equilibrium
defined by the constant perturbation is non-equilibrium.
% However,
% after the new equilibrium is established, there is no non-equilibrium
% process in the system.
The first example of the manuscript is in this sense.  2, the
perturbation is time-dependent.  The second example in the manuscript
is in this sense.  The first sense is only a special case of the
sencond sense.  In the first sense, the system can be studied by
equilibrium methods such as the Markov state model (MSM). However, the
equilibrium methods are NOT applicable in the second sense.  The
present paper develops a non-equilibrium molecular dynamics simulation
method that is more general in the sense that it is applicable to the
aformentioned two senses. Therefore, the proposed method cannot be replaced
by the equilibrium methods such as MSM.

Another commenly used equilibrium method that is able to study the non-equilibrium
responses is the linear responses thoery (Green-Kubo relation).
We also use it to test the
conformational shift of alanine dipeptide under the electric field
(EF). The response function, take the time-dependent probability of
left-handed $\alpha$-helix (Conformation $C$ in the old manuscript. The notation has been changed to $\alpha_L$ in the updated manuscript.) for example, is defined as
\begin{align}\label{eqn:tmp1}
  P_C(t) = \langle\chi_{_C}(t)\rangle = \langle \chi_{_C} \rangle_0 -
  \beta \int_0^t ds\; M_e(t - s)\langle j(0)\cdot \chi_{_C}(t) \rangle_0
\end{align}
where $\chi_{_C}$ is the characteristic function of set $C$ that takes
the value of 1 for $(\phi,\psi)\in C$, and takes value 0
otherwise. $M_e(t)$ is the magnitude of the EF. In the case of
constant EF, $M_e(t) = t/t_{warm}$ for $0\leq t<t_{warm}$, and
$M_e(t) = 1$ for $t\geq t_{warm}$.
$j$ is the dissipative flux that is defined by
\begin{align}
  j = - \sum_{i=1}^N E_\infty q_i v_{i,x},
\end{align}
where $q_i$ is the partial charge of the $i$th atom, and $v_{i,x}$ is
the $x$ component of the velocity of the $i$th atom.  The notation
$\langle\cdot\rangle_0$ denotes the equilibrium ensemble average.
Eq.~\eqref{eqn:tmp1} can be found in the text books of statistical
mechanics (e.g.~M.~Tuckerman \emph{Statistical Mechanics: Theory and
  Molecular Simulation}, pp.~499).  We plot the correlation function
$\langle j(0)\cdot \chi_{_C}(t) \rangle_0$ against corrlation time $t$
in Fig.~\ref{fig:tmp1} of this reply. The value of the function is estimated from
two independent equilibrium simulation, and the trajactory of each is
of 1~$\mu$s. Please note that the total length of the equilibrium
trajactories is the same as the non-equilibrium simulation (2000
trajactories, each 1000~ps long).
% With the knowledge of
% non-equilibrium simulation, the correlation function is expected to
% vanish at roughly 500~ps, however, it does not vanish even at
% 1000~ps. This is not surprising, because
We find that the statistical error is even larger than the value of
corrlation function.  Therefore, the
overwhelming statistical uncertainty does not allow us to use it 
in Eq.~\eqref{eqn:tmp1} to calculate the
non-equilibrium averages. 
% , and we actually do not know when the
% corrlation function vanish .
Since the total computational effort of
the equilibrium simulation is the same as the non-equilibrium
simulation, we conclude that non-equilibrium simulatoin is more
precise than the conventional equilibrium approach (linear response) at the same computational cost.
A similar
observation has already been reported by Ciccotti and Jacucci, PRL
1975.
\\
% Another limit of the linear response theory is that it can only be
% used to calculate the non-equilibrium properties when the
% non-equilibrium purturbation to the system is small, and it is also
% impossible to tell \emph{a priori} if the purturbation is small enough
% that the response theory is valid. This issue also does not exist in
% our non-equilibrium simulation method.

\begin{figure}
  \centering
  \includegraphics{figs/fig-corr-meta.eps}
  \caption{The corrlation function $\langle j(0)\cdot \chi_{_C}(t)
    \rangle_0$ against time $t$. The error bars in the figure denote
    the statistical uncertainty at 95\% confidence level. }
  \label{fig:tmp1}
\end{figure}

\emph{
In the alanine dipeptide system studied here, I am not sure that the
initial simulation is in fact fully converged and -- if the question is
how conformational preferences evolve in response to an external field
-- whether the short branch simulations are long enough to establish
convergent sampling. More specifically, I think that the lack of
sampling of the left-handed helix in the absence of an electric field
is a result of insufficient sampling to cross the kinetic barrier from
beta to alphaL conformations (alanine dipeptide with CHARMM27 has been
extensively characterized and I suggest a comparison with relevant
papers from MacKerell et al.). If such relevant conformations are
missing from the initial snapshots and the branch simulations are
short I am concerned that the resulting initial bias affects the
non-equilibrium results.
}\\

We have done an equilibrium simulation of 1~$\mu$s.  On the
trajactory, molecular conformations are recored every 500~ps,
therefore, in total 2000 equilibrium conformations are recoreded.  The
equilibrium probabilities of the conformations $A_1$, $A_2$, $B_1$,
$B_2$ and $C$ are 0.426 ($\pm 0.029$), 0.076 ($\pm 0.010$), 0.265
($\pm 0.013$), 0.182 ($\pm 0.019$) and 0.051 ($\pm 0.021$),
respectively.  We have run two addtional equilibrium simulations of
1~$\mu$s, and the probabilities of conformations are consistent with
the values listed above, which means that our new equilibrium
simulation is fully converged.  Comparing with our previous
equilibrium simulation (only 0.1~$\mu$s long),
% in which the
% probability of left-handed $\alpha$-helix is only 0.008,
the precision
of initial configuration sampling is substantially improved. All
simulations in the manuscript are reperformed according to the new set
of initial conformations, however, the strand of all time-dependent
observables are the same as the old simulation, and no change to the
conclusions is made.
% The difference between the new and the old
% results is no more than 0.05, which is basically within the
% statistical uncertainty (given in the new manuscript).

We also test the convergence of simulation result with respect to the
number of branching trajactories.  The time-dependent probabilities of
each conformation calculated from one branching trajactory is compared
with four braching trajactories (each of them is simulated with
different random seed for Langevin thermostat) in
Fig.~\ref{fig:tmp2} of this reply. The results are consistent, which means that the
sampling of the non-equilibrium trajactories is fully converged. In
summary, since the our non-equilibrium simulation includes the
sampling of both initial configurations and non-equilibrium
trajactories, the convergence of both aspects implies the convergence
of our simulation results.

The question on whether our non-equilibrium braching trajactories are
long enough so that the results are fully converged is a very subtle
question. There may exists an intrisic time-scale of 1 microsecond
long, so we cannot discover it by braching trajactories of only a few
nanoseconds.  What we can do by the proposed non-equilibrium simulation
method is to study time-dependent behaviours that are no longer than
the simulation time. We have modified the manuscript according to
make this point clear. A similar difficulty actualy exists for all equilibrium
simulations: how do we know whether an equilibrium simulation is fully converged,
especially when some rare events cannot be observed during the limited simualtion time.
\\
% We want to stress that the target of the non-equilibrium simulation is
% to test how the populations of conformations evolve under the external
% electric field

\begin{figure}
  \centering
  \includegraphics{figs/fig-meta-more.eps}
  \caption{A comparison between the simulation with one branching
    trajectory per every initial conformation and four branching
    trajectories  for the
    constant EF case. Each of the four
    branching trajectories is simulated with a different random seed for
    Langevin thermostat.
    The shadow region presented with each line of the one-branching-trajectory case
    denotes its statistical uncertainty at 95\% confidence level.  }
  \label{fig:tmp2}
\end{figure}

\emph{ It looks as if the CMAP correction was used with the CHARMM
  force field but no information is given in the methods section.}\\

Yes, the CMAP correction is used. We mention it in the
section III.A. of the updated manuscript.
\\

\emph{
I am curious how the choice of Rex for the thermostat would affect the
results.
}\\

We compared the simulation results of two different $R_{ex}$ values:
1.0~nm and 1.5~nm in Fig.~7 (pp.15) of the manuscript. The
$R_{ex}=1.0$~nm case was simulated in periodic cubic simulation box
of length $L=2.7$~nm and 4.0~nm.  The $R_{ex}=1.5$~nm case was
simulated in cubic box of length $L=4.0$~nm. Fig.~7 of the
manuscript demonstrates that all of the results are consistent. That
means $R_{ex}=1.0$~nm is already large enough, and a larger $R_{ex}$
would not change the results.\\

\emph{ I wonder about the motivation of using electric fields with
  periods of 10, 40, and 200ps. How do such fields relate to the
  practical question of electromagnetic radiation exposure?  }\\

The periods 10, 40~ps are roughly the same as the first two shortest
time scales of probability fluxes observed in the constant EF case,
see Table~I of the manuscript. We tried to simulation with period of
500~ps, which is the same as the longest timescales of the constant EF
case, however, the required simulation time is so long that exceed our
computational capability. Therefore, we made a compromise that only
the period of 200~ps is studied. The typical frequency of the microwave
irradiation is 2450~MHz, which corresponds to period of 400~ps. It is
the same order of magnitude as the $T_P=200$~ps studied by us.
\\

\emph{ The analysis of ``probability fluxes'' seems to be nothing else
  than a kinetic analysis. Maybe some comments on how these are
  related would be helpful.  }\\

Yes, the definition of the probability fluxes is similar to the
kinetic rate (we use joint probabilities in (6) rather than
conditional probabilities). However, we want to stress that, in genarl,
the probability fluxes calculated in the manuscript should not be
interpreted as a kinetic rate, and one cannot replace the
non-equilibrium molecular dynamics by a kinetic analysis. The main
reason is two folds:
Firstly, for a non-equilibrium system, the probability fluxes are
time-dependent, therefore, the lag-time $\Delta t$ in the definition (Eq.~(6))
should be small comparing with the typical time-scale of conformation change.
Secondly, for a small lag time $\Delta t$ (1~ps in the manuscript), the conformational
dynamics of biomolecules is generally not
Markovian (see e.g.~C.~Sch\"utte et.~al.~JCP 2011 and J.-H.~Prinz et.~al.~JCP 2011).
Since the basic assumption -- Markovianity -- of the kinetic analysis
may not be satisfied, a direct
application of the kinetic analysis in the non-equilibrium cases is questionable. Although one may
gain usefuly information from the kinetic analysis, the reliability
and the effectiveness of this approach should be carefully checked case
by case.  Since the main goal of our research is to propose a
non-equilibrium molecular dynamics simulation method, the numerical
results are not compared with a kinetic analysis.

A comment on this direction has been added to the end of section III.B.
\\

\emph{Finally, given the apparent convergence issues with alanine
  dipeptide I have difficulties seeing how this method could be
  applied in a reasonable manner to more complex systems. Maybe some
  comments to that extent would be helpful.  }\\

Please see the reply to the seocond question concerning the convergence
of our simulation results. We believe that the better initial
state sampling and the new convergence check with respect to the
number of branching trajectories will strengthen the reliablity
of our method.
% manuscript and

% We have added a section in the appendix in the manuscript discussing
% the convergence and reliablity of our method. Please also see the
% answer to the 2nd question.

\section*{The scientific issues from referee 2}

\emph{
It would be useful if the authors would briefly comment on the
relationship between time-varying electric fields and terahertz
spectroscopy. Experimental work in this frequency range may be related
directly to the results reported here. See work by Plusquellic et al
(ChemPhysChem 2007), Havenith et al. (Faraday 2009) and others.
}\\

The frequency investigated in our manuscript is from 5~GHz to 100~GHz,
the largest of which is still one order of magnitude smaller than the
terahertz spectroscopy. Therefore, we find our simulation results
cannot be directly compared with the terahertz experiments.\\

\emph{ The procedure for controlling the temperature under neq
  conditions is reminiscent of the ``stochastic boundary conditions''
  introduced by Brooks and Karplus (JCP 1983). Can the authors provide
  a more formal description of their procedure and touch on
  similarities/dissimilarities with the Brooks/Karplus approach?  }\\

Yes, a comment and comparison on this direction has been added to the
manuscript.\\

\emph{ In the methods sections the treatment of H-involving bonds is
  not explained (SHAKE, RATTLE, ??). Also, a reference for the TIP3P
  model should be given. What cutoffs are required for an "energy
  conserving PME" simulation and how were the vdw interactions
  handled?  }\\

The asked details has been added to the manuscript.\\

\emph{
It is suggested to adapt the labeling of the conformational substates
of alanine dipeptide to that used in the literature ($C_7^{eq}$, $\alpha_L$,
$C_7^{ax}$, etc.) - see e.g. Caflisch et al., JCP 1999.
}\\

We have changed the labelling of conformations.\\

\emph{
The sentence ``..how the behaviour of the electric dipole moment of the
molecule is influenced..'' reads somewhat strange. Obviously, each of
the metastable states has its own dipole moment and this is reported
later on p. 12. However, there is no reason why the EF should
\emph{influence} the dipole moment as the simulations employ a force field
with fixed charges. It would probably be helpful to clarify that the
EF leads to ``conformational selection'' through alignment of the
molecular dipole along the EF.
}\\

We have made corresponding changes to the manuscript.\\

\emph{ It would be interesting to relate the probability fluxes from
  Fig 11 to the work by Rao et al. (PNAS 2007) and the Caflisch JCP
  1999 article. It should be possible to relate the probability fluxes
  to free energy differences.}\\

This is indeed a very interesting point. Although the Fig.11 is
plotted for the non-equilibrium oscillatory EF case, the
confromational transition pathways are qulitatively comparable to the
previous works on the transition pathways studied in equilibrium.
Both the connectivity of conformations and the relatively strength of
the transitions are similar. A short comment has been added to the
manuscript.

The transition fluxes can be used to calculate the free energy only in
the equilibrium case. In the non-equilibrium cased, especially the
oscillatory EF case, the conformational kinetics of the system is generally
not Markovian. Therefore, the standard kinetic analysis cannot be used
here.

\end{document}

### 2014-02-24 writedown/npt-neq/alanine.tex
revise

@@
 and how likely they are (probability).
+\recheck{
+  In the appendix of the paper, we also compare our nonequilibrium method with
+  the equilibrium linear response theory,
+  which is able to study the nonequilibrium properties
+  by only calculating equilibrium correlation functions.}
 To our knowledge, this study is one of the few (if not the first)  where
@@
   four branching trajectories from each initial conformation (each with
-  different random seed for the Langevin thermostat).
+  different random seed for the Langevin thermostat in the thermostated region).
   They are consistent within the statistical uncertainty, which
@@
 \recheck{
-  Although the conformational transitions presented Fig.~\ref{fig:tmp11} are studied under
-  the nonequilibrium scenario, it is actually qualitatively similar to those
-  discovered in the equilibrium studies, e.g.~\cite{apostolakis1999calculation, gfeller2007complex}.
+  Although the network presented Fig.~\ref{fig:tmp11} is similar to those
+  discovered in the equilibrium studies, e.g.~\cite{apostolakis1999calculation, gfeller2007complex}
+  in the sense of the steady conformations and connections among them,
+  the physical meaning is quit different in our study:
+  The system is under the nonequilibrium condition, and
+  the fluxes are lasting. In contrast,
+  such probability fluxes do not exist in the equilibrium case.
+  % Although the conformational transitions presented Fig.~\ref{fig:tmp11} are studied under
+  % the nonequilibrium scenario, it is actually qualitatively similar to those
+  % discovered in the equilibrium studies, e.g.~\cite{apostolakis1999calculation, gfeller2007complex}.
 }
@@
 
+  \appendix
+\section{Comparison with the linear response theory}  
+\recheck{
+A commenly used equilibrium method that is able to study the nonequilibrium
+responses is the linear responses thoery (Green-Kubo relation~\cite{green1954markoff,kubo1957statistical}).
+We also use it to test the
+conformational dynamics of alanine dipeptide under the EF.
+The response function, take the time-dependent probability of
+left-handed $\alpha$-helix for example, is defined as~\cite{tuckeman2010statistical}
+\begin{align}\label{eqn:appdx1}
+  P_\confc(t) = \langle\chi_{\confc}(t)\rangle = \langle \chi_{\confc} \rangle_0 -
+  \beta \int_0^t ds\; M_e(t - s)\langle j(0)\cdot \chi_{\confc}(t) \rangle_0,
+\end{align}
+where $\chi_{\confc}$ is the characteristic function of set $\confc$ that takes
+the value of 1 for $(\phi,\psi)\in \confc$, and takes value 0
+otherwise. $M_e(t)$ is the relative magnitude of the EF. Take the case of
+constant EF for example, $M_e(t) = t/t_{warm}$ for $0\leq t<t_{warm}$, and
+$M_e(t) = 1$ for $t\geq t_{warm}$.
+$j$ is the dissipative flux that is defined by
+\begin{align}
+  j = - \sum_{i=1}^N E_\infty q_i v_{i,x},
+\end{align}
+where $q_i$ is the partial charge of the $i$th atom, and $v_{i,x}$ is
+the $x$ component of the velocity of the $i$th atom.  The notation
+$\langle\cdot\rangle_0$ denotes the equilibrium ensemble average.
+We plot the correlation function
+$\langle j(0)\cdot \chi_{\confc}(t) \rangle_0$ against corrlation time $t$
+in Fig.~\ref{fig:appdx1}. The value of the function is estimated from
+two independent 1~$\mu$s equilibrium simulations.
+Please notice that the total length of the equilibrium
+trajactories is the same as the nonequilibrium simulation (2000
+trajactories, each 1000~ps long).
+% With the knowledge of
+% nonequilibrium simulation, the correlation function is expected to
+% vanish at roughly 500~ps, however, it does not vanish even at
+% 1000~ps. This is not surprising, because
+We find that the statistical error is even larger than the value of
+corrlation function.  Therefore, the
+overwhelming statistical uncertainty does not allow us to use it 
+in Eq.~\eqref{eqn:tmp1} to calculate the
+nonequilibrium averages. 
+% , and we actually do not know when the
+% corrlation function vanish .
+Since the total computational effort of
+the equilibrium simulation is the same as the nonequilibrium
+simulation, we conclude that nonequilibrium simulatoin is more
+precise than the conventional equilibrium approach (linear response) at the same computational cost.
+A similar
+observation has already been reported by Ciccotti and Jacucci~\cite{ciccotti1975direct}.
+}
+
+\begin{figure}
+  \centering
+  \includegraphics{fig.ala.new/fig-corr-meta.eps}
+  \caption{The corrlation function $\langle j(0)\cdot \chi_{\confc}(t)
+    \rangle_0$ against time $t$. The error bars in the figure denote
+    the statistical uncertainty at 95\% confidence level. }
+  \label{fig:appdx1}
+\end{figure}
+
 \bibliography{ref}{}

### 2014-02-24 writedown/npt-neq/reply/reply.tex
revise

@@
 in Fig.~\ref{fig:tmp1} of this reply. The value of the function is estimated from
-two independent equilibrium simulation, and the trajactory of each is
+two independent equilibrium simulations, and the trajactory of each is
 of 1~$\mu$s. Please note that the total length of the equilibrium
@@
 observation has already been reported by Ciccotti and Jacucci, PRL
-1975.
+1975. We have added the comparison between our non-equilibrium
+simulation and the linear response thoery to an appendix of the manuscript.
 \\
@@
 terahertz spectroscopy. Therefore, we find our simulation results
-cannot be directly compared with the terahertz experiments.\\
+cannot be directly compared with the terahertz experiments.
+\recheck{please say something here}.
+\\
 
@@
 
-This is indeed a very interesting point. Although the Fig.11 is
-plotted for the non-equilibrium oscillatory EF case, the
-confromational transition pathways are qulitatively comparable to the
-previous works on the transition pathways studied in equilibrium.
-Both the connectivity of conformations and the relatively strength of
-the transitions are similar. A short comment has been added to the
+This is indeed a very interesting point.
+Although the network presented Fig.11 is similar to those
+discovered in the mentioned equilibrium studies,
+in the sense of the steady conformations and connections among them,
+the physical meaning is quit different in our study:
+The system is under the nonequilibrium condition, and
+the fluxes are directional and lasting (although the averged population of the steady conformations do not change). In contrast,
+such probability fluxes do not exist in the equilibrium case.
+A short comment has been added to the
 manuscript.

### 2014-03-03 writedown/npt-neq/alanine.tex
Luigi's revise, send to Giovanni and Christof

--- 2014-02-24 writedown/npt-neq/alanine.tex
@@
 % \affiliation{Department of Physics, University of Roma "La Sapienza", Italy}
-\affiliation{School of Physics, Room 302B UCD-EMSC, University College Dublin, Belfield, Dublin 4, Ireland}
+\affiliation{School of Physics, University College Dublin, Belfield, Dublin 4, Ireland}
 \affiliation{Dipartimento di Fisica, Universit\`a ``La Sapienza'' and CNISM, Piazzale Aldo Moro 5, 00185 Roma, Italy}
@@
 and how likely they are (probability).
+\recheck{One may wonder whether the information extracted from the D-NEMD simulation could have been
+extracted just as well from conventional equilibrium simulations.
+  In the appendix we show that in this case the D-NEMD approach shall be preferred to the equilibrium approach.
+The argument is provided by the comparison between the results of the nonequilibrium method and
+  those from equilibrium simulations, within the linear response theory, based on the analysis of correlation functions.}
 To our knowledge, this study is one of the few (if not the first)  where
@@
 reasonably large.
-
-\recheck{ The proposed temperature control method is very similar to
-  the stochastic boundary condition proposed by Brooks~III and Karplus~\cite{brooks1983deformable}.
-  The only difference is that we do not explicitly consider a boundary
-  region: The system that is divided into a dynamical region (reaction region in their paper) and
-  a thermostated regoin (stochastic buffer region in their paper)
-  is put into a 3-D cubic periodic simulation box.
+\recheck{ The proposed temperature control method has similarities with 
+  the stochastic boundary condition proposed by Brooks and Karplus~\cite{brooks1983deformable}.
+  However, differently from their approach, we do not explicitly consider a boundary region: The system is instead divided into a dynamical region (corresponding to the reaction region of \cite{brooks1983deformable}) and
+  a thermostated region (corresponding to the stochastic buffer region in \cite{brooks1983deformable}) in a 3-D cubic periodic simulation box.
 }
@@
 water molecules.  \recheck{The grid-based energy correction map (CMAP)~\cite{mackerell2004extending}
-for the backbone dihedral angles is also taken into consider.}
+for the backbone dihedral angles is also used.}
 %The EF exserts force $\vect F = q \vect E(t)$ on
@@
 interaction (van der Waals interaction)
-had the cut-off radius of 1.0~nm, and was smoothed from $0.8$ to $1.0$~nm by the
-``switch'' method provided by GROMACS.
+have a cut-off radius of 1.0~nm, and has been smoothed from $0.8$ to $1.0$~nm by the
+``switch'' method provided by the GROMACS code.
 A energy conserving particle mesh Ewald method (PME)~\cite{darden1993pme, essmann1995spm}
 method was applied to calculate the electrostatic interaction in this
-periodic system. The the direct space part of PME was cut-offed and smoothed in the
-same way as the van der Waals interaction.}
-\recheck {All hydrogen involving bonds are constrained by LINCS~\cite{hess1997lincs}, expect that
-  the TIP3P water molecules are constrained by SETTLE algorithm~\cite{miyamoto2004settle}.}
+periodic system. For the direct space part of PME the cut-off and smoothing follow the same principles as those applied to the van der Waals interaction.}
+\recheck {All hydrogen involving bonds are constrained by LINCS~\cite{hess1997lincs}, except 
+  the TIP3P water molecules which are constrained by the SETTLE algorithm~\cite{miyamoto2004settle}.}
 In the thermostated region, the original dynamics was
@@
 At the same time,  $\Delta t$ should be also large enough compared with
-the timestep of the MD integrator, 
+the time step of the MD integrator, 
 so that the quantities of Eq.~\eqref{eqn:tmp7} are well-defined, and can be
@@
 is projected onto the analysis of the probabilistic link between discretized conformations $\{\confaa, \confab, \confba, \confbb, \confc\}$.
-
-\recheck{ The definition of the probability flux is similar to the
-  kinetic rate.  However, we want to stress that, in general, the
-  probability flux should not be interpreted as a kinetic rate, and
-  one cannot replace the nonequilibrium molecular dynamics by a
-  kinetic analysis. The main reason is, firstly, that the nonequilibrium
-  nature of the problem asks for a small time interval $\Delta t$ so that the probability flux is well defined.
+\recheck{ The concept of net probability flux employed by us is similar to the
+  concept of kinetic rate.  However, it must be underlined that, in general, the
+  probability flux should not be interpreted as a kinetic rate.
+  Nonequilibrium molecular dynamics cannot be replaced by 
+  kinetic analysis, the main reason is, firstly, that the nonequilibrium
+  nature of the problem requires the use of a small time interval $\Delta t$ so that the probability flux is well defined.
   Secondly, within the small
@@
   therefore, a direct application of the kinetic
-  analysis is questionable.
-  % Since the main goal of our research is to propose a
-  % nonequilibrium molecular dynamics simulation method, the numerical
-  % results will not be compared with the kinetic analysis.
-}
-
+  analysis may be questionable.}
 In the case of oscillatory EF, the behaviour of the net probability flux is also highly oscillatory, thus, in order to clearly identify the essential features of the molecular conformational changes, it is convenient to study the integrated net probability flux, defined as:
@@
       conformation.
-      The shadow region with each solid line denotes the
+      The shadowed region with each solid line denotes the
       statistical uncertainty of the result at 95\% confidence level.
@@
 \end{figure}
-
 The time-dependent probability density of the system to stay in a certain
@@
 Fig.~\ref{fig:tmp5}.
-\recheck{The simulation results of starting one branching trajectory
-  from each initial conformation are compared with those starting
-  four branching trajectories from each initial conformation (each with
-  different random seed for the Langevin thermostat).
-  They are consistent within the statistical uncertainty, which
-  means our simulation result is robust with respect to the randomness
-  introduced by the (local) Langevin thermostat.
+\recheck{In order to show that  our simulation results are robust with respect to the randomness introduced by the (local) Langevin thermostat, we have tested the effects of changing random seeds for the thermostat in the thermostated region.
+We compared simulation results obtained by starting a branching trajectory
+  from each initial conformation with those obtained from four different branching trajectories from each initial conformation (each of four with
+  different random seed for the Langevin thermostat in the thermostated region).
+  Results are consistent within the statistical uncertainty (see Fig.\ref{fig:tmp5}).
 }
@@
 equilibrium (at zero EF);  This is a nonequilibrium process.
-\recheck{After a time long enough, the system
+\recheck{After sufficiently long time, the system
 is fully relaxed to the new conformations,
-and stays there as long as the EF is kept. However, whether the new conformations
-are in the new equilibrium defined the constant EF is not clear, because
-there may exist very slow nonequilibrium processes, for example as long as 1~$\mu$s,
-which cannot be discovered by our nonequilibrium simulation of only 1~ns.
-What we can do by the proposed nonequilibrium simulation
-method is to study time-dependent behaviours that are no longer than
+and remains in such a state as long as the EF is switched on. However, on the very long time scale,
+there may exist very slow nonequilibrium processes, for example within an 1~$\mu$s range,
+which cannot be captured by the duration of our nonequilibrium simulation (1~ns).
+Obviously, the proposed nonequilibrium simulation
+method can study time-dependent behaviours that are no longer than
 the simulation time. 
@@
 The fact that our external perturbation corresponds to the action of
-an electric field, naturally leads to the question of how
+an electric field, naturally leads to the question 
 \recheck{
-  the molecular dipole aligns along the direction of external EF}, and, in turn, how this is related
+  about the alignment of the molecular dipole vector along the direction of external EF}, and, in turn, how this is related
 to the overall \recheck{conformational selection} of the molecule reported in
@@
     See the text for more details.
-    \recheck{The shadow region denotes the
+    \recheck{The shadowed region denotes the
       statistical uncertainty of the $L=2.7$~nm $R_{ex}=1.0$~nm case at 95\% confidence level.
@@
 \recheck{
-  Although the conformational transitions presented Fig.~\ref{fig:tmp11} are studied under
-  the nonequilibrium scenario, it is actually qualitatively similar to those
-  discovered in the equilibrium studies, e.g.~\cite{apostolakis1999calculation, gfeller2007complex}.
+  Although the network presented in Fig.~\ref{fig:tmp11} is similar to those
+  discovered in the equilibrium studies 
+  in the sense of the steady conformations and connections among them (e.g.~in Ref.~\cite{apostolakis1999calculation, gfeller2007complex}),
+  the physical meaning is quite different in our study:
+  The system is under nonequilibrium conditions due to a controlled physical external perturbation, and
+  the related net probability fluxes are based on trajectories generated by such a perturbation. In contrast, in the equilibrium studies,
+  such net probability fluxes do not explicitly exist.
 }
@@
 is of the same order of magnitude as the microwave
-irradiation available in laboratory (2.45~GHz). }
+radiation available in laboratory (2.45~GHz)~\cite{damm2012can}.
+The highest frequency (100~GHz, i.e.~$\period = 10$~ps) is
+one order of magnitude lower than the tetrahertz spectroscopy experiments~\cite{plusquellic2007applications, born2009terahertz},
+so our results cannot be directly connected to these experimental results.}
+% {\bf REFERENCE HERE, AND WHAT ABOUT TETRAHERTS SPECTROSCOPY?????}}
 The authors are fully aware
@@
 
+  \appendix
+\section{Comparison with the linear response theory}  
+\recheck{
+A commonly used equilibrium approach that can describe the nonequilibrium
+response is the linear response theory (Green-Kubo relation~\cite{green1954markoff,kubo1957statistical}).
+We employed such a method to test the
+conformational dynamics of alanine dipeptide under the EF.
+The response function, for example the time-dependent probability of
+left-handed $\alpha$-helix, is defined as~\cite{tuckeman2010statistical}
+\begin{align}\label{eqn:appdx1}
+  P_\confc(t) = \langle\chi_{\confc}(t)\rangle = \langle \chi_{\confc} \rangle_0 -
+  \beta \int_0^t ds\; M_e(t - s)\langle j(0)\cdot \chi_{\confc}(t) \rangle_0,
+\end{align}
+where $\chi_{\confc}$ is the characteristic function of set $\confc$ that takes
+the value of 1 for $(\phi,\psi)\in \confc$, and takes value 0
+otherwise. $M_e(t)$ is the relative magnitude of the EF. For the case of
+constant EF, for example, $M_e(t) = t/t_{warm}$ for $0\leq t<t_{warm}$, and
+$M_e(t) = 1$ for $t\geq t_{warm}$.
+$j$ is the dissipative flux that is defined by
+\begin{align}
+  j = - \sum_{i=1}^N E_\infty q_i v_{i,x},
+\end{align}
+where $q_i$ is the partial charge of the $i$th atom, and $v_{i,x}$ is
+the $x$ component of the velocity of the $i$th atom.  The notation
+$\langle\cdot\rangle_0$ denotes the equilibrium ensemble average.
+We report the correlation function
+$\langle j(0)\cdot \chi_{\confc}(t) \rangle_0$ as a function of correlation time $t$
+in Fig.~\ref{fig:appdx1}. The value of the function is estimated from
+two independent 1~$\mu$s equilibrium simulations.
+It must be noticed that the total length of the equilibrium
+trajectories is the same as the nonequilibrium simulation (2000
+trajectories, each 1000~ps long).
+Results show that the statistical error is much larger than the value of
+correlation function itself.  Therefore, the
+overwhelming statistical uncertainty does not allow us to use such a quantity
+in Eq.~\eqref{eqn:tmp1} to calculate the
+nonequilibrium averages. 
+Since the total computational effort of
+the equilibrium simulation is the same as the nonequilibrium
+simulation, we conclude that nonequilibrium simulation is more
+accurate than the conventional equilibrium approach (linear response) at the same computational cost.
+A similar
+observation has already been reported in ~\cite{ciccotti1975direct}.
+}
+
+\begin{figure}
+  \centering
+  \includegraphics{fig.ala.new/fig-corr-meta.eps}
+  \caption{The correlation function $\langle j(0)\cdot \chi_{\confc}(t)
+    \rangle_0$ against time $t$. The error bars in the figure denote
+    the statistical uncertainty at 95\% confidence level. }
+  \label{fig:appdx1}
+\end{figure}
+
 \bibliography{ref}{}
@@
 
-% \begin{thebibliography}{10}
-
-% \bibitem{bohr2000microwave}
-% Henrik Bohr and Jakob Bohr.
-% \newblock Microwave-enhanced folding and denaturation of globular proteins.
-% \newblock {\em Physical Review E}, 61(4):4310, 2000.
-
-% \bibitem{bohr2000microwave-1}
-% Henrik Bohr and Jakob Bohr.
-% \newblock Microwave enhanced kinetics observed in ord studies of a protein.
-% \newblock {\em Bioelectromagnetics}, 21(1):68--72, 2000.
-
-% \bibitem{dePomerai2000cell}
-% David de~Pomerai, Clare Daniells, Helen David, Joanna Allan, Ian Duce, Mohammed
-%   Mutwakil, David Thomas, Phillip Sewell, John Tattersall, Don Jones, and Peter
-%   Candido.
-% \newblock Cell biology: Non-thermal heat-shock response to microwaves.
-% \newblock {\em Nature}, 405:417--418, 2000.
-
-% \bibitem{inskip2001cellular}
-% Peter~D Inskip, Robert~E Tarone, Elizabeth~E Hatch, Timothy~C Wilcosky,
-%   William~R Shapiro, Robert~G Selker, Howard~A Fine, Peter~M Black, Jay~S
-%   Loeffler, and Martha~S Linet.
-% \newblock Cellular-telephone use and brain tumors.
-% \newblock {\em New England Journal of Medicine}, 344(2):79--86, 2001.
-
-% \bibitem{mancinelli2004non}
-% Fabrizio Mancinelli, Michele Caraglia, Alberto Abbruzzese, Guglielmo
-%   d'Ambrosio, Rita Massa, and Ettore Bismuto.
-% \newblock Non-thermal effects of electromagnetic fields at mobile phone
-%   frequency on the refolding of an intracellular protein: Myoglobin.
-% \newblock {\em Journal of cellular biochemistry}, 93(1):188--196, 2004.
-
-% \bibitem{budi2005electric}
-% A.~Budi, F.S. Legge, H.~Treutlein, and I.~Yarovsky.
-% \newblock Electric field effects on insulin chain-b conformation.
-% \newblock {\em The Journal of Physical Chemistry B}, 109(47):22641--22648,
-%   2005.
-
-% \bibitem{budi2007effect}
-% A.~Budi, F.S. Legge, H.~Treutlein, and I.~Yarovsky.
-% \newblock Effect of frequency on insulin response to electric field stress.
-% \newblock {\em The Journal of Physical Chemistry B}, 111(20):5748--5756, 2007.
-
-% \bibitem{budi2008comparative}
-% Akin Budi, F~Sue Legge, Herbert Treutlein, and Irene Yarovsky.
-% \newblock Comparative study of insulin chain-b in isolated and monomeric
-%   environments under external stress.
-% \newblock {\em The Journal of Physical Chemistry B}, 112(26):7916--7924, 2008.
-
-% \bibitem{toschi2008effects}
-% Francesca Toschi, Francesca Lugli, Fabio Biscarini, and Francesco Zerbetto.
-% \newblock Effects of electric field stress on a $\beta$-amyloid peptide.
-% \newblock {\em The Journal of Physical Chemistry B}, 113(1):369--376, 2008.
-
-% \bibitem{astrakas2011electric}
-% Loukas Astrakas, Christos Gousias, and Margaret Tzaphlidou.
-% \newblock Electric field effects on chignolin conformation.
-% \newblock {\em Journal of Applied Physics}, 109(9):094702--094702, 2011.
-
-% \bibitem{astrakas2012structural}
-% Loukas~G Astrakas, Christos Gousias, and Margaret Tzaphlidou.
-% \newblock Structural destabilization of chignolin under the influence of
-%   oscillating electric fields.
-% \newblock {\em Journal of Applied Physics}, 111(7):074702--074702, 2012.
-
-% \bibitem{damm2012can}
-% Markus Damm, Christoph Nusshold, David Cantillo, Gerald~N Rechberger, Karl
-%   Gruber, Wolfgang Sattler, and C~Oliver Kappe.
-% \newblock Can electromagnetic fields influence the structure and enzymatic
-%   digest of proteins? a critical evaluation of microwave-assisted proteomics
-%   protocols.
-% \newblock {\em Journal of proteomics}, 75:5533--5543, 2012.
-
-% \bibitem{starzyk2013proteins}
-% A.~Starzyk and M.~Cieplak.
-% \newblock Proteins in the electric field near the surface of mica.
-% \newblock {\em The Journal of Chemical Physics}, 139:045102, 2013.
-
-% \bibitem{english2009nonequilibrium}
-% N.J. English, G.Y. Solomentsev, and P.~O'Brien.
-% \newblock Nonequilibrium molecular dynamics study of electric and low-frequency
-%   microwave fields on hen egg white lysozyme.
-% \newblock {\em The Journal of chemical physics}, 131:035106, 2009.
-
-% \bibitem{solomentsev2012effects}
-% G.Y. Solomentsev, N.J. English, and D.A. Mooney.
-% \newblock Effects of external electromagnetic fields on the conformational
-%   sampling of a short alanine peptide.
-% \newblock {\em Journal of Computational Chemistry}, 33:917--923, 2012.
-
-% \bibitem{ciccotti1975direct}
-% G~Ciccotti and G~Jacucci.
-% \newblock Direct computation of dynamical response by molecular dynamics: The
-%   mobility of a charged lennard-jones particle.
-% \newblock {\em Physical Review Letters}, 35(12):789, 1975.
-
-% \bibitem{ciccotti1979thought}
-% G.~Ciccotti, G.~Jacucci, and I.R. McDonald.
-% \newblock "thought-experiments" by molecular dynamics.
-% \newblock {\em Journal of Statistical Physics}, 21(1):1--22, 1979.
-
-% \bibitem{ciccotti1993theoretical}
-% G.~Ciccotti, C.~Pierleoni, and J.P. Ryckaert.
-% \newblock Theoretical foundation and rheological application of non-equilibrium
-%   molecular dynamics.
-% \newblock In {\em Microscopic simulations of complex hydrodynamic phenomena},
-%   pages 25--45. Plenum Press, 1993.
-
-% \bibitem{palla2008bulk}
-% P.L. Palla, C.~Pierleoni, and G.~Ciccotti.
-% \newblock Bulk viscosity of the lennard-jones system at the triple point by
-%   dynamical nonequilibrium molecular dynamics.
-% \newblock {\em Physical Review E}, 78(2):021204, 2008.
-
-% \bibitem{orlandini2011hydrodynamics}
-% S.~Orlandini, S.~Meloni, and G.~Ciccotti.
-% \newblock Hydrodynamics from statistical mechanics: combined dynamical-nemd and
-%   conditional sampling to relax an interface between two immiscible liquids.
-% \newblock {\em Phys. Chem. Chem. Phys.}, 13:13177--13181, 2011.
-
-% \bibitem{orlandini2011hydrodynamics-01}
-% Sergio Orlandini, Simone Meloni, and Giovanni Ciccotti.
-% \newblock Hydrodynamics from dynamical non-equilibrium md.
-% \newblock In {\em AIP Conference Proceedings}, volume 1332, page~77, 2011.
-
-% \bibitem{delaHoz2005microwaves}
-% Antonio de~la Hoz, Angel Diaz-Ortiz, and Andres Moreno.
-% \newblock Microwaves in organic synthesis. thermal and non-thermal microwave
-%   effects.
-% \newblock {\em Chemical Society Reviews}, 34(2):164--178, 2005.
-
-% \bibitem{pronk2013gromacs}
-% S.~Pronk, S.~P{\'a}ll, R.~Schulz, P.~Larsson, P.~Bjelkmar, R.~Apostolov, M.R.
-%   Shirts, J.C. Smith, P.M. Kasson, D.~van~der Spoel, and Hess B.~Lindahl E.
-% \newblock Gromacs 4.5: a high-throughput and highly parallel open source
-%   molecular simulation toolkit.
-% \newblock {\em Bioinformatics}, pages 1--10, 2013.
-
-% \bibitem{parrinello1981polymorphic}
-% M.~Parrinello and A.~Rahman.
-% \newblock Polymorphic transitions in single crystals: A new molecular dynamics
-%   method.
-% \newblock {\em Journal of Applied Physics}, 52:7182, 1981.
-
-% \bibitem{schuette2011markov}
-% C.~Sch{\"u}tte, F.~No{\'e}, J.~Lu, M.~Sarich, and E.~Vanden-Eijnden.
-% \newblock Markov state models based on milestoning.
-% \newblock {\em The Journal of Chemical Physics}, 134:204105, 2011.
-
-% \bibitem{scovell2000phase}
-% Dawn~L Scovell, Tim~D Pinkerton, Valentin~K Medvedev, and Eric~M Stuve.
-% \newblock Phase transitions in vapor-deposited water under the influence of
-%   high surface electric fields.
-% \newblock {\em Surface science}, 457(3):365--376, 2000.
-
-% \bibitem{vogel2008femtosecond}
-% A.~Vogel, N.~Linz, S.~Freidank, and G.~Paltauf.
-% \newblock Femtosecond-laser-induced nanocavitation in water: implications for
-%   optical breakdown threshold and cell surgery.
-% \newblock {\em Physical review letters}, 100(3):38102, 2008.
-
-% \bibitem{vitalini2013speed}
-% F.~Vitalini, A.S.J.S. Mey, F.~No\'e, and B.G. Keller.
-% \newblock The speed of force fields.
-% \newblock {\em private communication}, 2013.
-
-% \end{thebibliography}
-
 \end{document}

### 2014-03-03 writedown/npt-neq/reply/reply.tex
Luigi's revise, send to Giovanni and Christof

--- 2014-02-24 writedown/npt-neq/reply/reply.tex
@@
 
-\section*{The scientific issues from referee 1}
+Dear Editor,\\
+
+Below you find our reply to the the referees.
+We apologize for the long time needed for the reply due to the holiday of one of the authors.
+The request of the referees implied a rather massive additional computational effort.
+The result of such effort is highly satisfactory and the validity of the paper is now much higher.
+We are now confident that the paper can be accepted for publication.\\
+
+Best Regards\\
+
+Han Wang (on behalf of all authors) 
+\section*{Reply to referee 1}
 
@@
 
-The non-equilibrium responses in the paper are discussed in two
-different senses: 1, the perturbation to the system is
-time-independent.
-The relaxation of the system to the new equilibrium
-defined by the constant perturbation is non-equilibrium.
-% However,
-% after the new equilibrium is established, there is no non-equilibrium
-% process in the system.
-The first example of the manuscript is in this sense.  2, the
-perturbation is time-dependent.  The second example in the manuscript
-is in this sense.  The first sense is only a special case of the
-sencond sense.  In the first sense, the system can be studied by
-equilibrium methods such as the Markov state model (MSM). However, the
-equilibrium methods are NOT applicable in the second sense.  The
-present paper develops a non-equilibrium molecular dynamics simulation
-method that is more general in the sense that it is applicable to the
-aformentioned two senses. Therefore, the proposed method cannot be replaced
-by the equilibrium methods such as MSM.
+We understand the concern of the referee and in the revised version of our manuscript have performed a numerical test.
 
-Another commenly used equilibrium method that is able to study the non-equilibrium
-responses is the linear responses thoery (Green-Kubo relation).
-We also use it to test the
-conformational shift of alanine dipeptide under the electric field
-(EF). The response function, take the time-dependent probability of
-left-handed $\alpha$-helix (Conformation $C$ in the old manuscript. The notation has been changed to $\alpha_L$ in the updated manuscript.) for example, is defined as
+We have employed equilibrium simulations to obtain the non-equilibrium
+responses within the framework of linear responses theory (Green-Kubo relation).
+With this approach we studied the conformational shift of alanine dipeptide under the electric field
+(EF). As response function we have considered the time-dependent probability of
+left-handed $\alpha$-helix (Conformation $C$ in the old manuscript. The notation has been changed to $\alpha_L$ in the updated manuscript.) This is defined as
 \begin{align}\label{eqn:tmp1}
@@
 $\langle\cdot\rangle_0$ denotes the equilibrium ensemble average.
-Eq.~\eqref{eqn:tmp1} can be found in the text books of statistical
-mechanics (e.g.~M.~Tuckerman \emph{Statistical Mechanics: Theory and
-  Molecular Simulation}, pp.~499).  We plot the correlation function
-$\langle j(0)\cdot \chi_{_C}(t) \rangle_0$ against corrlation time $t$
+ We then plot the correlation function
+$\langle j(0)\cdot \chi_{_C}(t) \rangle_0$ against correlation time $t$
 in Fig.~\ref{fig:tmp1} of this reply. The value of the function is estimated from
-two independent equilibrium simulation, and the trajactory of each is
-of 1~$\mu$s. Please note that the total length of the equilibrium
-trajactories is the same as the non-equilibrium simulation (2000
-trajactories, each 1000~ps long).
-% With the knowledge of
-% non-equilibrium simulation, the correlation function is expected to
-% vanish at roughly 500~ps, however, it does not vanish even at
-% 1000~ps. This is not surprising, because
+two independent equilibrium simulations, and the trajectory of each is
+of 1~$\mu$s. The total length of the equilibrium
+trajectories is the same as the non-equilibrium simulation (2000
+trajectories, each 1000~ps long).
+
 We find that the statistical error is even larger than the value of
-corrlation function.  Therefore, the
-overwhelming statistical uncertainty does not allow us to use it 
+correlation function.  Therefore, the
+overwhelming statistical uncertainty does not allow us to use the equilibrium approach 
 in Eq.~\eqref{eqn:tmp1} to calculate the
@@
 the equilibrium simulation is the same as the non-equilibrium
-simulation, we conclude that non-equilibrium simulatoin is more
-precise than the conventional equilibrium approach (linear response) at the same computational cost.
-A similar
-observation has already been reported by Ciccotti and Jacucci, PRL
-1975.
+simulation, we conclude that non-equilibrium simulation is more
+accurate and efficient than the conventional equilibrium approach  at the same computational cost.
+It must be noticed that a similar
+observation has already been reported by Ciccotti and Jacucci, (Phys.~Rev.~Lett.~35, 789, 1975). We report the description above in the appendix of the manuscript.
 \\
-% Another limit of the linear response theory is that it can only be
-% used to calculate the non-equilibrium properties when the
-% non-equilibrium purturbation to the system is small, and it is also
-% impossible to tell \emph{a priori} if the purturbation is small enough
-% that the response theory is valid. This issue also does not exist in
-% our non-equilibrium simulation method.
-
 \begin{figure}
@@
   \includegraphics{figs/fig-corr-meta.eps}
-  \caption{The corrlation function $\langle j(0)\cdot \chi_{_C}(t)
+  \caption{The correlation function $\langle j(0)\cdot \chi_{_C}(t)
     \rangle_0$ against time $t$. The error bars in the figure denote
@@
 
-We have done an equilibrium simulation of 1~$\mu$s.  On the
-trajactory, molecular conformations are recored every 500~ps,
-therefore, in total 2000 equilibrium conformations are recoreded.  The
+We have done an equilibrium simulation of 1~$\mu$s.  Along the
+trajectory, molecular conformations are recorded every 500~ps,
+therefore, in total 2000 equilibrium conformations are extracted.  The
 equilibrium probabilities of the conformations $A_1$, $A_2$, $B_1$,
@@
 ($\pm 0.013$), 0.182 ($\pm 0.019$) and 0.051 ($\pm 0.021$),
-respectively.  We have run two addtional equilibrium simulations of
+respectively.  We run two additional equilibrium simulations of
 1~$\mu$s, and the probabilities of conformations are consistent with
-the values listed above, which means that our new equilibrium
+the values listed above, which means that our ``new'' equilibrium
 simulation is fully converged.  Comparing with our previous
@@
 of initial configuration sampling is substantially improved. All
-simulations in the manuscript are reperformed according to the new set
-of initial conformations, however, the strand of all time-dependent
-observables are the same as the old simulation, and no change to the
-conclusions is made.
-% The difference between the new and the old
-% results is no more than 0.05, which is basically within the
-% statistical uncertainty (given in the new manuscript).
+simulations in the manuscript are re-performed according to the new set
+of initial conformations, however nothing substantially changed compared to the original results.\\
 
-We also test the convergence of simulation result with respect to the
-number of branching trajactories.  The time-dependent probabilities of
-each conformation calculated from one branching trajactory is compared
-with four braching trajactories (each of them is simulated with
-different random seed for Langevin thermostat) in
-Fig.~\ref{fig:tmp2} of this reply. The results are consistent, which means that the
-sampling of the non-equilibrium trajactories is fully converged. In
-summary, since the our non-equilibrium simulation includes the
+We have also tested the convergence of simulation results with respect to the
+number of branching trajectories.  The time-dependent probabilities of
+each conformation calculated from one branching trajectory is compared
+with four branching trajectories (each of them is simulated with
+different random seeds for Langevin thermostat) in
+Fig.~\ref{fig:tmp2} of this reply. The results are consistent with the original ones, which means that the
+sampling of the non-equilibrium trajectories is fully converged. In
+summary, since our non-equilibrium simulation includes the
 sampling of both initial configurations and non-equilibrium
-trajactories, the convergence of both aspects implies the convergence
+trajectories, the convergence of both  implies the convergence
 of our simulation results. 
+The updated results are added in the paper.\\
 
-The question on whether our non-equilibrium braching trajactories are
+The question on whether our non-equilibrium branching trajectories are
 long enough so that the results are fully converged is a very subtle
-question. There may exists an intrisic time-scale of 1 microsecond
-long, so we cannot discover it by braching trajactories of only a few
-nanoseconds.  What we can do by the proposed non-equilibrium simulation
-method is to study time-dependent behaviours that are no longer than
-the simulation time. We have modified the manuscript according to
-make this point clear. A similar difficulty actualy exists for all equilibrium
-simulations: how do we know whether an equilibrium simulation is fully converged,
-especially when some rare events cannot be observed during the limited simualtion time.
+question.
+There may exists an intrinsic time-scale longer than our simulation time, however this is obvious and implicitly imply that the validity of our results is restricted to the time scale simulated.
 \\
-% We want to stress that the target of the non-equilibrium simulation is
-% to test how the populations of conformations evolve under the external
-% electric field
 
@@
 simulated in cubic box of length $L=4.0$~nm. Fig.~7 of the
-manuscript demonstrates that all of the results are consistent. That
+manuscript demonstrates that all the results are consistent. This
 means $R_{ex}=1.0$~nm is already large enough, and a larger $R_{ex}$
@@
 500~ps, which is the same as the longest timescales of the constant EF
-case, however, the required simulation time is so long that exceed our
-computational capability. Therefore, we made a compromise that only
-the period of 200~ps is studied. The typical frequency of the microwave
+case, however, the required simulation time is prohibitive at this stage. Therefore, we made a reasonable compromise and considered only
+a period of 200~ps. The typical frequency of the microwave
 irradiation is 2450~MHz, which corresponds to period of 400~ps. It is
 the same order of magnitude as the $T_P=200$~ps studied by us.
+We have added a comment along these lines in the revised manuscript.
 \\
@@
 kinetic rate (we use joint probabilities in (6) rather than
-conditional probabilities). However, we want to stress that, in genarl,
+conditional probabilities). However, we want to stress out that, in general,
 the probability fluxes calculated in the manuscript should not be
@@
 non-equilibrium molecular dynamics by a kinetic analysis. The main
-reason is two folds:
+reasons are:
 Firstly, for a non-equilibrium system, the probability fluxes are
 time-dependent, therefore, the lag-time $\Delta t$ in the definition (Eq.~(6))
-should be small comparing with the typical time-scale of conformation change.
+should be small compared with the typical time-scale of conformation change.\\
 Secondly, for a small lag time $\Delta t$ (1~ps in the manuscript), the conformational
@@
 application of the kinetic analysis in the non-equilibrium cases is questionable. Although one may
-gain usefuly information from the kinetic analysis, the reliability
+gain useful information from the kinetic analysis, the reliability
 and the effectiveness of this approach should be carefully checked case
@@
 non-equilibrium molecular dynamics simulation method, the numerical
-results are not compared with a kinetic analysis.
+results are not compared with a kinetic analysis.\\
 
-A comment on this direction has been added to the end of section III.B.
+A comment along this direction has been added to the end of section III.B.
 \\
@@
 
-Please see the reply to the seocond question concerning the convergence
-of our simulation results. We believe that the better initial
+The referee is invited to look at the reply to the second question concerning the convergence
+of our simulation results. We believe that a better initial
 state sampling and the new convergence check with respect to the
-number of branching trajectories will strengthen the reliablity
+number of branching trajectories will strengthen the reliability
 of our method.
@@
 
-\section*{The scientific issues from referee 2}
+\section*{Reply to referee 2}
 
@@
 
-The frequency investigated in our manuscript is from 5~GHz to 100~GHz,
-the largest of which is still one order of magnitude smaller than the
-terahertz spectroscopy. Therefore, we find our simulation results
-cannot be directly compared with the terahertz experiments.\\
+The frequencies investigated in our manuscript span from 5~GHz to 100~GHz,
+the largest of which is still one order of magnitude smaller than those normally used in  terahertz spectroscopy.
+Therefore, we find our simulation results, at this stage, cannot be directly compared with the terahertz experiments.
+{To make fully aware the readers about the current limitation of our study, with respect to experimental connections, we have added the comment above in the manuscript.}
+\\
 
@@
 
-Yes, a comment and comparison on this direction has been added to the
+Yes, a comment and comparison along this direction has been added to the
 manuscript.\\
@@
 It is suggested to adapt the labeling of the conformational substates
-of alanine dipeptide to that used in the literature ($C_7^{eq}$, $\alpha_L$,
-$C_7^{ax}$, etc.) - see e.g. Caflisch et al., JCP 1999.
+of alanine dipeptide to that used in the literature ($C7_{eq}$, $\alpha_L$,
+$C7_{ax}$, etc.) - see e.g. Caflisch et al., JCP 1999.
 }\\
 
-We have changed the labelling of conformations.\\
+We have changed the labeling of conformations.\\
 
@@
 
-This is indeed a very interesting point. Although the Fig.11 is
-plotted for the non-equilibrium oscillatory EF case, the
-confromational transition pathways are qulitatively comparable to the
-previous works on the transition pathways studied in equilibrium.
-Both the connectivity of conformations and the relatively strength of
-the transitions are similar. A short comment has been added to the
-manuscript.
+This is indeed a very interesting point.
+Although the network presented Fig.11 is similar to those
+discovered in the mentioned equilibrium studies,
+regarding the map of the steady conformations and connections among them,
+the physical meaning is instead quite different in our study:
+The system is under the nonequilibrium conditions, and
+the fluxes are explicitly induced by a physically realistic control, i.e.~EF, although the averaged population of the steady conformations do not change. In contrast,
+such probability fluxes do not exist, as a result of an explicit physical action, in the equilibrium case.
+A comment along such direction has been added to the
+manuscript.\\
 
-The transition fluxes can be used to calculate the free energy only in
-the equilibrium case. In the non-equilibrium cased, especially the
+It must be also added that the transition fluxes can be used to calculate the free energy only in
+the equilibrium case. In the non-equilibrium case, especially for the
 oscillatory EF case, the conformational kinetics of the system is generally

### 2014-03-05 writedown/npt-neq/alanine.tex
2nd round

@@
 time range of the order of 10-60 nanoseconds.
-During this simulation time 
+During these simulations time 
 relevant conformational changes characterizing the solvated molecule can be observed. 
@@
 secondary structure, root mean square displacement (RMSD), dipole
-moment, shape parameters are calculated as a function of time, or
+moment, and shape parameters are calculated as a function of time, or
 in stationary condition, taking time averages.
@@
 \section{Methodology}
-\subsection{Nonequilibrium molecular dynamics simulation}
+\subsection{Dynamical nonequilibrium molecular dynamics simulation (D-NEMD)}
 In this section we briefly review the dynamical approach to nonequilibrium
@@
 and $J$ is
-the symplectic matrix. The Liouville equation for the probability
+the symplectic matrix
+\begin{align}
+  J = \left(
+    \begin{array}{rr}
+      0 & I\\
+      -I & 0
+    \end{array}
+    \right).
+\end{align}
+The Liouville equation for the probability
 distribution writes:
@@
 the microscopic observable computed along trajectories, starting from
-initial configurations sampled from an \emph{equilibrium}
+initial configurations sampled from an initial or, sometimes, an \emph{equilibrium}
 distribution. In practical terms we proceed by first running an equilibrium MD simulation
@@
 The size of the  dynamical region is $R_{ex} = 1.0$~nm.
-All simulations are performed by a home-modified GROMACS~4.5~\cite{pronk2013gromacs} with support to the CHARMM
+All simulations are performed by a home-modified GROMACS~4.5~\cite{pronk2013gromacs} together with the CHARMM
 force field~\cite{bjelkmar2010implementation}.
@@
 The branching trajectories were integrated by the
-Leap-frog scheme with the aforementioned nonequilibrium
+Leap-frog scheme \bluec{(standard Gromacs implementation)} with the aforementioned nonequilibrium
 temperature control technique.  The
@@
 ``switch'' method provided by the GROMACS code.
-A energy conserving particle mesh Ewald method (PME)~\cite{darden1993pme, essmann1995spm}
+A energy conserving Particle Mesh Ewald (PME)~\cite{darden1993pme, essmann1995spm}
 method was applied to calculate the electrostatic interaction in this
@@
   are not presented in this paper).
-The whole system is also coupled to a Parrinello-Rahman barostat~\cite{parrinello1981polymorphic} with $\tau_P = 2.0~\textsf{ps}$ to keep
+The whole system is also coupled to a Parrinello-Rahman barostat~\cite{parrinello1981polymorphic}~\bluec{(in standard Gromacs implementation)} with $\tau_P = 2.0~\textsf{ps}$ to keep
 the pressure at ambient condition (1~Bar). Since the
@@
 dynamics of the system.
+% \bluec{The use of leap-frog scheme and Parrinello-Rahman barostat
+% was not our choice, but the default one of Gromacs.}
 At time $t=0$~ps, the system
@@
 are found in different secondary structures of a peptide chain:
-$\confaa$ and $\confab$ are
-corresponding to the $\alpha$-helix. $\confba$ and $\confbb$ are
-corresponding to the $\beta$-sheet. $\confc$ is corresponding to the
+$\confaa$ and $\confab$ 
+correspond to the $\alpha$-helix. $\confba$ and $\confbb$ 
+correspond to the $\beta$-sheet. $\confc$ corresponds to the
 left-handed $\alpha$-helix.
@@
 \begin{align}
-  P_I(t) = \mathbb P ( (\phi_t,\psi_t) \in I), \quad  I \in \{\confaa, \confab, \confba, \confbb, \confc\},
+  P_I(t) = \mathbb P ( (\phi_t,\psi_t) \in I), \quad  I \textrm{ being one of the five regions } \{\confaa, \confab, \confba, \confbb, \confc\},
 \end{align}
@@
 Next,
-we consider the net probability flux from conformation $I$ to $J$, defined by:
+we consider the \emph{net probability flux} from conformation $J$ to $I$, defined by:
 \begin{align}\nonumber
@@
 is projected onto the analysis of the probabilistic link between discretized conformations $\{\confaa, \confab, \confba, \confbb, \confc\}$.
-\recheck{ The concept of net probability flux employed by us is similar to the
-  concept of kinetic rate.  However, it must be underlined that, in general, the
-  probability flux should not be interpreted as a kinetic rate.
-  Nonequilibrium molecular dynamics cannot be replaced by 
-  kinetic analysis, the main reason is, firstly, that the nonequilibrium
-  nature of the problem requires the use of a small time interval $\Delta t$ so that the probability flux is well defined.
-  Secondly, within the small
-  time interval (we use 1~ps), the conformational
-  dynamics of alanine dipeptide is generally not Markovian~\cite{schuette2011markov, prinz2011markov},
-  therefore, a direct application of the kinetic
-  analysis may be questionable.}
+\recheck{ The concept of net probability flux employed by us is very close to the
+  concept of kinetic rate.  However, we prefer to stick to our definition which
+is mathematically simpler and univocal.}
 In the case of oscillatory EF, the behaviour of the net probability flux is also highly oscillatory, thus, in order to clearly identify the essential features of the molecular conformational changes, it is convenient to study the integrated net probability flux, defined as:
@@
       starting from each initial conformation, while the dashed lines denote
-      the results of four branching trajectories (different random seeds for the Langevin thermostat) starting from each initial
+      the average of the four branching trajectories (different random seeds for the Langevin thermostat, see text) starting from each initial
       conformation.
@@
     for $J=\confc$.
+    \bluec{This plot is drawn from the four-branching-trajectories case (see the text).}
     }
@@
 The left-hand helix conformation $\confc$ noticeably grows from 0 to 0.22.
-We plot the net probability fluxes in Fig.~\ref{fig:tmp6}.
+We plot the net probability fluxes \bluec{of the four-branching-trajectories case} in Fig.~\ref{fig:tmp6}.
 Results show that for short $t$, the net fluxes are generally non-zero,
@@
 all fluxes converge to zero. This indicates
-that as the EF is switched on, the system first is driven away from the initial
-equilibrium (at zero EF);  This is a nonequilibrium process.
+that as the EF is switched on, the system is driven away from the initial
+equilibrium (at zero EF),  starting a dynamical nonequilibrium process.
 \recheck{After sufficiently long time, the system
-is fully relaxed to the new conformations,
-and remains in such a state as long as the EF is switched on. However, on the very long time scale,
-there may exist very slow nonequilibrium processes, for example within an 1~$\mu$s range,
-which cannot be captured by the duration of our nonequilibrium simulation (1~ns).
-Obviously, the proposed nonequilibrium simulation
-method can study time-dependent behaviours that are no longer than
-the simulation time. 
+is fully relaxed to the new stationary state, in
+which it remains as long as the EF is switched on.
+Of course we cannot exclude very slow nonequilibrium processes,
+which cannot be captured by the duration of
+our nonequilibrium simulation (1~ns), since it is
+obviously that the proposed nonequilibrium approach
+can only study time-dependent behaviours that are shorter than
+the total time of the branching trajectories. 
 }
@@
 \recheck{
-  about the alignment of the molecular dipole vector along the direction of external EF}, and, in turn, how this is related
-to the overall \recheck{conformational selection} of the molecule reported in
+  of the alignment of the molecular dipole vector along the direction of external EF}, and, in turn, of how this is related
+to the overall \recheck{conformational change} of the molecule as reported in
 the previous section.
@@
   \bigg\langle
-  \sum_{i\in \{\textrm{atoms of alanine}\}}
+  \sum_{i\in \{\textrm{point charges of alanine}\}}
   q_i\, \vect r_i(t)
@@
 \end{align}
-where $q_i$ denotes the partial charge of any point particle $i$ defining our model of alanine,
+where $q_i$ denotes the partial charge of any point charge $i$ defining our model of alanine,
 the molecule being neutral, i.e.~$\sum_iq_i = 0$.
-$\vect r_i$ denotes the position of the particle $i$.
+$\vect r_i$ denotes the position of the point $i$.
 Fig.~\ref{fig:tmp3}
@@
 of c.a.~$-13.6$~kJ/mol.
-We calculate the averaged dipole moment of different conformations
-(defined by taking average in Eqn.~\eqref{eqn:tmp8}
-only for a certain conformation)
-under the constant EF, and they are 6.8, 6.0, 5.1, 3.1 and 7.1~Debye
+We calculated the averaged dipole moment of different conformations
+(defined by taking averages in Eqn.~\eqref{eqn:tmp8}
+only for given conformations)
+under constant EF, and found 6.8, 6.0, 5.1, 3.1 and 7.1~Debye
 for $\confaa$, $\confab$, $\confba$, $\confbb$ and $\confc$, respectively.
@@
 To this aim, let us define
-the geometric direction of the alanine by the red vector in
+the geometric direction of the alanine by the red vector in the inset in
 Fig.~\ref{fig:tmp3}, i.e.~by the angle bisector of the two black vectors,
@@
 decreases from 0 to $-0.15$, which means a weak alignment of the molecule to the external field.
-Then from $t=0$ to 500~ps, the molecule slowly changes to the orientation
+Then from $t=10$ to 500~ps, the molecule slowly changes to the orientation
 that is almost perpendicular to the EF.
@@
 Fig.~\ref{fig:tmp7a}~(b) presents the number of hydrogen bonds between the
-alanine and water molecules, and between two water molecules.
+alanine and water molecules, and between two neighboring water molecules.
 The number of hydrogen bonds are calculated by standard GROMACS
@@
 does not have enough time to fully relax the dipole, as a consequence the maximum dipole moment is smaller than the previous case.
-Fig.~\ref{fig:tmp9}~(b) presents the orientational order
-parameter. The notations are the same as Fig~\ref{fig:tmp9}~(a).
+Fig.~\ref{fig:tmp8}~(b) presents the orientational order
+parameter. The notations are the same as Fig~\ref{fig:tmp8}~(a).
 For all cases the order parameter is much
@@
 not exposed to a strong enough EF for a time long enough.
-For  $\period =10$ and 40~ps, the orientation of the alanine shows a weak tendency
+For  $\period =10$ and 40~ps, the orientation of the alanine shows a \bluec{very} weak tendency
 to be parallel to the EF. It is worth to notice that for constant EF,
@@
   \includegraphics[width=0.6\textwidth]{fig.ala.new/graphs/graph-t0010-2.eps}
-  \caption{Schematic plot of the main probability flux between conformations
-    for periodically oscillatory EF, $\period =10$~ps. The thickness 
+  \caption{Schematic plot of the main probability fluxes between conformations
+    for oscillatory EF, $\period =10$~ps. The thickness 
     of the arrows approximately presents the strength of the flux.
@@
 integrated probability net fluxes, which imply some lasting and directional
-fluxes among the conformations (see Fig.~\ref{fig:tmp9}).
+fluxes among the conformations \bluec{in steady state}.
 Fig.~\ref{fig:tmp11} presents
@@
 $\langle j(0)\cdot \chi_{\confc}(t) \rangle_0$ as a function of correlation time $t$
-in Fig.~\ref{fig:appdx1}. The value of the function is estimated from
+in Fig.~\ref{fig:appdx1}~(a). The value of the function is estimated from
 two independent 1~$\mu$s equilibrium simulations.
@@
 Results show that the statistical error is much larger than the value of
-correlation function itself.  Therefore, the
-overwhelming statistical uncertainty does not allow us to use such a quantity
-in Eq.~\eqref{eqn:tmp1} to calculate the
-nonequilibrium averages. 
-Since the total computational effort of
+correlation function itself.
+\bluec{
+  In Fig.~\ref{fig:appdx1}~(b),
+  the probability of conformation $\confc$ calculated from
+  the linear response theory~\eqref{eqn:appdx1} is compared with that
+  computed from D-NEMD~\eqref{eqn:tmp1}.
+  The linear response result follows the D-NEMD result only in the very first
+  15~ps, then it diverges. Since it is meaningless for a probability
+  being larger than 1, the linear response result is qualitatively wrong.
+Therefore, the
+overwhelming statistical uncertainty suggest to prefer
+D-NEMD~Eq.~\eqref{eqn:tmp1} to calculate the
+nonequilibrium averages. }
+In fact, since the total computational effort of
 the equilibrium simulation is the same as the nonequilibrium
-simulation, we conclude that nonequilibrium simulation is more
+simulation, the nonequilibrium simulation is more
 accurate than the conventional equilibrium approach (linear response) at the same computational cost.
 A similar
-observation has already been reported in ~\cite{ciccotti1975direct}.
+observation has already been reported in Ref.~\cite{ciccotti1975direct}.
 }
@@
   \includegraphics{fig.ala.new/fig-corr-meta.eps}
-  \caption{The correlation function $\langle j(0)\cdot \chi_{\confc}(t)
-    \rangle_0$ against time $t$. The error bars in the figure denote
-    the statistical uncertainty at 95\% confidence level. }
+  \includegraphics{fig.ala.new/fig-corr-meta-c.eps}
+  \caption{
+    \bluec{The numerical result of the linear response theory.
+    (a): The correlation function $\langle j(0)\cdot \chi_{\confc}(t)
+    \rangle_0$ against time $t$.
+    The error bars in the figure denote
+    the statistical uncertainty at 95\% confidence level. 
+    (b): The probability of conformation $\confc$ computed from the
+    linear response theory~\eqref{eqn:appdx1} versus that
+    computed from D-NEMD~\eqref{eqn:tmp1}.}
+  }
   \label{fig:appdx1}

### 2014-03-05 writedown/npt-neq/reply/reply.tex
2nd round

@@
 $\langle j(0)\cdot \chi_{_C}(t) \rangle_0$ against correlation time $t$
-in Fig.~\ref{fig:tmp1} of this reply. The value of the function is estimated from
+in Fig.~\ref{fig:tmp1}~(a) of this reply. The value of the function is estimated from
 two independent equilibrium simulations, and the trajectory of each is
@@
 trajectories, each 1000~ps long).
-
 We find that the statistical error is even larger than the value of
-correlation function.  Therefore, the
-overwhelming statistical uncertainty does not allow us to use the equilibrium approach 
+correlation function.
+In Fig.~\ref{fig:tmp1}~(b),
+  the probability of conformation $C$ calculated from
+  the linear response theory is compared with that
+  computed from non-equilibrium simulation.
+  The linear response result follows the non-equilibrium result only in the very first
+  15~ps, then it diverges. Since it is meaningless for a probability
+  being larger than 1, the linear response result is qualitatively wrong.
+Therefore, the
+overwhelming statistical uncertainty does not suggest to use the equilibrium approach 
 in Eq.~\eqref{eqn:tmp1} to calculate the
@@
   \includegraphics{figs/fig-corr-meta.eps}
-  \caption{The correlation function $\langle j(0)\cdot \chi_{_C}(t)
-    \rangle_0$ against time $t$. The error bars in the figure denote
-    the statistical uncertainty at 95\% confidence level. }
+  \includegraphics{figs/fig-corr-meta-c.eps}
+  \caption{
+    The numerical result of the linear response theory.
+    (a): The correlation function $\langle j(0)\cdot \chi_{C}(t)
+    \rangle_0$ against time $t$.
+    The error bars in the figure denote
+    the statistical uncertainty at 95\% confidence level. 
+    (b): The probability of conformation $C$ computed from the
+    linear response theory versus that
+    computed from non-equilibrium simulation (D-NEMD).}
   \label{fig:tmp1}
@@
 The question on whether our non-equilibrium branching trajectories are
-long enough so that the results are fully converged is a very subtle
-question.
+long enough so that the results are fully converged is an always present problem.
 There may exists an intrinsic time-scale longer than our simulation time, however this is obvious and implicitly imply that the validity of our results is restricted to the time scale simulated.
@@
 time scales of probability fluxes observed in the constant EF case,
-see Table~I of the manuscript. We tried to simulation with period of
+see Table~I of the manuscript. We tried to do a simulation with period of
 500~ps, which is the same as the longest timescales of the constant EF
@@
 kinetic rate (we use joint probabilities in (6) rather than
-conditional probabilities). However, we want to stress out that, in general,
-the probability fluxes calculated in the manuscript should not be
-interpreted as a kinetic rate, and one cannot replace the
-non-equilibrium molecular dynamics by a kinetic analysis. The main
-reasons are:
-Firstly, for a non-equilibrium system, the probability fluxes are
-time-dependent, therefore, the lag-time $\Delta t$ in the definition (Eq.~(6))
-should be small compared with the typical time-scale of conformation change.\\
-Secondly, for a small lag time $\Delta t$ (1~ps in the manuscript), the conformational
-dynamics of biomolecules is generally not
-Markovian (see e.g.~C.~Sch\"utte et.~al.~JCP 2011 and J.-H.~Prinz et.~al.~JCP 2011).
-Since the basic assumption -- Markovianity -- of the kinetic analysis
-may not be satisfied, a direct
-application of the kinetic analysis in the non-equilibrium cases is questionable. Although one may
-gain useful information from the kinetic analysis, the reliability
-and the effectiveness of this approach should be carefully checked case
-by case.  Since the main goal of our research is to propose a
-non-equilibrium molecular dynamics simulation method, the numerical
-results are not compared with a kinetic analysis.\\
-
+conditional probabilities).
+However, we prefer to stick to our definition which
+is mathematically simpler and univocal.
 A comment along this direction has been added to the end of section III.B.
 \\
+% However, we want to stress out that, in general,
+% the probability fluxes calculated in the manuscript should not be
+% interpreted as a kinetic rate, and one cannot replace the
+% non-equilibrium molecular dynamics by a kinetic analysis. The main
+% reasons are:
+% Firstly, for a non-equilibrium system, the probability fluxes are
+% time-dependent, therefore, the lag-time $\Delta t$ in the definition (Eq.~(6))
+% should be small compared with the typical time-scale of conformation change.\\
+% Secondly, for a small lag time $\Delta t$ (1~ps in the manuscript), the conformational
+% dynamics of biomolecules is generally not
+% Markovian (see e.g.~C.~Sch\"utte et.~al.~JCP 2011 and J.-H.~Prinz et.~al.~JCP 2011).
+% Since the basic assumption -- Markovianity -- of the kinetic analysis
+% may not be satisfied, a direct
+% application of the kinetic analysis in the non-equilibrium cases is questionable. Although one may
+% gain useful information from the kinetic analysis, the reliability
+% and the effectiveness of this approach should be carefully checked case
+% by case.  Since the main goal of our research is to propose a
+% non-equilibrium molecular dynamics simulation method, the numerical
+% results are not compared with a kinetic analysis.\\
 
@@
 the largest of which is still one order of magnitude smaller than those normally used in  terahertz spectroscopy.
-Therefore, we find our simulation results, at this stage, cannot be directly compared with the terahertz experiments.
-{To make fully aware the readers about the current limitation of our study, with respect to experimental connections, we have added the comment above in the manuscript.}
+Therefore, we find that our simulation results, at this stage, cannot be directly compared with the terahertz experiments.
+{To make fully aware the readers about the current limitation of our study, with respect to experimental connections, we have added the comment above and the experimental references in the manuscript.}
 \\
@@
 This is indeed a very interesting point.
-Although the network presented Fig.11 is similar to those
+Although the network presented in Fig.11 is similar to those
 discovered in the mentioned equilibrium studies,
@@
 the physical meaning is instead quite different in our study:
-The system is under the nonequilibrium conditions, and
+The system is under nonequilibrium conditions, and
 the fluxes are explicitly induced by a physically realistic control, i.e.~EF, although the averaged population of the steady conformations do not change. In contrast,
@@
 
-It must be also added that the transition fluxes can be used to calculate the free energy only in
-the equilibrium case. In the non-equilibrium case, especially for the
-oscillatory EF case, the conformational kinetics of the system is generally
-not Markovian. Therefore, the standard kinetic analysis cannot be used
-here.
+% It must be also added that the transition fluxes can be used to calculate the free energy only in
+% the equilibrium case. In the non-equilibrium case, especially for the
+% oscillatory EF case, the conformational kinetics of the system is generally
+% not Markovian. Therefore, the standard kinetic analysis cannot be used
+% here.
 

### 2014-03-05 writedown/npt-neq/submit.tex
prepare the files for submission

--- 2014-03-05 writedown/npt-neq/alanine.tex
@@
-% \documentclass[aip,jcp,preprint,unsortedaddress,a4paper,onecolum]{revtex4-1}
-\documentclass[a4paper,preprint,unsortedaddress,onecolumn]{revtex4-1}
-% \documentclass[aps,pre,twocolumn,unsortedaddress]{revtex4-1}
-% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% This is a (brief) model paper using the achemso class
+%% The document class accepts keyval options, which should include
+%% the target journal and optionally the manuscript type.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[journal=jctcce,manuscript=manuscript]{achemso}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Place any additional packages needed here.  Only include packages
+%% which are essential, to avoid problems later. Do NOT use any
+%% packages which require e-TeX (for example etoolbox): the e-TeX
+%% extensions are not currently available on the ACS conversion
+%% servers.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
 \usepackage[fleqn]{amsmath}
 \usepackage{amssymb}
-\usepackage[dvips]{graphicx}
-\usepackage{color}
-\usepackage{tabularx}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-
-\makeatletter
-\makeatother
-
-\newcommand{\recheck}[1]{{\color{red} #1}}
-\newcommand{\redc}[1]{{\color{red} #1}}
-\newcommand{\bluec}[1]{{\color{blue} #1}}
-\newcommand{\greenc}[1]{{\color{green} #1}}
+% \usepackage[dvips]{graphicx}
+% \usepackage{color}
+% \usepackage{tabularx}
+% \usepackage{algorithm}
+% \usepackage{algorithmic}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% If issues arise when submitting your manuscript, you may want to
+%% un-comment the next line.  This provides information on the
+%% version of every file you have used.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%\listfiles
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Place any additional macros here.  Please use \newcommand* where
+%% possible, and avoid layout-changing macros (which are not used
+%% when typesetting).
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \newcommand{\recheck}[1]{{\color{red} #1}}
+% \newcommand{\redc}[1]{{\color{red} #1}}
+% \newcommand{\bluec}[1]{{\color{blue} #1}}
+% \newcommand{\greenc}[1]{{\color{green} #1}}
 \newcommand{\vect}[1]{\textbf{\textit{#1}}}
@@
 
-\begin{document}
-
-\title{Exploring the conformational dynamics of alanine dipeptide in solution subjected to an external electric field: A nonequilibrium molecular dynamics simulation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Meta-data block
+%% ---------------
+%% Each author should be given as a separate \author command.
+%%
+%% Corresponding authors should have an e-mail given after the author
+%% name as an \email command. Phone and fax numbers can be given
+%% using \phone and \fax, respectively; this information is optional.
+%%
+%% The affiliation of authors is given after the authors; each
+%% \affiliation command applies to all preceding authors not already
+%% assigned an affiliation.
+%%
+%% The affiliation takes an option argument for the short name.  This
+%% will typically be something like "University of Somewhere".
+%%
+%% The \altaffiliation macro should be used for new address, etc.
+%% On the other hand, \alsoaffiliation is used on a per author basis
+%% when authors are associated with multiple institutions.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \author{Han Wang}
+\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
 \email{han.wang@fu-berlin.de}
-\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
 \author{Christof Sch\"utte}
 \affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
-\affiliation{Zuse Institute Berlin, Germany}
+\alsoaffiliation{Zuse Institute Berlin, Germany}
 \author{Giovanni Ciccotti}
@@
 \affiliation{School of Physics, University College Dublin, Belfield, Dublin 4, Ireland}
-\affiliation{Dipartimento di Fisica, Universit\`a ``La Sapienza'' and CNISM, Piazzale Aldo Moro 5, 00185 Roma, Italy}
+\alsoaffiliation{Dipartimento di Fisica, Universit\`a ``La Sapienza'' and CNISM, Piazzale Aldo Moro 5, 00185 Roma, Italy}
 \author{Luigi Delle Site}
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% The document title should be given as usual. Some journals require
+%% a running title from the author: this should be supplied as an
+%% optional argument to \title.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\title{Exploring the conformational dynamics of alanine dipeptide in solution subjected to an external electric field: A nonequilibrium molecular dynamics simulation}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Some journals require a list of abbreviations or keywords to be
+%% supplied. These should be set up here, and will be printed after
+%% the title and author information, if needed.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \abbreviations{IR,NMR,UV}
+% \keywords{American Chemical Society, \LaTeX}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% The manuscript does not need to include \maketitle, which is
+%% executed automatically.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{document}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% The "tocentry" environment can be used to create an entry for the
+%% graphical table of contents. It is given here as some journals
+%% require that it is printed as part of the abstract page. It will
+%% be automatically moved as appropriate.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{tocentry}
+\includegraphics[height=3.6cm]{fig.ala.new/graphs/final-3.eps}
+% Some journals require a graphical entry for the Table of Contents.
+% This should be laid out ``print ready'' so that the sizing of the
+% text is correct.
+
+% Inside the \texttt{tocentry} environment, the font used is Helvetica
+% 8\,pt, as required by \emph{Journal of the American Chemical
+% Society}.
+
+% The surrounding frame is 9\,cm by 3.5\,cm, which is the maximum
+% permitted for  \emph{Journal of the American Chemical Society}
+% graphical table of content entries. The box will not resize if the
+% content is too big: instead it will overflow the edge of the box.
+
+% This box and the associated title will always be printed on a
+% separate page at the end of the document.
+
+\end{tocentry}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% The abstract environment will automatically gobble the contents
+%% if an abstract is not used by the target journal.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{abstract}
@@
    integrated net probability fluxes.
-  % In this paper, we investigate the conformational dynamics of alanine dipeptide under an external electric field by nonequilibrium molecular dynamics simulation.
-We consider the case of a constant and of an oscillatory field.
-In this context we propose a procedure to implement the temperature control, which removes the irrelevant thermal effects of the field.
-For the constant field different time-scales are identified  in the conformational, dipole moment, and orientational dynamics.
-Moreover, we prove that the solvent structure only marginally changes when the external field is switched on.
-In the case of oscillatory field, the conformational changes are shown to be as strong as in the previous case, and non-trivial nonequilibrium circular paths in the conformation space are revealed by calculating the integrated net probability fluxes.
 \end{abstract}
 
-\maketitle
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% Start the main part of the manuscript here.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 and how likely they are (probability).
-\recheck{One may wonder whether the information extracted from the D-NEMD simulation could have been
+{One may wonder whether the information extracted from the D-NEMD simulation could have been
 extracted just as well from conventional equilibrium simulations.
@@
 reasonably large.
-\recheck{ The proposed temperature control method has similarities with 
+{ The proposed temperature control method has similarities with 
   the stochastic boundary condition proposed by Brooks and Karplus~\cite{brooks1983deformable}.
@@
 described by the CHARMM27 force field~\cite{foloppe2000all}, and dissolved in 644 TIP3P~\cite{jorgensen1983comparison}
-water molecules.  \recheck{The grid-based energy correction map (CMAP)~\cite{mackerell2004extending}
-for the backbone dihedral angles is also used.}
+water molecules. The grid-based energy correction map (CMAP)~\cite{mackerell2004extending}
+for the backbone dihedral angles is also used.
 %The EF exserts force $\vect F = q \vect E(t)$ on
@@
 The branching trajectories were integrated by the
-Leap-frog scheme \bluec{(standard Gromacs implementation)} with the aforementioned nonequilibrium
+Leap-frog scheme (standard Gromacs implementation) with the aforementioned nonequilibrium
 temperature control technique.  The
 time step was $0.002~\textsf{ps}$.
-\recheck{The short-range
+The short-range
 interaction (van der Waals interaction)
@@
 method was applied to calculate the electrostatic interaction in this
-periodic system. For the direct space part of PME the cut-off and smoothing follow the same principles as those applied to the van der Waals interaction.}
-\recheck {All hydrogen involving bonds are constrained by LINCS~\cite{hess1997lincs}, except 
-  the TIP3P water molecules which are constrained by the SETTLE algorithm~\cite{miyamoto2004settle}.}
+periodic system. For the direct space part of PME the cut-off and smoothing follow the same principles as those applied to the van der Waals interaction.
+All hydrogen involving bonds are constrained by LINCS~\cite{hess1997lincs}, except 
+the TIP3P water molecules which are constrained by the SETTLE algorithm~\cite{miyamoto2004settle}.
 In the thermostated region, the original dynamics was
@@
 are not presented in this paper).
-The whole system is also coupled to a Parrinello-Rahman barostat~\cite{parrinello1981polymorphic}~\bluec{(in standard Gromacs implementation)} with $\tau_P = 2.0~\textsf{ps}$ to keep
+The whole system is also coupled to a Parrinello-Rahman barostat~\cite{parrinello1981polymorphic}~(in standard Gromacs implementation) with $\tau_P = 2.0~\textsf{ps}$ to keep
 the pressure at ambient condition (1~Bar). Since the
@@
 dynamics of the system.
-% \bluec{The use of leap-frog scheme and Parrinello-Rahman barostat
+% {The use of leap-frog scheme and Parrinello-Rahman barostat
 % was not our choice, but the default one of Gromacs.}
@@
 estimated with sufficient numerical accuracy (see also Ref.~\cite{schuette2011markov}).
-\recheck{In all the numerical examples of this work, $\Delta t = 1$~ps is used}.
+{In all the numerical examples of this work, $\Delta t = 1$~ps is used}.
 A positive value of $F_{J,I}(t)$ indicates that the
@@
 is projected onto the analysis of the probabilistic link between discretized conformations $\{\confaa, \confab, \confba, \confbb, \confc\}$.
-\recheck{ The concept of net probability flux employed by us is very close to the
+The concept of net probability flux employed by us is very close to the
   concept of kinetic rate.  However, we prefer to stick to our definition which
-is mathematically simpler and univocal.}
+is mathematically simpler and univocal.
 In the case of oscillatory EF, the behaviour of the net probability flux is also highly oscillatory, thus, in order to clearly identify the essential features of the molecular conformational changes, it is convenient to study the integrated net probability flux, defined as:
@@
     green to $\confab$, dark blue to $\confba$, purple to $\confbb$ and light blue
-    to $\confc$. \recheck{
+    to $\confc$. {
       The solid lines denote the results of one branching trajectory
@@
     for $J=\confc$.
-    \bluec{This plot is drawn from the four-branching-trajectories case (see the text).}
+    {This plot is drawn from the four-branching-trajectories case (see the text).}
     }
@@
 Fig.~\ref{fig:tmp5}.
-\recheck{In order to show that  our simulation results are robust with respect to the randomness introduced by the (local) Langevin thermostat, we have tested the effects of changing random seeds for the thermostat in the thermostated region.
+In order to show that  our simulation results are robust with respect to the randomness introduced by the (local) Langevin thermostat, we have tested the effects of changing random seeds for the thermostat in the thermostated region.
 We compared simulation results obtained by starting a branching trajectory
@@
 Results are consistent within the statistical uncertainty (see Fig.\ref{fig:tmp5}).
-}
 The $\beta$-sheet conformations $\confba$ and $\confbb$,
 which are present at the initial stage after EF is switched on,
-\recheck{fade away as the system relaxes}. The
+{fade away as the system relaxes}. The
 probability of the $\alpha$-helix conformation $\confaa$, grows from 0.45 to 0.69.
@@
 The left-hand helix conformation $\confc$ noticeably grows from 0 to 0.22.
-We plot the net probability fluxes \bluec{of the four-branching-trajectories case} in Fig.~\ref{fig:tmp6}.
+We plot the net probability fluxes {of the four-branching-trajectories case} in Fig.~\ref{fig:tmp6}.
 Results show that for short $t$, the net fluxes are generally non-zero,
@@
 equilibrium (at zero EF),  starting a dynamical nonequilibrium process.
-\recheck{After sufficiently long time, the system
+After sufficiently long time, the system
 is fully relaxed to the new stationary state, in
@@
 the total time of the branching trajectories. 
-}
 % After a time long enough, the system
@@
 an electric field, naturally leads to the question 
-\recheck{
-  of the alignment of the molecular dipole vector along the direction of external EF}, and, in turn, of how this is related
-to the overall \recheck{conformational change} of the molecule as reported in
+  of the alignment of the molecular dipole vector along the direction of external EF, and, in turn, of how this is related
+to the overall conformational change of the molecule as reported in
 the previous section.
@@
     See the text for more details.
-    \recheck{The shadowed region denotes the
+    {The shadowed region denotes the
       statistical uncertainty of the $L=2.7$~nm $R_{ex}=1.0$~nm case at 95\% confidence level.
@@
 not exposed to a strong enough EF for a time long enough.
-For  $\period =10$ and 40~ps, the orientation of the alanine shows a \bluec{very} weak tendency
+For  $\period =10$ and 40~ps, the orientation of the alanine shows a {very} weak tendency
 to be parallel to the EF. It is worth to notice that for constant EF,
@@
 integrated probability net fluxes, which imply some lasting and directional
-fluxes among the conformations \bluec{in steady state}.
+fluxes among the conformations {in steady state}.
 Fig.~\ref{fig:tmp11} presents
@@
 conformations and how an electric field is likely to modify it.
-\recheck{
   Although the network presented in Fig.~\ref{fig:tmp11} is similar to those
@@
   such net probability fluxes do not explicitly exist.
-}
 The probability flux of $\period =40$~ps is quantitatively
@@
 equipment~\cite{vogel2008femtosecond}.
-\recheck{The minimal frequency investigated here (5.00~GHz, i.e.~$\period = 200$~ps)
+{The minimal frequency investigated here (5.00~GHz, i.e.~$\period = 200$~ps)
 is of the same order of magnitude as the microwave
@@
 
-\section*{Acknowledgment}
-  H.W. acknowledges the valuable discussions with Simone Meloni and Burkhard Schmidt.
-  This work was partially supported by the Deutsche
-  Forschungsgemeinschaft (DFG), with the Heisenberg
-  Grant provided to L.D.S. (Grant No. DE 1140/5-1),
-  and with the support within the priority program ``Ionic Liquids'' SPP 1191
-  (H.W. and L.D.S.). 
-  H.W.~and C.S.~thank the financial support by DFG research center MATHEON.
-  Funding from the IIT SEED project SIMBEDD and from the SFI Grant 08-IN.1-I1869 is acknowledged by G.C..
-
   \appendix
 \section{Comparison with the linear response theory}  
-\recheck{
 A commonly used equilibrium approach that can describe the nonequilibrium
@@
 correlation function itself.
-\bluec{
   In Fig.~\ref{fig:appdx1}~(b),
@@
 D-NEMD~Eq.~\eqref{eqn:tmp1} to calculate the
-nonequilibrium averages. }
+nonequilibrium averages. 
 In fact, since the total computational effort of
@@
 observation has already been reported in Ref.~\cite{ciccotti1975direct}.
-}
 
@@
   \caption{
-    \bluec{The numerical result of the linear response theory.
+    {The numerical result of the linear response theory.
     (a): The correlation function $\langle j(0)\cdot \chi_{\confc}(t)
@@
 
-\bibliography{ref}{}
-\bibliographystyle{unsrt}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% The "Acknowledgement" section can be given in all manuscript
+%% classes.  This should be given within the "acknowledgement"
+%% environment, which will make the correct section or running title.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{acknowledgement}
+
+  H.W. acknowledges the valuable discussions with Simone Meloni and Burkhard Schmidt.
+  This work was partially supported by the Deutsche
+  Forschungsgemeinschaft (DFG), with the Heisenberg
+  Grant provided to L.D.S. (Grant No. DE 1140/5-1),
+  and with the support within the priority program ``Ionic Liquids'' SPP 1191
+  (H.W. and L.D.S.). 
+  H.W.~and C.S.~thank the financial support by DFG research center MATHEON.
+  Funding from the IIT SEED project SIMBEDD and from the SFI Grant 08-IN.1-I1869 is acknowledged by G.C..
+\end{acknowledgement}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% The same is true for Supporting Information, which should use the
+%% suppinfo environment.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{suppinfo}
+
+% This will usually read something like: ``Experimental procedures and
+% characterization data for all new compounds. The class will
+% automatically add a sentence pointing to the information on-line:
+
+\end{suppinfo}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% The appropriate \bibliography command should be placed here.
+%% Notice that the class file automatically sets \bibliographystyle
+%% and also names the section correctly.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\bibliography{ref}
 

### 2014-03-05 writedown/npt-neq/reply/reply.tex
prepare the files for submission
convert for submission

@@
 
-Below you find our reply to the the referees.
-We apologize for the long time needed for the reply due to the holiday of one of the authors.
+Below you find our reply to the the referees. We apologize for the long time needed for the reply due to the holiday of one of the authors.
 The request of the referees implied a rather massive additional computational effort.
 The result of such effort is highly satisfactory and the validity of the paper is now much higher.
-We are now confident that the paper can be accepted for publication.\\
+We are now confident that the paper can be accepted for publication.
+To help the referees, we have also submitted a seperate file (alanine.pdf) with all changes to the manuscript colored in red.
+\\
 
@@
 Yes, the CMAP correction is used. We mention it in the
-section III.A. of the updated manuscript.
+section III.A (3.1). of the updated manuscript.
 \\
@@
 is mathematically simpler and univocal.
-A comment along this direction has been added to the end of section III.B.
+A comment along this direction has been added to the end of section III.B (3.2).
 \\

### 2014-03-05 writedown/npt-neq/submit.tex
convert for submission

@@
 \begin{tocentry}
-\includegraphics[height=3.6cm]{fig.ala.new/graphs/final-3.eps}
+\includegraphics[height=3.6cm]{final-3.eps}
 % Some journals require a graphical entry for the Table of Contents.
@@
   \centering
-  \includegraphics[width=1.00\textwidth]{fig.ala.new/fig.all/fig-all.eps}
+  \includegraphics[width=1.00\textwidth]{fig-all.eps}
   % \raisebox{0.2\height}{\includegraphics[width=0.22\textwidth]{c-2.eps}}
@@
   \centering
-  \includegraphics[]{fig.ala.new/fig-meta-more.eps}
+  \includegraphics[]{fig-meta-more.eps}
   \caption{The time-dependent probability of conformations $P_I(t)$ 
@@
   \centering
-  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-1.eps}
-  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-2.eps}
-  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-3.eps}
-  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-4.eps}
-  \includegraphics[width=0.3\textwidth]{fig.ala.new/fig-trans-010-flux-5.eps}
+  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-1.eps}
+  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-2.eps}
+  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-3.eps}
+  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-4.eps}
+  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-5.eps}
   \caption{
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{fig.ala.new/field.dipole/fig-dipol-order-conf.eps}
+  \includegraphics[width=0.45\textwidth]{fig-dipol-order-conf.eps}
   \caption{The
@@
   \centering
-  \includegraphics[]{fig.ala.new/fig-meta-conv.eps}
+  \includegraphics[]{fig-meta-conv.eps}
   \caption{Testing the finite-size effect on the dynamical and thermostated region.
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{fig.ala.new/fig-mode2-dipol.eps}
-  \includegraphics[width=0.48\textwidth]{fig.ala.new/fig-mode2-order.eps}
+  \includegraphics[width=0.48\textwidth]{fig-mode2-dipol.eps}
+  \includegraphics[width=0.48\textwidth]{fig-mode2-order.eps}
   \caption{Illustration of the effect of the oscillatory EF on the system:
@@
   \centering
-  \includegraphics[width=0.32\textwidth]{fig.ala.new/fig-meta-mode2-0010.eps}
-  \includegraphics[width=0.32\textwidth]{fig.ala.new/fig-meta-mode2-0040.eps}
-  \includegraphics[width=0.32\textwidth]{fig.ala.new/fig-meta-mode2-0200.eps}
+  \includegraphics[width=0.32\textwidth]{fig-meta-mode2-0010.eps}
+  \includegraphics[width=0.32\textwidth]{fig-meta-mode2-0040.eps}
+  \includegraphics[width=0.32\textwidth]{fig-meta-mode2-0200.eps}
   % \includegraphics[width=0.49\textwidth]{fig-meta-mode2-2000.eps}
@@
   \centering
-  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-1.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-2.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-3.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-4.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0010-iflux-5.eps}\\
-  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-1.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-2.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-3.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-4.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0040-iflux-5.eps}\\
-  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-1.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-2.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-3.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-4.eps}
-  \includegraphics[width=0.19\textwidth]{fig.ala.new/fig-trans-mode2-0200-iflux-5.eps}\\
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-1.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0010-iflux-5.eps}\\
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-1.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0040-iflux-5.eps}\\
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-1.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig-trans-mode2-0200-iflux-5.eps}\\
   \caption{
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{fig.ala.new/graphs/graph-t0010-2.eps}
+  \includegraphics[width=0.6\textwidth]{graph-t0010-2.eps}
   \caption{Schematic plot of the main probability fluxes between conformations
@@
   \centering
-  \includegraphics{fig.ala.new/fig-corr-meta.eps}
-  \includegraphics{fig.ala.new/fig-corr-meta-c.eps}
+  \includegraphics{fig-corr-meta.eps}
+  \includegraphics{fig-corr-meta-c.eps}
   \caption{

### 2014-05-12 writedown/zm/group.nlist/cutoff.tex
add write down for zm

\documentclass[aps,pre,preprint]{revtex4-1}

\usepackage[fleqn]{amsmath}
\usepackage{amssymb}
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{tabularx}
\usepackage{algorithm}
\usepackage{algorithmic}

\newcommand{\gromacs}[0]{\texttt{Gromacs}}
\newcommand{\rlist}[0]{\texttt{rlist}}
\newcommand{\rcoulomb}[0]{\texttt{rcoulomb}}

\begin{document}

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{fig/cutoff.eps}
  \caption{The schematic plot of gromacs cut-off method. The two molecules
  in the plot are considered to be neighbors.}
  \label{fig:tmp1}
\end{figure}

For simplicity, in this instruction we only consider a system of water
molecules. In \gromacs, there are two steps of finding a pair of interacting atoms:
\begin{enumerate}
\item Building a neighbor list
\item Finding a pair of interacting atoms out of the neighbor list.
\end{enumerate}
The neighbor list may not be updated every timestep of MD
simulation. When a neighbor list is built, it may be used for several
following time-steps, so the computational cost of building neighbor
list can be saved.  \gromacs{} builds the neighbor list by using the
``group'' method.  The range of building
neighbor list is called \rlist{}, see the Fig.~\ref{fig:tmp1}.
The ``group'' method means that all pair of water
molecules, whoes center-of-geometry (COG) distance is shorter than
\rlist, will be recoreded by the neighbor list.
% In fact, all pair of
% atoms on the pair of molecules are built into the neighbor list.

Whether the a pair of molecules in the neighbor list interacts
depends on the cut-off of the interaction. We only consider the
Coulomb interaction, the cut-off of which is denoted by \rcoulomb, see
Fig~\ref{fig:tmp1}. \gromacs{} actually allows $\rcoulomb = \rlist$,
then the molecules are interacting in a ``group'' fashion:
when the neighbor list is built, all pairs of molecules in the neighbor list
interact as long as the neighbor list is considered valid.
However, when \rcoulomb{} is shorter than \rlist{}, then the interaction
fashion is different.
At this point I was confused: I thought that the interaction between two
molecules in the neighbor list that is built in the ``group'' fashion is also
cut-offed in a ``group'' fashion, however, in fact, the interaction is 
cut-offed in an atomistic fashion.

I confirm the atomistic cut-off fashion by doing simulation in the
following two cases in Tab.~\ref{tab:tmp1} and~\ref{tab:tmp2}. In both cases, $\rcoulomb
= 1.2$~nm and $\rlist=1.5$~nm. The system contains only 2 water molecules.
The van der Waals interaction is switched off.
In the 1st case, the COG distance between the molecules is shorter than
the \rcoulomb, while it is langer than \rcoulomb{} in the 2nd case.
It is obvious that whether two atoms interact depends only on the atomistic
distance, and is independent with the COG distance. This confirms the
atomistic cut-off fashion.
% \begin{enumerate}
% \item $\rcoulomb = 1.2$~nm, $rlist=1.5$~nm. 
% \item $\rcoulomb = 1.2$~nm, $rlist=1.5$~nm.
% \end{enumerate}
\begin{table}
  \centering
  \caption{The 1st testing cases of the cut-off scheme. First two columns: the atom pairs recoreded in the neighbor list.
    They are from two neighboring molecules.
    COG is the center of geometry. H1 means the first hydrogen and the H2 means the second hydrogen.
    If the two atoms are interacting, we write ``y'' in the fourth column, otherwise, we write ``n''.
  }
  \label{tab:tmp1}
  \begin{tabular*}{0.8\textwidth}{@{\extracolsep{\fill}}cccc}\hline\hline
    1st atom  & 2nd atom & Distance [nm] & Interacting \\\hline
    COG & COG &  1.1413 & --\\
    O	&O	&1.0940	&y \\
    O	&H1	&1.1890	&y \\
    O	&H2	&1.0740	&y \\
    H1	&H1 	&1.2840	&n \\
    H1	&H2 	&1.1687	&y \\
    H2	&H2	&1.0460	&y \\
    \hline\hline
  \end{tabular*}
\end{table}

\begin{table}
  \centering
  \caption{The 2nd testing cases of the cut-off scheme. }
  \label{tab:tmp2}
  \begin{tabular*}{0.8\textwidth}{@{\extracolsep{\fill}}cccc}\hline\hline
    1st atom  & 2nd atom & Distance [nm] & Interacting \\\hline
    COG & COG &  1.2413 & --\\
    O	&O	&1.1940	&y \\
    O	&H1	&1.2890	&n \\
    O	&H2	&1.1740	&y \\
    H1	&H1 	&1.3840	&n \\
    H1	&H2 	&1.2687	&n \\
    H2	&H2	&1.1460	&y \\
    \hline\hline
  \end{tabular*}
\end{table}

If we assume \rlist{} is sufficiently larger than \rcoulomb{}, then
the ``group'' neighbor searching method can mimic the atomistic
neighbor searching method, in total we use the \gromacs{}
implementation of the ZM method is in an atomistic cut-off way.
Here ``sufficiently'' means that
\begin{align}
  d_{COG} + r_{COG,H} < \frac12 (\rlist - \rcoulomb),
\end{align}
where $d_{COG}$ is the COG displacement with respect to the COG position
when the neighbor list was built, and $r_{COG,H}$ is the distance between
the COG and the hydrogen atom (notice that  $r_{COG,H} >  r_{COG,O}$).
For TIP3P, $r_{COG,H}\approx 0.078$~nm, then
in the case of $\rlist - \rcoulomb = 0.3$~nm, we have
\begin{align}\label{eqn:tmp2}
  d_{COG} < 0.072\ \textrm{nm}.
\end{align}
In the numerical tests, the maximum velocity found in our simulation
of TIP3P water at 300~K was bounded by 8~nm/ps. The time step was
0.001~ps, and the neighbor list was updated every 5 time-steps, so
$d_{COG}$ is estimated to be bounded by $0.001 \times 5 \times 8 = 0.04$~nm,
which satisfies Eq.~\eqref{eqn:tmp2}.

Since all of our simulations had $\rlist - \rcoulomb = 0.3$~nm, the ZM
interaction was indeed treated in an atomistic way.

% when the \rlist{} is sufficiently larger than \rcoulomb{}
% (the region between them is called the buffer region), the atoms are
% interacting in an atomistic fashion.

% however, when we use $\rcoulomb < \rlist$,
% the region between \rcoulomb and \rlist is called the buffer region.
% If the size of the buffer region is large enough, then

\end{document}

### 2014-05-12 writedown/zm/report/report.tex
add write down for zm

\documentclass[a4paper,reprint,unsortedaddress,onecolumn]{revtex4-1}
% \documentclass[reprint,unsortedadress,oneclumn]{revtex4-1}

\usepackage{amsmath,amssymb,amsfonts,latexsym}
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{indentfirst}

\newcommand{\eps}{\varepsilon}
\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}            
\newcommand{\bluec}[1]{{\color{blue} #1}}            
\newcommand{\vect}[1]{\textbf{\textit{#1}}}

\begin{document}

\title{A Critical Appraisal of Zero-Multiple Method in Simulation Biomolecular Systems}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\author{Ikuo Fukuda}
\email{ifukuda@protein.osaka-u.ac.jp}
\affiliation{Institute for Protein Research, Osaka University, Japan}

\begin{abstract}
\end{abstract}

\maketitle

\begin{table}
  \centering
  \caption{A list of systems tested in this work. We report, from left to right, the number of water
    molecules in the system (TIP3P model), box size, length of equilibriation, length of productive trajecty and the frequency
    that the configurations are recorded or the phsical properties are calculted.}
  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}c rrrrr}\hline\hline
    System      & \# of Water Mols. & Box size [$\textrm{nm}^3$]  & Equilibriation [ps] & Traj. Length [ps] & Freq. Record [ps]  \\\hline
    S1          & 4,500          & $5.15^3$              & 3,000        & 17,000        & 5.0 \\
    S1'         &   4,500        & $5.15^3$              & --           &  6,000        & -- \\
    L0          &   13,824       & $7.49^3$              & 200          & 1,800         & 0.1 \\
    L1          &   13,824       & $7.49^3$              & 3,000        & 17,000        & 10.0 \\
    L1'         &   13,824       & $7.49^3$              & --           & 10,000        & -- \\
    \hline\hline
  \end{tabular*}
  \label{tab:tmp1}
\end{table}

The systems used for MD simulations are listed in
Table.\ref{tab:tmp1}.  The initial configurations are prepared by in
the following steps: (1) A NPT simulation of system L0 with SPME~\cite{darden1993pme, essmann1995spm}
electrostatic. The equilibrium density of the system is calculated
from this simulation. (2) Initial configurations that has 4,500 and
13,824 molecules are generated at the calculated equilibrium
density. (3) NVT simulations with SPME electrostatic for system S1'
and L1' are performed. (4) The output configuration of S1' is used as
initial configuration for system S1, and the output configuration of
L1' is used as initial configuration for system L0 and L1.  The SPME
parameters for all simulations reported by this work is: real space
cut-off 1.90~nm. The cut-off is smoothed from 1.85 to 1.90~nm by the
``\texttt{switch}'' method provide by Gromacs
4.6~\cite{hess2008gromacs, pronk2013gromacs}. The reciprocal space
grid spacing is 0.06~nm. The B-Spline interpolation order is 6. The
splitting parameter is optimized by the error estimate for the SPME method~\cite{wang2010optimizing}.

\subsubsection{Pressure}
The results are plotted in Fig.~\ref{fig:tmp0}.
\begin{figure}
  \centering
  \includegraphics[]{pressure-methods.eps}
  \caption{The pressure convergence with respect to the cut-off radius.
    For ZM method, the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
  }
  \label{fig:tmp0}
\end{figure}

\subsubsection{The dielectric constant}

The dielectric constant:
\begin{align}
  \eps = 1 + \frac{1}{3L^3 k_BT} ( \langle \vert \vect M\vert^2\rangle - \vert\langle \vect M\rangle\vert^2 )
\end{align}
where
\begin{align}
  \vect M = \sum_i\boldsymbol\mu_i = \sum_{\alpha\in i} q_\alpha\vect r_\alpha
\end{align}
The results are listed in Tab.~\ref{tab:tmp2}

\begin{table}
  \centering
  \caption{A list of the dielectric constant calculated for different systems by different methods.
    The paremeters are provided. The parenthesises in the last column show the statistical uncertanty
    of the last two digits upto the confidence level of 95~\%.}
  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}cccc rr}\hline\hline
    System & Method      &       $\alpha$ [$\textrm{nm}^{-1}$] & $r_c$ [nm] &    $l$     &       $\eps$ \\\hline
    S1  &       ZM          &       0.00    &       1.2     &       1       &       99.8 (3.8)\\ 
    S1  &       ZM          &       0.00    &       1.2     &       2       &       95.2 (3.6)\\ 
    S1  &       ZM          &       0.00    &       1.2     &       3       &       93.9 (3.7)\\ 
    S1  &       ZM          &       0.00    &       1.5     &       3       &       98.7 (3.8)\\ 
    S1  &       ZM          &       0.00    &       1.8     &       3       &      100.7 (3.6)\\ 
    S1  &       ZM          &       0.00    &       1.2     &       4       &       94.7 (3.6)\\
    S1   & SPME          & 2.09  & 1.9   &       --      &       98.8 (4.0) \\
    S1  & RF             & --  & 1.2 & -- & 60.6   (1.7) \\
    L1  &       ZM          &       0.00    &       1.2     &       1       &       97.1 (3.2)\\ 
    L1  &       ZM          &       0.00    &       1.2     &       2       &       95.6 (3.5)\\ 
    L1  &       ZM          &       0.00    &       1.2     &       3       &       95.8 (4.6)\\ 
    L1  &       ZM          &       0.00    &       1.5     &       3       &       98.0 (3.3)\\ 
    L1  &       ZM          &       0.00    &       1.8     &       3       &       98.9 (4.2)\\ 
    L1  &       ZM          &       0.00    &       2.1     &       3       &       98.8 (3.9)\\ 
    L1  &       ZM          &       0.00    &       1.2     &       4       &       97.8 (3.9)\\
   L1   & SPME          & 2.09  & 1.9   &       --      &       98.7 (3.5) \\
    L1  & RF             & --  & 1.2 & -- & 60.8   (2.0) \\
    \hline\hline
  \end{tabular*}
  \label{tab:tmp2}
\end{table}

\subsubsection{Kirkwood G-factor}

The Kirkwood G-factor is defined by~\cite{vanderSpoel2006origin}
\begin{align}
  G_k(r) =
  \Big\langle
  \frac 1N
  \sum_{i=1}^N \sum_{j, r_{ij} < r}
  \frac {\boldsymbol\mu_i \cdot \boldsymbol\mu_j}{\vert \boldsymbol\mu_i\vert \cdot \vert\boldsymbol\mu_j\vert}
  \Big\rangle,
\end{align}
where $r_{ij}$ denotes the oxygen-oxygen distance between two water
molecules.  It is well know that the G-factor is system size
dependent~\cite{vanderSpoel2006origin}. Here we show the G-factor for
both a smaller system S1 (Fig.~\ref{fig:tmp1}) and a larger system L1
(Fig.~\ref{fig:tmp2}).  In the figures, the statistical uncertanty of
the SPME method is denoted by the red error bar, while thoes of the
other methods are essentially the same, so they are not presented for
clarity.  In both the system, the RF method is qualitatively
wrong. The results of the ZM method are consistent with SPME
method. The lower order produces better consistency.  An artificial
oscillation around the cut-off radius presents for $l=1$, but it is
not obvious for $l\geq 2$.  For high order ZM (here $l=3$ is investigated),
using larger cut-off radius can substantially improve the accuracy.

\begin{figure}
  \centering
  \includegraphics[]{fig-gkr-small.eps}
  \includegraphics[]{fig-gkr-small-conv.eps}
  \caption{The Kirkwood G-factor calculated for system S1.
    % The result of different methods are compared in the left plot.
    For all ZM methods the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
    In the left plot the cut-off radius for all orders is set to $1.2$~nm, while
    in the right plot, only the order $l=3$ is considered and different cut-off radii are compared.
    The RF method uses a cut-off radius of 1.2~nm, and dielectric constant of 80.
    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red bar.
  }
  \label{fig:tmp1}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[]{fig-gkr.eps}
  \includegraphics[]{fig-gkr-conv.eps}
  \caption{The Kirkwood G-factor calculated for system L1.
    % The result of different methods are compared in the left plot.
    For all ZM methods the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
    In the left plot the cut-off radius for all orders is set to $1.2$~nm, while
    in the right plot, only the order $l=3$ is considered and different cut-off radii are compared.
    The RF method uses a cut-off radius of 1.2~nm, and dielectric constant of 80.
    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red bar.
  }
  \label{fig:tmp2}
\end{figure}

\newpage
\bibliography{ref}{}
\bibliographystyle{unsrt}

\end{document}

### 2014-05-13 zm/template.water/parameters.sh
prepare for TI simulation

@@ -28,3 +28,6 @@ gmx_e_rf=80.0
 zm_l=2
 zm_alpha=0.1
 
+gmx_lambda_start=0
+gmx_lambda_step=0.05
+gmx_lambda_end=1

### 2014-05-13 zm/template.water/run.ti.sh

@@ -1,0 +1,56 @@
+#!/bin/bash
+
+if [ $# -ne 1 ] ; then
+    echo useage:
+    echo run.ti.sh TARGET
+    exit
+fi
+target=$1
+if test ! -d $target; then
+    echo "No dir $target"
+    exit
+fi
+
+source env.sh
+source parameters.sh
+
+if echo "$gmx_ele_method" | grep pme &> /dev/null ; then
+    echo "# run with ele method pme"
+    gmx_ele_method_gromacs=pme
+    gmx_ele_method_ind=1
+    if echo "$gmx_ele_method" | grep pme-switch &> /dev/null ; then
+	echo "# run with ele method pme-switch"
+	gmx_ele_method_gromacs=pme-switch
+	gmx_ele_method_ind=11
+    fi
+else if echo "$gmx_ele_method" | grep zm &> /dev/null ; then
+    echo "# run with ele method zm"
+    gmx_ele_method_gromacs=user
+    gmx_ele_method_ind=0
+else if echo "$gmx_ele_method" | grep rf &> /dev/null ; then
+    echo "# run with ele method rf"
+    gmx_ele_method_gromacs=reaction-field
+    gmx_ele_method_ind=2
+fi
+fi
+fi
+
+echo "# doing in $target"
+echo "# call grompp"
+cd $target
+$gmx_grompp_command > /dev/null
+if [ $gmx_ele_method_ind -eq 1 ] || [ $gmx_ele_method_ind -eq 11 ]; then
+    echo "# tune pme parameter"
+    $gmx_tune_command -tune yes -self 1e-4 -seed $gmx_seed -nice 0
+    mv -f tuned.tpr topol.tpr
+fi
+cd ..
+
+echo "# call mdrun"
+echo "## run with `which mdrun`"
+echo "## run with $gmx_mdrun_command"
+cd ti
+$gmx_mdrun_command
+cd ..
+
+

### 2014-05-13 zm/template.water/setup.ti.sh

@@ -1,0 +1,196 @@
+#!/bin/bash
+
+source env.sh
+source parameters.sh
+
+if echo "$gmx_ele_method" | grep pme &> /dev/null ; then
+    echo "# run with ele method pme"
+    gmx_ele_method_gromacs=pme
+    gmx_ele_method_ind=1
+    if echo "$gmx_ele_method" | grep pme-switch &> /dev/null ; then
+	echo "# run with ele method pme-switch"
+	gmx_ele_method_gromacs=pme-switch
+	gmx_ele_method_ind=11
+    fi
+else if echo "$gmx_ele_method" | grep zm &> /dev/null ; then
+    echo "# run with ele method zm"
+    gmx_ele_method_gromacs=user
+    gmx_ele_method_ind=0
+else if echo "$gmx_ele_method" | grep rf &> /dev/null ; then
+    echo "# run with ele method rf"
+    gmx_ele_method_gromacs=reaction-field
+    gmx_ele_method_ind=2
+fi
+fi
+fi
+
+echo "# copy files"
+if test -d ti; then
+    mv -f ti ti.`date +%s`
+fi
+mkdir -p ti
+cp -a $gmx_sys_tempalte_dir ./ti/seed
+
+echo "# revise grompp"
+cd ti/seed/
+gmx_nsteps=`echo "($gmx_time + 0.5 * $gmx_dt) / $gmx_dt" | bc`
+gmx_nstenergy=`echo "($gmx_energy_feq + 0.5 * $gmx_dt) / $gmx_dt" | bc`
+gmx_nstxtcout=`echo "($gmx_conf_feq   + 0.5 * $gmx_dt) / $gmx_dt" | bc`
+gmx_seed=`date +%s`
+if test $gmx_ele_method_ind -eq 0; then # zm
+    gmx_nstlist=$gmx_nstlist
+    gmx_rcut_ele_switch=$gmx_rcut_ele
+fi
+if test $gmx_ele_method_ind -eq 1; then # pme
+    gmx_rcut_ele=$gmx_rlist
+    gmx_rcut_ele_switch=$gmx_rcut_ele
+fi
+if test $gmx_ele_method_ind -eq 2; then # rf
+    gmx_rcut_ele=$gmx_rlist
+    gmx_rcut_ele_switch=$gmx_rcut_ele
+fi
[…]

### 2014-05-13 zm/template.water/auto.allegro.ti.sh
fix bugs. add auto submission file

@@ -1,0 +1,35 @@
+#!/bin/bash
+
+if [ $# -ne 1 ] ; then
+    echo useage:
+    echo auto.allegro.ti.sh TARGET
+    exit
+fi
+target=$1
+
+source env.sh
+
+cwd=`pwd`
+tmpname=$cwd/$target
+jobname=${tmpname##*/}
+
+rm -f allegro.$jobname.out
+
+echo "#!/bin/bash"				>  submit.$jobname.sh
+echo "#PBS -N $jobname"				>> submit.$jobname.sh
+echo "#PBS -o allegro.$jobname.out"		>> submit.$jobname.sh
+echo "#PBS -e allegro.$jobname.out"		>> submit.$jobname.sh
+echo "#PBS -M han.wang@fu-berlin.de"		>> submit.$jobname.sh
+echo "#PBS -l walltime=24:00:00"		>> submit.$jobname.sh
+echo "#PBS -l nodes=1:ppn=$nnodes"		>> submit.$jobname.sh
+echo "#PBS -l pmem=1000mb"			>> submit.$jobname.sh
+
+echo "cd $cwd"					>> submit.$jobname.sh
+echo "hostname"					>> submit.$jobname.sh
+echo "date"					>> submit.$jobname.sh
+echo "pwd"					>> submit.$jobname.sh
+#echo "./assign.param.sh"			>> submit.$jobname.sh
+echo "./run.ti.sh $target"			>> submit.$jobname.sh
+
+qsub submit.$jobname.sh &> jobid
+

### 2014-05-13 zm/template.water/env.allegro.sh

@@ -1,4 +1,4 @@
-nnodes=64
+nnodes=8
 
 gmx_dir=$HOME/local/gromacs/4.6.5/
 source $gmx_dir/bin/GMXRC

### 2014-05-13 zm/template.water/run.ti.sh

@@ -41,6 +41,7 @@ cd $target
 $gmx_grompp_command > /dev/null
 if [ $gmx_ele_method_ind -eq 1 ] || [ $gmx_ele_method_ind -eq 11 ]; then
     echo "# tune pme parameter"
+    gmx_seed=`date +%s`
     $gmx_tune_command -tune yes -self 1e-4 -seed $gmx_seed -nice 0
     mv -f tuned.tpr topol.tpr
 fi
@@ -49,7 +50,7 @@ cd ..
 echo "# call mdrun"
 echo "## run with `which mdrun`"
 echo "## run with $gmx_mdrun_command"
-cd ti
+cd $target
 $gmx_mdrun_command
 cd ..
 

### 2014-05-13 zm/template.water/setup.ti.sh

@@ -126,6 +126,7 @@ do
     fi
     fi
     sed -e "/^free-energy /s/=.*/= yes/g" grompp.mdp |\
+    sed -e "/^constraints /s/=.*/= h-bonds/g" |\
     sed -e "/^init_lambda /s/=.*/= $i/g" |\
     sed -e "/^delta_lambda /s/=.*/= 0/g" |\
     sed -e "/^foreign_lambda /s/=.*/= $tmp_foreign/g" |\

### 2014-05-13 zm/template.water/tools/scripts/epsilon.sh

@@ -9,8 +9,8 @@ function do_epsilon () {
     source parameters.sh
     echo "# find $folder, cal epsilon"
     cd $folder
-    echo "# command: $command -b $gmx_equi_skip"
-    $command -b $gmx_equi_skip | head -n 4 > epsilon.out
+    echo "# command: $command -b $gmx_equi_skip --num-data-block 32"
+    $command -b $gmx_equi_skip --num-data-block 32 | head -n 4 > epsilon.out
     cd ..
 }
 

### 2014-05-13 zm/template.water/run.ti.sh
fix bug

@@ -11,6 +11,7 @@ if test ! -d $target; then
     exit
 fi
 
+cwd=`pwd`
 source env.sh
 source parameters.sh
 
@@ -45,13 +46,13 @@ if [ $gmx_ele_method_ind -eq 1 ] || [ $gmx_ele_method_ind -eq 11 ]; then
     $gmx_tune_command -tune yes -self 1e-4 -seed $gmx_seed -nice 0
     mv -f tuned.tpr topol.tpr
 fi
-cd ..
+cd $cwd
 
 echo "# call mdrun"
 echo "## run with `which mdrun`"
 echo "## run with $gmx_mdrun_command"
 cd $target
 $gmx_mdrun_command
-cd ..
+cd $cwd
 
 

### 2014-05-20 zm/template.water/tools/scripts/diffusivity.sh
fix bug, change default num-in-block, add missing files

@@ -1,0 +1,17 @@
+#!/bin/bash
+
+source env.sh
+source parameters.sh
+
+cd nvt
+
+echo 0 | g_msd -nice 0 -b $gmx_equi_skip &> msd.out
+
+result=`grep D msd.out | grep System `
+
+value=`echo $result | cut -d ']' -f 2 | awk '{print $1}'`
+error=`echo $result | cut -d ']' -f 2 | awk '{print $3}' | cut -d ')' -f 1`
+
+echo "# value error"> diffusivity.out
+echo $value $error >> diffusivity.out
+

### 2014-05-21 writedown/zm/report/report.tex
add table for result of some numbers

@@
 \subsubsection{Pressure}
-The results are plotted in Fig.~\ref{fig:tmp0}.
+The results are plotted in Fig.~\ref{fig:tmp0}. All pressure calculations are done with system L0.
 \begin{figure}
@@
 
+\begin{table}
+  \centering
+  \caption{A list of the dielectric constant calculated for different systems by different methods.
+    The paremeters are provided. The parenthesises in the last column show the statistical uncertanty
+    of the last two digits upto the confidence level of 95~\%.}
+  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}cccc rrrr}\hline\hline
+    Method      &   $r_c$ [nm] &    $l$     &  $\mu$ [kJ/mol] & $D$ [$10^{-9}\textrm{m}^2/\textrm{s}$] & $C_v$ [J/(mol K)] & $\eps$ & $\eta$ [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
+    SPME        &         1.9     &       --      &       $-26.08$ (0.24) & 5.93 (0.42)   & 72.21 (0.97)  & 97.6 (3.4)  & 0.315 (0.007)\\
+    RF          &         1.2     & -- & $-26.03$   (0.32)    & 6.27 (0.11)   & 72.28 (0.81)  & 59.4  (1.3)     & 0.449 (0.020) \\
+    ZM          &         1.2     &       1       &       $-26.12$ (0.30) & 5.55 (0.02)   & 71.75 (0.89)  & 95.5 (2.4)  & 0.346 (0.006)\\ 
+    ZM          &         1.2     &       2       &       $-26.00$ (0.24) & 5.72 (0.37)   & 71.53 (0.88)  & 95.4 (2.5)  & 0.318 (0.012)\\ 
+    ZM          &         1.2     &       3       &       $-25.76$ (0.20) & 5.82 (0.12)   & 71.58 (0.88)  & 96.0 (2.7)  & 0.321 (0.008)\\ 
+    ZM          &         1.2     &       4       &       $-25.37$ (0.26) & 5.92 (0.08)   & 71.07 (0.84)  & 99.7 (2.2)  & 0.318 (0.013)\\
+    \hline\hline
+  \end{tabular*}
+  \label{tab:tmp2}
+\end{table}
+
 \subsubsection{Kirkwood G-factor}
@@
   \includegraphics[]{fig-gkr-small-conv.eps}
+  \includegraphics[]{fig/result.nvt.small/fig-eps-t-3000.eps}
+  \includegraphics[]{fig/result.nvt.small/fig-eps-t-zm3-3000.eps}
+  \includegraphics[]{fig/result.nvt.small/fig-eps-t-10000.eps}
+  \includegraphics[]{fig/result.nvt.small/fig-eps-t-zm3-10000.eps}
   \caption{The Kirkwood G-factor calculated for system S1.
@@
   \includegraphics[]{fig-gkr-conv.eps}
+  \includegraphics[]{fig/result.nvt/fig-eps-t-3000.eps}
+  \includegraphics[]{fig/result.nvt/fig-eps-t-zm3-3000.eps}
   \caption{The Kirkwood G-factor calculated for system L1.
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[]{fig-gkr-10000.eps}
+  \includegraphics[]{fig-gkr-conv-10000.eps}
+  \includegraphics[]{fig/result.nvt/fig-eps-t-10000.eps}
+  \includegraphics[]{fig/result.nvt/fig-eps-t-zm3-10000.eps}
+  \caption{The Kirkwood G-factor calculated for system L1. Equilibriation time is 10~ns, and the production simulation time is 10~ns.
+    % The result of different methods are compared in the left plot.
+    For all ZM methods the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
+    In the left plot the cut-off radius for all orders is set to $1.2$~nm, while
+    in the right plot, only the order $l=3$ is considered and different cut-off radii are compared.
+    The RF method uses a cut-off radius of 1.2~nm, and dielectric constant of 80.
+    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red bar.
+  }
+  \label{fig:tmp3}
+\end{figure}
+
 \newpage

### 2014-05-21 zm/tools/gen.pot/app/zm.cpp
print lj 6-12 for short-range

@@ -20,6 +20,49 @@ namespace po = boost::program_options;
 using namespace std;
 using namespace ZeroMultipole;
 
+class C6
+{
+public:
+  double u  (const double & rr) const;
+  double up (const double & rr) const;
+}
+    ;
+
+class C12
+{
+public:
+  double u  (const double & rr) const;
+  double up (const double & rr) const;
+}
+    ;
+
+double C6::
+u  (const double & rr) const 
+{
+  return 1./(rr * rr * rr * rr * rr * rr);
+}
+
+double C6::
+up (const double & rr) const 
+{
+  return -6./(rr * rr * rr * rr * rr * rr * rr);
+}
+
+double C12::
+u  (const double & rr) const 
+{
+  double rr6 = rr * rr * rr * rr * rr * rr;
+  return 1./(rr6 * rr6);
+}
+
+double C12::
+up (const double & rr) const 
+{
+  double rr6 = rr * rr * rr * rr * rr * rr;
+  return -12./(rr6 * rr6 * rr);
+}
+
+
 int main(int argc, char * argv[])
 {
   std::string ofile;
@@ -61,6 +104,10 @@ int main(int argc, char * argv[])
     }
   }
 
+  C6 pc6;
+  C12 pc12;
+
+  
   FILE * fp = fopen (ofile.c_str(), "w");
   if (fp == NULL){
     cerr << "cannot open output file " << ofile << endl;
@@ -68,8 +115,30 @@ int main(int argc, char * argv[])
   }
   fprintf (fp, "# generated by %s \n", argv[0]);
   fprintf (fp, "# l: %d alpha: %f rc: %f \n", ll, alpha, rc);
+  double fmax = 1e30;
   for (int ii = 0; ii < nbin+1; ++ii){
-    fprintf (fp, "%f \t %e %e \t 0.0 0.0 \t 0.0 0.0\n", xx[ii], vv[ii], ff[ii]);
+    double vc6, fc6, vc12, fc12;
+    if (ii == 0){
+      vc6 = fc6 = vc12 = fc12 = 0.;
+    }
+    else {
+      vc6 = -pc6.u(xx[ii]);
+      fc6 = pc6.up(xx[ii]);
+      vc12 = pc12.u(xx[ii]);
+      fc12 = -pc12.up(xx[ii]);
+    }
+    if (fc6 > fmax) {
+      fc6 = 0;
[…]

### 2014-05-21 zm/tools/gen.pot/src/Functions.cpp

@@ -243,6 +243,7 @@ energyCorr (const vector<double > & charges)
     sum += charges[ii] * charges[ii];
   }
   
+  // return - (coeff[0] * 0.5 + alpha / sqrt(M_PI)) * sum;
   return - (coeff[0] * 0.5 + alpha / sqrt(M_PI)) * sum;
 }
 

### 2014-05-22 zm/tools/gen.pot/app/energy.corr.water.cpp
add energy correction for water

@@ -1,0 +1,63 @@
+#include <algorithm>
+#include <fstream>
+#include <iomanip>
+#include <iostream>
+#include <iterator>
+#include <list>
+#include <map>
+#include <set>
+#include <sstream>
+#include <string>
+#include <queue>
+#include <vector>
+#include <cmath>
+#include <boost/program_options.hpp>
+#include "Functions.h"
+
+#define MaxLineLength 2048
+
+namespace po = boost::program_options;
+using namespace std;
+using namespace ZeroMultipole;
+
+int main(int argc, char * argv[])
+{
+  double alpha, rc, qo, roh, ahoh;
+  int ll;
+
+  po::options_description desc ("\nTo calcualte the energy correction for one water molecule.\nPlz provide the charge of the oxygen.\n\nAllow options");
+  desc.add_options()
+      ("help,h", "print this message")
+      ("alpha,a",  po::value<double > (&alpha)->default_value (1.2), "alpha")
+      ("rc,c",  po::value<double > (&rc)->default_value (1.5), "cut-off")
+      ("order,l",  po::value<int > (&ll)->default_value (0), "order")
+      ("charge-o,q",  po::value<double > (&qo)->default_value (-0.834), "charge of oxygen")
+      ("dist-oh,q",  po::value<double > (&roh)->default_value (0.09572), "charge of oxygen")
+      ("angle-hoh,q",  po::value<double > (&ahoh)->default_value (104.52), "charge of oxygen");
+    
+  po::variables_map vm;
+  po::store(po::parse_command_line(argc, argv, desc), vm);
+  po::notify (vm);
+  if (vm.count("help")){
+    std::cout << desc<< "\n";
+    return 0;
+  }
+
+  double rhh = 2. * roh * sin (0.5 * ahoh / 180. * M_PI);
+  cout << rhh << endl;
+  double qh = -0.5 * qo;  
+  Potential potzm (ll, alpha, rc);
+
+  double sum = 0.;
+  double factor = 138.935485;
+
+  sum += 2. * qo * qh * (potzm.ulpot(roh) - 1./roh);
+  sum += qh * qh * (potzm.ulpot(rhh) - 1./rhh);
+
+  cout << potzm.ulpot(roh) - 1./roh << endl;
+  cout << potzm.ulpot(rhh) - 1./rhh << endl;
+  
+  cout << sum * factor << endl;
+
+  return 0;
+}

### 2014-05-22 zm/tools/gen.pot/include/Functions.h

@@ -35,6 +35,7 @@ public:
 		 const double & alpha,
 		 const double & rc);
     double pot (const double & rr);
+    double ulpot (const double & rr);
     double mpotp (const double & rr);
 public:
     double energyCorr (const vector<double > & charges);

### 2014-05-22 zm/tools/gen.pot/src/Functions.cpp

@@ -224,6 +224,13 @@ pot (const double & rr)
 }
 
 double ZeroMultipole::Potential::
+ulpot (const double & rr)
+{
+  return pot(rr) + coeff[0];
+}
+
+
+double ZeroMultipole::Potential::
 mpotp (const double & rr) {
   if (rr > rc) return 0.;
   double tmp0 = - funcD1V (alpha, rr);

### 2014-05-22 writedown/zm/report/report.tex
add a lot new results

--- 2014-05-12 writedown/zm/report/report.tex
@@
-\documentclass[a4paper,reprint,unsortedaddress,onecolumn]{revtex4-1}
+\documentclass[aip,jcp,a4paper,reprint,unsortedaddress,onecolumn,fleqn]{revtex4-1}
 % \documentclass[reprint,unsortedadress,oneclumn]{revtex4-1}
@@
 \newcommand{\vect}[1]{\textbf{\textit{#1}}}
+\newcommand{\exc}{\textrm{ex}}
+\newcommand{\systemsa}{S_0}
+\newcommand{\systemsb}{S_1}
+\newcommand{\systemsbp}{S'_1}
+\newcommand{\systemma}{M_0}
+\newcommand{\systemmb}{M_1}
+\newcommand{\systemmbp}{M'_1}
+\newcommand{\systemla}{L_0}
+\newcommand{\systemlbp}{L'_1}
+\newcommand{\systemlb}{L_1}
 
@@
 
+\section{Simulation protocols}
+
 \begin{table}
@@
   \caption{A list of systems tested in this work. We report, from left to right, the number of water
-    molecules in the system (TIP3P model), box size, length of equilibriation, length of productive trajecty and the frequency
-    that the configurations are recorded or the phsical properties are calculted.}
-  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}c rrrrr}\hline\hline
-    System      & \# of Water Mols. & Box size [$\textrm{nm}^3$]  & Equilibriation [ps] & Traj. Length [ps] & Freq. Record [ps]  \\\hline
-    S1          & 4,500          & $5.15^3$              & 3,000        & 17,000        & 5.0 \\
-    S1'         &   4,500        & $5.15^3$              & --           &  6,000        & -- \\
-    L0          &   13,824       & $7.49^3$              & 200          & 1,800         & 0.1 \\
-    L1          &   13,824       & $7.49^3$              & 3,000        & 17,000        & 10.0 \\
-    L1'         &   13,824       & $7.49^3$              & --           & 10,000        & -- \\
+    molecules in the system (TIP3P model), box size, length of equilibriation, length of productive trajectory, the thermostat and the coupling time scale of the thermostat.
+    }
+  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}c rrrrrr}\hline\hline
+    System      & $N$ & $V$ [$\textrm{nm}^3$]  & $T_{eq}$ [ps] & Traj. Length [ps] & Thermostat & $\tau$ [ps]  \\\hline
+    $\systemsb$          & 2,500          & $4.24^3$              & 3,000        & 27,000        & Nose-Hoover & 1.0 \\
+    $\systemsbp$         &   2,500        & $4.24^3$              & --           &  6,000        & Nose-Hoover & 1.0\\
+    $\systemmb$          & 4,500          & $5.15^3$              & 3,000        & 17,000        & Langevin & 0.1\\
+    $\systemmbp$         &   4,500        & $5.15^3$              & --           &  6,000        & Langevin & 0.1\\
+    $\systemla$          &   13,824       & $7.49^3$              & 200          & 1,800         & Langevin & 0.1\\
+    $\systemlb$          &   13,824       & $7.49^3$              & 3,000        & 17,000        & Langevin & 0.1\\
+    $\systemlbp$         &   13,824       & $7.49^3$              & --           & 10,000        & Langevin & 0.1\\
     \hline\hline
@@
 Table.\ref{tab:tmp1}.  The initial configurations are prepared by in
-the following steps: (1) A NPT simulation of system L0 with SPME~\cite{darden1993pme, essmann1995spm}
+the following steps: (1) A NPT simulation of system $\systemla$ with SPME~\cite{darden1993pme, essmann1995spm}
 electrostatic. The equilibrium density of the system is calculated
@@
 13,824 molecules are generated at the calculated equilibrium
-density. (3) NVT simulations with SPME electrostatic for system S1'
-and L1' are performed. (4) The output configuration of S1' is used as
-initial configuration for system S1, and the output configuration of
-L1' is used as initial configuration for system L0 and L1.  The SPME
+density. (3) NVT simulations with SPME electrostatic for system $\systemmbp$
+and $\systemlbp$ are performed. (4) The output configuration of $\systemmbp$ is used as
+initial configuration for system $\systemmb$, and the output configuration of
+$\systemlbp$ is used as initial configuration for system $\systemla$ and $\systemlb$.  The SPME
 parameters for all simulations reported by this work is: real space
@@
 
+We add a new system $\systemsb$, and use the Nose-Hoover
+thermostat. The reason is that for the fluctuation properties (in this
+work heat capacity, dielectric constant, diffusion constant and
+viscosity are fluctuation properties), simply increase the size of the
+system does not improve the accuracy of the
+simulation~\cite{ferrenberg1991statistical}. The only way to improve
+the accuracy is to run longer simulation to do more
+time-average. Therefore, the optimal way of measuring these properties
+is to use smaller system (as far as the finite size effect is not
+important) and run as long simulation as possible, as the equilibrium
+state is reached. The reason of using Nose-Hoover thermostat is that
+it perturbs the dynamics of the system only slightly, while the
+Langevin thermostat is likely to substantially change the dynamics
+when the coupling is very strong.
+
+\subsection{Static properties}
+
 \subsubsection{Pressure}
-The results are plotted in Fig.~\ref{fig:tmp0}.
+The results are plotted in Fig.~\ref{fig:tmp0}. All pressure calculations are done with system $\systemla$.
 \begin{figure}
@@
 \end{figure}
+
+\subsubsection{Chemical potential}
+
+The chemical potential of the NVT system is defined by
+\begin{align}
+  \mu = \frac{\partial A}{\partial N}\Big\vert_{V,T}
+\end{align}
+In practice the excess chemical potential $\mu^\exc$, which is the
+chemical potential abstracted by the kinetic contribution, is of
+special interest. We calculate the excess chemical potential by the
+thermodynamic integration (TI). In this approach, the interaction
+between an inserted molecule and the rest of the system is controlled
+by a coupling parameter $\lambda$. $\lambda$ goes from 0 to 1, where 0
+indicates no coupling while 1 indicates full coupling. Therefore the
+Hamiltonian of the system is function of the coupling parameter. The
+excess chemical is calculated by:
+\begin{align}
+  \mu^\exc = \int_0^1 \Big\langle \frac{\partial \mathcal H(\lambda)}{\partial \lambda} \Big\rangle_\lambda d\lambda
+\end{align}
+We use a two step coupling approach: firstly couple the van der Waals
+interaction (stage vdw), and then couple the electrostatic interaction
+(stage ele).  During stage vdw, 21 $\lambda$ values are equally
+distributed in $[0,1]$.  During stage ele, 6 $\lambda$ values are
+equally distributed in $[0,0.05]$, while the other 20 $\lambda$ values
+are equally distributed in $[0.05, 1]$. Therefore, in total 47
+simulations are performed for all $\lambda$ values. The simulation was
+in system $\systemla$.
+
+\begin{table}
+  \centering
+  \caption{The excess chemical potential $\mu^\exc$, constant volume molar heat capacity $C_{v,m}$, dielectric constant $\eps$, diffusion constant $D$ and viscosity $\eta$
+    calculated by different methods.    
+    The parenthesises in the last column show the statistical uncertainty
+    at the confidence level of 95~\%.
+    The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
+  }
+  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}cccc cccc}\hline\hline
+    Method      &   $r_c$ [nm] &    $l$     &  $\mu^\exc$ [kJ/mol] &$C_{v,m}$ [J/(mol K)] & $\eps$ (Sys.~$\systemsb$) & $D$ [$10^{-9}\textrm{m}^2/\textrm{s}$] &  $\eta$ [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
+    SPME        &         1.9     &       --      &       $-26.08$ (0.24) & 72.21 (0.97)  & 97.6 (3.4)  & 5.86 (0.07)   & 0.315 (0.007)\\
+    RF          &         1.2     & --            &       $-26.03$ (0.32) & 72.28 (0.81)  & \textbf{59.4} (1.3)  & \textbf{6.27} (0.19)   & \textbf{0.449} (0.020)\\
+    ZM          &         1.2     &       1       &       $-26.22$ (0.30) & 71.75 (0.89)  & 95.5 (2.4)  & \textbf{5.53} (0.11)   & \textbf{0.346} (0.006)\\ 
+    ZM          &         1.2     &       2       &       $-26.24$ (0.24) & 71.53 (0.88)  & 95.4 (2.5)  & 5.82 (0.27)   & 0.318 (0.012)\\ 
+    ZM          &         1.2     &       3       &       $-{26.18}$ (0.20) & 71.58 (0.88)  & 96.0 (2.7)  & 5.79 (0.09)   & 0.321 (0.008)\\ 
+    ZM          &         1.2     &       4       &       $-{26.01}$ (0.26) & 71.07 (0.84)  & 99.7 (2.2)  & 5.89 (0.09)   & 0.318 (0.013)\\
+    \hline\hline
+  \end{tabular*}
+  \label{tab:tmp3}
+\end{table}
+
+\subsubsection{Constant volume molar heat capacity}
+The constant volume molar heat capacity is defined by:
+\begin{align}
+  C_{v,m} = \frac{1}{k_BT N} \langle (\mathcal H - \langle\mathcal H\rangle)^2 \rangle,
+\end{align}
+where $\mathcal H$ is the Hamiltonian of the system. Since constant
+volume heat capacity is a extensive thermodynamics quantity, it is
+normalized by the number molecules in the system.
+It is calculated in system $\systemsb$.
 
@@
 \end{align}
-The results are listed in Tab.~\ref{tab:tmp2}
+The results are listed in Tab.~\ref{tab:tmp2}. The dielectric constant calculated in system $\systemsb$ is reported in Table.~\ref{tab:tmp3}.
 
@@
   \caption{A list of the dielectric constant calculated for different systems by different methods.
-    The paremeters are provided. The parenthesises in the last column show the statistical uncertanty
-    of the last two digits upto the confidence level of 95~\%.}
+    The parameters are provided. The parenthesises in the last column show the statistical uncertainty
+    of the last two digits up to the confidence level of 95~\%.}
   \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}cccc rr}\hline\hline
     System & Method      &       $\alpha$ [$\textrm{nm}^{-1}$] & $r_c$ [nm] &    $l$     &       $\eps$ \\\hline
-    S1  &       ZM          &       0.00    &       1.2     &       1       &       99.8 (3.8)\\ 
-    S1  &       ZM          &       0.00    &       1.2     &       2       &       95.2 (3.6)\\ 
-    S1  &       ZM          &       0.00    &       1.2     &       3       &       93.9 (3.7)\\ 
-    S1  &       ZM          &       0.00    &       1.5     &       3       &       98.7 (3.8)\\ 
-    S1  &       ZM          &       0.00    &       1.8     &       3       &      100.7 (3.6)\\ 
-    S1  &       ZM          &       0.00    &       1.2     &       4       &       94.7 (3.6)\\
-    S1   & SPME          & 2.09  & 1.9   &       --      &       98.8 (4.0) \\
-    S1  & RF             & --  & 1.2 & -- & 60.6   (1.7) \\
-    L1  &       ZM          &       0.00    &       1.2     &       1       &       97.1 (3.2)\\ 
-    L1  &       ZM          &       0.00    &       1.2     &       2       &       95.6 (3.5)\\ 
-    L1  &       ZM          &       0.00    &       1.2     &       3       &       95.8 (4.6)\\ 
-    L1  &       ZM          &       0.00    &       1.5     &       3       &       98.0 (3.3)\\ 
-    L1  &       ZM          &       0.00    &       1.8     &       3       &       98.9 (4.2)\\ 
-    L1  &       ZM          &       0.00    &       2.1     &       3       &       98.8 (3.9)\\ 
-    L1  &       ZM          &       0.00    &       1.2     &       4       &       97.8 (3.9)\\
-   L1   & SPME          & 2.09  & 1.9   &       --      &       98.7 (3.5) \\
-    L1  & RF             & --  & 1.2 & -- & 60.8   (2.0) \\
+    $\systemmb$  &       ZM          &       0.00    &       1.2     &       1       &       99.8 (3.8)\\ 
+    $\systemmb$  &       ZM          &       0.00    &       1.2     &       2       &       95.2 (3.6)\\ 
+    $\systemmb$  &       ZM          &       0.00    &       1.2     &       3       &       93.9 (3.7)\\ 
+    $\systemmb$  &       ZM          &       0.00    &       1.5     &       3       &       98.7 (3.8)\\ 
+    $\systemmb$  &       ZM          &       0.00    &       1.8     &       3       &      100.7 (3.6)\\ 
+    $\systemmb$  &       ZM          &       0.00    &       1.2     &       4       &       94.7 (3.6)\\
+    $\systemmb$   & SPME          & 2.09  & 1.9   &       --      &       98.8 (4.0) \\
+    $\systemmb$  & RF             & --  & 1.2 & -- & 60.6   (1.7) \\
+    $\systemlb$  &       ZM          &       0.00    &       1.2     &       1       &       97.1 (3.2)\\ 
+    $\systemlb$  &       ZM          &       0.00    &       1.2     &       2       &       95.6 (3.5)\\ 
+    $\systemlb$  &       ZM          &       0.00    &       1.2     &       3       &       95.8 (4.6)\\ 
+    $\systemlb$  &       ZM          &       0.00    &       1.5     &       3       &       98.0 (3.3)\\ 
+    $\systemlb$  &       ZM          &       0.00    &       1.8     &       3       &       98.9 (4.2)\\ 
+    $\systemlb$  &       ZM          &       0.00    &       2.1     &       3       &       98.8 (3.9)\\ 
+    $\systemlb$  &       ZM          &       0.00    &       1.2     &       4       &       97.8 (3.9)\\
+   $\systemlb$   & SPME          & 2.09  & 1.9   &       --      &       98.7 (3.5) \\
+    $\systemlb$  & RF             & --  & 1.2 & -- & 60.8   (2.0) \\
     \hline\hline
@@
 \end{table}
+
+\subsubsection{Radial distribution function}
+The results are plotted in Fig.~\ref{fig:rdf}. As the order of ZM method goes higher, the precision of RDF improves. In addition, the precision of RF method is between $l=2$ and $l=3$.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.4\textwidth]{fig/result.nvt/fig-rdf.eps}  
+  \caption{The RDF of different method. The insert is a zoom-in of range 0.9 -- 1.5~nm. In the insert, the position of the cut-off (1.2~nm) is indicated by a vertical black line.}
+  \label{fig:rdf}
+\end{figure}
 
@@
 dependent~\cite{vanderSpoel2006origin}. Here we show the G-factor for
-both a smaller system S1 (Fig.~\ref{fig:tmp1}) and a larger system L1
-(Fig.~\ref{fig:tmp2}).  In the figures, the statistical uncertanty of
-the SPME method is denoted by the red error bar, while thoes of the
+both a smaller system $\systemmb$ (Fig.~\ref{fig:tmp1}) and a larger system $\systemlb$
+(Fig.~\ref{fig:tmp2}).  In the figures, the statistical uncertainty of
+the SPME method is denoted by the red error bar, while those of the
 other methods are essentially the same, so they are not presented for
@@
   \includegraphics[]{fig-gkr-small-conv.eps}
-  \caption{The Kirkwood G-factor calculated for system S1.
+  \includegraphics[]{fig/result.nvt.small/fig-eps-t-3000.eps}
+  \includegraphics[]{fig/result.nvt.small/fig-eps-t-zm3-3000.eps}
+  \includegraphics[]{fig/result.nvt.small/fig-eps-t-10000.eps}
+  \includegraphics[]{fig/result.nvt.small/fig-eps-t-zm3-10000.eps}
+  \caption{The Kirkwood G-factor calculated for system $\systemmb$.
     % The result of different methods are compared in the left plot.
@@
   \includegraphics[]{fig-gkr-conv.eps}
-  \caption{The Kirkwood G-factor calculated for system L1.
+  \includegraphics[]{fig/result.nvt/fig-eps-t-3000.eps}
+  \includegraphics[]{fig/result.nvt/fig-eps-t-zm3-3000.eps}
+  \caption{The Kirkwood G-factor calculated for system $\systemlb$.
     % The result of different methods are compared in the left plot.
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[]{fig-gkr-10000.eps}
+  \includegraphics[]{fig-gkr-conv-10000.eps}
+  \includegraphics[]{fig/result.nvt/fig-eps-t-10000.eps}
+  \includegraphics[]{fig/result.nvt/fig-eps-t-zm3-10000.eps}
+  \caption{The Kirkwood G-factor calculated for system $\systemlb$. Equilibriation time is 10~ns, and the production simulation time is 10~ns.
+    % The result of different methods are compared in the left plot.
+    For all ZM methods the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
+    In the left plot the cut-off radius for all orders is set to $1.2$~nm, while
+    in the right plot, only the order $l=3$ is considered and different cut-off radii are compared.
+    The RF method uses a cut-off radius of 1.2~nm, and dielectric constant of 80.
+    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red bar.
+  }
+  \label{fig:tmp3}
+\end{figure}
+
+\subsection{Dynamical properties}
+
+\subsubsection{Diffusion constant}
+The diffusion constant is calculated from the Einstein relation:
+\begin{align}
+  D = \lim_{t\rightarrow \infty}\frac {1}{6t} \langle \vert \vect r_i(t) - \vect r_i(0)\vert^2\rangle.
+\end{align}
+In practice, the mean-square-displacement $\langle\vert \vect r_i(t) - \vect
+r_i(0)\vert^2\rangle$ is calculated, then the value is linearly fitted. The
+resulting slop is used to calculate the diffusion constant. The results are listed in Table~\ref{tab:tmp3}.
+The ZM method $l\geq 2$ is consistent with the SPME
+result, while the RF method is off. The system for simulation is $\systemsb$.
+
+\subsubsection{Viscosity}
+The viscosity is calculated from the Green-Kubo relation:
+\begin{align}
+  \eta = \frac{V}{k_BT}\int_0^\infty\langle P_{\alpha\beta}(0) P_{\alpha\beta}(t)\rangle\,dt, \quad \alpha,\beta \in \{x, y, z\}
+\end{align}
+where $\alpha$ and $\beta$ denote the directions, and
+$P_{\alpha\beta}$ denotes the off-diagonal components of the pressure
+tensor. Since we used the isotropic system setting, then it is obvious
+that $P_{xy}$, $P_{yz}$ and $P_{xz}$ are equivalent. Moreover, it has
+been pointed out that in addition $(P_{xx} - P_{yy})/2$ and $(P_{xx} -
+P_{yy})/2$ are two independent components that are equivalent to the
+first three~\cite{alfe1998first}. Therefore, the viscosity is
+calculated from the auto-correlation functions of five independent
+components, and the statistical error is estimated from the standard
+deviation of the viscosities calculated from the five components.
+
+We investigate the convergence of the integral of the auto-correlation function w.r.t.~time:
+\begin{align}
+  I_\eta(T) = \frac{V}{k_BT}\int_0^T\langle P_{\alpha\beta}(0) P_{\alpha\beta}(t)\rangle\,dt,
+\end{align}
+and plot the function $I_\eta(T) $ for all method in
+Fig.~\ref{fig:tmp4}.  It is clear the integral for the RF method
+converges at 6~ps, while the ZM method converges only in 2~ps, which
+is consistent with the SPME result.  The value of ZM $l=1$ method is
+different from the rest ZM method an SPME result.  The value
+$I_\eta(10\,\textrm{ps})$ is given in Table~\ref{tab:tmp3}.  The
+system for simulation is $\systemsb$.
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig/result.tiny/fig-vis.eps}
+  \caption{The convergence of the integrated auto-correlation function $I_\eta(T) $. The error bars indicating 95\% confidence level are plotted with the SPME method.}
+  \label{fig:tmp4}
+\end{figure}
+
 \newpage

### 2014-05-22 writedown/zm/report/fig/result.nvt/join.rdf.sh

@@ -1,0 +1,7 @@
+#!/bin/bash
+
+join rf.rc1.2.long/nvt/rdf.0.01.xvg spme.tune.nvt.smooth.20ns/nvt/rdf.0.01.xvg   > tmp.out; mv -f tmp.out rdf.all.0.01.out
+join rdf.all.0.01.out zm.l1.alpha0.00.rc1.2.long/nvt/rdf.0.01.xvg   > tmp.out; mv -f tmp.out rdf.all.0.01.out
+join rdf.all.0.01.out zm.l2.alpha0.00.rc1.2.long/nvt/rdf.0.01.xvg   > tmp.out; mv -f tmp.out rdf.all.0.01.out
+join rdf.all.0.01.out zm.l3.alpha0.00.rc1.2.long/nvt/rdf.0.01.xvg   > tmp.out; mv -f tmp.out rdf.all.0.01.out
+join rdf.all.0.01.out zm.l4.alpha0.00.rc1.2.long/nvt/rdf.0.01.xvg   > tmp.out; mv -f tmp.out rdf.all.0.01.out

### 2014-05-22 wimley.white/template.simul/parameters.sh
rename files and folders

@@ -3,16 +3,16 @@
 # simulation result from spme.tune
 # nvt_num_density=32.90917546138462644658
 
-gmx_init_conf=./confs/conf.alanine.amber99sb-ildn.gro
-gmx_init_index=
-gmx_sys_tempalte_dir=./tools/system.alanine.amber99sb-ildn
-gmx_dt=0.001
-gmx_time=50			# in ps
+gmx_init_conf=./confs/conf.gro
+gmx_init_index=./confs/index.ndx
+gmx_sys_tempalte_dir=./tools/system.wwa.oplsaa
+gmx_dt=0.002
+gmx_time=2			# in ps
 gmx_equi_skip=100		# in ps
 gmx_conf_feq=1			# in ps
 gmx_energy_feq=1		# in ps
-gmx_ele_method=zm		# pme or zm or rf
-gmx_rlist=1.44			# 
+gmx_ele_method=pme-switch	# pme or zm or rf
+gmx_rlist=1.50			# 
 gmx_nstlist=5			# 
 gmx_rcut_ele=1.2		# if pme is used, set this value to rlist
 gmx_rcut_ele_switch=1.15
@@ -22,8 +22,8 @@ gmx_vdw_type=shift		# using adress will overwrite it with "user"
 gmx_rcut_vdw=1.2
 gmx_rcut_vdw_switch=1.15
 gmx_tab_ext=0.5
-gmx_thermostat=nose-hoover	# hose-hoover or sd
-gmx_taut=1.0
+gmx_thermostat=sd		# hose-hoover or sd
+gmx_taut=0.1
 gmx_npt=yes
 gmx_taup=2.0
 gmx_e_rf=80.0

### 2014-05-22 wimley.white/template.simul/env.fu.sh
uniform format of gromacs keywords. add new conf and index files for box 4 system

@@ -1,4 +1,4 @@
-nnodes=6
+nnodes=8
 
 gmx_dir=$HOME/local/
 source $gmx_dir/bin/GMXRC

### 2014-05-22 wimley.white/template.simul/parameters.sh

@@ -3,11 +3,11 @@
 # simulation result from spme.tune
 # nvt_num_density=32.90917546138462644658
 
-gmx_init_conf=./confs/conf.gro
-gmx_init_index=./confs/index.ndx
+gmx_init_conf=./confs/conf.wwa.oplsaa.box004.gro
+gmx_init_index=./confs/index.wwa.oplsaa.box004.ndx
 gmx_sys_tempalte_dir=./tools/system.wwa.oplsaa
 gmx_dt=0.002
-gmx_time=2			# in ps
+gmx_time=1000000		# in ps
 gmx_equi_skip=100		# in ps
 gmx_conf_feq=1			# in ps
 gmx_energy_feq=1		# in ps
@@ -22,8 +22,8 @@ gmx_vdw_type=shift		# using adress will overwrite it with "user"
 gmx_rcut_vdw=1.2
 gmx_rcut_vdw_switch=1.15
 gmx_tab_ext=0.5
-gmx_thermostat=sd		# hose-hoover or sd
-gmx_taut=0.1
+gmx_thermostat=nose-hoover	# hose-hoover or sd
+gmx_taut=1.0
 gmx_npt=yes
 gmx_taup=2.0
 gmx_e_rf=80.0

### 2014-05-22 wimley.white/template.simul/run.sh

@@ -90,18 +90,16 @@ sed -e "/^coulombtype /s/=.*/= $gmx_ele_method_gromacs/g"|\
 sed -e "/^rcoulomb-switch /s/=.*/= $gmx_rcut_ele_switch/g"|\
 sed -e "/^rcoulomb /s/=.*/= $gmx_rcut_ele/g"|\
 sed -e "/^fourierspacing /s/=.*/= $gmx_pme_F_spacing/g"|\
-sed -e "/^pme_order /s/=.*/= $gmx_pme_order/g"|\
+sed -e "/^pme-order /s/=.*/= $gmx_pme_order/g"|\
 sed -e "/^vdwtype /s/=.*/= $gmx_vdw_type/g"|\
 sed -e "/^vdw-type /s/=.*/= $gmx_vdw_type/g"|\
-sed -e "/^vdw_type /s/=.*/= $gmx_vdw_type/g"|\
 sed -e "/^rvdw-switch /s/=.*/= $gmx_rcut_vdw_switch/g"|\
-sed -e "/^rvdw_switch /s/=.*/= $gmx_rcut_vdw_switch/g"|\
 sed -e "/^rvdw /s/=.*/= $gmx_rcut_vdw/g"|\
-sed -e "/^tau_t /s/=.*/= $gmx_taut/g"|\
-sed -e "/^tau_p /s/=.*/= $gmx_taup/g"|\
+sed -e "/^tau-t /s/=.*/= $gmx_taut/g"|\
+sed -e "/^tau-p /s/=.*/= $gmx_taup/g"|\
 sed -e "/^Pcoupl /s/=.*/= no/g"|\
-sed -e "/^epsilon_rf /s/=.*/= $gmx_e_rf/g"|\
-sed -e "/^gen_vel /s/=.*/= no/g"|\
+sed -e "/^epsilon-rf /s/=.*/= $gmx_e_rf/g"|\
+sed -e "/^gen-vel /s/=.*/= no/g"|\
 sed -e "/^couple-moltype /s/=.*/= /g"|\
 sed -e "/^integrator /s/=.*/= $gmx_integrator/g"|\
 sed -e "/^Tcoupl /s/=.*/= $gmx_tcouple/g"|\
@@ -119,15 +117,14 @@ if grep "^adress " grompp.mdp | grep yes &> /dev/null; then
     hboxz=`echo "$boxz * 0.5" | bc -l`
     cat grompp.mdp |\
[…]

### 2014-06-18 wimley.white/template.simul/tools/analyze/app/dist.2d.cpp
add dist.2d to calculate the 2d distribution of dih angles

@@ -1,0 +1,150 @@
+#include <algorithm>
+#include <fstream>
+#include <iomanip>
+#include <iostream>
+#include <iterator>
+#include <list>
+#include <map>
+#include <set>
+#include <sstream>
+#include <string>
+#include <queue>
+#include <cmath>
+#include <boost/program_options.hpp>
+#include <vector>
+#include "StringSplit.h"
+#include "BlockAverage.h"
+
+#define MaxLineLength 2048
+
+namespace po = boost::program_options;
+using namespace std;
+
+int main(int argc, char * argv[])
+{
+  std::string ofile, phifile, psifile;
+  unsigned column, nBin, nDataInBlock;
+  double aup, alow;
+  
+  po::options_description desc ("Allow options");
+  desc.add_options()
+      ("help,h", "print this message")
+      ("input-list-phi-files,f", po::value<std::string > (&phifile)->default_value ("angaver.phi.xvg"), "the input files of dihedral angles phi.")
+      ("input-list-psi-files,f", po::value<std::string > (&psifile)->default_value ("angaver.psi.xvg"), "the input files of dihedral angles psi.")
+      ("column,c", po::value<unsigned > (&column)->default_value (2), "the column used.")
+      ("num-data-block", po::value<unsigned > (&nDataInBlock)->default_value (320), "number data in blocks.")
+      ("num-bins,n", po::value<unsigned > (&nBin)->default_value (72), "number bins for distribution.")
+      ("angle-up", po::value<double > (&aup)->default_value (180.), "upper bond of the angle.")
+      ("angle-low", po::value<double > (&alow)->default_value (-180.), "lower bond of the angle.")
+      ("output,o", po::value<std::string > (&ofile)->default_value ("dist.out"), "the output of the discrete trajectory");
+
+  po::variables_map vm;
+  po::store(po::parse_command_line(argc, argv, desc), vm);
+  po::notify (vm);
+  if (vm.count("help")){
+    std::cout << desc<< "\n";
+    return 0;
+  }
+
+  double binSize = (aup - alow) / double(nBin);
+  double binSizeI = 1./binSize;
+  
+  vector<vector<BlockAverage_acc > > avgs (nBin);
+  for (unsigned ii = 0; ii < nBin; ++ii){
+    avgs[ii].resize (nBin);
[…]

### 2014-06-18 writedown/zm/report/report.tex
save

@@
   }
-  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}cccc cccc}\hline\hline
-    Method      &   $r_c$ [nm] &    $l$     &  $\mu^\exc$ [kJ/mol] &$C_{v,m}$ [J/(mol K)] & $\eps$ (Sys.~$\systemsb$) & $D$ [$10^{-9}\textrm{m}^2/\textrm{s}$] &  $\eta$ [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
+  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}ccc ccccc}\hline\hline
+    Method      &   $r_c$ &    $l$      & $\mu^\exc$  &$C_{v,m}$ &  $\eps$ & $D$ &  $\eta$ \\
+                &    [nm] &             &   [kJ/mol] &[J/(mol K)] & (Sys.~$\systemsb$) & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
+    % Method      &   $r_c$ [nm] &    $l$      & $\mu^\exc$ [kJ/mol] &$C_{v,m}$ [J/(mol K)] & $\eps$ (Sys.~$\systemsb$) & $D$ [$10^{-9}\textrm{m}^2/\textrm{s}$] &  $\eta$ [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
     SPME        &         1.9     &       --      &      $-26.08$ (0.24) & 72.21 (0.97)  & 97.6 (3.4)  & 5.86 (0.07)   & 0.315 (0.007)\\
@@
 \end{table}
+    % SPME        &         1.9     &       --      & 1.67049 (0.00014)     $-26.08$ (0.24) & 72.21 (0.97)  & 97.6 (3.4)  & 5.86 (0.07)   & 0.315 (0.007)\\
+    % RF          &         1.2     & --            & 1.66733 (0.00016)      $-26.03$ (0.32) & 72.28 (0.81)  & \textbf{59.4} (1.3)  & \textbf{6.27} (0.19)   & \textbf{0.449} (0.020)\\
+    % ZM          &         1.2     &       1       & 1.67052 (0.00022)     $-26.22$ (0.30) & 71.75 (0.89)  & 95.5 (2.4)  & \textbf{5.53} (0.11)   & \textbf{0.346} (0.006)\\ 
+    % ZM          &         1.2     &       2       & 1.67029 (0.00013)     $-26.24$ (0.24) & 71.53 (0.88)  & 95.4 (2.5)  & 5.82 (0.27)   & 0.318 (0.012)\\ 
+    % ZM          &         1.2     &       3       & 1.67024 (0.00018)     $-{26.18}$ (0.20) & 71.58 (0.88)  & 96.0 (2.7)  & 5.79 (0.09)   & 0.321 (0.008)\\ 
+    % ZM          &         1.2     &       4       & 1.67031 (0.00010)     $-{26.01}$ (0.26) & 71.07 (0.84)  & 99.7 (2.2)  & 5.89 (0.09)   & 0.318 (0.013)\\
+
+\begin{table}
+  \centering
+  \caption{The constant pressure molar heat capacity $C_{v,m}$, isothermal compressibility $\kappa_T$ and
+    thermal expansion coefficient $\alpha$
+    calculated by different methods.    
+    The parenthesises in the last column show the statistical uncertainty
+    at the confidence level of 95~\%.
+    The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
+  }
+  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}ccc ccc}\hline\hline
+    Method      &   $r_c$ [nm] &    $l$      & $\kappa_T$ [$10^{-10}\textrm{m}^2/\textrm{N}$] & $C_{p,m}$ [J/(mol K)] & $\alpha$ [$10^{-3}\textrm{K}^{-1}$]\\\hline
+    SPME        &         1.9     &       --      & 5.941 (0.050)               &79.18 (0.94)           &1.026 (0.016)          \\
+    RF          &         1.2     & --            & \textbf{6.508} (0.058)      &\textbf{82.34} (0.95)  &\textbf{1.149} (0.018) \\
+    ZM          &         1.2     &       1       & 5.872 (0.050)               &78.91 (0.95)           &1.009 (0.018)          \\
+    ZM          &         1.2     &       2       & 5.952 (0.051)               &79.70 (0.96)           &1.033 (0.016)          \\
+    ZM          &         1.2     &       3       & 5.991 (0.050)               &79.49 (1.01)           &1.024 (0.019)          \\
+    ZM          &         1.2     &       4       & 5.961 (0.054)               &79.46 (0.98)           &1.034 (0.017)          \\
+    \hline\hline
+  \end{tabular*}
+  \label{tab:tmp3a}
+\end{table}
+
+% \subsubsection{Hydrogen bonding}
+% We count
 
@@
 \begin{align}
-  C_{v,m} = \frac{1}{k_BT N} \langle (\mathcal H - \langle\mathcal H\rangle)^2 \rangle,
+  C_{v,m} = \frac{1}{k_BT^2 N} \langle (\mathcal H - \langle\mathcal H\rangle)^2 \rangle,
 \end{align}
@@
 It is calculated in system $\systemsb$.
+
+\subsubsection{Constant pressure molar heat capacity}
+The constant pressure molar heat capacity is defined by:
+\begin{align}
+  C_{p,m} = \frac{1}{k_BT^2 N} \langle ( H - \langle H\rangle)^2 \rangle,
+\end{align}
+where $ H$ is the enthalpy of the system, defined by $H = \mathcal H + PV$. Since constant
+pressure heat capacity is a extensive thermodynamics quantity, it is
+normalized by the number molecules in the system.
+It is calculated by a NPT simulation of  system $\systemsb$.
+
+\subsubsection{Isothermal heat capacity}
+The isothermal heat capacity is defined by
+\begin{align}
+  \kappa_T = \frac{1}{k_BT} \frac{\langle (V - \langle V\rangle)^2 \rangle}{\langle V\rangle}.
+\end{align}
+It is calculated by a NPT simulation of  system $\systemsb$.
+
+\subsubsection{Thermal expansion coefficient}
+The thermal expansion coefficient is defined by
+\begin{align}
+  \alpha = \frac{1}{k_BT^2\langle V\rangle} \langle (H - \langle H\rangle)\cdot(V - \langle V\rangle) \rangle
+\end{align}
+It is calculated by a NPT simulation of  system $\systemsb$.
 
@@
 
+\subsection{Simulation with alanine dipeptide}
+
+Here we denote the full phase space by $\Omega$, and the phase space
+variable by $\vect x$. We assume that 1, the trajectory $\vect x(t)$
+is Markovian; 2, it is ergodic and as $t\rightarrow\infty$ the phase
+space probability density $p(\vect x)$ converges to the unique
+equilibrium probability density $\mu(\vect x)$ and 3, the trajectory
+is reversible (detailed balance condition is satisfied). One can
+easily write down a propagator for the probability density
+\begin{equation}
+\label{eq:propagator}  
+p_{t+\tau}(\vect x) = \mathcal Q(\tau)\circ
+p_t(\vect x),
+\end{equation}
+where the constant $\tau$ is called the lag time. Due to the
+Markovianity of the system, the propagator satisfies the
+Chapman-Kolmogorov equation:
+\begin{equation}
+  \label{eq:chapman}
+  p_{t+k\tau}(\vect x) = \mathcal Q^k(\tau)\circ p_t(\vect x).
+\end{equation}
+Since the dynamics is reversible, the eigenvalues of $\mathcal
+Q(\tau)$ are real-valued. We consider the first $m$ dominant
+eigenvalues from the spectrum: $1 = \lambda_1 > \lambda_2 \geq
+\lambda_3 \geq \cdots \geq \lambda_m$. For most of the biomolecule
+systems, it is reasonable to assume a spectrum gap, i.e.~for a certain
+$m$ $\lambda_m$ is much larger than the magnitude of the rest
+eigenvalues. For the first $m$ leading eigenvalues one define the
+corresponding timescales by
+\begin{equation}
+  \label{eq:timescale}
+  t_i = -\frac{\tau}{\log \lambda_i}, \quad i= 2,\cdots, m
+\end{equation}
+Usually the first $m$ leading timescales can be identified with the
+slowest conformational changes of the biomolecule. The spectrum gap is
+considered as a timescale separation between the slow conformational
+changes and the fast motion in the system, e.g.~bond vibration, angle
+vibration, solvent motion, and other relatively fast conformational
+changes. The eigenfunction of the first eigenvalue is nothing but the
+equilibrium probability density $\mu(\vect x)$. We denote the
+eigenfunctions corresponding to $\lambda_2, \cdot, \lambda_m$ by
+$\phi_2(\vect x), \cdots, \phi_m(\vect x)$, then the original dynamics
+of the system~\eqref{eq:chapman} is approximated by
+\begin{equation}
+  \label{eq:app-dynamics}
+  p_{t+k\tau}(\vect x) = \mu(\vect x) + \sum_{i=2}^m e^{-\frac{k\tau}{t_i}} a_i \phi_i(\vect x) + \textrm{fast decaying dynamics}
+\end{equation}
+where $a_i$ are constants calculated by $a_i = \int \frac{1}{\mu(\vect
+  x)} p_t(\vect x)\phi_i(\vect x) d\vect x$. This means that the
+evolution of the phase space probability is a summation of the
+time-independent equilibrium probability and a series of slow decaying
+processes that are defined by the timescales $t_i$ and eigenfunctions
+$\phi_i(\vect x)$. The eigenfunctions indicates how the conformational
+change happens.
+The slowest timescales and the corresponding conformational
+changes are usually of the most biological interest.  Since the
+slowest timescales determine the convergence speed of the system with
+respect to the equilibrium probability distribution, they are the most
+difficult part to sample and estimate in molecular dynamics
+simulations.
+
+In practice, it is not easy to directly calculate the eigenvalues and
+eigenfunctions from molecular trajectories. Therefore, the continuous
+trajectories are usually projected on to a finite number of sets, so
+that the original dynamics is reduced to a Markov jump process that is
+also called the Markov state model. We expect the Markov jump process
+is a good approximate to the original dynamics in the sense that the
+eigen pairs of the reduced process accurately reproduce those of the
+original dynamics. How to do the discretized and the accuracy are
+explained in detailed in Ref.~\cite{prinz2011markov}.
+
+\begin{figure}
+  \centering  
+  \includegraphics[width=0.49\textwidth]{fig/result.alanine.amber/c-2.eps}
+  \caption{(a) A schematic plot of the alanine dipeptide and the
+    dihedral angles $\phi$ and $\psi$. (b) The free energy landscape on the
+    $\phi$-$\psi$ dihedral angle space.}
+  \label{fig:free-energy}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.40\textwidth]{fig/result.alanine.amber/fig-dih-dist-phi.eps}\\
+  \includegraphics[width=0.40\textwidth]{fig/result.alanine.amber/fig-dih-dist-psi.eps}
+  \caption{The probability distributions of the dihedral angles.}
+  \label{fig:dih-dist}
+\end{figure}
+
+We simulate the alanine dipeptide with the Amber
+ff-99SB-ILDN~\cite{lindorff2010improved} force field.  The dihedral
+angles $\phi$ and $\psi$ (see Fig.~\ref{fig:free-energy}~(a)) are
+widely accepted as collective variables that can describe the
+conformational dynamics of the system.  The free energy landscape
+on $\phi$-$\psi$ space is given in Fig.~\ref{fig:free-energy}~(b).  The projected
+probability distributions on both dihedral angles
+with error bars are presented in Fig.~\ref{fig:dih-dist}. It can be easily seen
+from the distribution $P(\psi)$ and $P(\psi)$ that the ZM method with
+$l=2$ and 3 reproduce the over-all probability of the main
+conformations, i.e.~the $\alpha$-helix (right-handed), $\beta$-sheet and
+the left-handed $\alpha$-helix with satisfactory accuracy.  For these
+methods, deviations of $P(\phi)$ at $\phi = -75^\circ$ and $\phi =
+-140^\circ$ are observed. They correspond to the double-peak structure
+of the right-handed $\alpha$-helix and $\beta$-sheet, which means the
+error happens at the sub-structure of the right-handed $\alpha$-helix
+and $\beta$-sheet, which are of relatively smaller biological interest
+comparing with the main conformations.
+
+\begin{table}
+  \centering
+  \caption{The first three non-trivial timescales in ps computed at lag-time $\tau = 20$~ps.
+  }
+  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}c   ccc}\hline\hline
+    Method      &        $t_2$ [ps]  & $t_3$ [ps] &  $t_4$ [ps] \\\hline
+    SPME        &         1292  (148)     &          69.95  (0.76)  &         36.0 (4.7)    \\
+    RF          & \textbf{1615} (155)     &  \textbf{68.48} (0.37)  &         34.1 (1.6)    \\
+    ZM $l=1$    & \textbf{1607} (218)     &  \textbf{72.08} (0.50)  &         31.4 (1.9)    \\
+    ZM $l=2$    &         1324  (110)     &          69.97  (0.58)  &         40.4 (2.8)    \\
+    ZM $l=3$    &         1312  (157)     &          70.50  (0.72)  &         37.1 (4.3)    \\
+    ZM $l=4$    & \textbf{1635} (156)     &          69.71  (0.54)  &         39.2 (3.6)    \\
+    \hline\hline
+  \end{tabular*}
+  \label{tab:tmp3}
+\end{table}
+
+% \begin{table}
+%   \centering
+%   \caption{The leading time scales in ps.
+%   }
+%   \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}ccc ccc}\hline\hline
+%     Method      &   $r_c$ &    $l$      & $t_2$  & $t_3$ &  $t_4$ \\\hline
+%     SPME        &         1.9     &       --      &         1292  (148)     &          69.95  (0.76)  &         36.0 (4.7)    \\
+%     RF          &         1.2     & --            & \textbf{1615} (155)     &  \textbf{68.48} (0.37)  &         34.1 (1.6)    \\
+%     ZM          &         1.2     &       1       & \textbf{1607} (218)     &  \textbf{72.08} (0.50)  &         31.4 (1.9)    \\
+%     ZM          &         1.2     &       2       &         1324  (110)     &          69.97  (0.58)  &         40.4 (2.8)    \\
+%     ZM          &         1.2     &       3       &         1312  (157)     &          70.50  (0.72)  &         37.1 (4.3)    \\
+%     ZM          &         1.2     &       4       & \textbf{1635} (156)     &          69.71  (0.54)  &         39.2 (3.6)    \\
+%     \hline\hline
+%   \end{tabular*}
+%   \label{tab:tmp3}
+% \end{table}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-2.eps}
+  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-2.eps}\\
+  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-3.eps}
+  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-3.eps}\\
+  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-4.eps}
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-2-comp.eps}
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-3-comp.eps}
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-4-comp.eps}\\
+  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-4.eps}
+  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-4.eps}
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-5.eps}\\
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-2-comp.eps}
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-3-comp.eps}
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-4-comp.eps}
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-5-comp.eps}\\
+  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-4.eps}\\
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-5.eps}\\
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-spme-eig-vec-2.eps}
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-2.eps}
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-2.eps}
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-2.eps}\\
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-spme-eig-vec-3.eps}
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-3.eps}
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-3.eps}
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-3.eps}\\
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-spme-eig-vec-4.eps}
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-4.eps}
+  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-2-comp.eps}
+  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-3-comp.eps}
+  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-4-comp.eps}\\
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-4.eps}
+  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-5.eps}\\
+  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-2-comp.eps}
+  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-3-comp.eps}
+  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-4-comp.eps}
+  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-5-comp.eps}\\
+  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-4.eps}\\
+  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-5.eps}\\
+  \caption{The eigenfunctions corresponding to the largest three
+    non-trivial timescales, computed with lag-time 20~ps.}
+  \label{fig:tmp5}
+\end{figure}
+
+The leading timescales and corresponding eigenfunctions are given in
+Tab.~\label{tab:tmp3} and Fig.~\ref{fig:tmp5}. The ZM method with
+order 2 and 3 presents best accuracy.
+
 \newpage

### 2014-06-19 wimley.white/template.simul/tools/scripts/upgrade.pynum.sh
add upgrade.pynum.sh

@@ -1,0 +1,3 @@
+#!/bin/bash
+
+easy_install --user --upgrade numpy

### 2014-06-19 wimley.white/template.simul/parameters.example/parameters.alanine.charmm27.adress.sh
can change tf file, not fully tested

@@ -35,4 +35,5 @@ zm_alpha=0.0
 adress_ex_region=0.6
 adress_hy_region=1.2
 adress_type=sphere
+adress_tf_file=tools/adress.tf/tabletf_CMW.charmm27.ex0.6.hy1.0.xvg
 

### 2014-06-19 wimley.white/template.simul/parameters.sh

@@ -35,4 +35,5 @@ zm_alpha=0.0
 adress_ex_region=1.5
 adress_hy_region=1.5
 adress_type=sphere
+adress_tf_file=tools/adress.tf/tabletf_CMW.charmm27.ex0.6.hy1.0.xvg
 

### 2014-06-19 wimley.white/template.simul/run.sh

@@ -128,6 +128,12 @@ if grep "^adress " grompp.mdp | grep yes &> /dev/null; then
     sed -e "/^vdw-type /s/=.*/= user/g"|\
     sed -e "/^adress-reference-coords /s/=.*/= $hboxx $hboxy $hboxz/g" > tmp.mdp
     mv -f tmp.mdp grompp.mdp
+    if [ -f $wwd/$adress_tf_file ]; then
+	if [ -f tabletf_CMW.xvg ]; then
+	    echo "# rm existing tf table"
+	fi
+	cp $wwd/$adress_tf_file ./tabletf_CMW.xvg
+    fi
 fi
 if echo "$gmx_npt" | grep yes &> /dev/null ; then
     cat grompp.mdp |\

### 2014-06-19 wimley.white/template.simul/env.hlrn.sh
set the default gromacs on hlrn to 4.6.5.localsd

@@ -1,5 +1,5 @@
 
-gmx_dir=$WORK/local/gromacs/4.6.5
+gmx_dir=$WORK/local/gromacs/4.6.5.localsd
 source $gmx_dir/bin/GMXRC.bash
 
 zm_gen_dir=$WORK/study/adress.noneq/zm/tools/gen.pot

### 2014-06-19 wimley.white/template.simul/tools/scripts/dih.dist.sh
change some default settings

@@ -4,12 +4,15 @@ script_dir=$(cd ${0%/*} && echo $PWD)
 base_dir=$script_dir/..
 analyze_dir=$base_dir/analyze
 dist_command=$analyze_dir/dist
-traj_dir=gromacs.traj.npt
-phi_file_name=angaver.phi.xvg
-psi_file_name=angaver.psi.xvg
-
 cwd=`pwd`
-targets=`ls | grep ^simul | grep [0-9]$`
+
+if [ -f mm.alanine.parameters.sh ]; then
+    echo "# use parameters file: $cwd/mm.alanine.parameters.sh"
+    source mm.alanine.parameters.sh
+else
+    echo "# use parameters file: $script_dir/mm.alanine.parameters.sh"
+    source $script_dir/mm.alanine.parameters.sh
+fi
 
 phi_list=""
 psi_list=""
@@ -17,6 +20,7 @@ psi_list=""
 for ii in $targets;
 do
     test ! -d $ii/$traj_dir/ && continue
+    echo "# doing $ii/$traj_dir/"
     cd $ii/$traj_dir/
     if [ ! -f $phi_file_name ] || [ ! -f $psi_file_name ]; then
 	echo "# no angle file, make them"

### 2014-06-19 wimley.white/template.simul/tools/scripts/mm.alanine.parameters.sh

@@ -1,9 +1,10 @@
 
-redo=0
+redo=1
 nbins=20
 lag_times="`seq 1 1 20` `seq 22 2 40`"
+lag_times="`seq 1 1 20`"
 #lag_times="`seq 1 1 3`"
-selected_lag_time=10
+selected_lag_time=20
 num_eig=5
 err_num_samples=8
 

### 2014-07-10 wimley.white/template.simul/auto.submit.sh
fix bug of auto.hlrn.con.de, when specify different version of gromacs

@@ -42,6 +42,7 @@ do
 		    exit
 		fi
 		ln -sf ../$con_submit_command .
+		ln -sf ../env.sh .
 		$con_submit_command
 		mv -f jobid ..
 		cd ..

### 2014-07-10 writedown/period.noneq.msm/main.tex
add doc for period driven system

\documentclass[aip,jcp,preprint,unsortedaddress,a4paper,onecolumn]{revtex4-1}
% \documentclass[acs, jctcce, a4paper,preprint,unsortedaddress,onecolumn]{revtex4-1}
% \documentclass[aps,pre,twocolumn,unsortedaddress]{revtex4-1}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}

\usepackage[fleqn]{amsmath}
\usepackage{amssymb}
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{tabularx}
\usepackage{algorithm}
\usepackage{algorithmic}

\makeatletter
\makeatother

\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{red} #1}}
\newcommand{\greenc}[1]{{\color{green} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\dd}[1]{\textsf{#1}}
\newcommand{\fwd}[0]{\textrm{fwd}}
\newcommand{\bwd}[0]{\textrm{bwd}}
\newcommand{\period}[0]{T_{\textrm{P}}}
\newcommand{\ml}[0]{\mathcal {L}}
\newcommand{\mo}[0]{\mathcal {O}}
\newcommand{\mbp}[0]{\mathbb {P}}
\newcommand{\dt}[0]{\Delta t}

\newcommand{\confaa}[0]{{\alpha_{\textrm{R}}}}
\newcommand{\confab}[0]{{\alpha_{\textrm{R}}'}}
\newcommand{\confba}[0]{{\textrm{C}7_{\textrm{eq}}}}
\newcommand{\confbb}[0]{{\textrm{C}5}}
\newcommand{\confc}[0]{{\alpha_{\textrm{L}}}}

\begin{document}

\title{Building Markov State Model for a Periodically Driven Non-Equilibrium System}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{Zuse Institut Berlin, Germany}
\author{Christof Sch\"utte}
\email{Christof.Schuette@fu-berlin.de}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\affiliation{Zuse Institut Berlin, Germany}

\begin{abstract}
\end{abstract}

\maketitle

\section{Discretization of the non-equilibrium molecular dynamics}

We denote the phase space by $\Omega$, and the variable by $\vect
x$. The time-dependent probability distribution on the phase space is
denoted by $\rho(\vect x, t)$. The dynamics of the system is governed
by
\begin{align}
  \label{eqn:tmp1}
  \frac{\partial \rho(\vect x, t)}{\partial t} = \ml(t) \rho(\vect x,t),
\end{align}
where the generator $\ml(t)$ is time-dependent and assumed to be
periodic, i.e.~$\ml(t) = \ml(t+T)$, with period denoted by $T$.  Now
we discretize the phase space $\Omega$ into finite number of disjoint
sets $\{ S_1, \cdots, S_n\}$, which satisfy $\Omega = \cup_i S_i$,
$S_j\cap S_j = \emptyset,\ \forall i\neq j$.
Now the original dynamics of the system can be discretized to a time-dependent
Markov jump process:
\begin{align}
  \label{eqn:tmp2}
  \frac{d\vect p(t)}{dt} = \vect M(t)\cdot \vect p(t)
\end{align}
where
\begin{align}
  \vect p(t) = (p_1(t), \cdots, p_n(t))^T, \quad \textrm{with}\ p_i(t) = \int_{S_i} \rho(\vect x,t)d\vect x,
\end{align}
and the generator is approximated by finite difference scheme:
\begin{align}
  \label{eqn:tmp4}
  M_{ij}(t) \approx \frac{1}{\tau} \,[\, \mbp (\vect x_{t+\tau} \in S_j \vert \vect x_{t} \in S_i) - \delta_{ij} \,]
\end{align}
From Eqn.~\eqref{eqn:tmp1} to Eqn.~\eqref{eqn:tmp2} involves several
approximations:
\begin{enumerate}
\item Eqn.~\eqref{eqn:tmp2} assumes Markovianity, which is not
  necessarily true for a reduce dynamics $\vect p(t)$.
\item Numerical error from the finite difference introduced in
  Eqn.~\eqref{eqn:tmp4}. The lag-time $\tau$ should not be too large
  to control the finite difference error, and at the same time should
  not be too small, because otherwise the statistical error would be
  large, and the Markovianity would be disturbed.
\item Although the original dynamics defined by generator $\ml(t)$ is
  periodic, the reduced one defined by $\vect M(t)$ is not necessary
  periodic, i.e.~$\vect M(t) \neq \vect M(t+T)$ in general.  In the
  simulation of biomolecules, it is reasonable, in most cases to
  assume a time-scale separation in the system. For example, the
  conformational change of the molecules is much faster than the
  covalent bond vibrations. Therefore, if the discretion $\{ S_1,
  \cdots, S_n\}$ properly captures the slow dynamics of interest, in
  the sense that within the lag-time $\tau$, the system is fully
  relaxed to a local equilibrium in the set $S_i$, then it is clear
  that the reduce system is periodic. It suggests that the lag-time
  should be right in the spectrum gap: it is shorter than the dominant
  implied timescale, and longer than the fast-relaxing time-scales.
\end{enumerate}

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{fig/confs/fig-begin-1.eps}
  \caption{The Ramachandran plot presents the main conformations of the alanine dipeptide.}
  \label{fig:tmp1}
\end{figure}

At this stage we do have any analytical result regarding the quality
of approximating Eqn.~\eqref{eqn:tmp1} by
Eqn.~\eqref{eqn:tmp2}. However, it would be useful to do some
numerical experiments. We have studied the alanine dipeptide system
under oscillatory EF, which was studied by
Ref.~\cite{wang2014exploring}. We use the two dihedral angles $\phi$
and $\psi$ as slow variables. The definition of the conformations
$\confaa$, $\confab$, $\confba$, $\confbb$ and $\confc$ are presented
by Fig.~\ref{fig:tmp1}.  We are interested in the time-dependent
probability of the conformations. In Fig.~\ref{fig:tmp2}, the brute
force molecular dynamics simulation result
(i.e.~Eqn.~\eqref{eqn:tmp1}) is compared with different discretization
methods, which give different generator in Eqn.~\eqref{eqn:tmp2}. For
clarity, only the probability of conformation $\confc$ is plotted.  In
the figure, ``5 sets'' means the $\phi$-$\psi$ space is discretized by
5 sets as shown in Fig.~\ref{fig:tmp1}, ``Uni. $M=$'' stands for the
uniform discretization on $\phi$-$\psi$ space, and $M$ denotes the
number of bins on both $\phi$ and $\psi$ directions.  Both $M=10$ and
20 methods present very good accuracy.  Please notice that for $M=10$,
for example, the number of discretized sets is $n=M^2=100$.  The
lag-time in all cases is chosen to be $\tau = 0.5$~ps. A test with
$\tau = 1.0$~ps shows good consistency with $\tau = 0.5$~ps.
The generator
$\vect M(t)$ is assumed to be periodic, and is estimated from the
trajectories from $t=300$ to 1000~ps.

The phenomena presented by Fig.~\ref{fig:tmp2} is very similar to the
equilibrium MSM: the quality of the MSM depends on how accurate the
eigenfunctions are approximated by the discretization. The ``5 sets''
method achieve better accuracy than the uniform $M=5$ method by using
much less DOFs, because it captures the positive and negative signs of
the eigenfunctions. With larger $M$ the discretization error of the
eigenfunctions becomes smaller, so the accuracy of the MSM is improved.

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{fig/t040/fig-cg-prob.eps}  
  \caption{The time-dependent probability of conformation
    $\confc$. The brute force MD simulation is compared with different
    discretization methods.}
  \label{fig:tmp2}
\end{figure}

\section{Floquet theory}

The Floquet theory states that for a periodic system
Eqn.~\ref{eqn:tmp2}, the solution can be written as
\begin{align}
  \label{eqn:tmp5}
  \vect p(t)  = \vect Q(t) e^{t\vect B} \vect p(0)
\end{align}
where $\vect Q(t)$ is periodic and $\vect B$ is a constant matrix.  To
analyze the spectrum, it is not difficult to infer the implied
timescales, on which the system relaxes to the periodic steady states
defined by $\vect Q(t)$.
Assume that the fundamental solution to Eqn.~\ref{eqn:tmp2} is denoted by $\boldsymbol \Phi(t)$, then
the matrix $\vect B$ can be expressed by
\begin{align}
  e^{T\vect B} = \boldsymbol \Phi^{-1}(0)\cdot \boldsymbol \Phi(T)
\end{align}
It is fully justified by choosing $ \boldsymbol \Phi(0) = I$, then
$e^{T\vect B}$ is estimated by evolving the fundamental solutions by
one period.  Calculating the eigenvalues of $e^{T\vect B}$ reveals the
implied timescales on which the non-equilibrium dynamics converges to
the periodic steady state. However, it can only resolve the processes that are longer than the period $T$.
The largest non-trivial timescales is given in table
Tab.~\ref{tab:tmp1}, which corresponds very well to the dynamics of the  $\confc$ probability.

\begin{table}
  \centering
  \caption{The first non-trivial timescales calculated from $e^{T\vect B}$.
  }
  \begin{tabular*}{0.3\textwidth}{@{\extracolsep{\fill}}c   c}\hline\hline
    Method      &        $t_2$ [ps]  \\\hline
    5 sets      & 72.4     \\
    Uni. $M=05$ & 53.6     \\
    Uni. $M=10$ &107.2     \\
    Uni. $M=20$ &113.8     \\
    Uni. $M=30$ &120.6     \\
    \hline\hline
  \end{tabular*}
  \label{tab:tmp1}
\end{table}

\section{To do}

\begin{itemize}
\item Theoretical analysis of the accuracy of the discretization, a
generalization of the equilibrium case. the numerical results indicate
a very close link. The perodicity is very nice, if the generator is
``continuous'', then it should be uniformly continuous, then it should
be possible to develop estimates that are similar to the equilibrium
case.
\item More tests on the effect of choosing different lag-time $\tau$ (0.5 and 1.0~ps are done).
\item More theoretical consideration on the Floquet theory, what is the
explict form of matrix $\vect B$, and does it has any nice properties,
such as self-joint.
\end{itemize}

\section{Reversibility of the original dynamics}

Now we assume the overdamped dynamics
\begin{align}
  dx_t = -\nabla_x V(x_t,t) dt + \sigma dw_t
\end{align}
where $V$ is the time-dependent and $t$-periodic potential. For simplicity we denote the force by $F(x_t,t) = -\nabla_x V(x_t, t)$. $dw_t$ is
the standard Wiener process.  Assuming a discretization of the
stochastic process at time $0 < t_1 < t_2 < \cdots < t_N = T$, where
$t_i = iT / N$. We denote $x_i = x_{t_i}$, and $w_i = w_{t_i}$, then we have the
conditional probability:
\begin{align}\nonumber
  p(x_T,T\vert x_0,0) =\lim_{N\rightarrow\infty} &\,
  \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx_1\cdots\int dx_{N-1}\\\nonumber
  &\,
  \exp\bigg\{\frac1\sigma\sum_{i=0}^{N-1} F(x_i,t_i)(w_{i+1} - w_{i}) - \frac1{2\sigma^2}\sum_{i=0}^{N-1}F^2(x_i,t_i)\dt\bigg\} \times\\\label{eqn:tmp8}
  &\,
  \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=0}^{N-1} \frac{(x_{i+1} - x_i)^2}{\dt}\bigg\}.
\end{align}
Now consider the differentiation:
\begin{align}\nonumber
  F(x_i,t_i) - F(x_{i+1},t_{i+1}) =
  &\,
  F(x_i,t_i) - F(x_{i+1},t_{i}) + F(x_{i+1},t_{i}) -  F(x_{i+1},t_{i+1})\\\nonumber
  =&\,
  -\sigma\nabla_x F(x_{i+1},t_{i})dw_t + \mo(\dt) \\\label{eqn:tmp9}
  =&\,
  -\sigma\nabla_x F(x_{i+1},t_{i+1})dw_t + \mo(\dt) 
\end{align}
and
\begin{align}\label{eqn:tmp10}
  \sigma(w_{i+1} - w_{i}) =
  &\,
  x_{i+1} - x_i 
\end{align}
Inserting Eq.~\eqref{eqn:tmp9} and \eqref{eqn:tmp10} into Eq.~\eqref{eqn:tmp8}, all terms of order $\mo(\dt)$ vanish at the limit $N\rightarrow\infty$,
% so with the formal identity $(dw_t)^2 = dt$,  we have
\begin{align}\nonumber
  p(x_T,T\vert x_0,0) =\lim_{N\rightarrow\infty} &\,
  \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx_1\cdots\int dx_{N-1}\\\nonumber
  &\,
  \exp\bigg\{\frac1{\sigma^2}\sum_{i=0}^{N-1} F(x_{i+1},t_{i+1})(x_{i+1} - x_i) \bigg\} \times \\ \nonumber
  &\,
  \exp\bigg\{-\frac{1}{\sigma^2}\sum_{i=0}^{N-1}  \nabla_x F(x_{i+1},t_{i+1}) (x_{i+1} - x_{i})^2\bigg\} \times \\\nonumber
  &\,
  \exp\bigg\{-\frac1{2\sigma^2}\sum_{i=0}^{N-1}F^2(x_i,t_i)\dt\bigg\} \times\\\label{eqn:tmp11}
  &\,
  \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=0}^{N-1} \frac{(x_{i+1} - x_i)^2}{\dt}\bigg\}.
\end{align}
Now, consider a trajectory that starts at $x_T$, ends at $x_0$, and visits $x_{N-i}$ at time $t_i$, the conditional probability
gives
\begin{align}\nonumber
  p(x_0,T\vert x_T,0)
  =\lim_{N\rightarrow\infty} &\,
  \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx_{N-1}\cdots\int dx_{1}\\\nonumber
  &\,
  \exp\bigg\{\frac1\sigma\sum_{i=N}^{1} F(x_i,t_{N-i})(x_{i-1} - x_{i}) - \frac1{2\sigma^2}\sum_{i=N}^{1}F^2(x_i,t_{N-i})\dt\bigg\} \times\\\nonumber
  &\,
  \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=N}^{1} \frac{(x_{i-1} - x_{i})^2}{\dt}\bigg\} \\\nonumber
  =\lim_{N\rightarrow\infty} &\,
  \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx_{1}\cdots\int dx_{N}\\\nonumber
  &\,
  \exp\bigg\{\frac1\sigma\sum_{i=0}^{N-1} -F(x_{i+1},t_{i+1})(x_{i} - x_{i+1}) - \frac1{2\sigma^2}\sum_{i=0}^{N-1}F^2(x_{i+1},t_{i+1})\dt\bigg\} \times\\\nonumber
  &\,
  \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=0}^{N-1} \frac{(x_{i} - x_{i+1})^2}{\dt}\bigg\}\\\nonumber
  =\lim_{N\rightarrow\infty} &\,
  \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx_{1}\cdots\int dx_{N}\\\nonumber
  &\,
  \exp\bigg\{\frac1\sigma\sum_{i=0}^{N-1} F(x_{i+1},t_{i+1})(x_{i+1} - x_{i})\bigg\}\times\\\nonumber
  &\,
  \exp\bigg\{- \frac1{2\sigma^2}\sum_{i=0}^{N-1}F^2(x_{i+1},t_{i+1})\dt\bigg\} \times\\\nonumber
  &\,
  \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=0}^{N-1} \frac{(x_{i} - x_{i+1})^2}{\dt}\bigg\}.
\end{align}

% Now we consider the time-reversed process $y_{N-i} = x_i$,
% \begin{align}\nonumber
%   p(y_0,T\vert y_N,0) =\lim_{N\rightarrow\infty} &\,
%   \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dy_1\cdots\int dx_{y-1}\\\nonumber
%   &\,
%   \exp\bigg\{\frac1\sigma\sum_{i=0}^{N-1} F(y_{N - i-1},t_{N-i-1})(w_{N-i-1} - w_{N-i}) \bigg\} \times \\ \nonumber
%   &\,
%   \exp\bigg\{-\sum_{i=0}^{N-1}  \nabla_x F(x_{i+1},t_{i+1})\dt\bigg\} \times \\\nonumber
%   &\,
%   \exp\bigg\{-\frac1{2\sigma^2}\sum_{i=0}^{N-1}F^2(x_i,t_i)\dt\bigg\} \times\\\label{eqn:tmp8}
%   &\,
%   \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=0}^{N-1} \frac{(x_{i+1} - x_i)^2}{\dt}\bigg\}.
% \end{align}

We notice that
\begin{align}\nonumber
  dV(x, t) = &\, \frac{\partial V}{\partial x} dx + \frac{\partial V}{\partial t} dt\\\nonumber
  =&\,
  (\nabla_x V F + \frac12 \sigma^2 \nabla^2_x V) dt + \sigma \nabla V dw_t + \frac{\partial V}{\partial t} dt \\\nonumber
  =&\,
  -F^2dt + \frac12 \sigma^2\nabla_x F dt - \sigma F dw_t + \frac{\partial V}{\partial t} dt 
\end{align}

\bibliography{ref}{}
\bibliographystyle{unsrt}

\end{document}

### 2014-07-14 writedown/period.noneq.msm/main.tex

@@
-\documentclass[aip,jcp,preprint,unsortedaddress,a4paper,onecolumn]{revtex4-1}
+\documentclass[preprint,unsortedaddress,a4paper,onecolumn]{revtex4-1}
 % \documentclass[acs, jctcce, a4paper,preprint,unsortedaddress,onecolumn]{revtex4-1}
@@
 \newcommand{\mbp}[0]{\mathbb {P}}
+\newcommand{\mc}[0]{\mathcal {C}}
 \newcommand{\dt}[0]{\Delta t}
@@
 Now we assume the overdamped dynamics
-\begin{align}
+\begin{align}\label{eqn:tmp7}
   dx_t = -\nabla_x V(x_t,t) dt + \sigma dw_t
@@
 \end{align}
-Now consider the differentiation:
-\begin{align}\nonumber
-  F(x_i,t_i) - F(x_{i+1},t_{i+1}) =
-  &\,
-  F(x_i,t_i) - F(x_{i+1},t_{i}) + F(x_{i+1},t_{i}) -  F(x_{i+1},t_{i+1})\\\nonumber
-  =&\,
-  -\sigma\nabla_x F(x_{i+1},t_{i})dw_t + \mo(\dt) \\\label{eqn:tmp9}
-  =&\,
-  -\sigma\nabla_x F(x_{i+1},t_{i+1})dw_t + \mo(\dt) 
-\end{align}
-and
+Notice that
 \begin{align}\label{eqn:tmp10}
@@
 \end{align}
-Inserting Eq.~\eqref{eqn:tmp9} and \eqref{eqn:tmp10} into Eq.~\eqref{eqn:tmp8}, all terms of order $\mo(\dt)$ vanish at the limit $N\rightarrow\infty$,
+we have
 % so with the formal identity $(dw_t)^2 = dt$,  we have
 \begin{align}\nonumber
-  p(x_T,T\vert x_0,0) =\lim_{N\rightarrow\infty} &\,
+  p(x_T,T\vert x_0,0)
+  =\lim_{N\rightarrow\infty} &\,
   \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx_1\cdots\int dx_{N-1}\\\nonumber
   &\,
-  \exp\bigg\{\frac1{\sigma^2}\sum_{i=0}^{N-1} F(x_{i+1},t_{i+1})(x_{i+1} - x_i) \bigg\} \times \\ \nonumber
-  &\,
-  \exp\bigg\{-\frac{1}{\sigma^2}\sum_{i=0}^{N-1}  \nabla_x F(x_{i+1},t_{i+1}) (x_{i+1} - x_{i})^2\bigg\} \times \\\nonumber
-  &\,
-  \exp\bigg\{-\frac1{2\sigma^2}\sum_{i=0}^{N-1}F^2(x_i,t_i)\dt\bigg\} \times\\\label{eqn:tmp11}
+  \exp\bigg\{\frac1{\sigma^2}\sum_{i=0}^{N-1} F(x_{i},t_{i})(x_{i+1} - x_i) -\frac1{2\sigma^2}\sum_{i=0}^{N-1}F^2(x_i,t_i)\dt\bigg\} \times\\\label{eqn:tmp10}
   &\,
@@
 \end{align}
-Now, consider a trajectory that starts at $x_T$, ends at $x_0$, and visits $x_{N-i}$ at time $t_i$, the conditional probability
-gives
+Now, consider a conjugate trajectory $x^\dagger_t = x_{T-t}$ that starts at $x_T$, ends at $x_0$. The conjugate dynamics is driven by  $F^\dagger(x^\dagger_t,t) = F(x^\dagger_t, T-t)$.
+Since we have the symmetry $F(x_t, -t) = -F(x_t, t)$, the conjugate dynamics also satisfies Eq.~\eqref{eqn:tmp7}.
+Therefore, we have the probability:
 \begin{align}\nonumber
-  p(x_0,T\vert x_T,0)
-  =\lim_{N\rightarrow\infty} &\,
-  \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx_{N-1}\cdots\int dx_{1}\\\nonumber
+  p(x_0,T\vert x_T,0) = &\,
+  p^\dagger(x^\dagger_T,T\vert x^\dagger_0,0)  \\\nonumber
+  = &\,
+  \lim_{N\rightarrow\infty}
+  \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx^\dagger_1\cdots\int dx^\dagger_{N-1}\\\nonumber
   &\,
-  \exp\bigg\{\frac1\sigma\sum_{i=N}^{1} F(x_i,t_{N-i})(x_{i-1} - x_{i}) - \frac1{2\sigma^2}\sum_{i=N}^{1}F^2(x_i,t_{N-i})\dt\bigg\} \times\\\nonumber
+  \exp\bigg\{\frac1{\sigma^2}\sum_{i=0}^{N-1} F^\dagger(x^\dagger_{i},t_{i})(x^\dagger_{i+1} - x^\dagger_i) -\frac1{2\sigma^2}\sum_{i=0}^{N-1}[F^\dagger(x^\dagger_i,t_i)]^2\dt\bigg\} \times\\\nonumber
   &\,
-  \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=N}^{1} \frac{(x_{i-1} - x_{i})^2}{\dt}\bigg\} \\\nonumber
-  =\lim_{N\rightarrow\infty} &\,
-  \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx_{1}\cdots\int dx_{N}\\\nonumber
+  \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=0}^{N-1} \frac{(x^\dagger_{i+1} - x^\dagger_i)^2}{\dt}\bigg\} \\\nonumber
+  =&\,
+  \lim_{N\rightarrow\infty} 
+  \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx_1\cdots\int dx_{N-1}\\\nonumber
   &\,
-  \exp\bigg\{\frac1\sigma\sum_{i=0}^{N-1} -F(x_{i+1},t_{i+1})(x_{i} - x_{i+1}) - \frac1{2\sigma^2}\sum_{i=0}^{N-1}F^2(x_{i+1},t_{i+1})\dt\bigg\} \times\\\nonumber
+  \exp\bigg\{\frac1{\sigma^2}\sum_{i=N}^{1} F(x_{i},t_{i})(x_{i-1} - x_i) -\frac1{2\sigma^2}\sum_{i=N}^{1}F^2(x_i,t_i)\dt\bigg\} \times\\\label{eqn:tmp11}
   &\,
-  \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=0}^{N-1} \frac{(x_{i} - x_{i+1})^2}{\dt}\bigg\}\\\nonumber
-  =\lim_{N\rightarrow\infty} &\,
-  \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx_{1}\cdots\int dx_{N}\\\nonumber
+  \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=N}^{1} \frac{(x_{i-1} - x_i)^2}{\dt}\bigg\}.
+\end{align}
+The difference between the single trajectory probabilities is
+\begin{align}\label{eqn:tmp12}
+  \log\bigg\{\frac{  p[x_t] }{ p[x^\dagger_t]} \bigg\}
+  =&\,
+  \frac1{\sigma^2}\sum_{i=1}^{N-1} F(x_i,t_i)(x_{i+1} - x_{i}) + F(x_i,t_i)(x_{i} - x_{i-1}) 
+\end{align}
+Now consider the differentiation:
+\begin{align}\nonumber
+  F(x_{i},t_{i}) - F(x_{i-1},t_{i-1}) =
   &\,
-  \exp\bigg\{\frac1\sigma\sum_{i=0}^{N-1} F(x_{i+1},t_{i+1})(x_{i+1} - x_{i})\bigg\}\times\\\nonumber
-  &\,
-  \exp\bigg\{- \frac1{2\sigma^2}\sum_{i=0}^{N-1}F^2(x_{i+1},t_{i+1})\dt\bigg\} \times\\\nonumber
-  &\,
-  \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=0}^{N-1} \frac{(x_{i} - x_{i+1})^2}{\dt}\bigg\}.
+  F(x_{i},t_{i}) - F(x_{i-1},t_{i}) + F(x_{i-1},t_{i}) -  F(x_{i-1},t_{i-1})\\\nonumber
+  =&\,
+  \nabla_x F(x_{i-1},t_{i})(x_i - x_{i-1}) + \mo(\dt) \\\label{eqn:tmp13}
+  =&\,
+  \nabla_x F(x_{i-1},t_{i-1})(x_i - x_{i-1}) + \mo(\dt)
 \end{align}
-
-% Now we consider the time-reversed process $y_{N-i} = x_i$,
-% \begin{align}\nonumber
-%   p(y_0,T\vert y_N,0) =\lim_{N\rightarrow\infty} &\,
-%   \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dy_1\cdots\int dx_{y-1}\\\nonumber
-%   &\,
-%   \exp\bigg\{\frac1\sigma\sum_{i=0}^{N-1} F(y_{N - i-1},t_{N-i-1})(w_{N-i-1} - w_{N-i}) \bigg\} \times \\ \nonumber
-%   &\,
-%   \exp\bigg\{-\sum_{i=0}^{N-1}  \nabla_x F(x_{i+1},t_{i+1})\dt\bigg\} \times \\\nonumber
-%   &\,
-%   \exp\bigg\{-\frac1{2\sigma^2}\sum_{i=0}^{N-1}F^2(x_i,t_i)\dt\bigg\} \times\\\label{eqn:tmp8}
-%   &\,
-%   \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=0}^{N-1} \frac{(x_{i+1} - x_i)^2}{\dt}\bigg\}.
-% \end{align}
-
+Then the \eqref{eqn:tmp12} becomes
+\begin{align}\label{eqn:tmp14}
+  \log\bigg\{\frac{  p[x_t] }{ p[x^\dagger_t]} \bigg\}
+  =&\,
+  \frac2{\sigma^2}\sum_{i=0}^{N-1} F(x_i,t_i)(x_{i+1} - x_{i}) +
+  \frac1{\sigma^2}\sum_{i=0}^{N-1}\nabla_xF(x_i,t_i)(x_{i+1} - x_{i})^2
+\end{align}
 We notice that
@@
   =&\,
-  (\nabla_x V F + \frac12 \sigma^2 \nabla^2_x V) dt + \sigma \nabla V dw_t + \frac{\partial V}{\partial t} dt \\\nonumber
+  \frac12 \sigma^2 \nabla^2_x V dt +  \nabla V dx_t + \frac{\partial V}{\partial t} dt \\
   =&\,
-  -F^2dt + \frac12 \sigma^2\nabla_x F dt - \sigma F dw_t + \frac{\partial V}{\partial t} dt 
+  -\frac12 \sigma^2 \nabla_x F dt -  F dx_t + \frac{\partial V}{\partial t} dt
 \end{align}
+and the identity
+\begin{align}
+  dt = (dw_t)^2 = \frac1{\sigma^2} dx_t^2
+\end{align}
+Eq.~\eqref{eqn:tmp14} becomes
+\begin{align}
+  \log\bigg\{\frac{  p[x_t] }{ p[x^\dagger_t]} \bigg\}
+  =&\,
+  -\frac2{\sigma^2}\bigg[
+  V(x_N,t_N) - V(x_0,t_0) + \sum_{i=0}^{N-1}\partial_tV(x_i,t_i)\dt
+  \bigg]
+\end{align}
+According to the  Einstein relation $T = \sigma^2/2$, by denoting $\beta = 1/T$
+\begin{align}
+  \log\bigg\{\frac{  p[x_t] }{ p[x^\dagger_t]} \bigg\}
+  =&\,
+  -\beta\bigg[
+  V(x_N,t_N) - V(x_0,t_0) + \sum_{i=0}^{N-1}\partial_tV(x_i,t_i)\dt
+  \bigg]  
+\end{align}
+Therefore
+\begin{align}\nonumber
+  p(x_0,T\vert x_T,0)
+  =&\,
+  % \lim_{N\rightarrow\infty} 
+  % \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx_{N-1}\cdots\int dx_{1}
+  \int_{\mc\{x_0,0;x_T,T\}}
+  \frac{  p[x^\dagger_t] }{ p[x_t]} \cdot p[x_t] \\\label{eqn:tmp19}
+  = &\,
+  \frac{e^{-\beta V(x_0,t_0)}}{e^{-\beta V(x_N,t_N)}}
+  \int_{\mc\{x_0,0;x_T,T\}}
+  \exp\bigg\{
+  \beta\int_0^T \partial_t V(x_t,t)dt 
+  \bigg\} \cdot p[x_t]
+\end{align}
+where $\mc\{x_0,0;x_T,T\}$ denotes all continuous trajectories starting at $x_0$ and ending at $x_T$.
+If $\partial_t V = 0$, i.e.~equilibrium, we have
+\begin{align}
+  p(x_0,T\vert x_T,0)e^{-\beta V(x_T,T)} =  p(x_T,T\vert x_0,0) e^{-\beta V(x_0,0)},
+\end{align}
+which proves the reversibility of the equilibrium dynamics.
+The term
+\begin{align}
+  W[x_t] = - \int_0^T \partial_t V(x_t,t)dt
+\end{align}
+is the non-equilibrium work associated to all possible
+the dynamics $x_t$ starting at $x_0$ and ending at $x_T$ (see e.g.~Ref.~\cite{seifert2012stochastic}).
+Therefore Eq.~\eqref{eqn:tmp19} is the detailed Jarzynski relation.
+Now the problem becomes if we can write a nice form (e.g.~the difference of a state function measured at $x_T$ and $x_0$) for the non-equilibrium work.
 

### 2014-07-14 alanine.nanma/template/functions.sh
update it for more ele method. tested to be consistent with old spme-switch mehtod

@@ -40,31 +40,64 @@ function set_parameters_pert () {
     file=$1
     grep nstcalcenergy $file &> /dev/null
     if [ $? -eq 1 ]; then
-	echo "nstcalcenergy=1" >> $file
+	echo "nstcalcenergy = 1" >> $file
     fi
     pert_nstep=`echo "$pert_time / $pert_dt" | bc -l | cut -d '.' -f 1`
     pert_xtcout_feq=`echo "$pert_frame_feq / $pert_dt" | bc -l | cut -d '.' -f 1`
-    pert_xvout_feq=$pert_xtcout_feq
+    pert_xvout_feq=0
     pert_energy_feq=$pert_xtcout_feq
-    sed -e "/^dt/s/=.*/= $pert_dt/g" $file |\
+    pert_nstcalce=`echo "$pert_energy_feq" | bc`
+    pert_nstcomm=`echo "$pert_energy_feq" | bc`
+    if test $pert_ele_method_ind -eq 0; then # zm
+	pert_nstlist=$pert_nstlist
+	pert_rcut_ele_switch=$pert_rcut_ele
+    fi
+    if test $pert_ele_method_ind -eq 1; then # pme
+	pert_rcut_ele=$pert_rlist
+	pert_rcut_ele_switch=$pert_rcut_ele
+    fi
+    if test $pert_ele_method_ind -eq 2; then # rf
+	pert_rcut_ele=$pert_rlist
+	pert_rcut_ele_switch=$pert_rcut_ele
+    fi
+    sed -e "/^dt /s/=.*/= $pert_dt/g" $file |\
+    sed -e "/^nstep /s/=.*/= $pert_nstep/g" |\
+    sed -e "/^ld-seed /s/=.*/= `date +%s`/g" |\
+    sed -e "/^nstcalcenergy /s/=.*/= $pert_nstcalce/g"|\
+    sed -e "/^nstcomm /s/=.*/= $pert_nstcomm/g"|\
+    sed -e "/^nstenergy /s/=.*/= $pert_energy_feq/g"|\
     sed -e "/^integrator/s/=.*/= $pert_integrator/g" |\
-    sed -e "/^Tcoupl /s/=.*/= no/g" |\
-    sed -e "/^Pcoupl /s/=.*/= $pert_barostat/g" |\
[…]

### 2014-07-14 alanine.nanma/template/parameters.sh

@@ -1,15 +1,5 @@
-# method of run:
-run_method=atom.inhomo.sd
+# gromacs seed dir
 gro_dir=gromacs.conf.box.002.70
-nthreads=8
-
-# # productive equilibrium run settings
-# long_equi_warm_time=200		# ps
-# long_equi_frame_feq=5		# ps
-# long_equi_num_frame=100		# n
-# long_equi_dt=0.002		# ps
-# long_equi_taut=0.5		# ps
-# long_equi_seed=`date +%s`	# 
 
 # equilibrium run settings
 equi_warm_time=200		# ps
@@ -20,8 +10,9 @@ equi_taut=0.5			# ps
 equi_seed=`date +%s`		# 
 
 # non-equilibrium settings
+## non-equilibrium control parameters
 pert_equi_result="$HOME/group_storage/run.result.equi.box02.70.more/result.equi/"
-pert_num_conf_use=20000	#
+pert_num_conf_use=1		#
 pert_mode=2			# 1: relax, 2: cos wave
 pert_strength=1.0		# nm/ps velocity
 pert_warm_time=40		# ps 1: warm time, 2: periodicity
@@ -29,42 +20,38 @@ pert_shift=0			# unitless
 pert_phi=270			# deg. shift of the phase
 pert_time=1000			# ps
 pert_frame_feq=0.5		# ps
+
+## electrostatic and vdw method
+pert_ele_method=pme-switch	# pme or zm or rf
+pert_rlist=1.3			# 
+pert_nstlist=5			# 
+pert_rcut_ele=1.0		# if pme is used, set this value to rlist
+pert_rcut_ele_switch=0.95
+pert_pme_F_spacing=0.12
+pert_pme_order=4
+pert_vdw_type=shift		# using adress will overwrite it with "user"
+pert_rcut_vdw=1.0
+pert_rcut_vdw_switch=0.95
+pert_tab_ext=0.5
+pert_e_rf=80.0
+pert_zm_l=3
+pert_zm_alpha=0.0
+
+## timestep and ensemble control
 pert_dt=0.002			# ps
+pert_integrator=sd1		# now should be sd1
+pert_local_sd_range=1.0
 pert_taut=0.1			# ps
-pert_noSdRange=1.0		# nm
-pert_barostat=Parrinello-Rahman # Parrinello-Rahman or no
+pert_barostat=Parrinello-Rahman	# Parrinello-Rahman or no
 pert_taup=2.0			# ps
+
+## parallel simultion control
[…]

### 2014-07-14 alanine.nanma/template/run.pert.sh

@@ -1,5 +1,6 @@
 #!/bin/bash
 
+source env.sh
 source parameters.sh
 source functions.sh
 
@@ -7,7 +8,7 @@ make -C tools/angles/ makedir
 # make -C tools/angles/ clean
 make -C tools/angles/ -j$nthreads
 
-cwd=`pwd`
+wwd=`pwd`
 # prepare files
 if test ! -d $pert_equi_result ; then
     echo "no dir $pert_equi_result, exit"
@@ -21,9 +22,28 @@ if test ! -d $gro_dir; then
     echo "no dir $gro_dir, exit"
     exit
 fi
-#rm -f angle.name
-#rm -f gxs.name
-#rm -f success.dir.name
+
+if echo "$pert_ele_method" | grep pme &> /dev/null ; then
+    echo "# run with ele method pme"
+    pert_ele_method_gromacs=pme
+    pert_ele_method_ind=1
+    if echo "$pert_ele_method" | grep pme-switch &> /dev/null ; then
+	echo "# run with ele method pme-switch"
+	pert_ele_method_gromacs=pme-switch
+	pert_ele_method_ind=11
+    fi
+else if echo "$pert_ele_method" | grep zm &> /dev/null ; then
+    echo "# run with ele method zm"
+    pert_ele_method_gromacs=user
+    pert_ele_method_ind=0
+else if echo "$pert_ele_method" | grep rf &> /dev/null ; then
+    echo "# run with ele method rf"
+    pert_ele_method_gromacs=reaction-field
+    pert_ele_method_ind=2
+fi
+fi
+fi
+
 touch angle.name gxs.name success.dir.name
 
 # targets=`awk '{print $1}' $pert_equi_result/equi.frame | head -n $pert_num_conf_use`
@@ -52,29 +72,43 @@ do
     cd $my_dir
     rm -f run.log
     set_parameters_pert grompp.mdp
+
+    if test $pert_ele_method_ind -eq 0; then
+	echo "# gen zm pot"
+	zm_xup=`echo $pert_rlist + $pert_tab_ext + .1 | bc -l`
+	make -C $zm_gen_dir &> /dev/null
+	$zm_gen_dir/zm -l $pert_zm_l --xup $zm_xup --alpha $pert_zm_alpha --rc $pert_rcut_ele --output table.xvg &> /dev/null
+	rm -f tablep.xvg
+	cp $wwd/tools/table6-12.xvg tablep.xvg
+    fi
+    
[…]

### 2014-07-14 alanine.nanma/template/env.maotai.sh
add missing env file

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+gmx_dir=$HOME/local/gromacs/4.6.5.localsd.fcorr
+source $gmx_dir/bin/GMXRC.bash
+
+zm_gen_dir=$WORK/study/adress.noneq/zm/tools/gen.pot
+
+gmx_grompp_command="grompp"
+gmx_tune_command="g_pme_error"
+gmx_mdrun_command="mdrun -notunepme"

### 2014-07-14 alanine.nanma/template/env.maotai.sh
fix bug

@@ -5,6 +5,6 @@ source $gmx_dir/bin/GMXRC.bash
 
 zm_gen_dir=$WORK/study/adress.noneq/zm/tools/gen.pot
 
-gmx_grompp_command="grompp"
-gmx_tune_command="g_pme_error"
-gmx_mdrun_command="mdrun -notunepme"
+pert_grompp_command="grompp"
+pert_tune_command="g_pme_error"
+pert_mdrun_command="mdrun -notunepme"

### 2014-07-14 alanine.nanma/template/functions.sh
fix bug

@@ -91,13 +91,13 @@ function set_parameters_pert () {
     sed -e "/^tau-t/s/=.*/= $pert_taut/g" |\
     sed -e "/^tau_p/s/=.*/= $pert_taup/g" |\
     sed -e "/^tau-p/s/=.*/= $pert_taup/g" |\
-    sed -e "/^epsilon-rf /s/=.*/= $gmx_e_rf/g"|\
+    sed -e "/^epsilon-rf /s/=.*/= $pert_e_rf/g"|\
     sed -e "/^userreal1/s/=.*/= $pert_local_sd_range/g" |\
     sed -e "/^gen_vel /s/=.*/= no/g" |\
     sed -e "/^gen-vel /s/=.*/= no/g"|\
     sed -e "/^couple-moltype /s/=.*/= /g"|\
     sed -e "/^E-x /s/=.*/= 1 $pert_strength 0.0/g" |\
-    sed -e "/^table-extension /s/=.*/= $gmx_tab_ext/g"> tmptmptmp.mdp
+    sed -e "/^table-extension /s/=.*/= $pert_tab_ext/g"> tmptmptmp.mdp
     mv -f tmptmptmp.mdp $file
     if test $pert_mode -eq 1; then
 	sed -e "/^E-xt /s/=.*/= 1 $pert_warm_time 0.0/g" $file > tmptmptmp.mdp

### 2014-07-14 alanine.nanma/template/functions.sh
fix bugs

@@ -61,7 +61,7 @@ function set_parameters_pert () {
 	pert_rcut_ele_switch=$pert_rcut_ele
     fi
     sed -e "/^dt /s/=.*/= $pert_dt/g" $file |\
-    sed -e "/^nstep /s/=.*/= $pert_nstep/g" |\
+    sed -e "/^nsteps /s/=.*/= $pert_nstep/g" |\
     sed -e "/^ld-seed /s/=.*/= `date +%s`/g" |\
     sed -e "/^nstcalcenergy /s/=.*/= $pert_nstcalce/g"|\
     sed -e "/^nstcomm /s/=.*/= $pert_nstcomm/g"|\

### 2014-07-14 alanine.nanma/template/env.maotai.sh
fix bug, can run for rf and zm

@@ -3,7 +3,7 @@
 gmx_dir=$HOME/local/gromacs/4.6.5.localsd.fcorr
 source $gmx_dir/bin/GMXRC.bash
 
-zm_gen_dir=$WORK/study/adress.noneq/zm/tools/gen.pot
+zm_gen_dir=$HOME/study/adress.noneq/zm/tools/gen.pot
 
 pert_grompp_command="grompp"
 pert_tune_command="g_pme_error"

### 2014-07-14 alanine.nanma/template/functions.sh
add adress support.

@@ -125,11 +125,11 @@ function set_parameters_pert () {
 	hboxz=`echo "$boxz * 0.5" | bc -l`
 	cat $file |\
         sed -e "/^DispCorr /s/=.*/= no/g"|\
-        sed -e "/^adress-type /s/=.*/= $adress_type/g" |\
+        sed -e "/^adress-type /s/=.*/= $pert_adress_type/g" |\
         sed -e "/^adress-interface-correction /s/=.*/= thermoforce/g" |\
         sed -e "/^adress-site /s/=.*/= com/g" |\
-        sed -e "/^adress-ex-width /s/=.*/= $adress_ex_region/g" |\
-        sed -e "/^adress-hy-width /s/=.*/= $adress_hy_region/g" |\
+        sed -e "/^adress-ex-width /s/=.*/= $pert_adress_ex_region/g" |\
+        sed -e "/^adress-hy-width /s/=.*/= $pert_adress_hy_region/g" |\
         sed -e "/^vdwtype /s/=.*/= user/g"|\
         sed -e "/^vdw-type /s/=.*/= user/g"|\
         sed -e "/^vdw_type /s/=.*/= user/g"|\

### 2014-07-14 alanine.nanma/template/run.pert.sh

@@ -73,13 +73,25 @@ do
     rm -f run.log
     set_parameters_pert grompp.mdp
 
-    if test $pert_ele_method_ind -eq 0; then
+    if test $pert_ele_method_ind -eq 0; then	# zm
 	echo "# gen zm pot"
 	zm_xup=`echo $pert_rlist + $pert_tab_ext + .1 | bc -l`
 	make -C $zm_gen_dir &> /dev/null
 	$zm_gen_dir/zm -l $pert_zm_l --xup $zm_xup --alpha $pert_zm_alpha --rc $pert_rcut_ele --output table.xvg &> /dev/null
 	rm -f tablep.xvg
 	cp $wwd/tools/table6-12.xvg tablep.xvg
+    fi
+    if echo $pert_adress | grep yes &> /dev/null; then	# vdw tables for adress
+	rm -f table.xvg tablep.xvg
+	cp $wwd/tools/table6-12.xvg tablep.xvg
+	cp $wwd/tools/table6-12.xvg table.xvg
+    fi
+    if [ -f $wwd/$pert_adress_tf_file ]; then	# tf table for adress
+	if [ -f tabletf_CMW.xvg ]; then
+	    echo "# rm existing tf table"
+	    rm -f tabletf_CMW.xvg
+	fi
+	cp $wwd/$pert_adress_tf_file ./tabletf_CMW.xvg
     fi
     
     count_1=`echo "($count % $nlines_equi_frame) + 1" | bc `

### 2014-07-14 alanine.nanma/template/sample.parameters/parameters.adress.sh

@@ -1,5 +1,5 @@
 # gromacs seed dir
-gro_dir=gromacs.conf.box.002.70
+gro_dir=gromacs.conf.box.006.00.adress
 
 # equilibrium run settings
 equi_warm_time=200		# ps
@@ -11,7 +11,7 @@ equi_seed=`date +%s`		#
 
 # non-equilibrium settings
 ## non-equilibrium control parameters
-pert_equi_result="$HOME/group_storage/run.result.equi.box02.70.more/result.equi/"
+pert_equi_result="$HOME/group_storage/run.result.equi.box06.00.adress/gromacs.traj.nvt/"
 pert_num_conf_use=1		#
 pert_mode=2			# 1: relax, 2: cos wave
 pert_strength=1.0		# nm/ps velocity
@@ -22,8 +22,8 @@ pert_time=1000			# ps
 pert_frame_feq=0.5		# ps
 
 ## electrostatic and vdw method
-pert_ele_method=pme-switch	# pme or zm or rf
-pert_rlist=1.3			# 
+pert_ele_method=rf		# pme or zm or rf
+pert_rlist=1.0			# 
 pert_nstlist=5			# 
 pert_rcut_ele=1.0		# if pme is used, set this value to rlist
 pert_rcut_ele_switch=0.95
@@ -40,9 +40,9 @@ pert_zm_alpha=0.0
 ## timestep and ensemble control
 pert_dt=0.002			# ps
 pert_integrator=sd1		# now should be sd1
-pert_local_sd_range=1.0
+pert_local_sd_range=0.60
 pert_taut=0.1			# ps
-pert_barostat=Parrinello-Rahman	# Parrinello-Rahman or no
+pert_barostat=no		# Parrinello-Rahman or no
 pert_taup=2.0			# ps
 
 ## parallel simultion control
@@ -50,7 +50,7 @@ pert_parallel_num_pro=1		# n
 pert_parallel_my_id=0		# n
 
 ## adress stuff
-pert_adress=no
+pert_adress=yes
 pert_adress_ex_region=0.60
 pert_adress_hy_region=1.01
 pert_adress_type=sphere

### 2014-07-14 alanine.nanma/template/run.pert.sh
link files to save space

@@ -68,8 +68,17 @@ do
 	fi
     fi
     echo "# doing in dir $my_dir"
-    cp -a $gro_dir $my_dir
-    cd $my_dir
+    mkdir -p $my_dir
+#    cp -a $gro_dir $my_dir
+    cd $wwd/$gro_dir
+    ln_file_list=`ls | grep -v grompp | grep -v mdp$`
+    cd $wwd/$my_dir
+    for file in $ln_file_list;
+    do
+	ln -sf $wwd/$gro_dir/$file .
+    done
+    rm -f grompp.mdp
+    cp $wwd/$gro_dir/grompp.mdp .
     rm -f run.log
     set_parameters_pert grompp.mdp
 
@@ -85,13 +94,13 @@ do
 	rm -f table.xvg tablep.xvg
 	cp $wwd/tools/table6-12.xvg tablep.xvg
 	cp $wwd/tools/table6-12.xvg table.xvg
-    fi
-    if [ -f $wwd/$pert_adress_tf_file ]; then	# tf table for adress
-	if [ -f tabletf_CMW.xvg ]; then
-	    echo "# rm existing tf table"
-	    rm -f tabletf_CMW.xvg
+	if [ -f $wwd/$pert_adress_tf_file ]; then	# tf table for adress
+	    if [ -f tabletf_CMW.xvg ]; then
+		echo "# rm existing tf table"
+		rm -f tabletf_CMW.xvg
+	    fi
+	    cp $wwd/$pert_adress_tf_file ./tabletf_CMW.xvg
 	fi
-	cp $wwd/$pert_adress_tf_file ./tabletf_CMW.xvg
     fi
     
     count_1=`echo "($count % $nlines_equi_frame) + 1" | bc `
@@ -131,7 +140,7 @@ do
     if [ $count -eq 0 ]; then
 	cp -a ..//pert.$count ..//backup.pert.$count
     fi
-    rm -f traj.xtc traj.trr state*.cpt topol.tpr conf.gro index.ndx angle.log md.log genbox.log mdout.mdp protein.gro run.log confout.gro
+    rm -f traj.xtc traj.trr state*.cpt topol.tpr conf.gro index.ndx angle.log md.log genbox.log mdout.mdp protein.gro run.log confout.gro error.out grompp.mdp topol.top
     
     cd $wwd
     echo "$my_dir/angle.dat" >> angle.name

### 2014-07-14 alanine.nanma/template/env.hlrn.sh
add env for hlrn

@@ -1,0 +1,10 @@
+#!/bin/bash
+
+gmx_dir=$WORK/local/gromacs/4.6.5.localsd.fcorr
+source $gmx_dir/bin/GMXRC.bash
+
+zm_gen_dir=$WORK/study/adress.noneq/zm/tools/gen.pot
+
+pert_grompp_command="grompp"
+pert_tune_command="aprun -B g_pme_error"
+pert_mdrun_command="aprun -B mdrun -notunepme"

### 2014-07-15 alanine.nanma/template/auto.allegro.sh
run on allegro

@@ -1,5 +1,6 @@
 #!/bin/bash
 
+source env.sh
 source parameters.sh
 
 cwd=`pwd`
@@ -13,7 +14,7 @@ echo "#PBS -o allegro.out"			>> submit.sh
 echo "#PBS -e allegro.err"			>> submit.sh
 echo "#PBS -M han.wang@fu-berlin.de"		>> submit.sh
 echo "#PBS -l walltime=70:00:00"		>> submit.sh
-echo "#PBS -l nodes=1:ppn=$nthreads"		>> submit.sh
+echo "#PBS -l nodes=1:ppn=$nnodes"		>> submit.sh
 echo "#PBS -l pmem=1000mb"			>> submit.sh
 
 echo "cd $cwd"					>> submit.sh

### 2014-08-14 alanine.nanma/template/tools/scripts/msm.analyze.brute.force.sh
improved scripts

@@ -28,8 +28,31 @@ fi
 mycommand="$msm_dir/calculate.commitor --num-bin $msm_dih_nbin --input-cluster-map $target_dir/cluster.map.out --input-traj-dir dir.name --input-disc-traj traj.dih.disc.periodT --output-fw $target_dir/commitor.fw.out --output-bw $target_dir/commitor.bw.out"
 echo "# calculate commitor by command: $mycommand"
 $mycommand
+paste $target_dir/commitor.fw.out $target_dir/commitor.bw.out > $target_dir/commitor.out
 
 mycommand="$msm_dir/calculate.steady.dist --num-bin $msm_dih_nbin --input-traj-dir dir.name --input-disc-traj traj.dih.disc.periodT --output $target_dir/steady.dist.out"
 echo "# calculate steady dist by command: $mycommand"
 $mycommand
+
+mycommand="$msm_dir/calculate.fht --input-largest-set $target_dir/largestSet.dih --input-cluster-map $target_dir/cluster.map.out  --num-bin $msm_dih_nbin --input-traj-dir dir.name --input-disc-traj traj.dih.disc.periodT --output $target_dir/fht.out"
+echo "# calculate first hitting time by command: $mycommand"
+$mycommand
+
+if [ -f $target_dir/cluster.map.1.out ]; then
+    mycommand="$msm_dir/calculate.fht --input-largest-set $target_dir/largestSet.dih --input-cluster-map $target_dir/cluster.map.1.out  --num-bin $msm_dih_nbin --input-traj-dir dir.name --input-disc-traj traj.dih.disc.periodT --output $target_dir/fht.1.out"
+    echo "# calculate first hitting time 1 by command: $mycommand"
+    $mycommand
+fi
+
+if [ -f $target_dir/cluster.map.2.out ]; then
+    mycommand="$msm_dir/calculate.fht --input-largest-set $target_dir/largestSet.dih --input-cluster-map $target_dir/cluster.map.2.out  --num-bin $msm_dih_nbin --input-traj-dir dir.name --input-disc-traj traj.dih.disc.periodT --output $target_dir/fht.2.out"
+    echo "# calculate first hitting time 2 by command: $mycommand"
+    $mycommand
+fi
+
+if [ -f $target_dir/cluster.map.3.out ]; then
[…]

### 2014-08-14 alanine.nanma/template/tools/scripts/msm.analyze.disc.sh

@@ -34,7 +34,30 @@ echo "." > current.name
 mycommand="$msm_dir/calculate.commitor --num-bin $msm_dih_nbin --input-cluster-map $target_dir/cluster.map.out --input-traj-dir current.name --input-disc-traj traj.out --output-fw $target_dir/commitor.fw.msm.out --output-bw $target_dir/commitor.bw.msm.out"
 echo "# compute commitor by $mycommand"
 $mycommand
+paste $target_dir/commitor.fw.msm.out $target_dir/commitor.bw.msm.out > $target_dir/commitor.msm.out
 
 mycommand="$msm_dir/calculate.steady.dist --num-bin $msm_dih_nbin --input-traj-dir current.name --input-disc-traj traj.out --output $target_dir/steady.dist.msm.out"
 echo "# compute steady dist by $mycommand"
 $mycommand
+
+mycommand="$msm_dir/calculate.fht --input-largest-set $target_dir/largestSet.dih --input-cluster-map $target_dir/cluster.map.out  --num-bin $msm_dih_nbin --input-traj-dir current.name --input-disc-traj traj.out --output $target_dir/fht.msm.out"
+echo "# calculate first hitting time by command: $mycommand"
+$mycommand
+
+if [ -f $target_dir/cluster.map.1.out ]; then
+    mycommand="$msm_dir/calculate.fht --input-largest-set $target_dir/largestSet.dih --input-cluster-map $target_dir/cluster.map.1.out  --num-bin $msm_dih_nbin --input-traj-dir current.name --input-disc-traj traj.out --output $target_dir/fht.msm.1.out"
+    echo "# calculate first hitting time 1 by command: $mycommand"
+    $mycommand
+fi
+    
+if [ -f $target_dir/cluster.map.2.out ]; then
+    mycommand="$msm_dir/calculate.fht --input-largest-set $target_dir/largestSet.dih --input-cluster-map $target_dir/cluster.map.2.out  --num-bin $msm_dih_nbin --input-traj-dir current.name --input-disc-traj traj.out --output $target_dir/fht.msm.2.out"
+    echo "# calculate first hitting time 2 by command: $mycommand"
+    $mycommand
+fi
+    
+if [ -f $target_dir/cluster.map.3.out ]; then
[…]

### 2014-08-15 alanine.nanma/template/tools/scripts/msm.floquet.eig.m
add eigenvalue calculator for floquet matrix

@@ -1,0 +1,7 @@
+fm = load('floque.B.out');
+fm = fm';
+[v e] = eig(fm);
+ee = sum(e)';
+vv =v(:,1:5);
+save ('floquet.eigvalue.out', 'ee');
+save ('floquet.eigvector.out', 'vv');

### 2014-08-15 alanine.nanma/template/tools/scripts/msm.floquet.eig.sh

@@ -1,0 +1,42 @@
+#!/bin/bash
+
+if [ $# -ne 1 ]; then
+    echo "usage:"
+    echo "$0 DIR_STORING_MSM"
+    exit
+fi
+
+target_dir=$1
+script_dir=$(cd ${0%/*} && echo $PWD)
+base_dir=$script_dir/..
+angle_dir=$base_dir/angles
+msm_dir=$base_dir/msm
+cwd=`pwd`
+
+if [ ! -d $target_dir ]; then
+    echo "no dir $target_dir"
+    exit
+fi
+
+if [ ! -f $target_dir/msm.parameters.sh ]; then
+    echo "no file $target_dir/msm.parameters.sh"
+    exit
+else
+    source $target_dir/msm.parameters.sh
+fi
+
+cd $target_dir
+octave $script_dir/msm.floquet.eig.m
+
+neig=`grep columns floquet.eigvector.out | awk '{print $3}'`
+echo "# $neig eigenvectors are printed"
+
+for ii in `seq 1 $neig`;
+do
+    grep -v \# floquet.eigvector.out | awk "{print \$$ii}"  | grep -v \# > tmp.vec.in
+    $msm_dir/vector.set2dih --input-largest-set largestSet.dih --num-bin $msm_dih_nbin --input tmp.vec.in --output floquet.eigvector.$ii.out
+done
+# rm -f tmp.vec.in
+
+cd $cwd
+

### 2014-08-15 writedown/period.noneq.msm/main.tex
backup

@@
-\documentclass[preprint,unsortedaddress,a4paper,onecolumn]{revtex4-1}
+\documentclass[aps, pre, preprint,unsortedaddress,a4paper,onecolumn]{revtex4-1}
 % \documentclass[acs, jctcce, a4paper,preprint,unsortedaddress,onecolumn]{revtex4-1}
@@
 \maketitle
+
+\section{Introduction}
+Non-equilibrium, especically periodically driven system. Interesting.
+
+MSM tools for analyzing, provide profund understanding.
+
+Current achievement of MSM in equilibrium cases.
+
+Importance: first application of MSM in a non-equilibrium system.
 
@@
   \centering
-  \caption{The first non-trivial timescales calculated from $e^{T\vect B}$.
+  \caption{The first four non-trivial timescales calculated from $e^{T\vect B}$. The unit of time in the table is ps.
+    $\tau$ is the lag time used to calculate the generator~\eqref{eqn:tmp4}. $[T_0,T_1]$ is the time interval,
+    in which the generator is estimated from the MD trajectories. The 5th eigenvalue of uniform decomposition with $\tau=8.0$~ps is not real, so
+    the corresponding timescale is not calculated.
   }
-  \begin{tabular*}{0.3\textwidth}{@{\extracolsep{\fill}}c   c}\hline\hline
-    Method      &        $t_2$ [ps]  \\\hline
-    5 sets      & 72.4     \\
-    Uni. $M=05$ & 53.6     \\
-    Uni. $M=10$ &107.2     \\
-    Uni. $M=20$ &113.8     \\
-    Uni. $M=30$ &120.6     \\
+  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}c ccc rrrr}\hline\hline
+    Method  &  $M$ & $\tau$ & $[T_0,T_1]$ &   $t_2$ &   $t_3$ &   $t_4$ &   $t_5$  \\\hline
+    5 sets  & --   & 0.5    & $[300,1000]$    &  72.4 & 17.8 &  2.1 & 2.8    \\
+    Uniform & $05$ & 0.5    & $[300,1000]$    &  53.6 & 17.4 &  9.4 & 2.8    \\
+    Uniform & $10$ & 0.5    & $[300,1000]$    & 107.2 & 27.0 & 16.4 & 3.6    \\
+    Uniform & $20$ & 0.5    & $[300,1000]$    & 118.6 & 30.4 & 20.3 & 4.3    \\
+    Uniform & $30$ & 0.5    & $[300,1000]$    & 120.6 & 31.1 & 20.9 & 4.4    \\\hline
+    Uniform & $20$ & 0.5    & $[0,40]$    & 156.5 & 34.4 & 20.7 & 4.4    \\
+    Uniform & $20$ & 0.5    & $[0,80]$    & 133.8 & 32.8 & 20.4 & 4.4    \\
+    Uniform & $20$ & 0.5    & $[0,120]$   & 127.5 & 32.0 & 20.3 & 4.3    \\
+    Uniform & $20$ & 0.5    & $[0,200]$   & 122.0 & 31.3 & 20.3 & 4.3    \\
+    Uniform & $20$ & 0.5    & $[0,320]$   & 120.4 & 31.0 & 20.3 & 4.3    \\\hline
+    Uniform & $20$ & 1.0    & $[300,1000]$    & 119.8 & 30.5 & 21.7 & 4.9   \\
+    Uniform & $20$ & 2.0    & $[300,1000]$    & 117.8 & 29.2 & 21.5 & 5.3   \\
+    Uniform & $20$ & 4.0    & $[300,1000]$    & 114.2 & 27.0 & 20.2 & 4.8   \\
+    Uniform & $20$ & 8.0    & $[300,1000]$    & 110.6 & 25.0 & 18.1 & --   \\
     \hline\hline
@@
 \end{table}
+
+\section{Discussions}
+\subsection{The periodicity of the reduced dynamics}
+
+As discussed before, if the reduced dynamics captures the slow
+dynamics of interest, then the reduced dynamics is also periodic,
+which implies that the generator $M(t)$ can be estimated from any time
+interval by Eq.~\eqref{eqn:tmp4}. In practice, the reduced dynamics
+may not be perfectly periodic. The generator calculated from
+different time intervals can be used to test the periodicity of the
+reduced dynamics. The results are shown in Tab.~\ref{tab:tmp1} and
+Fig.~\ref{fig:tmp2}.  The dependency with respect to the time
+interval, in which the generator is calculated, indicates the reduced
+dynamics is not perfectly periodic. The reduced dynamics from $[0,40]$
+reproduces the best probability in interval $[0,40]$, and worst in the
+steady state. Moreover, the leading non-trivial timescale is also off
+(see Tab.~\ref{tab:tmp1}), while the accuracy of the second and third
+non-trivial timescales are better, because they are comparable to the
+period, 40~ps, in which the dynamics is relaxed. The reduced dynamics
+from $[300,1000]$ reproduces the best steady state probability, while
+worst in reproducing the initial relaxation process. The reduced
+dynamics from $[0,320]$ is indistinguishable from the one from
+$[300,1000]$, which implies that in practice, one only have to
+simulation relatively short non-equilibrium trajectories (that are
+almost relaxed), and compute the generator from it to build the reduced dynamics. \redc{This saves a great
+amount of computational resources comparing with calculating the
+reduced dynamics only from steady state trajectories.}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{fig/t040/fig-cg-prob-range.eps}  
+  \caption{The time-dependent probability of conformation
+    $\confc$. The brute force MD simulation is compared with reduced
+    dynamics, the transition matrix of which are calculated from
+    different ranges. The red shadow region is the statistical uncertainty of the brute force MD simulation.
+    The inserts show the zoom-ined probability at the relaxation stage $[0,120 ]~\textrm{ps}$ and at the steady state $[800,880 ]~\textrm{ps}$.}
+  \label{fig:tmp2}
+\end{figure}
+
+\subsection{The choice of lag time $\tau$}
+Table~\ref{tab:tmp1} shows a clear trend of worse accuracy with
+increased $\tau$, however, the timescales are not very sensitive to
+the choice of lag time $\tau$.
 
@@
 
+\section{Numerical results}
+\subsection{Steady state distribution}
+\begin{figure}
+  \centering  
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-dist.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-dist-msm.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-1.eps}
+  \caption{The steady state distribution calculated by brute force non-equilibrium comparing with MSM.}
+  \label{fig:num-1}
+\end{figure}
+\begin{figure}
+  \centering  
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-2-simple.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-3-simple.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-4-simple.eps}
+  \caption{The steady state distribution calculated by brute force non-equilibrium comparing with MSM.}
+  \label{fig:num-2}
+\end{figure}
+
+\subsection{Committors}
+\begin{figure}
+  \centering
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-1.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-1.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-1.eps}
+  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}  
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-2.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-2.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-2.eps}
+  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}  
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-3.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-3.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-3.eps}
+  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}  
+  \label{fig:num-2}
+\end{figure}
+
 \section{Reversibility of the original dynamics}
@@
 \end{align}
-where $V$ is the time-dependent and $t$-periodic potential. For simplicity we denote the force by $F(x_t,t) = -\nabla_x V(x_t, t)$. $dw_t$ is
-the standard Wiener process.  Assuming a discretization of the
+where $V$ is the time-dependent and $T$-periodic potential. For simplicity we denote the force by $F(x_t,t) = -\nabla_x V(x_t, t)$. $dw_t$ is
+the standard Wiener process.
+According to Girsanov, we have
+\begin{align}
+  \label{eq:tmp8}
+  \frac{dp[x_t]}{dw[x_t]}  =
+  \exp \bigg\{
+  \frac 1{\sigma^2}\int_0^T F(x_t,t) dx_t -
+  \frac1{2\sigma^2}\int_0^T F^2(x_t,t) dt
+  \bigg\}
+\end{align}
+where $dp$ is the probability measure of trajectory $x_t$, while $dw$ is the
+probability measure of the standard Wiener process $dx_t = \sigma dw_t$.
+Assuming a discretization of the
 stochastic process at time $0 < t_1 < t_2 < \cdots < t_N = T$, where
-$t_i = iT / N$. We denote $x_i = x_{t_i}$, and $w_i = w_{t_i}$, then we have the
-conditional probability:
-\begin{align}\nonumber
-  p(x_T,T\vert x_0,0) =\lim_{N\rightarrow\infty} &\,
-  \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx_1\cdots\int dx_{N-1}\\\nonumber
-  &\,
-  \exp\bigg\{\frac1\sigma\sum_{i=0}^{N-1} F(x_i,t_i)(w_{i+1} - w_{i}) - \frac1{2\sigma^2}\sum_{i=0}^{N-1}F^2(x_i,t_i)\dt\bigg\} \times\\\label{eqn:tmp8}
-  &\,
-  \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=0}^{N-1} \frac{(x_{i+1} - x_i)^2}{\dt}\bigg\}.
-\end{align}
-Notice that
-\begin{align}\label{eqn:tmp10}
-  \sigma(w_{i+1} - w_{i}) =
-  &\,
-  x_{i+1} - x_i 
-\end{align}
-we have
-% so with the formal identity $(dw_t)^2 = dt$,  we have
-\begin{align}\nonumber
-  p(x_T,T\vert x_0,0)
-  =\lim_{N\rightarrow\infty} &\,
-  \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx_1\cdots\int dx_{N-1}\\\nonumber
-  &\,
-  \exp\bigg\{\frac1{\sigma^2}\sum_{i=0}^{N-1} F(x_{i},t_{i})(x_{i+1} - x_i) -\frac1{2\sigma^2}\sum_{i=0}^{N-1}F^2(x_i,t_i)\dt\bigg\} \times\\\label{eqn:tmp10}
-  &\,
-  \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=0}^{N-1} \frac{(x_{i+1} - x_i)^2}{\dt}\bigg\}.
+$t_i = iT / N$. We denote $x_i = x_{t_i}$, and $w_i = w_{t_i}$, then we have,
+in the sense of Ito,
+\begin{align}\label{eq:tmp9}
+  \frac{dp[x_t]}{dw[x_t]}  \approx
+  \exp\bigg\{\frac1{\sigma^2}\sum_{i=0}^{N-1} F(x_{i},t_{i})(x_{i+1} - x_i) -\frac1{2\sigma^2}\sum_{i=0}^{N-1}F^2(x_i,t_i)\dt\bigg\} 
 \end{align}
 Now, consider a conjugate trajectory $x^\dagger_t = x_{T-t}$ that starts at $x_T$, ends at $x_0$. The conjugate dynamics is driven by  $F^\dagger(x^\dagger_t,t) = F(x^\dagger_t, T-t)$.
-Since we have the symmetry $F(x_t, -t) = -F(x_t, t)$, the conjugate dynamics also satisfies Eq.~\eqref{eqn:tmp7}.
-Therefore, we have the probability:
-\begin{align}\nonumber
-  p(x_0,T\vert x_T,0) = &\,
-  p^\dagger(x^\dagger_T,T\vert x^\dagger_0,0)  \\\nonumber
-  = &\,
-  \lim_{N\rightarrow\infty}
-  \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx^\dagger_1\cdots\int dx^\dagger_{N-1}\\\nonumber
-  &\,
-  \exp\bigg\{\frac1{\sigma^2}\sum_{i=0}^{N-1} F^\dagger(x^\dagger_{i},t_{i})(x^\dagger_{i+1} - x^\dagger_i) -\frac1{2\sigma^2}\sum_{i=0}^{N-1}[F^\dagger(x^\dagger_i,t_i)]^2\dt\bigg\} \times\\\nonumber
-  &\,
-  \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=0}^{N-1} \frac{(x^\dagger_{i+1} - x^\dagger_i)^2}{\dt}\bigg\} \\\nonumber
-  =&\,
-  \lim_{N\rightarrow\infty} 
-  \frac{1}{(2\pi\sigma^2\dt)^{(N-1)/2}} \int dx_1\cdots\int dx_{N-1}\\\nonumber
-  &\,
-  \exp\bigg\{\frac1{\sigma^2}\sum_{i=N}^{1} F(x_{i},t_{i})(x_{i-1} - x_i) -\frac1{2\sigma^2}\sum_{i=N}^{1}F^2(x_i,t_i)\dt\bigg\} \times\\\label{eqn:tmp11}
-  &\,
-  \exp\bigg\{- \frac1{2\sigma^2} \sum_{i=N}^{1} \frac{(x_{i-1} - x_i)^2}{\dt}\bigg\}.
+Writting the Girsanov for the conjugate dynamics
+\begin{align}\label{eq:dagger-0}
+  \frac{dp^\dagger[x^\dagger_t]}{dw[x^\dagger_t]}  
+  \approx\,&
+  \exp\bigg\{
+  \frac1{\sigma^2}\sum_{i=0}^{N-1} F^\dagger(x^\dagger_{i},t_{i})(x^\dagger_{i+1} - x^\dagger_i) -
+  \frac1{2\sigma^2}\sum_{i=0}^{N-1}[F^\dagger(x^\dagger_i,t_i)]^2\dt\bigg\} \\ \nonumber
+  =\,&
+  \exp\bigg\{
+  \frac1{\sigma^2}\sum_{i=0}^{N-1} F(x^\dagger_{i},T - t_{i})(x^\dagger_{i+1} - x^\dagger_i) -
+  \frac1{2\sigma^2}\sum_{i=0}^{N-1}[F(x^\dagger_i, T-t_i)]^2\dt\bigg\} \\\nonumber
+  =\,&
+  \exp\bigg\{
+  \frac1{\sigma^2}\sum_{i=0}^{N-1} F(x_{N-i},t_{N-i})(x_{N-i-1} - x_{N-i}) -
+  \frac1{2\sigma^2}\sum_{i=0}^{N-1}[F(x_{N-i},t_{N-i})]^2\dt\bigg\} \\
+  = \,&
+  \exp\bigg\{
+  \frac1{\sigma^2}\sum_{i=N}^{1} F(x_{i},t_{i})(x_{i-1} - x_i) -
+  \frac1{2\sigma^2}\sum_{i=N}^{1}F^2(x_i,t_i)\dt\bigg\}
+\end{align}
+% Therefore,
+% \begin{align}\nonumber
+%   \frac{dp[x^\dagger_t]}{dw[x^\dagger_t]}  =
+%   \,&
+%   \frac{dp^\dagger[x^\dagger_t]}{dw[x^\dagger_t]} \\\nonumber
+%   \approx\,&
+%   \exp\bigg\{
+%   \frac1{\sigma^2}\sum_{i=0}^{N-1} F^\dagger(x^\dagger_{i},t_{i})(x^\dagger_{i+1} - x^\dagger_i) -
+%   \frac1{2\sigma^2}\sum_{i=0}^{N-1}[F^\dagger(x^\dagger_i,t_i)]^2\dt\bigg\} \\\nonumber
+% \end{align}
+Since it is obvious that $dw[x^\dagger_t] / dw[x_t] = 1$,
+\begin{align}
+  \label{eq:tmp10}
+  \frac{dp^\dagger[x^\dagger_t]}{dw[x_t]}
+  \approx \,&
+  \exp\bigg\{
+  \frac1{\sigma^2}\sum_{i=1}^{N} F(x_{i},t_{i})(x_{i-1} - x_i) -
+  \frac1{2\sigma^2}\sum_{i=1}^{N}F^2(x_i,t_i)\dt\bigg\}
 \end{align}
@@
 \begin{align}\label{eqn:tmp12}
-  \log\bigg\{\frac{  p[x_t] }{ p[x^\dagger_t]} \bigg\}
-  =&\,
-  \frac1{\sigma^2}\sum_{i=1}^{N-1} F(x_i,t_i)(x_{i+1} - x_{i}) + F(x_i,t_i)(x_{i} - x_{i-1}) 
+  \frac{  dp^\dagger[x^\dagger_t] }{ dp[x_t]}
+  \approx&\,
+  \exp\bigg\{
+  -\frac1{\sigma^2}\sum_{i=1}^{N-1}
+  \bigg[
+  F(x_i,t_i)(x_{i+1} - x_{i}) + F(x_i,t_i)(x_{i} - x_{i-1})
+  \bigg]
+  \bigg\}
 \end{align}
-Now consider the differentiation:
+Assuming the smoothness of the external perturbation, consider the differentiation:
 \begin{align}\nonumber
@@
 \end{align}
+The second order expansion w.r.t.~$x_i - x_{i-1}$ is of order $\dt$, so it is absorbed into $ \mo(\dt)$.
 Then the \eqref{eqn:tmp12} becomes
 \begin{align}\label{eqn:tmp14}
-  \log\bigg\{\frac{  p[x_t] }{ p[x^\dagger_t]} \bigg\}
-  =&\,
-  \frac2{\sigma^2}\sum_{i=0}^{N-1} F(x_i,t_i)(x_{i+1} - x_{i}) +
-  \frac1{\sigma^2}\sum_{i=0}^{N-1}\nabla_xF(x_i,t_i)(x_{i+1} - x_{i})^2
+  \frac{  dp^\dagger[x^\dagger_t] }{ dp[x_t]}
+  \approx&\,
+  \exp\bigg\{
+ -\frac2{\sigma^2}\sum_{i=0}^{N-1} F(x_i,t_i)(x_{i+1} - x_{i}) 
+ -\frac1{\sigma^2}\sum_{i=0}^{N-1}\nabla_xF(x_i,t_i)(x_{i+1} - x_{i})^2
+ \bigg\}
 \end{align}
+Using the identity
+$  dt = (dw_t)^2 = {\sigma^{-2}} dx_t^2$,
+Eq.~\eqref{eqn:tmp14} is written in the integral form
+\begin{align}\label{eqn:tmp14-0}
+  \frac{  dp^\dagger[x^\dagger_t] }{ dp[x_t]}
+  \approx&\,
+  \exp\bigg\{
+ -\frac2{\sigma^2}\int_0^T F(x_t,t) dx_t
+ -\int_0^T\nabla_xF(x_t,t)dt
+ \bigg\}  
+\end{align}
+One would not have the second integral on the exponent if the first integral of the exponent were defined in the sense of Stratonovich.
+
 We notice that
@@
 \end{align}
-and the identity
+Eq.~\eqref{eqn:tmp14-0} becomes
 \begin{align}
-  dt = (dw_t)^2 = \frac1{\sigma^2} dx_t^2
+  \frac{  dp^\dagger[x^\dagger_t] }{ dp[x_t]}
+  =&\,
+  \exp\bigg\{
+  \frac2{\sigma^2}\bigg[
+  V(x_T,T) - V(x_0,t_0) - \int_0^T\partial_tV(x_t,t)dt
+  \bigg]
+  \bigg\}
 \end{align}
-Eq.~\eqref{eqn:tmp14} becomes
+According to the  Einstein relation, the temperature $\mathcal T = \sigma^2/2$, we denote $\beta = 1/{\mathcal T} = 2/\sigma^2$.
+Take the limit of infinite small time interval, and notice the equilibrium
+invariant probability density with respect to potential $V(x,0)$ satisfies $\mu(x) \propto e^{-\beta V(x,0)}$,
 \begin{align}
-  \log\bigg\{\frac{  p[x_t] }{ p[x^\dagger_t]} \bigg\}
+  \frac{  dp^\dagger[x^\dagger_t] }{ dp[x_t]}
   =&\,
-  -\frac2{\sigma^2}\bigg[
-  V(x_N,t_N) - V(x_0,t_0) + \sum_{i=0}^{N-1}\partial_tV(x_i,t_i)\dt
-  \bigg]
+  \frac{\mu(x_0)}{\mu(x_T)}\times
+  \exp\bigg\{
+  - \beta\int_0^T\partial_tV(x_t,t)dt
+  \bigg\}
 \end{align}
-According to the  Einstein relation $T = \sigma^2/2$, by denoting $\beta = 1/T$
+
+In Eq.~\eqref{eq:dagger-0}, we assume the periodicity of the perturbation $F(x,t) = F(x,t+T)$, and the symmetry of the external perturbation, i.e.~$F(x, -t) = F(x, t)$, we have
 \begin{align}
-  \log\bigg\{\frac{  p[x_t] }{ p[x^\dagger_t]} \bigg\}
-  =&\,
-  -\beta\bigg[
-  V(x_N,t_N) - V(x_0,t_0) + \sum_{i=0}^{N-1}\partial_tV(x_i,t_i)\dt
-  \bigg]  
+  \frac{dp^\dagger[x^\dagger_t]}{dw[x^\dagger_t]}  
+  \approx\,&
+  \exp\bigg\{
+  \frac1{\sigma^2}\sum_{i=0}^{N-1} F(x^\dagger_{i},t_{i})(x^\dagger_{i+1} - x^\dagger_i) -
+  \frac1{2\sigma^2}\sum_{i=0}^{N-1}[F(x^\dagger_i, t_i)]^2\dt\bigg\}  
 \end{align}
+By changing notation $x^\dagger$ back to $x$, and comparing with~\eqref{eq:tmp9}, the reversed dynamics is subject to the Eq.~\eqref{eqn:tmp7},
+i.e.~$dp^\dagger = dp$.
 Therefore
@@
   p(x_0,T\vert x_T,0)
+  =&\,\int_{\mc\{x_T,0;x_0,T\}}
+  dp[x^\dagger_t] \\\nonumber  
+  =&\,
+  \int_{\mc\{x_0,0;x_T,T\}}
+  \frac{  dp[x^\dagger_t] }{ dp[x_t]} \cdot dp[x_t] \\\nonumber
   =&\,
@@
   \int_{\mc\{x_0,0;x_T,T\}}
-  \frac{  p[x^\dagger_t] }{ p[x_t]} \cdot p[x_t] \\\label{eqn:tmp19}
+  \frac{  dp^\dagger[x^\dagger_t] }{ dp[x_t]} \cdot dp[x_t] \\\label{eqn:tmp18}
   = &\,
-  \frac{e^{-\beta V(x_0,t_0)}}{e^{-\beta V(x_N,t_N)}}
+  \frac{\mu(x_0)}{\mu(x_T)}
   \int_{\mc\{x_0,0;x_T,T\}}
   \exp\bigg\{
-  \beta\int_0^T \partial_t V(x_t,t)dt 
-  \bigg\} \cdot p[x_t]
+  -\beta\int_0^T \partial_t V(x_t,t)dt 
+  \bigg\} \cdot dp[x_t]
 \end{align}
@@
 \begin{align}
-  W[x_t] = - \int_0^T \partial_t V(x_t,t)dt
+  W[x_t] = \int_0^T \partial_t V(x_t,t)dt
 \end{align}
@@
 the dynamics $x_t$ starting at $x_0$ and ending at $x_T$ (see e.g.~Ref.~\cite{seifert2012stochastic}).
-Therefore Eq.~\eqref{eqn:tmp19} is the detailed Jarzynski relation.
-Now the problem becomes if we can write a nice form (e.g.~the difference of a state function measured at $x_T$ and $x_0$) for the non-equilibrium work.
+Therefore Eq.~\eqref{eqn:tmp18} is the detailed Jarzynski relation.
+% Now the problem becomes if we can write a nice form (e.g.~the difference of a state function measured at $x_T$ and $x_0$) for the non-equilibrium work.
+Noticing that
+\begin{align}
+  \label{eq:tmp21}
+  p(x_T,T\vert x_0,0) = \int_{\mc\{x_0,0;x_T,T\}}dp[x_t],
+\end{align}
+From Eq.~\eqref{eqn:tmp18} we have
+\begin{align}
+  \label{eq:tmp22}
+  \frac{p(x_0,T\vert x_T,0)}{  p(x_T,T\vert x_0,0)  }
+  =
+  \frac{\mu(x_0)}{\mu(x_T)}
+  \mathbb E_{x_0\rightarrow x_T} [e^{-\beta W}]
+\end{align}
+% Maybe we want a more symmetric form.
+% The expectation value of the reversed dynamics reads,
+% \begin{align}\nonumber
+%   \mathbb E_{x^\dagger_0\rightarrow x^\dagger_T} [e^{-\beta W^\dagger}]
+%   =\,&
+%   \int_{\mc\{x^\dagger_0,0;x^\dagger_T,T\}}
+%   \exp\bigg\{
+%   -\beta\int_0^T \partial_t V(x^\dagger_t,t)dt 
+%   \bigg\} \cdot dp[x^\dagger_t]   \\\nonumber
+%   =\,&
+%   \int_{\mc\{x_0,0;x_T,T\}}
+%   \exp\bigg\{
+%   -\beta\int_0^T \partial_t V(x_{T-t},t)dt 
+%   -\beta\int_0^T \partial_t V(x_{t},t)dt 
+%   \bigg\}
+%   \cdot dp[x_t]   \\  \nonumber
+%   =\,&
+%   \int_{\mc\{x_T,0;x_0,T\}}
+%   \exp\bigg\{
+%   \beta\int_0^T \partial_t V(x_t,t)dt 
+%   \bigg\} \cdot dp[x_t]   \\
+%   \label{eq:tmp23}
+%   = \,&
+%   \mathbb E_{x_0\rightarrow x_T} [e^{- 2\beta W}]  
+% \end{align}
+% Noticing that \eqref{eq:tmp22}  is true for the reversed dynamics, we have
+% \begin{align}
+%   \label{eq:24}
+%   \frac{p(x_T,T\vert x_0,0)}{  p(x_0,T\vert x_T,0)  }
+%   =
+%   \frac{\mu(x_T)}{\mu(x_0)}
+%   \mathbb E_{x_T\rightarrow x_0} [e^{\beta W}]  
+% \end{align}
 

### 2014-08-15 alanine.nanma/template/tools/scripts/msm.floquet.eig.m
normalize the first eigen vector

@@ -2,6 +2,9 @@ fm = load('floque.B.out');
 fm = fm';
 [v e] = eig(fm);
 ee = sum(e)';
+vv1 = v(:,1);
+vv1 = vv1 / sum(vv1);
 vv =v(:,1:5);
+vv(:,1) = vv1;
 save ('floquet.eigvalue.out', 'ee');
 save ('floquet.eigvector.out', 'vv');

### 2014-08-22 writedown/period.noneq.msm/main.tex
backup

@@
-\documentclass[aps, pre, preprint,unsortedaddress,a4paper,onecolumn]{revtex4-1}
+\documentclass[aps, pre, preprint,unsortedaddress,a4paper,onecolumn]{revtex4}
+% \documentclass[aps, pre, preprint,unsortedaddress,a4paper,twocolumn]{revtex4}
 % \documentclass[acs, jctcce, a4paper,preprint,unsortedaddress,onecolumn]{revtex4-1}
@@
 \newcommand{\dd}[1]{\textsf{#1}}
-\newcommand{\fwd}[0]{\textrm{fwd}}
-\newcommand{\bwd}[0]{\textrm{bwd}}
+\newcommand{\fwd}[0]{\textrm{fw}}
+\newcommand{\bwd}[0]{\textrm{bw}}
 \newcommand{\period}[0]{T_{\textrm{P}}}
@@
 \item Eqn.~\eqref{eqn:tmp2} assumes Markovianity, which is not
-  necessarily true for a reduce dynamics $\vect p(t)$.
+  necessarily true for a reduce dynamics $\vect p(t)$, see e.g.~\cite{prinz2011markov}.
 \item Numerical error from the finite difference introduced in
@@
 
+\subsection{Perodicity of the reduced dynamics: investigated by alanine dipeptide under oscillatory electric field}
 \begin{figure}
   \centering
-  \includegraphics[width=0.6\textwidth]{fig/confs/fig-begin-1.eps}
-  \caption{The Ramachandran plot presents the main conformations of the alanine dipeptide.}
+  \includegraphics[width=0.3\textwidth]{fig/confs/c-2.eps}
+  \caption{A schematic plot of the alanine dipeptide molecule and the dihedral angles $\phi$ and $\psi$.}
   \label{fig:tmp1}
@@
 of approximating Eqn.~\eqref{eqn:tmp1} by
-Eqn.~\eqref{eqn:tmp2}. However, it would be useful to do some
-numerical experiments. We have studied the alanine dipeptide system
-under oscillatory EF, which was studied by
-Ref.~\cite{wang2014exploring}. We use the two dihedral angles $\phi$
-and $\psi$ as slow variables. The definition of the conformations
-$\confaa$, $\confab$, $\confba$, $\confbb$ and $\confc$ are presented
-by Fig.~\ref{fig:tmp1}.  We are interested in the time-dependent
-probability of the conformations. In Fig.~\ref{fig:tmp2}, the brute
-force molecular dynamics simulation result
-(i.e.~Eqn.~\eqref{eqn:tmp1}) is compared with different discretization
-methods, which give different generator in Eqn.~\eqref{eqn:tmp2}. For
-clarity, only the probability of conformation $\confc$ is plotted.  In
-the figure, ``5 sets'' means the $\phi$-$\psi$ space is discretized by
-5 sets as shown in Fig.~\ref{fig:tmp1}, ``Uni. $M=$'' stands for the
-uniform discretization on $\phi$-$\psi$ space, and $M$ denotes the
-number of bins on both $\phi$ and $\psi$ directions.  Both $M=10$ and
-20 methods present very good accuracy.  Please notice that for $M=10$,
-for example, the number of discretized sets is $n=M^2=100$.  The
-lag-time in all cases is chosen to be $\tau = 0.5$~ps. A test with
-$\tau = 1.0$~ps shows good consistency with $\tau = 0.5$~ps.
-The generator
-$\vect M(t)$ is assumed to be periodic, and is estimated from the
-trajectories from $t=300$ to 1000~ps.
+Eqn.~\eqref{eqn:tmp2}.
+It is therefore useful to investigate the discussed approximations
+by a numerical example. The Markovianity of the reduce dynamics
+was extensively discussed in e.g.~\cite{prinz2011markov}, so we 
+will not touch this topic in the current paper. The choice of the lag-time
+will be discussed later, and in this subsection we focus on the periodicity
+of the reduced dynamics.
+Throughout this paper, we take the alanine dipeptide system
+under oscillatory EF, as an example, which was extensively studied by
+Ref.~\cite{wang2014exploring}.
+We choose the two dihedral angles $\phi$
+and $\psi$ as slow variables (see Fig.~\ref{fig:tmp1}), and the discretization
+is a uniform division of the $\phi$--$\psi$ plane. We denote the number of
+division on each dihedral by $K$.
 
-The phenomena presented by Fig.~\ref{fig:tmp2} is very similar to the
-equilibrium MSM: the quality of the MSM depends on how accurate the
-eigenfunctions are approximated by the discretization. The ``5 sets''
-method achieve better accuracy than the uniform $M=5$ method by using
-much less DOFs, because it captures the positive and negative signs of
-the eigenfunctions. With larger $M$ the discretization error of the
-eigenfunctions becomes smaller, so the accuracy of the MSM is improved.
+The alanine dipeptide was put into the local thermostating
+environment, and was driven by a periodic electric field with period
+$T = 10$~ps. The 20,000 branching trajectories started from 20,000
+initial configurations that samples the equilibrium distribution.
+\redc{Write a lot of details on non-equilibrium MD.}  The branching
+trajectories were each 1000~ps long, and the system reaches
+non-equilibrium steady state in roughly 300~ps. We compute the
+generator from non-equilibrium trajectories in time interval $[t_1,
+t_2]$. If the reduced dynamics were periodic, then generator $\vect
+M(t)$ would not depends on the choice of the time interval. We compute
+the reduced generator by two discretizations $K=2$ and $K=20$, and two
+choices of time intervals $[0, 40]$ and $[320, 1000]$, and then
+compare the results with the brute force result in
+Fig.~\ref{fig:tmp2}. In the figure, we show the time-dependent
+probability $\mathbb P\big(\phi\in[0,180), \psi\in [0,180)\big)$.
+Using $K=2$ the dynamics depends on the time interval used for
+calculating the generator: using time intervals $[0, 40]$ the reduced
+dynamics can only reproduces the brute force result in $[0, 40]$,
+while using time intervals $[0, 40]$ the reduced dynamics can only
+reproduces the brute force result after 300~ps.  This shows that the
+reduced dynamics is lack of periodicity.  The reason is that the
+discretization is too coarse so that the dynamics cannot be fully
+equilibriated within the lag-time $\tau$ in each discretized set.  For
+$K=20$, the reduced dynamics does not depend on the time interval of
+calculating the generator, and is consistent with the brute force
+non-equilibrium simulation within the error bar. Therefore, the $K=20$
+is a reliable discretization for the alanine dipeptide system.
 
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{fig/t040/fig-cg-prob.eps}  
-  \caption{The time-dependent probability of conformation
-    $\confc$. The brute force MD simulation is compared with different
-    discretization methods.}
+  \includegraphics[width=0.4\textwidth]{fig/t010/discrete/fig-cg-prob.eps}  
+  \caption{The time-dependent probability $\mathbb
+    P\big(\phi\in[0,180), \psi\in [0,180)\big)$.  The brute force
+    non-equilibrium MD simulation is compared with different
+    discretization methods. The red shadow region indicates the
+    statsitical uncertainty of the brute force simulation.}
   \label{fig:tmp2}
@@
 
+\subsection{The choice of lag-time $\tau$}
+
+As discussed before, the lag-time should be chosen a value that lies
+in the spectrum gap of the original dynamics, so that it resolves the
+slow dynamics, and at the same time relaxes the fast dynamics. In
+practice, it is very difficult to estimate the lag-time in
+priori. Therefore, we discretize the original non-equilibrium based on
+different choices of $\tau$ (0.5, 1.0, 2.0 and 5.0~ps) and compare the
+time dependent probability of $\mathbb P\big(\phi\in[0,180), \psi\in
+[0,180)\big)$ estimated out of the reduced dynamics in
+Fig.~\ref{fig:tmp3}.  All cases use idential discretization: $K=20$.
+It is clear that when lag-time is close to the period (10~ps), the
+reduced dynamics cannot resolve the probability change within a
+period. However, the large lag-times are able to capture the
+the overall log time behavior of the probability.
+We observe no significant difference between $\tau=0.5$ and
+$\tau=1.0$~ps, which means the reduced dynamics is not very sensitive
+to the choice of $\tau$.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.4\textwidth]{fig/t010/discrete/fig-cg-prob-tau.eps}  
+  \caption{The time-dependent probability $\mathbb
+    P\big(\phi\in[0,180), \psi\in [0,180)\big)$.  The brute force
+    non-equilibrium MD simulation is compared with different
+    discretization methods. The red shadow region indicates the
+    statsitical uncertainty of the brute force simulation.}
+  \label{fig:tmp3}
+\end{figure}
+
+% The definition of the conformations
+% $\confaa$, $\confab$, $\confba$, $\confbb$ and $\confc$ are presented
+% by Fig.~\ref{fig:tmp1}.  We are interested in the time-dependent
+% probability of the conformations. In Fig.~\ref{fig:tmp2}, the brute
+% force molecular dynamics simulation result
+% (i.e.~Eqn.~\eqref{eqn:tmp1}) is compared with different discretization
+% methods, which give different generator in Eqn.~\eqref{eqn:tmp2}. For
+% clarity, only the probability of conformation $\confc$ is plotted.  In
+% the figure, ``5 sets'' means the $\phi$-$\psi$ space is discretized by
+% 5 sets as shown in Fig.~\ref{fig:tmp1}, ``Uni. $M=$'' stands for the
+% uniform discretization on $\phi$-$\psi$ space, and $M$ denotes the
+% number of bins on both $\phi$ and $\psi$ directions.  Both $M=10$ and
+% 20 methods present very good accuracy.  Please notice that for $M=10$,
+% for example, the number of discretized sets is $n=M^2=100$.  The
+% lag-time in all cases is chosen to be $\tau = 0.5$~ps. A test with
+% $\tau = 1.0$~ps shows good consistency with $\tau = 0.5$~ps.
+% The generator
+% $\vect M(t)$ is assumed to be periodic, and is estimated from the
+% trajectories from $t=300$ to 1000~ps.
+
+% The phenomena presented by Fig.~\ref{fig:tmp2} is very similar to the
+% equilibrium MSM: the quality of the MSM depends on how accurate the
+% eigenfunctions are approximated by the discretization. The ``5 sets''
+% method achieve better accuracy than the uniform $M=5$ method by using
+% much less DOFs, because it captures the positive and negative signs of
+% the eigenfunctions. With larger $M$ the discretization error of the
+% eigenfunctions becomes smaller, so the accuracy of the MSM is improved.
+
 \section{Floquet theory}
 
-The Floquet theory states that for a periodic system
-Eqn.~\ref{eqn:tmp2}, the solution can be written as
+The reduced dynamics will not provide a lot further interesting
+information until we introduce the MSM to analyze the reduced dynamics. The main
+difficulty is that the reduced dynamics is time-inhomogeneous, however, this can
+be overcome by the Floquet theory.
+The Floquet theory states that for a periodic system, e.g.~Eq.~\eqref{eqn:tmp2}, the solution can be written as
 \begin{align}
@@
 $e^{T\vect B}$ is estimated by evolving the fundamental solutions by
-one period.  Calculating the eigenvalues of $e^{T\vect B}$ reveals the
+one period.
+Since it is obvious that $Q(kT) = Q(0) = I,\ k\in\mathbb N$, if we only consider the state of the system
+at time $kT$, then from Eq.~\eqref{eqn:tmp5} we have
+\begin{align}
+  \label{eqn:tmp5a}
+  \vect p(kT)  = \boldsymbol\Phi^k(T) \,\vect p(0),
+\end{align}
+which is a time-homogeneous Markov process with transition matrix $\boldsymbol\Phi(T)$.
+Please notice that in general this Markov process is not reversible.
+Calculating the eigenvalues of $\boldsymbol\Phi(T)$ reveals the
 implied timescales on which the non-equilibrium dynamics converges to
-the periodic steady state. However, it can only resolve the processes that are longer than the period $T$.
-The largest non-trivial timescales is given in table
-Tab.~\ref{tab:tmp1}, which corresponds very well to the dynamics of the  $\confc$ probability.
+the periodic steady state.
+The Eq.~\eqref{eqn:tmp5a} allows one to use the available techniques for time-homogeneous
+Markov jump process (especially for irreversible processes)
+to analyze the time-inhomogeneous dynamics Eq.~\eqref{eqn:tmp2}.
+However, it can only resolve the processes that are longer than the period $T$.
+Therefore, rather than going directly from Eq.~\eqref{eqn:tmp1} to Eq.~\eqref{eqn:tmp5a},
+we would like to keep the intermediate step Eq.~\eqref{eqn:tmp2}.
+In the following we compare the MSM with the brute force non-equilibrium simulation
+by considering several properties that are of special interest.
 
-\begin{table}
+% The largest non-trivial timescales is given in table
+% Tab.~\ref{tab:tmp1}, which corresponds very well to the dynamics of the  $\confc$ probability.
+% \begin{table}
+%   \centering
+%   \caption{The first four non-trivial timescales calculated from ${\vect B}$. The unit of time in the table is ps.
+%     $\tau$ is the lag time used to calculate the generator~\eqref{eqn:tmp4}. $[T_0,T_1]$ is the time interval,
+%     in which the generator is estimated from the MD trajectories. The 5th eigenvalue of uniform decomposition with $\tau=8.0$~ps is not real, so
+%     the corresponding timescale is not calculated.
+%   }
+%   \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}c ccc rrrr}\hline\hline
+%     Method  &  $M$ & $\tau$ & $[T_0,T_1]$ &   $t_2$ &   $t_3$ &   $t_4$ &   $t_5$  \\\hline
+%     5 sets  & --   & 0.5    & $[300,1000]$    &  72.4 & 17.8 &  2.1 & 2.8    \\
+%     Uniform & $05$ & 0.5    & $[300,1000]$    &  53.6 & 17.4 &  9.4 & 2.8    \\
+%     Uniform & $10$ & 0.5    & $[300,1000]$    & 107.2 & 27.0 & 16.4 & 3.6    \\
+%     Uniform & $20$ & 0.5    & $[300,1000]$    & 118.6 & 30.4 & 20.3 & 4.3    \\
+%     Uniform & $30$ & 0.5    & $[300,1000]$    & 120.6 & 31.1 & 20.9 & 4.4    \\\hline
+%     Uniform & $20$ & 0.5    & $[0,40]$    & 156.5 & 34.4 & 20.7 & 4.4    \\
+%     Uniform & $20$ & 0.5    & $[0,80]$    & 133.8 & 32.8 & 20.4 & 4.4    \\
+%     Uniform & $20$ & 0.5    & $[0,120]$   & 127.5 & 32.0 & 20.3 & 4.3    \\
+%     Uniform & $20$ & 0.5    & $[0,200]$   & 122.0 & 31.3 & 20.3 & 4.3    \\
+%     Uniform & $20$ & 0.5    & $[0,320]$   & 120.4 & 31.0 & 20.3 & 4.3    \\\hline
+%     Uniform & $20$ & 1.0    & $[300,1000]$    & 119.8 & 30.5 & 21.7 & 4.9   \\
+%     Uniform & $20$ & 2.0    & $[300,1000]$    & 117.8 & 29.2 & 21.5 & 5.3   \\
+%     Uniform & $20$ & 4.0    & $[300,1000]$    & 114.2 & 27.0 & 20.2 & 4.8   \\
+%     Uniform & $20$ & 8.0    & $[300,1000]$    & 110.6 & 25.0 & 18.1 & --   \\
+%     \hline\hline
+%   \end{tabular*}
+%   \label{tab:tmp1}
+% \end{table}
+
+% \section{Numerical investigation of the accuracy of the MSM}
+
+% At this stage we do have any analytical result regarding the quality
+% of approximating Eqn.~\eqref{eqn:tmp1} by
+% Eqn.~\eqref{eqn:tmp2}. However, it would be useful to do some
+% numerical experiments. We have studied the alanine dipeptide system
+% under oscillatory EF, which was studied by
+% Ref.~\cite{wang2014exploring}. We use the two dihedral angles $\phi$
+% and $\psi$ as slow variables. The discretization is the uniform division of
+% the $\phi$--$\psi$ plan in to 2-dimentional bins. 
+% The quality of the MSM~\eqref{eqn:tmp5a} can be checked by comparing the physical properties
+% computed from the MSM and those computed by the brute force non-equilibrium molecular
+% dynamics simulation from Ref.~\cite{wang2014exploring}.
+
+\subsection{Core set identification}
+
+\redc{Write how to detact the core sets for irreversible Markovian process}.
+
+The coresets are denoted by $C_{R_\alpha}$, $C_\beta$ and $C_{L_\alpha}$, which correspond to
+right-handed alpha-helix, beta-sheet and left-handed alpha-helix, respectively.
+
+\subsection{Steady state distribution and eigenfunctions}
+We investigate the steady state properties distribution at time $kT$. To make it comparible to
+the free energy in equilibrium case, we take the logrithm of the properties, i.e.
+\begin{align}
+  \label{eq:num-tmp1}
+  F_{\textrm{st}}(\phi,\psi) = \lim_{k\rightarrow\infty} -k_B\mathcal T \log p(\phi,\psi,kT),
+\end{align}
+where $k_B$ is the Boltzmann constant and $\mathcal T$ is the temperature of the system.
+The result is given in Fig.~\ref{fig:num-1}. A good consistency between the brute force
+MD simulation and the MSM is observed.
+
+\begin{figure}
   \centering  
-  \caption{The first four non-trivial timescales calculated from $e^{T\vect B}$. The unit of time in the table is ps.
-    $\tau$ is the lag time used to calculate the generator~\eqref{eqn:tmp4}. $[T_0,T_1]$ is the time interval,
-    in which the generator is estimated from the MD trajectories. The 5th eigenvalue of uniform decomposition with $\tau=8.0$~ps is not real, so
-    the corresponding timescale is not calculated.
-  }
-  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}c ccc rrrr}\hline\hline
-    Method  &  $M$ & $\tau$ & $[T_0,T_1]$ &   $t_2$ &   $t_3$ &   $t_4$ &   $t_5$  \\\hline
-    5 sets  & --   & 0.5    & $[300,1000]$    &  72.4 & 17.8 &  2.1 & 2.8    \\
-    Uniform & $05$ & 0.5    & $[300,1000]$    &  53.6 & 17.4 &  9.4 & 2.8    \\
-    Uniform & $10$ & 0.5    & $[300,1000]$    & 107.2 & 27.0 & 16.4 & 3.6    \\
-    Uniform & $20$ & 0.5    & $[300,1000]$    & 118.6 & 30.4 & 20.3 & 4.3    \\
-    Uniform & $30$ & 0.5    & $[300,1000]$    & 120.6 & 31.1 & 20.9 & 4.4    \\\hline
-    Uniform & $20$ & 0.5    & $[0,40]$    & 156.5 & 34.4 & 20.7 & 4.4    \\
-    Uniform & $20$ & 0.5    & $[0,80]$    & 133.8 & 32.8 & 20.4 & 4.4    \\
-    Uniform & $20$ & 0.5    & $[0,120]$   & 127.5 & 32.0 & 20.3 & 4.3    \\
-    Uniform & $20$ & 0.5    & $[0,200]$   & 122.0 & 31.3 & 20.3 & 4.3    \\
-    Uniform & $20$ & 0.5    & $[0,320]$   & 120.4 & 31.0 & 20.3 & 4.3    \\\hline
-    Uniform & $20$ & 1.0    & $[300,1000]$    & 119.8 & 30.5 & 21.7 & 4.9   \\
-    Uniform & $20$ & 2.0    & $[300,1000]$    & 117.8 & 29.2 & 21.5 & 5.3   \\
-    Uniform & $20$ & 4.0    & $[300,1000]$    & 114.2 & 27.0 & 20.2 & 4.8   \\
-    Uniform & $20$ & 8.0    & $[300,1000]$    & 110.6 & 25.0 & 18.1 & --   \\
-    \hline\hline
-  \end{tabular*}
-  \label{tab:tmp1}
-\end{table}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-dist.eps}
+  % \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-dist-msm.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-1.eps}
+  \caption{The steady state distribution calculated by brute force non-equilibrium comparing with MSM.}
+  \label{fig:num-1}
+\end{figure}
+
+% \begin{figure}
+%   \centering  
+%   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-2-simple.eps}
+%   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-3-simple.eps}
+%   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-4-simple.eps}
+%   \caption{The first three non-trivial eigenfunctions cdalculated by the MSM.}
+%   \label{fig:num-2}
+% \end{figure}
+
+\subsection{Committors}
+
+The forward committor $q^\fwd_i(\phi,\psi)$ of a coreset $C_i,\ i\in\{R_\alpha, \beta, L_\alpha\}$ is defined as
+the probability of visiting coreset $C_i$ next conditioned on being at configuration $(\phi,\psi)$.
+The backward committor $q^\bwd_i(\phi,\psi)$ of a coreset $C_i,\ i\in\{R_\alpha, \beta, L_\alpha\}$ is defined as
+the probability of last coming from $C_i$  conditioned on being at configuration $(\phi,\psi)$.
+For  reversible Markov processes, the forward and backward committors are identical, however, it is in general not the case
+for irreversible processes. Please see Fig.~\ref{fig:num-3}--\ref{fig:num-5} for the committors.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-1.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-1.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-1.eps}
+  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}
+  \label{fig:num-3}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-2.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-2.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-2.eps}
+  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}  
+  \label{fig:num-4}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-3.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-3.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-3.eps}
+  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}  
+  \label{fig:num-5}
+\end{figure}
 
@@
 \end{itemize}
-
-\section{Numerical results}
-\subsection{Steady state distribution}
-\begin{figure}
-  \centering  
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-dist.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-dist-msm.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-1.eps}
-  \caption{The steady state distribution calculated by brute force non-equilibrium comparing with MSM.}
-  \label{fig:num-1}
-\end{figure}
-\begin{figure}
-  \centering  
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-2-simple.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-3-simple.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-4-simple.eps}
-  \caption{The steady state distribution calculated by brute force non-equilibrium comparing with MSM.}
-  \label{fig:num-2}
-\end{figure}
-
-\subsection{Committors}
-\begin{figure}
-  \centering
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-1.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-1.eps}\\
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-1.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-1.eps}\\
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-1.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-1.eps}
-  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}  
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-2.eps}\\
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-2.eps}\\
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-2.eps}
-  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}  
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-3.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-3.eps}\\
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-3.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-3.eps}\\
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-3.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-3.eps}
-  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}  
-  \label{fig:num-2}
-\end{figure}
 

### 2014-08-27 alanine.nanma/template/tools/msm/app/calculate.coreset.msm.cpp
adding coreset msm builder

@@ -88,7 +88,6 @@ int main(int argc, char * argv[])
   po::options_description desc ("Calculates the forward and backward commitor.\nAllow options");
   desc.add_options()
       ("help,h", "print this message")
-      ("num-data-block", po::value<unsigned > (&nDataInBlock)->default_value (1), "number of data in each block.")
       ("num-bin,n", po::value<unsigned > (&nbin)->default_value (20), "number of blocks.")
       ("angle-up", po::value<double > (&aup)->default_value (180.), "upper bond of the angle.")
       ("angle-low", po::value<double > (&alow)->default_value (-180.), "lower bond of the angle.")      
@@ -121,12 +120,31 @@ int main(int argc, char * argv[])
     fclose (fp);
   }
   unsigned nstate = setMap.size();
+  map<unsigned,unsigned> mymap;
+  for (unsigned ii = 0; ii < setMap.size(); ++ii){
+    mymap[setMap[ii]] = ii;
+  }
 
   double binSize = (aup - alow) / double(nbin);
   unsigned nbin2 = nbin * nbin;
 
   vector<unsigned > clusterMap;
   unsigned numCluster = load_cluster_map (ismfile, nbin, clusterMap);
+  vector<unsigned > clusterMapOrig (nstate, 0);
+  for (unsigned ii = 0; ii < nbin; ++ii){
+    for (unsigned jj = 0; jj < nbin; ++jj){
+      unsigned dihIndex = ii * nbin + jj;
+      map<unsigned, unsigned> :: const_iterator it = mymap.find(dihIndex);
+      if (it != mymap.end()){
+	unsigned fileIndex = it -> second;
+	clusterMapOrig[fileIndex] = clusterMap[dihIndex];
+      }
+    }
+  }
+  for (unsigned ii = 0; ii < nstate; ++ii){
+    printf ("%d\n", clusterMapOrig[ii]);
+  }
+  
 
   vector<vector<BlockAverage_acc > > fwCommitor (numCluster);
   vector<vector<BlockAverage_acc > > bwCommitor (numCluster);

### 2014-08-27 alanine.nanma/template/tools/msm/app/calculate.steady.dist.cpp

@@ -35,6 +35,7 @@ int main(int argc, char * argv[])
       ("num-bin,n", po::value<unsigned > (&nbin)->default_value (20), "number of blocks.")
       ("angle-up", po::value<double > (&aup)->default_value (180.), "upper bond of the angle.")
       ("angle-low", po::value<double > (&alow)->default_value (-180.), "lower bond of the angle.")      
+      ("input-largest-set,s", po::value<std::string > (&isfile)->default_value ("largestSet"), "the input file of largest set.")
       ("input-traj-dir", po::value<string > (&idfile)->default_value ("success.dir.name"), "the traj dir name.")
       ("input-disc-traj", po::value<string > (&ifile)->default_value ("disc.traj"), "the traj file name.")
       ("output", po::value<string > (&ofile)->default_value ("steady.dist.out"), "the output of forward commitor.");
@@ -46,6 +47,21 @@ int main(int argc, char * argv[])
     std::cout << desc<< "\n";
     return 0;
   }
+
+  vector<int > setMap ;
+  {
+    FILE * fp  = fopen (isfile.c_str(), "r");
+    if (fp == NULL){
+      cerr << "cannot open file " << isfile << endl;
+      return 1;
+    }
+    int tmpint;
+    while (fscanf(fp, "%d", &tmpint) == 1){
+      setMap.push_back (tmpint);
+    }
+    fclose (fp);
+  }
+  unsigned nstate = setMap.size();
 
   unsigned nbin2 = nbin * nbin;
 
@@ -111,7 +127,17 @@ int main(int argc, char * argv[])
     }
     fprintf (fp, "\n");
   }
+  fclose (fp);
 
+  string origname = ofile+".orig";
+  fp = fopen ((origname).c_str(), "w");
+  if (fp == NULL){
+    cerr << "cannot open file " << ofile << endl;
+    return 1;
+  }
+  for (unsigned ii = 0; ii < nstate; ++ii){
+    fprintf (fp, "%e\n", dist[setMap[ii]].getAvg());
+  }
   fclose (fp);
 
   double eps = 1e-10;

### 2014-08-27 alanine.nanma/template/tools/msm/app/calculate.coreset.msm.cpp
adding coreset msm builder, not tested

@@ -42,6 +42,46 @@ unsigned load_cluster_map (const string & file,
   return max;
 }
 
+void load_steady_dist (const string & file,
+		       vector<double > & dist)
+{
+  FILE * fp = fopen (file.c_str(), "r");
+  if (fp == NULL){
+    cerr << "cannot open file " << file <<  endl;
+    exit(1);
+  }
+  double tmp;
+  dist.clear ();
+  while (1 == fscanf(fp, "%lf", &tmp)){
+    dist.push_back (tmp);
+  }
+  fclose (fp);
+}
+
+void load_committor (const string & file,
+		     const unsigned & ncluster,
+		     vector<vector<double > > & fwq)
+{
+  FILE * fp = fopen (file.c_str(), "r");
+  if (fp == NULL){
+    cerr << "cannot open file " << file <<  endl;
+    exit(1);
+  }
+  double tmp;
+  unsigned countC = 0;
+  fwq.clear();
+  fwq.resize(ncluster);
+  while (1 == fscanf(fp, "%lf", &tmp)){
+    if (countC == ncluster){
+      countC = 0;
+    }
+    fwq[countC].push_back (tmp);
+    countC++;
+  }
+  fclose (fp);
+}
+
+
 void deposite_traj (const vector<unsigned > & traj,
 		    const int & startPosi,
 		    const int & stopPosi,
@@ -79,24 +119,66 @@ void deposite_traj (const vector<unsigned > & traj,
   }
 }
 
+void read_tmatrix (const string & filename,
+		   vector<vector<double > > & tmatrix,
+		   unsigned & nstate)
+{
+  ifstream fpname (filename.c_str());
+  if (!fpname){
+    std::cerr << "cannot open file " << filename << std::endl;
+    exit(1);
+  }
+  char valueline [MaxLineLength];
+  int countLine = 0;
+  while (fpname.getline(valueline, MaxLineLength)){
+    vector<string > words;
+    StringOperation::split (string(valueline), words);
+    if (countLine == 0){
+      nstate = words.size();
+      tmatrix.resize(nstate);
+      for (unsigned ii = 0; ii < nstate; ++ii){
+	tmatrix[ii].resize(nstate);
+      }
+    }
+    if (words.size() != nstate){
+      cerr << "format error of tmatrix reading " << endl;
[…]

### 2014-08-27 alanine.nanma/template/tools/msm/app/calculate.commitor.cpp
fix bug in committor calculator

@@ -245,8 +245,20 @@ int main(int argc, char * argv[])
   }
   for (unsigned ii = 0; ii < nstate; ++ii){
     for (unsigned mm = 0; mm < fwCommitor.size(); ++mm){
+      if (0 == clusterMap[setMap[ii]]){
       fprintf (fpfw, "%e ", fwCommitor[mm][setMap[ii]].getAvg());
       fprintf (fpbw, "%e ", bwCommitor[mm][setMap[ii]].getAvg());
+      }
+      else {
+	if ( mm+1 == clusterMap[setMap[ii]] ){
+	  fprintf (fpfw, "%e ", 1.);
+	  fprintf (fpbw, "%e ", 1.);
+	}
+	else {
+	  fprintf (fpfw, "%e ", 0.);
+	  fprintf (fpbw, "%e ", 0.);
+	}
+      }
     }
     fprintf (fpfw, "\n");
     fprintf (fpbw, "\n");

### 2014-08-27 alanine.nanma/template/tools/msm/app/calculate.coreset.msm.cpp
fix bugs

@@ -166,7 +166,7 @@ void apply_trans (const vector<vector<double > > & tmatrix,
 
 int main(int argc, char * argv[])
 {
-  std::string ofwfile, obwfile, ifile, idfile, isfile, ismfile, ifloquetfile, isdfile;
+  std::string ofwfile, obwfile, idfile, isfile, ismfile, ifloquetfile, isdfile;
   unsigned nbin;
   
   po::options_description desc ("Calculates the forward and backward commitor.\nAllow options");
@@ -209,10 +209,14 @@ int main(int argc, char * argv[])
 
   vector<vector<double > > tmatrix;
   unsigned nstate1;
-  read_tmatrix (ifile, tmatrix, nstate1);
+  read_tmatrix (ifloquetfile, tmatrix, nstate1);
   if (nstate1 != nstate){
     cerr << "the largest set file is not consistent with the transition matrix" << endl;
     return 1;
+  }
+  vector<vector<double > > pmatrix(tmatrix);
+  for (unsigned ii = 0; ii < nstate; ++ii){
+    pmatrix[ii][ii] -= 1.;
   }
 
   vector<unsigned > clusterMap;
@@ -236,17 +240,55 @@ int main(int argc, char * argv[])
   vector<vector<double > > fwq;
   vector<vector<double > > bwq;
   load_committor (ofwfile, numCluster, fwq);
-  load_committor (obwfile, numCluster, fwq);
+  load_committor (obwfile, numCluster, bwq);
   vector<double > dist;
   load_steady_dist (isdfile, dist);
+  // for (unsigned ii = 0; ii < numCluster; ++ii){
+  //   double sum = 0.;
+  //   for (unsigned jj = 0; jj < nstate; ++jj){
+  //     sum += bwq[ii][jj];
+  //     // if (dist[jj] != 0) bwq[ii][jj] /= dist[jj];
+  //     // if (dist[jj] != 0) fwq[ii][jj] /= dist[jj];
+  //   }
+  //   cout <<  (sum) << endl;
+  //   sum = 0.;
+  //   for (unsigned jj = 0; jj < nstate; ++jj){
+  //     sum += fwq[ii][jj];
+  //   }
+  //   cout <<  (sum) << endl;
+  // }
+  // for (unsigned jj = 0; jj < nstate; ++jj){
+  //   double sum = 0;
[…]

### 2014-08-28 writedown/period.noneq.msm/main.tex
backup before merge with C.S.

@@
 Using $K=2$ the dynamics depends on the time interval used for
-calculating the generator: using time intervals $[0, 40]$ the reduced
+calculating the generator: using time intervals $[320, 1000]$ the reduced
 dynamics can only reproduces the brute force result in $[0, 40]$,
@@
 
-\subsection{Core set identification}
-
-\redc{Write how to detact the core sets for irreversible Markovian process}.
-
-The coresets are denoted by $C_{R_\alpha}$, $C_\beta$ and $C_{L_\alpha}$, which correspond to
-right-handed alpha-helix, beta-sheet and left-handed alpha-helix, respectively.
-
 \subsection{Steady state distribution and eigenfunctions}
@@
   \centering  
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-dist.eps}
+  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.40/fig-dist.eps}
   % \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-dist-msm.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-1.eps}
+  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-1.eps}
   \caption{The steady state distribution calculated by brute force non-equilibrium comparing with MSM.}
@@
 
+\subsection{Coreset identification}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.4\textwidth]{fig/t040/cluster.marco/fig-cluster-2.eps}
+  \caption{The coreset identification. Different colors indicate different coresets: $C_{R_\alpha}$ (yellow), $C_\beta$ (red) and $C_{L_\alpha}$ (green).
+    The blue color means out of any coreset. (By Marco)}
+  \label{fig:cluster}
+\end{figure}
+
+\redc{Write how to detact the core sets for irreversible Markovian process}.
+
+The coresets (see Fig.~\ref{fig:cluster}) are denoted by $C_{R_\alpha}$ (yellow), $C_\beta$ (red) and $C_{L_\alpha}$ (green), which correspond to
+right-handed alpha-helix, beta-sheet and left-handed alpha-helix, respectively.
+
 \subsection{Committors}
@@
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-1.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-1.eps}\\
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-1.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-1.eps}\\
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-1.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-1.eps}
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-1.eps}
-  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}
+  \caption{The forward $q^\fwd_{L_\alpha}$ and backward committors $q^\bwd_{L_\alpha}$ computed by MSM (second row) is compared with those computed by brute force non-equilibrium simulations (first row).}
   \label{fig:num-3}
@@
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-2.eps}\\
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-2.eps}\\
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-2.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-2.eps}
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-2.eps}
-  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}  
+  \caption{The forward $q^\fwd_{R_\alpha}$ and backward $q^\fwd_{R_\alpha}$ committors computed by MSM (second row) is compared with those computed by brute force non-equilibrium simulations (first row).}
   \label{fig:num-4}
@@
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-3.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-3.eps}\\
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-3.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-3.eps}\\
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-3.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-3.eps}
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-3.eps}
-  \caption{The forward and backward committors computed by MSM is compared with those computed by brute force non-equilibrium simulations.}  
+  \caption{The forward $q^\fwd_{\beta}$ and backward $q^\fwd_{\beta}$ committors computed by MSM (second row) is compared with those computed by brute force non-equilibrium simulations (first row).}  
   \label{fig:num-5}
@@
 
-\section{Discussions}
-\subsection{The periodicity of the reduced dynamics}
+\subsection{First mean hitting time}
 
-As discussed before, if the reduced dynamics captures the slow
-dynamics of interest, then the reduced dynamics is also periodic,
-which implies that the generator $M(t)$ can be estimated from any time
-interval by Eq.~\eqref{eqn:tmp4}. In practice, the reduced dynamics
-may not be perfectly periodic. The generator calculated from
-different time intervals can be used to test the periodicity of the
-reduced dynamics. The results are shown in Tab.~\ref{tab:tmp1} and
-Fig.~\ref{fig:tmp2}.  The dependency with respect to the time
-interval, in which the generator is calculated, indicates the reduced
-dynamics is not perfectly periodic. The reduced dynamics from $[0,40]$
-reproduces the best probability in interval $[0,40]$, and worst in the
-steady state. Moreover, the leading non-trivial timescale is also off
-(see Tab.~\ref{tab:tmp1}), while the accuracy of the second and third
-non-trivial timescales are better, because they are comparable to the
-period, 40~ps, in which the dynamics is relaxed. The reduced dynamics
-from $[300,1000]$ reproduces the best steady state probability, while
-worst in reproducing the initial relaxation process. The reduced
-dynamics from $[0,320]$ is indistinguishable from the one from
-$[300,1000]$, which implies that in practice, one only have to
-simulation relatively short non-equilibrium trajectories (that are
-almost relaxed), and compute the generator from it to build the reduced dynamics. \redc{This saves a great
-amount of computational resources comparing with calculating the
-reduced dynamics only from steady state trajectories.}
+The first mean hitting time is presented in Fig.~\ref{fig:num-6}.
 
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{fig/t040/fig-cg-prob-range.eps}  
-  \caption{The time-dependent probability of conformation
-    $\confc$. The brute force MD simulation is compared with reduced
-    dynamics, the transition matrix of which are calculated from
-    different ranges. The red shadow region is the statistical uncertainty of the brute force MD simulation.
-    The inserts show the zoom-ined probability at the relaxation stage $[0,120 ]~\textrm{ps}$ and at the steady state $[800,880 ]~\textrm{ps}$.}
-  \label{fig:tmp2}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-3.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-msm-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-msm-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-msm-3.eps}
+  \caption{The first mean htting time comparsion between the brute force simulation (first row) and the MSM (second row).
+  From left to right are first mean hitting time to coresets $C_{L_\alpha}$, $C_{R_\alpha}$ and $C_{\beta}$, respectively}  
+  \label{fig:num-6}
 \end{figure}
 
-\subsection{The choice of lag time $\tau$}
-Table~\ref{tab:tmp1} shows a clear trend of worse accuracy with
-increased $\tau$, however, the timescales are not very sensitive to
-the choice of lag time $\tau$.
+% \section{Discussions}
+% \subsection{The periodicity of the reduced dynamics}
 
-\section{To do}
+% As discussed before, if the reduced dynamics captures the slow
+% dynamics of interest, then the reduced dynamics is also periodic,
+% which implies that the generator $M(t)$ can be estimated from any time
+% interval by Eq.~\eqref{eqn:tmp4}. In practice, the reduced dynamics
+% may not be perfectly periodic. The generator calculated from
+% different time intervals can be used to test the periodicity of the
+% reduced dynamics. The results are shown in Tab.~\ref{tab:tmp1} and
+% Fig.~\ref{fig:tmp2}.  The dependency with respect to the time
+% interval, in which the generator is calculated, indicates the reduced
+% dynamics is not perfectly periodic. The reduced dynamics from $[0,40]$
+% reproduces the best probability in interval $[0,40]$, and worst in the
+% steady state. Moreover, the leading non-trivial timescale is also off
+% (see Tab.~\ref{tab:tmp1}), while the accuracy of the second and third
+% non-trivial timescales are better, because they are comparable to the
+% period, 40~ps, in which the dynamics is relaxed. The reduced dynamics
+% from $[300,1000]$ reproduces the best steady state probability, while
+% worst in reproducing the initial relaxation process. The reduced
+% dynamics from $[0,320]$ is indistinguishable from the one from
+% $[300,1000]$, which implies that in practice, one only have to
+% simulation relatively short non-equilibrium trajectories (that are
+% almost relaxed), and compute the generator from it to build the reduced dynamics. \redc{This saves a great
+% amount of computational resources comparing with calculating the
+% reduced dynamics only from steady state trajectories.}
 
-\begin{itemize}
-\item Theoretical analysis of the accuracy of the discretization, a
-generalization of the equilibrium case. the numerical results indicate
-a very close link. The perodicity is very nice, if the generator is
-``continuous'', then it should be uniformly continuous, then it should
-be possible to develop estimates that are similar to the equilibrium
-case.
-\item More tests on the effect of choosing different lag-time $\tau$ (0.5 and 1.0~ps are done).
-\item More theoretical consideration on the Floquet theory, what is the
-explict form of matrix $\vect B$, and does it has any nice properties,
-such as self-joint.
-\end{itemize}
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.5\textwidth]{fig/t040/fig-cg-prob-range.eps}  
+%   \caption{The time-dependent probability of conformation
+%     $\confc$. The brute force MD simulation is compared with reduced
+%     dynamics, the transition matrix of which are calculated from
+%     different ranges. The red shadow region is the statistical uncertainty of the brute force MD simulation.
+%     The inserts show the zoom-ined probability at the relaxation stage $[0,120 ]~\textrm{ps}$ and at the steady state $[800,880 ]~\textrm{ps}$.}
+%   \label{fig:tmp2}
+% \end{figure}
+
+% \subsection{The choice of lag time $\tau$}
+% Table~\ref{tab:tmp1} shows a clear trend of worse accuracy with
+% increased $\tau$, however, the timescales are not very sensitive to
+% the choice of lag time $\tau$.
+
+% \section{To do}
+
+% \begin{itemize}
+% \item Theoretical analysis of the accuracy of the discretization, a
+% generalization of the equilibrium case. the numerical results indicate
+% a very close link. The perodicity is very nice, if the generator is
+% ``continuous'', then it should be uniformly continuous, then it should
+% be possible to develop estimates that are similar to the equilibrium
+% case.
+% \item More tests on the effect of choosing different lag-time $\tau$ (0.5 and 1.0~ps are done).
+% \item More theoretical consideration on the Floquet theory, what is the
+% explict form of matrix $\vect B$, and does it has any nice properties,
+% such as self-joint.
+% \end{itemize}
+
+\section{Approximation quality of the Markov state model}
+
+The whole Floquet theory can be applied to the original dynamics, and we denote that the resulting transition matrix by $\psi(T)$, then
+the time-dependent probability density can be written as
+\begin{align*}
+  \rho(\vect x, kT) = 
+\end{align*}
+
+In general, the original dynamics of the molecular system under perodical external driven
+is not reversible, see the discussion in Sec.~\ref{sec:revs}. However, we can assume the,
 
 \section{Reversibility of the original dynamics}
+\label{sec:revs}
 
@@
 
+\subsection{Irreversibility of the perodical symmetrical dynamics}
+
 In Eq.~\eqref{eq:dagger-0}, we assume the periodicity of the perturbation $F(x,t) = F(x,t+T)$, and the symmetry of the external perturbation, i.e.~$F(x, -t) = F(x, t)$, we have

### 2014-08-28 alanine.nanma/template/tools/msm/app/calculate.coreset.msm.cpp
add output

@@ -166,7 +166,7 @@ void apply_trans (const vector<vector<double > > & tmatrix,
 
 int main(int argc, char * argv[])
 {
-  std::string ofwfile, obwfile, idfile, isfile, ismfile, ifloquetfile, isdfile;
+  std::string ifwfile, ibwfile, idfile, isfile, ismfile, ifloquetfile, isdfile, otmfile;
   unsigned nbin;
   
   po::options_description desc ("Calculates the forward and backward commitor.\nAllow options");
@@ -177,8 +177,9 @@ int main(int argc, char * argv[])
       ("input-floquet,f", po::value<string > (&ifloquetfile)->default_value ("floque.B.out"), "the input transition matrix.")
       ("input-cluster-map", po::value<string > (&ismfile)->default_value ("cluster.map.out"), "the input of cluster map.")
       ("input-steady", po::value<string > (&isdfile)->default_value ("steady.dist.out.orig"), "the input steady state.")
-      ("input-fw", po::value<string > (&ofwfile)->default_value ("commitor.fw.out.orig"), "the input of forward commitor.")
-      ("input-bw", po::value<string > (&obwfile)->default_value ("commitor.bw.out.orig"), "the input of backward commitor.");
+      ("input-fw", po::value<string > (&ifwfile)->default_value ("commitor.fw.out.orig"), "the input of forward commitor.")
+      ("input-bw", po::value<string > (&ibwfile)->default_value ("commitor.bw.out.orig"), "the input of backward commitor.")
+      ("output-tmatrix", po::value<string > (&otmfile)->default_value ("coreset.tmatrix.out"), "the output transition matrix of coreset MSM.");
   
   po::variables_map vm;
   po::store(po::parse_command_line(argc, argv, desc), vm);
@@ -239,8 +240,8 @@ int main(int argc, char * argv[])
 
   vector<vector<double > > fwq;
   vector<vector<double > > bwq;
-  load_committor (ofwfile, numCluster, fwq);
-  load_committor (obwfile, numCluster, bwq);
+  load_committor (ifwfile, numCluster, fwq);
+  load_committor (ibwfile, numCluster, bwq);
   vector<double > dist;
   load_steady_dist (isdfile, dist);
   // for (unsigned ii = 0; ii < numCluster; ++ii){
[…]

### 2014-08-28 alanine.nanma/template/tools/scripts/msm.analyze.brute.force.sh
compute l eigenvector, compute coreset msm

@@ -25,17 +25,21 @@ else
     source $target_dir/msm.parameters.sh
 fi
 
-mycommand="$msm_dir/calculate.commitor --num-bin $msm_dih_nbin --input-cluster-map $target_dir/cluster.map.out --input-traj-dir dir.name --input-disc-traj traj.dih.disc.periodT --output-fw $target_dir/commitor.fw.out --output-bw $target_dir/commitor.bw.out"
+mycommand="$msm_dir/calculate.commitor --input-largest-set $target_dir/largestSet.dih --num-bin $msm_dih_nbin --input-cluster-map $target_dir/cluster.map.out --input-traj-dir dir.name --input-disc-traj traj.dih.disc.periodT --output-fw $target_dir/commitor.fw.out --output-bw $target_dir/commitor.bw.out"
 echo "# calculate commitor by command: $mycommand"
 $mycommand
 paste $target_dir/commitor.fw.out $target_dir/commitor.bw.out > $target_dir/commitor.out
 
-mycommand="$msm_dir/calculate.steady.dist --num-bin $msm_dih_nbin --input-traj-dir dir.name --input-disc-traj traj.dih.disc.periodT --output $target_dir/steady.dist.out"
+mycommand="$msm_dir/calculate.steady.dist --input-largest-set $target_dir/largestSet.dih --num-bin $msm_dih_nbin --input-traj-dir dir.name --input-disc-traj traj.dih.disc.periodT --output $target_dir/steady.dist.out"
 echo "# calculate steady dist by command: $mycommand"
 $mycommand
 
 mycommand="$msm_dir/calculate.fht --input-largest-set $target_dir/largestSet.dih --input-cluster-map $target_dir/cluster.map.out  --num-bin $msm_dih_nbin --input-traj-dir dir.name --input-disc-traj traj.dih.disc.periodT --output $target_dir/fht.out"
 echo "# calculate first hitting time by command: $mycommand"
+$mycommand
+
+mycommand="$msm_dir/calculate.coreset.msm --num-bin $msm_dih_nbin --input-largest-set $target_dir/largestSet.dih  --input-floquet $target_dir/floque.B.out --input-cluster-map $target_dir/cluster.map.out --input-steady $target_dir/steady.dist.out.orig --input-fw $target_dir/commitor.fw.out.orig --input-bw $target_dir/commitor.bw.out.orig --output-tmatrix $target_dir/coreset.tmatrix.out"
[…]

### 2014-08-28 alanine.nanma/template/tools/scripts/msm.analyze.disc.sh

@@ -31,17 +31,21 @@ $mycommand
 
 rm -f current.name
 echo "." > current.name
-mycommand="$msm_dir/calculate.commitor --num-bin $msm_dih_nbin --input-cluster-map $target_dir/cluster.map.out --input-traj-dir current.name --input-disc-traj traj.out --output-fw $target_dir/commitor.fw.msm.out --output-bw $target_dir/commitor.bw.msm.out"
+mycommand="$msm_dir/calculate.commitor --input-largest-set $target_dir/largestSet.dih --num-bin $msm_dih_nbin --input-cluster-map $target_dir/cluster.map.out --input-traj-dir current.name --input-disc-traj traj.out --output-fw $target_dir/commitor.fw.msm.out --output-bw $target_dir/commitor.bw.msm.out"
 echo "# compute commitor by $mycommand"
 $mycommand
 paste $target_dir/commitor.fw.msm.out $target_dir/commitor.bw.msm.out > $target_dir/commitor.msm.out
 
-mycommand="$msm_dir/calculate.steady.dist --num-bin $msm_dih_nbin --input-traj-dir current.name --input-disc-traj traj.out --output $target_dir/steady.dist.msm.out"
+mycommand="$msm_dir/calculate.steady.dist --input-largest-set $target_dir/largestSet.dih --num-bin $msm_dih_nbin --input-traj-dir current.name --input-disc-traj traj.out --output $target_dir/steady.dist.msm.out"
 echo "# compute steady dist by $mycommand"
 $mycommand
 
 mycommand="$msm_dir/calculate.fht --input-largest-set $target_dir/largestSet.dih --input-cluster-map $target_dir/cluster.map.out  --num-bin $msm_dih_nbin --input-traj-dir current.name --input-disc-traj traj.out --output $target_dir/fht.msm.out"
 echo "# calculate first hitting time by command: $mycommand"
+$mycommand
+
+mycommand="$msm_dir/calculate.coreset.msm --num-bin $msm_dih_nbin --input-largest-set $target_dir/largestSet.dih  --input-floquet $target_dir/floque.B.out --input-cluster-map $target_dir/cluster.map.out --input-steady $target_dir/steady.dist.msm.out.orig --input-fw $target_dir/commitor.fw.msm.out.orig --input-bw $target_dir/commitor.bw.msm.out.orig --output-tmatrix $target_dir/coreset.tmatrix.msm.out"
[…]

### 2014-08-28 alanine.nanma/template/tools/scripts/msm.floquet.eig.m

@@ -8,3 +8,26 @@ vv =v(:,1:5);
 vv(:,1) = vv1;
 save ('floquet.eigvalue.out', 'ee');
 save ('floquet.eigvector.out', 'vv');
+
+for ii=1:length(vv(:,2))
+	 if vv1(ii) ~= 0
+	 vv(ii,2) = vv(ii,2)./vv1(ii);
+end
+end
+for ii=1:length(vv(:,3))
+	 if vv1(ii) ~= 0
+	 vv(ii,3) = vv(ii,3)./vv1(ii);
+end
+end
+for ii=1:length(vv(:,4))
+	 if vv1(ii) ~= 0
+	 vv(ii,4) = vv(ii,4)./vv1(ii);
+end
+end
+for ii=1:length(vv(:,5))
+	 if vv1(ii) ~= 0
+	 vv(ii,5) = vv(ii,5)./vv1(ii);
+end
+end
+
+save ('floquet.eigvector.l.out', 'vv');

### 2014-08-28 alanine.nanma/template/tools/scripts/msm.floquet.eig.sh

@@ -36,6 +36,11 @@ do
     grep -v \# floquet.eigvector.out | awk "{print \$$ii}"  | grep -v \# > tmp.vec.in
     $msm_dir/vector.set2dih --input-largest-set largestSet.dih --num-bin $msm_dih_nbin --input tmp.vec.in --output floquet.eigvector.$ii.out
 done
+for ii in `seq 1 $neig`;
+do
+    grep -v \# floquet.eigvector.l.out | awk "{print \$$ii}"  | grep -v \# > tmp.vec.in
+    $msm_dir/vector.set2dih --input-largest-set largestSet.dih --num-bin $msm_dih_nbin --input tmp.vec.in --output floquet.eigvector.l.$ii.out
+done
 # rm -f tmp.vec.in
 
 cd $cwd

### 2014-08-28 writedown/period.noneq.msm/paper.tex
add paper.tex, merging with C.S.

--- 2014-08-28 writedown/period.noneq.msm/main.tex
@@
 
-We denote the phase space by $\Omega$, and the variable by $\vect
-x$. The time-dependent probability distribution on the phase space is
-denoted by $\rho(\vect x, t)$. The dynamics of the system is governed
-by
+We consider  the following SDE form of the externally driven MD:
 \begin{align}
-  \label{eqn:tmp1}
-  \frac{\partial \rho(\vect x, t)}{\partial t} = \ml(t) \rho(\vect x,t),
+  \label{eq:dis-1}
+  d\vect x_t = \Big(-\nabla V(\vect x_t) + E(t) D(\vect x_t)\Big)dt + \sqrt{2\beta^{-1}} d\vect w_t, 
 \end{align}
-where the generator $\ml(t)$ is time-dependent and assumed to be
-periodic, i.e.~$\ml(t) = \ml(t+T)$, with period denoted by $T$.  Now
-we discretize the phase space $\Omega$ into finite number of disjoint
-sets $\{ S_1, \cdots, S_n\}$, which satisfy $\Omega = \cup_i S_i$,
-$S_j\cap S_j = \emptyset,\ \forall i\neq j$.
+where the configurational space is denoted by $\Omega$, and the variable by
+$\vect x$.   $V(\vect x)$ is the molecular interaction potential and
+$E(t)D(x_t)$ the time-dependent external perturbation with the
+$T$-periodic external field $E(t)$. $\beta$ is the inversed temperature,
+i.e.~$\beta = 1/(k_B\mathcal T)$.
+The propagation of probability
+densities $\rho=\rho(\vect x,t)$ based on this kind of dynamics in the sense
+of $\rho(\vect x,t)dx=\mathbb P[\vect x_t\in [\vect x,\vect x+d\vect x)]$ is governed by
+Fokker-Planck equation:
+\begin{align}
+  \label{eq:dis-2}
+  \frac{\partial \rho}{\partial t} = \ml^\dagger(t) \rho,
+\end{align}
+where $\ml^\dagger(t)$ is the adjoint of the generator
+\begin{align}
+  \label{eq:dis-3}
+  \ml(t)=\beta^{-1}\Delta_{\vect x}+\Big(-\nabla V(\vect x) + E(t)D(\vect x)\Big)\cdot\nabla_{\vect x},
+\end{align}
+where $\Delta_{\vect x}$ denotes the Laplacian operator and $\nabla_{\vect x}$
+the nabla-operator wrt to $\vect x$. 
+The periodicity of the external driven indicates the periodicity of the generator,
+i.e.~$\ml(t) = \ml(t+T)$.  Now
+introduce a partition of the configurational space $\Omega$ into finite number of disjoint
+sets $\{ \Omega_1, \cdots, \Omega_n\}$, which satisfy $\Omega = \cup_i \Omega_i$,
+$\Omega_j\cap \Omega_j = \emptyset,\ \forall i\neq j$.
 Now the original dynamics of the system can be discretized to a time-dependent
@@
 \begin{align}
-  \vect p(t) = (p_1(t), \cdots, p_n(t))^T, \quad \textrm{with}\ p_i(t) = \int_{S_i} \rho(\vect x,t)d\vect x,
+  \vect p(t) = (p_1(t), \cdots, p_n(t))^T, \quad \textrm{with}\ p_i(t) = \int_{\Omega_i} \rho(\vect x,t)d\vect x,
 \end{align}
@@
   \label{eqn:tmp4}
-  M_{ij}(t) \approx \frac{1}{\tau} \,[\, \mbp (\vect x_{t+\tau} \in S_j \vert \vect x_{t} \in S_i) - \delta_{ij} \,]
+  M_{ij}(t) \approx \frac{1}{\tau} \,[\, \mbp (\vect x_{t+\tau} \in \Omega_j \vert \vect x_{t} \in \Omega_i) - \delta_{ij} \,]
 \end{align}
-From Eqn.~\eqref{eqn:tmp1} to Eqn.~\eqref{eqn:tmp2} involves several
+From Eqn.~\eqref{eq:dis-2} to Eqn.~\eqref{eqn:tmp2} involves several
 approximations:
@@
   conformational change of the molecules is much faster than the
-  covalent bond vibrations. Therefore, if the discretion $\{ S_1,
-  \cdots, S_n\}$ properly captures the slow dynamics of interest, in
+  covalent bond vibrations. Therefore, if the discretion $\{ \Omega_1,
+  \cdots, \Omega_n\}$ properly captures the slow dynamics of interest, in
   the sense that within the lag-time $\tau$, the system is fully
-  relaxed to a local equilibrium in the set $S_i$, then it is clear
+  relaxed to a local equilibrium in the set $\Omega_i$, then it is clear
   that the reduce system is periodic. It suggests that the lag-time
@@
 At this stage we do have any analytical result regarding the quality
-of approximating Eqn.~\eqref{eqn:tmp1} by
+of approximating Eqn.~\eqref{eq:dis-2} by
 Eqn.~\eqref{eqn:tmp2}.
@@
 % force molecular dynamics simulation result
-% (i.e.~Eqn.~\eqref{eqn:tmp1}) is compared with different discretization
+% (i.e.~Eqn.~\eqref{eq:dis-2}) is compared with different discretization
 % methods, which give different generator in Eqn.~\eqref{eqn:tmp2}. For
@@
 However, it can only resolve the processes that are longer than the period $T$.
-Therefore, rather than going directly from Eq.~\eqref{eqn:tmp1} to Eq.~\eqref{eqn:tmp5a},
+Therefore, rather than going directly from Eq.~\eqref{eq:dis-2} to Eq.~\eqref{eqn:tmp5a},
 we would like to keep the intermediate step Eq.~\eqref{eqn:tmp2}.
@@
 % At this stage we do have any analytical result regarding the quality
-% of approximating Eqn.~\eqref{eqn:tmp1} by
+% of approximating Eqn.~\eqref{eq:dis-2} by
 % Eqn.~\eqref{eqn:tmp2}. However, it would be useful to do some

### 2014-08-28 alanine.nanma/template/tools/scripts/msm.dih.disc.sh
fix bug

@@ -92,5 +92,5 @@ do
     rm -f tmp.init.out tmp.perid.out
 done
 
-store_dir_name="dis.dih$msm_dih_nbin.tau$msm_tau.b$msm_steady_begin.e$pert_time"
+store_dir_name="dis.dih$msm_dih_nbin.tau$msm_tau.b$msm_steady_begin.e$msm_steady_end"
 $script_dir/msm.dih.store.sh $store_dir_name

### 2014-08-29 writedown/period.noneq.msm/paper.tex
add paper.tex

--- 2014-08-28 writedown/period.noneq.msm/main.tex
@@
 \newcommand{\greenc}[1]{{\color{green} #1}}
-\newcommand{\vect}[1]{\textbf{\textit{#1}}}
+% \newcommand{\vect}[1]{\textbf{\textit{#1}}}
+\newcommand{\vect}[1]{#1}
 \newcommand{\dd}[1]{\textsf{#1}}
@@
 \newcommand{\dt}[0]{\Delta t}
+\newcommand{\id}{\mathrm{Id}}
+% \newcommand{\myphi}{\boldsymbol\Phi}
+% \newcommand{\mymu}{\boldsymbol\mu}
+\newcommand{\myphi}{\Phi}
+\newcommand{\mymu}{\mu}
+\newcommand{\prob}{\textrm{P}}
 
@@
 \section{Discretization of the non-equilibrium molecular dynamics}
+\label{sec:disc}
 
-We denote the phase space by $\Omega$, and the variable by $\vect
-x$. The time-dependent probability distribution on the phase space is
-denoted by $\rho(\vect x, t)$. The dynamics of the system is governed
-by
+We consider  the following SDE form of the externally driven MD:
 \begin{align}
-  \label{eqn:tmp1}
-  \frac{\partial \rho(\vect x, t)}{\partial t} = \ml(t) \rho(\vect x,t),
+  \label{eq:disc-1}
+  d\vect x_t = \Big(-\nabla V(\vect x_t) + E(t) D(\vect x_t)\Big)dt + \sqrt{2\beta^{-1}} d\vect w_t, 
 \end{align}
-where the generator $\ml(t)$ is time-dependent and assumed to be
-periodic, i.e.~$\ml(t) = \ml(t+T)$, with period denoted by $T$.  Now
-we discretize the phase space $\Omega$ into finite number of disjoint
-sets $\{ S_1, \cdots, S_n\}$, which satisfy $\Omega = \cup_i S_i$,
-$S_j\cap S_j = \emptyset,\ \forall i\neq j$.
-Now the original dynamics of the system can be discretized to a time-dependent
-Markov jump process:
+where the configurational space is denoted by $\Omega$, and the variable by
+$\vect x$.   $V(\vect x)$ is the molecular interaction potential and
+$E(t)D(x_t)$ the time-dependent external perturbation with the
+$T$-periodic external field $E(t)$. $\beta$ is the inversed temperature,
+i.e.~$\beta = 1/(k_B\mathcal T)$.
+The propagation of probability
+densities $\rho=\rho(\vect x,t)$ based on this kind of dynamics in the sense
+of $\rho(\vect x,t)dx=\prob[\vect x_t\in [\vect x,\vect x+d\vect x)]$ is governed by
+Fokker-Planck equation:
 \begin{align}
-  \label{eqn:tmp2}
-  \frac{d\vect p(t)}{dt} = \vect M(t)\cdot \vect p(t)
+  \label{eq:disc-2}
+  \frac{\partial \rho}{\partial t} = \ml^\dagger(t) \rho,
 \end{align}
-where
+where $\ml^\dagger(t)$ is the adjoint of the generator
 \begin{align}
-  \vect p(t) = (p_1(t), \cdots, p_n(t))^T, \quad \textrm{with}\ p_i(t) = \int_{S_i} \rho(\vect x,t)d\vect x,
+  \label{eq:disc-3}
+  \ml(t)=\beta^{-1}\Delta_{\vect x}+\Big(-\nabla V(\vect x) + E(t)D(\vect x)\Big)\cdot\nabla_{\vect x},
 \end{align}
-and the generator is approximated by finite difference scheme:
+where $\Delta_{\vect x}$ denotes the Laplacian operator and $\nabla_{\vect x}$
+the nabla-operator wrt to $\vect x$. 
+The periodicity of the external driven indicates the periodicity of the generator,
+i.e.~$\ml(t) = \ml(t+T)$.  Now
+introduce a partition of the configurational space $\Omega$ into finite number of disjoint
+sets $\{ \Omega_1, \cdots, \Omega_n\}$, which satisfy $\Omega = \cup_i \Omega_i$,
+$\Omega_j\cap \Omega_j = \emptyset,\ \forall i\neq j$.
+Following Ref.~\cite{latorre2011structure}, the Fokker-Planck Eq.~\ref{eq:disc-2}
+is discretized, which results in a time-inhomogeneous Markov jump process in state
+space $S = \{1, \cdots, n\}$ with time-dependent rate
+matrix $\vect L(t) \in \mathbb R^{n\times n}$ satisfying
+\begin{align}\label{eq:disc-4}
+\sum\limits_{j=1}^n L_{ij}(t) & =  0\\ \label{eq:disc-5}
+L_{ij}(t) & \ge  0, \quad i\not= j\\
+L_{ij}(t) & =  L_{ij}(t+T)
+\end{align}
+for all real time $t\geq 0$.
+\recheck{Moreover,
+the rate matrix $L$ has the form $\vect L(t)=\vect L_0+E(t)\vect L_1$
+where $E(t)$ is periodic with period $T>0$.}
+One possible approximation to $L(t)$ is via the following forward finite difference scheme:
 \begin{align}
   \label{eqn:tmp4}
-  M_{ij}(t) \approx \frac{1}{\tau} \,[\, \mbp (\vect x_{t+\tau} \in S_j \vert \vect x_{t} \in S_i) - \delta_{ij} \,]
+  L_{ij}(t) \approx \frac{1}{\tau}
+  \,[\, \prob (\vect X_{t+\tau} = i \vert \vect X_{t} = j) - \delta_{ij} \,]
 \end{align}
-From Eqn.~\eqref{eqn:tmp1} to Eqn.~\eqref{eqn:tmp2} involves several
-approximations:
+where $\vect X_t$ denotes the Markov jump process generated by $\vect L(t)$, 
+and $\tau$ is the disretization time-step.
+In analogy to \eqref{eq:disc-2}, the Markov jump process generated by
+$\vect L(t)$ transports probability densities according to the associated Master equation
+\begin{align}
+  \label{eq:disc-7}
+  \frac{d\vect p(t)}{dt} = \vect L^T(t)\cdot \vect p(t)
+\end{align}
+where $\vect L(t)^T$ denotes the matrix transpose of $\vect L(t)$ and
+$p_i(t)$, for example, the probability to be in state $i$ at time $t$.
+As usual the properties (\ref{eq:disc-4}) and (\ref{eq:disc-5}) of
+$\vect L(t)$ guarantee that the total probability mass is conserved,
+i.e., if $p_i(0)\ge 0$ componentwise, then $p_i(t)\ge 0$ and $\sum_i
+p_i(t) = \sum_ip_i(0)$.
+% The solution of the master equation need no be
+% periodic.
+It can be formally written
+\begin{align}  \label{eq:disc-8}
+\vect p(t)=\myphi(t)\vect p(0)
+\end{align}
+by using the
+associated propagator matrix $\myphi(t)\in\mathbb R^{n\times n}$ that solves
+\begin{align}
+  \label{eq:disc-9}
+  \frac{d}{dt}\myphi(t) = \vect L^T(t)\myphi(t), \quad \myphi(0) = \id
+\end{align}
+Since the last equation can be considered column-wise, the propagator matrix inherits column-wise conservation properties:
+$\Phi_{ij}(t) \ge  0$
+and $\sum\limits_{i=1}^n \Phi_{ij}(t)  =  1$,
+that is, $\myphi^T(t)$ is a
+stochastic matrix satisfying $\myphi^T(t)\vect e=\vect e$
+with $\vect e=(1,\ldots,1)^T\in \mathbb R^n$.
+Regarding these considerations, we find
+\begin{align}
+\label{eq:disc-10}  
+\myphi_{ij}(t)=\prob\left(\vect X_t=i\mid \vect X_0=j \right),
+\end{align}
+ The
+discretization sets that we used to go from $\vect x_t$ and $\ml(t)$ to $\vect X_t$
+and $\vect L(t)$, respectively, can be assumed to provide an arbitrarily fine
+partition of the original state space; then the transport properties
+of $\vect L(t)$ are almost perfect approximations of the transport properties
+of $\ml(t)$, in particular $p_i(t)=\prob[x_t\in \Omega_i]$.
+
+\section{Floquet theory}
+\label{sec:floquet}
+
+As an effect of the periodicity of $\vect L(t)$ the propagator $\myphi(t+T)$
+satisfies
+\begin{equation}\label{compo-1}
+\myphi(t+T)=\myphi(t)\myphi(T),
+\end{equation}
+for all $t\ge 0$. This can be seen by considering $\vect Y(t)=\myphi(t+T)$. $\vect Y$ satisfies
+\[
+\frac{d\ }{dt}\vect Y(t)=\vect L(t+T)^T \vect Y(t)=\vect L(t)^T\vect Y(t),\quad \vect Y(0)=\myphi(T).
+\]
+When we consider this identity column-wise and use the propagator property of $\myphi(t)$ we get $\myphi(t+T)=\vect Y(t)=\myphi(t)\myphi(T)$.
+As a consequence of (\ref{compo-1}) we get for all integers $m=0,1,2,\ldots$ that
+\begin{equation}\label{compo-2}
+\myphi(t+mT)=\myphi(t)\myphi^m(T),
+\end{equation}
+and in particular we get the long-term evolution of the propagator:
+\begin{align}
+\label{eq:floq-13}  
+\myphi(mT)=\myphi^m(T).
+\end{align}
+In combination with Eq.~\eqref{eq:disc-8}, we therefore
+know the solution $\vect p(t)$ of the Master equation for all $t\ge 0$,
+if we can compute $\myphi(t)$ for $t\in (0,T]$.
+
+Since $\myphi(T)$ is a stochastic matrix, the spectrum $\sigma(\myphi(T))$
+of the matrix $\myphi(T)$ is contained in the circle in
+the complex plane, i.e., each eigenvalue $\lambda\in \sigma(\myphi(T))$
+satisfies $|\lambda|\le 1$. Furthermore $1\in\sigma(\myphi(T))$ is an
+eigenvalue with left eigenvector $\vect e$ and a right eigenvector $\mymu$
+satisfying
+$\myphi(T)\mymu=\mymu$.
+From now on, we assume $\myphi(T)$ to be irreducible and aperiodic such that the Perron Frobenius theorem the eigenvalue $\lambda=1$ is  non-negative componentwise, and unique (up to normalization $\sum_j\mu_j=1$).
+In this case $\mymu$ is the stationary measure in the sense that
+\begin{align}
+\label{eq:floq-14}  
+\myphi(mT) \mymu = \mymu,\quad m=0,1,2,\ldots,
+\end{align}
+and (more precisely) the asymptotic evolution of an initial probability distribution $\vect p(t=0)=\vect p_0$ by the process satisfies
+\begin{align}
+\label{eq:floq-15}  
+\myphi(mT)\vect p_0\to \mymu,\quad m\to\infty.
+\end{align}
+
+\section{Building the Markov state model}
+\label{sec:build-msm}
+
+If the discretization cells $\Omega_i$, $i=1,\ldots,n$ form a fine
+partition of the molecular state space, the Markov chain defined via
+the transition matrix $\vect P=\myphi^T(T)$ still is a fine-scale description of the
+dynamics.  Now we want to coarse our description much further by
+constructing a Markov State Model (MSM) for $\vect P$ with $k\ll n$
+macrostates: The resulting $k\times k$ MSM transition matrix $\hat{\vect P}$
+then defines the coarse grained long term kinetics that should
+approximate the original long term kinetics well. In Ref.~\cite{sarich2010approximation}
+and \cite{schuette2011markov} it
+has been shown how to do this if $\vect P$ satisfies the detailed balance
+condition: (1) Identify the cores of the metastable sets of the
+dynamics, (2) use them as milestones to construct an MSM in which the
+macrostates are the metastable core sets and $\hat{\vect P}$ is the transition
+matrix of the milestone process that models the jumping behavior of
+the original dynamics between the metastable regions.
+
+However, since we cannot assume $P$ to satisfy detailed balance, we
+instead follow the approach recently proposed in Ref.~\cite{sarich2014utilizing}.
+It allows to identify the metastable core sets for the
+non-reversible transition matrix $P$. Assume that this approach leads
+to the $k$ core sets $C_1,\ldots, C_k\subset S$, and we denote $C=S\setminus\cup_j C_j$. Following
+Ref.~\cite{djurdjevac2010markov}, Thm. 3.1, the coarse grained transition
+matrix $\hat{P}$ has to be computed as follows:
 \begin{enumerate}
-\item Eqn.~\eqref{eqn:tmp2} assumes Markovianity, which is not
-  necessarily true for a reduce dynamics $\vect p(t)$, see e.g.~\cite{prinz2011markov}.
-\item Numerical error from the finite difference introduced in
-  Eqn.~\eqref{eqn:tmp4}. The lag-time $\tau$ should not be too large
-  to control the finite difference error, and at the same time should
-  not be too small, because otherwise the statistical error would be
-  large, and the Markovianity would be disturbed.
-\item Although the original dynamics defined by generator $\ml(t)$ is
-  periodic, the reduced one defined by $\vect M(t)$ is not necessary
-  periodic, i.e.~$\vect M(t) \neq \vect M(t+T)$ in general.  In the
-  simulation of biomolecules, it is reasonable, in most cases to
-  assume a time-scale separation in the system. For example, the
-  conformational change of the molecules is much faster than the
-  covalent bond vibrations. Therefore, if the discretion $\{ S_1,
-  \cdots, S_n\}$ properly captures the slow dynamics of interest, in
-  the sense that within the lag-time $\tau$, the system is fully
-  relaxed to a local equilibrium in the set $S_i$, then it is clear
-  that the reduce system is periodic. It suggests that the lag-time
-  should be right in the spectrum gap: it is shorter than the dominant
-  implied timescale, and longer than the fast-relaxing time-scales.
+\item For the process associated with $P$ compute the forward and backward committors $q^\fwd_j$ and $q^\bwd_j$  for each core set $C_j$. This can be done by solving the linear equations
+\begin{align}
+(P-\id) q^\fwd_j(i) & =  0, \quad i\in C\\
+q^\fwd_j(i) & =  1,\quad i\in C_j\\
+q^\fwd_j(i) & =  0,\quad i\in C_l,l\not=j
+\end{align}
+and
+\begin{align}
+(P^b-\id) q^\bwd_j(i) & =  0, \quad i\in C\\
+q^\bwd_j(i) & =  1,\quad i\in C_j\\
+q^\bwd_j(i) & =  0,\quad i\in C_l,l\not=j
+\end{align}
+where $P^b$ denotes the transition matrix of the time-reversed process
+given by $P^b_{ji}=\mu_i P_{ij}/\mu_j$.
+
+Alternatively, the forward and
+backward committors can be sampled via the definitions: The forward
+committor $q^\fwd_j(i)$ is defined as the probability of visiting coreset
+$C_j$ next conditioned on being at state $i$.  The
+backward committor $q^\bwd_j(i)$  is defined as the probability
+of last coming from $C_j$ conditioned on being at state $i$.
+\item Compute $\hat{\mu}(j)=\sum_{i\in S} q^\bwd_j(i)\mu(i)$,
+  which is the invariant measure of the MSM
+\item Construct the MSM transition matrix $\hat{P}$ according to
+  \begin{align}
+    \label{eq:msm-tmatrix}
+    \hat{\vect P}_{jk}
+    = &
+    \frac{1}{\hat{\mu}(j)}
+    \langle (\vect P^b - \id) q^\bwd_j,q^\fwd_k \rangle_\mu,\qquad j\not= k, \\
+    \hat{\vect P}_{jj}
+    =&
+    1-\sum_{k\not=j} \hat{\vect P}_{jk}
+  \end{align}
+where the inner product is defined by
+$\langle u,v \rangle_\mu=\sum_{i\in S} u_i v_i \mu_i$.
 \end{enumerate}
 
-\subsection{Perodicity of the reduced dynamics: investigated by alanine dipeptide under oscillatory electric field}
+\section{Numerical example:
+  Alanine dipeptide under oscillatory electric field}
+
+If the spacial discretization is fine enough, the Markov jump
+process~\eqref{eq:disc-7} is a good approximation to the original
+MD~\eqref{eq:disc-1}.  In practice, it is firstly difficult to predict
+how many discret set is fine enough; Secondly, since the
+total configurational dimension of the system is $3N$ ($N$ being the
+number of atoms), it is prohibitive to do a very fine discretization
+over all DOFs for most of systems of practical interest.  In the
+simulation of biomolecules, in most cases it is reasonable to assume a
+time-scale separation in the system.
+For example, the conformational
+change of the molecules is much faster than the covalent bond
+vibrations. 
+% It should be noted that we do NOT assume that the fast time-scales are decoupled with the slow time-scales~\footnote{If the fast time-scales
+%   are decoupled from the slow ones, then the story would become much simpler,
+% however, this situation is lack of generality, we will not discuss.}.
+In this context,
+it is usually possible to pick a relatively small number of discrete sets that
+correctly describe the slow dynamics in the sense that
+the original dynamics fully relaxes in every set
+within the discretization time-step (denoted by $\tau$). Or equivalently the discretized
+dynamics~\eqref{eq:disc-7} is a good approximation to~\eqref{eq:disc-1}.
+One possible way to define the discretized set is to firstly find few collective
+variables, and then to discretize the dynamics as fine as possible only on these
+variables either by uniform or adaptive
+discretization~\cite{chodera2007automatic, prinz2011markov}.
+This process also suggests that the choice of the lag-time should be 
+shorter than the dominant implied timescale so that they can be resolved,
+and be longer than the fast time-scales to relax the unresolved dynamics
+within the discretized sets.
+However, it is in general difficult to tell in priori how to choose the collect
+variables, how fine the discretization should be and how large
+the time-steps should be.
+For large system, these questions are usually
+not trivial to answer.
+
 \begin{figure}
@@
 
-At this stage we do have any analytical result regarding the quality
-of approximating Eqn.~\eqref{eqn:tmp1} by
-Eqn.~\eqref{eqn:tmp2}.
-It is therefore useful to investigate the discussed approximations
-by a numerical example. The Markovianity of the reduce dynamics
-was extensively discussed in e.g.~\cite{prinz2011markov}, so we 
-will not touch this topic in the current paper. The choice of the lag-time
-will be discussed later, and in this subsection we focus on the periodicity
-of the reduced dynamics.
-Throughout this paper, we take the alanine dipeptide system
-under oscillatory EF, as an example, which was extensively studied by
-Ref.~\cite{wang2014exploring}.
-We choose the two dihedral angles $\phi$
-and $\psi$ as slow variables (see Fig.~\ref{fig:tmp1}), and the discretization
-is a uniform division of the $\phi$--$\psi$ plane. We denote the number of
-division on each dihedral by $K$.
-
+To illustrate how the procedure works in practice, it is therefore
+useful to investigate the discussed approximations by a numerical
+example.  We take the alanine dipeptide system under an oscillatory EF,
+as an example, the non-equilibrium MD simulation of which was
+extensively studied by Ref.~\cite{wang2014exploring}.  
 The alanine dipeptide was put into the local thermostating
@@
 \redc{Write a lot of details on non-equilibrium MD.}  The branching
-trajectories were each 1000~ps long, and the system reaches
-non-equilibrium steady state in roughly 300~ps. We compute the
-generator from non-equilibrium trajectories in time interval $[t_1,
-t_2]$. If the reduced dynamics were periodic, then generator $\vect
-M(t)$ would not depends on the choice of the time interval. We compute
-the reduced generator by two discretizations $K=2$ and $K=20$, and two
-choices of time intervals $[0, 40]$ and $[320, 1000]$, and then
-compare the results with the brute force result in
-Fig.~\ref{fig:tmp2}. In the figure, we show the time-dependent
-probability $\mathbb P\big(\phi\in[0,180), \psi\in [0,180)\big)$.
-Using $K=2$ the dynamics depends on the time interval used for
-calculating the generator: using time intervals $[320, 1000]$ the reduced
-dynamics can only reproduces the brute force result in $[0, 40]$,
-while using time intervals $[0, 40]$ the reduced dynamics can only
-reproduces the brute force result after 300~ps.  This shows that the
-reduced dynamics is lack of periodicity.  The reason is that the
-discretization is too coarse so that the dynamics cannot be fully
-equilibriated within the lag-time $\tau$ in each discretized set.  For
-$K=20$, the reduced dynamics does not depend on the time interval of
-calculating the generator, and is consistent with the brute force
-non-equilibrium simulation within the error bar. Therefore, the $K=20$
-is a reliable discretization for the alanine dipeptide system.
+trajectories were each 4000~ps long, and the system reaches
+non-equilibrium steady state in roughly 300~ps.
 
+We choose the
+two dihedral angles $\phi$ and $\psi$ as collective variables (see
+Fig.~\ref{fig:tmp1}), and the discretization is a uniform division of
+the $\phi$--$\psi$ plane. We denote the number of division on each
+dihedral by $K$. In the following subsections, we investigate the discretization
+quality firstly by considering the choice of $K$ and time-step $\tau$. Then
+the discretized dynamics is compared with original (non-equilibrium brute force simulation)
+via considering the steady state probability density, the first mean hitting time
+and the forward and backward committors.
+
+\subsection{Discretizing the dihedral angles}
 \begin{figure}
@@
 
+We estimate the discretized generator $L(t), \ t\in[0,T)$
+from non-equilibrium trajectories generated by $\ml(t)$ in time interval $[t_1,
+t_2]$.
+Due to the periodicity of $\ml(t)$, if the discretized dynamics approximate the original
+dynamics good enough, generator  $L(t)$ should not depend on in which interval
+it is estimated, provided that the initial state of the system
+is not very far from the steady state.
+This is a good indicator of the discretization quality.
+We compute $L(t)$ by two discretizations $K=2$ and $K=20$, and two
+choices of time intervals $[0, 80]$~ps and $[320, 400]$~ps, and then
+compare the time-dependent
+probability $\prob\big(\phi_t\in[0,180), \psi_t\in [0,180)\big)$
+with the brute force result in
+Fig.~\ref{fig:tmp2}. 
+Using $K=2$ the dynamics depends on the time interval used for
+calculating the generator: using time interval $[0, 80]$~ps the discretized
+dynamics deviates the brute force result,
+while using time interval $[320, 400]$~ps the discretized dynamics can only
+reproduces the brute force result after 300~ps.  This therefore indicates poor 
+approximations to the original dynamics with $K=2$. The reason is that the
+discretization is too coarse so that the dynamics cannot be fully
+equilibriated within the lag-time $\tau$ in each discretized set,
+therefore, the discretization presents state dependency.  For
+$K=20$, the discretized dynamics does not depend on the time interval of
+calculating the generator, and is consistent with the brute force
+non-equilibrium simulation within the error bar. Therefore, in this paper we use $K=20$
+to discretize  the dihedral angle space of the alanine dipeptide.
+For a good statistical accuracy, if not stated otherwise,
+we will use the full trajectories, i.e.~a time interval of
+$[0,4000]$~ps for estimating the discretized dynamics.
+
 \subsection{The choice of lag-time $\tau$}
-
-As discussed before, the lag-time should be chosen a value that lies
-in the spectrum gap of the original dynamics, so that it resolves the
-slow dynamics, and at the same time relaxes the fast dynamics. In
-practice, it is very difficult to estimate the lag-time in
-priori. Therefore, we discretize the original non-equilibrium based on
-different choices of $\tau$ (0.5, 1.0, 2.0 and 5.0~ps) and compare the
-time dependent probability of $\mathbb P\big(\phi\in[0,180), \psi\in
-[0,180)\big)$ estimated out of the reduced dynamics in
-Fig.~\ref{fig:tmp3}.  All cases use idential discretization: $K=20$.
-It is clear that when lag-time is close to the period (10~ps), the
-reduced dynamics cannot resolve the probability change within a
-period. However, the large lag-times are able to capture the
-the overall log time behavior of the probability.
-We observe no significant difference between $\tau=0.5$ and
-$\tau=1.0$~ps, which means the reduced dynamics is not very sensitive
-to the choice of $\tau$.
 
@@
 
-% The definition of the conformations
-% $\confaa$, $\confab$, $\confba$, $\confbb$ and $\confc$ are presented
-% by Fig.~\ref{fig:tmp1}.  We are interested in the time-dependent
-% probability of the conformations. In Fig.~\ref{fig:tmp2}, the brute
-% force molecular dynamics simulation result
-% (i.e.~Eqn.~\eqref{eqn:tmp1}) is compared with different discretization
-% methods, which give different generator in Eqn.~\eqref{eqn:tmp2}. For
-% clarity, only the probability of conformation $\confc$ is plotted.  In
-% the figure, ``5 sets'' means the $\phi$-$\psi$ space is discretized by
-% 5 sets as shown in Fig.~\ref{fig:tmp1}, ``Uni. $M=$'' stands for the
-% uniform discretization on $\phi$-$\psi$ space, and $M$ denotes the
-% number of bins on both $\phi$ and $\psi$ directions.  Both $M=10$ and
-% 20 methods present very good accuracy.  Please notice that for $M=10$,
-% for example, the number of discretized sets is $n=M^2=100$.  The
-% lag-time in all cases is chosen to be $\tau = 0.5$~ps. A test with
-% $\tau = 1.0$~ps shows good consistency with $\tau = 0.5$~ps.
-% The generator
-% $\vect M(t)$ is assumed to be periodic, and is estimated from the
-% trajectories from $t=300$ to 1000~ps.
+As discussed before, the lag-time should be chosen a value that lies
+in the spectrum gap of the original dynamics, so that it resolves the
+slow dynamics, and at the same time relaxes the fast dynamics. In
+practice, it is very difficult to estimate the lag-time in
+priori. Therefore, we consider 
+different choices of $\tau$ (0.5, 1.0, 2.0 and 5.0~ps)
+discretizing the same original dynamics, and compare the
+time-dependent probability $\prob\big(\phi\in[0,180), \psi\in
+[0,180)\big)$ calculated from different time discretization with the brute force simulation
+of the original dynamics
+(see Fig.~\ref{fig:tmp3}).  All cases use idential dihedral angle discretization: $K=20$.
+It is clear that when lag-time is close to the period (10~ps), the
+discretized dynamics cannot resolve the probability change within a
+period. However, it is surprising  that the large lag-times are able to capture the
+the overall log time behavior of the probability.
+We observe no significant difference between $\tau=0.5$ and
+$\tau=1.0$~ps, which means the discretized dynamics is not very sensitive
+to the choice of $\tau$. 
+We do not investigate the small $\tau$ limit, because saving trajectories
+more frequently requires more hard disk space, and is usually not preferred.
 
-% The phenomena presented by Fig.~\ref{fig:tmp2} is very similar to the
-% equilibrium MSM: the quality of the MSM depends on how accurate the
-% eigenfunctions are approximated by the discretization. The ``5 sets''
-% method achieve better accuracy than the uniform $M=5$ method by using
-% much less DOFs, because it captures the positive and negative signs of
-% the eigenfunctions. With larger $M$ the discretization error of the
-% eigenfunctions becomes smaller, so the accuracy of the MSM is improved.
-
-\section{Floquet theory}
-
-The reduced dynamics will not provide a lot further interesting
-information until we introduce the MSM to analyze the reduced dynamics. The main
-difficulty is that the reduced dynamics is time-inhomogeneous, however, this can
-be overcome by the Floquet theory.
-The Floquet theory states that for a periodic system, e.g.~Eq.~\eqref{eqn:tmp2}, the solution can be written as
-\begin{align}
-  \label{eqn:tmp5}
-  \vect p(t)  = \vect Q(t) e^{t\vect B} \vect p(0)
-\end{align}
-where $\vect Q(t)$ is periodic and $\vect B$ is a constant matrix.  To
-analyze the spectrum, it is not difficult to infer the implied
-timescales, on which the system relaxes to the periodic steady states
-defined by $\vect Q(t)$.
-Assume that the fundamental solution to Eqn.~\ref{eqn:tmp2} is denoted by $\boldsymbol \Phi(t)$, then
-the matrix $\vect B$ can be expressed by
-\begin{align}
-  e^{T\vect B} = \boldsymbol \Phi^{-1}(0)\cdot \boldsymbol \Phi(T)
-\end{align}
-It is fully justified by choosing $ \boldsymbol \Phi(0) = I$, then
-$e^{T\vect B}$ is estimated by evolving the fundamental solutions by
-one period.
-Since it is obvious that $Q(kT) = Q(0) = I,\ k\in\mathbb N$, if we only consider the state of the system
-at time $kT$, then from Eq.~\eqref{eqn:tmp5} we have
-\begin{align}
-  \label{eqn:tmp5a}
-  \vect p(kT)  = \boldsymbol\Phi^k(T) \,\vect p(0),
-\end{align}
-which is a time-homogeneous Markov process with transition matrix $\boldsymbol\Phi(T)$.
-Please notice that in general this Markov process is not reversible.
-Calculating the eigenvalues of $\boldsymbol\Phi(T)$ reveals the
-implied timescales on which the non-equilibrium dynamics converges to
-the periodic steady state.
-The Eq.~\eqref{eqn:tmp5a} allows one to use the available techniques for time-homogeneous
-Markov jump process (especially for irreversible processes)
-to analyze the time-inhomogeneous dynamics Eq.~\eqref{eqn:tmp2}.
-However, it can only resolve the processes that are longer than the period $T$.
-Therefore, rather than going directly from Eq.~\eqref{eqn:tmp1} to Eq.~\eqref{eqn:tmp5a},
-we would like to keep the intermediate step Eq.~\eqref{eqn:tmp2}.
-In the following we compare the MSM with the brute force non-equilibrium simulation
-by considering several properties that are of special interest.
-
-% The largest non-trivial timescales is given in table
-% Tab.~\ref{tab:tmp1}, which corresponds very well to the dynamics of the  $\confc$ probability.
-% \begin{table}
-%   \centering
-%   \caption{The first four non-trivial timescales calculated from ${\vect B}$. The unit of time in the table is ps.
-%     $\tau$ is the lag time used to calculate the generator~\eqref{eqn:tmp4}. $[T_0,T_1]$ is the time interval,
-%     in which the generator is estimated from the MD trajectories. The 5th eigenvalue of uniform decomposition with $\tau=8.0$~ps is not real, so
-%     the corresponding timescale is not calculated.
-%   }
-%   \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}c ccc rrrr}\hline\hline
-%     Method  &  $M$ & $\tau$ & $[T_0,T_1]$ &   $t_2$ &   $t_3$ &   $t_4$ &   $t_5$  \\\hline
-%     5 sets  & --   & 0.5    & $[300,1000]$    &  72.4 & 17.8 &  2.1 & 2.8    \\
-%     Uniform & $05$ & 0.5    & $[300,1000]$    &  53.6 & 17.4 &  9.4 & 2.8    \\
-%     Uniform & $10$ & 0.5    & $[300,1000]$    & 107.2 & 27.0 & 16.4 & 3.6    \\
-%     Uniform & $20$ & 0.5    & $[300,1000]$    & 118.6 & 30.4 & 20.3 & 4.3    \\
-%     Uniform & $30$ & 0.5    & $[300,1000]$    & 120.6 & 31.1 & 20.9 & 4.4    \\\hline
-%     Uniform & $20$ & 0.5    & $[0,40]$    & 156.5 & 34.4 & 20.7 & 4.4    \\
-%     Uniform & $20$ & 0.5    & $[0,80]$    & 133.8 & 32.8 & 20.4 & 4.4    \\
-%     Uniform & $20$ & 0.5    & $[0,120]$   & 127.5 & 32.0 & 20.3 & 4.3    \\
-%     Uniform & $20$ & 0.5    & $[0,200]$   & 122.0 & 31.3 & 20.3 & 4.3    \\
-%     Uniform & $20$ & 0.5    & $[0,320]$   & 120.4 & 31.0 & 20.3 & 4.3    \\\hline
-%     Uniform & $20$ & 1.0    & $[300,1000]$    & 119.8 & 30.5 & 21.7 & 4.9   \\
-%     Uniform & $20$ & 2.0    & $[300,1000]$    & 117.8 & 29.2 & 21.5 & 5.3   \\
-%     Uniform & $20$ & 4.0    & $[300,1000]$    & 114.2 & 27.0 & 20.2 & 4.8   \\
-%     Uniform & $20$ & 8.0    & $[300,1000]$    & 110.6 & 25.0 & 18.1 & --   \\
-%     \hline\hline
-%   \end{tabular*}
-%   \label{tab:tmp1}
-% \end{table}
-
-% \section{Numerical investigation of the accuracy of the MSM}
-
-% At this stage we do have any analytical result regarding the quality
-% of approximating Eqn.~\eqref{eqn:tmp1} by
-% Eqn.~\eqref{eqn:tmp2}. However, it would be useful to do some
-% numerical experiments. We have studied the alanine dipeptide system
-% under oscillatory EF, which was studied by
-% Ref.~\cite{wang2014exploring}. We use the two dihedral angles $\phi$
-% and $\psi$ as slow variables. The discretization is the uniform division of
-% the $\phi$--$\psi$ plan in to 2-dimentional bins. 
-% The quality of the MSM~\eqref{eqn:tmp5a} can be checked by comparing the physical properties
-% computed from the MSM and those computed by the brute force non-equilibrium molecular
-% dynamics simulation from Ref.~\cite{wang2014exploring}.
-
-\subsection{Steady state distribution and eigenfunctions}
-We investigate the steady state properties distribution at time $kT$. To make it comparible to
-the free energy in equilibrium case, we take the logrithm of the properties, i.e.
-\begin{align}
-  \label{eq:num-tmp1}
-  F_{\textrm{st}}(\phi,\psi) = \lim_{k\rightarrow\infty} -k_B\mathcal T \log p(\phi,\psi,kT),
-\end{align}
-where $k_B$ is the Boltzmann constant and $\mathcal T$ is the temperature of the system.
-The result is given in Fig.~\ref{fig:num-1}. A good consistency between the brute force
-MD simulation and the MSM is observed.
+\subsection{Steady state distribution}
 
@@
   \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-1.eps}
-  \caption{The steady state distribution calculated by brute force non-equilibrium comparing with MSM.}
+  \caption{The steady state distribution calculated by brute force non-equilibrium is compared with that by the discretized dynamics.}
   \label{fig:num-1}
@@
 
-% \begin{figure}
-%   \centering  
-%   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-2-simple.eps}
-%   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-3-simple.eps}
-%   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-4-simple.eps}
-%   \caption{The first three non-trivial eigenfunctions cdalculated by the MSM.}
-%   \label{fig:num-2}
-% \end{figure}
+An important check of the discretized dynamics is that if it reporduces the steady probability
+density $\mymu$ of $\myphi(T)$.
+To make it comparible to
+the free energy in equilibrium case, we take the logrithm of the properties, i.e.
+\begin{align}
+  \label{eq:num-tmp1}
+  F_{\textrm{st}}(\phi,\psi) = \lim_{m\rightarrow\infty} -k_B\mathcal T \log p(\phi,\psi,mT),
+\end{align}
+where $k_B$ is the Boltzmann constant and $\mathcal T$ is the temperature of the system.
+The result is given in Fig.~\ref{fig:num-1}. A good consistency between the brute force
+MD simulation and the discretized dynamics is observed.
 
@@
   \includegraphics[width=0.4\textwidth]{fig/t040/cluster.marco/fig-cluster-2.eps}
-  \caption{The coreset identification. Different colors indicate different coresets: $C_{R_\alpha}$ (yellow), $C_\beta$ (red) and $C_{L_\alpha}$ (green).
+  \caption{The coreset identification. Different colors indicate different coresets: $C_{\confaa}$ (yellow), $C_\beta$ (red) and $C_{\confc}$ (green).
     The blue color means out of any coreset. (By Marco)}
@@
 
-The coresets (see Fig.~\ref{fig:cluster}) are denoted by $C_{R_\alpha}$ (yellow), $C_\beta$ (red) and $C_{L_\alpha}$ (green), which correspond to
+The coresets (see Fig.~\ref{fig:cluster}) are denoted by $C_{\confaa}$ (yellow), $C_\beta$ (red) and $C_{\confc}$ (green), which correspond to
 right-handed alpha-helix, beta-sheet and left-handed alpha-helix, respectively.
 
-\subsection{Committors}
+\subsection{First mean hitting time}
 
-The forward committor $q^\fwd_i(\phi,\psi)$ of a coreset $C_i,\ i\in\{R_\alpha, \beta, L_\alpha\}$ is defined as
-the probability of visiting coreset $C_i$ next conditioned on being at configuration $(\phi,\psi)$.
-The backward committor $q^\bwd_i(\phi,\psi)$ of a coreset $C_i,\ i\in\{R_\alpha, \beta, L_\alpha\}$ is defined as
-the probability of last coming from $C_i$  conditioned on being at configuration $(\phi,\psi)$.
-For  reversible Markov processes, the forward and backward committors are identical, however, it is in general not the case
-for irreversible processes. Please see Fig.~\ref{fig:num-3}--\ref{fig:num-5} for the committors.
+Since the largest first mean hitting time (starting fom coreset $\confaa$ to $\confc$) is
+longer than 600~ps, if we use the trajectories of length 4000~ps, the
+results will be biased. Therefore, we use 100 non-equilibrium trajectories
+of $2\times 10^5$~ps instead.
+The first mean hitting time is presented in Fig.~\ref{fig:num-6}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-3.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-msm-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-msm-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-msm-3.eps}
+  \caption{The first mean htting time comparsion between the brute
+    force simulation (first row) and the discretized dynamics (second row).  From left
+    to right are first mean hitting time to coresets $C_{\confc}$,
+    $C_{\confaa}$ and $C_{\beta}$, respectively}
+  \label{fig:num-6}
+\end{figure}
+
+\subsection{Forward and backward committors}
+
+The forward committor $q^\fwd_i(\phi,\psi)$ of a coreset $C_i,\
+i\in\{\confaa, \beta, \confc\}$ is defined as the probability of
+visiting coreset $C_i$ next conditioned on being at configuration
+$(\phi,\psi)$.  The backward committor $q^\bwd_i(\phi,\psi)$ of a
+coreset $C_i,\ i\in\{\confaa, \beta, \confc\}$ is defined as the
+probability of last coming from $C_i$ conditioned on being at
+configuration $(\phi,\psi)$.  For reversible Markov processes, the
+forward and backward committors are identical, however, it is in
+general not the case for irreversible processes. Please see
+Fig.~\ref{fig:num-3}--\ref{fig:num-5} for the committors.
 
@@
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-1.eps}
-  \caption{The forward $q^\fwd_{L_\alpha}$ and backward committors $q^\bwd_{L_\alpha}$ computed by MSM (second row) is compared with those computed by brute force non-equilibrium simulations (first row).}
+  \caption{The forward $q^\fwd_{\confc}$ and backward committors
+    $q^\bwd_{\confc}$ computed by discretized dynamics (second row) is compared with
+    those computed by brute force non-equilibrium simulations (first
+    row).}
   \label{fig:num-3}
@@
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-2.eps}
-  \caption{The forward $q^\fwd_{R_\alpha}$ and backward $q^\fwd_{R_\alpha}$ committors computed by MSM (second row) is compared with those computed by brute force non-equilibrium simulations (first row).}
+  \caption{The forward $q^\fwd_{\confaa}$ and backward
+    $q^\bwd_{\confaa}$ committors computed by discretized dynamics (second row) is
+    compared with those computed by brute force non-equilibrium
+    simulations (first row).}
   \label{fig:num-4}
@@
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-3.eps}
-  \caption{The forward $q^\fwd_{\beta}$ and backward $q^\fwd_{\beta}$ committors computed by MSM (second row) is compared with those computed by brute force non-equilibrium simulations (first row).}  
+  \caption{The forward $q^\fwd_{\beta}$ and backward $q^\bwd_{\beta}$
+    committors computed by discretized dynamics (second row) is
+    compared with those computed by brute force non-equilibrium
+    simulations (first row).}
   \label{fig:num-5}
@@
 
-\subsection{First mean hitting time}
+\subsection{Building MSM}
+Following the process described in Sec.~\ref{sec:build-msm}, we are able to build a 
+three states MSM for the alanine dipeptide system.
+The leading eigenvalues of $P$ is compared with those of the MSM, i.e.~$\hat P$ in
+Tab.~\ref{tab:tmp1}.
 
-The first mean hitting time is presented in Fig.~\ref{fig:num-6}.
+\begin{table}
+  \centering
+  \caption{
+    The eigenvalue comparison
+  }
+  \begin{tabular*}{0.4\textwidth}{@{\extracolsep{\fill}}c rr}\hline\hline
+      &  $\lambda_2$ & $\lambda_3$ \\\hline
+    $P$         &0.907  &0.686        \\
+    $\hat P$    &0.914  &0.744        \\
+    \hline\hline
+  \end{tabular*}
+  \label{tab:tmp1}
+\end{table}
 
@@
   \centering
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-1.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-3.eps}\\
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-msm-1.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-msm-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-msm-3.eps}
-  \caption{The first mean htting time comparsion between the brute force simulation (first row) and the MSM (second row).
-  From left to right are first mean hitting time to coresets $C_{L_\alpha}$, $C_{R_\alpha}$ and $C_{\beta}$, respectively}  
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-eig-vec-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-eig-vec-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-eig-vec-4.eps}\\
+  \caption{The eigenfunctions of $P$.}
   \label{fig:num-6}
@@
 
-% \section{Discussions}
-% \subsection{The periodicity of the reduced dynamics}
-
-% As discussed before, if the reduced dynamics captures the slow
-% dynamics of interest, then the reduced dynamics is also periodic,
-% which implies that the generator $M(t)$ can be estimated from any time
-% interval by Eq.~\eqref{eqn:tmp4}. In practice, the reduced dynamics
-% may not be perfectly periodic. The generator calculated from
-% different time intervals can be used to test the periodicity of the
-% reduced dynamics. The results are shown in Tab.~\ref{tab:tmp1} and
-% Fig.~\ref{fig:tmp2}.  The dependency with respect to the time
-% interval, in which the generator is calculated, indicates the reduced
-% dynamics is not perfectly periodic. The reduced dynamics from $[0,40]$
-% reproduces the best probability in interval $[0,40]$, and worst in the
-% steady state. Moreover, the leading non-trivial timescale is also off
-% (see Tab.~\ref{tab:tmp1}), while the accuracy of the second and third
-% non-trivial timescales are better, because they are comparable to the
-% period, 40~ps, in which the dynamics is relaxed. The reduced dynamics
-% from $[300,1000]$ reproduces the best steady state probability, while
-% worst in reproducing the initial relaxation process. The reduced
-% dynamics from $[0,320]$ is indistinguishable from the one from
-% $[300,1000]$, which implies that in practice, one only have to
-% simulation relatively short non-equilibrium trajectories (that are
-% almost relaxed), and compute the generator from it to build the reduced dynamics. \redc{This saves a great
-% amount of computational resources comparing with calculating the
-% reduced dynamics only from steady state trajectories.}
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.5\textwidth]{fig/t040/fig-cg-prob-range.eps}  
-%   \caption{The time-dependent probability of conformation
-%     $\confc$. The brute force MD simulation is compared with reduced
-%     dynamics, the transition matrix of which are calculated from
-%     different ranges. The red shadow region is the statistical uncertainty of the brute force MD simulation.
-%     The inserts show the zoom-ined probability at the relaxation stage $[0,120 ]~\textrm{ps}$ and at the steady state $[800,880 ]~\textrm{ps}$.}
-%   \label{fig:tmp2}
-% \end{figure}
-
-% \subsection{The choice of lag time $\tau$}
-% Table~\ref{tab:tmp1} shows a clear trend of worse accuracy with
-% increased $\tau$, however, the timescales are not very sensitive to
-% the choice of lag time $\tau$.
-
-% \section{To do}
-
-% \begin{itemize}
-% \item Theoretical analysis of the accuracy of the discretization, a
-% generalization of the equilibrium case. the numerical results indicate
-% a very close link. The perodicity is very nice, if the generator is
-% ``continuous'', then it should be uniformly continuous, then it should
-% be possible to develop estimates that are similar to the equilibrium
-% case.
-% \item More tests on the effect of choosing different lag-time $\tau$ (0.5 and 1.0~ps are done).
-% \item More theoretical consideration on the Floquet theory, what is the
-% explict form of matrix $\vect B$, and does it has any nice properties,
-% such as self-joint.
-% \end{itemize}
-
-\section{Approximation quality of the Markov state model}
-
-The whole Floquet theory can be applied to the original dynamics, and we denote that the resulting transition matrix by $\psi(T)$, then
-the time-dependent probability density can be written as
-\begin{align*}
-  \rho(\vect x, kT) = 
-\end{align*}
-
-In general, the original dynamics of the molecular system under perodical external driven
-is not reversible, see the discussion in Sec.~\ref{sec:revs}. However, we can assume the,
+\appendix
 
@@
 
-Now we assume the overdamped dynamics
-\begin{align}\label{eqn:tmp7}
-  dx_t = -\nabla_x V(x_t,t) dt + \sigma dw_t
-\end{align}
-where $V$ is the time-dependent and $T$-periodic potential. For simplicity we denote the force by $F(x_t,t) = -\nabla_x V(x_t, t)$. $dw_t$ is
-the standard Wiener process.
+We consider the gonverning dynamics Eq.~\eqref{eq:disc-1}.
+For simplicity we denote the force by $F(x_t,t) = -\nabla_x V(x_t)+ E(t)D(x_t) $.  We denote $\sigma =  \sqrt{2\beta^{-1}} $.
 According to Girsanov, we have
@@
 \end{align}
-According to the  Einstein relation, the temperature $\mathcal T = \sigma^2/2$, we denote $\beta = 1/{\mathcal T} = 2/\sigma^2$.
-Take the limit of infinite small time interval, and notice the equilibrium
-invariant probability density with respect to potential $V(x,0)$ satisfies $\mu(x) \propto e^{-\beta V(x,0)}$,
+% According to the  Einstein relation, the temperature $\mathcal T = \sigma^2/2$, we denote $\beta = 1/{\mathcal T} = 2/\sigma^2$.
+Take the limit of infinite small time interval, notice the equilibrium
+invariant probability density with respect to potential $V(x,0)$ satisfies $\mymu(x) \propto e^{-\beta V(x,0)}$, and replace $\sigma^2$ by $2\beta^{-1}$,
 \begin{align}
@@
   =&\,
-  \frac{\mu(x_0)}{\mu(x_T)}\times
+  \frac{\mymu(x_0)}{\mymu(x_T)}\times
   \exp\bigg\{
@@
 \end{align}
-By changing notation $x^\dagger$ back to $x$, and comparing with~\eqref{eq:tmp9}, the reversed dynamics is subject to the Eq.~\eqref{eqn:tmp7},
+By changing notation $x^\dagger$ back to $x$, and comparing with~\eqref{eq:tmp9}, the reversed dynamics is subject to the Eq.~\eqref{eq:disc-1},
 i.e.~$dp^\dagger = dp$.

### 2014-09-01 alanine.nanma/template/tools/msm/app/calculate.coreset.msm.cpp
fix bug

@@ -164,6 +164,29 @@ void apply_trans (const vector<vector<double > > & tmatrix,
   }
 }
 
+void reverse_tmatrix (const vector<vector<double > > & tmatrix,
+		      const vector<double > & dist,
+		      vector<vector<double > > & omatrix)
+{
+  omatrix = tmatrix;
+  for (unsigned ii = 0; ii < tmatrix.size(); ++ii){
+    for (unsigned jj = 0; jj < tmatrix[ii].size(); ++jj){
+      if (dist[jj] != 0){
+	omatrix[jj][ii] = dist[ii] * tmatrix[ii][jj] / dist[jj];
+      }
+      else {
+	if (dist[ii] * tmatrix[ii][jj] != 0){
+	  cerr << "problem of reverse" <<endl;
+	}
+	else{
+	  omatrix[jj][ii] =0.;
+	}
+      }
+    }
+  }  
+}
+
+
 int main(int argc, char * argv[])
 {
   std::string ifwfile, ibwfile, idfile, isfile, ismfile, ifloquetfile, isdfile, otmfile;
@@ -208,18 +231,6 @@ int main(int argc, char * argv[])
     mymap[setMap[ii]] = ii;
   }
 
-  vector<vector<double > > tmatrix;
-  unsigned nstate1;
-  read_tmatrix (ifloquetfile, tmatrix, nstate1);
-  if (nstate1 != nstate){
-    cerr << "the largest set file is not consistent with the transition matrix" << endl;
-    return 1;
-  }
-  vector<vector<double > > pmatrix(tmatrix);
-  for (unsigned ii = 0; ii < nstate; ++ii){
-    pmatrix[ii][ii] -= 1.;
-  }
-
   vector<unsigned > clusterMap;
   unsigned numCluster = load_cluster_map (ismfile, nbin, clusterMap);
   vector<unsigned > clusterMapOrig (nstate, 0);
@@ -233,17 +244,37 @@ int main(int argc, char * argv[])
       }
     }
   }
-  // for (unsigned ii = 0; ii < nstate; ++ii){
-  //   printf ("%d\n", clusterMapOrig[ii]);
-  // }
-  
 
+  vector<vector<double > > tmatrix;
+  unsigned nstate1;
+  read_tmatrix (ifloquetfile, tmatrix, nstate1);
+  if (nstate1 != nstate){
[…]

### 2014-09-01 alanine.nanma/template/tools/msm/app/calculate.coreset.msm.cpp
add coreset projection of the time-dep prob

@@ -192,7 +192,7 @@ int main(int argc, char * argv[])
   std::string ifwfile, ibwfile, idfile, isfile, ismfile, ifloquetfile, isdfile, otmfile;
   unsigned nbin;
   
-  po::options_description desc ("Calculates the forward and backward commitor.\nAllow options");
+  po::options_description desc ("Calculates the MSM based on coreset milestoning.\nAllow options");
   desc.add_options()
       ("help,h", "print this message")
       ("num-bin,n", po::value<unsigned > (&nbin)->default_value (20), "number of blocks.")

### 2014-09-01 alanine.nanma/template/tools/msm/app/calculate.coreset.proj.cpp

@@ -1,0 +1,151 @@
+#include <algorithm>
+#include <fstream>
+#include <iomanip>
+#include <iostream>
+#include <iterator>
+#include <list>
+#include <map>
+#include <set>
+#include <sstream>
+#include <string>
+#include <queue>
+#include <cmath>
+#include <boost/program_options.hpp>
+#include <vector>
+#include "StringSplit.h"
+#include "BlockAverage.h"
+#include "MetaSet.h"
+
+#define MaxLineLength 65536
+
+namespace po = boost::program_options;
+using namespace std;
+
+void load_committor (const string & file,
+		     vector<vector<double > > & fwq)
+{
+  ifstream fpname (file.c_str());
+  if (!fpname){
+    std::cerr << "cannot open file " << file << std::endl;
+    exit( 1);
+  }
+  char nameline [MaxLineLength];
+  unsigned countFile = 0;
+  fwq.clear();
+  while (fpname.getline(nameline, MaxLineLength)){
+    if (nameline[0] == '#') continue;
+    vector<string > words;
+    StringOperation::split (nameline, words);
+    if (countFile == 0){
+      fwq.resize (words.size());
+    }
+    else {
+      if (fwq.size() != words.size()){
+	cerr << "format error of committor at line: " << nameline << endl;
+	exit (1);
+      }
+    }
+    for (unsigned ii = 0; ii < words.size(); ++ii){
+      fwq[ii].push_back (atof(words[ii].c_str()));
+    }
+  }
+}
+
+void read_tmatrix (const string & filename,
+		   vector<vector<double > > & tmatrix,
+		   unsigned & nstate)
+{
+  ifstream fpname (filename.c_str());
+  if (!fpname){
+    std::cerr << "cannot open file " << filename << std::endl;
+    exit(1);
+  }
+  char valueline [MaxLineLength];
+  int countLine = 0;
+  while (fpname.getline(valueline, MaxLineLength)){
+    vector<string > words;
+    StringOperation::split (string(valueline), words);
+    if (countLine == 0){
+      nstate = words.size();
+      tmatrix.resize(nstate);
+      for (unsigned ii = 0; ii < nstate; ++ii){
+	tmatrix[ii].resize(nstate);
+      }
+    }
+    if (words.size() != nstate){
+      cerr << "format error of tmatrix reading " << endl;
+      exit (1);
+    }
[…]

### 2014-09-01 alanine.nanma/template/tools/msm/app/calculate.coreset.evlove.cpp
evolve the prob based on coreset MSM

@@ -1,0 +1,256 @@
+#include <algorithm>
+#include <fstream>
+#include <iomanip>
+#include <iostream>
+#include <iterator>
+#include <list>
+#include <map>
+#include <set>
+#include <sstream>
+#include <string>
+#include <queue>
+#include <cmath>
+#include <boost/program_options.hpp>
+#include <vector>
+#include "StringSplit.h"
+#include "BlockAverage.h"
+#include "MetaSet.h"
+
+#define MaxLineLength 65536
+
+namespace po = boost::program_options;
+using namespace std;
+
+unsigned load_cluster_map (const string & file,
+			   const unsigned & nbin,
+			   vector<unsigned > & clusterMap)
+{
+  clusterMap.resize(nbin*nbin);
+  FILE * fp = fopen (file.c_str(), "r");
+  if (fp == NULL){
+    cerr << "cannot open file " << file <<  endl;
+    exit(1);
+  }
+  unsigned max = 0;
+  for (unsigned ii = 0; ii < nbin * nbin; ++ii){
+    if (fscanf (fp, "%d", &clusterMap[ii]) != 1){
+      cerr << "error reading " << file << endl;
+      exit(1);
+    }
+    if (clusterMap[ii] > max) max = clusterMap[ii];
+  }
+  return max;
+}
+
+void load_steady_dist (const string & file,
+		       vector<double > & dist)
+{
+  FILE * fp = fopen (file.c_str(), "r");
+  if (fp == NULL){
+    cerr << "cannot open file " << file <<  endl;
+    exit(1);
+  }
+  double tmp;
+  dist.clear ();
+  while (1 == fscanf(fp, "%lf", &tmp)){
+    dist.push_back (tmp);
+  }
+  fclose (fp);
+}
+
+void load_committor (const string & file,
+		     const unsigned & ncluster,
+		     vector<vector<double > > & fwq)
+{
+  FILE * fp = fopen (file.c_str(), "r");
+  if (fp == NULL){
+    cerr << "cannot open file " << file <<  endl;
+    exit(1);
+  }
+  double tmp;
+  unsigned countC = 0;
+  fwq.clear();
+  fwq.resize(ncluster);
+  while (1 == fscanf(fp, "%lf", &tmp)){
+    if (countC == ncluster){
+      countC = 0;
+    }
+    fwq[countC].push_back (tmp);
+    countC++;
+  }
+  fclose (fp);
+}
+
+
[…]

### 2014-09-02 writedown/period.noneq.msm/paper.tex
add t-d prob of coresets

@@
   \centering  
-  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.40/fig-dist.eps}
+  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.40.steadyDist//fig-dist.eps}
   % \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-dist-msm.eps}
@@
   }
-  \begin{tabular*}{0.4\textwidth}{@{\extracolsep{\fill}}c rr}\hline\hline
-      &  $\lambda_2$ & $\lambda_3$ \\\hline
-    $P$         &0.907  &0.686        \\
-    $\hat P$    &0.914  &0.744        \\
+  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}c rrr}\hline\hline
+      &  $\lambda_2$ & $\lambda_3$ & $\lambda_4$ \\\hline
+    $P$         &0.907  &0.686 & 0.553       \\
+    $\hat P$    &0.914  &0.744 & --       \\
     \hline\hline
@@
 \end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.40/fig-coreset-prob.eps}
+  \caption{The time-dependent probability $\hat P_l$. Solid lines are from brute force MD simulation, while the dashed lines are from MSM.}
+  \label{fig:num-7}
+\end{figure}
+
+We study the time-dependent expectation values of
+the properties, i.e.
+\begin{align}
+  \mathcal A(t) = \langle A(i)\rangle_t = \sum_{i\in S} A(i) p(i,t),
+\end{align}
+which are linear combinations of the backward
+committor, i.e.
+\begin{align}
+  A(i) = \sum_{l=1}^k \alpha_l q^\bwd_l(i)
+\end{align}
+then
+\begin{align}\nonumber
+  \mathcal A(t) &=
+  \sum_{i\in S} \sum_{l=1}^k \alpha_l q^\bwd_l(i)  p(i,t) \\\nonumber
+  & =
+  \sum_{i\in S} \sum_{l=1}^k \alpha_l \prob (\hat X_t = l \vert X_t = i) \prob (X_t = i) \\\nonumber
+  & =
+  \sum_{i\in S} \sum_{l=1}^k \alpha_l \prob (\hat X_t = l ,X_t = i) \\\nonumber
+  & =
+  \sum_{l=1}^k \alpha_l \prob (\hat X_t = l) \\\label{eq:num-28}
+  & =
+   \sum_{l=1}^k \alpha_l \,\hat p (l, t),
+\end{align}
+where the time-dependent projected probability is governed by the MSM:
+\begin{align}\label{eq:num-29}
+  \hat p(i, t+T) = \sum_{j\in S} \hat p(j,t)\hat P_{ji}
+\end{align}
+In Fig.~\ref{fig:num-7} we compare the numerical calculation of $\hat p (l, mT), \ m\in\mathbb N$ from brute force and MSM calculations.
+In the brute force calculation, the RHS terms on the projection $\hat p (l, mT) = \sum_{i\in S}  q^\bwd_l(i)  p(i,mT) $ are estimated from the
+non-equilibrium MD simulations. For MSM, the projection for the initial probability is applied $\hat p (l, 0) = \sum_{i\in S}  q^\bwd_l(i)  p(i,0) $, then
+the time-dependent probability at $mT$ is generated by Eq.~\eqref{eq:num-29}.
+% The projected probability, e.g.~$\hat p (l', mT)$ is calculated
+% by Eq.~\eqref{eq:num-28} letting $\alpha_l = \delta_{l'l}$.
 

### 2014-09-02 alanine.nanma/template/tools/msm/app/calculate.coreset.evlove.cpp
fix bugs.

@@ -159,33 +159,10 @@ void apply_trans (const vector<vector<double > > & tmatrix,
   for (unsigned ii = 0; ii < tmatrix.size(); ++ii){
     pout[ii] = 0.;
     for (unsigned jj = 0; jj < tmatrix[ii].size(); ++jj){
-      pout[ii] += tmatrix[ii][jj] * pin[jj];
+      pout[ii] += tmatrix[jj][ii] * pin[jj];
     }
   }
 }
-
-void reverse_tmatrix (const vector<vector<double > > & tmatrix,
-		      const vector<double > & dist,
-		      vector<vector<double > > & omatrix)
-{
-  omatrix = tmatrix;
-  for (unsigned ii = 0; ii < tmatrix.size(); ++ii){
-    for (unsigned jj = 0; jj < tmatrix[ii].size(); ++jj){
-      if (dist[jj] != 0){
-	omatrix[jj][ii] = dist[ii] * tmatrix[ii][jj] / dist[jj];
-      }
-      else {
-	if (dist[ii] * tmatrix[ii][jj] != 0){
-	  cerr << "problem of reverse" <<endl;
-	}
-	else{
-	  omatrix[jj][ii] =0.;
-	}
-      }
-    }
-  }  
-}
-
 
 int main(int argc, char * argv[])
 {

### 2014-09-02 alanine.nanma/template/tools/msm/app/calculate.coreset.proj.cpp

@@ -86,12 +86,13 @@ void read_tmatrix (const string & filename,
 
 int main(int argc, char * argv[])
 {
-  std::string ismfile, ibwfile, ofile, ifile;
+  std::string isfile, ibwfile, ofile, ifile;
   
   po::options_description desc ("Calculates the coreset projection of time-dep prob..\nAllow options");
   desc.add_options()
       ("help,h", "print this message")
-      ("input", po::value<string > (&ifile)->default_value ("cg.prob.dih.out"), "the time-dependent prob..")
+      ("input", po::value<string > (&ifile)->default_value ("bf.prob.dih.out"), "the time-dependent prob..")
+      ("input-largest-set,s", po::value<std::string > (&isfile)->default_value ("largestSet"), "the input file of largest set.")
       ("input-bw", po::value<string > (&ibwfile)->default_value ("commitor.bw.out.orig"), "the input of backward commitor.")
       ("output", po::value<string > (&ofile)->default_value ("coreset.prob.out"), "the output prob of coreset MSM.");
   
@@ -103,10 +104,29 @@ int main(int argc, char * argv[])
     return 0;
   }  
 
+  vector<int > setMap ;
+  {
+    FILE * fp  = fopen (isfile.c_str(), "r");
+    if (fp == NULL){
+      cerr << "cannot open file " << isfile << endl;
+      return 1;
+    }
+    int tmpint;
+    while (fscanf(fp, "%d", &tmpint) == 1){
+      setMap.push_back (tmpint);
+    }
+    fclose (fp);
+  }
+  unsigned nstate = setMap.size();
+
   vector<vector<double > > bwq;
   load_committor (ibwfile, bwq);
   unsigned ncluster = bwq.size();
-  unsigned nstate = bwq[0].size();
+  unsigned nstate1 = bwq[0].size();
+  if (nstate1 != nstate) {
+    cerr << "inconsistent between the setmap and the committor" << endl;
+    return 1;
+  }
 
   ifstream fpname (ifile.c_str());
   if (!fpname){
@@ -123,16 +143,24 @@ int main(int argc, char * argv[])
   while (fpname.getline(valueline, MaxLineLength)){
     vector<string > words;
     StringOperation::split (string(valueline), words);
-    if (words.size() != nstate+1){
-      cerr << "format error at t-d prob." << endl;
-      return 1;
-    }
+    // if (words.size() != nstate+1){
[…]

### 2014-09-02 alanine.nanma/template/tools/scripts/msm.analyze.brute.force.sh

@@ -13,6 +13,9 @@ angle_dir=$base_dir/angles
 msm_dir=$base_dir/msm
 cwd=`pwd`
 
+echo "# use running parameter: parameters.sh"
+source parameters.sh
+
 if [ ! -d $target_dir ]; then
     echo "no dir $target_dir"
     exit
@@ -22,8 +25,18 @@ if [ ! -f $target_dir/msm.parameters.sh ]; then
     echo "no file $target_dir/msm.parameters.sh"
     exit
 else
+    echo "# use parameter: $target_dir/msm.parameters.sh"
     source $target_dir/msm.parameters.sh
 fi
+
+for ii in `cat dir.name`;
+do
+    echo "# prepare $ii/traj.dih.disc.periodT"
+    period_frame=`echo "$pert_warm_time / $pert_frame_feq" | bc -l |  cut -d "." -f 1`
+    n_head_line=`echo "$msm_steady_end / $pert_warm_time + 1" | bc -l | cut -d "." -f 1`
+    n_tail_line=`echo "$n_head_line - $msm_steady_begin / $pert_warm_time" | bc -l | cut -d "." -f 1`
+    sed -n "1~${period_frame}p" $ii/traj.dih.disc | head -n $n_head_line | tail -n $n_tail_line > $ii/traj.dih.disc.periodT
+done
 
 mycommand="$msm_dir/calculate.commitor --input-largest-set $target_dir/largestSet.dih --num-bin $msm_dih_nbin --input-cluster-map $target_dir/cluster.map.out --input-traj-dir dir.name --input-disc-traj traj.dih.disc.periodT --output-fw $target_dir/commitor.fw.out --output-bw $target_dir/commitor.bw.out"
 echo "# calculate commitor by command: $mycommand"
@@ -41,6 +54,18 @@ $mycommand
 mycommand="$msm_dir/calculate.coreset.msm --num-bin $msm_dih_nbin --input-largest-set $target_dir/largestSet.dih  --input-floquet $target_dir/floque.B.out --input-cluster-map $target_dir/cluster.map.out --input-steady $target_dir/steady.dist.out.orig --input-fw $target_dir/commitor.fw.out.orig --input-bw $target_dir/commitor.bw.out.orig --output-tmatrix $target_dir/coreset.tmatrix.out"
 echo "# calculate coreset msm tmatrix by command: $mycommand"
 $mycommand
+
+if [ -f $target_dir/bf.prob.dih.out ]; then
[…]

### 2014-09-06 writedown/period.noneq.msm/paper.tex
backup

@@
 \section{Introduction}
-Non-equilibrium, especically periodically driven system. Interesting.
+Non-equilibrium, especially periodically driven system. Interesting.
 
-MSM tools for analyzing, provide profund understanding.
+MSM tools for analyzing, provide profound understanding.
 
@@
 $E(t)D(x_t)$ the time-dependent external perturbation with the
-$T$-periodic external field $E(t)$. $\beta$ is the inversed temperature,
+$T$-periodic external field $E(t)$. $\beta$ is the inverse temperature,
 i.e.~$\beta = 1/(k_B\mathcal T)$.
@@
 \begin{align}
-  \label{eq:disc-2}
+  \label{eq:disc-fp}
   \frac{\partial \rho}{\partial t} = \ml^\dagger(t) \rho,
@@
 $\Omega_j\cap \Omega_j = \emptyset,\ \forall i\neq j$.
-Following Ref.~\cite{latorre2011structure}, the Fokker-Planck Eq.~\ref{eq:disc-2}
+Following Ref.~\cite{latorre2011structure}, the Fokker-Planck Eq.~\ref{eq:disc-fp}
 is discretized, which results in a time-inhomogeneous Markov jump process in state
@@
 for all real time $t\geq 0$.
-\recheck{Moreover,
+{Moreover,
 the rate matrix $L$ has the form $\vect L(t)=\vect L_0+E(t)\vect L_1$
 where $E(t)$ is periodic with period $T>0$.}
-One possible approximation to $L(t)$ is via the following forward finite difference scheme:
-\begin{align}
-  \label{eqn:tmp4}
-  L_{ij}(t) \approx \frac{1}{\tau}
-  \,[\, \prob (\vect X_{t+\tau} = i \vert \vect X_{t} = j) - \delta_{ij} \,]
-\end{align}
-where $\vect X_t$ denotes the Markov jump process generated by $\vect L(t)$, 
-and $\tau$ is the disretization time-step.
-In analogy to \eqref{eq:disc-2}, the Markov jump process generated by
+In analogy to \eqref{eq:disc-fp}, the Markov jump process generated by
 $\vect L(t)$ transports probability densities according to the associated Master equation
 \begin{align}
-  \label{eq:disc-7}
+  \label{eq:disc-master}
   \frac{d\vect p(t)}{dt} = \vect L^T(t)\cdot \vect p(t)
@@
 \begin{align}
-  \label{eq:disc-9}
+  \label{eq:disc-master-phi}
   \frac{d}{dt}\myphi(t) = \vect L^T(t)\myphi(t), \quad \myphi(0) = \id
@@
 \end{align}
+where $\vect X_t$ denotes the Markov process generated by $\vect L(t)$.
  The
@@
 of $\vect L(t)$ are almost perfect approximations of the transport properties
-of $\ml(t)$, in particular $p_i(t)=\prob[x_t\in \Omega_i]$.
+of $\ml(t)$, in particular $p_i(t)=\prob(x_t\in \Omega_i)$.
 
@@
 \begin{equation}\label{compo-2}
-\myphi(t+mT)=\myphi(t)\myphi^m(T),
+\myphi(t+mT)=\myphi(t)\myphi^m(T).
 \end{equation}
-and in particular we get the long-term evolution of the propagator:
-\begin{align}
-\label{eq:floq-13}  
-\myphi(mT)=\myphi^m(T).
-\end{align}
 In combination with Eq.~\eqref{eq:disc-8}, we therefore
@@
 if we can compute $\myphi(t)$ for $t\in (0,T]$.  
+In particular we get the long-term evolution of the propagator:
+\begin{align}
+\label{eq:floq-13}  
+\myphi(mT)=\myphi^m(T),
+\end{align}
+and for the probability at integral period we have
+\begin{align}
+  \label{eq:floq-dynamics}
+  p(mT) =  \myphi(mT)\, p(0) = \myphi^m(T)\, p(0).
+\end{align}
 
@@
 \end{align}
-and (more precisely) the asymptotic evolution of an initial probability distribution $\vect p(t=0)=\vect p_0$ by the process satisfies
+and (more precisely) the asymptotic evolution of an initial probability distribution $\vect p(t=0)$ by the process satisfies
 \begin{align}
 \label{eq:floq-15}  
-\myphi(mT)\vect p_0\to \mymu,\quad m\to\infty.
+\myphi(mT)\vect p(0)\to \mymu,\quad m\to\infty.
 \end{align}
+
+Using the Floquet theorem, the time-inhomogeneous Markov process $X_t$
+is simplified into a \emph{time-homogeneous} (not necessarily
+reversible) Markov jump process $\tilde X_{m} = X_{mT}, \ m\in\mathbb
+N$.
+Therefore, comparing with $X_t$, we prefer to consider the process $\tilde X_{m}$
+that helps understand the original dynamics $x_t$, because the powerful theories and
+computational tools for time-homogeneous processes can be directly applied.
+There is no doubt that information within one period is lost by using this temporal
+discretization, however, information regarding the long-term behaviors
+of the system would be satisfactorily described as long as their time-scales
+are much longer than the period.
+At the same time,
+the computational cost of generating $\tilde X_{m}$ is mush less demanding
+than the brute force simulations of NEMD, which implies lower
+statistically uncertainty in calculating the observables of interest.
+% due to the discretization in both the spacial and temperal directions.
+% In the numercal example in Sec.~\ref{sec:alanine}, we
+% compute the
 
@@
   Alanine dipeptide under oscillatory electric field}
+\label{sec:alanine}
 
 If the spacial discretization is fine enough, the Markov jump
-process~\eqref{eq:disc-7} is a good approximation to the original
-MD~\eqref{eq:disc-1}.  In practice, it is firstly difficult to predict
-how many discret set is fine enough; Secondly, since the
+process~\eqref{eq:disc-master} is a good approximation to the original
+MD~\eqref{eq:disc-1}.  In practice, it is difficult to predict
+how many discrete set is fine enough; Moreover, since the
 total configurational dimension of the system is $3N$ ($N$ being the
 number of atoms), it is prohibitive to do a very fine discretization
-over all DOFs for most of systems of practical interest.  In the
-simulation of biomolecules, in most cases it is reasonable to assume a
-time-scale separation in the system.
+over all DOFs for most of systems of practical interest.
+In the systems that possess a
+time-scale separation, it is possible, in most cases, to pick up
+a characteristic time (or lag-time) $\tau$ that distinguishes the slow
+and fast time-scales.
 For example, the conformational
-change of the molecules is much faster than the covalent bond
+transitions of a large biomolecule is much slower than the covalent bond
 vibrations. 
@@
 In this context,
-it is usually possible to pick a relatively small number of discrete sets that
-correctly describe the slow dynamics in the sense that
-the original dynamics fully relaxes in every set
-within the discretization time-step (denoted by $\tau$). Or equivalently the discretized
-dynamics~\eqref{eq:disc-7} is a good approximation to~\eqref{eq:disc-1}.
-One possible way to define the discretized set is to firstly find few collective
+it is usually possible to construct a
+relatively small number of discrete sets that
+correctly describe the slow  dynamics, and 
+in each set the fast dynamics relaxes within the lag-time $\tau$.
+Then if the discretized dynamics~\eqref{eq:disc-master}
+reproduces the slow time-scales and the corresponding transitions
+of the original dynamics~\eqref{eq:disc-1},
+the former is considered to be a good approximation of the later.
+% Then the 
+% dynamics~\eqref{eq:disc-master} built on top of the discretization
+% is a good approximation to~\eqref{eq:disc-1}
+% in the sense of reproducing the slow dynamics.
+One possible way to define the discretized set is firstly to find a few collective
 variables, and then to discretize the dynamics as fine as possible only on these
@@
 discretization~\cite{chodera2007automatic, prinz2011markov}.
-This process also suggests that the choice of the lag-time should be 
-shorter than the dominant implied timescale so that they can be resolved,
-and be longer than the fast time-scales to relax the unresolved dynamics
-within the discretized sets.
-However, it is in general difficult to tell in priori how to choose the collect
-variables, how fine the discretization should be and how large
-the time-steps should be.
-For large system, these questions are usually
-not trivial to answer.
+% This process also suggests that the choice of the lag-time should be 
+% shorter than the dominant implied timescale so that they can be resolved,
+% and be longer than the fast time-scales to relax the unresolved dynamics
+% within the discretized sets.
+However, it is difficult to give a general answer in prior regarding, e.g.
+how large is the lag-time,
+how to choose the collect variables, how fine the discretization should be.
+For large or high dimensional systems, these questions usually become non-trivial.
 
@@
 
-To illustrate how the procedure works in practice, it is therefore
+To illustrate how the discretization works in practice, it is therefore
 useful to investigate the discussed approximations by a numerical
 example.  We take the alanine dipeptide system under an oscillatory EF,
-as an example, the non-equilibrium MD simulation of which was
+as an example, the NEMD simulation of which was
 extensively studied by Ref.~\cite{wang2014exploring}.  
@@
 environment, and was driven by a periodic electric field with period
-$T = 10$~ps. The 20,000 branching trajectories started from 20,000
-initial configurations that samples the equilibrium distribution.
-\redc{Write a lot of details on non-equilibrium MD.}  The branching
+$T = 10$~ps. The 20,000 branching trajectories were simulated from 20,000
+initial configurations that sample the equilibrium distribution.
+\redc{Write a lot of details on NEMD.}  The branching
 trajectories were each 4000~ps long, and the system reaches
-non-equilibrium steady state in roughly 300~ps.
+non-equilibrium stationary state in roughly 300~ps.
 
@@
 the $\phi$--$\psi$ plane. We denote the number of division on each
-dihedral by $K$. In the following subsections, we investigate the discretization
-quality firstly by considering the choice of $K$ and time-step $\tau$. Then
-the discretized dynamics is compared with original (non-equilibrium brute force simulation)
-via considering the steady state probability density, the first mean hitting time
+dihedral by $K$, then the discretized sets are
+$\{\Omega_i\},\ i\in S = \{1,\cdots,K^2\}$.
+One possible approximation to
+the discretized generator $L(t)$ is via
+the following forward finite difference scheme:
+\begin{align}
+  \label{eqn:tmp4}
+  L_{ij}(t) \approx \frac{1}{\tau}
+  \,[\, \prob (\vect X_{t+\tau} = i \vert \vect X_{t} = j) - \delta_{ij} \,],
+  \quad i,j\in S
+\end{align}
+and $\tau$ is the lag-time.
+In the following subsections~\ref{sec:alanine-disc} and \ref{sec:alanine-tau},
+we investigate the discretization
+quality with respect to  the choice of $K$ and  lag-time $\tau$.
+Then
+the discretized dynamics generated by the Floquet transition matrix
+is compared with original NEMD simulation
+via considering the stationary probability density, the first mean hitting time
 and the forward and backward committors.
@@
 \subsection{Discretizing the dihedral angles}
+\label{sec:alanine-disc}
+
 \begin{figure}
@@
   \caption{The time-dependent probability $\mathbb
-    P\big(\phi\in[0,180), \psi\in [0,180)\big)$.  The brute force
-    non-equilibrium MD simulation is compared with different
+    P\big(\phi\in[0,180), \psi\in [0,180)\big)$.  The NEMD simulation is compared with different
     discretization methods. The red shadow region indicates the
-    statsitical uncertainty of the brute force simulation.}
+    statistical uncertainty of the NEMD simulation.}
   \label{fig:tmp2}
@@
 We estimate the discretized generator $L(t), \ t\in[0,T)$
-from non-equilibrium trajectories generated by $\ml(t)$ in time interval $[t_1,
+from NEMD trajectories generated by $\ml(t)$ in time interval $[t_1,
 t_2]$.
@@
 it is estimated, provided that the initial state of the system
-is not very far from the steady state.
-This is a good indicator of the discretization quality.
+is not very far from the stationary state at long-time limit.
+Therefore, this is an indicator for calibrating the discretization quality.
 We compute $L(t)$ by two discretizations $K=2$ and $K=20$, and two
@@
 probability $\prob\big(\phi_t\in[0,180), \psi_t\in [0,180)\big)$
-with the brute force result in
+with the NEMD result in
 Fig.~\ref{fig:tmp2}.
+The time derivative of the master equation~\eqref{eq:disc-master}
+is discretized by the forward Euler scheme with a time step of 0.5~ps.
 Using $K=2$ the dynamics depends on the time interval used for
 calculating the generator: using time interval $[0, 80]$~ps the discretized
-dynamics deviates the brute force result,
+dynamics deviates from the NEMD result,
 while using time interval $[320, 400]$~ps the discretized dynamics can only
-reproduces the brute force result after 300~ps.  This therefore indicates poor 
+reproduces the NEMD result after 300~ps.  This therefore indicates poor 
 approximations to the original dynamics with $K=2$. The reason is that the
@@
 $K=20$, the discretized dynamics does not depend on the time interval of
-calculating the generator, and is consistent with the brute force
-non-equilibrium simulation within the error bar. Therefore, in this paper we use $K=20$
+calculating the generator, and is consistent with the
+NEMD simulation within the error bar. Therefore, throughout this paper we use $K=20$
 to discretize  the dihedral angle space of the alanine dipeptide.
@@
 we will use the full trajectories, i.e.~a time interval of
-$[0,4000]$~ps for estimating the discretized dynamics.
+$[0,4000]$~ps for estimating the discretized generator $L(t)$.
 
 \subsection{The choice of lag-time $\tau$}
+\label{sec:alanine-tau}
 
@@
   \caption{The time-dependent probability $\mathbb
-    P\big(\phi\in[0,180), \psi\in [0,180)\big)$.  The brute force
-    non-equilibrium MD simulation is compared with different
+    P\big(\phi\in[0,180), \psi\in [0,180)\big)$.  The NEMD simulation is compared with different
     discretization methods. The red shadow region indicates the
-    statsitical uncertainty of the brute force simulation.}
+    statistical uncertainty of the NEMD simulation.}
   \label{fig:tmp3}
@@
 practice, it is very difficult to estimate the lag-time in
-priori. Therefore, we consider 
+prior. Therefore, we consider 
 different choices of $\tau$ (0.5, 1.0, 2.0 and 5.0~ps)
@@
 time-dependent probability $\prob\big(\phi\in[0,180), \psi\in
-[0,180)\big)$ calculated from different time discretization with the brute force simulation
+[0,180)\big)$ calculated from different time discretization with the NEMD simulation
 of the original dynamics
-(see Fig.~\ref{fig:tmp3}).  All cases use idential dihedral angle discretization: $K=20$.
+(see Fig.~\ref{fig:tmp3}).  All cases use identical dihedral angle discretization: $K=20$.
 It is clear that when lag-time is close to the period (10~ps), the
@@
 period. However, it is surprising  that the large lag-times are able to capture the
-the overall log time behavior of the probability.
+the overall long time behavior of the original dynamics.
 We observe no significant difference between $\tau=0.5$ and
@@
 to the choice of $\tau$.
+Therefore, throughout this paper $\tau=0.5$~ps will be used.
 We do not investigate the small $\tau$ limit, because saving trajectories
-more frequently requires more hard disk space, and is usually not preferred.
+more frequently requires more hard disk space, and is usually not preferred in practice.
 
@@
   \centering  
-  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.40.steadyDist//fig-dist.eps}
-  % \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-dist-msm.eps}
-  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.40/fig-floquet-vec-1.eps}
-  \caption{The steady state distribution calculated by brute force non-equilibrium is compared with that by the discretized dynamics.}
+  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3.steadyDist//fig-dist.eps}
+  % \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-dist-msm.eps}
+  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3/fig-floquet-vec-1.eps}
+  \caption{The color scale plot of the logarithm stationary probability
+    of (a) the NEMD  and (b)
+    the Floquet matrix $\Phi(T)$.
+  }
   \label{fig:num-1}
@@
 
-An important check of the discretized dynamics is that if it reporduces the steady probability
-density $\mymu$ of $\myphi(T)$.
-To make it comparible to
-the free energy in equilibrium case, we take the logrithm of the properties, i.e.
+Comparing with the time-homogeneous Markov processes, there are not as
+many tools for understanding the time-inhomogeneous Markov process.
+Therefore, in the following subsections,
+we consider the time-homogeneous process $\tilde X_{m}$ generated by
+the Floquet transition matrix $P = \Phi^T(T)$, and investigate if it
+reproduces the properties of the original  non-equilibrium process $x_t$.
+In this context, only the configurations at the  integral periods $mT$ along the original process
+are taken into consider.
+
+An important check is the consistency between the
+stationary probability density of $\Phi(T)$ (i.e.~the leading eigenvector $\mu$) and that 
+estimated form the original NEMD simulation, along which only integral periods $mT$ are considered:
 \begin{align}
   \label{eq:num-tmp1}
-  F_{\textrm{st}}(\phi,\psi) = \lim_{m\rightarrow\infty} -k_B\mathcal T \log p(\phi,\psi,mT),
+  \rho_{\textrm{st}}(\phi,\psi) = \lim_{m\rightarrow\infty} \rho (\phi,\psi,mT),
 \end{align}
-where $k_B$ is the Boltzmann constant and $\mathcal T$ is the temperature of the system.
-The result is given in Fig.~\ref{fig:num-1}. A good consistency between the brute force
-MD simulation and the discretized dynamics is observed.
+On each NEMD branching trajectory, the very beginning 320~ps is discarded, and
+the rest of the trajectory in $[320,4000]$~ps is used to estimate
+the stationary probability. $\Phi(T)$ is computed by solving~\eqref{eq:disc-master-phi}
+in one period, where the discretized generator $L(t)$ was estimated
+from the full NEMD trajectories of $4000$~ps long.
+Moreover, to make it comparable to the free energy in equilibrium case, we take
+the logarithm of the properties, i.e.~$F_{\textrm{st}}(\phi,\psi)=
+-k_B\mathcal T\log \rho_{\textrm{st}}(\phi,\psi)$
+for NEMD and $F_{\textrm{st}}(\phi,\psi)=
+-k_B\mathcal T\log \mu(\phi,\psi)$ for $\Phi(T)$, where $k_B$ is the
+Boltzmann constant and $\mathcal T$ is the temperature of the system.
+% Under the aformentioned discretization, the stationary distribution is
+% defined for the each bin of the dihedral angle space, i.e.~$F_{pq} =
+% \int_{ph}^{(p+1)h}d\phi\int_{qh}^{(q+1)h}d\psi
+% F_{\textrm{st}}(\phi,\psi), \ 0\leq p,q<K-1$, where $h = 360/K$ being
+% the size of the bin, $p$ and $q$ here being the bin indexes.
+The
+results are  compared in Fig.~\ref{fig:num-1}. A good consistency between
+the  NEMD simulation and 
+$\Phi(T)$ is observed.
 
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{fig/t040/cluster.marco/fig-cluster-2.eps}
-  \caption{The coreset identification. Different colors indicate different coresets: $C_{\confaa}$ (yellow), $C_\beta$ (red) and $C_{\confc}$ (green).
+  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3/fig-cluster.eps}
+  \caption{The coreset identification. Different colors indicate different coresets: $C_{\confaa}$ (green), $C_\beta$ (yellow) and $C_{\confc}$ (red).
     The blue color means out of any coreset. (By Marco)}
@@
 
-\redc{Write how to detact the core sets for irreversible Markovian process}.
+\redc{Write how to detect the core sets for irreversible Markov process}.
 
@@
 \subsection{First mean hitting time}
-
-Since the largest first mean hitting time (starting fom coreset $\confaa$ to $\confc$) is
-longer than 600~ps, if we use the trajectories of length 4000~ps, the
-results will be biased. Therefore, we use 100 non-equilibrium trajectories
-of $2\times 10^5$~ps instead.
-The first mean hitting time is presented in Fig.~\ref{fig:num-6}.
+\label{sec:alanine-fmht}
 
@@
   \centering
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-1.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-3.eps}\\
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-msm-1.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-msm-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40.fht/fig-fht-msm-3.eps}
-  \caption{The first mean htting time comparsion between the brute
-    force simulation (first row) and the discretized dynamics (second row).  From left
-    to right are first mean hitting time to coresets $C_{\confc}$,
-    $C_{\confaa}$ and $C_{\beta}$, respectively}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-msm-1.eps}\\
+  \vskip -.5cm
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-msm-2.eps}\\
+  \vskip -.5cm
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-msm-3.eps}\\
+  \caption{The first mean hitting time (FMHT) comparison between the NEMD
+    simulation (first column) and the discretized dynamics (second column).  From up
+    to down are first mean hitting time to coresets $C_{\confaa}$ and $C_{\beta}$
+    and $C_{\confc}$, respectively}
   \label{fig:num-6}
@@
 
+The first mean hitting time, as a function of the dihedral angles $(\phi,\psi)$,
+is defined by the
+averaged first time needed for hitting a certain coreset
+$i\in\{\alpha_R,\beta,\alpha_L\}$, conditioned on starting from the
+conformation $(\phi,\psi)$.  Since the largest first mean hitting
+time (starting from coreset $\confaa$ to $\confc$) is longer than
+600~ps, if we use the NEMD trajectories of length 4000~ps,
+the results will be biased. Therefore, we use 100 NEMD
+trajectories of $2\times 10^5$~ps instead. We also compute the first mean hitting
+time of 
+a  $10^9$~ps long (being $T=10$~ps, $m = 1,\cdots, 10^8$)
+discretized trajectory $\tilde
+X_{m}$ that is generated by the Floquet transition matrix $P=\Phi^T(T)$.
+The first mean hitting time is presented in Fig.~\ref{fig:num-6}.  The
+good consistency between the NEMD and the discretized Markov process
+$\tilde X_{m}$ indicates a good approximation quality.
+Since the length of the discretized process is substantially longer than
+the total length of NEMD
+simulation ($10^9$~ps v.s.~$2\times10^7$~ps), the statistically uncertainty
+is much smaller. 
+However, one should notice that systematic errors
+are introduced during the discretization (estimating $L(t)$), and 
+its potential influence on the observables,
+e.g.~the first mean hitting time, is not straightforward to estimate.
+This topic is out of the scope of the current paper,
+and will not be discussed in detail.
+In summary, very long discretized trajectories helps in calculating the observables
+in a smoother  (less statistical error) but not necessarily more accurate manner.
+On the other hand, the computational cost of
+discretized process, if the cost for estimating $\Phi(T)$ is not included, is
+essentially cheaper than NEMD:
+it took roughly 10 minutes on one core of an Intel Xeon E31245 CPU for generating the discretized trajectory, while the
+NEMD trajectories took $1.6\times 10^4$ core hours for Intel Xeon E5-4650 CPUs.
+
 \subsection{Forward and backward committors}
-
-The forward committor $q^\fwd_i(\phi,\psi)$ of a coreset $C_i,\
-i\in\{\confaa, \beta, \confc\}$ is defined as the probability of
-visiting coreset $C_i$ next conditioned on being at configuration
-$(\phi,\psi)$.  The backward committor $q^\bwd_i(\phi,\psi)$ of a
-coreset $C_i,\ i\in\{\confaa, \beta, \confc\}$ is defined as the
-probability of last coming from $C_i$ conditioned on being at
-configuration $(\phi,\psi)$.  For reversible Markov processes, the
-forward and backward committors are identical, however, it is in
-general not the case for irreversible processes. Please see
-Fig.~\ref{fig:num-3}--\ref{fig:num-5} for the committors.
-
+\label{sec:alanine-committor}
 \begin{figure}
   \centering
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-1.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-1.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-1.eps}\\
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-1.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-1.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-1.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-msm-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-msm-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-msm-1.eps}
   \caption{The forward $q^\fwd_{\confc}$ and backward committors
     $q^\bwd_{\confc}$ computed by discretized dynamics (second row) is compared with
-    those computed by brute force non-equilibrium simulations (first
+    those computed by NEMD simulations (first
     row).}
@@
   \centering
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-2.eps}\\
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-2.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-msm-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-msm-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-msm-2.eps}
   \caption{The forward $q^\fwd_{\confaa}$ and backward
     $q^\bwd_{\confaa}$ committors computed by discretized dynamics (second row) is
-    compared with those computed by brute force non-equilibrium
+    compared with those computed by NEMD
     simulations (first row).}
@@
   \centering
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-3.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-3.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-3.eps}\\
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-fw-msm-3.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-bw-msm-3.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-commitor-diff-msm-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-3.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-msm-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-msm-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-msm-3.eps}
   \caption{The forward $q^\fwd_{\beta}$ and backward $q^\bwd_{\beta}$
     committors computed by discretized dynamics (second row) is
-    compared with those computed by brute force non-equilibrium
+    compared with those computed by NEMD
     simulations (first row).}
@@
 
+Committors are very important statistical properties of Markov processes, and play
+an important role in the later MSM building, therefore, it is worth
+checking if the discretized process $\tilde X_m$ reproduces the NEMD committors.
+The forward committor $q^\fwd_i(\phi,\psi)$ of a coreset $C_i,\
+i\in\{\confaa, \beta, \confc\}$ is defined as the probability of
+visiting coreset $C_i$ next conditioned on being at conformation
+$(\phi,\psi)$.  The backward committor $q^\bwd_i(\phi,\psi)$ of a
+coreset $C_i,\ i\in\{\confaa, \beta, \confc\}$ is defined as the
+probability of last coming from $C_i$ conditioned on being at
+configuration $(\phi,\psi)$.
+For reversible Markov processes, the
+forward and backward committors are identical, however, it is in
+general not the case for irreversible processes.
+The committors estimated from NEMD simulations ($20000$ trajectories $4000$~ps each) is compared with
+those estimated from the discretized trajectory $\tilde X_m$, which is the same as the one used in Sec.~\ref{sec:alanine-fmht} for first mean hitting time.
+Fig.~\ref{fig:num-3}--\ref{fig:num-5} presents both
+committors as well as their difference corresponding to different coresets.
+The committors of the discretized process is in good consistency with those of
+the NEMD simulations. The non-zero values in the committor differences
+indicate that the NEMD process, projected on the discretized
+dihedral angle space, is irreversible, and
+the discretized process is able to correctly describe this irreversiblity.
+Also the accurate reproduction of the committors indicates it is reasonable to build the 
+MSM out of the committors of the  discretized process.
+
 \subsection{Building MSM}
 Following the process described in Sec.~\ref{sec:build-msm}, we are able to build a 
-three states MSM for the alanine dipeptide system.
-The leading eigenvalues of $P$ is compared with those of the MSM, i.e.~$\hat P$ in
+three states MSM for the alanine dipeptide system,
+where the stationary probability and the committors are
+estimated by the discretized process $\tilde X_m$, see
+Sec.~\ref{sec:alanine-committor}.
+The leading eigenvalues of $P=\Phi^T(T)$ is compared with those of the MSM, i.e.~$\hat P$ in
 Tab.~\ref{tab:tmp1}.
+The MSM is able to accurately reproduce
+the largest non-trivial eigenvalue, which means a precise reproduction
+of the longest non-trivial implied time-scale. The accuracy of the second non-trivial
+time-scale is not as good as the first, but is still acceptable. The reason
+for the lower accuracy is that
+the corresponding time scale is 26.5~ps (calculated by $-T/\log(\lambda_2)$),
+which is NOT significantly longer than the time resolution $T=10$~ps.
+It worth noting that although the discretized process $\tilde X_m$ is irreversible,
+the MSM built out of it is almost reversible:
+The magnitude of the anti-symmetric part of the
+matrix $\textrm{diag}(\hat \mu)\cdot \hat P$ is only of order $10^{-4}$.
 
@@
     $P$         &0.907  &0.686 & 0.553       \\
-    $\hat P$    &0.914  &0.744 & --       \\
+    $\hat P$    &0.911  &0.724 & --       \\
     \hline\hline
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-eig-vec-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-eig-vec-3.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.40/fig-eig-vec-4.eps}\\
-  \caption{The eigenfunctions of $P$.}
-  \label{fig:num-6}
-\end{figure}
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-eig-vec-2.eps}
+%   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-eig-vec-3.eps}
+%   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-eig-vec-4.eps}\\
+%   \caption{The eigenfunctions of $P$.}
+%   \label{fig:num-6}
+% \end{figure}
 
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.40/fig-coreset-prob.eps}
-  \caption{The time-dependent probability $\hat P_l$. Solid lines are from brute force MD simulation, while the dashed lines are from MSM.}
+  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3/fig-coreset-prob.eps}
+  \caption{The time-dependent probability $\hat P_l$.
+    Solid lines are from NEMD simulation, while the dashed lines are from MSM.}
   \label{fig:num-7}
@@
 \end{align}
-In Fig.~\ref{fig:num-7} we compare the numerical calculation of $\hat p (l, mT), \ m\in\mathbb N$ from brute force and MSM calculations.
-In the brute force calculation, the RHS terms on the projection $\hat p (l, mT) = \sum_{i\in S}  q^\bwd_l(i)  p(i,mT) $ are estimated from the
-non-equilibrium MD simulations. For MSM, the projection for the initial probability is applied $\hat p (l, 0) = \sum_{i\in S}  q^\bwd_l(i)  p(i,0) $, then
+In Fig.~\ref{fig:num-7} we compare the numerical calculation of $\hat p (l, mT), \ m\in\mathbb N$ from NEMD and MSM calculations.
+In the former case, the backward committor and probability density
+on RHS of the projection $\hat p (l, mT) = \sum_{i\in S}  q^\bwd_l(i)  p(i,mT) $
+are estimated from the
+NEMD trajectories. For MSM, the projection of the initial probability is applied $\hat p (l, 0) = \sum_{i\in S}  q^\bwd_l(i)  p(i,0) $, then
 the time-dependent probability at $mT$ is generated by Eq.~\eqref{eq:num-29}.
@@
 
-We consider the gonverning dynamics Eq.~\eqref{eq:disc-1}.
+We consider the governing dynamics Eq.~\eqref{eq:disc-1}.
 For simplicity we denote the force by $F(x_t,t) = -\nabla_x V(x_t)+ E(t)D(x_t) $.  We denote $\sigma =  \sqrt{2\beta^{-1}} $.
@@
 Now, consider a conjugate trajectory $x^\dagger_t = x_{T-t}$ that starts at $x_T$, ends at $x_0$. The conjugate dynamics is driven by  $F^\dagger(x^\dagger_t,t) = F(x^\dagger_t, T-t)$.
-Writting the Girsanov for the conjugate dynamics
+Writing the Girsanov for the conjugate dynamics
 \begin{align}\label{eq:dagger-0}
@@
 
-\subsection{Irreversibility of the perodical symmetrical dynamics}
+\subsection{Irreversibility of the periodical symmetrical dynamics}
 

### 2014-09-10 alanine.nanma/template/tools/msm/app/calculate.coreset.msm.nemd.cpp
fix bugs, not all

@@ -213,14 +213,14 @@ int main(int argc, char * argv[])
   
   po::options_description desc ("Calculates the MSM based on coreset milestoning.\nAllow options");
   desc.add_options()
-      ("help,h", "print this message")
-      ("input,f",  po::value<std::string > (&ifile)->default_value ("traj.disc.periodT"), "the file of file names")
-      ("input-dir,d", po::value<std::string > (&idfile)->default_value ("dir.name"), "the output of metastable propulation")
-      ("n-data-block,n", po::value<unsigned > (&ndataBlock)->default_value (1), "num data in each block.")
-      ("num-bin,n", po::value<unsigned > (&nbin)->default_value (20), "number of blocks.")
-      ("input-cluster-map", po::value<string > (&ismfile)->default_value ("cluster.map.out"), "the input of cluster map.")
-      ("output-tmatrix-t", po::value<string > (&otmfile)->default_value ("coreset.t.out"), "the output matrix T of coreset MSM.")
-      ("output-tmatrix-t", po::value<string > (&ommfile)->default_value ("coreset.m.out"), "the output matrix M of coreset MSM.");
+    ("help,h", "print this message")
+    ("input,f",  po::value<std::string > (&ifile)->default_value ("traj.dih.disc.periodT"), "the file of file names")
+    ("input-dir,d", po::value<std::string > (&idfile)->default_value ("dir.name"), "the output of metastable propulation")
+    ("n-data-block,n", po::value<unsigned > (&ndataBlock)->default_value (1), "num data in each block.")
+    ("num-bin,n", po::value<unsigned > (&nbin)->default_value (20), "number of blocks.")
+    ("input-cluster-map", po::value<string > (&ismfile)->default_value ("cluster.map.out"), "the input of cluster map.")
+    ("output-matrix-t", po::value<string > (&otmfile)->default_value ("coreset.t.out"), "the output matrix T of coreset MSM.")
+    ("output-matrix-m", po::value<string > (&ommfile)->default_value ("coreset.m.out"), "the output matrix M of coreset MSM.");
   
   po::variables_map vm;
[…]

### 2014-09-10 alanine.nanma/template/tools/msm/app/calculate.coreset.msm.nemd.cpp
bug fixing

@@ -304,12 +304,30 @@ int main(int argc, char * argv[])
 	for (unsigned kk = 0; kk < numCluster; ++kk){
 	  if (kk == nextindex){
 	    mmatrix[curtindex][kk].deposite (1.);
-	    if (ii >= curtposi+1) tmatrix[curtindex][kk].deposite (1.);
+	    if (ii < nextposi - 1) tmatrix[curtindex][kk].deposite (1.);
 	    // cout << "depo " << curtindex << " " << nextindex << endl;
 	  }
 	  else{
 	    mmatrix[curtindex][kk].deposite (0.);
-	    if (ii >= curtposi+1) tmatrix[curtindex][kk].deposite (0.);
+	    if (ii < nextposi - 1) tmatrix[curtindex][kk].deposite (0.);
+	  }
+	}
+      }
+      unsigned next2posi = nextposi;
+      while (milestone_traj[next2posi] == milestone_traj[nextposi]) {
+	next2posi ++;
+	if (next2posi >= milestone_traj.size()){
+	  break;
+	}
+      }
+      if (next2posi < milestone_traj.size()){
+	unsigned next2index = milestone_traj[next2posi] - 1;
+	for (unsigned kk = 0; kk < numCluster; ++kk){
+	  if (kk == next2index){
+	    tmatrix[curtindex][kk].deposite (1.);
+	  }
+	  else{
+	    tmatrix[curtindex][kk].deposite (0.);
 	  }
 	}
       }

### 2014-09-10 alanine.nanma/template/tools/msm/app/calculate.coreset.msm.nemd.cpp
add error printing

@@ -352,9 +352,12 @@ int main(int argc, char * argv[])
   for (unsigned ii = 0; ii < numCluster; ++ii){
     for (unsigned jj = 0; jj < numCluster; ++jj){
       fprintf (fp, "%f ", tmatrix[ii][jj].getAvg());
+      printf ("%f ", tmatrix[ii][jj].getAvgError());
     }
     fprintf (fp, "\n");
+    printf("\n");
   }
+    printf("\n");
   fclose (fp);
   FILE * fp1 = fopen (ommfile.c_str(), "w");
   if (fp1 == NULL){
@@ -364,8 +367,10 @@ int main(int argc, char * argv[])
   for (unsigned ii = 0; ii < numCluster; ++ii){
     for (unsigned jj = 0; jj < numCluster; ++jj){
       fprintf (fp1, "%f ", mmatrix[ii][jj].getAvg());
+      printf ("%f ", mmatrix[ii][jj].getAvgError());
     }
     fprintf (fp1, "\n");
+    printf("\n");
   }
   fclose (fp1);
   

### 2014-09-10 alanine.nanma/template/tools/msm/app/calculate.coreset.msm.nemd.cpp
fixing bug

@@ -204,6 +204,27 @@ void convert_milestone (const vector<unsigned > & input,
   }
 }
 
+int compute_next_index (const vector<unsigned > & disc_traj,
+			const vector<unsigned > & clusterMap,
+			const unsigned & curtposi_)
+{
+  unsigned curtposi (curtposi_);
+  if (curtposi >= disc_traj.size()) return -1;
+  if (clusterMap[disc_traj[curtposi]] != 0){
+    return clusterMap[disc_traj[curtposi]] - 1;
+  }
+  else {
+    while (curtposi < disc_traj.size() && clusterMap[disc_traj[curtposi]] == 0){
+      curtposi ++;
+    }
+    if (curtposi == disc_traj.size()){
+      return -1;
+    }
+    else {
+      return clusterMap[disc_traj[curtposi]] - 1;
+    }
+  }
+}
 
 
 int main(int argc, char * argv[])
@@ -213,14 +234,14 @@ int main(int argc, char * argv[])
   
   po::options_description desc ("Calculates the MSM based on coreset milestoning.\nAllow options");
   desc.add_options()
-    ("help,h", "print this message")
-    ("input,f",  po::value<std::string > (&ifile)->default_value ("traj.dih.disc.periodT"), "the file of file names")
-    ("input-dir,d", po::value<std::string > (&idfile)->default_value ("dir.name"), "the output of metastable propulation")
-    ("n-data-block,n", po::value<unsigned > (&ndataBlock)->default_value (1), "num data in each block.")
-    ("num-bin,n", po::value<unsigned > (&nbin)->default_value (20), "number of blocks.")
-    ("input-cluster-map", po::value<string > (&ismfile)->default_value ("cluster.map.out"), "the input of cluster map.")
-    ("output-matrix-t", po::value<string > (&otmfile)->default_value ("coreset.t.out"), "the output matrix T of coreset MSM.")
-    ("output-matrix-m", po::value<string > (&ommfile)->default_value ("coreset.m.out"), "the output matrix M of coreset MSM.");
+      ("help,h", "print this message")
+      ("input,f",  po::value<std::string > (&ifile)->default_value ("traj.dih.disc.periodT"), "the file of file names")
[…]

### 2014-09-10 alanine.nanma/template/tools/msm/app/calculate.coreset.msm.nemd.cpp
fix bug, consistent with those matrices computed from the committors

@@ -303,12 +303,13 @@ int main(int argc, char * argv[])
     // cout << endl;
     // cout << endl;
     unsigned curtposi = 0;
+    while (milestone_traj[curtposi] == 0) curtposi ++;
     while (curtposi < disc_traj.size()){
       unsigned curtindex = milestone_traj[curtposi] - 1;
       int nextindex = compute_next_index (disc_traj, clusterMap, curtposi);
       int next2index = compute_next_index (disc_traj, clusterMap, curtposi + 1);
       if (nextindex < 0 ) break;
-      for (int kk = 0; kk < numCluster; ++kk){
+      for (int kk = 0; kk < int(numCluster); ++kk){
 	if ((kk) == nextindex){
 	  mmatrix[curtindex][kk].deposite (1.);
 	}
@@ -317,12 +318,12 @@ int main(int argc, char * argv[])
 	}
       }
       if (next2index >= 0){
-	for (int kk = 0; kk < numCluster; ++kk){
+	for (int kk = 0; kk < int(numCluster); ++kk){
 	  if (kk == next2index){
-	    mmatrix[curtindex][kk].deposite (1.);
+	    tmatrix[curtindex][kk].deposite (1.);
 	  }
 	  else{
-	    mmatrix[curtindex][kk].deposite (0.);
+	    tmatrix[curtindex][kk].deposite (0.);
 	  }
 	}	
       }

### 2014-09-10 alanine.nanma/template/tools/msm/app/calculate.coreset.msm.nemd.cpp
fix bug

@@ -237,7 +237,7 @@ int main(int argc, char * argv[])
       ("help,h", "print this message")
       ("input,f",  po::value<std::string > (&ifile)->default_value ("traj.dih.disc.periodT"), "the file of file names")
       ("input-dir,d", po::value<std::string > (&idfile)->default_value ("dir.name"), "the output of metastable propulation")
-      ("n-data-block,n", po::value<unsigned > (&ndataBlock)->default_value (1), "num data in each block.")
+      ("n-data-block", po::value<unsigned > (&ndataBlock)->default_value (1), "num data in each block.")
       ("num-bin,n", po::value<unsigned > (&nbin)->default_value (20), "number of blocks.")
       ("input-cluster-map", po::value<string > (&ismfile)->default_value ("cluster.map.out"), "the input of cluster map.")
       ("output-matrix-t", po::value<string > (&otmfile)->default_value ("coreset.t.out"), "the output matrix T of coreset MSM.")

### 2014-09-11 writedown/period.noneq.msm/paper.tex
further revise

@@
 \newcommand{\dd}[1]{\textsf{#1}}
-\newcommand{\fwd}[0]{\textrm{fw}}
-\newcommand{\bwd}[0]{\textrm{bw}}
+% \newcommand{\fwd}[0]{\textrm{fw}}
+% \newcommand{\bwd}[0]{\textrm{bw}}
+\newcommand{\fwd}[0]{+}
+\newcommand{\bwd}[0]{-}
 \newcommand{\period}[0]{T_{\textrm{P}}}
@@
 
-\title{Building Markov State Model for a Periodically Driven Non-Equilibrium System}
+\title{Building Markov State Models for Periodically Driven Non-Equilibrium Systems}
 \author{Han Wang}
@@
 
-Current achievement of MSM in equilibrium cases.
+Current achievement of MSM in equilibrium cases:
+\begin{itemize}
+\item well developed in theory and applications \cite{A19-31, A19-1}
+\item software for MSM building \cite{A19-49, MSMBuilder}
+\end{itemize}
 
@@
 
-\section{Discretization of the non-equilibrium molecular dynamics}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Non-equilibrium molecular dynamics and its discretization}
 \label{sec:disc}
-
-We consider  the following SDE form of the externally driven MD:
+For the sake of simplicity we consider diffusive molecular dynamics in an energy landscape $V$ driven by the time-dependet external driving force $E(t)D(x_t)$ with the
+$T$-periodic external field $E(t)$:
 \begin{align}
@@
 \end{align}
-where the configurational space is denoted by $\Omega$, and the variable by
-$\vect x$.   $V(\vect x)$ is the molecular interaction potential and
-$E(t)D(x_t)$ the time-dependent external perturbation with the
-$T$-periodic external field $E(t)$. $\beta$ is the inverse temperature,
+where $x_t\in\Omega$ denotes the state of the molecular system at time $t$ in state space $\Omega$, $\vect w_t$ denotes standard $n$-dimensional Brownian motion, and $\beta$ the inverse temperature,
 i.e.~$\beta = 1/(k_B\mathcal T)$.
@@
   \label{eq:disc-3}
-  \ml(t)=\beta^{-1}\Delta_{\vect x}+\Big(-\nabla V(\vect x) + E(t)D(\vect x)\Big)\cdot\nabla_{\vect x},
+  \ml(t)=\beta^{-1}\Delta_{\vect x}+\Big(-\nabla_x V(\vect x) + E(t)D(\vect x)\Big)\cdot\nabla_{\vect x},
 \end{align}
@@
 the nabla-operator wrt to $\vect x$. 
-The periodicity of the external driven indicates the periodicity of the generator,
-i.e.~$\ml(t) = \ml(t+T)$.  Now
-introduce a partition of the configurational space $\Omega$ into finite number of disjoint
-sets $\{ \Omega_1, \cdots, \Omega_n\}$, which satisfy $\Omega = \cup_i \Omega_i$,
+The periodicity of the external driving force induces the periodicity of the generator,
+i.e.~$\ml(t) = \ml(t+T)$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Spatial discretization: Master equation}
+We will now introduce an appropriate spatial discretization of this kind of non-equilibirium MD -- this is done for reasons of simplicity only; we could completely avoid it for the price of more technical arguments.
+For achieving this discretization, we 
+introduce a partition of state space $\Omega$ into a finite number of disjoint
+sets $\{ \Omega_1, \cdots, \Omega_n\}$ satisfying $\Omega = \cup_i \Omega_i$,
 $\Omega_j\cap \Omega_j = \emptyset,\ \forall i\neq j$.
-Following Ref.~\cite{latorre2011structure}, the Fokker-Planck Eq.~\ref{eq:disc-fp}
-is discretized, which results in a time-inhomogeneous Markov jump process in state
+Utilizing the procedure described in Ref.~\cite{latorre2011structure} the original Fokker-Planck equation~(\ref{eq:disc-fp})
+is discretized, resulting in a time-inhomogeneous Markov jump process in state
 space $S = \{1, \cdots, n\}$ with time-dependent rate
@@
 for all real time $t\geq 0$.
-{Moreover,
-the rate matrix $L$ has the form $\vect L(t)=\vect L_0+E(t)\vect L_1$
-where $E(t)$ is periodic with period $T>0$.}
+Moreover, the rate matrix $L$ has the form $\vect L(t)=\vect L_0+E(t)\vect L_1$
+where $E(t)$ is periodic with period $T>0$.
 In analogy to \eqref{eq:disc-fp}, the Markov jump process generated by
-$\vect L(t)$ transports probability densities according to the associated Master equation
+$\vect L(t)$ transports probability distributions according to the associated Master equation
 \begin{align}
@@
 \end{align}
-where $\vect L(t)^T$ denotes the matrix transpose of $\vect L(t)$ and
-$p_i(t)$, for example, the probability to be in state $i$ at time $t$.
+where $\vect L(t)^T$ denotes the matrix transpose of $\vect L(t)$, $\vect p(t)$ is an $n$-vector denoting the probability distribution on $S$ at time $t$, and
+$p_i(t)$, for example, the probability to be in state $i$ (which corresponds to set $\Omega_i$) at time $t$.
 As usual the properties (\ref{eq:disc-4}) and (\ref{eq:disc-5}) of
@@
 % periodic.
-It can be formally written
+The temporal evolution of the probability distribution $\vect p(t)$ can be formally written
 \begin{align}  \label{eq:disc-8}
@@
   \label{eq:disc-master-phi}
-  \frac{d}{dt}\myphi(t) = \vect L^T(t)\myphi(t), \quad \myphi(0) = \id
+  \frac{d}{dt}\myphi(t) = \vect L^T(t)\myphi(t), \quad \myphi(0) = \id .
 \end{align}
@@
 where $\vect X_t$ denotes the Markov process generated by $\vect L(t)$.
- The
-discretization sets that we used to go from $\vect x_t$ and $\ml(t)$ to $\vect X_t$
+
+The discretization sets that we used to go from $\vect x_t$ and $\ml(t)$ to $\vect X_t$
 and $\vect L(t)$, respectively, can be assumed to provide an arbitrarily fine
@@
 of $\vect L(t)$ are almost perfect approximations of the transport properties
-of $\ml(t)$, in particular $p_i(t)=\prob(x_t\in \Omega_i)$.
-
-\section{Floquet theory}
+of $\ml(t)$, in particular the approximation $p_i(t)\approx \prob(x_t\in \Omega_i)$ is almost perfect.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Temporal discretization: Floquet theory}
 \label{sec:floquet}
@@
 \end{equation}
-for all $t\ge 0$. This can be seen by considering $\vect Y(t)=\myphi(t+T)$. $\vect Y$ satisfies
+for all $t\ge 0$. This can be seen by considering $\vect Y(t)=\myphi(t+T)$. It satisfies
 \[
@@
 know the solution $\vect p(t)$ of the Master equation for all $t\ge 0$,
-if we can compute $\myphi(t)$ for $t\in (0,T]$.  
+if we can compute $\myphi(t)$ for $t\in (0,T)$.  
 In particular we get the long-term evolution of the propagator:
@@
   \label{eq:floq-dynamics}
-  p(mT) =  \myphi(mT)\, p(0) = \myphi^m(T)\, p(0).
-\end{align}
-
-Since $\myphi(T)$ is a stochastic matrix, the spectrum $\sigma(\myphi(T))$
-of the matrix $\myphi(T)$ is contained in the circle in
-the complex plane, i.e., each eigenvalue $\lambda\in \sigma(\myphi(T))$
-satisfies $|\lambda|\le 1$. Furthermore $1\in\sigma(\myphi(T))$ is an
-eigenvalue with left eigenvector $\vect e$ and a right eigenvector $\mymu$
+  p(mT) =  \myphi(mT)\, p(0) = \myphi^m(T)\, p(0),
+\end{align}
+where $\myphi^m(T)$ denotes the $m$th power of the matrix $\myphi(T)$.
+Since $\myphi(T)$ is a stochastic matrix, its eigenvalues are contained in the unit circle in
+the complex plane, i.e., each eigenvalue $\lambda$ (potentially coomplex-valued)
+satisfies $|\lambda|\le 1$. Furthermore $\lambda=1$ is an
+eigenvalue with left eigenvector $\vect e=(1,\ldots,1)^T$ and a right eigenvector $\mymu$
 satisfying
@@
 \label{eq:floq-15}  
-\myphi(mT)\vect p(0)\to \mymu,\quad m\to\infty.
-\end{align}
-
-Using the Floquet theorem, the time-inhomogeneous Markov process $X_t$
+\myphi(mT)\vect p(0)\to \mymu,\quad m\to\infty,
+\end{align}
+so that $\mymu$ can be seen as the quasi-stationary distribution of our non-stationary process.
+
+Using the Floquet theorem, the time-inhomogeneous Markov jump process $X_t$
 is simplified into a \emph{time-homogeneous} (not necessarily
@@
 N$.
-Therefore, comparing with $X_t$, we prefer to consider the process $\tilde X_{m}$
-that helps understand the original dynamics $x_t$, because the powerful theories and
-computational tools for time-homogeneous processes can be directly applied.
+Therefore, we prefer to consider the discrete-time process $\tilde X_{m}$ instead of the time-continuous process $X_t$
+because the powerful theories and
+computational tools for time-homogeneous Markov processes can be directly applied.
+Many of these tools require the transition matrix $\myphi(T)$ to satisfy the detailed balance condition.
+The computations in the Appendix show that $\myphi$ will in general \emph{not} satisfy this condition; in fact  the deviation form reversibility can be estimated from the work of the periodic driving does to the system.
+
 There is no doubt that information within one period is lost by using this temporal
-discretization, however, information regarding the long-term behaviors
-of the system would be satisfactorily described as long as their time-scales
-are much longer than the period.
+discretization, however, information regarding the long-term behavior of the system on time-scales
+much longer than the period will be perfectly described because of $\tilde X_{m} = X_{mT}\approx x_{mT}$ whenever our spatial discretization is fine enough.
 At the same time,
-the computational cost of generating $\tilde X_{m}$ is mush less demanding
+the computational cost of generating $\tilde X_{m}$ is much less demanding
 than the brute force simulations of NEMD, which implies lower
 statistically uncertainty in calculating the observables of interest.
+
 % due to the discretization in both the spacial and temperal directions.
@@
 
-\section{Building the Markov state model}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Markov State Model}
 \label{sec:build-msm}
 
+% \subsection{Building the Markov State Model from the Floquet transition matrix}
 If the discretization cells $\Omega_i$, $i=1,\ldots,n$ form a fine
 partition of the molecular state space, the Markov chain defined via
-the transition matrix $\vect P=\myphi^T(T)$ still is a fine-scale description of the
-dynamics.  Now we want to coarse our description much further by
+the transition matrix 
+\begin{equation}\label{P}
+\vect P=\myphi^T(T)
+\end{equation}
+ is discrete in time but in space it still is a fine-scale description of the transport properties of the
+dynamics with a very large number $n$ of states.  Now we want to coarsen our description much further by
 constructing a Markov State Model (MSM) for $\vect P$ with $k\ll n$
-macrostates: The resulting $k\times k$ MSM transition matrix $\hat{\vect P}$
-then defines the coarse grained long term kinetics that should
-approximate the original long term kinetics well. In Ref.~\cite{sarich2010approximation}
-and \cite{schuette2011markov} it
-has been shown how to do this if $\vect P$ satisfies the detailed balance
+\emph{macrostates} that should be the metastable states of the system: The resulting $k\times k$ MSM transition matrix $\hat{\vect P}$
+then defines the coarse grained long term kinetics that shall
+approximate the original long term kinetics well. 
+The idea behind MSM building is that given the molecular system under consideration exhibits metastable conformations then it is usually possible to construct a
+relatively small number of discrete sets --the metastable sets that form the so-called macrostates-- that
+correctly describe the slow  dynamics, and 
+in each set the fast dynamics relaxes on some timescale significantly shorter than the metastable timescales.
+Then if the MSM dynamics reproduces the slow timescales and the corresponding transitions
+of the original dynamics~\eqref{eq:disc-1},
+the former is considered to be a good approximation of the later.
+
+MSM building has been attracted a lot of attention recently, and theory  \cite{A19-31} as well as algorithms \cite{A19-1}, applications (see e.g.
+\cite{A19-26,PNAS09} for two of hundreds of articles) and software \cite{A19-49, MSMBuilder} have been developed to quite an extend.
+However,
+by far most of the literature is related to building \emph{standard} MSMs for equilibirium MD.
+In standard MSM also the transition region has to be discretized, a feature that often forces the user to incorporate more macrostates than essentially needed to approximate the long-term kinetics.
+In Ref.~\cite{sarich2010approximation, A19-31,schuette2011markov,BucheteHummer} it has been shown how to construct \emph{non-standard} MSM that avoid this problem for equilibrium MD, i.e., if $\vect P$ satisfies the detailed balance
 condition: (1) Identify the cores of the metastable sets of the
@@
 macrostates are the metastable core sets and $\hat{\vect P}$ is the transition
-matrix of the milestone process that models the jumping behavior of
+matrix of the milestone process \cite{A19-31,schuette2011markov,A19-29} that models the jumping behavior of
 the original dynamics between the metastable regions.
@@
 However, since we cannot assume $P$ to satisfy detailed balance, we
-instead follow the approach recently proposed in Ref.~\cite{sarich2014utilizing}.
+instead follow the approach to non-standard MSMs recently proposed in Ref.~\cite{sarich2014utilizing}.
 It allows to identify the metastable core sets for the
@@
 Ref.~\cite{djurdjevac2010markov}, Thm. 3.1, the coarse grained transition
-matrix $\hat{P}$ has to be computed as follows:
+matrix $\hat{P}$ then has to be computed as follows:
 \begin{enumerate}
@@
 \begin{align}
-(P-\id) q^\fwd_j(i) & =  0, \quad i\in C\\
-q^\fwd_j(i) & =  1,\quad i\in C_j\\
-q^\fwd_j(i) & =  0,\quad i\in C_l,l\not=j
+(P-\id) q^\fwd_j(i) & =  0, \quad i\in C\label{qfwd}\\
+q^\fwd_j(i) & =  1,\quad i\in C_j\nonumber\\
+q^\fwd_j(i) & =  0,\quad i\in C_l,l\not=j\nonumber
 \end{align}
@@
 \begin{align}
-(P^b-\id) q^\bwd_j(i) & =  0, \quad i\in C\\
-q^\bwd_j(i) & =  1,\quad i\in C_j\\
-q^\bwd_j(i) & =  0,\quad i\in C_l,l\not=j
+(P^b-\id) q^\bwd_j(i) & =  0, \quad i\in C\label{qbwd}\\
+q^\bwd_j(i) & =  1,\quad i\in C_j\nonumber \\
+q^\bwd_j(i) & =  0,\quad i\in C_l,l\not=j\nonumber
 \end{align}
@@
 given by $P^b_{ji}=\mu_i P_{ij}/\mu_j$.
-
+\item Compute $\hat{\mu}(j)=\sum_{i\in S} q^\bwd_j(i)\mu(i)$,
+  which is the invariant measure of the MSM
+\item Construct the MSM transition matrix $\hat{P}$ according to
+  \begin{align}
+    \label{eq:msm-tmatrix-00}
+    \begin{split}      
+    \hat{\vect P}_{jk}
+    = &
+    \frac{1}{\hat{\mu}(j)}
+    \langle (\vect P^b - \id) q^\bwd_j,q^\fwd_k \rangle_\mu,\qquad j\not= k, \\    %\label{eq:msm-tmatrix-01}
+    \hat{\vect P}_{jj}
+    =&
+    1-\sum_{k\not=j} \hat{\vect P}_{jk}
+    \end{split}
+  \end{align}
+where the inner product is defined by
+$\langle u,v \rangle_\mu=\sum_{i\in S} u_i v_i \mu_i$.
+\end{enumerate}
+
+\noindent\textbf{Remark 1:}
 Alternatively, the forward and
-backward committors can be sampled via the definitions: The forward
+backward committors can be \emph{sampled} by means of the following procedure: The forward
 committor $q^\fwd_j(i)$ is defined as the probability of visiting coreset
@@
 of last coming from $C_j$ conditioned on being at state $i$.
-\item Compute $\hat{\mu}(j)=\sum_{i\in S} q^\bwd_j(i)\mu(i)$,
-  which is the invariant measure of the MSM
-\item Construct the MSM transition matrix $\hat{P}$ according to
-  \begin{align}
-    \label{eq:msm-tmatrix}
-    \hat{\vect P}_{jk}
-    = &
-    \frac{1}{\hat{\mu}(j)}
-    \langle (\vect P^b - \id) q^\bwd_j,q^\fwd_k \rangle_\mu,\qquad j\not= k, \\
-    \hat{\vect P}_{jj}
-    =&
-    1-\sum_{k\not=j} \hat{\vect P}_{jk}
-  \end{align}
-where the inner product is defined by
-$\langle u,v \rangle_\mu=\sum_{i\in S} u_i v_i \mu_i$.
-\end{enumerate}
+
+% \subsection{Building the Markov State Model from the NEMD simulation}
+\noindent\textbf{Remark 2:}
+Sometimes, it is not easy to have an explicit expression for the committors, however, we
+can still build the MSM by using the following procedure: Firstly compute the
+matrixes $\hat T$ and $\hat M$ by
+\begin{align}\label{eq:msm-ht}
+  \hat M_{jk} &= P [\,h_{mT}(C_k) < h_{mT}(\cup_{l\neq k}C_l) \,\vert\, \hat x_{mT} = j\,],\\\label{eq:msm-hm}
+  \hat T_{jk} &= P [\,h_{mT+T}(C_k) < h_{mT+T}(\cup_{l\neq k}C_l) \,\vert\, \hat x_{mT} = j\,],
+\end{align}
+where $\hat x_{mT}$ is milestone process corresponding to the NEMD trajectory $x_{mT}$ (notice here
+only integral periods $mT$ along the NEMD trajectories are used for building the milestone process).
+In Eq.~\eqref{eq:msm-ht} and \eqref{eq:msm-hm}, the time parameterized first hitting time of  set $A$ is defined by:
+\begin{align}
+  h_{t}(A) = \inf_{s\geq t}\{ s : x_s \in A \}.
+\end{align}
+It can be shown that (see Appendix~\ref{sec:app-prove} for details):
+\begin{align}\label{eq:msm-ht-1}
+  \hat T_{jk} &= \frac{\langle q_j^\bwd, P q_k^\fwd \rangle_\mu}{\hat \mu(j)},\\\label{eq:msm-hm-1}
+  \hat M_{jk} &= \frac{\langle q_j^\bwd, q_k^\fwd \rangle_\mu}{\hat \mu(j)}.
+\end{align}
+% \recheck{We may need to write why do these formula works, because in literature it is only available for reversible processes.}
+Therefore we have
+\begin{align}\label{eq:msm-tmp26}
+  \hat T_{ij} - \hat M_{ij}
+  = \frac{\langle q_j^\bwd, P q_k^\fwd \rangle_\mu}{\hat \mu(j)}
+  - \frac{\langle q_j^\bwd,  q_k^\fwd \rangle_\mu}{\hat \mu(j)}
+  = \frac{\langle (P^b - \id) q_j^\bwd, q_k^\fwd \rangle_\mu}{\hat \mu(j)}
+  = \hat P_{jk}, \quad j\neq k
+\end{align}
+By Eq.~\eqref{eq:msm-ht} and \eqref{eq:msm-hm}, we have $\sum_i\hat M_{ij} = \sum_i\hat T_{ij} = 1$, then
+$\sum_k(\hat M_{jk}- \hat T_{jk}) = 0$. By the second line of \eqref{eq:msm-tmatrix-00}, $\sum_k\hat P_{jk} = 1$, so using \eqref{eq:msm-tmp26} we have
+$\hat T_{jj} - \hat M_{jj} + 1 = \hat P_{jj}$.
+In the matrix expression the MSM transition matrix $\hat P$ is given by
+\begin{align}\label{eq:msm-tmatrix-10}
+  \hat P = \hat T - \hat M + \id
+\end{align}
+% Given coresets $\{C_1, \cdots, C_k\}$, the procedure \eqref{eq:msm-ht}--\eqref{eq:msm-tmatrix-10}
+% If assuming that we have the coresets $\{C_1, \cdots, C_k\}$, no matter how they are identified,
+In constrast to Eq.~\eqref{eq:msm-tmatrix-00}, which needs the intermediate spacial and
+temporal discretization (i.e.~the Floquet transition matrix $P$), 
+Eq.~\eqref{eq:msm-ht}, \eqref{eq:msm-hm} and \eqref{eq:msm-tmatrix-10} allows a direct derivation of the MSM from the original NEMD
+trajectories, which substantially simplified the MSM building.
+However, in the present paper, we present both the approachs,
+because the former contains more information regarding the original dynamics in $P$ and $L(t)$ than in $\hat P$.
+Moreover, the coreset identification may need a good spacial discretization to the original NEMD trajectories, which is
+usually consisten with that used to go from $\ml(T)$ to $L(t)$. In the end, the MSM
+built from both approachs should be consistent, taking no account of the statistical uncertainty in the samplings.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-If the spacial discretization is fine enough, the Markov jump
-process~\eqref{eq:disc-master} is a good approximation to the original
-MD~\eqref{eq:disc-1}.  In practice, it is difficult to predict
-how many discrete set is fine enough; Moreover, since the
-total configurational dimension of the system is $3N$ ($N$ being the
-number of atoms), it is prohibitive to do a very fine discretization
-over all DOFs for most of systems of practical interest.
-In the systems that possess a
-time-scale separation, it is possible, in most cases, to pick up
-a characteristic time (or lag-time) $\tau$ that distinguishes the slow
-and fast time-scales.
-For example, the conformational
-transitions of a large biomolecule is much slower than the covalent bond
-vibrations. 
-% It should be noted that we do NOT assume that the fast time-scales are decoupled with the slow time-scales~\footnote{If the fast time-scales
-%   are decoupled from the slow ones, then the story would become much simpler,
-% however, this situation is lack of generality, we will not discuss.}.
-In this context,
-it is usually possible to construct a
-relatively small number of discrete sets that
-correctly describe the slow  dynamics, and 
-in each set the fast dynamics relaxes within the lag-time $\tau$.
-Then if the discretized dynamics~\eqref{eq:disc-master}
-reproduces the slow time-scales and the corresponding transitions
-of the original dynamics~\eqref{eq:disc-1},
-the former is considered to be a good approximation of the later.
-% Then the 
-% dynamics~\eqref{eq:disc-master} built on top of the discretization
-% is a good approximation to~\eqref{eq:disc-1}
-% in the sense of reproducing the slow dynamics.
-One possible way to define the discretized set is firstly to find a few collective
-variables, and then to discretize the dynamics as fine as possible only on these
-variables either by uniform or adaptive
+We know that --in theory-- whenever the spatial discretization is fine enough, the Markov jump
+process $X_t$ associated with the Master equation \eqref{eq:disc-master} is a good approximation to the original
+MD process $x_t$ governed by \eqref{eq:disc-1}.  In practice, however, it is difficult to predict
+how many discrete sets we need to be fine enough. Moreover, since the
+total dimension of $x_t$ is $3N$ ($N$ being the number of atoms), it is prohibitive to do a really fine discretization
+over all DOFs for most systems of practical interest.
+
+One possible way to define appropriate discretization sets is firstly to find a few collective
+variables, and then to discretize these collective variables as finely as needed either by uniform or adaptive
 discretization~\cite{chodera2007automatic, prinz2011markov}.
@@
 % within the discretized sets.
-However, it is difficult to give a general answer in prior regarding, e.g.
-how large is the lag-time,
-how to choose the collect variables, how fine the discretization should be.
+However, it is difficult to give a general answer in prior regarding
+how to choose the collect variables and how fine their discretization should be.
 For large or high dimensional systems, these questions usually become non-trivial.
@@
 
-To illustrate how the discretization works in practice, it is therefore
-useful to investigate the discussed approximations by a numerical
-example.  We take the alanine dipeptide system under an oscillatory EF,
+To illustrate how the discretization works in practice we take the alanine dipeptide system under an oscillatory EF,
 as an example, the NEMD simulation of which was
-extensively studied by Ref.~\cite{wang2014exploring}.  
+extensively studied in Ref.~\cite{wang2014exploring}.
+The system was simulated in a $2.7\times 2.7\times 2.7$~$\textrm{nm}^3$ periodic simulation
+region, with one alanine dipeptide molecules described by the CHARMM27 force field~\cite{foloppe2000all} dissolved in 641 TIP3P water molecules~\cite{jorgensen1983comparison}.
+The grid-based energy correction map (CMAP)~\cite{mackerell2004extending} was used
+to correct the backbone dihedral angle energies.
+All simulations were performed by a home-modified
+Gromacs~4.6.5~\cite{pronk2013gromacs} with CHARMM27 force field implemented~\cite{bjelkmar2010implementation}.
 The alanine dipeptide was put into the local thermostating
-environment, and was driven by a periodic electric field with period
-$T = 10$~ps. The 20,000 branching trajectories were simulated from 20,000
+environment, with a spherical dynamical region of radius~1.0~nm
+centered at the alpha-carbon.
+The Langevin thermostat with target temperature $\mathcal T = 300$~K
+and time-scale $\tau_T = 0.1$~ps was
+coupled to the thermostated region.
+The whole system was coupled to the Parrinello-Rahman barostat~\cite{parrinello1981polymorphic} (in standard Gromacs implementation) with $\tau_P = 2.0$~ps to
+keep the system at 1~Bar. The non-equilibirium trajectories
+were integrated by the Leap-frog scheme with a time-step of 0.002~ps.
+The short-range van der Waals interactions were cut-off at 1.00~nm, and were smoothed from
+0.95~nm to 1.00~nm by the ``\texttt{shift}'' method provide by Gromacs.
+The energy conserving 
+Particle Mesh Ewald (PME)~\cite{darden1993pme, essmann1995spm} method (``\texttt{pme-switch}'') was
+used to compute the long-range electrostatic interaction,
+with the same real-space cut-off radius as the van der Waals interactoins,
+and the Gromacs default Fourier spacing of 0.12~nm.
+The splitting
+parameter optimized with respect to the electrostatic force computing
+accuracy by Gromacs tool \texttt{g\char`_pme\char`_error}~\cite{wang2010optimizing}.
+The neighbor list was updated every 5 time-steps with a list-building radius 1.20~nm.
+All hydrogen involving covalent bonds were constrained by the LINCS algorithm~\cite{hess1997lincs}, except the water molecules that were constrained by the SETTLE algorithm~\cite{miyamoto2004settle}.
+The whole system was driven by a periodic electric field
+$E(t) = E_0\sin(2\pi t/T)$ and $D(x) = (1,0,0)^T$
+with intensity of the field being $E_0 = 1.0$~V/nm and period being
+$T = 10$~ps.
+The 20,000 branching trajectories were simulated from 20,000
 initial configurations that sample the equilibrium distribution.
-\redc{Write a lot of details on NEMD.}  The branching
-trajectories were each 4000~ps long, and the system reaches
-non-equilibrium stationary state in roughly 300~ps.
+% \redc{Write a lot of details on NEMD.}
+The equilibrium configurations were prepared by an equilibrium MD simulation
+of $10^6$~ps long, along which the snapshots were saved every 50~ps.
+% In the
+% equilibrium simulation the system was coupled to a global Langevin thermostat
+% with coupling time-scale $\tau_T = 0.5$~ps.
+The branching
+trajectories were each 4000~ps long, and the system reached
+non-equilibrium quasi-stationary state in roughly 300~ps.
+
+For this periodically driven molecular system we will first show how to choose an appropriately fine discretization. After validating this discretization we will consider
+the discretized dynamics generated by the Floquet transition matrix $\vect P$
+in comparison to the original NEMD simulation.
+Finally we will coarse grain this description further by constructiion of a $3$ state Markov State Model that is able to describe the long-term kinetics of the system correctly.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Spatial discretization}
 
@@
 two dihedral angles $\phi$ and $\psi$ as collective variables (see
-Fig.~\ref{fig:tmp1}), and the discretization is a uniform division of
-the $\phi$--$\psi$ plane. We denote the number of division on each
-dihedral by $K$, then the discretized sets are
+Fig.~\ref{fig:tmp1}), and the discretization is a uniform partition of
+the $\phi$--$\psi$ plane. We denote the number of discretization intervals on each
+dihedral by $K$, then we get $K^2$ discretization sets 
 $\{\Omega_i\},\ i\in S = \{1,\cdots,K^2\}$.
-One possible approximation to
-the discretized generator $L(t)$ is via
+
+Based on a given spatial discretization we can aggregate the transition matrix $\vect P=\myphi^T(T)$ just by counting the transition behavior of MD trajectories 
+\[
+\vect P_{ij}=\prob\left(\vect x_T=j\mid \vect x_0=i \right).
+\]
+However, $\vect P$ allows to approximate the original dynamics on multiples $mT$ of the period only. In order to have a time-continuos description we need the generator $L(t)$ of the Master equation. 
+If the discretization is fine enough one possible approximation to $L(t)$ is via
 the following forward finite difference scheme:
@@
   L_{ij}(t) \approx \frac{1}{\tau}
-  \,[\, \prob (\vect X_{t+\tau} = i \vert \vect X_{t} = j) - \delta_{ij} \,],
+  \,[\, \prob (\vect x_{t+\tau} = i \vert \vect x_{t} = j) - \delta_{ij} \,],
   \quad i,j\in S
 \end{align}
-and $\tau$ is the lag-time.
-In the following subsections~\ref{sec:alanine-disc} and \ref{sec:alanine-tau},
+and $\tau$ is an appropriate small enough lag-time.
+In the following 
 we investigate the discretization
 quality with respect to  the choice of $K$ and  lag-time $\tau$.
-Then
-the discretized dynamics generated by the Floquet transition matrix
-is compared with original NEMD simulation
-via considering the stationary probability density, the first mean hitting time
-and the forward and backward committors.
-
-\subsection{Discretizing the dihedral angles}
-\label{sec:alanine-disc}
 
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{fig/t010/discrete/fig-cg-prob.eps}  
-  \caption{The time-dependent probability $\mathbb
-    P\big(\phi\in[0,180), \psi\in [0,180)\big)$.  The NEMD simulation is compared with different
-    discretization methods. The red shadow region indicates the
+  \includegraphics[width=0.7\textwidth]{fig/t010/discrete/fig-cg-prob.eps}  
+  \caption{Time-dependent probability $\mathbb
+    P\big(\phi\in[0,180), \psi\in [0,180)\big)$.  The brute force NEMD simulation is compared with different
+    spatial discretization methods. The red shadow region indicates the
     statistical uncertainty of the NEMD simulation.}
@@
 We estimate the discretized generator $L(t), \ t\in[0,T)$
-from NEMD trajectories generated by $\ml(t)$ in time interval $[t_1,
+from NEMD trajectories generated by $\ml(t)$ in different time intervals $[t_1,
 t_2]$.
-Due to the periodicity of $\ml(t)$, if the discretized dynamics approximate the original
-dynamics good enough, generator  $L(t)$ should not depend on in which interval
-it is estimated, provided that the initial state of the system
+Whenever the discretization is fine enough the discretized dynamics approximates the original
+dynamics well, and the time-periodic generator $L(t)$ should not depend on the choice of the interval $[t_1,t_2]$ in the estimation procedure (\ref{eqn:tmp4}), provided that the initial state of the system
 is not very far from the stationary state at long-time limit.
@@
 choices of time intervals $[0, 80]$~ps and $[320, 400]$~ps, and then
-compare the time-dependent
-probability $\prob\big(\phi_t\in[0,180), \psi_t\in [0,180)\big)$
-with the NEMD result in
-Fig.~\ref{fig:tmp2}.
-The time derivative of the master equation~\eqref{eq:disc-master}
-is discretized by the forward Euler scheme with a time step of 0.5~ps.
+compare the time-dependent probability $\prob\big(\phi_t\in[0,180), \psi_t\in [0,180)\big)$
+with the (brute force) NEMD result in Fig.~\ref{fig:tmp2} using a lag-time $\tau=0.5$~ps.
 Using $K=2$ the dynamics depends on the time interval used for
@@
 approximations to the original dynamics with $K=2$. The reason is that the
-discretization is too coarse so that the dynamics cannot be fully
+discretization with $K=2$ is too coarse so that the dynamics cannot be fully
 equilibriated within the lag-time $\tau$ in each discretized set,
@@
 NEMD simulation within the error bar. Therefore, throughout this paper we use $K=20$
-to discretize  the dihedral angle space of the alanine dipeptide.
-For a good statistical accuracy, if not stated otherwise,
-we will use the full trajectories, i.e.~a time interval of
-$[0,4000]$~ps for estimating the discretized generator $L(t)$.
-
-\subsection{The choice of lag-time $\tau$}
-\label{sec:alanine-tau}
+to discretize  the dihedral angle space of alanine dipeptide.
+%For a good statistical accuracy, if not stated otherwise,
+%we will use the full trajectories, i.e.~a time interval of
+%$[0,4000]$~ps for estimating the discretized generator $L(t)$.
 
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{fig/t010/discrete/fig-cg-prob-tau.eps}  
-  \caption{The time-dependent probability $\mathbb
-    P\big(\phi\in[0,180), \psi\in [0,180)\big)$.  The NEMD simulation is compared with different
-    discretization methods. The red shadow region indicates the
+  \includegraphics[width=0.7\textwidth]{fig/t010/discrete/fig-cg-prob-tau.eps}  
+  \caption{Time-dependent probability $\mathbb
+    P\big(\phi\in[0,180), \psi\in [0,180)\big)$.
+The NEMD simulation is compared with the Master equation using generators discretized with $K=20$ and different lag time $\tau$.
+The red shadow region indicates the
     statistical uncertainty of the NEMD simulation.}
@@
 
-As discussed before, the lag-time should be chosen a value that lies
-in the spectrum gap of the original dynamics, so that it resolves the
-slow dynamics, and at the same time relaxes the fast dynamics. In
-practice, it is very difficult to estimate the lag-time in
-prior. Therefore, we consider 
+Next we discuss the effect of the lag time $\tau$ on the estimation of the generator. Therefore, we consider 
 different choices of $\tau$ (0.5, 1.0, 2.0 and 5.0~ps)
-discretizing the same original dynamics, and compare the
-time-dependent probability $\prob\big(\phi\in[0,180), \psi\in
-[0,180)\big)$ calculated from different time discretization with the NEMD simulation
-of the original dynamics
-(see Fig.~\ref{fig:tmp3}).  All cases use identical dihedral angle discretization: $K=20$.
-It is clear that when lag-time is close to the period (10~ps), the
+(see Fig.~\ref{fig:tmp3}), all based on the identical dihedral angle discretization using $K=20$.
+It is clear that when the lag-time is close to the period (10~ps), the
 discretized dynamics cannot resolve the probability change within a
-period. However, it is surprising  that the large lag-times are able to capture the
+period. However, it is surprising  that even quite large lag-times are able to capture the
 the overall long time behavior of the original dynamics.
@@
 Therefore, throughout this paper $\tau=0.5$~ps will be used.
-We do not investigate the small $\tau$ limit, because saving trajectories
-more frequently requires more hard disk space, and is usually not preferred in practice.
-
-\subsection{Steady state distribution}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Quasi-stationary distribution $\mymu$}
 
@@
   \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3/fig-floquet-vec-1.eps}
-  \caption{The color scale plot of the logarithm stationary probability
+  \caption{The color scale plot of the logarithmic quasi-stationary distribution $\mymu$
     of (a) the NEMD  and (b)
-    the Floquet matrix $\Phi(T)$.
+    the Floquet matrix $\vect P=\myphi^T(T)$.
   }
@@
 
-Comparing with the time-homogeneous Markov processes, there are not as
-many tools for understanding the time-inhomogeneous Markov process.
-Therefore, in the following subsections,
-we consider the time-homogeneous process $\tilde X_{m}$ generated by
-the Floquet transition matrix $P = \Phi^T(T)$, and investigate if it
+After having validated the fine-scale spatial discretization 
+we will now consider the time-homogeneous process $\tilde X_{m}$ generated by
+the Floquet transition matrix $P = \Phi^T(T)$, and investigate whether it
 reproduces the properties of the original  non-equilibrium process $x_t$.
@@
 An important check is the consistency between the
-stationary probability density of $\Phi(T)$ (i.e.~the leading eigenvector $\mu$) and that 
-estimated form the original NEMD simulation, along which only integral periods $mT$ are considered:
+stationary probability density of $\Phi(T)$ (i.e.~the leading eigenvector $\mymu$) and that 
+estimated form the original NEMD simulation,
+% along which only integral periods $mT$ are considered:
 \begin{align}
@@
 \end{align}
-On each NEMD branching trajectory, the very beginning 320~ps is discarded, and
-the rest of the trajectory in $[320,4000]$~ps is used to estimate
-the stationary probability. $\Phi(T)$ is computed by solving~\eqref{eq:disc-master-phi}
-in one period, where the discretized generator $L(t)$ was estimated
-from the full NEMD trajectories of $4000$~ps long.
-Moreover, to make it comparable to the free energy in equilibrium case, we take
-the logarithm of the properties, i.e.~$F_{\textrm{st}}(\phi,\psi)=
+On each NEMD branching trajectory the initial 320~ps is discarded and
+the rest of the trajectory in time interval $[320,4000]$~ps is used to estimate
+the quasi-stationary probability distribution $\rho_{\textrm{st}}$. 
+$\myphi(T)$ is computed as described above, and then $\mymu$ is computed as its leading eigenvector. In order to make it comparable to the free energy in the equilibrium case, we take
+the logarithm of the distributions, i.e.~$F_{\textrm{st}}(\phi,\psi)=
 -k_B\mathcal T\log \rho_{\textrm{st}}(\phi,\psi)$
@@
 
-\subsection{Coreset identification}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Core set identification}
 
@@
   \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3/fig-cluster.eps}
-  \caption{The coreset identification. Different colors indicate different coresets: $C_{\confaa}$ (green), $C_\beta$ (yellow) and $C_{\confc}$ (red).
-    The blue color means out of any coreset. (By Marco)}
+  \caption{The coreset identification. Different colors indicate different core sets: $C_{\confaa}$ (green), $C_\beta$ (yellow) and $C_{\confc}$ (red).
+    The blue color indicates the transition region $C$ that does not belong to one of the core sets.}
   \label{fig:cluster}
@@
 
-\redc{Write how to detect the core sets for irreversible Markov process}.
-
-The coresets (see Fig.~\ref{fig:cluster}) are denoted by $C_{\confaa}$ (yellow), $C_\beta$ (red) and $C_{\confc}$ (green), which correspond to
-right-handed alpha-helix, beta-sheet and left-handed alpha-helix, respectively.
-
-\subsection{First mean hitting time}
+The procedure for identifying good metastable core sets of the irreversible Markov process associated with $\vect P$ is described in detail in Ref.~\cite{sarich2014utilizing}; here we just provide the fundamental idea behind it: If  strong metastable sets $C_j$, $j=1,\ldots,k$ exist they should have one main property: When starting from a state in $C_i$ the expected hitting time of a state in $C_i$ should be much shorter than that of any state in one of the other sets $C_j$, $j\not=i$; in fact, the hitting time distribution should exhibit roughly constant levels in each set $C_j$ and should vary significantly in the transition region $C=\Omega\setminus\cup_j C_j$ between the metastable sets.
+If starting from some randomly chosen initial states, one thus can identify the metastable core sets and the transition region by analyzing the hitting time distributions.
+This procedure is similar to the procedures used for reversible processes \cite{PCCAplus,A19-1,prinz2011markov} but utilizes hitting time distributions instead of any eigenvector information.
+
+The metastable core sets identified by this procedure based on the estimate of $\vect P$ are illustrated in Fig.~\ref{fig:cluster} and denoted by $C_{\confaa}$ (yellow), $C_\beta$ (red) and $C_{\confc}$ (green).
+They correspond to the centers of the wells in the free energy landscapes shown in Fig.~\ref{fig:num-1} and to the
+right-handed alpha-helix, beta-sheet and left-handed alpha-helix conformations of the peptide, respectively.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{First mean hitting times}
 \label{sec:alanine-fmht}
@@
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-msm-3.eps}\\
-  \caption{The first mean hitting time (FMHT) comparison between the NEMD
-    simulation (first column) and the discretized dynamics (second column).  From up
-    to down are first mean hitting time to coresets $C_{\confaa}$ and $C_{\beta}$
-    and $C_{\confc}$, respectively}
+  \caption{Comparisons of the first mean hitting time (FMHT) based on NEMD
+    simulation (first column) and discretized dynamics (second column).  From top
+    to bottom the first mean hitting times to the core sets $C_{\confaa}$, $C_{\beta}$,
+    and $C_{\confc}$ are shown, respectively}
   \label{fig:num-6}
@@
 
-The first mean hitting time, as a function of the dihedral angles $(\phi,\psi)$,
-is defined by the
-averaged first time needed for hitting a certain coreset
-$i\in\{\alpha_R,\beta,\alpha_L\}$, conditioned on starting from the
-conformation $(\phi,\psi)$.  Since the largest first mean hitting
-time (starting from coreset $\confaa$ to $\confc$) is longer than
-600~ps, if we use the NEMD trajectories of length 4000~ps,
-the results will be biased. Therefore, we use 100 NEMD
-trajectories of $2\times 10^5$~ps instead. We also compute the first mean hitting
-time of 
-a  $10^9$~ps long (being $T=10$~ps, $m = 1,\cdots, 10^8$)
-discretized trajectory $\tilde
-X_{m}$ that is generated by the Floquet transition matrix $P=\Phi^T(T)$.
-The first mean hitting time is presented in Fig.~\ref{fig:num-6}.  The
+The first mean hitting time as a function of the dihedral angles $(\phi,\psi)$,
+is defined by the expected first time needed for hitting a certain core set $C_j$,
+$j\in\{\alpha_R,\beta,\alpha_L\}$ conditioned on starting from the
+conformation $(\phi,\psi)$, more exactly from equilibirum conformations $(\phi,\psi)\in\Omega_i$.  Since the largest first mean hitting
+time (starting from states in coreset $\confaa$ and hitting $\confc$) is longer than
+600~ps the results will be biased if we use the NEMD trajectories of length 4000~ps for brute force Monte Carlo estimation of the hitting time. 
+Therefore, we base our Monte Carlo estimate on 100 NEMD
+trajectories of $2\times 10^5$~ps instead. For comparison we compute the first mean hitting
+time of the discretized dynamics via its transition matrix $\vect P$: the first mean hitting time $h_C(i)$ of core set $C$ starting in $\Omega_i$ can  be computed by means of solving the linear problem \cite{A19-31}
+\[
+(\vect P-\id) h_C(i) = -1,\qquad \mathrm{if} \, C\cap \Omega_i=\emptyset.
+\] 
+The resulting first mean hitting times are presented in Fig.~\ref{fig:num-6}.  The
 good consistency between the NEMD and the discretized Markov process
 $\tilde X_{m}$ indicates a good approximation quality.
-Since the length of the discretized process is substantially longer than
-the total length of NEMD
-simulation ($10^9$~ps v.s.~$2\times10^7$~ps), the statistically uncertainty
-is much smaller. 
-However, one should notice that systematic errors
-are introduced during the discretization (estimating $L(t)$), and 
-its potential influence on the observables,
-e.g.~the first mean hitting time, is not straightforward to estimate.
-This topic is out of the scope of the current paper,
-and will not be discussed in detail.
-In summary, very long discretized trajectories helps in calculating the observables
-in a smoother  (less statistical error) but not necessarily more accurate manner.
-On the other hand, the computational cost of
+One should note that the NEMD estimate of the first mean hitting time is subject to statistical sampling errors while the first mean hitting times $h_C$ only contain the statistical errors coming from the estimation of $\vect P$.
+Thus, using $P$ helps in calculating the observables
+in a smoother  manner (less statistical error, no additional sampling).
+Additionally, the computational cost of the
 discretized process, if the cost for estimating $\Phi(T)$ is not included, is
-essentially cheaper than NEMD:
-it took roughly 10 minutes on one core of an Intel Xeon E31245 CPU for generating the discretized trajectory, while the
+essentially smaller than NEMD:
+the computation of $h_C$ is an issue of miiliseconds on a laptop, while the
 NEMD trajectories took $1.6\times 10^4$ core hours for Intel Xeon E5-4650 CPUs.
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Forward and backward committors}
@@
   \caption{The forward $q^\fwd_{\confc}$ and backward committors
-    $q^\bwd_{\confc}$ computed by discretized dynamics (second row) is compared with
-    those computed by NEMD simulations (first
+    $q^\bwd_{\confc}$ computed by the discretized dynamics (second row) and NEMD simulations (first
     row).}
@@
   \caption{The forward $q^\fwd_{\confaa}$ and backward
-    $q^\bwd_{\confaa}$ committors computed by discretized dynamics (second row) is
-    compared with those computed by NEMD
+    $q^\bwd_{\confaa}$ committors computed by discretized dynamics (second row) and NEMD
     simulations (first row).}
@@
   \caption{The forward $q^\fwd_{\beta}$ and backward $q^\bwd_{\beta}$
-    committors computed by discretized dynamics (second row) is
-    compared with those computed by NEMD
+    committors computed by discretized dynamics (second row) and  NEMD
     simulations (first row).}
@@
 
-Committors are very important statistical properties of Markov processes, and play
-an important role in the later MSM building, therefore, it is worth
+Committors are very important statistical properties of Markov processes \cite{PrinzHeldSmithNoe_Committorprep,PNAS09}, and play
+an important role in MSM building \cite{A19-31,A19-29,djurdjevac2010markov} (see below), therefore, it is worth
 checking if the discretized process $\tilde X_m$ reproduces the NEMD committors.
@@
 i\in\{\confaa, \beta, \confc\}$ is defined as the probability of
-visiting coreset $C_i$ next conditioned on being at conformation
+visiting coreset $C_i$ next conditioned on starting at conformation
 $(\phi,\psi)$.  The backward committor $q^\bwd_i(\phi,\psi)$ of a
 coreset $C_i,\ i\in\{\confaa, \beta, \confc\}$ is defined as the
-probability of last coming from $C_i$ conditioned on being at
+probability of last coming from $C_i$ conditioned on having arrived presently at
 configuration $(\phi,\psi)$.
@@
 general not the case for irreversible processes.
-The committors estimated from NEMD simulations ($20000$ trajectories $4000$~ps each) is compared with
-those estimated from the discretized trajectory $\tilde X_m$, which is the same as the one used in Sec.~\ref{sec:alanine-fmht} for first mean hitting time.
+The committors estimated from NEMD simulations ($20000$ trajectories $4000$~ps each) are compared with
+those computed from $P$ by means of solving the linear equations (\ref{qfwd}) and (\ref{qbwd}).
 Fig.~\ref{fig:num-3}--\ref{fig:num-5} presents both
-committors as well as their difference corresponding to different coresets.
-The committors of the discretized process is in good consistency with those of
+committors as well as their difference corresponding to different core sets.
+The committors of the discretized process are in good consistency with those of
 the NEMD simulations. The non-zero values in the committor differences
@@
 the discretized process is able to correctly describe this irreversiblity.
-Also the accurate reproduction of the committors indicates it is reasonable to build the 
+In addition, and subsequently of central importance, the accurate reproduction of the committors indicates it is reasonable to build the 
 MSM out of the committors of the  discretized process.
 
-\subsection{Building MSM}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{MSM building and validation}
+
 Following the process described in Sec.~\ref{sec:build-msm}, we are able to build a 
-three states MSM for the alanine dipeptide system,
-where the stationary probability and the committors are
-estimated by the discretized process $\tilde X_m$, see
-Sec.~\ref{sec:alanine-committor}.
-The leading eigenvalues of $P=\Phi^T(T)$ is compared with those of the MSM, i.e.~$\hat P$ in
+three state MSM for the externally driven alanine dipeptide system,
+where the quasi-stationary probability distribution $\mu$, the three core sets, and the forward and backward committors are
+estimated as described above, and the MSM transition matrix $\hat P$ is then evaluated using Eq.~\eqref{eq:msm-tmatrix-00}.
+Alternatively, the MSM  transition matrix $\hat P$ is calculated directly from the NEMD trajectories by Eq.~\eqref{eq:msm-tmatrix-10}.
+The leading eigenvalues of $P=\myphi^T(T)$ are compared with those of $\hat P$ in
 Tab.~\ref{tab:tmp1}.
+Without surprising, the two approaches for MSM building are consitent.
 The MSM is able to accurately reproduce
@@
 the corresponding time scale is 26.5~ps (calculated by $-T/\log(\lambda_2)$),
-which is NOT significantly longer than the time resolution $T=10$~ps.
-It worth noting that although the discretized process $\tilde X_m$ is irreversible,
+which is NOT significantly longer than the temporal resolution given by the period $T=10$~ps of the external driving force.
+It is worth noting that although the discretized process $\tilde X_m$ is irreversible,
 the MSM built out of it is almost reversible:
@@
   \caption{
-    The eigenvalue comparison
+    Comparison of second and third eigenvalues of $\vect P$ and $3\times 3$ MSM transition matrix $\hat{P}$ from two approaches.
   }
-  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}c rrr}\hline\hline
-      &  $\lambda_2$ & $\lambda_3$ & $\lambda_4$ \\\hline
-    $P$         &0.907  &0.686 & 0.553       \\
-    $\hat P$    &0.911  &0.724 & --       \\
+  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}cc rrr}\hline\hline
+      & method &  $\lambda_2$ & $\lambda_3$ & $\lambda_4$ \\\hline
+    $P$         & --         &0.907  &0.686 & 0.553       \\
+    $\hat P$    &\eqref{eq:msm-tmatrix-00} & 0.911  &0.724 & --       \\
+    $\hat P$    &\eqref{eq:msm-tmatrix-10} & 0.909  &0.712 & --       \\
     \hline\hline
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3/fig-coreset-prob.eps}
-  \caption{The time-dependent probability $\hat P_l$.
-    Solid lines are from NEMD simulation, while the dashed lines are from MSM.}
+  \includegraphics[width=0.85\textwidth]{fig/t010/cluster.marco.3/fig-coreset-prob.eps}
+  \caption{Comparison of NEMD and MSM long-term kinetics of alanine dipeptide in an oscillatory electrc field.
+The plots show the time-dependent probability $p_j=\hat p(j,t)$ to be assigned to core set $C_j$ (corresponding to the observable $\mathcal A$ given in (\ref{A}) with $\alpha_j=1$ and $\alpha_i=0$ for $i\not= j$).
+Solid lines are from brute force NEMD simulations, while the dashed lines are from our MSM.}
   \label{fig:num-7}
@@
 
-We study the time-dependent expectation values of
-the properties, i.e.
+In fact, $\hat{P}$ can be considered as the fingerprint of the long-term kinetics (cf. \cite{A19-39,PrinzKellerNoe_PCCP11_Perspective}) of alanine dipeptide in an oscillatory electric field.
+In order to provide further validation of this statement, we study  time-dependent expectation values of
+the form
 \begin{align}
@@
 \end{align}
-which are linear combinations of the backward
-committor, i.e.
-\begin{align}
-  A(i) = \sum_{l=1}^k \alpha_l q^\bwd_l(i)
-\end{align}
-then
+where $p_i(t)=\prob(X_t=i)$ denotes the probability to be in set $\Omega_i$ at time $t$ as governed by the Master equation, and the observable $\mathcal A$ is spanned by the backward
+committors, i.e.,
+\begin{align}\label{A}
+  A(i) = \sum_{l=1}^k \alpha_l q^\bwd_l(i).
+\end{align}
+Then
 \begin{align}\nonumber
   \mathcal A(t) &=
-  \sum_{i\in S} \sum_{l=1}^k \alpha_l q^\bwd_l(i)  p(i,t) \\\nonumber
+  \sum_{i\in S} \sum_{l=1}^k \alpha_l q^\bwd_l(i)  p(i,t)=\sum_{i\in S} \sum_{l=1}^k \alpha_l \prob (\hat X_t = l \vert X_t = i) \prob (X_t = i) \\
   & =
-  \sum_{i\in S} \sum_{l=1}^k \alpha_l \prob (\hat X_t = l \vert X_t = i) \prob (X_t = i) \\\nonumber
-  & =
-  \sum_{i\in S} \sum_{l=1}^k \alpha_l \prob (\hat X_t = l ,X_t = i) \\\nonumber
-  & =
-  \sum_{l=1}^k \alpha_l \prob (\hat X_t = l) \\\label{eq:num-28}
-  & =
-   \sum_{l=1}^k \alpha_l \,\hat p (l, t),
-\end{align}
-where the time-dependent projected probability is governed by the MSM:
+  \sum_{i\in S} \sum_{l=1}^k \alpha_l \prob (\hat X_t = l ,X_t = i)  =
+  \sum_{l=1}^k \alpha_l \prob (\hat X_t = l) 
+ =
+   \sum_{l=1}^k \alpha_l \,\hat p (l, t), \label{eq:num-28}
+\end{align}
+where the time-dependent probability $\hat{p}(i,t)$ of being assigned to MSM macrostate $i$ at time $t$ can be computed  by means of the MSM via simple matrix multiplications:
 \begin{align}\label{eq:num-29}
-  \hat p(i, t+T) = \sum_{j\in S} \hat p(j,t)\hat P_{ji}
+  \hat p(i, t+T) = \sum_{j\in S} \hat p(j,t)\hat P_{ji}.
 \end{align}
 In Fig.~\ref{fig:num-7} we compare the numerical calculation of $\hat p (l, mT), \ m\in\mathbb N$ from NEMD and MSM calculations.
-In the former case, the backward committor and probability density
-on RHS of the projection $\hat p (l, mT) = \sum_{i\in S}  q^\bwd_l(i)  p(i,mT) $
-are estimated from the
-NEMD trajectories. For MSM, the projection of the initial probability is applied $\hat p (l, 0) = \sum_{i\in S}  q^\bwd_l(i)  p(i,0) $, then
-the time-dependent probability at $mT$ is generated by Eq.~\eqref{eq:num-29}.
+In the NEMD case, the backward committor and the probability density $\hat p (l, mT) = \sum_{i\in S}  q^\bwd_l(i)  p(i,mT) $
+are estimated directly from the
+NEMD trajectories. For the MSM, the projection of the initial probability is applied, $\hat p (l, 0) = \sum_{i\in S}  q^\bwd_l(i)  p(i,0) $, then
+the time-dependent probability at $mT$ is generated by Eq.~\eqref{eq:num-29}, i.e., by simple matrix multiplication. The agreement is almost perfect.
 % The projected probability, e.g.~$\hat p (l', mT)$ is calculated
 % by Eq.~\eqref{eq:num-28} letting $\alpha_l = \delta_{l'l}$.
+
+\section{Concluding remarks}
+
+In this paper we present the way of building MSM for a periodically
+driven non-equilibrium system.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.5\textwidth]{fig/flowchart/flowchart.eps}
+  \caption{The flowchart of this work.}
+  \label{fig:flowchart}
+\end{figure}
 
@@
 
+\section{Proves for Equations~\eqref{eq:msm-ht-1} and \eqref{eq:msm-hm-1} }
+\label{sec:app-prove}
+
+We firstly define $\hat q^\bwd_j (i) = P (X_t = i \vert \hat X_t =
+j)$, and always assume $t = mT$. Then due to the Bayes' Theorem we have
+\begin{align}
+  \hat q^\bwd_j (i) =
+  \frac{P (\hat X_t = j \vert X_t = i) P(X_t = i)}{ P(\hat X_t = j) } =
+  \frac{q^\bwd_j(i) \mu(i)}{\hat \mu(j)}
+\end{align}
+Then
+\begin{align*}
+  P& [\,h_t(C_k) < h_t(\cup_{l\neq k} C_l) \,\vert\, \hat X_t = j\,]\\
+  &=
+  \sum_{i=1}^n
+  \frac{P [\,h_t(C_k) < h_t(\cup_{l\neq k} C_l) , X_t = i, \hat X_t = j\,]}
+  { P(\hat X_t = j )} \\
+  &=
+  \sum_{i=1}^n
+  {P [\,h_t(C_k) < h_t(\cup_{l\neq k} C_l) \,\vert\, X_t = i, \hat X_t = j\,]}\,
+  \hat q^\bwd_j(i) \\
+  &=
+  \sum_{i=1}^n
+  {P [\,h_t(C_k) < h_t(\cup_{l\neq k} C_l) \,\vert\, X_t = i\,]}\,
+  \hat q^\bwd_j(i)  \\
+  &=
+  \sum_{i=1}^n
+  q^\fwd_k(i) \frac{q^\bwd_j(i) \mu(i)}{\hat \mu(i)} \\
+  &=
+  \frac{\langle q_j^\bwd, q_k^\fwd\rangle_\mu}{\hat \mu(j)}
+\end{align*}
+The third equation holds because of the Markovianity of the process $X_t$.
+The fourth equation is due to the definition of the forward committor.
+This proves Eq.~\eqref{eq:msm-ht-1}.
+To prove Eq.~\eqref{eq:msm-hm-1}, we firstly need
+\begin{align*}
+  P & [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \,\vert\, X_t = i\,]\\
+  &=
+  \sum_{l=1}^n
+  \frac{P [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l), X_{t+T} = l, X_t = i\,]}
+  {X_t = i} \\
+  &=
+  \sum_{l=1}^n
+  {P [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \vert X_{t+T} = l, X_t = i\,]}
+  {P( X_{t+T} = l \vert X_t = i)}\\
+  & =
+  \sum_{l=1}^n
+  {P [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \vert X_{t+T} = l\,]}
+  {P( X_{t+T} = l \vert X_t = i)} \\
+  &=
+  \sum_{l=1}^n
+  q^\fwd_k(l) P_{il}
+\end{align*}
+We used the Markovianity of $X_T$ at the third equation,
+and the time-homogeneity at the fourth equation.
+Therefore, following the same procedure proving Eq.~\eqref{eq:msm-ht-1}, we have
+\begin{align*}
+  P& [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \,\vert\, \hat X_t = j\,]\\
+  &=
+  \sum_{i=1}^n\sum_{l=1}^n
+  q^\fwd_k(l) P_{il}
+  \frac{q^\bwd_j(i) \mu(i)}{\hat \mu(i)} \\
+  &=
+  \frac{\langle q_j^\bwd, P q_k^\fwd\rangle_\mu}{\hat \mu(j)}  
+\end{align*}
+This proves Eq.~\eqref{eq:msm-hm-1}.
+
 \bibliography{ref}{}

### 2014-09-11 writedown/period.noneq.msm/paper.tex
added conclusion. worrying about the Markovianity of the L(t)

@@
 
-\section{Concluding remarks}
-
-In this paper we present the way of building MSM for a periodically
-driven non-equilibrium system.
+\section{Concluding remarks and discussions}
+
 \begin{figure}
@@
   \includegraphics[width=0.5\textwidth]{fig/flowchart/flowchart.eps}
-  \caption{The flowchart of this work.}
+  \caption{The flowchart of this work. A lighter color indicates
+  a ``more coarse'' approximation to the original NEMD dynamics.}
   \label{fig:flowchart}
 \end{figure}
+
+In this paper we methods of building MSM for a periodically driven
+non-equilibrium system. The methods are shown, by a numerical example
+of the alanine dipeptide under periodically oscillatory EF, to be
+valid and successfully captures the long-time behavior of the original
+non-equilibrium dynamics. We have provided and verified two equivalent
+pathways of building MSM, as is shown by the two branches in
+Fig.~\ref{fig:flowchart}.
+
+The the key steps of the first pathway are
+summarized as following:
+\begin{enumerate}
+\item By a fine discretization of the molecular configuration space,
+  the original NEMD dynamics is discretized into a (in principle)
+  time-continuous \recheck{Markov} jump process with a time-dependent generator $L(t)$.
+  If the discretization is good enough, then the discretized
+  dynamics is expected to reproduce the original dynamics.
+  In principle most of the discretiztion methods for the
+  equilibirum case can be generalized to  non-equilibrium without
+  substantial difficulty, however,
+  we have not discussed which discretiztion method is the best choice,
+  since it is out of the scope of the present work.
+  \recheck{It should be noticed that
+    we assume the jump process is Markovian, althogh in
+    general it is not true. However, if (1) the system present time-scale
+    seperation; (2) the spatial discretiztion is fine enough; (3)
+    we approximately consider a discretizted time
+    (can be very fine, and in computer the molecular configurations are
+    saved at discretizted time)
+    by lag-time $\tau$, so that within the lag-time
+    the fast dynamics of the system is fully relaxed; then
+    the Markovianity is a good assumption for the discretizted dynamics.
+  }
+  We show that, by numerical example, a uniform $20\times20$ discretiztion 
+  over the dihedral angles $\phi$--$\psi$ space is a good choice for
+  alanine dipeptide.
+  In the tests, the state independency of computing $L(t)$
+  is used as an indicator for
+  the quality of the discretiztion.
+\item By the Floquet thoerem, the time-inhomogeneous process generated
+  by $L(t)$ is temporally discretized in to a time-homogeneous,
+  but not necessarily reversible, jump process that has a transition
+  matrix denoted by $P$. This temporal discretiztion only  considers
+  the state of the system at integral periods, therefore all information
+  within one-period is not preserved. This is, however, not a serious
+  problem whenever the long-time hehaviors of the system is of interst, and
+  their corresponding time-scales are significantly longer than one period.
+  The advantage of this discretiztion
+  is also obvious: All well-developed theories and computational tools
+  for time-homogeneous Markov processes
+  can be directly appled. In the
+  alanine dipeptide system, we compare
+  the the quasi-stationary probability,
+  first mean hitting time, and the forward and backward committors
+  of the discretized dynamics with those computed directly from the
+  NEMD simulation. An almost perfect consistency 
+  indicates a good approximation quality of the discretized dynamics.
+\item From the disretized dynamics, building the MSM is straightforward
+  by using Eq.~\eqref{eq:msm-tmatrix-00} and a set of coresets.
+  Numerical results shows that a 3-state MSM can reporduce the leading
+  non-trivial eigenvalue with very good accuracy, while the second
+  non-trivial eigenvalue with acceptable accuracy. The lower accuracy
+  regarding the second non-trivial eigenvalue may be due to the fact that
+  the second slowest time-scale is not significantly longer than the
+  period. Using this three state MSM, we can also reproduce, with
+  almost perfect accuracy, the 
+  time-evolution of the metastable state
+  pobabilities from equilibirum (no external driven)
+  to the non-equilibrium quasi-stationary state.
+\end{enumerate}
+
+The right branch in Fig.~\ref{fig:flowchart} presents a
+equivalent, and seemingly
+much simpler alternative to the left branch, provided the
+coresets are known. Neverthless, in pactice, identifying
+the coresets is not a trivial task, especially for the
+non-equilibrium molecular systems.
+Therefore, a good discretization is  usually a must for computing the coreset.
+For example, in the present work, we computed the coresets by
+finding the roughly constant levels of the hitting time distribution.
+This method only works for the discretized dynamics $P$, and its continuous
+counterpart is still an open question.
+
+In this paper, we mainly focus on the methodology development for MSM
+building in non-equilibrium systems. It is worth noting that the
+numerical example itself presenst interesting phenomena: under the
+oscillatory EF, the population of the left-handed $\alpha$-helix
+significantly increases with respect to the equilibirum population
+(see also the discussions in Ref.~\cite{wang2014exploring}).  Along
+with building MSM, it is in principle possible to apply the non-equilibrium
+linear response theory~\cite{wang2013linear} to build a MSM for the perturbed
+system~\cite{schutte2014markov} with respect to original
+non-equilibrium system. This makes possible the molecular design under
+oscillatory EF, and could be used to answer the question like:
+in order to achieve a certain population of  the left-handed $\alpha$-helix,
+what kind of EF should be used to drive the system.
+In this work, we have not investigated in this direction, however, it will
+be treated in the future studies.
 

### 2014-09-11 writedown/zm/group.nlist/cutoff.tex
backup

@@
 
+A looser condition can be considered. Since only 0.16\% of the molecules
+has velocity larger than 5~nm/ps at a certain time frame, the velocity can be
+roughly bounded by  5~nm/ps.
+If the neighbor list is updated every 10 time-steps, 
+$d_{COG}$ is estimated to be roughly bounded $0.001 \times 10 \times 5 = 0.05$~nm.
+We can set  $\rlist - \rcoulomb = 0.26$~nm, then we need $d_{COG} < 0.052\ \textrm{nm}$, which is satisfied.
+
 Since all of our simulations had $\rlist - \rcoulomb = 0.3$~nm, the ZM

### 2014-09-11 writedown/zm/report/report.tex
backup

@@
   \centering
-  \includegraphics[]{pressure-methods.eps}
+  \includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
   \caption{The pressure convergence with respect to the cut-off radius.
@@
   \centering
-  \includegraphics[]{fig-gkr-small.eps}
-  \includegraphics[]{fig-gkr-small-conv.eps}
+  \includegraphics[]{fig/result.nvt.small/fig-gkr-small.eps}
+  \includegraphics[]{fig/result.nvt.small/fig-gkr-small-conv.eps}
   \includegraphics[]{fig/result.nvt.small/fig-eps-t-3000.eps}
@@
   \centering
-  \includegraphics[]{fig-gkr.eps}
-  \includegraphics[]{fig-gkr-conv.eps}
+  \includegraphics[]{fig/result.nvt/fig-gkr.eps}
+  \includegraphics[]{fig/result.nvt/fig-gkr-conv.eps}
   \includegraphics[]{fig/result.nvt/fig-eps-t-3000.eps}
@@
   \centering
-  \includegraphics[]{fig-gkr-10000.eps}
-  \includegraphics[]{fig-gkr-conv-10000.eps}
+  \includegraphics[]{fig/result.nvt/fig-gkr-10000.eps}
+  \includegraphics[]{fig/result.nvt/fig-gkr-conv-10000.eps}
   \includegraphics[]{fig/result.nvt/fig-eps-t-10000.eps}
@@
 conformations, i.e.~the $\alpha$-helix (right-handed), $\beta$-sheet and
-the left-handed $\alpha$-helix with satisfactory accuracy.  For these
-methods, deviations of $P(\phi)$ at $\phi = -75^\circ$ and $\phi =
--140^\circ$ are observed. They correspond to the double-peak structure
-of the right-handed $\alpha$-helix and $\beta$-sheet, which means the
-error happens at the sub-structure of the right-handed $\alpha$-helix
-and $\beta$-sheet, which are of relatively smaller biological interest
-comparing with the main conformations.
+the left-handed $\alpha$-helix with satisfactory accuracy.
+% For these
+% methods, deviations of $P(\phi)$ at $\phi = -75^\circ$ and $\phi =
+% -140^\circ$ are observed. They correspond to the double-peak structure
+% of the right-handed $\alpha$-helix and $\beta$-sheet, which means the
+% error happens at the sub-structure of the right-handed $\alpha$-helix
+% and $\beta$-sheet, which are of relatively smaller biological interest
+% comparing with the main conformations.
 
@@
     Method      &        $t_2$ [ps]  & $t_3$ [ps] &  $t_4$ [ps] \\\hline
-    SPME        &         1292  (148)     &          69.95  (0.76)  &         36.0 (4.7)    \\
-    RF          & \textbf{1615} (155)     &  \textbf{68.48} (0.37)  &         34.1 (1.6)    \\
-    ZM $l=1$    & \textbf{1607} (218)     &  \textbf{72.08} (0.50)  &         31.4 (1.9)    \\
-    ZM $l=2$    &         1324  (110)     &          69.97  (0.58)  &         40.4 (2.8)    \\
-    ZM $l=3$    &         1312  (157)     &          70.50  (0.72)  &         37.1 (4.3)    \\
-    ZM $l=4$    & \textbf{1635} (156)     &          69.71  (0.54)  &         39.2 (3.6)    \\
+    SPME        &         1374  (235)     &          70.03  (0.64)  &         39.2  (4.3)    \\
+    RF          &        {1615} (177)     &  \textbf{68.49} (0.42)  & \textbf{34.1} (2.2)    \\
+    ZM $l=1$    &        {1244} (099)     &         {71.00} (0.46)  &         36.2  (4.4)    \\
+    ZM $l=2$    &         1407  (194)     &          70.46  (0.76)  &         38.7  (2.4)    \\
+    ZM $l=3$    &         1449  (116)     &          70.20  (0.57)  &         37.4  (2.5)    \\
+    ZM $l=4$    &        {1119} (129)     &          70.05  (0.71)  &         34.6  (1.8)    \\
     \hline\hline
@@
 
+% \begin{figure}
+%   \centering
+%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-2.eps}
+%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-2.eps}
+%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-2.eps}
+%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-2.eps}
+%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-2.eps}\\
+%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-3.eps}
+%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-3.eps}
+%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-3.eps}
+%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-3.eps}
+%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-3.eps}\\
+%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-4.eps}
+%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-4.eps}
+%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-4.eps}
+%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-4.eps}
+%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-4.eps}\\
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-5.eps}\\
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-2-comp.eps}
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-3-comp.eps}
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-4-comp.eps}\\
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-2-comp.eps}
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-3-comp.eps}
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-4-comp.eps}\\
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-2-comp.eps}
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-3-comp.eps}
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-4-comp.eps}\\
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-5-comp.eps}\\
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-5.eps}\\
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-spme-eig-vec-2.eps}
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-2.eps}
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-2.eps}
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-2.eps}\\
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-spme-eig-vec-3.eps}
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-3.eps}
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-3.eps}
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-3.eps}\\
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-spme-eig-vec-4.eps}
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-4.eps}
+%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-2-comp.eps}
+%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-3-comp.eps}
+%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-4-comp.eps}\\
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-4.eps}
+%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-5.eps}\\
+%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-2-comp.eps}
+%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-3-comp.eps}
+%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-4-comp.eps}
+%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-5-comp.eps}\\
+%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-4.eps}\\
+%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-5.eps}\\
+%   \caption{The eigenfunctions corresponding to the largest three
+%     non-trivial timescales, computed with lag-time 20~ps.}
+%   \label{fig:tmp5}
+% \end{figure}
+
 \begin{figure}
   \centering
-  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-2.eps}
-  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-2.eps}
-  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-2.eps}
-  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-2.eps}
-  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-2.eps}\\
-  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-3.eps}
-  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-3.eps}
-  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-3.eps}
-  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-3.eps}
-  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-3.eps}\\
-  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-4.eps}
-  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-4.eps}
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-2-comp.eps}
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-3-comp.eps}
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-4-comp.eps}\\
-  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-4.eps}
-  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-4.eps}
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-5.eps}\\
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-2-comp.eps}
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-3-comp.eps}
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-4-comp.eps}
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-5-comp.eps}\\
-  \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-4.eps}\\
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-5.eps}\\
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-spme-eig-vec-2.eps}
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-2.eps}
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-2.eps}
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-2.eps}\\
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-spme-eig-vec-3.eps}
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-3.eps}
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-3.eps}
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-3.eps}\\
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-spme-eig-vec-4.eps}
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-4.eps}
-  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-2-comp.eps}
-  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-3-comp.eps}
-  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-4-comp.eps}\\
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-4.eps}
-  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-5.eps}\\
-  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-2-comp.eps}
-  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-3-comp.eps}
-  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-4-comp.eps}
-  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-5-comp.eps}\\
-  % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-4.eps}\\
-  % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-5.eps}\\
+  \includegraphics[width=0.24\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-2.eps}
+  \raisebox{.35cm}{\includegraphics[width=0.21\textwidth]{fig/result.alanine.amber/fig-eig-vec-error-2-phi.eps}}
+  \raisebox{.35cm}{\includegraphics[width=0.21\textwidth]{fig/result.alanine.amber/fig-eig-vec-error-2-psi.eps}}\\
+  \includegraphics[width=0.24\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-3.eps}
+  \raisebox{.35cm}{\includegraphics[width=0.21\textwidth]{fig/result.alanine.amber/fig-eig-vec-error-3-phi.eps}}
+  \raisebox{.35cm}{\includegraphics[width=0.21\textwidth]{fig/result.alanine.amber/fig-eig-vec-error-3-psi.eps}}\\
+  \includegraphics[width=0.24\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-4.eps}
+  \raisebox{.35cm}{\includegraphics[width=0.21\textwidth]{fig/result.alanine.amber/fig-eig-vec-error-4-phi.eps}}
+  \raisebox{.35cm}{\includegraphics[width=0.21\textwidth]{fig/result.alanine.amber/fig-eig-vec-error-4-psi.eps}}\\
   \caption{The eigenfunctions corresponding to the largest three
-    non-trivial timescales, computed with lag-time 20~ps.}
+    non-trivial timescales, computed with lag-time 20~ps.  The left
+    colume shows the eigenfunctions computed by SPME method. The right colume
+    shows the deviation of RF, ZM ($l=1,\cdots,4$) with respect to
+    SPME.  To present the statistical uncertainty, the second
+    eigenfunction is projected on to dihedral angle $\phi$, while the
+    third and fourth eigenfunctions are projected on $\psi$.  The red
+    shadow region presents the statistical uncertainty of SPME. For
+    clarity, only the statistical uncertainty of RF and ZM $l=3$ are
+    presented by error bars.  }
   \label{fig:tmp5}

### 2014-09-12 writedown/period.noneq.msm/paper.tex
some minor revise on the conclusion

@@
 
-In this paper we methods of building MSM for a periodically driven
-non-equilibrium system. The methods are shown, by a numerical example
-of the alanine dipeptide under periodically oscillatory EF, to be
-valid and successfully captures the long-time behavior of the original
+In this paper we developped methods of building MSM for a periodically driven
+non-equilibrium system. By a numerical example
+of the alanine dipeptide under periodically oscillatory EF,
+the methods are shown  to be
+valid and be able to capture the long-time behavior of the original
 non-equilibrium dynamics. We have provided and verified two equivalent
@@
     (can be very fine, and in computer the molecular configurations are
-    saved at discretizted time)
+    saved at discretizted time steps)
     by lag-time $\tau$, so that within the lag-time
@@
   alanine dipeptide.
-  In the tests, the state independency of computing $L(t)$
+  In the tests, the state independency in computing $L(t)$
   is used as an indicator for
@@
   the state of the system at integral periods, therefore all information
-  within one-period is not preserved. This is, however, not a serious
+  within the period is not preserved. This is, however, not a serious
   problem whenever the long-time hehaviors of the system is of interst, and
@@
 significantly increases with respect to the equilibirum population
-(see also the discussions in Ref.~\cite{wang2014exploring}).  Along
-with building MSM, it is in principle possible to apply the non-equilibrium
+(see also the discussions in Ref.~\cite{wang2014exploring}),
+and the leading time-scale is much shorter than the equilibirum case.
+It is in principle possible to apply the non-equilibrium
 linear response theory~\cite{wang2013linear} to build a MSM for the perturbed
-system~\cite{schutte2014markov} with respect to original
-non-equilibrium system. This makes possible the molecular design under
+non-equilibrium system with respect to original
+non-equilibrium system
+(the equilibirum counterpart is provided by Ref.~\cite{schutte2014markov}).
+This makes possible the molecular design under
 oscillatory EF, and could be used to answer the question like:

### 2014-09-12 writedown/period.noneq.msm/paper.tex
revise by CS

@@
 However, since we cannot assume $P$ to satisfy detailed balance, we
-instead follow the approach to non-standard MSMs recently proposed in Ref.~\cite{sarich2014utilizing}.
-It allows to identify the metastable core sets for the
+instead follow the approach to non-standard MSMs recently proposed in Ref.~\cite{sarich2014utilizing} which allows to identify the metastable core sets for the
 non-reversible transition matrix $P$. Assume that this approach leads
-to the $k$ core sets $C_1,\ldots, C_k\subset S$, and we denote $C=S\setminus\cup_j C_j$. Following
-Ref.~\cite{djurdjevac2010markov}, Thm. 3.1, the coarse grained transition
-matrix $\hat{P}$ then has to be computed as follows:
-\begin{enumerate}
-\item For the process associated with $P$ compute the forward and backward committors $q^\fwd_j$ and $q^\bwd_j$  for each core set $C_j$. This can be done by solving the linear equations
+to the $k$ core sets $C_1,\ldots, C_k\subset S$ that are appropriate metastable sets. 
+Following \cite{A19-31,schuette2011markov} the process $(X_m)$ associated with $P$ is coarse grained into the so-called milestone process $(\hat{X}_m)$ in the following way: 
+\begin{itemize}
+\item $\hat{X}_m$ just has $k$ states associated with the sets $C_j$, $j=1,\ldots,k$. 
+\item The sequence of random variables $(\hat{X}_m)$ is defined via the sequence $(X_m)$, i.e., trajectories of $(X_m)$ induce trajectories of $(\hat{X}_m)$: We set $\hat{X}_m=j$ if the last core set that the process $(X_m)$ entered prior to or at time $m$ has been the core set $C_j$.
+\end{itemize}
+Now consider infinitely long trajectory of $(X_m)$.
+Because of ergodicity we know that the states in this trajectory will be distributed due to the quasi-stationary distribution $\mu$.
+Based on such an infinitely long trajectory we can consider the probability $q_j^\bwd(i)$ that conditioned on $X_m=i$ the last core set hit has been $C_j$.
+This function is called the backward committor of $(X_m)$ associated with the set $C_j$ and is associated with the milestone process via
+\[
+q^\bwd_j(i)=\prob_\mu(\hat{X}_m=j|X_m=i),
+\] 
+where  the index $\mu$ refers to the fact that $\hat{X}_m$ is distributed due to $\mu$.
+From the last equation we get that the stationary distribution of the milestone process is given by
+\[
+\hat{\mu}(j)=\sum_{i\in S} q^\bwd_j(i)\mu(i),
+\]
+that is, the probability to find $\hat{X}_m=j$ in (infinitely) long trajectories of the milestoning process is $\hat{\mu}(j)$.
+
+Following \cite{discreteTPT} one also has to consider the forward committor $q^\fwd_j(i)$ identical to the probability  that conditioned on $X_m=i$ the next core set to be hit will be $C_j$.
+The forward and backward committors $q^\fwd_j$ and $q^\bwd_j$  for each core set $C_j$ can be computed from $P$ by solving the linear equations \cite{discreteTPT}
 \begin{align}
@@
 \end{align}
-and
+where $C=S\setminus\cup_j C_j$, and
 \begin{align}
@@
 given by $P^b_{ji}=\mu_i P_{ij}/\mu_j$.
-\item Compute $\hat{\mu}(j)=\sum_{i\in S} q^\bwd_j(i)\mu(i)$,
-  which is the invariant measure of the MSM
-\item Construct the MSM transition matrix $\hat{P}$ according to
+
+Following
+Ref.~\cite{djurdjevac2010markov}, Thm. 3.1, the one-step transition
+matrix $\hat{\vect P}$ associated with the milestone process $\hat{X}_m)$ is given by
   \begin{align}
@@
     \begin{split}      
-    \hat{\vect P}_{jk}
+    \hat{\vect P}_{jl}
     = &
     \frac{1}{\hat{\mu}(j)}
-    \langle (\vect P^b - \id) q^\bwd_j,q^\fwd_k \rangle_\mu,\qquad j\not= k, \\    %\label{eq:msm-tmatrix-01}
+    \langle (\vect P^b - \id) q^\bwd_j,q^\fwd_l \rangle_\mu,\qquad j\not= l, \\    %\label{eq:msm-tmatrix-01}
     \hat{\vect P}_{jj}
     =&
-    1-\sum_{k\not=j} \hat{\vect P}_{jk}
+    1-\sum_{l\not=j} \hat{\vect P}_{jl}
     \end{split}
@@
 where the inner product is defined by
-$\langle u,v \rangle_\mu=\sum_{i\in S} u_i v_i \mu_i$.
-\end{enumerate}
-
-\noindent\textbf{Remark 1:}
-Alternatively, the forward and
-backward committors can be \emph{sampled} by means of the following procedure: The forward
-committor $q^\fwd_j(i)$ is defined as the probability of visiting coreset
-$C_j$ next conditioned on being at state $i$.  The
-backward committor $q^\bwd_j(i)$  is defined as the probability
-of last coming from $C_j$ conditioned on being at state $i$.
-
-% \subsection{Building the Markov State Model from the NEMD simulation}
-\noindent\textbf{Remark 2:}
-Sometimes, it is not easy to have an explicit expression for the committors, however, we
-can still build the MSM by using the following procedure: Firstly compute the
-matrixes $\hat T$ and $\hat M$ by
-\begin{align}\label{eq:msm-ht}
-  \hat M_{jk} &= P [\,h_{mT}(C_k) < h_{mT}(\cup_{l\neq k}C_l) \,\vert\, \hat x_{mT} = j\,],\\\label{eq:msm-hm}
-  \hat T_{jk} &= P [\,h_{mT+T}(C_k) < h_{mT+T}(\cup_{l\neq k}C_l) \,\vert\, \hat x_{mT} = j\,],
-\end{align}
-where $\hat x_{mT}$ is milestone process corresponding to the NEMD trajectory $x_{mT}$ (notice here
-only integral periods $mT$ along the NEMD trajectories are used for building the milestone process).
-In Eq.~\eqref{eq:msm-ht} and \eqref{eq:msm-hm}, the time parameterized first hitting time of  set $A$ is defined by:
-\begin{align}
-  h_{t}(A) = \inf_{s\geq t}\{ s : x_s \in A \}.
-\end{align}
-It can be shown that (see Appendix~\ref{sec:app-prove} for details):
+$\langle u,v \rangle_\mu=\sum_{i\in S} u_i v_i \mu_i$. More precisely, we have
+\begin{equation}\label{hatP_prob}
+\hat{\vect P}_{jl}=\prob_\mu\Big(\hat{X}_{m+1}=l\vert \hat{X}_m=j\Big).
+\end{equation}
+In general the milestone process need not be a Markov process.
+The results in \cite{A1-31,sarich2014utilizing} show, however, that it is an approximate Markov process as long as the core sets are proper metastable sets, i.e., if the typical timecale on which $(X_m)$ leaves $C$ is much smaller than the typical expected hitting times between the core sets.
+Thus, by taking $\hat{P}$ as our MSM transition matrix, we introduce an additional modelling error that is the smaller the more metastable the core sets are.
+With this MSM transition matrix, we can define the MSM kinetics:
+If we start from some initial probability $\hat{p}(l,0)$ of being in state $l$ at time $t=0$ then its evolution $\hat{p}(l,t)$ in time is discrete in multiples of period $T$ and given by
+\recheck{
+\begin{equation}\label{eq:num-29}
+\hat{p}(l,T)=\sum_j \hat{p}(j,0)\,\,\hat{\vect P}_{jl}.
+\end{equation}}
+In our approach $p(j,mT)$ is a good approximation of $\prob(\hat{X}_m=j)$.
+
+\textbf{Remark 1:} Our definition of the milestoning process in terms of the process $(X_m)$ generated by $P$ guarantees that we can directly compute $\hat{P}$ via (\ref{hatP_prob})  from trajectories of $(X_m)$ without computing the committor functions.
+This is of importance if the spatial discretization underlying $(X_m)$ is fine enough, because then the kinetics of $(X_m)$
+approximates the original kinetics of $(x_{mT})$ so that we can directly compute   $\hat{P}$ via (\ref{hatP_prob})  from NEMD trajectories without computing $P$ first (which substantially simplified the MSM building if the core sets are already known).
+
+\textbf{Remark 2:}
+Following \cite{A19-31} we can also define another pair of stochastic MSM matrices: 
 \begin{align}\label{eq:msm-ht-1}
   \hat T_{jk} &= \frac{\langle q_j^\bwd, P q_k^\fwd \rangle_\mu}{\hat \mu(j)},\\\label{eq:msm-hm-1}
-  \hat M_{jk} &= \frac{\langle q_j^\bwd, q_k^\fwd \rangle_\mu}{\hat \mu(j)}.
-\end{align}
-% \recheck{We may need to write why do these formula works, because in literature it is only available for reversible processes.}
-Therefore we have
+  \hat M_{jk} &= \frac{\langle q_j^\bwd, q_k^\fwd \rangle_\mu}{\hat \mu(j)},
+\end{align}
+that are connected to $\hat{P}$ by the following identity
+\[
+\hat{P}=\hat{T}-\hat{M}+\id,
+\]
+That can be seen by means of direct computation: For the off-diagonal entries we have
 \begin{align}\label{eq:msm-tmp26}
@@
 \end{align}
-By Eq.~\eqref{eq:msm-ht} and \eqref{eq:msm-hm}, we have $\sum_i\hat M_{ij} = \sum_i\hat T_{ij} = 1$, then
-$\sum_k(\hat M_{jk}- \hat T_{jk}) = 0$. By the second line of \eqref{eq:msm-tmatrix-00}, $\sum_k\hat P_{jk} = 1$, so using \eqref{eq:msm-tmp26} we have
-$\hat T_{jj} - \hat M_{jj} + 1 = \hat P_{jj}$.
-In the matrix expression the MSM transition matrix $\hat P$ is given by
-\begin{align}\label{eq:msm-tmatrix-10}
-  \hat P = \hat T - \hat M + \id
-\end{align}
+Stochasticity yields
+$\hat T_{jj} - \hat M_{jj} + 1 = \hat P_{jj}$ for the diagonal entries.
+Furthermore, as shown in the Appendix $\hat{T}$ as well as $\hat{M}$ can be computed from trajectories without need to have the committors.
+The importance of the pair $\hat{T}$ and $\hat{M}$ for MSM building comes from the following observation: The main NEMD relaxation timescales are given by the dominant eigenvalues of $P$ \cite{A19-31, A19-1}.
+These dominant eigenvalues can be approximated by discretizing the related eigenvalue problem $Pu=\lambda u$ by means of a Galerkin approximation with the finite dimensional ansatz space 
+spanned by the forward committors $q^+_j$, $j=1,\ldots,k$ together  with the finite dimensional test function space spanned by the backward committors $q^-_j$, $j=1,\ldots,k$ (test functions multiplied from the left by the inner product $\langle\cdot,\cdot\rangle_\mu$).
+The thus discretize eigenproblem takes the form  of a generalized eigenproblem
+\[
+\hat{T}\hat{u}=\hat{\lambda}\hat{M}\hat{u}.
+\]
+For the reversible case it is known that its $k$ eigenvalues $\hat{\lambda}$ are very good approximation of the dominant eigenvalues $\lambda$ of the original problem if the core sets are proper metastable sets \cite{Eigenvalues}.
+Whether this is true for the non-reversible case is not known yet, but if the deviation from reversibility is weak and the dominant eigenvalues of $P$ are real-valued then the results should hold analogously, see \cite{A19-31}, Thm.
+4.19.
+
+The pair $\hat{T}$ and $\hat{M}$, or the matrix $\hat{M}^{-1}\hat{T}$ (if all of its entries are positive such that it is a stochastic matrix), thus can also be taken as MSM transition matrices.
+In the case of  $\hat{T}$ and $\hat{M}$ the MSM modelling error results from Galerkin discretization, while the MSM modelling error of $\hat{P}$ results from ignoring the potential non-Markovianity of $\hat{X}_m$.
+The lesson learnt in the reversible case are that $\hat{P}$ is better suited to approximate the molecular kinetics on large timescales while $\hat{T}$ and $\hat{M}$ should be used for approximating eigenvalues and long relaxation timescales.
+
 % Given coresets $\{C_1, \cdots, C_k\}$, the procedure \eqref{eq:msm-ht}--\eqref{eq:msm-tmatrix-10}
 % If assuming that we have the coresets $\{C_1, \cdots, C_k\}$, no matter how they are identified,
-In constrast to Eq.~\eqref{eq:msm-tmatrix-00}, which needs the intermediate spacial and
-temporal discretization (i.e.~the Floquet transition matrix $P$), 
-Eq.~\eqref{eq:msm-ht}, \eqref{eq:msm-hm} and \eqref{eq:msm-tmatrix-10} allows a direct derivation of the MSM from the original NEMD
-trajectories, which substantially simplified the MSM building.
-However, in the present paper, we present both the approachs,
-because the former contains more information regarding the original dynamics in $P$ and $L(t)$ than in $\hat P$.
-Moreover, the coreset identification may need a good spacial discretization to the original NEMD trajectories, which is
-usually consisten with that used to go from $\ml(T)$ to $L(t)$. In the end, the MSM
-built from both approachs should be consistent, taking no account of the statistical uncertainty in the samplings.
 
@@
 where the quasi-stationary probability distribution $\mu$, the three core sets, and the forward and backward committors are
-estimated as described above, and the MSM transition matrix $\hat P$ is then evaluated using Eq.~\eqref{eq:msm-tmatrix-00}.
-Alternatively, the MSM  transition matrix $\hat P$ is calculated directly from the NEMD trajectories by Eq.~\eqref{eq:msm-tmatrix-10}.
-The leading eigenvalues of $P=\myphi^T(T)$ are compared with those of $\hat P$ in
+estimated as described above, and the MSM transition matrices $\hat P$, $\hat{M}$, and $\hat{T}$ is then evaluated using Eq.~\eqref{eq:msm-tmatrix-00}and \eqref{eq:msm-ht-1}.
+Alternatively, the MSM  transition matrix $\hat P$ is calculated directly from the NEMD trajectories using Eq.~\eqref{hatP_prob} (very good agreement with the one computed from the committors).
+The leading eigenvalues of $P=\myphi^T(T)$ are compared with those of $\hat P$ and $\hat{M}^{-1}\hat{T}$ in
 Tab.~\ref{tab:tmp1}.
@@
 of the longest non-trivial implied time-scale. The accuracy of the second non-trivial
-time-scale is not as good as the first, but is still acceptable. The reason
+time-scale is not as good as the first, but is still acceptable (even good for $\hat{M}^{-1}\hat{T}$). The reason
 for the lower accuracy is that
@@
 which is NOT significantly longer than the temporal resolution given by the period $T=10$~ps of the external driving force.
+Numerically the two MSM transition matrices are:
+\[
+\hat{M}^{-1}\hat{T}=\left(\begin{array}{ccc}
+   0.866 &   0.128 &   0.006 \\
+    0.183  &  0.783  &  0.034\\
+    0.018   & 0.067 &   0.915
+\end{array}
+\right),\qquad \hat{P}=\left(\begin{array}{ccc}
+   0.888 &   0.105 &   0.007 \\
+    0.149  &  0.822  &  0.029\\
+    0.021   & 0.055 &   0.923
+\end{array}
+\right),
+\]
+from which we see that the longest relaxation timescale results from  the dominant metastability of the left-handed alpha-helix conformations of the peptide.
+
 It is worth noting that although the discretized process $\tilde X_m$ is irreversible,
@@
   \caption{
-    Comparison of second and third eigenvalues of $\vect P$ and $3\times 3$ MSM transition matrix $\hat{P}$ from two approaches.
+    Comparison of second and third eigenvalues of $\vect P$ and $3\times 3$ MSM transition matrices $\hat{P}$ and $\hat{M}^{-1}\hat{T}$, respectively, from the two different MSM approaches.
   }
-  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}cc rrr}\hline\hline
-      & method &  $\lambda_2$ & $\lambda_3$ & $\lambda_4$ \\\hline
-    $P$         & --         &0.907  &0.686 & 0.553       \\
-    $\hat P$    &\eqref{eq:msm-tmatrix-00} & 0.911  &0.724 & --       \\
-    $\hat P$    &\eqref{eq:msm-tmatrix-10} & 0.909  &0.712 & --       \\
+  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}c rrr}\hline\hline
+      &  $\lambda_2$ & $\lambda_3$ & $\lambda_4$ \\\hline
+    $P$                 &0.907  &0.686 & 0.553       \\
+    $\hat P$     & 0.911  &0.724 & --       \\
+    $\hat{M}^{-1}\hat{T}$    & 0.903  &0.662 & --       \\
     \hline\hline
@@
 \end{align}
-where the time-dependent probability $\hat{p}(i,t)$ of being assigned to MSM macrostate $i$ at time $t$ can be computed  by means of the MSM via simple matrix multiplications:
-\begin{align}\label{eq:num-29}
-  \hat p(i, t+T) = \sum_{j\in S} \hat p(j,t)\hat P_{ji}.
-\end{align}
+where the time-dependent probability $\hat{p}(i,t)$ of being assigned to MSM macrostate $i$ at time $t$ can be computed  by means of the MSM via simple matrix multiplications using (\ref{eq:num-29}).
+
 In Fig.~\ref{fig:num-7} we compare the numerical calculation of $\hat p (l, mT), \ m\in\mathbb N$ from NEMD and MSM calculations.
@@
 
-\section{Proves for Equations~\eqref{eq:msm-ht-1} and \eqref{eq:msm-hm-1} }
+\section{Computation of $\hat{T}$ and $\hat{M}$ directly from trajectories}
 \label{sec:app-prove}
 
-We firstly define $\hat q^\bwd_j (i) = P (X_t = i \vert \hat X_t =
+In order to show how to compute $\hat{T}$ and $\hat{M}$ directly from trajectories let us start by denoting the first hitting time of set $A$ starting at time $t$ by $h_t(A)$.
+In addition we define $\hat q^\bwd_j (i) = P (X_t = i \vert \hat X_t =
 j)$, and always assume $t = mT$. Then due to the Bayes' Theorem we have
@@
   \sum_{i=1}^n
-  q^\fwd_k(i) \frac{q^\bwd_j(i) \mu(i)}{\hat \mu(i)} \\
-  &=
-  \frac{\langle q_j^\bwd, q_k^\fwd\rangle_\mu}{\hat \mu(j)}
+  q^\fwd_k(i) \frac{q^\bwd_j(i) \mu(i)}{\hat \mu(i)} =\frac{\langle q_j^\bwd, q_k^\fwd\rangle_\mu}{\hat \mu(j)}={\hat M}_{jk}
 \end{align*}
-The third equation holds because of the Markovianity of the process $X_t$.
-The fourth equation is due to the definition of the forward committor.
-This proves Eq.~\eqref{eq:msm-ht-1}.
-To prove Eq.~\eqref{eq:msm-hm-1}, we firstly need
+where the third equation holds because of the Markovianity of the process $X_t$, and the fourth equation is due to the definition of the forward committor.
+The interpretation of the result is that when starting with the milestone process in state $j$ we have to determine the fraction of all trajectories that hit core set $C_k$ first of all core sets to estimate $\hat{M}_{jk}$.
+
+To see the same for $\hat{T}$, we first need
 \begin{align*}
@@
   {P [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \vert X_{t+T} = l\,]}
-  {P( X_{t+T} = l \vert X_t = i)} \\
-  &=
-  \sum_{l=1}^n
+  {P( X_{t+T} = l \vert X_t = i)}  = \sum_{l=1}^n
   q^\fwd_k(l) P_{il}
@@
 We used the Markovianity of $X_T$ at the third equation,
-and the time-homogeneity at the fourth equation.
-Therefore, following the same procedure proving Eq.~\eqref{eq:msm-ht-1}, we have
+and the time-homogeneity in the fourth equation.
+Therefore, following the same procedure as before we have
 \begin{align*}
-  P& [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \,\vert\, \hat X_t = j\,]\\
-  &=
+  P [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \,\vert\, \hat X_t = j\,]=
   \sum_{i=1}^n\sum_{l=1}^n
   q^\fwd_k(l) P_{il}
-  \frac{q^\bwd_j(i) \mu(i)}{\hat \mu(i)} \\
+  \frac{q^\bwd_j(i) \mu(i)}{\hat \mu(i)} = \frac{\langle q_j^\bwd, P q_k^\fwd\rangle_\mu}{\hat \mu(j)}  = {\hat T}_{jk}
+\end{align*}
+Thus, when starting with the milestone process in state $j$ at some time $t$ we have to determine the fraction of all trajectories of length at least $T$ that hit core set $C_k$ first of all core sets to estimate $\hat{T}_{jk}$.
+
+\section{The equivalence}
+\begin{align*}
+  \hat T_{jk} &=
+  P [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \,\vert\, \hat X_t = j\,]\\
   &=
-  \frac{\langle q_j^\bwd, P q_k^\fwd\rangle_\mu}{\hat \mu(j)}  
+  \frac{P [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l), \hat X_t = j\,] }{P(\hat X_t = j)}\\
+  & =
+  \sum_l \frac{P [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l), \hat X_{t+T} = l, \hat X_t = j\,] }{P(\hat X_t = j)}\\
+  & =
+  \sum_l P [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l)\vert \hat X_{t+T} = l, \hat X_t = j\,] \hat P_{jl}\\  
+  & =
+  \sum_l P [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l)\vert \hat X_{t+T} = l\,] \hat P_{jl}\\
+  &= 
+  \sum_l  \hat P_{jl}\hat M_{lk}
 \end{align*}
-This proves Eq.~\eqref{eq:msm-hm-1}.
 

### 2014-09-13 writedown/period.noneq.msm/fig/t010/cluster.marco.3/paste.commitor.sh
add missing files

@@ -1,0 +1,4 @@
+#!/bin/bash
+paste  commitor.fw.out commitor.bw.out > commitor.out
+paste  commitor.fw.msm.out commitor.bw.msm.out > commitor.msm.out
+

### 2014-09-13 writedown/period.noneq.msm/paper.tex
add new result and comment of the identity PM = T. update the T, M values, so that they are from sampling, rather than committors.

@@
 
-Following
-Ref.~\cite{djurdjevac2010markov}, Thm. 3.1, the one-step transition
-matrix $\hat{\vect P}$ associated with the milestone process $\hat{X}_m)$ is given by
+\recheck{
+We define the one-step transition matrix $\hat{\vect P}$ for the milestone process by
+\begin{equation}\label{hatP_prob}
+\hat{\vect P}_{jl}=\prob_\mu\Big(\hat{X}_{m+1}=l\vert \hat{X}_m=j\Big).
+\end{equation}
+Then Following
+Ref.~\cite{djurdjevac2010markov}, Thm.~3.1, 
+$\hat{\vect P}$ is associated with the milestone process $(\hat{X}_m)$ in terms of committors by}
   \begin{align}
@@
 where the inner product is defined by
-$\langle u,v \rangle_\mu=\sum_{i\in S} u_i v_i \mu_i$. More precisely, we have
-\begin{equation}\label{hatP_prob}
-\hat{\vect P}_{jl}=\prob_\mu\Big(\hat{X}_{m+1}=l\vert \hat{X}_m=j\Big).
-\end{equation}
+$\langle u,v \rangle_\mu=\sum_{i\in S} u_i v_i \mu_i$. 
 In general the milestone process need not be a Markov process.
-The results in \cite{A1-31,sarich2014utilizing} show, however, that it is an approximate Markov process as long as the core sets are proper metastable sets, i.e., if the typical timecale on which $(X_m)$ leaves $C$ is much smaller than the typical expected hitting times between the core sets.
+The results in \cite{A19-31,sarich2014utilizing} show, however, that it is an approximate Markov process as long as the core sets are proper metastable sets, i.e., if the typical timecale on which $(X_m)$ leaves $C$ is much smaller than the typical expected hitting times between the core sets.
 Thus, by taking $\hat{P}$ as our MSM transition matrix, we introduce an additional modelling error that is the smaller the more metastable the core sets are.
@@
 $\hat T_{jj} - \hat M_{jj} + 1 = \hat P_{jj}$ for the diagonal entries.
-Furthermore, as shown in the Appendix $\hat{T}$ as well as $\hat{M}$ can be computed from trajectories without need to have the committors.
+Furthermore, as shown in the Appendix~\ref{sec:app-prove}, $\hat{T}$ as well as $\hat{M}$ can be computed from trajectories without need to have the committors.
 The importance of the pair $\hat{T}$ and $\hat{M}$ for MSM building comes from the following observation: The main NEMD relaxation timescales are given by the dominant eigenvalues of $P$ \cite{A19-31, A19-1}.
@@
 The thus discretize eigenproblem takes the form  of a generalized eigenproblem
-\[
+\begin{align}
+  \label{eq:msm-gen-ev}
 \hat{T}\hat{u}=\hat{\lambda}\hat{M}\hat{u}.  
-\]
-For the reversible case it is known that its $k$ eigenvalues $\hat{\lambda}$ are very good approximation of the dominant eigenvalues $\lambda$ of the original problem if the core sets are proper metastable sets \cite{Eigenvalues}.
-Whether this is true for the non-reversible case is not known yet, but if the deviation from reversibility is weak and the dominant eigenvalues of $P$ are real-valued then the results should hold analogously, see \cite{A19-31}, Thm.
-4.19.
-
-The pair $\hat{T}$ and $\hat{M}$, or the matrix $\hat{M}^{-1}\hat{T}$ (if all of its entries are positive such that it is a stochastic matrix), thus can also be taken as MSM transition matrices.
+\end{align}
+For the reversible case it is known that its $k$ eigenvalues $\hat{\lambda}$ are very good approximation of the dominant eigenvalues $\lambda$ of the original problem if the core sets are proper metastable sets~\cite{Eigenvalues}.
+Whether this is true for the non-reversible case is not known yet, but if the deviation from reversibility is weak and the dominant eigenvalues of $P$ are real-valued then the results should hold analogously, see~\cite{A19-31}, Thm.~4.19.
+
+\textbf{Remark 3:}
+The pair $\hat{T}$ and $\hat{M}$, or the matrix $\hat{T}\hat{M}^{-1}$ (if all of its entries are positive such that it is a stochastic matrix), thus can also be taken as MSM transition matrices.
 In the case of  $\hat{T}$ and $\hat{M}$ the MSM modelling error results from Galerkin discretization, while the MSM modelling error of $\hat{P}$ results from ignoring the potential non-Markovianity of $\hat{X}_m$.
+\recheck{As a matter fact, if $\hat X_m$ is Markovian, we prove the identity of the transition matrices: $\hat P = \hat T \hat M^{-1}$ (see~Appendix~\ref{sec:app-ptm} for detail).
+Therefore, in practice, the deviation of the eigenvalues of $\hat P$ from those of $\hat{T}\hat{M}^{-1}$ indicates the non-Markovianity implied in the process $\hat{X}_m$.}
 The lesson learnt in the reversible case are that $\hat{P}$ is better suited to approximate the molecular kinetics on large timescales while $\hat{T}$ and $\hat{M}$ should be used for approximating eigenvalues and long relaxation timescales.
@@
 where the quasi-stationary probability distribution $\mu$, the three core sets, and the forward and backward committors are
-estimated as described above, and the MSM transition matrices $\hat P$, $\hat{M}$, and $\hat{T}$ is then evaluated using Eq.~\eqref{eq:msm-tmatrix-00}and \eqref{eq:msm-ht-1}.
+estimated as described above, and the MSM transition matrices $\hat P$, $\hat{T}$, and $\hat{M}$ is then evaluated using Eq.~\eqref{eq:msm-tmatrix-00}, \eqref{eq:msm-ht-1} and \eqref{eq:msm-hm-1}, correspondingly.
 Alternatively, the MSM  transition matrix $\hat P$ is calculated directly from the NEMD trajectories using Eq.~\eqref{hatP_prob} (very good agreement with the one computed from the committors).
-The leading eigenvalues of $P=\myphi^T(T)$ are compared with those of $\hat P$ and $\hat{M}^{-1}\hat{T}$ in
+The leading eigenvalues of $P=\myphi^T(T)$ are compared with those of $\hat P$ and $\hat{T}\hat{M}^{-1}$ in
 Tab.~\ref{tab:tmp1}.
@@
 of the longest non-trivial implied time-scale. The accuracy of the second non-trivial
-time-scale is not as good as the first, but is still acceptable (even good for $\hat{M}^{-1}\hat{T}$). The reason
-for the lower accuracy is that
+time-scale is not as good as the first, but is still acceptable (even good for $\hat{T}\hat{M}^{-1}$).
+\recheck{The difference between the eigenvalues of $\hat P$ and $\hat T\hat{M}^{-1}$
+  is an indication for the non-Markovianity of the milestone process $\hat X_m$. This
+  non-Markovianity present more significant influence in the second non-trivial time-scale.}
+The reason
+for the lower accuracy may also be that
 the corresponding time scale is 26.5~ps (calculated by $-T/\log(\lambda_2)$),
@@
 \[
-\hat{M}^{-1}\hat{T}=\left(\begin{array}{ccc}
-   0.866 &   0.128 &   0.006 \\
-    0.183  &  0.783  &  0.034\\
-    0.018   & 0.067 &   0.915
+\hat{T}\hat{M}^{-1}=\left(\begin{array}{ccc}
+   0.860 &   0.134 &   0.007 \\
+    0.190  &  0.775  &  0.034\\
+    0.020   & 0.065 &   0.915
 \end{array}
 \right),\qquad \hat{P}=\left(\begin{array}{ccc}
-   0.888 &   0.105 &   0.007 \\
+   0.888 &   0.104 &   0.007 \\
     0.149  &  0.822  &  0.029\\
-    0.021   & 0.055 &   0.923
+    0.021   & 0.056 &   0.923
 \end{array}
@@
 from which we see that the longest relaxation timescale results from  the dominant metastability of the left-handed alpha-helix conformations of the peptide. 
-
 It is worth noting that although the discretized process $\tilde X_m$ is irreversible,
@@
     $P$                 &0.907  &0.686 & 0.553       \\
-    $\hat P$     & 0.911  &0.724 & --       \\
-    $\hat{M}^{-1}\hat{T}$    & 0.903  &0.662 & --       \\
+    $\hat P$     & 0.911  &0.723 & --       \\
+    $\hat{T}\hat{M}^{-1}$    & 0.901  &0.649 & --       \\
     \hline\hline
@@
   \includegraphics[width=0.85\textwidth]{fig/t010/cluster.marco.3/fig-coreset-prob.eps}
-  \caption{Comparison of NEMD and MSM long-term kinetics of alanine dipeptide in an oscillatory electrc field.
-The plots show the time-dependent probability $p_j=\hat p(j,t)$ to be assigned to core set $C_j$ (corresponding to the observable $\mathcal A$ given in (\ref{A}) with $\alpha_j=1$ and $\alpha_i=0$ for $i\not= j$).
-Solid lines are from brute force NEMD simulations, while the dashed lines are from our MSM.}
+  \caption{Comparison of NEMD and MSM long-term kinetics of alanine
+    dipeptide in an oscillatory electrc field. The plots show the
+    time-dependent probability $p_j=\hat p(j,t)$ to be assigned to
+    core set $C_j$ (corresponding to the observable $\mathcal A$ given
+    in (\ref{A}) with $\alpha_j=1$ and $\alpha_i=0$ for $i\not=
+    j$). Solid lines are from brute force NEMD simulations, while the
+    dashed lines are from our MSM.}
   \label{fig:num-7}
@@
 In order to show how to compute $\hat{T}$ and $\hat{M}$ directly from trajectories let us start by denoting the first hitting time of set $A$ starting at time $t$ by $h_t(A)$.
-In addition we define $\hat q^\bwd_j (i) = P (X_t = i \vert \hat X_t =
+In addition we define $\hat q^\bwd_j (i) = \prob (X_t = i \vert \hat X_t =
 j)$, and always assume $t = mT$. Then due to the Bayes' Theorem we have
@@
   \hat q^\bwd_j (i) =
-  \frac{P (\hat X_t = j \vert X_t = i) P(X_t = i)}{ P(\hat X_t = j) } =
+  \frac{\prob (\hat X_t = j \vert X_t = i) \prob(X_t = i)}{ \prob(\hat X_t = j) } =
   \frac{q^\bwd_j(i) \mu(i)}{\hat \mu(j)}
@@
 \begin{align*}
-  P& [\,h_t(C_k) < h_t(\cup_{l\neq k} C_l) \,\vert\, \hat X_t = j\,]\\
+  \prob& [\,h_t(C_k) < h_t(\cup_{l\neq k} C_l) \,\vert\, \hat X_t = j\,]\\
   &=
   \sum_{i=1}^n
-  \frac{P [\,h_t(C_k) < h_t(\cup_{l\neq k} C_l) , X_t = i, \hat X_t = j\,]}
-  { P(\hat X_t = j )} \\
+  \frac{\prob [\,h_t(C_k) < h_t(\cup_{l\neq k} C_l) , X_t = i, \hat X_t = j\,]}
+  { \prob(\hat X_t = j )} \\
   &=
   \sum_{i=1}^n
-  {P [\,h_t(C_k) < h_t(\cup_{l\neq k} C_l) \,\vert\, X_t = i, \hat X_t = j\,]}\,
+  {\prob [\,h_t(C_k) < h_t(\cup_{l\neq k} C_l) \,\vert\, X_t = i, \hat X_t = j\,]}\,
   \hat q^\bwd_j(i) \\
@@
   \sum_{i=1}^n
-  {P [\,h_t(C_k) < h_t(\cup_{l\neq k} C_l) \,\vert\, X_t = i\,]}\,
+  {\prob [\,h_t(C_k) < h_t(\cup_{l\neq k} C_l) \,\vert\, X_t = i\,]}\,
   \hat q^\bwd_j(i)  \\
@@
 \begin{align*}
-  P & [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \,\vert\, X_t = i\,]\\
+  \prob & [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \,\vert\, X_t = i\,]\\
   &=
   \sum_{l=1}^n
-  \frac{P [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l), X_{t+T} = l, X_t = i\,]}
-  {X_t = i} \\
+  \frac{\prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l), X_{t+T} = l, X_t = i\,]}
+  {\prob (X_t = i)} \\
   &=
   \sum_{l=1}^n
-  {P [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \vert X_{t+T} = l, X_t = i\,]}
-  {P( X_{t+T} = l \vert X_t = i)}\\
+  {\prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \vert X_{t+T} = l, X_t = i\,]}\,
+  {\prob( X_{t+T} = l \vert X_t = i)}\\
   & =
   \sum_{l=1}^n
-  {P [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \vert X_{t+T} = l\,]}
-  {P( X_{t+T} = l \vert X_t = i)}  = \sum_{l=1}^n
+  {\prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \vert X_{t+T} = l\,]}\,
+  {\prob( X_{t+T} = l \vert X_t = i)}  = \sum_{l=1}^n
   q^\fwd_k(l) P_{il}
@@
 \begin{align*}
-  P [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \,\vert\, \hat X_t = j\,]=
+  \prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \,\vert\, \hat X_t = j\,]=
   \sum_{i=1}^n\sum_{l=1}^n
@@
 
-\section{The equivalence}
+\section{The prove of identity $\hat P = \hat T\hat M^{-1}$}
+\label{sec:app-ptm}
 \begin{align*}
   \hat T_{jk} &=
-  P [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \,\vert\, \hat X_t = j\,]\\
+  \prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \,\vert\, \hat X_t = j\,]\\
   &=
-  \frac{P [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l), \hat X_t = j\,] }{P(\hat X_t = j)}\\
+  \frac{\prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l), \hat X_t = j\,] }{\prob(\hat X_t = j)}\\
   & =
-  \sum_l \frac{P [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l), \hat X_{t+T} = l, \hat X_t = j\,] }{P(\hat X_t = j)}\\
+  \sum_l \frac{\prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l), \hat X_{t+T} = l, \hat X_t = j\,] }{\prob(\hat X_t = j)}\\
   & =
-  \sum_l P [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l)\vert \hat X_{t+T} = l, \hat X_t = j\,] \hat P_{jl}\\  
+  \sum_l \prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l)\vert \hat X_{t+T} = l, \hat X_t = j\,] \hat P_{jl}\\  
   & =
-  \sum_l P [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l)\vert \hat X_{t+T} = l\,] \hat P_{jl}\\
+  \sum_l \prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l)\vert \hat X_{t+T} = l\,] \hat P_{jl}\\
   &= 
@@
 \end{align*}
+This proves the identity $\hat P = \hat T\hat M^{-1}$.
+Notice that in the fifth equation we assumes the Markovianity of the milestone process $\hat X_m$.
 

### 2014-09-15 zm/template.water/run.npt.sh
fix bug in run.npt.sh

@@ -24,6 +24,16 @@ fi
 fi
 fi
 
+
+if echo "$gmx_thermostat" | grep sd &> /dev/null; then
+    gmx_integrator=sd
+    gmx_tcouple=no
+else if echo "$gmx_thermostat" | grep nose-hoover &> /dev/null; then
+    gmx_integrator=md
+    gmx_tcouple=nose-hoover
+fi
+fi
+
 echo "# copy files"
 if test -d npt; then
     mv -f npt npt.`date +%s`
@@ -72,6 +82,9 @@ sed -e "/^tau_t /s/=.*/= $gmx_taut/g"|\
 sed -e "/^tau_p /s/=.*/= $gmx_taup/g"|\
 sed -e "/^epsilon_rf /s/=.*/= $gmx_e_rf/g"|\
 sed -e "/^gen_vel /s/=.*/= no/g"|\
+sed -e "/^couple-moltype /s/=.*/= /g"|\
+sed -e "/^integrator /s/=.*/= $gmx_integrator/g"|\
+sed -e "/^Tcoupl /s/=.*/= $gmx_tcouple/g"|\
 sed -e "/^table-extension /s/=.*/= $gmx_tab_ext/g"> tmp.mdp
 mv -f tmp.mdp grompp.mdp
 cd ..

### 2014-09-15 writedown/period.noneq.msm/paper.tex
make the notations more consistent. backup before major structure change

@@
 \newcommand{\prob}{\textrm{P}}
+\newcommand{\dih}{\textrm{dih}}
 
@@
 introduce a partition of state space $\Omega$ into a finite number of disjoint
-sets $\{ \Omega_1, \cdots, \Omega_n\}$ satisfying $\Omega = \cup_i \Omega_i$,
+sets $\{ \Omega_1, \cdots, \Omega_N\}$ satisfying $\Omega = \cup_i \Omega_i$,
 $\Omega_j\cap \Omega_j = \emptyset,\ \forall i\neq j$.
@@
 is discretized, resulting in a time-inhomogeneous Markov jump process in state
-space $S = \{1, \cdots, n\}$ with time-dependent rate
-matrix $\vect L(t) \in \mathbb R^{n\times n}$ satisfying
+space $S = \{1, \cdots, N\}$ with time-dependent rate
+matrix $\vect L(t) \in \mathbb R^{N\times N}$ satisfying
 \begin{align}\label{eq:disc-4}
-\sum\limits_{j=1}^n L_{ij}(t) & =  0\\ \label{eq:disc-5}
+\sum\limits_{j=1}^N L_{ij}(t) & =  0\\ \label{eq:disc-5}
 L_{ij}(t) & \ge  0, \quad i\not= j\\
@@
 \end{align}
-where $\vect L(t)^T$ denotes the matrix transpose of $\vect L(t)$, $\vect p(t)$ is an $n$-vector denoting the probability distribution on $S$ at time $t$, and
-$p_i(t)$, for example, the probability to be in state $i$ (which corresponds to set $\Omega_i$) at time $t$.
+where $\vect L^T(t)$ denotes the matrix transpose of $\vect L(t)$, $\vect p(t)$ is an $N$-vector denoting the probability distribution on $S$ at time $t$, $p_i(t)$, for example, the probability to be in state $i$ (which corresponds to set $\Omega_i$) at time $t$.
 As usual the properties (\ref{eq:disc-4}) and (\ref{eq:disc-5}) of
@@
 by using the
-associated propagator matrix $\myphi(t)\in\mathbb R^{n\times n}$ that solves
+associated propagator matrix $\myphi(t)\in\mathbb R^{N\times N}$ that solves
 \begin{align}
@@
 $\Phi_{ij}(t) \ge  0$
-and $\sum\limits_{i=1}^n \Phi_{ij}(t)  =  1$,
+and $\sum\limits_{i=1}^N \Phi_{ij}(t)  =  1$,
 that is, $\myphi^T(t)$ is a
 stochastic matrix satisfying $\myphi^T(t)\vect e=\vect e$
-with $\vect e=(1,\ldots,1)^T\in \mathbb R^n$.
+with $\vect e=(1,\ldots,1)^T\in \mathbb R^N$.
 Regarding these considerations, we find
@@
 \[
-\frac{d\ }{dt}\vect Y(t)=\vect L(t+T)^T \vect Y(t)=\vect L(t)^T\vect Y(t),\quad \vect Y(0)=\myphi(T).
+\frac{d\ }{dt}\vect Y(t)=\vect L^T(t+T) \vect Y(t)=\vect L^T(t)\vect Y(t),\quad \vect Y(0)=\myphi(T).
 \]
@@
 % \subsection{Building the Markov State Model from the Floquet transition matrix}
-If the discretization cells $\Omega_i$, $i=1,\ldots,n$ form a fine
+If the discretization cells $\Omega_i$, $i=1,\ldots,N$ form a fine
 partition of the molecular state space, the Markov chain defined via
@@
  is discrete in time but in space it still is a fine-scale description of the transport properties of the
-dynamics with a very large number $n$ of states.  Now we want to coarsen our description much further by
-constructing a Markov State Model (MSM) for $\vect P$ with $k\ll n$
-\emph{macrostates} that should be the metastable states of the system: The resulting $k\times k$ MSM transition matrix $\hat{\vect P}$
+dynamics with a very large number $N$ of states.  Now we want to coarsen our description much further by
+constructing a Markov State Model (MSM) for $\vect P$ with $K\ll N$
+\emph{macrostates} that should be the metastable states of the system: The resulting $K\times K$ MSM transition matrix $\hat{\vect P}$
 then defines the coarse grained long term kinetics that shall
@@
 non-reversible transition matrix $P$. Assume that this approach leads
-to the $k$ core sets $C_1,\ldots, C_k\subset S$ that are appropriate metastable sets. 
-Following \cite{A19-31,schuette2011markov} the process $(X_m)$ associated with $P$ is coarse grained into the so-called milestone process $(\hat{X}_m)$ in the following way: 
+to the $K$ core sets $C_1,\ldots, C_K\subset S$ that are appropriate metastable sets. 
+Following~\cite{A19-31,schuette2011markov} the process $(\tilde X_m)$ associated with $P$ is coarse grained into the so-called milestone process $(\hat{X}_m)$ in the following way: 
 \begin{itemize}
-\item $\hat{X}_m$ just has $k$ states associated with the sets $C_j$, $j=1,\ldots,k$. 
-\item The sequence of random variables $(\hat{X}_m)$ is defined via the sequence $(X_m)$, i.e., trajectories of $(X_m)$ induce trajectories of $(\hat{X}_m)$: We set $\hat{X}_m=j$ if the last core set that the process $(X_m)$ entered prior to or at time $m$ has been the core set $C_j$.
+\item $\hat{X}_m$ just has $K$ states associated with the sets $C_j$, $j=1,\ldots,K$. 
+\item The sequence of random variables $(\hat{X}_m)$ is defined via the sequence $(\tilde X_m)$, i.e., trajectories of $(\tilde X_m)$ induce trajectories of $(\hat{X}_m)$: We set $\hat{X}_m=j$ if the last core set that the process $(\tilde X_m)$ entered prior to or at time $m$ has been the core set $C_j$.
 \end{itemize}
-Now consider infinitely long trajectory of $(X_m)$.
+Now consider infinitely long trajectory of $(\tilde X_m)$.
 Because of ergodicity we know that the states in this trajectory will be distributed due to the quasi-stationary distribution $\mu$.
-Based on such an infinitely long trajectory we can consider the probability $q_j^\bwd(i)$ that conditioned on $X_m=i$ the last core set hit has been $C_j$.
-This function is called the backward committor of $(X_m)$ associated with the set $C_j$ and is associated with the milestone process via
+Based on such an infinitely long trajectory we can consider the probability $q_j^\bwd(i)$ that conditioned on $\tilde X_m=i$ the last core set hit has been $C_j$.
+This function is called the backward committor of $(\tilde X_m)$ associated with the set $C_j$ and is associated with the milestone process via
 \[
@@
 where  the index $\mu$ refers to the fact that $\hat{X}_m$ is distributed due to $\mu$.
+\recheck{COMMENT: Here it is a \emph{conditional} probability,
+  due to the time-homogeneity,
+  it does not matter whether it is defined from quasi-stationary probability
+  or not.}
 From the last equation we get that the stationary distribution of the milestone process is given by
 \[
-\hat{\mu}(j)=\sum_{i\in S} q^\bwd_j(i)\mu(i),
+\hat{\mu}_j=\sum_{i\in S} q^\bwd_j(i)\mu(i),
 \]
-that is, the probability to find $\hat{X}_m=j$ in (infinitely) long trajectories of the milestoning process is $\hat{\mu}(j)$.
-
-Following \cite{discreteTPT} one also has to consider the forward committor $q^\fwd_j(i)$ identical to the probability  that conditioned on $X_m=i$ the next core set to be hit will be $C_j$.
+that is, the probability to find $\hat{X}_m=j$ in (infinitely) long trajectories of the milestoning process is $\hat{\mu}_j$.
+
+Following \cite{discreteTPT} one also has to consider the forward committor $q^\fwd_j(i)$ identical to the probability  that conditioned on $\tilde X_m=i$ the next core set to be hit will be $C_j$.
 The forward and backward committors $q^\fwd_j$ and $q^\bwd_j$  for each core set $C_j$ can be computed from $P$ by solving the linear equations \cite{discreteTPT}
@@
 q^\fwd_j(i) & =  1,\quad i\in C_j\nonumber\\
-q^\fwd_j(i) & =  0,\quad i\in C_l,l\not=j\nonumber
+q^\fwd_j(i) & =  0,\quad i\in C_k,k\not=j\nonumber
 \end{align}
@@
 q^\bwd_j(i) & =  1,\quad i\in C_j\nonumber \\
-q^\bwd_j(i) & =  0,\quad i\in C_l,l\not=j\nonumber
+q^\bwd_j(i) & =  0,\quad i\in C_k,k\not=j\nonumber
 \end{align}
 where $P^b$ denotes the transition matrix of the time-reversed process
-given by $P^b_{ji}=\mu_i P_{ij}/\mu_j$.
+given by $P^b_{ji}=\mu(i) P_{ij}/\mu(j)$.
 
@@
 \begin{equation}\label{hatP_prob}
-\hat{\vect P}_{jl}=\prob_\mu\Big(\hat{X}_{m+1}=l\vert \hat{X}_m=j\Big).
+\hat{\vect P}_{jk}=\prob_\mu\Big(\hat{X}_{m+1}=k\,\vert\, \hat{X}_m=j\Big).
 \end{equation}
@@
     \begin{split}      
-    \hat{\vect P}_{jl}
+    \hat{\vect P}_{jk}
     = &
     \frac{1}{\hat{\mu}(j)}
-    \langle (\vect P^b - \id) q^\bwd_j,q^\fwd_l \rangle_\mu,\qquad j\not= l, \\    %\label{eq:msm-tmatrix-01}
+    \langle (\vect P^b - \id) q^\bwd_j,q^\fwd_k \rangle_\mu,\qquad j\not= k, \\    %\label{eq:msm-tmatrix-01}
     \hat{\vect P}_{jj}
     =&
-    1-\sum_{l\not=j} \hat{\vect P}_{jl}
+    1-\sum_{k\not=j} \hat{\vect P}_{jk}
     \end{split}
@@
 where the inner product is defined by
-$\langle u,v \rangle_\mu=\sum_{i\in S} u_i v_i \mu_i$. 
+$\langle u,v \rangle_\mu=\sum_{i\in S} u(i) v(i) \mu(i)$. 
 In general the milestone process need not be a Markov process.
@@
 With this MSM transition matrix, we can define the MSM kinetics:
-If we start from some initial probability $\hat{p}(l,0)$ of being in state $l$ at time $t=0$ then its evolution $\hat{p}(l,t)$ in time is discrete in multiples of period $T$ and given by
+If we start from some initial probability $\hat{p}_j(0)$ of being in state $j$ at time $t=0$ then its evolution $\hat{p}_j(t)$ in time is discrete in multiples of period $T$ and given by
 \recheck{
 \begin{equation}\label{eq:num-29}
-\hat{p}(l,T)=\sum_j \hat{p}(j,0)\,\,\hat{\vect P}_{jl}.
+\hat{p}_j(T)=\sum_k \hat{p}_k(0)\hat{\vect P}_{kj}.
 \end{equation}}
-In our approach $p(j,mT)$ is a good approximation of $\prob(\hat{X}_m=j)$.
-
-\textbf{Remark 1:} Our definition of the milestoning process in terms of the process $(X_m)$ generated by $P$ guarantees that we can directly compute $\hat{P}$ via (\ref{hatP_prob})  from trajectories of $(X_m)$ without computing the committor functions.
-This is of importance if the spatial discretization underlying $(X_m)$ is fine enough, because then the kinetics of $(X_m)$
+In our approach $\hat p_j(mT)$ is a good approximation of $\prob(\hat{X}_m=j)$.
+
+\textbf{Remark 1:} Our definition of the milestoning process in terms of the process $(\tilde X_m)$ generated by $P$ guarantees that we can directly compute $\hat{P}$ via (\ref{hatP_prob})  from trajectories of $(\tilde X_m)$ without computing the committor functions.
+This is of importance if the spatial discretization underlying $(\tilde X_m)$ is fine enough, because then the kinetics of $(\tilde X_m)$
 approximates the original kinetics of $(x_{mT})$ so that we can directly compute   $\hat{P}$ via (\ref{hatP_prob})  from NEMD trajectories without computing $P$ first (which substantially simplified the MSM building if the core sets are already known).
@@
 \begin{align}\label{eq:msm-ht-1}
-  \hat T_{jk} &= \frac{\langle q_j^\bwd, P q_k^\fwd \rangle_\mu}{\hat \mu(j)},\\\label{eq:msm-hm-1}
-  \hat M_{jk} &= \frac{\langle q_j^\bwd, q_k^\fwd \rangle_\mu}{\hat \mu(j)},
+  \hat T_{jk} &= \frac{\langle q_j^\bwd, P q_k^\fwd \rangle_\mu}{\hat \mu_j},\\\label{eq:msm-hm-1}
+  \hat M_{jk} &= \frac{\langle q_j^\bwd, q_k^\fwd \rangle_\mu}{\hat \mu_j},
 \end{align}
@@
 \begin{align}\label{eq:msm-tmp26}
-  \hat T_{ij} - \hat M_{ij}
-  = \frac{\langle q_j^\bwd, P q_k^\fwd \rangle_\mu}{\hat \mu(j)}
-  - \frac{\langle q_j^\bwd,  q_k^\fwd \rangle_\mu}{\hat \mu(j)}
-  = \frac{\langle (P^b - \id) q_j^\bwd, q_k^\fwd \rangle_\mu}{\hat \mu(j)}
+  \hat T_{jk} - \hat M_{jk}
+  = \frac{\langle q_j^\bwd, P q_k^\fwd \rangle_\mu}{\hat \mu_j}
+  - \frac{\langle q_j^\bwd,  q_k^\fwd \rangle_\mu}{\hat \mu_j}
+  = \frac{\langle (P^b - \id) q_j^\bwd, q_k^\fwd \rangle_\mu}{\hat \mu_j}
   = \hat P_{jk}, \quad j\neq k
@@
 These dominant eigenvalues can be approximated by discretizing the related eigenvalue problem $Pu=\lambda u$ by means of a Galerkin approximation with the finite dimensional ansatz space 
-spanned by the forward committors $q^+_j$, $j=1,\ldots,k$ together  with the finite dimensional test function space spanned by the backward committors $q^-_j$, $j=1,\ldots,k$ (test functions multiplied from the left by the inner product $\langle\cdot,\cdot\rangle_\mu$).
+spanned by the forward committors $q^+_j$, $j=1,\ldots,K$ together  with the finite dimensional test function space spanned by the backward committors $q^-_j$, $j=1,\ldots,K$ (test functions multiplied from the left by the inner product $\langle\cdot,\cdot\rangle_\mu$).
 The thus discretize eigenproblem takes the form  of a generalized eigenproblem
@@
 In the case of  $\hat{T}$ and $\hat{M}$ the MSM modelling error results from Galerkin discretization, while the MSM modelling error of $\hat{P}$ results from ignoring the potential non-Markovianity of $\hat{X}_m$.
-\recheck{As a matter fact, if $\hat X_m$ is Markovian, we prove the identity of the transition matrices: $\hat P = \hat T \hat M^{-1}$ (see~Appendix~\ref{sec:app-ptm} for detail).
+\recheck{As a matter fact, if $\hat X_m$ is Markovian, the identity of the transition matrices holds: $\hat P = \hat T \hat M^{-1}$ (see~Appendix~\ref{sec:app-ptm} for the prove).
 Therefore, in practice, the deviation of the eigenvalues of $\hat P$ from those of $\hat{T}\hat{M}^{-1}$ indicates the non-Markovianity implied in the process $\hat{X}_m$.}
@@
 how many discrete sets we need to be fine enough. Moreover, since the
-total dimension of $x_t$ is $3N$ ($N$ being the number of atoms), it is prohibitive to do a really fine discretization
+total dimension of $x_t$ is $3N_{\textrm{atom}}$ ($N_{\textrm{atom}}$ being the number of atoms), it is prohibitive to do a really fine discretization
 over all DOFs for most systems of practical interest.
@@
 the $\phi$--$\psi$ plane. We denote the number of discretization intervals on each
-dihedral by $K$, then we get $K^2$ discretization sets 
-$\{\Omega_i\},\ i\in S = \{1,\cdots,K^2\}$.
+dihedral by $N_\dih$, then we get $N = N_\dih^2$ discretization sets 
+$\{\Omega_i\},\ i\in S = \{1,\cdots,N_\dih^2\}$.
 
@@
 \[
-\vect P_{ij}=\prob\left(\vect x_T=j\mid \vect x_0=i \right).
+\vect P_{ij}=\prob\left(\vect X_T=j\mid \vect X_0=i \right).
 \]
@@
   L_{ij}(t) \approx \frac{1}{\tau}
-  \,[\, \prob (\vect x_{t+\tau} = i \vert \vect x_{t} = j) - \delta_{ij} \,],
+  \,[\, \prob (\vect X_{t+\tau} = j \mid \vect X_{t} = i) - \delta_{ji} \,],
   \quad i,j\in S
@@
 we investigate the discretization
-quality with respect to  the choice of $K$ and  lag-time $\tau$.
+quality with respect to  the choice of $N_\dih$ and  lag-time $\tau$.
 
@@
   \includegraphics[width=0.7\textwidth]{fig/t010/discrete/fig-cg-prob.eps}  
-  \caption{Time-dependent probability $\mathbb
-    P\big(\phi\in[0,180), \psi\in [0,180)\big)$.  The brute force NEMD simulation is compared with different
+  \caption{Time-dependent probability $\prob\big(\phi\in[0,180), \psi\in [0,180)\big)$.  The brute force NEMD simulation is compared with different
     spatial discretization methods. The red shadow region indicates the
@@
 Therefore, this is an indicator for calibrating the discretization quality.
-We compute $L(t)$ by two discretizations $K=2$ and $K=20$, and two
+We compute $L(t)$ by two discretizations $N_\dih=2$ and $N_\dih=20$, and two
 choices of time intervals $[0, 80]$~ps and $[320, 400]$~ps, and then
@@
 with the (brute force) NEMD result in Fig.~\ref{fig:tmp2} using a lag-time $\tau=0.5$~ps.
-Using $K=2$ the dynamics depends on the time interval used for
+Using $N_\dih=2$ the dynamics depends on the time interval used for
 calculating the generator: using time interval $[0, 80]$~ps the discretized
@@
 reproduces the NEMD result after 300~ps.  This therefore indicates poor 
-approximations to the original dynamics with $K=2$. The reason is that the
-discretization with $K=2$ is too coarse so that the dynamics cannot be fully
+approximations to the original dynamics with $N_\dih=2$. The reason is that the
+discretization with $N_\dih=2$ is too coarse so that the dynamics cannot be fully
 equilibriated within the lag-time $\tau$ in each discretized set,
 therefore, the discretization presents state dependency.  For
-$K=20$, the discretized dynamics does not depend on the time interval of
+$N_\dih=20$, the discretized dynamics does not depend on the time interval of
 calculating the generator, and is consistent with the
-NEMD simulation within the error bar. Therefore, throughout this paper we use $K=20$
+NEMD simulation within the error bar. Therefore, throughout this paper we use $N_\dih=20$
 to discretize  the dihedral angle space of alanine dipeptide.
@@
   \includegraphics[width=0.7\textwidth]{fig/t010/discrete/fig-cg-prob-tau.eps}  
-  \caption{Time-dependent probability $\mathbb
-    P\big(\phi\in[0,180), \psi\in [0,180)\big)$.
-The NEMD simulation is compared with the Master equation using generators discretized with $K=20$ and different lag time $\tau$.
+  \caption{Time-dependent probability $\prob\big(\phi\in[0,180), \psi\in [0,180)\big)$.
+The NEMD simulation is compared with the Master equation using generators discretized with $N_\dih=20$ and different lag time $\tau$.
 The red shadow region indicates the
@@
 different choices of $\tau$ (0.5, 1.0, 2.0 and 5.0~ps)
-(see Fig.~\ref{fig:tmp3}), all based on the identical dihedral angle discretization using $K=20$.
+(see Fig.~\ref{fig:tmp3}), all based on the identical dihedral angle discretization using $N_\dih=20$.
 It is clear that when the lag-time is close to the period (10~ps), the
@@
     of (a) the NEMD  and (b)
-    the Floquet matrix $\vect P=\myphi^T(T)$.
+    the discretized dynamics governed by Floquet transition matrix $\vect P=\myphi^T(T)$.
   }
@@
 % \int_{ph}^{(p+1)h}d\phi\int_{qh}^{(q+1)h}d\psi
-% F_{\textrm{st}}(\phi,\psi), \ 0\leq p,q<K-1$, where $h = 360/K$ being
+% F_{\textrm{st}}(\phi,\psi), \ 0\leq p,q<N_\dih-1$, where $h = 360/N_\dih$ being
 % the size of the bin, $p$ and $q$ here being the bin indexes.
@@
 
-The procedure for identifying good metastable core sets of the irreversible Markov process associated with $\vect P$ is described in detail in Ref.~\cite{sarich2014utilizing}; here we just provide the fundamental idea behind it: If  strong metastable sets $C_j$, $j=1,\ldots,k$ exist they should have one main property: When starting from a state in $C_i$ the expected hitting time of a state in $C_i$ should be much shorter than that of any state in one of the other sets $C_j$, $j\not=i$; in fact, the hitting time distribution should exhibit roughly constant levels in each set $C_j$ and should vary significantly in the transition region $C=\Omega\setminus\cup_j C_j$ between the metastable sets.
+The procedure for identifying good metastable core sets of the irreversible Markov process associated with $\vect P$ is described in detail in Ref.~\cite{sarich2014utilizing}; here we just provide the fundamental idea behind it: If  strong metastable sets $C_j$, $j=1,\ldots,K$ exist they should have one main property: When starting from a state in $C_i$ the expected hitting time of a state in $C_i$ should be much shorter than that of any state in one of the other sets $C_j$, $j\not=i$; in fact, the hitting time distribution should exhibit roughly constant levels in each set $C_j$ and should vary significantly in the transition region $C=\Omega\setminus\cup_j C_j$ between the metastable sets.
 If starting from some randomly chosen initial states, one thus can identify the metastable core sets and the transition region by analyzing the hitting time distributions.
@@
 
-The metastable core sets identified by this procedure based on the estimate of $\vect P$ are illustrated in Fig.~\ref{fig:cluster} and denoted by $C_{\confaa}$ (yellow), $C_\beta$ (red) and $C_{\confc}$ (green).
+The metastable core sets identified by this procedure based on the estimate of $\vect P$ are illustrated in Fig.~\ref{fig:cluster} and denoted by $C_{\confaa}$ (green), $C_\beta$ (yellow) and $C_{\confc}$ (red).
 They correspond to the centers of the wells in the free energy landscapes shown in Fig.~\ref{fig:num-1} and to the
@@
 trajectories of $2\times 10^5$~ps instead. For comparison we compute the first mean hitting
-time of the discretized dynamics via its transition matrix $\vect P$: the first mean hitting time $h_C(i)$ of core set $C$ starting in $\Omega_i$ can  be computed by means of solving the linear problem \cite{A19-31}
+time of the discretized dynamics via its transition matrix $\vect P$: the first mean hitting time $h_{C_j}(i)$ of core set $C_j$ starting in $\Omega_i$ can  be computed by means of solving the linear problem \cite{A19-31}
 \[
-(\vect P-\id) h_C(i) = -1,\qquad \mathrm{if} \, C\cap \Omega_i=\emptyset.
+(\vect P-\id) h_{C_j}(i) = -1,\qquad \mathrm{if} \, C\cap \Omega_i=\emptyset.
 \] 
@@
 $\tilde X_{m}$ indicates a good approximation quality.
-One should note that the NEMD estimate of the first mean hitting time is subject to statistical sampling errors while the first mean hitting times $h_C$ only contain the statistical errors coming from the estimation of $\vect P$.
+One should note that the NEMD estimate of the first mean hitting time is subject to statistical sampling errors while the first mean hitting times $h_{C_j}$ only contain the statistical errors coming from the estimation of $\vect P$.
 Thus, using $P$ helps in calculating the observables
@@
 essentially smaller than NEMD:
-the computation of $h_C$ is an issue of miiliseconds on a laptop, while the
+the computation of $h_{C_j}$ is an issue of miiliseconds on a laptop, while the
 NEMD trajectories took $1.6\times 10^4$ core hours for Intel Xeon E5-4650 CPUs.
@@
 checking if the discretized process $\tilde X_m$ reproduces the NEMD committors.
-The forward committor $q^\fwd_i(\phi,\psi)$ of a coreset $C_i,\
-i\in\{\confaa, \beta, \confc\}$ is defined as the probability of
-visiting coreset $C_i$ next conditioned on starting at conformation
-$(\phi,\psi)$.  The backward committor $q^\bwd_i(\phi,\psi)$ of a
-coreset $C_i,\ i\in\{\confaa, \beta, \confc\}$ is defined as the
-probability of last coming from $C_i$ conditioned on having arrived presently at
-configuration $(\phi,\psi)$.
+The forward committor $q^\fwd_j(i)$ of a coreset $C_j,\
+j\in\{\confaa, \beta, \confc\}$ is defined as the probability of
+visiting coreset $C_j$ next conditioned on starting at conformation
+$(\phi,\psi)\in\Omega_i$.  The backward committor $q^\bwd_j(i)$ of a
+coreset $C_j,\ j\in\{\confaa, \beta, \confc\}$ is defined as the
+probability of last coming from $C_j$ conditioned on having arrived presently at
+configuration $(\phi,\psi)\in\Omega_i$.
 For reversible Markov processes, the
@@
 general not the case for irreversible processes.
-The committors estimated from NEMD simulations ($20000$ trajectories $4000$~ps each) are compared with
+The committors estimated from NEMD simulations ($20000$ trajectories, $4000$~ps each) are compared with
 those computed from $P$ by means of solving the linear equations (\ref{qfwd}) and (\ref{qbwd}).
@@
 time-scale is not as good as the first, but is still acceptable (even good for $\hat{T}\hat{M}^{-1}$).
-\recheck{The difference between the eigenvalues of $\hat P$ and $\hat T\hat{M}^{-1}$
-  is an indication for the non-Markovianity of the milestone process $\hat X_m$. This
-  non-Markovianity present more significant influence in the second non-trivial time-scale.}
 The reason
@@
 which is NOT significantly longer than the temporal resolution given by the period $T=10$~ps of the external driving force.
+\recheck{The difference between the eigenvalues of $\hat P$ and $\hat T\hat{M}^{-1}$
+  is an indication for the non-Markovianity of the milestone process $\hat X_m$. This
+  non-Markovianity present more significant influence in the second non-trivial time-scale.}
 Numerically the two MSM transition matrices are:
@@
 \begin{align}\label{A}
-  A(i) = \sum_{l=1}^k \alpha_l q^\bwd_l(i).
+  A(i) = \sum_{l=1}^K \alpha_l q^\bwd_l(i).
 \end{align}
@@
   \mathcal A(t) &=
-  \sum_{i\in S} \sum_{l=1}^k \alpha_l q^\bwd_l(i)  p(i,t)=\sum_{i\in S} \sum_{l=1}^k \alpha_l \prob (\hat X_t = l \vert X_t = i) \prob (X_t = i) \\
+  \sum_{i\in S} \sum_{j=1}^K \alpha_j q^\bwd_j(i)  p(i,t)=\sum_{i\in S} \sum_{j=1}^K \alpha_j \prob (\hat X_t = j \vert X_t = i) \prob (X_t = i) \\
   & =
-  \sum_{i\in S} \sum_{l=1}^k \alpha_l \prob (\hat X_t = l ,X_t = i)  =
-  \sum_{l=1}^k \alpha_l \prob (\hat X_t = l) 
+  \sum_{i\in S} \sum_{j=1}^K \alpha_j \prob (\hat X_t = j ,X_t = i)  =
+  \sum_{j=1}^K \alpha_j \prob (\hat X_t = j) 
  =
-   \sum_{l=1}^k \alpha_l \,\hat p (l, t), \label{eq:num-28}
-\end{align}
-where the time-dependent probability $\hat{p}(i,t)$ of being assigned to MSM macrostate $i$ at time $t$ can be computed  by means of the MSM via simple matrix multiplications using (\ref{eq:num-29}).
-
-In Fig.~\ref{fig:num-7} we compare the numerical calculation of $\hat p (l, mT), \ m\in\mathbb N$ from NEMD and MSM calculations.
-In the NEMD case, the backward committor and the probability density $\hat p (l, mT) = \sum_{i\in S}  q^\bwd_l(i)  p(i,mT) $
+   \sum_{j=1}^K \alpha_j \,\hat p_j (t), \label{eq:num-28}
+\end{align}
+where the time-dependent probability $\hat{p}_j(t)$ of being assigned to MSM macrostate $j$ at time $t$ can be computed  by means of the MSM via simple matrix multiplications using (\ref{eq:num-29}).
+
+In Fig.~\ref{fig:num-7} we compare the numerical calculation of $\hat p_j (mT), \ m\in\mathbb N$ from NEMD and MSM calculations.
+In the NEMD case, the backward committor and the probability density $\hat p_j (mT) = \sum_{i\in S}  q^\bwd_j(i)  p(i,mT) $
 are estimated directly from the
-NEMD trajectories. For the MSM, the projection of the initial probability is applied, $\hat p (l, 0) = \sum_{i\in S}  q^\bwd_l(i)  p(i,0) $, then
+NEMD trajectories. For the MSM, the projection of the initial probability is applied, $\hat p_j (0) = \sum_{i\in S}  q^\bwd_j(i)  p(i,0) $, then
 the time-dependent probability at $mT$ is generated by Eq.~\eqref{eq:num-29}, i.e., by simple matrix multiplication. The agreement is almost perfect.
@@
   \frac{\prob (\hat X_t = j \vert X_t = i) \prob(X_t = i)}{ \prob(\hat X_t = j) } =
-  \frac{q^\bwd_j(i) \mu(i)}{\hat \mu(j)}
+  \frac{q^\bwd_j(i) \mu(i)}{\hat \mu_j}
 \end{align}
 Then
-\begin{align*}
-  \prob& [\,h_t(C_k) < h_t(\cup_{l\neq k} C_l) \,\vert\, \hat X_t = j\,]\\
+\begin{align}\nonumber
+  \prob& [\,h_t(C_k) < h_t(\cup_{l\neq k} C_l) \,\vert\, \hat X_t = j\,]\\\nonumber
   &=
-  \sum_{i=1}^n
+  \sum_{i=1}^N
   \frac{\prob [\,h_t(C_k) < h_t(\cup_{l\neq k} C_l) , X_t = i, \hat X_t = j\,]}
-  { \prob(\hat X_t = j )} \\
+  { \prob(\hat X_t = j )} \\\nonumber
   &=
-  \sum_{i=1}^n
+  \sum_{i=1}^N
   {\prob [\,h_t(C_k) < h_t(\cup_{l\neq k} C_l) \,\vert\, X_t = i, \hat X_t = j\,]}\,
-  \hat q^\bwd_j(i) \\
+  \hat q^\bwd_j(i) \\\nonumber
   &=
-  \sum_{i=1}^n
+  \sum_{i=1}^N
   {\prob [\,h_t(C_k) < h_t(\cup_{l\neq k} C_l) \,\vert\, X_t = i\,]}\,
-  \hat q^\bwd_j(i)  \\
+  \hat q^\bwd_j(i)  \\\label{eq:appb-m}
   &=
-  \sum_{i=1}^n
-  q^\fwd_k(i) \frac{q^\bwd_j(i) \mu(i)}{\hat \mu(i)} =\frac{\langle q_j^\bwd, q_k^\fwd\rangle_\mu}{\hat \mu(j)}={\hat M}_{jk}
-\end{align*}
+  \sum_{i=1}^N
+  q^\fwd_k(i) \frac{q^\bwd_j(i) \mu(i)}{\hat \mu_j} =\frac{\langle q_j^\bwd, q_k^\fwd\rangle_\mu}{\hat \mu_j}={\hat M}_{jk}
+\end{align}
 where the third equation holds because of the Markovianity of the process $X_t$, and the fourth equation is due to the definition of the forward committor.
@@
   &=
-  \sum_{l=1}^n
+  \sum_{l=1}^N
   \frac{\prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l), X_{t+T} = l, X_t = i\,]}
@@
   &=
-  \sum_{l=1}^n
+  \sum_{l=1}^N
   {\prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \vert X_{t+T} = l, X_t = i\,]}\,
@@
   & =
-  \sum_{l=1}^n
+  \sum_{l=1}^N
   {\prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \vert X_{t+T} = l\,]}\,
-  {\prob( X_{t+T} = l \vert X_t = i)}  = \sum_{l=1}^n
+  {\prob( X_{t+T} = l \vert X_t = i)}  = \sum_{l=1}^N
   q^\fwd_k(l) P_{il}
@@
 Therefore, following the same procedure as before we have
-\begin{align*}
+\begin{align}\label{eq:appb-t}
   \prob [\,h_{t+T}(C_k) < h_{t+T}(\cup_{l\neq k} C_l) \,\vert\, \hat X_t = j\,]=
-  \sum_{i=1}^n\sum_{l=1}^n
+  \sum_{i=1}^N\sum_{l=1}^N
   q^\fwd_k(l) P_{il}
-  \frac{q^\bwd_j(i) \mu(i)}{\hat \mu(i)} = \frac{\langle q_j^\bwd, P q_k^\fwd\rangle_\mu}{\hat \mu(j)}  = {\hat T}_{jk}
-\end{align*}
+  \frac{q^\bwd_j(i) \mu(i)}{\hat \mu_j} = \frac{\langle q_j^\bwd, P q_k^\fwd\rangle_\mu}{\hat \mu_j}  = {\hat T}_{jk}
+\end{align}
 Thus, when starting with the milestone process in state $j$ at some time $t$ we have to determine the fraction of all trajectories of length at least $T$ that hit core set $C_k$ first of all core sets to estimate $\hat{T}_{jk}$.
@@
 \label{sec:app-ptm}
+In this section we prove the identity  $\hat P = \hat T\hat M^{-1}$. Starting from the
+result Eq.~\eqref{eq:appb-t},
 \begin{align*}
@@
   &= 
-  \sum_l  \hat P_{jl}\hat M_{lk}
+  \sum_l  \hat P_{jl}\hat M_{lk}.
 \end{align*}
@@
 Notice that in the fifth equation we assumes the Markovianity of the milestone process $\hat X_m$.
+In the sixth equation we use the result Eq.~\eqref{eq:appb-m}, and the time-homogeneity of the milestone process.
 

### 2014-09-16 writedown/period.noneq.msm/paper.tex
backup

@@
   \label{eq:disc-master}
-  \frac{d\vect p(t)}{dt} = \vect L^T(t)\cdot \vect p(t)
-\end{align}
-where $\vect L^T(t)$ denotes the matrix transpose of $\vect L(t)$, $\vect p(t)$ is an $N$-vector denoting the probability distribution on $S$ at time $t$, $p_i(t)$, for example, the probability to be in state $i$ (which corresponds to set $\Omega_i$) at time $t$.
+  \frac{d\vect p(t)}{dt} = \vect L^{\top}(t)\cdot \vect p(t)
+\end{align}
+where $\vect L^{\top}(t)$ denotes the matrix transpose of $\vect L(t)$, $\vect p(t)$ is an $N$-vector denoting the probability distribution on $S$ at time $t$, $p_i(t)$, for example, the probability to be in state $i$ (which corresponds to set $\Omega_i$) at time $t$.
 As usual the properties (\ref{eq:disc-4}) and (\ref{eq:disc-5}) of
@@
   \label{eq:disc-master-phi}
-  \frac{d}{dt}\myphi(t) = \vect L^T(t)\myphi(t), \quad \myphi(0) = \id .
+  \frac{d}{dt}\myphi(t) = \vect L^{\top}(t)\myphi(t), \quad \myphi(0) = \id .
 \end{align}
@@
 and $\sum\limits_{i=1}^N \Phi_{ij}(t)  =  1$,
-that is, $\myphi^T(t)$ is a
-stochastic matrix satisfying $\myphi^T(t)\vect e=\vect e$
-with $\vect e=(1,\ldots,1)^T\in \mathbb R^N$.
+that is, $\myphi^{\top}(t)$ is a
+stochastic matrix satisfying $\myphi^{\top}(t)\vect e=\vect e$
+with $\vect e=(1,\ldots,1)^{\top}\in \mathbb R^N$.
 Regarding these considerations, we find
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Temporal discretization: Floquet theory}
+\subsection{Temporal discretization: Floquet theorem}
 \label{sec:floquet}
@@
 \[
-\frac{d\ }{dt}\vect Y(t)=\vect L^T(t+T) \vect Y(t)=\vect L^T(t)\vect Y(t),\quad \vect Y(0)=\myphi(T).
+\frac{d\ }{dt}\vect Y(t)=\vect L^{\top}(t+T) \vect Y(t)=\vect L^{\top}(t)\vect Y(t),\quad \vect Y(0)=\myphi(T).
 \]
@@
 if we can compute $\myphi(t)$ for $t\in (0,T)$.
+\recheck{This is known as the Floquet theorem~\cite{floquet1883equations}.}
 In particular we get the long-term evolution of the propagator:
@@
 where $\myphi^m(T)$ denotes the $m$th power of the matrix $\myphi(T)$.
-Since $\myphi(T)$ is a stochastic matrix, its eigenvalues are contained in the unit circle in
-the complex plane, i.e., each eigenvalue $\lambda$ (potentially coomplex-valued)
-satisfies $|\lambda|\le 1$. Furthermore $\lambda=1$ is an
-eigenvalue with left eigenvector $\vect e=(1,\ldots,1)^T$ and a right eigenvector $\mymu$
-satisfying
-$\myphi(T)\mymu=\mymu$.
-From now on, we assume $\myphi(T)$ to be irreducible and aperiodic such that the Perron Frobenius theorem the eigenvalue $\lambda=1$ is  non-negative componentwise, and unique (up to normalization $\sum_j\mu_j=1$).
-In this case $\mymu$ is the stationary measure in the sense that
-\begin{align}
-\label{eq:floq-14}  
-\myphi(mT) \mymu = \mymu,\quad m=0,1,2,\ldots,
-\end{align}
-and (more precisely) the asymptotic evolution of an initial probability distribution $\vect p(t=0)$ by the process satisfies
-\begin{align}
-\label{eq:floq-15}  
-\myphi(mT)\vect p(0)\to \mymu,\quad m\to\infty,
-\end{align}
-so that $\mymu$ can be seen as the quasi-stationary distribution of our non-stationary process.
-
+
+\recheck{
 Using the Floquet theorem, the time-inhomogeneous Markov jump process $X_t$
-is simplified into a \emph{time-homogeneous} (not necessarily
+is therefore discretized into a \emph{time-homogeneous} (not necessarily
 reversible) Markov jump process $\tilde X_{m} = X_{mT}, \ m\in\mathbb
-N$.
-Therefore, we prefer to consider the discrete-time process $\tilde X_{m}$ instead of the time-continuous process $X_t$
+N$, which is generated by transition matrix
+\begin{equation}\label{P}
+\vect P=\myphi^{\top}(T).
+\end{equation}
+We prefer to consider the discrete-time process $\tilde X_{m}$ instead of the time-continuous process $X_t$
 because the powerful theories and
 computational tools for time-homogeneous Markov processes can be directly applied.
-Many of these tools require the transition matrix $\myphi(T)$ to satisfy the detailed balance condition.
-The computations in the Appendix show that $\myphi$ will in general \emph{not} satisfy this condition; in fact  the deviation form reversibility can be estimated from the work of the periodic driving does to the system.
-
+It worth noting that many of these tools require the transition matrix $P$ to satisfy the detailed balance condition.
+The computations in the Appendix~\ref{sec:app-revs} show that $P$ will in general \emph{not} satisfy this condition; in fact  the deviation form reversibility can be estimated from the work of the periodic driving does to the system.
 There is no doubt that information within one period is lost by using this temporal
@@
 statistically uncertainty in calculating the observables of interest.
+}
+
+Since \recheck{$P$} \recheck{(\underline{COMMENT}: using $P$ instead of $\myphi(T)$.)} is a stochastic matrix, its eigenvalues are contained in the unit circle in
+the complex plane, i.e., each eigenvalue $\lambda$ (potentially coomplex-valued)
+satisfies $|\lambda|\le 1$. Furthermore $\lambda=1$ is an
+eigenvalue with \recheck{right} eigenvector $\vect e=(1,\ldots,1)^{\top}$ and a \recheck{left} eigenvector $\mymu$
+satisfying
+\recheck{$\mymu^{\top}P=\mymu^{\top}$.}
+From now on, we assume $P$ to be irreducible and aperiodic such that the Perron Frobenius theorem the eigenvalue $\lambda=1$ is  non-negative componentwise, and unique (up to normalization $\sum_j\mu_j=1$).
+\recheck{In this case $\mymu$ is the stationary measure in the sense that
+$
+ \mymu^{\top} P^m = \mymu^{\top},\ m\in\mathbb N
+$,
+% \begin{align}
+% \label{eq:floq-14}  
+% \end{align}
+and (more precisely) the asymptotic evolution of an initial probability distribution $\vect p(t=0)$ by the process satisfies
+$
+\vect p^{\top}(0)\,P^m \to \mymu^{\top},\ m\to\infty,
+$
+% \begin{align}
+% \label{eq:floq-15}  
+% \end{align}
+so that $\mymu$ can be seen as the quasi-stationary distribution of our non-stationary process.}
 
@@
 partition of the molecular state space, the Markov chain defined via
-the transition matrix 
-\begin{equation}\label{P}
-\vect P=\myphi^T(T)
-\end{equation}
- is discrete in time but in space it still is a fine-scale description of the transport properties of the
-dynamics with a very large number $N$ of states.  Now we want to coarsen our description much further by
+the transition matrix $P$
+ is discrete in time, but in space it still is a fine-scale description of the transport properties of the
+dynamics with a very large number $N$ of states.  Now we want to coarse our description much further by
 constructing a Markov State Model (MSM) for $\vect P$ with $K\ll N$
@@
 correctly describe the slow  dynamics, and 
-in each set the fast dynamics relaxes on some timescale significantly shorter than the metastable timescales.
+in each set the fast dynamics relaxes on some timescales significantly shorter than the metastable timescales.
 Then if the MSM dynamics reproduces the slow timescales and the corresponding transitions
@@
 This function is called the backward committor of $(\tilde X_m)$ associated with the set $C_j$ and is associated with the milestone process via
-\[
-q^\bwd_j(i)=\prob_\mu(\hat{X}_m=j|X_m=i),
-\]
+\begin{align}
+\label{eq:msm-bwd-committor}  
+q^\bwd_j(i)=\prob_\mu(\hat{X}_m=j \mid X_m=i),
+\end{align}
 where  the index $\mu$ refers to the fact that $\hat{X}_m$ is distributed due to $\mu$.
-\recheck{COMMENT: Here it is a \emph{conditional} probability,
+\recheck{\underline{QUESTION}: Here it is a \emph{conditional} probability,
   due to the time-homogeneity,
@@
 From the last equation we get that the stationary distribution of the milestone process is given by
-\[
+\begin{align}  
 \hat{\mu}_j=\sum_{i\in S} q^\bwd_j(i)\mu(i),
-\]
+\end{align}
 that is, the probability to find $\hat{X}_m=j$ in (infinitely) long trajectories of the milestoning process is $\hat{\mu}_j$.
@@
 The whole system was driven by a periodic electric field
-$E(t) = E_0\sin(2\pi t/T)$ and $D(x) = (1,0,0)^T$
+$E(t) = E_0\sin(2\pi t/T)$ and $D(x) = (1,0,0)^{\top}$
 with intensity of the field being $E_0 = 1.0$~V/nm and period being
@@
 
-Based on a given spatial discretization we can aggregate the transition matrix $\vect P=\myphi^T(T)$ just by counting the transition behavior of MD trajectories 
+Based on a given spatial discretization we can aggregate the transition matrix $\vect P=\myphi^{\top}(T)$ just by counting the transition behavior of MD trajectories 
 \[
@@
 \end{align}
-and $\tau$ is an appropriate small enough lag-time.
+and $\tau$ is an appropriate small enough lag-time \recheck{(small error in
+  the finite difference approximation).}
+\recheck{
+  % COMMENT: shouldn't be discussions on the lag-time and the Markovianity?
+  In the meanwhile,
+  since the dimensionality is reduced by using only a few collective
+  variables, the lag-time should be chosen large enough so that
+  the original dynamics $x_t$ is properly relaxed at
+  the unresolved degrees of freedoms in timescales shorter than the lag-time
+  (possible if the collective variables capture the slow dynamics).
+  Then the implied Markovianity assumption in the master equation is
+  reasonable, and the discretization from $\ml(t)$ to $L(t)$ is state-independent.}
 In the following 
@@
 quality with respect to  the choice of $N_\dih$ and  lag-time $\tau$.
+
+\recheck{\underline{QUESTION}: Is the above discussion correct?
+  Does the ``Markovianity'' always need a time discretization with the
+  lag-time?
+}
 
@@
 t_2]$.
-Whenever the discretization is fine enough the discretized dynamics approximates the original
+\recheck{As discussed above, }whenever  the discretized dynamics approximates the original
 dynamics well, and the time-periodic generator $L(t)$ should not depend on the choice of the interval $[t_1,t_2]$ in the estimation procedure (\ref{eqn:tmp4}), provided that the initial state of the system
@@
     of (a) the NEMD  and (b)
-    the discretized dynamics governed by Floquet transition matrix $\vect P=\myphi^T(T)$.
+    the discretized dynamics governed by Floquet transition matrix $\vect P=\myphi^{\top}(T)$.
   }
@@
 we will now consider the time-homogeneous process $\tilde X_{m}$ generated by
-the Floquet transition matrix $P = \Phi^T(T)$, and investigate whether it
+the Floquet transition matrix $P = \Phi^{\top}(T)$, and investigate whether it
 reproduces the properties of the original  non-equilibrium process $x_t$.
@@
 the quasi-stationary probability distribution $\rho_{\textrm{st}}$. 
-$\myphi(T)$ is computed as described above, and then $\mymu$ is computed as its leading eigenvector. In order to make it comparable to the free energy in the equilibrium case, we take
+$P$ is computed as described above, and then $\mymu$ is computed as its leading eigenvector. In order to make it comparable to the free energy in the equilibrium case, we take
 the logarithm of the distributions, i.e.~$F_{\textrm{st}}(\phi,\psi)=
@@
 for NEMD and $F_{\textrm{st}}(\phi,\psi)=
--k_B\mathcal T\log \mu(\phi,\psi)$ for $\Phi(T)$, where $k_B$ is the
+-k_B\mathcal T\log \mu(\phi,\psi)$ for $P$, where $k_B$ is the
 Boltzmann constant and $\mathcal T$ is the temperature of the system.
@@
 the  NEMD simulation and 
-$\Phi(T)$ is observed.
+$P$ is observed.
 
@@
 \[
-(\vect P-\id) h_{C_j}(i) = -1,\qquad \mathrm{if} \, C\cap \Omega_i=\emptyset.
+(\vect P-\id) h_{C_j}(i) = -1,\qquad \mathrm{if} \, C_j\cap \Omega_i=\emptyset.
 \] 
@@
 Alternatively, the MSM  transition matrix $\hat P$ is calculated directly from the NEMD trajectories using Eq.~\eqref{hatP_prob} (very good agreement with the one computed from the committors).
-The leading eigenvalues of $P=\myphi^T(T)$ are compared with those of $\hat P$ and $\hat{T}\hat{M}^{-1}$ in
+The leading eigenvalues of $P=\myphi^{\top}(T)$ are compared with those of $\hat P$ and $\hat{T}\hat{M}^{-1}$ in
 Tab.~\ref{tab:tmp1}.
@@
 of the longest non-trivial implied time-scale. The accuracy of the second non-trivial
-time-scale is not as good as the first, but is still acceptable (even good for $\hat{T}\hat{M}^{-1}$).
+time-scale is not as good as the first, but is still acceptable.
 The reason
@@
   non-Markovianity present more significant influence in the second non-trivial time-scale.}
+\recheck{\underline{COMMENT}: any theoretial explanation behind?}
 Numerically the two MSM transition matrices are:
@@
     dipeptide in an oscillatory electrc field. The plots show the
-    time-dependent probability $p_j=\hat p(j,t)$ to be assigned to
+    time-dependent probability $\hat p_j(t)$ to be assigned to
     core set $C_j$ (corresponding to the observable $\mathcal A$ given
-    in (\ref{A}) with $\alpha_j=1$ and $\alpha_i=0$ for $i\not=
+    in (\ref{A}) with $\alpha_j=1$ and $\alpha_k=0$ for $k\not=
     j$). Solid lines are from brute force NEMD simulations, while the
@@
 \end{align}
-where $p_i(t)=\prob(X_t=i)$ denotes the probability to be in set $\Omega_i$ at time $t$ as governed by the Master equation, and the observable $\mathcal A$ is spanned by the backward
+where $p(i,t) = p_i(t)=\prob(X_t=i)$ denotes the probability to be in set $\Omega_i$ at time $t$ as governed by the Master equation, and the observable $\mathcal A$ is spanned by the backward
 committors, i.e.,
 \begin{align}\label{A}
-  A(i) = \sum_{l=1}^K \alpha_l q^\bwd_l(i).
+  A(i) = \sum_{j=1}^K \alpha_j q^\bwd_j(i).
 \end{align}
@@
 In Fig.~\ref{fig:num-7} we compare the numerical calculation of $\hat p_j (mT), \ m\in\mathbb N$ from NEMD and MSM calculations.
-In the NEMD case, the backward committor and the probability density $\hat p_j (mT) = \sum_{i\in S}  q^\bwd_j(i)  p(i,mT) $
+\recheck{In the NEMD case, the identity  $\hat p_j (mT) = \sum_{i\in S}  q^\bwd_j(i)  p(i,mT) $ is used, and
+the backward committor and the probability density on the R.H.S.
 are estimated directly from the
-NEMD trajectories. For the MSM, the projection of the initial probability is applied, $\hat p_j (0) = \sum_{i\in S}  q^\bwd_j(i)  p(i,0) $, then
+NEMD trajectories.} For the MSM, the projection of the initial probability is applied, $\hat p_j (0) = \sum_{i\in S}  q^\bwd_j(i)  p(i,0) $, then
 the time-dependent probability at $mT$ is generated by Eq.~\eqref{eq:num-29}, i.e., by simple matrix multiplication. The agreement is almost perfect.
@@
 \section{Reversibility of the original dynamics}
-\label{sec:revs}
+\label{sec:app-revs}
 

### 2014-09-18 writedown/period.noneq.msm/paper.tex
CS's revise

@@
 if we can compute $\myphi(t)$ for $t\in (0,T)$.
-\recheck{This is known as the Floquet theorem~\cite{floquet1883equations}.}
+This is known as the Floquet theorem~\cite{floquet1883equations}.
 In particular we get the long-term evolution of the propagator:
@@
 \end{align}
-and for the probability at integral period we have
+where $\myphi^m(T)$ denotes the $m$th power of $\myphi(T)$. Thus, for the probability at integral periods we have
 \begin{align}
   \label{eq:floq-dynamics}
-  p(mT) =  \myphi(mT)\, p(0) = \myphi^m(T)\, p(0),
-\end{align}
-where $\myphi^m(T)$ denotes the $m$th power of the matrix $\myphi(T)$.
-
-\recheck{
+  p(mT) =  \myphi(mT)\, p(0) = \myphi^m(T)\, p(0).
+\end{align}
+
 Using the Floquet theorem, the time-inhomogeneous Markov jump process $X_t$
@@
 statistically uncertainty in calculating the observables of interest.
-}
-
-Since \recheck{$P$} \recheck{(\underline{COMMENT}: using $P$ instead of $\myphi(T)$.)} is a stochastic matrix, its eigenvalues are contained in the unit circle in
+
+Since $P$ is a stochastic matrix, its eigenvalues are contained in the unit circle in
 the complex plane, i.e., each eigenvalue $\lambda$ (potentially coomplex-valued)
 satisfies $|\lambda|\le 1$. Furthermore $\lambda=1$ is an
-eigenvalue with \recheck{right} eigenvector $\vect e=(1,\ldots,1)^{\top}$ and a \recheck{left} eigenvector $\mymu$
+eigenvalue with right eigenvector $\vect e=(1,\ldots,1)^{\top}$ and a left eigenvector $\mymu$
 satisfying
-\recheck{$\mymu^{\top}P=\mymu^{\top}$.}
+$\mymu^{\top}P=\mymu^{\top}$.
 From now on, we assume $P$ to be irreducible and aperiodic such that the Perron Frobenius theorem the eigenvalue $\lambda=1$ is  non-negative componentwise, and unique (up to normalization $\sum_j\mu_j=1$).
-\recheck{In this case $\mymu$ is the stationary measure in the sense that
+In this case $\mymu$ is the stationary measure in the sense that
 $
@@
 % \end{align}
-so that $\mymu$ can be seen as the quasi-stationary distribution of our non-stationary process.}
+so that $\mymu$ can be seen as the quasi-stationary distribution of our non-stationary process.
 
@@
 \end{itemize}
-Now consider infinitely long trajectory of $(\tilde X_m)$.
+Now consider an arbitrary infinitely long trajectory of $(\tilde X_m)$.
 Because of ergodicity we know that the states in this trajectory will be distributed due to the quasi-stationary distribution $\mu$.
@@
 where  the index $\mu$ refers to the fact that $\hat{X}_m$ is distributed due to $\mu$.
-\recheck{\underline{QUESTION}: Here it is a \emph{conditional} probability,
-  due to the time-homogeneity,
-  it does not matter whether it is defined from quasi-stationary probability
-  or not.}
+%\recheck{\underline{QUESTION}: Here it is a \emph{conditional} probability,
+%  due to the time-homogeneity,
+%  it does not matter whether it is defined from quasi-stationary probability
+%  or not.}
 From the last equation we get that the stationary distribution of the milestone process is given by
@@
 
-\recheck{
 We define the one-step transition matrix $\hat{\vect P}$ for the milestone process by
@@
 Ref.~\cite{djurdjevac2010markov}, Thm.~3.1, 
-$\hat{\vect P}$ is associated with the milestone process $(\hat{X}_m)$ in terms of committors by}
+$\hat{\vect P}$ can be computed by matrix multiplication using the committors:
   \begin{align}
@@
 If we start from some initial probability $\hat{p}_j(0)$ of being in state $j$ at time $t=0$ then its evolution $\hat{p}_j(t)$ in time is discrete in multiples of period $T$ and given by
-\recheck{
 \begin{equation}\label{eq:num-29}
 \hat{p}_j(T)=\sum_k \hat{p}_k(0)\hat{\vect P}_{kj}.
-\end{equation}}
-In our approach $\hat p_j(mT)$ is a good approximation of $\prob(\hat{X}_m=j)$.
+\end{equation}
+In our approach $\hat p_j(mT)$ is a good approximation of $\prob(\hat{X}_m=j)$ (for appropriately chosen core sets).
 
@@
   \label{eq:msm-gen-ev}
-\hat{T}\hat{u}=\hat{\lambda}\hat{M}\hat{u}.  
+\hat{T}\hat{u}=\hat{\lambda}\hat{M}\hat{u},\quad\mathrm{or, equivalently}\quad \hat{M}^{-1}\hat{T}\hat{u}=\hat{\lambda}\hat{u},.  
 \end{align}
@@
 
-\textbf{Remark 3:}
-The pair $\hat{T}$ and $\hat{M}$, or the matrix $\hat{T}\hat{M}^{-1}$ (if all of its entries are positive such that it is a stochastic matrix), thus can also be taken as MSM transition matrices.
-In the case of  $\hat{T}$ and $\hat{M}$ the MSM modelling error results from Galerkin discretization, while the MSM modelling error of $\hat{P}$ results from ignoring the potential non-Markovianity of $\hat{X}_m$.
-\recheck{As a matter fact, if $\hat X_m$ is Markovian, the identity of the transition matrices holds: $\hat P = \hat T \hat M^{-1}$ (see~Appendix~\ref{sec:app-ptm} for the prove).
-Therefore, in practice, the deviation of the eigenvalues of $\hat P$ from those of $\hat{T}\hat{M}^{-1}$ indicates the non-Markovianity implied in the process $\hat{X}_m$.}
-The lesson learnt in the reversible case are that $\hat{P}$ is better suited to approximate the molecular kinetics on large timescales while $\hat{T}$ and $\hat{M}$ should be used for approximating eigenvalues and long relaxation timescales.
+If all of its entries are positive such that it is a stochastic matrix, $\hat{M}^{-1}\hat{T}$ thus can also be taken as MSM transition matrices.
+In the case of $\hat{M}^{-1}\hat{T}$ the MSM modelling error results from Galerkin discretization, while the MSM modelling error of $\hat{P}$ results from ignoring the potential non-Markovianity of $\hat{X}_m$.
+
+\textbf{Remark 3:} As a matter of fact, if $\hat X_m$ were Markovian, the following identity would hold: $\hat P = \hat T \hat M^{-1}$ (see~Appendix~\ref{sec:app-ptm} for the proof).
+In this case, we would have $\hat{M}^{-1}\hat{T}=\hat{M}^{-1}\hat{P}\hat{M}$ and the eigenvalues of $\hat{P}$ and $\hat{M}^{-1}\hat{T}$ would be identical.
+Therefore, in practice, the deviation of the eigenvalues of $\hat P$ from those of $\hat{M}^{-1}\hat{T}$ indicates the deviation from Markovianity regarding the process $\hat{X}_m$.
+%The lesson learnt in the reversible case are that $\hat{P}$ is better suited to approximate the molecular kinetics on large timescales while $\hat{M}^{-1}\hat{T}$ should be used for approximating eigenvalues and long relaxation timescales.
 
@@
 The equilibrium configurations were prepared by an equilibrium MD simulation
-of $10^6$~ps long, along which the snapshots were saved every 50~ps.
+of length $10^6$~ps, along which snapshots were saved every 50~ps.
 % In the
@@
 % with coupling time-scale $\tau_T = 0.5$~ps.
-The branching
+The branching NEMD
 trajectories were each 4000~ps long, and the system reached
@@
 Based on a given spatial discretization we can aggregate the transition matrix $\vect P=\myphi^{\top}(T)$ just by counting the transition behavior of MD trajectories 
-\[
+\begin{equation}\label{Pdirect}
 \vect P_{ij}=\prob\left(\vect X_T=j\mid \vect X_0=i \right).
-\]
+\end{equation}
 However, $\vect P$ allows to approximate the original dynamics on multiples $mT$ of the period only. In order to have a time-continuos description we need the generator $L(t)$ of the Master equation. 
@@
 \end{align}
-and $\tau$ is an appropriate small enough lag-time \recheck{(small error in
-  the finite difference approximation).}
-\recheck{
-  % COMMENT: shouldn't be discussions on the lag-time and the Markovianity?
-  In the meanwhile,
-  since the dimensionality is reduced by using only a few collective
+and $\tau$ is an appropriate small enough lag-time.
+  Since the dimensionality is reduced by using only a few collective
   variables, the lag-time should be chosen large enough so that
-  the original dynamics $x_t$ is properly relaxed at
-  the unresolved degrees of freedoms in timescales shorter than the lag-time
-  (possible if the collective variables capture the slow dynamics).
-  Then the implied Markovianity assumption in the master equation is
-  reasonable, and the discretization from $\ml(t)$ to $L(t)$ is state-independent.}
+  the original dynamics $x_t$ is properly relaxed with regard to
+  the unresolved degrees of freedoms on timescales shorter than the lag-time
+  (assuming  that the collective variables capture the slow dynamics).
   In the following 
@@
 
-\recheck{\underline{QUESTION}: Is the above discussion correct?
-  Does the ``Markovianity'' always need a time discretization with the
-  lag-time?
-}
+%\recheck{\underline{QUESTION}: Is the above discussion correct?
+%  Does the ``Markovianity'' always need a time discretization with the
+%  lag-time?
+%}
+%
 
@@
   \includegraphics[width=0.7\textwidth]{fig/t010/discrete/fig-cg-prob.eps}  
-  \caption{Time-dependent probability $\prob\big(\phi\in[0,180), \psi\in [0,180)\big)$.  The brute force NEMD simulation is compared with different
+  \caption{Time-dependent probability $\prob\big(\phi_t\in[0,180), \psi_t\in [0,180)\big)$.  The brute force NEMD simulation is compared with different
     spatial discretization methods. The red shadow region indicates the
@@
 t_2]$.
-\recheck{As discussed above, }whenever  the discretized dynamics approximates the original
-dynamics well, and the time-periodic generator $L(t)$ should not depend on the choice of the interval $[t_1,t_2]$ in the estimation procedure (\ref{eqn:tmp4}), provided that the initial state of the system
+As discussed above, whenever  the discretized dynamics approximates the original
+dynamics well, the time-periodic generator $L(t)$ should not depend on the choice of the interval $[t_1,t_2]$ in the estimation procedure (\ref{eqn:tmp4}), provided that the initial state of the system
 is not very far from the stationary state at long-time limit.
@@
 \end{align}
-On each NEMD branching trajectory the initial 320~ps is discarded and
+On each NEMD branching trajectory the initial 320~ps are discarded and
 the rest of the trajectory in time interval $[320,4000]$~ps is used to estimate
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3/fig-cluster.eps}
+  \includegraphics[width=0.6\textwidth]{fig/t010/cluster.marco.3/fig-cluster.eps}
   \caption{The coreset identification. Different colors indicate different core sets: $C_{\confaa}$ (green), $C_\beta$ (yellow) and $C_{\confc}$ (red).
@@
 The resulting first mean hitting times are presented in Fig.~\ref{fig:num-6}.  The
-good consistency between the NEMD and the discretized Markov process
+good consistency between the NEMD estimate and the discretized Markov process
 $\tilde X_{m}$ indicates a good approximation quality.
@@
 Committors are very important statistical properties of Markov processes \cite{PrinzHeldSmithNoe_Committorprep,PNAS09}, and play
-an important role in MSM building \cite{A19-31,A19-29,djurdjevac2010markov} (see below), therefore, it is worth
+an important role in MSM building \cite{A19-31,A19-29,djurdjevac2010markov} (see below). Therefore, it is worth
 checking if the discretized process $\tilde X_m$ reproduces the NEMD committors.
@@
 For reversible Markov processes, the
-forward and backward committors are identical, however, it is in
+forward and backward committors are identical, however, this is in
 general not the case for irreversible processes.
@@
 where the quasi-stationary probability distribution $\mu$, the three core sets, and the forward and backward committors are
-estimated as described above, and the MSM transition matrices $\hat P$, $\hat{T}$, and $\hat{M}$ is then evaluated using Eq.~\eqref{eq:msm-tmatrix-00}, \eqref{eq:msm-ht-1} and \eqref{eq:msm-hm-1}, correspondingly.
+estimated as described above, and the MSM transition matrices $\hat P$, $\hat{M}$, and $\hat{T}$ are then evaluated using Eq.~\eqref{eq:msm-tmatrix-00}, \eqref{eq:msm-ht-1} and \eqref{eq:msm-hm-1}, correspondingly.
 Alternatively, the MSM  transition matrix $\hat P$ is calculated directly from the NEMD trajectories using Eq.~\eqref{hatP_prob} (very good agreement with the one computed from the committors).
-The leading eigenvalues of $P=\myphi^{\top}(T)$ are compared with those of $\hat P$ and $\hat{T}\hat{M}^{-1}$ in
+The leading eigenvalues of $P=\myphi^{\top}(T)$ are compared with those of $\hat P$ and $\hat{M}^{-1}\hat{T}$ in
 Tab.~\ref{tab:tmp1}.
@@
 which is NOT significantly longer than the temporal resolution given by the period $T=10$~ps of the external driving force.
-\recheck{The difference between the eigenvalues of $\hat P$ and $\hat T\hat{M}^{-1}$
-  is an indication for the non-Markovianity of the milestone process $\hat X_m$. This
-  non-Markovianity present more significant influence in the second non-trivial time-scale.}
-\recheck{\underline{COMMENT}: any theoretial explanation behind?}
+The difference between the eigenvalues of $\hat P$ and $\hat{M}^{-1}\hat T$
+  can be taken as an indication for the non-Markovianity of the milestone process $\hat X_m$. This
+  non-Markovianity seems to have stronger influence on the second non-trivial time-scale in comparison to the first one; this may be caused by shorter decorrelation timescales due to weaker metastability of the core sets involved.
 Numerically the two MSM transition matrices are:
 \[
-\hat{T}\hat{M}^{-1}=\left(\begin{array}{ccc}
+\hat{M}^{-1}\hat{T}=\left(\begin{array}{ccc}
    0.860 &   0.134 &   0.007 \\
@@
 \]
-from which we see that the longest relaxation timescale results from  the dominant metastability of the left-handed alpha-helix conformations of the peptide. 
+from which we see that  the left-handed alpha-helix conformations of the peptide exhibits the strongest metastability.
+
 It is worth noting that although the discretized process $\tilde X_m$ is irreversible,
@@
     $\hat P$     & 0.911  &0.723 & --       \\
-    $\hat{T}\hat{M}^{-1}$    & 0.901  &0.649 & --       \\
+    $\hat{M}^{-1}\hat{T}$    & 0.901  &0.649 & --       \\
     \hline\hline
@@
 In Fig.~\ref{fig:num-7} we compare the numerical calculation of $\hat p_j (mT), \ m\in\mathbb N$ from NEMD and MSM calculations.
-\recheck{In the NEMD case, the identity  $\hat p_j (mT) = \sum_{i\in S}  q^\bwd_j(i)  p(i,mT) $ is used, and
+In the NEMD case, the identity  $\hat p_j (mT) = \sum_{i\in S}  q^\bwd_j(i)  p(i,mT) $ is used, and
 the backward committor and the probability density on the R.H.S.
 are estimated directly from the
-NEMD trajectories.} For the MSM, the projection of the initial probability is applied, $\hat p_j (0) = \sum_{i\in S}  q^\bwd_j(i)  p(i,0) $, then
+NEMD trajectories. For the MSM, the projection of the initial probability is applied, $\hat p_j (0) = \sum_{i\in S}  q^\bwd_j(i)  p(i,0) $, then
 the time-dependent probability at $mT$ is generated by Eq.~\eqref{eq:num-29}, i.e., by simple matrix multiplication. The agreement is almost perfect.
@@
 % by Eq.~\eqref{eq:num-28} letting $\alpha_l = \delta_{l'l}$.
+
+\recheck{Han: Here we have $p_j(t)$, $p(j,t)$ and $\hat p_j (0)$. That's a little confusing since I do not see a clear distinction between the former two. What can we do? What do you want to express?}
 

### 2014-09-18 alanine.nanma/template/tools/msm/app/calculate.floquet.cpp
add floquet matrix directly from NEMD

@@ -1,0 +1,173 @@
+#include <algorithm>
+#include <fstream>
+#include <iomanip>
+#include <iostream>
+#include <iterator>
+#include <list>
+#include <map>
+#include <set>
+#include <sstream>
+#include <string>
+#include <queue>
+#include <cmath>
+#include <boost/program_options.hpp>
+#include <vector>
+#include "StringSplit.h"
+#include "BlockAverage.h"
+
+#define MaxLineLength 2048
+
+namespace po = boost::program_options;
+using namespace std;
+
+int conv_multi_single (const vector<int > & indexes,
+		       const int & nBin)
+{
+  int result = 0;
+  for (unsigned ii = 0; ii < indexes.size(); ++ii){
+    result = result * nBin + indexes[ii];
+  }
+  return result;
+}
+
+
+int main(int argc, char * argv[])
+{
+  std::string ofile, ifile, isfile, idfile, opfile;
+  double dt, period, begin, end;
+  unsigned ndataBlock;
+  double maxRelError;
+  
+  po::options_description desc ("Allow options");
+  desc.add_options()
+      ("help,h", "print this message")
+      ("input,f",  po::value<std::string > (&ifile)->default_value ("traj.disc"), "the file of file names")
+      ("input-dir,d", po::value<std::string > (&idfile)->default_value ("dir.name"), "the output of metastable propulation")
+      ("input-largest-set,s", po::value<std::string > (&isfile)->default_value ("largestSet"), "the input file of largest set.")
+      ("n-data-block,n", po::value<unsigned > (&ndataBlock)->default_value (1), "num data in each block.")
+      ("max-rel-error,m", po::value<double > (&maxRelError)->default_value (2e-0), "maximum relative error.")
+      ("dt,t", po::value<double > (&dt)->default_value (1.0), "time step of disc traj.")
+      ("period,p", po::value<double > (&period)->default_value (40.0), "the period, in ps. should be multiples of dt")
+      ("begin,b", po::value<double > (&begin)->default_value (0), "the begin of using data.")
+      ("end,e", po::value<double > (&end)->default_value (0), "the end of using data.")
[…]

### 2014-09-18 alanine.nanma/template/tools/msm/app/calculate.floquet.cpp
rm useless variable

@@ -36,7 +36,6 @@ int main(int argc, char * argv[])
   std::string ofile, ifile, isfile, idfile, opfile;
   double dt, period, begin, end;
   unsigned ndataBlock;
-  double maxRelError;
   
   po::options_description desc ("Allow options");
   desc.add_options()
@@ -45,7 +44,6 @@ int main(int argc, char * argv[])
       ("input-dir,d", po::value<std::string > (&idfile)->default_value ("dir.name"), "the output of metastable propulation")
       ("input-largest-set,s", po::value<std::string > (&isfile)->default_value ("largestSet"), "the input file of largest set.")
       ("n-data-block,n", po::value<unsigned > (&ndataBlock)->default_value (1), "num data in each block.")
-      ("max-rel-error,m", po::value<double > (&maxRelError)->default_value (2e-0), "maximum relative error.")
       ("dt,t", po::value<double > (&dt)->default_value (1.0), "time step of disc traj.")
       ("period,p", po::value<double > (&period)->default_value (40.0), "the period, in ps. should be multiples of dt")
       ("begin,b", po::value<double > (&begin)->default_value (0), "the begin of using data.")

### 2014-09-18 alanine.nanma/template/tools/msm/app/calculate.floquet.cpp
fix bug: line sum should be 1

@@ -48,7 +48,7 @@ int main(int argc, char * argv[])
       ("period,p", po::value<double > (&period)->default_value (40.0), "the period, in ps. should be multiples of dt")
       ("begin,b", po::value<double > (&begin)->default_value (0), "the begin of using data.")
       ("end,e", po::value<double > (&end)->default_value (0), "the end of using data.")
-      ("output,o", po::value<string > (&ofile)->default_value ("floquet.p.out"), "the output transition matrix.");
+      ("output,o", po::value<string > (&ofile)->default_value ("direct.floquet.out"), "the output transition matrix.");
   
 
   po::variables_map vm;
@@ -151,6 +151,21 @@ int main(int argc, char * argv[])
     cpTmatrix[ii].resize(nstate);
     for (unsigned jj = 0; jj < nstate; ++jj){
       cpTmatrix[ii][jj] = tmatrix[ii][jj].getAvg();
+    }
+  }
+
+  for (unsigned kk = 0; kk < nstate; ++kk){
+    double sum = 0;
+    for (unsigned jj = 0; jj < nstate; ++jj){
+      sum += cpTmatrix[kk][jj];
+    }
+    if (fabs(sum - 1) > 1e-12){
+      if (fabs(sum) < 1e-12){
+	cpTmatrix[kk][kk] = 1.;
+      }
+      else {
+	cerr << "sum is " << sum << " problematic" << endl;
+      }
     }
   }
 

### 2014-09-18 alanine.nanma/template/tools/msm/app/calculate.floquet.cpp
print reading

@@ -108,7 +108,9 @@ int main(int argc, char * argv[])
       std::cerr << "cannot open file " << filename << std::endl;
       return 1;
     }
-    // cout << "reading file " << filename << endl;
+    if (countFile % 100 == 0){
+      cout << "reading file " << filename << endl;
+    }
     countFile ++;
     vector<unsigned > disc_traj;
     unsigned count_read = 0;

### 2014-09-22 writedown/period.noneq.msm/paper.tex
backup changes

@@
 \end{align}
-where $\vect L^{\top}(t)$ denotes the matrix transpose of $\vect L(t)$, $\vect p(t)$ is an $N$-vector denoting the probability distribution on $S$ at time $t$, $p_i(t)$, for example, the probability to be in state $i$ (which corresponds to set $\Omega_i$) at time $t$.
+where $\vect L^{\top}(t)$ denotes the matrix transpose of $\vect L(t)$, $\vect p(t)$ is an $N$-vector denoting the probability distribution on $S$ at time $t$, $p(i,t)$, for example, the probability to be in state $i$ (which corresponds to set $\Omega_i$) at time $t$.
 As usual the properties (\ref{eq:disc-4}) and (\ref{eq:disc-5}) of
 $\vect L(t)$ guarantee that the total probability mass is conserved,
-i.e., if $p_i(0)\ge 0$ componentwise, then $p_i(t)\ge 0$ and $\sum_i
-p_i(t) = \sum_ip_i(0)$.
+i.e., if $p(i,0)\ge 0$ componentwise, then $p(i,t)\ge 0$ and $\sum_i
+p(i,t) = \sum_ip(i,0)$.
 % The solution of the master equation need no be
@@
 of $\vect L(t)$ are almost perfect approximations of the transport properties
-of $\ml(t)$, in particular the approximation $p_i(t)\approx \prob(x_t\in \Omega_i)$ is almost perfect.
+of $\ml(t)$, in particular the approximation $p(i,t)\approx \prob(x_t\in \Omega_i)$ is almost perfect.
 
@@
 $\mymu^{\top}P=\mymu^{\top}$.
-From now on, we assume $P$ to be irreducible and aperiodic such that the Perron Frobenius theorem the eigenvalue $\lambda=1$ is  non-negative componentwise, and unique (up to normalization $\sum_j\mu_j=1$).
+From now on, we assume $P$ to be irreducible and aperiodic such that the Perron Frobenius theorem the eigenvalue $\lambda=1$ is  non-negative componentwise, and unique (up to normalization $\sum_i\mu(i)=1$).
 In this case $\mymu$ is the stationary measure in the sense that
@@
 of the original dynamics~\eqref{eq:disc-1},
-the former is considered to be a good approximation of the later.
+the former is considered to be a good approximation of the latter.
 
@@
 Tab.~\ref{tab:tmp1}.
-Without surprising, the two approaches for MSM building are consitent.
+Without surprising, the two approaches for MSM building are consitent, \recheck{and the latter is slightly better}.
 The MSM is able to accurately reproduce
@@
 \right),\qquad \hat{P}=\left(\begin{array}{ccc}
-   0.888 &   0.104 &   0.007 \\
-    0.149  &  0.822  &  0.029\\
-    0.021   & 0.056 &   0.923
+   0.882 &   0.110 &   0.008 \\
+    0.158  &  0.815  &  0.028\\
+    0.023   & 0.055 &   0.922
 \end{array}
@@
       &  $\lambda_2$ & $\lambda_3$ & $\lambda_4$ \\\hline
-    $P$                 &0.907  &0.686 & 0.553       \\
-    $\hat P$     & 0.911  &0.723 & --       \\
+    $P$                 &0.905  &0.668 & 0.551       \\
+    $\hat P$     & 0.909  &0.710 & --       \\
     $\hat{M}^{-1}\hat{T}$    & 0.901  &0.649 & --       \\
@@
 \end{align}
-where $p(i,t) = p_i(t)=\prob(X_t=i)$ denotes the probability to be in set $\Omega_i$ at time $t$ as governed by the Master equation, and the observable $\mathcal A$ is spanned by the backward
+where $p(i,t)=\prob(X_t=i)$ is the probability to be in set $\Omega_i$ at time $t$ as governed by the Master equation, and the observable $\mathcal A$ is spanned by the backward
 committors, i.e.,
@@
 
-\recheck{Han: Here we have $p_j(t)$, $p(j,t)$ and $\hat p_j (0)$. That's a little confusing since I do not see a clear distinction between the former two. What can we do? What do you want to express?}
+% \recheck{Han: Here we have $p_j(t)$, $p(j,t)$ and $\hat p_j (0)$.
+That's a little confusing since I do not see a clear distinction between the former two.
+What can we do?
+What do you want to express?}
 

### 2014-09-22 writedown/period.noneq.msm/paper.tex
right data of matrix
revise the conclusion accordingly

@@
     = &
-    \frac{1}{\hat{\mu}(j)}
+    \frac{1}{\hat{\mu}_j}
     \langle (\vect P^b - \id) q^\bwd_j,q^\fwd_k \rangle_\mu,\qquad j\not= k, \\    %\label{eq:msm-tmatrix-01}
@@
 Tab.~\ref{tab:tmp1}.
-Without surprising, the two approaches for MSM building are consitent, \recheck{and the latter is slightly better}.
+Without surprising, the two approaches for MSM building are consitent.
 The MSM is able to accurately reproduce
@@
 \hat{M}^{-1}\hat{T}=\left(\begin{array}{ccc}
-   0.860 &   0.134 &   0.007 \\
-    0.190  &  0.775  &  0.034\\
-    0.020   & 0.065 &   0.915
+   0.860 &   0.133 &   0.008 \\
+    0.192  &  0.775  &  0.033\\
+    0.019   & 0.066 &   0.915
 \end{array}
@@
 valid and be able to capture the long-time behavior of the original
-non-equilibrium dynamics. We have provided and verified two equivalent
-pathways of building MSM, as is shown by the two branches in
-Fig.~\ref{fig:flowchart}.
-
-The the key steps of the first pathway are
-summarized as following:
-\begin{enumerate}
-\item By a fine discretization of the molecular configuration space,
-  the original NEMD dynamics is discretized into a (in principle)
-  time-continuous \recheck{Markov} jump process with a time-dependent generator $L(t)$.
-  If the discretization is good enough, then the discretized
-  dynamics is expected to reproduce the original dynamics.
-  In principle most of the discretiztion methods for the
-  equilibirum case can be generalized to  non-equilibrium without
-  substantial difficulty, however,
-  we have not discussed which discretiztion method is the best choice,
-  since it is out of the scope of the present work.
-  \recheck{It should be noticed that
-    we assume the jump process is Markovian, althogh in
-    general it is not true. However, if (1) the system present time-scale
-    seperation; (2) the spatial discretiztion is fine enough; (3)
-    we approximately consider a discretizted time
-    (can be very fine, and in computer the molecular configurations are
-    saved at discretizted time steps)
-    by lag-time $\tau$, so that within the lag-time
-    the fast dynamics of the system is fully relaxed; then
-    the Markovianity is a good assumption for the discretizted dynamics.
-  }
-  We show that, by numerical example, a uniform $20\times20$ discretiztion 
-  over the dihedral angles $\phi$--$\psi$ space is a good choice for
-  alanine dipeptide.
-  In the tests, the state independency in computing $L(t)$
-  is used as an indicator for
-  the quality of the discretiztion.
-\item By the Floquet thoerem, the time-inhomogeneous process generated
-  by $L(t)$ is temporally discretized in to a time-homogeneous,
-  but not necessarily reversible, jump process that has a transition
-  matrix denoted by $P$. This temporal discretiztion only  considers
-  the state of the system at integral periods, therefore all information
-  within the period is not preserved. This is, however, not a serious
-  problem whenever the long-time hehaviors of the system is of interst, and
-  their corresponding time-scales are significantly longer than one period.
-  The advantage of this discretiztion
-  is also obvious: All well-developed theories and computational tools
-  for time-homogeneous Markov processes
-  can be directly appled. In the
-  alanine dipeptide system, we compare
-  the the quasi-stationary probability,
-  first mean hitting time, and the forward and backward committors
-  of the discretized dynamics with those computed directly from the
-  NEMD simulation. An almost perfect consistency 
-  indicates a good approximation quality of the discretized dynamics.
-\item From the disretized dynamics, building the MSM is straightforward
-  by using Eq.~\eqref{eq:msm-tmatrix-00} and a set of coresets.
-  Numerical results shows that a 3-state MSM can reporduce the leading
-  non-trivial eigenvalue with very good accuracy, while the second
-  non-trivial eigenvalue with acceptable accuracy. The lower accuracy
-  regarding the second non-trivial eigenvalue may be due to the fact that
-  the second slowest time-scale is not significantly longer than the
-  period. Using this three state MSM, we can also reproduce, with
-  almost perfect accuracy, the 
-  time-evolution of the metastable state
-  pobabilities from equilibirum (no external driven)
-  to the non-equilibrium quasi-stationary state.
-\end{enumerate}
-
-The right branch in Fig.~\ref{fig:flowchart} presents a
+non-equilibrium dynamics.
+
+We firstly provide effective methods for discretizing the original NEMD trajectories
+both temporally and spacially, and the end-product is a time-homogeneous
+(not necessarily reversible) Markov jump process.
+There are two equivalent approaches discussed in the paper:
+one can either do a two-steps discretization,
+i.e.~firstly spacial and then temperoal,
+or a single step  involes both discretizations simulteneously.
+They are exhibited by the left-most and middle branches in Fig.~\ref{fig:flowchart}.
+
+By a fine discretization of the molecular configuration space, the
+original NEMD dynamics is discretized into a (in principle)
+continuous and time-inhomogeneous {Markov} jump process.
+In principle most of the discretiztion methods for the equilibirum
+case can be generalized to non-equilibrium without substantial
+difficulty, however, we have not compare different discretiztion methods
+regarding the accuracy, since it is out of the scope of the present work.
+We show that, by numerical example, a uniform $20\times20$
+discretiztion over the dihedral angles $\phi$--$\psi$ space is a good
+choice for alanine dipeptide.  In the tests, the state independency in
+computing the generator is used as an indicator for the quality of the
+discretiztion.
+
+The Floquet thoerem discretize a periodic process by taking only
+integral periods, so that
+the time-inhomogeneous process
+is discretized in to a time-homogeneous, but not
+necessarily reversible process.
+The advantage of this discretiztion is  obvious: All
+well-developed theories and computational tools for time-homogeneous
+Markov processes can be directly appled. In the alanine dipeptide
+system, we compare the the quasi-stationary probability, first mean
+hitting time, and the forward and backward committors of the
+discretized dynamics with those computed directly from the NEMD
+simulation. An almost perfect consistency indicates a good
+approximation quality of the discretized dynamics.
+
+Although the end-product of the two-step and one-step discretiztions are equivalent,
+it is clear that the one-step discretiztion does not preserve any information
+within one period, because only the states
+at integral periods are considered. This is not a serious problem
+whenever the long-time hehaviors of the system is of interst, and
+their corresponding time-scales are significantly longer than one
+period. However, if the time-scale of any interested behavior
+is comparable to, or even shorter than the period, the two-step
+discretiztion is prefered, so that one can recover the dynamics within
+one period no matter when it is necessary. If the longest non-trivial
+time-scale is comparable to one period, thenn the Floquet theorem
+is not preferable, and the non-equilibrium dynamics may be well
+described by the quasi-equilibrium approximation.
+
+Building the MSM from the time-homogeneous disretized dynamics is straightforward by
+using Eq.~\eqref{eq:msm-tmatrix-00} and a set of coresets that are
+derived from the discretized dynamics.  Numerical
+results shows that a 3-state MSM can reporduce the leading non-trivial
+eigenvalue with very good accuracy, while the second non-trivial
+eigenvalue with acceptable accuracy. The lower accuracy regarding the
+second non-trivial eigenvalue may be due to the fact that the second
+slowest time-scale is not significantly longer than the period. Using
+this three state MSM, we can also reproduce, with almost perfect
+accuracy, the time-evolution of the metastable state pobabilities from
+equilibirum (no external driven) to the non-equilibrium
+quasi-stationary state.
+
+The right-most branch in Fig.~\ref{fig:flowchart} presents an
 equivalent, and seemingly
-much simpler alternative to the left branch, provided the
-coresets are known. Neverthless, in pactice, identifying
-the coresets is not a trivial task, especially for the
+much simpler alternative to the middle branch, i.e. building
+the MSM directly from the NEMD trajectories.
+In practice, however, this method may not be applicable, because
+it requires known coresets, and the coresets identification 
+is usually not a trivial task, especially for the
 non-equilibrium molecular systems.
-Therefore, a good discretization is  usually a must for computing the coreset.
-For example, in the present work, we computed the coresets by
-finding the roughly constant levels of the hitting time distribution.
-This method only works for the discretized dynamics $P$, and its continuous
-counterpart is still an open question.
+This task is substantially
+simplified when an accurate time-homogeneous discretiztion 
+to the original time-inhomogeneous NEMD is accessible.
+In the present work, we computed the coresets by
+finding the roughly constant levels of the hitting time distribution 
+of the discretized dynamics.
+It should be noticed that the continuous
+counterpart of the current coresets identification method is still an open question.
+% This method only works for the discretized dynamics. and its
+% Therefore, a good discretization is  usually a must for computing the coreset.
 

### 2014-10-16 writedown/auto.correlations/h.bond.notes/main.tex
add notes on h-bond auto-correlation

\documentclass[unsortedaddress,a4paper,onecolumn]{revtex4}
% \documentclass[aps, pre, preprint,unsortedaddress,a4paper,twocolumn]{revtex4}
% \documentclass[acs, jctcce, a4paper,preprint,unsortedaddress,onecolumn]{revtex4-1}
% \documentclass[aps,pre,twocolumn,unsortedaddress]{revtex4-1}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}

\usepackage[fleqn]{amsmath}
\usepackage{amssymb}
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{tabularx}
\usepackage{algorithm}
\usepackage{algorithmic}

\makeatletter
\makeatother

\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}
\newcommand{\bluec}[1]{{\color{red} #1}}
\newcommand{\greenc}[1]{{\color{green} #1}}
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\dd}[1]{\textsf{#1}}
\newcommand{\fwd}[0]{\textrm{fw}}
\newcommand{\bwd}[0]{\textrm{bw}}
\newcommand{\period}[0]{T_{\textrm{P}}}
\newcommand{\ml}[0]{\mathcal {L}}
\newcommand{\mo}[0]{\mathcal {O}}
\newcommand{\mbp}[0]{\mathbb {P}}
\newcommand{\mc}[0]{\mathcal {C}}
\newcommand{\dt}[0]{\Delta t}

\newcommand{\confaa}[0]{{\alpha_{\textrm{R}}}}
\newcommand{\confab}[0]{{\alpha_{\textrm{R}}'}}
\newcommand{\confba}[0]{{\textrm{C}7_{\textrm{eq}}}}
\newcommand{\confbb}[0]{{\textrm{C}5}}
\newcommand{\confc}[0]{{\alpha_{\textrm{L}}}}

\newcommand{\oxy}[0]{{\textrm{O}}}
\newcommand{\hyd}[0]{{\textrm{H}}}

\begin{document}

\title{Notes on the hydrogen-bond auto-correlation}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{Zuse Institut Berlin, Germany}

\begin{abstract}
  In this note I describe the implmentational details of the hydrogen-bond auto-correlations.
\end{abstract}

\maketitle

\section{Definitions}
Here I use the definition of hydrogen-bond population from
Ref.~\cite{luzar1996effect, luzar1996hydrogen}.  The population $h(t)$
is defined to be 1 if a certain pair of molecules forms hydrogen-bond,
otherwise is defined to be 0. Therefore, the averaged total number of
hydrogen-bond in an equilibrium system is $\frac12 N(N-1)\langle
h\rangle$, where $\langle\cdot\rangle$ denotes the ensemble average.
The auto-correlation
\begin{align}
  c(t) = \frac{\langle h(0) h(t)\rangle}{\langle h\rangle}
\end{align}
is studied. The physical meaning is that given a hydrogen-bond formed
at time $0$, the probability of observing a hydrogen-bond between the
same pair at time $t$.
The rate of relaxation to equilibrium is of paricular interest:
\begin{align}\label{eqn:k-def}
  k(t) &= -\frac{dc}{dt}\\\label{eqn:k-exp}
  &= -\frac{\langle \dot h(0) [1 - h(t)] \rangle}{\langle h\rangle}
\end{align}
where $\dot h(0) = (dh/dt)\vert_{t=0}$. The Eq.~\eqref{eqn:k-exp} holds because
\begin{align} \label{eqn:tmp3}
  \langle h(0) \dot h(t) \rangle &= - \langle \dot h(0) h(t)\rangle \\\label{eqn:tmp4}
  \langle \dot h(0) \rangle &= 0
\end{align}
Eq.~\eqref{eqn:tmp4} is obvious because the system is in equilibrium. Eq.~\eqref{eqn:tmp3} holds because
\begin{align}
  0 = \frac{d [ h(\tau) h(\tau+t) ] }{d\tau} =  \langle h(\tau) \dot h(\tau+t)\rangle  + \langle \dot h(\tau) h(\tau+t)\rangle.
\end{align}
Letting $\tau \rightarrow 0$ on both sides yields Eq.~\eqref{eqn:tmp3}.

\section{Implementation details regarding the rate of relaxation}

The rate of relaxation to equilibrium $k(t)$ can be calculated by
definition~\eqref{eqn:k-def}, or calculated from Eq.~\eqref{eqn:k-exp}
with an explicit estimation of the function $\dot h$. We want to discuss the second way.

Two water molecules are hydrogen-bonded if (1) the O--O distance is less than a cut-off $r_c$, \emph{and} (2)
the O--H...O angle is less than a cut-off $\theta_c$. To mathematically define the function $h$, we introduce
the Heaviside function:
\begin{equation}\label{eqn:heavi}
  H(x) =
  \left\{
    \begin{alignedat}{3}
      &1 &\quad& x\geq0, \\
      &0 &     & x < 0.
    \end{alignedat}
  \right.
\end{equation}
And important property of the Heaviside function is that
\begin{align}
  \delta (x) = \frac{dH(x)}{dx}
\end{align}
If we denote the DOFs of two water molecules by $\vect x_1$ and $\vect x_2$, then the hydrogen-bond population function $h$ is expressed by
\begin{align}
  h(\vect x_1, \vect x_2) = H [r_c - R(\vect x_1, \vect x_2)] \cdot H [\theta_c - \theta(\vect x_1, \vect x_2)]
\end{align}
where function $R(\vect x_1, \vect x_2)$ computes the O--O distance
between the molecules, while $\theta(\vect x_1, \vect x_2)$ computes
the O--H...O angle. In practice, it is not easy to calcualte the
angle, but the cosine angle is relatively easy. Therefore we use the
definition 
\begin{align}
  h(\vect x_1, \vect x_2) = H [r_c - R(\vect x_1, \vect x_2)] \cdot H[\cos(\theta(\vect x_1, \vect x_2)) - \cos \theta_c]
\end{align}
If we notice the fact that the DOFs of the molecules are functions of
time, i.e.~$\vect x_1 = \vect x_1(t)$, and $\vect x_2 = \vect x_2(t)$, then
taking the derivative w.r.t.~time on both sides of the equation, we have
\begin{align}
  \frac{d h}{dt}
  =
  \frac{dH [r_c - R(\vect x_1, \vect x_2)]}{dt} \cdot H[\cos(\theta(\vect x_1, \vect x_2)) - \cos \theta_c] +
  H [r_c - R(\vect x_1, \vect x_2)] \cdot \frac{dH[\cos(\theta(\vect x_1, \vect x_2)) - \cos \theta_c]}{dt}
\end{align}
We compute the two derivatives in the equation:
\begin{align}
  \frac{dH [r_c - R(\vect x_1, \vect x_2)]}{dt}
  &=
  -\delta[r_c - R(\vect x_1, \vect x_2)]
  \cdot  \frac{dR(\vect x_1, \vect x_2)}{dt} \\
  \frac{dH[\cos(\theta(\vect x_1, \vect x_2)) - \cos \theta_c]}{dt}
  &=
  \delta[\cos(\theta(\vect x_1, \vect x_2)) - \cos \theta_c]
  \cdot \frac{d \cos(\theta(\vect x_1, \vect x_2))}{dt}
\end{align}
In practice, the delta function can be approximated by
\begin{align}
  \delta(x) =
  \left\{
    \begin{alignedat}{3}
      &\frac 1{2\Delta L}, &\qquad& -\frac{\Delta L}{2} \leq x < \frac{\Delta L}{2}, \\
      & 0, &     & \textrm{otherwise},
    \end{alignedat}
  \right.
\end{align}
with a small enough $\Delta L$.
Now the problem is to compute $dR(\vect x_1, \vect x_2)/dt$ and $d
\cos(\theta(\vect x_1, \vect x_2))/dt$. To compute $dR(\vect x_1,
\vect x_2)/dt$, we fristly derive the derivative w.r.t.~the distance
between any two positions $\vert \vect r_1 - \vect r_2\vert$:
\begin{align} 
  \frac{d\vert \vect r_1(t) - \vect r_2(t)\vert}{dt}
  &=
  \frac{( \vect r_1(t) - \vect r_2(t) )}{  \vert \vect r_1(t) - \vect r_2(t)\vert} \cdot
  \frac{ d( \vect x_1(t) - \vect x_2(t) )}{dt}  
  =
  \frac{( \vect r_1(t) - \vect r_2(t) ) \cdot (\vect v_1(t) - \vect v_2(t))}{  \vert \vect r_1(t) - \vect r_2(t)\vert} 
  =
  \frac{\vect r_{12}\cdot \vect v_{12}}{r_{12}}.
\end{align}
Then
\begin{align}
  \frac{dR(\vect x_1, \vect x_2)}{dt} = \frac{d r^{\oxy\oxy}_{12}}{dt} = \frac{\vect r^{\oxy\oxy}_{12}\cdot \vect v^{\oxy\oxy}_{12}}{r^{\oxy\oxy}_{12}}.
\end{align}
where $\vect r_{12}^{\oxy\oxy}$ denotes the oxygen--oxygen distance between molecules 1 and 2. For the derivative of the cosine angle:
\begin{align}\nonumber
  \frac{d \cos(\theta(\vect x_1, \vect x_2))}{dt}
  &=
  \frac{d}{dt}
  \Big (
  \frac{\vect r_{11}^{\oxy\hyd}\cdot \vect r_{12}^{\oxy\oxy}}{r_{11}^{\oxy\hyd} \, r_{12}^{\oxy\oxy}}
  \Big ) \\\nonumber
  &=
  \frac{(\vect r_{11}^{\oxy\hyd}\cdot \vect r_{12}^{\oxy\oxy})'r_{11}^{\oxy\hyd}\, r_{12}^{\oxy\oxy} - \vect r_{11}^{\oxy\hyd}\cdot \vect r_{12}^{\oxy\oxy} (r_{11}^{\oxy\hyd}\cdot r_{12}^{\oxy\oxy})'}{ ( r_{11}^{\oxy\hyd}\, r_{12}^{\oxy\oxy} )^2} \\\nonumber
  & =
  \frac{\vect v_{11}^{\oxy\hyd}\cdot \vect r_{12}^{\oxy\oxy}  + \vect r_{11}^{\oxy\hyd}\cdot \vect v_{12}^{\oxy\oxy}}{ r_{11}^{\oxy\hyd}r_{12}^{\oxy\oxy}}
  -
  \frac{\vect r_{11}^{\oxy\hyd}\cdot \vect r_{12}^{\oxy\oxy} } { ( r_{11}^{\oxy\hyd}\, r_{12}^{\oxy\oxy} )^2 } \times
  \frac{ \vect r_{11}^{\oxy\hyd}\cdot \vect v_{11}^{\oxy\hyd} (r_{12}^{\oxy\oxy})^2 + \vect r_{12}^{\oxy\oxy}\cdot \vect v_{12}^{\oxy\oxy} (r_{11}^{\oxy\hyd})^2  }{ r_{11}^{\oxy\hyd}\, r_{12}^{\oxy\oxy} }
  \\\nonumber  
\end{align}

\bibliography{ref}{}
\bibliographystyle{unsrt}

\end{document}

### 2014-10-16 writedown/auto.correlations/h.bond.notes/main.tex
fix bugs

@@
 \begin{abstract}
-  In this note I describe the implmentational details of the hydrogen-bond auto-correlations.
+  In this note I describe the implementation details of the hydrogen-bond auto-correlations.
 \end{abstract}
@@
 same pair at time $t$.
-The rate of relaxation to equilibrium is of paricular interest:
+The rate of relaxation to equilibrium is of particular interest:
 \begin{align}\label{eqn:k-def}
@@
 definition~\eqref{eqn:k-def}, or calculated from Eq.~\eqref{eqn:k-exp}
-with an explicit estimation of the function $\dot h$. We want to discuss the second way.
+with an explicit estimation of the function $\dot h$. I want to discuss the second way.
 
 Two water molecules are hydrogen-bonded if (1) the O--O distance is less than a cut-off $r_c$, \emph{and} (2)
-the O--H...O angle is less than a cut-off $\theta_c$. To mathematically define the function $h$, we introduce
+the O--H...O angle is less than a cut-off $\theta_c$. To mathematically define the function $h$, I introduce
 the Heaviside function:
@@
 \end{align}
-If we denote the DOFs of two water molecules by $\vect x_1$ and $\vect x_2$, then the hydrogen-bond population function $h$ is expressed by
+If I denote the DOFs of two water molecules by $\vect x_1$ and $\vect x_2$, then the hydrogen-bond population function $h$ is expressed by
 \begin{align}
@@
 between the molecules, while $\theta(\vect x_1, \vect x_2)$ computes
-the O--H...O angle. In practice, it is not easy to calcualte the
-angle, but the cosine angle is relatively easy. Therefore we use the
+the O--H...O angle. In practice, it is not easy to calculate the
+angle, but the cosine angle is relatively easy. Therefore I use the
 definition 
@@
 \end{align}
-If we notice the fact that the DOFs of the molecules are functions of
+If noticing the fact that the DOFs of the molecules are functions of
 time, i.e.~$\vect x_1 = \vect x_1(t)$, and $\vect x_2 = \vect x_2(t)$, then
@@
 \end{align}
-We compute the two derivatives in the equation:
+The two derivatives in the equation is computed by:
 \begin{align}
@@
     \begin{alignedat}{3}
-      &\frac 1{2\Delta L}, &\qquad& -\frac{\Delta L}{2} \leq x < \frac{\Delta L}{2}, \\
+      &\frac 1{\Delta L}, &\qquad& -\frac{\Delta L}{2} \leq x < \frac{\Delta L}{2}, \\
       & 0, &     & \textrm{otherwise},
@@
 \cos(\theta(\vect x_1, \vect x_2))/dt$. To compute $dR(\vect x_1,
-\vect x_2)/dt$, we fristly derive the derivative w.r.t.~the distance
-between any two positions $\vert \vect r_1 - \vect r_2\vert$:
+\vect x_2)/dt$, I firstly derive the time-derivative of the distance
+between any two positions $r_{12} = \vert \vect r_{12}\vert  = \vert \vect r_2 - \vect r_1\vert$:
 \begin{align} 
-  \frac{d\vert \vect r_1(t) - \vect r_2(t)\vert}{dt}
+  \frac{d\vert \vect r_2(t) - \vect r_1(t)\vert}{dt}
   &=
-  \frac{( \vect r_1(t) - \vect r_2(t) )}{  \vert \vect r_1(t) - \vect r_2(t)\vert} \cdot
-  \frac{ d( \vect x_1(t) - \vect x_2(t) )}{dt}  
+  \frac{( \vect r_2(t) - \vect r_1(t) )}{  \vert \vect r_2(t) - \vect r_1(t)\vert} \cdot
+  \frac{ d( \vect x_2(t) - \vect x_1(t) )}{dt}  
   =
-  \frac{( \vect r_1(t) - \vect r_2(t) ) \cdot (\vect v_1(t) - \vect v_2(t))}{  \vert \vect r_1(t) - \vect r_2(t)\vert} 
+  \frac{( \vect r_2(t) - \vect r_1(t) ) \cdot (\vect v_2(t) - \vect v_1(t))}{  \vert \vect r_2(t) - \vect r_1(t)\vert} 
   =
@@
 \end{align}
-where $\vect r_{12}^{\oxy\oxy}$ denotes the oxygen--oxygen distance between molecules 1 and 2. For the derivative of the cosine angle:
+where $r_{12}^{\oxy\oxy}$ denotes the oxygen--oxygen distance between molecules 1 and 2. For the derivative of the cosine angle:
 \begin{align}\nonumber
@@
 \end{align}
+The meaning of the notations should be self-explanatory.
 

### 2014-10-16 zm/template.water/tools/scripts/ti.sh
fix bug when # appears in the output of energy correction program

@@ -43,7 +43,7 @@ do
 done
 
 if echo $gmx_ele_method | grep zm &> /dev/null; then    
-    energy_corr=`$zm_gen_dir/energy.corr -l $zm_l --alpha $zm_alpha --rc $gmx_rcut_ele `
+    energy_corr=`$zm_gen_dir/energy.corr -l $zm_l --alpha $zm_alpha --rc $gmx_rcut_ele | grep -v \#`
 else
     energy_corr=0.0
 fi

### 2014-10-17 writedown/auto.correlations/h.bond.notes/main.tex
rename

@@
 
-\title{Notes on the hydrogen-bond auto-correlation}
+\title{Note on the hydrogen-bond auto-correlation}
 \author{Han Wang}
@@
 \begin{abstract}
-  In this note I describe the implementation details of the hydrogen-bond auto-correlations.
+  In this note I describe the implementation details of the hydrogen-bond auto-correlation.
 \end{abstract}
@@
   &=
-  \frac{(\vect r_{11}^{\oxy\hyd}\cdot \vect r_{12}^{\oxy\oxy})'r_{11}^{\oxy\hyd}\, r_{12}^{\oxy\oxy} - \vect r_{11}^{\oxy\hyd}\cdot \vect r_{12}^{\oxy\oxy} (r_{11}^{\oxy\hyd}\cdot r_{12}^{\oxy\oxy})'}{ ( r_{11}^{\oxy\hyd}\, r_{12}^{\oxy\oxy} )^2} \\\nonumber
+  \frac{(\vect r_{11}^{\oxy\hyd}\cdot \vect r_{12}^{\oxy\oxy})'r_{11}^{\oxy\hyd}\, r_{12}^{\oxy\oxy} - \vect r_{11}^{\oxy\hyd}\cdot \vect r_{12}^{\oxy\oxy} (r_{11}^{\oxy\hyd}\cdot r_{12}^{\oxy\oxy})'}{ ( r_{11}^{\oxy\hyd}\, r_{12}^{\oxy\oxy} )^2} \\
   & =
@@
   \frac{ \vect r_{11}^{\oxy\hyd}\cdot \vect v_{11}^{\oxy\hyd} (r_{12}^{\oxy\oxy})^2 + \vect r_{12}^{\oxy\oxy}\cdot \vect v_{12}^{\oxy\oxy} (r_{11}^{\oxy\hyd})^2  }{ r_{11}^{\oxy\hyd}\, r_{12}^{\oxy\oxy} }
-  \\\nonumber  
 \end{align}

### 2014-10-17 writedown/osci.ele/submit.tex
rename

--- 2014-03-05 writedown/npt-neq/submit.tex
@@
 First, an equilibrium NVT simulation at 300~K of
-100~\textsf{ns} was performed with a Langevin thermostat (time-scale
+1000~\textsf{ns} was performed with a Langevin thermostat (time-scale
 $\tau_T = 0.5~\textsf{ps}$).  Along the trajectory, configurations were taken every
-50~\textsf{ps} and we used 2000 initial configurations for each nonequilibrium
+0.5~\textsf{ns} and we used 2000 initial configurations for each nonequilibrium
 MD simulation (if not stated otherwise for specific cases).
@@
 interaction (van der Waals interaction)
-have a cut-off radius of 1.0~nm, and has been smoothed from $0.8$ to $1.0$~nm by the
+had a cut-off radius of 1.0~nm, and had been smoothed from $0.8$ to $1.0$~nm by the
 ``switch'' method provided by the GROMACS code.
@@
 periodic system. For the direct space part of PME the cut-off and smoothing follow the same principles as those applied to the van der Waals interaction.
-All hydrogen involving bonds are constrained by LINCS~\cite{hess1997lincs}, except 
-the TIP3P water molecules which are constrained by the SETTLE algorithm~\cite{miyamoto2004settle}.
+All hydrogen involving bonds were constrained by LINCS~\cite{hess1997lincs}, except 
+the TIP3P water molecules which were constrained by the SETTLE algorithm~\cite{miyamoto2004settle}.
 In the thermostated region, the original dynamics was
@@
 
-\begin{figure}
+\begin{figure*}
   \centering
@@
   \label{fig:tmp4}
-\end{figure}
+\end{figure*}
 
@@
   \centering
-  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-1.eps}
-  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-2.eps}
-  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-3.eps}
-  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-4.eps}
-  \includegraphics[width=0.3\textwidth]{fig-trans-010-flux-5.eps}
+  \includegraphics[width=0.22\textwidth]{fig-trans-010-flux-1.eps}
+  \includegraphics[width=0.22\textwidth]{fig-trans-010-flux-2.eps}\\
+  \vskip .3cm
+  \includegraphics[width=0.22\textwidth]{fig-trans-010-flux-3.eps}
+  \includegraphics[width=0.22\textwidth]{fig-trans-010-flux-4.eps}\\
+  \vskip .3cm
+  \includegraphics[width=0.22\textwidth]{fig-trans-010-flux-5.eps}
   \caption{
@@
     The probability flux $F_{J,I}(t)$ (defined by Eqn.~\eqref{eqn:tmp7}) is reported in units of $\textrm{ps}^{-1}$.
-    From top, left to right we report $I = \confaa$, $\confab$, $\confba$; bottom, left to right $\confbb$ and
+    From top to bottom, left to right we report $I = \confaa$, $\confab$, $\confba$, $\confbb$ and
     $\confc$, respectively. In each plot, the red line stands for $J=\confaa$,
@@
 {fade away as the system relaxes}. The
-probability of the $\alpha$-helix conformation $\confaa$, grows from 0.45 to 0.69.
+probability of the $\alpha$-helix conformation $\confaa$, grows from 0.43 to 0.65.
 The $\alpha$-helix $\confab$  does not change significantly  under the action of EF.
-The left-hand helix conformation $\confc$ noticeably grows from 0 to 0.22.
+The left-hand helix conformation $\confc$ noticeably grows from 0.05 to 0.25.
 We plot the net probability fluxes {of the four-branching-trajectories case} in Fig.~\ref{fig:tmp6}.
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{fig-rdf.eps}
-  \includegraphics[width=0.48\textwidth]{fig-hbond.eps}
+  \includegraphics[width=0.4\textwidth]{fig-rdf.eps}
+  \includegraphics[width=0.4\textwidth]{fig-hbond.eps}
   \caption{The solvent structure around the alanine dipeptide.  
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{fig-mode2-dipol.eps}
-  \includegraphics[width=0.48\textwidth]{fig-mode2-order.eps}
+  \includegraphics[width=0.4\textwidth]{fig-mode2-dipol.eps}
+  \includegraphics[width=0.4\textwidth]{fig-mode2-order.eps}
   \caption{Illustration of the effect of the oscillatory EF on the system:
@@
   \label{fig:tmp9}
-\end{figure}
-
-\begin{figure}
+\end{figure*}
+
+\begin{figure*}
   \centering
@@
   \label{fig:tmp10}
-\end{figure}
+\end{figure*}
 
@@
 \begin{align}\label{eqn:appdx1}
-  P_\confc(t) = \langle\chi_{\confc}(t)\rangle = \langle \chi_{\confc} \rangle_0 -
+  P_\confc(t) = \langle\chi_{\confc}(t)\rangle \approx \langle \chi_{\confc} \rangle_0 -
   \beta \int_0^t ds\; M_e(t - s)\langle j(0)\cdot \chi_{\confc}(t) \rangle_0,
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{suppinfo}
+% \begin{suppinfo}
 
@@
 
-\end{suppinfo}
+% \end{suppinfo}
 

### 2014-10-26 writedown/period.noneq.msm/paper.tex
add intro

@@
 \section{Introduction}
-Non-equilibrium, especially periodically driven system. Interesting.
-
-MSM tools for analyzing, provide profound understanding.
-
-Current achievement of MSM in equilibrium cases:
-\begin{itemize}
-\item well developed in theory and applications \cite{A19-31, A19-1}
-\item software for MSM building \cite{A19-49, MSMBuilder}
-\end{itemize}
-
-Importance: first application of MSM in a non-equilibrium system.
+% \textbf{Non-equilibrium, especially periodically driven system. Interesting.}
+
+The non-equilibrium biomolecular systems, especially
+those systems under periodic driven, are attracting increasing
+interest.  For example, the potential effects of an electromagnetic
+radiation on the human body tissue (e.g.~DNA, protein, and membrane)  has been extensively
+investigated by a vast number of literatures, and a very limited
+subset of them is Ref.~\cite{bohr2000microwave, bohr2000microwave-1, dePomerai2000cell,
+  dePomerai2003microwave, mancinelli2004non, inskip2001cellular, bekard2013electric, budi2005electric,
+  budi2007effect, budi2008comparative, astrakas2012structural,
+  damm2012can, english2009nonequilibrium, solomentsev2012effects,
+  wang2014exploring}.  Among those theoretical investigations, the
+molecular dynamics (MD) has been shown  useful in understanding
+the response of the biomolecular conformation to the external electric field,
+due to its ability of resolving the molecular
+details, which are sometimes not achievable in experiments. Only
+recently, a dynamical non-equilibrium MD simulation (D-NEMD) method has
+been proposed.  With the local thermostating technique, the D-NEMD
+method is able to sample the non-equilibrium probability density at the
+constant temperature, therefore opens the possibility of studying the
+non-equilibrium processes in a statistically reliable and
+thermodynamically consistent way.
+
+% \textbf{MSM tools for analyzing, provide profound understanding.}
+
+Despite their high resolution in presenting a molecular system, MD the
+trajectories including the time-dependent position and velocity of every atom
+sometimes impose non-trivial challenge for data analyzing, in the sense that 
+extracting the essential structure and dynamical properties is
+becoming increasingly difficult as the  system size and trajectory length grow.
+% by merely visulizing (not only molecular cartoons but also order parameters)
+% and observing the molecules.
+The Markov state model
+(MSM)~\cite{A19-31}, which is a promising method for data analyzing of
+the high-dimensional MD trajectories, has been well developed over the
+past decade in theory and applications \cite{A19-31, A19-1}, and in
+the software implementations~\cite{A19-49, MSMBuilder}.  The principal
+idea of MSM is to approximate the original high-dimensional system by
+a reduced Markovian dynamics over a finite number of states, from
+which the essential structures and dynamics can be formulated by the spectrum analysis.
+By assigning the spacial and temporal discretizations, 
+the transition probabilities are sampled from MD trajectories, and
+the MSM does not need more information from the MD simulation.
+The quality of the MSM therefore relies on the quality of the discretizations.
+Moreover, the characteristic of the original dynamics plays a role:
+It has been shown that in principle good approximate accuracy would be achieved
+by using only a few ``coresets'',
+if the system is dominated by a few metastable states, in the sense that
+the MD trajectories stay in the vicinity of a metastable state substantially longer than
+transform to another such state~\cite{schuette2011markov}.
+Besides the applications in analyzing the MD trajectories, it worth noting that MSM is
+also used for designing initial configurations for massively parallel MD
+simulations~\cite{kohlhoff2014cloud}.
+
+% Current achievement of MSM in equilibrium cases:
+% \begin{itemize}
+% \item well developed in theory and applications \cite{A19-31, A19-1}
+% \item software for MSM building \cite{A19-49, MSMBuilder}
+% \end{itemize}
+
+% \textbf{Importance: first application of MSM in a non-equilibrium system.}
+
+Despite the significance of the non-equilibrium phenomena, the
+analysis of the non-equilibrium MD simulations mainly follows the
+visualizing (not only molecular cartoons but also order parameters)
+and observing approach, and the quantitative description of
+the essential conformational dynamics is still lacking. On the other
+hand, the MSM, to the best of our knowledge, has only been applied to
+equilibrium systems,  and most of them are assumed reversible. This work is the first attempt
+of using the MSM in analyzing a class of truly non-equilibrium systems:
+periodic external driven. Being more specifically,
+we investigate the protein conformational dynamics
+under the oscillating electric field (EF).
+In Sec.~\ref{sec:disc}, we discuss the temporal and spacial
+discretizations of the non-equilibrium dynamics. The spacial discretization
+is on the dihedral angle space, which can be interpreted as a
+MSM in the traditional sense of full spacial partition.
+In the temporal direction, the non-equilibrium process
+is  discretized by the Floquet theorem into a time-homogeneous
+but not necessarily reversible dynamics. Since the full spacial partition
+is not preferable in high-dimensional system, in Sec.~\ref{sec:build-msm},
+the MSM based on milestoning is introduced for the discretized irreversible process.
+The validity of the discretizations and the MSM is checked in Sec.~\ref{sec:alanine}
+by comparing to the brute force
+non-equilibrium simulation of alanine dipeptide under oscillating EF.
+This work is summarized in Sec.~\ref{sec:conclusion} by a chart presenting
+the workflow of building MSM for non-equilibrium systems,
+and open questions are presented in the end.
 
@@
 \label{sec:disc}
-For the sake of simplicity we consider diffusive molecular dynamics in an energy landscape $V$ driven by the time-dependet external driving force $E(t)D(x_t)$ with the
+For the sake of simplicity we consider diffusive molecular dynamics in an energy landscape $V$ driven by the time-dependent external driving force $E(t)D(x_t)$ with the
 $T$-periodic external field $E(t)$:
@@
 \subsection{Spatial discretization: Master equation}
-We will now introduce an appropriate spatial discretization of this kind of non-equilibirium MD -- this is done for reasons of simplicity only; we could completely avoid it for the price of more technical arguments.
+We will now introduce an appropriate spatial discretization of this kind of non-equilibrium MD -- this is done for reasons of simplicity only; we could completely avoid it for the price of more technical arguments.
 For achieving this discretization, we 
@@
 Since $P$ is a stochastic matrix, its eigenvalues are contained in the unit circle in
-the complex plane, i.e., each eigenvalue $\lambda$ (potentially coomplex-valued)
+the complex plane, i.e., each eigenvalue $\lambda$ (potentially complex-valued)
 satisfies $|\lambda|\le 1$. Furthermore $\lambda=1$ is an
@@
 However,
-by far most of the literature is related to building \emph{standard} MSMs for equilibirium MD.
+by far most of the literature is related to building \emph{standard} MSMs for equilibrium MD.
 In standard MSM also the transition region has to be discretized, a feature that often forces the user to incorporate more macrostates than essentially needed to approximate the long-term kinetics.
@@
 In general the milestone process need not be a Markov process.
-The results in \cite{A19-31,sarich2014utilizing} show, however, that it is an approximate Markov process as long as the core sets are proper metastable sets, i.e., if the typical timecale on which $(X_m)$ leaves $C$ is much smaller than the typical expected hitting times between the core sets.
-Thus, by taking $\hat{P}$ as our MSM transition matrix, we introduce an additional modelling error that is the smaller the more metastable the core sets are.
+The results in \cite{A19-31,sarich2014utilizing} show, however, that it is an approximate Markov process as long as the core sets are proper metastable sets, i.e., if the typical timescale on which $(X_m)$ leaves $C$ is much smaller than the typical expected hitting times between the core sets.
+Thus, by taking $\hat{P}$ as our MSM transition matrix, we introduce an additional modeling error that is the smaller the more metastable the core sets are.
 With this MSM transition matrix, we can define the MSM kinetics:
@@
 If all of its entries are positive such that it is a stochastic matrix, $\hat{M}^{-1}\hat{T}$ thus can also be taken as MSM transition matrices.
-In the case of $\hat{M}^{-1}\hat{T}$ the MSM modelling error results from Galerkin discretization, while the MSM modelling error of $\hat{P}$ results from ignoring the potential non-Markovianity of $\hat{X}_m$.
+In the case of $\hat{M}^{-1}\hat{T}$ the MSM modeling error results from Galerkin discretization, while the MSM modeling error of $\hat{P}$ results from ignoring the potential non-Markovianity of $\hat{X}_m$.
 
@@
 The whole system was coupled to the Parrinello-Rahman barostat~\cite{parrinello1981polymorphic} (in standard Gromacs implementation) with $\tau_P = 2.0$~ps to
-keep the system at 1~Bar. The non-equilibirium trajectories
+keep the system at 1~Bar. The non-equilibrium trajectories
 were integrated by the Leap-frog scheme with a time-step of 0.002~ps.
@@
 used to compute the long-range electrostatic interaction,
-with the same real-space cut-off radius as the van der Waals interactoins,
+with the same real-space cut-off radius as the van der Waals interactions,
 and the Gromacs default Fourier spacing of 0.12~nm.
@@
 in comparison to the original NEMD simulation.
-Finally we will coarse grain this description further by constructiion of a $3$ state Markov State Model that is able to describe the long-term kinetics of the system correctly.
+Finally we will coarse grain this description further by construction of a $3$ state Markov State Model that is able to describe the long-term kinetics of the system correctly.
 
@@
 \end{equation}
-However, $\vect P$ allows to approximate the original dynamics on multiples $mT$ of the period only. In order to have a time-continuos description we need the generator $L(t)$ of the Master equation. 
+However, $\vect P$ allows to approximate the original dynamics on multiples $mT$ of the period only.
+In order to have a time-continuous description we need the generator $L(t)$ of the Master equation.
 If the discretization is fine enough one possible approximation to $L(t)$ is via
@@
 $j\in\{\alpha_R,\beta,\alpha_L\}$ conditioned on starting from the
-conformation $(\phi,\psi)$, more exactly from equilibirum conformations $(\phi,\psi)\in\Omega_i$.  Since the largest first mean hitting
+conformation $(\phi,\psi)$, more exactly from equilibrium conformations $(\phi,\psi)\in\Omega_i$.  Since the largest first mean hitting
 time (starting from states in coreset $\confaa$ and hitting $\confc$) is longer than
@@
 essentially smaller than NEMD:
-the computation of $h_{C_j}$ is an issue of miiliseconds on a laptop, while the
+the computation of $h_{C_j}$ is an issue of milliseconds on a laptop, while the
 NEMD trajectories took $1.6\times 10^4$ core hours for Intel Xeon E5-4650 CPUs.
@@
 Tab.~\ref{tab:tmp1}.
-Without surprising, the two approaches for MSM building are consitent.
+Without surprising, the two approaches for MSM building are consistent.
 The MSM is able to accurately reproduce
@@
   \caption{Comparison of NEMD and MSM long-term kinetics of alanine
-    dipeptide in an oscillatory electrc field. The plots show the
+    dipeptide in an oscillatory electric field. The plots show the
     time-dependent probability $\hat p_j(t)$ to be assigned to
@@
 \section{Concluding remarks and discussions}
+\label{sec:conclusion}
 
@@
 
-In this paper we developped methods of building MSM for a periodically driven
+In this paper we developed methods of building MSM for a periodically driven
 non-equilibrium system. By a numerical example
@@
 We firstly provide effective methods for discretizing the original NEMD trajectories
-both temporally and spacially, and the end-product is a time-homogeneous
+both temporally and spatially, and the end-product is a time-homogeneous
 (not necessarily reversible) Markov jump process.
@@
 one can either do a two-steps discretization,
-i.e.~firstly spacial and then temperoal,
-or a single step  involes both discretizations simulteneously.
+i.e.~firstly spacial and then temporal,
+or a single step  involves both discretizations simultaneously.
 They are exhibited by the left-most and middle branches in Fig.~\ref{fig:flowchart}.
@@
 continuous and time-inhomogeneous {Markov} jump process.
-In principle most of the discretiztion methods for the equilibirum
+In principle most of the discretization methods for the equilibrium
 case can be generalized to non-equilibrium without substantial
-difficulty, however, we have not compare different discretiztion methods
+difficulty, however, we have not compare different discretization methods
 regarding the accuracy, since it is out of the scope of the present work.
 We show that, by numerical example, a uniform $20\times20$
-discretiztion over the dihedral angles $\phi$--$\psi$ space is a good
+discretization over the dihedral angles $\phi$--$\psi$ space is a good
 choice for alanine dipeptide.  In the tests, the state independency in
 computing the generator is used as an indicator for the quality of the
-discretiztion.
-
-The Floquet thoerem discretize a periodic process by taking only
+discretization.
+
+The Floquet theorem discretize a periodic process by taking only
 integral periods, so that
@@
 necessarily reversible process.
-The advantage of this discretiztion is  obvious: All
+The advantage of this discretization is  obvious: All
 well-developed theories and computational tools for time-homogeneous
-Markov processes can be directly appled. In the alanine dipeptide
+Markov processes can be directly applied. In the alanine dipeptide
 system, we compare the the quasi-stationary probability, first mean
@@
 
-Although the end-product of the two-step and one-step discretiztions are equivalent,
-it is clear that the one-step discretiztion does not preserve any information
+Although the end-product of the two-step and one-step discretizations are equivalent,
+it is clear that the one-step discretization does not preserve any information
 within one period, because only the states
 at integral periods are considered. This is not a serious problem
-whenever the long-time hehaviors of the system is of interst, and
+whenever the long-time behaviors of the system is of interest, and
 their corresponding time-scales are significantly longer than one
@@
 is comparable to, or even shorter than the period, the two-step
-discretiztion is prefered, so that one can recover the dynamics within
+discretization is preferred, so that one can recover the dynamics within
 one period no matter when it is necessary. If the longest non-trivial
-time-scale is comparable to one period, thenn the Floquet theorem
+time-scale is comparable to one period, then the Floquet theorem
 is not preferable, and the non-equilibrium dynamics may be well
@@
 
-Building the MSM from the time-homogeneous disretized dynamics is straightforward by
+Building the MSM from the time-homogeneous discretized dynamics is straightforward by
 using Eq.~\eqref{eq:msm-tmatrix-00} and a set of coresets that are
 derived from the discretized dynamics.  Numerical
-results shows that a 3-state MSM can reporduce the leading non-trivial
+results shows that a 3-state MSM can reproduce the leading non-trivial
 eigenvalue with very good accuracy, while the second non-trivial
@@
 this three state MSM, we can also reproduce, with almost perfect
-accuracy, the time-evolution of the metastable state pobabilities from
-equilibirum (no external driven) to the non-equilibrium
+accuracy, the time-evolution of the metastable state probabilities from
+equilibrium (no external driven) to the non-equilibrium
 quasi-stationary state.
@@
 This task is substantially
-simplified when an accurate time-homogeneous discretiztion 
+simplified when an accurate time-homogeneous discretization 
 to the original time-inhomogeneous NEMD is accessible.
@@
 building in non-equilibrium systems. It is worth noting that the
-numerical example itself presenst interesting phenomena: under the
+numerical example itself presents interesting phenomena: under the
 oscillatory EF, the population of the left-handed $\alpha$-helix
-significantly increases with respect to the equilibirum population
+significantly increases with respect to the equilibrium population
 (see also the discussions in Ref.~\cite{wang2014exploring}),
-and the leading time-scale is much shorter than the equilibirum case.
+and the leading time-scale is much shorter than the equilibrium case.
 It is in principle possible to apply the non-equilibrium
@@
 non-equilibrium system
-(the equilibirum counterpart is provided by Ref.~\cite{schutte2014markov}).
+(the equilibrium counterpart is provided by Ref.~\cite{schutte2014markov}).
 This makes possible the molecular design under

### 2014-10-29 writedown/zm/report/report.tex

@@
   }
-  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}ccc ccccc}\hline\hline
-    Method      &   $r_c$ &    $l$      & $\mu^\exc$  &$C_{v,m}$ &  $\eps$ & $D$ &  $\eta$ \\
-                &    [nm] &             &   [kJ/mol] &[J/(mol K)] & (Sys.~$\systemsb$) & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
+  \begin{tabular*}{0.95\textwidth}{@{\extracolsep{\fill}}cccc ccccc}\hline\hline
+    Method      &   $r_c$ &    $l$ & $\alpha$  & $\mu^\exc$  &$C_{v,m}$ &  $\eps$ & $D$ &  $\eta$ \\
+                &    [nm] &        & [$\textrm{nm}^{-1}$] &   [kJ/mol] &[J/(mol K)] & (Sys.~$\systemsb$) & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
     % Method      &   $r_c$ [nm] &    $l$      & $\mu^\exc$ [kJ/mol] &$C_{v,m}$ [J/(mol K)] & $\eps$ (Sys.~$\systemsb$) & $D$ [$10^{-9}\textrm{m}^2/\textrm{s}$] &  $\eta$ [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
-    SPME        &         1.9     &       --      &      $-26.08$ (0.24) & 72.21 (0.97)  & 97.6 (3.4)  & 5.86 (0.07)   & 0.315 (0.007)\\
-    RF          &         1.2     & --            &      $-26.03$ (0.32) & 72.28 (0.81)  & \textbf{59.4} (1.3)  & \textbf{6.27} (0.19)   & \textbf{0.449} (0.020)\\
-    ZM          &         1.2     &       1       &      $-26.22$ (0.30) & 71.75 (0.89)  & 95.5 (2.4)  & \textbf{5.53} (0.11)   & \textbf{0.346} (0.006)\\ 
-    ZM          &         1.2     &       2       &      $-26.24$ (0.24) & 71.53 (0.88)  & 95.4 (2.5)  & 5.82 (0.27)   & 0.318 (0.012)\\ 
-    ZM          &         1.2     &       3       &      $-{26.18}$ (0.20) & 71.58 (0.88)  & 96.0 (2.7)  & 5.79 (0.09)   & 0.321 (0.008)\\ 
-    ZM          &         1.2     &       4       &      $-{26.01}$ (0.26) & 71.07 (0.84)  & 99.7 (2.2)  & 5.89 (0.09)   & 0.318 (0.013)\\
+    SPME        &1.9 & -- &    & $-26.08$ (0.24) & 72.21 (0.97)  & 97.6 (3.4)  & 5.86 (0.07)   & 0.315 (0.007)\\
+    RF          &1.2 & -- &--  & $-26.03$ (0.32) & 72.28 (0.81)  & \textbf{59.4} (1.3)  & \textbf{6.27} (0.19)   & \textbf{0.449} (0.020)\\\hline
+    ZM          &1.2 & 1  &0.0 & $-26.22$ (0.30) & 71.75 (0.89)  & 95.5 (2.4)  & \textbf{5.53} (0.11)   & \textbf{0.346} (0.006)\\ 
+    ZM          &1.2 & 1  &0.5 & $-26.36$ (0.30) & 72.25 (0.78)  & 97.1 (2.2)  & \textbf{5.52} (0.25)   & \textbf{0.339} (0.008)\\ 
+    ZM          &1.2 & 1  &1.0 & $-26.01$ (0.22) & 72.44 (0.84)  & 96.2 (2.3)  &        {5.78} (0.25)   & \textbf{0.330} (0.011)\\ 
+    ZM          &1.2 & 1  &1.5 & $-26.03$ (0.24) & 71.31 (0.78)  & 99.1 (2.5)  & \textbf{5.71} (0.09)   &        {0.312} (0.008)\\ 
+    ZM          &1.2 & 1  &2.0 & $-26.14$ (0.34) & 71.27 (0.78)  & 95.9 (2.5)  &        {5.90} (0.04)   &        {0.307} (0.007)\\ \hline
+    ZM          &1.2 & 2  &0.0 & $-26.24$ (0.24) & 71.53 (0.88)  & 95.4 (2.5)  & 5.82 (0.27)   & 0.318 (0.012)\\ 
+    ZM          &1.2 & 3  &0.0 & $-{26.18}$ (0.20) & 71.58 (0.88)  & 96.0 (2.7)  & 5.79 (0.09)   & 0.321 (0.008)\\ 
+    ZM          &1.2 & 4  &0.0 & $-{26.01}$ (0.26) & 71.07 (0.84)  & 99.7 (2.2)  & 5.89 (0.09)   & 0.318 (0.013)\\
     \hline\hline
@@
   }
-  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}ccc ccc}\hline\hline
-    Method      &   $r_c$ [nm] &    $l$      & $\kappa_T$ [$10^{-10}\textrm{m}^2/\textrm{N}$] & $C_{p,m}$ [J/(mol K)] & $\alpha$ [$10^{-3}\textrm{K}^{-1}$]\\\hline
-    SPME        &         1.9     &       --      & 5.941 (0.050)               &79.18 (0.94)           &1.026 (0.016)          \\
-    RF          &         1.2     & --            & \textbf{6.508} (0.058)      &\textbf{82.34} (0.95)  &\textbf{1.149} (0.018) \\
-    ZM          &         1.2     &       1       & 5.872 (0.050)               &78.91 (0.95)           &1.009 (0.018)          \\
-    ZM          &         1.2     &       2       & 5.952 (0.051)               &79.70 (0.96)           &1.033 (0.016)          \\
-    ZM          &         1.2     &       3       & 5.991 (0.050)               &79.49 (1.01)           &1.024 (0.019)          \\
-    ZM          &         1.2     &       4       & 5.961 (0.054)               &79.46 (0.98)           &1.034 (0.017)          \\
+  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}cccc ccc}\hline\hline
+    Method      &   $r_c$ [nm] &    $l$ & $\alpha$ [$\textrm{nm}^{-1}$]     & $\kappa_T$ [$10^{-10}\textrm{m}^2/\textrm{N}$] & $C_{p,m}$ [J/(mol K)] & $\alpha$ [$10^{-3}\textrm{K}^{-1}$]\\\hline
+    SPME        &  1.9     &       -- &    & 5.941 (0.050)               &79.18 (0.94)           &1.026 (0.016)          \\
+    RF          &  1.2     & --       &    & \textbf{6.508} (0.058)      &\textbf{82.34} (0.95)  &\textbf{1.149} (0.018) \\\hline
+    ZM          &  1.2     &       1  & 0.0& 5.872 (0.050)               &78.91 (0.95)           &1.009 (0.018)          \\
+    ZM          &  1.2     &       1  & 0.5& 5.920 (0.050)               &78.90 (0.92)           &\textbf{1.003} (0.016) \\
+    ZM          &  1.2     &       1  & 1.0& 5.946 (0.050)               &78.37 (0.92)           &1.008 (0.016)          \\
+    ZM          &  1.2     &       1  & 1.5& 5.974 (0.050)               &80.23 (0.86)           &1.040 (0.017)          \\
+    ZM          &  1.2     &       1  & 2.0& \textbf{6.052} (0.051)      &79.41 (0.91)           &1.045 (0.016)          \\\hline
+    ZM          &  1.2     &       2  & 0.0& 5.952 (0.051)               &79.70 (0.96)           &1.033 (0.016)          \\
+    ZM          &  1.2     &       3  & 0.0& 5.991 (0.050)               &79.49 (1.01)           &1.024 (0.019)          \\
+    ZM          &  1.2     &       4  & 0.0& 5.961 (0.054)               &79.46 (0.98)           &1.034 (0.017)          \\
     \hline\hline
@@
   \label{fig:tmp4}
+\end{figure}
+
+\subsection{Damping effect}
+
+In this section we investigate the damping effect. The pressure is plotted as a function of  the cut-off radius is plotted for different choices of
+the splitting parameter $\alpha$ in Fig.~\ref{fig:damp-pres}. The system for the simulation was $L_0$.
+\begin{figure}
+  \centering
+  \includegraphics[width=0.49\textwidth]{fig/nvt.pressure.1/pressure-l1.eps}
+  \includegraphics[width=0.49\textwidth]{fig/nvt.pressure.1/pressure-l2.eps}\\
+  \includegraphics[width=0.49\textwidth]{fig/nvt.pressure.1/pressure-l3.eps}
+  \includegraphics[width=0.49\textwidth]{fig/nvt.pressure.1/pressure-l4.eps}
+  \caption{The pressure convergence with respect to the cut-off radius.
+    For ZM method, different splitting parameter $\alpha$ (in unit of $\textrm{nm}^{-1}$) are shown for different orders:  $l=1$, 2, 4, and 4.
+  }
+  \label{fig:damp-pres}
+\end{figure}
+
+The convergence of the integrated auto-correlation function $I_\eta(T) $ is shown in Fig.~\ref{fig:damp-vis-l1}.
+\begin{figure}
+  \centering
+  \includegraphics[]{fig/result.tiny/fig-vis-l1-damp.eps}
+  \caption{The convergence of the integrated auto-correlation function $I_\eta(T) $.
+The error bars indicating 95\% confidence level are plotted with the SPME method.
+The different splitting parameters for ZM $l=1$ method are plotted}
+  \label{fig:damp-vis-l1}
+\end{figure}
+
+The RDF is plotted for different splitting parameters $\alpha$ for ZM $l=2$ and 3 in Fig.~\ref{fig:damp-rdf-l23}. Higher $\alpha$ reproduces the RDF better.
+The system was $L_1$.
+\begin{figure}[]
+  \centering
+  \includegraphics[width=0.49\textwidth]{fig/result.nvt/fig-rdf-l2-damp.eps}
+  \includegraphics[width=0.49\textwidth]{fig/result.nvt/fig-rdf-l3-damp.eps}
+  \caption{Radial distribution function for different splitting parameters $\alpha$ for ZM $l=2$ (left) and $l=3$ (right).}
+  \label{fig:damp-rdf-l23}
+\end{figure}
+
+The Kirkwood G-factor is plotted for different splitting parameters $\alpha$ for ZM $l=2$ and 3 in Fig.~\ref{fig:damp-gkr-l23}. 
+The system was $L_1$.
+\begin{figure}[]
+  \centering
+  \includegraphics[width=0.49\textwidth]{fig/result.nvt/fig-gkr-l2-damp.eps}
+  \includegraphics[width=0.49\textwidth]{fig/result.nvt/fig-gkr-l3-damp.eps}
+  \caption{Kirkwood G-factor for different splitting parameters $\alpha$ for ZM $l=2$ (left) and 3 (right).}
+  \label{fig:damp-gkr-l23}
 \end{figure}

### 2014-10-30 writedown/zm/paper.water/main.tex
add new manuscript files

--- 2014-10-29 writedown/zm/report/report.tex
@@
-\documentclass[aip,jcp,a4paper,reprint,unsortedaddress,onecolumn,fleqn]{revtex4-1}
+\documentclass[aip,jcp,a4paper,preprint,unsortedaddress,onecolumn,fleqn]{revtex4-1}
 % \documentclass[reprint,unsortedadress,oneclumn]{revtex4-1}
@@
 \email{han.wang@fu-berlin.de}
-\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
+\affiliation{CAEP Software Center for High Performance Numerical Simulation, Beijing, China}
 \author{Ikuo Fukuda}

### 2014-10-30 writedown/zm/paper.water/main.tex
merge tables

@@
 \usepackage{indentfirst} 
+\usepackage{rotating,booktabs}
 
@@
 
-\begin{table}
+\begin{sidewaystable}
   \centering
-  \caption{The excess chemical potential $\mu^\exc$, constant volume molar heat capacity $C_{v,m}$, dielectric constant $\eps$, diffusion constant $D$ and viscosity $\eta$
+  \caption{The excess chemical potential $\mu^\exc$, constant volume molar heat capacity $C_{v,m}$, dielectric constant $\eps$, diffusion constant $D$, viscosity $\eta$, constant pressure molar heat capacity $C_{v,m}$, isothermal compressibility $\kappa_T$ and
+    thermal expansion coefficient $\alpha$
     calculated by different methods.    
@@
   }
-  \begin{tabular*}{0.95\textwidth}{@{\extracolsep{\fill}}cccc ccccc}\hline\hline
-    Method      &   $r_c$ &    $l$ & $\alpha$  & $\mu^\exc$  &$C_{v,m}$ &  $\eps$ & $D$ &  $\eta$ \\
-                &    [nm] &        & [$\textrm{nm}^{-1}$] &   [kJ/mol] &[J/(mol K)] & (Sys.~$\systemsb$) & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
-    % Method      &   $r_c$ [nm] &    $l$      & $\mu^\exc$ [kJ/mol] &$C_{v,m}$ [J/(mol K)] & $\eps$ (Sys.~$\systemsb$) & $D$ [$10^{-9}\textrm{m}^2/\textrm{s}$] &  $\eta$ [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
-    SPME        &1.9 & -- &    & $-26.08$ (0.24) & 72.21 (0.97)  & 97.6 (3.4)  & 5.86 (0.07)   & 0.315 (0.007)\\
-    RF          &1.2 & -- &--  & $-26.03$ (0.32) & 72.28 (0.81)  & \textbf{59.4} (1.3)  & \textbf{6.27} (0.19)   & \textbf{0.449} (0.020)\\\hline
-    ZM          &1.2 & 1  &0.0 & $-26.22$ (0.30) & 71.75 (0.89)  & 95.5 (2.4)  & \textbf{5.53} (0.11)   & \textbf{0.346} (0.006)\\ 
-    ZM          &1.2 & 1  &0.5 & $-26.36$ (0.30) & 72.25 (0.78)  & 97.1 (2.2)  & \textbf{5.52} (0.25)   & \textbf{0.339} (0.008)\\ 
-    ZM          &1.2 & 1  &1.0 & $-26.01$ (0.22) & 72.44 (0.84)  & 96.2 (2.3)  &        {5.78} (0.25)   & \textbf{0.330} (0.011)\\ 
-    ZM          &1.2 & 1  &1.5 & $-26.03$ (0.24) & 71.31 (0.78)  & 99.1 (2.5)  & \textbf{5.71} (0.09)   &        {0.312} (0.008)\\ 
-    ZM          &1.2 & 1  &2.0 & $-26.14$ (0.34) & 71.27 (0.78)  & 95.9 (2.5)  &        {5.90} (0.04)   &        {0.307} (0.007)\\ \hline
-    ZM          &1.2 & 2  &0.0 & $-26.24$ (0.24) & 71.53 (0.88)  & 95.4 (2.5)  & 5.82 (0.27)   & 0.318 (0.012)\\ 
-    ZM          &1.2 & 3  &0.0 & $-{26.18}$ (0.20) & 71.58 (0.88)  & 96.0 (2.7)  & 5.79 (0.09)   & 0.321 (0.008)\\ 
-    ZM          &1.2 & 4  &0.0 & $-{26.01}$ (0.26) & 71.07 (0.84)  & 99.7 (2.2)  & 5.89 (0.09)   & 0.318 (0.013)\\
+  \bigskip
+  \centering\small\setlength\tabcolsep{2pt}
+  \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}cccc cccccccc}\hline\hline
+    Method      &   $r_c$ &    $l$ & $\alpha$  & $\mu^\exc$  &$C_{v,m}$ &  $\eps$ & $D$ &  $\eta$  &  $\kappa_T$  & $C_{p,m}$ & $\alpha$ \\
+                &    [nm] &        & [$\textrm{nm}^{-1}$] &   [kJ/mol] &[J/(mol K)] & (Sys.~$\systemsb$) & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$]  & [$10^{-10}\textrm{m}^2/\textrm{N}$] & [J/(mol K)] & [$10^{-3}\textrm{K}^{-1}$]\\\hline
+    SPME        &1.9 & -- &    & $-26.08$ (0.24) & 72.21 (0.97)  & 97.6 (3.4)          & 5.86 (0.07)         & 0.315 (0.007)         & 5.941 (0.050)               &79.18 (0.94)           &1.026 (0.016)          \\
+    RF          &1.2 & -- &--  & $-26.03$ (0.32) & 72.28 (0.81)  & \textbf{59.4} (1.3) & \textbf{6.27} (0.19)& \textbf{0.449} (0.020)& \textbf{6.508} (0.058)      &\textbf{82.34} (0.95)  &\textbf{1.149} (0.018) \\\hline
+    ZM          &1.2 & 1  &0.0 & $-26.22$ (0.30) & 71.75 (0.89)  & 95.5 (2.4)          & \textbf{5.53} (0.11)& \textbf{0.346} (0.006)& 5.872 (0.050)               &78.91 (0.95)           &1.009 (0.018)          \\
+    ZM          &1.2 & 1  &0.5 & $-26.36$ (0.30) & 72.25 (0.78)  & 97.1 (2.2)          & \textbf{5.52} (0.25)& \textbf{0.339} (0.008)& 5.920 (0.050)               &78.90 (0.92)           &\textbf{1.003} (0.016) \\
+    ZM          &1.2 & 1  &1.0 & $-26.01$ (0.22) & 72.44 (0.84)  & 96.2 (2.3)          &        {5.78} (0.25)& \textbf{0.330} (0.011)& 5.946 (0.050)               &78.37 (0.92)           &1.008 (0.016)          \\
+    ZM          &1.2 & 1  &1.5 & $-26.03$ (0.24) & 71.31 (0.78)  & 99.1 (2.5)          & \textbf{5.71} (0.09)&        {0.312} (0.008)& 5.974 (0.050)               &80.23 (0.86)           &1.040 (0.017)          \\
+    ZM          &1.2 & 1  &2.0 & $-26.14$ (0.34) & 71.27 (0.78)  & 95.9 (2.5)          &        {5.90} (0.04)&        {0.307} (0.007)& \textbf{6.052} (0.051)      &79.41 (0.91)           &1.045 (0.016)          \\\hline
+    ZM          &1.2 & 2  &0.0 & $-26.24$ (0.24) & 71.53 (0.88)  & 95.4 (2.5)          & 5.82 (0.27)         & 0.318 (0.012)         & 5.952 (0.051)               &79.70 (0.96)           &1.033 (0.016)          \\
+    ZM          &1.2 & 3  &0.0 & $-26.18$ (0.20) & 71.58 (0.88)  & 96.0 (2.7)          & 5.79 (0.09)         & 0.321 (0.008)         & 5.991 (0.050)               &79.49 (1.01)           &1.024 (0.019)          \\
+    ZM          &1.2 & 4  &0.0 & $-26.01$ (0.26) & 71.07 (0.84)  & 99.7 (2.2)          & 5.89 (0.09)         & 0.318 (0.013)         & 5.961 (0.054)               &79.46 (0.98)           &1.034 (0.017)          \\
     \hline\hline
@@
   \label{tab:tmp3}
-\end{table}
+\end{sidewaystable}
+
+% \begin{table}
+%   \centering
+%   \caption{The constant pressure molar heat capacity $C_{v,m}$, isothermal compressibility $\kappa_T$ and
+%     thermal expansion coefficient $\alpha$
+%     calculated by different methods.    
+%     The parenthesises in the last column show the statistical uncertainty
+%     at the confidence level of 95~\%.
+%     The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
+%   }
+%   \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}cccc ccc}\hline\hline
+%     Method      &   $r_c$ [nm] &    $l$ & $\alpha$ [$\textrm{nm}^{-1}$]     &  $\kappa_T$ [$10^{-10}\textrm{m}^2/\textrm{N}$] & $C_{p,m}$ [J/(mol K)] & $\alpha$ [$10^{-3}\textrm{K}^{-1}$]\\\hline
+%     SPME        &  1.9     &       -- &    & 5.941 (0.050)               &79.18 (0.94)           &1.026 (0.016)          \\
+%     RF          &  1.2     & --       &    & \textbf{6.508} (0.058)      &\textbf{82.34} (0.95)  &\textbf{1.149} (0.018) \\\hline
+%     ZM          &  1.2     &       1  & 0.0& 5.872 (0.050)               &78.91 (0.95)           &1.009 (0.018)          \\
+%     ZM          &  1.2     &       1  & 0.5& 5.920 (0.050)               &78.90 (0.92)           &\textbf{1.003} (0.016) \\
+%     ZM          &  1.2     &       1  & 1.0& 5.946 (0.050)               &78.37 (0.92)           &1.008 (0.016)          \\
+%     ZM          &  1.2     &       1  & 1.5& 5.974 (0.050)               &80.23 (0.86)           &1.040 (0.017)          \\
+%     ZM          &  1.2     &       1  & 2.0& \textbf{6.052} (0.051)      &79.41 (0.91)           &1.045 (0.016)          \\\hline
+%     ZM          &  1.2     &       2  & 0.0& 5.952 (0.051)               &79.70 (0.96)           &1.033 (0.016)          \\
+%     ZM          &  1.2     &       3  & 0.0& 5.991 (0.050)               &79.49 (1.01)           &1.024 (0.019)          \\
+%     ZM          &  1.2     &       4  & 0.0& 5.961 (0.054)               &79.46 (0.98)           &1.034 (0.017)          \\
+%     \hline\hline
+%   \end{tabular*}
+%   \label{tab:tmp3a}
+% \end{table}
+
+% \begin{table}
+%   \centering
+%   \caption{The excess chemical potential $\mu^\exc$, constant volume molar heat capacity $C_{v,m}$, dielectric constant $\eps$, diffusion constant $D$ and viscosity $\eta$
+%     calculated by different methods.    
+%     The parenthesises in the last column show the statistical uncertainty
+%     at the confidence level of 95~\%.
+%     The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
+%   }
+%   \begin{tabular*}{0.95\textwidth}{@{\extracolsep{\fill}}cccc ccccc}\hline\hline
+%     Method      &   $r_c$ &    $l$ & $\alpha$  & $\mu^\exc$  &$C_{v,m}$ &  $\eps$ & $D$ &  $\eta$ \\
+%                 &    [nm] &        & [$\textrm{nm}^{-1}$] &   [kJ/mol] &[J/(mol K)] & (Sys.~$\systemsb$) & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
+%     % Method      &   $r_c$ [nm] &    $l$      & $\mu^\exc$ [kJ/mol] &$C_{v,m}$ [J/(mol K)] & $\eps$ (Sys.~$\systemsb$) & $D$ [$10^{-9}\textrm{m}^2/\textrm{s}$] &  $\eta$ [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
+%     SPME        &1.9 & -- &    & $-26.08$ (0.24) & 72.21 (0.97)  & 97.6 (3.4)  & 5.86 (0.07)   & 0.315 (0.007)\\
+%     RF          &1.2 & -- &--  & $-26.03$ (0.32) & 72.28 (0.81)  & \textbf{59.4} (1.3)  & \textbf{6.27} (0.19)   & \textbf{0.449} (0.020)\\\hline
+%     ZM          &1.2 & 1  &0.0 & $-26.22$ (0.30) & 71.75 (0.89)  & 95.5 (2.4)  & \textbf{5.53} (0.11)   & \textbf{0.346} (0.006)\\ 
+%     ZM          &1.2 & 1  &0.5 & $-26.36$ (0.30) & 72.25 (0.78)  & 97.1 (2.2)  & \textbf{5.52} (0.25)   & \textbf{0.339} (0.008)\\ 
+%     ZM          &1.2 & 1  &1.0 & $-26.01$ (0.22) & 72.44 (0.84)  & 96.2 (2.3)  &        {5.78} (0.25)   & \textbf{0.330} (0.011)\\ 
+%     ZM          &1.2 & 1  &1.5 & $-26.03$ (0.24) & 71.31 (0.78)  & 99.1 (2.5)  & \textbf{5.71} (0.09)   &        {0.312} (0.008)\\ 
+%     ZM          &1.2 & 1  &2.0 & $-26.14$ (0.34) & 71.27 (0.78)  & 95.9 (2.5)  &        {5.90} (0.04)   &        {0.307} (0.007)\\ \hline
+%     ZM          &1.2 & 2  &0.0 & $-26.24$ (0.24) & 71.53 (0.88)  & 95.4 (2.5)  & 5.82 (0.27)   & 0.318 (0.012)\\ 
+%     ZM          &1.2 & 3  &0.0 & $-{26.18}$ (0.20) & 71.58 (0.88)  & 96.0 (2.7)  & 5.79 (0.09)   & 0.321 (0.008)\\ 
+%     ZM          &1.2 & 4  &0.0 & $-{26.01}$ (0.26) & 71.07 (0.84)  & 99.7 (2.2)  & 5.89 (0.09)   & 0.318 (0.013)\\
+%     \hline\hline
+%   \end{tabular*}
+%   \label{tab:tmp3}
+% \end{table}
     % SPME        &         1.9     &       --      & 1.67049 (0.00014)     $-26.08$ (0.24) & 72.21 (0.97)  & 97.6 (3.4)  & 5.86 (0.07)   & 0.315 (0.007)\\
@@
     % ZM          &         1.2     &       4       & 1.67031 (0.00010)     $-{26.01}$ (0.26) & 71.07 (0.84)  & 99.7 (2.2)  & 5.89 (0.09)   & 0.318 (0.013)\\
-
-\begin{table}
-  \centering
-  \caption{The constant pressure molar heat capacity $C_{v,m}$, isothermal compressibility $\kappa_T$ and
-    thermal expansion coefficient $\alpha$
-    calculated by different methods.    
-    The parenthesises in the last column show the statistical uncertainty
-    at the confidence level of 95~\%.
-    The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
-  }
-  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}cccc ccc}\hline\hline
-    Method      &   $r_c$ [nm] &    $l$ & $\alpha$ [$\textrm{nm}^{-1}$]     & $\kappa_T$ [$10^{-10}\textrm{m}^2/\textrm{N}$] & $C_{p,m}$ [J/(mol K)] & $\alpha$ [$10^{-3}\textrm{K}^{-1}$]\\\hline
-    SPME        &  1.9     &       -- &    & 5.941 (0.050)               &79.18 (0.94)           &1.026 (0.016)          \\
-    RF          &  1.2     & --       &    & \textbf{6.508} (0.058)      &\textbf{82.34} (0.95)  &\textbf{1.149} (0.018) \\\hline
-    ZM          &  1.2     &       1  & 0.0& 5.872 (0.050)               &78.91 (0.95)           &1.009 (0.018)          \\
-    ZM          &  1.2     &       1  & 0.5& 5.920 (0.050)               &78.90 (0.92)           &\textbf{1.003} (0.016) \\
-    ZM          &  1.2     &       1  & 1.0& 5.946 (0.050)               &78.37 (0.92)           &1.008 (0.016)          \\
-    ZM          &  1.2     &       1  & 1.5& 5.974 (0.050)               &80.23 (0.86)           &1.040 (0.017)          \\
-    ZM          &  1.2     &       1  & 2.0& \textbf{6.052} (0.051)      &79.41 (0.91)           &1.045 (0.016)          \\\hline
-    ZM          &  1.2     &       2  & 0.0& 5.952 (0.051)               &79.70 (0.96)           &1.033 (0.016)          \\
-    ZM          &  1.2     &       3  & 0.0& 5.991 (0.050)               &79.49 (1.01)           &1.024 (0.019)          \\
-    ZM          &  1.2     &       4  & 0.0& 5.961 (0.054)               &79.46 (0.98)           &1.034 (0.017)          \\
-    \hline\hline
-  \end{tabular*}
-  \label{tab:tmp3a}
-\end{table}
-
 % \subsubsection{Hydrogen bonding}

### 2014-10-30 writedown/zm/paper.water/main.tex
rm alanine

@@
 
-\subsection{Simulation with alanine dipeptide}
-
-Here we denote the full phase space by $\Omega$, and the phase space
-variable by $\vect x$. We assume that 1, the trajectory $\vect x(t)$
-is Markovian; 2, it is ergodic and as $t\rightarrow\infty$ the phase
-space probability density $p(\vect x)$ converges to the unique
-equilibrium probability density $\mu(\vect x)$ and 3, the trajectory
-is reversible (detailed balance condition is satisfied). One can
-easily write down a propagator for the probability density
-\begin{equation}
-\label{eq:propagator}  
-p_{t+\tau}(\vect x) = \mathcal Q(\tau)\circ
-p_t(\vect x),
-\end{equation}
-where the constant $\tau$ is called the lag time. Due to the
-Markovianity of the system, the propagator satisfies the
-Chapman-Kolmogorov equation:
-\begin{equation}
-  \label{eq:chapman}
-  p_{t+k\tau}(\vect x) = \mathcal Q^k(\tau)\circ p_t(\vect x).
-\end{equation}
-Since the dynamics is reversible, the eigenvalues of $\mathcal
-Q(\tau)$ are real-valued. We consider the first $m$ dominant
-eigenvalues from the spectrum: $1 = \lambda_1 > \lambda_2 \geq
-\lambda_3 \geq \cdots \geq \lambda_m$. For most of the biomolecule
-systems, it is reasonable to assume a spectrum gap, i.e.~for a certain
-$m$ $\lambda_m$ is much larger than the magnitude of the rest
-eigenvalues. For the first $m$ leading eigenvalues one define the
-corresponding timescales by
-\begin{equation}
-  \label{eq:timescale}
-  t_i = -\frac{\tau}{\log \lambda_i}, \quad i= 2,\cdots, m
-\end{equation}
-Usually the first $m$ leading timescales can be identified with the
-slowest conformational changes of the biomolecule. The spectrum gap is
-considered as a timescale separation between the slow conformational
-changes and the fast motion in the system, e.g.~bond vibration, angle
-vibration, solvent motion, and other relatively fast conformational
-changes. The eigenfunction of the first eigenvalue is nothing but the
-equilibrium probability density $\mu(\vect x)$. We denote the
-eigenfunctions corresponding to $\lambda_2, \cdot, \lambda_m$ by
-$\phi_2(\vect x), \cdots, \phi_m(\vect x)$, then the original dynamics
-of the system~\eqref{eq:chapman} is approximated by
-\begin{equation}
-  \label{eq:app-dynamics}
-  p_{t+k\tau}(\vect x) = \mu(\vect x) + \sum_{i=2}^m e^{-\frac{k\tau}{t_i}} a_i \phi_i(\vect x) + \textrm{fast decaying dynamics}
-\end{equation}
-where $a_i$ are constants calculated by $a_i = \int \frac{1}{\mu(\vect
-  x)} p_t(\vect x)\phi_i(\vect x) d\vect x$. This means that the
-evolution of the phase space probability is a summation of the
-time-independent equilibrium probability and a series of slow decaying
-processes that are defined by the timescales $t_i$ and eigenfunctions
-$\phi_i(\vect x)$. The eigenfunctions indicates how the conformational
-change happens.
-The slowest timescales and the corresponding conformational
-changes are usually of the most biological interest.  Since the
-slowest timescales determine the convergence speed of the system with
-respect to the equilibrium probability distribution, they are the most
-difficult part to sample and estimate in molecular dynamics
-simulations.
-
-In practice, it is not easy to directly calculate the eigenvalues and
-eigenfunctions from molecular trajectories. Therefore, the continuous
-trajectories are usually projected on to a finite number of sets, so
-that the original dynamics is reduced to a Markov jump process that is
-also called the Markov state model. We expect the Markov jump process
-is a good approximate to the original dynamics in the sense that the
-eigen pairs of the reduced process accurately reproduce those of the
-original dynamics. How to do the discretized and the accuracy are
-explained in detailed in Ref.~\cite{prinz2011markov}.
-
-\begin{figure}
-  \centering  
-  \includegraphics[width=0.49\textwidth]{fig/result.alanine.amber/c-2.eps}
-  \caption{(a) A schematic plot of the alanine dipeptide and the
-    dihedral angles $\phi$ and $\psi$. (b) The free energy landscape on the
-    $\phi$-$\psi$ dihedral angle space.}
-  \label{fig:free-energy}
-\end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.40\textwidth]{fig/result.alanine.amber/fig-dih-dist-phi.eps}\\
-  \includegraphics[width=0.40\textwidth]{fig/result.alanine.amber/fig-dih-dist-psi.eps}
-  \caption{The probability distributions of the dihedral angles.}
-  \label{fig:dih-dist}
-\end{figure}
-
-We simulate the alanine dipeptide with the Amber
-ff-99SB-ILDN~\cite{lindorff2010improved} force field.  The dihedral
-angles $\phi$ and $\psi$ (see Fig.~\ref{fig:free-energy}~(a)) are
-widely accepted as collective variables that can describe the
-conformational dynamics of the system.  The free energy landscape
-on $\phi$-$\psi$ space is given in Fig.~\ref{fig:free-energy}~(b).  The projected
-probability distributions on both dihedral angles
-with error bars are presented in Fig.~\ref{fig:dih-dist}. It can be easily seen
-from the distribution $P(\psi)$ and $P(\psi)$ that the ZM method with
-$l=2$ and 3 reproduce the over-all probability of the main
-conformations, i.e.~the $\alpha$-helix (right-handed), $\beta$-sheet and
-the left-handed $\alpha$-helix with satisfactory accuracy.
-% For these
-% methods, deviations of $P(\phi)$ at $\phi = -75^\circ$ and $\phi =
-% -140^\circ$ are observed. They correspond to the double-peak structure
-% of the right-handed $\alpha$-helix and $\beta$-sheet, which means the
-% error happens at the sub-structure of the right-handed $\alpha$-helix
-% and $\beta$-sheet, which are of relatively smaller biological interest
-% comparing with the main conformations.
-
-\begin{table}
-  \centering
-  \caption{The first three non-trivial timescales in ps computed at lag-time $\tau = 20$~ps.
-  }
-  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}c   ccc}\hline\hline
-    Method      &        $t_2$ [ps]  & $t_3$ [ps] &  $t_4$ [ps] \\\hline
-    SPME        &         1374  (235)     &          70.03  (0.64)  &         39.2  (4.3)    \\
-    RF          &        {1615} (177)     &  \textbf{68.49} (0.42)  & \textbf{34.1} (2.2)    \\
-    ZM $l=1$    &        {1244} (099)     &         {71.00} (0.46)  &         36.2  (4.4)    \\
-    ZM $l=2$    &         1407  (194)     &          70.46  (0.76)  &         38.7  (2.4)    \\
-    ZM $l=3$    &         1449  (116)     &          70.20  (0.57)  &         37.4  (2.5)    \\
-    ZM $l=4$    &        {1119} (129)     &          70.05  (0.71)  &         34.6  (1.8)    \\
-    \hline\hline
-  \end{tabular*}
-  \label{tab:tmp3}
-\end{table}
-
-% \begin{table}
-%   \centering
-%   \caption{The leading time scales in ps.
-%   }
-%   \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}ccc ccc}\hline\hline
-%     Method      &   $r_c$ &    $l$      & $t_2$  & $t_3$ &  $t_4$ \\\hline
-%     SPME        &         1.9     &       --      &         1292  (148)     &          69.95  (0.76)  &         36.0 (4.7)    \\
-%     RF          &         1.2     & --            & \textbf{1615} (155)     &  \textbf{68.48} (0.37)  &         34.1 (1.6)    \\
-%     ZM          &         1.2     &       1       & \textbf{1607} (218)     &  \textbf{72.08} (0.50)  &         31.4 (1.9)    \\
-%     ZM          &         1.2     &       2       &         1324  (110)     &          69.97  (0.58)  &         40.4 (2.8)    \\
-%     ZM          &         1.2     &       3       &         1312  (157)     &          70.50  (0.72)  &         37.1 (4.3)    \\
-%     ZM          &         1.2     &       4       & \textbf{1635} (156)     &          69.71  (0.54)  &         39.2 (3.6)    \\
-%     \hline\hline
-%   \end{tabular*}
-%   \label{tab:tmp3}
-% \end{table}
-
-% \begin{figure}
-%   \centering
-%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-2.eps}
-%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-2.eps}
-%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-2.eps}
-%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-2.eps}
-%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-2.eps}\\
-%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-3.eps}
-%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-3.eps}
-%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-3.eps}
-%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-3.eps}
-%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-3.eps}\\
-%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-4.eps}
-%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-4.eps}
-%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-4.eps}
-%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-4.eps}
-%   \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-4.eps}\\
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-5.eps}\\
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-2-comp.eps}
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-3-comp.eps}
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-rf-eig-vec-4-comp.eps}\\
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-2-comp.eps}
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-3-comp.eps}
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm2-eig-vec-4-comp.eps}\\
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-2-comp.eps}
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-3-comp.eps}
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-4-comp.eps}\\
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm3-eig-vec-5-comp.eps}\\
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.amber/fig-zm4-eig-vec-5.eps}\\
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-spme-eig-vec-2.eps}
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-2.eps}
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-2.eps}
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-2.eps}\\
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-spme-eig-vec-3.eps}
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-3.eps}
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-3.eps}
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-3.eps}\\
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-spme-eig-vec-4.eps}
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-4.eps}
-%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-2-comp.eps}
-%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-3-comp.eps}
-%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-rf-eig-vec-4-comp.eps}\\
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-4.eps}
-%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-5.eps}\\
-%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-2-comp.eps}
-%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-3-comp.eps}
-%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-4-comp.eps}
-%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm3-eig-vec-5-comp.eps}\\
-%   % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-4.eps}\\
-%   % % \includegraphics[width=0.19\textwidth]{fig/result.alanine.charmm27/fig-zm4-eig-vec-5.eps}\\
-%   \caption{The eigenfunctions corresponding to the largest three
-%     non-trivial timescales, computed with lag-time 20~ps.}
-%   \label{fig:tmp5}
-% \end{figure}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.24\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-2.eps}
-  \raisebox{.35cm}{\includegraphics[width=0.21\textwidth]{fig/result.alanine.amber/fig-eig-vec-error-2-phi.eps}}
-  \raisebox{.35cm}{\includegraphics[width=0.21\textwidth]{fig/result.alanine.amber/fig-eig-vec-error-2-psi.eps}}\\
-  \includegraphics[width=0.24\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-3.eps}
-  \raisebox{.35cm}{\includegraphics[width=0.21\textwidth]{fig/result.alanine.amber/fig-eig-vec-error-3-phi.eps}}
-  \raisebox{.35cm}{\includegraphics[width=0.21\textwidth]{fig/result.alanine.amber/fig-eig-vec-error-3-psi.eps}}\\
-  \includegraphics[width=0.24\textwidth]{fig/result.alanine.amber/fig-spme-eig-vec-4.eps}
-  \raisebox{.35cm}{\includegraphics[width=0.21\textwidth]{fig/result.alanine.amber/fig-eig-vec-error-4-phi.eps}}
-  \raisebox{.35cm}{\includegraphics[width=0.21\textwidth]{fig/result.alanine.amber/fig-eig-vec-error-4-psi.eps}}\\
-  \caption{The eigenfunctions corresponding to the largest three
-    non-trivial timescales, computed with lag-time 20~ps.  The left
-    colume shows the eigenfunctions computed by SPME method. The right colume
-    shows the deviation of RF, ZM ($l=1,\cdots,4$) with respect to
-    SPME.  To present the statistical uncertainty, the second
-    eigenfunction is projected on to dihedral angle $\phi$, while the
-    third and fourth eigenfunctions are projected on $\psi$.  The red
-    shadow region presents the statistical uncertainty of SPME. For
-    clarity, only the statistical uncertainty of RF and ZM $l=3$ are
-    presented by error bars.  }
-  \label{fig:tmp5}
-\end{figure}
-
-The leading timescales and corresponding eigenfunctions are given in
-Tab.~\label{tab:tmp3} and Fig.~\ref{fig:tmp5}. The ZM method with
-order 2 and 3 presents best accuracy.
-
 \newpage

### 2014-10-31 writedown/zm/paper.water/main.tex
finish the definitions of the benchmark quantities, organize the result, write descriptions on the system.

@@
 
-\title{A Critical Appraisal of Zero-Multiple Method in Simulation Biomolecular Systems}
+\title{A Critical Appraisal of Zero-Multiple Method in Classical Water Simulation}
 \author{Han Wang}
 \email{han.wang@fu-berlin.de}
-\affiliation{CAEP Software Center for High Performance Numerical Simulation, Beijing, China}
+\affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road 6, 100088 Beijing, China}
 \author{Ikuo Fukuda}
 \email{ifukuda@protein.osaka-u.ac.jp}
-\affiliation{Institute for Protein Research, Osaka University, Japan}
+\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita, Osaka 565-0871, Japan}
+\affiliation{RIKEN (The Institute of Physical and Chemical Research), 2-1 Hirosawa, Wako, Saitama 351-0198, Japan}
 
@@
 
+\section{Introduction}
+
+A very short overview of the existing electrostatic interaction methods.
+Long-range treatment, Ewald and derived methods like SPME.
+Short-range treatment.
+
+The importance of developing a short-range method for the electrostatic interaction.
+
+Zero-Multiple method, an overview, achievements, sucessful applications.
+
+The propuse of this work: Extensive and strict tests investigating the reliablility of Zero-Multiple method in water simulation, which is the most important solvent.
+
+The structure of the paper.
+
+\section{Zero-Multiple Method}
+
+Introduction of the ZM method, formula...
+
+A short mention of the group cut-off v.s.~the atom cut-off method. (will discuss the implmentation in gromacs later)
+
+\section{Benchmark quantities}
+
+In order to investigate the performance of ZM method, we simulation
+the water system by using both SPME and ZM method, and calculate a set
+of \emph{benchmark quantities}.  This set covers a broad range of
+water propertis that are of general interest, and includes the
+structure property (radial distribution function), the thermodynamic
+properties (pressure, excess chemical potential, constant
+volume/pressure heat capacity, isothermal compressibility, thermal
+expansion coefficient), dielectric properties (dielectric constant and
+Kirkwood-G factor) and dynamical properties (diffusion coefficient and
+viscosity).  By comparing ZM to SPME, a good consistency in computing
+the benchmark quantities would indicate a good accuracy of the ZM
+method.  Moreover, being aware of the weakness of the ZM method also
+prevents the application the method in wrong applications.  The ZM
+method is also compared to the traditional short-range method: RF.
+The definitions for computing these quantities are provided in details
+in Appendix.~\ref{appendix:benchmark}.
+
 \section{Simulation protocols}
+
+In this work, we investigate the water system modeled by
+TIP3P~\cite{jorgensen1983comparison} point-charge water model.
+The size of the systems and corresponding number of molecules used for MD simulations are summarized in Tab.~\ref{tab:tmp1}.
+The benchmark quantities were calculated in either  canonical (NVT) or isothermal-isobaric (NPT) ensemble.
+In order to equilibriate the temperature,
+the systems were coupled to either Nose-Hoover~\cite{nose1984molecular,hoover1985canonical} or Langevin thermostat (Tab.~\ref{tab:tmp1})
+at 300~K.
+In the NPT simulations, the systems were further coupled
+to the Parrinello-Rahman barostat~\cite{parrinello1980crystal,parrinello1981polymorphic} (in Gromacs implementation)
+with time-scale $\tau_P = 0.5$~ps to equilibriate the system at 1~Bar.
+All systems were integrated with leap-frog scheme at the time-step of 0.001~ps.
+For the ZM and SPME methods,
+the neighbor lists were updated every 5 time-steps.
+The ``\texttt{group}'' cut-off scheme in Gromacs was used. In order to mimic the atomistic
+cut-off manner, the radius for neighbor list building was set 0.3~nm
+larger than the cut-off radius (the maximum of Coulomb cut-off and the van der Waals cut-off).
+To make sure the van der Waals interactions were cut-off in a smooth way,
+they are modified in a shell of $0.05$~nm width near the cut-off sphere by the Gromacs ``\texttt{shift}'' method.
+The short-range part of SPME method is also smoothed in a shell of $0.05$~nm width  by the Gromacs ``\texttt{pme-switch}'' method.
+The reciprocal space
+grid spacing is 0.06~nm. The B-Spline interpolation order is 6. The
+splitting parameter is optimized by the error estimate for the SPME method~\cite{wang2010optimizing}.
+In the simulations of the RF method, the interactoins were cut-off in the group manner,
+so the radius for neighbor list building is set identical to the cut-off radius.
+No cut-off smoothing was applied in the cases of RF simulation.
 
@@
   \centering
-  \caption{A list of systems tested in this work. We report, from left to right, the number of water
-    molecules in the system (TIP3P model), box size, length of equilibriation, length of productive trajectory, the thermostat and the coupling time scale of the thermostat.
+  \caption{A list of systems simulated in this work. We report, from left to right, the number of water
+    molecules in the system (TIP3P model), equilibrium box size, length of equilibriation, length of productive trajectory, the thermostats and the corresponding coupling time-scales.
   }
+  \vskip .5cm
   \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}c rrrrrr}\hline\hline
     System      & $N$ & $V$ [$\textrm{nm}^3$]  & $T_{eq}$ [ps] & Traj. Length [ps] & Thermostat & $\tau$ [ps]  \\\hline
-    $\systemsb$          & 2,500          & $4.24^3$              & 3,000        & 27,000        & Nose-Hoover & 1.0 \\
     $\systemsbp$         &   2,500        & $4.24^3$              & --           &  6,000        & Nose-Hoover & 1.0\\
-    $\systemmb$          & 4,500          & $5.15^3$              & 3,000        & 17,000        & Langevin & 0.1\\
+    $\systemsb$          & 2,500          & $4.24^3$              & 3,000        & 27,000        & Nose-Hoover & 1.0 \\\hline
     $\systemmbp$         &   4,500        & $5.15^3$              & --           &  6,000        & Langevin & 0.1\\
+    $\systemmb$          & 4,500          & $5.15^3$              & 3,000        & 17,000        & Langevin & 0.1\\\hline
     $\systemla$          &   13,824       & $7.49^3$              & 200          & 1,800         & Langevin & 0.1\\
+    $\systemlbp$         &   13,824       & $7.49^3$              & --           & 10,000        & Langevin & 0.1\\
     $\systemlb$          &   13,824       & $7.49^3$              & 3,000        & 17,000        & Langevin & 0.1\\
-    $\systemlbp$         &   13,824       & $7.49^3$              & --           & 10,000        & Langevin & 0.1\\
     \hline\hline
@@
 
-The systems used for MD simulations are listed in
-Table.\ref{tab:tmp1}.  The initial configurations are prepared by in
-the following steps: (1) A NPT simulation of system $\systemla$ with SPME~\cite{darden1993pme, essmann1995spm}
-electrostatic. The equilibrium density of the system is calculated
-from this simulation. (2) Initial configurations that has 4,500 and
-13,824 molecules are generated at the calculated equilibrium
-density. (3) NVT simulations with SPME electrostatic for system $\systemmbp$
-and $\systemlbp$ are performed. (4) The output configuration of $\systemmbp$ is used as
-initial configuration for system $\systemmb$, and the output configuration of
-$\systemlbp$ is used as initial configuration for system $\systemla$ and $\systemlb$.  The SPME
-parameters for all simulations reported by this work is: real space
-cut-off 1.90~nm. The cut-off is smoothed from 1.85 to 1.90~nm by the
-``\texttt{switch}'' method provide by Gromacs
-4.6~\cite{hess2008gromacs, pronk2013gromacs}. The reciprocal space
-grid spacing is 0.06~nm. The B-Spline interpolation order is 6. The
-splitting parameter is optimized by the error estimate for the SPME method~\cite{wang2010optimizing}.
+The initial configurations were prepared by in
+the following steps:
+(1) An NPT simulation of system $\systemla$ with SPME
+electrostatic was performed. The equilibrium density (984.1~$\textrm{kg}/\textrm{m}^{-3}$) of the system is calculated
+from this simulation.
+(2) Initial configurations that contains 2500, 4500 and
+13824 molecules were generated at the calculated equilibrium
+density.
+(3) NVT simulations with SPME electrostatic for system $\systemsbp$, $\systemmbp$
+and $\systemlbp$ are performed.
+(4) The output configurations of $\systemsbp$ and $\systemmbp$ were used as
+initial configurations for system $\systemsb$ and $\systemmb$, respectively.  The output configuration of
+$\systemlbp$ was used as initial configurations for system $\systemla$ and $\systemlb$.
+% The SPME
+% parameters for all simulations reported by this work is: real space
+% cut-off 1.90~nm.
 
-We add a new system $\systemsb$, and use the Nose-Hoover
-thermostat. The reason is that for the fluctuation properties (in this
-work heat capacity, dielectric constant, diffusion constant and
-viscosity are fluctuation properties), simply increase the size of the
+% The cut-off is smoothed from 1.85 to 1.90~nm by the
+% ``\texttt{switch}'' method provide by Gromacs
+% 4.6~\cite{hess2008gromacs, pronk2013gromacs}.
+
+The smallest system $\systemsb$ was adopted,
+because for the quantities that are computed  by estimating fluctuations (in this
+work heat capacities, compressibility, thermal expansion coefficient, dielectric constant, diffusion constant and
+viscosity are fluctuations. See details in Appendix~\ref{appendix:benchmark}), simply increase the size of the
 system does not improve the accuracy of the 
-simulation~\cite{ferrenberg1991statistical}. The only way to improve
-the accuracy is to run longer simulation to do more
-time-average. Therefore, the optimal way of measuring these properties
-is to use smaller system (as far as the finite size effect is not
-important) and run as long simulation as possible, as the equilibrium
-state is reached. The reason of using Nose-Hoover thermostat is that
+simulation~\cite{milchev1986fluctuations,ferrenberg1991statistical}.
+The optimal way of measuring these properties
+is to simulate with smaller systems (as far as the finite size effect is negligible) and run longer simulations for longer time-averages.
+The reason of using Nose-Hoover thermostat is that
 it perturbs the dynamics of the system only slightly, while the
 Langevin thermostat is likely to substantially change the dynamics
-when the coupling is very strong.
+when the coupling is very strong, therefore, the former was used in computing the dynamical
+properties like the diffusion constant and viscosity.
+The quantities that
+are ensemble averages (in this work, pressure, chemical potential, radial distribution function and Kirkwood-G factor are of this type)
+were computed by the largest system $\systemlb$,
+in order to achieve higher parallel efficiency.
+The system $\sustemmb$ is simulated to investigate the size-dependency of the
+Kirkwood-G factor~\cite{vanderSpoel2006origin}.
 
-\subsection{Static properties}
+\section{Results and discussions}
 
-\subsubsection{Pressure}
 The results are plotted in Fig.~\ref{fig:tmp0}. All pressure calculations are done with system $\systemla$.
@@
 \end{figure}
-
-\subsubsection{Chemical potential}
-
-The chemical potential of the NVT system is defined by
-\begin{align}
-  \mu = \frac{\partial A}{\partial N}\Big\vert_{V,T}
-\end{align}
-In practice the excess chemical potential $\mu^\exc$, which is the
-chemical potential abstracted by the kinetic contribution, is of
-special interest. We calculate the excess chemical potential by the
-thermodynamic integration (TI). In this approach, the interaction
-between an inserted molecule and the rest of the system is controlled
-by a coupling parameter $\lambda$. $\lambda$ goes from 0 to 1, where 0
-indicates no coupling while 1 indicates full coupling. Therefore the
-Hamiltonian of the system is function of the coupling parameter. The
-excess chemical is calculated by:
-\begin{align}
-  \mu^\exc = \int_0^1 \Big\langle \frac{\partial \mathcal H(\lambda)}{\partial \lambda} \Big\rangle_\lambda d\lambda
-\end{align}
-We use a two step coupling approach: firstly couple the van der Waals
-interaction (stage vdw), and then couple the electrostatic interaction
-(stage ele).  During stage vdw, 21 $\lambda$ values are equally
-distributed in $[0,1]$.  During stage ele, 6 $\lambda$ values are
-equally distributed in $[0,0.05]$, while the other 20 $\lambda$ values
-are equally distributed in $[0.05, 1]$. Therefore, in total 47
-simulations are performed for all $\lambda$ values. The simulation was
-in system $\systemla$.
 
@@
   \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}cccc cccccccc}\hline\hline
-    Method      &   $r_c$ &    $l$ & $\alpha$  & $\mu^\exc$  &$C_{v,m}$ &  $\eps$ & $D$ &  $\eta$  &  $\kappa_T$  & $C_{p,m}$ & $\alpha$ \\
-                &    [nm] &        & [$\textrm{nm}^{-1}$] &   [kJ/mol] &[J/(mol K)] & (Sys.~$\systemsb$) & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$]  & [$10^{-10}\textrm{m}^2/\textrm{N}$] & [J/(mol K)] & [$10^{-3}\textrm{K}^{-1}$]\\\hline
-    SPME        &1.9 & -- &    & $-26.08$ (0.24) & 72.21 (0.97)  & 97.6 (3.4)          & 5.86 (0.07)         & 0.315 (0.007)         & 5.941 (0.050)               &79.18 (0.94)           &1.026 (0.016)          \\
-    RF          &1.2 & -- &--  & $-26.03$ (0.32) & 72.28 (0.81)  & \textbf{59.4} (1.3) & \textbf{6.27} (0.19)& \textbf{0.449} (0.020)& \textbf{6.508} (0.058)      &\textbf{82.34} (0.95)  &\textbf{1.149} (0.018) \\\hline
-    ZM          &1.2 & 1  &0.0 & $-26.22$ (0.30) & 71.75 (0.89)  & 95.5 (2.4)          & \textbf{5.53} (0.11)& \textbf{0.346} (0.006)& 5.872 (0.050)               &78.91 (0.95)           &1.009 (0.018)          \\
-    ZM          &1.2 & 1  &0.5 & $-26.36$ (0.30) & 72.25 (0.78)  & 97.1 (2.2)          & \textbf{5.52} (0.25)& \textbf{0.339} (0.008)& 5.920 (0.050)               &78.90 (0.92)           &\textbf{1.003} (0.016) \\
-    ZM          &1.2 & 1  &1.0 & $-26.01$ (0.22) & 72.44 (0.84)  & 96.2 (2.3)          &        {5.78} (0.25)& \textbf{0.330} (0.011)& 5.946 (0.050)               &78.37 (0.92)           &1.008 (0.016)          \\
-    ZM          &1.2 & 1  &1.5 & $-26.03$ (0.24) & 71.31 (0.78)  & 99.1 (2.5)          & \textbf{5.71} (0.09)&        {0.312} (0.008)& 5.974 (0.050)               &80.23 (0.86)           &1.040 (0.017)          \\
-    ZM          &1.2 & 1  &2.0 & $-26.14$ (0.34) & 71.27 (0.78)  & 95.9 (2.5)          &        {5.90} (0.04)&        {0.307} (0.007)& \textbf{6.052} (0.051)      &79.41 (0.91)           &1.045 (0.016)          \\\hline
-    ZM          &1.2 & 2  &0.0 & $-26.24$ (0.24) & 71.53 (0.88)  & 95.4 (2.5)          & 5.82 (0.27)         & 0.318 (0.012)         & 5.952 (0.051)               &79.70 (0.96)           &1.033 (0.016)          \\
-    ZM          &1.2 & 3  &0.0 & $-26.18$ (0.20) & 71.58 (0.88)  & 96.0 (2.7)          & 5.79 (0.09)         & 0.321 (0.008)         & 5.991 (0.050)               &79.49 (1.01)           &1.024 (0.019)          \\
-    ZM          &1.2 & 4  &0.0 & $-26.01$ (0.26) & 71.07 (0.84)  & 99.7 (2.2)          & 5.89 (0.09)         & 0.318 (0.013)         & 5.961 (0.054)               &79.46 (0.98)           &1.034 (0.017)          \\
+    Method      &   $r_c$ &    $l$ & $\alpha$  & $\mu^\exc$  &$C_{v,m}$ & $C_{p,m}$ &   $\kappa_T$  &$\alpha$ &  $\eps$ & $D$ &  $\eta$  \\
+                & [nm] & & [$\textrm{nm}^{-1}$] &   [kJ/mol] &[J/(mol K)] & [J/(mol K)] & [$10^{-10}\textrm{m}^2/\textrm{N}$] &  [$10^{-3}\textrm{K}^{-1}$]&  & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$]  \\
+                &    &    &    &NVT $\systemla$&NVT $\systemsb$&  NPT $\systemsb$          &  NPT $\systemsb$    &  NPT $\systemsb$    & NVT $\systemsb$& NVT $\systemsb$    & NVT $\systemsb$       \\\hline
+    SPME        &1.9 & -- &2.1 & $-26.1$ (0.2) & 72.2 (1.0)  &79.2 (0.9)           & 5.94 (0.05)               &1.03 (0.02)          & 98 (3)          &         5.86  (0.07)&         0.315  (0.007)\\
+    RF          &1.2 & -- &--  & $-26.0$ (0.3) & 72.3 (0.8)  &\textbf{82.3} (1.0)  & \textbf{6.51} (0.06)      &\textbf{1.15} (0.02) & \textbf{59} (1) & \textbf{6.27} (0.19)& \textbf{0.449} (0.020)\\\hline
+    ZM          &1.2 & 1  &0.0 & $-26.2$ (0.3) & 71.8 (0.9)  &78.9 (1.0)           & 5.87 (0.05)               &1.01 (0.02)          & 96 (2)          & \textbf{5.53} (0.11)& \textbf{0.346} (0.006)\\ 
+    ZM          &1.2 & 1  &0.5 & $-26.4$ (0.3) & 72.3 (0.8)  &78.9 (0.9)           & 5.92 (0.05)               &\textbf{1.00} (0.02) & 97 (2)          & \textbf{5.52} (0.25)& \textbf{0.339} (0.008)\\ 
+    ZM          &1.2 & 1  &1.0 & $-26.0$ (0.2) & 72.4 (0.8)  &78.4 (0.9)           & 5.95 (0.05)               &1.01 (0.02)          & 96 (2)          &        {5.78} (0.25)& \textbf{0.330} (0.011)\\ 
+    ZM          &1.2 & 1  &1.5 & $-26.0$ (0.2) & 71.3 (0.8)  &80.2 (0.9)           & 5.97 (0.05)               &1.04 (0.02)          & 99 (3)          & \textbf{5.71} (0.09)&        {0.312} (0.008)\\ 
+    ZM          &1.2 & 1  &2.0 & $-26.1$ (0.3) & 71.3 (0.8)  &79.4 (0.9)           & \textbf{6.05} (0.05)      &1.05 (0.02)          & 96 (3)          &        {5.90} (0.04)&        {0.307} (0.007)\\\hline
+    ZM          &1.2 & 2  &0.0 & $-26.2$ (0.2) & 71.5 (0.9)  &79.7 (1.0)           & 5.95 (0.05)               &1.03 (0.02)          & 95 (3)          &         5.82  (0.27)&         0.318  (0.012)\\
+    ZM          &1.2 & 3  &0.0 & $-26.2$ (0.2) & 71.6 (0.9)  &79.5 (1.0)           & 5.99 (0.05)               &1.02 (0.02)          & 96 (3)          &         5.79  (0.09)&         0.321  (0.008)\\
+    ZM          &1.2 & 4  &0.0 & $-26.0$ (0.3) & 71.1 (0.8)  &79.5 (1.0)           & 5.96 (0.05)               &1.03 (0.02)          &100 (2)          &         5.89  (0.09)&         0.318  (0.013)\\
     \hline\hline
@@
 
-\subsubsection{Constant volume molar heat capacity}
-The constant volume molar heat capacity is defined by:
-\begin{align}
-  C_{v,m} = \frac{1}{k_BT^2 N} \langle (\mathcal H - \langle\mathcal H\rangle)^2 \rangle,
-\end{align}
-where $\mathcal H$ is the Hamiltonian of the system. Since constant
-volume heat capacity is a extensive thermodynamics quantity, it is
-normalized by the number molecules in the system.
-It is calculated in system $\systemsb$.
-
-\subsubsection{Constant pressure molar heat capacity}
-The constant pressure molar heat capacity is defined by:
-\begin{align}
-  C_{p,m} = \frac{1}{k_BT^2 N} \langle ( H - \langle H\rangle)^2 \rangle,
-\end{align}
-where $ H$ is the enthalpy of the system, defined by $H = \mathcal H + PV$. Since constant
-pressure heat capacity is a extensive thermodynamics quantity, it is
-normalized by the number molecules in the system.
-It is calculated by a NPT simulation of  system $\systemsb$.
-
-\subsubsection{Isothermal heat capacity}
-The isothermal heat capacity is defined by
-\begin{align}
-  \kappa_T = \frac{1}{k_BT} \frac{\langle (V - \langle V\rangle)^2 \rangle}{\langle V\rangle}.
-\end{align}
-It is calculated by a NPT simulation of  system $\systemsb$.
-
-\subsubsection{Thermal expansion coefficient}
-The thermal expansion coefficient is defined by
-\begin{align}
-  \alpha = \frac{1}{k_BT^2\langle V\rangle} \langle (H - \langle H\rangle)\cdot(V - \langle V\rangle) \rangle
-\end{align}
-It is calculated by a NPT simulation of  system $\systemsb$.
-
-\subsubsection{The dielectric constant}
-
-The dielectric constant:
-\begin{align}
-  \eps = 1 + \frac{1}{3L^3 k_BT} ( \langle \vert \vect M\vert^2\rangle - \vert\langle \vect M\rangle\vert^2 )
-\end{align}
-where
-\begin{align}
-  \vect M = \sum_i\boldsymbol\mu_i = \sum_{\alpha\in i} q_\alpha\vect r_\alpha
-\end{align}
-The results are listed in Tab.~\ref{tab:tmp2}. The dielectric constant calculated in system $\systemsb$ is reported in Table.~\ref{tab:tmp3}.
-
 \begin{table}
@@
 
-\subsubsection{Radial distribution function}
-The results are plotted in Fig.~\ref{fig:rdf}. As the order of ZM method goes higher, the precision of RDF improves. In addition, the precision of RF method is between $l=2$ and $l=3$.
 \begin{figure}
   \centering
-  \includegraphics[width=0.4\textwidth]{fig/result.nvt/fig-rdf.eps}  
+  \includegraphics[]{fig/result.nvt/fig-rdf.eps}  
   \caption{The RDF of different method. The insert is a zoom-in of range 0.9 -- 1.5~nm. In the insert, the position of the cut-off (1.2~nm) is indicated by a vertical black line.}
@@
 \end{figure}
-
-\subsubsection{Kirkwood G-factor}
-
-The Kirkwood G-factor is defined by~\cite{vanderSpoel2006origin}
-\begin{align}
-  G_k(r) =
-  \Big\langle
-  \frac 1N
-  \sum_{i=1}^N \sum_{j, r_{ij} < r}
-  \frac {\boldsymbol\mu_i \cdot \boldsymbol\mu_j}{\vert \boldsymbol\mu_i\vert \cdot \vert\boldsymbol\mu_j\vert}
-  \Big\rangle,
-\end{align}
-where $r_{ij}$ denotes the oxygen-oxygen distance between two water
-molecules.  It is well know that the G-factor is system size
-dependent~\cite{vanderSpoel2006origin}. Here we show the G-factor for
-both a smaller system $\systemmb$ (Fig.~\ref{fig:tmp1}) and a larger system $\systemlb$
-(Fig.~\ref{fig:tmp2}).  In the figures, the statistical uncertainty of
-the SPME method is denoted by the red error bar, while those of the
-other methods are essentially the same, so they are not presented for
-clarity.  In both the system, the RF method is qualitatively
-wrong. The results of the ZM method are consistent with SPME
-method. The lower order produces better consistency.  An artificial
-oscillation around the cut-off radius presents for $l=1$, but it is
-not obvious for $l\geq 2$.  For high order ZM (here $l=3$ is investigated),
-using larger cut-off radius can substantially improve the accuracy.
 
@@
 
-\subsection{Dynamical properties}
-
-\subsubsection{Diffusion constant}
-The diffusion constant is calculated from the Einstein relation:
-\begin{align}
-  D = \lim_{t\rightarrow \infty}\frac {1}{6t} \langle \vert \vect r_i(t) - \vect r_i(0)\vert^2\rangle.
-\end{align}
-In practice, the mean-square-displacement $\langle\vert \vect r_i(t) - \vect
-r_i(0)\vert^2\rangle$ is calculated, then the value is linearly fitted. The
-resulting slop is used to calculate the diffusion constant. The results are listed in Table~\ref{tab:tmp3}.
-The ZM method $l\geq 2$ is consistent with the SPME
-result, while the RF method is off. The system for simulation is $\systemsb$.
-
-\subsubsection{Viscosity}
-The viscosity is calculated from the Green-Kubo relation:
-\begin{align}
-  \eta = \frac{V}{k_BT}\int_0^\infty\langle P_{\alpha\beta}(0) P_{\alpha\beta}(t)\rangle\,dt, \quad \alpha,\beta \in \{x, y, z\}
-\end{align}
-where $\alpha$ and $\beta$ denote the directions, and
-$P_{\alpha\beta}$ denotes the off-diagonal components of the pressure
-tensor. Since we used the isotropic system setting, then it is obvious
-that $P_{xy}$, $P_{yz}$ and $P_{xz}$ are equivalent. Moreover, it has
-been pointed out that in addition $(P_{xx} - P_{yy})/2$ and $(P_{xx} -
-P_{yy})/2$ are two independent components that are equivalent to the
-first three~\cite{alfe1998first}. Therefore, the viscosity is
-calculated from the auto-correlation functions of five independent
-components, and the statistical error is estimated from the standard
-deviation of the viscosities calculated from the five components.
-
-We investigate the convergence of the integral of the auto-correlation function w.r.t.~time:
-\begin{align}
-  I_\eta(T) = \frac{V}{k_BT}\int_0^T\langle P_{\alpha\beta}(0) P_{\alpha\beta}(t)\rangle\,dt,
-\end{align}
-and plot the function $I_\eta(T) $ for all method in
-Fig.~\ref{fig:tmp4}.  It is clear the integral for the RF method
-converges at 6~ps, while the ZM method converges only in 2~ps, which
-is consistent with the SPME result.  The value of ZM $l=1$ method is
-different from the rest ZM method an SPME result.  The value
-$I_\eta(10\,\textrm{ps})$ is given in Table~\ref{tab:tmp3}.  The
-system for simulation is $\systemsb$.
-
-\begin{figure}
-  \centering
-  \includegraphics[]{fig/result.tiny/fig-vis.eps}
-  \caption{The convergence of the integrated auto-correlation function $I_\eta(T) $. The error bars indicating 95\% confidence level are plotted with the SPME method.}
-  \label{fig:tmp4}
-\end{figure}
-
 \subsection{Damping effect}
@@
 
+It is well know that the G-factor is system size
+dependent~\cite{vanderSpoel2006origin}. Here we show the G-factor for
+both a smaller system $\systemmb$ (Fig.~\ref{fig:tmp1}) and a larger system $\systemlb$
+(Fig.~\ref{fig:tmp2}).  In the figures, the statistical uncertainty of
+the SPME method is denoted by the red error bar, while those of the
+other methods are essentially the same, so they are not presented for
+clarity.  In both the system, the RF method is qualitatively
+wrong. The results of the ZM method are consistent with SPME
+method. The lower order produces better consistency.  An artificial
+oscillation around the cut-off radius presents for $l=1$, but it is
+not obvious for $l\geq 2$.  For high order ZM (here $l=3$ is investigated),
+using larger cut-off radius can substantially improve the accuracy.
+
+The
+resulting slop is used to calculate the diffusion constant. The results are listed in Table~\ref{tab:tmp3}.
+The ZM method $l\geq 2$ is consistent with the SPME
+result, while the RF method is off.
+
+\appendix
+
+\section{The computation of benchmark quantities}
+\label{appendix:benchmark}
+
+In this section we proivde the formula used for computing the benchmark quantities. We assume that there are
+$N$ molecules in the water system. The position and configuration of each molecule are fully described
+by $\{\vect r_{3i},\vect r_{3i+1}, \vect r_{3i+2}\},\, i\in 1,\cdots,N$, and the corresponding velocities
+are denoted by $\{\vect v_{3i},\vect v_{3i+1}, \vect v_{3i+2}\},\, i\in 1,\cdots,N$. The mass of each
+atom is denoted by $m_i$.
+
+\subsection{Radial distribution function}
+The radial distribution function (RDF) $g(r)$ is a scalor function of distance $r$, which indicates the
+probability of finding two atoms of distance $r$ apart.  It is a very
+impotant equilibrium structure property, by which the X-ray scattering
+intensity and a mount of thermodynamic properties can be computed.
+In this work, we investigate the center-of-mass RDF in the water
+system.
+
+% The results are plotted in Fig.~\ref{fig:rdf}. As the order of ZM method goes higher, the precision of RDF improves. In addition, the precision of RF method is between $l=2$ and $l=3$.
+
+\subsection{Pressure}
+The pressure of the system calculated by the virial formulus:
+\begin{align}
+  P = \frac1{3V}
+  \Bigg\langle
+  \sum_{i=1}^{3N} \Big( m_i\vect v_i^2 + \vect r_i\cdot \vect F_i \Big)
+  \Bigg\rangle,
+\end{align}
+where $V$ is the volume of the system.
+
+\subsection{Chemical potential}
+
+The chemical potential is defined by
+\begin{align}
+  \mu = \Big(\frac{\partial A}{\partial N}\Big)_{V,T}
+\end{align}
+In practice the excess chemical potential $\mu^\exc$, which is the
+chemical potential abstracted by the kinetic contribution, is of
+special interest. We calculate the excess chemical potential by the
+thermodynamic integration (TI). In this approach, the interaction
+between an inserted testing molecule and the system is
+denotedd by $U_t(\lambda)$, where $\lambda$
+is a coupling parameter in range $[0,1]$.
+When $\lambda = 1$ the testing molecule is fully coupled to the system
+with the TIP3P interaction. When $\lambda=0$, the testing molecule
+is decoupled with the system.
+Therefore the
+Hamiltonian of the system is function of the coupling parameter. The
+excess chemical is calculated by the free energy difference between
+the fully coupled and decoupled states:
+\begin{align}
+  \mu^\exc = \int_0^1 \Big\langle \frac{\partial U_t(\lambda)}{\partial \lambda} \Big\rangle_\lambda d\lambda
+\end{align}
+This integral is usually calculated by numerical integration, which
+equally paritions the range of $\lambda$, simulates the system at each
+discretized $\lambda$, and computes chemical potential by trapezoidal formulus.
+Here for the sake of accuracy, 
+we adopt a two step coupling approach: firstly couple the van der Waals
+interaction of the testing particle with the rest of the system (stage vdw),
+and then couple the electrostatic interaction (stage ele).
+During stage vdw, 21 $\lambda$ values are equally
+distributed in $[0,1]$.  During stage ele, 6 $\lambda$ values are
+equally distributed in $[0,0.05]$, while the other 20 $\lambda$ values
+are equally distributed in $(0.05, 1]$. Therefore, in total 47
+simulations are performed for all $\lambda$ values.
+The free energy differences and the error estimates are calculated
+by the Bennet's acceptance ratio method (BAR)~\cite{bennett1976efficient}. 
+The simulation was
+in system $\systemla$.
+
+\subsection{Constant volume/pressure molar heat capacity}
+
+The constant volume heat capacity is defined by the infiniesimal
+increment of the energy due to an infiniesimal increment of the temperature
+at constnat volume condition: 
+\begin{align}
+  C_V = \Big(\frac{\partial E}{\partial T}\Big)_V
+\end{align}
+Since it is a extensive thermodynamics quantity, we  normalize
+it by the number molecules in the system $N$ to obtain the
+constnat volume molar heat capacity $C_{V,m} = C_V/N$.
+In the MD simlations, 
+the constant volume molar heat capacity is calculated by estimating the
+fulctuation of the Hamiltonian in an NVT simulation:
+\begin{align}
+  C_{V,m} = \frac{1}{k_BT^2 N} \langle (\mathcal H - \langle\mathcal H\rangle)^2 \rangle,
+\end{align}
+where $\mathcal H$ is the 
+Hamiltonian of the system. 
+% It is calculated in system $\systemsb$.
+
+The constant pressure molar heat capacity is defined in
+a similar way, but at constant pressure
+condition. 
+It is calculated by estimating
+the fluctuation of the enthalpy in an NPT simulation~\cite{wang2011existence}:
+\begin{align}
+  C_{p,m} = \frac{1}{k_BT^2 N} \langle ( H - \langle H\rangle)^2 \rangle,
+\end{align}
+where $ H$ is the enthalpy of the system,
+defined by $H = \mathcal H + P\mathcal V$, and $\mathcal V$ is the instantaneous volume
+of the system.
+It has been shown that the statistical error in estimating
+the fluctuations does not decrease with
+respect to the system size~\cite{milchev1986fluctuations,ferrenberg1991statistical}.
+Therefore, both constant volume and pressure molar heat capacities
+are calculated from the simulation of the smallest system: $\systemsb$.
+
+\subsection{Isothermal heat capacity}
+The isothermal heat capacity is defined
+by the normalized increment of volume due to an infiniesimal
+decrement of pressure under constant temperature condition:
+\begin{align}
+  \kappa_T = - \frac 1V \Big(\frac{\partial V}{\partial P}\Big)_T
+\end{align}
+It can be calculated by estimating the fluctuation
+of the instantaneous volume in an NPT simulation~\cite{wang2011existence}:
+\begin{align}
+  \kappa_T = \frac{1}{k_BT} \frac{\langle (\mathcal V - \langle \mathcal V\rangle)^2 \rangle}{\langle \mathcal V\rangle}.
+\end{align}
+Since it is also a fluctuation, the system $\systemsb$ is adopted for simulation.
+
+\subsection{Thermal expansion coefficient}
+The thermal expansion coefficient is defined by
+the normalized increment of volume due to an infiniesimal
+increment of temperature under the constant pressure condition:
+\begin{align}
+  \alpha_V = - \frac 1V \Big(\frac{\partial V}{\partial T}\Big)_P
+\end{align}
+It can be calculated by estimating the cross fluctuation
+of the enthalpy and instantaneous volume  in an NPT simulation:
+\begin{align}
+  \alpha_V = \frac{1}{k_BT^2\langle \mathcal V\rangle} \langle (H - \langle H\rangle)\cdot(\mathcal V - \langle \mathcal V\rangle) \rangle
+\end{align}
+The system $\systemsb$ adopted for simulation.
+
+\subsection{The dielectric constant}
+
+The dielectric constant can be estimated in a direct manner:
+\begin{align}
+  \eps = 1 + \frac{1}{3L^3 k_BT} ( \langle \vert \vect M\vert^2\rangle - \vert\langle \vect M\rangle\vert^2 )
+\end{align}
+where
+\begin{align}
+  \vect M = \sum_i\boldsymbol\mu_i = \sum_{\alpha\in i} q_\alpha\vect r_\alpha
+\end{align}
+is the total dipole moment of the system. Since it is a fluctuation, the simulated system is $\systemsb$.
+% The results are listed in Tab.~\ref{tab:tmp2}. The dielectric constant calculated in system $\systemsb$ is reported in Table.~\ref{tab:tmp3}.
+
+\subsection{Kirkwood G-factor}
+
+The Kirkwood G-factor is defined by~\cite{vanderSpoel2006origin}
+\begin{align}
+  G_k(r) =
+  \Big\langle
+  \frac 1N
+  \sum_{i=1}^N \sum_{j, r_{ij} < r}
+  \frac {\boldsymbol\mu_i \cdot \boldsymbol\mu_j}{\vert \boldsymbol\mu_i\vert \cdot \vert\boldsymbol\mu_j\vert}
+  \Big\rangle,
+\end{align}
+where $r_{ij}$ denotes the oxygen-oxygen distance between two water
+molecules.
+
+\subsection{Diffusion constant}
+The diffusion constant is calculated from the Einstein relation:
+\begin{align}
+  D = \lim_{t\rightarrow \infty}\frac {1}{6t} \langle \vert \vect r_i(t) - \vect r_i(0)\vert^2\rangle.
+\end{align}
+In practice, the mean-square-displacement $\langle\vert \vect r_i(t) - \vect
+r_i(0)\vert^2\rangle$ is calculated, then the value is linearly fitted. The system for simulation is $\systemsb$.
+
+\subsection{Viscosity}
+The viscosity is calculated from the Green-Kubo relation:
+\begin{align}
+  \eta = \frac{V}{k_BT}\int_0^\infty\langle P_{\alpha\beta}(0) P_{\alpha\beta}(t)\rangle\,dt, \quad \alpha,\beta \in \{x, y, z\}
+\end{align}
+where $\alpha$ and $\beta$ denote the directions, and
+$P_{\alpha\beta}$ denotes the off-diagonal components of the pressure
+tensor. Since we used the isotropic system setting, then it is obvious
+that $P_{xy}$, $P_{yz}$ and $P_{xz}$ are equivalent. Moreover, it has
+been pointed out that in addition $(P_{xx} - P_{yy})/2$ and $(P_{xx} -
+P_{yy})/2$ are two independent components that are equivalent to the
+first three~\cite{alfe1998first}. Therefore, the viscosity is
+calculated from the auto-correlation functions of five independent
+components, and the statistical error is estimated from the standard
+deviation of the viscosities calculated from the five components.
+
+We investigate the convergence of the integral of the auto-correlation function w.r.t.~time:
+\begin{align}
+  I_\eta(T) = \frac{V}{k_BT}\int_0^T\langle P_{\alpha\beta}(0) P_{\alpha\beta}(t)\rangle\,dt,
+\end{align}
+and plot the function $I_\eta(T) $ for all method in
+Fig.~\ref{fig:conv-vis}.  It is clear the integral for the RF method
+converges at 6~ps, while the ZM method converges only in 2~ps, which
+is consistent with the SPME result.  The value of ZM $l=1$ method is
+different from the rest ZM method an SPME result.
+The values listed  in Table~\ref{tab:tmp3} are computed with $I_\eta(10\,\textrm{ps})$.
+The
+system for simulation is $\systemsb$.
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig/result.tiny/fig-vis.eps}
+  \caption{The convergence of the integrated auto-correlation function $I_\eta(T) $. The error bars indicating 95\% confidence level are plotted with the SPME method.}
+  \label{fig:conv-vis}
+\end{figure}
+
 \newpage

### 2014-10-31 writedown/zm/paper.water/main.tex
backup adding result discussion

@@
 TIP3P~\cite{jorgensen1983comparison} point-charge water model.
+All simulations were performed by Gromacs~4.6~\cite{hess2008gromacs, pronk2013gromacs} complied by GNU C compiler with single float precision.
 The size of the systems and corresponding number of molecules used for MD simulations are summarized in Tab.~\ref{tab:tmp1}.
-The benchmark quantities were calculated in either  canonical (NVT) or isothermal-isobaric (NPT) ensemble.
-In order to equilibriate the temperature,
-the systems were coupled to either Nose-Hoover~\cite{nose1984molecular,hoover1985canonical} or Langevin thermostat (Tab.~\ref{tab:tmp1})
-at 300~K.
+The benchmark quantities were calculated in either  canonical (NVT) or isothermal-isobaric (NPT) ensemble, with equilibrium temperature $T=300$~K.
+In order to simulate at the desired temperature,
+the systems $\systemsb$ and $\systemsbp$ were coupled to either Nose-Hoover~\cite{nose1984molecular,hoover1985canonical} thermostat with time-scale $\tau_T = 1.0$~ps,
+while systems $\systemmb$, $\systemmbp$, $\systemla$, $\systemlb$ and $\systemlbp$ were coupled to Langevin thermostat with time-scale $\tau_T = 0.1$~ps.
 In the NPT simulations, the systems were further coupled
@@
 The reciprocal space
-grid spacing is 0.06~nm. The B-Spline interpolation order is 6. The
-splitting parameter is optimized by the error estimate for the SPME method~\cite{wang2010optimizing}.
+grid spacing is 0.06~nm. The B-Spline interpolation order is 6.
+These parameters are chosen to be more accurate than the Gromacs default choices (grid spacing 0.12~nm and interpolation order 4).
+The splitting parameter is optimized by the error estimate for the SPME method~\cite{wang2010optimizing}.
+The optimized real space and reciprocal space force computing errors are both $1.4\times10^{-4}$~kJ/(mol nm).
 In the simulations of the RF method, the interactoins were cut-off in the group manner,
@@
 in order to achieve higher parallel efficiency.
-The system $\sustemmb$ is simulated to investigate the size-dependency of the
+The system $\systemmb$ is simulated to investigate the size-dependency of the
 Kirkwood-G factor~\cite{vanderSpoel2006origin}.
@@
 
-The results are plotted in Fig.~\ref{fig:tmp0}. All pressure calculations are done with system $\systemla$.
+In this section we compare the benchmark quantities of the ZM method
+to the SPME method to investigate the accuracy of the former.
+The comparison to the RF method will also be mentioned, to show that
+the ZM is a promising replacement of the RF method.
+
+\subsection{Thermodynamic properties}
+
 \begin{figure}
@@
   \caption{The pressure convergence with respect to the cut-off radius.
-    For ZM method, the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
+    The ZM methods with order from 1 to 4 are compared with the RF. 
+    The splitting parameter of ZM method is set to be $\alpha = 0.00\,\textrm{nm}^{-1}$.
+    The black solid line indicates the maganitude  of the correct pressure: 1~Bar.
+    The error bars present the statistical uncertainty at 95\% confidence level.
   }
-  \label{fig:tmp0}
+  \label{fig:pres-comp}
 \end{figure}
+
+The equilibrium density of the system was determined by an NPT SPME
+simulation.  In the NVT simulation the SPME electrostatic, computed
+pressure ($-0.4\pm 1.5$~Bar) is reproducing the target pressure of
+1.0~Bar.  The accuracy of ZM method, can be investigate by checking if
+the NVT pressure is consistent with the target pressure.  In
+Fig.~\ref{fig:pres-comp}, the pressure calculated by ZM method of
+order $l=1,2,3$ and 4 are plotted against the cut-off radius.
+All the  simulations are done with system $\systemla$.
+It is concluded from the Figure that all ZM methods converges to the
+target pressure at large enough cut-off radius.
+ZM $l=1$ converges from an under-estimate of the pressure, while ZM $l=2,3$ and 4 converges
+from an over-estimate.
+The higher order of ZM presents an larger error in the pressure calculation than
+the lower order ZM method. The ZM method is also compared with
+the RF method using the experimental dielectric constant $\varepsilon_{\textrm{rf}} = 80$, 
+from which it is concluded that the accuracy of ZM in pressure calculation is much higher
+than the RF method.
+It should be noted that even with the largest system of 13824 water molecules,
+the fluctuation (measured by standard deviation) of the pressure is roughly 100~Bar, which means that it is
+very difficult achieve very accurate estimate for this quantity. In practice a pressure error of 20~Bar is
+still acceptable.
 
@@
   \end{tabular*}
-  \label{tab:tmp3}
+  \label{tab:thermo}
 \end{sidewaystable}
+
+Ohter thermodynamic quantities including the chemical potential,
+constant volume/pressure molar heat capacity, isothermal
+compressibility and heat expansion coefficient are compared in
+Tab.~\ref{tab:thermo}.
+The ZM results are in good consistency with the SPME results, and out-perform
+the RF method.
+
+\recheck{Discussion of the energy correction in the chemical potential calculation. TO be added later}
 
@@
 %   \centering
-%   \caption{The constant pressure molar heat capacity $C_{v,m}$, isothermal compressibility $\kappa_T$ and
-%     thermal expansion coefficient $\alpha$
-%     calculated by different methods.    
-%     The parenthesises in the last column show the statistical uncertainty
-%     at the confidence level of 95~\%.
-%     The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
-%   }
-%   \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}cccc ccc}\hline\hline
-%     Method      &   $r_c$ [nm] &    $l$ & $\alpha$ [$\textrm{nm}^{-1}$]     &  $\kappa_T$ [$10^{-10}\textrm{m}^2/\textrm{N}$] & $C_{p,m}$ [J/(mol K)] & $\alpha$ [$10^{-3}\textrm{K}^{-1}$]\\\hline
-%     SPME        &  1.9     &       -- &    & 5.941 (0.050)               &79.18 (0.94)           &1.026 (0.016)          \\
-%     RF          &  1.2     & --       &    & \textbf{6.508} (0.058)      &\textbf{82.34} (0.95)  &\textbf{1.149} (0.018) \\\hline
-%     ZM          &  1.2     &       1  & 0.0& 5.872 (0.050)               &78.91 (0.95)           &1.009 (0.018)          \\
-%     ZM          &  1.2     &       1  & 0.5& 5.920 (0.050)               &78.90 (0.92)           &\textbf{1.003} (0.016) \\
-%     ZM          &  1.2     &       1  & 1.0& 5.946 (0.050)               &78.37 (0.92)           &1.008 (0.016)          \\
-%     ZM          &  1.2     &       1  & 1.5& 5.974 (0.050)               &80.23 (0.86)           &1.040 (0.017)          \\
-%     ZM          &  1.2     &       1  & 2.0& \textbf{6.052} (0.051)      &79.41 (0.91)           &1.045 (0.016)          \\\hline
-%     ZM          &  1.2     &       2  & 0.0& 5.952 (0.051)               &79.70 (0.96)           &1.033 (0.016)          \\
-%     ZM          &  1.2     &       3  & 0.0& 5.991 (0.050)               &79.49 (1.01)           &1.024 (0.019)          \\
-%     ZM          &  1.2     &       4  & 0.0& 5.961 (0.054)               &79.46 (0.98)           &1.034 (0.017)          \\
+%   \caption{A list of the dielectric constant calculated for different systems by different methods.
+%     The parameters are provided. The parenthesises in the last column show the statistical uncertainty
+%     of the last two digits up to the confidence level of 95~\%.}
+%   \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}cccc rr}\hline\hline
+%     System & Method      &       $\alpha$ [$\textrm{nm}^{-1}$] & $r_c$ [nm] &    $l$     &       $\eps$ \\\hline
+%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       1       &       99.8 (3.8)\\ 
+%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       2       &       95.2 (3.6)\\ 
+%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       3       &       93.9 (3.7)\\ 
+%     $\systemmb$  &       ZM          &       0.00    &       1.5     &       3       &       98.7 (3.8)\\ 
+%     $\systemmb$  &       ZM          &       0.00    &       1.8     &       3       &      100.7 (3.6)\\ 
+%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       4       &       94.7 (3.6)\\
+%     $\systemmb$   & SPME          & 2.09  & 1.9   &       --      &       98.8 (4.0) \\
+%     $\systemmb$  & RF             & --  & 1.2 & -- & 60.6   (1.7) \\
+%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       1       &       97.1 (3.2)\\ 
+%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       2       &       95.6 (3.5)\\ 
+%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       3       &       95.8 (4.6)\\ 
+%     $\systemlb$  &       ZM          &       0.00    &       1.5     &       3       &       98.0 (3.3)\\ 
+%     $\systemlb$  &       ZM          &       0.00    &       1.8     &       3       &       98.9 (4.2)\\ 
+%     $\systemlb$  &       ZM          &       0.00    &       2.1     &       3       &       98.8 (3.9)\\ 
+%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       4       &       97.8 (3.9)\\
+%    $\systemlb$   & SPME          & 2.09  & 1.9   &       --      &       98.7 (3.5) \\
+%     $\systemlb$  & RF             & --  & 1.2 & -- & 60.8   (2.0) \\
 %     \hline\hline
 %   \end{tabular*}
-%   \label{tab:tmp3a}
+%   \label{tab:tmp2}
 % \end{table}
 
-% \begin{table}
-%   \centering
-%   \caption{The excess chemical potential $\mu^\exc$, constant volume molar heat capacity $C_{v,m}$, dielectric constant $\eps$, diffusion constant $D$ and viscosity $\eta$
-%     calculated by different methods.    
-%     The parenthesises in the last column show the statistical uncertainty
-%     at the confidence level of 95~\%.
-%     The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
-%   }
-%   \begin{tabular*}{0.95\textwidth}{@{\extracolsep{\fill}}cccc ccccc}\hline\hline
-%     Method      &   $r_c$ &    $l$ & $\alpha$  & $\mu^\exc$  &$C_{v,m}$ &  $\eps$ & $D$ &  $\eta$ \\
-%                 &    [nm] &        & [$\textrm{nm}^{-1}$] &   [kJ/mol] &[J/(mol K)] & (Sys.~$\systemsb$) & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
-%     % Method      &   $r_c$ [nm] &    $l$      & $\mu^\exc$ [kJ/mol] &$C_{v,m}$ [J/(mol K)] & $\eps$ (Sys.~$\systemsb$) & $D$ [$10^{-9}\textrm{m}^2/\textrm{s}$] &  $\eta$ [$10^{-3}\textrm{Pa}\cdot\textrm{s}$] \\\hline
-%     SPME        &1.9 & -- &    & $-26.08$ (0.24) & 72.21 (0.97)  & 97.6 (3.4)  & 5.86 (0.07)   & 0.315 (0.007)\\
-%     RF          &1.2 & -- &--  & $-26.03$ (0.32) & 72.28 (0.81)  & \textbf{59.4} (1.3)  & \textbf{6.27} (0.19)   & \textbf{0.449} (0.020)\\\hline
-%     ZM          &1.2 & 1  &0.0 & $-26.22$ (0.30) & 71.75 (0.89)  & 95.5 (2.4)  & \textbf{5.53} (0.11)   & \textbf{0.346} (0.006)\\ 
-%     ZM          &1.2 & 1  &0.5 & $-26.36$ (0.30) & 72.25 (0.78)  & 97.1 (2.2)  & \textbf{5.52} (0.25)   & \textbf{0.339} (0.008)\\ 
-%     ZM          &1.2 & 1  &1.0 & $-26.01$ (0.22) & 72.44 (0.84)  & 96.2 (2.3)  &        {5.78} (0.25)   & \textbf{0.330} (0.011)\\ 
-%     ZM          &1.2 & 1  &1.5 & $-26.03$ (0.24) & 71.31 (0.78)  & 99.1 (2.5)  & \textbf{5.71} (0.09)   &        {0.312} (0.008)\\ 
-%     ZM          &1.2 & 1  &2.0 & $-26.14$ (0.34) & 71.27 (0.78)  & 95.9 (2.5)  &        {5.90} (0.04)   &        {0.307} (0.007)\\ \hline
-%     ZM          &1.2 & 2  &0.0 & $-26.24$ (0.24) & 71.53 (0.88)  & 95.4 (2.5)  & 5.82 (0.27)   & 0.318 (0.012)\\ 
-%     ZM          &1.2 & 3  &0.0 & $-{26.18}$ (0.20) & 71.58 (0.88)  & 96.0 (2.7)  & 5.79 (0.09)   & 0.321 (0.008)\\ 
-%     ZM          &1.2 & 4  &0.0 & $-{26.01}$ (0.26) & 71.07 (0.84)  & 99.7 (2.2)  & 5.89 (0.09)   & 0.318 (0.013)\\
-%     \hline\hline
-%   \end{tabular*}
-%   \label{tab:tmp3}
-% \end{table}
-    % SPME        &         1.9     &       --      & 1.67049 (0.00014)     $-26.08$ (0.24) & 72.21 (0.97)  & 97.6 (3.4)  & 5.86 (0.07)   & 0.315 (0.007)\\
-    % RF          &         1.2     & --            & 1.66733 (0.00016)      $-26.03$ (0.32) & 72.28 (0.81)  & \textbf{59.4} (1.3)  & \textbf{6.27} (0.19)   & \textbf{0.449} (0.020)\\
-    % ZM          &         1.2     &       1       & 1.67052 (0.00022)     $-26.22$ (0.30) & 71.75 (0.89)  & 95.5 (2.4)  & \textbf{5.53} (0.11)   & \textbf{0.346} (0.006)\\ 
-    % ZM          &         1.2     &       2       & 1.67029 (0.00013)     $-26.24$ (0.24) & 71.53 (0.88)  & 95.4 (2.5)  & 5.82 (0.27)   & 0.318 (0.012)\\ 
-    % ZM          &         1.2     &       3       & 1.67024 (0.00018)     $-{26.18}$ (0.20) & 71.58 (0.88)  & 96.0 (2.7)  & 5.79 (0.09)   & 0.321 (0.008)\\ 
-    % ZM          &         1.2     &       4       & 1.67031 (0.00010)     $-{26.01}$ (0.26) & 71.07 (0.84)  & 99.7 (2.2)  & 5.89 (0.09)   & 0.318 (0.013)\\
-% \subsubsection{Hydrogen bonding}
-% We count
-
-\begin{table}
-  \centering
-  \caption{A list of the dielectric constant calculated for different systems by different methods.
-    The parameters are provided. The parenthesises in the last column show the statistical uncertainty
-    of the last two digits up to the confidence level of 95~\%.}
-  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}cccc rr}\hline\hline
-    System & Method      &       $\alpha$ [$\textrm{nm}^{-1}$] & $r_c$ [nm] &    $l$     &       $\eps$ \\\hline
-    $\systemmb$  &       ZM          &       0.00    &       1.2     &       1       &       99.8 (3.8)\\ 
-    $\systemmb$  &       ZM          &       0.00    &       1.2     &       2       &       95.2 (3.6)\\ 
-    $\systemmb$  &       ZM          &       0.00    &       1.2     &       3       &       93.9 (3.7)\\ 
-    $\systemmb$  &       ZM          &       0.00    &       1.5     &       3       &       98.7 (3.8)\\ 
-    $\systemmb$  &       ZM          &       0.00    &       1.8     &       3       &      100.7 (3.6)\\ 
-    $\systemmb$  &       ZM          &       0.00    &       1.2     &       4       &       94.7 (3.6)\\
-    $\systemmb$   & SPME          & 2.09  & 1.9   &       --      &       98.8 (4.0) \\
-    $\systemmb$  & RF             & --  & 1.2 & -- & 60.6   (1.7) \\
-    $\systemlb$  &       ZM          &       0.00    &       1.2     &       1       &       97.1 (3.2)\\ 
-    $\systemlb$  &       ZM          &       0.00    &       1.2     &       2       &       95.6 (3.5)\\ 
-    $\systemlb$  &       ZM          &       0.00    &       1.2     &       3       &       95.8 (4.6)\\ 
-    $\systemlb$  &       ZM          &       0.00    &       1.5     &       3       &       98.0 (3.3)\\ 
-    $\systemlb$  &       ZM          &       0.00    &       1.8     &       3       &       98.9 (4.2)\\ 
-    $\systemlb$  &       ZM          &       0.00    &       2.1     &       3       &       98.8 (3.9)\\ 
-    $\systemlb$  &       ZM          &       0.00    &       1.2     &       4       &       97.8 (3.9)\\
-   $\systemlb$   & SPME          & 2.09  & 1.9   &       --      &       98.7 (3.5) \\
-    $\systemlb$  & RF             & --  & 1.2 & -- & 60.8   (2.0) \\
-    \hline\hline
-  \end{tabular*}
-  \label{tab:tmp2}
-\end{table}
+\subsection{Radial distribution function}
 
@@
   \includegraphics[]{fig/result.nvt/fig-rdf.eps}  
-  \caption{The RDF of different method. The insert is a zoom-in of range 0.9 -- 1.5~nm. In the insert, the position of the cut-off (1.2~nm) is indicated by a vertical black line.}
+  \caption{The comparison of the center-of-mass radial distribution functions
+    calculated by SPME, ZM and RF methods. The insert is a zoom-in of
+    range 0.9 -- 1.5~nm. In the insert, the position of the cut-off
+    (1.2~nm) is indicated by a vertical black line.
+    For ZM method, the splitting parameter $\alpha$ was set to 0.
+  }
   \label{fig:rdf}
 \end{figure}
+
+We plot in Fig.~\ref{fig:rdf} the center-of-mass radial distribution functions (RDFs) of TIP3P water
+calculated by the SPME, ZM ($l=1,2,3$ and 4) and RF method.  The RDFs
+are computed from NVT simulations of system $\systemlb$. It is
+observed from the Figure that the ZM RDFs are consistency very well
+with the SPME RDF, except an artificial oscillation around the
+cut-off radius. Higher orders of ZM method present lower oscillation, and when
+$l\geq 3$, the oscillation is almost negligible. Therefore, for the sake
+of high accuracy RDF computation, the ZM method of order at least 3 should be used.
+
+\recheck{Shall we comment here on the fact that group cut-off produces smoother RDF?}
+
+\subsection{Dielectric quantities}
 
@@
 The
-resulting slop is used to calculate the diffusion constant. The results are listed in Table~\ref{tab:tmp3}.
+resulting slop is used to calculate the diffusion constant. The results are listed in Table~\ref{tab:thermo}.
 The ZM method $l\geq 2$ is consistent with the SPME
@@
 is the total dipole moment of the system. Since it is a fluctuation, the simulated system is $\systemsb$.
-% The results are listed in Tab.~\ref{tab:tmp2}. The dielectric constant calculated in system $\systemsb$ is reported in Table.~\ref{tab:tmp3}.
+% The results are listed in Tab.~\ref{tab:tmp2}. The dielectric constant calculated in system $\systemsb$ is reported in Table.~\ref{tab:thermo}.
 
@@
 different from the rest ZM method an SPME result.
-The values listed  in Table~\ref{tab:tmp3} are computed with $I_\eta(10\,\textrm{ps})$.
+The values listed  in Table~\ref{tab:thermo} are computed with $I_\eta(10\,\textrm{ps})$.
 The

### 2014-11-03 writedown/zm/paper.water/main.tex
backup the work

@@
 target pressure at large enough cut-off radius.
-ZM $l=1$ converges from an under-estimate of the pressure, while ZM $l=2,3$ and 4 converges
-from an over-estimate.
-The higher order of ZM presents an larger error in the pressure calculation than
-the lower order ZM method. The ZM method is also compared with
+In general, the higher order of ZM presents an larger error in the pressure calculation than
+the lower order ZM method.
+Higher order are also more sensitve in the  cut-off radius dependency.
+ZM $l=1$ tends to under-estimate the pressure, while ZM $l=2,3$ and 4 tends to over-estimate.
+The ZM method is also compared with
 the RF method using the experimental dielectric constant $\varepsilon_{\textrm{rf}} = 80$, 
@@
 still acceptable.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l1.eps}
+  \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l2.eps}\\
+  \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l3.eps}
+  \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l4.eps}
+  \caption{The pressure convergence with respect to the cut-off radius
+    for ZM methods with  splitting parameter from $0.0$ to $2.0\,\textrm{nm}^{-1}$.
+    From left to right, up to down presensts the ZM method of order 1 to 4.
+    The black solid line indicates the maganitude  of the correct pressure: 1~Bar.
+    The error bars present the statistical uncertainty at 95\% confidence level.
+  }
+  \label{fig:pres-l1}
+\end{figure}
+
+The effect of using different splitting parameter on the convergence
+of the pressure is investigate in Fig.~\ref{fig:pres-l1}.
+In general, the higher order indicates less significant dependency on the splitting parameter.
+In the case of $l=1$, the splitting parameter 0.0 is consistent with  $0.5\,\textrm{nm}^{-1}$, and
+by using higher splitting parameter, the pressure shifts to the higher pressure side.
+For $l=2,3$ and 4, the convergence is not sensitive to $\alpha$ upto  $1.0\,\textrm{nm}^{-1}$.
+More importantly, for all orders,
+the pressure does not converges to the desired value 1~Bar by using $\alpha = 1.5$ or $2.0\,\textrm{nm}^{-1}$.
 
@@
 
-Ohter thermodynamic quantities including the chemical potential,
+Other thermodynamic quantities including the chemical potential,
 constant volume/pressure molar heat capacity, isothermal
@@
 the RF method.
-
+The splitting parameter does not have significant influence on these thermodynamic quantities.
 \recheck{Discussion of the energy correction in the chemical potential calculation. TO be added later}
@@
     (1.2~nm) is indicated by a vertical black line.
-    For ZM method, the splitting parameter $\alpha$ was set to 0.
+    For ZM method, the splitting parameter $\alpha$ was set to 0.0~$\textrm{nm}^{-1}$.
   }
@@
 
-\recheck{Shall we comment here on the fact that group cut-off produces smoother RDF?}
+\recheck{Shall we comment here on the fact that group cut-off produces smoother RDF? Add figures in Supplementary material}
+
+\begin{figure}
+  \centering
+  \includegraphics[]{fig/result.nvt/fig-rdf-l1-damp.eps}  
+  \caption{
+    The splitting parameter dependency in calculating the center-of-mass RDF for
+    ZM method $l=1$. The insert is a zoom-in of
+    range 0.9 -- 1.5~nm. In the insert, the position of the cut-off
+    (1.2~nm) is indicated by a vertical black line.
+  }
+  \label{fig:rdf-damp}
+\end{figure}
+
+The artificial oscillation can be substantially improved by using larger splitting parameter $\alpha$.
+In Fig.~\ref{fig:rdf-damp} presents the RDF of ZM $l=1$ with splitting parameter from 0.0 to 2.0~$\textrm{nm}^{-1}$.
+A clear trend of better RDF by using larger splitting parameter is observed.
+At $\alpha = 2.0\ \textrm{nm}^{-1}$ the RDF is almost overlapping with the SPME result.
+
+\recheck{If we want $l=2,3$, add in supplementary material..}
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[]{fig/result.nvt.small/fig-gkr-small.eps}
-  \includegraphics[]{fig/result.nvt.small/fig-gkr-small-conv.eps}
-  \includegraphics[]{fig/result.nvt.small/fig-eps-t-3000.eps}
-  \includegraphics[]{fig/result.nvt.small/fig-eps-t-zm3-3000.eps}
-  \includegraphics[]{fig/result.nvt.small/fig-eps-t-10000.eps}
-  \includegraphics[]{fig/result.nvt.small/fig-eps-t-zm3-10000.eps}
-  \caption{The Kirkwood G-factor calculated for system $\systemmb$.
-    % The result of different methods are compared in the left plot.
-    For all ZM methods the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
-    In the left plot the cut-off radius for all orders is set to $1.2$~nm, while
-    in the right plot, only the order $l=3$ is considered and different cut-off radii are compared.
-    The RF method uses a cut-off radius of 1.2~nm, and dielectric constant of 80.
-    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red bar.
-  }
-  \label{fig:tmp1}
-\end{figure}
+The dielectric constant computed by ZM method at different orders are listed in Tab.~\ref{tab:thermo},
+and are consistent with the SPME computed results. In contrast, the RF method has poor accuracy in
+the dielectric constant.
 
@@
   \includegraphics[]{fig/result.nvt/fig-gkr.eps}
-  \includegraphics[]{fig/result.nvt/fig-gkr-conv.eps}
-  \includegraphics[]{fig/result.nvt/fig-eps-t-3000.eps}
-  \includegraphics[]{fig/result.nvt/fig-eps-t-zm3-3000.eps}
-  \caption{The Kirkwood G-factor calculated for system $\systemlb$.
-    % The result of different methods are compared in the left plot.
-    For all ZM methods the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
-    In the left plot the cut-off radius for all orders is set to $1.2$~nm, while
-    in the right plot, only the order $l=3$ is considered and different cut-off radii are compared.
-    The RF method uses a cut-off radius of 1.2~nm, and dielectric constant of 80.
-    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red bar.
+  \includegraphics[]{fig/result.nvt.small/fig-gkr-small.eps}
+  \caption{The Kirkwood G-factor calculated for system $\systemlb$ (a) and $\systemmb$ (b).
+    ZM method of orders $l=1,2,3$ and 4 with the cut-off 1.2~nm and splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$ are plotted.
+    The RF method is shown as an comparison, which uses a cut-off radius of 1.2~nm and dielectric constant of 80.
+    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red error bars.
   }
-  \label{fig:tmp2}
+  \label{fig:gkr}
 \end{figure}
+
+As a measurement of the dipole correlation as a function of molecular distance, the Kirkwood-G factor
+is an important qnantity of the water system.
+It is well know that the G-factor is system size
+dependent~\cite{vanderSpoel2006origin}, therefore we show the G-factor for
+both  system $\systemlb$ in FIg.~\ref{fig:gkr}~(a) and a smaller system $\systemmb$
+Fig.~\ref{fig:gkr} (b).  In the figures, the statistical uncertainty of
+the SPME method is denoted by the red error bars. The statistical uncertainties of the
+other methods are essentially of the same size as the SPME, so they are not presented in the figure for
+clarity.  In the figure, ZM adaopts a cut-off radius of 1.2~nm and a splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
+RF uses a cut-off 1.2~nm and a dielectric constant of 80.
+
+In both the system, the RF method is qualitatively
+wrong. The accuracy of the ZM method is much higher than RF.
+In the system of larger size ($\systemlb$), the ZM mehtod of $l=1$ is in consistency with the SPME mehtod. However
+order $l=2,3$ and 4  present less but still acceptable accuracy.
+In the system of smaller size ($\systemmb$), ZM method of all orders are consistent with the SPME result.
+This means ZM performs better in calculated Kirkwood-G factor for smaller systems.
+In both systems, ZM $l=1$ presents  an artificial
+oscillation around the cut-off radius (1.2~nm), while this oscillation is
+not obvious for $l\geq 2$.
 
@@
   \centering
-  \includegraphics[]{fig/result.nvt/fig-gkr-10000.eps}
-  \includegraphics[]{fig/result.nvt/fig-gkr-conv-10000.eps}
-  \includegraphics[]{fig/result.nvt/fig-eps-t-10000.eps}
-  \includegraphics[]{fig/result.nvt/fig-eps-t-zm3-10000.eps}
-  \caption{The Kirkwood G-factor calculated for system $\systemlb$. Equilibriation time is 10~ns, and the production simulation time is 10~ns.
-    % The result of different methods are compared in the left plot.
-    For all ZM methods the splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
-    In the left plot the cut-off radius for all orders is set to $1.2$~nm, while
-    in the right plot, only the order $l=3$ is considered and different cut-off radii are compared.
-    The RF method uses a cut-off radius of 1.2~nm, and dielectric constant of 80.
-    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red bar.
+  \includegraphics[]{fig/result.nvt/fig-gkr-conv.eps}
+  \includegraphics[]{fig/result.nvt/fig-gkr-l3-damp.eps} 
+  \caption{
+    The cut-off (a) and spliting parameter (b) dependency in calculating the Kirkwood-G factor.
+    The order of ZM method is $l=3$. In plot (a) the spliting parameter is $\alpha = 0.00\,\textrm{nm}^{-1}$.
+    in plot (b) the cut-off radius is 1.2~nm.
+    The statistical uncertainty is presented at 95~\% confidence level with the  error bars.
   }
-  \label{fig:tmp3}
+  \label{fig:gkr-conv}
 \end{figure}
 
-\subsection{Damping effect}
+The cut-off and spliting parameter dependency in calculating the Kirkwood-G factor
+is presented in Fig.~\ref{fig:gkr-conv}  for ZM method of order $l=3$. With out surprising,
+the Kirkwood-G factor converges to the SPME result when using increasing cut-off radius. 
+However, unlike the case of calculating RDF, the accuracy Kirkwood-G factor is not improved
+with increasing spliting parameter. This fact should be noticed in choosing parameters for
+high accuracy calcualtion of Kirkwood-G factor.
 
-In this section we investigate the damping effect. The pressure is plotted as a function of  the cut-off radius is plotted for different choices of
-the splitting parameter $\alpha$ in Fig.~\ref{fig:damp-pres}. The system for the simulation was $L_0$.
-\begin{figure}
-  \centering
-  \includegraphics[width=0.49\textwidth]{fig/nvt.pressure.1/pressure-l1.eps}
-  \includegraphics[width=0.49\textwidth]{fig/nvt.pressure.1/pressure-l2.eps}\\
-  \includegraphics[width=0.49\textwidth]{fig/nvt.pressure.1/pressure-l3.eps}
-  \includegraphics[width=0.49\textwidth]{fig/nvt.pressure.1/pressure-l4.eps}
-  \caption{The pressure convergence with respect to the cut-off radius.
-    For ZM method, different splitting parameter $\alpha$ (in unit of $\textrm{nm}^{-1}$) are shown for different orders:  $l=1$, 2, 4, and 4.
-  }
-  \label{fig:damp-pres}
-\end{figure}
+\subsection{Dynamical quantities}
 
-The convergence of the integrated auto-correlation function $I_\eta(T) $ is shown in Fig.~\ref{fig:damp-vis-l1}.
-\begin{figure}
-  \centering
-  \includegraphics[]{fig/result.tiny/fig-vis-l1-damp.eps}
-  \caption{The convergence of the integrated auto-correlation function $I_\eta(T) $.
+The dynamical quantities, diffusion constant and viscosity, are listed in Tab.~\ref{tab:thermo}.
+The ZM method of order $l\geq 2$ can almost perfactly reproduce the SPME dynamical quantities.
+The ZM order $l=1$ is of less accurate than higher orders, but is more accurate than the RF.
+Using larger spliting parameters improves the accuracy, and the value $\alpha= 2.0\ \textrm{nm}^{-1}$ is
+sugguested for calculating the dynamical quantities.
+
+% \subsection{Damping effect}
+
+% The convergence of the integrated auto-correlation function $I_\eta(T) $ is shown in Fig.~\ref{fig:damp-vis-l1}.
+% \begin{figure}
+%   \centering
+%   \includegraphics[]{fig/result.tiny/fig-vis-l1-damp.eps}
+%   \caption{The convergence of the integrated auto-correlation function $I_\eta(T) $.
 The error bars indicating 95\% confidence level are plotted with the SPME method.
 The different splitting parameters for ZM $l=1$ method are plotted}
-  \label{fig:damp-vis-l1}
-\end{figure}
+%   \label{fig:damp-vis-l1}
+% \end{figure}
 
-The RDF is plotted for different splitting parameters $\alpha$ for ZM $l=2$ and 3 in Fig.~\ref{fig:damp-rdf-l23}. Higher $\alpha$ reproduces the RDF better.
-The system was $L_1$.
-\begin{figure}[]
-  \centering
-  \includegraphics[width=0.49\textwidth]{fig/result.nvt/fig-rdf-l2-damp.eps}
-  \includegraphics[width=0.49\textwidth]{fig/result.nvt/fig-rdf-l3-damp.eps}
-  \caption{Radial distribution function for different splitting parameters $\alpha$ for ZM $l=2$ (left) and $l=3$ (right).}
-  \label{fig:damp-rdf-l23}
-\end{figure}
+% The RDF is plotted for different splitting parameters $\alpha$ for ZM $l=2$ and 3 in Fig.~\ref{fig:damp-rdf-l23}. Higher $\alpha$ reproduces the RDF better.
+% The system was $L_1$.
+% \begin{figure}[]
+%   \centering
+%   \includegraphics[width=0.49\textwidth]{fig/result.nvt/fig-rdf-l2-damp.eps}
+%   \includegraphics[width=0.49\textwidth]{fig/result.nvt/fig-rdf-l3-damp.eps}
+%   \caption{Radial distribution function for different splitting parameters $\alpha$ for ZM $l=2$ (left) and $l=3$ (right).}
+%   \label{fig:damp-rdf-l23}
+% \end{figure}
 
-The Kirkwood G-factor is plotted for different splitting parameters $\alpha$ for ZM $l=2$ and 3 in Fig.~\ref{fig:damp-gkr-l23}. 
-The system was $L_1$.
-\begin{figure}[]
-  \centering
-  \includegraphics[width=0.49\textwidth]{fig/result.nvt/fig-gkr-l2-damp.eps}
-  \includegraphics[width=0.49\textwidth]{fig/result.nvt/fig-gkr-l3-damp.eps}
-  \caption{Kirkwood G-factor for different splitting parameters $\alpha$ for ZM $l=2$ (left) and 3 (right).}
-  \label{fig:damp-gkr-l23}
-\end{figure}
-
-It is well know that the G-factor is system size
-dependent~\cite{vanderSpoel2006origin}. Here we show the G-factor for
-both a smaller system $\systemmb$ (Fig.~\ref{fig:tmp1}) and a larger system $\systemlb$
-(Fig.~\ref{fig:tmp2}).  In the figures, the statistical uncertainty of
-the SPME method is denoted by the red error bar, while those of the
-other methods are essentially the same, so they are not presented for
-clarity.  In both the system, the RF method is qualitatively
-wrong. The results of the ZM method are consistent with SPME
-method. The lower order produces better consistency.  An artificial
-oscillation around the cut-off radius presents for $l=1$, but it is
-not obvious for $l\geq 2$.  For high order ZM (here $l=3$ is investigated),
-using larger cut-off radius can substantially improve the accuracy.
-
-The
-resulting slop is used to calculate the diffusion constant. The results are listed in Table~\ref{tab:thermo}.
-The ZM method $l\geq 2$ is consistent with the SPME
-result, while the RF method is off.
+% The
+% resulting slop is used to calculate the diffusion constant. The results are listed in Table~\ref{tab:thermo}.
+% The ZM method $l\geq 2$ is consistent with the SPME
+% result, while the RF method is off.
 
@@
 In this work, we investigate the center-of-mass RDF in the water
-system.
+system. The RDFs presented in the main text were computed in system $\systemlb$.
 
@@
 \end{align}
-where $V$ is the volume of the system.
+where $V$ is the volume of the system. The presented pressures were computed in system $\systemla$.
 
@@
 \begin{align}
-  \mu = \Big(\frac{\partial A}{\partial N}\Big)_{V,T}
+  \mu = \Big(\frac{\partial A}{\partial N}\Big)_{V,T},
 \end{align}
+where $A$ is the Helmholtz free energy.
 In practice the excess chemical potential $\mu^\exc$, which is the
@@
 by the Bennet's acceptance ratio method (BAR)~\cite{bennett1976efficient}. 
-The simulation was
-in system $\systemla$.
+The simulations were performed with system $\systemla$.
 
@@
 Therefore, both constant volume and pressure molar heat capacities
-are calculated from the simulation of the smallest system: $\systemsb$.
+were calculated from the simulation of the smallest system: $\systemsb$.
 
@@
 \end{align}
-Since it is also a fluctuation, the system $\systemsb$ is adopted for simulation.
+Since it is also a fluctuation, the system $\systemsb$ was adopted for simulation.
 
@@
 \end{align}
-The system $\systemsb$ adopted for simulation.
+The system $\systemsb$ was adopted for simulation.
 
@@
 \end{align}
-is the total dipole moment of the system. Since it is a fluctuation, the simulated system is $\systemsb$.
+is the total dipole moment of the system. Since it is a fluctuation, the simulated system was $\systemsb$.
 % The results are listed in Tab.~\ref{tab:tmp2}. The dielectric constant calculated in system $\systemsb$ is reported in Table.~\ref{tab:thermo}.
@@
 where $r_{ij}$ denotes the oxygen-oxygen distance between two water
-molecules.
+molecules.  The system for computing this quantity is $\systemlb$.
 
@@
 In practice, the mean-square-displacement $\langle\vert \vect r_i(t) - \vect
-r_i(0)\vert^2\rangle$ is calculated, then the value is linearly fitted. The system for simulation is $\systemsb$.
+r_i(0)\vert^2\rangle$ is calculated, then the value is linearly fitted. The system for simulation was $\systemsb$.
 
@@
 The
-system for simulation is $\systemsb$.
+system for simulation was $\systemsb$.
 

### 2014-11-03 writedown/zm/paper.water/main.tex
spell checking

@@
 
-Zero-Multiple method, an overview, achievements, sucessful applications.
+Zero-Multiple method, an overview, achievements, successful applications.
 
-The propuse of this work: Extensive and strict tests investigating the reliablility of Zero-Multiple method in water simulation, which is the most important solvent.
+The purpose of this work: Extensive and strict tests investigating the reliability of Zero-Multiple method in water simulation, which is the most important solvent.
 
@@
 
-A short mention of the group cut-off v.s.~the atom cut-off method. (will discuss the implmentation in gromacs later)
+A short mention of the group cut-off v.s.~the atom cut-off method. (will discuss the implementation in gromacs later)
 
@@
 of \emph{benchmark quantities}.  This set covers a broad range of
-water propertis that are of general interest, and includes the
+water properties that are of general interest, and includes the
 structure property (radial distribution function), the thermodynamic
@@
 they are modified in a shell of $0.05$~nm width near the cut-off sphere by the Gromacs ``\texttt{shift}'' method.
+The ZM method was implemented in Gromacs with the tabulated electrostatic interaction (Home-made codes for generating the interaction tables).
 The short-range part of SPME method is also smoothed in a shell of $0.05$~nm width  by the Gromacs ``\texttt{pme-switch}'' method.
 The reciprocal space
-grid spacing is 0.06~nm. The B-Spline interpolation order is 6.
+grid spacing is set to 0.06~nm, with B-Spline interpolation order of 6.
 These parameters are chosen to be more accurate than the Gromacs default choices (grid spacing 0.12~nm and interpolation order 4).
-The splitting parameter is optimized by the error estimate for the SPME method~\cite{wang2010optimizing}.
-The optimized real space and reciprocal space force computing errors are both $1.4\times10^{-4}$~kJ/(mol nm).
-In the simulations of the RF method, the interactoins were cut-off in the group manner,
+The splitting parameter is optimized by the error estimate for the SPME method, which is implemented in Gromacs by tool ``\texttt{g\_pme\_error}''~\cite{wang2010optimizing}.
+The optimized real space and reciprocal space force computing errors were equally distributed as $1.4\times10^{-4}$~kJ/(mol nm).
+In the simulations of the RF method, the interactions were cut-off in the group manner,
 so the radius for neighbor list building is set identical to the cut-off radius.
@@
     The splitting parameter of ZM method is set to be $\alpha = 0.00\,\textrm{nm}^{-1}$.
-    The black solid line indicates the maganitude  of the correct pressure: 1~Bar.
+    The black solid line indicates the magnitude  of the correct pressure: 1~Bar.
     The error bars present the statistical uncertainty at 95\% confidence level.
@@
 the lower order ZM method.
-Higher order are also more sensitve in the  cut-off radius dependency.
+Higher order are also more sensitive in the  cut-off radius dependency.
 ZM $l=1$ tends to under-estimate the pressure, while ZM $l=2,3$ and 4 tends to over-estimate.
@@
     for ZM methods with  splitting parameter from $0.0$ to $2.0\,\textrm{nm}^{-1}$.
-    From left to right, up to down presensts the ZM method of order 1 to 4.
-    The black solid line indicates the maganitude  of the correct pressure: 1~Bar.
+    From left to right, up to down presents the ZM method of order 1 to 4.
+    The black solid line indicates the magnitude  of the correct pressure: 1~Bar.
     The error bars present the statistical uncertainty at 95\% confidence level.
@@
 by using higher splitting parameter, the pressure shifts to the higher pressure side.
-For $l=2,3$ and 4, the convergence is not sensitive to $\alpha$ upto  $1.0\,\textrm{nm}^{-1}$.
+For $l=2,3$ and 4, the convergence is not sensitive to $\alpha$ up to  $1.0\,\textrm{nm}^{-1}$.
 More importantly, for all orders,
@@
     calculated by different methods.    
-    The parenthesises in the last column show the statistical uncertainty
+    The parentheses in the last column show the statistical uncertainty
     at the confidence level of 95~\%.
@@
 As a measurement of the dipole correlation as a function of molecular distance, the Kirkwood-G factor
-is an important qnantity of the water system.
+is an important quantity of the water system.
 It is well know that the G-factor is system size
 dependent~\cite{vanderSpoel2006origin}, therefore we show the G-factor for
-both  system $\systemlb$ in FIg.~\ref{fig:gkr}~(a) and a smaller system $\systemmb$
+both  system $\systemlb$ in Fig.~\ref{fig:gkr}~(a) and a smaller system $\systemmb$
 Fig.~\ref{fig:gkr} (b).  In the figures, the statistical uncertainty of
@@
 other methods are essentially of the same size as the SPME, so they are not presented in the figure for
-clarity.  In the figure, ZM adaopts a cut-off radius of 1.2~nm and a splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
+clarity.  In the figure, ZM adopts a cut-off radius of 1.2~nm and a splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
 RF uses a cut-off 1.2~nm and a dielectric constant of 80.
@@
 wrong. The accuracy of the ZM method is much higher than RF.
-In the system of larger size ($\systemlb$), the ZM mehtod of $l=1$ is in consistency with the SPME mehtod. However
+In the system of larger size ($\systemlb$), the ZM method of $l=1$ is in consistency with the SPME method. However
 order $l=2,3$ and 4  present less but still acceptable accuracy.
@@
   \caption{
-    The cut-off (a) and spliting parameter (b) dependency in calculating the Kirkwood-G factor.
-    The order of ZM method is $l=3$. In plot (a) the spliting parameter is $\alpha = 0.00\,\textrm{nm}^{-1}$.
+    The cut-off (a) and splitting parameter (b) dependency in calculating the Kirkwood-G factor.
+    The order of ZM method is $l=3$. In plot (a) the splitting parameter is $\alpha = 0.00\,\textrm{nm}^{-1}$.
     in plot (b) the cut-off radius is 1.2~nm.
@@
 
-The cut-off and spliting parameter dependency in calculating the Kirkwood-G factor
+The cut-off and splitting parameter dependency in calculating the Kirkwood-G factor
 is presented in Fig.~\ref{fig:gkr-conv}  for ZM method of order $l=3$. With out surprising,
@@
 However, unlike the case of calculating RDF, the accuracy Kirkwood-G factor is not improved
-with increasing spliting parameter. This fact should be noticed in choosing parameters for
-high accuracy calcualtion of Kirkwood-G factor.
+with increasing splitting parameter. This fact should be noticed in choosing parameters for
+high accuracy calculation of Kirkwood-G factor.
 
@@
 The dynamical quantities, diffusion constant and viscosity, are listed in Tab.~\ref{tab:thermo}.
-The ZM method of order $l\geq 2$ can almost perfactly reproduce the SPME dynamical quantities.
+The ZM method of order $l\geq 2$ can almost perfectly reproduce the SPME dynamical quantities.
 The ZM order $l=1$ is of less accurate than higher orders, but is more accurate than the RF.
-Using larger spliting parameters improves the accuracy, and the value $\alpha= 2.0\ \textrm{nm}^{-1}$ is
-sugguested for calculating the dynamical quantities.
+Using larger splitting parameters improves the accuracy, and the value $\alpha= 2.0\ \textrm{nm}^{-1}$ is
+suggested for calculating the dynamical quantities.
 
@@
 
-In this section we proivde the formula used for computing the benchmark quantities. We assume that there are
+In this section we provide the formula used for computing the benchmark quantities. We assume that there are
 $N$ molecules in the water system. The position and configuration of each molecule are fully described
@@
 \subsection{Radial distribution function}
-The radial distribution function (RDF) $g(r)$ is a scalor function of distance $r$, which indicates the
+The radial distribution function (RDF) $g(r)$ is a scalar function of distance $r$, which indicates the
 probability of finding two atoms of distance $r$ apart.  It is a very
-impotant equilibrium structure property, by which the X-ray scattering
+important equilibrium structure property, by which the X-ray scattering
 intensity and a mount of thermodynamic properties can be computed.
@@
 \subsection{Pressure}
-The pressure of the system calculated by the virial formulus:
+The pressure of the system calculated by the virial formula:
 \begin{align}
@@
 between an inserted testing molecule and the system is
-denotedd by $U_t(\lambda)$, where $\lambda$
+denoted by $U_t(\lambda)$, where $\lambda$
 is a coupling parameter in range $[0,1]$.
@@
 This integral is usually calculated by numerical integration, which
-equally paritions the range of $\lambda$, simulates the system at each
-discretized $\lambda$, and computes chemical potential by trapezoidal formulus.
+equally partitions the range of $\lambda$, simulates the system at each
+discretized $\lambda$, and computes chemical potential by trapezoidal formula.
 Here for the sake of accuracy, 
@@
 
-The constant volume heat capacity is defined by the infiniesimal
-increment of the energy due to an infiniesimal increment of the temperature
-at constnat volume condition: 
+The constant volume heat capacity is defined by the infinitesimal
+increment of the energy due to an infinitesimal increment of the temperature
+at constant volume condition: 
 \begin{align}
@@
 it by the number molecules in the system $N$ to obtain the
-constnat volume molar heat capacity $C_{V,m} = C_V/N$.
-In the MD simlations, 
+constant volume molar heat capacity $C_{V,m} = C_V/N$.
+In the MD simulations, 
 the constant volume molar heat capacity is calculated by estimating the
-fulctuation of the Hamiltonian in an NVT simulation:
+fluctuation of the Hamiltonian in an NVT simulation:
 \begin{align}
@@
 The isothermal heat capacity is defined
-by the normalized increment of volume due to an infiniesimal
+by the normalized increment of volume due to an infinitesimal
 decrement of pressure under constant temperature condition:
@@
 The thermal expansion coefficient is defined by
-the normalized increment of volume due to an infiniesimal
+the normalized increment of volume due to an infinitesimal
 increment of temperature under the constant pressure condition:

### 2014-11-03 writedown/zm/paper.water/main.tex
further polish the paper.

@@
 
-A very short overview of the existing electrostatic interaction methods.
-Long-range treatment, Ewald and derived methods like SPME.
-Short-range treatment.
+A very short overview of the existing electrostatic interaction methods. Two classes in general:
+Long-range treatment, e.g.~Ewald and derived methods like SPME.
+Short-range treatment, like RF and ZM.
 
@@
 
-A short mention of the group cut-off v.s.~the atom cut-off method. (will discuss the implementation in gromacs later)
+\recheck{If we want to discuss the issue of cut-off method, a short
+  introduction of the group cut-off v.s.~the atom cut-off
+  method. (will discuss the implementation in gromacs later)}
 
@@
 In order to investigate the performance of ZM method, we simulation
-the water system by using both SPME and ZM method, and calculate a set
+the water system by using both SPME and ZM methods, and calculate a set
 of \emph{benchmark quantities}.  This set covers a broad range of
-water properties that are of general interest, and includes the
+water properties that are of general interest. It includes the
 structure property (radial distribution function), the thermodynamic
@@
 expansion coefficient), dielectric properties (dielectric constant and
-Kirkwood-G factor) and dynamical properties (diffusion coefficient and
-viscosity).  By comparing ZM to SPME, a good consistency in computing
+Kirkwood-G factor) and dynamical properties (diffusion constant and
+viscosity).
+The definitions and computing methods of these quantities are provided in details
+in Appendix.~\ref{appendix:benchmark}.
+By comparing ZM to SPME, a good consistency in computing
 the benchmark quantities would indicate a good accuracy of the ZM
-method.  Moreover, being aware of the weakness of the ZM method also
-prevents the application the method in wrong applications.  The ZM
-method is also compared to the traditional short-range method: RF.
-The definitions for computing these quantities are provided in details
-in Appendix.~\ref{appendix:benchmark}.
+method.
+More importantly, the benchmark tests provide knowledge in the
+stituations when the ZM method does not work so well, and help in
+finding the way of tuning the working parameters to achieve higher accuracy.
+The ZM method is also compared to the traditional short-range method: RF.
 
@@
 
-In this work, we investigate the water system modeled by
+In this work, we focus on the water system modeled by
 TIP3P~\cite{jorgensen1983comparison} point-charge water model.
-All simulations were performed by Gromacs~4.6~\cite{hess2008gromacs, pronk2013gromacs} complied by GNU C compiler with single float precision.
+% Other point-charge water models differ in the modeling parameters, and
+The accuracy of ZM method in other water models is out of the scope of the current work.
+However, since the point-charge water models share similar idea, and  only differ
+in the model parameters, it is highly probable that ZM works well with other water models if it works
+well with TIP3P.
+
+All simulations were performed by Gromacs~4.6.5~\cite{hess2008gromacs, pronk2013gromacs} complied by GNU C compiler with single-precision floating point.
 The size of the systems and corresponding number of molecules used for MD simulations are summarized in Tab.~\ref{tab:tmp1}.
@@
 In order to simulate at the desired temperature,
-the systems $\systemsb$ and $\systemsbp$ were coupled to either Nose-Hoover~\cite{nose1984molecular,hoover1985canonical} thermostat with time-scale $\tau_T = 1.0$~ps,
+the systems $\systemsb$ and $\systemsbp$ were coupled to Nose-Hoover~\cite{nose1984molecular,hoover1985canonical} thermostat with time-scale $\tau_T = 1.0$~ps,
 while systems $\systemmb$, $\systemmbp$, $\systemla$, $\systemlb$ and $\systemlbp$ were coupled to Langevin thermostat with time-scale $\tau_T = 0.1$~ps.
@@
 with time-scale $\tau_P = 0.5$~ps to equilibriate the system at 1~Bar.
-All systems were integrated with leap-frog scheme at the time-step of 0.001~ps.
-For the ZM and SPME methods,
-the neighbor lists were updated every 5 time-steps.
+All systems were integrated with leap-frog scheme at a time-step of 0.001~ps.
+The neighbor lists were updated every 5 time-steps.
 The ``\texttt{group}'' cut-off scheme in Gromacs was used. In order to mimic the atomistic
@@
 they are modified in a shell of $0.05$~nm width near the cut-off sphere by the Gromacs ``\texttt{shift}'' method.
-The ZM method was implemented in Gromacs with the tabulated electrostatic interaction (Home-made codes for generating the interaction tables).
-The short-range part of SPME method is also smoothed in a shell of $0.05$~nm width  by the Gromacs ``\texttt{pme-switch}'' method.
+The ZM method was implemented in Gromacs with the tabulated electrostatic interaction. A home-made code was used to generate the interaction tables.
+The short-range part of SPME method is smoothed in a shell of $0.05$~nm width  by the Gromacs ``\texttt{pme-switch}'' method.
 The reciprocal space
@@
 The optimized real space and reciprocal space force computing errors were equally distributed as $1.4\times10^{-4}$~kJ/(mol nm).
+Since the magnitude of the forces are of order $10^{2}$~kJ/(mol nm), this force computing precision almost reaches the limit of the single-precision representation of the floating point numbers.
 In the simulations of the RF method, the interactions were cut-off in the group manner,
 so the radius for neighbor list building is set identical to the cut-off radius.
-No cut-off smoothing was applied in the cases of RF simulation.
+No cut-off smoothing of the electrostatic interaction was applied in the cases of RF simulation.
 
@@
   \caption{A list of systems simulated in this work. We report, from left to right, the number of water
-    molecules in the system (TIP3P model), equilibrium box size, length of equilibriation, length of productive trajectory, the thermostats and the corresponding coupling time-scales.
+    molecules in the system (TIP3P model), equilibrium box size, length of equilibriation, length of productive trajectory.
   }
   \vskip .5cm
-  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}c rrrrrr}\hline\hline
-    System      & $N$ & $V$ [$\textrm{nm}^3$]  & $T_{eq}$ [ps] & Traj. Length [ps] & Thermostat & $\tau$ [ps]  \\\hline
-    $\systemsbp$         &   2,500        & $4.24^3$              & --           &  6,000        & Nose-Hoover & 1.0\\
-    $\systemsb$          & 2,500          & $4.24^3$              & 3,000        & 27,000        & Nose-Hoover & 1.0 \\\hline
-    $\systemmbp$         &   4,500        & $5.15^3$              & --           &  6,000        & Langevin & 0.1\\
-    $\systemmb$          & 4,500          & $5.15^3$              & 3,000        & 17,000        & Langevin & 0.1\\\hline
-    $\systemla$          &   13,824       & $7.49^3$              & 200          & 1,800         & Langevin & 0.1\\
-    $\systemlbp$         &   13,824       & $7.49^3$              & --           & 10,000        & Langevin & 0.1\\
-    $\systemlb$          &   13,824       & $7.49^3$              & 3,000        & 17,000        & Langevin & 0.1\\
+  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}c rrrr}\hline\hline
+    System      & $N$ & $V$ [$\textrm{nm}^3$]  & $T_{\textrm{eq}}$ [ps] & $T_{\textrm{prod}}$ [ps]  \\\hline
+    $\systemsbp$         &   2,500        & $4.24^3$              & --           &  6,000        \\
+    $\systemsb$          & 2,500          & $4.24^3$              & 3,000        & 27,000        \\\hline
+    $\systemmbp$         &   4,500        & $5.15^3$              & --           &  6,000        \\
+    $\systemmb$          & 4,500          & $5.15^3$              & 3,000        & 17,000        \\\hline
+    $\systemla$          &   13,824       & $7.49^3$              & 200          & 1,800         \\
+    $\systemlbp$         &   13,824       & $7.49^3$              & --           & 10,000        \\
+    $\systemlb$          &   13,824       & $7.49^3$              & 3,000        & 17,000        \\
     \hline\hline
@@
 (1) An NPT simulation of system $\systemla$ with SPME
-electrostatic was performed. The equilibrium density (984.1~$\textrm{kg}/\textrm{m}^{-3}$) of the system is calculated
+electrostatic was performed. The equilibrium density (984.1~$\textrm{kg}/\textrm{m}^{3}$) of the system is calculated
 from this simulation.
@@
 The optimal way of measuring these properties
-is to simulate with smaller systems (as far as the finite size effect is negligible) and run longer simulations for longer time-averages.
+is to simulate with smaller systems
+% (as far as the finite size effect is negligible)
+and run longer simulations for longer time-averages.
 The reason of using Nose-Hoover thermostat is that
@@
 The equilibrium density of the system was determined by an NPT SPME
-simulation.  In the NVT simulation the SPME electrostatic, computed
+simulation.  Then using this density in the NVT simulation with SPME electrostatic, the
 pressure ($-0.4\pm 1.5$~Bar) is reproducing the target pressure of
-1.0~Bar.  The accuracy of ZM method, can be investigate by checking if
-the NVT pressure is consistent with the target pressure.  In
+1.0~Bar, which means the system is in desired thermodynamic state.  The accuracy of ZM method, can be investigate by checking if
+the NVT pressure is consistent with the target pressure, when the SPME equilibrium density is used.  In
 Fig.~\ref{fig:pres-comp}, the pressure calculated by ZM method of
@@
 For $l=2,3$ and 4, the convergence is not sensitive to $\alpha$ up to  $1.0\,\textrm{nm}^{-1}$.
-More importantly, for all orders,
-the pressure does not converges to the desired value 1~Bar by using $\alpha = 1.5$ or $2.0\,\textrm{nm}^{-1}$.
+More importantly,  by using $\alpha = 1.5$ or $2.0\,\textrm{nm}^{-1}$,
+the pressure does not converges to the desired value 1~Bar. Therefore, the high splitting parameter
+is not suggested in the simulations where the high pressure accuracy is important.
 
@@
 The artificial oscillation can be substantially improved by using larger splitting parameter $\alpha$.
-In Fig.~\ref{fig:rdf-damp} presents the RDF of ZM $l=1$ with splitting parameter from 0.0 to 2.0~$\textrm{nm}^{-1}$.
+Fig.~\ref{fig:rdf-damp} presents the RDF of ZM $l=1$ with splitting parameter from 0.0 to 2.0~$\textrm{nm}^{-1}$.
 A clear trend of better RDF by using larger splitting parameter is observed.
@@
 dependent~\cite{vanderSpoel2006origin}, therefore we show the G-factor for
-both  system $\systemlb$ in Fig.~\ref{fig:gkr}~(a) and a smaller system $\systemmb$
-Fig.~\ref{fig:gkr} (b).  In the figures, the statistical uncertainty of
+system $\systemlb$ in Fig.~\ref{fig:gkr}~(a) and a smaller system $\systemmb$
+in Fig.~\ref{fig:gkr} (b).  In the figures, the statistical uncertainty of
 the SPME method is denoted by the red error bars. The statistical uncertainties of the
@@
 is presented in Fig.~\ref{fig:gkr-conv}  for ZM method of order $l=3$. With out surprising,
-the Kirkwood-G factor converges to the SPME result when using increasing cut-off radius. 
+the Kirkwood-G factor converges to the SPME result when using increasingly large cut-off radius. 
 However, unlike the case of calculating RDF, the accuracy Kirkwood-G factor is not improved

### 2014-11-04 writedown/period.noneq.msm/paper.tex
adjust the plots

@@
 \documentclass[aps, pre, preprint,unsortedaddress,a4paper,onecolumn]{revtex4}
-% \documentclass[aps, pre, preprint,unsortedaddress,a4paper,twocolumn]{revtex4}
+% \documentclass[aps, pre, reprint,unsortedaddress,a4paper,twocolumn]{revtex4}
 % \documentclass[acs, jctcce, a4paper,preprint,unsortedaddress,onecolumn]{revtex4-1}
@@
 By assigning the spacial and temporal discretizations, 
-the transition probabilities are sampled from MD trajectories, and
-the MSM does not need more information from the MD simulation.
-The quality of the MSM therefore relies on the quality of the discretizations.
+the transition probabilities are sampled from MD trajectories, 
+% the MSM does not need more information from the MD simulation.
+so the quality of the MSM  relies on the quality of the discretizations.
 Moreover, the characteristic of the original dynamics plays a role:
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{fig/t010/discrete/fig-cg-prob.eps}  
+  \includegraphics[width=0.45\textwidth]{fig/t010/discrete/fig-cg-prob.eps}  
   \caption{Time-dependent probability $\prob\big(\phi_t\in[0,180), \psi_t\in [0,180)\big)$.  The brute force NEMD simulation is compared with different
@@
   \centering
-  \includegraphics[width=0.7\textwidth]{fig/t010/discrete/fig-cg-prob-tau.eps}  
+  \includegraphics[width=0.45\textwidth]{fig/t010/discrete/fig-cg-prob-tau.eps}  
   \caption{Time-dependent probability $\prob\big(\phi\in[0,180), \psi\in [0,180)\big)$.
@@
   \centering  
-  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3.steadyDist//fig-dist.eps}
+  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3.steadyDist//fig-dist.eps}\\
   % \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-dist-msm.eps}
   \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3/fig-floquet-vec-1.eps}
-  \caption{The color scale plot of the logarithmic quasi-stationary distribution $\mymu$
+  \caption{The color-scale plot of the logarithmic quasi-stationary distribution $\mymu$
     of (a) the NEMD  and (b)
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{fig/t010/cluster.marco.3/fig-cluster.eps}
+  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3/fig-cluster.eps}
   \caption{The coreset identification. Different colors indicate different core sets: $C_{\confaa}$ (green), $C_\beta$ (yellow) and $C_{\confc}$ (red).
@@
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-msm-1.eps}\\
-  \vskip -.5cm
+  \vskip -.7cm
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-2.eps}
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-msm-2.eps}\\
-  \vskip -.5cm
+  \vskip -.7cm
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-3.eps}
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-msm-3.eps}\\
+  \vskip -.5cm
   \caption{Comparisons of the first mean hitting time (FMHT) based on NEMD
-    simulation (first column) and discretized dynamics (second column).  From top
+    simulation (left column) and discretized dynamics (right column).  From top
     to bottom the first mean hitting times to the core sets $C_{\confaa}$, $C_{\beta}$,
@@
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-msm-1.eps}\\
+  \vskip -.7cm
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-1.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-1.eps}\\
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-msm-1.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-msm-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-msm-1.eps}\\
+  \vskip -.7cm
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-1.eps}
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-msm-1.eps}
-  \caption{The forward $q^\fwd_{\confc}$ and backward committors
-    $q^\bwd_{\confc}$ computed by the discretized dynamics (second row) and NEMD simulations (first
-    row).}
+  \vskip -.5cm
+  \caption{The forward $q^\fwd_{\confaa}$ and backward 
+    $q^\bwd_{\confaa}$ committors
+    and their difference $q^\fwd_{\confaa} - q^\bwd_{\confaa}$
+    computed by the NEMD simulations (left
+    column) and the  discretized dynamics (right column).}
   \label{fig:num-3}
@@
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-msm-2.eps}\\
+  \vskip -.7cm
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-2.eps}\\
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-msm-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-msm-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-msm-2.eps}
-  \caption{The forward $q^\fwd_{\confaa}$ and backward
-    $q^\bwd_{\confaa}$ committors computed by discretized dynamics (second row) and NEMD
-    simulations (first row).}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-msm-2.eps}\\
+  \vskip -.7cm
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-msm-2.eps}\\
+  \vskip -.5cm
+  \caption{The forward $q^\fwd_{\beta}$ and backward
+    $q^\bwd_{\beta}$ committors
+    and their difference  $q^\fwd_{\beta} - q^\bwd_{\beta}$ 
+    computed by the NEMD simulations (left
+    column) and the  discretized dynamics (right column).}
   \label{fig:num-4}
@@
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-msm-3.eps}\\
+  \vskip -.7cm
   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-3.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-3.eps}\\
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-msm-3.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-msm-3.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-msm-3.eps}
-  \caption{The forward $q^\fwd_{\beta}$ and backward $q^\bwd_{\beta}$
-    committors computed by discretized dynamics (second row) and  NEMD
-    simulations (first row).}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-msm-3.eps}\\
+  \vskip -.7cm
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-msm-3.eps}\\
+  \vskip -.5cm
+  \caption{The forward $q^\fwd_{\confc}$ and backward $q^\bwd_{\confc}$
+    committors
+    and their difference  $q^\fwd_{\confc} - q^\bwd_{\confc}$ 
+    computed by the NEMD simulations (left
+    column) and the  discretized dynamics (right column).}
   \label{fig:num-5}
@@
   }
-  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}c rrr}\hline\hline
+  \begin{tabular*}{0.45\textwidth}{@{\extracolsep{\fill}}c rrr}\hline\hline
       &  $\lambda_2$ & $\lambda_3$ & $\lambda_4$ \\\hline
@@
   \centering
-  \includegraphics[width=0.85\textwidth]{fig/t010/cluster.marco.3/fig-coreset-prob.eps}
+  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3/fig-coreset-prob.eps}
   \caption{Comparison of NEMD and MSM long-term kinetics of alanine
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{fig/flowchart/flowchart.eps}
+  \includegraphics[width=0.48\textwidth]{fig/flowchart/flowchart.eps}
   \caption{The flowchart of this work. A lighter color indicates
-  a ``more coarse'' approximation to the original NEMD dynamics.}
+  a ``coarser'' approximation to the original NEMD dynamics.}
   \label{fig:flowchart}

### 2014-11-05 writedown/period.noneq.msm/paper.tex
merge CS's revise, add some from mine

@@
 \newcommand{\redc}[1]{{\color{red} #1}}
-\newcommand{\bluec}[1]{{\color{red} #1}}
+\newcommand{\bluec}[1]{{\color{blue} #1}}
 \newcommand{\greenc}[1]{{\color{green} #1}}
@@
 \email{han.wang@fu-berlin.de}
-\affiliation{Zuse Institut Berlin, Germany}
+\affiliation{CAEP Software Center for High Performance Numerical Simulation, Beijing, China}
+\affiliation{Zuse Institute Berlin, Germany}
 \author{Christof Sch\"utte}
@@
 \affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
-\affiliation{Zuse Institut Berlin, Germany}
+\affiliation{Zuse Institute Berlin, Germany}
 
 \begin{abstract}
+Recent years have seen an increased interest in non-equilibrium molecular dynamics (NEMD) simulations, especially for molecular systems with periodic forcing by external fields, e.g., in the context of studying  effects of electromagnetic radiation on the human body tissue.
+Lately, an NEMD methods with local thermostating has been proposed that allows for studying
+non-equilibrium processes in a statistically reliable and thermodynamically consistent way.
+In this article, we demonstrate how to construct Markov State Models (MSMs) for such NEMD simulations.
+MSM building has been well-established for systems in equilibrium where MSMs with just a few (macro-)states allow for accurate reproduction of the essential kinetics of the molecular system under consideration.
+Non-equilibrium MSMs have been lacking so far.
+The article presents how to construct such MSMs and illustrates their validity and usefulness for the case of conformation dynamics of alanine dipeptide in an external electric field.
 \end{abstract}
@@
 
-The non-equilibrium biomolecular systems, especially
-those systems under periodic driven, are attracting increasing
-interest.  For example, the potential effects of an electromagnetic
+Biomolecular systems under non-equilibrium conditions caused by external fields, especially
+systems under periodic forcing, have attracted increasing
+interest recently.  For example, the potential effects of electromagnetic
 radiation on the human body tissue (e.g.~DNA, protein, and membrane)  has been extensively
-investigated by a vast number of literatures, and a very limited
-subset of them is Ref.~\cite{bohr2000microwave, bohr2000microwave-1, dePomerai2000cell,
+investigated in a vast number of articles, with the following list just representing an incomplete selection~\cite{bohr2000microwave, bohr2000microwave-1, dePomerai2000cell,
   dePomerai2003microwave, mancinelli2004non, inskip2001cellular, bekard2013electric, budi2005electric,
   budi2007effect, budi2008comparative, astrakas2012structural,
-  damm2012can, english2009nonequilibrium, solomentsev2012effects,
-  wang2014exploring}.  Among those theoretical investigations, the
-molecular dynamics (MD) has been shown  useful in understanding
-the response of the biomolecular conformation to the external electric field,
-due to its ability of resolving the molecular
-details, which are sometimes not achievable in experiments. Only
-recently, a dynamical non-equilibrium MD simulation (D-NEMD) method has
-been proposed.  With the local thermostating technique, the D-NEMD
-method is able to sample the non-equilibrium probability density at the
-constant temperature, therefore opens the possibility of studying the
-non-equilibrium processes in a statistically reliable and
-thermodynamically consistent way.
+  damm2012can, english2009nonequilibrium, solomentsev2012effects}.  Molecular dynamics (MD) simulations have proved particularly useful for understanding
+the response of biomolecular conformations to external fields because of their ability to  resolve molecular
+details that \recheck{sometimes} cannot be resolved in experiments. Only
+recently, a \recheck{dynamical} non-equilibrium MD simulation (D-NEMD) method with local thermostating has been proposed~\cite{wang2014exploring} that allows for studying 
+non-equilibrium processes in a statistically reliable and thermodynamically consistent way. 
+Despite the significance of the non-equilibrium phenomena, the
+analysis of the non-equilibrium MD simulations mainly follows standard approaches, and reliable tools for quantitative description of
+the essential conformational dynamics of the molecular system under external forcing are still lacking.
 
@@
 
-Despite their high resolution in presenting a molecular system, MD the
-trajectories including the time-dependent position and velocity of every atom
-sometimes impose non-trivial challenge for data analyzing, in the sense that 
-extracting the essential structure and dynamical properties is
-becoming increasingly difficult as the  system size and trajectory length grow.
-% by merely visulizing (not only molecular cartoons but also order parameters)
-% and observing the molecules.
-The Markov state model
-(MSM)~\cite{A19-31}, which is a promising method for data analyzing of
-the high-dimensional MD trajectories, has been well developed over the
-past decade in theory and applications \cite{A19-31, A19-1}, and in
-the software implementations~\cite{A19-49, MSMBuilder}.  The principal
-idea of MSM is to approximate the original high-dimensional system by
-a reduced Markovian dynamics over a finite number of states, from
-which the essential structures and dynamics can be formulated by the spectrum analysis.
-By assigning the spacial and temporal discretizations, 
-the transition probabilities are sampled from MD trajectories, 
-% the MSM does not need more information from the MD simulation.
-so the quality of the MSM  relies on the quality of the discretizations.
-Moreover, the characteristic of the original dynamics plays a role:
-It has been shown that in principle good approximate accuracy would be achieved
-by using only a few ``coresets'',
-if the system is dominated by a few metastable states, in the sense that
-the MD trajectories stay in the vicinity of a metastable state substantially longer than
-transform to another such state~\cite{schuette2011markov}.
-Besides the applications in analyzing the MD trajectories, it worth noting that MSM is
-also used for designing initial configurations for massively parallel MD
-simulations~\cite{kohlhoff2014cloud}.
+Despite their many advantages, MD simulations have severe limitations.
+For example, one has to assume that the underlying force fields are appropriately describing the internal and external molecular interactions, and the maximal possible simulation length often is shorter than the timescale of interest.
+This article is mainly concerned with circumventing the latter obstacle by introducing non-equilibrium Markov State Models. Markov State Models
+(MSM) have been well developed over the
+past decade in theory~\cite{A19-31,prinz2011markov} and applications (see the recent book~\cite{A19-1} for an overview), and software implementations~\cite{A19-49, MSMBuilder}, but for systems under equilibrium conditions only!
+The principal idea of equilibrium MSMs is to approximate the original high-dimensional MD system by
+a reduced Markovian dynamics over a finite number of (macro-)states. These (macro-)states
+have to be identified with the dominant metastable sets, in the sense that
+typical MD trajectories stay in the vicinity of a metastable set substantially longer than
+the systems needs for a transition to another such state~\cite{A19-31,schuette2011markov}.
+In this case, the metastable sets are the main conformations of the molecular system under consideration which, often enough, are given by the main wells in the energy landscape.
+It has been shown that for molecular systems exhibiting such metastable sets the Markovian dynamics given by an MSM allows very close approximation of the longest relaxation processes of the underlying molecular system, at least under equilibrium conditions~\cite{sarich2010approximation,Eigenvalues}.
+Moreover, it has been demonstrated that in such cases MSM building requires short MD trajectories only, much shorter than the timescales of interest~\cite{PNAS09,kohlhoff2014cloud}.  
+Thus, MSM building often allows to study the dynamical behavior on long timescales without requiring MD trajectories of comparable length.
+Moreover, MSMs are utilized for understanding very long MD simulations: Extracting the essential structures and dynamical properties from long MD runs is
+becoming increasingly difficult as the system size and trajectory length grow; MSMs have been used to construct kinetic fingerprints from MD simulations~\cite{A19-39} that help understanding the essential dynamics and in comparison with experiments~\cite{PrinzKellerNoe_PCCP11_Perspective}.
 
@@
 % \textbf{Importance: first application of MSM in a non-equilibrium system.}
-
-Despite the significance of the non-equilibrium phenomena, the
-analysis of the non-equilibrium MD simulations mainly follows the
-visualizing (not only molecular cartoons but also order parameters)
-and observing approach, and the quantitative description of
-the essential conformational dynamics is still lacking. On the other
-hand, the MSM, to the best of our knowledge, has only been applied to
-equilibrium systems,  and most of them are assumed reversible. This work is the first attempt
-of using the MSM in analyzing a class of truly non-equilibrium systems:
-periodic external driven. Being more specifically,
-we investigate the protein conformational dynamics
-under the oscillating electric field (EF).
-In Sec.~\ref{sec:disc}, we discuss the temporal and spacial
-discretizations of the non-equilibrium dynamics. The spacial discretization
-is on the dihedral angle space, which can be interpreted as a
-MSM in the traditional sense of full spacial partition.
+To the knowledge of the authors this work is the first attempt of using MSMs for analyzing non-equilibrium systems under periodic external forcing.
+More precisely, we will demonstrate how to use MSMs for investigate the conformational dynamics of a peptide (alanine dipeptide) under an oscillating electric field (EF).
+To this end, we will show how to generalize Markov state modeling to periodic non-equilibrium conditions where one cannot assume reversibility of the dynamics as it is mostly done in the literature on MSM building.
+
+The outline of the article is as follows: 
+In Sec.~\ref{sec:disc}, we discuss the temporal and spatial
+discretizations needed to construct an MSM. We consider spatial discretization
+of the dihedral angle space in the traditional sense of full partition MSMs~\cite{pande2010everything,A19-29}.
 In the temporal direction, the non-equilibrium process
-is  discretized by the Floquet theorem into a time-homogeneous
-but not necessarily reversible dynamics. Since the full spacial partition
-is not preferable in high-dimensional system, in Sec.~\ref{sec:build-msm},
-the MSM based on milestoning is introduced for the discretized irreversible process.
-The validity of the discretizations and the MSM is checked in Sec.~\ref{sec:alanine}
-by comparing to the brute force
-non-equilibrium simulation of alanine dipeptide under oscillating EF.
-This work is summarized in Sec.~\ref{sec:conclusion} by a chart presenting
-the workflow of building MSM for non-equilibrium systems,
-and open questions are presented in the end.
+is discretized utilizing Floquet's theorem. This results in a time-homogeneous, 
+but not necessarily reversible, that is, irreversible Markov process. Since  full spatial partition does not make any sense
+for high-dimensional systems, we next show how to construct a \emph{few-state} MSM based on milestoning~\cite{schuette2011markov,A19-29} of the discretized irreversible Markov process in Sec.~\ref{sec:build-msm}.
+The validity of the discretizations and the resulting MSM is checked in Sec.~\ref{sec:alanine}
+by comparing the kinetic fingerprints given by the MSM to brute force
+non-equilibrium \recheck{MD} simulations of alanine dipeptide under oscillating EF.
+The findings are summarized in Sec.~\ref{sec:conclusion} including a chart presenting
+the workflow of MSM building for non-equilibrium systems, and a list of open questions.
 
@@
 \label{sec:disc}
-For the sake of simplicity we consider diffusive molecular dynamics in an energy landscape $V$ driven by the time-dependent external driving force $E(t)D(x_t)$ with the
+\recheck{We consider diffusive molecular dynamics} in an energy landscape $V$ driven by the time-dependent external driving force $E(t)D(x_t)$ with the
 $T$-periodic external field $E(t)$:
@@
 i.e.~$\beta = 1/(k_B\mathcal T)$.
+\recheck{The Hamiltonain or Langevin dynamics can be treated in the same way as that will be presented, so for sake of simplicity we focus on the discussion of diffusive dynamics.}
 The propagation of probability
@@
 \subsection{Spatial discretization: Master equation}
-We will now introduce an appropriate spatial discretization of this kind of non-equilibrium MD -- this is done for reasons of simplicity only; we could completely avoid it for the price of more technical arguments.
+We will now introduce an appropriate spatial discretization of this kind of non-equilibrium MD -- \recheck{\bluec{(why saying this red sentence?
+we need the spatial discretization for calculating the core sets...)} this is done for reasons of simplicity only; we could completely avoid it for the price of more technical arguments.}
 For achieving this discretization, we 
@@
 It worth noting that many of these tools require the transition matrix $P$ to satisfy the detailed balance condition.
-The computations in the Appendix~\ref{sec:app-revs} show that $P$ will in general \emph{not} satisfy this condition; in fact  the deviation form reversibility can be estimated from the work of the periodic driving does to the system.
+The computations in the Appendix~\ref{sec:app-revs} show that $P$ will in general \emph{not} satisfy this condition; in fact  the deviation {from} reversibility can be estimated from the work of the periodic driving does to the system.
 There is no doubt that information within one period is lost by using this temporal
-discretization, however, information regarding the long-term behavior of the system on time-scales
+discretization, however, information regarding the long-term behavior of the system on timescales
 much longer than the period will be perfectly described because of $\tilde X_{m} = X_{mT}\approx x_{mT}$ whenever our spatial discretization is fine enough.
@@
 $\mymu^{\top}P=\mymu^{\top}$.
-From now on, we assume $P$ to be irreducible and aperiodic such that the Perron Frobenius theorem the eigenvalue $\lambda=1$ is  non-negative componentwise, and unique (up to normalization $\sum_i\mu(i)=1$).
+From now on, we assume $P$ to be irreducible and aperiodic such that the Perron-Frobenius theorem \recheck{holds, so the eigenvector corresponding to} the eigenvalue $\lambda=1$ is  non-negative componentwise, and unique (up to normalization $\sum_i\mu(i)=1$).
 In this case $\mymu$ is the stationary measure in the sense that
@@
 % \end{align}
-so that $\mymu$ can be seen as the quasi-stationary distribution of our non-stationary process.
-
-% due to the discretization in both the spacial and temperal directions.
+so that $\mymu$ can be seen as the quasi-stationary distribution of the non-stationary process.
+
+% due to the discretization in both the spacial and temporal directions.
 % In the numercal example in Sec.~\ref{sec:alanine}, we
@@
 
-% Given coresets $\{C_1, \cdots, C_k\}$, the procedure \eqref{eq:msm-ht}--\eqref{eq:msm-tmatrix-10}
-% If assuming that we have the coresets $\{C_1, \cdots, C_k\}$, no matter how they are identified,
+% Given core sets $\{C_1, \cdots, C_k\}$, the procedure \eqref{eq:msm-ht}--\eqref{eq:msm-tmatrix-10}
+% If assuming that we have the core sets $\{C_1, \cdots, C_k\}$, no matter how they are identified,
 
@@
 total dimension of $x_t$ is $3N_{\textrm{atom}}$ ($N_{\textrm{atom}}$ being the number of atoms), it is prohibitive to do a really fine discretization
-over all DOFs for most systems of practical interest.
+over all degrees of freedom for most systems of practical interest.
 
@@
 % shorter than the dominant implied timescale so that they can be resolved,
-% and be longer than the fast time-scales to relax the unresolved dynamics
+% and be longer than the fast timescales to relax the unresolved dynamics
 % within the discretized sets.
@@
 The Langevin thermostat with target temperature $\mathcal T = 300$~K
-and time-scale $\tau_T = 0.1$~ps was
+and timescale $\tau_T = 0.1$~ps was
 coupled to the thermostated region.
@@
 used to compute the long-range electrostatic interaction,
-with the same real-space cut-off radius as the van der Waals interactions,
-and the Gromacs default Fourier spacing of 0.12~nm.
+with the same real-space cut-off radius as the van der Waals interactions.
+\recheck{The Gromacs default Fourier spacing of 0.12~nm and B-spline interpolation order of 4 were adopted.}
 The splitting
-parameter optimized with respect to the electrostatic force computing
+parameter was optimized with respect to the electrostatic force computing
 accuracy by Gromacs tool \texttt{g\char`_pme\char`_error}~\cite{wang2010optimizing}.
@@
 % equilibrium simulation the system was coupled to a global Langevin thermostat
-% with coupling time-scale $\tau_T = 0.5$~ps.
+% with coupling timescale $\tau_T = 0.5$~ps.
 The branching NEMD
-trajectories were each 4000~ps long, and the system reached
+trajectories were each 4,000~ps long, and the system reached
 non-equilibrium quasi-stationary state in roughly 300~ps.
 
-For this periodically driven molecular system we will first show how to choose an appropriately fine discretization. After validating this discretization we will consider
-the discretized dynamics generated by the Floquet transition matrix $\vect P$
+For this periodically driven molecular system we will first show how to choose an appropriately fine \recheck{spatial} discretization. After validating this discretization we will consider
+the \recheck{temporal} discretized dynamics generated by the Floquet transition matrix $\vect P$
 in comparison to the original NEMD simulation.
@@
 On each NEMD branching trajectory the initial 320~ps are discarded and
-the rest of the trajectory in time interval $[320,4000]$~ps is used to estimate
+the rest of the trajectory in time interval $[320,4000]$~ps is \recheck{averaged} to estimate
 the quasi-stationary probability distribution $\rho_{\textrm{st}}$. 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Core set identification}
+\subsection{Core Set identification}
 
@@
   \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3/fig-cluster.eps}
-  \caption{The coreset identification. Different colors indicate different core sets: $C_{\confaa}$ (green), $C_\beta$ (yellow) and $C_{\confc}$ (red).
+  \caption{The core set identification. Different colors indicate different core sets: $C_{\confaa}$ (green), $C_\beta$ (yellow) and $C_{\confc}$ (red).
     The blue color indicates the transition region $C$ that does not belong to one of the core sets.}
@@
 conformation $(\phi,\psi)$, more exactly from equilibrium conformations $(\phi,\psi)\in\Omega_i$.  Since the largest first mean hitting
-time (starting from states in coreset $\confaa$ and hitting $\confc$) is longer than
+time (starting from states in core set $\confaa$ and hitting $\confc$) is longer than
 600~ps the results will be biased if we use the NEMD trajectories of length 4000~ps for brute force Monte Carlo estimation of the hitting time. 
@@
   \vskip -.5cm
-  \caption{The forward $q^\fwd_{\confaa}$ and backward 
+  \caption{\recheck{The forward $q^\fwd_{\confaa}$ and backward 
     $q^\bwd_{\confaa}$ committors
@@
     computed by the NEMD simulations (left
-    column) and the  discretized dynamics (right column).}
+    column) and the  discretized dynamics (right column).}}
   \label{fig:num-3}
@@
   \vskip -.5cm
-  \caption{The forward $q^\fwd_{\beta}$ and backward
+  \caption{\recheck{The forward $q^\fwd_{\beta}$ and backward
     $q^\bwd_{\beta}$ committors
@@
     computed by the NEMD simulations (left
-    column) and the  discretized dynamics (right column).}
+    column) and the  discretized dynamics (right column).}}
   \label{fig:num-4}
@@
   \vskip -.5cm
-  \caption{The forward $q^\fwd_{\confc}$ and backward $q^\bwd_{\confc}$
+  \caption{\recheck{The forward $q^\fwd_{\confc}$ and backward $q^\bwd_{\confc}$
     committors
@@
     computed by the NEMD simulations (left
-    column) and the  discretized dynamics (right column).}
+    column) and the  discretized dynamics (right column).}}
   \label{fig:num-5}
@@
 checking if the discretized process $\tilde X_m$ reproduces the NEMD committors.
-The forward committor $q^\fwd_j(i)$ of a coreset $C_j,\
+The forward committor $q^\fwd_j(i)$ of a core set $C_j,\
 j\in\{\confaa, \beta, \confc\}$ is defined as the probability of
-visiting coreset $C_j$ next conditioned on starting at conformation
+visiting core set $C_j$ next conditioned on starting at conformation
 $(\phi,\psi)\in\Omega_i$.  The backward committor $q^\bwd_j(i)$ of a
-coreset $C_j,\ j\in\{\confaa, \beta, \confc\}$ is defined as the
+core set $C_j,\ j\in\{\confaa, \beta, \confc\}$ is defined as the
 probability of last coming from $C_j$ conditioned on having arrived presently at
@@
 the largest non-trivial eigenvalue, which means a precise reproduction
-of the longest non-trivial implied time-scale. The accuracy of the second non-trivial
-time-scale is not as good as the first, but is still acceptable.
+of the longest non-trivial implied timescale. The accuracy of the second non-trivial
+timescale is not as good as the first, but is still acceptable.
 The reason
@@
   can be taken as an indication for the non-Markovianity of the milestone process $\hat X_m$. This
-  non-Markovianity seems to have stronger influence on the second non-trivial time-scale in comparison to the first one; this may be caused by shorter decorrelation timescales due to weaker metastability of the core sets involved.
+  non-Markovianity seems to have stronger influence on the second non-trivial timescale in comparison to the first one; this may be caused by shorter decorrelation timescales due to weaker metastability of the core sets involved.
 Numerically the two MSM transition matrices are:
@@
 
-In fact, $\hat{P}$ can be considered as the fingerprint of the long-term kinetics (cf. \cite{A19-39,PrinzKellerNoe_PCCP11_Perspective}) of alanine dipeptide in an oscillatory electric field.
+In fact, $\hat{P}$ can be considered as the fingerprint of the long-term kinetics (cf.~\cite{A19-39,PrinzKellerNoe_PCCP11_Perspective}) of alanine dipeptide in an oscillatory electric field.
 In order to provide further validation of this statement, we study  time-dependent expectation values of
@@
 \end{align}
-where $p(i,t)=\prob(X_t=i)$ is the probability to be in set $\Omega_i$ at time $t$ as governed by the Master equation, and the observable $\mathcal A$ is spanned by the backward
+where $p(i,t)=\prob(X_t=i)$ is the probability to be in set $\Omega_i$ at time $t$ as governed by the Master equation, and the observable $\mathcal A$ is \recheck{linearly} spanned by the backward
 committors, i.e.,
@@
 
-\section{Concluding remarks and discussions}
+\section{Concluding remarks and discussion}
 \label{sec:conclusion}
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{fig/flowchart/flowchart.eps}
-  \caption{The flowchart of this work. A lighter color indicates
-  a ``coarser'' approximation to the original NEMD dynamics.}
+  \includegraphics[width=0.48\textwidth]{fig/flowchart/flowchart2.eps}
+  \caption{Flowchart showing optional procedures for MSM building based on NEMD trajectories. A lighter color indicates
+  a "coarser'' approximation to the original NEMD dynamics. Please note that "equivalence" only means that the respective procedures result in the same matrix/MSM if one assumes perfect sampling.}
   \label{fig:flowchart}
@@
 
-In this paper we developed methods of building MSM for a periodically driven
-non-equilibrium system. By a numerical example
-of the alanine dipeptide under periodically oscillatory EF,
-the methods are shown  to be
-valid and be able to capture the long-time behavior of the original
+In this paper we proposed methods of MSM building for a periodically driven
+non-equilibrium system. We demonstrated their validity and performance by application to  alanine dipeptide under an oscillatory electric field. We showed that the proposed 
+methods allow for capturing the long-time behavior of the original
 non-equilibrium dynamics.
 
-We firstly provide effective methods for discretizing the original NEMD trajectories
-both temporally and spatially, and the end-product is a time-homogeneous
-(not necessarily reversible) Markov jump process.
-There are two equivalent approaches discussed in the paper:
-one can either do a two-steps discretization,
-i.e.~firstly spacial and then temporal,
-or a single step  involves both discretizations simultaneously.
-They are exhibited by the left-most and middle branches in Fig.~\ref{fig:flowchart}.
-
-By a fine discretization of the molecular configuration space, the
-original NEMD dynamics is discretized into a (in principle)
-continuous and time-inhomogeneous {Markov} jump process.
-In principle most of the discretization methods for the equilibrium
-case can be generalized to non-equilibrium without substantial
-difficulty, however, we have not compare different discretization methods
-regarding the accuracy, since it is out of the scope of the present work.
-We show that, by numerical example, a uniform $20\times20$
-discretization over the dihedral angles $\phi$--$\psi$ space is a good
-choice for alanine dipeptide.  In the tests, the state independency in
-computing the generator is used as an indicator for the quality of the
-discretization.
-
-The Floquet theorem discretize a periodic process by taking only
-integral periods, so that
-the time-inhomogeneous process
-is discretized in to a time-homogeneous, but not
-necessarily reversible process.
-The advantage of this discretization is  obvious: All
-well-developed theories and computational tools for time-homogeneous
-Markov processes can be directly applied. In the alanine dipeptide
-system, we compare the the quasi-stationary probability, first mean
-hitting time, and the forward and backward committors of the
-discretized dynamics with those computed directly from the NEMD
-simulation. An almost perfect consistency indicates a good
-approximation quality of the discretized dynamics.
-
-Although the end-product of the two-step and one-step discretizations are equivalent,
+We provided effective methods for discretizing the original NEMD dynamics
+both temporally and spatially; the end-product is a time-homogeneous, in general irreversible Markov jump process.
+Discretization was done via two equivalent approaches:
+either by a two-step version,
+i.e.~first spatial and then temporal discretization,
+or a one-step version that involves both discretizations simultaneously.
+These two version are shown by the left-most and middle branches of the diagram  in Fig.~\ref{fig:flowchart}.
+
+Although the end-product of the two-step and one-step discretization procedures are formally equivalent,
 it is clear that the one-step discretization does not preserve any information
-within one period, because only the states
-at integral periods are considered. This is not a serious problem
-whenever the long-time behaviors of the system is of interest, and
-their corresponding time-scales are significantly longer than one
-period. However, if the time-scale of any interested behavior
-is comparable to, or even shorter than the period, the two-step
-discretization is preferred, so that one can recover the dynamics within
-one period no matter when it is necessary. If the longest non-trivial
-time-scale is comparable to one period, then the Floquet theorem
-is not preferable, and the non-equilibrium dynamics may be well
-described by the quasi-equilibrium approximation.
-
-Building the MSM from the time-homogeneous discretized dynamics is straightforward by
-using Eq.~\eqref{eq:msm-tmatrix-00} and a set of coresets that are
-derived from the discretized dynamics.  Numerical
-results shows that a 3-state MSM can reproduce the leading non-trivial
-eigenvalue with very good accuracy, while the second non-trivial
+\emph{within} one period, because only the states
+at integral multiples of the period of the external forcing are considered. This is no serious problem
+whenever the long-time behavior of the system is of interest, and
+the corresponding timescales are significantly longer than one
+period. However, if the timescale of interest 
+is comparable to the period, the two-step
+discretization is preferable because it allows to recover the dynamics between multiples of
+the period.
+
+Building the final MSM based on the time-homogeneous discretized dynamics is straightforward by
+using Eq.~\eqref{eq:msm-tmatrix-00} and a set of core sets that are
+derived from the discretized dynamics.  In application to alanine dipeptide numerical
+results show that a three-state MSM can reproduce the leading non-trivial
+eigenvalue with very good accuracy, and the second non-trivial
 eigenvalue with acceptable accuracy. The lower accuracy regarding the
-second non-trivial eigenvalue may be due to the fact that the second
-slowest time-scale is not significantly longer than the period. Using
-this three state MSM, we can also reproduce, with almost perfect
-accuracy, the time-evolution of the metastable state probabilities from
-equilibrium (no external driven) to the non-equilibrium
-quasi-stationary state.
+second non-trivial eigenvalue may result from the fact that the second
+slowest timescale is not significantly longer than the period. By means of
+this three-state MSM we can reproduce, with almost perfect
+accuracy, the time-evolution of the population of the main conformations induced by the periodic forcing when starting from the  
+equilibrium distribution of the unforced molecular system.
 
@@
 equivalent, and seemingly
-much simpler alternative to the middle branch, i.e. building
-the MSM directly from the NEMD trajectories.
+much simpler alternative to the middle branch: MSM building directly from NEMD trajectories.
 In practice, however, this method may not be applicable, because
-it requires known coresets, and the coresets identification 
-is usually not a trivial task, especially for the
-non-equilibrium molecular systems.
-This task is substantially
-simplified when an accurate time-homogeneous discretization 
-to the original time-inhomogeneous NEMD is accessible.
-In the present work, we computed the coresets by
-finding the roughly constant levels of the hitting time distribution 
-of the discretized dynamics.
-It should be noticed that the continuous
-counterpart of the current coresets identification method is still an open question.
+it requires pre-defined core sets, and the identification of core sets 
+usually is no trivial task, especially for molecular dynamics under non-equilibrium conditions.
+This task is substantially simplified when an accurate time-homogeneous discretization 
+to the original NEMD process is available (that is, has been constructed in advance).
+In the present work, we computed the core sets by
+finding almost constant levels of the hitting time distribution for the discretized dynamics. 
+This procedures is itself a novelty since it does not require any spectral information like eigenvectors as in standard approaches, cf.~\cite{prinz2011markov,A19-1}.
+
 % This method only works for the discretized dynamics. and its
-% Therefore, a good discretization is  usually a must for computing the coreset.
-
-In this paper, we mainly focus on the methodology development for MSM
-building in non-equilibrium systems. It is worth noting that the
-numerical example itself presents interesting phenomena: under the
-oscillatory EF, the population of the left-handed $\alpha$-helix
-significantly increases with respect to the equilibrium population
+% Therefore, a good discretization is  usually a must for computing the core set.
+
+In this paper, we mainly focus on the development of the first available methods for MSM
+building in non-equilibrium systems.
+However, the application of these methods to the conformation dynamics of alanine dipeptide results in some observations that are interesting in itself: Under an
+oscillatory EF, the population of the left-handed $\alpha$-helical conformation
+significantly increases relative to the equilibrium population
 (see also the discussions in Ref.~\cite{wang2014exploring}),
-and the leading time-scale is much shorter than the equilibrium case.
-It is in principle possible to apply the non-equilibrium
-linear response theory~\cite{wang2013linear} to build a MSM for the perturbed
-non-equilibrium system with respect to original
-non-equilibrium system
-(the equilibrium counterpart is provided by Ref.~\cite{schutte2014markov}).
-This makes possible the molecular design under
-oscillatory EF, and could be used to answer the question like:
-in order to achieve a certain population of  the left-handed $\alpha$-helix,
-what kind of EF should be used to drive the system.
-In this work, we have not investigated in this direction, however, it will
+and the leading relaxation timescale of the system is much shorter than in the equilibrium case.
+
+A final remark concerning the utilization of the proposed methodology may be in order. 
+Based on an MSM for a given periodic forcing optimal control problems may come into reach:
+Using available methods like non-equilibrium
+linear response theory~\cite{wang2013linear} or computational alchemy for MSMs ~\cite{schutte2014markov} one can construct the MSM for slightly changed parameters (e.g., period and amplitude) of the external forcing by appropriate reweighting of the MSM for the given forcing.
+This in principle allows for  answering questions like the following:
+For which parameters of the external forcing does one achieve maximal population of  the left-handed $\alpha$-helix?
+Such questions, however, will
 be treated in the future studies.

### 2014-11-05 writedown/period.noneq.msm/paper.tex
final revise from CS

@@
 the response of biomolecular conformations to external fields because of their ability to  resolve molecular
-details that \recheck{sometimes} cannot be resolved in experiments. Only
-recently, a \recheck{dynamical} non-equilibrium MD simulation (D-NEMD) method with local thermostating has been proposed~\cite{wang2014exploring} that allows for studying 
+details that sometimes cannot be resolved in experiments. Only
+recently, a non-equilibrium MD simulation (D-NEMD) method with local thermostating has been proposed~\cite{wang2014exploring} that allows for studying 
 non-equilibrium processes in a statistically reliable and thermodynamically consistent way. 
@@
 by comparing the kinetic fingerprints given by the MSM to brute force
-non-equilibrium \recheck{MD} simulations of alanine dipeptide under oscillating EF.
+non-equilibrium MD simulations of alanine dipeptide under oscillating EF.
 The findings are summarized in Sec.~\ref{sec:conclusion} including a chart presenting
@@
 \label{sec:disc}
-\recheck{We consider diffusive molecular dynamics} in an energy landscape $V$ driven by the time-dependent external driving force $E(t)D(x_t)$ with the
+We consider diffusive molecular dynamics in an energy landscape $V$ driven by the time-dependent external driving force $E(t)D(x_t)$ with the
 $T$-periodic external field $E(t)$:
@@
 i.e.~$\beta = 1/(k_B\mathcal T)$.
-\recheck{The Hamiltonain or Langevin dynamics can be treated in the same way as that will be presented, so for sake of simplicity we focus on the discussion of diffusive dynamics.}
+Thermostatted Hamiltonain or Langevin dynamics can be treated in the same way as explained herein, so for sake of simplicity we focus on the discussion of diffusive dynamics.
 The propagation of probability
@@
 \subsection{Spatial discretization: Master equation}
-We will now introduce an appropriate spatial discretization of this kind of non-equilibrium MD -- \recheck{\bluec{(why saying this red sentence?
-we need the spatial discretization for calculating the core sets...)} this is done for reasons of simplicity only; we could completely avoid it for the price of more technical arguments.}
+We will now introduce an appropriate spatial discretization of this kind of non-equilibrium MD --  this is done for reasons of simplicity only; we could completely avoid it for the price of more technical arguments.
 For achieving this discretization, we 
@@
 $\mymu^{\top}P=\mymu^{\top}$.
-From now on, we assume $P$ to be irreducible and aperiodic such that the Perron-Frobenius theorem \recheck{holds, so the eigenvector corresponding to} the eigenvalue $\lambda=1$ is  non-negative componentwise, and unique (up to normalization $\sum_i\mu(i)=1$).
+From now on, we assume $P$ to be irreducible and aperiodic such that the Perron-Frobenius theorem holds, so the eigenvector corresponding to the eigenvalue $\lambda=1$ is  non-negative componentwise, and unique (up to normalization $\sum_i\mu(i)=1$).
 In this case $\mymu$ is the stationary measure in the sense that
@@
 with the same real-space cut-off radius as the van der Waals interactions.
-\recheck{The Gromacs default Fourier spacing of 0.12~nm and B-spline interpolation order of 4 were adopted.}
+The Gromacs default Fourier spacing of 0.12~nm and B-spline interpolation order of 4 were adopted.
 The splitting
@@
 
-For this periodically driven molecular system we will first show how to choose an appropriately fine \recheck{spatial} discretization. After validating this discretization we will consider
-the \recheck{temporal} discretized dynamics generated by the Floquet transition matrix $\vect P$
+For this periodically driven molecular system we will first show how to choose an appropriately fine spatial discretization. After validating this discretization we will consider
+the time-discretized dynamics generated by the Floquet transition matrix $\vect P$
 in comparison to the original NEMD simulation.
@@
 On each NEMD branching trajectory the initial 320~ps are discarded and
-the rest of the trajectory in time interval $[320,4000]$~ps is \recheck{averaged} to estimate
+the rest of the trajectory in time interval $[320,4000]$~ps is averaged to estimate
 the quasi-stationary probability distribution $\rho_{\textrm{st}}$. 
@@
   \vskip -.5cm
-  \caption{\recheck{The forward $q^\fwd_{\confaa}$ and backward 
+  \caption{Forward $q^\fwd_{\confaa}$ and backward 
     $q^\bwd_{\confaa}$ committors
     and their difference $q^\fwd_{\confaa} - q^\bwd_{\confaa}$
-    computed by the NEMD simulations (left
-    column) and the  discretized dynamics (right column).}}
+    computed from the NEMD trajectories (left
+    column) and the  discretized dynamics (right column).}
   \label{fig:num-3}
@@
   \vskip -.5cm
-  \caption{\recheck{The forward $q^\fwd_{\beta}$ and backward
+  \caption{Forward $q^\fwd_{\beta}$ and backward
     $q^\bwd_{\beta}$ committors
     and their difference  $q^\fwd_{\beta} - q^\bwd_{\beta}$ 
-    computed by the NEMD simulations (left
-    column) and the  discretized dynamics (right column).}}
+    computed from NEMD trajectories (left
+    column) and the  discretized dynamics (right column).}
   \label{fig:num-4}
@@
   \vskip -.5cm
-  \caption{\recheck{The forward $q^\fwd_{\confc}$ and backward $q^\bwd_{\confc}$
+  \caption{Forward $q^\fwd_{\confc}$ and backward $q^\bwd_{\confc}$
     committors
     and their difference  $q^\fwd_{\confc} - q^\bwd_{\confc}$ 
-    computed by the NEMD simulations (left
-    column) and the  discretized dynamics (right column).}}
+    computed from NEMD trajectories (left
+    column) and the  discretized dynamics (right column).}
   \label{fig:num-5}
@@
 \end{align}
-where $p(i,t)=\prob(X_t=i)$ is the probability to be in set $\Omega_i$ at time $t$ as governed by the Master equation, and the observable $\mathcal A$ is \recheck{linearly} spanned by the backward
+where $p(i,t)=\prob(X_t=i)$ is the probability to be in set $\Omega_i$ at time $t$ as governed by the Master equation, and the observable $\mathcal A$ is  spanned by the backward
 committors, i.e.,

### 2014-11-06 writedown/period.noneq.msm/submit.jctc/paper.tex
add the source for submission

--- 2014-11-05 writedown/period.noneq.msm/paper.tex
@@
-\documentclass[aps, pre, preprint,unsortedaddress,a4paper,onecolumn]{revtex4}
+\documentclass[journal=jctcce,manuscript=article]{achemso}
+% \documentclass[aps, pre, preprint,unsortedaddress,a4paper,onecolumn,showkeys]{revtex4}
 % \documentclass[aps, pre, reprint,unsortedaddress,a4paper,twocolumn]{revtex4}
@@
 % \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}
-
-\usepackage[fleqn]{amsmath}
+\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
+\setkeys{acs}{keywords = true}
+
+\usepackage{amsmath}
 \usepackage{amssymb}
-\usepackage[dvips]{graphicx}
-\usepackage{color}
-\usepackage{tabularx}
-\usepackage{algorithm}
-\usepackage{algorithmic}
+\usepackage{graphicx}
+% \usepackage{color}
+% \usepackage{tabularx}
+% \usepackage{algorithm}
+% \usepackage{algorithmic}
 
@@
 
-\begin{document}
-
 \title{Building Markov State Models for Periodically Driven Non-Equilibrium Systems}
@@
 \affiliation{CAEP Software Center for High Performance Numerical Simulation, Beijing, China}
-\affiliation{Zuse Institute Berlin, Germany}
+\alsoaffiliation{Zuse Institute Berlin, Germany}
 \author{Christof Sch\"utte}
@@
 \affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
-\affiliation{Zuse Institute Berlin, Germany}
+\alsoaffiliation{Zuse Institute Berlin, Germany}
+
+\begin{document}
 
@@
 The article presents how to construct such MSMs and illustrates their validity and usefulness for the case of conformation dynamics of alanine dipeptide in an external electric field.
+\\
+\textbf{Keywords:} {Non-equilibrium, Markov states model, Alanine dipeptide, Electric field, Floquet theory}
 \end{abstract}
@@
   \centering
-  \includegraphics[width=0.3\textwidth]{fig/confs/c-2.eps}
+  \includegraphics[width=0.3\textwidth]{c-2.eps}
   \caption{A schematic plot of the alanine dipeptide molecule and the dihedral angles $\phi$ and $\psi$.}
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{fig/t010/discrete/fig-cg-prob.eps}  
+  \includegraphics[width=0.45\textwidth]{fig-cg-prob.eps}  
   \caption{Time-dependent probability $\prob\big(\phi_t\in[0,180), \psi_t\in [0,180)\big)$.  The brute force NEMD simulation is compared with different
@@
   \centering
-  \includegraphics[width=0.45\textwidth]{fig/t010/discrete/fig-cg-prob-tau.eps}  
+  \includegraphics[width=0.45\textwidth]{fig-cg-prob-tau.eps}  
   \caption{Time-dependent probability $\prob\big(\phi\in[0,180), \psi\in [0,180)\big)$.
@@
   \centering  
-  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3.steadyDist//fig-dist.eps}\\
+  \includegraphics[width=0.4\textwidth]{fig-dist.eps}\\
   % \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-dist-msm.eps}
-  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3/fig-floquet-vec-1.eps}
+  \includegraphics[width=0.4\textwidth]{fig-floquet-vec-1.eps}
   \caption{The color-scale plot of the logarithmic quasi-stationary distribution $\mymu$
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3/fig-cluster.eps}
+  \includegraphics[width=0.4\textwidth]{fig-cluster.eps}
   \caption{The core set identification. Different colors indicate different core sets: $C_{\confaa}$ (green), $C_\beta$ (yellow) and $C_{\confc}$ (red).
@@
   \centering
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-1.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-msm-1.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig-fht-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig-fht-msm-1.eps}\\
   \vskip -.7cm
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-msm-2.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig-fht-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig-fht-msm-2.eps}\\
   \vskip -.7cm
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-3.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-msm-3.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig-fht-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig-fht-msm-3.eps}\\
   \vskip -.5cm
@@
   \centering
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-1.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-msm-1.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig-commitor-fw-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig-commitor-fw-msm-1.eps}\\
   \vskip -.7cm
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-1.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-msm-1.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig-commitor-bw-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig-commitor-bw-msm-1.eps}\\
   \vskip -.7cm
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-1.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-msm-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig-commitor-diff-1.eps}
+  \includegraphics[width=0.23\textwidth]{fig-commitor-diff-msm-1.eps}
   \vskip -.5cm
@@
   \centering
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-msm-2.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig-commitor-fw-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig-commitor-fw-msm-2.eps}\\
   \vskip -.7cm
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-msm-2.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig-commitor-bw-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig-commitor-bw-msm-2.eps}\\
   \vskip -.7cm
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-2.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-msm-2.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig-commitor-diff-2.eps}
+  \includegraphics[width=0.23\textwidth]{fig-commitor-diff-msm-2.eps}\\
   \vskip -.5cm
@@
   \centering
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-3.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-msm-3.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig-commitor-fw-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig-commitor-fw-msm-3.eps}\\
   \vskip -.7cm
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-3.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-msm-3.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig-commitor-bw-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig-commitor-bw-msm-3.eps}\\
   \vskip -.7cm
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-3.eps}
-  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-msm-3.eps}\\
+  \includegraphics[width=0.23\textwidth]{fig-commitor-diff-3.eps}
+  \includegraphics[width=0.23\textwidth]{fig-commitor-diff-msm-3.eps}\\
   \vskip -.5cm
@@
 %   \centering
-%   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-eig-vec-2.eps}
-%   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-eig-vec-3.eps}
-%   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-eig-vec-4.eps}\\
+%   \includegraphics[width=0.23\textwidth]{fig-eig-vec-2.eps}
+%   \includegraphics[width=0.23\textwidth]{fig-eig-vec-3.eps}
+%   \includegraphics[width=0.23\textwidth]{fig-eig-vec-4.eps}\\
 %   \caption{The eigenfunctions of $P$.}
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3/fig-coreset-prob.eps}
+  \includegraphics[width=0.4\textwidth]{fig-coreset-prob.eps}
   \caption{Comparison of NEMD and MSM long-term kinetics of alanine
@@
   \centering
-  \includegraphics[width=0.48\textwidth]{fig/flowchart/flowchart2.eps}
+  \includegraphics[width=0.48\textwidth]{flowchart2.eps}
   \caption{Flowchart showing optional procedures for MSM building based on NEMD trajectories. A lighter color indicates
@@
 
-\bibliography{ref}{}
-\bibliographystyle{unsrt}
+\begin{thebibliography}{10}
+
+\bibitem{bohr2000microwave}
+Henrik Bohr and Jakob Bohr.
+\newblock Microwave-enhanced folding and denaturation of globular proteins.
+\newblock {\em Phys. Rev. E}, 61(4):4310, 2000.
+
+\bibitem{bohr2000microwave-1}
+Henrik Bohr and Jakob Bohr.
+\newblock Microwave enhanced kinetics observed in ord studies of a protein.
+\newblock {\em Bioelectromagnetics}, 21(1):68--72, 2000.
+
+\bibitem{dePomerai2000cell}
+David de~Pomerai, Clare Daniells, Helen David, Joanna Allan, Ian Duce, Mohammed
+  Mutwakil, David Thomas, Phillip Sewell, John Tattersall, Don Jones, and Peter
+  Candido.
+\newblock Cell biology: Non-thermal heat-shock response to microwaves.
+\newblock {\em Nature}, 405:417--418, 2000.
+
+\bibitem{dePomerai2003microwave}
+David~I de~Pomerai, Brette Smith, Adam Dawe, Kate North, Tim Smith, David~B
+  Archer, Ian~R Duce, Donald Jones, and E~Peter~M Candido.
+\newblock Microwave radiation can alter protein conformation without bulk
+  heating.
+\newblock {\em FEBS letters}, 543(1):93--97, 2003.
+
+\bibitem{mancinelli2004non}
+Fabrizio Mancinelli, Michele Caraglia, Alberto Abbruzzese, Guglielmo
+  d'Ambrosio, Rita Massa, and Ettore Bismuto.
+\newblock Non-thermal effects of electromagnetic fields at mobile phone
+  frequency on the refolding of an intracellular protein: Myoglobin.
+\newblock {\em J. Cell. Biochem.}, 93(1):188--196, 2004.
+
+\bibitem{inskip2001cellular}
+Peter~D Inskip, Robert~E Tarone, Elizabeth~E Hatch, Timothy~C Wilcosky,
+  William~R Shapiro, Robert~G Selker, Howard~A Fine, Peter~M Black, Jay~S
+  Loeffler, and Martha~S Linet.
+\newblock Cellular-telephone use and brain tumors.
+\newblock {\em N. Engl. J. Med.}, 344(2):79--86, 2001.
+
+\bibitem{bekard2013electric}
+I.~Bekard and D.E. Dunstan.
+\newblock Electric field induced changes in protein conformation.
+\newblock {\em Soft Matter}, pages~--, 2014.
+
+\bibitem{budi2005electric}
+A.~Budi, F.S. Legge, H.~Treutlein, and I.~Yarovsky.
+\newblock Electric field effects on insulin chain-b conformation.
+\newblock {\em J. Phys. Chem. B}, 109(47):22641--22648, 2005.
+
+\bibitem{budi2007effect}
+A.~Budi, F.S. Legge, H.~Treutlein, and I.~Yarovsky.
+\newblock Effect of frequency on insulin response to electric field stress.
+\newblock {\em J. Phys. Chem. B}, 111(20):5748--5756, 2007.
+
+\bibitem{budi2008comparative}
+Akin Budi, F~Sue Legge, Herbert Treutlein, and Irene Yarovsky.
+\newblock Comparative study of insulin chain-b in isolated and monomeric
+  environments under external stress.
+\newblock {\em J. Phys. Chem. B}, 112(26):7916--7924, 2008.
+
+\bibitem{astrakas2012structural}
+Loukas~G Astrakas, Christos Gousias, and Margaret Tzaphlidou.
+\newblock Structural destabilization of chignolin under the influence of
+  oscillating electric fields.
+\newblock {\em J. Appl. Phys.}, 111(7):074702--074702, 2012.
+
+\bibitem{damm2012can}
+Markus Damm, Christoph Nusshold, David Cantillo, Gerald~N Rechberger, Karl
+  Gruber, Wolfgang Sattler, and C~Oliver Kappe.
+\newblock Can electromagnetic fields influence the structure and enzymatic
+  digest of proteins? a critical evaluation of microwave-assisted proteomics
+  protocols.
+\newblock {\em J. Proteomics}, 75:5533--5543, 2012.
+
+\bibitem{english2009nonequilibrium}
+N.J. English, G.Y. Solomentsev, and P.~O'Brien.
+\newblock Nonequilibrium molecular dynamics study of electric and low-frequency
+  microwave fields on hen egg white lysozyme.
+\newblock {\em J. Chem. Phys.}, 131:035106, 2009.
+
+\bibitem{solomentsev2012effects}
+G.Y. Solomentsev, N.J. English, and D.A. Mooney.
+\newblock Effects of external electromagnetic fields on the conformational
+  sampling of a short alanine peptide.
+\newblock {\em J. Comput. Chem.}, 33:917--923, 2012.
+
+\bibitem{wang2014exploring}
+Han Wang, Christof Sch{\"u}tte, Giovanni Ciccotti, and Luigi Delle~Site.
+\newblock Exploring the conformational dynamics of alanine dipeptide in
+  solution subjected to an external electric field: {A} nonequilibrium
+  molecular dynamics simulation.
+\newblock {\em Journal of Chemical Theory and Computation}, 10(4):1376--1386,
+  2014.
+
+\bibitem{A19-31}
+Ch. Sch\"utte and M.~Sarich.
+\newblock {\em Metastability and {{Markov}} State Models in Molecular Dynamics:
+  Modeling, Analysis, Algorithmic Approaches}, volume~24 of {\em Courant
+  Lecture Notes}.
+\newblock American Mathematical Society, December 2013.
+
+\bibitem{prinz2011markov}
+J.H. Prinz, H.~Wu, M.~Sarich, B.~Keller, M.~Senne, M.~Held, J.D. Chodera,
+  C.~Sch{\"u}tte, and F.~No{\'e}.
+\newblock {{Markov} models of molecular kinetics: Generation and validation}.
+\newblock {\em J. Chem. Phys.}, 134:174105, 2011.
+
+\bibitem{A19-1}
+G.~R. Bowman, V.~S. Pande, and F.~No\'e, editors.
+\newblock {\em An Introduction to {{Markov}} State Models and Their Application
+  to Long Timescale Molecular Simulation}, volume 797 of {\em Advances in
+  Experimental Medicine and Biology}.
+\newblock Springer, 2014.
+
+\bibitem{A19-49}
+M.~Senne, B.~Trendelkamp-Schroer, A.~S. J.~S. Mey, Ch. Sch\"utte, and F.~No\'e.
+\newblock Emma - a software package for {{Markov}} model building and analysis.
+\newblock {\em J. Chem. Theory Comput.}, 8:2223--2238, 2012.
+
+\bibitem{MSMBuilder}
+Kyle~A Beauchamp, Gregory R~Bowman andThomas J~Lane, Lutz Maibaum, Imran~S
+  Haque, and Vijay~S Pande.
+\newblock {MSMBuilder2}: {M}odeling conformational dynamics at the picosecond
+  to millisecond scale.
+\newblock {\em J Chem Theor Comput}, 2011.
+
+\bibitem{schuette2011markov}
+C.~Sch{\"u}tte, F.~No{\'e}, J.~Lu, M.~Sarich, and E.~Vanden-Eijnden.
+\newblock {{Markov} State Models based on Milestoning}.
+\newblock {\em J. Chem. Phys.}, 134:204105, 2011.
+
+\bibitem{sarich2010approximation}
+Marco Sarich, Frank No{\'e}, and Christof Sch{\"u}tte.
+\newblock On the approximation quality of {Markov} state models.
+\newblock {\em Multiscale Modeling \& Simulation}, 8(4):1154--1177, 2010.
+
+\bibitem{Eigenvalues}
+N.~Djurdjevac, M.~Sarich, and Ch~Sch{\"u}tte.
+\newblock Estimating the eigenvalue error of {M}arkov state models.
+\newblock {\em Multiscale Modeling \& Simulation}, 10(1):61--81, 2012.
+
+\bibitem{PNAS09}
+F.~No\'{e}, C.~Sch\"utte, E.~Vanden-Eijnden, L.~Reich, and T.~R. Weikl.
+\newblock Constructing the full ensemble of folding pathways from short
+  off-equilibrium simulations.
+\newblock {\em Proc. Natl. Acad. Sci. USA}, 106:19011--19016, 2009.
+
+\bibitem{kohlhoff2014cloud}
+Kai~J Kohlhoff, Diwakar Shukla, Morgan Lawrenz, Gregory~R Bowman, David~E
+  Konerding, Dan Belov, Russ~B Altman, and Vijay~S Pande.
+\newblock Cloud-based simulations on google exacycle reveal ligand modulation
+  of gpcr activation pathways.
+\newblock {\em Nature chemistry}, 6(1):15--21, 2014.
+
+\bibitem{A19-39}
+B.~G. Keller, J.-H. Prinz, and F.~No\'e.
+\newblock {{Markov}} models and dynamical fingerprints: {U}nraveling the
+  complexity of molecular kinetics.
+\newblock {\em Chem. Phys.}, 396:92--107, 2012.
+
+\bibitem{PrinzKellerNoe_PCCP11_Perspective}
+Jan-Hendrik Prinz, Bettina~G. Keller, and Frank No{\'e}.
+\newblock Probing molecular kinetics with {{{Markov}}} models: Metastable
+  states, transition pathways and spectroscopic observables.
+\newblock {\em Phys. Chem. Chem. Phys.}, 13:16912--16927, 2011.
+
+\bibitem{pande2010everything}
+V.S. Pande, K.~Beauchamp, and G.R. Bowman.
+\newblock Everything you wanted to know about {Markov} state models but were
+  afraid to ask.
+\newblock {\em Methods}, 52(1):99--105, 2010.
+
+\bibitem{A19-29}
+M.~Sarich, Ralf Banisch, C.~Hartmann, and Ch. Sch\"utte.
+\newblock {{Markov}} state models for rare events in molecular dynamics.
+\newblock {\em Entropy (Special Issue)}, 16(1):258--286, December 2013.
+
+\bibitem{latorre2011structure}
+Juan~C Latorre, Philipp Metzner, Carsten Hartmann, and Christof Sch{\"u}tte.
+\newblock A structure-preserving numerical discretization of reversible
+  diffusions.
+\newblock {\em Commun. Math. Sci}, 9(4):1051--1072, 2011.
+
+\bibitem{floquet1883equations}
+G~Floquet.
+\newblock Sur les {\'e}quations diff{\'e}rentielles lin{\'e}aires {\`a}
+  coefficients p{\'e}riodiques.
+\newblock {\em Annales scientifiques de l'{\'E}cole Normale Sup{\'e}rieure},
+  12:47--82, 1883.
+
+\bibitem{A19-26}
+F.~No\'e, H.~Wu, J.-H. Prinz, and N.~Plattner.
+\newblock Projected and hidden {{Markov}} models for calculating kinetics and
+  metastable states of complex molecules.
+\newblock {\em J. Chem. Phys.}, 139:184114, 2013.
+
+\bibitem{BucheteHummer}
+Nicaolae~V. Buchete and Gerhard Hummer.
+\newblock Coarse master equations for peptide folding dynamics.
+\newblock {\em J. Phys. Chem. B}, 112:6057--6069, 2008.
+
+\bibitem{sarich2014utilizing}
+Marco Sarich and Christof Sch{\"u}tte.
+\newblock Utilizing hitting times for finding metastable sets in non-reversible
+  {Markov} chains.
+\newblock {\em submitted to the Journal of Computational Dynamics}, 2014.
+
+\bibitem{discreteTPT}
+P.~Metzner, Ch. Sch{\"u}tte, and E.~Vanden-Eijnden.
+\newblock Transition path theory for {M}arkov jump processes.
+\newblock {\em Multiscale Modeling and Simulation}, 7(3):1192--1219, 2009.
+
+\bibitem{djurdjevac2010markov}
+N.~Djurdjevac, M.~Sarich, and C.~Sch{\"u}tte.
+\newblock On {{Markov}} state models for metastable processes.
+\newblock In {\em Proceedings of the International Congress of Mathematicians},
+  volume 901, pages 3105--3131, 2010.
+
+\bibitem{chodera2007automatic}
+J.D. Chodera, N.~Singhal, V.S. Pande, K.A. Dill, and W.C. Swope.
+\newblock Automatic discovery of metastable states for the construction of
+  {Markov} models of macromolecular conformational dynamics.
+\newblock {\em J. Chem. Phys.}, 126:155101, 2007.
+
+\bibitem{foloppe2000all}
+Nicolas Foloppe and Alexander~D MacKerell~Jr.
+\newblock All-atom empirical force field for nucleic acids: I. parameter
+  optimization based on small molecule and condensed phase macromolecular
+  target data.
+\newblock {\em J. Comput. Chem.}, 21(2):86--104, 2000.
+
+\bibitem{jorgensen1983comparison}
+William~L Jorgensen, Jayaraman Chandrasekhar, Jeffry~D Madura, Roger~W Impey,
+  and Michael~L Klein.
+\newblock Comparison of simple potential functions for simulating liquid water.
+\newblock {\em J. Chem. Phys.}, 79(2):926--935, 1983.
+
+\bibitem{mackerell2004extending}
+Alexander~D MacKerell, Michael Feig, and Charles~L Brooks~III.
+\newblock Extending the treatment of backbone energetics in protein force
+  fields: Limitations of gas-phase quantum mechanics in reproducing protein
+  conformational distributions in molecular dynamics simulations.
+\newblock {\em J. Comput. Chem.}, 25(11):1400--1415, 2004.
+
+\bibitem{pronk2013gromacs}
+S.~Pronk, S.~P{\'a}ll, R.~Schulz, P.~Larsson, P.~Bjelkmar, R.~Apostolov, M.R.
+  Shirts, J.C. Smith, P.M. Kasson, D.~van~der Spoel, Hess B., and Lindahl E.
+\newblock Gromacs 4.5: a high-throughput and highly parallel open source
+  molecular simulation toolkit.
+\newblock {\em Bioinformatics}, pages 1--10, 2013.
+
+\bibitem{bjelkmar2010implementation}
+P\"{a}r Bjelkmar, Per Larsson, Michel~A Cuendet, Berk Hess, and Erik Lindahl.
+\newblock Implementation of the charmm force field in gromacs: Analysis of
+  protein stability effects from correction maps, virtual interaction sites,
+  and water models.
+\newblock {\em J. Chem. Theory Comput.}, 6(2):459--466, 2010.
+
+\bibitem{parrinello1981polymorphic}
+M.~Parrinello and A.~Rahman.
+\newblock Polymorphic transitions in single crystals: A new molecular dynamics
+  method.
+\newblock {\em J. Appl. Phys.}, 52:7182, 1981.
+
+\bibitem{darden1993pme}
+T.~Darden, D.~York, and L.~Pedersen.
+\newblock {Particle mesh Ewald: An $N \log (N)$ method for Ewald sums in large
+  systems}.
+\newblock {\em J. Chem. Phys.}, 98:10089, 1993.
+
+\bibitem{essmann1995spm}
+U.~Essmann, L.~Perera, M.L. Berkowitz, T.~Darden, H.~Lee, and L.G. Pedersen.
+\newblock {A smooth Particle Mesh Ewald method}.
+\newblock {\em J. Chem. Phys.}, 103(19):8577, 1995.
+
+\bibitem{wang2010optimizing}
+Han Wang, Florian Dommert, and Christian Holm.
+\newblock Optimizing working parameters of the smooth particle mesh ewald
+  algorithm in terms of accuracy and efficiency.
+\newblock {\em The Journal of chemical physics}, 133(3):034117, 2010.
+
+\bibitem{hess1997lincs}
+B.~Hess, H.~Bekker, H.J.C. Berendsen, and J.G.E.M. Fraaije.
+\newblock {LINCS: a linear constraint solver for molecular simulations}.
+\newblock {\em J. Comput. Chem.}, 18(12):1463--1472, 1997.
+
+\bibitem{miyamoto2004settle}
+S.~Miyamoto and P.A. Kollman.
+\newblock {SETTLE: an analytical version of the SHAKE and RATTLE algorithm for
+  rigid water models}.
+\newblock {\em J. Comput. Chem.}, 13(8):952--962, 2004.
+
+\bibitem{PCCAplus}
+P.~Deuflhard and M.~Weber.
+\newblock Robust {P}erron cluster analysis in conformation dynamics.
+\newblock {\em Linear Algebra and its Applications}, 161(184), 2005.
+\newblock 398 Special issue on matrices and mathematical biology.
+
+\bibitem{PrinzHeldSmithNoe_Committorprep}
+Jan-Hendrik Prinz, Martin Held, Jeremy~C. Smith, and Frank No{\'e}.
+\newblock Efficient computation of committor probabilities and transition state
+  ensembles.
+\newblock {\em SIAM Multiscale Model. Simul.}, 9:545, 2011.
+
+\bibitem{wang2013linear}
+Han Wang, Carsten Hartmann, and Christof Sch{\"u}tte.
+\newblock Linear response theory and optimal control for a molecular system
+  under non-equilibrium conditions.
+\newblock {\em Molecular Physics}, 111(22-23):3555--3564, 2013.
+
+\bibitem{schutte2014markov}
+Christof Sch{\"u}tte, Adam Nielsen, and Marcus Weber.
+\newblock Markov state models and molecular alchemy.
+\newblock {\em Molecular Physics}, ahead-of-print, 2014.
+
+\bibitem{seifert2012stochastic}
+Udo Seifert.
+\newblock Stochastic thermodynamics, fluctuation theorems and molecular
+  machines.
+\newblock {\em Reports on Progress in Physics}, 75(12):126001, 2012.
+
+\end{thebibliography}
+% \bibliography{ref}{}
+% % \bibliographystyle{unsrt}
 

### 2014-11-06 writedown/period.noneq.msm/coverletter/letter-jctc.tex
add keywords, some revises from CS

\documentclass{letter}

\usepackage{graphicx}

\renewcommand{\baselinestretch}{1.0}
% \setlength{\footskip}{0cm}
%\addtolength{\textheight}{10cm}
% \sloppy

\address{Han Wang\\
  Zuse Institute Berlin \\
  Takustrasse 7\\
  14195 Berlin, Germany 
}
\signature{Han Wang}

% \def\urltilda{\kern -.15em\lower .7ex\hbox{\~{}}\kern .04em}
% \def\urlunder{\lower .1ex\hbox{\_{}}\kern .04em}
% \def\urldot{\kern -.10em.\kern -.10em}
% \def\urlhttp{http\kern -.10em\lower -.1ex\hbox{:}\kern -.12em\lower 0ex\hbox{/}\kern -.18em\lower 0ex\hbox{/}}
% \parindent0ex

\begin{document}

\begin{letter}{
    The Editors of\\
    Journal of Chemical Theory and Computation\\
    \vskip 1cm
  }
% \begin{picture}(0,0)
%   \put(-30,22){
%     \parbox{0.25\textwidth}{
% %	\includegraphics[scale=0.4]{logo-icp-notext.pdf}
%     }
%   }
%   \put(264,10){
%     \parbox{0.25\textwidth}{
% 	\includegraphics[scale=0.28]{Fub-logo.eps}
%     }
%   }
% \end{picture}

\opening{Dear Editors,\vskip .5cm}
Hereby we would like to submit our article: 
\textit{``Building Markov State Models for Periodically Driven Non-Equilibrium Systems''
} by H. Wang and C. Sch\"utte to the
\textit{Journal of Chemical Theory and Computation}, as a regular article.

In this paper, we demonstrate how to build the Markov state model
(MSM) for the non-equilibrium systems under a periodic external
driving.  The MSM reproduces the essential long timescale
conformational dynamics of the original system, and at the same time
it does not require the ergodicity of each single molecular
trajectory.  Therefore, it does not only describes, but also provides
more insightful understanding of the non-equilibrium system than the
standard analyses of the molecular trajectories.  Our methods are
tested and validated by an example non-equilibrium system: The alanine
dipeptide under periodic electric field.

To the knowledge of the authors, this work is the first attempt of
building MSM for non-equilibrium systems under periodic external
driving. The significance of our method is that it does not assume
reversibility of the dynamics, as it is mostly done in building MSM
for equilibrium systems.

As experts who can judge the validity of the work we suggest the
following names:
\begin{itemize}\itemsep -1pt
\item Vijay Pande, Stanford University, pande@stanford.edu
\item John Chodera, Memorial Sloan Kettering Cancer Center, choderaj@mskcc.org
\item Giovanni Ciccotti,  University of Rome La Sapienza, Giovanni.Ciccotti@roma1.infn.it
\end{itemize}

\vskip 1cm

Best regards,\\
Han Wang

\end{letter} \end{document}

### 2014-11-06 writedown/period.noneq.msm/paper.tex
add keywords, some revises from CS

@@
-\documentclass[aps, pre, preprint,unsortedaddress,a4paper,onecolumn]{revtex4}
+\documentclass[aps, pre, preprint,unsortedaddress,a4paper,onecolumn,showkeys]{revtex4}
 % \documentclass[aps, pre, reprint,unsortedaddress,a4paper,twocolumn]{revtex4}
@@
 \affiliation{CAEP Software Center for High Performance Numerical Simulation, Beijing, China}
-\affiliation{Zuse Institute Berlin, Germany}
+\affiliation{Zuse Institute Berlin (ZIB), Germany}
 \author{Christof Sch\"utte}
-\email{Christof.Schuette@fu-berlin.de}
+\email{schuette@zib.de}
 \affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
-\affiliation{Zuse Institute Berlin, Germany}
+\affiliation{Zuse Institute Berlin (ZIB), Germany}
 
@@
 \end{abstract}
+
+\keywords{Non-equilibrium, Markov states model, Alanine dipeptide, Electric field, Floquet theory}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Core Set identification}
+\subsection{Core set identification}
 
@@
 
-\subsection{Irreversibility of the periodical symmetrical dynamics}
+\subsection{Irreversibility of the periodic time-symmetric dynamics}
 
@@
 
-\section{The prove of identity $\hat P = \hat T\hat M^{-1}$}
+\section{Prove of the identity $\hat P = \hat T\hat M^{-1}$}
 \label{sec:app-ptm}

### 2014-11-08 writedown/zm/paper.water/main.tex
merge with I.F., add my revise

@@
-\documentclass[aip,jcp,a4paper,preprint,unsortedaddress,onecolumn,fleqn]{revtex4-1}
+%2multibyte Version: 5.50.0.2952 CodePage: 932
 % \documentclass[reprint,unsortedadress,oneclumn]{revtex4-1}
+%\documentclass[aip,jcp,a4paper,preprint,unsortedaddress,onecolumn,fleqn]{revtex4-1}
 
+\documentclass[a4paper,preprint,unsortedaddress,onecolumn,fleqn]{revtex4}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \usepackage{amsmath,amssymb,amsfonts,latexsym}
@@
 \usepackage{rotating,booktabs}
+
+\setcounter{MaxMatrixCols}{10}
+%TCIDATA{OutputFilter=LATEX.DLL}
+%TCIDATA{Version=5.50.0.2952}
+%TCIDATA{Codepage=932}
+%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
+%TCIDATA{BibliographyScheme=BibTeX}
+%TCIDATA{LastRevised=Friday, November 07, 2014 19:42:26}
+%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
+%TCIDATA{Language=American English}
 
@@
 \newcommand{\systemlb}{L_1}
-
+% \input{tcilatex}
 \begin{document}
 
-\title{A Critical Appraisal of Zero-Multiple Method in Classical Water Simulation}
+\title{A Critical Appraisal of the Zero-Multiple Method: Structural,
+Thermodynamic, Dielectric, and Dynamical Properties of a Water System}
 \author{Han Wang}
 \email{han.wang@fu-berlin.de}
-\affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road 6, 100088 Beijing, China}
 \author{Ikuo Fukuda}
 \email{ifukuda@protein.osaka-u.ac.jp}
-\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita, Osaka 565-0871, Japan}
-\affiliation{RIKEN (The Institute of Physical and Chemical Research), 2-1 Hirosawa, Wako, Saitama 351-0198, Japan}
 
@@
 \maketitle
+\affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road
+6, 100088 Beijing, China}
+\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
+Osaka 565-0871, Japan}
+\affiliation{RIKEN (The Institute of Physical and Chemical Research), 2-1 Hirosawa, Wako,
+Saitama 351-0198, Japan}
+
+% A Critical Appraisal of Zero-Multiple Method in Classical Water Simulation}
 
@@
 
-A very short overview of the existing electrostatic interaction methods. Two classes in general:
-Long-range treatment, e.g.~Ewald and derived methods like SPME.
-Short-range treatment, like RF and ZM.
+A very short overview of the existing electrostatic interaction methods. Two
+classes in general: Long-range treatment, e.g.~Ewald and derived methods
+like SPME. Short-range treatment, like RF and ZM.
 
-The importance of developing a short-range method for the electrostatic interaction.
+The importance of developing a short-range method for the electrostatic
+interaction.
 
@@
 
-The purpose of this work: Extensive and strict tests investigating the reliability of Zero-Multiple method in water simulation, which is the most important solvent.
+The purpose of this work: Extensive and strict tests investigating the
+reliability of Zero-Multiple method in water simulation, which is the most
+important solvent.
 
@@
 
-\section{Zero-Multiple Method}
+[{\color{blue} COMMENT: I can contribute this section later}]
 
-Introduction of the ZM method, formula...
+\section{Zero-Multipole Summation}
 
-\recheck{If we want to discuss the issue of cut-off method, a short
-  introduction of the group cut-off v.s.~the atom cut-off
-  method. (will discuss the implementation in gromacs later)}
+Introduction of the ZM method, formula...[ {\color{blue} COMMENT: I can
+write here later}]
 
-\section{Benchmark quantities}
+{\color{red} If we want to discuss the issue of cut-off method, a short
+introduction of the group cut-off v.s.~the atom cut-off method. (will
+discuss the implementation in gromacs later) }[ {\color{blue} COMMENT: what
+do you mean? \recheck{I mean the explanation of group and atomistic cut-off method. the traditional gromacs uses gropu cut-off as default. We need instead the atomistic cut-off}}]
 
-In order to investigate the performance of ZM method, we simulation
-the water system by using both SPME and ZM methods, and calculate a set
-of \emph{benchmark quantities}.  This set covers a broad range of
-water properties that are of general interest. It includes the
-structure property (radial distribution function), the thermodynamic
-properties (pressure, excess chemical potential, constant
-volume/pressure heat capacity, isothermal compressibility, thermal
-expansion coefficient), dielectric properties (dielectric constant and
-Kirkwood-G factor) and dynamical properties (diffusion constant and
-viscosity).
-The definitions and computing methods of these quantities are provided in details
-in Appendix.~\ref{appendix:benchmark}.
-By comparing ZM to SPME, a good consistency in computing
-the benchmark quantities would indicate a good accuracy of the ZM
-method.
-More importantly, the benchmark tests provide knowledge in the
-stituations when the ZM method does not work so well, and help in
-finding the way of tuning the working parameters to achieve higher accuracy.
-The ZM method is also compared to the traditional short-range method: RF.
+\section{Material and Methods}
 
-\section{Simulation protocols}
+\subsection{Benchmark quantities}
 
-In this work, we focus on the water system modeled by
-TIP3P~\cite{jorgensen1983comparison} point-charge water model.
+In order to investigate the performance of ZM method, we simulate the water
+system by using both SPME and ZM methods, and evaluate a set of \emph{%
+benchmark quantities}. This set covers a broad range of water properties
+that are of general interest. It includes the structure property (radial
+distribution function), the thermodynamic properties (pressure, excess
+chemical potential, constant volume/pressure heat capacity, isothermal
+compressibility, thermal expansion coefficient), dielectric properties
+(dielectric constant and Kirkwood-G factor) and dynamical properties
+(diffusion constant and viscosity). The definitions and computing methods of
+these quantities are provided in details in Appendix.~\ref%
+{appendix:benchmark}. By comparing ZM to SPME, a good consistency in
+computing the benchmark quantities would indicate a good accuracy of the ZM
+method. More importantly, the benchmark tests provide knowledge in the
+situations when the ZM method does not work so well, and help in finding the
+way of tuning the working parameters to achieve higher accuracy. The ZM
+method is also compared to the traditional short-range method: RF.
+
+\subsection{Simulation protocols}
+\label{sec:protocols}
+In this work, we focus on a system of water molecules modeled
+by TIP3P~\cite{jorgensen1983comparison} point-charge particles. 
 % Other point-charge water models differ in the modeling parameters, and
-The accuracy of ZM method in other water models is out of the scope of the current work.
-However, since the point-charge water models share similar idea, and  only differ
-in the model parameters, it is highly probable that ZM works well with other water models if it works
-well with TIP3P.
+The accuracy of ZM method in other water models is out of the scope of the
+current work. However, since the point-charge water models share similar
+idea, and only differ in the model parameters, it is highly probable that ZM
+works well with other water models if it works well with TIP3P.
 
-All simulations were performed by Gromacs~4.6.5~\cite{hess2008gromacs, pronk2013gromacs} complied by GNU C compiler with single-precision floating point.
-The size of the systems and corresponding number of molecules used for MD simulations are summarized in Tab.~\ref{tab:tmp1}.
-The benchmark quantities were calculated in either  canonical (NVT) or isothermal-isobaric (NPT) ensemble, with equilibrium temperature $T=300$~K.
-In order to simulate at the desired temperature,
-the systems $\systemsb$ and $\systemsbp$ were coupled to Nose-Hoover~\cite{nose1984molecular,hoover1985canonical} thermostat with time-scale $\tau_T = 1.0$~ps,
-while systems $\systemmb$, $\systemmbp$, $\systemla$, $\systemlb$ and $\systemlbp$ were coupled to Langevin thermostat with time-scale $\tau_T = 0.1$~ps.
-In the NPT simulations, the systems were further coupled
-to the Parrinello-Rahman barostat~\cite{parrinello1980crystal,parrinello1981polymorphic} (in Gromacs implementation)
-with time-scale $\tau_P = 0.5$~ps to equilibriate the system at 1~Bar.
-All systems were integrated with leap-frog scheme at a time-step of 0.001~ps.
-The neighbor lists were updated every 5 time-steps.
-The ``\texttt{group}'' cut-off scheme in Gromacs was used. In order to mimic the atomistic
-cut-off manner, the radius for neighbor list building was set 0.3~nm
-larger than the cut-off radius (the maximum of Coulomb cut-off and the van der Waals cut-off).
-To make sure the van der Waals interactions were cut-off in a smooth way,
-they are modified in a shell of $0.05$~nm width near the cut-off sphere by the Gromacs ``\texttt{shift}'' method.
-The ZM method was implemented in Gromacs with the tabulated electrostatic interaction. A home-made code was used to generate the interaction tables.
-The short-range part of SPME method is smoothed in a shell of $0.05$~nm width  by the Gromacs ``\texttt{pme-switch}'' method.
-The reciprocal space
-grid spacing is set to 0.06~nm, with B-Spline interpolation order of 6.
-These parameters are chosen to be more accurate than the Gromacs default choices (grid spacing 0.12~nm and interpolation order 4).
-The splitting parameter is optimized by the error estimate for the SPME method, which is implemented in Gromacs by tool ``\texttt{g\_pme\_error}''~\cite{wang2010optimizing}.
-The optimized real space and reciprocal space force computing errors were equally distributed as $1.4\times10^{-4}$~kJ/(mol nm).
-Since the magnitude of the forces are of order $10^{2}$~kJ/(mol nm), this force computing precision almost reaches the limit of the single-precision representation of the floating point numbers.
-In the simulations of the RF method, the interactions were cut-off in the group manner,
-so the radius for neighbor list building is set identical to the cut-off radius.
-No cut-off smoothing of the electrostatic interaction was applied in the cases of RF simulation.
+All simulations were performed by Gromacs~4.6.5~\cite{hess2008gromacs,
+pronk2013gromacs} complied by GNU C compiler with single-precision floating
+point. The size of the systems and corresponding number of molecules used
+for MD simulations are summarized in Tab.~\ref{tab:tmp1}. The benchmark
+quantities were calculated in either canonical (NVT) or isothermal-isobaric
+(NPT) ensemble, with equilibrium temperature $T=300$~K. In order to simulate
+at the desired temperature, the systems $S_{1}$ and $S_{1}^{\prime }$ were
+coupled to Nos\'{e}-Hoover~\cite{nose1984molecular,hoover1985canonical}
+thermostat with time-scale $\tau _{T}=1.0$~ps, while systems $M_{1}$, $%
+M_{1}^{\prime }$, $L_{0}$, $L_{1}$ and $L_{1}^{\prime }$ were coupled to
+Langevin thermostat with time-scale $\tau _{T}=0.1$~ps. In the NPT
+simulations, the systems were further coupled to the Parrinello-Rahman
+barostat~\cite{parrinello1980crystal,parrinello1981polymorphic} (in Gromacs
+implementation) with time-scale $\tau _{P}=0.5$~ps to equilibrate the system
+at 1~Bar. All systems were integrated with leap-frog scheme at a time-step
+of 0.001~ps.
 
-\begin{table}
-  \centering
-  \caption{A list of systems simulated in this work. We report, from left to right, the number of water
-    molecules in the system (TIP3P model), equilibrium box size, length of equilibriation, length of productive trajectory.
-  }
+The neighbor lists were updated every 5 time-steps. The \textquotedblleft 
+\texttt{group}\textquotedblright\ cut-off scheme in Gromacs was used. In
+order to mimic the atomistic cut-off manner, the radius for neighbor list
+building was set 0.3~nm larger than the cut-off radius (the maximum of
+Coulomb cut-off and the van der Waals cut-off). [ {\color{blue} COMMENT:
+Yes,..., this is not easy to understand how we mimic AC. \recheck{it should be OK as it is now.}}] To make sure the
+van der Waals interactions were cut-off in a smooth way, they are modified
+in a shell of $0.05$~nm width near the cut-off sphere by the Gromacs
+\textquotedblleft \texttt{shift}\textquotedblright\ method.
+
+The short-range part of SPME method \recheck{was cut-offed at 1.9~nm, and was} smoothed in a shell of $0.05$~nm
+width by the Gromacs \textquotedblleft \texttt{pme-switch}%
+\textquotedblright\ method. The reciprocal space grid spacing was set to
+0.06~nm, with B-Spline interpolation order of 6. These parameters were
+chosen to be more accurate than the Gromacs default choices (grid spacing
+0.12~nm and interpolation order 4). The splitting parameter was optimized by
+the error estimate for the SPME method, which is implemented in Gromacs by
+tool \textquotedblleft \texttt{g\_pme\_error}\textquotedblright ~\cite%
+{wang2010optimizing}. The optimized real space and reciprocal space force
+computing errors were equally distributed as $1.4\times 10^{-4}$~kJ/(mol
+nm). Since the magnitude of the forces are of order $10^{2}$~kJ/(mol nm),
+this force computing precision almost reaches the limit of the
+single-precision representation of the floating point numbers.
+
+In the simulations of the RF method, the interactions were cut-off in the
+group manner, so the radius for neighbor list building is set identical to
+the cut-off radius. No cut-off smoothing of the electrostatic interaction
+was applied in the cases of RF simulations. We used $1.2$~nm
+cut-off and the experimental dielectric constant $\varepsilon _{\textrm{rf}}=80$.
+
+The ZM method was implemented in Gromacs with the tabulated electrostatic
+interaction. A home-made code was used to generate the interaction tables.
+
+\begin{table}[tbp]
+\caption{A list of systems simulated in this work. We report, from left to
+right, the number of water molecules in the system (TIP3P model),
+equilibrium box size, length of equilibriation, length of productive
+trajectory. }
+\label{tab:tmp1}\centering
 \vskip .5cm 
-  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}c rrrr}\hline\hline
-    System      & $N$ & $V$ [$\textrm{nm}^3$]  & $T_{\textrm{eq}}$ [ps] & $T_{\textrm{prod}}$ [ps]  \\\hline
-    $\systemsbp$         &   2,500        & $4.24^3$              & --           &  6,000        \\
-    $\systemsb$          & 2,500          & $4.24^3$              & 3,000        & 27,000        \\\hline
-    $\systemmbp$         &   4,500        & $5.15^3$              & --           &  6,000        \\
-    $\systemmb$          & 4,500          & $5.15^3$              & 3,000        & 17,000        \\\hline
-    $\systemla$          &   13,824       & $7.49^3$              & 200          & 1,800         \\
-    $\systemlbp$         &   13,824       & $7.49^3$              & --           & 10,000        \\
-    $\systemlb$          &   13,824       & $7.49^3$              & 3,000        & 17,000        \\
+\begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}crrrr}
 \hline\hline
-  \end{tabular*}
-  \label{tab:tmp1}
+System & $N$ & $V$ [$\text{nm}^3$] & $T_{\text{eq}}$ [ps] & $T_{\text{prod}}$
+[ps] \\ \hline
+$S^{\prime }_1$ & 2,500 & $4.24^3$ & -- & 6,000 \\ 
+$S_1$ & 2,500 & $4.24^3$ & 3,000 & 27,000 \\ \hline
+$M^{\prime }_1$ & 4,500 & $5.15^3$ & -- & 6,000 \\ 
+$M_1$ & 4,500 & $5.15^3$ & 3,000 & 17,000 \\ \hline
+$L_0$ & 13,824 & $7.49^3$ & 200 & 1,800 \\ 
+$L^{\prime }_1$ & 13,824 & $7.49^3$ & -- & 10,000 \\ 
+$L_1$ & 13,824 & $7.49^3$ & 3,000 & 17,000 \\ \hline\hline
+\end{tabular*}%
 \end{table}
 
-The initial configurations were prepared by in
-the following steps:
-(1) An NPT simulation of system $\systemla$ with SPME
-electrostatic was performed. The equilibrium density (984.1~$\textrm{kg}/\textrm{m}^{3}$) of the system is calculated
-from this simulation.
-(2) Initial configurations that contains 2500, 4500 and
-13824 molecules were generated at the calculated equilibrium
-density.
-(3) NVT simulations with SPME electrostatic for system $\systemsbp$, $\systemmbp$
-and $\systemlbp$ are performed.
-(4) The output configurations of $\systemsbp$ and $\systemmbp$ were used as
-initial configurations for system $\systemsb$ and $\systemmb$, respectively.  The output configuration of
-$\systemlbp$ was used as initial configurations for system $\systemla$ and $\systemlb$.
-% The SPME
+The initial configurations were prepared by in the following steps: (1) An
+NPT simulation of system $L_{0}$ with SPME electrostatic was performed. The
+equilibrium density (984.1~$\text{kg}/\text{m}^{3}$) of the system is
+calculated from this simulation. (2) Initial configurations that contains
+2500, 4500 and 13824 molecules were generated at the calculated equilibrium
+density. (3) NVT simulations with SPME electrostatic for system $%
+S_{1}^{\prime }$, $M_{1}^{\prime }$ and $L_{1}^{\prime }$ are performed. (4)
+The final configurations of $S_{1}^{\prime }$ and $M_{1}^{\prime }$
+were used as initial configurations for system $S_{1}$ and $M_{1}$,
+respectively. The final configuration of $L_{1}^{\prime }$ was
+used as initial configurations for system $L_{0}$ and $L_{1}$. % The SPME
 % parameters for all simulations reported by this work is: real space
 % cut-off 1.90~nm.
+% [ {\color{blue} COMMENT: The following has been moved here, OK? If we need a
+%   special care, please modify.}]
+Using the density in the NVT simulation with
+SPME electrostatic, the pressure ($-0.4\pm 1.5$~Bar) is reproducing the
+target pressure of 1.0~Bar, which means the system is in desired
+thermodynamic state.
 
@@
 
-The smallest system $\systemsb$ was adopted,
-because for the quantities that are computed  by estimating fluctuations (in this
-work heat capacities, compressibility, thermal expansion coefficient, dielectric constant, diffusion constant and
-viscosity are fluctuations. See details in Appendix~\ref{appendix:benchmark}), simply increase the size of the
-system does not improve the accuracy of the 
-simulation~\cite{milchev1986fluctuations,ferrenberg1991statistical}.
-The optimal way of measuring these properties
-is to simulate with smaller systems
+The smallest system $S_{1}$ was adopted for the quantities that are computed
+by estimating fluctuations (in this work heat capacities, compressibility,
+thermal expansion coefficient, dielectric constant, diffusion constant and
+viscosity are fluctuations. See details in Appendix~\ref{appendix:benchmark}%
+), because simply increasing the size of the system does not
+improve the accuracy of the simulation~\cite%
+{milchev1986fluctuations,ferrenberg1991statistical}. The optimal way of
+measuring these properties is to simulate with smaller systems 
 % (as far as the finite size effect is negligible)
-and run longer simulations for longer time-averages.
-The reason of using Nose-Hoover thermostat is that
-it perturbs the dynamics of the system only slightly, while the
-Langevin thermostat is likely to substantially change the dynamics
-when the coupling is very strong, therefore, the former was used in computing the dynamical
-properties like the diffusion constant and viscosity.
-The quantities that
-are ensemble averages (in this work, pressure, chemical potential, radial distribution function and Kirkwood-G factor are of this type)
-were computed by the largest system $\systemlb$,
-in order to achieve higher parallel efficiency.
-The system $\systemmb$ is simulated to investigate the size-dependency of the
-Kirkwood-G factor~\cite{vanderSpoel2006origin}.
+and run longer simulations for longer time-averages. The reason of using Nos%
+\'{e}-Hoover thermostat is that it perturbs the dynamics of the system only
+slightly, while the Langevin thermostat is likely to substantially change
+the dynamics when the coupling is very strong, therefore, the former was
+used in computing the dynamical properties like the diffusion constant and
+viscosity. The quantities that are ensemble averages (in this work,
+pressure, chemical potential, radial distribution function and Kirkwood-G
+factor are of this type) were computed by the largest system $L_{0}$ or $L_{1}$, in order to
+achieve higher parallel efficiency. The system $M_{1}$ is simulated to
+investigate the size-dependency of the Kirkwood-G factor~\cite%
+{vanderSpoel2006origin}.
 
@@
 
-In this section we compare the benchmark quantities of the ZM method
-to the SPME method to investigate the accuracy of the former.
-The comparison to the RF method will also be mentioned, to show that
-the ZM is a promising replacement of the RF method.
+In this section we compare the benchmark quantities of the ZM method to the
+SPME method to investigate the accuracy of the former. The comparison to the
+RF method will also be mentioned, to show that the ZM is a promising
+replacement of the RF method.
 
 \subsection{Thermodynamic properties}
-
-\begin{figure}
-  \centering
-  \includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
-  \caption{The pressure convergence with respect to the cut-off radius.
-    The ZM methods with order from 1 to 4 are compared with the RF. 
-    The splitting parameter of ZM method is set to be $\alpha = 0.00\,\textrm{nm}^{-1}$.
-    The black solid line indicates the magnitude  of the correct pressure: 1~Bar.
-    The error bars present the statistical uncertainty at 95\% confidence level.
-  }
-  \label{fig:pres-comp}
-\end{figure}
-
-The equilibrium density of the system was determined by an NPT SPME
-simulation.  Then using this density in the NVT simulation with SPME electrostatic, the
-pressure ($-0.4\pm 1.5$~Bar) is reproducing the target pressure of
-1.0~Bar, which means the system is in desired thermodynamic state.  The accuracy of ZM method, can be investigate by checking if
-the NVT pressure is consistent with the target pressure, when the SPME equilibrium density is used.  In
-Fig.~\ref{fig:pres-comp}, the pressure calculated by ZM method of
-order $l=1,2,3$ and 4 are plotted against the cut-off radius.
-All the  simulations are done with system $\systemla$.
-It is concluded from the Figure that all ZM methods converges to the
-target pressure at large enough cut-off radius.
-In general, the higher order of ZM presents an larger error in the pressure calculation than
-the lower order ZM method.
-Higher order are also more sensitive in the  cut-off radius dependency.
-ZM $l=1$ tends to under-estimate the pressure, while ZM $l=2,3$ and 4 tends to over-estimate.
-The ZM method is also compared with
-the RF method using the experimental dielectric constant $\varepsilon_{\textrm{rf}} = 80$, 
-from which it is concluded that the accuracy of ZM in pressure calculation is much higher
-than the RF method.
-It should be noted that even with the largest system of 13824 water molecules,
-the fluctuation (measured by standard deviation) of the pressure is roughly 100~Bar, which means that it is
-very difficult achieve very accurate estimate for this quantity. In practice a pressure error of 20~Bar is
-still acceptable.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l1.eps}
-  \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l2.eps}\\
-  \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l3.eps}
-  \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l4.eps}
-  \caption{The pressure convergence with respect to the cut-off radius
-    for ZM methods with  splitting parameter from $0.0$ to $2.0\,\textrm{nm}^{-1}$.
-    From left to right, up to down presents the ZM method of order 1 to 4.
-    The black solid line indicates the magnitude  of the correct pressure: 1~Bar.
-    The error bars present the statistical uncertainty at 95\% confidence level.
-  }
-  \label{fig:pres-l1}
-\end{figure}
-
-The effect of using different splitting parameter on the convergence
-of the pressure is investigate in Fig.~\ref{fig:pres-l1}.
-In general, the higher order indicates less significant dependency on the splitting parameter.
-In the case of $l=1$, the splitting parameter 0.0 is consistent with  $0.5\,\textrm{nm}^{-1}$, and
-by using higher splitting parameter, the pressure shifts to the higher pressure side.
-For $l=2,3$ and 4, the convergence is not sensitive to $\alpha$ up to  $1.0\,\textrm{nm}^{-1}$.
-More importantly,  by using $\alpha = 1.5$ or $2.0\,\textrm{nm}^{-1}$,
-the pressure does not converges to the desired value 1~Bar. Therefore, the high splitting parameter
-is not suggested in the simulations where the high pressure accuracy is important.
 
@@
   \caption{The excess chemical potential $\mu^\exc$, constant volume molar heat capacity $C_{v,m}$, dielectric constant $\eps$, diffusion constant $D$, viscosity $\eta$, constant pressure molar heat capacity $C_{v,m}$, isothermal compressibility $\kappa_T$ and
-    thermal expansion coefficient $\alpha$
+    thermal expansion coefficient $\alpha_V$
     calculated by different methods.    
@@
   \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}cccc cccccccc}\hline\hline
-    Method      &   $r_c$ &    $l$ & $\alpha$  & $\mu^\exc$  &$C_{v,m}$ & $C_{p,m}$ &   $\kappa_T$  &$\alpha$ &  $\eps$ & $D$ &  $\eta$  \\
+    Method      &   $r_c$ &    $l$ & $\alpha$  & $\mu^\exc$  &$C_{v,m}$ & $C_{p,m}$ &   $\kappa_T$  &$\alpha_V$ &  $\eps$ & $D$ &  $\eta$  \\
                 & [nm] & & [$\textrm{nm}^{-1}$] &   [kJ/mol] &[J/(mol K)] & [J/(mol K)] & [$10^{-10}\textrm{m}^2/\textrm{N}$] &  [$10^{-3}\textrm{K}^{-1}$]&  & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$]  \\
@@
 
-Other thermodynamic quantities including the chemical potential,
-constant volume/pressure molar heat capacity, isothermal
-compressibility and heat expansion coefficient are compared in
-Tab.~\ref{tab:thermo}.
-The ZM results are in good consistency with the SPME results, and out-perform
-the RF method.
-The splitting parameter does not have significant influence on these thermodynamic quantities.
-\recheck{Discussion of the energy correction in the chemical potential calculation. TO be added later}
+Thermodynamic quantities including, the chemical potential, constant
+volume/pressure molar heat capacity, isothermal compressibility and heat
+expansion coefficient, are compared in Tab.~\ref{tab:thermo}. The ZM results
+are in good consistency with the SPME results. In almost all cases the
+deviations from the SPME results are smaller than the statistical
+uncertainty. The RF was not so bad, but the results of the constant pressure
+molar heat capacity and the isothermal compressibility show considerable
+errors.
+The dependence of the ZM results on the order\ $l$\ is \recheck{little}.
+Although the splitting parameter, $\alpha $, also does not have significant
+influence on almost all these thermodynamic quantities for $l=1$, only the
+isothermal compressibility admits a weak dependence [\recheck{all except $\alpha=2$ are in the statistical uncertainty, by which we cannot say $\alpha=1$ is optimal...
+I remove ``and $\alpha=1$ seems optimal''}].
+Overall, the ZM\ agrees with the SPME results without any bias and
+out-performs the RF.
+
+\recheck{
+  It should be noticed that in the calculation of the chemical potential,
+  the energy correction plays an important role. In the case of $l=1$, $\alpha = 0.0\,\text{nm}^{-1}$,
+  it contributes $-0.1$~kJ/mol to the final result.
+  By increasing $l$ or $\alpha$, this contribution
+  becomes more significant, and reaches $-0.6$~kJ/mol for $l=4$, $\alpha = 0.0\,\text{nm}^{-1}$, and
+  $-1.0$~kJ/mol for $l=1$, $\alpha = 2.0\,\text{nm}^{-1}$, respectively.
+}
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
+\caption{The pressure convergence with respect to the cut-off radius. The ZM
+methods with order from 1 to 4 are compared with the RF. The splitting
+parameter of ZM method is set to be $\protect\alpha =0.00\,\text{nm}^{-1}$.
+The black solid line indicates the magnitude of the correct pressure: 1~Bar.
+The error bars present the statistical uncertainty at 95\% confidence level.
+\recheck{This uncertainty is twice of the standard deviation of the estimates (which are averages along MD trajectories) that
+is calculated by the block average method~\cite{janke2002statistical}.}
+}
+\label{fig:pres-comp}
+\end{figure}
+
+We investigated the dependence on the cut-off radius, $r_{\text{c}}$, on the
+pressure, simulated with system $L_{0}$. The pressure calculated by ZM
+method of order $l=1,2,3$ and $4$ with $\alpha =0$ \ and that by the RF
+method are plotted in Fig.~\ref{fig:pres-comp}. All ZM methods converges to
+the target pressure at large enough cut-off radius. Lower order ZM presents
+an smaller error in the pressure calculation than the higher order ZM
+method. Note ZM $l=1$ tends to under-estimate the pressure, while ZM $l=2,3$
+and 4 tends to over-estimate. However, the accuracy of ZM in pressure
+calculation is much higher than that of the RF method.
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=0.5\textwidth]{fig/nvt.pressure.1/pressure-l1.eps} %
+% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l2.eps}%
+% \newline
+% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l3.eps} %
+% \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l4.eps}
+\caption{
+The pressure convergence with respect to the cut-off radius for ZM
+method $l=1$ with splitting parameter from $0.0$ to $2.0\,\text{nm}^{-1}$. The black
+solid line indicates the magnitude of the correct pressure: 1~Bar. The error
+bars present the statistical uncertainty at 95\% confidence level.}
+\label{fig:pres-l1}
+\end{figure}
+
+The effect of $\alpha $ in the case of $l=1$ is shown in Fig.~\ref%
+{fig:pres-l1}. The result of $\alpha =0.5\,$nm$^{-1}$ is similar to $\alpha
+=0$ and shows good convergence. However, a higher $\alpha $ shifts the
+pressure to higher side, and in particular $\alpha =2.0\,\text{nm}^{-1}$ is
+too large to show no convergence to 1~Bar. This implies that $\alpha \leq 1$
+should be used in the simulations where the high accuracy in the pressure is
+important. This "anti-damping effect" is similarly seen in the energy
+accuracy in the TIP3P model~\cite{fukuda2014zero}.
+% [JCP2014 (J. Chem. Phys. 140, 194307 (2014))].
+In SI the results of the higher order are shown, which are similar to that
+of $l=1$, but indicate less significant dependency on $\alpha $ for a large $%
+l$\ and for a small $r_{\text{c}}$, which is consistent with the property of
+the pair potential of the ZM~\cite{fukuda2014zero}. The convergence is not sensitive to $%
+\alpha $ up to $1.0\,\text{nm}^{-1}$.
+
+\recheck{It should be noted that even with the system $L_0$ that contains 13824 water molecules}, the
+fluctuation (measured by standard deviation) of the pressure is roughly
+100~Bar, which means that it is very difficult to achieve very accurate
+estimate for this quantity. In practice a pressure error of 20~Bar is still
+acceptable.
 
@@
 
-\subsection{Radial distribution function}
+\subsection{Dielectric quantities}
 
-\begin{figure}
+\begin{figure}[tbp]
+\centering
+\includegraphics[width=0.5\textwidth]{fig/result.nvt.tiny/fig-eps-t-3000.eps}
+\caption{The dielectric constant convergence with respect to
+  length of the trajectories used to compute the value.
+  The SPME, ZM method $l=1$ to 4 and RF are presented.
+  The cut-off distance of ZM and RF methods was 1.2~nm. The working parameters of SPME are given in Sec.~\ref{sec:protocols}
+  The system used for simulation is $S_1$.
+}
+\label{fig:eps-conv}
+\end{figure}
+
+The dielectric constant computed by ZM method at different orders are listed
+in Tab.~\ref{tab:thermo}, and are consistent with the SPME computed results.
+In contrast, the RF method has poor accuracy in the dielectric constant.
+It is
+well known that the dielectric feature shows system-size dependence~\cite%
+{vanderSpoel2006origin}, therefore we further investigated this dependence
+and also the effect of the cutoff length, as shown in Table~I of SI. ZM shows
+good results without any \recheck{system-size dependency} and indicate $r_{\text{c}}\sim
+1.2\, $nm\ being suffice for the accuracy. Since a slow convergence is also known for
+the dielectric constant, we have monitored the behavior as shown in Fig.~\ref{fig:eps-conv},
+and confirm the sufficient convergence w.r.t.~the length of the trajectories.
+\recheck{[COMMENT: the system size and cut-off dependency
+  are important,
+  but since the result are consistent with system $S_1$ and rc=1.2~nm (shown in table II),
+  and NO new phenomenum is observed, 
+  they are put in SI.]}
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[]{fig/result.nvt.small/fig-gkr-small.eps}\\
+\includegraphics[]{fig/result.nvt/fig-gkr.eps} 
+\caption{The Kirkwood G-factor calculated for system $%
+M_{1}$ (a) and $L_{1} $ (b). ZM method of orders $l=1,2,3$ and 4 with the
+cut-off 1.2~nm and splitting parameter $\protect\alpha =0.0\,\text{nm}^{-1}$
+are plotted. The RF method is shown as an comparison, which uses a cut-off
+radius of 1.2~nm and dielectric constant of 80. The statistical uncertainty
+of the SPME method is presented at 95~\% confidence level with the red error
+bars. the statistical uncertainty of the SPME method is denoted by the red
+error bars. The statistical uncertainties of the other methods are
+essentially of the same size as the SPME, so they are not presented in the
+figure for clarity.}
+\label{fig:gkr}
+\end{figure}
+
+As a measurement of the dipole correlation as a function of molecular
+distance, the Kirkwood-G factor is an important quantity of the water
+system. Considering the system size dependence~\cite{vanderSpoel2006origin},
+we show the G-factor for system $M_{1}$ in Fig.~\ref{fig:gkr}~(a) and a
+larger system $L_{1}$ in Fig.~\ref{fig:gkr} (b). In both the system, the RF
+method is qualitatively wrong, and the accuracy of the ZM method is much
+higher. In the system of smaller size ($M_{1}$), ZM method of all orders are
+highly consistent with the SPME result, and $l=2$ seems the best. In the
+system of larger size ($L_{1}$), the accuracies of the ZM method is less for
+order $l\geq 2$, while they may be in still acceptable accuracy. In both
+systems, ZM $l=1$ presents an artificial oscillation around the cut-off
+radius (1.2~nm), while this oscillation is not obvious for $l\geq 2$.
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[]{fig/result.nvt/fig-gkr-conv.eps} %
+\caption{ The cut-off dependency in calculating the Kirkwood-G factor. The
+order of ZM method is $l=3$. The splitting parameter is $\protect%
+\alpha =0.0\,\text{nm}^{-1}$. The
+statistical uncertainty is presented at 95~\% confidence level by the
+error bars. }
+\label{fig:gkr-conv}
+\end{figure}
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[]{fig/result.nvt/fig-gkr-l1-damp.eps} %
+\caption{ The splitting parameter dependency in calculating the Kirkwood-G factor at order $l=1$.
+  The cut-off radius is 1.2~nm. The
+statistical uncertainty is presented at 95~\% confidence level by the
+error bars. }
+\label{fig:gkr-damp-l1}
+\end{figure}
+
+We thus investigated the cut-off dependency in calculating the Kirkwood-G
+factor and present it in Fig.~\ref{fig:gkr-conv} for ZM method of order $l=3$.
+Without surprising, the Kirkwood-G factor converges to the SPME result
+when using increasingly large cut-off radius.
+\recheck{In Fig.~\ref{fig:gkr-damp-l1}, it shows that in the case of $l=1$, 
+  the largest splitting parameter ($\alpha=2.0\ \textrm{nm}^{-1}$) is worse in calculating
+  the Kirkwood-G factor than smaller splitting parameters.}
+Splitting parameter dependency
+was not so clear for $l=2$ and 3 (shown in SI).  Note that in many cases the discrepancies
+from the SPME were relatively prominent in the middle range of the distance
+and they tend small for larger distance.
+
+\subsection{Dynamical quantities}
+
+The dynamical quantities, diffusion constant and viscosity, are listed in
+Tab.~\ref{tab:thermo}. The ZM method of order $l\geq 2$ can almost perfectly
+reproduce the SPME dynamical quantities. The ZM order $l=1$ is of less
+accurate than higher orders, but is more accurate than the RF. Using larger
+splitting parameters improves the accuracy of the order $l=1$, as understood
+as the damping effect.
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[]{fig/result.nvt.tiny/fig-vis.eps}
+\caption{The convergence
+  of the integrated auto-correlation function $I_{\protect\eta }(T)$.
+  Different orders of ZM method are compared with the SPME as well as RF results.
+  The error bars indicating 95\% confidence level are plotted with the SPME
+  method. }
+\label{fig:conv-vis}
+\end{figure}
+
+\begin{figure}[tbp]
+\centering
+\includegraphics[]{fig/result.nvt.tiny/fig-vis-l1-damp.eps}
+\caption{The convergence
+  of the integrated auto-correlation function $I_{\protect\eta }(T)$.
+  Different splitting parameters for ZM order $l=1$ are plotted.
+The
+error bars indicating 95\% confidence level are plotted with the SPME
+method. }
+\label{fig:conv-vis-damp}
+\end{figure}
+
+Similar tendency is confirmed in the auto-correlation function $I_{\eta }(T)$
+as shown in Fig.~\ref{fig:conv-vis}. It is clear that the integral for the
+RF method converges at 6~ps, while the ZM method converges only in 2~ps,
+which is consistent with the SPME result. The value of ZM $l=1$ method is
+different from the rest ZM methods and SPME result, but the results was
+improved by the damping effect as shown in Fig.~\ref{fig:conv-vis-damp}.
+
+\subsection{Structure property}
+
+\begin{figure}[tbp]
 \centering
@@
 \caption{The comparison of the center-of-mass radial distribution functions
-    calculated by SPME, ZM and RF methods. The insert is a zoom-in of
-    range 0.9 -- 1.5~nm. In the insert, the position of the cut-off
-    (1.2~nm) is indicated by a vertical black line.
-    For ZM method, the splitting parameter $\alpha$ was set to 0.0~$\textrm{nm}^{-1}$.
-  }
+calculated by SPME, ZM and RF methods. The insert is a zoom-in of range 0.9
+-- 1.5~nm. In the inset, the position of the cut-off (1.2~nm) is indicated
+by a vertical black line. For ZM method, the splitting parameter $\protect%
+\alpha $ was set to 0.0~$\text{nm}^{-1}$. }
 \label{fig:rdf}
@@
 
-We plot in Fig.~\ref{fig:rdf} the center-of-mass radial distribution functions (RDFs) of TIP3P water
-calculated by the SPME, ZM ($l=1,2,3$ and 4) and RF method.  The RDFs
-are computed from NVT simulations of system $\systemlb$. It is
-observed from the Figure that the ZM RDFs are consistency very well
-with the SPME RDF, except an artificial oscillation around the
-cut-off radius. Higher orders of ZM method present lower oscillation, and when
-$l\geq 3$, the oscillation is almost negligible. Therefore, for the sake
-of high accuracy RDF computation, the ZM method of order at least 3 should be used.
+We plot in Fig.~\ref{fig:rdf} the center-of-mass radial distribution
+functions (RDFs) of TIP3P water calculated by the SPME, ZM ($l=1,2,3$ and $4$%
+) with $\alpha =0$\ and RF methods. It is observed from the figure
+that the ZM RDFs are consist very well with the SPME RDF, except
+oscillations around the cut-off radius. This oscillations are not so large,
+as the maximum magnitude of the discrepancies from the SPME is about $2\%$, but should be artificial. However,
+higher order ZM method present lower amplitude oscillation, and when $l\geq 3
+$, the improvement is dramatic and the oscillation is almost negligible.
 
-\recheck{Shall we comment here on the fact that group cut-off produces smoother RDF? Add figures in Supplementary material}
+{\color{red} Shall we comment here on the fact that group cut-off produces
+smoother RDF? Add figures in Supplementary material \bluec{ Do you
+mean the reason of the goodness in RF?} \recheck{Yes, shall we discuss it? or it is too complicated and not very relavant to the current paper?}}
 
-\begin{figure}
+\begin{figure}[tbp]
 \centering
 \includegraphics[]{fig/result.nvt/fig-rdf-l1-damp.eps}
-  \caption{
-    The splitting parameter dependency in calculating the center-of-mass RDF for
-    ZM method $l=1$. The insert is a zoom-in of
-    range 0.9 -- 1.5~nm. In the insert, the position of the cut-off
-    (1.2~nm) is indicated by a vertical black line.
-  }
+\caption{ The splitting parameter dependency in calculating the
+center-of-mass RDF for ZM method $l=1$. The insert is a zoom-in of range 0.9
+-- 1.5~nm. In the insert, the position of the cut-off (1.2~nm) is indicated
+by a vertical black line. }
 \label{fig:rdf-damp}
@@
 
-The artificial oscillation can be substantially improved by using larger splitting parameter $\alpha$.
-Fig.~\ref{fig:rdf-damp} presents the RDF of ZM $l=1$ with splitting parameter from 0.0 to 2.0~$\textrm{nm}^{-1}$.
-A clear trend of better RDF by using larger splitting parameter is observed.
-At $\alpha = 2.0\ \textrm{nm}^{-1}$ the RDF is almost overlapping with the SPME result.
+The oscillations for $l=1$\ can also be substantially improved by using a
+larger splitting parameter $\alpha $. Figure~\ref{fig:rdf-damp} presents the
+RDF of ZM $l=1$ with splitting parameter from $0.0$ to $2.0$~$\text{nm}^{-1}$%
+. The damping effect, viz., a clear trend of better RDF by using a larger $%
+\alpha $, is observed. At $\alpha =2.0\ \text{nm}^{-1}$ the RDF is almost
+overlapping with the SPME result. This damping effect is clearer for a
+smaller order $l$\ (see SI for results of {$l=2$ and $3$}), as expected from
+the pair potential behavior~\cite{fukuda2014zero}.
 
-\recheck{If we want $l=2,3$, add in supplementary material..}
-
-\subsection{Dielectric quantities}
-
-The dielectric constant computed by ZM method at different orders are listed in Tab.~\ref{tab:thermo},
-and are consistent with the SPME computed results. In contrast, the RF method has poor accuracy in
-the dielectric constant.
-
-\begin{figure}
-  \centering
-  \includegraphics[]{fig/result.nvt/fig-gkr.eps}
-  \includegraphics[]{fig/result.nvt.small/fig-gkr-small.eps}
-  \caption{The Kirkwood G-factor calculated for system $\systemlb$ (a) and $\systemmb$ (b).
-    ZM method of orders $l=1,2,3$ and 4 with the cut-off 1.2~nm and splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$ are plotted.
-    The RF method is shown as an comparison, which uses a cut-off radius of 1.2~nm and dielectric constant of 80.
-    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red error bars.
-  }
-  \label{fig:gkr}
-\end{figure}
-
-As a measurement of the dipole correlation as a function of molecular distance, the Kirkwood-G factor
-is an important quantity of the water system.
-It is well know that the G-factor is system size
-dependent~\cite{vanderSpoel2006origin}, therefore we show the G-factor for
-system $\systemlb$ in Fig.~\ref{fig:gkr}~(a) and a smaller system $\systemmb$
-in Fig.~\ref{fig:gkr} (b).  In the figures, the statistical uncertainty of
-the SPME method is denoted by the red error bars. The statistical uncertainties of the
-other methods are essentially of the same size as the SPME, so they are not presented in the figure for
-clarity.  In the figure, ZM adopts a cut-off radius of 1.2~nm and a splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
-RF uses a cut-off 1.2~nm and a dielectric constant of 80.
-
-In both the system, the RF method is qualitatively
-wrong. The accuracy of the ZM method is much higher than RF.
-In the system of larger size ($\systemlb$), the ZM method of $l=1$ is in consistency with the SPME method. However
-order $l=2,3$ and 4  present less but still acceptable accuracy.
-In the system of smaller size ($\systemmb$), ZM method of all orders are consistent with the SPME result.
-This means ZM performs better in calculated Kirkwood-G factor for smaller systems.
-In both systems, ZM $l=1$ presents  an artificial
-oscillation around the cut-off radius (1.2~nm), while this oscillation is
-not obvious for $l\geq 2$.
-
-\begin{figure}
-  \centering
-  \includegraphics[]{fig/result.nvt/fig-gkr-conv.eps}
-  \includegraphics[]{fig/result.nvt/fig-gkr-l3-damp.eps} 
-  \caption{
-    The cut-off (a) and splitting parameter (b) dependency in calculating the Kirkwood-G factor.
-    The order of ZM method is $l=3$. In plot (a) the splitting parameter is $\alpha = 0.00\,\textrm{nm}^{-1}$.
-    in plot (b) the cut-off radius is 1.2~nm.
-    The statistical uncertainty is presented at 95~\% confidence level with the  error bars.
-  }
-  \label{fig:gkr-conv}
-\end{figure}
-
-The cut-off and splitting parameter dependency in calculating the Kirkwood-G factor
-is presented in Fig.~\ref{fig:gkr-conv}  for ZM method of order $l=3$. With out surprising,
-the Kirkwood-G factor converges to the SPME result when using increasingly large cut-off radius. 
-However, unlike the case of calculating RDF, the accuracy Kirkwood-G factor is not improved
-with increasing splitting parameter. This fact should be noticed in choosing parameters for
-high accuracy calculation of Kirkwood-G factor.
-
-\subsection{Dynamical quantities}
-
-The dynamical quantities, diffusion constant and viscosity, are listed in Tab.~\ref{tab:thermo}.
-The ZM method of order $l\geq 2$ can almost perfectly reproduce the SPME dynamical quantities.
-The ZM order $l=1$ is of less accurate than higher orders, but is more accurate than the RF.
-Using larger splitting parameters improves the accuracy, and the value $\alpha= 2.0\ \textrm{nm}^{-1}$ is
-suggested for calculating the dynamical quantities.
+% {\color{red} If we want $l=2,3$, add in supplementary material.{>}
+% Please add them. }
 
@@
 %   \centering
-%   \includegraphics[]{fig/result.tiny/fig-vis-l1-damp.eps}
+%   \includegraphics[]{fig/result.nvt.tiny/fig-vis-l1-damp.eps}
 %   \caption{The convergence of the integrated auto-correlation function $I_\eta(T) $.
@@
 
+\section{Summary and conclusion}
+
+In summary, ZM works well for almost all cases. Damping effect of the
+splitting parameter, viz., larger $\alpha $\ gives accurate results, was
+seen in several quantities. The weak effect is seen in the isothermal
+compressibility, \recheck{Kirkwood-G factor (only $l=1$)} and dynamical quantities including the diffusion constant
+and viscosity, while the strong effect is seen in the RDF. Anti-damping
+effect was also observed in the pressure when $\alpha >1$. A larger order is
+preferable slightly for dynamical quantities including diffusion constant
+and viscosity, and significantly for the RDF. Whereas a smaller order is
+preferable for the pressure, though $l=1,2$\ are similar.
+
+\recheck{
+At cut-off radius of 1.2~nm, the recommanded choices of parameters for TIP3P system are
+thus $\alpha \leq 1$~$\textrm{nm}^{-1}$ and  $l=2$ or $l=3$.
+Using these parameters, the ZM method achieves almost perfect accuracy in
+computing the excess chemical potential, constant volume/pressure heat capacity, isothermal
+compressibility, thermal expansion coefficient, dielectric constant
+diffusion constant and viscosity.
+The order $l=2$ performs better in reproducing the
+pressure than $l=3$ (10 v.s.~17~Bar), but worse in calculating the RDF (0.2\% error v.s.~almost negligible).
+Both of orders 2 and 3 are not sensitve to the splitting parameter up to 1.0~$\textrm{nm}^{-1}$.
+Further increasing the splitting parameter will push the accuracy of RDF in case $l=2$ to as high as $l=3$, however, the
+pressure accuracy decreases to 40~Bar (anti-damping effect), so it is not recommanded.
+It should be noticed that the recommanded parameters are less accurate (largest $\sim 5$\% error)
+in calculating the Kirkwood-G factor for large systems (in our case $L_1$ containing 13,824 molecules).
+The accuracy can be improved by using larger cut-off radius, and thus more computer
+time should be invested.
+}
+% Further increasing the splitting paraemter
+% Optimal parameter value for the TIP3P system is thus $l=2,\alpha \leq 1$,
+% where the error about $0.2\%$\  remains in the RDF. An
+% alternative choice is $l=3,\alpha =0$, where the accuracy in the pressure is
+% not the best but highly accurate RDF can be obtained.
+
+[{\color{blue}---%
+$>$ IPSp; I can contribute later. IPSp should be good for the
+current water system since IPSp is developed for "polar" molecule (while
+IPSn is not)}]
+
+\bigskip
+
 \appendix
@@
 \section{The computation of benchmark quantities}
+
 \label{appendix:benchmark}
 
-In this section we provide the formula used for computing the benchmark quantities. We assume that there are
-$N$ molecules in the water system. The position and configuration of each molecule are fully described
-by $\{\vect r_{3i},\vect r_{3i+1}, \vect r_{3i+2}\},\, i\in 1,\cdots,N$, and the corresponding velocities
-are denoted by $\{\vect v_{3i},\vect v_{3i+1}, \vect v_{3i+2}\},\, i\in 1,\cdots,N$. The mass of each
-atom is denoted by $m_i$.
+In this section we provide the formula used for computing the benchmark
+quantities. We assume that there are $N$ molecules in the water system. The
+position and configuration of each molecule are fully described by $\{%
+\mathbf{\mathit{r}}_{3i-2},\mathbf{\mathit{r}}_{3i-1},\mathbf{\mathit{r}}%
+_{3i}\},\,i\in 1,\cdots ,N$, and the corresponding velocities are denoted
+by $\{\mathbf{\mathit{v}}_{3i-2},\mathbf{\mathit{v}}_{3i-1},\mathbf{\mathit{v}}%
+_{3i}\},\,i\in 1,\cdots ,N$. The mass of each atom is denoted by $m_{i}$.
 
 \subsection{Radial distribution function}
-The radial distribution function (RDF) $g(r)$ is a scalar function of distance $r$, which indicates the
-probability of finding two atoms of distance $r$ apart.  It is a very
-important equilibrium structure property, by which the X-ray scattering
-intensity and a mount of thermodynamic properties can be computed.
-In this work, we investigate the center-of-mass RDF in the water
-system. The RDFs presented in the main text were computed in system $\systemlb$.
+
+The radial distribution function (RDF) $g(r)$ is a scalar function of
+distance $r$, which indicates the probability of finding two atoms of
+distance $r$ apart. It is a very important equilibrium structure property,
+by which the X-ray scattering intensity and a mount of thermodynamic
+properties can be computed. In this work, we investigate the center-of-mass
+RDF in the water system. The RDFs presented in the main text were computed
+in system $L_1$.
 
@@
 \subsection{Pressure}
-The pressure of the system calculated by the virial formula:
-\begin{align}
-  P = \frac1{3V}
-  \Bigg\langle
-  \sum_{i=1}^{3N} \Big( m_i\vect v_i^2 + \vect r_i\cdot \vect F_i \Big)
+
+The pressure of the system calculated by the virial formula:[ {\color{blue}
+Modified $3N\longrightarrow N$} \recheck{should be $3N$!, each molecule contains 3 atoms. The pressure is computed by atom based virial formula}]%
+\begin{equation*}
+P=\frac{1}{3V}\Bigg\langle\sum_{i=1}^{3N}\Big(m_{i}\mathbf{\mathit{v}}%
+_{i}^{2}+\mathbf{\mathit{r}}_{i}\cdot \mathbf{\mathit{F}}_{i}\Big)%
 \Bigg\rangle,
-\end{align}
-where $V$ is the volume of the system. The presented pressures were computed in system $\systemla$.
+\end{equation*}%
+where $V$ is the volume of the system. The presented pressures were computed
+in system $L_{0}$.
 
@@
 \end{align}
-where $A$ is the Helmholtz free energy.
-In practice the excess chemical potential $\mu^\exc$, which is the
-chemical potential abstracted by the kinetic contribution, is of
-special interest. We calculate the excess chemical potential by the
-thermodynamic integration (TI). In this approach, the interaction
-between an inserted testing molecule and the system is
-denoted by $U_t(\lambda)$, where $\lambda$
-is a coupling parameter in range $[0,1]$.
-When $\lambda = 1$ the testing molecule is fully coupled to the system
-with the TIP3P interaction. When $\lambda=0$, the testing molecule
-is decoupled with the system.
-Therefore the
-Hamiltonian of the system is function of the coupling parameter. The
-excess chemical is calculated by the free energy difference between
-the fully coupled and decoupled states:
+where $A$ is the Helmholtz free energy. In practice the excess chemical
+potential $\mu^\text{ex}$, which is the chemical potential abstracted by the
+kinetic contribution, is of special interest. We calculate the excess
+chemical potential by the thermodynamic integration (TI). In this approach,
+the interaction between an inserted testing molecule and the system is
+denoted by $U_t(\lambda)$, where $\lambda$ is a coupling parameter in range $%
+[0,1]$. When $\lambda = 1$ the testing molecule is fully coupled to the
+system with the TIP3P interaction. When $\lambda=0$, the testing molecule is
+decoupled with the system. Therefore the Hamiltonian of the system is
+function of the coupling parameter. The excess chemical is calculated by the
+free energy difference between the fully coupled and decoupled states: 
 \begin{align}
-  \mu^\exc = \int_0^1 \Big\langle \frac{\partial U_t(\lambda)}{\partial \lambda} \Big\rangle_\lambda d\lambda
+\mu^\text{ex} = \int_0^1 \Big\langle \frac{\partial U_t(\lambda)}{\partial
+\lambda} \Big\rangle_\lambda d\lambda
 \end{align}
-This integral is usually calculated by numerical integration, which
-equally partitions the range of $\lambda$, simulates the system at each
-discretized $\lambda$, and computes chemical potential by trapezoidal formula.
-Here for the sake of accuracy, 
-we adopt a two step coupling approach: firstly couple the van der Waals
-interaction of the testing particle with the rest of the system (stage vdw),
-and then couple the electrostatic interaction (stage ele).
-During stage vdw, 21 $\lambda$ values are equally
-distributed in $[0,1]$.  During stage ele, 6 $\lambda$ values are
-equally distributed in $[0,0.05]$, while the other 20 $\lambda$ values
-are equally distributed in $(0.05, 1]$. Therefore, in total 47
-simulations are performed for all $\lambda$ values.
-The free energy differences and the error estimates are calculated
-by the Bennet's acceptance ratio method (BAR)~\cite{bennett1976efficient}. 
-The simulations were performed with system $\systemla$.
+This integral is usually calculated by numerical integration, which equally
+partitions the range of $\lambda$, simulates the system at each discretized $%
+\lambda$, and computes chemical potential by trapezoidal formula. Here for
+the sake of accuracy, we adopt a two step coupling approach: firstly couple
+the van der Waals interaction of the testing particle with the rest of the
+system (stage vdw), and then couple the electrostatic interaction (stage
+ele). During stage vdw, 21 $\lambda$ values are equally distributed in $%
+[0,1] $. During stage ele, 6 $\lambda$ values are equally distributed in $%
+[0,0.05]$, while the other 20 $\lambda$ values are equally distributed in $%
+(0.05, 1]$. Therefore, in total 47 simulations are performed for all $%
+\lambda $ values. The free energy differences and the error estimates are
+calculated by the Bennet's acceptance ratio method (BAR)~\cite%
+{bennett1976efficient}. The simulations were performed with system $L_0$.
 
@@
 
-The constant volume heat capacity is defined by the infinitesimal
-increment of the energy due to an infinitesimal increment of the temperature
-at constant volume condition: 
+The constant volume heat capacity is defined by the infinitesimal increment
+of the energy due to an infinitesimal increment of the temperature at
+constant volume condition: 
 \begin{align}
@@
 \end{align}
-Since it is a extensive thermodynamics quantity, we  normalize
-it by the number molecules in the system $N$ to obtain the
-constant volume molar heat capacity $C_{V,m} = C_V/N$.
-In the MD simulations, 
-the constant volume molar heat capacity is calculated by estimating the
-fluctuation of the Hamiltonian in an NVT simulation:
+Since it is a extensive thermodynamics quantity, we normalize it by the
+number molecules in the system $N$ to obtain the constant volume molar heat
+capacity $C_{V,m} = C_V/N$. In the MD simulations, the constant volume molar
+heat capacity is calculated by estimating the fluctuation of the Hamiltonian
+in an NVT simulation: 
 \begin{align}
-  C_{V,m} = \frac{1}{k_BT^2 N} \langle (\mathcal H - \langle\mathcal H\rangle)^2 \rangle,
+C_{V,m} = \frac{1}{k_BT^2 N} \langle (\mathcal{H }- \langle\mathcal{H}%
+\rangle)^2 \rangle,
 \end{align}
-where $\mathcal H$ is the 
-Hamiltonian of the system. 
+where $\mathcal{H}$ is the Hamiltonian of the system. 
 % It is calculated in system $\systemsb$.
 
-The constant pressure molar heat capacity is defined in
-a similar way, but at constant pressure
-condition. 
-It is calculated by estimating
-the fluctuation of the enthalpy in an NPT simulation~\cite{wang2011existence}:
+The constant pressure molar heat capacity is defined in a similar way, but
+at constant pressure condition. It is calculated by estimating the
+fluctuation of the enthalpy in an NPT simulation~\cite{wang2011existence}: 
 \begin{align}
@@
 \end{align}
-where $ H$ is the enthalpy of the system,
-defined by $H = \mathcal H + P\mathcal V$, and $\mathcal V$ is the instantaneous volume
-of the system.
-It has been shown that the statistical error in estimating
-the fluctuations does not decrease with
-respect to the system size~\cite{milchev1986fluctuations,ferrenberg1991statistical}.
-Therefore, both constant volume and pressure molar heat capacities
-were calculated from the simulation of the smallest system: $\systemsb$.
+where $H$ is the enthalpy of the system, defined by $H = \mathcal{H }+ P%
+\mathcal{V}$, and $\mathcal{V}$ is the instantaneous volume of the system.
+It has been shown that the statistical error in estimating the fluctuations
+does not decrease with respect to the system size~\cite%
+{milchev1986fluctuations,ferrenberg1991statistical}. Therefore, both
+constant volume and pressure molar heat capacities were calculated from the
+simulation of the smallest system: $S_1$.
 
 \subsection{Isothermal heat capacity}
-The isothermal heat capacity is defined
-by the normalized increment of volume due to an infinitesimal
-decrement of pressure under constant temperature condition:
+
+The isothermal heat capacity is defined by the normalized increment of
+volume due to an infinitesimal decrement of pressure under constant
+temperature condition: 
 \begin{align}
@@
 \end{align}
-It can be calculated by estimating the fluctuation
-of the instantaneous volume in an NPT simulation~\cite{wang2011existence}:
+It can be calculated by estimating the fluctuation of the instantaneous
+volume in an NPT simulation~\cite{wang2011existence}: 
 \begin{align}
-  \kappa_T = \frac{1}{k_BT} \frac{\langle (\mathcal V - \langle \mathcal V\rangle)^2 \rangle}{\langle \mathcal V\rangle}.
+\kappa_T = \frac{1}{k_BT} \frac{\langle (\mathcal{V }- \langle \mathcal{V}%
+\rangle)^2 \rangle}{\langle \mathcal{V}\rangle}.
 \end{align}
-Since it is also a fluctuation, the system $\systemsb$ was adopted for simulation.
+Since it is also a fluctuation, the system $S_1$ was adopted for simulation.
 
 \subsection{Thermal expansion coefficient}
-The thermal expansion coefficient is defined by
-the normalized increment of volume due to an infinitesimal
-increment of temperature under the constant pressure condition:
+
+The thermal expansion coefficient is defined by the normalized increment of
+volume due to an infinitesimal increment of temperature under the constant
+pressure condition: 
 \begin{align}
@@
 \end{align}
-It can be calculated by estimating the cross fluctuation
-of the enthalpy and instantaneous volume  in an NPT simulation:
+It can be calculated by estimating the cross fluctuation of the enthalpy and
+instantaneous volume in an NPT simulation: 
 \begin{align}
-  \alpha_V = \frac{1}{k_BT^2\langle \mathcal V\rangle} \langle (H - \langle H\rangle)\cdot(\mathcal V - \langle \mathcal V\rangle) \rangle
+\alpha_V = \frac{1}{k_BT^2\langle \mathcal{V}\rangle} \langle (H - \langle
+H\rangle)\cdot(\mathcal{V }- \langle \mathcal{V}\rangle) \rangle
 \end{align}
-The system $\systemsb$ was adopted for simulation.
+The system $S_1$ was adopted for simulation.
 
@@
 \begin{align}
-  \eps = 1 + \frac{1}{3L^3 k_BT} ( \langle \vert \vect M\vert^2\rangle - \vert\langle \vect M\rangle\vert^2 )
+\varepsilon = 1 + \frac{1}{3L^3 k_BT} ( \langle \vert \mathbf{\mathit{M}}%
+\vert^2\rangle - \vert\langle \mathbf{\mathit{M}}\rangle\vert^2 )
 \end{align}
@@
 \begin{align}
-  \vect M = \sum_i\boldsymbol\mu_i = \sum_{\alpha\in i} q_\alpha\vect r_\alpha
+\mathbf{\mathit{M }} = \sum_i\boldsymbol{\mu}_i = \sum_{\alpha\in i} q_\alpha%
+\mathbf{\mathit{r}}_\alpha
 \end{align}
-is the total dipole moment of the system. Since it is a fluctuation, the simulated system was $\systemsb$.
+is the total dipole moment of the system. Since it is a fluctuation, the
+simulated system was $S_1$. 
 % The results are listed in Tab.~\ref{tab:tmp2}. The dielectric constant calculated in system $\systemsb$ is reported in Table.~\ref{tab:thermo}.
@@
 \begin{align}
-  G_k(r) =
-  \Big\langle
-  \frac 1N
-  \sum_{i=1}^N \sum_{j, r_{ij} < r}
-  \frac {\boldsymbol\mu_i \cdot \boldsymbol\mu_j}{\vert \boldsymbol\mu_i\vert \cdot \vert\boldsymbol\mu_j\vert}
-  \Big\rangle,
+G_k(r) = \Big\langle \frac 1N \sum_{i=1}^N \sum_{j, r_{ij} < r} \frac {%
+\boldsymbol{\mu}_i \cdot \boldsymbol{\mu}_j}{\vert \boldsymbol{\mu}_i\vert
+\cdot \vert\boldsymbol{\mu}_j\vert} \Big\rangle,
 \end{align}
 where $r_{ij}$ denotes the oxygen-oxygen distance between two water
-molecules.  The system for computing this quantity is $\systemlb$.
+molecules. The system for computing this quantity is $L_1$.
 
 \subsection{Diffusion constant}
+
 The diffusion constant is calculated from the Einstein relation: 
 \begin{align}
-  D = \lim_{t\rightarrow \infty}\frac {1}{6t} \langle \vert \vect r_i(t) - \vect r_i(0)\vert^2\rangle.
+D = \lim_{t\rightarrow \infty}\frac {1}{6t} \langle \vert \mathbf{\mathit{r}}%
+_i(t) - \mathbf{\mathit{r}}_i(0)\vert^2\rangle.
 \end{align}
-In practice, the mean-square-displacement $\langle\vert \vect r_i(t) - \vect
-r_i(0)\vert^2\rangle$ is calculated, then the value is linearly fitted. The system for simulation was $\systemsb$.
+In practice, the mean-square-displacement $\langle\vert \mathbf{\mathit{r}}%
+_i(t) - \mathbf{\mathit{r}}_i(0)\vert^2\rangle$ is calculated, then the
+value is linearly fitted. The system for simulation was $S_1$.
 
 \subsection{Viscosity}
+
 The viscosity is calculated from the Green-Kubo relation: 
 \begin{align}
-  \eta = \frac{V}{k_BT}\int_0^\infty\langle P_{\alpha\beta}(0) P_{\alpha\beta}(t)\rangle\,dt, \quad \alpha,\beta \in \{x, y, z\}
+\eta = \frac{V}{k_BT}\int_0^\infty\langle P_{\alpha\beta}(0)
+P_{\alpha\beta}(t)\rangle\,dt, \quad \alpha,\beta \in \{x, y, z\}
 \end{align}
-where $\alpha$ and $\beta$ denote the directions, and
-$P_{\alpha\beta}$ denotes the off-diagonal components of the pressure
-tensor. Since we used the isotropic system setting, then it is obvious
-that $P_{xy}$, $P_{yz}$ and $P_{xz}$ are equivalent. Moreover, it has
-been pointed out that in addition $(P_{xx} - P_{yy})/2$ and $(P_{xx} -
-P_{yy})/2$ are two independent components that are equivalent to the
-first three~\cite{alfe1998first}. Therefore, the viscosity is
-calculated from the auto-correlation functions of five independent
-components, and the statistical error is estimated from the standard
-deviation of the viscosities calculated from the five components.
+where $\alpha$ and $\beta$ denote the directions, and $P_{\alpha\beta}$
+denotes the off-diagonal components of the pressure tensor. Since we used
+the isotropic system setting, then it is obvious that $P_{xy}$, $P_{yz}$ and 
+$P_{xz}$ are equivalent. Moreover, it has been pointed out that in addition $%
+(P_{xx} - P_{yy})/2$ and $(P_{xx} - P_{yy})/2$ are two independent
+components that are equivalent to the first three~\cite{alfe1998first}.
+Therefore, the viscosity is calculated from the auto-correlation functions
+of five independent components, and the statistical error is estimated from
+the standard deviation of the viscosities calculated from the five
+components.
 
-We investigate the convergence of the integral of the auto-correlation function w.r.t.~time:
-\begin{align}
-  I_\eta(T) = \frac{V}{k_BT}\int_0^T\langle P_{\alpha\beta}(0) P_{\alpha\beta}(t)\rangle\,dt,
-\end{align}
-and plot the function $I_\eta(T) $ for all method in
-Fig.~\ref{fig:conv-vis}.  It is clear the integral for the RF method
-converges at 6~ps, while the ZM method converges only in 2~ps, which
-is consistent with the SPME result.  The value of ZM $l=1$ method is
-different from the rest ZM method an SPME result.
-The values listed  in Table~\ref{tab:thermo} are computed with $I_\eta(10\,\textrm{ps})$.
+We investigate the convergence of the integral of the auto-correlation
+function w.r.t.~time: 
+\begin{equation*}
+I_{\eta }(T)=\frac{V}{k_{B}T}\int_{0}^{T}\langle P_{\alpha \beta
+}(0)P_{\alpha \beta }(t)\rangle \,dt.
+\end{equation*}%
 The
-system for simulation was $\systemsb$.
-
-\begin{figure}
-  \centering
-  \includegraphics[]{fig/result.tiny/fig-vis.eps}
-  \caption{The convergence of the integrated auto-correlation function $I_\eta(T) $. The error bars indicating 95\% confidence level are plotted with the SPME method.}
-  \label{fig:conv-vis}
-\end{figure}
+values listed in Table~\ref{tab:thermo} are computed with $I_{\eta }(10\,%
+\text{ps})$. The system for simulation was $S_{1}$.
 
 \newpage
+
 \bibliography{ref}{}

### 2014-11-08 writedown/zm/paper.water/si.tex
add SI and gp files.

--- 2014-11-03 writedown/zm/paper.water/main.tex
@@
-\documentclass[aip,jcp,a4paper,preprint,unsortedaddress,onecolumn,fleqn]{revtex4-1}
-% \documentclass[reprint,unsortedadress,oneclumn]{revtex4-1}
-
+\documentclass[aip,jcp,a4paper,reprint,unsortedaddress,onecolumn,fleqn]{revtex4}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \usepackage{amsmath,amssymb,amsfonts,latexsym}
@@
 \newcommand{\systemlb}{L_1}
-
+% \input{tcilatex}
 \begin{document}
 
-\title{A Critical Appraisal of Zero-Multiple Method in Classical Water Simulation}
+\title{\textbf{Supplementary Materials}\\
+  A Critical Appraisal of the Zero-Multiple Method: Structural,
+Thermodynamic, Dielectric, and Dynamical Properties of a Water System}
 \author{Han Wang}
 \email{han.wang@fu-berlin.de}
-\affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road 6, 100088 Beijing, China}
 \author{Ikuo Fukuda}
 \email{ifukuda@protein.osaka-u.ac.jp}
-\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita, Osaka 565-0871, Japan}
-\affiliation{RIKEN (The Institute of Physical and Chemical Research), 2-1 Hirosawa, Wako, Saitama 351-0198, Japan}
 
@@
 \maketitle
+\affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road
+6, 100088 Beijing, China}
+\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
+Osaka 565-0871, Japan}
+\affiliation{RIKEN (The Institute of Physical and Chemical Research), 2-1 Hirosawa, Wako,
+Saitama 351-0198, Japan}
 
-\section{Introduction}
+% A Critical Appraisal of Zero-Multiple Method in Classical Water Simulation}
 
-A very short overview of the existing electrostatic interaction methods.
-Long-range treatment, Ewald and derived methods like SPME.
-Short-range treatment.
-
-The importance of developing a short-range method for the electrostatic interaction.
-
-Zero-Multiple method, an overview, achievements, successful applications.
-
-The purpose of this work: Extensive and strict tests investigating the reliability of Zero-Multiple method in water simulation, which is the most important solvent.
-
-The structure of the paper.
-
-\section{Zero-Multiple Method}
-
-Introduction of the ZM method, formula...
-
-A short mention of the group cut-off v.s.~the atom cut-off method. (will discuss the implementation in gromacs later)
-
-\section{Benchmark quantities}
-
-In order to investigate the performance of ZM method, we simulation
-the water system by using both SPME and ZM method, and calculate a set
-of \emph{benchmark quantities}.  This set covers a broad range of
-water properties that are of general interest, and includes the
-structure property (radial distribution function), the thermodynamic
-properties (pressure, excess chemical potential, constant
-volume/pressure heat capacity, isothermal compressibility, thermal
-expansion coefficient), dielectric properties (dielectric constant and
-Kirkwood-G factor) and dynamical properties (diffusion coefficient and
-viscosity).  By comparing ZM to SPME, a good consistency in computing
-the benchmark quantities would indicate a good accuracy of the ZM
-method.  Moreover, being aware of the weakness of the ZM method also
-prevents the application the method in wrong applications.  The ZM
-method is also compared to the traditional short-range method: RF.
-The definitions for computing these quantities are provided in details
-in Appendix.~\ref{appendix:benchmark}.
-
-\section{Simulation protocols}
-
-In this work, we investigate the water system modeled by
-TIP3P~\cite{jorgensen1983comparison} point-charge water model.
-All simulations were performed by Gromacs~4.6~\cite{hess2008gromacs, pronk2013gromacs} complied by GNU C compiler with single float precision.
-The size of the systems and corresponding number of molecules used for MD simulations are summarized in Tab.~\ref{tab:tmp1}.
-The benchmark quantities were calculated in either  canonical (NVT) or isothermal-isobaric (NPT) ensemble, with equilibrium temperature $T=300$~K.
-In order to simulate at the desired temperature,
-the systems $\systemsb$ and $\systemsbp$ were coupled to either Nose-Hoover~\cite{nose1984molecular,hoover1985canonical} thermostat with time-scale $\tau_T = 1.0$~ps,
-while systems $\systemmb$, $\systemmbp$, $\systemla$, $\systemlb$ and $\systemlbp$ were coupled to Langevin thermostat with time-scale $\tau_T = 0.1$~ps.
-In the NPT simulations, the systems were further coupled
-to the Parrinello-Rahman barostat~\cite{parrinello1980crystal,parrinello1981polymorphic} (in Gromacs implementation)
-with time-scale $\tau_P = 0.5$~ps to equilibriate the system at 1~Bar.
-All systems were integrated with leap-frog scheme at the time-step of 0.001~ps.
-For the ZM and SPME methods,
-the neighbor lists were updated every 5 time-steps.
-The ``\texttt{group}'' cut-off scheme in Gromacs was used. In order to mimic the atomistic
-cut-off manner, the radius for neighbor list building was set 0.3~nm
-larger than the cut-off radius (the maximum of Coulomb cut-off and the van der Waals cut-off).
-To make sure the van der Waals interactions were cut-off in a smooth way,
-they are modified in a shell of $0.05$~nm width near the cut-off sphere by the Gromacs ``\texttt{shift}'' method.
-The ZM method was implemented in Gromacs with the tabulated electrostatic interaction (Home-made codes for generating the interaction tables).
-The short-range part of SPME method is also smoothed in a shell of $0.05$~nm width  by the Gromacs ``\texttt{pme-switch}'' method.
-The reciprocal space
-grid spacing is set to 0.06~nm, with B-Spline interpolation order of 6.
-These parameters are chosen to be more accurate than the Gromacs default choices (grid spacing 0.12~nm and interpolation order 4).
-The splitting parameter is optimized by the error estimate for the SPME method, which is implemented in Gromacs by tool ``\texttt{g\_pme\_error}''~\cite{wang2010optimizing}.
-The optimized real space and reciprocal space force computing errors were equally distributed as $1.4\times10^{-4}$~kJ/(mol nm).
-In the simulations of the RF method, the interactions were cut-off in the group manner,
-so the radius for neighbor list building is set identical to the cut-off radius.
-No cut-off smoothing was applied in the cases of RF simulation.
+\begin{figure}[]
+\centering
+\includegraphics[width=0.5\textwidth]{fig/nvt.pressure.1/pressure-l2.eps}\\
+\includegraphics[width=0.5\textwidth]{fig/nvt.pressure.1/pressure-l3.eps}\\
+\includegraphics[width=0.5\textwidth]{fig/nvt.pressure.1/pressure-l4.eps}
+\caption{The pressure convergence with respect to the cut-off radius for ZM
+methods with splitting parameter from $0.0$ to $2.0\,\text{nm}^{-1}$. From
+left to right, the ZM method of order 2 to 4. The black
+solid line indicates the magnitude of the correct pressure: 1~Bar. The error
+bars present the statistical uncertainty at 95\% confidence level.}
+\label{fig:pres-l1}
+\end{figure}
 
@@
   \centering
-  \caption{A list of systems simulated in this work. We report, from left to right, the number of water
-    molecules in the system (TIP3P model), equilibrium box size, length of equilibriation, length of productive trajectory, the thermostats and the corresponding coupling time-scales.
-  }
-  \vskip .5cm
-  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}c rrrrrr}\hline\hline
-    System      & $N$ & $V$ [$\textrm{nm}^3$]  & $T_{eq}$ [ps] & Traj. Length [ps] & Thermostat & $\tau$ [ps]  \\\hline
-    $\systemsbp$         &   2,500        & $4.24^3$              & --           &  6,000        & Nose-Hoover & 1.0\\
-    $\systemsb$          & 2,500          & $4.24^3$              & 3,000        & 27,000        & Nose-Hoover & 1.0 \\\hline
-    $\systemmbp$         &   4,500        & $5.15^3$              & --           &  6,000        & Langevin & 0.1\\
-    $\systemmb$          & 4,500          & $5.15^3$              & 3,000        & 17,000        & Langevin & 0.1\\\hline
-    $\systemla$          &   13,824       & $7.49^3$              & 200          & 1,800         & Langevin & 0.1\\
-    $\systemlbp$         &   13,824       & $7.49^3$              & --           & 10,000        & Langevin & 0.1\\
-    $\systemlb$          &   13,824       & $7.49^3$              & 3,000        & 17,000        & Langevin & 0.1\\
+  \caption{A list of the dielectric constant calculated for different systems by different methods.
+    The parameters are provided. The parenthesises in the last column show the statistical uncertainty
+    of the last two digits up to the confidence level of 95~\%.}
+  \begin{tabular*}{0.8\textwidth}{@{\extracolsep{\fill}}cccc rr}\hline\hline
+    System & Method      &       $\alpha$ [$\textrm{nm}^{-1}$] & $r_c$ [nm] &    $l$     &       $\eps$ \\\hline
+    $\systemmb$  &       ZM          &       0.0    &       1.2     &       1       &       99.8 (3.8)\\ 
+    $\systemmb$  &       ZM          &       0.0    &       1.2     &       2       &       95.2 (3.6)\\ 
+    $\systemmb$  &       ZM          &       0.0    &       1.2     &       3       &       93.9 (3.7)\\ 
+    $\systemmb$  &       ZM          &       0.0    &       1.5     &       3       &       98.7 (3.8)\\ 
+    $\systemmb$  &       ZM          &       0.0    &       1.8     &       3       &      100.7 (3.6)\\ 
+    $\systemmb$  &       ZM          &       0.0    &       1.2     &       4       &       94.7 (3.6)\\
+    $\systemmb$   & SPME          & 2.1  & 1.9   &       --      &       98.8 (4.0) \\
+    $\systemmb$  & RF             & --  & 1.2 & -- & 60.6   (1.7) \\\hline
+    $\systemlb$  &       ZM          &       0.0    &       1.2     &       1       &       97.1 (3.2)\\ 
+    $\systemlb$  &       ZM          &       0.0    &       1.2     &       2       &       95.6 (3.5)\\ 
+    $\systemlb$  &       ZM          &       0.0    &       1.2     &       3       &       95.8 (4.6)\\ 
+    $\systemlb$  &       ZM          &       0.0    &       1.5     &       3       &       98.0 (3.3)\\ 
+    $\systemlb$  &       ZM          &       0.0    &       1.8     &       3       &       98.9 (4.2)\\ 
+    $\systemlb$  &       ZM          &       0.0    &       2.1     &       3       &       98.8 (3.9)\\ 
+    $\systemlb$  &       ZM          &       0.0    &       1.2     &       4       &       97.8 (3.9)\\
+   $\systemlb$   & SPME          & 2.1  & 1.9   &       --      &       98.7 (3.5) \\
+    $\systemlb$  & RF             & --  & 1.2 & -- & 60.8   (2.0) \\
     \hline\hline
   \end{tabular*}
-  \label{tab:tmp1}
+  \label{tab:tmp2}
 \end{table}
 
-The initial configurations were prepared by in
-the following steps:
-(1) An NPT simulation of system $\systemla$ with SPME
-electrostatic was performed. The equilibrium density (984.1~$\textrm{kg}/\textrm{m}^{-3}$) of the system is calculated
-from this simulation.
-(2) Initial configurations that contains 2500, 4500 and
-13824 molecules were generated at the calculated equilibrium
-density.
-(3) NVT simulations with SPME electrostatic for system $\systemsbp$, $\systemmbp$
-and $\systemlbp$ are performed.
-(4) The output configurations of $\systemsbp$ and $\systemmbp$ were used as
-initial configurations for system $\systemsb$ and $\systemmb$, respectively.  The output configuration of
-$\systemlbp$ was used as initial configurations for system $\systemla$ and $\systemlb$.
-% The SPME
-% parameters for all simulations reported by this work is: real space
-% cut-off 1.90~nm.
-
-% The cut-off is smoothed from 1.85 to 1.90~nm by the
-% ``\texttt{switch}'' method provide by Gromacs
-% 4.6~\cite{hess2008gromacs, pronk2013gromacs}.
-
-The smallest system $\systemsb$ was adopted,
-because for the quantities that are computed  by estimating fluctuations (in this
-work heat capacities, compressibility, thermal expansion coefficient, dielectric constant, diffusion constant and
-viscosity are fluctuations. See details in Appendix~\ref{appendix:benchmark}), simply increase the size of the
-system does not improve the accuracy of the 
-simulation~\cite{milchev1986fluctuations,ferrenberg1991statistical}.
-The optimal way of measuring these properties
-is to simulate with smaller systems (as far as the finite size effect is negligible) and run longer simulations for longer time-averages.
-The reason of using Nose-Hoover thermostat is that
-it perturbs the dynamics of the system only slightly, while the
-Langevin thermostat is likely to substantially change the dynamics
-when the coupling is very strong, therefore, the former was used in computing the dynamical
-properties like the diffusion constant and viscosity.
-The quantities that
-are ensemble averages (in this work, pressure, chemical potential, radial distribution function and Kirkwood-G factor are of this type)
-were computed by the largest system $\systemlb$,
-in order to achieve higher parallel efficiency.
-The system $\systemmb$ is simulated to investigate the size-dependency of the
-Kirkwood-G factor~\cite{vanderSpoel2006origin}.
-
-\section{Results and discussions}
-
-In this section we compare the benchmark quantities of the ZM method
-to the SPME method to investigate the accuracy of the former.
-The comparison to the RF method will also be mentioned, to show that
-the ZM is a promising replacement of the RF method.
-
-\subsection{Thermodynamic properties}
-
-\begin{figure}
+\begin{figure}[tbp]
 \centering
-  \includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
-  \caption{The pressure convergence with respect to the cut-off radius.
-    The ZM methods with order from 1 to 4 are compared with the RF. 
-    The splitting parameter of ZM method is set to be $\alpha = 0.00\,\textrm{nm}^{-1}$.
-    The black solid line indicates the magnitude  of the correct pressure: 1~Bar.
-    The error bars present the statistical uncertainty at 95\% confidence level.
-  }
-  \label{fig:pres-comp}
+\includegraphics[]{fig/result.nvt/fig-gkr-l2-damp.eps}\\
+\includegraphics[]{fig/result.nvt/fig-gkr-l3-damp.eps}
+\caption{  The 
+  splitting parameter dependency in calculating the Kirkwood-G factor.
+  The orders of ZM method $l=2$ (a)  and $l=3$ (b) are presented.
+  In both plots the cut-off radius is 1.2~nm. The
+  statistical uncertainty is presented at 95~\% confidence level with the
+  error bars. }
+\label{fig:gkr-conv-alpha}
 \end{figure}
 
-The equilibrium density of the system was determined by an NPT SPME
-simulation.  In the NVT simulation the SPME electrostatic, computed
-pressure ($-0.4\pm 1.5$~Bar) is reproducing the target pressure of
-1.0~Bar.  The accuracy of ZM method, can be investigate by checking if
-the NVT pressure is consistent with the target pressure.  In
-Fig.~\ref{fig:pres-comp}, the pressure calculated by ZM method of
-order $l=1,2,3$ and 4 are plotted against the cut-off radius.
-All the  simulations are done with system $\systemla$.
-It is concluded from the Figure that all ZM methods converges to the
-target pressure at large enough cut-off radius.
-In general, the higher order of ZM presents an larger error in the pressure calculation than
-the lower order ZM method.
-Higher order are also more sensitive in the  cut-off radius dependency.
-ZM $l=1$ tends to under-estimate the pressure, while ZM $l=2,3$ and 4 tends to over-estimate.
-The ZM method is also compared with
-the RF method using the experimental dielectric constant $\varepsilon_{\textrm{rf}} = 80$, 
-from which it is concluded that the accuracy of ZM in pressure calculation is much higher
-than the RF method.
-It should be noted that even with the largest system of 13824 water molecules,
-the fluctuation (measured by standard deviation) of the pressure is roughly 100~Bar, which means that it is
-very difficult achieve very accurate estimate for this quantity. In practice a pressure error of 20~Bar is
-still acceptable.
-
-\begin{figure}
+\begin{figure}[tbp]
 \centering
-  \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l1.eps}
-  \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l2.eps}\\
-  \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l3.eps}
-  \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l4.eps}
-  \caption{The pressure convergence with respect to the cut-off radius
-    for ZM methods with  splitting parameter from $0.0$ to $2.0\,\textrm{nm}^{-1}$.
-    From left to right, up to down presents the ZM method of order 1 to 4.
-    The black solid line indicates the magnitude  of the correct pressure: 1~Bar.
-    The error bars present the statistical uncertainty at 95\% confidence level.
-  }
-  \label{fig:pres-l1}
-\end{figure}
-
-The effect of using different splitting parameter on the convergence
-of the pressure is investigate in Fig.~\ref{fig:pres-l1}.
-In general, the higher order indicates less significant dependency on the splitting parameter.
-In the case of $l=1$, the splitting parameter 0.0 is consistent with  $0.5\,\textrm{nm}^{-1}$, and
-by using higher splitting parameter, the pressure shifts to the higher pressure side.
-For $l=2,3$ and 4, the convergence is not sensitive to $\alpha$ up to  $1.0\,\textrm{nm}^{-1}$.
-More importantly, for all orders,
-the pressure does not converges to the desired value 1~Bar by using $\alpha = 1.5$ or $2.0\,\textrm{nm}^{-1}$.
-
-\begin{sidewaystable}
-  \centering
-  \caption{The excess chemical potential $\mu^\exc$, constant volume molar heat capacity $C_{v,m}$, dielectric constant $\eps$, diffusion constant $D$, viscosity $\eta$, constant pressure molar heat capacity $C_{v,m}$, isothermal compressibility $\kappa_T$ and
-    thermal expansion coefficient $\alpha$
-    calculated by different methods.    
-    The parentheses in the last column show the statistical uncertainty
-    at the confidence level of 95~\%.
-    The bold numbers indicating that its deviation from the SPME result is larger than the statistical uncertainty.
-  }
-  \bigskip
-  \centering\small\setlength\tabcolsep{2pt}
-  \begin{tabular*}{0.99\textwidth}{@{\extracolsep{\fill}}cccc cccccccc}\hline\hline
-    Method      &   $r_c$ &    $l$ & $\alpha$  & $\mu^\exc$  &$C_{v,m}$ & $C_{p,m}$ &   $\kappa_T$  &$\alpha$ &  $\eps$ & $D$ &  $\eta$  \\
-                & [nm] & & [$\textrm{nm}^{-1}$] &   [kJ/mol] &[J/(mol K)] & [J/(mol K)] & [$10^{-10}\textrm{m}^2/\textrm{N}$] &  [$10^{-3}\textrm{K}^{-1}$]&  & [$10^{-9}\textrm{m}^2/\textrm{s}$] &  [$10^{-3}\textrm{Pa}\cdot\textrm{s}$]  \\
-                &    &    &    &NVT $\systemla$&NVT $\systemsb$&  NPT $\systemsb$          &  NPT $\systemsb$    &  NPT $\systemsb$    & NVT $\systemsb$& NVT $\systemsb$    & NVT $\systemsb$       \\\hline
-    SPME        &1.9 & -- &2.1 & $-26.1$ (0.2) & 72.2 (1.0)  &79.2 (0.9)           & 5.94 (0.05)               &1.03 (0.02)          & 98 (3)          &         5.86  (0.07)&         0.315  (0.007)\\
-    RF          &1.2 & -- &--  & $-26.0$ (0.3) & 72.3 (0.8)  &\textbf{82.3} (1.0)  & \textbf{6.51} (0.06)      &\textbf{1.15} (0.02) & \textbf{59} (1) & \textbf{6.27} (0.19)& \textbf{0.449} (0.020)\\\hline
-    ZM          &1.2 & 1  &0.0 & $-26.2$ (0.3) & 71.8 (0.9)  &78.9 (1.0)           & 5.87 (0.05)               &1.01 (0.02)          & 96 (2)          & \textbf{5.53} (0.11)& \textbf{0.346} (0.006)\\ 
-    ZM          &1.2 & 1  &0.5 & $-26.4$ (0.3) & 72.3 (0.8)  &78.9 (0.9)           & 5.92 (0.05)               &\textbf{1.00} (0.02) & 97 (2)          & \textbf{5.52} (0.25)& \textbf{0.339} (0.008)\\ 
-    ZM          &1.2 & 1  &1.0 & $-26.0$ (0.2) & 72.4 (0.8)  &78.4 (0.9)           & 5.95 (0.05)               &1.01 (0.02)          & 96 (2)          &        {5.78} (0.25)& \textbf{0.330} (0.011)\\ 
-    ZM          &1.2 & 1  &1.5 & $-26.0$ (0.2) & 71.3 (0.8)  &80.2 (0.9)           & 5.97 (0.05)               &1.04 (0.02)          & 99 (3)          & \textbf{5.71} (0.09)&        {0.312} (0.008)\\ 
-    ZM          &1.2 & 1  &2.0 & $-26.1$ (0.3) & 71.3 (0.8)  &79.4 (0.9)           & \textbf{6.05} (0.05)      &1.05 (0.02)          & 96 (3)          &        {5.90} (0.04)&        {0.307} (0.007)\\\hline
-    ZM          &1.2 & 2  &0.0 & $-26.2$ (0.2) & 71.5 (0.9)  &79.7 (1.0)           & 5.95 (0.05)               &1.03 (0.02)          & 95 (3)          &         5.82  (0.27)&         0.318  (0.012)\\
-    ZM          &1.2 & 3  &0.0 & $-26.2$ (0.2) & 71.6 (0.9)  &79.5 (1.0)           & 5.99 (0.05)               &1.02 (0.02)          & 96 (3)          &         5.79  (0.09)&         0.321  (0.008)\\
-    ZM          &1.2 & 4  &0.0 & $-26.0$ (0.3) & 71.1 (0.8)  &79.5 (1.0)           & 5.96 (0.05)               &1.03 (0.02)          &100 (2)          &         5.89  (0.09)&         0.318  (0.013)\\
-    \hline\hline
-  \end{tabular*}
-  \label{tab:thermo}
-\end{sidewaystable}
-
-Other thermodynamic quantities including the chemical potential,
-constant volume/pressure molar heat capacity, isothermal
-compressibility and heat expansion coefficient are compared in
-Tab.~\ref{tab:thermo}.
-The ZM results are in good consistency with the SPME results, and out-perform
-the RF method.
-The splitting parameter does not have significant influence on these thermodynamic quantities.
-\recheck{Discussion of the energy correction in the chemical potential calculation. TO be added later}
-
-% \begin{table}
-%   \centering
-%   \caption{A list of the dielectric constant calculated for different systems by different methods.
-%     The parameters are provided. The parenthesises in the last column show the statistical uncertainty
-%     of the last two digits up to the confidence level of 95~\%.}
-%   \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}cccc rr}\hline\hline
-%     System & Method      &       $\alpha$ [$\textrm{nm}^{-1}$] & $r_c$ [nm] &    $l$     &       $\eps$ \\\hline
-%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       1       &       99.8 (3.8)\\ 
-%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       2       &       95.2 (3.6)\\ 
-%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       3       &       93.9 (3.7)\\ 
-%     $\systemmb$  &       ZM          &       0.00    &       1.5     &       3       &       98.7 (3.8)\\ 
-%     $\systemmb$  &       ZM          &       0.00    &       1.8     &       3       &      100.7 (3.6)\\ 
-%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       4       &       94.7 (3.6)\\
-%     $\systemmb$   & SPME          & 2.09  & 1.9   &       --      &       98.8 (4.0) \\
-%     $\systemmb$  & RF             & --  & 1.2 & -- & 60.6   (1.7) \\
-%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       1       &       97.1 (3.2)\\ 
-%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       2       &       95.6 (3.5)\\ 
-%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       3       &       95.8 (4.6)\\ 
-%     $\systemlb$  &       ZM          &       0.00    &       1.5     &       3       &       98.0 (3.3)\\ 
-%     $\systemlb$  &       ZM          &       0.00    &       1.8     &       3       &       98.9 (4.2)\\ 
-%     $\systemlb$  &       ZM          &       0.00    &       2.1     &       3       &       98.8 (3.9)\\ 
-%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       4       &       97.8 (3.9)\\
-%    $\systemlb$   & SPME          & 2.09  & 1.9   &       --      &       98.7 (3.5) \\
-%     $\systemlb$  & RF             & --  & 1.2 & -- & 60.8   (2.0) \\
-%     \hline\hline
-%   \end{tabular*}
-%   \label{tab:tmp2}
-% \end{table}
-
-\subsection{Radial distribution function}
-
-\begin{figure}
-  \centering
-  \includegraphics[]{fig/result.nvt/fig-rdf.eps}  
-  \caption{The comparison of the center-of-mass radial distribution functions
-    calculated by SPME, ZM and RF methods. The insert is a zoom-in of
-    range 0.9 -- 1.5~nm. In the insert, the position of the cut-off
-    (1.2~nm) is indicated by a vertical black line.
-    For ZM method, the splitting parameter $\alpha$ was set to 0.0~$\textrm{nm}^{-1}$.
-  }
-  \label{fig:rdf}
-\end{figure}
-
-We plot in Fig.~\ref{fig:rdf} the center-of-mass radial distribution functions (RDFs) of TIP3P water
-calculated by the SPME, ZM ($l=1,2,3$ and 4) and RF method.  The RDFs
-are computed from NVT simulations of system $\systemlb$. It is
-observed from the Figure that the ZM RDFs are consistency very well
-with the SPME RDF, except an artificial oscillation around the
-cut-off radius. Higher orders of ZM method present lower oscillation, and when
-$l\geq 3$, the oscillation is almost negligible. Therefore, for the sake
-of high accuracy RDF computation, the ZM method of order at least 3 should be used.
-
-\recheck{Shall we comment here on the fact that group cut-off produces smoother RDF? Add figures in Supplementary material}
-
-\begin{figure}
-  \centering
-  \includegraphics[]{fig/result.nvt/fig-rdf-l1-damp.eps}  
-  \caption{
-    The splitting parameter dependency in calculating the center-of-mass RDF for
-    ZM method $l=1$. The insert is a zoom-in of
-    range 0.9 -- 1.5~nm. In the insert, the position of the cut-off
-    (1.2~nm) is indicated by a vertical black line.
-  }
-  \label{fig:rdf-damp}
-\end{figure}
-
-The artificial oscillation can be substantially improved by using larger splitting parameter $\alpha$.
-In Fig.~\ref{fig:rdf-damp} presents the RDF of ZM $l=1$ with splitting parameter from 0.0 to 2.0~$\textrm{nm}^{-1}$.
-A clear trend of better RDF by using larger splitting parameter is observed.
-At $\alpha = 2.0\ \textrm{nm}^{-1}$ the RDF is almost overlapping with the SPME result.
-
-\recheck{If we want $l=2,3$, add in supplementary material..}
-
-\subsection{Dielectric quantities}
-
-The dielectric constant computed by ZM method at different orders are listed in Tab.~\ref{tab:thermo},
-and are consistent with the SPME computed results. In contrast, the RF method has poor accuracy in
-the dielectric constant.
-
-\begin{figure}
-  \centering
-  \includegraphics[]{fig/result.nvt/fig-gkr.eps}
-  \includegraphics[]{fig/result.nvt.small/fig-gkr-small.eps}
-  \caption{The Kirkwood G-factor calculated for system $\systemlb$ (a) and $\systemmb$ (b).
-    ZM method of orders $l=1,2,3$ and 4 with the cut-off 1.2~nm and splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$ are plotted.
-    The RF method is shown as an comparison, which uses a cut-off radius of 1.2~nm and dielectric constant of 80.
-    The statistical uncertainty of the SPME method is presented at 95~\% confidence level with the red error bars.
-  }
-  \label{fig:gkr}
-\end{figure}
-
-As a measurement of the dipole correlation as a function of molecular distance, the Kirkwood-G factor
-is an important quantity of the water system.
-It is well know that the G-factor is system size
-dependent~\cite{vanderSpoel2006origin}, therefore we show the G-factor for
-both  system $\systemlb$ in Fig.~\ref{fig:gkr}~(a) and a smaller system $\systemmb$
-Fig.~\ref{fig:gkr} (b).  In the figures, the statistical uncertainty of
-the SPME method is denoted by the red error bars. The statistical uncertainties of the
-other methods are essentially of the same size as the SPME, so they are not presented in the figure for
-clarity.  In the figure, ZM adopts a cut-off radius of 1.2~nm and a splitting parameter $\alpha = 0.00\,\textrm{nm}^{-1}$.
-RF uses a cut-off 1.2~nm and a dielectric constant of 80.
-
-In both the system, the RF method is qualitatively
-wrong. The accuracy of the ZM method is much higher than RF.
-In the system of larger size ($\systemlb$), the ZM method of $l=1$ is in consistency with the SPME method. However
-order $l=2,3$ and 4  present less but still acceptable accuracy.
-In the system of smaller size ($\systemmb$), ZM method of all orders are consistent with the SPME result.
-This means ZM performs better in calculated Kirkwood-G factor for smaller systems.
-In both systems, ZM $l=1$ presents  an artificial
-oscillation around the cut-off radius (1.2~nm), while this oscillation is
-not obvious for $l\geq 2$.
-
-\begin{figure}
-  \centering
-  \includegraphics[]{fig/result.nvt/fig-gkr-conv.eps}
-  \includegraphics[]{fig/result.nvt/fig-gkr-l3-damp.eps} 
-  \caption{
-    The cut-off (a) and splitting parameter (b) dependency in calculating the Kirkwood-G factor.
-    The order of ZM method is $l=3$. In plot (a) the splitting parameter is $\alpha = 0.00\,\textrm{nm}^{-1}$.
-    in plot (b) the cut-off radius is 1.2~nm.
-    The statistical uncertainty is presented at 95~\% confidence level with the  error bars.
-  }
-  \label{fig:gkr-conv}
-\end{figure}
-
-The cut-off and splitting parameter dependency in calculating the Kirkwood-G factor
-is presented in Fig.~\ref{fig:gkr-conv}  for ZM method of order $l=3$. With out surprising,
-the Kirkwood-G factor converges to the SPME result when using increasing cut-off radius. 
-However, unlike the case of calculating RDF, the accuracy Kirkwood-G factor is not improved
-with increasing splitting parameter. This fact should be noticed in choosing parameters for
-high accuracy calculation of Kirkwood-G factor.
-
-\subsection{Dynamical quantities}
-
-The dynamical quantities, diffusion constant and viscosity, are listed in Tab.~\ref{tab:thermo}.
-The ZM method of order $l\geq 2$ can almost perfectly reproduce the SPME dynamical quantities.
-The ZM order $l=1$ is of less accurate than higher orders, but is more accurate than the RF.
-Using larger splitting parameters improves the accuracy, and the value $\alpha= 2.0\ \textrm{nm}^{-1}$ is
-suggested for calculating the dynamical quantities.
-
-% \subsection{Damping effect}
-
-% The convergence of the integrated auto-correlation function $I_\eta(T) $ is shown in Fig.~\ref{fig:damp-vis-l1}.
-% \begin{figure}
-%   \centering
-%   \includegraphics[]{fig/result.tiny/fig-vis-l1-damp.eps}
-%   \caption{The convergence of the integrated auto-correlation function $I_\eta(T) $.
-The error bars indicating 95\% confidence level are plotted with the SPME method.
-The different splitting parameters for ZM $l=1$ method are plotted}
-%   \label{fig:damp-vis-l1}
-% \end{figure}
-
-% The RDF is plotted for different splitting parameters $\alpha$ for ZM $l=2$ and 3 in Fig.~\ref{fig:damp-rdf-l23}. Higher $\alpha$ reproduces the RDF better.
-% The system was $L_1$.
-% \begin{figure}[]
-%   \centering
-%   \includegraphics[width=0.49\textwidth]{fig/result.nvt/fig-rdf-l2-damp.eps}
-%   \includegraphics[width=0.49\textwidth]{fig/result.nvt/fig-rdf-l3-damp.eps}
-%   \caption{Radial distribution function for different splitting parameters $\alpha$ for ZM $l=2$ (left) and $l=3$ (right).}
-%   \label{fig:damp-rdf-l23}
-% \end{figure}
-
-% The
-% resulting slop is used to calculate the diffusion constant. The results are listed in Table~\ref{tab:thermo}.
-% The ZM method $l\geq 2$ is consistent with the SPME
-% result, while the RF method is off.
-
-\appendix
-
-\section{The computation of benchmark quantities}
-\label{appendix:benchmark}
-
-In this section we provide the formula used for computing the benchmark quantities. We assume that there are
-$N$ molecules in the water system. The position and configuration of each molecule are fully described
-by $\{\vect r_{3i},\vect r_{3i+1}, \vect r_{3i+2}\},\, i\in 1,\cdots,N$, and the corresponding velocities
-are denoted by $\{\vect v_{3i},\vect v_{3i+1}, \vect v_{3i+2}\},\, i\in 1,\cdots,N$. The mass of each
-atom is denoted by $m_i$.
-
-\subsection{Radial distribution function}
-The radial distribution function (RDF) $g(r)$ is a scalar function of distance $r$, which indicates the
-probability of finding two atoms of distance $r$ apart.  It is a very
-important equilibrium structure property, by which the X-ray scattering
-intensity and a mount of thermodynamic properties can be computed.
-In this work, we investigate the center-of-mass RDF in the water
-system. The RDFs presented in the main text were computed in system $\systemlb$.
-
-% The results are plotted in Fig.~\ref{fig:rdf}. As the order of ZM method goes higher, the precision of RDF improves. In addition, the precision of RF method is between $l=2$ and $l=3$.
-
-\subsection{Pressure}
-The pressure of the system calculated by the virial formula:
-\begin{align}
-  P = \frac1{3V}
-  \Bigg\langle
-  \sum_{i=1}^{3N} \Big( m_i\vect v_i^2 + \vect r_i\cdot \vect F_i \Big)
-  \Bigg\rangle,
-\end{align}
-where $V$ is the volume of the system. The presented pressures were computed in system $\systemla$.
-
-\subsection{Chemical potential}
-
-The chemical potential is defined by
-\begin{align}
-  \mu = \Big(\frac{\partial A}{\partial N}\Big)_{V,T},
-\end{align}
-where $A$ is the Helmholtz free energy.
-In practice the excess chemical potential $\mu^\exc$, which is the
-chemical potential abstracted by the kinetic contribution, is of
-special interest. We calculate the excess chemical potential by the
-thermodynamic integration (TI). In this approach, the interaction
-between an inserted testing molecule and the system is
-denoted by $U_t(\lambda)$, where $\lambda$
-is a coupling parameter in range $[0,1]$.
-When $\lambda = 1$ the testing molecule is fully coupled to the system
-with the TIP3P interaction. When $\lambda=0$, the testing molecule
-is decoupled with the system.
-Therefore the
-Hamiltonian of the system is function of the coupling parameter. The
-excess chemical is calculated by the free energy difference between
-the fully coupled and decoupled states:
-\begin{align}
-  \mu^\exc = \int_0^1 \Big\langle \frac{\partial U_t(\lambda)}{\partial \lambda} \Big\rangle_\lambda d\lambda
-\end{align}
-This integral is usually calculated by numerical integration, which
-equally partitions the range of $\lambda$, simulates the system at each
-discretized $\lambda$, and computes chemical potential by trapezoidal formula.
-Here for the sake of accuracy, 
-we adopt a two step coupling approach: firstly couple the van der Waals
-interaction of the testing particle with the rest of the system (stage vdw),
-and then couple the electrostatic interaction (stage ele).
-During stage vdw, 21 $\lambda$ values are equally
-distributed in $[0,1]$.  During stage ele, 6 $\lambda$ values are
-equally distributed in $[0,0.05]$, while the other 20 $\lambda$ values
-are equally distributed in $(0.05, 1]$. Therefore, in total 47
-simulations are performed for all $\lambda$ values.
-The free energy differences and the error estimates are calculated
-by the Bennet's acceptance ratio method (BAR)~\cite{bennett1976efficient}. 
-The simulations were performed with system $\systemla$.
-
-\subsection{Constant volume/pressure molar heat capacity}
-
-The constant volume heat capacity is defined by the infinitesimal
-increment of the energy due to an infinitesimal increment of the temperature
-at constant volume condition: 
-\begin{align}
-  C_V = \Big(\frac{\partial E}{\partial T}\Big)_V
-\end{align}
-Since it is a extensive thermodynamics quantity, we  normalize
-it by the number molecules in the system $N$ to obtain the
-constant volume molar heat capacity $C_{V,m} = C_V/N$.
-In the MD simulations, 
-the constant volume molar heat capacity is calculated by estimating the
-fluctuation of the Hamiltonian in an NVT simulation:
-\begin{align}
-  C_{V,m} = \frac{1}{k_BT^2 N} \langle (\mathcal H - \langle\mathcal H\rangle)^2 \rangle,
-\end{align}
-where $\mathcal H$ is the 
-Hamiltonian of the system. 
-% It is calculated in system $\systemsb$.
-
-The constant pressure molar heat capacity is defined in
-a similar way, but at constant pressure
-condition. 
-It is calculated by estimating
-the fluctuation of the enthalpy in an NPT simulation~\cite{wang2011existence}:
-\begin{align}
-  C_{p,m} = \frac{1}{k_BT^2 N} \langle ( H - \langle H\rangle)^2 \rangle,
-\end{align}
-where $ H$ is the enthalpy of the system,
-defined by $H = \mathcal H + P\mathcal V$, and $\mathcal V$ is the instantaneous volume
-of the system.
-It has been shown that the statistical error in estimating
-the fluctuations does not decrease with
-respect to the system size~\cite{milchev1986fluctuations,ferrenberg1991statistical}.
-Therefore, both constant volume and pressure molar heat capacities
-were calculated from the simulation of the smallest system: $\systemsb$.
-
-\subsection{Isothermal heat capacity}
-The isothermal heat capacity is defined
-by the normalized increment of volume due to an infinitesimal
-decrement of pressure under constant temperature condition:
-\begin{align}
-  \kappa_T = - \frac 1V \Big(\frac{\partial V}{\partial P}\Big)_T
-\end{align}
-It can be calculated by estimating the fluctuation
-of the instantaneous volume in an NPT simulation~\cite{wang2011existence}:
-\begin{align}
-  \kappa_T = \frac{1}{k_BT} \frac{\langle (\mathcal V - \langle \mathcal V\rangle)^2 \rangle}{\langle \mathcal V\rangle}.
-\end{align}
-Since it is also a fluctuation, the system $\systemsb$ was adopted for simulation.
-
-\subsection{Thermal expansion coefficient}
-The thermal expansion coefficient is defined by
-the normalized increment of volume due to an infinitesimal
-increment of temperature under the constant pressure condition:
-\begin{align}
-  \alpha_V = - \frac 1V \Big(\frac{\partial V}{\partial T}\Big)_P
-\end{align}
-It can be calculated by estimating the cross fluctuation
-of the enthalpy and instantaneous volume  in an NPT simulation:
-\begin{align}
-  \alpha_V = \frac{1}{k_BT^2\langle \mathcal V\rangle} \langle (H - \langle H\rangle)\cdot(\mathcal V - \langle \mathcal V\rangle) \rangle
-\end{align}
-The system $\systemsb$ was adopted for simulation.
-
-\subsection{The dielectric constant}
-
-The dielectric constant can be estimated in a direct manner:
-\begin{align}
-  \eps = 1 + \frac{1}{3L^3 k_BT} ( \langle \vert \vect M\vert^2\rangle - \vert\langle \vect M\rangle\vert^2 )
-\end{align}
-where
-\begin{align}
-  \vect M = \sum_i\boldsymbol\mu_i = \sum_{\alpha\in i} q_\alpha\vect r_\alpha
-\end{align}
-is the total dipole moment of the system. Since it is a fluctuation, the simulated system was $\systemsb$.
-% The results are listed in Tab.~\ref{tab:tmp2}. The dielectric constant calculated in system $\systemsb$ is reported in Table.~\ref{tab:thermo}.
-
-\subsection{Kirkwood G-factor}
-
-The Kirkwood G-factor is defined by~\cite{vanderSpoel2006origin}
-\begin{align}
-  G_k(r) =
-  \Big\langle
-  \frac 1N
-  \sum_{i=1}^N \sum_{j, r_{ij} < r}
-  \frac {\boldsymbol\mu_i \cdot \boldsymbol\mu_j}{\vert \boldsymbol\mu_i\vert \cdot \vert\boldsymbol\mu_j\vert}
-  \Big\rangle,
-\end{align}
-where $r_{ij}$ denotes the oxygen-oxygen distance between two water
-molecules.  The system for computing this quantity is $\systemlb$.
-
-\subsection{Diffusion constant}
-The diffusion constant is calculated from the Einstein relation:
-\begin{align}
-  D = \lim_{t\rightarrow \infty}\frac {1}{6t} \langle \vert \vect r_i(t) - \vect r_i(0)\vert^2\rangle.
-\end{align}
-In practice, the mean-square-displacement $\langle\vert \vect r_i(t) - \vect
-r_i(0)\vert^2\rangle$ is calculated, then the value is linearly fitted. The system for simulation was $\systemsb$.
-
-\subsection{Viscosity}
-The viscosity is calculated from the Green-Kubo relation:
-\begin{align}
-  \eta = \frac{V}{k_BT}\int_0^\infty\langle P_{\alpha\beta}(0) P_{\alpha\beta}(t)\rangle\,dt, \quad \alpha,\beta \in \{x, y, z\}
-\end{align}
-where $\alpha$ and $\beta$ denote the directions, and
-$P_{\alpha\beta}$ denotes the off-diagonal components of the pressure
-tensor. Since we used the isotropic system setting, then it is obvious
-that $P_{xy}$, $P_{yz}$ and $P_{xz}$ are equivalent. Moreover, it has
-been pointed out that in addition $(P_{xx} - P_{yy})/2$ and $(P_{xx} -
-P_{yy})/2$ are two independent components that are equivalent to the
-first three~\cite{alfe1998first}. Therefore, the viscosity is
-calculated from the auto-correlation functions of five independent
-components, and the statistical error is estimated from the standard
-deviation of the viscosities calculated from the five components.
-
-We investigate the convergence of the integral of the auto-correlation function w.r.t.~time:
-\begin{align}
-  I_\eta(T) = \frac{V}{k_BT}\int_0^T\langle P_{\alpha\beta}(0) P_{\alpha\beta}(t)\rangle\,dt,
-\end{align}
-and plot the function $I_\eta(T) $ for all method in
-Fig.~\ref{fig:conv-vis}.  It is clear the integral for the RF method
-converges at 6~ps, while the ZM method converges only in 2~ps, which
-is consistent with the SPME result.  The value of ZM $l=1$ method is
-different from the rest ZM method an SPME result.
-The values listed  in Table~\ref{tab:thermo} are computed with $I_\eta(10\,\textrm{ps})$.
-The
-system for simulation was $\systemsb$.
-
-\begin{figure}
-  \centering
-  \includegraphics[]{fig/result.tiny/fig-vis.eps}
-  \caption{The convergence of the integrated auto-correlation function $I_\eta(T) $. The error bars indicating 95\% confidence level are plotted with the SPME method.}
-  \label{fig:conv-vis}
+\includegraphics[]{fig/result.nvt/fig-rdf-l2-damp.eps}\\
+\includegraphics[]{fig/result.nvt/fig-rdf-l3-damp.eps}
+\caption{  The 
+  splitting parameter dependency in calculating the RDF.
+  The orders of ZM method  $l=2$ (b)  and $l=3$ (c) are presented.
+  In both plots the cut-off radius is 1.2~nm. }
+\label{fig:gkr-conv-alpha}
 \end{figure}
@@
 \newpage
+
 \bibliography{ref}{}

### 2014-11-12 writedown/zm/paper.water/main.tex
small revise...
revise by Fukuda

@@
 %\documentclass[aip,jcp,a4paper,preprint,unsortedaddress,onecolumn,fleqn]{revtex4-1}
+% \input{tcilatex}
 
@@
 %TCIDATA{BibliographyScheme=BibTeX}
-%TCIDATA{LastRevised=Friday, November 07, 2014 19:42:26}
+%TCIDATA{LastRevised=Tuesday, November 11, 2014 22:18:30}
 %TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
@@
 \newcommand{\systemlb}{L_1}
-% \input{tcilatex}
+\input{tcilatex}
 \begin{document}
@@
 \email{ifukuda@protein.osaka-u.ac.jp}
+\author{Haruki Nakamura}
+\date{\today}
 
@@
 discuss the implementation in gromacs later) }[ {\color{blue} COMMENT: what
-do you mean? \recheck{I mean the explanation of group and atomistic cut-off method. the traditional gromacs uses gropu cut-off as default. We need instead the atomistic cut-off}}]
+do you mean? {\color{red} I mean the explanation of group and atomistic
+cut-off method. the traditional gromacs uses gropu cut-off as default. We
+need instead the atomistic cut-off}}] [ {\color{blue} COMMENT: OK, the
+matter for {traditional gromacs} will be discussed in Sec. IIIB, and the
+relevant matter of ZM will be discussed around $\bigstar ${\ in Sec. IIIB.
+If we feel the resulted descriptions are too detailed, they will go to SI.}] 
+}
 
@@
 \subsection{Simulation protocols}
-\label{sec:protocols}
-In this work, we focus on a system of water molecules modeled
-by TIP3P~\cite{jorgensen1983comparison} point-charge particles. 
+
+\label{sec:protocols} In this work, we focus on a system of water molecules
+modeled by TIP3P~\cite{jorgensen1983comparison} point-charge particles. 
 % Other point-charge water models differ in the modeling parameters, and
@@
 Coulomb cut-off and the van der Waals cut-off). [ {\color{blue} COMMENT:
-Yes,..., this is not easy to understand how we mimic AC. \recheck{it should be OK as it is now.}}] To make sure the
-van der Waals interactions were cut-off in a smooth way, they are modified
-in a shell of $0.05$~nm width near the cut-off sphere by the Gromacs
-\textquotedblleft \texttt{shift}\textquotedblright\ method.
+Yes,..., this is not easy to understand how we mimic AC. {\color{red} it
+should be OK as it is now.}} {\color{blue} Please see COMMENT in SecII.}] To
+make sure the van der Waals interactions were cut-off in a smooth way, they
+are modified in a shell of $0.05$~nm width near the cut-off sphere by the
+Gromacs \textquotedblleft \texttt{shift}\textquotedblright\ method.
 
-The short-range part of SPME method \recheck{was cut-offed at 1.9~nm, and was} smoothed in a shell of $0.05$~nm
-width by the Gromacs \textquotedblleft \texttt{pme-switch}%
-\textquotedblright\ method. The reciprocal space grid spacing was set to
-0.06~nm, with B-Spline interpolation order of 6. These parameters were
-chosen to be more accurate than the Gromacs default choices (grid spacing
-0.12~nm and interpolation order 4). The splitting parameter was optimized by
-the error estimate for the SPME method, which is implemented in Gromacs by
-tool \textquotedblleft \texttt{g\_pme\_error}\textquotedblright ~\cite%
-{wang2010optimizing}. The optimized real space and reciprocal space force
-computing errors were equally distributed as $1.4\times 10^{-4}$~kJ/(mol
-nm). Since the magnitude of the forces are of order $10^{2}$~kJ/(mol nm),
-this force computing precision almost reaches the limit of the
-single-precision representation of the floating point numbers.
+The short-range part of SPME method {\color{red} was cut-offed at 1.9~nm,
+and was}[ {\color{blue} OK] }smoothed in a shell of $0.05$~nm width by the
+Gromacs \textquotedblleft \texttt{pme-switch}\textquotedblright\ method. The
+reciprocal space grid spacing was set to 0.06~nm, with B-Spline
+interpolation order of 6. These parameters were chosen to be more accurate
+than the Gromacs default choices (grid spacing 0.12~nm and interpolation
+order 4). The splitting parameter was optimized by the error estimate for
+the SPME method, which is implemented in Gromacs by tool \textquotedblleft 
+\texttt{g\_pme\_error}\textquotedblright ~\cite{wang2010optimizing}. The
+optimized real space and reciprocal space force computing errors were
+equally distributed as $1.4\times 10^{-4}$~kJ/(mol nm). Since the magnitude
+of the forces are of order $10^{2}$~kJ/(mol nm), this force computing
+precision almost reaches the limit of the single-precision representation of
+the floating point numbers. [ {\color{blue} COMMENT: Did you use the
+conducting boundary conditions? (maybe it is default in gromacs.) Please
+state the thing.}]
 
@@
 the cut-off radius. No cut-off smoothing of the electrostatic interaction
-was applied in the cases of RF simulations. We used $1.2$~nm
-cut-off and the experimental dielectric constant $\varepsilon _{\textrm{rf}}=80$.
+was applied in the cases of RF simulations. We used $1.2$~nm cut-off and the
+experimental dielectric constant $\varepsilon _{\text{rf}}=80$.
 
 The ZM method was implemented in Gromacs with the tabulated electrostatic
-interaction. A home-made code was used to generate the interaction tables.
+interaction. A home-made code was used to generate the interaction tables. {%
+\color{blue} }$\bigstar $
 
@@
 S_{1}^{\prime }$, $M_{1}^{\prime }$ and $L_{1}^{\prime }$ are performed. (4)
-The final configurations of $S_{1}^{\prime }$ and $M_{1}^{\prime }$
-were used as initial configurations for system $S_{1}$ and $M_{1}$,
-respectively. The final configuration of $L_{1}^{\prime }$ was
-used as initial configurations for system $L_{0}$ and $L_{1}$. % The SPME
+The final configurations of $S_{1}^{\prime }$ and $M_{1}^{\prime }$ were
+used as initial configurations for system $S_{1}$ and $M_{1}$, respectively.
+The final configuration of $L_{1}^{\prime }$ was used as initial
+configurations for system $L_{0}$ and $L_{1}$. % The SPME
 % parameters for all simulations reported by this work is: real space
@@
 %   special care, please modify.}]
-Using the density in the NVT simulation with
-SPME electrostatic, the pressure ($-0.4\pm 1.5$~Bar) is reproducing the
-target pressure of 1.0~Bar, which means the system is in desired
-thermodynamic state.
+Using the density in the NVT simulation with SPME electrostatic, the
+pressure ($-0.4\pm 1.5$~Bar) is reproducing the target pressure of 1.0~Bar,
+which means the system is in desired thermodynamic state. [ {\color{blue}
+COMMENT: If there are any specific conditions only for the pressure
+calculation, please state around here or elsewhere.] }
 
@@
 viscosity are fluctuations. See details in Appendix~\ref{appendix:benchmark}%
-), because simply increasing the size of the system does not
-improve the accuracy of the simulation~\cite%
+), because simply increasing the size of the system does not improve the
+accuracy of the simulation~\cite%
 {milchev1986fluctuations,ferrenberg1991statistical}. The optimal way of
@@
 pressure, chemical potential, radial distribution function and Kirkwood-G
-factor are of this type) were computed by the largest system $L_{0}$ or $L_{1}$, in order to
-achieve higher parallel efficiency. The system $M_{1}$ is simulated to
-investigate the size-dependency of the Kirkwood-G factor~\cite%
-{vanderSpoel2006origin}.
+factor are of this type) were computed by the largest system $L_{0}$ or $%
+L_{1}$, in order to achieve higher parallel efficiency. The system $M_{1}$
+is simulated to investigate the size-dependency of the Kirkwood-G factor~%
+\cite{vanderSpoel2006origin}.
 
@@
 molar heat capacity and the isothermal compressibility show considerable
-errors.
-The dependence of the ZM results on the order\ $l$\ is \recheck{little}.
-Although the splitting parameter, $\alpha $, also does not have significant
-influence on almost all these thermodynamic quantities for $l=1$, only the
-isothermal compressibility admits a weak dependence [\recheck{all except $\alpha=2$ are in the statistical uncertainty, by which we cannot say $\alpha=1$ is optimal...
-I remove ``and $\alpha=1$ seems optimal''}].
-Overall, the ZM\ agrees with the SPME results without any bias and
-out-performs the RF.
+errors. The dependence of the ZM results on the order\ $l$\ is {\color{red}
+little}. Although the splitting parameter, $\alpha $, also does not have
+significant influence on almost all these thermodynamic quantities for $l=1$%
+, only the isothermal compressibility admits a weak dependence [{\color{red}
+all except $\alpha =2$ are in the statistical uncertainty, by which we
+cannot say $\alpha =1$ is optimal... I remove \textquotedblleft and $\alpha
+=1$ seems optimal\textquotedblright } {\color{blue} OK}]. Overall, the ZM\
+agrees with the SPME results without any bias and out-performs the RF.
 
-\recheck{
-  It should be noticed that in the calculation of the chemical potential,
-  the energy correction plays an important role. In the case of $l=1$, $\alpha = 0.0\,\text{nm}^{-1}$,
-  it contributes $-0.1$~kJ/mol to the final result.
-  By increasing $l$ or $\alpha$, this contribution
-  becomes more significant, and reaches $-0.6$~kJ/mol for $l=4$, $\alpha = 0.0\,\text{nm}^{-1}$, and
-  $-1.0$~kJ/mol for $l=1$, $\alpha = 2.0\,\text{nm}^{-1}$, respectively.
-}
+{\color{red} It should be noticed that in the calculation of the chemical
+potential, the energy correction plays an important role. In the case of $%
+l=1 $, $\alpha =0.0\,\text{nm}^{-1}$, it contributes $-0.1$~kJ/mol to the
+final result. By increasing $l$ or $\alpha $, this contribution becomes more
+significant, and reaches $-0.6$~kJ/mol for $l=4$, $\alpha =0.0\,\text{nm}%
+^{-1}$, and $-1.0$~kJ/mol for $l=1$, $\alpha =2.0\,\text{nm}^{-1}$,
+respectively. [\color{blue}COMMENT: We will clarify what is the "energy
+correction" after making SecII, and describe the relation to IPSp after
+making Appendix B.] }
 
@@
 The error bars present the statistical uncertainty at 95\% confidence level. 
-\recheck{This uncertainty is twice of the standard deviation of the estimates (which are averages along MD trajectories) that
-is calculated by the block average method~\cite{janke2002statistical}.}
-}
+{\color{red} This uncertainty is twice of the standard deviation of the
+estimates (which are averages along MD trajectories) that is calculated by
+the block average method~\protect\cite{janke2002statistical}.} }
 \label{fig:pres-comp}
@@
 % \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l4.eps}
-\caption{
-The pressure convergence with respect to the cut-off radius for ZM
-method $l=1$ with splitting parameter from $0.0$ to $2.0\,\text{nm}^{-1}$. The black
-solid line indicates the magnitude of the correct pressure: 1~Bar. The error
-bars present the statistical uncertainty at 95\% confidence level.}
+\caption{ The pressure convergence with respect to the cut-off radius for ZM
+method $l=1$ with splitting parameter from $0.0$ to $2.0\,\text{nm}^{-1}$.
+The black solid line indicates the magnitude of the correct pressure: 1~Bar.
+The error bars present the statistical uncertainty at 95\% confidence level.}
 \label{fig:pres-l1}
@@
 l$\ and for a small $r_{\text{c}}$, which is consistent with the property of
-the pair potential of the ZM~\cite{fukuda2014zero}. The convergence is not sensitive to $%
-\alpha $ up to $1.0\,\text{nm}^{-1}$.
+the pair potential of the ZM~\cite{fukuda2014zero}. The convergence is not
+sensitive to $\alpha $ up to $1.0\,\text{nm}^{-1}$.
 
-\recheck{It should be noted that even with the system $L_0$ that contains 13824 water molecules}, the
-fluctuation (measured by standard deviation) of the pressure is roughly
-100~Bar, which means that it is very difficult to achieve very accurate
-estimate for this quantity. In practice a pressure error of 20~Bar is still
-acceptable.
+{\color{red} It should be noted that even with the system $L_{0}$ that
+contains 13824 water molecules[} {\color{blue} OK}], the fluctuation
+(measured by standard deviation) of the pressure is roughly 100~Bar, which
+means that it is very difficult to achieve very accurate estimate for this
+quantity. In practice a pressure error of 20~Bar is still acceptable.
 
@@
 \includegraphics[width=0.5\textwidth]{fig/result.nvt.tiny/fig-eps-t-3000.eps}
-\caption{The dielectric constant convergence with respect to
-  length of the trajectories used to compute the value.
-  The SPME, ZM method $l=1$ to 4 and RF are presented.
-  The cut-off distance of ZM and RF methods was 1.2~nm. The working parameters of SPME are given in Sec.~\ref{sec:protocols}
-  The system used for simulation is $S_1$.
-}
+\caption{The dielectric constant convergence with respect to length of the
+trajectories used to compute the value. The SPME, ZM method $l=1$ to 4 and
+RF are presented. The cut-off distance of ZM and RF methods was 1.2~nm. The
+working parameters of SPME are given in Sec.~\protect\ref{sec:protocols} The
+system used for simulation is $S_{1}$.[ {\color{blue} This is for $S_{1}$
+and not shown in your report. right? }]}
 \label{fig:eps-conv}
@@
 in Tab.~\ref{tab:thermo}, and are consistent with the SPME computed results.
-In contrast, the RF method has poor accuracy in the dielectric constant.
-It is
-well known that the dielectric feature shows system-size dependence~\cite%
+In contrast, the RF method has poor accuracy in the dielectric constant. It
+is well known that the dielectric feature shows system-size dependence~\cite%
 {vanderSpoel2006origin}, therefore we further investigated this dependence
-and also the effect of the cutoff length, as shown in Table~I of SI. ZM shows
-good results without any \recheck{system-size dependency} and indicate $r_{\text{c}}\sim
-1.2\, $nm\ being suffice for the accuracy. Since a slow convergence is also known for
-the dielectric constant, we have monitored the behavior as shown in Fig.~\ref{fig:eps-conv},
-and confirm the sufficient convergence w.r.t.~the length of the trajectories.
-\recheck{[COMMENT: the system size and cut-off dependency
+and also the effect of the cutoff length, as shown in Table~I of SI. ZM
+shows good results without any {\color{red} system-size dependency} {[} {%
+\color{blue} OK}]and indicate $r_{\text{c}}\sim 1.2\,$nm\ being suffice for
+the accuracy. Since a slow convergence is also known for the dielectric
+constant, we have monitored the behavior as shown in Fig.~\ref{fig:eps-conv}%
+, and confirm the sufficient convergence w.r.t.~the length of the
+trajectories. {%
+\color{red} [COMMENT: the system size and cut-off dependency
   are important,
@@
   and NO new phenomenum is observed, 
-  they are put in SI.]}
+  they are put in SI.]\lbrack } {\color{blue} OK}]
 
@@
 \centering
-\includegraphics[]{fig/result.nvt.small/fig-gkr-small.eps}\\
+\includegraphics[]{fig/result.nvt.small/fig-gkr-small.eps}\newline
 \includegraphics[]{fig/result.nvt/fig-gkr.eps}
-\caption{The Kirkwood G-factor calculated for system $%
-M_{1}$ (a) and $L_{1} $ (b). ZM method of orders $l=1,2,3$ and 4 with the
-cut-off 1.2~nm and splitting parameter $\protect\alpha =0.0\,\text{nm}^{-1}$
-are plotted. The RF method is shown as an comparison, which uses a cut-off
-radius of 1.2~nm and dielectric constant of 80. The statistical uncertainty
-of the SPME method is presented at 95~\% confidence level with the red error
-bars. the statistical uncertainty of the SPME method is denoted by the red
-error bars. The statistical uncertainties of the other methods are
-essentially of the same size as the SPME, so they are not presented in the
-figure for clarity.}
+\caption{The Kirkwood G-factor calculated for system $M_{1}$ (a) and $L_{1} $
+(b). ZM method of orders $l=1,2,3$ and 4 with the cut-off 1.2~nm and
+splitting parameter $\protect\alpha =0.0\,\text{nm}^{-1}$ are plotted. The
+RF method is shown as an comparison, which uses a cut-off radius of 1.2~nm
+and dielectric constant of 80. The statistical uncertainty of the SPME
+method is presented at 95~\% confidence level with the red error bars. the
+statistical uncertainty of the SPME method is denoted by the red error bars.
+The statistical uncertainties of the other methods are essentially of the
+same size as the SPME, so they are not presented in the figure for clarity.}
 \label{fig:gkr}
@@
 \centering
-\includegraphics[]{fig/result.nvt/fig-gkr-conv.eps} %
+\includegraphics[]{fig/result.nvt/fig-gkr-conv.eps}
 \caption{ The cut-off dependency in calculating the Kirkwood-G factor. The
-order of ZM method is $l=3$. The splitting parameter is $\protect%
-\alpha =0.0\,\text{nm}^{-1}$. The
-statistical uncertainty is presented at 95~\% confidence level by the
-error bars. }
+order of ZM method is $l=3$. The splitting parameter is $\protect\alpha %
+=0.0\,\text{nm}^{-1}$. The statistical uncertainty is presented at 95~\%
+confidence level by the error bars. }
 \label{fig:gkr-conv}
@@
 \centering
-\includegraphics[]{fig/result.nvt/fig-gkr-l1-damp.eps} %
-\caption{ The splitting parameter dependency in calculating the Kirkwood-G factor at order $l=1$.
-  The cut-off radius is 1.2~nm. The
-statistical uncertainty is presented at 95~\% confidence level by the
-error bars. }
+\includegraphics[]{fig/result.nvt/fig-gkr-l1-damp.eps}
+\caption{ The splitting parameter dependency in calculating the Kirkwood-G
+factor at order $l=1$. The cut-off radius is 1.2~nm. The statistical
+uncertainty is presented at 95~\% confidence level by the error bars. [ {\ 
+\color{blue} This is also not shown in your report. right? }]}
 \label{fig:gkr-damp-l1}
@@
 We thus investigated the cut-off dependency in calculating the Kirkwood-G
-factor and present it in Fig.~\ref{fig:gkr-conv} for ZM method of order $l=3$.
-Without surprising, the Kirkwood-G factor converges to the SPME result
-when using increasingly large cut-off radius.
-\recheck{In Fig.~\ref{fig:gkr-damp-l1}, it shows that in the case of $l=1$, 
-  the largest splitting parameter ($\alpha=2.0\ \textrm{nm}^{-1}$) is worse in calculating
-  the Kirkwood-G factor than smaller splitting parameters.}
-Splitting parameter dependency
-was not so clear for $l=2$ and 3 (shown in SI).  Note that in many cases the discrepancies
-from the SPME were relatively prominent in the middle range of the distance
-and they tend small for larger distance.
+factor and present it in Fig.~\ref{fig:gkr-conv} for ZM method of order $l=3$%
+. Without surprising, the Kirkwood-G factor converges to the SPME result
+when using increasingly large cut-off radius. {\color{red} In Fig.~\ref%
+{fig:gkr-damp-l1}, it shows that in the case of $l=1$, the largest splitting
+parameter ($\alpha =2.0\ \text{nm}^{-1}$) is worse in calculating the
+Kirkwood-G factor than smaller splitting parameters.[} {\color{blue} OK}]
+Splitting parameter dependency was not so clear for $l=2$ and 3 (shown in
+SI). Note that in many cases the discrepancies from the SPME were relatively
+prominent in the middle range of the distance and they tend small for larger
+distance.
 
@@
 \includegraphics[]{fig/result.nvt.tiny/fig-vis.eps}
-\caption{The convergence
-  of the integrated auto-correlation function $I_{\protect\eta }(T)$.
-  Different orders of ZM method are compared with the SPME as well as RF results.
-  The error bars indicating 95\% confidence level are plotted with the SPME
-  method. }
+\caption{The convergence of the integrated auto-correlation function $I_{%
+\protect\eta }(T)$. Different orders of ZM method are compared with the SPME
+as well as RF results. The error bars indicating 95\% confidence level are
+plotted with the SPME method. }
 \label{fig:conv-vis}
@@
 \includegraphics[]{fig/result.nvt.tiny/fig-vis-l1-damp.eps}
-\caption{The convergence
-  of the integrated auto-correlation function $I_{\protect\eta }(T)$.
-  Different splitting parameters for ZM order $l=1$ are plotted.
-The
-error bars indicating 95\% confidence level are plotted with the SPME
-method. }
+\caption{The convergence of the integrated auto-correlation function $I_{%
+\protect\eta }(T)$. Different splitting parameters for ZM order $l=1$ are
+plotted. The error bars indicating 95\% confidence level are plotted with
+the SPME method. }
 \label{fig:conv-vis-damp}
@@
 functions (RDFs) of TIP3P water calculated by the SPME, ZM ($l=1,2,3$ and $4$%
-) with $\alpha =0$\ and RF methods. It is observed from the figure
-that the ZM RDFs are consist very well with the SPME RDF, except
-oscillations around the cut-off radius. This oscillations are not so large,
-as the maximum magnitude of the discrepancies from the SPME is about $2\%$, but should be artificial. However,
-higher order ZM method present lower amplitude oscillation, and when $l\geq 3
-$, the improvement is dramatic and the oscillation is almost negligible.
+) with $\alpha =0$\ and RF methods. It is observed from the figure that the
+ZM RDFs are consist very well with the SPME RDF, except oscillations around
+the cut-off radius. This oscillations are not so large, as the maximum
+magnitude of the discrepancies from the SPME is about $2\%$,{[} {\color{blue}
+"$2\%"$ is just my guess. How about stating here the maximum error for
+individual $l$}] but should be artificial. However, higher order ZM method
+present lower amplitude oscillation, and when $l\geq 3$, the improvement is
+dramatic and the oscillation is almost negligible.
 
 {\color{red} Shall we comment here on the fact that group cut-off produces
-smoother RDF? Add figures in Supplementary material \bluec{ Do you
-mean the reason of the goodness in RF?} \recheck{Yes, shall we discuss it? or it is too complicated and not very relavant to the current paper?}}
+smoother RDF? Add figures in Supplementary material {\color{blue} Do you
+mean the reason of the goodness in RF?} {\color{red} Yes, shall we discuss
+it? or it is too complicated and not very relevant to the current paper?}[} {%
+\color{blue} It is preferable to write it if the reason of the goodness is
+clear. Anyway, please describe.... This is the only matter ZM is inferior to
+RF. So, it may be interesting if the reason is clear. }]
 
@@
 seen in several quantities. The weak effect is seen in the isothermal
-compressibility, \recheck{Kirkwood-G factor (only $l=1$)} and dynamical quantities including the diffusion constant
-and viscosity, while the strong effect is seen in the RDF. Anti-damping
-effect was also observed in the pressure when $\alpha >1$. A larger order is
+compressibility, {\color{red} } and dynamical quantities including the
+diffusion constant and viscosity, while the strong effect is seen in the
+RDF. Anti-damping effect was also observed in the pressure when $\alpha >1$
+and  {\color{blue}Kirkwood-G factor (only $l=1$).[ OK??}] A larger order is
 preferable slightly for dynamical quantities including diffusion constant
@@
 
-\recheck{
-At cut-off radius of 1.2~nm, the recommanded choices of parameters for TIP3P system are
-thus $\alpha \leq 1$~$\textrm{nm}^{-1}$ and  $l=2$ or $l=3$.
-Using these parameters, the ZM method achieves almost perfect accuracy in
-computing the excess chemical potential, constant volume/pressure heat capacity, isothermal
-compressibility, thermal expansion coefficient, dielectric constant
-diffusion constant and viscosity.
-The order $l=2$ performs better in reproducing the
-pressure than $l=3$ (10 v.s.~17~Bar), but worse in calculating the RDF (0.2\% error v.s.~almost negligible).
-Both of orders 2 and 3 are not sensitve to the splitting parameter up to 1.0~$\textrm{nm}^{-1}$.
-Further increasing the splitting parameter will push the accuracy of RDF in case $l=2$ to as high as $l=3$, however, the
-pressure accuracy decreases to 40~Bar (anti-damping effect), so it is not recommanded.
-It should be noticed that the recommanded parameters are less accurate (largest $\sim 5$\% error)
-in calculating the Kirkwood-G factor for large systems (in our case $L_1$ containing 13,824 molecules).
-The accuracy can be improved by using larger cut-off radius, and thus more computer
-time should be invested.
-}
+{\color{red} At cut-off radius of 1.2~nm, the recommended choices of
+parameters for TIP3P system are thus $\alpha \leq 1$~$\text{nm}^{-1}$ and $%
+l=2$ or $l=3$. Using these parameters, the ZM method achieves almost perfect
+accuracy in computing the excess chemical potential, constant
+volume/pressure heat capacity, isothermal compressibility, thermal expansion
+coefficient, dielectric constant diffusion constant and viscosity. The order 
+$l=2$ performs better in reproducing the pressure than $l=3$ (10
+v.s.~17~Bar), but worse in calculating the RDF (0.2\% error v.s.~almost
+negligible). Both of orders 2 and 3 are not sensitive to the splitting
+parameter up to 1.0~$\text{nm}^{-1}$.} {\color{blue} Although further
+increasing the splitting parameter will push the accuracy of RDF in case $l=2
+$ to as high as $l=3$, the pressure accuracy decreases (anti-damping
+effect), so that $\alpha >1$\ for $l=2$ or $l=3$ is not recommended. It
+should be noticed that the recommended parameters indicate $5$\% error
+(largest) in calculating the Kirkwood-G factor for a larger system ($L_{1}$
+containing 13,824 molecules). [\color{blue}COMMENT:Did you calculate the G
+factor for the smallest $S_{1}$? \ If so, how was the results?] If we seek
+more accuracy for the G factor, we should use a larger cut-off radius at the
+expense of the computational time. } 
 % Further increasing the splitting paraemter
@@
 
-[{\color{blue}---%
-$>$ IPSp; I can contribute later. IPSp should be good for the
-current water system since IPSp is developed for "polar" molecule (while
+[{\color{blue}---$>$ IPSp; I can contribute later. IPSp should be good for
+the current water system since IPSp is developed for "polar" molecule (while
 IPSn is not)}]
@@
 \mathbf{\mathit{r}}_{3i-2},\mathbf{\mathit{r}}_{3i-1},\mathbf{\mathit{r}}%
-_{3i}\},\,i\in 1,\cdots ,N$, and the corresponding velocities are denoted
-by $\{\mathbf{\mathit{v}}_{3i-2},\mathbf{\mathit{v}}_{3i-1},\mathbf{\mathit{v}}%
+_{3i}\},\,i\in 1,\cdots ,N$, and the corresponding velocities are denoted by 
+$\{\mathbf{\mathit{v}}_{3i-2},\mathbf{\mathit{v}}_{3i-1},\mathbf{\mathit{v}}%
 _{3i}\},\,i\in 1,\cdots ,N$. The mass of each atom is denoted by $m_{i}$.
@@
 The pressure of the system calculated by the virial formula:[ {\color{blue}
-Modified $3N\longrightarrow N$} \recheck{should be $3N$!, each molecule contains 3 atoms. The pressure is computed by atom based virial formula}]%
+Modified $3N\longrightarrow N$} {\color{red} should be $3N$!, each molecule
+contains 3 atoms. The pressure is computed by atom based virial formula. %
+\color{blue} OK, I was just confusing}]%
 \begin{equation*}
@@
 \end{equation*}%
-The
-values listed in Table~\ref{tab:thermo} are computed with $I_{\eta }(10\,%
+The values listed in Table~\ref{tab:thermo} are computed with $I_{\eta }(10\,%
 \text{ps})$. The system for simulation was $S_{1}$.
@@
 
-\bibliography{ref}{}
-\bibliographystyle{unsrt}
+\bibliographystyle{plain}
+\bibliography{ref}
+{}
 

### 2014-11-13 writedown/zm/paper.water/main.tex
my revise

@@
 \newcommand{\systemlb}{L_1}
-\input{tcilatex}
+% \input{tcilatex}
 \begin{document}
@@
 \email{han.wang@fu-berlin.de}
+\affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road
+6, 100088 Beijing, China}
+\affiliation{Zuse Institute Berlin (ZIB), Germany}
 \author{Ikuo Fukuda}
 \email{ifukuda@protein.osaka-u.ac.jp}
+\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
+Osaka 565-0871, Japan}
+\affiliation{RIKEN (The Institute of Physical and Chemical Research), 2-1 Hirosawa, Wako,
+Saitama 351-0198, Japan}
 \author{Haruki Nakamura}
+\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
+Osaka 565-0871, Japan}
+
 \date{\today}
@@
 \maketitle
-\affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road
-6, 100088 Beijing, China}
-\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
-Osaka 565-0871, Japan}
-\affiliation{RIKEN (The Institute of Physical and Chemical Research), 2-1 Hirosawa, Wako,
-Saitama 351-0198, Japan}
 
@@
 }
+[\recheck{please see the red part in Sec. III B. The order of the paragraphs are also rearranged.}]
 
@@
 
-The neighbor lists were updated every 5 time-steps. The \textquotedblleft 
-\texttt{group}\textquotedblright\ cut-off scheme in Gromacs was used. In
-order to mimic the atomistic cut-off manner, the radius for neighbor list
-building was set 0.3~nm larger than the cut-off radius (the maximum of
-Coulomb cut-off and the van der Waals cut-off). [ {\color{blue} COMMENT:
-Yes,..., this is not easy to understand how we mimic AC. {\color{red} it
-should be OK as it is now.}} {\color{blue} Please see COMMENT in SecII.}] To
-make sure the van der Waals interactions were cut-off in a smooth way, they
-are modified in a shell of $0.05$~nm width near the cut-off sphere by the
-Gromacs \textquotedblleft \texttt{shift}\textquotedblright\ method.
+The neighbor lists were updated every 5 time-steps.
+\recheck{The Gromacs by default uses the group cut-off scheme, while the ZM method suggests
+  an atom cut-off scheme~\cite{fukuda2011molecular,fukuda2013zero}. The difference between
+  these cut-off schemes is discussed in detail in e.g.~Ref.~\cite{hunenberger1998alternative,baumketner2009removing}.
+  We adopted the atom based cut-off scheme in the simulations using the
+  SPME (short-range part) and ZM electrostatic methods.
+  In order to mimic the atom cut-off scheme in the Gromacs group cut-off implementation,
+  the radius for neighbor list
+  updating was set 0.3~nm larger than the cut-off radius (the maximum of
+  Coulomb cut-off and the van der Waals cut-off). 
+}
 
-The short-range part of SPME method {\color{red} was cut-offed at 1.9~nm,
-and was}[ {\color{blue} OK] }smoothed in a shell of $0.05$~nm width by the
+% The \textquotedblleft 
+% \texttt{group}\textquotedblright\ cut-off scheme in Gromacs was used.[ {\color{blue} COMMENT:
+% Yes,..., this is not easy to understand how we mimic AC. {\color{red} it
+%   should be OK as it is now.}} {\color{blue} Please see COMMENT in SecII.}]
+
+The short-range part of SPME method was cut-offed at 1.9~nm,
+and was smoothed in a shell of $0.05$~nm width by the
 Gromacs \textquotedblleft \texttt{pme-switch}\textquotedblright\ method. The
@@
 than the Gromacs default choices (grid spacing 0.12~nm and interpolation
-order 4). The splitting parameter was optimized by the error estimate for
-the SPME method, which is implemented in Gromacs by tool \textquotedblleft 
+order 4).
+\recheck{The conducting boundary condition was used with SPME.}
+The splitting parameter was optimized by the error estimate, which is implemented in Gromacs by tool \textquotedblleft 
 \texttt{g\_pme\_error}\textquotedblright ~\cite{wang2010optimizing}. The
@@
 precision almost reaches the limit of the single-precision representation of
-the floating point numbers. [ {\color{blue} COMMENT: Did you use the
-conducting boundary conditions? (maybe it is default in gromacs.) Please
-state the thing.}]
+the floating point numbers.
+% [ {\color{blue} COMMENT: Did you use the
+% conducting boundary conditions? (maybe it is default in gromacs.) Please
+% state the thing.}]
+
+The ZM method was implemented in Gromacs with the tabulated electrostatic
+interaction. A home-made code was used to generate the interaction tables. {%
+\color{blue} }$\bigstar $
 
@@
 the cut-off radius. No cut-off smoothing of the electrostatic interaction
-was applied in the cases of RF simulations. We used $1.2$~nm cut-off and the
+was applied in the cases of RF simulations. We used $1.2$~nm cut-off radius and the
 experimental dielectric constant $\varepsilon _{\text{rf}}=80$.
 
-The ZM method was implemented in Gromacs with the tabulated electrostatic
-interaction. A home-made code was used to generate the interaction tables. {%
-\color{blue} }$\bigstar $
+The van der Waals interaction was always cut-offed at 1.2~nm, and it was
+modified in a shell of $0.05$~nm width near the cut-off sphere by the
+Gromacs \textquotedblleft \texttt{shift}\textquotedblright\ method.
 
@@
 COMMENT: If there are any specific conditions only for the pressure
-calculation, please state around here or elsewhere.] }
+calculation, please state around here or elsewhere.] [\recheck{No.}]}
 
@@
 significant influence on almost all these thermodynamic quantities for $l=1$%
-, only the isothermal compressibility admits a weak dependence [{\color{red}
-all except $\alpha =2$ are in the statistical uncertainty, by which we
-cannot say $\alpha =1$ is optimal... I remove \textquotedblleft and $\alpha
-=1$ seems optimal\textquotedblright } {\color{blue} OK}]. Overall, the ZM\
+, only the isothermal compressibility admits a weak dependence. Overall, the ZM\
 agrees with the SPME results without any bias and out-performs the RF.
@@
 
-{\color{red} It should be noted that even with the system $L_{0}$ that
-contains 13824 water molecules[} {\color{blue} OK}], the fluctuation
+It should be noted that even with the system $L_{0}$ that
+contains 13824 water molecules, the fluctuation
 (measured by standard deviation) of the pressure is roughly 100~Bar, which
@@
 system used for simulation is $S_{1}$.[ {\color{blue} This is for $S_{1}$
-and not shown in your report. right? }]}
+and not shown in your report. right? } \recheck{Right, it was not shown}]}
 \label{fig:eps-conv}
@@
 In contrast, the RF method has poor accuracy in the dielectric constant. It
-is well known that the dielectric feature shows system-size dependence~\cite%
-{vanderSpoel2006origin}, therefore we further investigated this dependence
+is well known that the dielectric feature shows system-size dependence~\cite{vanderSpoel2006origin},
+therefore we further investigated this dependence
 and also the effect of the cutoff length, as shown in Table~I of SI. ZM
-shows good results without any {\color{red} system-size dependency} {[} {%
-\color{blue} OK}]and indicate $r_{\text{c}}\sim 1.2\,$nm\ being suffice for
+shows good results without any system-size dependency and indicate $r_{\text{c}}\sim 1.2\,$nm\ being suffice for
 the accuracy. Since a slow convergence is also known for the dielectric
-constant, we have monitored the behavior as shown in Fig.~\ref{fig:eps-conv}%
-, and confirm the sufficient convergence w.r.t.~the length of the
-trajectories. {%
-\color{red} [COMMENT: the system size and cut-off dependency
-  are important,
-  but since the result are consistent with system $S_1$ and rc=1.2~nm (shown in table II),
-  and NO new phenomenum is observed, 
-  they are put in SI.]\lbrack } {\color{blue} OK}]
+constant, we have monitored the behavior as shown in Fig.~\ref{fig:eps-conv},
+and confirm the sufficient convergence w.r.t.~the length of the
+trajectories.
 
@@
 radius (1.2~nm), while this oscillation is not obvious for $l\geq 2$.
+\recheck{
+  The Kirkwood-G factor computed by ZM in system $S_1$ is as good as that computed in $M_1$,
+  and is presented in SI.}
 
@@
 uncertainty is presented at 95~\% confidence level by the error bars. [ {\ 
-\color{blue} This is also not shown in your report. right? }]}
+\color{blue} This is also not shown in your report. right? } \recheck{Right, it was not shown.}]}
 \label{fig:gkr-damp-l1}
@@
 . Without surprising, the Kirkwood-G factor converges to the SPME result
-when using increasingly large cut-off radius. {\color{red} In Fig.~\ref%
+when using increasingly large cut-off radius. In Fig.~\ref%
 {fig:gkr-damp-l1}, it shows that in the case of $l=1$, the largest splitting
 parameter ($\alpha =2.0\ \text{nm}^{-1}$) is worse in calculating the
-Kirkwood-G factor than smaller splitting parameters.[} {\color{blue} OK}]
+Kirkwood-G factor than smaller splitting parameters.
 Splitting parameter dependency was not so clear for $l=2$ and 3 (shown in
@@
 the cut-off radius. This oscillations are not so large, as the maximum
-magnitude of the discrepancies from the SPME is about $2\%$,{[} {\color{blue}
-"$2\%"$ is just my guess. How about stating here the maximum error for
-individual $l$}] but should be artificial. However, higher order ZM method
+magnitude of the discrepancies from the SPME is about \recheck{ $1.9\%$ for $l=1$ and 0.3\% for $l=2$,}
+% {[} {\color{blue}
+% "$2\%"$ is just my guess. How about stating here the maximum error for
+% individual $l$}]
+but should be artificial. However, higher order ZM method
 present lower amplitude oscillation, and when $l\geq 3$, the improvement is
@@
 clear. Anyway, please describe.... This is the only matter ZM is inferior to
-RF. So, it may be interesting if the reason is clear. }]
+RF. So, it may be interesting if the reason is clear. } \recheck{I agree, if the
+reason is not clear for us, we should not touch this topic.}]
 
@@
 RDF. Anti-damping effect was also observed in the pressure when $\alpha >1$
-and  {\color{blue}Kirkwood-G factor (only $l=1$).[ OK??}] A larger order is
+and  Kirkwood-G factor (only $l=1$). A larger order is
 preferable slightly for dynamical quantities including diffusion constant
@@
 containing 13,824 molecules). [\color{blue}COMMENT:Did you calculate the G
-factor for the smallest $S_{1}$? \ If so, how was the results?] If we seek
+factor for the smallest $S_{1}$? \ If so, how was the results? \recheck{see the added
+  in Sec. IV B and SI}] If we seek
 more accuracy for the G factor, we should use a larger cut-off radius at the
@@
 
-The pressure of the system calculated by the virial formula:[ {\color{blue}
-Modified $3N\longrightarrow N$} {\color{red} should be $3N$!, each molecule
-contains 3 atoms. The pressure is computed by atom based virial formula. %
-\color{blue} OK, I was just confusing}]%
+The pressure of the system calculated by the virial formula:
+% [ {\color{blue}
+% Modified $3N\longrightarrow N$} {\color{red} should be $3N$!, each molecule
+% contains 3 atoms. The pressure is computed by atom based virial formula. %
+% \color{blue} OK, I was just confusing}]%
 \begin{equation*}
@@
 
-\bibliographystyle{plain}
+% \bibliographystyle{plain}
 \bibliography{ref}

### 2014-11-13 writedown/zm/paper.water/si.tex
my revise

@@
 \email{han.wang@fu-berlin.de}
+\affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road
+6, 100088 Beijing, China}
+\affiliation{Zuse Institute Berlin (ZIB), Germany}
 \author{Ikuo Fukuda}
 \email{ifukuda@protein.osaka-u.ac.jp}
+\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
+Osaka 565-0871, Japan}
+\affiliation{RIKEN (The Institute of Physical and Chemical Research), 2-1 Hirosawa, Wako,
+Saitama 351-0198, Japan}
+\author{Haruki Nakamura}
+\affiliation{Institute for Protein Research, Osaka University, 3-2 Yamadaoka, Suita,
+Osaka 565-0871, Japan}
 
@@
 \centering
+\includegraphics[]{fig/result.nvt.tiny/fig-gkr.eps}
+\caption{
+  The Kirkwood G-factor calculated for system $S_{1}$.
+  ZM method of orders $l=1,2,3$ and 4 with the cut-off 1.2~nm and
+splitting parameter $\protect\alpha =0.0\,\text{nm}^{-1}$ are plotted. The
+RF method is shown as an comparison, which uses a cut-off radius of 1.2~nm
+and dielectric constant of 80. The statistical uncertainty of the SPME
+method is presented at 95~\% confidence level with the red error bars. the
+statistical uncertainty of the SPME method is denoted by the red error bars.
+The statistical uncertainties of the other methods are essentially of the
+same size as the SPME, so they are not presented in the figure for clarity.
+}
+\label{fig:gkr-conv-alpha}
+\end{figure}
+
+\begin{figure}[tbp]
+\centering
 \includegraphics[]{fig/result.nvt/fig-gkr-l2-damp.eps}\\

### 2014-11-14 writedown/zm/paper.water/main.tex
another round...

@@
 %\documentclass[aip,jcp,a4paper,preprint,unsortedaddress,onecolumn,fleqn]{revtex4-1}
+% \input{tcilatex}
 % \input{tcilatex}
@@
 %TCIDATA{BibliographyScheme=BibTeX}
-%TCIDATA{LastRevised=Tuesday, November 11, 2014 22:18:30}
+%TCIDATA{LastRevised=Thursday, November 13, 2014 17:19:51}
 %TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
@@
 Osaka 565-0871, Japan}
-
 \date{\today}
@@
 do you mean? {\color{red} I mean the explanation of group and atomistic
-cut-off method. the traditional gromacs uses gropu cut-off as default. We
+cut-off method. the traditional gromacs uses group cut-off as default. We
 need instead the atomistic cut-off}}] [ {\color{blue} COMMENT: OK, the
@@
 If we feel the resulted descriptions are too detailed, they will go to SI.}] 
-}
-[\recheck{please see the red part in Sec. III B. The order of the paragraphs are also rearranged.}]
+} [{\color{red} please see the red part in Sec. III B. The order of the
+paragraphs are also rearranged.}][ {\color{blue} I added comments.}]
 
@@
 at 1~Bar. All systems were integrated with leap-frog scheme at a time-step
-of 0.001~ps.
+of $0.001$~ps.
 
-The neighbor lists were updated every 5 time-steps.
-\recheck{The Gromacs by default uses the group cut-off scheme, while the ZM method suggests
-  an atom cut-off scheme~\cite{fukuda2011molecular,fukuda2013zero}. The difference between
-  these cut-off schemes is discussed in detail in e.g.~Ref.~\cite{hunenberger1998alternative,baumketner2009removing}.
-  We adopted the atom based cut-off scheme in the simulations using the
-  SPME (short-range part) and ZM electrostatic methods.
-  In order to mimic the atom cut-off scheme in the Gromacs group cut-off implementation,
-  the radius for neighbor list
-  updating was set 0.3~nm larger than the cut-off radius (the maximum of
+The neighbor lists were updated every 5 time-steps. {\color{red} The Gromacs
+by default uses the group cut-off scheme, while the ZM method suggests an
+atom cut-off scheme~\cite{fukuda2011molecular,fukuda2013zero}.} [{%
+\color{blue} COMMENT: I am confusing. Is "rcoulomb"="rlist" default in
+gromacs? If so, "Gromacs by default uses the group cut-off scheme" is
+correct. Or, here, you want to say the "neighbor list making" is done by
+group cut-off? (I reread your "cutoff.pdf")} \recheck{the default is rcoulomb = rlist. both
+the neighbor list making and the force computing are in group manner.
+I prefer not describing this issue in the paper in detail, because the reader
+may not be familiar with the terminology (rlist, rcoulomb, and so on) and
+the mechanism behind. I think describing how to use ZM correctly in gromacs is enough.
+}] The difference between these
+cut-off schemes is discussed in detail in e.g.~Ref.~\cite%
+{hunenberger1998alternative,baumketner2009removing}. We adopted the atom
+based cut-off scheme in the simulations using the SPME (short-range part)
+and ZM electrostatic methods. In order to mimic the atom cut-off scheme in
+the Gromacs group cut-off implementation, the radius for neighbor list
+updating was set ${0.3}$~nm larger than the cut-off radius (the maximum of
 Coulomb cut-off and the van der Waals cut-off).
-}
 
@@
 
-The short-range part of SPME method was cut-offed at 1.9~nm,
-and was smoothed in a shell of $0.05$~nm width by the
-Gromacs \textquotedblleft \texttt{pme-switch}\textquotedblright\ method. The
-reciprocal space grid spacing was set to 0.06~nm, with B-Spline
-interpolation order of 6. These parameters were chosen to be more accurate
-than the Gromacs default choices (grid spacing 0.12~nm and interpolation
-order 4).
-\recheck{The conducting boundary condition was used with SPME.}
-The splitting parameter was optimized by the error estimate, which is implemented in Gromacs by tool \textquotedblleft 
-\texttt{g\_pme\_error}\textquotedblright ~\cite{wang2010optimizing}. The
-optimized real space and reciprocal space force computing errors were
-equally distributed as $1.4\times 10^{-4}$~kJ/(mol nm). Since the magnitude
-of the forces are of order $10^{2}$~kJ/(mol nm), this force computing
-precision almost reaches the limit of the single-precision representation of
-the floating point numbers.
-% [ {\color{blue} COMMENT: Did you use the
+The short-range part of SPME method was cut-offed at $1.9$~nm, and was
+smoothed in a shell of $0.05$~nm width by the Gromacs \textquotedblleft 
+\texttt{pme-switch}\textquotedblright\ method. The reciprocal space grid
+spacing was set to $0.06$~nm, with B-Spline interpolation order of $6$.
+These parameters were chosen to be more accurate than the Gromacs default
+choices (grid spacing $0.12$~nm and interpolation order $4$).
+The conducting boundary condition was used with SPME.
+The splitting parameter was optimized by the error estimate, which is
+implemented in Gromacs by tool \textquotedblleft \texttt{g\_pme\_error}%
+\textquotedblright ~\cite{wang2010optimizing}. The optimized real space and
+reciprocal space force computing errors were equally distributed as $%
+1.4\times 10^{-4}$~kJ/(mol nm). Since the magnitude of the forces are of
+order $10^{2}$~kJ/(mol nm), this force computing precision almost reaches
+the limit of the single-precision representation of the floating point
+numbers. % [ {\color{blue} COMMENT: Did you use the
 % conducting boundary conditions? (maybe it is default in gromacs.) Please
@@
 
-In the simulations of the RF method, the interactions were cut-off in the
-group manner, so the radius for neighbor list building is set identical to
-the cut-off radius. No cut-off smoothing of the electrostatic interaction
-was applied in the cases of RF simulations. We used $1.2$~nm cut-off radius and the
-experimental dielectric constant $\varepsilon _{\text{rf}}=80$.
+In the simulations using RF method, the electrostatic interactions were cut-off in the
+group manner (Gromacs default), so the radius for neighbor list updating is set identical to
+the cut-off radius. [{\color{blue} COMMENT: Is "rcoulomb"="rlist" default
+  for RF? If so, please describe it.} \recheck{Describing "rcoulomb"="rlist" by human languange} ]
+\recheck{We used $1.2$~nm for both of them}, and the experimental dielectric constant $%
+\varepsilon _{\text{rf}}=80$.
 
-The van der Waals interaction was always cut-offed at 1.2~nm, and it was
+The van der Waals interaction was always cut-offed at $1.2$~nm, and it was
 modified in a shell of $0.05$~nm width near the cut-off sphere by the
@@
 pressure ($-0.4\pm 1.5$~Bar) is reproducing the target pressure of 1.0~Bar,
-which means the system is in desired thermodynamic state. [ {\color{blue}
-COMMENT: If there are any specific conditions only for the pressure
-calculation, please state around here or elsewhere.] [\recheck{No.}]}
+which means the system is in desired thermodynamic state.
 
@@
 molar heat capacity and the isothermal compressibility show considerable
-errors. The dependence of the ZM results on the order\ $l$\ is {\color{red}
-little}. Although the splitting parameter, $\alpha $, also does not have
-significant influence on almost all these thermodynamic quantities for $l=1$%
-, only the isothermal compressibility admits a weak dependence. Overall, the ZM\
-agrees with the SPME results without any bias and out-performs the RF.
+errors. The dependence of the ZM results on the order\ $l$\ is little. Although the splitting parameter, $\alpha $,
+also does not have significant influence on almost all these thermodynamic
+quantities for $l=1$, only the isothermal compressibility admits a weak
+dependence. Overall, the ZM\ agrees with the SPME results without any bias
+and out-performs the RF.
 
-{\color{red} It should be noticed that in the calculation of the chemical
+It should be noticed that in the calculation of the chemical
 potential, the energy correction plays an important role. In the case of $%
@@
 ^{-1}$, and $-1.0$~kJ/mol for $l=1$, $\alpha =2.0\,\text{nm}^{-1}$,
-respectively. [\color{blue}COMMENT: We will clarify what is the "energy
+respectively. [{\color{blue}COMMENT: We will clarify what is the "energy
 correction" after making SecII, and describe the relation to IPSp after
-making Appendix B.] }
+making Appendix B.}]
 
@@
 estimates (which are averages along MD trajectories) that is calculated by
-the block average method~\protect\cite{janke2002statistical}.} }
+the block average method~\protect\cite{janke2002statistical}.} [ {\ 
+\color{blue}It maybe good to repeat such explanation in Sec.IIIA.}].[{\ 
+\color{blue} another COMMENT: In these figures, can we see the statistical
+uncertainty of the pressure obtained by the SPME? Viz., I found no error
+bars for SPME.} \recheck{NO SPME result is given in this figure!}]}
 \label{fig:pres-comp}
@@
 
-It should be noted that even with the system $L_{0}$ that
-contains 13824 water molecules, the fluctuation
-(measured by standard deviation) of the pressure is roughly 100~Bar, which
-means that it is very difficult to achieve very accurate estimate for this
-quantity. In practice a pressure error of 20~Bar is still acceptable.
+It should be noted that even with the system $L_{0}$ that contains 13824
+water molecules, the fluctuation (measured by standard deviation) of the
+pressure is roughly 100~Bar, which means that it is very difficult to
+achieve very accurate estimate for this quantity.
+\recheck{In practice a pressure
+error of 20~Bar will only cause a
+density deviation (calculated by the NPT simulations) of roughly 0.1\%.
+Taking different orders ZM method at cut-off 1.2~nm for example,
+the density deviations are 0.051\%, 0.061\%, 0.097\% and 0.146\% for $l=1,2,3$ and 4, respectively.
+For $l\leq 3$ the pressure error is less than 20~Bar, while for $l=4$ the pressure error is less than 30~Bar (see Fig.~\ref{fig:pres-comp}).
+}
+
+[{\color{blue} COMMENT1: Can we have a
+trajectory figure of the pressure? It will show that the fluctuation is
+large and the 10 Bar error for ZM looks small. If there is a suitable one,
+it may be good to put it in SI.} \recheck{Could you explain why? The SD should be enough for our purpose.}] [ {\color{blue} COMMENT2: Can we have some
+data on the (mass) density? Some potential users of ZM\ may worry about the
+deviation of the density from the reality due to the pressure error. I
+remember that the density error for ZM was small. It is helpful to show that
+the deviation of the density is sufficiently small. These two comments
+indicates that one wants to feel how good or bad about the 10 Bar error.} \recheck{Done}]
 
@@
 working parameters of SPME are given in Sec.~\protect\ref{sec:protocols} The
-system used for simulation is $S_{1}$.[ {\color{blue} This is for $S_{1}$
-and not shown in your report. right? } \recheck{Right, it was not shown}]}
+system used for simulation is $S_{1}$.}
 \label{fig:eps-conv}
@@
 In contrast, the RF method has poor accuracy in the dielectric constant. It
-is well known that the dielectric feature shows system-size dependence~\cite{vanderSpoel2006origin},
-therefore we further investigated this dependence
+is well known that the dielectric feature shows system-size dependence~\cite%
+{vanderSpoel2006origin}, therefore we further investigated this dependence
 and also the effect of the cutoff length, as shown in Table~I of SI. ZM
-shows good results without any system-size dependency and indicate $r_{\text{c}}\sim 1.2\,$nm\ being suffice for
-the accuracy. Since a slow convergence is also known for the dielectric
-constant, we have monitored the behavior as shown in Fig.~\ref{fig:eps-conv},
-and confirm the sufficient convergence w.r.t.~the length of the
-trajectories.
+shows good results without any system-size dependency and indicate $r_{\text{%
+c}}\sim 1.2\,$nm\ being suffice for the accuracy. Since a slow convergence
+is also known for the dielectric constant, we have monitored the behavior as
+shown in Fig.~\ref{fig:eps-conv}, and confirm the sufficient convergence
+w.r.t.~the length of the trajectories.
 
@@
 radius (1.2~nm), while this oscillation is not obvious for $l\geq 2$. 
-\recheck{
-  The Kirkwood-G factor computed by ZM in system $S_1$ is as good as that computed in $M_1$,
-  and is presented in SI.}
+The Kirkwood-G factor computed by ZM in system $S_{1}$ is as
+good as that computed in $M_{1}$, and is presented in SI.
 
@@
 factor at order $l=1$. The cut-off radius is 1.2~nm. The statistical
-uncertainty is presented at 95~\% confidence level by the error bars. [ {\ 
-\color{blue} This is also not shown in your report. right? } \recheck{Right, it was not shown.}]}
+uncertainty is presented at 95~\% confidence level by the error bars. }
 \label{fig:gkr-damp-l1}
@@
 . Without surprising, the Kirkwood-G factor converges to the SPME result
-when using increasingly large cut-off radius. In Fig.~\ref%
-{fig:gkr-damp-l1}, it shows that in the case of $l=1$, the largest splitting
-parameter ($\alpha =2.0\ \text{nm}^{-1}$) is worse in calculating the
-Kirkwood-G factor than smaller splitting parameters.
-Splitting parameter dependency was not so clear for $l=2$ and 3 (shown in
-SI). Note that in many cases the discrepancies from the SPME were relatively
-prominent in the middle range of the distance and they tend small for larger
-distance.
+when using increasingly large cut-off radius. In Fig.~\ref{fig:gkr-damp-l1},
+it shows that in the case of $l=1$, the largest splitting parameter ($\alpha
+=2.0\ \text{nm}^{-1}$) is worse in calculating the Kirkwood-G factor than
+smaller splitting parameters. Splitting parameter dependency was not so
+clear for $l=2$ and 3 (shown in SI). Note that in many cases the
+discrepancies from the SPME were relatively prominent in the middle range of
+the distance and they tend small for larger distance.
 
@@
 improved by the damping effect as shown in Fig.~\ref{fig:conv-vis-damp}. 
+Similar to the behaviors seen in Fig.~\ref{fig:conv-vis}, the
+convergence is quick for a large $\alpha $.
 
@@
 We plot in Fig.~\ref{fig:rdf} the center-of-mass radial distribution
-functions (RDFs) of TIP3P water calculated by the SPME, ZM ($l=1,2,3$ and $4$%
-) with $\alpha =0$\ and RF methods. It is observed from the figure that the
+functions (RDFs) of TIP3P water calculated by the SPME, ZM ($l=1,2,3$ and $4$)
+with $\alpha =0$\ and RF methods. It is observed from the figure that the
 ZM RDFs are consist very well with the SPME RDF, except oscillations around
 the cut-off radius. This oscillations are not so large, as the maximum
-magnitude of the discrepancies from the SPME is about \recheck{ $1.9\%$ for $l=1$ and 0.3\% for $l=2$,}
-% {[} {\color{blue}
+magnitude of the discrepancies from the SPME is about $1.9\%$
+for $l=1$ and ${0.3\%}$ for $l=2$, % {[} {\color{blue}
 % "$2\%"$ is just my guess. How about stating here the maximum error for
 % individual $l$}]
-but should be artificial. However, higher order ZM method
-present lower amplitude oscillation, and when $l\geq 3$, the improvement is
-dramatic and the oscillation is almost negligible.
+but should be artificial. However, higher order
+ZM method present lower amplitude oscillation, and when $l\geq 3$, the
+improvement is dramatic and the oscillation is almost negligible.
 
@@
 clear. Anyway, please describe.... This is the only matter ZM is inferior to
-RF. So, it may be interesting if the reason is clear. } \recheck{I agree, if the
-reason is not clear for us, we should not touch this topic.}]
+RF. So, it may be interesting if the reason is clear. } {\color{red} I
+agree, if the reason is not clear for us, we should not touch this topic.}][ 
+{\color{blue} COMMENT: Thank you very much for the O-O RDF. If you have time
+to reconsider this issue, it may be useful to calculate the RDF with H-H
+length (MD trajectory also remains). Deviations should be larger for H-H
+than O-O, but this is my guess: (1) eventually COG-COG is near O-O, sorry I
+did not notice.; (2) RDF deviations appear in 0.6 nm width around the cutoff
+and the H-H length is just the twice of this 0.6 nm). Rather, the true
+reason may be other, e.g., group cuotff MD scheme may intrinsically give the
+accracy at least for RDF. }]
 
@@
 RDF. Anti-damping effect was also observed in the pressure when $\alpha >1$
-and  Kirkwood-G factor (only $l=1$). A larger order is
-preferable slightly for dynamical quantities including diffusion constant
-and viscosity, and significantly for the RDF. Whereas a smaller order is
-preferable for the pressure, though $l=1,2$\ are similar.
+and Kirkwood-G factor (only $l=1$). A larger order is preferable slightly
+for dynamical quantities including diffusion constant and viscosity, and
+significantly for the RDF. Whereas a smaller order is preferable for the
+pressure, though $l=1,2$\ are similar.
 
-{\color{red} At cut-off radius of 1.2~nm, the recommended choices of
+At cut-off radius of 1.2~nm, the recommended choices of
 parameters for TIP3P system are thus $\alpha \leq 1$~$\text{nm}^{-1}$ and $%
@@
 negligible). Both of orders 2 and 3 are not sensitive to the splitting
-parameter up to 1.0~$\text{nm}^{-1}$.} {\color{blue} Although further
-increasing the splitting parameter will push the accuracy of RDF in case $l=2
-$ to as high as $l=3$, the pressure accuracy decreases (anti-damping
+parameter up to 1.0~$\text{nm}^{-1}$. Although further
+increasing the splitting parameter will push the accuracy of RDF in case $%
+l=2 $ to as high as $l=3$, the pressure accuracy decreases (anti-damping
 effect), so that $\alpha >1$\ for $l=2$ or $l=3$ is not recommended. It
@@
 (largest) in calculating the Kirkwood-G factor for a larger system ($L_{1}$
-containing 13,824 molecules). [\color{blue}COMMENT:Did you calculate the G
-factor for the smallest $S_{1}$? \ If so, how was the results? \recheck{see the added
-  in Sec. IV B and SI}] If we seek
-more accuracy for the G factor, we should use a larger cut-off radius at the
-expense of the computational time. } 
+containing 13,824 molecules).  If we seek more
+accuracy for the G factor, we should use a larger cut-off radius at the
+expense of the computational time. 
 % Further increasing the splitting paraemter
@@
 
-\bigskip
+[ {\color{blue} COMMENT0: Although I know this paper's aim is to judge the
+accuracy of the ZM, I also know many people may also be interested in some
+different aspects. So please see the following.}]
+
+[ {\color{blue} COMMENT1: The first one is the accuracy comparison between
+the ZM\ and a "default PME" that uses default protocol and parameters, e.g.,
+group-based cutoff scheme (OK?) and a short cutoff length(about 1 nm?) for
+the real part and a lower order spline and default grid spacing for the
+reciprocal part. Many peoples are not the specialist of the electrostatic
+calculation, and they just uses the default PME. Thus it would be OK\ for
+them if the difference between the ZM\ and a "default PME" is small. Is it
+possible to calculate e.g., pressure or KG factor for {$L_{1}$} (n{ot all
+the quantities}), using the {"default PME"?}}]
+
+[ {\color{blue} COMMENT2: The second one is the comparison of the
+computational timing between the ZM\ and a "default PME."\ Many people,
+including e.g. reviewers, should be interested in it. How about this
+comparison using a short time simulation?\ One expects ZM\ is faster than
+SPME. But is SPME with rc=1.0 nm along with the buffer length 0.2nm (are
+they default length?) faster than ZM\ with rc=1.2 nm along with the buffer
+length 0.3nm?? }]
 
@@
 quantities. We assume that there are $N$ molecules in the water system. The
-position and configuration of each molecule are fully described by $\{%
-\mathbf{\mathit{r}}_{3i-2},\mathbf{\mathit{r}}_{3i-1},\mathbf{\mathit{r}}%
+position and configuration of each molecule are fully described by $\{\vect r_{3i-2},\mathbf{\mathit{r}}_{3i-1},\mathbf{\mathit{r}}
 _{3i}\},\,i\in 1,\cdots ,N$, and the corresponding velocities are denoted by 
 $\{\mathbf{\mathit{v}}_{3i-2},\mathbf{\mathit{v}}_{3i-1},\mathbf{\mathit{v}}%
-_{3i}\},\,i\in 1,\cdots ,N$. The mass of each atom is denoted by $m_{i}$.
+_{3i}\},\,i\in 1,\cdots ,N$. The mass of each atom is denoted by $m_{i}$.[ {%
+\color{blue} minor: I like bold font a little bit for $\mathbf{\mathit{r}}${%
+\ and }$\mathbf{\mathit{v}}${\ as in the first version, which is also seen
+in }$\boldsymbol{\mu }_{i}${. (In particular, }$\mathbf{\mathit{r}}${\ seems
+the distance, not vector. $\mathbf{\mathit{r}}$ appears below also. But if
+you like this font, please use it also for $\boldsymbol{\mu }_{i}$)}} \recheck{I prefer the original one, I did not change it.
+I guess your program did it automatically.
+I suggest you compile this file with standard latex that dose not do any automatic change to the source file!.
+Now I change the one of them back, please see if it works on your machine}]
 
@@
 RDF in the water system. The RDFs presented in the main text were computed
-in system $L_1$.
+from NVT simulations of system $L_1$.
 
@@
 where $V$ is the volume of the system. The presented pressures were computed
-in system $L_{0}$.
+from NVT simulations of $L_{0}$.
 
@@
 calculated by the Bennet's acceptance ratio method (BAR)~\cite%
-{bennett1976efficient}. The simulations were performed with system $L_0$.
+{bennett1976efficient}. The NVT simulations were performed with system $L_0$.
 
@@
 \end{align}
-is the total dipole moment of the system. Since it is a fluctuation, the
-simulated system was $S_1$. 
+is the total dipole moment of the system. Since it is a fluctuation, and is calculated by NVT simulations of $S_1$. 
 % The results are listed in Tab.~\ref{tab:tmp2}. The dielectric constant calculated in system $\systemsb$ is reported in Table.~\ref{tab:thermo}.
@@
 where $r_{ij}$ denotes the oxygen-oxygen distance between two water
-molecules. The system for computing this quantity is $L_1$.
+molecules. The system for computing this quantity is $L_1$ in NVT ensemble.
 
@@
 _i(t) - \mathbf{\mathit{r}}_i(0)\vert^2\rangle$ is calculated, then the
-value is linearly fitted. The system for simulation was $S_1$.
+value is linearly fitted. It is calculated by NVT simulations of system $S_1$.
 
@@
 The values listed in Table~\ref{tab:thermo} are computed with $I_{\eta }(10\,%
-\text{ps})$. The system for simulation was $S_{1}$.
+\text{ps})$. The quantity is calculated by NVT simulations of system $S_{1}$.
 
@@
 % \bibliographystyle{plain}
+\bibliographystyle{plain}
 \bibliography{ref}

### 2014-11-23 writedown/zm/paper.water/main.tex
improve

@@
 
-The neighbor lists were updated every 5 time-steps. {\color{red} The Gromacs
-by default uses the group cut-off scheme, while the ZM method suggests an
-atom cut-off scheme~\cite{fukuda2011molecular,fukuda2013zero}.} [{%
+[{%
 \color{blue} COMMENT: I am confusing. Is "rcoulomb"="rlist" default in
@@
 correct. Or, here, you want to say the "neighbor list making" is done by
-group cut-off? (I reread your "cutoff.pdf")} \recheck{the default is rcoulomb = rlist. both
-the neighbor list making and the force computing are in group manner.
-I prefer not describing this issue in the paper in detail, because the reader
-may not be familiar with the terminology (rlist, rcoulomb, and so on) and
-the mechanism behind. I think describing how to use ZM correctly in gromacs is enough.
-}] The difference between these
+group cut-off? (I reread your "cutoff.pdf")} \recheck{
+In the main text I only mention the ``group cut-off'' and ``atom cut-off'' and
+put how to implement them in the Appendix.  So those who are not familiar with Gromacs would not be confused by the Gormacs terminology (e.g. rlist, rcoulomb, ...).
+see the revise below:
+}]
+
+The neighbor lists were updated every 5 time-steps. The Gromacs
+by default uses the group cut-off scheme, while the ZM method suggests an
+atom cut-off scheme~\cite{fukuda2011molecular,fukuda2013zero}. The difference between these
 cut-off schemes is discussed in detail in e.g.~Ref.~\cite%
@@
 based cut-off scheme in the simulations using the SPME (short-range part)
-and ZM electrostatic methods. In order to mimic the atom cut-off scheme in
-the Gromacs group cut-off implementation, the radius for neighbor list
-updating was set ${0.3}$~nm larger than the cut-off radius (the maximum of
-Coulomb cut-off and the van der Waals cut-off).
+and ZM electrostatic methods, \recheck{while group cut-off scheme for RF.
+  We treated RF differently because the group cut-off scheme is the default scheme in Gromacs.}
+\recheck{The implementation details of the atom cut-off scheme in Gromacs are proivded in Appendix.~\ref{app:cut-off}.}
+
+% In order to mimic the atom cut-off scheme in
+% the Gromacs group cut-off implementation, the radius for neighbor list
+% updating was set ${0.3}$~nm larger than the cut-off radius (the maximum of
+% Coulomb cut-off and the van der Waals cut-off).
 
@@
 % state the thing.}]
+\recheck{The ZM method was implemented in Gromacs with the tabulated electrostatic
+interaction, and the interaction tables were generated by a home-made code.
+The experimental dielectric consistency  $\varepsilon _{\text{rf}}=80$
+was adopted for the RF method.}
 
-The ZM method was implemented in Gromacs with the tabulated electrostatic
-interaction. A home-made code was used to generate the interaction tables. {%
-\color{blue} }$\bigstar $
-
-In the simulations using RF method, the electrostatic interactions were cut-off in the
-group manner (Gromacs default), so the radius for neighbor list updating is set identical to
-the cut-off radius. [{\color{blue} COMMENT: Is "rcoulomb"="rlist" default
-  for RF? If so, please describe it.} \recheck{Describing "rcoulomb"="rlist" by human languange} ]
-\recheck{We used $1.2$~nm for both of them}, and the experimental dielectric constant $%
-\varepsilon _{\text{rf}}=80$.
+% In the simulations using RF method, the electrostatic interactions were cut-off in the
+% group manner (Gromacs default), so the radius for neighbor list updating is set identical to
+% the cut-off radius. [{\color{blue} COMMENT: Is "rcoulomb"="rlist" default
+%   for RF? If so, please describe it.} \recheck{Describing "rcoulomb"="rlist" by human languange} ]
+% \recheck{We used $1.2$~nm for both of them}, and the experimental dielectric constant $%
+% \varepsilon _{\text{rf}}=80$.
 
@@
 uncertainty of the pressure obtained by the SPME? Viz., I found no error
-bars for SPME.} \recheck{NO SPME result is given in this figure!}]}
+bars for SPME.} \recheck{NO SPME result is given in this figure, 1 Bar is the target pressure.}]}
 \label{fig:pres-comp}
@@
 
+\section{Implementation of atom cut-off scheme in Gromacs}
+\label{app:cut-off}
+
+The Gromacs code 4.6 does not directly 
+support the atomistic cut-off scheme for tabulated electrostatic interaction that is
+needed for ZM method. The atom cut-off scheme can be implemented
+by using the default ``\texttt{Group}'' neighbor searching method, while setting
+the radius of neighbor list ``\texttt{rlist}'' 0.3~nm larger than the cut-off radius,
+which is the maximum of the electrostatic cut-off ``\texttt{rcoulomb}'' and the van der Waals cut-off ``\texttt{rvdw}''.
+Due to the buffering region that is of thickness 0.3~nm, the atom cut-off scheme in Gromacs is in general more expensive than the group cut-off scheme.
+
 \section{The computation of benchmark quantities}

### 2014-12-05 writedown/zm/paper.water/main.tex
partially finish revising

@@
 %TCIDATA{BibliographyScheme=BibTeX}
-%TCIDATA{LastRevised=Thursday, November 13, 2014 17:19:51}
+%TCIDATA{LastRevised=Monday, December 01, 2014 18:07:38}
 %TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
@@
 \newcommand{\systemlb}{L_1}
-% \input{tcilatex}
+
 \begin{document}
@@
 \author{Han Wang}
-\email{han.wang@fu-berlin.de}
+\email{wang_han@iapcm.ac.cn}
 \affiliation{CAEP Software Center for High Performance Numerical Simulation, Huayuan Road
@@
 
-{\color{red} If we want to discuss the issue of cut-off method, a short
-introduction of the group cut-off v.s.~the atom cut-off method. (will
-discuss the implementation in gromacs later) }[ {\color{blue} COMMENT: what
-do you mean? {\color{red} I mean the explanation of group and atomistic
-cut-off method. the traditional gromacs uses group cut-off as default. We
-need instead the atomistic cut-off}}] [ {\color{blue} COMMENT: OK, the
-matter for {traditional gromacs} will be discussed in Sec. IIIB, and the
-relevant matter of ZM will be discussed around $\bigstar ${\ in Sec. IIIB.
-If we feel the resulted descriptions are too detailed, they will go to SI.}] 
-} [{\color{red} please see the red part in Sec. III B. The order of the
-paragraphs are also rearranged.}][ {\color{blue} I added comments.}]
+% {\color{red} If we want to discuss the issue of cut-off method, a short
+% introduction of the group cut-off v.s.~the atom cut-off method. (will
+% discuss the implementation in gromacs later) }[ {\color{blue} COMMENT: what
+% do you mean? {\color{red} I mean the explanation of group and atomistic
+% cut-off method. the traditional gromacs uses group cut-off as default. We
+% need instead the atomistic cut-off}}] [ {\color{blue} COMMENT: OK, the
+% matter for {traditional gromacs} will be discussed in Sec. IIIB, and the
+% relevant matter of ZM will be discussed around $\bigstar ${\ in Sec. IIIB.
+% If we feel the resulted descriptions are too detailed, they will go to SI.}] 
+% } [{\color{red} please see the red part in Sec. III B. The order of the
+% paragraphs are also rearranged.}][ {\color{blue} I added comments.}]
 
@@
 
-[{%
-\color{blue} COMMENT: I am confusing. Is "rcoulomb"="rlist" default in
-gromacs? If so, "Gromacs by default uses the group cut-off scheme" is
-correct. Or, here, you want to say the "neighbor list making" is done by
-group cut-off? (I reread your "cutoff.pdf")} \recheck{
-In the main text I only mention the ``group cut-off'' and ``atom cut-off'' and
-put how to implement them in the Appendix.  So those who are not familiar with Gromacs would not be confused by the Gormacs terminology (e.g. rlist, rcoulomb, ...).
-see the revise below:
-}]
+% [{\color{blue} COMMENT: I am confusing. Is "rcoulomb"="rlist" default in
+% gromacs? If so, "Gromacs by default uses the group cut-off scheme" is
+% correct. Or, here, you want to say the "neighbor list making" is done by
+% group cut-off? (I reread your "cutoff.pdf")} {\color{red} In the main text I
+% only mention the \textquotedblleft group cut-off\textquotedblright\ and
+% \textquotedblleft atom cut-off\textquotedblright\ and put how to implement
+% them in the Appendix. So those who are not familiar with Gromacs would not
+% be confused by the Gormacs terminology (e.g. rlist, rcoulomb, ...). see the
+% revise below: }][ {\color{blue} I see and also modified. check it.]}
 
-The neighbor lists were updated every 5 time-steps. The Gromacs
-by default uses the group cut-off scheme, while the ZM method suggests an
-atom cut-off scheme~\cite{fukuda2011molecular,fukuda2013zero}. The difference between these
-cut-off schemes is discussed in detail in e.g.~Ref.~\cite%
+The neighbor lists were updated every 5 time-steps. The Gromacs by default
+uses the group cut-off scheme, while the ZM method recommends
+an atom cut-off scheme~\cite{fukuda2011molecular,fukuda2013zero}. The difference between these cut-off
+schemes is discussed in detail in e.g.~Ref.~\cite%
 {hunenberger1998alternative,baumketner2009removing}. We adopted the atom
 based cut-off scheme in the simulations using the SPME (short-range part)
-and ZM electrostatic methods, \recheck{while group cut-off scheme for RF.
-  We treated RF differently because the group cut-off scheme is the default scheme in Gromacs.}
-\recheck{The implementation details of the atom cut-off scheme in Gromacs are proivded in Appendix.~\ref{app:cut-off}.}
+and ZM electrostatic methods. The implementation details of the
+atom cut-off scheme in Gromacs are provided in Appendix.~\ref{app:cut-off}.
+The ZM method was implemented in Gromacs with the tabulated electrostatic
+interaction, and the interaction tables were generated by a home-made code.
 
+We treated the RF with the group cut-off scheme because the
+group cut-off scheme is the default scheme in Gromacs. The experimental
+dielectric consistency $\varepsilon _{\text{rf}}=80$ was adopted for the RF
+method.
 % In order to mimic the atom cut-off scheme in
@@
 % Coulomb cut-off and the van der Waals cut-off). 
-
 % The \textquotedblleft 
@@
 These parameters were chosen to be more accurate than the Gromacs default
-choices (grid spacing $0.12$~nm and interpolation order $4$).
-The conducting boundary condition was used with SPME.
-The splitting parameter was optimized by the error estimate, which is
-implemented in Gromacs by tool \textquotedblleft \texttt{g\_pme\_error}%
-\textquotedblright ~\cite{wang2010optimizing}. The optimized real space and
-reciprocal space force computing errors were equally distributed as $%
-1.4\times 10^{-4}$~kJ/(mol nm). Since the magnitude of the forces are of
-order $10^{2}$~kJ/(mol nm), this force computing precision almost reaches
-the limit of the single-precision representation of the floating point
-numbers. % [ {\color{blue} COMMENT: Did you use the
+choices (grid spacing $0.12$~nm and interpolation order $4$). The conducting
+boundary condition was used with SPME. The splitting parameter was optimized
+by the error estimate, which is implemented in Gromacs by tool
+\textquotedblleft \texttt{g\_pme\_error}\textquotedblright ~\cite%
+{wang2010optimizing}. The optimized real space and reciprocal space force
+computing errors were equally distributed as $1.4\times 10^{-4}$~kJ/(mol
+nm). Since the magnitude of the forces are of order $10^{2}$~kJ/(mol nm),
+this force computing precision almost reaches the limit of the
+single-precision representation of the floating point numbers. 
+% [ {\color{blue} COMMENT: Did you use the
 % conducting boundary conditions? (maybe it is default in gromacs.) Please
 % state the thing.}]
-\recheck{The ZM method was implemented in Gromacs with the tabulated electrostatic
-interaction, and the interaction tables were generated by a home-made code.
-The experimental dielectric consistency  $\varepsilon _{\text{rf}}=80$
-was adopted for the RF method.}
-
 % In the simulations using RF method, the electrostatic interactions were cut-off in the
@@
 molar heat capacity and the isothermal compressibility show considerable
-errors. The dependence of the ZM results on the order\ $l$\ is little. Although the splitting parameter, $\alpha $,
-also does not have significant influence on almost all these thermodynamic
-quantities for $l=1$, only the isothermal compressibility admits a weak
-dependence. Overall, the ZM\ agrees with the SPME results without any bias
-and out-performs the RF.
+errors. The dependence of the ZM results on the order\ $l$\ is little.
+Although the splitting parameter, $\alpha $, also does not have significant
+influence on almost all these thermodynamic quantities for $l=1$, only the
+isothermal compressibility admits a weak dependence. Overall, the ZM\ agrees
+with the SPME results without any bias and out-performs the RF.
 
-It should be noticed that in the calculation of the chemical
-potential, the energy correction plays an important role. In the case of $%
-l=1 $, $\alpha =0.0\,\text{nm}^{-1}$, it contributes $-0.1$~kJ/mol to the
-final result. By increasing $l$ or $\alpha $, this contribution becomes more
-significant, and reaches $-0.6$~kJ/mol for $l=4$, $\alpha =0.0\,\text{nm}%
-^{-1}$, and $-1.0$~kJ/mol for $l=1$, $\alpha =2.0\,\text{nm}^{-1}$,
-respectively. [{\color{blue}COMMENT: We will clarify what is the "energy
-correction" after making SecII, and describe the relation to IPSp after
-making Appendix B.}]
+It should be noticed that in the calculation of the chemical potential, the
+energy correction plays an important role. In the case of $l=1$, $\alpha
+=0.0\,\text{nm}^{-1}$, it contributes $-0.1$~kJ/mol to the final result. By
+increasing $l$ or $\alpha $, this contribution becomes more significant, and
+reaches $-0.6$~kJ/mol for $l=4$, $\alpha =0.0\,\text{nm}^{-1}$, and $-1.0$%
+~kJ/mol for $l=1$, $\alpha =2.0\,\text{nm}^{-1}$, respectively. [{%
+\color{blue}COMMENT: We will clarify what is the "energy correction" after
+making SecII, and describe the relation to IPSp after making Appendix B.}]
 
@@
 estimates (which are averages along MD trajectories) that is calculated by
-the block average method~\protect\cite{janke2002statistical}.} [ {\ 
-\color{blue}It maybe good to repeat such explanation in Sec.IIIA.}].[{\ 
-\color{blue} another COMMENT: In these figures, can we see the statistical
-uncertainty of the pressure obtained by the SPME? Viz., I found no error
-bars for SPME.} \recheck{NO SPME result is given in this figure, 1 Bar is the target pressure.}]}
+the block average method~\protect\cite{janke2002statistical}.}
+% [ {\ 
+% \color{blue}It maybe good to repeat such explanation in Sec.IIIA.}].[{\ 
+% \color{blue} another COMMENT: In these figures, can we see the statistical
+% uncertainty of the pressure obtained by the SPME? Viz., I found no error
+% bars for SPME.} {\color{red} NO SPME result is given in this figure, 1 Bar
+% is the target pressure.}][{\color{blue} Can I konw the the statistical
+% uncertainty of the pressure obtained by the SPME?}]
+}
 \label{fig:pres-comp}
@@
 pressure is roughly 100~Bar, which means that it is very difficult to
-achieve very accurate estimate for this quantity.
-\recheck{In practice a pressure
-error of 20~Bar will only cause a
-density deviation (calculated by the NPT simulations) of roughly 0.1\%.
-Taking different orders ZM method at cut-off 1.2~nm for example,
-the density deviations are 0.051\%, 0.061\%, 0.097\% and 0.146\% for $l=1,2,3$ and 4, respectively.
-For $l\leq 3$ the pressure error is less than 20~Bar, while for $l=4$ the pressure error is less than 30~Bar (see Fig.~\ref{fig:pres-comp}).
-}
+achieve very accurate estimate for this quantity.  In practice a
+pressure error of 20~Bar will only cause a density deviation (calculated by
+the NPT simulations) of roughly 0.1\%. Taking different orders ZM method at
+cut-off 1.2~nm for example, the density deviations are 0.051\%, 0.061\%,
+0.097\% and 0.146\% for $l=1,2,3$ and 4, respectively. For $l\leq 3$ the
+pressure error is less than 20~Bar, while for $l=4$ the pressure error is
+less than 30~Bar (see Fig.~\ref{fig:pres-comp}).
 
-[{\color{blue} COMMENT1: Can we have a
-trajectory figure of the pressure? It will show that the fluctuation is
-large and the 10 Bar error for ZM looks small. If there is a suitable one,
-it may be good to put it in SI.} \recheck{Could you explain why? The SD should be enough for our purpose.}] [ {\color{blue} COMMENT2: Can we have some
-data on the (mass) density? Some potential users of ZM\ may worry about the
-deviation of the density from the reality due to the pressure error. I
-remember that the density error for ZM was small. It is helpful to show that
-the deviation of the density is sufficiently small. These two comments
-indicates that one wants to feel how good or bad about the 10 Bar error.} \recheck{Done}]
+% [{\color{blue} {COMMENT1:} Can we have a trajectory figure of the pressure?
+% It will show that the fluctuation is large and the 10 Bar error for ZM looks
+% small. If there is a suitable one, it may be good to put it in SI.} {%
+% \color{red} Could you explain why? The SD should be enough for our purpose.}%
+% ] [ {\color{blue} COMMENT2: Can we have some data on the (mass) density?
+% Some potential users of ZM\ may worry about the deviation of the density
+% from the reality due to the pressure error. I remember that the density
+% error for ZM was small. It is helpful to show that the deviation of the
+% density is sufficiently small. These two comments indicates that one wants
+% to feel how good or bad about the 10 Bar error.} {\color{red} Done}][ {%
+% \color{blue} Thank you very much for your consideration of the density. {%
+% COMMENT1: please see my question in the last page. COMMENT2: The deviation
+% of the pressure between the ZM and PME should be due to this density
+% deviation between the ZM and PME (0.1\%). Namely {0.1\% density deviation
+% should cause 10 atm deviation.}\ How about this confirmation? ---The
+% pressure by ZM\ in figs1\&2 was calculated with the NTV MD where the cell
+% size was determined by the \textit{PME} NTP. So, if we will do NTV MD with
+% the cell size determined by the \textit{ZM} NTP (which was used to calculate
+% the current density), and if we calculate the pressure by ZM with this new
+% NTV, then we should have 1 atm pressure for may cutoff lengths. If this is
+% true, then we can show that the 10 atm deviation from the PME is not the
+% serious problem but a tiny density deviation issue.--- How about this idea? }%
+% }]
 
@@
 systems, ZM $l=1$ presents an artificial oscillation around the cut-off
-radius (1.2~nm), while this oscillation is not obvious for $l\geq 2$. 
-The Kirkwood-G factor computed by ZM in system $S_{1}$ is as
-good as that computed in $M_{1}$, and is presented in SI.
+radius (1.2~nm), while this oscillation is not obvious for $l\geq 2$. The
+Kirkwood-G factor computed by ZM in system $S_{1}$ is as good as that
+computed in $M_{1}$, and is presented in SI.
 
@@
 improved by the damping effect as shown in Fig.~\ref{fig:conv-vis-damp}.
-Similar to the behaviors seen in Fig.~\ref{fig:conv-vis}, the
-convergence is quick for a large $\alpha $.
+Similar to the behaviors seen in Fig.~\ref{fig:conv-vis}, the convergence is
+quick for a large $\alpha $.
 
@@
 We plot in Fig.~\ref{fig:rdf} the center-of-mass radial distribution
-functions (RDFs) of TIP3P water calculated by the SPME, ZM ($l=1,2,3$ and $4$)
-with $\alpha =0$\ and RF methods. It is observed from the figure that the
+functions (RDFs) of TIP3P water calculated by the SPME, ZM ($l=1,2,3$ and $4$%
+) with $\alpha =0$\ and RF methods. It is observed from the figure that the
 ZM RDFs are consist very well with the SPME RDF, except oscillations around
 the cut-off radius. This oscillations are not so large, as the maximum
-magnitude of the discrepancies from the SPME is about $1.9\%$
-for $l=1$ and ${0.3\%}$ for $l=2$, % {[} {\color{blue}
+magnitude of the discrepancies from the SPME is about $1.9\%$ for $l=1$ and $%
+{0.3\%}$ for $l=2$, % {[} {\color{blue}
 % "$2\%"$ is just my guess. How about stating here the maximum error for
 % individual $l$}]
-but should be artificial. However, higher order
-ZM method present lower amplitude oscillation, and when $l\geq 3$, the
-improvement is dramatic and the oscillation is almost negligible.
+but should be artificial. However, higher order ZM method present lower
+amplitude oscillation, and when $l\geq 3$, the improvement is dramatic and
+the oscillation is almost negligible. \recheck{The RF RDF is more accurate than the ZM ones,
+this is mainly because of the group cut-off used in simulating with RF. When changing
+the cut-off scheme to atom scheme, the accuracy is RF is roughly same as ZM $l=1$ (see SI).
+We could not explain the reason, but the numerical evidence suggests if only the RDF is
+of interest, a group cut-off scheme or higher order of ZM is preferable.
+}
 
-{\color{red} Shall we comment here on the fact that group cut-off produces
-smoother RDF? Add figures in Supplementary material {\color{blue} Do you
-mean the reason of the goodness in RF?} {\color{red} Yes, shall we discuss
-it? or it is too complicated and not very relevant to the current paper?}[} {%
-\color{blue} It is preferable to write it if the reason of the goodness is
-clear. Anyway, please describe.... This is the only matter ZM is inferior to
-RF. So, it may be interesting if the reason is clear. } {\color{red} I
-agree, if the reason is not clear for us, we should not touch this topic.}][ 
-{\color{blue} COMMENT: Thank you very much for the O-O RDF. If you have time
-to reconsider this issue, it may be useful to calculate the RDF with H-H
-length (MD trajectory also remains). Deviations should be larger for H-H
-than O-O, but this is my guess: (1) eventually COG-COG is near O-O, sorry I
-did not notice.; (2) RDF deviations appear in 0.6 nm width around the cutoff
-and the H-H length is just the twice of this 0.6 nm). Rather, the true
-reason may be other, e.g., group cuotff MD scheme may intrinsically give the
-accracy at least for RDF. }]
+% {\color{red} Shall we comment here on the fact that group cut-off produces
+% smoother RDF? Add figures in Supplementary material {\color{blue} Do you
+% mean the reason of the goodness in RF?} {\color{red} Yes, shall we discuss
+% it? or it is too complicated and not very relevant to the current paper?}[} {%
+% \color{blue} It is preferable to write it if the reason of the goodness is
+% clear. Anyway, please describe.... This is the only matter ZM is inferior to
+% RF. So, it may be interesting if the reason is clear. } {\color{red} I
+% agree, if the reason is not clear for us, we should not touch this topic.}][ 
+% {\color{blue} COMMENT: Thank you very much for the O-O RDF. If you have time
+% to reconsider this issue, it may be useful to calculate the RDF with H-H
+% length (MD trajectory also remains). Deviations should be larger for H-H
+% than O-O, but this is my guess: (1) eventually COG-COG is near O-O, sorry I
+% did not notice.; (2) RDF deviations appear in 0.6 nm width around the cutoff
+% and the H-H length is just the twice of this 0.6 nm). Rather, the true
+% reason may be other, e.g., group cuotff MD scheme may intrinsically give the
+% accracy at least for RDF. }][{\color{blue} COMMENT: Thank you very much for
+% the HH trial. The reason may be other. Since we do not have the reason why
+% RF was so good, one choice is the deletion of the RF data in the RDF. How do
+% you think about it?}]
 
@@
 
-At cut-off radius of 1.2~nm, the recommended choices of
-parameters for TIP3P system are thus $\alpha \leq 1$~$\text{nm}^{-1}$ and $%
-l=2$ or $l=3$. Using these parameters, the ZM method achieves almost perfect
-accuracy in computing the excess chemical potential, constant
-volume/pressure heat capacity, isothermal compressibility, thermal expansion
-coefficient, dielectric constant diffusion constant and viscosity. The order 
-$l=2$ performs better in reproducing the pressure than $l=3$ (10
-v.s.~17~Bar), but worse in calculating the RDF (0.2\% error v.s.~almost
-negligible). Both of orders 2 and 3 are not sensitive to the splitting
-parameter up to 1.0~$\text{nm}^{-1}$. Although further
-increasing the splitting parameter will push the accuracy of RDF in case $%
-l=2 $ to as high as $l=3$, the pressure accuracy decreases (anti-damping
-effect), so that $\alpha >1$\ for $l=2$ or $l=3$ is not recommended. It
-should be noticed that the recommended parameters indicate $5$\% error
-(largest) in calculating the Kirkwood-G factor for a larger system ($L_{1}$
-containing 13,824 molecules).  If we seek more
+At cut-off radius of 1.2~nm, the recommended choices of parameters for TIP3P
+system are thus $\alpha \leq 1$~$\text{nm}^{-1}$ and $l=2$ or $l=3$. Using
+these parameters, the ZM method achieves almost perfect accuracy in
+computing the excess chemical potential, constant volume/pressure heat
+capacity, isothermal compressibility, thermal expansion coefficient,
+dielectric constant diffusion constant and viscosity. The order $l=2$
+performs better in reproducing the pressure than $l=3$ (10 v.s.~17~Bar), but
+worse in calculating the RDF (0.2\% error v.s.~almost negligible). Both of
+orders 2 and 3 are not sensitive to the splitting parameter up to 1.0~$\text{%
+nm}^{-1}$. Although further increasing the splitting parameter will push the
+accuracy of RDF in case $l=2 $ to as high as $l=3$, the pressure accuracy
+decreases (anti-damping effect), so that $\alpha >1$\ for $l=2$ or $l=3$ is
+not recommended. It should be noticed that the recommended parameters
+indicate $5$\% error (largest) in calculating the Kirkwood-G factor for a
+larger system ($L_{1}$ containing 13,824 molecules). If we seek more
 accuracy for the G factor, we should use a larger cut-off radius at the
@@
 \section{Implementation of atom cut-off scheme in Gromacs}
+
 \label{app:cut-off}
 
-The Gromacs code 4.6 does not directly 
-support the atomistic cut-off scheme for tabulated electrostatic interaction that is
-needed for ZM method. The atom cut-off scheme can be implemented
-by using the default ``\texttt{Group}'' neighbor searching method, while setting
-the radius of neighbor list ``\texttt{rlist}'' 0.3~nm larger than the cut-off radius,
-which is the maximum of the electrostatic cut-off ``\texttt{rcoulomb}'' and the van der Waals cut-off ``\texttt{rvdw}''.
-Due to the buffering region that is of thickness 0.3~nm, the atom cut-off scheme in Gromacs is in general more expensive than the group cut-off scheme.
+The Gromacs code 4.6 does not directly support the atomistic cut-off scheme, 
+{\color{blue}which is recommended in the ZM method, in }using tabulated
+electrostatic interaction. The atom cut-off scheme can be implemented by
+using the default \textquotedblleft \texttt{Group}\textquotedblright\
+neighbor searching method, while setting the radius of neighbor list
+\textquotedblleft \texttt{rlist}\textquotedblright\ 0.3~nm larger than the
+cut-off radius, which is the maximum of the electrostatic cut-off
+\textquotedblleft \texttt{rcoulomb}\textquotedblright\ and the van der Waals
+cut-off \textquotedblleft \texttt{rvdw}\textquotedblright . Due to the
+buffering region that is of thickness 0.3~nm, the atom cut-off scheme in
+Gromacs is in general \recheck{twice} expensive \recheck{in computing the electrostatic interaction} as the group cut-off scheme.
+\recheck{It should be pointed out that this implementation is not optimal,
+  when the gromacs build-in atom cut-off scheme supports the tablulated potential, we expect better performance of ZM method.}
+% {%
+% \color{blue}How much? (just my interest)}
 
@@
 quantities. We assume that there are $N$ molecules in the water system. The
-position and configuration of each molecule are fully described by $\{\vect r_{3i-2},\mathbf{\mathit{r}}_{3i-1},\mathbf{\mathit{r}}
+position and configuration of each molecule are fully described by $\{%
+\mathbf{\mathit{r}}_{3i-2},\mathbf{\mathit{r}}_{3i-1},\mathbf{\mathit{r}}%
 _{3i}\},\,i\in 1,\cdots ,N$, and the corresponding velocities are denoted by 
 $\{\mathbf{\mathit{v}}_{3i-2},\mathbf{\mathit{v}}_{3i-1},\mathbf{\mathit{v}}%
-_{3i}\},\,i\in 1,\cdots ,N$. The mass of each atom is denoted by $m_{i}$.[ {%
-\color{blue} minor: I like bold font a little bit for $\mathbf{\mathit{r}}${%
-\ and }$\mathbf{\mathit{v}}${\ as in the first version, which is also seen
-in }$\boldsymbol{\mu }_{i}${. (In particular, }$\mathbf{\mathit{r}}${\ seems
-the distance, not vector. $\mathbf{\mathit{r}}$ appears below also. But if
-you like this font, please use it also for $\boldsymbol{\mu }_{i}$)}} \recheck{I prefer the original one, I did not change it.
-I guess your program did it automatically.
-I suggest you compile this file with standard latex that dose not do any automatic change to the source file!.
-Now I change the one of them back, please see if it works on your machine}]
+_{3i}\},\,i\in 1,\cdots ,N$. The mass of each atom is denoted by $m_{i}$.
+% [ {%
+% \color{blue} minor: I like bold font a little bit for $\mathbf{\mathit{r}}${%
+% \ and }$\mathbf{\mathit{v}}${\ as in the first version, which is also seen
+% in }$\boldsymbol{\mu }_{i}${. (In particular, }$\mathbf{\mathit{r}}${\ seems
+% the distance, not vector. $\mathbf{\mathit{r}}$ appears below also. But if
+% you like this font, please use it also for $\boldsymbol{\mu }_{i}$)}} {%
+% \color{red} I prefer the original one, I did not change it. I guess your
+% program did it automatically. I suggest you compile this file with standard
+% latex that dose not do any automatic change to the source file!. Now I
+% change the one of them back, please see if it works on your machine}][ {%
+% \color{blue} Sorry, maybe this is just the problem of my program, now I can
+% see }$\mathbf{\mathit{r}}_{3i-2}${\ to be bold in your original pdf.}]
 
@@
 \end{align}
-is the total dipole moment of the system. Since it is a fluctuation, and is calculated by NVT simulations of $S_1$. 
+is the total dipole moment of the system. Since it is a fluctuation, and is
+calculated by NVT simulations of $S_1$. 
 % The results are listed in Tab.~\ref{tab:tmp2}. The dielectric constant calculated in system $\systemsb$ is reported in Table.~\ref{tab:thermo}.
@@
 _i(t) - \mathbf{\mathit{r}}_i(0)\vert^2\rangle$ is calculated, then the
-value is linearly fitted. It is calculated by NVT simulations of system $S_1$.
+value is linearly fitted. It is calculated by NVT simulations of system $S_1$%
+.
 
@@
 
+{\color{blue} Question1: I see that the statistical uncertainty is twice of
+the standard deviation of time series.\ Let $\{A(x(t),p(t))\}_{t\in \Lambda }
+${\ be time series of physical quantity }$A(x,p)${. Then I want to confirm
+how you defined the average and the standard deviation. (i) Are they for }$%
+\{A(x(t),p(t))\}_{t\in \Lambda }${\ itself? (ii) }Or are they {for }$\left\{ 
+\frac{1}{t}\int_{0}^{t}A(x(s),p(s))ds\right\} _{t\in \Lambda }${? }}
+
+{\color{blue}Maybe (ii) is correct. But "100~Bar" in the description "the
+fluctuation (measured by standard deviation) of the pressure is roughly
+100~Bar" should come from (i). If so, I proposed the presentation of the
+trajectory of pressures $\{P(x(t),p(t))\}_{t\in \Lambda }$ in SI.}
+
+{\color{blue}Question2 (this is just from my interest): When you did the ZM
+NTP with P-R method, how was the cell shape? You obtained the good density,
+but how about the cell deformation? Was it keep almost the cubic structure?}
+
 % \bibliographystyle{plain}

### 2014-12-05 writedown/zm/paper.water/si.tex
partially finish revising

@@
 % A Critical Appraisal of Zero-Multiple Method in Classical Water Simulation}
+
+\begin{figure}[]
+\centering
+\includegraphics[width=0.5\textwidth]{fig/result.nvt/fig-press.eps}\\
+\caption{A typical pressure trajectory. Simulated with system $L_1$ and SPME electrostatic method.}
+\label{fig:pres-l1}
+\end{figure}
 
@@
 
+\begin{figure}[tbp]
+\centering
+\includegraphics[]{fig/result.nvt/fig-rdf-cutoff.eps}\\
+\caption{  The comparison between the RDF calculated by RF method with group and atom cut-off schemes.
+The results of SPME and ZM $l=1$ are also presented for comparison.}
+\label{fig:gkr-conv-alpha}
+\end{figure}
+
 \newpage

### 2014-12-17 writedown/zm/paper.water/main.tex
backup revise

@@
 
-Introduction of the ZM method, formula...[ {\color{blue} COMMENT: I can
+Introduction of the ZMM, formula...[ {\color{blue} COMMENT: I can
 write here later}]
@@
 
-In order to investigate the performance of ZM method, we simulate the water
-system by using both SPME and ZM methods, and evaluate a set of \emph{%
+In order to investigate the physical-chemical properties obtained  by ZMM, we simulate the water
+system by using both SPME and ZMM, and evaluate a set of \emph{%
 benchmark quantities}. This set covers a broad range of water properties
@@
 these quantities are provided in details in Appendix.~\ref%
-{appendix:benchmark}. By comparing ZM to SPME, a good consistency in
-computing the benchmark quantities would indicate a good accuracy of the ZM
-method. More importantly, the benchmark tests provide knowledge in the
-situations when the ZM method does not work so well, and help in finding the
-way of tuning the working parameters to achieve higher accuracy. The ZM
-method is also compared to the traditional short-range method: RF.
+{appendix:benchmark}. By comparing ZMM to SPME, a good consistency in
+computing the benchmark quantities should indicate a good accuracy of the ZMM.
+More importantly, the benchmark tests provide knowledge in the
+situations when the ZMM does not work so well, and help in finding the
+way of tuning the working parameters to achieve higher accuracy. The ZMM
+is also compared to the traditional short-range method: RF.
 
@@
 % Other point-charge water models differ in the modeling parameters, and
-The accuracy of ZM method in other water models is out of the scope of the
+The accuracy of ZMM in other water models is out of the scope of the
 current work. However, since the point-charge water models share similar
-idea, and only differ in the model parameters, it is highly probable that ZM
+idea, and only differ in the model parameters, it is highly probable that ZMM
 works well with other water models if it works well with TIP3P.
@@
 The neighbor lists were updated every 5 time-steps. The Gromacs by default
-uses the group cut-off scheme, while the ZM method recommends
+uses the group cut-off scheme, while the ZMM recommends
 an atom cut-off scheme~\cite{fukuda2011molecular,fukuda2013zero}. The difference between these cut-off
@@
 based cut-off scheme in the simulations using the SPME (short-range part)
-and ZM electrostatic methods. The implementation details of the
+and ZMM electrostatic. The implementation details of the
 atom cut-off scheme in Gromacs are provided in Appendix.~\ref{app:cut-off}.
-The ZM method was implemented in Gromacs with the tabulated electrostatic
+The ZMM was implemented in Gromacs with the tabulated electrostatic
 interaction, and the interaction tables were generated by a home-made code.
@@
 group cut-off scheme is the default scheme in Gromacs. The experimental
-dielectric consistency $\varepsilon _{\text{rf}}=80$ was adopted for the RF
-method.
+dielectric consistency $\varepsilon _{\text{rf}}=80$ was adopted for the RF.
 % In order to mimic the atom cut-off scheme in
@@
 
-In this section we compare the benchmark quantities of the ZM method to the
+In this section we compare the benchmark quantities of the ZMM to the
 SPME method to investigate the accuracy of the former. The comparison to the
-RF method will also be mentioned, to show that the ZM is a promising
-replacement of the RF method.
+RF  is also mentioned, to show that the ZMM could be a promising
+replacement of the RF.
 
@@
     RF          &1.2 & -- &--  & $-26.0$ (0.3) & 72.3 (0.8)  &\textbf{82.3} (1.0)  & \textbf{6.51} (0.06)      &\textbf{1.15} (0.02) & \textbf{59} (1) & \textbf{6.27} (0.19)& \textbf{0.449} (0.020)\\\hline
-    ZM          &1.2 & 1  &0.0 & $-26.2$ (0.3) & 71.8 (0.9)  &78.9 (1.0)           & 5.87 (0.05)               &1.01 (0.02)          & 96 (2)          & \textbf{5.53} (0.11)& \textbf{0.346} (0.006)\\ 
-    ZM          &1.2 & 1  &0.5 & $-26.4$ (0.3) & 72.3 (0.8)  &78.9 (0.9)           & 5.92 (0.05)               &\textbf{1.00} (0.02) & 97 (2)          & \textbf{5.52} (0.25)& \textbf{0.339} (0.008)\\ 
-    ZM          &1.2 & 1  &1.0 & $-26.0$ (0.2) & 72.4 (0.8)  &78.4 (0.9)           & 5.95 (0.05)               &1.01 (0.02)          & 96 (2)          &        {5.78} (0.25)& \textbf{0.330} (0.011)\\ 
-    ZM          &1.2 & 1  &1.5 & $-26.0$ (0.2) & 71.3 (0.8)  &80.2 (0.9)           & 5.97 (0.05)               &1.04 (0.02)          & 99 (3)          & \textbf{5.71} (0.09)&        {0.312} (0.008)\\ 
-    ZM          &1.2 & 1  &2.0 & $-26.1$ (0.3) & 71.3 (0.8)  &79.4 (0.9)           & \textbf{6.05} (0.05)      &1.05 (0.02)          & 96 (3)          &        {5.90} (0.04)&        {0.307} (0.007)\\\hline
-    ZM          &1.2 & 2  &0.0 & $-26.2$ (0.2) & 71.5 (0.9)  &79.7 (1.0)           & 5.95 (0.05)               &1.03 (0.02)          & 95 (3)          &         5.82  (0.27)&         0.318  (0.012)\\
-    ZM          &1.2 & 3  &0.0 & $-26.2$ (0.2) & 71.6 (0.9)  &79.5 (1.0)           & 5.99 (0.05)               &1.02 (0.02)          & 96 (3)          &         5.79  (0.09)&         0.321  (0.008)\\
-    ZM          &1.2 & 4  &0.0 & $-26.0$ (0.3) & 71.1 (0.8)  &79.5 (1.0)           & 5.96 (0.05)               &1.03 (0.02)          &100 (2)          &         5.89  (0.09)&         0.318  (0.013)\\
+    ZMM          &1.2 & 1  &0.0 & $-26.2$ (0.3) & 71.8 (0.9)  &78.9 (1.0)           & 5.87 (0.05)               &1.01 (0.02)          & 96 (2)          & \textbf{5.53} (0.11)& \textbf{0.346} (0.006)\\
+    ZMM          &1.2 & 1  &0.5 & $-26.4$ (0.3) & 72.3 (0.8)  &78.9 (0.9)           & 5.92 (0.05)               &\textbf{1.00} (0.02) & 97 (2)          & \textbf{5.52} (0.25)& \textbf{0.339} (0.008)\\
+    ZMM          &1.2 & 1  &1.0 & $-26.0$ (0.2) & 72.4 (0.8)  &78.4 (0.9)           & 5.95 (0.05)               &1.01 (0.02)          & 96 (2)          &        {5.78} (0.25)& \textbf{0.330} (0.011)\\
+    ZMM          &1.2 & 1  &1.5 & $-26.0$ (0.2) & 71.3 (0.8)  &80.2 (0.9)           & 5.97 (0.05)               &1.04 (0.02)          & 99 (3)          & \textbf{5.71} (0.09)&        {0.312} (0.008)\\
+    ZMM          &1.2 & 1  &2.0 & $-26.1$ (0.3) & 71.3 (0.8)  &79.4 (0.9)           & \textbf{6.05} (0.05)      &1.05 (0.02)          & 96 (3)          &        {5.90} (0.04)&        {0.307} (0.007)\\\hline
+    ZMM          &1.2 & 2  &0.0 & $-26.2$ (0.2) & 71.5 (0.9)  &79.7 (1.0)           & 5.95 (0.05)               &1.03 (0.02)          & 95 (3)          &         5.82  (0.27)&         0.318  (0.012)\\
+    ZMM          &1.2 & 3  &0.0 & $-26.2$ (0.2) & 71.6 (0.9)  &79.5 (1.0)           & 5.99 (0.05)               &1.02 (0.02)          & 96 (3)          &         5.79  (0.09)&         0.321  (0.008)\\
+    ZMM          &1.2 & 4  &0.0 & $-26.0$ (0.3) & 71.1 (0.8)  &79.5 (1.0)           & 5.96 (0.05)               &1.03 (0.02)          &100 (2)          &         5.89  (0.09)&         0.318  (0.013)\\
     \hline\hline
@@
 volume/pressure molar heat capacity, isothermal compressibility and heat
-expansion coefficient, are compared in Tab.~\ref{tab:thermo}. The ZM results
+expansion coefficient, are compared in Tab.~\ref{tab:thermo}. The ZMM results
 are in good consistency with the SPME results. In almost all cases the
@@
 molar heat capacity and the isothermal compressibility show considerable
-errors. The dependence of the ZM results on the order\ $l$\ is little.
+errors. The dependence of the ZMM results on the order\ $l$\ is little.
 Although the splitting parameter, $\alpha $, also does not have significant
 influence on almost all these thermodynamic quantities for $l=1$, only the
-isothermal compressibility admits a weak dependence. Overall, the ZM\ agrees
+isothermal compressibility admits a weak dependence. Overall, the ZMM\ agrees
 with the SPME results without any bias and out-performs the RF.
@@
 \includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
-\caption{The pressure convergence with respect to the cut-off radius. The ZM
-methods with order from 1 to 4 are compared with the RF. The splitting
-parameter of ZM method is set to be $\protect\alpha =0.00\,\text{nm}^{-1}$.
+\caption{The pressure convergence with respect to the cut-off radius. The ZMM
+  with order from 1 to 4 are compared with the RF. The splitting
+parameter of ZMM  is set to be $\protect\alpha =0.00\,\text{nm}^{-1}$.
 The black solid line indicates the magnitude of the correct pressure: 1~Bar.
@@
 We investigated the dependence on the cut-off radius, $r_{\text{c}}$, on the
-pressure, simulated with system $L_{0}$. The pressure calculated by ZM
-method of order $l=1,2,3$ and $4$ with $\alpha =0$ \ and that by the RF
-method are plotted in Fig.~\ref{fig:pres-comp}. All ZM methods converges to
-the target pressure at large enough cut-off radius. Lower order ZM presents
-an smaller error in the pressure calculation than the higher order ZM
-method. Note ZM $l=1$ tends to under-estimate the pressure, while ZM $l=2,3$
-and 4 tends to over-estimate. However, the accuracy of ZM in pressure
-calculation is much higher than that of the RF method.
+pressure, simulated with system $L_{0}$. The pressure calculated by ZMM
+of order $l=1,2,3$ and $4$ with $\alpha =0$ \ and that by the RF
+are plotted in Fig.~\ref{fig:pres-comp}. All ZMM  converges to
+the target pressure at large enough cut-off radius. Lower order ZMM presents
+an smaller error in the pressure calculation than the higher order ZMM.
+Note ZMM $l=1$ tends to under-estimate the pressure, while ZMM $l=2,3$
+and 4 tends to over-estimate. However, the accuracy of ZMM in pressure
+calculation is much higher than that of the RF.
 
@@
 % \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l4.eps}
-\caption{ The pressure convergence with respect to the cut-off radius for ZM
-method $l=1$ with splitting parameter from $0.0$ to $2.0\,\text{nm}^{-1}$.
+\caption{ The pressure convergence with respect to the cut-off radius for ZMM
+  $l=1$ with splitting parameter from $0.0$ to $2.0\,\text{nm}^{-1}$.
 The black solid line indicates the magnitude of the correct pressure: 1~Bar.
@@
 pressure to higher side, and in particular $\alpha =2.0\,\text{nm}^{-1}$ is
-too large to show no convergence to 1~Bar. This implies that $\alpha \leq 1$
+too large to show no convergence to 1~Bar. This implies that $\alpha \leq 1\,\text{nm}^{-1}$
 should be used in the simulations where the high accuracy in the pressure is
@@
 l$\ and for a small $r_{\text{c}}$, which is consistent with the property of
-the pair potential of the ZM~\cite{fukuda2014zero}. The convergence is not
+the pair potential of the ZMM~\cite{fukuda2014zero}. The convergence is not
 sensitive to $\alpha $ up to $1.0\,\text{nm}^{-1}$.
@@
 pressure error of 20~Bar will only cause a density deviation (calculated by
-the NPT simulations) of roughly 0.1\%. Taking different orders ZM method at
+the NPT simulations) of roughly 0.1\%. Taking different orders ZMM  at
 cut-off 1.2~nm for example, the density deviations are 0.051\%, 0.061\%,
@@
 % [{\color{blue} {COMMENT1:} Can we have a trajectory figure of the pressure?
-% It will show that the fluctuation is large and the 10 Bar error for ZM looks
+% It will show that the fluctuation is large and the 10 Bar error for ZMM looks
 % small. If there is a suitable one, it may be good to put it in SI.} {%
@@
 % ] [ {\color{blue} COMMENT2: Can we have some data on the (mass) density?
-% Some potential users of ZM\ may worry about the deviation of the density
+% Some potential users of ZMM\ may worry about the deviation of the density
 % from the reality due to the pressure error. I remember that the density
-% error for ZM was small. It is helpful to show that the deviation of the
+% error for ZMM was small. It is helpful to show that the deviation of the
 % density is sufficiently small. These two comments indicates that one wants
@@
 % COMMENT1: please see my question in the last page. COMMENT2: The deviation
-% of the pressure between the ZM and PME should be due to this density
-% deviation between the ZM and PME (0.1\%). Namely {0.1\% density deviation
+% of the pressure between the ZMM and PME should be due to this density
+% deviation between the ZMM and PME (0.1\%). Namely {0.1\% density deviation
 % should cause 10 atm deviation.}\ How about this confirmation? ---The
-% pressure by ZM\ in figs1\&2 was calculated with the NTV MD where the cell
+% pressure by ZMM\ in figs1\&2 was calculated with the NTV MD where the cell
 % size was determined by the \textit{PME} NTP. So, if we will do NTV MD with
-% the cell size determined by the \textit{ZM} NTP (which was used to calculate
-% the current density), and if we calculate the pressure by ZM with this new
+% the cell size determined by the \textit{ZMM} NTP (which was used to calculate
+% the current density), and if we calculate the pressure by ZMM with this new
 % NTV, then we should have 1 atm pressure for may cutoff lengths. If this is
@@
 %     System & Method      &       $\alpha$ [$\textrm{nm}^{-1}$] & $r_c$ [nm] &    $l$     &       $\eps$ \\\hline
-%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       1       &       99.8 (3.8)\\ 
-%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       2       &       95.2 (3.6)\\ 
-%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       3       &       93.9 (3.7)\\ 
-%     $\systemmb$  &       ZM          &       0.00    &       1.5     &       3       &       98.7 (3.8)\\ 
-%     $\systemmb$  &       ZM          &       0.00    &       1.8     &       3       &      100.7 (3.6)\\ 
-%     $\systemmb$  &       ZM          &       0.00    &       1.2     &       4       &       94.7 (3.6)\\
+%     $\systemmb$  &       ZMM          &       0.00    &       1.2     &       1       &       99.8 (3.8)\\ 
+%     $\systemmb$  &       ZMM          &       0.00    &       1.2     &       2       &       95.2 (3.6)\\ 
+%     $\systemmb$  &       ZMM          &       0.00    &       1.2     &       3       &       93.9 (3.7)\\ 
+%     $\systemmb$  &       ZMM          &       0.00    &       1.5     &       3       &       98.7 (3.8)\\ 
+%     $\systemmb$  &       ZMM          &       0.00    &       1.8     &       3       &      100.7 (3.6)\\ 
+%     $\systemmb$  &       ZMM          &       0.00    &       1.2     &       4       &       94.7 (3.6)\\
 %     $\systemmb$   & SPME          & 2.09  & 1.9   &       --      &       98.8 (4.0) \\
 %     $\systemmb$  & RF             & --  & 1.2 & -- & 60.6   (1.7) \\
-%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       1       &       97.1 (3.2)\\ 
-%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       2       &       95.6 (3.5)\\ 
-%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       3       &       95.8 (4.6)\\ 
-%     $\systemlb$  &       ZM          &       0.00    &       1.5     &       3       &       98.0 (3.3)\\ 
-%     $\systemlb$  &       ZM          &       0.00    &       1.8     &       3       &       98.9 (4.2)\\ 
-%     $\systemlb$  &       ZM          &       0.00    &       2.1     &       3       &       98.8 (3.9)\\ 
-%     $\systemlb$  &       ZM          &       0.00    &       1.2     &       4       &       97.8 (3.9)\\
+%     $\systemlb$  &       ZMM          &       0.00    &       1.2     &       1       &       97.1 (3.2)\\ 
+%     $\systemlb$  &       ZMM          &       0.00    &       1.2     &       2       &       95.6 (3.5)\\ 
+%     $\systemlb$  &       ZMM          &       0.00    &       1.2     &       3       &       95.8 (4.6)\\ 
+%     $\systemlb$  &       ZMM          &       0.00    &       1.5     &       3       &       98.0 (3.3)\\ 
+%     $\systemlb$  &       ZMM          &       0.00    &       1.8     &       3       &       98.9 (4.2)\\ 
+%     $\systemlb$  &       ZMM          &       0.00    &       2.1     &       3       &       98.8 (3.9)\\ 
+%     $\systemlb$  &       ZMM          &       0.00    &       1.2     &       4       &       97.8 (3.9)\\
 %    $\systemlb$   & SPME          & 2.09  & 1.9   &       --      &       98.7 (3.5) \\
@@
 \caption{The dielectric constant convergence with respect to length of the
-trajectories used to compute the value. The SPME, ZM method $l=1$ to 4 and
-RF are presented. The cut-off distance of ZM and RF methods was 1.2~nm. The
+trajectories used to compute the value. The SPME, ZMM  $l=1$ to 4 and
+RF are presented. The cut-off distance of ZMM and RF  was 1.2~nm. The
 working parameters of SPME are given in Sec.~\protect\ref{sec:protocols} The
@@
 
-The dielectric constant computed by ZM method at different orders are listed
+The dielectric constant computed by ZMM  at different orders are listed
 in Tab.~\ref{tab:thermo}, and are consistent with the SPME computed results.
-In contrast, the RF method has poor accuracy in the dielectric constant. It
+In contrast, the RF  has poor accuracy in the dielectric constant. It
 is well known that the dielectric feature shows system-size dependence~\cite%
 {vanderSpoel2006origin}, therefore we further investigated this dependence
-and also the effect of the cutoff length, as shown in Table~I of SI. ZM
+and also the effect of the cutoff length, as shown in Table~I of SI. ZMM
 shows good results without any system-size dependency and indicate $r_{\text{%
@@
 \caption{The Kirkwood G-factor calculated for system $M_{1}$ (a) and $L_{1} $
-(b). ZM method of orders $l=1,2,3$ and 4 with the cut-off 1.2~nm and
+(b). ZMM  of orders $l=1,2,3$ and 4 with the cut-off 1.2~nm and
 splitting parameter $\protect\alpha =0.0\,\text{nm}^{-1}$ are plotted. The
-RF method is shown as an comparison, which uses a cut-off radius of 1.2~nm
+RF  is shown as an comparison, which uses a cut-off radius of 1.2~nm
 and dielectric constant of 80. The statistical uncertainty of the SPME
@@
 larger system $L_{1}$ in Fig.~\ref{fig:gkr} (b). In both the system, the RF
-method is qualitatively wrong, and the accuracy of the ZM method is much
-higher. In the system of smaller size ($M_{1}$), ZM method of all orders are
-highly consistent with the SPME result, and $l=2$ seems the best. In the
-system of larger size ($L_{1}$), the accuracies of the ZM method is less for
+is qualitatively wrong, and the accuracy of the ZMM  is much
+higher. In the system of smaller size ($M_{1}$), ZMM  of all orders are
+highly consistent with the SPME result, and $l=2$ gave the best result. In the
+system of larger size ($L_{1}$), the accuracies of the ZMM  is less for
 order $l\geq 2$, while they may be in still acceptable accuracy. In both
-systems, ZM $l=1$ presents an artificial oscillation around the cut-off
+systems, ZMM $l=1$ presents an artificial oscillation around the cut-off
 radius (1.2~nm), while this oscillation is not obvious for $l\geq 2$. The
-Kirkwood-G factor computed by ZM in system $S_{1}$ is as good as that
+Kirkwood-G factor computed by ZMM in system $S_{1}$ is as good as that
 computed in $M_{1}$, and is presented in SI.
@@
 \caption{ The cut-off dependency in calculating the Kirkwood-G factor. The
-order of ZM method is $l=3$. The splitting parameter is $\protect\alpha %
+order of ZMM  is $l=3$. The splitting parameter is $\protect\alpha %
 =0.0\,\text{nm}^{-1}$. The statistical uncertainty is presented at 95~\%
@@
 We thus investigated the cut-off dependency in calculating the Kirkwood-G
-factor and present it in Fig.~\ref{fig:gkr-conv} for ZM method of order $l=3$%
+factor and present it in Fig.~\ref{fig:gkr-conv} for ZMM  of order $l=3$%
 . Without surprising, the Kirkwood-G factor converges to the SPME result
@@
 The dynamical quantities, diffusion constant and viscosity, are listed in
-Tab.~\ref{tab:thermo}. The ZM method of order $l\geq 2$ can almost perfectly
-reproduce the SPME dynamical quantities. The ZM order $l=1$ is of less
+Tab.~\ref{tab:thermo}. The ZMM  of order $l\geq 2$ can almost perfectly
+reproduce the SPME dynamical quantities. The ZMM order $l=1$ is of less
 accurate than higher orders, but is more accurate than the RF. Using larger
@@
 \caption{The convergence of the integrated auto-correlation function $I_{%
-\protect\eta }(T)$. Different orders of ZM method are compared with the SPME
+\protect\eta }(T)$. Different orders of ZMM  are compared with the SPME
 as well as RF results. The error bars indicating 95\% confidence level are
@@
 \caption{The convergence of the integrated auto-correlation function $I_{%
-\protect\eta }(T)$. Different splitting parameters for ZM order $l=1$ are
+\protect\eta }(T)$. Different splitting parameters for ZMM order $l=1$ are
 plotted. The error bars indicating 95\% confidence level are plotted with
@@
 as shown in Fig.~\ref{fig:conv-vis}. It is clear that the integral for the
-RF method converges at 6~ps, while the ZM method converges only in 2~ps,
-which is consistent with the SPME result. The value of ZM $l=1$ method is
-different from the rest ZM methods and SPME result, but the results was
+RF  converges at 6~ps, while the ZMM  converges only in 2~ps,
+which is consistent with the SPME result. The value of ZMM $l=1$  is
+different from the rest ZMM  and SPME result, but the results was
 improved by the damping effect as shown in Fig.~\ref{fig:conv-vis-damp}.
@@
 \caption{The comparison of the center-of-mass radial distribution functions
-calculated by SPME, ZM and RF methods. The insert is a zoom-in of range 0.9
+calculated by SPME, ZMM and RF. The insert is a zoom-in of range 0.9
 -- 1.5~nm. In the inset, the position of the cut-off (1.2~nm) is indicated
-by a vertical black line. For ZM method, the splitting parameter $\protect%
+by a vertical black line. For ZMM, the splitting parameter $\protect%
 \alpha $ was set to 0.0~$\text{nm}^{-1}$. }
@@
 We plot in Fig.~\ref{fig:rdf} the center-of-mass radial distribution
-functions (RDFs) of TIP3P water calculated by the SPME, ZM ($l=1,2,3$ and $4$%
-) with $\alpha =0$\ and RF methods. It is observed from the figure that the
-ZM RDFs are consist very well with the SPME RDF, except oscillations around
+functions (RDFs) of TIP3P water calculated by the SPME, ZMM ($l=1,2,3$ and $4$%
+) with $\alpha =0$\ and RF. It is observed from the figure that the
+ZMM RDFs are consist very well with the SPME RDF, except oscillations around
 the cut-off radius. This oscillations are not so large, as the maximum
@@
 % individual $l$}]
-but should be artificial. However, higher order ZM method present lower
+but should be artificial. However, higher order ZMM present lower
 amplitude oscillation, and when $l\geq 3$, the improvement is dramatic and
-the oscillation is almost negligible. \recheck{The RF RDF is more accurate than the ZM ones,
+the oscillation is almost negligible. \recheck{The RF RDF is more accurate than the ZMM ones,
 this is mainly because of the group cut-off used in simulating with RF. When changing
-the cut-off scheme to atom scheme, the accuracy is RF is roughly same as ZM $l=1$ (see SI).
+the cut-off scheme to atom scheme, the accuracy is RF is roughly same as ZMM $l=1$ (see SI).
 We could not explain the reason, but the numerical evidence suggests if only the RDF is
-of interest, a group cut-off scheme or higher order of ZM is preferable.
+of interest, a group cut-off scheme or higher order of ZMM is preferable.
 }
@@
 % \color{blue} It is preferable to write it if the reason of the goodness is
-% clear. Anyway, please describe.... This is the only matter ZM is inferior to
+% clear. Anyway, please describe.... This is the only matter ZMM is inferior to
 % RF. So, it may be interesting if the reason is clear. } {\color{red} I
@@
 \caption{ The splitting parameter dependency in calculating the
-center-of-mass RDF for ZM method $l=1$. The insert is a zoom-in of range 0.9
+center-of-mass RDF for ZMM  $l=1$. The insert is a zoom-in of range 0.9
 -- 1.5~nm. In the insert, the position of the cut-off (1.2~nm) is indicated
@@
 larger splitting parameter $\alpha $. Figure~\ref{fig:rdf-damp} presents the
-RDF of ZM $l=1$ with splitting parameter from $0.0$ to $2.0$~$\text{nm}^{-1}$%
+RDF of ZMM $l=1$ with splitting parameter from $0.0$ to $2.0$~$\text{nm}^{-1}$%
 . The damping effect, viz., a clear trend of better RDF by using a larger $%
@@
 The error bars indicating 95\% confidence level are plotted with the SPME method.
-The different splitting parameters for ZM $l=1$ method are plotted}
+The different splitting parameters for ZMM $l=1$ method are plotted}
 %   \label{fig:damp-vis-l1}
@@
 
-% The RDF is plotted for different splitting parameters $\alpha$ for ZM $l=2$ and 3 in Fig.~\ref{fig:damp-rdf-l23}. Higher $\alpha$ reproduces the RDF better.
+% The RDF is plotted for different splitting parameters $\alpha$ for ZMM $l=2$ and 3 in Fig.~\ref{fig:damp-rdf-l23}. Higher $\alpha$ reproduces the RDF better.
 % The system was $L_1$.
@@
 %   \includegraphics[width=0.49\textwidth]{fig/result.nvt/fig-rdf-l3-damp.eps}
-%   \caption{Radial distribution function for different splitting parameters $\alpha$ for ZM $l=2$ (left) and $l=3$ (right).}
+%   \caption{Radial distribution function for different splitting parameters $\alpha$ for ZMM $l=2$ (left) and $l=3$ (right).}
 %   \label{fig:damp-rdf-l23}
@@
 % resulting slop is used to calculate the diffusion constant. The results are listed in Table~\ref{tab:thermo}.
-% The ZM method $l\geq 2$ is consistent with the SPME
+% The ZMM method $l\geq 2$ is consistent with the SPME
 % result, while the RF method is off.
@@
 
-In summary, ZM works well for almost all cases. Damping effect of the
+In summary, ZMM works well for almost all cases. Damping effect of the
 splitting parameter, viz., larger $\alpha $\ gives accurate results, was
@@
 system are thus $\alpha \leq 1$~$\text{nm}^{-1}$ and $l=2$ or $l=3$. Using
-these parameters, the ZM method achieves almost perfect accuracy in
+these parameters, the ZMM  achieves almost perfect accuracy in
 computing the excess chemical potential, constant volume/pressure heat
@@
 [ {\color{blue} COMMENT0: Although I know this paper's aim is to judge the
-accuracy of the ZM, I also know many people may also be interested in some
+accuracy of the ZMM, I also know many people may also be interested in some
 different aspects. So please see the following.}]
@@
 [ {\color{blue} COMMENT1: The first one is the accuracy comparison between
-the ZM\ and a "default PME" that uses default protocol and parameters, e.g.,
+the ZMM\ and a "default PME" that uses default protocol and parameters, e.g.,
 group-based cutoff scheme (OK?) and a short cutoff length(about 1 nm?) for
@@
 calculation, and they just uses the default PME. Thus it would be OK\ for
-them if the difference between the ZM\ and a "default PME" is small. Is it
+them if the difference between the ZMM\ and a "default PME" is small. Is it
 possible to calculate e.g., pressure or KG factor for {$L_{1}$} (n{ot all
@@
 [ {\color{blue} COMMENT2: The second one is the comparison of the
-computational timing between the ZM\ and a "default PME."\ Many people,
+computational timing between the ZMM\ and a "default PME."\ Many people,
 including e.g. reviewers, should be interested in it. How about this
-comparison using a short time simulation?\ One expects ZM\ is faster than
+comparison using a short time simulation?\ One expects ZMM\ is faster than
 SPME. But is SPME with rc=1.0 nm along with the buffer length 0.2nm (are
-they default length?) faster than ZM\ with rc=1.2 nm along with the buffer
+they default length?) faster than ZMM\ with rc=1.2 nm along with the buffer
 length 0.3nm?? }]
@@
 The Gromacs code 4.6 does not directly support the atomistic cut-off scheme, 
-{\color{blue}which is recommended in the ZM method, in }using tabulated
+{\color{blue}which is recommended in the ZMM, in }using tabulated
 electrostatic interaction. The atom cut-off scheme can be implemented by
@@
 \recheck{It should be pointed out that this implementation is not optimal,
-  when the gromacs build-in atom cut-off scheme supports the tablulated potential, we expect better performance of ZM method.}
+  when the gromacs build-in atom cut-off scheme supports the tablulated potential, we expect better performance of ZMM.}
 % {%
@@
 
-% The results are plotted in Fig.~\ref{fig:rdf}. As the order of ZM method goes higher, the precision of RDF improves. In addition, the precision of RF method is between $l=2$ and $l=3$.
+% The results are plotted in Fig.~\ref{fig:rdf}. As the order of ZMM method goes higher, the precision of RDF improves. In addition, the precision of RF method is between $l=2$ and $l=3$.
 
@@
 
-{\color{blue}Question2 (this is just from my interest): When you did the ZM
+{\color{blue}Question2 (this is just from my interest): When you did the ZMM
 NTP with P-R method, how was the cell shape? You obtained the good density,
 but how about the cell deformation? Was it keep almost the cubic structure?}
+\recheck{The box is kept cubic by resizing isotropically in x, y and z directions.}
 

### 2014-12-17 writedown/zm/paper.water/main.tex
my revise

@@
 %TCIDATA{BibliographyScheme=BibTeX}
-%TCIDATA{LastRevised=Monday, December 01, 2014 18:07:38}
+%TCIDATA{LastRevised=Wednesday, December 10, 2014 19:23:08}
 %TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
@@
 \newcommand{\systemlb}{L_1}
-
+% \input{tcilatex}
 \begin{document}
@@
 
-Introduction of the ZMM, formula...[ {\color{blue} COMMENT: I can
-write here later}]
+Introduction of the ZMM, formula...[ {\color{blue} COMMENT: I can write here
+later}]
 
@@
 
-In order to investigate the physical-chemical properties obtained  by ZMM, we simulate the water
-system by using both SPME and ZMM, and evaluate a set of \emph{%
-benchmark quantities}. This set covers a broad range of water properties
-that are of general interest. It includes the structure property (radial
-distribution function), the thermodynamic properties (pressure, excess
-chemical potential, constant volume/pressure heat capacity, isothermal
-compressibility, thermal expansion coefficient), dielectric properties
-(dielectric constant and Kirkwood-G factor) and dynamical properties
-(diffusion constant and viscosity). The definitions and computing methods of
-these quantities are provided in details in Appendix.~\ref%
+In order to investigate the physical-chemical properties obtained by ZMM, we
+simulate the water system by using both SPME and ZMM, and evaluate a set of 
+\emph{benchmark quantities}. This set covers a broad range of water
+properties that are of general interest. It includes the structure property
+(radial distribution function), the thermodynamic properties (pressure,
+excess chemical potential, constant volume/pressure heat capacity,
+isothermal compressibility, thermal expansion coefficient), dielectric
+properties (dielectric constant and Kirkwood-G factor) and dynamical
+properties (diffusion constant and viscosity). The definitions and computing
+methods of these quantities are provided in details in Appendix.~\ref%
 {appendix:benchmark}. By comparing ZMM to SPME, a good consistency in
-computing the benchmark quantities should indicate a good accuracy of the ZMM.
-More importantly, the benchmark tests provide knowledge in the
-situations when the ZMM does not work so well, and help in finding the
-way of tuning the working parameters to achieve higher accuracy. The ZMM
-is also compared to the traditional short-range method: RF.
+computing the benchmark quantities should indicate a good accuracy of the
+ZMM. More importantly, the benchmark tests provide knowledge in the
+situations when the ZMM does not work so well, and help in finding the way
+of tuning the working parameters to achieve higher accuracy. The ZMM is also
+compared to the traditional short-range method: RF. Magnitude
+of the deviations between the ZMM and SPME is basically
+discussed considering the statistical uncertainty.  \recheck{More details of the statistical
+uncertainty in computing a physical quantity is provided in Appendix~\ref{app:error}.}
+% ....[COMMENTS: Since the critical issue of this ms is the
+% accuracy check, it is helpful (around here) to describe briefly how this
+% check is done. This is also helpful for readers to understand the PME\
+% pressure deviation "($-0.4\pm 1.5$~Bar){" appearing later. A little bit more
+% detailed descriptions may be added in Appendix. Duplication to the caption
+% of fig 1 is not the problem.]} }
 
@@
 % Other point-charge water models differ in the modeling parameters, and
-The accuracy of ZMM in other water models is out of the scope of the
-current work. However, since the point-charge water models share similar
-idea, and only differ in the model parameters, it is highly probable that ZMM
-works well with other water models if it works well with TIP3P.
+The accuracy of ZMM in other water models is out of the scope of the current
+work. However, since the point-charge water models share similar idea, and
+only differ in the model parameters, it is highly probable that ZMM works
+well with other water models if it works well with TIP3P.
 
@@
 The neighbor lists were updated every 5 time-steps. The Gromacs by default
-uses the group cut-off scheme, while the ZMM recommends
-an atom cut-off scheme~\cite{fukuda2011molecular,fukuda2013zero}. The difference between these cut-off
-schemes is discussed in detail in e.g.~Ref.~\cite%
+uses the group cut-off scheme, while the ZMM recommends an atom cut-off
+scheme~\cite{fukuda2011molecular,fukuda2013zero}. The difference between
+these cut-off schemes is discussed in detail in e.g.~Ref.~\cite%
 {hunenberger1998alternative,baumketner2009removing}. We adopted the atom
 based cut-off scheme in the simulations using the SPME (short-range part)
-and ZMM electrostatic. The implementation details of the
-atom cut-off scheme in Gromacs are provided in Appendix.~\ref{app:cut-off}.
-The ZMM was implemented in Gromacs with the tabulated electrostatic
-interaction, and the interaction tables were generated by a home-made code.
-
-We treated the RF with the group cut-off scheme because the
-group cut-off scheme is the default scheme in Gromacs. The experimental
-dielectric consistency $\varepsilon _{\text{rf}}=80$ was adopted for the RF.
+and ZMM electrostatic. The implementation details of the atom cut-off scheme
+in Gromacs are provided in Appendix.~\ref{app:cut-off}. The ZMM was
+implemented in Gromacs with the tabulated electrostatic interaction, and the
+interaction tables were generated by a home-made code.
+
+We treated the RF with the group cut-off scheme because the group cut-off
+scheme is the default scheme in Gromacs. The experimental dielectric
+consistency $\varepsilon _{\text{rf}}=80$ was adopted for the RF. 
 % In order to mimic the atom cut-off scheme in
@@
 
-In this section we compare the benchmark quantities of the ZMM to the
-SPME method to investigate the accuracy of the former. The comparison to the
-RF  is also mentioned, to show that the ZMM could be a promising
-replacement of the RF.
+In this section we compare the benchmark quantities of the ZMM to the SPME
+method to investigate the accuracy of the former. The comparison to the RF
+is also mentioned, to show that the ZMM could be a promising replacement of
+the RF.
 
@@
 volume/pressure molar heat capacity, isothermal compressibility and heat
-expansion coefficient, are compared in Tab.~\ref{tab:thermo}. The ZMM results
-are in good consistency with the SPME results. In almost all cases the
-deviations from the SPME results are smaller than the statistical
+expansion coefficient, are compared in Tab.~\ref{tab:thermo}. The ZMM
+results are in good consistency with the SPME results. In almost all cases
+the deviations from the SPME results are smaller than the statistical
 uncertainty. The RF was not so bad, but the results of the constant pressure
@@
 influence on almost all these thermodynamic quantities for $l=1$, only the
-isothermal compressibility admits a weak dependence. Overall, the ZMM\ agrees
-with the SPME results without any bias and out-performs the RF.
+isothermal compressibility admits a weak dependence. Overall, the ZMM\
+agrees with the SPME results without any bias and out-performs the RF.
 
@@
 \begin{figure}[tbp]
-\centering
+\caption{The pressure convergence with respect to the cut-off radius. The
+ZMM with order from 1 to 4 are compared with the RF. The splitting parameter
+of ZMM is set to be $\protect\alpha =0.00\,\text{nm}^{-1}$. The black solid
+line indicates the magnitude of the correct pressure: 1~Bar. The error bars
+present the statistical uncertainty at 95\% confidence level. {\color{red}
+This uncertainty is twice of the standard deviation of the estimates (which
+are averages along MD trajectories) that is calculated by the block average
+method~\protect\cite{janke2002statistical}.} }
+\label{fig:pres-comp}\centering
 \includegraphics[]{fig/nvt.pressure.1/pressure-methods.eps}
-\caption{The pressure convergence with respect to the cut-off radius. The ZMM
-  with order from 1 to 4 are compared with the RF. The splitting
-parameter of ZMM  is set to be $\protect\alpha =0.00\,\text{nm}^{-1}$.
-The black solid line indicates the magnitude of the correct pressure: 1~Bar.
-The error bars present the statistical uncertainty at 95\% confidence level. 
-{\color{red} This uncertainty is twice of the standard deviation of the
-estimates (which are averages along MD trajectories) that is calculated by
-the block average method~\protect\cite{janke2002statistical}.}
-% [ {\ 
-% \color{blue}It maybe good to repeat such explanation in Sec.IIIA.}].[{\ 
-% \color{blue} another COMMENT: In these figures, can we see the statistical
-% uncertainty of the pressure obtained by the SPME? Viz., I found no error
-% bars for SPME.} {\color{red} NO SPME result is given in this figure, 1 Bar
-% is the target pressure.}][{\color{blue} Can I konw the the statistical
-% uncertainty of the pressure obtained by the SPME?}]
-}
-\label{fig:pres-comp}
 \end{figure}
@@
 We investigated the dependence on the cut-off radius, $r_{\text{c}}$, on the
-pressure, simulated with system $L_{0}$. The pressure calculated by ZMM
-of order $l=1,2,3$ and $4$ with $\alpha =0$ \ and that by the RF
-are plotted in Fig.~\ref{fig:pres-comp}. All ZMM  converges to
-the target pressure at large enough cut-off radius. Lower order ZMM presents
-an smaller error in the pressure calculation than the higher order ZMM.
-Note ZMM $l=1$ tends to under-estimate the pressure, while ZMM $l=2,3$
-and 4 tends to over-estimate. However, the accuracy of ZMM in pressure
-calculation is much higher than that of the RF.
-
+pressure, simulated with system $L_{0}$. The pressure calculated by ZMM of
+order $l=1,2,3$ and $4$ with $\alpha =0$ \ and that by the RF are plotted in
+Fig.~\ref{fig:pres-comp}. All ZMM converges to the target pressure at large
+enough cut-off radius. Lower order ZMM presents an smaller error in the
+pressure calculation than the higher order ZMM. Note ZMM $l=1$ tends to
+under-estimate the pressure, while ZMM $l=2,3$ and 4 tends to over-estimate.
+However, the accuracy of ZMM in pressure calculation is much higher than
+that of the RF. 
 \begin{figure}[tbp]
@@
 % \includegraphics[width=0.24\textwidth]{fig/nvt.pressure.1/pressure-l4.eps}
-\caption{ The pressure convergence with respect to the cut-off radius for ZMM
-  $l=1$ with splitting parameter from $0.0$ to $2.0\,\text{nm}^{-1}$.
-The black solid line indicates the magnitude of the correct pressure: 1~Bar.
-The error bars present the statistical uncertainty at 95\% confidence level.}
+\caption{ The pressure convergence with respect to the cut-off radius for
+ZMM $l=1$ with splitting parameter from $0.0$ to $2.0\,\text{nm}^{-1}$. The
+black solid line indicates the magnitude of the correct pressure: 1~Bar. The
+error bars present the statistical uncertainty at 95\% confidence level.}
 \label{fig:pres-l1}
 \end{figure}
-
 The effect of $\alpha $ in the case of $l=1$ is shown in Fig.~\ref%
@@
 pressure to higher side, and in particular $\alpha =2.0\,\text{nm}^{-1}$ is
-too large to show no convergence to 1~Bar. This implies that $\alpha \leq 1\,\text{nm}^{-1}$
-should be used in the simulations where the high accuracy in the pressure is
-important. This "anti-damping effect" is similarly seen in the energy
-accuracy in the TIP3P model~\cite{fukuda2014zero}. 
+too large to show no convergence to 1~Bar. This implies that $\alpha \leq 1\,%
+\text{nm}^{-1}$ should be used in the simulations where the high accuracy in
+the pressure is important. This "anti-damping effect" is similarly seen in
+the energy accuracy in the TIP3P model~\cite{fukuda2014zero}. 
 % [JCP2014 (J. Chem. Phys. 140, 194307 (2014))].
@@
 
-It should be noted that even with the system $L_{0}$ that contains 13824
-water molecules, the fluctuation (measured by standard deviation) of the
-pressure is roughly 100~Bar, which means that it is very difficult to
-achieve very accurate estimate for this quantity.  In practice a
-pressure error of 20~Bar will only cause a density deviation (calculated by
-the NPT simulations) of roughly 0.1\%. Taking different orders ZMM  at
-cut-off 1.2~nm for example, the density deviations are 0.051\%, 0.061\%,
-0.097\% and 0.146\% for $l=1,2,3$ and 4, respectively. For $l\leq 3$ the
-pressure error is less than 20~Bar, while for $l=4$ the pressure error is
-less than 30~Bar (see Fig.~\ref{fig:pres-comp}).
-
+{Larger estimations of the pressure seen in the ZMMs with $l>1$
+should come from, roughly speaking, the suppression of the negative
+contribution of the dipole-dipole (Keesom) attractive interaction from a
+long distance. The suppression is larger, as the values of ${l}$ and $\alpha 
+$ increase due to the damping in the ZMM pair function, and larger as $r_{%
+\text{c}}$ decreases. Specifically, the ignorance of the Fourier part in the
+ZMM~\cite{fukuda2011molecular} accounts for this suppression, since
+suppressed function erf$(\alpha r)/r$ tends to the original Coulomb $1/r$ as 
+$\alpha $ increases (e.g., erf$(\alpha r)\sim 1$ for $\alpha r\gtrsim 2$).
+Thus the ignorance causes positive contribution to the pressure estimation
+with increasing $\alpha $, as observed in Fig.~\ref{fig:pres-l1}. This
+ignorance is validated for a small} { $\alpha $, which limits
+the use of large $\alpha $\ in the ZMM. In addition, the dependence on order 
+$l$ should be relevant to the excess energy error~\cite{fukuda2014zero},
+which depends on the order. }
+
+{The magnitude and origin of the deviations of the pressure in
+the ZMM\ are discussed more quantitatively. First note that even with the
+largest} system $L_{0}$ that contains 13824 water molecules, the fluctuation
+(measured by standard deviation) of the pressure is roughly 100~Bar {%
+(see SI fig.1)}, which means that it is very difficult to
+achieve very accurate estimate for this quantity. {A pressure
+error of 20~Bar only cause a density deviation, which is calculated by the
+NPT simulations of ZMM, of roughly }${0.1}${\% (The density
+deviation of ${0.1}$\% corresponds to each cell length deviation of about $%
+0.03$\%, which should not be important to many applications). In fact,}
+taking different orders ZMM at cut-off 1.2~nm with $\alpha =0$%
+ for example, the density deviations {were} $0.051$\%, 
+$0.061$\%, $0.097$\% and $0.146$\% for $l=1,2,3$ and 4, respectively.
+%For $l\leq 3$ the pressure error is less than 20~Bar, while
+%for $l=4$ the pressure error is less than 30~Bar (see Fig.~\ref%
+%{fig:pres-comp}).
 % [{\color{blue} {COMMENT1:} Can we have a trajectory figure of the pressure?
@@
 % }]
-
+{Namely, the density of
+the current simulation was fixed by the SPME NPT simulation, and this
+density was deviated about $0.1$\% from the equilibrated value of the ZMM.} {%
+The pressure deviations of the ZMM, although which may seem
+large, originated from this slight density deviations between the SPME and
+ZMM and from the sensitivity of the pressure to the density.} 
 % \begin{table}
@@
 \caption{The dielectric constant convergence with respect to length of the
-trajectories used to compute the value. The SPME, ZMM  $l=1$ to 4 and
-RF are presented. The cut-off distance of ZMM and RF  was 1.2~nm. The
-working parameters of SPME are given in Sec.~\protect\ref{sec:protocols} The
-system used for simulation is $S_{1}$.}
+trajectories used to compute the value. The SPME, ZMM $l=1$ to 4 and RF are
+presented. The cut-off distance of ZMM and RF was 1.2~nm. The working
+parameters of SPME are given in Sec.~\protect\ref{sec:protocols} The system
+used for simulation is $S_{1}$.}
 \label{fig:eps-conv}
@@
 
-The dielectric constant computed by ZMM  at different orders are listed
-in Tab.~\ref{tab:thermo}, and are consistent with the SPME computed results.
-In contrast, the RF  has poor accuracy in the dielectric constant. It
-is well known that the dielectric feature shows system-size dependence~\cite%
+The dielectric constant computed by ZMM at different orders are listed in
+Tab.~\ref{tab:thermo}, and are consistent with the SPME computed results. In
+contrast, the RF has poor accuracy in the dielectric constant. It is well
+known that the dielectric feature shows system-size dependence~\cite%
 {vanderSpoel2006origin}, therefore we further investigated this dependence
@@
 \caption{The Kirkwood G-factor calculated for system $M_{1}$ (a) and $L_{1} $
-(b). ZMM  of orders $l=1,2,3$ and 4 with the cut-off 1.2~nm and
-splitting parameter $\protect\alpha =0.0\,\text{nm}^{-1}$ are plotted. The
-RF  is shown as an comparison, which uses a cut-off radius of 1.2~nm
-and dielectric constant of 80. The statistical uncertainty of the SPME
-method is presented at 95~\% confidence level with the red error bars. the
-statistical uncertainty of the SPME method is denoted by the red error bars.
-The statistical uncertainties of the other methods are essentially of the
-same size as the SPME, so they are not presented in the figure for clarity.}
+(b). ZMM of orders $l=1,2,3$ and 4 with the cut-off 1.2~nm and splitting
+parameter $\protect\alpha =0.0\,\text{nm}^{-1}$ are plotted. The RF is shown
+as an comparison, which uses a cut-off radius of 1.2~nm and dielectric
+constant of 80. The statistical uncertainty of the SPME method is presented
+at 95~\% confidence level with the red error bars. the statistical
+uncertainty of the SPME method is denoted by the red error bars. The
+statistical uncertainties of the other methods are essentially of the same
+size as the SPME, so they are not presented in the figure for clarity.}
 \label{fig:gkr}
@@
 larger system $L_{1}$ in Fig.~\ref{fig:gkr} (b). In both the system, the RF
-is qualitatively wrong, and the accuracy of the ZMM  is much
-higher. In the system of smaller size ($M_{1}$), ZMM  of all orders are
-highly consistent with the SPME result, and $l=2$ gave the best result. In the
-system of larger size ($L_{1}$), the accuracies of the ZMM  is less for
-order $l\geq 2$, while they may be in still acceptable accuracy. In both
-systems, ZMM $l=1$ presents an artificial oscillation around the cut-off
-radius (1.2~nm), while this oscillation is not obvious for $l\geq 2$. The
-Kirkwood-G factor computed by ZMM in system $S_{1}$ is as good as that
-computed in $M_{1}$, and is presented in SI.
+is qualitatively wrong, and the accuracy of the ZMM is much higher. In the
+system of smaller size ($M_{1}$), ZMM of all orders are highly consistent
+with the SPME result, and $l=2$ gave the best result. In the system of
+larger size ($L_{1}$), the accuracies of the ZMM is less for order $l\geq 2$%
+, while they may be in still acceptable accuracy. In both systems, ZMM $l=1$
+presents an artificial oscillation around the cut-off radius (1.2~nm), while
+this oscillation is not obvious for $l\geq 2$. The Kirkwood-G factor
+computed by ZMM in system $S_{1}$ is as good as that computed in $M_{1}$,
+and is presented in SI.
 
@@
 \caption{ The cut-off dependency in calculating the Kirkwood-G factor. The
-order of ZMM  is $l=3$. The splitting parameter is $\protect\alpha %
-=0.0\,\text{nm}^{-1}$. The statistical uncertainty is presented at 95~\%
+order of ZMM is $l=3$. The splitting parameter is $\protect\alpha =0.0\,%
+\text{nm}^{-1}$. The statistical uncertainty is presented at 95~\%
 confidence level by the error bars. }
@@
 We thus investigated the cut-off dependency in calculating the Kirkwood-G
-factor and present it in Fig.~\ref{fig:gkr-conv} for ZMM  of order $l=3$%
-. Without surprising, the Kirkwood-G factor converges to the SPME result
-when using increasingly large cut-off radius. In Fig.~\ref{fig:gkr-damp-l1},
-it shows that in the case of $l=1$, the largest splitting parameter ($\alpha
+factor and present it in Fig.~\ref{fig:gkr-conv} for ZMM of order $l=3$.
+Without surprising, the Kirkwood-G factor converges to the SPME result when
+using increasingly large cut-off radius. In Fig.~\ref{fig:gkr-damp-l1}, it
+shows that in the case of $l=1$, the largest splitting parameter ($\alpha
 =2.0\ \text{nm}^{-1}$) is worse in calculating the Kirkwood-G factor than
@@
 \caption{The convergence of the integrated auto-correlation function $I_{%
-\protect\eta }(T)$. Different orders of ZMM  are compared with the SPME
-as well as RF results. The error bars indicating 95\% confidence level are
+\protect\eta }(t)$. Different orders of ZMM are compared with the SPME as
+well as RF results. The error bars indicating 95\% confidence level are
 plotted with the SPME method. }
@@
 \caption{The convergence of the integrated auto-correlation function $I_{%
-\protect\eta }(T)$. Different splitting parameters for ZMM order $l=1$ are
+\protect\eta }(t)$. Different splitting parameters for ZMM order $l=1$ are
 plotted. The error bars indicating 95\% confidence level are plotted with
@@
 as shown in Fig.~\ref{fig:conv-vis}. It is clear that the integral for the
-RF  converges at 6~ps, while the ZMM  converges only in 2~ps,
-which is consistent with the SPME result. The value of ZMM $l=1$  is
-different from the rest ZMM  and SPME result, but the results was
-improved by the damping effect as shown in Fig.~\ref{fig:conv-vis-damp}.
-Similar to the behaviors seen in Fig.~\ref{fig:conv-vis}, the convergence is
-quick for a large $\alpha $.
+RF converges at 6~ps, while the ZMM converges only in 2~ps, which is
+consistent with the SPME result. The value of ZMM $l=1$ is different from
+the rest ZMM and SPME result, but the results was improved by the damping
+effect as shown in Fig.~\ref{fig:conv-vis-damp}. Similar to the behaviors
+seen in Fig.~\ref{fig:conv-vis}, the convergence is quick for a large $%
+\alpha $.
 
@@
 \caption{The comparison of the center-of-mass radial distribution functions
-calculated by SPME, ZMM and RF. The insert is a zoom-in of range 0.9
--- 1.5~nm. In the inset, the position of the cut-off (1.2~nm) is indicated
-by a vertical black line. For ZMM, the splitting parameter $\protect%
-\alpha $ was set to 0.0~$\text{nm}^{-1}$. }
+calculated by SPME, ZMM and RF. The insert is a zoom-in of range 0.9 --
+1.5~nm. In the inset, the position of the cut-off (1.2~nm) is indicated by a
+vertical black line. For ZMM, the splitting parameter $\protect\alpha $ was
+set to 0.0~$\text{nm}^{-1}$. }
 \label{fig:rdf}
@@
 We plot in Fig.~\ref{fig:rdf} the center-of-mass radial distribution
-functions (RDFs) of TIP3P water calculated by the SPME, ZMM ($l=1,2,3$ and $4$%
-) with $\alpha =0$\ and RF. It is observed from the figure that the
-ZMM RDFs are consist very well with the SPME RDF, except oscillations around
-the cut-off radius. This oscillations are not so large, as the maximum
-magnitude of the discrepancies from the SPME is about $1.9\%$ for $l=1$ and $%
-{0.3\%}$ for $l=2$, % {[} {\color{blue}
+functions (RDFs) of TIP3P water calculated by the SPME, ZMM ($l=1,2,3$ and $%
+4 $) with $\alpha =0$\ and RF. It is observed from the figure that the ZMM
+RDFs are consist very well with the SPME RDF, except oscillations around the
+cut-off radius. This oscillations are not so large, as the maximum magnitude
+of the discrepancies from the SPME is about $1.9\%$ for $l=1$ and ${0.3\%}$
+for $l=2$, % {[} {\color{blue}
 % "$2\%"$ is just my guess. How about stating here the maximum error for
 % individual $l$}]
-but should be artificial. However, higher order ZMM present lower
-amplitude oscillation, and when $l\geq 3$, the improvement is dramatic and
-the oscillation is almost negligible. \recheck{The RF RDF is more accurate than the ZMM ones,
-this is mainly because of the group cut-off used in simulating with RF. When changing
-the cut-off scheme to atom scheme, the accuracy is RF is roughly same as ZMM $l=1$ (see SI).
-We could not explain the reason, but the numerical evidence suggests if only the RDF is
-of interest, a group cut-off scheme or higher order of ZMM is preferable.
-}
+but should be artificial. However, higher order ZMM present lower amplitude
+oscillation, and when $l\geq 3$, the improvement is dramatic and the
+oscillation is almost negligible. [ {\color{blue}COMMENT: I thank for your
+efforts to reveal that the GC is far better than AC in RDF. Complete pursuit
+of RF RDF, including the verification of Prof Nakamura's scenario, should be
+our future work. Thus I have omitted the descriptions of the difference
+between GC and AC in RDF]} %{\color{red} The RF RDF is more accurate
+%than the ZMM ones, this is mainly because of the group cut-off used in
+%simulating with RF. When changing the cut-off scheme to atom scheme, the
+%accuracy is RF is roughly same as ZMM $l=1$ (see SI). We could not explain
+%the reason, but the numerical evidence suggests if only the RDF is of
+%interest, a group cut-off scheme or higher order of ZMM is preferable. }
 
@@
 \caption{ The splitting parameter dependency in calculating the
-center-of-mass RDF for ZMM  $l=1$. The insert is a zoom-in of range 0.9
--- 1.5~nm. In the insert, the position of the cut-off (1.2~nm) is indicated
-by a vertical black line. }
+center-of-mass RDF for ZMM $l=1$. The insert is a zoom-in of range 0.9 --
+1.5~nm. In the insert, the position of the cut-off (1.2~nm) is indicated by
+a vertical black line. }
 \label{fig:rdf-damp}
@@
 larger splitting parameter $\alpha $. Figure~\ref{fig:rdf-damp} presents the
-RDF of ZMM $l=1$ with splitting parameter from $0.0$ to $2.0$~$\text{nm}^{-1}$%
-. The damping effect, viz., a clear trend of better RDF by using a larger $%
-\alpha $, is observed. At $\alpha =2.0\ \text{nm}^{-1}$ the RDF is almost
-overlapping with the SPME result. This damping effect is clearer for a
-smaller order $l$\ (see SI for results of {$l=2$ and $3$}), as expected from
-the pair potential behavior~\cite{fukuda2014zero}.
+RDF of ZMM $l=1$ with splitting parameter from $0.0$ to $2.0$~$\text{nm}%
+^{-1} $. The damping effect, viz., a clear trend of better RDF by using a
+larger $\alpha $, is observed. At $\alpha =2.0\ \text{nm}^{-1}$ the RDF is
+almost overlapping with the SPME result. This damping effect is clearer for
+a smaller order $l$\ (see SI for results of {$l=2$ and $3$}), as expected
+from the pair potential behavior~\cite{fukuda2014zero}.
 
@@
 system are thus $\alpha \leq 1$~$\text{nm}^{-1}$ and $l=2$ or $l=3$. Using
-these parameters, the ZMM  achieves almost perfect accuracy in
-computing the excess chemical potential, constant volume/pressure heat
-capacity, isothermal compressibility, thermal expansion coefficient,
-dielectric constant diffusion constant and viscosity. The order $l=2$
-performs better in reproducing the pressure than $l=3$ (10 v.s.~17~Bar), but
-worse in calculating the RDF (0.2\% error v.s.~almost negligible). Both of
-orders 2 and 3 are not sensitive to the splitting parameter up to 1.0~$\text{%
-nm}^{-1}$. Although further increasing the splitting parameter will push the
-accuracy of RDF in case $l=2 $ to as high as $l=3$, the pressure accuracy
-decreases (anti-damping effect), so that $\alpha >1$\ for $l=2$ or $l=3$ is
-not recommended. It should be noticed that the recommended parameters
-indicate $5$\% error (largest) in calculating the Kirkwood-G factor for a
-larger system ($L_{1}$ containing 13,824 molecules). If we seek more
-accuracy for the G factor, we should use a larger cut-off radius at the
-expense of the computational time. 
-% Further increasing the splitting paraemter
+these parameters, the ZMM achieves almost perfect accuracy in computing the
+excess chemical potential, constant volume/pressure heat capacity,
+isothermal compressibility, thermal expansion coefficient, dielectric
+constant diffusion constant and viscosity. The order $l=2$ performs better
+in reproducing the pressure than $l=3$ (10 v.s.~17~Bar), but worse in
+calculating the RDF (0.2\% error v.s.~almost negligible). Both of orders 2
+and 3 are not sensitive to the splitting parameter up to 1.0~$\text{nm}^{-1}$%
+. Although further increasing the splitting parameter will push the accuracy
+of RDF in case $l=2 $ to as high as $l=3$, the pressure accuracy decreases
+(anti-damping effect), so that $\alpha >1$\ for $l=2$ or $l=3$ is not
+recommended. It should be noticed that the recommended parameters indicate $%
+5 $\% error (largest) in calculating the Kirkwood-G factor for a larger
+system ($L_{1}$ containing 13,824 molecules). If we seek more accuracy for
+the G factor, we should use a larger cut-off radius at the expense of the
+computational time. % Further increasing the splitting paraemter
 % Optimal parameter value for the TIP3P system is thus $l=2,\alpha \leq 1$,
@@
 [ {\color{blue} COMMENT1: The first one is the accuracy comparison between
-the ZMM\ and a "default PME" that uses default protocol and parameters, e.g.,
-group-based cutoff scheme (OK?) and a short cutoff length(about 1 nm?) for
-the real part and a lower order spline and default grid spacing for the
+the ZMM\ and a "default PME" that uses default protocol and parameters,
+e.g., group-based cutoff scheme (OK?) and a short cutoff length(about 1 nm?)
+for the real part and a lower order spline and default grid spacing for the
 reciprocal part. Many peoples are not the specialist of the electrostatic
@@
 
+\section{The definition of statistical uncertainty of a physical quantity}
+\label{app:error}
+
+We denote the physical quantity under study by $\mathcal O$. In an MD simulation,
+a series of measurements of $\mathcal O$ is denoted by $\{O_0, O_1, \cdots, O_{M-1}\}$.
+Then the physical quantity can be estimated by:
+\begin{align}\label{eqn:sum-esti}
+  \mathcal O \approx \frac 1M \sum_{i=0}^M O_i
+\end{align}
+The twice the standard deviation of the right-hand-side of Eq.~\eqref{eqn:sum-esti}
+is defined to be the \emph{statistical uncertainty} (at 95\% confidence level) in computing
+the  physical quantity $\mathcal O$
+\begin{align}
+  \mathcal E_{O} = 2\sqrt{\Big\langle
+  \Big(
+  \frac 1M \sum_{i=0}^M O_i - 
+  \Big\langle \frac 1M \sum_{i=0}^M O_i \Big \rangle
+  \Big)^2
+  \Big \rangle}.
+\end{align}
+If the measurements are identical and independent random variables,
+then the statistical uncertainty is
+\begin{align}
+  \mathcal E_{O} = \frac{2}{\sqrt M} \sigma({O})
+\end{align}
+where $\sigma({O})$ is the standard deviation of measurements $O_i$.
+If the measurements are correlated, the statistical uncertainty is estimated
+by the block average method~\cite{janke2002statistical}.
+
 \section{Implementation of atom cut-off scheme in Gromacs}
@@
 The Gromacs code 4.6 does not directly support the atomistic cut-off scheme, 
-{\color{blue}which is recommended in the ZMM, in }using tabulated
+{which is recommended in the ZMM, in }using tabulated
 electrostatic interaction. The atom cut-off scheme can be implemented by
 using the default \textquotedblleft \texttt{Group}\textquotedblright\
-neighbor searching method, while setting the radius of neighbor list
-\textquotedblleft \texttt{rlist}\textquotedblright\ 0.3~nm larger than the
-cut-off radius, which is the maximum of the electrostatic cut-off
-\textquotedblleft \texttt{rcoulomb}\textquotedblright\ and the van der Waals
-cut-off \textquotedblleft \texttt{rvdw}\textquotedblright . Due to the
-buffering region that is of thickness 0.3~nm, the atom cut-off scheme in
-Gromacs is in general \recheck{twice} expensive \recheck{in computing the electrostatic interaction} as the group cut-off scheme.
-\recheck{It should be pointed out that this implementation is not optimal,
-  when the gromacs build-in atom cut-off scheme supports the tablulated potential, we expect better performance of ZMM.}
-% {%
-% \color{blue}How much? (just my interest)}
+neighbor searching method, {% {%
+% How much? (just my interest)}
+{by }}setting the radius of neighbor list \textquotedblleft 
+\texttt{rlist}\textquotedblright\ 0.3~nm larger than the cut-off radius,
+which is the maximum of the electrostatic cut-off \textquotedblleft \texttt{%
+rcoulomb}\textquotedblright\ and the van der Waals cut-off \textquotedblleft 
+\texttt{rvdw}\textquotedblright . {The size of the thickness
+0.3~nm of the buffering region was determined from the molecular size,
+average speed of molecules, and the neighbor-searching timing. Due to this buffering region}, the atom cut-off scheme in
+Gromacs is in general { twice} expensive { in
+computing the electrostatic interaction} as the group cut-off scheme. {%
+ It should be pointed out that this implementation is not
+optimal, {but an effective realization of atom cut-off scheme in
+the environment of the \textquotedblleft \texttt{Group}\textquotedblright\
+neighbor searching. If} the gromacs build-in atom cut-off scheme supports
+the tabulated potential, we expect better performance of ZMM. % {%
+% How much? (just my interest)}
+}
 
@@
 where $V$ is the volume of the system. The presented pressures were computed
-from NVT simulations of $L_{0}$.
+from NVT simulations of $L_{0}$. The dispersion correction~\cite{frenkel2001understanding} was
+added to correct the value.
 
@@
 We investigate the convergence of the integral of the auto-correlation
-function w.r.t.~time: 
+function w.r.t.~time $t$: 
 \begin{equation*}
-I_{\eta }(T)=\frac{V}{k_{B}T}\int_{0}^{T}\langle P_{\alpha \beta
-}(0)P_{\alpha \beta }(t)\rangle \,dt.
+I_{\eta }(t)=\frac{V}{k_{B}T}\int_{0}^{t}\langle P_{\alpha \beta
+}(0)P_{\alpha \beta }(t^{\prime })\rangle \,dt^{\prime }.
 \end{equation*}%
@@
 
-{\color{blue} Question1: I see that the statistical uncertainty is twice of
-the standard deviation of time series.\ Let $\{A(x(t),p(t))\}_{t\in \Lambda }
-${\ be time series of physical quantity }$A(x,p)${. Then I want to confirm
-how you defined the average and the standard deviation. (i) Are they for }$%
-\{A(x(t),p(t))\}_{t\in \Lambda }${\ itself? (ii) }Or are they {for }$\left\{ 
-\frac{1}{t}\int_{0}^{t}A(x(s),p(s))ds\right\} _{t\in \Lambda }${? }}
-
-{\color{blue}Maybe (ii) is correct. But "100~Bar" in the description "the
-fluctuation (measured by standard deviation) of the pressure is roughly
-100~Bar" should come from (i). If so, I proposed the presentation of the
-trajectory of pressures $\{P(x(t),p(t))\}_{t\in \Lambda }$ in SI.}
-
-{\color{blue}Question2 (this is just from my interest): When you did the ZMM
-NTP with P-R method, how was the cell shape? You obtained the good density,
-but how about the cell deformation? Was it keep almost the cubic structure?}
-\recheck{The box is kept cubic by resizing isotropically in x, y and z directions.}
+%{\color{blue} Question1: I see that the statistical uncertainty is twice of
+%the standard deviation of time series.\ Let $\{A(x(t),p(t))\}_{t\in \Lambda }
+%${\ be time series of physical quantity }$A(x,p)${. Then I want to confirm
+%how you defined the average and the standard deviation. (i) Are they for }$%
+%\{A(x(t),p(t))\}_{t\in \Lambda }${\ itself? (ii) }Or are they {for }$\left\{ 
+%\frac{1}{t}\int_{0}^{t}A(x(s),p(s))ds\right\} _{t\in \Lambda }${? }}
+%
+%{\color{blue}Maybe (ii) is correct. But "100~Bar" in the description "the
+%fluctuation (measured by standard deviation) of the pressure is roughly
+%100~Bar" should come from (i). If so, I proposed the presentation of the
+%trajectory of pressures $\{P(x(t),p(t))\}_{t\in \Lambda }$ in SI.}
+%
+%{\color{blue}Question2 (this is just from my interest): When you did the ZMM
+%NTP with P-R method, how was the cell shape? You obtained the good density,
+%but how about the cell deformation? Was it keep almost the cubic structure?} 
+%{\color{red} The box is kept cubic by resizing isotropically in x, y and z
+%directions.}
 

### 2015-01-26 writedown/period.noneq.msm/submit.jctc.reply/paper.tex
add source of the paper

--- 2014-11-06 writedown/period.noneq.msm/submit.jctc/paper.tex
@@
 \affiliation{CAEP Software Center for High Performance Numerical Simulation, Beijing, China}
-\alsoaffiliation{Zuse Institute Berlin, Germany}
+\alsoaffiliation{Zuse Institute Berlin (ZIB), Germany}
 \author{Christof Sch\"utte}
-\email{Christof.Schuette@fu-berlin.de}
+\email{schuette@zib.de}
 \affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
-\alsoaffiliation{Zuse Institute Berlin, Germany}
+\alsoaffiliation{Zuse Institute Berlin (ZIB), Germany}
 
@@
 \begin{abstract}
-Recent years have seen an increased interest in non-equilibrium molecular dynamics (NEMD) simulations, especially for molecular systems with periodic forcing by external fields, e.g., in the context of studying  effects of electromagnetic radiation on the human body tissue.
-Lately, an NEMD methods with local thermostating has been proposed that allows for studying
+Recent years have seen an increased interest in non-equilibrium molecular dynamics (NEMD) simulations, especially for molecular systems with periodic forcing by external fields, e.g., in the context of studying the  effects of electromagnetic radiation on human body tissues.
+Lately, and NEMD method with local thermostating has been proposed; that allows the study of
 non-equilibrium processes in a statistically reliable and thermodynamically consistent way.
 In this article, we demonstrate how to construct Markov State Models (MSMs) for such NEMD simulations.
-MSM building has been well-established for systems in equilibrium where MSMs with just a few (macro-)states allow for accurate reproduction of the essential kinetics of the molecular system under consideration.
-Non-equilibrium MSMs have been lacking so far.
-The article presents how to construct such MSMs and illustrates their validity and usefulness for the case of conformation dynamics of alanine dipeptide in an external electric field.
+MSM building is well-established for systems in equilibrium, where MSMs with only a few (macro-)states allow for accurate reproduction of the essential kinetics of the molecular system under consideration.
+Non-equilibrium MSMs have not been established yet.
+This article presents a method for construction of such MSMs and illustrates their validity and usefulness for the case of conformation dynamics of alanine dipeptide in an external electric field.
 \\
@@
 interest recently.  For example, the potential effects of electromagnetic
-radiation on the human body tissue (e.g.~DNA, protein, and membrane)  has been extensively
-investigated in a vast number of articles, with the following list just representing an incomplete selection~\cite{bohr2000microwave, bohr2000microwave-1, dePomerai2000cell,
+radiation on  human body tissues (e.g.,~DNA, protein, and membrane)  have been extensively
+investigated in a vast number of articles, with the following list  representing an incomplete selection~\cite{bohr2000microwave, bohr2000microwave-1, dePomerai2000cell,
   dePomerai2003microwave, mancinelli2004non, inskip2001cellular, bekard2013electric, budi2005electric,
   budi2007effect, budi2008comparative, astrakas2012structural,
-  damm2012can, english2009nonequilibrium, solomentsev2012effects}.  Molecular dynamics (MD) simulations have proved particularly useful for understanding
-the response of biomolecular conformations to external fields because of their ability to  resolve molecular
+  damm2012can, english2009nonequilibrium, solomentsev2012effects}.  Molecular dynamics (MD) simulations have proven particularly useful for understanding
+the response of biomolecular conformations to external fields, because of their ability to  resolve molecular
 details that sometimes cannot be resolved in experiments. Only
@@
 non-equilibrium processes in a statistically reliable and thermodynamically consistent way. 
-Despite the significance of the non-equilibrium phenomena, the
+Despite the significance of the non-equilibrium phenomena, 
 analysis of the non-equilibrium MD simulations mainly follows standard approaches, and reliable tools for quantitative description of
-the essential conformational dynamics of the molecular system under external forcing are still lacking.
+the essential conformational dynamics of the molecular system under external forcing remain unavailable.
 
@@
 Despite their many advantages, MD simulations have severe limitations.
-For example, one has to assume that the underlying force fields are appropriately describing the internal and external molecular interactions, and the maximal possible simulation length often is shorter than the timescale of interest.
+For example, one has to assume that the underlying force fields  describe the internal and external molecular interactions appropriately, and the maximal possible simulation length often is shorter than the timescale of interest.
 This article is mainly concerned with circumventing the latter obstacle by introducing non-equilibrium Markov State Models. Markov State Models
-(MSM) have been well developed over the
-past decade in theory~\cite{A19-31,prinz2011markov} and applications (see the recent book~\cite{A19-1} for an overview), and software implementations~\cite{A19-49, MSMBuilder}, but for systems under equilibrium conditions only!
-The principal idea of equilibrium MSMs is to approximate the original high-dimensional MD system by
-a reduced Markovian dynamics over a finite number of (macro-)states. These (macro-)states
+(MSM) have been  developed thoroughly over the
+past decade in theory~\cite{A19-31,prinz2011markov} and applications (see the recent book~\cite{A19-1} for an overview), and software implementations~\cite{A19-49, MSMBuilder}, but for systems under equilibrium conditions only.
+The main concept underlying equilibrium MSMs is to approximate the original high-dimensional MD system 
+using reduced Markovian dynamics over a finite number of (macro-)states. These (macro-)states
 have to be identified with the dominant metastable sets, in the sense that
-typical MD trajectories stay in the vicinity of a metastable set substantially longer than
-the systems needs for a transition to another such state~\cite{A19-31,schuette2011markov}.
-In this case, the metastable sets are the main conformations of the molecular system under consideration which, often enough, are given by the main wells in the energy landscape.
-It has been shown that for molecular systems exhibiting such metastable sets the Markovian dynamics given by an MSM allows very close approximation of the longest relaxation processes of the underlying molecular system, at least under equilibrium conditions~\cite{sarich2010approximation,Eigenvalues}.
-Moreover, it has been demonstrated that in such cases MSM building requires short MD trajectories only, much shorter than the timescales of interest~\cite{PNAS09,kohlhoff2014cloud}.  
-Thus, MSM building often allows to study the dynamical behavior on long timescales without requiring MD trajectories of comparable length.
-Moreover, MSMs are utilized for understanding very long MD simulations: Extracting the essential structures and dynamical properties from long MD runs is
-becoming increasingly difficult as the system size and trajectory length grow; MSMs have been used to construct kinetic fingerprints from MD simulations~\cite{A19-39} that help understanding the essential dynamics and in comparison with experiments~\cite{PrinzKellerNoe_PCCP11_Perspective}.
+typical MD trajectories remain close to a metastable set substantially longer than
+they need for a transition to another such state~\cite{A19-31,schuette2011markov}.
+In this case, the metastable sets are the main conformations of the molecular system under consideration, which, often enough, are given by the main wells in the energy landscape.
+It has been shown that for molecular systems exhibiting such metastable sets, the Markovian dynamics given by an MSM allows very close approximation of the longest relaxation processes of the underlying molecular system, at least under equilibrium conditions~\cite{sarich2010approximation,Eigenvalues}.
+Moreover, it has been demonstrated that, in such cases, MSM building requires short MD trajectories only, which are much shorter than the timescales of interest~\cite{PNAS09,kohlhoff2014cloud}.  
+Thus, MSM building often allows the study of dynamic behavior on long timescales without requiring MD trajectories of comparable length.
+Moreover, MSMs are utilized for understanding very long MD simulations. Extracting the essential structures and dynamic properties from long MD runs is
+becoming increasingly difficult as the system size and trajectory length grow; MSMs have been used to construct kinetic fingerprints from MD simulations~\cite{A19-39} which facilitates understanding of essential dynamics and comparison with experimental data~\cite{PrinzKellerNoe_PCCP11_Perspective}.
 
@@
 To the knowledge of the authors this work is the first attempt of using MSMs for analyzing non-equilibrium systems under periodic external forcing.
-More precisely, we will demonstrate how to use MSMs for investigate the conformational dynamics of a peptide (alanine dipeptide) under an oscillating electric field (EF).
-To this end, we will show how to generalize Markov state modeling to periodic non-equilibrium conditions where one cannot assume reversibility of the dynamics as it is mostly done in the literature on MSM building.
+More precisely, we will demonstrate how to use MSMs to investigate the conformational dynamics of a peptide (alanine dipeptide) under an oscillating electric field (EF).
+To this end, we will show how to generalize Markov state modeling to periodic non-equilibrium conditions, where one cannot assume reversibility of the dynamics as is most often case in the literature on MSM building.
 
 The outline of the article is as follows: 
-In Sec.~\ref{sec:disc}, we discuss the temporal and spatial
+In Section~\ref{sec:disc}, we discuss the temporal and spatial
 discretizations needed to construct an MSM. We consider spatial discretization
@@
 is discretized utilizing Floquet's theorem. This results in a time-homogeneous, 
-but not necessarily reversible, that is, irreversible Markov process. Since  full spatial partition does not make any sense
-for high-dimensional systems, we next show how to construct a \emph{few-state} MSM based on milestoning~\cite{schuette2011markov,A19-29} of the discretized irreversible Markov process in Sec.~\ref{sec:build-msm}.
-The validity of the discretizations and the resulting MSM is checked in Sec.~\ref{sec:alanine}
+but not necessarily reversible, that is, irreversible Markov process. Since  full spatial partition is not rational
+for high-dimensional systems, we next show how to construct a \emph{few-states} MSM, based on milestoning~\cite{schuette2011markov,A19-29} of the discretized irreversible Markov process in Section~\ref{sec:build-msm}.
+The validity of the discretizations and the resulting MSM is checked in Section~\ref{sec:alanine}
 by comparing the kinetic fingerprints given by the MSM to brute force
 non-equilibrium MD simulations of alanine dipeptide under oscillating EF.
-The findings are summarized in Sec.~\ref{sec:conclusion} including a chart presenting
+The findings are summarized in Section~\ref{sec:conclusion}, which includes a chart presenting
 the workflow of MSM building for non-equilibrium systems, and a list of open questions.
@@
 \label{sec:disc}
-We consider diffusive molecular dynamics in an energy landscape $V$ driven by the time-dependent external driving force $E(t)D(x_t)$ with the
+We consider diffusive molecular dynamics in an energy landscape $V$, driven by the time-dependent external driving force $E(t)D(x_t)$, with the
 $T$-periodic external field $E(t)$:
@@
 where $x_t\in\Omega$ denotes the state of the molecular system at time $t$ in state space $\Omega$, $\vect w_t$ denotes standard $n$-dimensional Brownian motion, and $\beta$ the inverse temperature,
-i.e.~$\beta = 1/(k_B\mathcal T)$.
-Thermostatted Hamiltonain or Langevin dynamics can be treated in the same way as explained herein, so for sake of simplicity we focus on the discussion of diffusive dynamics.
+i.e.,~$\beta = 1/(k_B\mathcal T)$.
+Thermostatted Hamiltonian or Langevin dynamics can be treated in the same way as explained herein, so for the sake of simplicity, we focus on the discussion of diffusive dynamics.
 The propagation of probability
 densities $\rho=\rho(\vect x,t)$ based on this kind of dynamics in the sense
-of $\rho(\vect x,t)dx=\prob[\vect x_t\in [\vect x,\vect x+d\vect x)]$ is governed by
-Fokker-Planck equation:
+of $\rho(\vect x,t)dx=\prob[\vect x_t\in [\vect x,\vect x+d\vect x)]$, is governed by
+the Fokker-Planck equation:
 \begin{align}
@@
 where $\Delta_{\vect x}$ denotes the Laplacian operator and $\nabla_{\vect x}$
-the nabla-operator wrt to $\vect x$. 
+the nabla-operator with respect to to $\vect x$. 
 The periodicity of the external driving force induces the periodicity of the generator,
-i.e.~$\ml(t) = \ml(t+T)$.
+i.e.,~$\ml(t) = \ml(t+T)$.
 
@@
 is discretized, resulting in a time-inhomogeneous Markov jump process in state
-space $S = \{1, \cdots, N\}$ with time-dependent rate
+space $S = \{1, \cdots, N\}$, with a time-dependent rate
 matrix $\vect L(t) \in \mathbb R^{N\times N}$ satisfying
@@
 for all real time $t\geq 0$.
-Moreover, the rate matrix $L$ has the form $\vect L(t)=\vect L_0+E(t)\vect L_1$
-where $E(t)$ is periodic with period $T>0$.
-In analogy to \eqref{eq:disc-fp}, the Markov jump process generated by
+Moreover, the rate matrix $L$ has the form $\vect L(t)=\vect L_0+E(t)\vect L_1$,
+where $E(t)$ is periodic, with period $T>0$.
+In analogy to~\eqref{eq:disc-fp}, the Markov jump process generated by
 $\vect L(t)$ transports probability distributions according to the associated Master equation
@@
   \label{eq:disc-master}
-  \frac{d\vect p(t)}{dt} = \vect L^{\top}(t)\cdot \vect p(t)
-\end{align}
-where $\vect L^{\top}(t)$ denotes the matrix transpose of $\vect L(t)$, $\vect p(t)$ is an $N$-vector denoting the probability distribution on $S$ at time $t$, $p(i,t)$, for example, the probability to be in state $i$ (which corresponds to set $\Omega_i$) at time $t$.
-As usual the properties (\ref{eq:disc-4}) and (\ref{eq:disc-5}) of
+  \frac{d\vect p(t)}{dt} = \vect L^{\top}(t)\cdot \vect p(t),
+\end{align}
+where $\vect L^{\top}(t)$ denotes the matrix transpose of $\vect L(t)$.
+$\vect p(t)$ is an $N$-vector denoting the probability distribution on $S$ at time $t$; $p(i,t)$, for example, is the probability of being in state $i$ (which corresponds to set $\Omega_i$) at time $t$.
+As usual,  properties (\ref{eq:disc-4}) and (\ref{eq:disc-5}) of
 $\vect L(t)$ guarantee that the total probability mass is conserved,
-i.e., if $p(i,0)\ge 0$ componentwise, then $p(i,t)\ge 0$ and $\sum_i
+i.e., if $p(i,0)\ge 0$ component-wise, then $p(i,t)\ge 0$ and $\sum_i
 p(i,t) = \sum_ip(i,0)$.
@@
 % periodic.
-The temporal evolution of the probability distribution $\vect p(t)$ can be formally written
+The temporal evolution of the probability distribution $\vect p(t)$ can be formally written as
 \begin{align}  \label{eq:disc-8}
@@
 that is, $\myphi^{\top}(t)$ is a
-stochastic matrix satisfying $\myphi^{\top}(t)\vect e=\vect e$
+stochastic matrix satisfying $\myphi^{\top}(t)\vect e=\vect e$,
 with $\vect e=(1,\ldots,1)^{\top}\in \mathbb R^N$.
@@
 and $\vect L(t)$, respectively, can be assumed to provide an arbitrarily fine
-partition of the original state space; then the transport properties
+partitioning of the original state space; then, the transport properties
 of $\vect L(t)$ are almost perfect approximations of the transport properties
-of $\ml(t)$, in particular the approximation $p(i,t)\approx \prob(x_t\in \Omega_i)$ is almost perfect.
+of $\ml(t)$, in particular, the approximation $p(i,t)\approx \prob(x_t\in \Omega_i)$ is almost perfect.
 
@@
 
-As an effect of the periodicity of $\vect L(t)$ the propagator $\myphi(t+T)$
+As an effect of the periodicity of $\vect L(t)$, the propagator $\myphi(t+T)$
 satisfies
@@
 \]
-When we consider this identity column-wise and use the propagator property of $\myphi(t)$ we get $\myphi(t+T)=\vect Y(t)=\myphi(t)\myphi(T)$.
-As a consequence of (\ref{compo-1}) we get for all integers $m=0,1,2,\ldots$ that
+When we consider this identity column-wise and use the propagator property of $\myphi(t)$, we get $\myphi(t+T)=\vect Y(t)=\myphi(t)\myphi(T)$.
+As a consequence of (\ref{compo-1}), we get for all integers $m=0,1,2,\ldots$ that
 \begin{equation}\label{compo-2}
@@
 This is known as the Floquet theorem~\cite{floquet1883equations}.
-In particular we get the long-term evolution of the propagator:
+In particular, we get the long-term evolution of the propagator:
 \begin{align}
@@
 \end{align}
-where $\myphi^m(T)$ denotes the $m$th power of $\myphi(T)$. Thus, for the probability at integral periods we have
+where $\myphi^m(T)$ denotes the $m$th power of $\myphi(T)$. Thus, for the probability at integral periods, we have
 \begin{align}
@@
 reversible) Markov jump process $\tilde X_{m} = X_{mT}, \ m\in\mathbb
-N$, which is generated by transition matrix
+N$, which is generated by the transition matrix
 \begin{equation}\label{P}
@@
 \end{equation}
-We prefer to consider the discrete-time process $\tilde X_{m}$ instead of the time-continuous process $X_t$
+We prefer to consider the discrete-time process $\tilde X_{m}$ instead of the time-continuous process $X_t$,
 because the powerful theories and
 computational tools for time-homogeneous Markov processes can be directly applied.
-It worth noting that many of these tools require the transition matrix $P$ to satisfy the detailed balance condition.
-The computations in the Appendix~\ref{sec:app-revs} show that $P$ will in general \emph{not} satisfy this condition; in fact  the deviation {from} reversibility can be estimated from the work of the periodic driving does to the system.
+It is worth noting that many of these tools require the transition matrix $P$ to satisfy the detailed balance condition.
+The computations in Appendix~\ref{sec:app-revs} show that $P$ will in general \emph{not} satisfy this condition; in fact,  the deviation {from} reversibility can be estimated from the work of the periodic driving does to the system.
 There is no doubt that information within one period is lost by using this temporal
-discretization, however, information regarding the long-term behavior of the system on timescales
-much longer than the period will be perfectly described because of $\tilde X_{m} = X_{mT}\approx x_{mT}$ whenever our spatial discretization is fine enough.
+discretization; however, information regarding the long-term behavior of the system on timescales
+much longer than the period will be perfectly described, because of $\tilde X_{m} = X_{mT}\approx x_{mT}$ whenever our spatial discretization is sufficiently fine.
 At the same time,
@@
 than the brute force simulations of NEMD, which implies lower
-statistically uncertainty in calculating the observables of interest.
+statistical uncertainty in calculating the observables of interest.
 
@@
 satisfies $|\lambda|\le 1$. Furthermore $\lambda=1$ is an
-eigenvalue with right eigenvector $\vect e=(1,\ldots,1)^{\top}$ and a left eigenvector $\mymu$
+eigenvalue with a right eigenvector $\vect e=(1,\ldots,1)^{\top}$ and a left eigenvector $\mymu$
 satisfying
 $\mymu^{\top}P=\mymu^{\top}$.
-From now on, we assume $P$ to be irreducible and aperiodic such that the Perron-Frobenius theorem holds, so the eigenvector corresponding to the eigenvalue $\lambda=1$ is  non-negative componentwise, and unique (up to normalization $\sum_i\mu(i)=1$).
-In this case $\mymu$ is the stationary measure in the sense that
+From now on, we assume $P$ to be irreducible and aperiodic, such that the Perron-Frobenius theorem holds; thus, the eigenvector corresponding to the eigenvalue $\lambda=1$ is  non-negative component-wise, and unique (up to normalization $\sum_i\mu(i)=1$).
+In this case, $\mymu$ is the stationary measure, in the sense that
 $
@@
 % due to the discretization in both the spacial and temporal directions.
-% In the numercal example in Sec.~\ref{sec:alanine}, we
+% In the numercal example in Section~\ref{sec:alanine}, we
 % compute the
@@
 % \subsection{Building the Markov State Model from the Floquet transition matrix}
-If the discretization cells $\Omega_i$, $i=1,\ldots,N$ form a fine
+If the discretization cells $\Omega_i$, $i=1,\ldots,N$, form a fine
 partition of the molecular state space, the Markov chain defined via
 the transition matrix $P$
- is discrete in time, but in space it still is a fine-scale description of the transport properties of the
-dynamics with a very large number $N$ of states.  Now we want to coarse our description much further by
+ is discrete in time, but in space it remains a fine-scale description of the transport properties of the
+dynamics with a very large number ($N$) of states.  Now we want to coarse our description much further by
 constructing a Markov State Model (MSM) for $\vect P$ with $K\ll N$
-\emph{macrostates} that should be the metastable states of the system: The resulting $K\times K$ MSM transition matrix $\hat{\vect P}$
-then defines the coarse grained long term kinetics that shall
+\emph{macrostates}, which would be the metastable states of the system. The resulting $K\times K$ MSM transition matrix $\hat{\vect P}$
+then defines the coarse-grained long-term kinetics that shall
 approximate the original long term kinetics well. 
-The idea behind MSM building is that given the molecular system under consideration exhibits metastable conformations then it is usually possible to construct a
+The idea behind MSM building is that, given that the molecular system under consideration exhibits metastable conformations,  it is usually possible to construct a
 relatively small number of discrete sets --the metastable sets that form the so-called macrostates-- that
 correctly describe the slow  dynamics, and 
-in each set the fast dynamics relaxes on some timescales significantly shorter than the metastable timescales.
-Then if the MSM dynamics reproduces the slow timescales and the corresponding transitions
+in each set the fast dynamics relaxes on some timescales that are significantly shorter than the metastable timescales.
+Then, if the MSM dynamics reproduces the slow timescales and the corresponding transitions
 of the original dynamics~\eqref{eq:disc-1},
@@
 
-MSM building has been attracted a lot of attention recently, and theory  \cite{A19-31} as well as algorithms \cite{A19-1}, applications (see e.g.
-\cite{A19-26,PNAS09} for two of hundreds of articles) and software \cite{A19-49, MSMBuilder} have been developed to quite an extend.
+MSM building has attracted much attention recently, and extensive theories~\cite{A19-31} as well as algorithms \cite{A19-1}, applications (see e.g.
+\cite{A19-26,PNAS09} for two of hundreds of articles), and software \cite{A19-49, MSMBuilder} have been developed.
 However,
 by far most of the literature is related to building \emph{standard} MSMs for equilibrium MD.
-In standard MSM also the transition region has to be discretized, a feature that often forces the user to incorporate more macrostates than essentially needed to approximate the long-term kinetics.
-In Ref.~\cite{sarich2010approximation, A19-31,schuette2011markov,BucheteHummer} it has been shown how to construct \emph{non-standard} MSM that avoid this problem for equilibrium MD, i.e., if $\vect P$ satisfies the detailed balance
-condition: (1) Identify the cores of the metastable sets of the
+In standard MSM, the transition region also has to be discretized, a feature that often forces the user to incorporate more macrostates than essentially needed to approximate the long-term kinetics.
+In Ref.~\cite{sarich2010approximation, A19-31,schuette2011markov,BucheteHummer} it is shown how to construct a \emph{non-standard} MSM in a way that avoids this problem for equilibrium MD, i.e., if $\vect P$ satisfies the detailed balance
+condition: (1) identify the cores of the metastable sets of the
 dynamics, (2) use them as milestones to construct an MSM in which the
@@
 
-However, since we cannot assume $P$ to satisfy detailed balance, we
-instead follow the approach to non-standard MSMs recently proposed in Ref.~\cite{sarich2014utilizing} which allows to identify the metastable core sets for the
+However, since we cannot assume $P$ to satisfy such a detailed balance, we
+instead follow the approach for non-standard MSM construction recently proposed in Ref.~\cite{sarich2014utilizing}, which allows  identification of the metastable core sets for the
 non-reversible transition matrix $P$. Assume that this approach leads
 to the $K$ core sets $C_1,\ldots, C_K\subset S$ that are appropriate metastable sets. 
-Following~\cite{A19-31,schuette2011markov} the process $(\tilde X_m)$ associated with $P$ is coarse grained into the so-called milestone process $(\hat{X}_m)$ in the following way: 
+Following~\cite{A19-31,schuette2011markov}, the process $(\tilde X_m)$ associated with $P$ is coarse-grained into the so-called milestone process $(\hat{X}_m)$ in the following way: 
 \begin{itemize}
-\item $\hat{X}_m$ just has $K$ states associated with the sets $C_j$, $j=1,\ldots,K$. 
-\item The sequence of random variables $(\hat{X}_m)$ is defined via the sequence $(\tilde X_m)$, i.e., trajectories of $(\tilde X_m)$ induce trajectories of $(\hat{X}_m)$: We set $\hat{X}_m=j$ if the last core set that the process $(\tilde X_m)$ entered prior to or at time $m$ has been the core set $C_j$.
+\item $\hat{X}_m$ only has $K$ states associated with the sets $C_j$, $j=1,\ldots,K$. 
+\item The sequence of random variables $(\hat{X}_m)$ is defined via the sequence $(\tilde X_m)$, i.e., trajectories of $(\tilde X_m)$ induce trajectories of $(\hat{X}_m)$.
+We set $\hat{X}_m=j$ if the last core set that the process $(\tilde X_m)$ entered prior to or at time $m$ is the core set $C_j$.
 \end{itemize}
-Now consider an arbitrary infinitely long trajectory of $(\tilde X_m)$.
-Because of ergodicity we know that the states in this trajectory will be distributed due to the quasi-stationary distribution $\mu$.
-Based on such an infinitely long trajectory we can consider the probability $q_j^\bwd(i)$ that conditioned on $\tilde X_m=i$ the last core set hit has been $C_j$.
+Now, consider an arbitrary infinitely long trajectory of $(\tilde X_m)$.
+Because of ergodicity, we know that the states in this trajectory will be distributed according to the quasi-stationary distribution $\mu$.
+Based on such an infinitely long trajectory, we can consider the probability $q_j^\bwd(i)$ that conditioned on $\tilde X_m=i$ the last core set hit has been $C_j$.
 This function is called the backward committor of $(\tilde X_m)$ associated with the set $C_j$ and is associated with the milestone process via
@@
 %  or not.}
-From the last equation we get that the stationary distribution of the milestone process is given by
+From the last equation, we get that the stationary distribution of the milestone process is given by
 \begin{align}  
@@
 
-Following \cite{discreteTPT} one also has to consider the forward committor $q^\fwd_j(i)$ identical to the probability  that conditioned on $\tilde X_m=i$ the next core set to be hit will be $C_j$.
+Following \cite{discreteTPT}, one also has to consider the forward committor $q^\fwd_j(i)$ identical to the probability  that conditioned on $\tilde X_m=i$, the next core set to be hit will be $C_j$.
 The forward and backward committors $q^\fwd_j$ and $q^\bwd_j$  for each core set $C_j$ can be computed from $P$ by solving the linear equations \cite{discreteTPT}
@@
 \end{equation}
-Then Following
+Then, following
 Ref.~\cite{djurdjevac2010markov}, Thm.~3.1, 
@@
 $\langle u,v \rangle_\mu=\sum_{i\in S} u(i) v(i) \mu(i)$. 
-In general the milestone process need not be a Markov process.
+In general, the milestone process need not be a Markov process.
 The results in \cite{A19-31,sarich2014utilizing} show, however, that it is an approximate Markov process as long as the core sets are proper metastable sets, i.e., if the typical timescale on which $(X_m)$ leaves $C$ is much smaller than the typical expected hitting times between the core sets.
@@
 \textbf{Remark 1:} Our definition of the milestoning process in terms of the process $(\tilde X_m)$ generated by $P$ guarantees that we can directly compute $\hat{P}$ via (\ref{hatP_prob})  from trajectories of $(\tilde X_m)$ without computing the committor functions.
-This is of importance if the spatial discretization underlying $(\tilde X_m)$ is fine enough, because then the kinetics of $(\tilde X_m)$
-approximates the original kinetics of $(x_{mT})$ so that we can directly compute   $\hat{P}$ via (\ref{hatP_prob})  from NEMD trajectories without computing $P$ first (which substantially simplified the MSM building if the core sets are already known).
+This is of importance if the spatial discretization underlying $(\tilde X_m)$ is fine enough, because the kinetics of $(\tilde X_m)$
+then approximates the original kinetics of $(x_{mT})$, so that we can directly compute   $\hat{P}$ via (\ref{hatP_prob})  from NEMD trajectories without computing $P$ first (which substantially simplifies MSM building if the core sets are already known).
 
 \textbf{Remark 2:}
-Following \cite{A19-31} we can also define another pair of stochastic MSM matrices: 
+Following \cite{A19-31}, we can also define another pair of stochastic MSM matrices: 
 \begin{align}\label{eq:msm-ht-1}
@@
 \]
-That can be seen by means of direct computation: For the off-diagonal entries we have
+That can be seen by means of direct computation: For the off-diagonal entries, we have
 \begin{align}\label{eq:msm-tmp26}
@@
 $\hat T_{jj} - \hat M_{jj} + 1 = \hat P_{jj}$ for the diagonal entries.
-Furthermore, as shown in the Appendix~\ref{sec:app-prove}, $\hat{T}$ as well as $\hat{M}$ can be computed from trajectories without need to have the committors.
-The importance of the pair $\hat{T}$ and $\hat{M}$ for MSM building comes from the following observation: The main NEMD relaxation timescales are given by the dominant eigenvalues of $P$ \cite{A19-31, A19-1}.
+Furthermore, as shown in the Appendix~\ref{sec:app-prove}, $\hat{T}$ as well as $\hat{M}$ can be computed from trajectories without requiring committors.
+The importance of the pair $\hat{T}$ and $\hat{M}$ for MSM building comes from the following observation: the main NEMD relaxation timescales are given by the dominant eigenvalues of $P$ \cite{A19-31, A19-1}.
 These dominant eigenvalues can be approximated by discretizing the related eigenvalue problem $Pu=\lambda u$ by means of a Galerkin approximation with the finite dimensional ansatz space 
-spanned by the forward committors $q^+_j$, $j=1,\ldots,K$ together  with the finite dimensional test function space spanned by the backward committors $q^-_j$, $j=1,\ldots,K$ (test functions multiplied from the left by the inner product $\langle\cdot,\cdot\rangle_\mu$).
-The thus discretize eigenproblem takes the form  of a generalized eigenproblem
+spanned by the forward committors $q^+_j$, $j=1,\ldots,K$, together  with the finite dimensional test function space spanned by the backward committors $q^-_j$, $j=1,\ldots,K$ (test functions multiplied from the left by the inner product $\langle\cdot,\cdot\rangle_\mu$).
+The thus discretized eigenproblem takes the form  of a generalized eigenproblem
 \begin{align}
@@
 \end{align}
-For the reversible case it is known that its $k$ eigenvalues $\hat{\lambda}$ are very good approximation of the dominant eigenvalues $\lambda$ of the original problem if the core sets are proper metastable sets~\cite{Eigenvalues}.
-Whether this is true for the non-reversible case is not known yet, but if the deviation from reversibility is weak and the dominant eigenvalues of $P$ are real-valued then the results should hold analogously, see~\cite{A19-31}, Thm.~4.19.
-
-If all of its entries are positive such that it is a stochastic matrix, $\hat{M}^{-1}\hat{T}$ thus can also be taken as MSM transition matrices.
-In the case of $\hat{M}^{-1}\hat{T}$ the MSM modeling error results from Galerkin discretization, while the MSM modeling error of $\hat{P}$ results from ignoring the potential non-Markovianity of $\hat{X}_m$.
+For the reversible case, it is known that the $k$ eigenvalues $\hat{\lambda}$ are very good approximations of the dominant eigenvalues $\lambda$ of the original problem, if the core sets are proper metastable sets~\cite{Eigenvalues}.
+Whether this is true for the non-reversible case is not yet known, but if the deviation from reversibility is weak and the dominant eigenvalues of $P$ are real-valued, then the results should hold analogously, see~\cite{A19-31} Thm.~4.19.
+
+If all of its entries are positive, such that it is a stochastic matrix, $\hat{M}^{-1}\hat{T}$ thus can also be taken as MSM transition matrices.
+In the case of $\hat{M}^{-1}\hat{T}$, the MSM modeling error results from Galerkin discretization, while the MSM modeling error of $\hat{P}$ results from ignoring the potential non-Markovianity of $\hat{X}_m$.
 
@@
 We know that --in theory-- whenever the spatial discretization is fine enough, the Markov jump
-process $X_t$ associated with the Master equation \eqref{eq:disc-master} is a good approximation to the original
+process $X_t$ associated with the Master equation \eqref{eq:disc-master} is a good approximation of the original
 MD process $x_t$ governed by \eqref{eq:disc-1}.  In practice, however, it is difficult to predict
-how many discrete sets we need to be fine enough. Moreover, since the
-total dimension of $x_t$ is $3N_{\textrm{atom}}$ ($N_{\textrm{atom}}$ being the number of atoms), it is prohibitive to do a really fine discretization
+how many discrete sets we need for sufficiently fine discretization. Moreover, since the
+total dimension of $x_t$ is $3N_{\textrm{atom}}$ ($N_{\textrm{atom}}$ being the number of atoms), it is prohibitive to perform an extensively discretization
 over all degrees of freedom for most systems of practical interest.
@@
 % within the discretized sets.
-However, it is difficult to give a general answer in prior regarding
-how to choose the collect variables and how fine their discretization should be.
+However, it is difficult to give a general answer \emph{a priori} regarding
+how to choose the collective variables and how fine their discretization should be.
 For large or high dimensional systems, these questions usually become non-trivial.
@@
 
-To illustrate how the discretization works in practice we take the alanine dipeptide system under an oscillatory EF,
+To illustrate how the discretization works in practice, we take the alanine dipeptide system under an oscillatory EF
 as an example, the NEMD simulation of which was
@@
 to correct the backbone dihedral angle energies.
-All simulations were performed by a home-modified
-Gromacs~4.6.5~\cite{pronk2013gromacs} with CHARMM27 force field implemented~\cite{bjelkmar2010implementation}.
+All simulations were performed using an in-house modified
+Gromacs~4.6.5~\cite{pronk2013gromacs} implementing the CHARMM27 force field~\cite{bjelkmar2010implementation}.
 The alanine dipeptide was put into the local thermostating
@@
 The whole system was coupled to the Parrinello-Rahman barostat~\cite{parrinello1981polymorphic} (in standard Gromacs implementation) with $\tau_P = 2.0$~ps to
-keep the system at 1~Bar. The non-equilibrium trajectories
+maintain the system at 1~Bar. The non-equilibrium trajectories
 were integrated by the Leap-frog scheme with a time-step of 0.002~ps.
@@
 The neighbor list was updated every 5 time-steps with a list-building radius 1.20~nm.
-All hydrogen involving covalent bonds were constrained by the LINCS algorithm~\cite{hess1997lincs}, except the water molecules that were constrained by the SETTLE algorithm~\cite{miyamoto2004settle}.
+All hydrogen-involving covalent bonds were constrained by the LINCS algorithm~\cite{hess1997lincs}, except for water molecules that were constrained by the SETTLE algorithm~\cite{miyamoto2004settle}.
 The whole system was driven by a periodic electric field
 $E(t) = E_0\sin(2\pi t/T)$ and $D(x) = (1,0,0)^{\top}$
-with intensity of the field being $E_0 = 1.0$~V/nm and period being
+with the intensity of the field being $E_0 = 1.0$~V/nm and the period being
 $T = 10$~ps.
 The 20,000 branching trajectories were simulated from 20,000
-initial configurations that sample the equilibrium distribution.
+initial configurations that sampled the equilibrium distribution.
 % \redc{Write a lot of details on NEMD.}
@@
 
-For this periodically driven molecular system we will first show how to choose an appropriately fine spatial discretization. After validating this discretization we will consider
+For this periodically driven molecular system, we will first show how to choose an appropriately fine spatial discretization. After validating this discretization, we will consider
 the time-discretized dynamics generated by the Floquet transition matrix $\vect P$
 in comparison to the original NEMD simulation.
-Finally we will coarse grain this description further by construction of a $3$ state Markov State Model that is able to describe the long-term kinetics of the system correctly.
+Finally, we will coarse grain this description further by construction of a $3$-state Markov State Model that is able to describe the long-term kinetics of the system correctly.
 
@@
 the $\phi$--$\psi$ plane. We denote the number of discretization intervals on each
-dihedral by $N_\dih$, then we get $N = N_\dih^2$ discretization sets 
+dihedral by $N_\dih$, yielding $N = N_\dih^2$ discretization sets 
 $\{\Omega_i\},\ i\in S = \{1,\cdots,N_\dih^2\}$.
 
-Based on a given spatial discretization we can aggregate the transition matrix $\vect P=\myphi^{\top}(T)$ just by counting the transition behavior of MD trajectories 
+Based on a given spatial discretization, we can aggregate the transition matrix $\vect P=\myphi^{\top}(T)$ simply by counting the transition behavior of MD trajectories 
 \begin{equation}\label{Pdirect}
@@
 \end{equation}
-However, $\vect P$ allows to approximate the original dynamics on multiples $mT$ of the period only.
-In order to have a time-continuous description we need the generator $L(t)$ of the Master equation.
-If the discretization is fine enough one possible approximation to $L(t)$ is via
+However, $\vect P$ allows approximation of the original dynamics on multiples $mT$ of the period only.
+In order to have a time-continuous description, we need the generator $L(t)$ of the Master equation.
+If the discretization is fine enough, one possible approximation to $L(t)$ is via
 the following forward finite difference scheme:
@@
   Since the dimensionality is reduced by using only a few collective
-  variables, the lag-time should be chosen large enough so that
+  variables, the lag-time should be chosen sufficiently large that
   the original dynamics $x_t$ is properly relaxed with regard to
@@
   (assuming  that the collective variables capture the slow dynamics).
-  In the following 
+  Below, 
 we investigate the discretization
@@
 Therefore, this is an indicator for calibrating the discretization quality.
-We compute $L(t)$ by two discretizations $N_\dih=2$ and $N_\dih=20$, and two
-choices of time intervals $[0, 80]$~ps and $[320, 400]$~ps, and then
+We compute $L(t)$ by two discretizations, viz.~$N_\dih=2$ and $N_\dih=20$, and two
+choices of time intervals, viz.~$[0, 80]$~ps and $[320, 400]$~ps, and then
 compare the time-dependent probability $\prob\big(\phi_t\in[0,180), \psi_t\in [0,180)\big)$
 with the (brute force) NEMD result in Fig.~\ref{fig:tmp2} using a lag-time $\tau=0.5$~ps.
-Using $N_\dih=2$ the dynamics depends on the time interval used for
-calculating the generator: using time interval $[0, 80]$~ps the discretized
+Using $N_\dih=2$, the dynamics depends on the time interval used for
+calculating the generator: using time interval $[0, 80]$~ps, the discretized
 dynamics deviates from the NEMD result,
 while using time interval $[320, 400]$~ps the discretized dynamics can only
-reproduces the NEMD result after 300~ps.  This therefore indicates poor 
-approximations to the original dynamics with $N_\dih=2$. The reason is that the
-discretization with $N_\dih=2$ is too coarse so that the dynamics cannot be fully
-equilibriated within the lag-time $\tau$ in each discretized set,
-therefore, the discretization presents state dependency.  For
+reproduce the NEMD result after 300~ps.  This therefore indicates poor 
+approximations of the original dynamics with $N_\dih=2$. The reason for this is that the
+discretization with $N_\dih=2$ is too coarse, so that the dynamics cannot be fully
+equilibriated within the lag-time $\tau$ in each discretized set;
+therefore, the discretization presents state-dependency.  For
 $N_\dih=20$, the discretized dynamics does not depend on the time interval of
 calculating the generator, and is consistent with the
-NEMD simulation within the error bar. Therefore, throughout this paper we use $N_\dih=20$
+NEMD simulation within the error bar. Therefore, throughout this paper, we use $N_\dih=20$
 to discretize  the dihedral angle space of alanine dipeptide.
@@
   \caption{Time-dependent probability $\prob\big(\phi\in[0,180), \psi\in [0,180)\big)$.
-The NEMD simulation is compared with the Master equation using generators discretized with $N_\dih=20$ and different lag time $\tau$.
+The NEMD simulation is compared with the Master equation using generators discretized with $N_\dih=20$ and different lag times ($\tau$).
 The red shadow region indicates the
@@
 
-Next we discuss the effect of the lag time $\tau$ on the estimation of the generator. Therefore, we consider 
-different choices of $\tau$ (0.5, 1.0, 2.0 and 5.0~ps)
-(see Fig.~\ref{fig:tmp3}), all based on the identical dihedral angle discretization using $N_\dih=20$.
-It is clear that when the lag-time is close to the period (10~ps), the
+Next, we discuss the effect of the lag time $\tau$ on the estimation of the generator. Therefore, we consider 
+different choices of $\tau$ (0.5, 1.0, 2.0, and 5.0~ps, see Fig.~\ref{fig:tmp3}), all based on the identical dihedral angle discretization using $N_\dih=20$.
+It is clear that, when the lag-time is close to the period (10~ps), the
 discretized dynamics cannot resolve the probability change within a
-period. However, it is surprising  that even quite large lag-times are able to capture the
-the overall long time behavior of the original dynamics.
+period. However, it is surprising  that even quite large lag-times are able of capturing 
+the overall long-term behavior of the original dynamics.
 We observe no significant difference between $\tau=0.5$ and
-$\tau=1.0$~ps, which means the discretized dynamics is not very sensitive
+$\tau=1.0$~ps, which means that the discretized dynamics is not very sensitive
 to the choice of $\tau$.
@@
 
-After having validated the fine-scale spatial discretization 
+After having validated the fine-scale spatial discretization, 
 we will now consider the time-homogeneous process $\tilde X_{m}$ generated by
@@
 In this context, only the configurations at the  integral periods $mT$ along the original process
-are taken into consider.
+are taken into consideration.
 
@@
 stationary probability density of $\Phi(T)$ (i.e.~the leading eigenvector $\mymu$) and that 
-estimated form the original NEMD simulation,
+estimated from the original NEMD simulation,
 % along which only integral periods $mT$ are considered:
@@
 \end{align}
-On each NEMD branching trajectory the initial 320~ps are discarded and
+On each NEMD branching trajectory, the initial 320~ps are discarded and
 the rest of the trajectory in time interval $[320,4000]$~ps is averaged to estimate
@@
 $P$ is computed as described above, and then $\mymu$ is computed as its leading eigenvector. In order to make it comparable to the free energy in the equilibrium case, we take
-the logarithm of the distributions, i.e.~$F_{\textrm{st}}(\phi,\psi)=
+the logarithm of the distributions, i.e.,~$F_{\textrm{st}}(\phi,\psi)=
 -k_B\mathcal T\log \rho_{\textrm{st}}(\phi,\psi)$
@@
   \includegraphics[width=0.4\textwidth]{fig-cluster.eps}
-  \caption{The core set identification. Different colors indicate different core sets: $C_{\confaa}$ (green), $C_\beta$ (yellow) and $C_{\confc}$ (red).
+  \caption{The core set identification. Different colors indicate different core sets: $C_{\confaa}$ (green), $C_\beta$ (yellow), and $C_{\confc}$ (red).
     The blue color indicates the transition region $C$ that does not belong to one of the core sets.}
@@
 
-The procedure for identifying good metastable core sets of the irreversible Markov process associated with $\vect P$ is described in detail in Ref.~\cite{sarich2014utilizing}; here we just provide the fundamental idea behind it: If  strong metastable sets $C_j$, $j=1,\ldots,K$ exist they should have one main property: When starting from a state in $C_i$ the expected hitting time of a state in $C_i$ should be much shorter than that of any state in one of the other sets $C_j$, $j\not=i$; in fact, the hitting time distribution should exhibit roughly constant levels in each set $C_j$ and should vary significantly in the transition region $C=\Omega\setminus\cup_j C_j$ between the metastable sets.
+The procedure for identifying good metastable core sets of the irreversible Markov process associated with $\vect P$ is described in detail in Ref.~\cite{sarich2014utilizing}; here, we only provide the fundamental idea behind it.
+If  strong metastable sets $C_j$, $j=1,\ldots,K$ exist, they should have one main property: when starting from a state in $C_i$, the expected hitting time of a state in $C_i$ should be much shorter than that of any state in one of the other sets $C_j$, $j\not=i$.
+In fact, the hitting time distribution should exhibit roughly constant levels in each set $C_j$ and should vary significantly in the transition region $C=\Omega\setminus\cup_j C_j$ between the metastable sets.
 If starting from some randomly chosen initial states, one thus can identify the metastable core sets and the transition region by analyzing the hitting time distributions.
-This procedure is similar to the procedures used for reversible processes \cite{PCCAplus,A19-1,prinz2011markov} but utilizes hitting time distributions instead of any eigenvector information.
-
-The metastable core sets identified by this procedure based on the estimate of $\vect P$ are illustrated in Fig.~\ref{fig:cluster} and denoted by $C_{\confaa}$ (green), $C_\beta$ (yellow) and $C_{\confc}$ (red).
+This procedure is similar to the procedures used for reversible processes \cite{PCCAplus,A19-1,prinz2011markov}, but utilizes hitting time distributions instead of any eigenvector information.
+
+The metastable core sets identified by this procedure based on the estimation of $\vect P$ are illustrated in Fig.~\ref{fig:cluster} and denoted by $C_{\confaa}$ (green), $C_\beta$ (yellow), and $C_{\confc}$ (red).
 They correspond to the centers of the wells in the free energy landscapes shown in Fig.~\ref{fig:num-1} and to the
-right-handed alpha-helix, beta-sheet and left-handed alpha-helix conformations of the peptide, respectively.
+right-handed alpha-helix, beta-sheet, and left-handed alpha-helix conformations of the peptide, respectively.
 
@@
     simulation (left column) and discretized dynamics (right column).  From top
-    to bottom the first mean hitting times to the core sets $C_{\confaa}$, $C_{\beta}$,
+    to bottom, the first mean hitting times to the core sets $C_{\confaa}$, $C_{\beta}$,
     and $C_{\confc}$ are shown, respectively}
@@
 is defined by the expected first time needed for hitting a certain core set $C_j$,
-$j\in\{\alpha_R,\beta,\alpha_L\}$ conditioned on starting from the
-conformation $(\phi,\psi)$, more exactly from equilibrium conformations $(\phi,\psi)\in\Omega_i$.  Since the largest first mean hitting
+$j\in\{\alpha_R,\beta,\alpha_L\}$, conditioned on starting from the
+conformation $(\phi,\psi)$, or more exactly, from equilibrium conformations $(\phi,\psi)\in\Omega_i$.  Since the largest first mean hitting
 time (starting from states in core set $\confaa$ and hitting $\confc$) is longer than
-600~ps the results will be biased if we use the NEMD trajectories of length 4000~ps for brute force Monte Carlo estimation of the hitting time. 
+600~ps, the results will be biased if we use the NEMD trajectories of length 4000~ps for brute force Monte Carlo estimation of the hitting time. 
 Therefore, we base our Monte Carlo estimate on 100 NEMD
-trajectories of $2\times 10^5$~ps instead. For comparison we compute the first mean hitting
+trajectories of $2\times 10^5$~ps instead. For comparison, we compute the first mean hitting
 time of the discretized dynamics via its transition matrix $\vect P$: the first mean hitting time $h_{C_j}(i)$ of core set $C_j$ starting in $\Omega_i$ can  be computed by means of solving the linear problem \cite{A19-31}
@@
 good consistency between the NEMD estimate and the discretized Markov process
-$\tilde X_{m}$ indicates a good approximation quality.
-One should note that the NEMD estimate of the first mean hitting time is subject to statistical sampling errors while the first mean hitting times $h_{C_j}$ only contain the statistical errors coming from the estimation of $\vect P$.
+$\tilde X_{m}$ indicates a good approximation.
+One should note that the NEMD estimate of the first mean hitting time is subject to statistical sampling errors, while the first mean hitting times $h_{C_j}$ only contain the statistical errors coming from the estimation of $\vect P$.
 Thus, using $P$ helps in calculating the observables
-in a smoother  manner (less statistical error, no additional sampling).
+more smoothly (less statistical error, no additional sampling).
 Additionally, the computational cost of the
@@
 essentially smaller than NEMD:
-the computation of $h_{C_j}$ is an issue of milliseconds on a laptop, while the
-NEMD trajectories took $1.6\times 10^4$ core hours for Intel Xeon E5-4650 CPUs.
+the computation of $h_{C_j}$ was a matter of milliseconds on a laptop, while the
+NEMD trajectories took $1.6\times 10^4$ core hours on Intel Xeon E5-4650 CPUs.
 
@@
 core set $C_j,\ j\in\{\confaa, \beta, \confc\}$ is defined as the
-probability of last coming from $C_j$ conditioned on having arrived presently at
-configuration $(\phi,\psi)\in\Omega_i$.
+probability of last coming from $C_j$, conditioned on having arrived  at
+configuration $(\phi,\psi)\in\Omega_i$ at this time.
 For reversible Markov processes, the
-forward and backward committors are identical, however, this is in
-general not the case for irreversible processes.
+forward and backward committors are identical; however, this is 
+generally not the case for irreversible processes.
 The committors estimated from NEMD simulations ($20000$ trajectories, $4000$~ps each) are compared with
 those computed from $P$ by means of solving the linear equations (\ref{qfwd}) and (\ref{qbwd}).
-Fig.~\ref{fig:num-3}--\ref{fig:num-5} presents both
+Figs.~\ref{fig:num-3}--\ref{fig:num-5} present both
 committors as well as their difference corresponding to different core sets.
@@
 indicate that the NEMD process, projected on the discretized
-dihedral angle space, is irreversible, and
-the discretized process is able to correctly describe this irreversiblity.
-In addition, and subsequently of central importance, the accurate reproduction of the committors indicates it is reasonable to build the 
+dihedral angle space, is irreversible, and that
+the discretized process is able to correctly describe this reversibility.
+In addition, and subsequently of central importance, the accurate reproduction of the committors indicates that it is reasonable to build the 
 MSM out of the committors of the  discretized process.
@@
 
-Following the process described in Sec.~\ref{sec:build-msm}, we are able to build a 
-three state MSM for the externally driven alanine dipeptide system,
+Following the process described in Section~\ref{sec:build-msm}, we are able to build a 
+3-state MSM for the externally driven alanine dipeptide system,
 where the quasi-stationary probability distribution $\mu$, the three core sets, and the forward and backward committors are
-estimated as described above, and the MSM transition matrices $\hat P$, $\hat{M}$, and $\hat{T}$ are then evaluated using Eq.~\eqref{eq:msm-tmatrix-00}, \eqref{eq:msm-ht-1} and \eqref{eq:msm-hm-1}, correspondingly.
+estimated as described above, and the MSM transition matrices $\hat P$, $\hat{M}$, and $\hat{T}$ are then evaluated using Eq.~\eqref{eq:msm-tmatrix-00}, \eqref{eq:msm-ht-1}, and \eqref{eq:msm-hm-1}, correspondingly.
 Alternatively, the MSM  transition matrix $\hat P$ is calculated directly from the NEMD trajectories using Eq.~\eqref{hatP_prob} (very good agreement with the one computed from the committors).
 The leading eigenvalues of $P=\myphi^{\top}(T)$ are compared with those of $\hat P$ and $\hat{M}^{-1}\hat{T}$ in
-Tab.~\ref{tab:tmp1}.
-Without surprising, the two approaches for MSM building are consistent.
+Table~\ref{tab:tmp1}.
+Not surprisingly, the two approaches for MSM building are consistent.
 The MSM is able to accurately reproduce
@@
 for the lower accuracy may also be that
-the corresponding time scale is 26.5~ps (calculated by $-T/\log(\lambda_2)$),
+the corresponding timescale is 26.5~ps (calculated by $-T/\log(\lambda_2)$),
 which is NOT significantly longer than the temporal resolution given by the period $T=10$~ps of the external driving force.
@@
   can be taken as an indication for the non-Markovianity of the milestone process $\hat X_m$. This
-  non-Markovianity seems to have stronger influence on the second non-trivial timescale in comparison to the first one; this may be caused by shorter decorrelation timescales due to weaker metastability of the core sets involved.
+  non-Markovianity seems to have stronger influence on the second non-trivial timescale than on the first; this may be caused by shorter decorrelation timescales due to weaker metastability of the core sets involved.
 Numerically the two MSM transition matrices are:
@@
 
-It is worth noting that although the discretized process $\tilde X_m$ is irreversible,
+It is worth noting that, although the discretized process $\tilde X_m$ is irreversible,
 the MSM built out of it is almost reversible:
@@
 
-In fact, $\hat{P}$ can be considered as the fingerprint of the long-term kinetics (cf.~\cite{A19-39,PrinzKellerNoe_PCCP11_Perspective}) of alanine dipeptide in an oscillatory electric field.
+In fact, $\hat{P}$ can be considered as the fingerprint of the long-term kinetics (cf.~\cite{A19-39,PrinzKellerNoe_PCCP11_Perspective}) of the alanine dipeptide in an oscillatory electric field.
 In order to provide further validation of this statement, we study  time-dependent expectation values of
@@
 \end{align}
-where $p(i,t)=\prob(X_t=i)$ is the probability to be in set $\Omega_i$ at time $t$ as governed by the Master equation, and the observable $\mathcal A$ is  spanned by the backward
+where $p(i,t)=\prob(X_t=i)$ is the probability of being in set $\Omega_i$ at time $t$, as governed by the Master equation, and the observable $\mathcal A$ is  spanned by the backward
 committors, i.e.,
@@
 
-In Fig.~\ref{fig:num-7} we compare the numerical calculation of $\hat p_j (mT), \ m\in\mathbb N$ from NEMD and MSM calculations.
+In Fig.~\ref{fig:num-7}, we compare the numerical calculation of $\hat p_j (mT), \ m\in\mathbb N$ from NEMD and MSM calculations.
 In the NEMD case, the identity  $\hat p_j (mT) = \sum_{i\in S}  q^\bwd_j(i)  p(i,mT) $ is used, and
@@
   \caption{Flowchart showing optional procedures for MSM building based on NEMD trajectories. A lighter color indicates
-  a "coarser'' approximation to the original NEMD dynamics. Please note that "equivalence" only means that the respective procedures result in the same matrix/MSM if one assumes perfect sampling.}
+  a ``coarser'' approximation of the original NEMD dynamics. Please note that "equivalence" only means that the respective procedures result in the same matrix/MSM if one assumes perfect sampling.}
   \label{fig:flowchart}
@@
 
-In this paper we proposed methods of MSM building for a periodically driven
+In this paper we proposed methods for MSM building for a periodically driven
 non-equilibrium system. We demonstrated their validity and performance by application to  alanine dipeptide under an oscillatory electric field. We showed that the proposed 
-methods allow for capturing the long-time behavior of the original
+methods allow capturing of the long-term behavior of the original
 non-equilibrium dynamics.
 
-We provided effective methods for discretizing the original NEMD dynamics
-both temporally and spatially; the end-product is a time-homogeneous, in general irreversible Markov jump process.
+We provided effective methods for discretizing the original NEMD dynamics,
+both temporally and spatially; the end-product is a time-homogeneous, and  generally irreversible Markov jump process.
 Discretization was done via two equivalent approaches:
-either by a two-step version,
-i.e.~first spatial and then temporal discretization,
-or a one-step version that involves both discretizations simultaneously.
+either by a two-step approach,
+i.e.,~first spatial and then temporal discretization,
+or a one-step approach, which involves both discretizations simultaneously.
 These two version are shown by the left-most and middle branches of the diagram  in Fig.~\ref{fig:flowchart}.
@@
 \emph{within} one period, because only the states
-at integral multiples of the period of the external forcing are considered. This is no serious problem
-whenever the long-time behavior of the system is of interest, and
+at integral multiples of the period of the external forcing are considered. This is not a serious problem
+whenever the long-term behavior of the system is of interest, and
 the corresponding timescales are significantly longer than one
@@
 is comparable to the period, the two-step
-discretization is preferable because it allows to recover the dynamics between multiples of
+discretization is preferable, because it allows recovery of the dynamics between multiples of
 the period.
@@
 using Eq.~\eqref{eq:msm-tmatrix-00} and a set of core sets that are
-derived from the discretized dynamics.  In application to alanine dipeptide numerical
-results show that a three-state MSM can reproduce the leading non-trivial
+derived from the discretized dynamics.  In application to the alanine dipeptide, numerical
+results show that a 3-state MSM can reproduce the leading non-trivial
 eigenvalue with very good accuracy, and the second non-trivial
-eigenvalue with acceptable accuracy. The lower accuracy regarding the
+eigenvalue with acceptable accuracy. The lower accuracy of the
 second non-trivial eigenvalue may result from the fact that the second
 slowest timescale is not significantly longer than the period. By means of
-this three-state MSM we can reproduce, with almost perfect
-accuracy, the time-evolution of the population of the main conformations induced by the periodic forcing when starting from the  
+this 3-state MSM, we can reproduce, with almost perfect
+accuracy, the time-evolution of the population of the main conformations induced by the periodic forcing, when starting from the  
 equilibrium distribution of the unforced molecular system.
@@
 In practice, however, this method may not be applicable, because
-it requires pre-defined core sets, and the identification of core sets 
-usually is no trivial task, especially for molecular dynamics under non-equilibrium conditions.
+it requires pre-defined core sets, and the identification of core sets is 
+usually  no trivial task, especially for molecular dynamics under non-equilibrium conditions.
 This task is substantially simplified when an accurate time-homogeneous discretization 
-to the original NEMD process is available (that is, has been constructed in advance).
-In the present work, we computed the core sets by
+of the original NEMD process is available (that is, has been constructed in advance).
+In the present study, we computed the core sets by
 finding almost constant levels of the hitting time distribution for the discretized dynamics. 
-This procedures is itself a novelty since it does not require any spectral information like eigenvectors as in standard approaches, cf.~\cite{prinz2011markov,A19-1}.
+This procedure is itself a novelty, since it does not require any spectral information, such as eigenvectors, as standard approaches do, cf.~\cite{prinz2011markov,A19-1}.
 
@@
 building in non-equilibrium systems.
-However, the application of these methods to the conformation dynamics of alanine dipeptide results in some observations that are interesting in itself: Under an
+However, the application of these methods to the conformation dynamics of the alanine dipeptide results in some observations that are interesting in themselves: Under an
 oscillatory EF, the population of the left-handed $\alpha$-helical conformation
@@
 A final remark concerning the utilization of the proposed methodology may be in order. 
-Based on an MSM for a given periodic forcing optimal control problems may come into reach:
-Using available methods like non-equilibrium
-linear response theory~\cite{wang2013linear} or computational alchemy for MSMs ~\cite{schutte2014markov} one can construct the MSM for slightly changed parameters (e.g., period and amplitude) of the external forcing by appropriate reweighting of the MSM for the given forcing.
-This in principle allows for  answering questions like the following:
-For which parameters of the external forcing does one achieve maximal population of  the left-handed $\alpha$-helix?
+Based on an MSM for given periodic forcing, optimal control problems may come into play:
+Using available methods, such as non-equilibrium
+linear response theory~\cite{wang2013linear} or computational alchemy for MSMs ~\cite{schutte2014markov}, one can construct the MSM for slightly changed parameters (e.g., period and amplitude) of the external forcing by appropriate reweighting of the MSM for the given forcing.
+This, in principle, allows for  answering questions such as the following:
+for which parameters of the external forcing does one achieve maximal population of  the left-handed $\alpha$-helix?
 Such questions, however, will
-be treated in the future studies.
+be addressed the future studies.
+
+\section*{Acknowledgment}
+
+H.W. Acknowledges support from the National High Technology Research and Development
+Program of China under Grant No. 2015AA011201.
 

### 2015-01-26 writedown/period.noneq.msm/submit.jctc.reply/reply.tex
add reply

\documentclass{article}

\addtolength{\textwidth}{2.5cm}
\addtolength{\hoffset}{-.4in}

\usepackage{graphicx}
\usepackage[margin=10pt,font=small,labelfont=bf]{caption}
\usepackage{lipsum}

\renewcommand{\baselinestretch}{1.0}
% \setlength{\footskip}{0cm}
%\addtolength{\textheight}{10cm}
% \sloppy

\renewcommand{\arraystretch}{1.2}

\begin{document}

\hfill\begin{tabular}{@{}p{.4\linewidth}@{}}
\multicolumn{1}{@{}c@{}}{} \\
        Han Wang\\
        CAEP Software Center for \\
        High Performance Numerical\\
        Simulation\\
        Huayuan Road 6\\
        Beijing 100088, China\\
        \\
        \today
\end{tabular}
\vskip .1cm
\noindent
\begin{tabular}{@{}p{.45\linewidth}@{}}
\multicolumn{1}{@{}c@{}}{} \\
Prof. William L. Jorgensen \\
\\
Yale University \\
Department of Chemistry\\
P.O. Box 208107 \\
New Haven, CT  06520-8107 \\
  USA\\  
\end{tabular}\hfill

\vskip 1cm

\noindent
\textbf{\large Resubmission for manuscript ct-2014-00997y}

\vskip .5cm
\noindent
Dear Prof. Jorgensen,\\

On behalf of the co-author, I would like to resubmit our article:
\textit{``Building Markov State Models for
  Periodically Driven Non-Equilibrium Systems''}
by H.~Wang and C.~Sch\"utte to the
\textit{Journal of Chemical Theory and Computation}.
We gratefuly acknowledge the reviewers for the positive reports, and for
their insight and suggestions, which helped us improving the quality
of the manuscript.  In response to their comments, the revisions are
reported below in details.  To help the referees spot the changes in
the manuscript, we have submitted a separate file (highlight.pdf) with
all changes highlighted in red.

\vskip 1cm

\noindent Best regards,\\
Han Wang

\vskip 1cm
\newpage
\section*{Reply to Referee 1}

\textit{
A periodically driven electric field is but one of several
non-equilibrium situations that may be of interest to the simulation
community.  Can the authors comment on how extensible their framework
is to non-periodic forces?  For instance, what about steered molecular
dynamics?  What if the work is far from equilibrium?  I believe the
group of K. Schulten has made available SMD pulling/unfolding
trajectories for deca-alanine. These simulations were performed at
multiple velocities, including one simulation that was fully
reversible.  It would be most outstanding for the authors to look into
retrieving that data to reconstruct a non-equilibrium MSM for a
larger, slightly more realistic system and for a different
non-equilibrium regime.
}\\

The current theoretical framework firstly reduces to an
time-homogeneous Markov process by the Floquet theory.  The extension
to the non-periodic driving forces is not straightforward, because in
general the Floquet theory is not applicable to for arbitrary driving
force. Nevertheless, the question raised by the referee is very
important, and we intend to address in future research.
\\

\textit{ Of course, alanine dipeptide is a toy system.  And, as the
  authors show, researchers may not be able to arrive at a perfect
  answer using their methods even for this toy system. I.e., the
  second non-trivial eigenvalue for their example had some error,
  already; therefore it would be my expectation that this would
  essentially be unresolvable (realistically) for biological systems
  of real interest.  As someone more in the applications field, I find
  this worrisome. It would be helpful for the authors to discuss the
  potential application of their framework to a realistic biological
  system (e.g., a normal size protein).
}\\

% \begin{minipage}{.8\linewidth}
%   \centering
%   \includegraphics[width=0.6\textwidth]{hitting.eps}
%   \captionof{figure}{Schematic plot of comparison between a continuous and time-discretized trajectories in hitting a core set.}
% \end{minipage}

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{hitting.eps}
  \caption{Schematic plot of comparison between a continuous and time-discretized trajectories in hitting a core set.}
  \label{fig:tmp1}
\end{figure}

The lower accuracy of the second non-trivial time scale stems from the
time-disretization problem in core set hitting, which is graphically
illustrated in Fig.~\ref{fig:tmp1}.  The milestone process is defined
to change state when the trajectory hits a core set that is not the
one it came from.  In Fig.~\ref{fig:tmp1}, if the trajectory is
continuum, then the milestone process changes to state ``2'' at the
first hitting at core set $C_2$. In comparison, the first hitting
event would not be recognized if the trajectory is discretized, and
the milestone process changes to state ``2'' only at the second
hitting at core set $C_2$.\\

This time-discretizations error would not be significant if the
interested time-scale is much longer than the discretized time-step.
However, it would be seen if the they are comparable. In our case, the minimum discretization
time-step is the period $T=10$~ps, which is not well separated from the second non-trivial time-scale
that is 26.5~ps.\\

\begin{table}
  \centering
  \begin{tabular*}{0.9\textwidth}{@{\extracolsep{\fill}}l cccccc}\hline\hline
    & NEMD & MSM & MSM &MSM &MSM &MSM \\
    Time Discr. [ps] & 0.5 &  $10$ &  $20$ & $40$ & $80$ & $120$\\
    $t_1$ [ps] & 100.2 & 104.8 & 108.8 & 115.5 & 127.6 & 142.4 \\\hline\hline
  \end{tabular*}
  \caption{The leading non-trivial time-scale computed by NEMD and MSM at different time-discretizations.
  The smallest time-discretization of MSM is constrained by the period of external driving $T$ that is 10~ps.}
  \label{tab:tmp1}
\end{table}
In order to further illustrate the artifact of time-discretizations,
we discretized the trajectory by increasing time-steps, and compare
the leading time-scale of the derived MSM with the NEMD, see Tab.~\ref{tab:tmp1}.
It can be easily concluded that as the time-discretizations increases and approaches
the leading non-trivial time-scale $t_1 = 100.2$~ps, the accuracy of MSM
in computing $t_1$ decreases. When the time-discretizations increases to $4T = 40$~ps, the relative
error is over 15\%.
\\

In the applications of the more complex and realistic problems, if the
system has time-scale separation between the external driving period and the interested implied
time-scales, then good accuracy is expected. Generally speaking, in
more complex molecular system, the interested time-scales are longer
than the alanine dipeptide toy system. Therefore, we would expect 
higher accuracy in more complex systems if the period of external field is 10~ps.
\\

\textit{ Also, the authors and others in the field have used the
  Chapman-Komolgorov tests to assess convergence or consistency of the
  MSMs with the underlying simulations.  The authors should include
  this metric, or the authors should state why they are not including
  it.  In particular, it would be helpful for the authors to discuss
  (if they are not using it) and clarify for the community, when it is
  appropriate to use the CK test to assess convergence and when it is
  not. Application of CK has been mysteriously lacking in all the
  “real world” examples of MSM and this is an opportunity to help
  clarify its application.
}\\

The discretizations time-step in the milestone MSM approach should be
distinguished from the lag-time in the space full partitioning MSM
approach. Larger time-discretizations in milestone MSM generally gives
worse prediction of implied time-scales, whereas larger lag-time in
space full partitioning MSM leads to better accuracy as long as the
lag-time is smaller than the interested time-scale. The
Chapman-Komolgorov test basically checks the consistency of full
partitioning MSM with different lag-times, and it does not apply to
the milestone MSM approach.

\end{document}

### 2015-01-28 writedown/period.noneq.msm/submit.jctc.reply/paper.tex
backup the revise

@@
 \author{Han Wang}
-\email{han.wang@fu-berlin.de}
+\email{wang_han@iapcm.ac.cn}
 \affiliation{CAEP Software Center for High Performance Numerical Simulation, Beijing, China}
@@
 Recent years have seen an increased interest in non-equilibrium molecular dynamics (NEMD) simulations, especially for molecular systems with periodic forcing by external fields, e.g., in the context of studying the  effects of electromagnetic radiation on human body tissues.
-Lately, and NEMD method with local thermostating has been proposed; that allows the study of
+Lately, an NEMD method with local thermostating has been proposed that allows the study of
 non-equilibrium processes in a statistically reliable and thermodynamically consistent way.
@@
 radiation on  human body tissues (e.g.,~DNA, protein, and membrane)  have been extensively
-investigated in a vast number of articles, with the following list  representing an incomplete selection~\cite{bohr2000microwave, bohr2000microwave-1, dePomerai2000cell,
+investigated in a vast number of studies, with the following list  representing an incomplete selection~\cite{bohr2000microwave, bohr2000microwave-1, dePomerai2000cell,
   dePomerai2003microwave, mancinelli2004non, inskip2001cellular, bekard2013electric, budi2005electric,
@@
 % \textbf{Importance: first application of MSM in a non-equilibrium system.}
-To the knowledge of the authors this work is the first attempt of using MSMs for analyzing non-equilibrium systems under periodic external forcing.
+To the best of our knowledge, this work is the first attempt of using MSMs for analyzing non-equilibrium systems under periodic external forcing.
 More precisely, we will demonstrate how to use MSMs to investigate the conformational dynamics of a peptide (alanine dipeptide) under an oscillating electric field (EF).

### 2015-02-09 writedown/period.noneq.msm/submit.jctc.reply/paper.tex
backup

@@
 radiation on  human body tissues (e.g.,~DNA, protein, and membrane)  have been extensively
-investigated in a vast number of studies, with the following list  representing an incomplete selection~\cite{bohr2000microwave, bohr2000microwave-1, dePomerai2000cell,
+investigated in a vast number of studies, with the following list  representing an incomplete selection Ref.~\cite{bohr2000microwave, bohr2000microwave-1, dePomerai2000cell,
   dePomerai2003microwave, mancinelli2004non, inskip2001cellular, bekard2013electric, budi2005electric,
@@
 details that sometimes cannot be resolved in experiments. Only
-recently, a non-equilibrium MD simulation (D-NEMD) method with local thermostating has been proposed~\cite{wang2014exploring} that allows for studying 
+recently, a non-equilibrium MD simulation (NEMD) method with local thermostating has been proposed~\cite{wang2014exploring} that allows for studying 
 non-equilibrium processes in a statistically reliable and thermodynamically consistent way. 
@@
 typical MD trajectories remain close to a metastable set substantially longer than
-they need for a transition to another such state~\cite{A19-31,schuette2011markov}.
+they need for a transition to another such set~\cite{A19-31,schuette2011markov}.
 In this case, the metastable sets are the main conformations of the molecular system under consideration, which, often enough, are given by the main wells in the energy landscape.
@@
 More precisely, we will demonstrate how to use MSMs to investigate the conformational dynamics of a peptide (alanine dipeptide) under an oscillating electric field (EF).
-To this end, we will show how to generalize Markov state modeling to periodic non-equilibrium conditions, where one cannot assume reversibility of the dynamics as is most often case in the literature on MSM building.
+To this end, we will show how to generalize Markov state modeling to periodic non-equilibrium conditions, where one cannot assume reversibility of the dynamics as is most often the case in the literature on MSM building.
 
@@
 by comparing the kinetic fingerprints given by the MSM to brute force
-non-equilibrium MD simulations of alanine dipeptide under oscillating EF.
+NEMD simulations of alanine dipeptide under oscillating EF.
 The findings are summarized in Section~\ref{sec:conclusion}, which includes a chart presenting
@@
 \end{align}
-where $x_t\in\Omega$ denotes the state of the molecular system at time $t$ in state space $\Omega$, $\vect w_t$ denotes standard $n$-dimensional Brownian motion, and $\beta$ the inverse temperature,
+where $x_t\in\Omega$ denotes the state of the molecular system at time $t$ in state space $\Omega \subset \mathbb R^{3N_{\textrm{atom}}}$ ($N_{\textrm{atom}}$ being the number of atoms), $\vect w_t$ denotes standard $3N_{\textrm{atom}}$-dimensional Brownian motion, and $\beta$ the inverse temperature,
 i.e.,~$\beta = 1/(k_B\mathcal T)$.
@@
 where $\Delta_{\vect x}$ denotes the Laplacian operator and $\nabla_{\vect x}$
-the nabla-operator with respect to to $\vect x$. 
+the nabla-operator with respect to $\vect x$. 
 The periodicity of the external driving force induces the periodicity of the generator,
@@
 \subsection{Spatial discretization: Master equation}
-We will now introduce an appropriate spatial discretization of this kind of non-equilibrium MD --  this is done for reasons of simplicity only; we could completely avoid it for the price of more technical arguments.
+We will now introduce an appropriate spatial discretization of this kind of NEMD --  this is done for reasons of simplicity only; we could completely avoid it for the price of more technical arguments.
 For achieving this discretization, we 
@@
 then defines the coarse-grained long-term kinetics that shall
-approximate the original long term kinetics well. 
+approximate the original long-term kinetics well. 
 The idea behind MSM building is that, given that the molecular system under consideration exhibits metastable conformations,  it is usually possible to construct a
@@
 \label{eq:msm-bwd-committor}  
-q^\bwd_j(i)=\prob_\mu(\hat{X}_m=j \mid X_m=i),
+q^\bwd_j(i)=\prob_\mu(\hat{X}_m=j \mid \tilde X_m=i),
 \end{align}
@@
 In general, the milestone process need not be a Markov process.
-The results in \cite{A19-31,sarich2014utilizing} show, however, that it is an approximate Markov process as long as the core sets are proper metastable sets, i.e., if the typical timescale on which $(X_m)$ leaves $C$ is much smaller than the typical expected hitting times between the core sets.
+The results in Ref.~\cite{A19-31,sarich2014utilizing} show, however, that it is an approximate Markov process as long as the core sets are proper metastable sets, i.e., if the typical timescale on which $(X_m)$ leaves $C$ is much smaller than the typical expected hitting times between the core sets.
 Thus, by taking $\hat{P}$ as our MSM transition matrix, we introduce an additional modeling error that is the smaller the more metastable the core sets are.
 With this MSM transition matrix, we can define the MSM kinetics:
-If we start from some initial probability $\hat{p}_j(0)$ of being in state $j$ at time $t=0$ then its evolution $\hat{p}_j(t)$ in time is discrete in multiples of period $T$ and given by
+If we start from some initial probability $\hat{p}_j(0)$ of being in state $j$ at time $t=0$, then its evolution $\hat{p}_j(t)$ in time is discrete in multiples of period $T$ and given by
 \begin{equation}\label{eq:num-29}
@@
 Furthermore, as shown in the Appendix~\ref{sec:app-prove}, $\hat{T}$ as well as $\hat{M}$ can be computed from trajectories without requiring committors.
-The importance of the pair $\hat{T}$ and $\hat{M}$ for MSM building comes from the following observation: the main NEMD relaxation timescales are given by the dominant eigenvalues of $P$ \cite{A19-31, A19-1}.
-These dominant eigenvalues can be approximated by discretizing the related eigenvalue problem $Pu=\lambda u$ by means of a Galerkin approximation with the finite dimensional ansatz space 
+The importance of the pair $\hat{T}$ and $\hat{M}$ for MSM building comes from the following observation: the main NEMD relaxation timescales are given by the dominant eigenvalues of $P$ \cite{A19-31, A19-1};
+and these dominant eigenvalues can be approximated by discretizing the related eigenvalue problem $Pu=\lambda u$ by means of a Galerkin approximation with the finite dimensional ansatz space 
 spanned by the forward committors $q^+_j$, $j=1,\ldots,K$, together  with the finite dimensional test function space spanned by the backward committors $q^-_j$, $j=1,\ldots,K$ (test functions multiplied from the left by the inner product $\langle\cdot,\cdot\rangle_\mu$).
@@
 For the reversible case, it is known that the $k$ eigenvalues $\hat{\lambda}$ are very good approximations of the dominant eigenvalues $\lambda$ of the original problem, if the core sets are proper metastable sets~\cite{Eigenvalues}.
-Whether this is true for the non-reversible case is not yet known, but if the deviation from reversibility is weak and the dominant eigenvalues of $P$ are real-valued, then the results should hold analogously, see~\cite{A19-31} Thm.~4.19.
+Whether this is true for the non-reversible case is not yet known, but if the deviation from reversibility is weak and the dominant eigenvalues of $P$ are real-valued, then the results should hold analogously, see Ref.~\cite{A19-31} Thm.~4.19.
 
@@
 in comparison to the original NEMD simulation.
-Finally, we will coarse grain this description further by construction of a $3$-state Markov State Model that is able to describe the long-term kinetics of the system correctly.
+Finally, we will coarse-grain this description further by construction of a $3$-state Markov State Model that is able to describe the long-term kinetics of the system correctly.
 

### 2015-02-10 writedown/period.noneq.msm/submit.jctc.reply/paper.tex
CS works on the revise

@@
 
-\newcommand{\recheck}[1]{{\color{red} #1}}
+\newcommand{\redrevision}[1]{\color{red} #1}
 \newcommand{\redc}[1]{{\color{red} #1}}
@@
 
+\begin{table}
+  \centering
+  \caption{
+    Comparison of second and third eigenvalues of $\vect P$ and $3\times 3$ MSM transition matrices $\hat{P}$ and $\hat{M}^{-1}\hat{T}$, respectively, from the two different MSM approaches.
+  }
+  \begin{tabular*}{0.45\textwidth}{@{\extracolsep{\fill}}c rrr}\hline\hline
+      &  $\lambda_2$ & $\lambda_3$ & $\lambda_4$ \\\hline
+    $P$                 &0.905  &0.668 & 0.551       \\
+    $\hat P$     & 0.909  &0.710 & --       \\
+    $\hat{M}^{-1}\hat{T}$    & 0.901  &0.649 & --       \\
+    \hline\hline
+  \end{tabular*}
+  \label{tab:tmp1}
+\end{table}
+
 Following the process described in Section~\ref{sec:build-msm}, we are able to build a 
@@
 timescale is not as good as the first, but is still acceptable.
-The reason
-for the lower accuracy may also be that
-the corresponding timescale is 26.5~ps (calculated by $-T/\log(\lambda_2)$),
-which is NOT significantly longer than the temporal resolution given by the period $T=10$~ps of the external driving force.
+%The  lower accuracy is due to the fact that
+%the corresponding timescale of 26.5~ps (calculated by $-T/\log(\lambda_2)$) is \emph{not} significantly longer than the temporal resolution given by the period $T=10$~ps of the external driving force:
+%%%CS
+\begin{figure}
+  \centering
+  \includegraphics[width=0.6\textwidth]{hitting.eps}
+  \caption{Schematic plot of comparison between a continuous and time-discretized trajectories in hitting a core set. }
+  \label{fig:hitting}
+\end{figure}
+The lower accuracy of the second non-trivial timescale stems from the
+time-disretization underlying our approach. The associated problem is graphically
+illustrated in Fig.~\ref{fig:hitting}.  The milestone process is defined
+to change state when the trajectory hits a core set that is not the
+one it came from.  In Fig.~\ref{fig:hitting}, the milestone process based on the time-continuous trajectory changes to state ``2'' at the
+first hit of core set $C_2$. In comparison, this first hitting
+event would not be correctly recognized using the time-discretized trajectory; instead, in the time-discretized case 
+the milestone process would change to state ``2'' only at the second
+hit of core set $C_2$. This respective error in detecting the correct first hitting time will \emph{not} be significant if it is much longer than the discretization time-step.
+However, it will become relevant if both are comparable. In our case, the temporal discretization is given by the period $T=10$~ps, which is not well separated from the second non-trivial time-scale
+that is 26.5~ps (calculated by $-T/\log(\lambda_2)$). Therefore, we observe an unavoidable deviation in the second timescale.
+In applications to more complex and realistic problems (especially larger systems), in particular for
+systems exhibiting timescale separation between the external driving period and the interested implied
+timescales, good accuracy is expected. 
+%%%
+
 The difference between the eigenvalues of $\hat P$ and $\hat{M}^{-1}\hat T$
@@
 
-\begin{table}
-  \centering
-  \caption{
-    Comparison of second and third eigenvalues of $\vect P$ and $3\times 3$ MSM transition matrices $\hat{P}$ and $\hat{M}^{-1}\hat{T}$, respectively, from the two different MSM approaches.
-  }
-  \begin{tabular*}{0.45\textwidth}{@{\extracolsep{\fill}}c rrr}\hline\hline
-      &  $\lambda_2$ & $\lambda_3$ & $\lambda_4$ \\\hline
-    $P$                 &0.905  &0.668 & 0.551       \\
-    $\hat P$     & 0.909  &0.710 & --       \\
-    $\hat{M}^{-1}\hat{T}$    & 0.901  &0.649 & --       \\
-    \hline\hline
-  \end{tabular*}
-  \label{tab:tmp1}
-\end{table}
-
 % \begin{figure}
@@
 
-A final remark concerning the utilization of the proposed methodology may be in order. 
-Based on an MSM for given periodic forcing, optimal control problems may come into play:
+A final remark concerning the utilization of the proposed methodology may be in order: 
+%%%CS
+The approach presented herein allows for MSM building for periodic forcings only; an extension
+to non-periodic driving forces is not straightforward, because in
+general Floquet theory is not applicable to non-periodic driving
+forcings. However 
+%%%
+based on an MSM for given periodic forcing, optimal control problems may come into play:
 Using available methods, such as non-equilibrium

### 2015-02-10 writedown/period.noneq.msm/submit.jctc.reply/reply.tex
backup
CS works on the revise

@@
 their insight and suggestions, which helped us improving the quality
-of the manuscript.  In response to their comments, the revisions are
-reported below in details.  To help the referees spot the changes in
+of the manuscript.  In response to their comments, the major questions raised by the referees are
+reported below in detail.
+
+We revised the manuscript repsectively and reworked the English completely.
+To help the referees spot the major changes in
 the manuscript, we have submitted a separate file (highlight.pdf) with
 all changes highlighted in red.
+
+We hope that the revised manuscript is fit for publication now.
 
@@
 
-The current theoretical framework firstly reduces to an
-time-homogeneous Markov process by the Floquet theory.  The extension
-to the non-periodic driving forces is not straightforward, because in
-general the Floquet theory is not applicable to for arbitrary driving
-force. Nevertheless, the question raised by the referee is very
-important, and we intend to address in future research.
-\\
+The theoretical framework presented in the manuscript firstly reduces the NEMD process to a
+time-homogeneous Markov process by utilizing Floquet theory.  An extension
+to non-periodic driving forces is not straightforward, because in
+general Floquet theory is not applicable to arbitrary driving
+force. Nevertheless, apart from the aspects related to Floquet theory our general approach does well extend to more general driving forces so that
+the question raised by the referee is very relevant: Applications of the approach presented in the manuscript to approach like the one of K. Schulten is one of the final goals. \\
+
+However, one should be aware that our approach is \emph{the first} application of the MSM idea to NEMD.
+We think that the combination of the results presented here with the approach of the ideas presented in Sarich et al., Markov State Models for Rare Events in Molecular Dynamics.
+Entropy, 16 (1).
+pp.
+258-286 (2013)  will allow for addressing the question of the referee in future research.\\
 
@@
 
-The lower accuracy of the second non-trivial time scale stems from the
+The lower accuracy of the second non-trivial timescale stems from the
 time-disretization problem in core set hitting, which is graphically
@@
 to change state when the trajectory hits a core set that is not the
-one it came from.  In Fig.~\ref{fig:tmp1}, if the trajectory is
-continuum, then the milestone process changes to state ``2'' at the
+one it came from.  In Fig.~\ref{fig:tmp1}, the milestone process based on the time-continuous trajectory changes to state ``2'' at the
 first hitting at core set $C_2$. In comparison, the first hitting
-event would not be recognized if the trajectory is discretized, and
-the milestone process changes to state ``2'' only at the second
-hitting at core set $C_2$.\\
-
-This time-discretizations error would not be significant if the
-interested time-scale is much longer than the discretized time-step.
-However, it would be seen if the they are comparable. In our case, the minimum discretization
+event would not be recognized using the time-discretized trajectory; in this case 
+the milestone process would change to state ``2'' only at the second
+hitting at core set $C_2$. This respective error in detecting the correct hitting time would not be significant if the
+first hitting time is much longer than the discretization time-step.
+However, it will become relevant whenever they are comparable. In our case, the minimum discretization
 time-step is the period $T=10$~ps, which is not well separated from the second non-trivial time-scale
-that is 26.5~ps.\\
+that is 26.5~ps. Therefore, we observe an unavoidable deviation in the second timescale.\\
 
@@
 we discretized the trajectory by increasing time-steps, and compare
-the leading time-scale of the derived MSM with the NEMD, see Tab.~\ref{tab:tmp1}.
-It can be easily concluded that as the time-discretizations increases and approaches
+the \emph{leading} timescale $t_1$ of the derived MSM with the NEMD, see Tab.~\ref{tab:tmp1}.
+It can be easily seen that as the discretization time-step increases and approaches
 the leading non-trivial time-scale $t_1 = 100.2$~ps, the accuracy of MSM
-in computing $t_1$ decreases. When the time-discretizations increases to $4T = 40$~ps, the relative
-error is over 15\%.
+in computing $t_1$ decreases. 
 \\
 
-In the applications of the more complex and realistic problems, if the
-system has time-scale separation between the external driving period and the interested implied
-time-scales, then good accuracy is expected. Generally speaking, in
-more complex molecular system, the interested time-scales are longer
-than the alanine dipeptide toy system. Therefore, we would expect 
-higher accuracy in more complex systems if the period of external field is 10~ps.
+In applications to more complex and realistic problems (larger systems), in particular for
+systems exhibiting timescale separation between the external driving period and the interested implied
+timescales, good accuracy is expected (and in fact guaranteed by general MSM theory). Generally speaking, in
+more complex molecular system, the  timescales of interest are longer
+than in the alanine dipeptide toy system. 
 \\
@@
 
-The discretizations time-step in the milestone MSM approach should be
-distinguished from the lag-time in the space full partitioning MSM
-approach. Larger time-discretizations in milestone MSM generally gives
-worse prediction of implied time-scales, whereas larger lag-time in
-space full partitioning MSM leads to better accuracy as long as the
-lag-time is smaller than the interested time-scale. The
+The discretization time-step in the milestoning MSM approach should be
+distinguished from the lag-time in the full partition MSM
+approach. Larger discretization time-steps in milestoning MSM generally result in
+worse prediction of implied timescales (as discussed above), while larger lag-times in
+full partition MSMs lead to better accuracy as long as the
+lag-time is smaller than the time-scales of interest. The
 Chapman-Komolgorov test basically checks the consistency of full
-partitioning MSM with different lag-times, and it does not apply to
-the milestone MSM approach.
+partition MSM with different lag-times, and thus does not apply to
+milestone MSMs. See Schütte et al. (2011), Markov State Models Based on Milestoning, J. Chem. Phys., 134 (20). 204105 (2011) for more details.
 

### 2015-02-10 writedown/period.noneq.msm/submit.jctc.reply/paper.tex
backup before resubmit

@@
 \usepackage{graphicx}
+\usepackage{wasysym}
 % \usepackage{color}
@@
 
-\newcommand{\redrevision}[1]{\color{red} #1}
+\newcommand{\redrevision}[1]{{\color{red} #1}}
 \newcommand{\redc}[1]{{\color{red} #1}}
@@
 
+\begin{tocentry}
+\includegraphics[height=3.6cm]{toc.eps}
+\end{tocentry}
+
 \begin{abstract}
@@
 investigated in a vast number of studies, with the following list  representing an incomplete selection Ref.~\cite{bohr2000microwave, bohr2000microwave-1, dePomerai2000cell,
-  dePomerai2003microwave, mancinelli2004non, inskip2001cellular, bekard2013electric, budi2005electric,
+  dePomerai2003microwave, mancinelli2004non, inskip2001cellular, bekard2014electric, budi2005electric,
   budi2007effect, budi2008comparative, astrakas2012structural,
@@
   \centering
-  \includegraphics[width=0.6\textwidth]{hitting.eps}
-  \caption{Schematic plot of comparison between a continuous and time-discretized trajectories in hitting a core set. }
+  \includegraphics[width=0.45\textwidth]{hitting.eps}
+  \caption{Schematic plot of comparison between a continuous and time-discretized trajectories in hitting a core set.
+    The time-continuous trajectory changes to state ``2'' at the first hit of the core set $C_2$ (indicated by changing from solid to dashed line).
+    The time-discretized trajectory changes to state ``2'' at the second hit (indicated by changing from ``$\times$'' to ``$\Circle$'').
+  }
   \label{fig:hitting}
 \end{figure}
+\redrevision{
 The lower accuracy of the second non-trivial timescale stems from the
@@
 systems exhibiting timescale separation between the external driving period and the interested implied
-timescales, good accuracy is expected. 
+timescales, good accuracy is expected.}
 %%%
@@
 A final remark concerning the utilization of the proposed methodology may be in order: 
-%%%CS
+%%% CS
+\redrevision{
 The approach presented herein allows for MSM building for periodic forcings only; an extension
@@
 general Floquet theory is not applicable to non-periodic driving
-forcings. However 
+forcings. However,}
 %%%
@@
 Using available methods, such as non-equilibrium
-linear response theory~\cite{wang2013linear} or computational alchemy for MSMs ~\cite{schutte2014markov}, one can construct the MSM for slightly changed parameters (e.g., period and amplitude) of the external forcing by appropriate reweighting of the MSM for the given forcing.
+linear response theory~\cite{wang2013linear} or computational alchemy for MSMs~\cite{schutte2014markov}, one can construct the MSM for slightly changed parameters (e.g., period and amplitude) of the external forcing by appropriate reweighting of the MSM for the given forcing.
 This, in principle, allows for  answering questions such as the following:
@@
 
-\section*{Acknowledgment}
-
+\begin{acknowledgement}
+
+The computation of this work was performed at the North-German Supercomputing Alliance (HLRN). The authors are grateful for this support.
 H.W. Acknowledges support from the National High Technology Research and Development
 Program of China under Grant No. 2015AA011201.
+\end{acknowledgement}
 
@@
 
-\begin{thebibliography}{10}
-
-\bibitem{bohr2000microwave}
-Henrik Bohr and Jakob Bohr.
-\newblock Microwave-enhanced folding and denaturation of globular proteins.
-\newblock {\em Phys. Rev. E}, 61(4):4310, 2000.
-
-\bibitem{bohr2000microwave-1}
-Henrik Bohr and Jakob Bohr.
-\newblock Microwave enhanced kinetics observed in ord studies of a protein.
-\newblock {\em Bioelectromagnetics}, 21(1):68--72, 2000.
-
-\bibitem{dePomerai2000cell}
-David de~Pomerai, Clare Daniells, Helen David, Joanna Allan, Ian Duce, Mohammed
-  Mutwakil, David Thomas, Phillip Sewell, John Tattersall, Don Jones, and Peter
-  Candido.
-\newblock Cell biology: Non-thermal heat-shock response to microwaves.
-\newblock {\em Nature}, 405:417--418, 2000.
-
-\bibitem{dePomerai2003microwave}
-David~I de~Pomerai, Brette Smith, Adam Dawe, Kate North, Tim Smith, David~B
-  Archer, Ian~R Duce, Donald Jones, and E~Peter~M Candido.
-\newblock Microwave radiation can alter protein conformation without bulk
-  heating.
-\newblock {\em FEBS letters}, 543(1):93--97, 2003.
-
-\bibitem{mancinelli2004non}
-Fabrizio Mancinelli, Michele Caraglia, Alberto Abbruzzese, Guglielmo
-  d'Ambrosio, Rita Massa, and Ettore Bismuto.
-\newblock Non-thermal effects of electromagnetic fields at mobile phone
-  frequency on the refolding of an intracellular protein: Myoglobin.
-\newblock {\em J. Cell. Biochem.}, 93(1):188--196, 2004.
-
-\bibitem{inskip2001cellular}
-Peter~D Inskip, Robert~E Tarone, Elizabeth~E Hatch, Timothy~C Wilcosky,
-  William~R Shapiro, Robert~G Selker, Howard~A Fine, Peter~M Black, Jay~S
-  Loeffler, and Martha~S Linet.
-\newblock Cellular-telephone use and brain tumors.
-\newblock {\em N. Engl. J. Med.}, 344(2):79--86, 2001.
-
-\bibitem{bekard2013electric}
-I.~Bekard and D.E. Dunstan.
-\newblock Electric field induced changes in protein conformation.
-\newblock {\em Soft Matter}, pages~--, 2014.
-
-\bibitem{budi2005electric}
-A.~Budi, F.S. Legge, H.~Treutlein, and I.~Yarovsky.
-\newblock Electric field effects on insulin chain-b conformation.
-\newblock {\em J. Phys. Chem. B}, 109(47):22641--22648, 2005.
-
-\bibitem{budi2007effect}
-A.~Budi, F.S. Legge, H.~Treutlein, and I.~Yarovsky.
-\newblock Effect of frequency on insulin response to electric field stress.
-\newblock {\em J. Phys. Chem. B}, 111(20):5748--5756, 2007.
-
-\bibitem{budi2008comparative}
-Akin Budi, F~Sue Legge, Herbert Treutlein, and Irene Yarovsky.
-\newblock Comparative study of insulin chain-b in isolated and monomeric
-  environments under external stress.
-\newblock {\em J. Phys. Chem. B}, 112(26):7916--7924, 2008.
-
-\bibitem{astrakas2012structural}
-Loukas~G Astrakas, Christos Gousias, and Margaret Tzaphlidou.
-\newblock Structural destabilization of chignolin under the influence of
-  oscillating electric fields.
-\newblock {\em J. Appl. Phys.}, 111(7):074702--074702, 2012.
-
-\bibitem{damm2012can}
-Markus Damm, Christoph Nusshold, David Cantillo, Gerald~N Rechberger, Karl
-  Gruber, Wolfgang Sattler, and C~Oliver Kappe.
-\newblock Can electromagnetic fields influence the structure and enzymatic
-  digest of proteins? a critical evaluation of microwave-assisted proteomics
-  protocols.
-\newblock {\em J. Proteomics}, 75:5533--5543, 2012.
-
-\bibitem{english2009nonequilibrium}
-N.J. English, G.Y. Solomentsev, and P.~O'Brien.
-\newblock Nonequilibrium molecular dynamics study of electric and low-frequency
-  microwave fields on hen egg white lysozyme.
-\newblock {\em J. Chem. Phys.}, 131:035106, 2009.
-
-\bibitem{solomentsev2012effects}
-G.Y. Solomentsev, N.J. English, and D.A. Mooney.
-\newblock Effects of external electromagnetic fields on the conformational
-  sampling of a short alanine peptide.
-\newblock {\em J. Comput. Chem.}, 33:917--923, 2012.
-
-\bibitem{wang2014exploring}
-Han Wang, Christof Sch{\"u}tte, Giovanni Ciccotti, and Luigi Delle~Site.
-\newblock Exploring the conformational dynamics of alanine dipeptide in
-  solution subjected to an external electric field: {A} nonequilibrium
-  molecular dynamics simulation.
-\newblock {\em Journal of Chemical Theory and Computation}, 10(4):1376--1386,
-  2014.
-
-\bibitem{A19-31}
-Ch. Sch\"utte and M.~Sarich.
-\newblock {\em Metastability and {{Markov}} State Models in Molecular Dynamics:
-  Modeling, Analysis, Algorithmic Approaches}, volume~24 of {\em Courant
-  Lecture Notes}.
-\newblock American Mathematical Society, December 2013.
-
-\bibitem{prinz2011markov}
-J.H. Prinz, H.~Wu, M.~Sarich, B.~Keller, M.~Senne, M.~Held, J.D. Chodera,
-  C.~Sch{\"u}tte, and F.~No{\'e}.
-\newblock {{Markov} models of molecular kinetics: Generation and validation}.
-\newblock {\em J. Chem. Phys.}, 134:174105, 2011.
-
-\bibitem{A19-1}
-G.~R. Bowman, V.~S. Pande, and F.~No\'e, editors.
-\newblock {\em An Introduction to {{Markov}} State Models and Their Application
-  to Long Timescale Molecular Simulation}, volume 797 of {\em Advances in
-  Experimental Medicine and Biology}.
-\newblock Springer, 2014.
-
-\bibitem{A19-49}
-M.~Senne, B.~Trendelkamp-Schroer, A.~S. J.~S. Mey, Ch. Sch\"utte, and F.~No\'e.
-\newblock Emma - a software package for {{Markov}} model building and analysis.
-\newblock {\em J. Chem. Theory Comput.}, 8:2223--2238, 2012.
-
-\bibitem{MSMBuilder}
-Kyle~A Beauchamp, Gregory R~Bowman andThomas J~Lane, Lutz Maibaum, Imran~S
-  Haque, and Vijay~S Pande.
-\newblock {MSMBuilder2}: {M}odeling conformational dynamics at the picosecond
-  to millisecond scale.
-\newblock {\em J Chem Theor Comput}, 2011.
-
-\bibitem{schuette2011markov}
-C.~Sch{\"u}tte, F.~No{\'e}, J.~Lu, M.~Sarich, and E.~Vanden-Eijnden.
-\newblock {{Markov} State Models based on Milestoning}.
-\newblock {\em J. Chem. Phys.}, 134:204105, 2011.
-
-\bibitem{sarich2010approximation}
-Marco Sarich, Frank No{\'e}, and Christof Sch{\"u}tte.
-\newblock On the approximation quality of {Markov} state models.
-\newblock {\em Multiscale Modeling \& Simulation}, 8(4):1154--1177, 2010.
-
-\bibitem{Eigenvalues}
-N.~Djurdjevac, M.~Sarich, and Ch~Sch{\"u}tte.
-\newblock Estimating the eigenvalue error of {M}arkov state models.
-\newblock {\em Multiscale Modeling \& Simulation}, 10(1):61--81, 2012.
-
-\bibitem{PNAS09}
-F.~No\'{e}, C.~Sch\"utte, E.~Vanden-Eijnden, L.~Reich, and T.~R. Weikl.
-\newblock Constructing the full ensemble of folding pathways from short
-  off-equilibrium simulations.
-\newblock {\em Proc. Natl. Acad. Sci. USA}, 106:19011--19016, 2009.
-
-\bibitem{kohlhoff2014cloud}
-Kai~J Kohlhoff, Diwakar Shukla, Morgan Lawrenz, Gregory~R Bowman, David~E
-  Konerding, Dan Belov, Russ~B Altman, and Vijay~S Pande.
-\newblock Cloud-based simulations on google exacycle reveal ligand modulation
-  of gpcr activation pathways.
-\newblock {\em Nature chemistry}, 6(1):15--21, 2014.
-
-\bibitem{A19-39}
-B.~G. Keller, J.-H. Prinz, and F.~No\'e.
-\newblock {{Markov}} models and dynamical fingerprints: {U}nraveling the
-  complexity of molecular kinetics.
-\newblock {\em Chem. Phys.}, 396:92--107, 2012.
-
-\bibitem{PrinzKellerNoe_PCCP11_Perspective}
-Jan-Hendrik Prinz, Bettina~G. Keller, and Frank No{\'e}.
-\newblock Probing molecular kinetics with {{{Markov}}} models: Metastable
-  states, transition pathways and spectroscopic observables.
-\newblock {\em Phys. Chem. Chem. Phys.}, 13:16912--16927, 2011.
-
-\bibitem{pande2010everything}
-V.S. Pande, K.~Beauchamp, and G.R. Bowman.
-\newblock Everything you wanted to know about {Markov} state models but were
-  afraid to ask.
-\newblock {\em Methods}, 52(1):99--105, 2010.
-
-\bibitem{A19-29}
-M.~Sarich, Ralf Banisch, C.~Hartmann, and Ch. Sch\"utte.
-\newblock {{Markov}} state models for rare events in molecular dynamics.
-\newblock {\em Entropy (Special Issue)}, 16(1):258--286, December 2013.
-
-\bibitem{latorre2011structure}
-Juan~C Latorre, Philipp Metzner, Carsten Hartmann, and Christof Sch{\"u}tte.
-\newblock A structure-preserving numerical discretization of reversible
-  diffusions.
-\newblock {\em Commun. Math. Sci}, 9(4):1051--1072, 2011.
-
-\bibitem{floquet1883equations}
-G~Floquet.
-\newblock Sur les {\'e}quations diff{\'e}rentielles lin{\'e}aires {\`a}
-  coefficients p{\'e}riodiques.
-\newblock {\em Annales scientifiques de l'{\'E}cole Normale Sup{\'e}rieure},
-  12:47--82, 1883.
-
-\bibitem{A19-26}
-F.~No\'e, H.~Wu, J.-H. Prinz, and N.~Plattner.
-\newblock Projected and hidden {{Markov}} models for calculating kinetics and
-  metastable states of complex molecules.
-\newblock {\em J. Chem. Phys.}, 139:184114, 2013.
-
-\bibitem{BucheteHummer}
-Nicaolae~V. Buchete and Gerhard Hummer.
-\newblock Coarse master equations for peptide folding dynamics.
-\newblock {\em J. Phys. Chem. B}, 112:6057--6069, 2008.
-
-\bibitem{sarich2014utilizing}
-Marco Sarich and Christof Sch{\"u}tte.
-\newblock Utilizing hitting times for finding metastable sets in non-reversible
-  {Markov} chains.
-\newblock {\em submitted to the Journal of Computational Dynamics}, 2014.
-
-\bibitem{discreteTPT}
-P.~Metzner, Ch. Sch{\"u}tte, and E.~Vanden-Eijnden.
-\newblock Transition path theory for {M}arkov jump processes.
-\newblock {\em Multiscale Modeling and Simulation}, 7(3):1192--1219, 2009.
-
-\bibitem{djurdjevac2010markov}
-N.~Djurdjevac, M.~Sarich, and C.~Sch{\"u}tte.
-\newblock On {{Markov}} state models for metastable processes.
-\newblock In {\em Proceedings of the International Congress of Mathematicians},
-  volume 901, pages 3105--3131, 2010.
-
-\bibitem{chodera2007automatic}
-J.D. Chodera, N.~Singhal, V.S. Pande, K.A. Dill, and W.C. Swope.
-\newblock Automatic discovery of metastable states for the construction of
-  {Markov} models of macromolecular conformational dynamics.
-\newblock {\em J. Chem. Phys.}, 126:155101, 2007.
-
-\bibitem{foloppe2000all}
-Nicolas Foloppe and Alexander~D MacKerell~Jr.
-\newblock All-atom empirical force field for nucleic acids: I. parameter
-  optimization based on small molecule and condensed phase macromolecular
-  target data.
-\newblock {\em J. Comput. Chem.}, 21(2):86--104, 2000.
-
-\bibitem{jorgensen1983comparison}
-William~L Jorgensen, Jayaraman Chandrasekhar, Jeffry~D Madura, Roger~W Impey,
-  and Michael~L Klein.
-\newblock Comparison of simple potential functions for simulating liquid water.
-\newblock {\em J. Chem. Phys.}, 79(2):926--935, 1983.
-
-\bibitem{mackerell2004extending}
-Alexander~D MacKerell, Michael Feig, and Charles~L Brooks~III.
-\newblock Extending the treatment of backbone energetics in protein force
-  fields: Limitations of gas-phase quantum mechanics in reproducing protein
-  conformational distributions in molecular dynamics simulations.
-\newblock {\em J. Comput. Chem.}, 25(11):1400--1415, 2004.
-
-\bibitem{pronk2013gromacs}
-S.~Pronk, S.~P{\'a}ll, R.~Schulz, P.~Larsson, P.~Bjelkmar, R.~Apostolov, M.R.
-  Shirts, J.C. Smith, P.M. Kasson, D.~van~der Spoel, Hess B., and Lindahl E.
-\newblock Gromacs 4.5: a high-throughput and highly parallel open source
-  molecular simulation toolkit.
-\newblock {\em Bioinformatics}, pages 1--10, 2013.
-
-\bibitem{bjelkmar2010implementation}
-P\"{a}r Bjelkmar, Per Larsson, Michel~A Cuendet, Berk Hess, and Erik Lindahl.
-\newblock Implementation of the charmm force field in gromacs: Analysis of
-  protein stability effects from correction maps, virtual interaction sites,
-  and water models.
-\newblock {\em J. Chem. Theory Comput.}, 6(2):459--466, 2010.
-
-\bibitem{parrinello1981polymorphic}
-M.~Parrinello and A.~Rahman.
-\newblock Polymorphic transitions in single crystals: A new molecular dynamics
-  method.
-\newblock {\em J. Appl. Phys.}, 52:7182, 1981.
-
-\bibitem{darden1993pme}
-T.~Darden, D.~York, and L.~Pedersen.
-\newblock {Particle mesh Ewald: An $N \log (N)$ method for Ewald sums in large
-  systems}.
-\newblock {\em J. Chem. Phys.}, 98:10089, 1993.
-
-\bibitem{essmann1995spm}
-U.~Essmann, L.~Perera, M.L. Berkowitz, T.~Darden, H.~Lee, and L.G. Pedersen.
-\newblock {A smooth Particle Mesh Ewald method}.
-\newblock {\em J. Chem. Phys.}, 103(19):8577, 1995.
-
-\bibitem{wang2010optimizing}
-Han Wang, Florian Dommert, and Christian Holm.
-\newblock Optimizing working parameters of the smooth particle mesh ewald
-  algorithm in terms of accuracy and efficiency.
-\newblock {\em The Journal of chemical physics}, 133(3):034117, 2010.
-
-\bibitem{hess1997lincs}
-B.~Hess, H.~Bekker, H.J.C. Berendsen, and J.G.E.M. Fraaije.
-\newblock {LINCS: a linear constraint solver for molecular simulations}.
-\newblock {\em J. Comput. Chem.}, 18(12):1463--1472, 1997.
-
-\bibitem{miyamoto2004settle}
-S.~Miyamoto and P.A. Kollman.
-\newblock {SETTLE: an analytical version of the SHAKE and RATTLE algorithm for
-  rigid water models}.
-\newblock {\em J. Comput. Chem.}, 13(8):952--962, 2004.
-
-\bibitem{PCCAplus}
-P.~Deuflhard and M.~Weber.
-\newblock Robust {P}erron cluster analysis in conformation dynamics.
-\newblock {\em Linear Algebra and its Applications}, 161(184), 2005.
-\newblock 398 Special issue on matrices and mathematical biology.
-
-\bibitem{PrinzHeldSmithNoe_Committorprep}
-Jan-Hendrik Prinz, Martin Held, Jeremy~C. Smith, and Frank No{\'e}.
-\newblock Efficient computation of committor probabilities and transition state
-  ensembles.
-\newblock {\em SIAM Multiscale Model. Simul.}, 9:545, 2011.
-
-\bibitem{wang2013linear}
-Han Wang, Carsten Hartmann, and Christof Sch{\"u}tte.
-\newblock Linear response theory and optimal control for a molecular system
-  under non-equilibrium conditions.
-\newblock {\em Molecular Physics}, 111(22-23):3555--3564, 2013.
-
-\bibitem{schutte2014markov}
-Christof Sch{\"u}tte, Adam Nielsen, and Marcus Weber.
-\newblock Markov state models and molecular alchemy.
-\newblock {\em Molecular Physics}, ahead-of-print, 2014.
-
-\bibitem{seifert2012stochastic}
-Udo Seifert.
-\newblock Stochastic thermodynamics, fluctuation theorems and molecular
-  machines.
-\newblock {\em Reports on Progress in Physics}, 75(12):126001, 2012.
-
-\end{thebibliography}
-% \bibliography{ref}{}
-% % \bibliographystyle{unsrt}
+\bibliography{ref}
 

### 2015-02-10 writedown/period.noneq.msm/submit.jctc.reply/reply.tex
backup before resubmit

@@
 \textit{Journal of Chemical Theory and Computation}.
-We gratefuly acknowledge the reviewers for the positive reports, and for
+We gratefully acknowledge the reviewers for the positive reports, and for
 their insight and suggestions, which helped us improving the quality
@@
 
-We revised the manuscript repsectively and reworked the English completely.
+We revised the manuscript respectively and reworked the English completely.
 To help the referees spot the major changes in
 the manuscript, we have submitted a separate file (highlight.pdf) with
-all changes highlighted in red.
+major changes highlighted in red.
 
@@
 \section*{Reply to Referee 1}
+
+\textit{ First, the authors need to shore up some of the English
+  language, which is currently not up-to-par for publication in this
+  journal.  The required edits are somewhat extensive, but manageable.}\\
+
+We have reworked the English completely.\\
 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.6\textwidth]{hitting.eps}
+  \caption{Schematic plot of comparison between a continuous and time-discretized trajectories in hitting a core set.}
+  \label{fig:tmp1}
+\end{figure}
+
 \textit{ Of course, alanine dipeptide is a toy system.  And, as the
@@
 % \end{minipage}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=0.6\textwidth]{hitting.eps}
-  \caption{Schematic plot of comparison between a continuous and time-discretized trajectories in hitting a core set.}
-  \label{fig:tmp1}
-\end{figure}
 
@@
 partition MSM with different lag-times, and thus does not apply to
-milestone MSMs. See Schütte et al. (2011), Markov State Models Based on Milestoning, J. Chem. Phys., 134 (20). 204105 (2011) for more details.
+milestone MSMs. See Sch\"utte et al., Markov State Models Based on Milestoning, J.~Chem.~Phys., 134(20), 204105 (2011) for more details.
 

### 2015-02-10 writedown/period.noneq.msm/coverletter/letter-jctc.tex
backup

@@
 (MSM) for the non-equilibrium systems under a periodic external
-driving.  The MSM reproduces the essential long timescale
-conformational dynamics of the original system, and at the same time
+driving.  The MSM reproduces the long-timescale
+conformational dynamics of the non-equilibrium system, and at the same time
 it does not require the ergodicity of each single molecular
@@
 \begin{itemize}\itemsep -1pt
-\item Vijay Pande, Stanford University, pande@stanford.edu
-\item John Chodera, Memorial Sloan Kettering Cancer Center, choderaj@mskcc.org
-\item Giovanni Ciccotti,  University of Rome La Sapienza, Giovanni.Ciccotti@roma1.infn.it
+\item Vijay Pande, Stanford University
+  % , pande@stanford.edu
+\item John Chodera, Memorial Sloan Kettering Cancer Center
+  % , choderaj@mskcc.org
+\item Giovanni Ciccotti,  University of Rome La Sapienza
+  % , Giovanni.Ciccotti@roma1.infn.it
 \end{itemize}
